### 2018-10-16 clustering_infinite_model.tex
Initial ShareLaTeX Import

\section{Clustering in $G_{\mathcal{P}}(\alpha, \nu)$}\label{sec:asymptotics_average_clustering_ast_P}

In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\infty$ and $c_{\infty}(k)$, respectively.

We shall first recall some necessary notations for computing the local clustering function in $G_{\Pcal}$ and introduce some new ones.

Recall that for $p\in \R \times \R_+$,
\[
	B(p) = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\}.
\]

Let $T_{\Pcal}(k)$ denote the number of triangles connected to nodes of degree $k$ in $G_{\Pcal}(\alpha, \nu)$, i.e.
\[
	T_{\Pcal}(k) = \sum_{p \in \Pcal} \ind{D_\Pcal(p) = k} T(p) = \sum_{p \in \Pcal} \ind{D_\Pcal(p) = k} \sum_{p_1, p_2 \in 2^\Pcal} T(p,p_1,p_2),
\]
where $2^{\Pcal}$ is the set of distinct pairs in $\Pcal \times \Pcal$ and
\[
	T(p,p_1,p_2) = \ind{p_1 \in B_\Pcal(p)} \ind{p_2 \in B_\Pcal(p)} \ind{p_1 \in B_\Pcal(p_2)},
\]
is the indicator that $\{p, p_1, p_2\}$ form a triangle. Then the local clustering function is given by
\begin{equation}\label{eq:def_local_clustering_P}
	c_{\Pcal}(k) = \begin{cases} 
		\frac{T_{\Pcal}(k)}{\binom{k}{2} N_\Pcal(k)} &\mbox{if } N_\Pcal(k) \ge 1\\
		0 &\mbox{else,}
		\end{cases}
\end{equation}
and the adjusted local clustering by
\begin{equation}\label{eq:def_local_clustering_ast_P}
	c_{\Pcal}^\ast(k) = \begin{cases} 
		\frac{T_{\Pcal}(k)}{\binom{k}{2} \Exp{N_\Pcal(k)}} &\mbox{if } N_\Pcal(k) \ge 1\\
		0 &\mbox{else,}
		\end{cases}.
\end{equation}

To analyze the local clustering we define the conditional expected number of triangles of a vertex $p$ with degree $k$ as
\[
	\Delta_{\Pcal}(p,k) = \CExp{\sum_{(p_1, p_2) \in 2^\Pcal} T_\Pcal(p, p_1, p_2)}{D_\Pcal(p) = k}.
\]
To compute this expression, let $Z_{1}, Z_{2}$ be two independent random variables on $B_{\Pcal}(p)$, with (marginal) probability measures $\eta_{p} = \frac{\mu|_{B_{\Pcal}(p)}}{\mu(B_{\Pcal}(p))}$. Then we define,
\begin{equation}\label{eq:def_delta_p}
	\Delta_{\Pcal}(p) = \Prob{ Z_{1} \in \mathcal{B}_{\Pcal}(Z_{2})} %Z_{1} \in \mathcal{B}_{\Pcal}(p), Z_{2} \in \mathcal{B}_{\Pcal}(p),
\end{equation}
as the probability that two random neighbors of a point $p \in \mathcal{P}$ are adjacent (note that $\pr = \pr_{\mathcal{P},p}$ denotes the joint probability measure of $Z_1$ and $Z_2$).

We shall often abuse notation and write $\Delta_\Pcal(y)$ to denote $\Delta_\Pcal((0,y))$. %Observe that $\Delta_\Pcal(p)$ is the probability that two random neighbors of $p$ are connected.
Next we note that conditioned on the Poisson process $\Pcal$ having $k$ points in $\mathcal{B}_{\Pcal}(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$, each with probability measure $\eta_{p}$ and hence
\[
	\Delta_{\Pcal}(p,k) = \binom{k}{2} \Delta_\Pcal(p).
\]

In addition, since $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}}$, with $\xi_{\alpha,\nu} = \frac{4\alpha\BL{\nu}}{(2\alpha - 1)\pi}$, and
\[
	\Delta_{\Pcal}(p) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{p}(x_1,y_1)\eta_{p}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
\]
we have that
\begin{equation}\label{eq:relation_T_vs_Delta_P}
	\Exp{T_\Pcal(p)} = \xi_{\alpha,\nu}^2 \frac{e^{y}}{2} \Delta_\Pcal(p).
\end{equation}

\begin{remark}[Notations for the finite graph $G_{\Pcal, n}(\alpha,\nu)$]\label{rmk:notations_clustering_P_n}
For the finite graph $G_{\Pcal,n}(\alpha, \nu)$ we will use notations similar to those for $G_{\Pcal}(\alpha, \nu)$ where we simply introduce a subscript $n$. For example, 
\[
	\Delta_{\Pcal,n}(p) = \pr_{\mathcal{P},p}( Z_{1,n} \in \BallPo{Z_{2,n}}),
\]
%Z_{1,n} \in \BallPo{p}, Z_{2,n} \in \BallPo{p},
where $Z_{1,n}$ and $Z_{2,n}$ are two independent random variables with probability measure \\
$\eta_{p,n}$.
\end{remark}

%and define $\epsilon(p_1,p_2)$ to be the indicator that $p_1$ and $p_2$ are neighbors in $G_{\Pcal}(\alpha,\nu)$, i.e.,
%\[
%	\epsilon(p_1,p_2) = \begin{cases}
%		1 &\mbox{if } p_1 \in B(p_2)\\
%		0 &\mbox{else.}
%	\end{cases}
%\]
%With these definition we then write, 
%\[
%	T_\Pcal(p_1,p_2,p_3) = \epsilon_n(p_1,p_2) \epsilon_n(p_2,p_3) \epsilon_n(p_3,p_1),
%\]
%to denote the indicator that the tripple $(p_1, p_2, p_3)$ forms a triangle in $G_\Pcal(\alpha,\nu)$ and the triangle counting function as
%\begin{equation}
%	T_{\Pcal}(p) = \sum_{p_1, p_2 \in \Pcal} 
%		\hspace{-5pt} T_\Pcal(p,p_1,p_2).
%\end{equation}
%
%The local clustering function then is
%\begin{equation}\label{eq:def_local_clustering_P}
%	c_{\Pcal}(k) = \begin{cases} 
%		\frac{1}{N_\Pcal(k)}\sum_{p \in \Pcal} \ind{D_\Pcal(p) = k} \frac{T_{\Pcal}(k)}{\binom{k}{2}} &\mbox{if } N_k \ge 1\\
%		0 &\mbox{else,}
%		\end{cases}
%\end{equation}
%and similarly for $c_{\Pcal}^\ast(k)$.
%
%To analyze the local clustering we define the conditional expectation of triangles of a vertex $p$ with degree $k$ as
%\[
%	\Delta_{\Pcal}(p,k) = \CExp{\sum_{(p_1, p_2) \in \Pcal} T_\Pcal(p, p_1, p_2)}{p, D_\Pcal(p) = k}.
%\]
%To compute this expression, let $Z_{1}, Z_{2}$ be two independent random variables on $B_{\Pcal}(p)$, with probability measure $\eta_{p} = \frac{\mu|_{B_{\Pcal}(p)}}{\mu(B_{\Pcal}(p))}$. Then we define,
%\begin{equation}\label{eq:def_delta_p}
%	\Delta_{\Pcal}(p) = \CProb{Z_{1} \in B_{\Pcal}(p), Z_{2} \in B_{\Pcal}(p), Z_{1} \in B_{\Pcal}(Z_{2})}{p}
%\end{equation}
%We shall often abuse notation and write $\Delta_\Pcal(y)$ to denote $\Delta_\Pcal((0,y))$. Observe that $\Delta_\Pcal(p)$ is the probability that two random neighbors of $p$ are connected. Next we note that conditioned on the Poisson process $\Pcal$ having $k$ points in $B_{\Pcal}(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$ with probability $\eta_{p}$ and hence
%\[
%	\Delta_{\Pcal}(p,k) = \binom{k}{2} \Delta_\Pcal(p).
%\]
%
%\begin{remark}[Notations for the finite graph $G_{\Pcal, n}(\alpha,\nu)$]\label{rmk:notations_clustering_P_n}
%For the finite graph $G_{\Pcal,n}(\alpha, \nu)$ we will use notations similar to those for $G_{\Pcal}(\alpha, \nu)$ where we simply introduce a subscript $n$. For example, 
%\[
%	\Delta_{\Pcal,n}(p) = \CProb{Z_{1,n} \in \BallPo{p}, Z_{2,n} \in \BallPo{p}, Z_{1,n} \in \BallPo{Z_{2,n}}}{p},
%\]
%where $Z_{1,n}$ and $Z_{2,n}$ are two independent random variables with probability measure \\
%$\eta_{p,n} = \mu_n|_{\BallPo{p}}/\mu_n(\BallPo{p})$.
%\end{remark}

We will start with some preliminary results on the degrees in $G_\Pcal(\alpha, \nu)$. The proof of Theorem \ref{thm:asymptotics_average_clustering_P} can be found in Section \ref{ssec:asymptotics_local_clustering_P}. The key ingredient for the proof is a result concerning the asymptotic behavior of $\Delta_\Pcal(y)$ (Proposition \ref{prop:asymptotics_Delta_y_P}) whose proof can be found in Section \ref{ssec:asymptotics_Delta_y_P}.

\subsection{Degree distribution in $G_\Pcal(\alpha, \nu)$}

Before we analyze local clustering in the infinite limit model, we first establish some results for its degree distribution. We define the probability distribution for the degree of node $p = (x,y)$ as
\begin{equation}
	\rho_{p}(k) = \Prob{D_\Pcal(p) = k} = \Prob{\Po(\mu_{\alpha,\nu}(\BallPo{p})) = k},
\end{equation}
where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Recall from equation \eqref{eq:mu_B_y_P} that
\[
	\mu_{\alpha,\nu}(B(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}},
\]
only depends on the $y$-coordinate of $p$. Therefore, we will often write $\rho_y(k)$ instead of $\rho_{p}(k)$.

Using the above equation and the transformation of variables $z = \xi_{\alpha,\nu}e^{\frac{y}{2}}$, we compute
\begin{align*}
	\int_0^\infty \rho(y,k) e^{-\alpha y} \, dy 
    &= \frac{1}{\Gamma(k+1)} \int_0^\infty \left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^k 
    	e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}} e^{-\alpha y} \, dy\\
    &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_0^\infty 
    	\left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}}
        \, dy\\
    &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_{\xi_{\alpha,\nu}}^{\infty} 
    	z^{k-2\alpha} e^{-z} \, dz\\
    &= (\xi_{\alpha,\nu})^{2\alpha}\frac{\Gamma(k-2\alpha)}{\Gamma(k+1)}
    	\left(1 - \frac{\gamma(k-2\alpha, \xi_{\alpha,\nu})}{\Gamma(k - 2\alpha)}\right),
        \numberthis \label{eq:degree_distribution_P}
\end{align*}
where $\Gamma$ denotes the Gamma-function and $\gamma$ the incomplete Gamma-function.

Thus we deduce that, as $k \to \infty$,
\begin{equation}\label{eq:degree_distribution_P_asymptotics}
	\Prob{D_\Pcal = k} = \int_0^\infty \rho_{y}(k) e^{-\alpha y} \, dy \sim (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}.
\end{equation}

By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$,
\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho_y(k) e^{-\alpha y} \, dy
    = \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} \frac{\Gamma(k - 2(\beta + \alpha))}{\Gamma(k+1)}
    	\left(1 - \frac{\gamma(k - 2(\beta + \alpha), \xi_{\alpha,\nu})}{\Gamma(k - 2(\beta + \alpha))}\right).
\end{equation}

\subsection{Asymptotic behavior of $c_\infty(k)$}\label{ssec:asymptotics_local_clustering_P}

%\begin{lemma}\label{lem:expectation_clustering_P}
%Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then
%\[
%	\Exp{c_{\Pcal}^\ast(k)} = \frac{\int_0^{\infty} \Delta_{\Pcal}(y) \, 
%	\rho_{y}(k) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) 
%	e^{-\alpha y} \, dy}.
%\]
%\end{lemma}
%
%\begin{proof}
%By the Palm-Mecke formula, we have
%\begin{align*}
%	\Exp{c_{\Pcal}^\ast(k)} &= \frac{1}{\Exp{N_\Pcal(k)}}
%		\int_0^{\infty} \int_{-\infty}^{\infty} \Exp{\frac{\ind{D_{\Pcal}(p) = k}}{\binom{k}{2}} \sum_{(p_1, p_2) \in \Pcal} T(p,p_1,p_2)} f_{\alpha,\nu}(x,y) \, dx \, dy\\
%	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} \int_{-\infty}^{\infty} \binom{k}{2}^{-1}
%		\Delta_{\Pcal}(p,k)\CProb{D_\Pcal(p) = k}{p} f_{\alpha,\nu}(x,y) \, dx \, dy.
%\end{align*}
%Conditioned on the Poisson process $\Pcal$ having $k$ points in $B(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$ with probability  distribution $\eta_{p} = \frac{\mu|_{B(p)}}{\mu(B(p))}$. Therefore we have
%\[
%	\Delta_{\Pcal}(p,k) = \binom{k}{2} T_\Pcal(p),
%\]
%and hence, since the entire expression inside the integral does not depend on $x$,
%\begin{align*}
%	\Exp{c_{\Gamma, n}^\ast(k)} 
%	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} \Delta_{\Pcal}(y) \rho_{\mu, y}(k) e^{-\alpha y} \, dy.
%\end{align*}
%Finally, we note that
%\begin{align*}
%	\Exp{N_\Pcal(k)} &= \Exp{\sum_{p \in \Pcal} \ind{D_\Pcal(p) = k}}
%	= \int_0^{\infty}\int_{-\infty}^\infty \rho_{\mu, p}(k) f_{\alpha,\nu}(x,y) \, dx \, dy
%	= \int_0^{\infty} \rho_{\mu, y}(k) e^{-\alpha y} \, dy
%\end{align*}
%which completes the proof.
%\end{proof}

Recall that
\[
	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) e^{-\alpha y} \dd y}.
\]
The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
\[
	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \, \rho(y,k) e^{-\alpha y} \, dy,
\]
and in particular the function $\Delta_\Pcal(y)$. The following result establishes the asymptotic behavior of the latter.

\begin{proposition}[Asymptotic behavior of $\Delta_\Pcal(y)$]\label{prop:asymptotics_Delta_y_P}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}. Then there are three, eventually decreasing, functions $\varepsilon_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
\[
	\lim_{y \to \infty} \varepsilon_i(y) = 0, 
\]
such that 
\begin{enumerate}
\item for $\frac{1}{2} < \alpha < \frac{3}{4}$,
\[
	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varepsilon_1(y)),
\]
\item for $\alpha = \frac{3}{4}$,
\[
	\Delta_\Pcal(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varepsilon_2(y)),
\]
\item and for $\alpha > \frac{3}{4}$,
\[
	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varepsilon_3(y)).
\]
\end{enumerate}
\end{proposition}

The proof of this proposition is involved and technical. We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.

\begin{proof}[Proof of Theorem \ref{thm:asymptotics_average_clustering_P}]

\PvdH{Include concentration argument in this proof.}
We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$. The proofs for the other two cases are similar. Let $\varepsilon_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
\[
	\xi_1(k_n) = \int_0^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy
\]
Then we have that
\[
	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho_{y}(k_n) e^{-\alpha y} \, dy
	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy + \xi_1(k_n).
\]

Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields
\[
	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy 
    = 2\xi^{6\alpha - 2} \frac{\Gamma(k_n-(6\alpha-2)}{\Gamma(k_n+1)}
	\left(1 - \frac{\gamma(k_n - (6\alpha - 2), \xi)}{\Gamma(k_n - (6\alpha-2))}\right).
\]
Since 
\[
	\lim_{n \to \infty} \frac{\gamma(k_n - 2\alpha, \xi)}{\Gamma(k_n - 2\alpha)} = 0,
\]
and $\Gamma(k_n - t)/\Gamma(k_n + 1) \sim k_n^{-(t+1)}$ as $n \to \infty$,
it follows that, as $n \to \infty$,
\begin{align*}
	c_\infty(k_n) \sim C_\alpha \xi^{4\alpha - 2} \frac{k_n^{-(6\alpha - 1)}}{k_n^{-(2\alpha - 1)}}
	+ \frac{\xi^{-2\alpha}\eta_1(k_n)}{2 k_n^{-(2\alpha - 1)}}
	\sim C_\alpha \xi^{4\alpha - 2} k_n^{-4\alpha + 2} 
    + \frac{\xi^{-2\alpha}\eta_1(k_n)}{2 k_n^{-(2\alpha - 1)}}.
\end{align*}
Hence, to prove the result it is enough to show that
\[
	\lim_{n \to \infty} k_n^{6\alpha - 1}\xi_1(k_n) = 0.
\]
For this let $0 < \varepsilon < 1$, define $a_n = 2\log((1-\varepsilon)k_n)$ and split the integral into two pieces
\begin{align*}
	\xi_1(k_n) &= \int_0^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
	&= \int_0^{a_n} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
	&\hspace{10pt}+ \int_{a_n}^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho_{y}(k_n) e^{-\alpha y} \, dy.
\end{align*} 
For the first integral we use that
\[
	k_n^{6\alpha - 1}\rho_{a_n}(k_n) = O\left(\frac{k_n^{6\alpha - 1 + (1-\varepsilon)k_n}}{k_n!} e^{-(1-\varepsilon)k_n}\right) = o(1),
\]
so that
\begin{align*}
	&\hspace{-30pt}\lim_{n \to \infty} k_n^{6\alpha - 1} \int_0^{a_n} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho_{y}(k_n) e^{-\alpha y} \, dy\\
	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a_n} \varepsilon_1(y)\right) k_n^{6\alpha - 1} 
    	\rho_{a_n}(k_n) \int_0^\infty e^{-\alpha y} \, dy = 0.
\end{align*}
For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
\[
	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy \sim k_n^{-(6\alpha - 1)}.
\] 
Therefore, using that $\varepsilon_1(y)$ is eventually decreasing and $\lim_{n \to \infty} \varepsilon_1(a_n) = 0$, we obtain
\begin{align*}
	&\hspace{-30pt}\lim_{n \to \infty} k_n^{6\alpha - 1} \int_{a_n}^{\infty} \varepsilon_1(y) 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
	&\le \lim_{n \to \infty} \varepsilon_1(a_n) k_n^{6\alpha - 1} \int_0^\infty 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy = 0,
\end{align*}
which finishes the proof.
\end{proof}

\subsection{Analyzing $\Delta_\Pcal(y)$, an overview.}\label{ssec:asymptotics_Delta_y_P}

We derive the following complete asymptotic expansion of $\Delta_{\Pcal}(y)$, from which then the leading terms can be extracted. The following result proves Proposition \ref{prop:asymptotics_Delta_y_P}, resp. implies it as a corollary after extracting the leading terms.
\begin{proposition}\label{prop:full_expression_delta_P}
\begin{enumerate}
	\item If $\alpha \not = 1$, then
	\begin{align*}
	 \Delta_{\Pcal}(y) &=-\frac{1}{8 (\alpha - 1) \alpha} + \frac{(\alpha - 1/2) e^{-\frac{1}{2}y}}{\alpha - 1} - \frac{(\alpha - 1/2)^2 e^{-y}}{
		4 (\alpha - 1)^2} \\
	&+ 
	(e^{-\frac{1}{2}y})^{4\alpha -2} \left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} + \frac{(\alpha - 
		1/2 ) B^-(1/2; 1 + 2 \alpha, 
		-2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right) \\
	&+ \frac{(1 - 
		e^{-\frac{1}{2}y})^{2 \alpha}}{8 (\alpha - 1) \alpha} - \frac{  
		(e^{-\frac{1}{2}y})^{4 \alpha - 2} B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
	\end{align*}
	\item If $\alpha = 1$, then
	\begin{align*}
	&\Delta_{\Pcal}(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
e^{-y}  + 
\frac{1}{2}e^{-y}\Li_2(e^{-y})
	\end{align*}
	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
\end{enumerate}
\end{proposition}

%We note that $\Delta_{\Pcal}(y_0)$ is the probability that $(x_1,y_1), (x_2,y_2)$ are neighbours, given that they are neighbours of $(0,y_0)$. (Here we think of $y_0$ as being fixed during the chance experiment and $(x_1,y_1), (x_2,y_2)$ chosen randomly.)

%The computation can be outlined as follows: First of all, we apply a change of variable $z_i = e^{-y_i/2}$, $i=0,1,2$. Then we find an expression for $P(y_0(z_0),y_1(z_1),y_2(z_2))$ depending on several cases in the input variables. The two innermost integrals, which we are going to denote by $P(y_0)$, are computed by partitioning the integration domain into four corresponding subdomains.

To derive this result, recall (see~\eqref{eq:def_delta_p}) that $\Delta_{\Pcal}(y)$ is the probability that $Z_1 \in \BallPo{Z_2}$, where $Z_1, Z_2$ are two independent random variables on $\BallPo{0,y}$ with density 
\[
	\eta_{y}(y^\prime,x^\prime) = \frac{f_{\alpha,\nu}(x^\prime, y^\prime)\ind{(x^\prime, y^\prime \in B_{\Pcal}(0,y)}}{\mu(B_{\Pcal}(0,y))}.
\]

For notational convenience we will switch to using $y_0$ instead of $y$. Note that the random variables $Z_i = (x_i,y_i)$, for $i = 1,2$, correspond to first sampling $y_i$ according to the density
\[
	g(y) := \left(\alpha -\frac{1}{2}\right) e^{-(\alpha-\frac{1}{2})y_1}
\] 
and then sampling $x_i$ uniformly in $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$. With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ form a triangle where $x_1$ and $x_2$ are uniform random variables in, respectively, $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.

Then we have that
\begin{align}\label{eq:delta_P}
 \Delta_{\Pcal}(y_0) = (\alpha-1/2)^2 \int_0^\infty \int_0^\infty P(y_0, y_1, y_2) e^{-(\alpha-1/2)(y_1+y_2)} 
 \dd y_2 \dd y_1.
\end{align}

\subsection{Triangle probability for nodes at given heights}
We proceed by first computing $P(y_0,y_1,y_2)$. To compute the integral~\ref{eq:delta_P} it will be convenient to use the change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$. We will write $y_i(z_i)$ to stress the dependence between $y_i$ and $z_i$. The following result completely characterizes $P(y_0,y_1,y_2)$.

\begin{lemma}\label{lem:triangle_prob_y_coordinates}
\begin{align*}
P(y_0(z_0),y_1(z_1),y_2(z_2)) = \begin{cases}
	1 &\text{ if } z_0 \geq z_1+z_2, z_0 > z_1 > z_2, \\
	1-G(z_0,z_1,z_2) &\text{ if } z_0 < z_1+z_2, z_0 > z_1 > z_2, \\
	\frac{z_0}{z_1} &\text{ if } z_1 \geq z_0+z_2, z_1 > \max(z_0,z_2), \\
	\frac{z_0}{z_1}\left(1-G(z_1,z_0,z_2)\right) &\text{ if } z_1 < z_0+z_2, z_1 > \max(z_0,z_2),
\end{cases}
\end{align*}
where 
\begin{align*}
G(a,b,c) = \frac{1}{4}
\left( b^{-1}c + bc^{-1} + a^2b^{-1}c^{-1} + 2 - 2ab^{-1}-2ac^{-1}\right)
\end{align*}
\end{lemma}

%\begin{align*}
%G'(z_0,z_1,z_2) = \frac14 ( z_1^{-1} z_2 +z_0^2 z_1^{-1} z_2^{-1} + z_1 z_2^{-1} + 2z_0z_1^{-1} - 2 - 2z_0z_2^{-1} )
%\end{align*}

We split the proof of this lemma into a couple of smaller pieces. We begin with the following lemma.
\begin{lemma}\label{lem:ordered}
Let $z_i = e^{-y_i/2}$, $i=0,1,2$. If $y_0<y_1<y_2$ (or equivalently $z_0 > z_1 > z_2$), then
\begin{align*}
P(y_0(z_0),y_1(z_1),y_2(z_2)) = \begin{cases}
1, &\text{ if } z_0 \geq z_1+z_2,  \\
1-G(z_0,z_1,z_2), &\text{ if } z_0 < z_1+z_2
\end{cases}
\end{align*}
\end{lemma}

\begin{figure}
\centering
\begin{tikzpicture}[scale=0.9]

	\draw node at (0,3.5) {\begin{minipage}{5cm}
		\begin{center}
		\begin{align*}
			&\text{I) } e^{\frac{y_0 + y_1}{2}} < e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}} \text{ or}\\
			&\text{II) } 0 \le x_1 \le e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}}
		\end{align*}
		\end{center}
	\end{minipage}};

	\draw[thick,red] (-2,1) -- (2,1);
	\draw[thick] (-2,0.8) -- (-2,1.2);
	\draw[thick] (2,0.8) -- (2,1.2);
	\draw node at (-2,1.5) {$-e^{\frac{y_0 + y_2}{2}}$};
	\draw node at (2,1.5) {$e^{\frac{y_0 + y_2}{2}}$};

	\draw[thick] (-3,0) -- (3,0);
	\draw[thick,red] (-2,0) -- (2,0);
	\draw[thick,red] (-2,-0.2) -- (-2,0.2);
	\draw[thick,red] (2,-0.2) -- (2,0.2);
	\draw[thick] (-3,-0.2) -- (-3,0.2);
	\draw[thick] (3,-0.2) -- (3,0.2);
	\draw node at (-3,-0.5) {$x_1 - e^{\frac{y_1 + y_2}{2}}$};
	\draw node at (3,-0.5) {$x_1 + e^{\frac{y_1 + y_2}{2}}$};

\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]

	\draw node at (0,3.5) {\begin{minipage}{5cm}
		\begin{center}
			$x_1 > e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}}$
		\end{center}
	\end{minipage}};

	\draw[thick] (-2,1) -- (2,1);
	\draw[thick,red] (-1.5,1) -- (2,1);
	\draw[thick] (-2,0.8) -- (-2,1.2);
	\draw[thick] (2,0.8) -- (2,1.2);
	\draw[thick,red] (-1.5,0.8) -- (-1.5,1.2);
	\draw node at (-2,1.5) {$-e^{\frac{y_0 + y_2}{2}}$};
	\draw node at (2,1.5) {$e^{\frac{y_0 + y_2}{2}}$};

	\draw[thick] (-1.5,0) -- (3,0);
	\draw[thick,red] (-1.5,0) -- (2,0);
	\draw[thick,red] (2,-0.2) -- (2,0.2);
	\draw[thick] (-1.5,-0.2) -- (-1.5,0.2);
	\draw[thick] (3,-0.2) -- (3,0.2);
	\draw node at (-1.5,-0.5) {$x_1 - e^{\frac{y_1 + y_2}{2}}$};
	\draw node at (3,-0.5) {$x_1 + e^{\frac{y_1 + y_2}{2}}$};

\end{tikzpicture}
\caption{Situation for the intersections of the connection intervals considered in Lemma~\ref{lem:ordered}, with $y_0 < y_1 <y_2$ and $0 \le x_1 \le e^{(y_0 + y_1)/2}$. The regime for $x_2$ in which case a triangle is formed is colored in red on both intervals. \PvdH{Maybe show the full connection balls.}}
\label{fig:triangle_prob_lemma}
\end{figure}

\begin{proof}
%pim pass1: $P(y_0,y_1,y_2)$ is the probability that $(x_1,y_1)$ and $(x_2,y_2)$ (which are given by a Poisson process in the upper half-plane) are neighbours of each other, given that they are neighbours of $(0,y_0)$ (see figure \ref{fig:triangle_prob_lemma}). By the properties of the Poisson process and our connection rule (which defines the neighourhood area of $(0,y_0)$ in the upper half-plane), given $y_0, y_1, y_2$ we have that $x_i$ is chosen u.a.r.~from $[-e^{y_0/2+y_i/2}, +e^{y_0/2+y_i/2}]$ for $i=1,2$.
Since the Poisson Point Process is translation invariant in the $x$-coordinate we can, without loss of generality, take $x_0 = 0$. By definition of the connection rule $P(y_0,y_1,y_2)$ is the probability that $|x_2-x_1| \leq  e^{(y_1+y_2)/2}$ (see figure \ref{fig:triangle_prob_lemma}). Consider $y_0, y_1, y_2$ and $x_1$ fixed. Then we are interested in computing the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y+2)/2},x_1+e^{(y_1+y_2)/2}]$ (given by the bottom interval in the Figure~\ref{fig:triangle_prob_lemma}), as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$ (given by the top interval in the Figure~\ref{fig:triangle_prob_lemma}).

%, i.e. the desired probability can be written as
%\[ 
%\frac{
%\Ee_{x_1} \text{length}( [x_1-e^{(y_1+y_2)/2}, x_1+e^{(y_1+y_2)/2}] \cap [-e^{(y_0+y_2)/2}, e^{(y_0+y_2)/2}] )
%}{
%2 e^{(y_0+y_2)/2}
%} \]
%
%\noindent

By symmetry, without loss of generality we can consider $x_1$ uniformly at random from $[0,e^{y_0/2+y_1/2}]$. 
%The probability will be the same.Let us assume for the moment that $y_0 < y_1 < y_2$. 
Since $y_0 < y_1 < y_2$ we have that $e^{(y_1+y_2)/2} > e^{(y_0+y_2)/2}$ and so, when $x_1 \geq 0$, the ``right half'' of the interval $[-e^{(y_0+y_2)/2}, e^{(y_0+y_2)/2}]$ is always covered by the interval $[x_1-e^{(y_1+y_2)/2}, x_1+e^{(y_1+y_2)/2}]$.
If $e^{(y_1+y_2)/2} - e^{(y_0+y_1)/2} \geq e^{(y_0+y_2)/2}$ then the ``left half'' is always covered as well.
In other words:
\[
	e^{(y_1+y_2)/2} - e^{(y_0+y_1)/2} \geq e^{(y_0+y_2)/2} \Rightarrow P(y_0,y_1,y_2) = 1.
\]

Now consider the case where $e^{(y_1+y_2)/2} - e^{(y_0+y_1)/2} < e^{(y_0+y_2)/2}$. Then, if $x_1 \in [0, e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2}]$ the whole interval $[-e^{(y_0+y_2)/2}, e^{(y_0+y_2)/2}]$ is still covered so that $p_0, p_1$ and $p_2$ form a triangle. If, on the other hand $e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2} < x_1 \leq e^{(y_0+y_1)/2}$ then
the probability that $|x_2-x_1| \leq e^{(y_1+y_2)/2}$ equals
\[ 
	1 - \frac{x_1 - (e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2)}) }{ 2e^{(y_0+y_2)/2} }. 
\]

Hence, when $e^{(y_1+y_2)/2} - e^{(y_0+y_1)/2} < e^{(y_0+y_2)/2}$ we have
\begin{align*}
	P(y_0,y_1,y_2) &= \frac{e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2} }{ e^{(y_0+y_1)/2} }  \\
	&\hspace{10pt}+ \int_{ e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2} }^{ e^{(y_0+y_1)/2} } 
	    \left(1 - \frac{x_1 - (e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2)}) }{ 2e^{(y_0+y_2)/2} }\right)
	    \cdot \frac{1}{e^{(y_0+y_1)/2}} \dd x_1 \\
	&= 1 - \frac{1}{2e^{y_0+y_1/2+y_2/2} } \int_0^{ e^{(y_0+y_1)/2}+e^{(y_0+y_2)/2}-e^{(y_1+y_2)/2} } x_1 \dd x_1 \\
	&= 1 - \frac{ \left( e^{(y_0+y_1)/2}+e^{(y_0+y_2)/2}-e^{(y_1+y_2)/2} \right)^2 }{ 4 e^{y_0+y_1/2+y_2/2} },
\end{align*}

At this point it is convenient to rewrite everything in terms of $z_i := e^{-y_i/2}$.
Note that $y_0 < y_1 < y_2$ if and only if $z_0 > z_1 > z_2$ while the condition $e^{(y_1+y_2)/2} - e^{(y_0+y_1)/2} < e^{(y_0+y_2)/2}$ becomes
\[ e^{(y_1+y_2)/2} - e^{(y_0+y_1)/2} < e^{(y_0+y_2)/2} \Leftrightarrow 
z_1^{-1} z_2^{-1} < z_0^{-1} z_1^{-1} + z_0^{-1}z_2^{-1} 
\Leftrightarrow
z_0 < z_1+z_2. 
\]

We now conclude that
\[
	P(y_0(z_0), y_1(z_1), y_2(z_2)) = 1 \quad \text{if} \quad z_0 > z_1 > z_2 \text{ and } z_0 \geq z_1 + z_2
\]
while for $z_0 > z_1 > z_2$ and $z_0 < z_1 + z_2$
\begin{align*}
	P(y_0, y_1, y_2) 
	&= 1 - \frac{z_0^2z_1z_2}{4} \cdot \left( z_0^{-1}z_1^{-1}+z_0^{-1}z_2^{-1}-z_1^{-1}z_2^{-1} \right)^2 \\
%	&= 1 - \frac{z_0^2z_1z_2}{4} \cdot \left( z_0^{-2}z_1^{-2} + z_0^{-2}z_2^{-2} + z_1^{-2}z_2^{-2}
%		+ 2z_0^{-2}z_1^{-1}z_2^{-1} - 2 z_0^{-1}z_1^{-2}z_2^{-1} - 2z_0^{-1}z_1^{-1}z_2^{-2} \right) \\
	&= 1 - \frac{1}{4} \left( z_1^{-1}z_2 + z_1z_2^{-1} + z_0^2z_1^{-1}z_2^{-1} + 2 - 2z_0z_1^{-1}-2z_0z_2^{-1}\right),
\end{align*}
which finishes the proof.
\end{proof}

The previous lemma covers the case when $y_0<y_1<y_2$. We now leverage it to take care of the other cases as well.

\begin{proof}[Proof of Lemma~\ref{lem:triangle_prob_y_coordinates}]
Let $y_i >0$ and $z_i = e^{-y_i/2}$, $i=0,1,2$. Lemma~\ref{lem:ordered} gives the expression for $P(y_0(z_0),y_1(z_1),y_2(z_2))$ in the case $y_0<y_1<y_2$, or equivalently $z_0>z_1>z_2$, i.e. the first two lines in the claim of Lemma~\ref{lem:triangle_prob_y_coordinates}. To analyze the other cases we shall express $P(y_1,y_0,y_2)$ and $P(y_1,y_2,y_0)$ in terms of $P(y_0,y_1,y_2)$ and $z_i$. For this we note that we can view $P(y_0,y_1,y_2)$ as a 2-fold integral of the indicator function
\[ 
	h(x_0, x_1, x_2) := \ind{ |x_0 - x_1| < e^{(y_0+y_1)/2}, |x_0 - x_2| < e^{(y_0+y_2)/2}, |x_1-x_2| < e^{(y_1+y_2)/2}}, 
\]
where $x_0$ was set to zero, without loss of generality, and the other two $x_i$ are uniform random variables on $[-e^{(y_0)+y_i)/2}, e^{(y_0+y_i)/2}]$. When we consider the probability $P(y_1,y_0,y_2)$, this is the 2-fold integral of $h(x_0,0,x_2)$ so that
\begin{align*}
	P(y_1,y_0,y_2) &= \frac{1}{2e^{(y_1+y_0)/2}} \cdot \frac{1}{2e^{(y_1+y_2)/2}} 
		\iint_{\R} h(x_0,0,x_2) \dd x_0 \dd x_2\\
	&= \frac{e^{y_0/2}}{e^{y_1/2}} \frac{1}{2e^{(y_0+y_1)/2}} \frac{1}{2e^{(y_0+y_2)/2}} 
		\iint_{\R} h(0,x_1,x_2) \dd x_1 \dd x_2\\
	&= \frac{e^{y_0/2}}{e^{y_1/2}} P(y_0,y_1,y_2) = \frac{z_1}{z_0}  P(y_0,y_1,y_2).
\end{align*}
Finally we note that $h(x_0,0,x_2) = h(x_2,0,x_0)$ from which we conclude that
\begin{equation}\label{eq:symmetry_relation_triangle_prob}
	P(y_0, y_1, y_2) = \left(z_0/z_1\right) P(y_1,y_0,y_2) = \left(z_0/z_1\right) P(y_1,y_2,y_0).
\end{equation}

To complete the proof for the other cases we note that since $P(y_0,y_1,y_2)$ is symmetric in $y_1$ and $y_2$, we can assume, without loss of generality, that $y_1 < y_2$. Then, there are two more orderings of $y_0, y_1, y_2$, namely $y_1< y_0< y_2$ and $y_1<y_2<y_0$, which can be summarized as $y_1 < \min (y_0,y_2)$, or equivalently $z_1 > \max(z_0,z_2)$. For $y_1 < y_0 < y_2$ and $y_1 < y_2<y_0$ we can apply Lemma~\ref{lem:ordered} to obtain $P(y_1,y_0,y_2) = P(y_1,y_2,y_0)$ which happen to agree due to the symmetry in the last two arguments of the expression found in Lemma~\ref{lem:ordered}. The expression for $P(y_0,y_1,y_2)$ then follows from~\eqref{eq:symmetry_relation_triangle_prob}.
\end{proof}

%\begin{lemma}\label{lem:leverage}
%We have
%
%\[ P(y_0, y_1, y_2) = \left(z_0/z_1\right) P(y_1,y_0,y_2) = \left(z_0/z_1\right) P(y_1,y_2,y_0), \]
%
%\noindent
%where $z_i = e^{-y_i/2}$ as before.
%\end{lemma}
%
%
%
%\begin{proof}
%We can think of $P(y_0,y_1,y_2)$ as a multiple of a 3-fold integral of the indicator function
%\[ 
%	h(x_0, x_1, x_2) := \ind{ |x_0-x_1| < e^{(y_0+y_1)/2}, |x_0-x_2| < e^{(y_0+y_2)/2}, |x_1-x_2| < e^{(y_1+y_2)/2}}, 
%\]
%where $x_0$ is selected uniformly $ x_1, x_2$ range over $\R$. More specifically $x_0$ u.a.r.~from $[-K,+K]$ and $x_i$ u.a.r.~from 
%$[x_0-e^{(y_0+y_i)/2}, x_0+e^{(y_0+y_i)/2}]$
%
%which we make into a 
%circle by identifying the endpoints and we take $K$ large enough.
%In more detail: we integrate the indicator function 
%
%\[ 
%	h(x_0, x_1, x_2) := 1_{\{ |x_0-x_1|_{2K} < e^{(y_0+y_1)/2}, |x_0-x_2|_{2K} < e^{(y_0+y_2)/2}, |x_1-x_2|_{2K} < e^{(y_1+y_2)/2} \}}, 
%\]
% 
%(where $|a|_b := \min(|a|, b-|a|)$ for $|a| \leq b$), and we multiply by 
%$\frac{1}{2K} \cdot \frac{1}{2e^{(y_0+y_1)/2}} \cdot \frac{1}{2e^{(y_0+y_2)/2}}$.
%(we think of taking $x_0$ u.a.r.~from $[-K,+K]$ and $x_i$ u.a.r.~from 
%$[x_0-e^{(y_0+y_i)/2}, x_0+e^{(y_0+y_i)/2}]$ -- interpreted modulo $K$ of course, so $K$ is chosen as a real number $>e^{(y_0+y_i)/2}$  s.t. the intervals $[x_0-e^{(y_0+y_i)/2},x_0+e^{(y_0+y_i)/2}]$ do not cover the circle).
%That is:
%
%\[ P(y_0, y_1, y_2) = \frac{1}{2K} \cdot \frac{1}{2e^{(y_0+y_1)/2}} \cdot \frac{1}{2e^{(y_0+y_2)/2}} \cdot \int_{[-K,K]^3} f. \]
%
%\noindent
%Completely analogously:
%
%\[ P(y_1,y_0,y_2) = \frac{1}{2K} \cdot \frac{1}{2e^{(y_1+y_0)/2}} \cdot \frac{1}{2e^{(y_1+y_2)/2}} \cdot \int_{[-K,K]^3} f
% = \frac{e^{y_0/2}}{e^{y_1/2}} P(y_0,y_1,y_2) = \frac{z_1}{z_0}  P(y_0,y_1,y_2), \]
%
%\noindent
%proving the first part of the lemma. The second part of the lemma holds as $P(y_1,y_2,y_0)=P(y_1,y_0,y_2)$.
%\end{proof}
%
%\begin{corollary} \label{cor:nonordered}
%$\text{ }$
%If $y_1 < \min(y_0,y_2)$ (or equivalently $z_1 > \max(z_0,z_2)$), then 
%\[ P(y_0,y_1,y_2) = \left\{ 
%\begin{array}{cl}
%\frac{z_0}{z_1} & \text{ if } z_1 \geq z_0 + z_2, \\
%\frac{z_0}{z_1} \cdot (1-G(z_1,z_0,z_2)) & \text{ if } z_1 < z_0+z_2. 
%\end{array} \right. 
%\]
%
%(Here $z_i := e^{-y_i/2}$ as before.)
%\end{corollary}
%
%Applying the expression found earlier, we find that 
%
%\[ \begin{array}{rcl}
%G(z_1,z_0,z_2)
%& = & 
%\frac14 ( z_0^{-1} z_2 + z_0 z_2^{-1} + z_1^2z_0^{-1} z_2^{-1}
%+ 2 -2z_1z_0^{-1}-2z_1z_2^{-1} ) \\
%\end{array} \]
%
%%\noindent
%Hence
%
%\[ \begin{array}{rcl}
%    G'(z_0,z_1,z_2) 
%    & := &  \frac{z_0}{z_1} G(z_1,z_0,z_2) \\
%    & = & \frac14 ( z_1^{-1} z_2 +z_0^2 z_1^{-1} z_2^{-1} + z_1 z_2^{-1} + 2z_0z_1^{-1} - 2 - 2z_0z_2^{-1} )
%   \end{array}
%\]
%
%We are now ready to complete the proof of Lemma~\ref{lem:triangle_prob_y_coordinates}.
%
%\begin{proof}[Proof of Lemma~\ref{lem:triangle_prob_y_coordinates}]
%Let $y_i >0$ and $z_i = e^{-y_i/2}$, $i=0,1,2$. Then lemma \ref{lem:ordered} gives the expression for $P(y_0(z_0),y_1(z_1),y_2(z_2))$ in the case $y_0<y_1<y_2$, or equivalently $z_0>z_1>z_2$, i.e. the first two lines in the claim of the proposition. As $P(y_0,y_1,y_2)$ is symmetric in $y_1$ and $y_2$, we can assume $y_1 < y_2$. Then, there are two more orderings of $y_0, y_1, y_2$, namely $y_1< y_0< y_2$ and $y_1<y_2<y_0$. That either of these orderings holds is equivalent to $y_1 < \min (y_0,y_2)$, or equivalently to $z_1 > \max(z_0,z_2)$. For $y_1 < y_0 < y_2$ and $y_1 < y_2<y_0$ we can apply lemma \ref{lem:ordered} to obtain $P(y_1,y_0,y_2)$ and $P(y_1,y_2,y_0)$ which happen to agree due to the symmetry in the last two arguments of the expression found in that lemma. Then lemma \ref{lem:leverage} yields $P(y_0,y_1,y_2)$ based on $P(y_1,y_0,y_2)=P(y_1,y_2,y_0)$ and corollary \ref{cor:nonordered} spells this out explicitly and together with the remarks after corollary \ref{cor:nonordered}, we obtain the remaining two lines in the claim of the proposition, which concludes the proof.
%\end{proof}

\subsection{Computing $\Delta_\Pcal(y_0)$}

Now that we have established the expression for $P(y_0,y_1,y_2)$ we can proceed with computing $\Delta_{\Pcal}(y_0)$, i.e. proving Proposition~\ref{prop:full_expression_delta_P}. We start with the following observation.

\begin{lemma}\label{lem:continuity_Delta_function}
The function $\alpha \mapsto \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ is continuous for all $\alpha > \frac{1}{2}$.
\end{lemma}
\begin{proof}
This follows from the theorem of dominated convergence:
Let $\alpha > \frac{1}{2}$ and $(\alpha_n)_{n\in \mathbb{N}}$ a sequence of real numbers converging to $\alpha$, so we can assume $|\alpha_n - \alpha| < \epsilon := \frac{\alpha-1/2}{2}$. This means that $-\epsilon < \alpha_n - \alpha < \epsilon$, i.e. $\frac{\alpha-1/2}{2} < \alpha_n - 1/2 < \frac{3\alpha-3/2}{2}$. Define $f_n(y_1,y_2) = P(y_0,y_1,y_2) (\alpha_n - 1/2)^2 e^{-(\alpha_n-1/2)(y_1+y_2)}$. As the function $x \mapsto x^2$ is increasing in $x$ for $x>0$ and the function $x \mapsto e^{-(y_1+y_2)x}$ is decreasing in $x$ and $P(y_0,y_1,y_2) \in [0,1]$, it holds that $|f_n(y_1,y_2)| \leq (\frac{3\alpha-3/2}{2})^2e^{-(y_1+y_2)\frac{\alpha-1/2}{2}}$ which is integrable over $\R_{\geq 0} \times \R_{\geq 0}$ (with integral equals $\frac{(6\alpha-3)^2}{(2\alpha-1)^2}$). Application of the theorem of dominated convergence and using equation~\eqref{eq:def_delta_p} yields that $\Delta_{\Pcal_{\alpha_n,\nu}}(y_0) \rightarrow \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ which gives the claim as the sequence $(\alpha_n)_n$ was arbitrary.
\end{proof}

Due to this lemma we can first assume $\alpha \notin \{ \frac{3}{4},1 \}$, compute $\Delta_{\Pcal}(y_0)$ and then obtain the values of $\Delta_\Pcal(y_0)$ at the remaining two points by taking the corresponding limit in $\alpha$. This strategy is executed below. It involves the computation of several integrals which are involved and will take up the next 7 pages. The proof is carefully structured, using headers, to aid the reader.

\begin{proof}[Proof of Proposition~\ref{prop:full_expression_delta_P}]\hfill

\paragraph{When $\bm{\alpha \notin \{3/4,1\}}$}
Note that when writing $\Delta_{\Pcal}(y_0)$ as in integral as in equation \eqref{eq:def_delta_p}, by symmetry in the integration variables $y_1$ and $y_2$, we can assume that $y_1<y_2$ in which case either $y_0$ or $y_1$ is the smallest height. This gives half the value of $\Delta_{\Pcal}(y_0)$ and hence
\[ 
	\Delta_\Pcal(y_0) = 2(I_1(y_0) +I_2(y_0)), 
\] 
where $I_1$ and $I_2$ are given by:
\begin{align*}
	I_1(y_0) &:= \int_{0<y_0<y_1<y_2} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)}  {\dd} y_2 {\dd} y_1 \\ 
	I_2(y_0) &:= \int_{0<y_1<y_0,y_2} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)} {\dd} y_2 {\dd} y_1 \\ 
\end{align*}

We proceed with computing each of these two integrals, each of which is split in two parts. The final expressions of those four integrals can be found in~\eqref{eq:Delta_P_computation_I11}, \eqref{eq:Delta_P_computation_I12}, \eqref{eq:Delta_P_computation_I21} and~\eqref{eq:Delta_P_computation_I22}.

\paragraph{Computing $\bm{I_1(y_0)}$}

Applying the change of variables $z_i := e^{-y_i/2}$ and Lemma~\ref{lem:triangle_prob_y_coordinates} gives %${\dd}y_i = -\frac{2{\dd}z_i}{z_i}$ and therefore
\begin{align*}
	I_1(y_0) &=	4 (\alpha-1/2)^2 \cdot \int_{z_0>z_1>z_2>0} P(y_0,y_1(z),y_2(z)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{z_0>z_1>z_2>0} 1 \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right. \\
	&\hspace{10pt} \left. - \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} G(z_0,z_1,z_2) \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 ( I_{11}(y_0) - I_{12}(y_0)). \numberthis \label{eq:Delta_P_computation_I11}
\end{align*}

The integral $I_{11}(y_0)$ is easily obtained:
\begin{align*}
	I_{11}(y_0) &= \int_0^{z_0} \int_0^{z_1} z_1^{2\alpha-2} z_2^{2\alpha-2} {\dd}z_2{\dd}z_1\\
	&= \int_0^{z_0} z_1^{2\alpha-2} \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1} \right]_0^{z_1} {\dd}z_1\\
	&= \frac{1}{2\alpha-1} \cdot \int_0^{z_0} z_1^{4\alpha-3} {\dd}z_1 \\
	&= \frac{1}{2(2\alpha-1)^2} \cdot z_0^{4\alpha-2}.
\end{align*}

To deal with $I_{12}$ we note that $G(z_0,z_1,z_2)$ is a linear combination of monomials of the form $z_0^az_1^bz_2^c$ with 
$a,b,c \in \{-1,0,1,2\}$ and $a+b+c=0$. Let us consider the integral $J_(a,b,c)(z_0)$
\begin{equation}\label{eq:def_Delta_P_computation_int_J_1}
	J_{a,b,c}(z_0) := z_0^a \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1.
\end{equation}
and note that
\begin{equation}\label{eq:Delta_P_computation_I12_with_J}
	I_{1,2}(y_0) = \frac{1}{4} (J_{0,-1,1}(z_0)+J_{0,1,-1}(z_0)+J_{2,-1,-1}(z_0)+2J_{0,0,0}(z_0)-2J_{1,-1,0}(z_0)-2J_{1,0,-1}(z_0)).
\end{equation}

Next we compute $J_{a,b,c}(z_0)$.
\begin{align*}
	J_{a,b,c} 
	&= z_0^a \int_{z_0/2}^{z_0}\int_{z_0-z_1}^{z_1} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
		= z_0^a \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} \left[ \frac{ z_2^{c+2\alpha-1} }{ c+2\alpha-1 } \right]_{z_0-z_1}^{z_1} \dd z_1\\
	&= \frac{z_0^a}{c+2\alpha-1} \cdot \left( \int_{z_0/2}^{z_0} z_1^{b+c+4\alpha-3} {\dd}z_1
	   - \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} (z_0-z_1)^{c+2\alpha-1} {\dd}z_1 \right) \\
	&= \frac{z_0^{a+b+c+4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{a+b+c+4\alpha-3}}{c+2\alpha-1} \int_{z_0/2}^{z_0}  \left(z_1/z_0\right)^{b+2\alpha-2} 
	    \left(1-(z_1/z_0)\right)^{c+2\alpha-1} {\dd}z_1\\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1}
	   \int_{1/2}^1  u^{b+2\alpha-2}(1-u)^{c+2\alpha-1} {\dd} u \\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1} B^-(1/2;c+2\alpha, b+2\alpha-1),
\end{align*}
where we've used the substitution $u := z_1/z_0$ giving $z_0 {\dd} u = {\dd} z_1$ in the penultimate line and
$B^-$ denotes the (lower) incomplete beta-function. Note that since $c \geq -1$, $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators that occur during the integration are all non-zero.

Plugging this back into~\eqref{eq:Delta_P_computation_I12_with_J} gives
\begin{align*}
	I_{1,2}(y_0)
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{4\alpha-2})}{32\alpha(\alpha-1/2)} 
   		- \frac{z_0^{4\alpha-2}}{8\alpha} B^-(1/2;1+2\alpha, 2\alpha-2)\\
	&\hspace{10pt}+ \frac{z_0^{4\alpha-2}(1-(1/2)^{4\alpha-2})}{32(\alpha-1)(\alpha-1/2)} 
   		-  \frac{z_0^{4\alpha-2}}{4(2\alpha-2)} B^-(1/2;2\alpha-1,2\alpha)\\
	&\hspace{10pt}+ \frac{z_0^{4\alpha-2}(1-(1/2)^{4\alpha-4})}{32(\alpha-1)^2} 
   		- \frac{z_0^{4\alpha-2}}{4(2\alpha-2)} B^-(1/2;-1+2\alpha, 2\alpha-2)\\
	&\hspace{10pt}+ \frac{z_0^{4\alpha-2}(1-(1/2)^{4\alpha-2})}{16(\alpha-1/2)^2} 
   		- \frac{z_0^{4\alpha-2}}{2(2\alpha-1)} B^-(1/2;2\alpha,2\alpha-1)\\
	&\hspace{10pt}- \frac{z_0^{4\alpha-2}(1-(1/2)^{4\alpha-3})}{16(\alpha-1/2)(\alpha-3/4)} 
   		+ \frac{z_0^{4\alpha-2}}{2(2\alpha-1)} B^-(1/2;2\alpha, 2\alpha-2)\\
	&\hspace{10pt}- \frac{z_0^{4\alpha-2}(1-(1/2)^{4\alpha-3})}{16(\alpha-1)(\alpha-3/4)} 
   		+ \frac{z_0^{4\alpha-2}}{2(2\alpha-2)} B^-(1/2;-1+2\alpha, 2\alpha-1) \\
	&=\frac{\left(\frac{3}{64}- \frac{3}{16} 2^{-4\alpha}+ 
   		\alpha (-\frac{41}{128} + \frac{13}{16}  2^{-4\alpha}) 
   		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} a^4\right) 
   		z_0^{4 \alpha-2} }{4(\alpha-1/2)^2 (\alpha-1)^2 (\alpha-3/4) \alpha} \\
	&\hspace{10pt}+ \frac{z_0^{4\alpha-2}}{8 (\alpha-1) \alpha (2\alpha-1)}(4 (\alpha-1) \alpha 
		(B^-(1/2; 2\alpha, 2\alpha-2) - B^-(1/2;2 \alpha,2\alpha-1) ) \\
    &\hspace{10pt}- (2 \alpha-1)\alpha ( B^-(1/2; 2\alpha-1, 2\alpha-2) + 
    	B^-(1/2; 2\alpha-1, 2\alpha) - 
    	2 B^-(1/2;2\alpha -1, 2\alpha-1) ) \\
    &\hspace{10pt}- (2\alpha-1)(\alpha-1) B^-(1/2; 1 + 2\alpha, 2\alpha-2)) \\
	&=\frac{\left(\frac{3}{64}- \frac{3}{16} 2^{-4\alpha} 
		+ \alpha (-\frac{41}{128} + \frac{13}{16}  2^{-4\alpha})  
		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} a^4\right) 
		z_0^{4 \alpha-2} }{4(\alpha-1/2)^2 (\alpha-1)^2 (\alpha-3/4) \alpha} \\
 	&\hspace{10pt}+ \frac{z_0^{4\alpha-2}}{8 (\alpha-1) \alpha (2\alpha-1)}(4 (\alpha-1) \alpha 
 		B^-(1/2; 2\alpha+1, 2\alpha-2) \\
  	&\hspace{10pt}- (2 \alpha-1)\alpha B^-(1/2;2\alpha+1,2\alpha-2) \\
    &\hspace{10pt}- (2\alpha-1)(\alpha-1) B^-(1/2; 2\alpha+1, 2\alpha-2)). \\
\end{align*}
For the last step we use the identities 
\begin{align}
	B^-(z;a,b)-B^-(z;a,b+1) &= B^-(z; a+1,b), \label{eq:Delta_P_computation_beta_id_1}\\
	B^-(z;a,b)+B^-(z;a,b+2)-2B^-(z;a,b+1) &= B^-(z;a+2,b). \label{eq:Delta_P_computation_beta_id_2}
\end{align}
to obtain
\begin{equation}
\begin{aligned}
	I_{1,2}(y_0) &=\frac{\left(\frac{3}{64}- \frac{3}{16} 2^{-4\alpha}
		+ \alpha (-\frac{41}{128} + \frac{13}{16}  2^{-4\alpha})
		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} a^4\right) 
		z_0^{4 \alpha-2} }{4(\alpha-1/2)^2 (\alpha-1)^2 (\alpha-3/4) \alpha} \\
 	&\hspace{10pt}- \frac{z_0^{4\alpha-2}B^-(1/2; 2\alpha+1, 2\alpha-2) }{8 (\alpha-1) \alpha (2\alpha-1)}	\label{eq:Delta_P_computation_I12}
\end{aligned}
\end{equation}

\paragraph{Computing $\bm{I_2(y_0)}$}

We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$ and Lemma~\ref{lem:triangle_prob_y_coordinates} we get
\begin{align*}
	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0(z_0),y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{1>z_1>z_0,z_2>0}  z_0 z_1^{2\alpha-3} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right. \\
	&\hspace{10pt}\left. - \int_{{1>z_1>z_0,z_2>0}\atop{z_1 < z_0+z_2}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
		z_2^{2\alpha-2} \dd z_2{\dd}z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 (I_{21}(y_0) - I_{22}(y_0)). \numberthis \label{eq:Delta_P_computation_I21}
\end{align*}

We proceed with the easy integral:
\begin{align*}
	I_{21}(y_0) &= z_0 \int_{1>z_1>\max(z_2,z_0);z_0,z_2>0} z_1^{2\alpha-3} z_2^{2\alpha-2} {\dd}z_2{\dd}z_1   
		= z_0 \int_{z_0}^1 \int_{0}^{z_1} z_1^{2\alpha-3} z_2^{2\alpha-2} {\dd}z_2{\dd}z_1\\
	&= z_0 \int_{z_0}^1 \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1}\right]_{0}^{z_1} z_1^{2\alpha-3} {\dd}z_1 
		= \frac{z_0}{2\alpha-1}  \int_{z_0}^1 z_1^{4\alpha-4} {\dd}z_1 \\
	&= \frac{z_0 - z_0^{4\alpha-2}}{(4\alpha-3)(2\alpha-1)}.
\end{align*}
We note that the denominators above are non-zero as $\alpha > \frac{1}{2}$ and $\alpha \not =\frac{3}{4}$.

To deal with $I_{22}(y_0)$ we consider the integral function
\[
	J_{a,b,c}^\prime(z_0) := z_0^a \int_{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\atop{z_1 < z_0+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
\]
and note that
\begin{equation}\label{eq:Delta_P_computation_I22_J}
	I_{2,2}(y_0) = \frac{1}{4}\left(J_{0,-1,1}^\prime(z_0) + J_{2,-1,-1}^\prime(z_0)
	+ J_{0,1,-1}^\prime(z_0) + 2J_{1,-1,0}^\prime(z_0) - 2J_{0,0,0}^\prime(z_0) - 2J_{1,0,-1}^\prime(z_0)\right)
\end{equation}

We know compute $J_{a,b,c}^\prime(z_0)$
\begin{align*}
	J_{a,b,c}^\prime(z_0) 
	&= z_0^a \int_{z_0}^1 \int_{z_1-z_0}^{z_1}  z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd} z_2 {\dd} z_1  \\
 	&= z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1}  z_1^{b+2\alpha-2}( z_1^{c+2\alpha-1}-(z_1-z_0)^{c+2\alpha-1})  {\dd} z_1  \\
 	&=z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1} z_1^{b+c+4\alpha-3} {\dd } z_1 -z_0^{a} \int_{z_0}^1 	
 		\frac{1}{c+2\alpha-1}z_1^{b+2\alpha-2}(z_1-z_0)^{c+2\alpha-1}  {\dd} z_1  \\
 	&= z_0^a  \frac{1}{(c+2\alpha-1)(b+c+4\alpha-2)}(1-z_0^{b+c+4\alpha-2}) \\
 	&\hspace{10pt}- \frac{z_0^a}{c+2\alpha-1}z_0^{b+c+4\alpha-2}B^-(1-z_0;c+2\alpha,-b-c-4\alpha+2) \\
	&= \frac{z_0^a -z_0^{4\alpha-2}}{(c+2\alpha-1)(b+c+4\alpha-2)}  
		- \frac{z_0^{4\alpha -2}B^-(1-z_0;c+2\alpha,-b-c-4\alpha+2)}{c+2\alpha-1}.  
\end{align*}
Here we used that for $x  \in \R,y>-1$ (note that as $c\geq -1$, it holds that $c+2\alpha-1 >-1$):
\begin{align*}
 \int_{z_0}^{1} z_1^x (z_1-z_0)^y {\dd} z_1 
 &= \int_0^{1-z_0} (s+z_0)^x s^y {\dd} s \\
 &= z_0^{x+y} \int_0^{1-z_0} \left( (s/z_0) + 1 \right)^x (s/z_0)^y {\dd} s \\
 &= z_0^{x+y+1} \int_{0}^{1/z_0 -1 } (t+1)^x t^y {\dd} t \\
 &= z_0^{x+y+1} \int_0^{1-z_0} u^y (1-u)^{-(x+y+2)} {\dd} u \\
 &= z_0^{x+y+1} B^-(1-z_0; y+1,-x-y-1 ).
\end{align*}
As $c \geq -1$ and $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators that occur during the computations above are non-zero.

Plugging the expression for $J_{a,b,c}^\prime(z_0)$ back into~\eqref{eq:Delta_P_computation_I22_J} we get,
\begin{align*}
	I_{2,2}(y_0) 
	&= \frac{1 -z_0^{4\alpha-2}}{32\alpha(\alpha-1/2)} 
		-  \frac{z_0^{4\alpha -2}B^-(1-z_0;1+2\alpha,-4\alpha+2)}{8\alpha} \\
	&\hspace{10pt}+ \frac{z_0^2 -z_0^{4\alpha-2}}{32(\alpha-1)^2}  
		- \frac{z_0^{4\alpha -2}B^-(1-z_0;-1+2\alpha,-4\alpha+4)}{8(\alpha-1)} \\
	&\hspace{10pt}+ \frac{1 -z_0^{4\alpha-2}}{32(\alpha-1)(\alpha-1/2)}  
		- \frac{z_0^{4\alpha -2}B^-(1-z_0;-1+2\alpha,-4\alpha+2)}{8(\alpha-1)} \\
	&\hspace{10pt}+ \frac{z_0 -z_0^{4\alpha-2}}{16(\alpha-1/2)(\alpha-3/4)}  
		- \frac{z_0^{4\alpha -2}B^-(1-z_0;2\alpha,-4\alpha+3)}{4(\alpha-1/2)} \\
	&\hspace{10pt}- \frac{1 -z_0^{4\alpha-2}}{16(\alpha-1/2)^2}  
		+ \frac{z_0^{4\alpha -2}B^-(1-z_0;2\alpha,-4\alpha+2)}{4(\alpha-1/2)}\\
	&\hspace{10pt}-\frac{z_0 -z_0^{4\alpha-2}}{16(\alpha-1)(\alpha-3/4)} 
		+ \frac{z_0^{4\alpha -2}B^-(1-z_0;-1+2\alpha,-4\alpha+3)}{4(\alpha-1)}.
\end{align*}
Using some algebra and the identities~\eqref{eq:Delta_P_computation_beta_id_1} and~\eqref{eq:Delta_P_computation_beta_id_2}  this can be reduced to
\begin{equation}\label{eq:Delta_P_computation_I22}
\begin{aligned}
	I_{2,2}(y_0)
	&=\frac{1}{64\alpha(\alpha-1/2)^2(\alpha-1)} -\frac{(1 - z_0)^{2\alpha}}{64\alpha(\alpha-1/2)^2 (\alpha-1)} 
		- \frac{z_0}{8(\alpha-1/2)(\alpha-1)(4\alpha-3)}\\ 
	&\hspace{10pt}+ \frac{z_0^2}{32(\alpha-1)^2} + \frac{(-6 + 25\alpha - 48\alpha^2 + 44\alpha^3 -16\alpha^4) 
   		z_0^{4\alpha-2}}{512\alpha(\alpha-1/2)^2(\alpha-1)^2(\alpha-3/4)} \\
	&\hspace{10pt}+ \frac{z_0^{4\alpha-2}B^-(1 - z_0; 2\alpha, 3 - 4\alpha)}{32(\alpha-1)(\alpha-1/2)^2}.
\end{aligned}
\end{equation}

%
%
%Combining the results for $I_{21}(y_0)$ and $I_{22}(y_0)$ we get
%\begin{equation}\label{eq:Delta_P_computation_I2}
%\begin{aligned}
%	I_2(y_0) = 
%\end{aligned}
%\end{equation}

\paragraph{Combining the results for $\bm{I_1(y_0)}$ and $\bm{I_2(y_0)}$}

Combining the results for $I_{11}(y_0), I_{12}(y_0), I_{21}(y_0)$ and $I_{22}(y_0)$ we get, after some algebra, an explicit expression for $\Delta_{\Pcal}(y_0)$ as a linear combination of terms of the form $z_0^u$, $(1-z_0)^u$ and $z_0^u B^-(1-z_0;a,b)$: 
\begin{align*}
\Delta_{\Pcal}(y_0)=& 2(I_1+I_2) = 8(\alpha- 1/2)^2(I_{1,1}-I_{1,2}+I_{2,1}-I_{2,2}) \\
=&8(\alpha-1/2)^2 \left(\frac{1}{2(2\alpha-1)^2 }z_0^{4\alpha -2} \right. \\ 
&\left.-\frac{\left(\frac{3}{64}- \frac{3}{16} 2^{-4\alpha}+ 
   \alpha (-\frac{41}{128} + \frac{13}{16}  2^{-4\alpha})  + 
   \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} a^4   \right) z_0^{4 \alpha-2} }{4(\alpha-1/2)^2 (\alpha-1)^2 (\alpha-3/4) \alpha} \right. \\ 
&\left.+\frac{z_0^{4\alpha-2}B^-(1/2; 2\alpha+1, 2\alpha-2) }{8 (\alpha-1) \alpha (2\alpha-1)} +\frac{z_0 - z_0^{4\alpha -2}}{(4\alpha-3)(2\alpha-1)} \right.\\
&\left.-\frac{1}{64\alpha(\alpha-1/2)^2(\alpha-1)} +\frac{(1 - z_0)^{2\alpha}}{64\alpha(\alpha-1/2)^2 (\alpha-1)} +\frac{z_0}{8(\alpha-1/2)(\alpha-1)(4\alpha-3)} \right.\\
   &\left. - \frac{z_0^2}{32(\alpha-1)^2}
   - \frac{(-6 + 25\alpha - 48\alpha^2 + 44\alpha^3 -16\alpha^4) z_0^{4\alpha-2}}{512\alpha(\alpha-1/2)^2(\alpha-1)^2(\alpha-3/4)} \right. \\
   & \left. - \frac{z_0^{4\alpha-2}B^-(1 - z_0; 2\alpha, 3 - 4\alpha)}{32(\alpha-1)(\alpha-1/2)^2} \right) \\
=&-\frac{1}{8 (\alpha - 1) \alpha} + \frac{(\alpha - 1/2) z_0}{\alpha - 1} - \frac{(\alpha - 1/2)^2 z_0^2}{
	4 (\alpha - 1)^2} \\
&+ 
z_0^{-2 + 4 \alpha} \left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} + \frac{(\alpha - 
	1/2 ) B^-(1/2; 1 + 2 \alpha, 
	-2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right) \\
&+ \frac{(1 - 
	z_0)^{2 \alpha}}{8 (\alpha - 1) \alpha} - \frac{  
	z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
\end{align*}

Observe that the above expression only contains terms of the form $\alpha - 1$ in the denominator. The only expression of the form $\alpha - 3/4$ is in the lower incomplete beta-function $B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)$ which appears twice in the expression for $\Delta_{\Pcal}(y_0)$.

\paragraph{The case of $\bm{\alpha = 3/4}$}\hfil\\

Note that the factor $\alpha-\frac{3}{4}$ does not occur in any denominator of the previously obtained expression. For the lower incomplete beta function, the last argument $3-4\alpha$ is zero for $\alpha=\frac{3}{4}$, however as $z_0 < 1$ the integration domain of the lower incomplete beta function does not touch the singularity at $t=1$ (note $B^-(1-z_0;2\alpha;3-4\alpha) = \int_0^{1-z_0} t^{2\alpha-1} (1-t)^{2-4\alpha}$). Therefore, the previous expression holds for this case as well.

\paragraph{The case of $\bm{\alpha = 1}$}

\PvdH{Realign formulas to fit them on page.}

We want to compute the limit $\lim_{\alpha \rightarrow 1} \Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0))$. For this, after factoring out $\frac{1}{\alpha-1}$ we compute the first two terms of the Taylor expansion of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ in $\alpha$ based at $\alpha = 1$. The constant term of this Taylor expansion is verified to vanish whereas the linear term gives the expression searched (after cancellation with $\frac{1}{\alpha-1}$). Note that two terms of $P(y_0(z_0))$ contain $(\alpha-1)^2$ in their denominator, so for those two another $\frac{1}{\alpha-1}$ is factored out and the first three terms of the Taylor expansion are computed. Their constant terms cancel and after multiplication with $\frac{1}{\alpha-1}$ their linear and quadratic terms become part of the constant and linear term of the overall expansion.

The first summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
\begin{align*}
-\frac{1}{8 \alpha} = -\frac{1}{8}+\frac{1}{8}(\alpha-1) +O( (\alpha-1)^2)
\end{align*}
The second summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
\begin{align*}
(\alpha-1/2)z_0 = \frac{1}{2}z_0 +z_0 (\alpha-1)+O( (\alpha-1)^2)
\end{align*}
The third summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$, needs a 3-term Taylor expansion after another multiplication with $(\alpha-1)$,
\begin{align*}
- \frac{(\alpha - 1/2)^2 z_0^2}{4} = -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+O( (\alpha-1)^3)
\end{align*}
The fourth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$, needs a  3-term Taylor expansion after another multiplication with $(\alpha-1)$,
\begin{align*}
z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha} &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+O( (\alpha-1)^3)
\end{align*}
as
\begin{align*}
\frac{d}{d\alpha}\left( \left(\frac{z_0}{2}\right)^{-2+4\alpha} 2^{-3}\left(3-\frac{1}{\alpha}\right) \right) = \left(\frac{z_0}{2}\right)^{-2+4\alpha}2^{-3}\left(4\ln\left(\frac{z_0}{2}\right)\left(3-\frac{1}{\alpha}\right)+\frac{1}{\alpha^2}\right)
\end{align*}
and
\begin{align*}
\frac{d^2}{d\alpha^2}\left( \left(\frac{z_0}{2}\right)^{-2+4\alpha} 2^{-3}\left(3-\frac{1}{\alpha}\right) \right) = \left( \frac{z_0}{2} \right)^{-2+4\alpha}2^{-3}\left(16\left(\ln\frac{z_0}{2}\right)^2\left(3-\frac{1}{\alpha}\right)+\frac{8\ln(\frac{z_0}{2})}{\alpha^2}-\frac{2}{\alpha^3} \right)
\end{align*}
The fifth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
\begin{align*}
z_0^{-2 + 4 \alpha} \frac{(\alpha - 
	1/2 ) B^-(1/2; 1 + 2 \alpha, 
	-2 + 2 \alpha)}{2\alpha} = \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
 \left.+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right)  (\alpha-1)+O( (\alpha-1)^2 )
\end{align*}
as
\begin{align*}
\frac{d}{d \alpha}\left( z_0^{-2 + 4 \alpha} \frac{(\alpha - 
	1/2 )}{2\alpha} B^-(1/2; 1 + 2 \alpha, 
	-2 + 2 \alpha)\right) = \ln(z_0) 4 z_0^{-2+4\alpha} \left(\frac{1}{2}-\frac{1}{4\alpha}\right)B^-(1/2;1+2\alpha,-2+2\alpha)\\
+z_0^{-2+4\alpha}\frac{1}{4\alpha^2}B^-(1/2;1+2\alpha,-2+2\alpha)+z_0^{-2+4\alpha}\left(\frac{1}{2}-\frac{1}{4\alpha}\right)\int_0^{\frac{1}{2}} \frac{d}{d\alpha}(t^{2\alpha}(1-t)^{2\alpha-3})dt
\end{align*}
where
\begin{align*}
\int_0^{\frac{1}{2}} \frac{d}{d\alpha}(t^{2\alpha}(1-t)^{2\alpha-3})dt = \int_0^{\frac{1}{2}} \ln(t)2t^{2\alpha}(1-t)^{2\alpha-3}+\ln(1-t)2t^{2\alpha}(1-t)^{2\alpha-3}dt
\end{align*}
The sixth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
\begin{align*}
\frac{(1 - z_0)^{2 \alpha}}{8 \alpha} = \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1)+O( (\alpha-1)^2 )
\end{align*}
The seventh and last summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
\begin{align*}
- \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4} = -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
\left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+O((\alpha-1)^2)
\end{align*}

We see that the constant coefficients cancel:
\begin{align*}
&-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) +\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 -\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 +\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 =0
\end{align*}
The expression for $\alpha=1$ is given by the sum of the linear coefficients:
\begin{align*}
&\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) +\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
&\qquad+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right) \\
&\qquad- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) \\
&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} - \frac{z_0^2}{32} \\
&\qquad-\frac{5}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2-\frac{5z_0^2}{32}+\frac{z_0^2 \ln2}{4}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \\
&\qquad+\frac{(1-z_0)^2}{4}\ln(1-z_0) -\frac{1}{8}+\frac{z_0}{4}-\frac{z_0^2}{8}\\
&\qquad+ z_0^2\ln(z_0)-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} +\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
&\qquad+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \\
&\qquad-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} +\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
&\qquad+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)) \\
&\qquad-z_0 \ln z_0-z_0^2(\ln z_0)^2+z_0(1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 \Li_2(z_0))\\
&\qquad-z_0^2   -\frac{1}{2}  z_0^2\Li_2(1) \\
&=\frac{9}{4}z_0-\frac{25}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} +\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
&\qquad-\frac{1}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)-\Li_2(1)+\Li_2(z_0)) \\
&\qquad-\frac{1}{2}z_0^2(\ln z_0)^2 - \frac{1}{2} z_0(1-z_0) \ln(1-z_0)
\end{align*}
where we used that the first integral is
\begin{align*}
[1/2 (-2 + 5 t + t^2 - \ln(1 - t)^2 - 2 t \ln t - t^2 \ln t - 
   \ln(1 - t) (-3 + 2 t + t^2 + 2\ln t) - 2 \Li_2(t))]_0^{\frac{1}{2}} \\
= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)
\end{align*}
and the second one is
\begin{align*}
[\frac{1}{-1+ t} (1 + \frac{1}{2}(1 + t) \ln(1 - t) + \frac{1}{2}(1 - t) \ln(
1 -t)^2 - \frac{1}{2} t \ln(t) +\frac{1}{2} (1 - t) \Li_2(1 -t))]_0^{1-z_0} \\
=-\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1)
\end{align*}
By expanding the squares and collecting terms, the last expression can be simplified to
\begin{align*}
&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) + 
z_0^2 \left(-7/8 - \frac{\ln(2)^2+2\Li_2(1/2) + 2\Li_2(1)}{4} \right) + 
\frac{1}{2}z_0^2 \Li_2(z) \\
=&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
z_0^2  + 
\frac{1}{2}z_0^2 \Li_2(z)
\end{align*}
This finishes the computation.

\end{proof}

\subsection{Exact expression for clustering, integrating $\Delta_{\Pcal}(y)$}

\PvdH{This part is still in the original form and has to be converted to match style and notation.}

We wish to compute

\[   
	c_\infty = \alpha \int_0^{\infty} \Delta_\Pcal(y) e^{-\alpha y} \left(1-e^{-\xi e^{y/2}} - \xi e^{y/2} 
	e^{-\xi e^{y_0/2}}\right) \dd y, 
\]

\noindent
and

\[ I^{(k)} := 
\int_0^{\infty} P(y_0) \alpha e^{-\alpha y_0} \frac{\left(\xi e^{y_0/2}\right)^k}{k!} e^{-\xi e^{y_0/2}} {\dd} y_0. \]

\noindent
(So $c = I$ and $c(k) = I^{(k)} / p_k $ for $k\geq 2$.) \\
Note that the integral for $I$ can be written as $J - I^{(0)} - I^{(1)}$ where

\[ J := \int_0^{\infty} P(y_0) \alpha e^{-\alpha y_0} {\dd} y_0. \]

\noindent
Note that, of course, the integrals $I^{(0)}$ and $I^{(1)}$ can be computed even though $c(0)$ and $c(1)$ are technically
speaking not well-defined.

\noindent
It seems helpful to change coordinates to $z_0 := e^{-y_0/2}$.
This gives ${\dd} y_0 = \REMOVEME{-}2 z_0^{-1} {\dd} z_0$, $e^{-\alpha y_0} = z_0^{2\alpha}$.
Hence

\[ J = 2 \alpha \int_0^1 P(y_0(z_0)) \cdot z_0^{2\alpha-1} {\dd} z_0, \]

\noindent
and

\[ I^{(k)} = \frac{2 \alpha \xi^k}{k!} \cdot \int_0^1 P(y_0(z_0)) \cdot z_0^{2\alpha-(k+1)} e^{-\xi/z_0} {\dd} z_0. \]

\noindent
Given the expression(s) we got for $P(y_0)$, we firstly deal with the case $\alpha \not = 1$. % As $J_\alpha$ and $I_\alpha^{(k)}$ (and hence also $c_\alpha$ and $c_\alpha(k)$) are continuous in $\alpha$ by the dominated convergence theorem, we will later obtain the result for $\alpha=1$ by taking the limit $\alpha \rightarrow 1$.

\noindent
Now we recall that for $\alpha \not =1$, $P(y_0(z_0))$ is in fact a linear combination of terms of the form $z_0^u$, $(1-z_0)^u$ and $z_0^u B^-(1-z_0,v,w)$, so we only need to compute the integrals $J$ and $I^{(k)}$ for these forms.

\vspace{1em}

\noindent
To work out $J$ we just need to observe that 
\[ \begin{array}{rcl} 
\int_0^1 z_0^{u+2\alpha-1} B^-(1-z_0;v,w) {\dd} z_0 
& = & 
\left[ \frac{z_0^{u+2\alpha}}{u+2\alpha} B^-(1-z_0;v,w) \right]_0^1 
+ \frac{1}{u+2\alpha} \int_0^1 z_0^{u+2\alpha+w-1} (1-z_0)^{v-1} {\dd} z_0 \\
& = & 
\frac{1}{u+2\alpha} B(u+w+2\alpha,v)
\end{array} \]
\noindent
(using that $\frac{\partial}{\partial z_0} B^-(1-z_0;v,w) = - z_0^{w-1} (1-z_0)^{v-1}$.)

This gives the expression for $J$ (note that it only depends on $\alpha$ but not on $\nu$)

\begin{align*}
J&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 
	24 \alpha^5}{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} +  \frac{2^{-1 - 
		4 \alpha}}{(\alpha - 1)^2} \\
	&\qquad+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)}
\end{align*}

%\begin{figure}
%	\centering
%	\includegraphics[scale=0.6]{0817J}
%	\caption{Plot of $J(\alpha)$ for $\alpha$ between 0.5 and 5 \REMOVEME{(and any $\nu$)}.}
%\end{figure}

\vspace{1em}

\noindent
To work out $I^{(k)}$ we first point out that

\[ \begin{array}{rcl} 
\int_a^b z_0^{u+2\alpha-(k+1)} e^{-\xi z_0^{-1}} {\dd} z_0
& = & 
\xi^{u+2\alpha-k} \int_{\xi/b}^{\xi/a} t^{k-1-2\alpha-u} e^{-t} {\dd} t \\
& = & 
\xi^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u;\xi/\REMOVEME{b}) - \Gamma^+( k-2\alpha-u; \xi/\REMOVEME{a}) \right), 
\end{array} \]
\REMOVEME{
In particular
\begin{align*}
\int_0^1 z_0^{u+2\alpha-k-1} e^{-\xi z_0^{-1}} {\dd} z_0 = \xi^{u+2\alpha-k} \Gamma^+(k-2\alpha-u;\xi)
\end{align*}}

\noindent
where $\Gamma^+$ denotes the (upper) incomplete gamma function, and we've used the subsitution
$t = \xi / z_0$ which gives ${\dd} z_0 = -\xi t^{-2} {\dd} t$. (And of course it is understood that 
$\xi/0 = \infty$.)

The hypergeometric U-function 
(also called Tricomi's confluent hypergeometric function) has the integral representation 
$$U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} dt$$ which holds for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $Re(a), Re(z) >0$, see \cite[p.255]{Erdelyi1953}. Applying the change of variables 
$t=\frac{1-s}{s}$ (i.e. $dt = -s^{-2} ds$ and $s = \frac{1}{t+1}$) yields the integral 
$\int_1^0 e^{-z(-1+\frac{1}{s})} (\frac{1-s}{s})^{a-1} (\frac{1}{s})^{b-a-1} (-s^2)ds = e^z\int_0^1 e^{-z/s} s^{-b}(1-s)^{a-1} ds$, i.e.
\begin{align*}
U(a,b,z) = \frac{e^z}{\Gamma(a)} \int_0^1 s^{-b} (1-s)^{a-1} e^{-z/s} ds
\end{align*}
Plugging in $a=2\alpha+1 >0$, $b=-2\alpha+k+1$, $z=\xi>0$, gives
\begin{align*}
\int_0^1 z_0^{2\alpha-k-1} e^{-\xi/z_0} (1-z_0)^{2\alpha} dz_0 = \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi)
\end{align*}

Let $a, c \in \R$, $\xi, b >0$ positive real numbers. 
Using the integral definition of the incomplete B-function, the change of variables $s=1-t$ gives:
\begin{align*}
\int_0^1 z^a e^{-\xi/z} B^-(1-z;b,c) dz &=\int_0^1 z^a e^{-\xi/z} \int_0^{1-z} t^{b-1} (1-t)^{c-1} dt dz \\
&=\int_0^1 z^a e^{-\xi/z} \int_z^1 s^{c-1} (1-s)^{b-1} ds dz
\end{align*}
Then changing the order of integration and using the substitution $u = \xi/z$  and recognizing the upper incomplete $\Gamma$-function yields
\begin{align*}
&=\int_0^1 \int_0^s z^a e^{-\xi/z} dz s^{c-1} (1-s)^{b-1} ds \\
&=\int_0^1 \int_{\xi/s}^\infty \xi^{a+1} u^{-a-2} e^{-u} du s^{c-1} (1-s)^{b-1} ds \\
&= \xi^{a+1} \int_0^1 \Gamma^+(-a-1,\xi/s) s^{c-1} (1-s)^{b-1} ds
\end{align*}
Now, the incomplete $\Gamma$-function has a representation in terms of Meijer's $G$-function $$\Gamma^+(-a-1,\xi/s) = \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}}$$ which holds for any $a\in \R$ and $s>0$ (see appendix; note that for a fixed second argument, the upper incomplete $\Gamma$-function is entire in the first argument, see \cite[pp. 899, 1032ff.]{Gradshteyn2007}).  Therefore, we get the integral

%formula 8.351.3, p. 
 %(see the wolfram functions website \url{http://functions.wolfram.com/06.06.26.0005.01}, it can also be found in the paper \url{https://arxiv.org/pdf/1507.05571}; , so we get the integral
\begin{align*}
= \xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}}ds
\end{align*}
applying the inversion identity for Meijer's $G$-function (see \cite[p. 209, 5.3.1.(9))]{Erdelyi1953})
\begin{align*}
=\xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{0}{2}{2}{1}{2+a,1}{0}{\frac{s}{\xi}}ds
\end{align*}
This is the Euler transform of Meijer's $G$-function (see \cite[p. 214, 5.5.2.(5)]{Erdelyi1953}) and (as the conditions $2+1<2(0+2)$ and $|\arg(\xi^{-1})| < \frac{\pi}{2}$ (as $\xi>0$) and $1-c-b<1-c$ (as $b>0$)  are satisfied) equals
\begin{align*}
=\xi^{a+1} \Gamma(b) \MeijerG{0}{3}{3}{2}{1-c,2+a,1}{0,1-c-b}{\xi^{-1}}
\end{align*}
Using again the inversion identity for Meijer's $G$-function
\begin{align*}
=\xi^{a+1} \Gamma(b) \MeijerG{3}{0}{2}{3}{1,b+c}{c,-1-a,0}{\xi}
\end{align*}
Plugging in $a= 6\alpha-k-3$, $b=2\alpha$, $c=3-4\alpha$ results in
\begin{align*}
=\xi^{6a-k-2} \Gamma(2\alpha) \MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}
\end{align*}
%(note that this agrees with the result in the old approach, after `bringing the power of $\xi$ into Meijer's $G$-function'.)

This allows us to write:
\begin{align*}
I^{(k)}&=\frac{\xi^{2\alpha}}{4k!(\alpha-1)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
&\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
&\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
&\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
\end{align*}%{4\alpha-k+1,6\alpha-k-1}{6\alpha-k-2,2\alpha-k+1,0}

Finally, we compute 
\begin{align*}
p_k := \Pee( D=k ) = \int_0^\infty e^{-\xi e^{y/2}} \frac{(\xi e^{y/2})^k}{k!}\alpha e^{-\alpha y} dy = 2\alpha \int_0^1 e^{-\frac{\xi}{z}} z^{2\alpha -k-1} dz =\frac{2\alpha \xi^{2\alpha}}{k!} \Gamma(k-2\alpha,\xi)
\end{align*}
%and thus
%\begin{align*}
%\GR{p_{\geq 2}} := \Pee( D \geq 2 ) = 1-2\alpha\xi^{2\alpha}(\Gamma(-2\alpha,\xi)-\Gamma(1-2\alpha,\xi))
%\end{align*}
and we can write down the average clustering coefficient

\begin{align*}
c &= J-I^{(0)}-I^{(1)} \\
&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 
	24 \alpha^5}{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} +  \frac{2^{-1 - 
		4 \alpha}}{(\alpha - 1)^2} \\
	&\qquad+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)} \\
	&\qquad-\frac{\xi^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+( - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(- 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
&\qquad\qquad\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+( - 2 \alpha - 1,\xi) \right.\\ 
&\qquad\qquad\left.+ 4\xi^{4\alpha - 2} \Gamma^+( - 6 \alpha + 2, 
      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
&\qquad\qquad\left.+ \xi^{-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1-2\alpha,\xi) \right. \\ 
&\qquad\qquad\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi}  \right) \\
&\qquad-\frac{\xi^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+(1 - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+( - 2 \alpha - 1, \xi)}{(\alpha - 1)} \right. \\ 
&\qquad\qquad\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(1 - 2 \alpha - 1,\xi) \right.\\ 
&\qquad\qquad\left.+ 4\xi^{4\alpha - 2} \Gamma^+(1 - 6 \alpha + 2, 
      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
&\qquad\qquad\left.+ \xi^{1-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,2-2\alpha,\xi) \right. \\ 
&\qquad\qquad\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi}  \right)
\end{align*}

and 
\begin{align*}
c(k) = \frac{I^{(k)}}{p_k} &=\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
&\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
&\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
&\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
\end{align*}

To determine the value of $c$ and $c(k)$ for $\alpha=1$, it suffices to find the value of $J$ and $I^{(k)}$ at $\alpha = 1$. 
We can do this by computing those integrals with the expression for $P(y_0)$ that we found for $\alpha=1$, i.e.
\begin{align*}
J &= 2\alpha\int_0^1 \left(\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
z_0^2  + 
\frac{1}{2}z_0^2 \Li_2(z)\right) z_0^{2\alpha -1} dz_0 \\
&=\frac{575-12\pi^2}{576}
\end{align*}
and 
\begin{align*}
I^{(k)} &= \frac{2\alpha \xi^k}{k!}\int_0^1 \left(\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
z_0^2  + 
\frac{1}{2}z_0^2 \Li_2(z) \right)z_0^{2\alpha-k-1} e^{-\xi/z_0} dz_0 \\
&= \frac{2 \eta^k}{k!}\int_0^1 \left(\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
z_0^2  + 
\frac{1}{2}z_0^2 \Li_2(z) \right)z_0^{1-k} e^{-\eta/z_0} dz_0 \\
&= \frac{9 \eta^k}{2 k!}\eta^{3-k}\Gamma^+(k-3,\eta)-\frac{\eta^k}{k!}\frac{7+\pi^2}{4}\eta^{4-k}\Gamma^+(k-4,\eta)\\
&+\frac{\eta^k}{2k!}\int_0^1 (1-4z_0+3z_0^2)\ln(1-z_0)z_0^{1-k}e^{-\eta/z_0}dz_0+\frac{\eta^k}{k!}\int_0^1 z_0^{3-k} \Li_2(z) e^{-\eta/z_0}dz_0 \\
&=\frac{9 \eta^3}{2 k!}\Gamma^+(k-3,\eta)-\frac{\eta^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
&+\frac{\eta^k}{2k!}\int_0^1 (1-4z_0+3z_0^2)\ln(1-z_0)z_0^{1-k}e^{-\eta/z_0}dz_0+\frac{\eta^k}{k!}\int_0^1 z_0^{3-k} \Li_2(z) e^{-\eta/z_0}dz_0
\end{align*}
where $\eta = \frac{4\nu}{\pi}$.

### 2018-10-16 concentration.tex
Initial ShareLaTeX Import

\section{Concentration for $c_{\mathcal{P}, n}(k)$ (Proving Proposition \ref{prop:concentration_local_clustering_P_n})}
\label{sec:concentration_c_P_n}

\subsection{The main contribution of triangles}

Recall the adjusted triangle count function \eqref{eq:def_tilde_triangle_indicator}
\[
	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal_n}.
\]
and the concentration set
\[
	\Kcal_C(k) = \left\{p \in \R : \frac{k - C \sqrt{k \log(k)}}{\xi_{\alpha,\nu}} \le e^{\frac{y}{2}}
		\le \frac{k + C \sqrt{k \log(k)}}{\xi_{\alpha,\nu}} \right\},
\]
We will define the corresponding triangle degree function
\begin{equation}\label{eq:def_degree_triangle_count_in_K}
	\widetilde{T}_{\Pcal,n}(k,C) = \sum_{p \in \Pcal_n \cap K_C(k)} \ind{D_{\Pcal,n}(p) = k} \widetilde{T}_{\Pcal,n}(p),
\end{equation}
where
\[
	\widetilde{T}_{\Pcal,n}(p) := \sum_{(p_1, p_2) \in 2^{\Pcal_n}} \widetilde{T}_{\Pcal,n}(p,p_1,p_2).
\]

By Lemma \ref{lem:clustering_error_T_term} and a concentration argument it follows that for $k_n \to \infty$
\[
	\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)} = (1+\smallO{1})\Exp{T_{\Pcal}(k_n)},
\]
for a appropriately selected $C > 0$. We conclude that the main contribution of triangles of degree $k_n$ is given by $\widetilde{T}_{\Pcal,n}(k_n,C)$. Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} we need to show that $\widetilde{T}_{\Pcal,n}(k_n,C)$ is sufficiently concentrated around its mean.

\subsection{Proving Proposition \ref{prop:concentration_local_clustering_P_n}}

We start with the concentration result for $\widetilde{T}_{\Pcal,n}(k_n,C)$.

\begin{proposition}[Concentration $\widetilde{T}_{\Pcal,n}(k_n,C)$]\label{prop:concentration_tilde_T_P_n}
Let $\alpha > \frac{1}{2}$, $0 < \varepsilon < \min\{2\alpha - 1,1\}$ and let $(k_n)_{n \ge 1}$ be any increasing sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
\[
	\Exp{\widetilde{T}_{\Pcal,n}(k_n, C)^2} = \left(1 + \smallO{1}\right)\Exp{\widetilde{T}_{\Pcal,n}(k_n, C)}^2.
\]
\end{proposition}

The proof of this proposition is lengthy and we therefore postpone it till Section \ref{ssec:concentration_tilde_T}. The remaining of this section will be devoted to prove Proposition \ref{prop:concentration_local_clustering_P_n}. We first show that $\Exp{c_{\Pcal,n}(k_n)} = (1+o(1))\Exp{c^\ast_{\Pcal,n}(k_n)}$.

\begin{lemma}\label{lem:L1_convergence_c_Pcal_n}
Let $\nu > 0$, $\alpha > \frac{1}{2}$ and $k_n = o\left(n^{\frac{1}{2\alpha + 1}}\right)$. Then, as $n \to \infty$,
\[
	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
\]
\end{lemma}

\begin{proof}
Let $0 < \delta < 1$ and define the following two events
\begin{align*}
	A_n &= \left\{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| \le \Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}\right\}\\
	B_n &= \left\{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| \le n\right\},
\end{align*}
so that
\[
	1 = \ind{A_n} + \ind{A_n^c}\ind{B_n} + \ind{B_n^c}.
\]
Next we note that on the event $A_n$
\[
	\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right| 
	\le \frac{\Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}}{\Exp{N_{\Pcal,n}(k_n)}+\Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}}
	\le \Exp{N_{\Pcal,n}(k_n)}^{-\frac{1 - \delta}{2}},
\]
and on the event $B_n$
\[
	\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right| 
	\le \frac{n}{\Exp{N_{\Pcal,n}(k_n)} + n} \le 1.
\]
Therefore we have
\begin{align*}
	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|}
	&= \Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|}\\
	&\le \Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n}}\Exp{N_{\Pcal,n}(k_n)}^{-\frac{1 - \delta}{2}} \\
	&\hspace{10pt}+ \Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}} \\
	&\hspace{10pt}+ \Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|\ind{B_n^c}}
\end{align*}
Since $\Exp{N_{\Pcal,n}(k_n)} \to \infty$, the first term is clearly $\smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}$. For the third term we have
\begin{align*}
	\Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|\ind{B_n^c}} 
	&= \bigO{\Prob{B_n^c}}
		= \bigO{\Prob{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| > n}}\\
	&= \bigO{e^{-\frac{n^2}{\Exp{N_{k_n}} + n}}} = \bigO{e^{-n}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
\end{align*}
Hence we are left to show that
\begin{equation}\label{eq:L1_convergence_second_term}
	\Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
\end{equation}
By writing
\begin{align*}
	c_{\Pcal, n}^\ast(k_n) = \frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
	+ \frac{T_{\Pcal,n}(k_n,\varepsilon)- \widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
\end{align*}
and using Lemma~\ref{lem:clustering_error_T_term} we get
\begin{align*}
	\Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}}
	&\le \Exp{\frac{(1+\smallO{1})\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
		\ind{A_n^c}} + \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
\end{align*}
For the last step we use H\"{o}lder's inequality and Proposition \ref{prop:concentration_tilde_T_P_n} to get
\begin{align*}
	\Exp{\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}\ind{A_n^c}}
	&\le \Exp{\left(\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}
		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}\right)^2}^{\frac{1}{2}} \Prob{A_n^c}^{\frac{1}{2}}\\
	&= \left(1 + \smallO{1}\right) 	
		\frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
		\Prob{A_n^c}^{\frac{1}{2}}\\
	&= \bigO{\Exp{c_{\Pcal, n}^\ast(k_n)}}\Prob{A_n^c}^{\frac{1}{2}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}},
\end{align*}
since $\Prob{A_n} = o(1)$. This establishes \eqref{eq:L1_convergence_second_term} and hence we conclude that
\[
	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
\]
\end{proof}

We are now in shape to prove the main result of this section.

\begin{proof}[Proof of Proposition \ref{prop:concentration_local_clustering_P_n}]
Again, we write
\begin{align*}
	c_{\Pcal, n}^\ast(k_n) = \frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
	+ \frac{\left(T_{\Pcal,n}(k_n)-\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)\right)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}},
\end{align*}
so that by Lemma \ref{lem:clustering_error_T_term},
\[
	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
	+ \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}}.
\]
Therefore, by Lemma \ref{lem:L1_convergence_c_Pcal_n},
\begin{align*}
	\Exp{\left|c_{\Pcal,n}(k_n) - \Exp{c_{\Pcal,n}^\ast(k_n)}\right|}
	&\le \Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{c_{\Pcal,n}^\ast(k_n)}\right|}
		+ \Exp{\left|c_{\Pcal,n}(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}\\
	&= \frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}}
		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}} + \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}}.
		\numberthis \label{eq:concentration_local_clustering_P_n_term1}
\end{align*}
Next, we use Proposition \ref{prop:concentration_tilde_T_P_n} to obtain
\begin{align*}
	\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}
	&\le \left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)^2} 
		- \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}^2\right)^{\frac{1}{2}}\\
	&= \smallO{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}.
\end{align*}
This implies
\begin{align*}
	\frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}}
		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
	&= \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}},
\end{align*}
which together with~\eqref{eq:concentration_local_clustering_P_n_term1} finishes the proof.
\end{proof}

\subsection{Concentration for main triangle contribution}\label{ssec:concentration_tilde_T}

We now turn to Proposition \ref{prop:concentration_tilde_T_P_n}. Before we dive into the proof let us first give a high level overview of the strategy and the flow of the arguments.

Recall (see \eqref{eq:def_degree_triangle_count_in_K}) that for any $C > 0$
\[
	\widetilde{T}_{\Pcal,n}(k,C) = \sum_{p \in \Pcal_n \cap \Kcal_{C}(k)} \ind{D_{\Pcal,n}(p) = k}
	\widetilde{T}_{\Pcal,n}(p)
\]
Then we have
\[
	\widetilde{T}_{\Pcal,n}(k,C)^2 = \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k)}
		\ind{D_{\Pcal,n}(p), \, D_{\Pcal,n}(p^\prime) = k} 
		\sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in 2^{\Pcal_n}}
		T_{\Pcal}(p,p_1,p_2) T_{\Pcal}(p^\prime, p_1^\prime, p_2^\prime),
\]
with $2^{\Pcal_n}$ denoting the distinct pairs in $\Pcal_n$.
This expression can be written as the sums of several terms, depending on how $\{p, p_1, p_2\}$ and $\{p^\prime, p_1^\prime, p_2^\prime\}$ intersect. To this end we define, for $a \in \{0,1\}$ and $b \in \{0,1,2\}$,
\[
	I_{a,b} = \hspace{-3pt} \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k) \atop |\{p\} \cap \{p^\prime\}| = a}
	\hspace{-5pt} \ind{D_{\Pcal,n}(p), \, D_{\Pcal,n}(p^\prime) = k} J_b(p,p^\prime),
\]
where
\[
	J_b(p,p^\prime) = \hspace{-10pt} \sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in 2^{\Pcal_n} 
		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b}
		\hspace{-5pt} T_{\Pcal,n}(p,p_1,p_2) T_{\Pcal,n}(p^\prime, p_1^\prime, p_2^\prime).
\]
Then we have
\[
	\widetilde{T}_{\Pcal,n}(k, C)^2 = \sum_{a = 0}^1 \sum_{b = 0}^2 I_{a,b}.
\]

To prove Proposition \ref{prop:concentration_tilde_T_P_n} we will deal with each of the $I_{a,b}$ separately, showing that 
\begin{equation}\label{eq:variance_T_I_00}
	\Exp{I_{0,0}} = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal,n}(k_n)}^2
\end{equation}
and for all other combinations
\begin{equation}\label{eq:variance_T_I_ab}
	\Exp{I_{a,b}} = \smallO{\Exp{\widetilde{T}_{\Pcal,n}(k_n)}^2}.
\end{equation}
Note that $J_{b}(p,p^\prime) \le J_{0}(p,p^\prime)$ and, since $I_{1,2} = \widetilde{T}_{\Pcal,n}(k_n,C)$, \eqref{eq:variance_T_I_ab} holds for $I_{1,2}$.

\begin{proof}[Proof of Proposition \ref{prop:concentration_tilde_T_P_n}]
The technical steps of this proof use Lemma \ref{lem:joint_degree_distribution_shift} and Lemma \ref{lem:joint_degree_distribution_P_n}, which deal with the joint degree distribution. Let $\Ncal_{\Pcal,n}^c(p,p^\prime)$ denote the number of nodes not connected to both $p$ and $p^\prime$ an fix $0 < \eps < (2\alpha - 1 \wedge 1)$. To be able to apply both lemmas, we first show that we only need to consider the case where $\Exp{\left|\Ncal_{\Pcal,n}^c(p,p^\prime)\right|} \ge k_n^{\varepsilon}$ and $|x - x^\prime| > k_n^{1+\eps}$. To this end define 
\[
	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
	\, : \, \Exp{\left|\Ncal_{\Pcal,n}^c(p,p^\prime)\right|} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}
\]
and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $p,p^\prime \in \Pcal_n \cap \mathcal{E}_\varepsilon(k_n)$. We first show that
\begin{eqnarray}\label{eq:I_ab_ast_main}
	\Exp{I_{a,b} - I_{a,b}^\ast} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
\end{eqnarray}
so that for the remainder of the proof we only need to consider $p, p^\prime \in \mathcal{E}_\varepsilon(k_n)$ and hence, we can apply Lemma \ref{lem:joint_degree_distribution_shift} and Lemma \ref{lem:joint_degree_distribution_P_n} to the joint degree distribution inside the integral.

Note that for all $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ we have that $e^{\frac{y^\ast}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) = \bigT{k_n^2}$, where $y^\ast = \min\{y,y^\prime\}$. Hence by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ with $\Exp{\left|\Ncal_{\Pcal,n}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ and $|x-x^\prime| > k_n^{1+\varepsilon}$ that either
\[
	|x - x^\prime| + \left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right| = O\left(k_n^\varepsilon\right)
	\quad \text{or} \quad
	\Exp{\left|\Ncal_{\Pcal,n}(p\Delta p^\prime)\right|} = \Omega(k_n).
\]
In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \notin \mathcal{E}_{\varepsilon}(k_n)$. Therefore, we have
\begin{align*}
	&\Exp{I_{a,b} - I_{a,b}^\ast}\\
	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
		\Exp{J_b(p,p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
	&= \bigO{\int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}} \rho_{y}(k) 
		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy}\\
	&= \bigO{k_n^{1+\varepsilon} \binom{k_n}{2} \left(\int_{a_n^-}^{a_n^+} \Delta_{\Pcal}(y^\prime) 
			e^{-\alpha y^\prime} \, dy^\prime\right) \Exp{T_{\Pcal,n}(k_n)}}\\
	&= \bigO{k_n^{3 + \varepsilon -2\alpha} s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}}\\
	&= \smallO{n k_n^{-(2\alpha - 1)}s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
\end{align*}
which proves \eqref{eq:I_ab_ast_main}. Here we used that $k_n^{2 + \varepsilon} = \smallO{n}$ and $\Exp{T_{\Pcal,n}(k_n)} = \bigT{n k_n^{-(2\alpha - 1)}s_\alpha(k_n)}$ for the last line.

We will now proceed to establish \eqref{eq:variance_T_I_00} and \eqref{eq:variance_T_I_ab}. We split these up into separate subsections because each term requires different bounding techniques.

\vspace{5pt}

\paragraph{I) $\bm{I_{0,0}^\ast}$:}
Let $i = |\{p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\} \cap B_{\Pcal,n}(p)|$ and $j = |\{p^\prime \cap B_{\Pcal,n}(p)\}|$ and let $i^\prime, j^\prime$ be defined, similarly, by interchanging the primed and non-primed variables. Then, by Lemma  \ref{lem:joint_degree_distribution_shift} and  Lemma \ref{lem:joint_degree_distribution_P_n}
\[
	\rho_(p,p^\prime, k_n-i,k_n-i^\prime) = (1+o(1))\rho(p,p^\prime, k_n-j,k_n-j^\prime) 
	= (1+o(1))\rho_{n}(p, k_n)\rho_{n}(p^\prime,k_n) 
\]
which now no longer depends on the other four points $p_1, p_2, p_1^\prime, p_2^\prime$. Hence, using the Mecke formula, we get
\[
	\Exp{I_{0,0}^\ast} = \frac{1 + \smallO{1}}{4}\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{n}(p, k_n)\rho_{n}(p^\prime,k_n)
		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y)
		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
\]
where the factor $\frac{1}{4}$ is because we consider distinct pairs $(p_1,p_2)$ and $(p_1^\prime, p_2^\prime)$.

Next, by Lemma \ref{lem:clustering_error_T_term} and Proposition~\ref{prop:asymptotics_average_clustering_ast_P} we have for $y \in K_C(k_n)$,
\[
	\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal}(p)} = (1 + \smallO{1}) k_n^2 \Delta_{\Pcal}(y)
\] 
and similar result holds for $p^\prime$. Hence 
\begin{align*}
	&\hspace{-10pt}\frac{1 + \smallO{1}}{4} \int_{\mathcal{E}_\varepsilon(k_n)} \rho_{p,p^\prime}(k-j,k-j^\prime)
		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y)
		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
	&= (1+\smallO{1})\binom{k_n}{2}^2 \int_{\mathcal{E}_\varepsilon(k_n)} 
		\rho_{p,p^\prime}(k-j,k-j^\prime) \Delta_{\Pcal}(y) \Delta_\Pcal(y^\prime) 	f_{\alpha,\nu}(x,y) 
		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
	&= (1+\smallO{1}) \left( \binom{k_n}{2} \int_{a_n^-}^{a_n^+}\int_{I_n} \rho_{y,n}(k_n)
		\Delta_{\Pcal}(y) f_{\alpha,\nu}(x,y) \, dx \, dy\right)^2\\
	&= (1 + \smallO{1})\left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right)^2,
\end{align*}
which proves \eqref{eq:variance_T_I_00}.

\paragraph{II) $\bm{I_{0,1}^\ast}$:}
Without loss of generality we will assume that $p_1 = p_1^\prime$. Similar to the previous computations, we let $i = |\{p^\prime, p_1, p_2, p_2^\prime\} \cap B_{\Pcal,n}(p)|$ and $j = |\{p^\prime\} \cap B_{\Pcal,n}(p)|$ and let $i^\prime$, $j^\prime$ be defined, similarly, by interchanging the primed and non-primed variables. Then, if we define
\[
	T^{(0,1)}_{\Pcal,n}(p,p^\prime) = \sum_{(p_1,p_2) \in 2^{\Pcal_n}} \sum_{p_2^\prime \in \Pcal_n} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) \widetilde{T}_{\Pcal,n}(p^\prime,p_1,p_2^\prime),
\]
we have
\begin{align*}
	\Exp{I_{0,1}^\ast} &= \frac{1+\smallO{1}}{2} \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_n(p,k)\rho_n(p^\prime,k)
			\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)} f_{\alpha,\nu}(x,y)
			f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
\end{align*} 
where we again used Lemma  \ref{lem:joint_degree_distribution_shift} and  Lemma \ref{lem:joint_degree_distribution_P_n}.
We will show that 
\[
	\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)} = \smallO{k_n^4 s_\alpha(k_n)^2},
\] 
from which \eqref{eq:variance_T_I_ab} follows since $k_n^4 s_\alpha(k_n)^2 = \bigO{\Exp{\widetilde{T}_{\Pcal,n}(p)} \Exp{\widetilde{T}_{\Pcal,n}(p^\prime)}}$ on $\Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$.

First we consider the contribution coming from $y_1 > 4 \log(k_n)$. Since the integration of $T_\Pcal(p,p_1,p_2) T_\Pcal(p^\prime,p_1,p_2^\prime)$ over $x_1, x_2$ and $x_2^\prime$ is bounded by $\bigO{e^{y}e^{\frac{y^\prime}{2}} e^{\frac{y_1 + y_2 + y_2^\prime}{2}}}$ it follows that contribution to $\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)}$ is bounded by
\begin{align*}
	\bigO{e^{y}e^{\frac{y^\prime}{2}} \int_{4\log(k_n)}^{a_n^+} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}\\
	&= \bigO{k_n^3 \int_{4\log(k_n)}^{a_n^+} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}\\
	&= \bigO{k_n^{3 - (4\alpha - 2)}} = \smallO{k_n^4 s_\alpha(k_n)^2}.
\end{align*}

To deal with the case where $y_1 \le 4\log(k_n)$ we define $b_n = 2\varepsilon\log(k_n))$ and will consider different cases for $\Exp{T^\ast_{\Pcal,n}(p,p^\prime)}$, depending on whether $y_2 \le b_n$ or $y_2 > b_n$ and similar for $y_2^\prime$.

When $y_1 \le 4\log(k_n)$ and $y_2 > b_n$, the contribution to $\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)}$ is bounded by
\begin{align*}
	\Exp{\widetilde{T}_{\Pcal,n}(p)}
		\bigO{e^{\frac{y^\prime}{2}}\int_{b_n}^{a_n^+} e^{-(\alpha -\frac{1}{2})y_2} \, dy_2}
	&= \bigO{k_n^{1 - \varepsilon}}\Exp{\widetilde{T}_{\Pcal,n}(p)}
	= \smallO{k_n^4 s_\alpha(k_n)^2}.
\end{align*}
Due to the symmetry in $p_2$ and $p_2^\prime$ the same results holds for the cases where $y_2 > b_n$.

Finally, when $y_1 \le 4\log(k_n)$ and both $y_2, y_2^\prime \le b_n$ we have that
\[
	|x_2 - x_2^\prime| \le |x_1 - x_2| + |x_1 - x_2^\prime| \le e^{\frac{y_1}{2}}\left(e^{\frac{y_2}{2}} + e^{\frac{y_2^\prime}{2}}\right) \le 2k_n^{2+\varepsilon}
\]
whenever $T_\Pcal(p,p_1,p_2) T_\Pcal(p^\prime,p_1,p_2^\prime) > 0$ while both $|x - x_2|, |x^\prime - x_2^\prime| = \bigO{k_n^{1 + \varepsilon}}$. Hence it follows that
\[
	|x - x^\prime| \le |x - x_2| + |x_2 - x_2^\prime| + |x_2^\prime - x^\prime| = \bigO{k_n^{2 + \varepsilon}}.
\]
Next, by integrating only over $x_2^\prime$ and $y_2^\prime $ we get the contribution to $\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)}$ for this regime is bounded by
\[
	\bigO{e^{\frac{y^\prime}{2}} \Exp{\widetilde{T}_{\Pcal,n}(p)}}
	= \bigO{k_n \Exp{\widetilde{T}_{\Pcal,n}(p)}} = \smallO{k_n^4 s_\alpha(k_n)^2}.
\]

The proofs for the other two cases $I_{0,2}^\ast$ and $I_{0,2}^\ast$ follows similar arguments.

%\paragraph{III) $\bm{I_{0,2}^\ast}$:}
%
%\paragraph{IV) $\bm{I_{1,1}^\ast}$:}

\end{proof}

\PvdH{Stopped here with general pass}

%\subsubsection{The case where $k_n = \bigO{1}$}
%
%Let $0 < \varepsilon < 1$, $\delta_n = (\varepsilon/k_n)^2$ and define
%\[
%	a_n = -\frac{1}{\alpha} \log\left(\delta_n\right)
%\]
%
%Then, for all $p,p^\prime \in \Rcal_n$ with 
%\[
%	|x-x^\prime| > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)\max\{e^{\frac{a_n}{2}},e^{\frac{y^\ast}{2}}\}
%	:= b_n(p,p^\prime)
%\] 
%we have that $h(p,p^\prime) > a_n$ and hence the neighborhoods of $p$ and $p^\prime$ below height $a_n$ are disjoint.

### 2018-10-16 concentration_argument.tex
Initial ShareLaTeX Import

\section{Concentration of heights for nodes with degree $k$}\label{sec:concentration_argument}

Many of the computations in this paper will involve integrals where the integrand contains $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$ and $\mu_n(y) \approx e^{y/2}$. For instance, the expected adjusted local clustering function $c_\infty(k)$ in $G_\Pcal$ equals
\[
	\frac{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \Delta_{\Pcal}(y) e^{-\alpha} \dd y}
	{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} e^{-\alpha} \dd y},
\]
where $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$.

In particular, the average degree of a node at height $y$ is approximately Poisson with mean $\xi_{\alpha,\nu} e^{y/2}$ while we are interested in those nodes with degree $k_n$. Since Poisson random variables are well concentrated around their mean, for our analysis we would therefore like to be able the integration to intervals where $e^{y/2} \approx k_n$. Moreover, we want to be able to do this for all three Poisson models $G_{\HP,n}$, $G_{\Pcal,n}$ and $G_\Pcal$ as well as simultaneously deal with the case where $k_n \to \infty$ and $k_n = \bigT{1}$. In this section we will establish such a result. We start with a concentration lemma for the infinite model (Lemma~\ref{lem:concentration_argument}) and explain in Remark~\ref{rmk:concentration_argument} how such a result will be used throughout the paper. To obtain similar results for the other two models we have to first analyze the average degree in these models which we do in Sections~\ref{ssec:average_degree_HP_n} and~\ref{ssec:average_degree_P_n}. We conclude this section with a general result that allows us to extend the concentration lemma for the infinite model to the hyperbolic random graph and finite box model.

\subsection{Concentration argument for the infinite model}

Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with mean $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$. 
For any sequence $\{k_n\}_{n \ge 1}$, possibly constant, define
\begin{equation}\label{eq:def_kappa_n}
	\kappa_n := \begin{cases}
		\log(n) &\mbox{if } k_n = \bigT{1},\\
		\sqrt{k_n \log(k_n)} &\mbox{else.}
	\end{cases}
\end{equation}
and define further, for any $C > 0$
\begin{equation}\label{eq:def_K_C_set}
	\Kcal_C(k_n) = \left\{p \in \R : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \wedge e^{R_n/2} \right\},
\end{equation}
Note that if $k_n = \Omega(\log(n))$ then $e^{y/2} = \bigT{k_n}$ whenever $p \in \Kcal_C(k_n)$. The next lemma states that for a large class of functions $h(y)$ to compute the integral 
\[
	\int_{\Rcal_n} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y
\]
it is enough to consider integration of $\Kcal_C(k_n)$ instead of $\Rcal_n$.

\begin{lemma}\label{lem:concentration_argument}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $\{k_n\}_{n \ge 1}$ be any sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$. In addition let $\beta < \alpha$ and $h : \R_+ \mapsto \R$ be a any function such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$. Then, for any $C > 0$,
\begin{equation}\label{eq:error_bound_int_rho_not_K}
\begin{aligned}
	&\hspace{-30pt} \int_{\Rcal_n \setminus \Kcal_{C}(k_n)} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y\\
	&= \begin{cases}
		\bigO{n^{1 - \frac{C}{2}}} &\mbox{if } k_n = \bigT{1} \\
		\bigO{n \left(k_n^{-(1+C^2)/2} + k_n^{-1/2} e^{-\frac{C\sqrt{k_n \log(k_n)}}{2}}\right)} &\mbox{else.}
	\end{cases}
\end{aligned}
\end{equation}
as $n \to \infty$.

In particular, if $g_n(y)$ is a function such that $g_n(y) = \bigO{n^{-1} k_n^{\beta}}\rho(y,k_n)$ for some $s \in \R$. Then for $C > 0$ large enough we have
\[
	\lim_{n \to \infty} \int_{\Rcal_n \setminus \Kcal_{C}(k_n)} g_n(y) f_{\alpha,\nu}(x,y) \dd x\dd y = 0,
\]
or equivalently,
\[
	\int_{\Rcal_n} \hspace{-5pt} g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y
	= (1+\smallO{1}) \int_{\Kcal_{C}(k_n)} \hspace{-5pt} g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
\]
\end{lemma}

\begin{proof}
Define 
\[
	\lambda_n^\pm = k_n \pm C \kappa_n, 
	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right).
\]
Then, since $\rho_{y}(k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$
\begin{align*}
	&\hspace{-20pt}\int_{\Rcal_n \setminus \Kcal_C(k_n)} h(y) \rho_{k_n}(y) 
		f_{\alpha,\nu}(x,y) \dd x \dd y\\
    &= \bigO{1} \int_0^{a_n^-} \int_{-I_n}^{I_n} e^{\beta y} \rho_{k_n}(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
    	+ \int_{a_n^+}^{R_n} \int_{-I_n}^{I_n} e^{\beta y} \rho_{k_n}(y) f_{\alpha,\nu}(x,y) \dd x \dd y \\
    &= \bigO{n} \int_0^{a_n^-} \rho_{k_n}(y) e^{-(\alpha-\beta) y} \dd y 
   		+ \bigO{n} \int_{a_n^+}^{R_n} \rho_{k_n}(y) e^{-(\alpha-\beta) y} \dd y\\
   	&\le \bigO{n}\rho(a_n^-,k_n)\int_0^{a_n^-} e^{-(\alpha-\beta) y} \, \dd y
   		+ \bigO{n} \rho(y,a_n^+) \int_{a_n^+}^{R_n} e^{-(\alpha-\beta) y} \, \dd y.
\end{align*}
Note that if $k_n = \bigT{1}$ then, for large enough $n$, the first integral is zero, it is $O(1)$ when $k_n \to \infty$. Because $\alpha > \beta$ the second integral is always $\bigO{1}$. Therefore

\begin{equation}\label{eq:concentration_lemma_integral_bound}
\begin{aligned}
	&\hspace{-30pt}\int_{\Rcal_n \setminus \Kcal_C(k_n)} h(y) \rho_{k_n}(y) f_{\alpha,\nu}(x,y) \dd x \dd y \\
	&= \begin{cases}
		\bigO{n} \rho(a_n^+,k_n) &\mbox{if } k_n = \bigT{1},\\
		\bigO{n} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right) &\mbox{else.}
	\end{cases}	
\end{aligned}
\end{equation}

We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^-,k_n)$. Note we only need to bound $\rho(a_n^-,k_n)$ when $k_n \to \infty$, in which case $\kappa_n = \sqrt{k_n \log(k_n)}$. Using that $k! > \sqrt{2\pi} k^{k + 1/2} e^{-k}$ we write
\begin{align*}
	\rho(a_n^-,k_n) &\le \frac{\mu(a_n^-)^{k_n}}{k_n!} e^{-\mu(a_n^-)} 
		\le (2\pi)^{-1/2} k_n^{-(k_n + 1/2)} e^{-(\mu(a_n^-) - k_n)}\\
	&= (2\pi)^{-1/2} k_n^{-1/2} 
		e^{-k_n\left(\frac{\mu(a_n^-)}{k_n} - 1 - \log\left(\frac{\mu(a_n^-)}{k_n}\right)\right)}.
\end{align*}
Since 
\[
	\frac{\mu(a_n^-)}{k_n} = \frac{\lambda_n^-}{k_n} = 1 - C \frac{\kappa_n}{k_n} = 1 - C \sqrt{\frac{\log(k_n)}{k_n}},
\]
and $-x - \log(1 - x) = \Omega(x^2/2)$, we get
\begin{align*}
	\rho(a_n^-,k_n) 
	&\le \sqrt{2\pi} k_n^{-1/2} 
		e^{-k_n\left(-C \frac{\kappa_n}{k_n} - \log\left(1 + C \frac{\kappa_n}{k_n}\right)\right)}\\
	&\le (2\pi)^{-1/2} k_n^{-1/2} e^{-\Omega\left(\frac{C^2 \log(k_n)}{2}\right)} = \bigO{k_n^{-(1+C^2)/2}}.
		\numberthis \label{eq:concentration_lemma_bound_an-}
\end{align*}

For $a_n^+$ we again use the bound for $k!$ to get
\begin{align*}
	\rho(a_n^+,k_n) &\le \frac{\mu(a_n^+)^{k_n}}{k_n!} e^{-\mu(a_n^+)} 
		\le (2\pi)^{-1/2} k_n^{-(k_n + 1/2)} e^{-(\mu(a_n^+) - k_n)}\\
	&= (2\pi)^{-1/2} k_n^{-1/2} 
		e^{-k_n\left(\frac{\mu(a_n^+)}{k_n} - 1 - \log\left(\frac{\mu(a_n^+)}{k_n}\right)\right)}.
\end{align*}
Since 
\[
	\frac{\mu(a_n^+)}{k_n} = \frac{\lambda_n^+}{k_n} = 1 + C \frac{\kappa_n}{k_n},
\]
with $\kappa_n/k_n = \omega(1)$ as $n \to \infty$, and $x - \log(1 + x) = \omega(x/2)$ as $x \to \infty$, we get
\begin{equation}\label{eq:concentration_lemma_bound_an+}
	\rho(a_n^+,k_n) \le \sqrt{2\pi} k_n^{-1/2} 
		e^{-k_n\left(C \frac{\kappa_n}{k_n} - \log\left(1 + C \frac{\kappa_n}{k_n}\right)\right)}
	= \bigO{k_n^{-1/2} e^{-\frac{C \kappa_n}{2}}}.
\end{equation}

Plugging~\eqref{eq:concentration_lemma_bound_an-} and~\eqref{eq:concentration_lemma_bound_an+} into~\eqref{eq:concentration_lemma_integral_bound} yields the result. The second statement immediately follows by our choice of $C$.

To see that the same holds when we use $\rho_n(y,k_n)$ it satisfies similar bounds as $\rho(y,k_n)$ for $y \in \Rcal_n \setminus \Kcal_\eps(k_n)$ hold for. We first note that $\mu_{\alpha, \nu}(\BallPon{y}) = \mu_{\alpha, \nu}(\BallPo{y})(1 - \phi_n(y))$ where $\phi_n(y) = \bigT{e^{-(\alpha - \frac{1}{2})(R_n - y)}}$, see Lemma~\ref{lem:average_degree_P_n}. In particular we have that $\mu_{\alpha, \nu}(\BallPon{y})$ is increasing in $y$ and hence for $0 \le y \le a_n^-$
\[
	\rho_n(y,k_n) \le \rho_n(a_n^-,k_n) \le \rho(a_n^-,k_n) \le 2 k_n^{-\frac{\varepsilon^2}{4}}.
\]
It remains to show that the same holds for $a_n^+ \le y \le R_n$. For this we define 
\[
	\lambda_n := \mu_{\alpha, \nu}(\BallPon{a_n^+}) = \left(k_n + C \sqrt{k_n \log(k_n)}\right)
	\left(1 - \phi_n(a_n^+)\right),
\] 
and note that $\lambda_n \ge k_n$ for large enough $n$. Hence
\begin{align*}
	\rho_n(y,k_n) &\le \rho_n(a_n^+,k_n) = \Prob{\Po(\mu_{\alpha, \nu}(\BallPon{a_n^+})) = k_n}\\
	&\le \Prob{\left|\Po(\lambda_n) - \lambda_n\right| \ge k_n - \lambda_n} \le 2e^{-\frac{(k_n - \lambda_n)^2}{2(k_n + \lambda_n)}}.
\end{align*}
To finish the argument we observe that $k_n + \lambda_n \le 2k_n$ and $(k_n - \lambda_n)^2 \ge C^2 k_n \log(k_n)$ for $n$ large enough. Therefore
\[
	\rho_n(y,k_n) \le 2e^{-\frac{(k_n - \lambda_n)^2}{2(k_n + \lambda_n)}} = \bigO{k_n^{-\frac{C^2}{4}}}
\] 
which finishes the proof.
\end{proof}

\begin{remark}[Concentration argument]\label{rmk:concentration_argument}
Lemma~\ref{lem:concentration_argument} will prove very useful in the remainder of this paper since we often have to deal with integrands of the form $g_n(y) f_{\alpha,\nu}(x,y)$ where $g_n(y) = \bigO{n^{-1} k_n^{s}}\rho(y,k_n)$ for some $s \in \R$. In this case the lemma tells us that for a suitable $C > 0$ we only need to integrate over $\Kcal_C(k_n)$. In order words, we may always assume for $g_n(y)$ (for a penalty of $\smallO{1}$) that $k_n - C \kappa_n \le \xi_{\alpha,\nu} e^{y/2} \le k_n + C \kappa_n$. We will refer to this as a \emph{concentration argument}, e.g. \emph{by a concentration argument}
\[
	\int_{\Rcal_n} g_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y 
	= (1+\smallO{1}) \int_{\Kcal_C(k_n)} \rho(y,k_n) g_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y.
\]
\end{remark}

\subsection{Average degree in the Hyperbolic graph}\label{ssec:average_degree_HP_n}

Recall that under the coupling between the hyperbolic random graph and the finite box model $|x-x^\prime|_{\pi e^{r_n/2}} \le \Omega(r,r^\prime)$, while the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that  
\[
	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Omega(r, r^\prime) 
		\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
\]
for $y + y^\prime < R_n$. This result enables us to determine the measure of a ball around a given point $p=(0,y)$ which will be fairly useful in our subsequent analysis.

\begin{lemma}\label{lem:average_degree_hyperbolic}
Let $\eps \in (0, 1)$. Then for all $0 \le y \le (1 - \eps)R_n$
\[
	 1 - \phi_{\H,n}^{(1)}(y) - \phi_{\H,n}^{(2)}(y) \le \frac{\Mu{\BallHyp{0,y}}}{\Mu{\BallPo{0,y}}} 
	 \le 1 - \phi_{\H,n}^{(1)}(y) + \phi_{\H,n}^{(2)}(y),
\]
where
\[
	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 3}{2} e^{-(\alpha - \frac{1}{2})(R_n - y)} 
		+ \frac{2\alpha - 1}{2}e^{-(\alpha - \frac{1}{2})R_n - y/2},
\]
and
\[
	\phi_{\H,n}^{(2)}(y) = 
	+ \begin{cases}
			\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(R_n - y)}\right)
			&\mbox{if } 1/2 < \alpha < 3/2,\\
			\frac{(2\alpha -1)K}{2} (R_n - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
			&\mbox{if } \alpha > 3/2.
		\end{cases}
\]
\end{lemma}

\begin{proof}
We will split the computation of $\Mu{\BallHyp{0,y}}$ over the case $y^\prime > R_n - y$ and $y^\prime \le R_n - y$ where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}. Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = 4\nu \alpha/(2\alpha - 1)\pi$. \PvdH{Check computations below for new $\xi_{\alpha,\nu} = 4\nu \alpha/(2\alpha - 1)\pi$}

By~\eqref{eq:tail_inclusion_hyperbolic_ball}, we have $\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])= \Rcal_n([R_n-y,R_n])$. 
Thus, 
\begin{align*}
	&\hspace{-30pt}\Mu{\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])} \\
	&= \int_{R_n - y}^{R_n} \int_{I_n} f_{\alpha,\nu}(x^\prime, y^\prime) \dd x^\prime \dd y^\prime
		= \nu \alpha e^{R_n/2}\left(e^{-\alpha(R_n - y)} - e^{-\alpha R_n}\right)\\
	&= \Mu{\BallPo{0,y}} \frac{2\alpha - 1}{2}\left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
		- e^{-(\alpha - \frac{1}{2})R_n - y/2}\right) \numberthis \label{eq:mu_hyperbolic_ball_part_1}
\end{align*}

Next we will establish upper and lower bounds on $\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]}$. Using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} we have 
\begin{align*}
	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} 
	&\le \nu \alpha \int_{0}^{R_n - y} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R_n}\right)
		e^{-\alpha y^\prime} \dd y^\prime\\
	&= \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right) \\
	&\hspace{10pt}+ \nu \alpha K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
\end{align*}
The last integral depend on the value of $\alpha$,
\[
	\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
	= \begin{cases}
		\frac{2}{3 - 2\alpha}\left(e^{(\frac{3}{2} - \alpha)(R_n - y)} - 1\right) &\mbox{if } 1/2 < \alpha < 3/2,\\
		R_n - y &\mbox{if } \alpha = 3/2,\\
		\frac{2}{2\alpha-3}\left(1 - e^{-(\alpha - \frac{3}{2})(R_n - y)}\right) &\mbox{if } \alpha > 3/2.
	\end{cases}
\]
Therefore we get
\begin{align*}
	&\hspace{-30pt}\nu \alpha K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime\\
	&= \Mu{\BallPo{0,y}}\begin{cases}
		\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(R_n - y)}\right)
		&\mbox{if } 1/2 < \alpha < 3/2,\\
		\frac{(2\alpha -1)K}{2} (R_n - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
		\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
		&\mbox{if } \alpha > 3/2.
	\end{cases}\\
	&= \Mu{\BallPo{0,y}} \phi_{\H,n}^{(2)}(y)
\end{align*}
and hence
\[
	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} = \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(R_n - y)} 
	+ \phi_{\H,n}^{(2)}(y)\right).
\]
Combining this with~\eqref{eq:mu_hyperbolic_ball_part_1} yields the required upper bound.

The lower bound follows by observing that the only difference with the above computations is the change of sign in front of 
\[
	\nu \alpha K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime.
\]
\end{proof}

\subsection{Average degree in the finite box model}\label{ssec:average_degree_P_n}

For the finite box model $G_{\Pcal,n}(\alpha, \nu)$ we obtain a similar result for the average degree.

\begin{lemma}\label{lem:average_degree_P_n}
For all $p \in \Rcal_n$, such that $y > 2\log(\pi/2)$,
\[
	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right)
\]
where $\phi_n(y) \ge 0$ is given by
\[
	\phi_n(y) = \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)}e^{-(\alpha-\frac{1}{2})(R_n - y)}
	- \frac{(2\alpha - 1)\pi}{4\alpha}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} 
	e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(\alpha - \frac{1}{2})R_n - \frac{y}{2}}\right).
\]
If, on the other hand, $y \le 2 \log(\pi/2)$ then
\[
	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
\]
\end{lemma}

\begin{proof}
First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$. We then have that
\[
	\BallPon{p} = \left\{p^\prime \in \Rcal_n \, : \, |x^\prime|_n \le e^{\frac{y + y^\prime}{2}}\right\},
\] 
whose boundaries given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$ intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
\[
	h(y) = R_n + 2 \log\left(\frac{\pi}{2}\right) - y.
\]
Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R_n$ of the box $\Rcal_n$ while in the other case the full region of the box above $h(y)$ is connected to $p$.

We will first consider the case where $y > 2 \log(\pi/2)$. Recall that $\mu_{\alpha,\nu}(B_\Pcal(p)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$ where $\xi_{\alpha,\nu} = \frac{4\alpha \nu}{(2\alpha - 1)\pi}$. Then, after some simple algebra, we have that
\begin{align*}
	\mu_{\alpha,\nu}(B_{\Pcal,n}(p))
	&= \int_0^{h(y)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
	&\hspace{10pt}+ \int_{h(y)}^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{h(y)} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime
		+ \alpha \nu e^{\frac{R_n}{2}} \int_{h(y)}^{R_n} e^{-\alpha y^\prime} \, dy^\prime \\
	&= \xi_{\alpha,\nu} e^{\frac{y}{2}}\left(1 - \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} 
		e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)\\
	&\hspace{10pt}+ \nu e^{\frac{R_n}{2}}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} e^{-\alpha(R_n - y)} 
		- e^{-\alpha R_n}\right)\\
	&= \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right).
\end{align*}
Since, for all $\alpha > \frac{1}{2}$,
\[
	\left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} \ge \frac{(2\alpha - 1)\pi}{4\alpha} \left(\frac{\pi}{2}\right)^{-2\alpha}
\]
it follows that $\phi_n(y) \ge 0$.

When $y \le 2 \log(\pi/2)$ we have
\begin{align*}
	\mu_{\alpha,\nu}(B_{\Pcal,n}(p))
	&= \int_0^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R_n} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
	&= \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
\end{align*}
\end{proof}

\subsection{Concentration argument for Hyperbolic and finite box models}

Next we establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the degree distributions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$ in $G_{\HP,n}$ and $G_{\Pcal,n}$, respectively.

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any increasing sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$ and $\Kcal_{C}(k_n)$ defined as in~\eqref{eq:def_K_C_set} for some $C > 0$. In addition, let $\hat{\mu}_n(y)$ be any function satisfying 
\[
	\Mu{\BallPo{0,y}}(1 - \phi_n^{(1)}(y)) \le \hat{\mu}_n(y) \le \Mu{\BallPo{0,y}}(1 + \phi_n^{(2)}(y))
\]
where $\phi_n^{(i)} : \R_+ \to \R_+$ are such that $\sup_{0 \le y \le R_n} \phi_n(y)^{(i)} = \smallO{1}$. Then if we define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, we have, for any $\beta < \alpha$,
\[
	\int_{\Rcal_n} \hat{\rho}_n(y,k_n) e^{\beta y} f_{\alpha,\nu}(x,y) \dd x \dd y 
	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) e^{\beta y} f_{\alpha,\nu}(x,y) \dd x \dd y.
\]
\end{lemma}

\begin{proof}
Similar to the proof of Lemma~\ref{lem:concentration_argument} we define 
\[
	\lambda_n^\pm = k_n \pm \varepsilon \sqrt{k_n \log(k_n)}, \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right),
\] 
and for simplicity write
\[
	\mu_1(y) := \mu_{\alpha,\nu}\left(\BallPo{y}\right) \quad \text{and} \quad 
	\mu_2(y) = \mu_{\alpha,\nu}\left(\BallPon{y}\right).
\]
Next we notice that for all $y > a_n^+$, $\mu_2(y) \ge \mu_1(a_n^+)(1 - \phi_n^{(1)}) = \omega(k_n)$ and hence
\begin{align*}
	\hat{\rho}_n(y,k) &\le \frac{\mu_1(y)^k(1 + \phi_n^{(2)}(y))^k}{k!} e^{-\mu_1(y)} e^{-\mu_1(y)\phi_n^{(2)}(y)}  \\
	&= \rho(y,k) e^{k \log\left(1 +  \phi_n^{(2)}(y)\right) - \mu_1(y) \phi_n^{(2)}(y)}\\
	&= \rho(y,k) \bigO{e^{(k - \mu_1(y))\phi_n^{(2)}(y)}}\\
	&= \rho(y,k) \bigO{e^{-C \kappa_n \phi_n^{(2)}(y)}} = \rho(y,k) \bigO{1}.
\end{align*}
Similar we have for all $y < a_n^-$,
\begin{align*}
	\hat{\rho}_n(y,k) &\le \frac{\mu_1(y)^k(1 - \phi_n^{(1)}(y))^k}{k!} e^{-\mu_1(y)} e^{\mu_1(y)\phi_n^{(1)}(y)}\\
	&= \rho(y,k) \bigO{e^{(k + \mu_1(y))\phi_n^{(1)}(y)}} \\
	&= \rho(y,k) \bigO{e^{-C \kappa_n \phi_n^{(1)}(y)}} = \rho(y,k) \bigO{1}.
\end{align*}

Therefore, by Lemma~\ref{lem:concentration_argument}, it is enough to show that
\[
	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha) y} \dd y = (1+o(1))\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) e^{(\beta - \alpha) y} \dd y.
\]

For this let us make a change of variables $y \to z$ such that
\[
	\mu_2(y) = \mu_1(z).
\]
and note that since
\[
	\mu_1^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
\]
is strictly monotonic in $y$, we have
\[
	z(y) \le 2 \log\left(\frac{\mu_1(y)}{\xi_{\alpha,\nu}}\right) + 2 \log\left(1 + \phi_n^{(2)}(y)\right)
	= y + 2 \log\left(1 + \phi_n^{(2)}(y)\right),
\]
and similarly
\[
	z(y) \ge y + 2 \log\left(1 + \phi_n^{(2)}(y)\right).
\]
Hence, for all $a_n^- \le y \le a_n^+$,
\begin{equation}
	e^{(\beta-\alpha) y} = (1 + o(1))e^{(\beta-\alpha) z}.
\end{equation}
For the derivatives we have, for $a_n^- \le y \le a_n^+$, $\mu_1^\prime(y) = \mu_1(y)/2$, while $(\phi_n^{(i)})^\prime(y) = O(1)$ and hence
\begin{align*}
	\mu_2^\prime(y) = \mu_1^\prime(y)\left(1 + o(1)\right).
\end{align*}
Therefore, with this change of variables, and using
\[
	\hat{a}_n^\pm := z(a_n^\pm) = a_n^\pm(1 + \smallO{1}),
\] 
we have
\begin{align*}
	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
	&=  \int_{a_n^-}^{a_n^+} \Prob{\mathrm{Po}\left(\mu_2(y) = k_n\right)} e^{(\beta-\alpha) y} \dd y\\
	&= (1 + \smallO{1})\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\mathrm{Po}\left(\mu_1(z) = k_n\right)}
		e^{-\alpha z} \frac{\mu_2^\prime(z)}{\mu_2^{\prime}(z)} \, dz\\
	&= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(y,k_n) e^{(\beta-\alpha) z} \, dz.
\end{align*}
\end{proof}

Observe that Lemma~\ref{lem:average_degree_P_n} implies that $\Mu{\BallHyp{(0,y)}}$ satisfies the requirements in Lemma~\ref{lem:concentration_argument_rho_approximation}. Lemma~\ref{lem:average_degree_hyperbolic} states that $\Mu{\BallPon{0,y}}$ satisfies these requirement when $y \le (1-\eps)R_n$. However, since for all $\eps < (2\alpha - 1)/2\alpha$
\[
	\Mu{\BallHyp{0,y} \cap \Rcal_n[(1-\eps)R_n, R_n]} = \bigO{e^{\frac{R_n}{2} - \alpha(1-\varepsilon)R_n}}
	= \bigO{n^{1 - 2\alpha(1 -\eps)}} = \smallO{1},
\]
the conclusion of Lemma~\ref{lem:concentration_argument_rho_approximation} still holds for this case. We therefore have the following important Corollary.

\begin{corollary}\label{cor:concentration_argument_other_models}
Let $\hat{\rho}_n(y,k)$ be any of the two distribution functions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$. Then, for any function $g_n(y)$ such that $g_n(y) = \bigO{n^{-1} k_n^{s}}\hat{\rho}_n(y,k_n)$, as $n \to \infty$, for some $s \in \R$,
\[
	\int_{\Rcal_n} g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y
	= (1+\smallO{1})\int_{\Kcal_C(k_n)} g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y,
\]
for some $C > 0$ large enough.
\end{corollary}

In particular we conclude that, similar to the infinite limit model, concentrations arguments as described in Remark~\ref{rmk:concentration_argument} can be applied in the case of the hyperbolic random graph and finite box model.

%\begin{lemma}
%\[
%	\Prob{D_{\HP,n}= k_n} = (1 + \smallO{1})\Prob{D_\Pcal = k_n}
%\]
%\end{lemma}

### 2018-10-16 introduction.tex
Initial ShareLaTeX Import

\section{Introduction and results}

\subsection{Motivation}

\MS{Some ideas:
\begin{enumerate}
\item Hyperbolic random graphs as an alternative to Euclidean/standard random geometric graphs
\end{enumerate}
}

\PvdH{Add intro on common features of complex networks and modeling of such networks.}
\MS{I would not write a length introduction to complex networks here (because the paper is quite long already and we do not study networks in general in this paper). So, I would remove the first paragraph/list (or incorporate it as a single sentence in the ensuing paragraph). }
The main topological features shared among many complex networks are:
\begin{enumerate}[\upshape 1)]
\item Broad degree distribution (power-law/scale-free)
\item Strong clustering (community structure)
\item Small path lengths (small world phenomenon)
\end{enumerate}

Hyperbolic random graphs were suggested as a suitable model for complex networks by Krioukov et al.~\cite{krioukov2010hyperbolic}. Indeed, in their seminal paper they show that these graphs have a power-law degree distribution and exhibit strong clustering. In addition it was found that hyperbolic random graphs have doubly logarithmic shortest path lengths~\cite{bringmann2016average} and allow for efficient routing algorithms~\cite{bringmann2017greedy}. Many other results regarding hyperbolic random graphs have since been established. These include size of the largest component~\cite{BodeFountoulakisMuller2015},~\cite{fountoulakis2018law}, [More?] and number of cliques and largest clique~\cite{blasius2018cliques}.

The aim of this paper is to study local clustering in hyperbolic random graphs. The first rigorous mathematical analysis of the local clustering coefficient was done by Gugelmann et al.~\cite{gugelmann2012random}. They show~\cite[Theorem 2.1]{gugelmann2012random} that the local clustering coefficient is concentrated around its expectation which is shown to be $\bigT{1}$ as the number of vertices tends to infinity. In particular this results implies that the local clustering coefficient is asymptotically bounded away from zero. The convergence of this coefficient was not proven. In contrast, the global clustering coefficient was shown~\cite{candellero2016clustering} to converge in probability to some constant which can be explicitly stated as an integral expression, see Theorem 1.2 in \cite{candellero2016clustering}. The authors mention, however, that their analysis needs significant modification to be able to deal with convergence of the local clustering coefficient.

In addition to the clustering coefficients, an important clustering measure that is often studied is the local clustering function $c(k)$. This function computes for any value of $k$ the average of the local clustering coefficient over all vertices of degree $k$. A general expression of this function for hyperbolic random graphs is given in \cite[Equation (59)]{krioukov2010hyperbolic}. The authors conjecture that as $k$ tends to infinity, $c(k)$ decays as $k^{-1}$, which they observe (Figure 8 in \cite{krioukov2010hyperbolic}) in experiments on the infrastructure of the Internet obtained in~\cite{claffy2009internet}. However, despite the importance of the local clustering function and these interesting observations, its behavior in hyperbolic random graphs had not been completely determined and the following crucial questions regarding clustering in hyperbolic random graphs remained open so far:
\begin{enumerate}[\upshape 1)]
\item Does the local clustering coefficient converge, and if so, what is the limit?
\item What is the limit of the local clustering function and how does it scale with the degree?
\end{enumerate}

In this work we resolve these important open questions. We obtain the asymptotic scaling of $c(k)$ as $k \to \infty$, including the leading constant, as well as an exact expression, in terms of known special functions, of the point-wise limit of the local clustering function as the number of vertices tends to infinity. Interestingly, the scaling of $c(k)$ depends on the exponent of the degree distribution and is only $k^{-1}$ when this exponent exceeds $5/2$. For values less than $5/2$ the scaling is $k^{-s}$ where the value of $s$ depends on the degree distribution exponent. Finally, our analysis allows us to also prove a convergence result for the local clustering coefficient where the limit can again be explicitly expressed in terms of known special functions.

\subsection{Outline of the paper}

In the next two subsections \ref{ssec:hyperbolic_model} and \ref{ssec:local_clustering} of the introduction, we give the definitions of the hyperbolic random graph and of the local clustering coefficient and function as used in this paper. After this we present our main results in Section \ref{ssec:main_results} and discuss several insights that can be obtained from them and in Section \ref{ssec:simulations} show simulations which confirm these results. Section \ref{sec:proof_outline} contains a detailed high level outline of the proofs of our main results, split up into different propositions. The proofs of these propositions can be found in the last four sections while Section~\ref{sec:concentration_argument} contains a crucial technical result regarding that will be used through the other sections.

\subsection{Hyperbolic random graphs}\label{ssec:hyperbolic_model}

%, which without loss of generality we take to be $-1$~[CITE]
%The \emph{Poincar\'{e} disc model} for the hyperbolic plane is defined by equipping the open unit disc in $\R^2$ with the metric given by the differential form $\dd s^2 = 4 \frac{\dd x^2 + \dd y^2}{(1 - x^2 - y^2)^2}$.
The hyperbolic plane is an infinite $2$-dimensional manifold with constant negative curvature. Many different representations of the hyperbolic plane exist and we refer to [CITE] for more details.  We will work with the \emph{native representation} of the hyperbolic plane which takes the elements of $\R^2$ in polar coordinates $(r,\theta)$ as the underlying set of points and where distances are determined by the hyperbolic law of cosines.

Let $\alpha > \frac{1}{2}$, $\nu > 0$ and define $R_n = 2\log(n/\nu)$. Then the hyperbolic random graph $G_{\H,n}(\alpha, \nu)$ is defined as follows:
\begin{enumerate}
\item The vertex set if given by $n$ points $u_1, \dots, u_n$ denoted in polar coordinates $(r_i, \theta_i)$, where the angular coordinate $\theta$ is chosen uniformly from $(-\pi,\pi]$ while the radial coordinate $r$ is sampled independently according to the cumulative distribution function
\begin{equation}\label{eq:def_hyperbolic_point_distribution}
	F_{n,\alpha,\nu}(r) = \begin{cases}
		0 &\mbox{if } r < 0\\
		\frac{\cosh(\alpha r)-1}{\cosh(\alpha R_n) - 1} &\mbox{if } 0 \le r \le R_n\\
		1&\mbox{if } r > R_n
	\end{cases}
\end{equation}
\item Any two vertices $u_i=(r_i,\theta_i)$ and $u_j=(r_j,\theta_j)$ are adjacent if and only if $d_\H(u_i,u_j) \le R_n$, where $d_\H$ denotes the distance in the hyperbolic plane, i.e.
\[
	\cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R_n),
\]
as follows from the hyperbolic cosine rule[CITE?].
\end{enumerate}

\begin{figure}[!t]
\centering
\includegraphics[scale=0.5]{figures/HyperRGG_N5000L5.eps}
\caption{Example of a Hyperbolic Random Graph $G_{\H,n}(\alpha, \nu)$ with $\alpha = ??$, $\nu = ??$ and $n = 500$.}
\label{fig:H_graph_example}
\end{figure}

Figure~\ref{fig:H_graph_example} shows an example of $G_{\H,n}(\alpha, \nu)$.

%We say that the points $u_i \in G_{\H, n}$ are distributed according to a \emph{$(\alpha, R_n)$-quasi uniform distribution}.

\subsection{Clustering}\label{ssec:local_clustering}

Clustering measures for networks consider the fraction of triangles (triples of connected vertices) in the network. 
\MS{Do we need the definition of the global clustering coefficient? Also, I thought it was defined as 3 times number of triangles divided by number of length 2 paths and I do not see yet whether this agrees with the definition below.}
For instance, Let $G$ be a simple graph, with vertex set $V(G)$ and edge set $E(G)$ and denote by $T_G$ the total number of triangles in $G$. Then the global clustering coefficient is defined as
\[
	c_G = \frac{\T_G}{\binom{E(G)}{2}}.
\]
This coefficient measures the fraction of triangles in the network compared to the total possible number of triangles. A different global measure for clustering, \emph{local clustering coefficient} computes the average triangle density per node. To define this function, let $D_G(v)$ denote the degree of node $v$ and $N_G(k)$ the number of nodes with degree $k$ in the graph $G$. In addition let $\T_G(v,v_1,v_2) = \ind{(v,v_1) \in E} \ind{(v, v_2) \in E} \ind{(v_1, v_2) \in E}$ be the indicator that $v, v_1$ and $v_2$ form a triangle and write
\begin{equation}
	\T_G(v) = \sum_{v_1, v_2 \in V(G)} \T_G(v,v_1,v_2),
\end{equation}
to denote the number of triangles in which node $v$ participates. Then the local clustering coefficient is given by
\[
	c_G = \frac{1}{|V(G)|} \sum_{v \in V(G)} \frac{T_G(v)}{\binom{D_G(v)}{2}}.
\]

However, since the local clustering coefficient assigns just one value to the whole network, representing its triangular structure, it is unable to characterize local structural properties involving triangles. The local clustering function, on the other hand, measures the fraction of triangles to which nodes of a given degree belong, compared to the maximum number of triangles in which they could participate. It therefore characterizes the triangular structure of nodes in the networks, based on their degree, and gives a more detailed look at the overall structure of the network.

The local clustering function is formally defined as
\begin{equation}\label{eq:def_local_clustering_general}
	c_{G}(k) = \begin{cases}
		\frac{1}{N_G(k)} \sum_{v \in V(G)}  \ind{D_G(v) = k} \frac{\T_G(v)}{\binom{k}{2}} &\mbox{if } N_G(k) \ge 1\\
		0 &\mbox{else.}
	\end{cases}
\end{equation}

We note that other versions of the local clustering function have been considered, for instance where nodes with degree larger than $k$ are considered instead of nodes with degree exactly $k$. \PvdH{Motivate our choice for this local clustering function.}

\begin{remark}[Notational convention]\label{rmk:notation}
In the remainder of this paper we will compare the local clustering function and many other characteristics between several different graph models. To make notation less cluttered we will often use a unique subscript to identify the graph with respect to which the specific property refers instead of the full graph description. For instance, we shall write $c_{\H,n}(k)$ to denote $c_{G_{\H,n}(\alpha, \nu)}(k)$ and similar, $D_{\H, n}(u)$ for $D_{G_{\H,n}(\alpha, \nu)}(u)$. For the infinite model we will use the subscript $\infty$.
\end{remark}

\subsection{Main results}\label{ssec:main_results}

We are now ready to state our main results for the clustering coefficient and local clustering function in the hyperbolic random graph. When the degree $k$ is a growing function of $n$ we are able to exactly compute the asymptotic behavior of $c_{\H,n}(k)$.

The results are obtained by coupling the hyperbolic random graph to an infinite random graph $G_\Pcal(\alpha,\nu)$, which we define in Section~\ref{ssec:infinite_model}, and show that the limit of the local clustering coefficient and function for the hyperbolic random graph are given by those for the infinite model. To express these expressions we define for any $y \in \R_+$ 
\[
	\rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k},
\]
where $\xi_{\alpha,\nu} = (4\alpha \nu)/(2\alpha - 1)\pi$ and $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. In addition we define the (marginal) probability measures on $\Rcal := \R_+ \times \R$ by  
\[
	\eta_{y}(x^\prime, y^\prime) = \frac{\alpha \nu e^{-\frac{y}{2}}}{\xi_{\alpha,\nu} \pi} \, \ind{|x^\prime|<e^{(y+y^\prime)/2}} \, e^{-\alpha y^\prime}
\]	
and let
\begin{equation}\label{eq:def_delta_p}
	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(y, x_1, x_2, y_1, y_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \dd x_1 \dd x_2  \dd y_1  \dd y_2,
\end{equation}
where 
\[
	T_\Pcal(y, x_1, x_2, y_1, y_2) 
	= \ind{|x_1| \, \le \, e^{(y+y_1)/2}}\ind{|x_2| \, \le \, e^{(y+y_2)/2}}\ind{|x_1-x_2| \, \le \, e^{(y_1+y_2)/2}}.
\]

With these expressions we define the limit local clustering coefficient as
\begin{equation}\label{eq:def_average_clustering_infinite_model}
	c_\infty := \alpha \int_0^\infty \Delta_{\Pcal}(y) (1 - \rho(y,0) - \rho(y,1)) e^{-\alpha y} \dd y,
\end{equation}
while the local clustering function limit is defined as
\begin{equation}\label{eq:def_c_infty_k}
	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) e^{-\alpha y} \dd y}.
\end{equation}

Finally to express the local clustering coefficient and function in the infinite limit model we need a couple of special functions.

%\subsubsection{Special functions}
We let $B(a,b)$ denote the beta-function 
%\[
%	B(a,b) = \int_0^1 t^{a-1}(1-t)^{b-1} \, dt
%\]
and $B^-(x,a,b)$ the lower incomplete beta-function
\[
	B^-(x,a,b) = \int_x^1 t^{a-1}(1-t)^{b-1} \, dt.
\]
In addition we write $\Gamma(z)$ for the Gamma function, $\Gamma^+(q,z)$ for the incomplete Gamma function
\[
	\Gamma^+(q,z) = \int_z^\infty t^{q - 1} e^{-t} \dd t
\]
and define $\Gamma^\ast(q,z) := \Gamma^+(1 + q, z) + \Gamma^+(q, z)$. Finally, we write $U(a,b,z)$ for the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $\mathrm{Re}(a), \mathrm{Re}(z) >0$ has the integral representation 
\[
	U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} dt,
\] 
see~\cite[p.255 Equation (2)]{erdelyi1953higher}, and let $\MeijerGnew{m}{\ell}{p}{q}{{\bf a}}{{\bf b}}{z}$ denote Meijer's G-Function~\cite{meijer1946g}, see Appendix~\ref{sec:Meijer_G_functions} for more details.

\subsubsection{Local clustering coefficient}

\PvdH{@All: I would be nice if we could show with simulations how close $c_{\H,n}$ actually is to $c_\infty$ for reasonably large $n$ in practice.}

Our first result shows that the local clustering coefficient in the Hyperbolic random graph converges in expectation to $c_\infty$.

\begin{theorem}[Limit for local clustering coefficient in $G_{\H,n}(\alpha,\nu)$] \label{thm:clustering_coefficient_hyperbolic}
Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then,
\[
	\lim_{n \to \infty} \Exp{\left|c_{\H,n} - c_\infty\right|} = 0.
\]
\end{theorem}

Next we establishes the full expression for the clustering coefficient $c_\infty$ in terms of the special function defined above.

\begin{theorem}[Exact expression for clustering coefficient limit]\label{thm:exact_expression_c_infty}
Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, if $\alpha \ne 1$
\begin{align*}
	c_\infty 
	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}
		{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} 
		+  \frac{2^{-1 - 4 \alpha}}{(\alpha - 1)^2} \\
	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}
		{2 (\alpha - 1) (3 \alpha - 1)} \\
	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{2\alpha} \Gamma^\ast( - 2 \alpha, \xi_{\alpha,\nu})}{4(\alpha-1)}
		+ \frac{\xi_{\alpha,\nu}^{2\alpha + 2}\alpha (\alpha - 1/2)^2 \Gamma^\ast(- 2 \alpha - 2, \xi_{\alpha,\nu})}
		{2(\alpha-1)^2} \\
	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{2\alpha + 1}\alpha (2\alpha - 1) \Gamma^\ast( - 2 \alpha - 1,\xi_{\alpha,\nu})}{(\alpha-1)}
		- \frac{\xi_{\alpha,\nu}^{6\alpha-2}2^{-4\alpha}(3\alpha - 1)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)^2}\\
	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{6\alpha - 2}(\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)} \\
	&\hspace{10pt}- \frac{e^{-\xi_{\alpha,\nu}} \Gamma(2\alpha+1) 
		\left(U(2\alpha+1,1-2\alpha,\xi_{\alpha,\nu}) + U(2\alpha+1,2-2\alpha,\xi_{\alpha,\nu})\right)}{4(\alpha-1)} \\
	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{6\alpha - 2} \Gamma(2\alpha+1)\left( 	
		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi_{\alpha,\nu}}
		+ \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi_{\alpha,\nu}}\right)}{4(\alpha-1)},
\end{align*}
while for $\alpha = 1$,
\begin{align*}
	c_\infty &= \frac{575 - 12 \pi^2}{576} + \frac{\eta^4(7 + \pi^2)\Gamma^\ast(-4, \eta)}{4}\\
	&\hspace{10pt}- \frac{1}{2} \int_0^1 (1 - 4z + 3z^3)\log(1-z)(z + \eta)e^{-\eta/z} \dd z\\
	&\hspace{10pt}- \int_0^1 \Li_2(z)(z^3 + \eta z^2) e^{-\eta/z} \dd z,		
\end{align*}
with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function\footnote{Note that the integrals in the expression for $c_\infty$ for $\alpha = 1$ exists: for the first one note that $1-4z+3z^2=(1-z)(1-3z)$, so the integrand can be bounded by $C(1-z)\log(1-z)$ on $[0,1)$ for some constant $C$, which can be continued continuously to the compact interval $[0,1]$ by noting that the limit for $z \rightarrow 1$ is zero, so the integrand is bounded on a bounded domain and hence, this integral is finite; for the second integral note that $\Li_2(z)$ is bounded by $\Li_2(1)$ on $[0,1]$, which is a series with well-known finite limit, so again the integrand is bounded on a bounded domain and hence the second integral is also finite.}. 
\end{theorem}

\subsubsection{Local clustering function}

We obtain similar results for the local clustering function. The first states that $c_{\H,n}(k)$ is asymptotically equivalent to $c_\infty(k)$ in an $L^1$ sense.

\begin{theorem}[Limit for local clustering function in $G_{\H,n}(\alpha, \nu)$]
\label{thm:asymptotic_local_clustering_hyperbolic}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, 
\[
	\lim_{n \to \infty} \Exp{\left|\frac{c_{\H,n}(k_n)}{c_\infty(k_n)} - 1\right|} = 0.
\]
%where
%\[
%	C_{\alpha,\nu} = \begin{cases}
%		C_\alpha \left(\frac{2\alpha \nu}{\pi\left(\alpha - \frac{1}{2}\right)}\right)^{4\alpha - 2}
%		&\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
%		\frac{2\alpha \nu}{\pi\left(\alpha - \frac{1}{4}\right)} &\mbox{if } \alpha = \frac{3}{4},\\
%		\frac{2\alpha \nu}{\pi\left(\alpha - \frac{3}{4}\right)} &\mbox{if } \alpha \ge \frac{3}{4}
%	\end{cases} 
%\]
%with $C_\alpha$ as defined in \eqref{eq:def_C_alpha}.
\end{theorem}

Next we give an exact expression for $c_\infty(k)$ in terms of the special functions defined earlier.

\begin{theorem}[Exact expression for local clustering function limit]
\label{thm:exact_expression_local_clustering}
Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, for $\alpha \ne 1$
\begin{align*}
	c_\infty(k) 
	&= \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma^+(k-6\alpha + 2,\xi_{\alpha,\nu})}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
		\left(\frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha - 1)^2} + \frac{(\alpha - \frac{1}{2})B^-\left(\frac{1}{2},2\alpha + 1, 2\alpha - 2\right)}{2\alpha(\alpha - 1)}\right)\\
	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma(2\alpha + 1)}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}\\
	&\hspace{10pt}+ \frac{1}{8\alpha(\alpha - 1)}
		\left(\frac{\xi_{\alpha,\nu}^{k-2\alpha}e^{-\xi}U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu})}
		{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}-1\right)\\
	&\hspace{10pt}- \frac{(\alpha - 1/2)^2 \xi_{\alpha,\nu}^2 \Gamma^+(k-2\alpha -2,\xi_{\alpha,\nu})}
		{4(\alpha - 1)^2 \Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
\end{align*}
while for $\alpha = 1$
\begin{align*}
	c_\infty(k) &= \frac{9 \eta^3}{2 k!} 	
		\Gamma^+(k-3,\eta)-\frac{\xi_{\alpha,\nu}^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
\end{align*}
with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function.
\end{theorem}

From the exact expression for $c_\infty(k)$ we obtain its asymptotic behavior as $k \to \infty$. For this we first define, for any $\frac{1}{2} < \alpha < \frac{3}{4}$,
\begin{equation}\label{eq:def_C_alpha}
	C_\alpha = \frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha-1)^2} 
	+ \frac{\alpha - \frac{1}{2}}{2(\alpha - 1)\alpha} B^-(\frac{1}{2},2\alpha + 1, 2\alpha - 2)
	- \frac{1}{4(\alpha - 1)}B(2\alpha, 3\alpha - 4).
\end{equation}
Moreover, to simplify the statement we define the scaling function 
\begin{equation}\label{eq:def_scaling_function}
s_\alpha(k_n) = \begin{cases} 
		k^{4\alpha-1} &\frac{1}{2}<\alpha<\frac{3}{4}, \\
		\frac{k}{\log(k)} & \alpha = \frac{3}{4}, \\
		k &\alpha > \frac{3}{4}.
\end{cases}
\end{equation}

We now have the following result, where the constant $C_\alpha$ emerges when we consider the local clustering function for $\frac{1}{2} < \alpha < \frac{3}{4}$.

\begin{theorem}[Asymptotic behavior of local clustering function limit]\label{thm:asymptotics_average_clustering_P}
Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then,
\[
	\lim_{k \to \infty} \frac{c_\infty(k)}{s_\alpha(k)} 
	= \begin{cases}
			C_\alpha \left(\frac{4\alpha \nu}{\pi\left(2\alpha - 1\right)}\right)^{4\alpha - 2}
			&\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
			\frac{3 \nu}{\pi} &\mbox{if } \alpha = \frac{3}{4},\\
			\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha \ge \frac{3}{4},
	\end{cases}
\]
with $C_\alpha$ as defined in \eqref{eq:def_C_alpha}.
\end{theorem}

The following is an immediate consequence of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.

\begin{corollary}[Asymptotic behavior of local clustering function in $G_{\H,n}(\alpha,\nu)$]
Let $\alpha > \frac{1}{2}$, $\nu > 0$, $(k_n)_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ and $s_\alpha(k)$ defined as in~\eqref{eq:def_scaling_function}. Then, as $n \to \infty$,
\[
	\frac{c_{\H,n}(k_n)}{s_\alpha(k_n)} \, \stackrel{L^1}{\rightarrow} \, 
	\begin{cases}
				C_\alpha \left(\frac{4\alpha \nu}{\pi\left(2\alpha - 1\right)}\right)^{4\alpha - 2}
				&\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
				\frac{3\nu}{\pi} &\mbox{if } \alpha = \frac{3}{4},\\
				\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha \ge \frac{3}{4},
		\end{cases}
\]
where $\stackrel{L^1}{\to}$ denotes converges in expectation.
\end{corollary}

This result completely characterizes the asymptotic behavior of the local clustering function in Hyperbolic Random Graphs. In particular we observe that the conjectured scaling of $k^{-1}$ from~\cite{krioukov2010hyperbolic} only occurs when $\alpha > 3/4$, or equivalently, when the exponent of the pdf of the degree distribution is larger than $5/2$.

\PvdH{@All: It would be nice if we could add some simulations showing this scaling in practice, especially the different regimes.}

The majority of the paper is dedicated to prove Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}, which is based on a sequence of subsequent results for the local clustering function in related random graph models and Theorem~\ref{thm:asymptotics_average_clustering_P}. The exact flow of the argument is explained in Section \ref{sec:proof_outline}. The proof for Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}, using these results, can be found in Section \ref{ssec:proof_main_results}. Here we also give the proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}. The exact result for the local clustering coefficient and function, as well as the proofs of Theorem~\ref{thm:exact_expression_c_infty} and~\ref{thm:asymptotics_average_clustering_P} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P}.

We end this section with some important observations regarding local clustering in hyperbolic random graphs.

\PvdH{Populate these paragraphs}

\paragraph{Transition in the scaling of local clustering}
%Note that Theorem \ref{thm:asymptotic_local_clustering_hyperbolic} implies that for $\frac{1}{2} < \alpha < \frac{3}{4}$ the local clustering $c_{\H,n}(k)$ decays as $k^{-(4\alpha - 2)}$ while for $\alpha > \frac{3}{4}$ it is $k^{-1}$.

\paragraph{Maximum scaling for $k_n$ is $n^{\frac{1}{2\alpha +1}}$}
%Maybe, it would make sense to incorporate this statement into theorem \ref{thm:asymptotic_local_clustering_hyperbolic}, i.e. that the asymptotic behaviour of $c(k_n)$ is not well-defined for $k_n \gg n^{\frac{1}{2\alpha+1}}$? Resp. claim that a.a.s. the number of vertices of degree $k_n \gg n^{\frac{1}{2\alpha+1}}$ is zero, such that taking the average over these is not well-defined.

\paragraph{Universality of scaling transition}

\paragraph{Geometric inhomogeneous random graphs}

%\paragraph{Local clustering for growing versus fixed degrees}
%%The main difference between Theorem \ref{thm:fixed_local_clustering_hyperbolic} and Theorem \ref{thm:asymptotic_local_clustering_hyperbolic} is that for fixed degrees $k$ we have a small correction term that depends on the value $k$. 
%
%\MS{We note that the above statements / theorems are disjoint: in one case the degree is fixed corresponding to a constant sequence and in this case the error only depends on $n$, whereas in the other case, the degrees are assumed to be increasing, so in particular unbounded resp. tending to infinity and only the leading term in the asymptotic expansion w.r.t. $k_n \rightarrow \infty$ is given. This allows to study vertices of relatively high degree, e.g. close to the maximum degree (note that there are a.a.s. no vertices with degree exactly the expected maximum degree of $k_n = n^{\frac{1}{2\alpha}}$).}

%The main difference between Theorem \ref{thm:fixed_local_clustering_hyperbolic} and Theorem \ref{thm:asymptotic_local_clustering_hyperbolic} is that for fixed degrees $k$ we have a small correction term that depends on the value $k$.

\subsection{Simulations}\label{ssec:simulations}

### 2018-10-16 paper.tex
Initial ShareLaTeX Import

\documentclass[a4paper,10pt]{article}
% * <m.f.schepers@rug.nl> 2018-10-12T08:13:57.409Z:
%
% ^.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%											Packages											  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{enumerate}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{bm}
\usepackage[mathscr]{eucal}
\usepackage{a4wide}
\usepackage{authblk}
\usepackage{appendix}
\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    urlcolor = {magenta},
    citecolor = {green},
    linkcolor = {blue}
}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,backgrounds,patterns,decorations.markings,decorations.pathreplacing,intersections}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}

\usepackage{subcaption}
\usepackage{dsfont}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%											Macros												  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                        Probability                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\pr}{\mathbb{P}}								%	short hand for blackboard P
\newcommand{\Pee}{\mathbb{P}}

%% Probability commands %%

\newcommand{\Prob}[1]{\pr\left(#1\right)}					%	Standard probability command, 
															%	argument is event

\newcommand{\Probn}[1]{\pr_n\left(#1\right)}				%	Probability command with subscript n

\newcommand{\Probc}[2]{\pr_{#2}\left(#1\right)}				%	Probability command conditioned on 
															%	the points of the graph specified in
															%	the second argument

\newcommand{\CProb}[2]{\pr\left(\left.#1\right|#2\right)}	%	Conditional probability command, 
															%	second argument is conditioned 
															%	event/random variable

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                         Expectation                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\e}{\mathbb{E}}								%	short hand for blackboard E
\newcommand{\E}{\mathbb{E}}

%% Expectation commands %%

\newcommand{\Exp}[1]{\e\left[#1\right]}					%	Standard expectation command, argument
														%	is random variable

\newcommand{\Expn}[1]{\e_n\left[#1\right]}				%	Expectation with subscript n

\newcommand{\Expc}[2]{\e_{#2}\left[#1\right]}			%	Expectation command conditioned on 
														%	the points of the graph specified in
														%	the second argument

\newcommand{\CExp}[2]{\e\left[\left.#1\right|#2\right]}	%	Conditional expectation, second 
														%	argument is conditioned event/random 
														%	variable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     Probabilistic limits                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\plim}{\ensuremath{\stackrel{\pr}{\rightarrow}}}	%	Convergence in probability
\newcommand{\dlim}{\ensuremath{\stackrel{d}{\rightarrow}}}		%	Convergence in distribution

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                        Scaling notations                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\bigO}[1]{O\left(#1\right)}				%	Big O notation
\newcommand{\smallO}[1]{o\left(#1\right)}			%	Small o notation
\newcommand{\bigT}[1]{\Theta\left(#1\right)}		%	Theta notation
\newcommand{\bigOp}[1]{O_\pr \left(#1\right)}		%	Probabilistic big O notation
\newcommand{\smallOp}[1]{o_\pr \left(#1\right)}		%	Probabilistic little o notation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                        Indicator commands                                       $
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\ind}[1]{\mathbbm{1}_{\left\{#1\right\}}}	%	Command for indicator where argument is a condition
\newcommand{\indE}[1]{\mathbbm{1}_{#1}}					%	Command for indicator where the argument is an event 
\newcommand{\1}{\mathds{1}}								%	Indication shorthand command

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                       Additional commands                                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\N}{\mathbb{N}}							%	Natural numbers
\newcommand{\R}{{\ensuremath{\mathbb R}}}			%	Real numbers

%%	Short hand commands:

\newcommand{\Kcal}{\ensuremath{{\mathcal K}}}		%	Mathcal K
\newcommand{\Bcal}{\ensuremath{{\mathcal B}}}		%	Mathcal B
\newcommand{\Ccal}{\ensuremath{{\mathcal C}}}		%	Mathcal C
\newcommand{\Ncal}{\ensuremath{{\mathcal N}}}		%	Mathcal N

\newcommand{\eps}{\varepsilon}						%	varepsilon
\DeclareMathOperator{\dd}{\, \mathrm{d}\hspace{-1pt}}			%	straight d for integration

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     Paper specific commands                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\H}{\ensuremath{\mathbb{H}}}			%	H used for the hyperbolic plane and hyperbolic random graph
\newcommand{\HP}{\ensuremath{\widetilde{\H}}}		%	Poisson hyperbolic random graph
\newcommand{\Dcal}[0]{\ensuremath{{\mathcal D}}}	%	Hyperbolic disc
\newcommand{\Rcal}[0]{\ensuremath{{\mathcal R}}}	%	Image of the hyperbolic disc under \Psi
\newcommand{\Pcal}[0]{\ensuremath{{\mathcal P}}}	%	Point process
\newcommand{\Po}[0]{\ensuremath{{\mathrm{Po}}}}		%	Poisson random variable

\newcommand{\T}{\ensuremath{T}}						%	Symbol for triangles

\newcommand{\BallHyp}[1]{\Bcal_{\H,n}\left(#1\right)}		%	The image of the hyperbolic ball around \Psi^{-1}(p)
\newcommand{\BallPo}[1]{\Bcal_{\Pcal}\left(#1\right)}		%	The neighborhood of a point p in the infinite limit model
\newcommand{\BallPon}[1]{\Bcal_{\Pcal,n}\left(#1\right)}	%	The neighborhood of a point p in the finit box model
\newcommand{\FatBallHyp}[1]{\check{\Bcal}_{\H,n}(#1)}		%
\newcommand{\BallSym}[1]{\Bcal_{\H \bigtriangleup \Pcal}\left(#1\right)}	%	Symmetric difference between balls in the 
																			%	hyperbolic and infinite limit model
\newcommand{\BallInter}[1]{\Bcal_{\H \cap \Pcal}\left(#1\right)}

\newcommand{\Mu}[1]{\mu_{\alpha,\nu}\left(#1\right)}

\newcommand{\hsym}[1]{h_{\H \bigtriangleup \Pcal}(#1)}
\newcommand{\EdgeDiff}{E_{\H \setminus \mathcal{P}}}
\newcommand{\expH}{\overline{n}_{\H}(k_n)}
\newcommand{\expP}{\overline{n}_{\Pcal}(k_n)}

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}	%	Use to insert equation number 
																		%	inside * environment

\newcommand{\MeijerG}[7]{G_{#3,#4}^{#1,#2} \left(\begin{matrix}#5  \\ #6 \end{matrix} \bigg| #7 \right)}
\newcommand{\MeijerGnew}[7]{G_{#3,#4}^{#1,#2} \left(#7 \bigg|\begin{matrix}#5  \\ #6 \end{matrix}\right)}

\newcommand{\Real}{\operatorname{Re}}
\newcommand{\Li}{\operatorname{Li}}

\newcommand{\Ee}[0]{\ensuremath{{\mathbb E}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%								For leaving comments to each other:								  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\definecolor{orange}{RGB}{255,127,0}
\definecolor{pink}{RGB}{255,150,150}
\newcommand{\BL}[1]{{{\color{blue} #1}}}
\newcommand{\RD}[1]{{{\color{red} #1}}}
\newcommand{\REMOVEME}[1]{{{\color{black} #1}}}
\newcommand{\GR}[1]{{{\color{green} #1}}}
\newcommand{\YW}[1]{{{\color{yellow} #1}}}
\newcommand{\OR}[1]{{{\color{orange} #1}}}
\newcommand{\NF}[1]{\YW{{\bf Nick:} #1}}
\newcommand{\PvdH}[1]{{\OR{{\bf Pim:} #1}}}
\newcommand{\TM}[1]{\BL{{\bf Tobias:} #1}}
\newcommand{\MS}[1]{\GR{{\bf Markus: }#1}}
\newcommand{\ToDo}[1]{{\color{red} {\bf To do:} #1}}

\allowdisplaybreaks

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%								Setup of the theorem environmnet								  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{remark}{Remark}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{assumption}[definition]{Assumption}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%											Authors												  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Exact asymptotic expressions for local clustering in hyperbolic random graphs}
\author[1]{Nikolaos Fountoulakis}
\author[2]{Pim van der Hoorn}
\author[3]{Tobias M\"{u}ller}
\author[3]{Markus Schepers}

\affil[1]{University of Birmingham, School of Mathematics, United Kingdom}
\affil[2]{Northeastern University, Department of Physics, United States}
\affil[3]{University of Groningen, Bernoulli Institute for Mathematics, Computer Science and Artificial Inteligence, The Netherlands}

\begin{document}

\maketitle

\begin{abstract}
\PvdH{The abstract will be written at the end.}
\end{abstract}

\PvdH{Below is a list of high and low level to do items. Please add comments using the commands below.

\noindent Comment commands:\\
Markus: \textbackslash MS\\
Nikolaos: \textbackslash NF\\
Pim: \textbackslash PvdH\\
Tobias: \textbackslash TM

}

\ToDo{High level list:

\begin{itemize}
\item Streamline notations and writing of some sections
\item Finish introduction
\item Complete bibliography list
\item Add additional explanation for the Hyperbolic model.
\item Add additional observations based on our main result
\end{itemize}
}

\newpage

\tableofcontents

\newpage

\input{introduction}

\input{proof_overview}

\input{concentration_argument}

\input{clustering_infinite_model}

\input{transition}

\input{concentration}

\input{coupling}

\input{appendix}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2018-10-16 proof_overview.tex
Initial ShareLaTeX Import

\section{Overview of the proof strategy for Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}}\label{sec:proof_outline}

We first give a detailed overview of the structure for the proof of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}. The proof itself can be found in Section~\ref{ssec:proof_main_results}, where we also prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}. Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic} based on the different propositions described below, plus the sections in which theses propositions are proved.

\begin{figure}[!t]
\centering

\begin{tikzpicture}

\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

\tikzstyle{block} = [draw, text centered, rounded corners, draw=black, thick, fill=white]
\tikzstyle{textblock} = [draw, text centered, draw=black, fill=white]

\tikzset{
  double arrow/.style args={#1 colored by #2 and #3}{
    -latex,line width=#1,#2, % first arrow
    postaction={draw,-latex,#3,line width=(#1)/2,
                shorten <=(#1)/3,shorten >=(#1)}, % second arrow
  }
}

\draw node (anchor) at (0,0) {};

%Hyperbolic graph: top left

\path (anchor)+(0,0) node (hyp_header) {\begin{minipage}[c]{10em}
	\begin{center}
		\textbf{Hyperbolic graph}\\
		$G_{\H,n}(\alpha, \nu)$
	\end{center}
\end{minipage}};

\path (hyp_header.south)+(0,-0.75) node (c_hyp) [block] {\begin{minipage}[c]{10em}
	\begin{center}
	Local clustering\\
	$\displaystyle c_{\H,n}(k_n)$
	\end{center}
\end{minipage}};

%Adjusted local clustering: middle left

\path (c_hyp.south)+(0,-3) node (c_ast_hyp) [block] {\begin{minipage}[c]{10em}
	\begin{center}
	Adjusted local clustering\\
	$\displaystyle c_{\H,n}^\ast(k_n)$
	\end{center}
\end{minipage}};

\path (c_ast_hyp.north)+(-2,1) node (hyp_text) [textblock] {\begin{minipage}[c]{7em}
	\begin{center}
		Lemma \ref{lem:clustering_ast_H}\\
		Section~\ref{ssec:coupling_H_HP}
	\end{center}
\end{minipage}};

%Poisson Hyperbolic graph: middle left

%\path (c_hyp.south)+(0,-6) node (c_pois_hyp) [block] {\begin{minipage}[c]{12em}
%	\begin{center}
%	Local clustering\\
%	$\displaystyle c_{\widetilde{\H},n}(k_n)$
%	\end{center}
%\end{minipage}};

\path (c_ast_hyp.south)+(0,-3) node (pois_hyp_header) {\begin{minipage}[c]{13em}
	\begin{center}
		\textbf{Poisson Hyperbolic graph}\\
		$G_{\HP,n}(\alpha,\nu)$
	\end{center}
\end{minipage}};

\path (pois_hyp_header.north)+(-2,1) node (pois_hyp_text) [textblock] {\begin{minipage}[c]{7em}
	\begin{center}
		Proposition \ref{prop:clustering_ast_H_Pois}\\
		Section~\ref{ssec:coupling_H_HP}
	\end{center}
\end{minipage}};

%Poisson Hyperbolic graph: bottom left

\path (pois_hyp_header.south)+(0,-1) node (c_ast_pois_hyp) [block] {\begin{minipage}[c]{10em}
	\begin{center}
	Adjusted local clustering\\
	$\displaystyle c_{\HP,n}^\ast(k_n)$
	\end{center}
\end{minipage}};

%Infinite limit model: top right

\path (hyp_header.east)+(6,0) node (pois_header) {\begin{minipage}[c]{10em}
	\begin{center}
		\textbf{Infinite limit model}\\
		$G_{\Pcal}(\alpha, \nu)$
	\end{center}
\end{minipage}};

\path (pois_header)+(0,-1.25) node (c_infty) [block] {\begin{minipage}[c]{10em}
	\begin{center}
	Clustering limit\\
	$\displaystyle c_\infty(k_n)$
	\end{center}
\end{minipage}};

\path (c_infty.south)+(2,-0.75) node (exp_c_pois_text) [textblock] {\begin{minipage}[c]{7em}
	\begin{center}
		Proposition \ref{prop:convergence_average_clustering_P_n}\\
		Section \ref{sec:clustering_Pn_to_P}
	\end{center}
\end{minipage}};

%Finite box model: bottom right

\path (c_ast_pois_hyp.east)+(6,0) node (c_ast_pois_n) [block] {\begin{minipage}[c]{10em}
	\begin{center}
	Adjusted local clustering\\
	$\displaystyle c_{\Pcal,n}^\ast(k_n)$
	\end{center}
\end{minipage}};

\path (c_ast_pois_n.south)+(-4.25,-0.5) node (c_ast_pois_n_text) [textblock] {\begin{minipage}[c]{7em}
	\begin{center}
		Proposition \ref{prop:couling_c_H_P}\\
		Section \ref{ssec:coupling_HP_ast_P}
	\end{center}
\end{minipage}};

\path (c_ast_pois_n.north)+(0,2.5) node (exp_c_pois_n) [block] {\begin{minipage}[c]{10em}
	\begin{center}
	Expected local clustering\\
	$\displaystyle \Exp{c_{\Pcal,n}^\ast(k_n)}$
	\end{center}
\end{minipage}};

\path (exp_c_pois_n.south)+(2,-0.75) node (exp_c_pois_n_text) [textblock] {\begin{minipage}[c]{7em}
	\begin{center}
		Proposition \ref{prop:concentration_local_clustering_P_n}\\
		Section \ref{sec:concentration_c_P_n}
	\end{center}
\end{minipage}};

\path (exp_c_pois_n.north)+(0,0.75) node (pois_n_header) {\begin{minipage}[c]{13em}
	\begin{center}
		\textbf{Finite box model}\\
		$G_{\Pcal,n}(\alpha, \nu)$
	\end{center}
\end{minipage}};

%Arrows

\path (c_hyp.south)+(0,-0.2) node (arrow_1l) {};
\path (c_ast_hyp.north)+(0,0.2) node (arrow_1r) {};

\draw [double arrow=6pt colored by black and white] (arrow_1l) -- (arrow_1r);

\path (c_ast_hyp.south)+(0,-0.1) node (arrow_2l) {};
\path (pois_hyp_header.north)+(0,0.1) node (arrow_2r) {};

\draw [double arrow=6pt colored by black and white] (arrow_2l) -- (arrow_2r);

\path (c_ast_pois_hyp.east)+(0.3,0) node (arrow_3l) {};
\path (c_ast_pois_n.west)+(-0.5,0) node (arrow_3r) {};

\draw [double arrow=6pt colored by black and white] (arrow_3l) -- (arrow_3r);

\path (c_ast_pois_n.north)+(0,0.2) node (arrow_4l) {};
\path (exp_c_pois_n.south)+(0,-0.2) node (arrow_4r) {};

\draw [double arrow=6pt colored by black and white] (arrow_4l) -- (arrow_4r);

\path (exp_c_pois_n.north)+(0,1.5) node (arrow_5l) {};
\path (c_infty.south)+(0,-0.2) node (arrow_5r) {};

\draw [double arrow=6pt colored by black and white] (arrow_5l) -- (arrow_5r);

\begin{pgfonlayer}{background}

\path (c_hyp)+(-3.5,2) node (hyp_a) {};
\path (c_ast_pois_hyp)+(3.5,-1.25) node (hyp_b) {};
\path[rounded corners, draw=black, dashed, thick, fill=black!10] (hyp_a) rectangle (hyp_b);

\path (pois_hyp_header)+(-2.5,0.75) node (pois_hyp_a) {};
\path (c_ast_pois_hyp)+(2.5,-1) node (pois_hyp_b) {};
\path[rounded corners, draw=black, dashed, thick, fill=black!20] (pois_hyp_a) rectangle (pois_hyp_b);

\path (c_infty)+(-3.5,2) node (pois_a) {};
\path (c_ast_pois_n)+(3.5,-1.25) node (pois_b) {};
\path[rounded corners, draw=black, dashed, thick, fill=black!10] (pois_a) rectangle (pois_b);

\path (exp_c_pois_n)+(-2.5,2) node (pois_n_a) {};
\path (c_ast_pois_n)+(2.5,-1) node (pois_n_b) {};
\path[rounded corners, draw=black, dashed, thick, fill=black!20] (pois_n_a) rectangle (pois_n_b);

\end{pgfonlayer}

\end{tikzpicture}

\caption{Overview of the proof strategy for Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}.}
\label{fig:overview_proof}
\end{figure}

The main idea behind the proof of Theorem \ref{thm:asymptotic_local_clustering_hyperbolic} is to couple the hyperbolic graph $G_{\H, n}(\alpha, \nu)$ with a subgraph of an infinite graph $G_\Pcal(\alpha,\nu)$ (see Section~\ref{ssec:infinite_model}). A similar approach is used in \cite{fountoulakis2018law} to analyze the size of the largest component in the hyperbolic model and in \cite{komjathy2018explosion} to analyze explosion times in a more general class of models.. 
The advantage of the infinite limit model is two-fold. First, it simplifies the actual computations, e.g. by replacing hyperbolic densities with exponential densities and the hyperbolic distance with a computationally easier expression. Secondly, it directly yields the limit as a result rather than having to determine this later from a long expression depending on $n$.

Very roughly, the proof falls into three parts: justifying the transitioning from the hyperbolic random graph to the infinite limit model, proving concentration results for local clustering and calculating the expected local clustering coefficient and function in the infinite limit model.

In this section, we state the required definitions, auxiliary lemmas and propositions and show how to assemble them to obtain Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.

\subsection{Infinite limit model}\label{ssec:infinite_model}

To analyze the limiting expressions for clustering in the hyperbolic random graph $G_{\H,n}(\alpha, \nu)$ we shall use an following infinite graph model which was also considered in~\cite{fountoulakis2018law} to analyze the largest component. Define $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and let $\mathcal{P}_{\alpha,\nu}$ be a Poisson point process on $\Rcal$ with intensity function
\begin{equation}\label{eq:def_intensity_function_f}
	f_{\alpha,\nu}(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y}.
\end{equation}

We will write $p = (x, y)$ for points in $\Rcal$. Then the \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
\[
	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
\]
For a point $p \in \Rcal$, we will write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
\begin{equation}\label{eq:def_ball_P}
	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
\end{equation}
With this notation we then have that $\BallPo{p} \cap \mathcal{P}$ denotes the set of neighbors of a vertex $p \in G_\Pcal(\alpha,\nu)$.  We denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e. for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
\begin{equation}\label{eq:def_mu_P}
	\mu_{\alpha,\nu}(S) = \int_S f_{\alpha,\nu}(x,y) \, dx \, dy,
\end{equation}
and for any point $p \in \Rcal$ we let $\eta_p$ be the corresponding probability measure on $\BallPo{p}$ 
\begin{equation}\label{eq:def_etq_P}
	\eta_p(S) = \frac{\mu_{\alpha,\nu}(S \cap \BallPo{p})}{\mu_{\alpha,\nu}(\BallPo{p})}.
\end{equation}
In addition we use $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation 
\begin{equation}\label{eq:mu_y_P}
	\mu_{\alpha, \nu}(\BallPo{p}) = \int_0^\infty \int_{-\infty}^\infty \ind{|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}}
	f_{\alpha,\nu}(x^\prime, y^\prime) \, dx^\prime \, dy^\prime 
	= \frac{4\alpha \nu}{(2\alpha - 1)\pi} e^{\frac{y}{2}} := \xi_{\alpha,\nu}e^{\frac{y}{2}},
\end{equation}
i.e.
\[
	\rho(p,k) = \rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k}.
\]
Note that $\rho(y,k)$ denote the probability that a node $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$.

\begin{remark}[Notations for points]\label{rmk:point_notation}
We will be working extensively with expressions in terms of points of $\Pcal_{\alpha, \nu}$, often relating them back to points in the hyperbolic disc $\Dcal_{\Rcal_n}$. Therefore, in the remainder of this paper we will always use $u = (r,\theta)$ to denote points in $\Dcal_{\Rcal_n}$ in polar coordinates while $p = (x,y)$ will denote points in $\Rcal := \mathbb{R} \times \mathbb{R}_+$ in Cartesian coordinates. In addition, when we write $p^\prime \in \mathbb{R} \times \mathbb{R}_+$ we will denote its Cartesian coordinates by $(x^\prime, y^\prime)$ and similarly for $p_i$, $u^\prime$ and $u_i$, e.g. $p_i = (x_i, y_i)$.
\end{remark}

\subsection{Finite box model}

Next we define the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ which we will couple to $G_{\H, n}(\alpha, \nu)$. Recall that $R_n = 2\log(n/\nu)$ and that $\Pcal_{\alpha, \nu}$ is a Poisson point process on $\Rcal = \R \times \R_+$, with intensity given by~\eqref{eq:def_intensity_function_f}. Now consider the finite box $\Rcal_n = (-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}] \times (0, R_n]$ in $\Rcal$. Then the \emph{finite box model} graph $G_{\mathcal{P},n}(\alpha, \nu)$ has vertex set $\mathcal{V}_n := \mathcal{P}_{\alpha, \nu} \cap \Rcal_n$ and edges set such that
\[
	(p_i, p_j) \in E(G_{\mathcal{P},n}(\alpha, \nu)) \iff |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}},
\]
where $|x|_{\pi e^{R_n/2}} = \inf_{k \in \mathbb{Z}} |x + k \pi e^{R_n/2}|$. In order words, $G_{\mathcal{P},n}(\alpha, \nu)$ is the subgraph of $G_{\mathcal{P}}(\alpha, \nu)$ induced on $\mathcal{V}_n$, where we have identified the boundaries of $(-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}]$ to exclude boundary effects and to make the model symmetric in the horizontal $x$-axis.

Similar to $G_{\Pcal}(\alpha,\nu)$, we define for any $p \in \Rcal_n$, its neighborhood ball
\[
	\BallPon{p} = \left\{p^\prime \in \Rcal_n : |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}}\right\}
\]
and associated functions $\mu_{\alpha,\nu ,n}$ and $\eta_{p,n}$ and others, by appending an additional subscript $n$. For instance
\[
	\mu_{\alpha,\nu,n}(S) = \Mu{S \cap \Rcal_n} \quad \text{and} \quad 
    \eta_{p,n}(S) = \frac{\mu_{\alpha,\nu ,n}(S \cap \BallPon{p}}{\mu_{\alpha,\nu,n}(\BallPon{p})}
    = \frac{\Mu{S\cap\BallPon{p}}}{\Mu{\BallPon{p}}}.
\]

\subsection{Coupling the hyperbolic model to the finite box model}\label{ssec:coupling_H_P}

To couple the hyperbolic graph to $G_{\mathcal{P},n}(\alpha, \nu)$ we consider the original hyperbolic graph on a Poisson distributed number of vertices as an intermediate step. For this we define $G_{\HP,n}(\alpha, \nu)$ to be the hyperbolic random graph where the vertex set is given by $N \stackrel{d}{=} \Po(n)$ points, distributed according to the $(\alpha, R_n)$-quasi uniform distribution~\eqref{eq:def_hyperbolic_point_distribution} defined in Section \ref{ssec:hyperbolic_model}. The following two lemmas from \cite{fountoulakis2018law} establishes a coupling between this version of the hyperbolic random graph and the finite box model and relate the hyperbolic neighborhoods to the neighborhood balls $\BallPo{p}$. The ensuing proposition verifies that this coupling also essentially preserves the local clustering function, i.e. that the difference between the local clustering functions in the hyperbolic model and the finite box graph converges to zero faster than the proposed scalings in the main result, Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}. Hence, it justifies the transition to the finite box model.

\begin{lemma}[{\cite[Lemma 27]{fountoulakis2018law}}]\label{lem:coupling_hyperbolic_poisson}
Let $\mathcal{V}_{\HP, n}$ denote the vertex set of $G_{\HP,n}(\alpha, \nu)$ and $\mathcal{V}_n$ the vertex set of $G_{\Pcal,n}(\alpha, \nu)$. Define the map $\Psi : [0,R_n] \times (-\pi, \pi] \to \mathcal{R}_n$ by
\begin{equation}\label{eq:def_Psi}
	\Psi(r,\theta) = \left(\theta \frac{e^{R_n/2}}{2}, R_n - r\right).
\end{equation}
Then there exists a coupling such that, a.a.s., $\mathcal{V}_n = \Psi(\mathcal{V}_{\HP,n})$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
%\begin{equation}\label{eq:convergence_miscoupling_hyperbolic_poisson}
%	\Prob{\Ccal_n^c} = \bigO{n^{-(2\alpha - 1)}}. 
%\end{equation}
\end{lemma}

In the remainder of this paper we will write $\BallHyp{p}$ to denote the image under $\Psi$ of the ball of hyperbolic radius $R_n$ around the point $\Psi^{-1}(p)$, i.e. 
\[
	\BallHyp{p} := \left\{p^\prime := \Psi(u) \, : \, u \in \Dcal_{R_n} \text{ and } d_\H(\Psi^{-1}(p),u) \le R_n\right\}.
\]
Note that we have that $\BallHyp{p} \subseteq \mathcal{R}_n$. In particular, a point $p = (x,y) \in \Rcal$ corresponds to $u := \Psi^{-1}(p) = (2 e^{R_n/2} x, R_n - y)$.

Let $u, u^\prime \in \Dcal_R$. The hypebolic law of cosines implies that $d_{\H}(u,u^\prime) < R_n$ if and only if their relative angle $\theta(u, u^\prime) := |\theta - \theta^\prime|_{2\pi}$ satisfies $\theta(u, u^\prime) < \theta_{R_n}(r,r^\prime)$, where $\theta_{R_n}(r,r^\prime)$ is the solution of the following equation
\[
	\cosh R_n =\cosh r \cosh r^\prime - \sinh r \sinh r^\prime \cos \theta_{R_n}(r,r^\prime).
\]
To write this differently, define
\begin{equation}\label{eq:def_Omega_hyperbolic}
	\Omega(r,r^\prime) := \frac{1}{2}e^{R_n/2} \arccos\left( \frac{\cosh r \cosh r^\prime - \cosh R_n}
	{\sinh r \sinh r^\prime} \right).
\end{equation}
Then $d_{\H}(u,u^\prime) < R_n$ if and only if $\theta(u, u^\prime) \leq 2 e^{-R_n/2}\Omega(r,r^\prime)$. Under the coupling map $\Psi$, this is equivalent to $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$.

Now consider a point $p \in \mathcal{V}_n$ and write $\Psi^{-1}(p) = (r,\theta)$. Then the triangle inequality implies that
for any point $u^\prime \in \Dcal_R$
\begin{equation}\label{eq:tail_inclusion_hyperbolic_ball}
	r^\prime \leq y = R_n - r \Rightarrow d_H (\Psi^{-1}(p),u^\prime) \leq R_n.
\end{equation}
In other words, we have $\Rcal_n ([r, R_n])  \subset \BallHyp{p}$. The shape of $\BallHyp{p}$ at the lower parts of $\Rcal_n$ is described by the following lemma which appears in~\cite{fountoulakis2018law}.

\begin{lemma}[{\cite[Lemma 28]{fountoulakis2018law}}]\label{lem:asymptotics_Omega_hyperbolic}
There exists a constant $K>0$ such that, for every $\varepsilon > 0$ and for $R_n$ sufficiently large, the following holds.
For every $r,r^\prime \in [\varepsilon R_n,R_n]$ with $r + r^\prime > R_n$ we have that 
\begin{equation}\label{eq:asymp1}
	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Omega(r, r^\prime) 
	\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
\end{equation}
where $y := R_n - r, y^\prime := R - r^\prime$. 
Moreover:
\begin{equation}\label{eq:asymp2} 
\Omega(r,r^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $r, r^\prime < R_n - K$.} 
\end{equation}
\end{lemma}

This result allows us to couple the neighborhoods in the hyperbolic random graph $G_{\H,n}(\alpha,\nu)$ to those in the finite box model $G_{\Pcal,n}(\alpha,\nu)$. This coupling is however not exact and hence we need to compute the difference in triangle counts between the two models. For this, and other computations later on, it will be more convenient to consider the following slight modified version of local clustering,
\begin{equation}\label{eq:def_local_clustering_ast_general}
	c_{G}^\ast(k) = \begin{cases}
			\frac{1}{\Exp{N_G(k)}} \sum_{v \in V(G)} \ind{D_G(v) = k} \frac{\T_G(v)}{\binom{k}{2}} &\mbox{if } N_G(k) \ge 1\\
			0 &\mbox{else.}
		\end{cases}
\end{equation}
Notice that the only difference between $c_G(k)$ and $c_G^\ast(k)$ is that we replace $N_G(k)$ by its expectation $\Exp{N_G(k)}$. Following the notational convention, see Remark~\ref{rmk:notation}, throughout the remainder of this paper we write $c_{\HP,n}^\ast(k)$ and $c_{\mathcal{P},n}^\ast(k)$ to denote the modified local clustering function in $G_{\HP,n}(\alpha, \nu)$ and $G_{\mathcal{P},n}(\alpha,\nu)$, respectively.

First we show that considering this adjusted version doesn't change anything in terms of the scaling, the proof is given in Section~\ref{ssec:coupling_H_HP}.

\begin{lemma}\label{lem:clustering_ast_H}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, as $n \to \infty$,
\[
	\Exp{\left|c_{\H,n}(k_n) - c_{\H,n}^\ast(k_n)\right|} = \smallO{s_\alpha(k_n)}.
\]
\end{lemma}

We then establish that the adjusted local clustering function in the hyperbolic model $G_{\H,n}(\alpha,\nu)$ behaves similar to that in the Poisson version $G_{\HP, n}(\alpha,\nu)$.

\begin{proposition}\label{prop:clustering_ast_H_Pois}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any increasing sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, as $n \to \infty$,
\[
	\Exp{\left|c_{\H,n}^\ast(k_n) - c_{\HP,n}^\ast(k_n)\right|} = \smallO{s_\alpha(k_n)}.
\]
\end{proposition}

The next step is to show that the modified clustering isn't influenced by the coupling describe above. The proof can be found in Section~\ref{ssec:coupling_HP_ast_P}.

\begin{proposition}[Coupling result for local clustering]\label{prop:couling_c_H_P}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any increasing sequence such that $k_n = \smallO{\min\left\{n^{\frac{1}{2\alpha + 1}}, n^{\frac{1}{3}}\right\}}$. Then, as $n \to \infty$,
\[
	\Exp{\left|c_{\HP,n}^\ast(k_n) - c_{\Pcal,n}^\ast(k_n)\right|} = \smallO{s_\alpha(k_n)}.
\]
\end{proposition}

These two results imply that the difference between the local clustering functions in the hyperbolic model and modified version in the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}. Hence, to proof this theorem it enough to prove it for $c_{\mathcal{P},n}^\ast(k)$.

\subsection{From the finite to the infinite model}

To compute the limit of the adjusted local clustering $c_{\mathcal{P},n}^\ast(k)$ in the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ we first prove in Section~\ref{sec:concentration_c_P_n} that it is concentrated around its mean $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$.

\begin{proposition}[Concentration local clustering in $G_{\mathcal{P},n}(\alpha, \nu)$]\label{prop:concentration_local_clustering_P_n}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any non-decreasing sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
\[
	\Exp{\left|c_{\mathcal{P},n}^\ast(k_n) - \Exp{c_{\mathcal{P},n}^\ast(k_n)}\right|} = \smallO{s_\alpha(k_n)}.
\]
\end{proposition}

With this concentration result, we are left with the task to compute the limit of $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$ as $n \to \infty$ and show that it is equivalent to $c_\infty(k_n)$. To accomplish this we move to the infinite limit model $G_\Pcal(\alpha,\nu)$. The next result shows that the difference between the expected value of the clustering function $c_G^\ast(k)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}.

\begin{proposition}[Transition to infinite limit model]\label{prop:convergence_average_clustering_P_n}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any positive sequence tending to infinity and satisfying $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
\[
	\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\infty(k_n)\right| = \smallO{s_\alpha(k_n)}.
\]
\end{proposition}

\subsection{Proof of the main results}\label{ssec:proof_main_results}

We are now ready to prove our main results, using the propositions stated in the previous sections. We begin with Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.

\begin{proof}[Proof of Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}]
By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
\begin{align*}
	&\hspace{-30pt}\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}\\
	&\le \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{}c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)}
		+ \frac{\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\infty(k_n)\right|}{C_{\alpha,\nu}s_\alpha(k_n)}
		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| \\
	&= \smallO{1}.
\end{align*}
%\[
%	\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
%	\le \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| 
%	+ \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - c_\infty(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
%\]
Combining this with Proposition~\ref{prop:couling_c_H_P} yields
\[
	\Exp{\left|\frac{c_{\H,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
	\le \Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|} 
	+ \frac{\Exp{\left|c_{\H,n}^\ast(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
\]
and the result then follows by applying Lemma~\ref{lem:clustering_ast_H}. 
\end{proof}

We can now use this result to prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.

\begin{proof}[Proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}]
First, let $a_n$ be any sequence such that $a_n \to \infty$. Then
\begin{align*}
	c_{\H,n} &= \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) \le a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}
		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
	&= \frac{1}{n} \sum_{t = 3}^{a_n} \sum_{i = 1}^n \ind{D_{\H,n}(i) = t} \frac{T_{\H,n}(i)}{\binom{t}{2}}
		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
	&= \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_{\H,n}(t)} c_{\H,n}(t)
		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}},
\end{align*}
where the expectation of last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. We have a similar result for $c_\infty$. Therefore
\begin{align*}
	\Exp{|c_{\H,n} - c_\infty|}
	&\le \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}(t) - 	
		\Exp{N_\Pcal(t)}c_{\infty}(t)\right)\right|}\\ 
	&\hspace{10pt}+ \Prob{D_{\H,n} > a_n} + \Prob{D_{\Pcal} > a_n},
\end{align*}
and since the last to probabilities are $\smallO{1}$ it is enough to prove that
\[
	\lim_{n \to \infty} \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}(t) - 	
			\Exp{N_\Pcal(t)}c_{\infty}(t)\right)\right|} = 0.
\]

We write
\begin{align*}
	\Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}(t) - 	
		\Exp{N_\Pcal(t)}c_{\infty}(t)\right)\right|}
	&\le \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_\Pcal(t)} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\\
	&\hspace{10pt}+ \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - N_\Pcal(t)\right|}\Exp{c_\infty(t)},
\end{align*}
and will show that both terms go to zero for some appropriately chosen sequence $a_n$.

Note that Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic} states that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
\[
	\lim_{n \to \infty} \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} = 0.
\]

Let $b_n := \log(n)^{-1} n^{1/(2\alpha + 1)}$ and define the sequence $k_n$ by
\[
	k_n = \arg \max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}.
\]
Then $k_n = \smallO{n^{1/(2\alpha + 1)}}$ and by Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}
\[
	\max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} = \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} \to 0.
\]
Similarly we note that
\[
	\arg \max_{3 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} \to 0.
\]

Now define
\[
	a_n := \left\lfloor \min \left\{
	\left(\max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\right)^{-1/2},
	\left(\arg \max_{3 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|}\right)^{-1/2},
	b_n - 1 \right\} \right\rfloor
\]
so that $a_n < b_n = \smallO{n^{1/(2\alpha + 1)}}$, $a_n \to \infty$, 
\[
	a_n \max_{3 \le t \le a_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} 
	\le a_n \max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} \to 0,
\]
and similarly
\[
	a_n \arg \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} \to 0.
\]

Then, since $\Exp{N_\Pcal(t)} = \bigT{1}n^{-1} t^{-(2\alpha + 1)}$
\begin{align*}
	&\hspace{-30pt}\frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_\Pcal(t)} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\\
	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}
	= \smallO{1},
\end{align*}
while $\Exp{c_\infty(t)} \le 1$ implies that
\begin{align*}
	&\hspace{-30pt}\frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - N_\Pcal(t)\right|}\Exp{c_\infty(t)} \\
	&\le \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_\Pcal(t)} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} \\
	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} 
		= \smallO{1}.
\end{align*}
This finishes the proof.
\end{proof}

### 2018-10-16 transition.tex
Initial ShareLaTeX Import

\section{From $G_{\mathcal{P}, n}(\alpha, \nu)$ to $G_{\mathcal{P}}(\alpha, \nu)$ (Proving Proposition \ref{prop:convergence_average_clustering_P_n})}\label{sec:clustering_Pn_to_P}

\PvdH{The text in this section needs a full overhaul.}

Our focus will however be on substituting $\rho_n(y,k_n)$ with $\rho(y,k_n)$ in integral expressions. We begin with the following useful lemma.

%\begin{lemma}\label{lem:average_degree_P_n}
%For all $p \in \Rcal_n$, such that $y > 2\log(\pi/2)$,
%\[
%	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right)
%\]
%where $\phi_n(y) \ge 0$ is given by
%\[
%	\phi_n(y) = \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)}e^{-(\alpha-\frac{1}{2})(R_n - y)}
%	- \frac{(2\alpha - 1)\pi}{4\alpha}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} 
%	e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(\alpha - \frac{1}{2})R_n - \frac{y}{2}}\right).
%\]
%If, on the other hand, $y \le 2 \log(\pi/2)$ then
%\[
%	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
%\]
%\end{lemma}
%
%\begin{proof}
%First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$. We then have that
%\[
%	\BallPon{p} = \left\{p^\prime \in \Rcal_n \, : \, |x^\prime|_n \le e^{\frac{y + y^\prime}{2}}\right\},
%\] 
%whose boundaries given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$ intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
%\[
%	h(y) = R_n + 2 \log\left(\frac{\pi}{2}\right) - y.
%\]
%Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R_n$ of the box $\Rcal_n$ while in the other case the full region of the box above $h(y)$ is connected to $p$. 
%
%We will first consider the case where $y > 2 \log(\pi/2)$. Recall that $\mu_{\alpha,\nu}(B_\Pcal(p)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$ where $\xi_{\alpha,\nu} = \frac{4\alpha \nu}{(2\alpha - 1)\pi}$. Then, after some simple algebra, we have that
%\begin{align*}
%	\mu_{\alpha,\nu}(B_{\Pcal,n}(p))
%	&= \int_0^{h(y)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
%		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
%	&\hspace{10pt}+ \int_{h(y)}^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
%		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
%	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{h(y)} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime
%		+ \alpha \nu e^{\frac{R_n}{2}} \int_{h(y)}^{R_n} e^{-\alpha y^\prime} \, dy^\prime \\
%	&= \xi_{\alpha,\nu} e^{\frac{y}{2}}\left(1 - \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} 
%		e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)\\
%	&\hspace{10pt}+ \nu e^{\frac{R_n}{2}}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} e^{-\alpha(R_n - y)} 
%		- e^{-\alpha R_n}\right)\\
%	&= \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right).
%\end{align*}
%Since, for all $\alpha > \frac{1}{2}$,
%\[
%	\left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} \ge \frac{(2\alpha - 1)\pi}{4\alpha} \left(\frac{\pi}{2}\right)^{-2\alpha}
%\]
%it follows that $\phi_n(y) \ge 0$.
%
%When $y \le 2 \log(\pi/2)$ we have
%\begin{align*}
%	\mu_{\alpha,\nu}(B_{\Pcal,n}(p))
%	&= \int_0^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
%		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
%	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R_n} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
%	&= \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
%\end{align*}
%\end{proof}

$\phi_n(y) = \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}$. 
This gives the following useful corollary to Lemma~\ref{lem:average_degree_P_n}.

\begin{corollary}\label{cor:average_degree_P_n_K}
Let $\alpha > \frac{1}{2}$, $0 < \varepsilon < 1$ and $k_n$ be an increasing sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha - 1}}}$. Then, for all $p \in \Kcal_{\varepsilon}(k_n)$,
\[
	\mu_{\alpha,\nu ,n}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}\right).
\]
\end{corollary}

With this lemma we can now show that we can replace $\rho_n(y,k_n)$ in integral expressions over $\Rcal_n$ with $\rho(y,k_n)$. This will help make the remaining computations easier.

%\begin{lemma}\label{lem:replace_rho_n_with_rho}
%Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n$ be any increasing sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$. Then, for any $h : \R_+ \mapsto \R$ such that $h(y) = \bigO{e^\beta}$ as $y \to \infty$ for some $\beta \in \R$ and $\varepsilon > 2 \sqrt{2 (\beta - \alpha \vee 1)(2\alpha + 1)}$,
%\[
%	\int_{\Rcal_n} \rho_n(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
%	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) e^{\beta y} f_{\alpha,\nu}(x,y) \dd x \dd y.
%\]
%\end{lemma}
%
%\begin{proof}
%Similar to the proof of Lemma~\ref{lem:concentration_argument} we define 
%\[
%	\lambda_n^\pm = k_n \pm \varepsilon \sqrt{k_n \log(k_n)}, \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right)
%\] 
%We will show that as $n \to \infty$,
%\begin{equation}\label{eq:P_n_nodes_degree_k}
%	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) e^{(\beta - \alpha) y} \dd y = (1+o(1))\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) e^{(\beta - \alpha) y} \dd y,
%\end{equation}
%from which the result follows by a concentration argument.
%
%For simplicity we will write
%\[
%	\mu_1(y) := \mu_{\alpha,\nu}\left(\BallPo{y}\right) \quad \text{and} \quad 
%	\mu_2(y) = \mu_{\alpha,\nu}\left(\BallPon{y}\right),
%\]
%and recall that $\mu_2(y) = \mu_1(y)(1 - \phi_n(y))$ with $\phi_n(y)$ defined as in Lemma~\ref{lem:average_degree_P_n}. Let us now make a change of variables $y \to z$ such that
%\[
%	\mu_2(y) = \mu_1(z).
%\]
%and note that since
%\[
%	\mu_1^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
%\]
%we have
%\[
%	z(y) = 2 \log\left(\frac{\mu_1(y)}{\xi_{\alpha,\nu}}\right) + 2 \log\left(1 - \phi_n(y)\right)
%	= y + 2 \log\left(1 - \phi_n(y)\right).
%\]
%
%Next we note that for any $a_n^- \le y \le a_n^+$
%\[
%	\phi_n(a_n^-) \le \phi_n(y) \le \phi_n(a_n^+) 
%\]
%which are both $o(1)$, as $n \to \infty$, and hence
%\begin{equation}
%	e^{(\beta-\alpha) y} = e^{(\beta-\alpha) z} e^{(\beta-\alpha) \log(1-\phi_n(y))} = e^{(\beta-\alpha) z}\left(1 - \phi_n(y)\right)^{\beta-\alpha}	= (1 + o(1))e^{(\beta-\alpha) z}
%\end{equation}
%uniformly for $a_n^- \le y \le a_n^+$. For the derivatives we have $\mu_1^\prime(y) = \mu_1(y)/2$, while $\phi_n^\prime(y) = O(1) \phi_n(y)$ and hence
%\begin{align*}
%	\mu_2^\prime(y) = \left(1 - \phi_n(y)\right)\mu_1^\prime(y)  
%	- \mu_1(y) \phi_n^\prime(y) = \mu_1^\prime(y)\left(1 - o(1)\right),
%\end{align*}
%uniformly for $a_n^- \le y \le a_n^+$. Therefore, with this change of variables, and using
%\[
%	\hat{a}_n^\pm := z(a_n^\pm) = a_n^\pm + 2\log(1 - \phi_n(a_n^\pm)),
%\] 
%we have
%\begin{align*}
%	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) e^{(\beta - \alpha)y} \dd y
%	&=  \int_{a_n^-}^{a_n^+} \Prob{\mathrm{Po}\left(\mu_2(y) = k_n\right)} e^{(\beta-\alpha) y} \dd y\\
%	&= (1 + \smallO{1})\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\mathrm{Po}\left(\mu_1(z) = k_n\right)}
%		e^{-\alpha z} \frac{\mu_2^\prime(z)}{\mu_2^{\prime}(z)} \, dz\\
%	&= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(y,k_n) e^{(\beta-\alpha) z} \, dz.
%\end{align*}
%\end{proof}

As a direct consequence of the above lemma we obtain asymptotic result for the number of nodes with degree $k_n$ in $G_{\Pcal,n}(\alpha,\nu)$.

\begin{lemma}\label{lem:nodes_degree_k_P_n}
Let $k_n$ be an non-decreasing sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then,
\[
	\Exp{N_{\Pcal,n}(k_n)} = (1+o(1)) \alpha n \int_{\R_+} \rho(y,k_n) e^{-\alpha} \dd y,
\]
so that in particular
\[
	\Exp{N_{\Pcal,n}(k_n)} = (1+\smallO{1}) \alpha n k_n^{-(2\alpha + 1)}.
\]
\end{lemma}

\begin{proof}
Since
\[
	\Exp{N_{\Pcal,n}(k_n)} = \int_{\Rcal} \rho_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y,
\]
and $2 I_n/\pi = n/\nu$, the result follows directly from Lemma~\ref{lem:replace_rho_n_with_rho}.
\begin{align*}
	\Exp{N_{\Pcal,n}(k_n)} &= (1+\smallO{1})\int_{\Rcal} \rho(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y\\
	&= \frac{2 \alpha \nu}{\pi} I_n \int_0^{R_n} \rho(y,k_n) e^{-\alpha} \dd y\\
	&= \alpha n \int_0^{R_n} \rho(y,k_n) e^{-\alpha} \dd y \\
	&= (1+\smallO{1}) \alpha n k_n^{-(2\alpha + 1)}.
\end{align*}
\end{proof}

%With this inside we define
%\begin{equation}\label{eq:def_triangle_count_K_epsilon}
%	\widetilde{T}_{\Pcal,n}(k,\varepsilon) = \sum_{p \in \Pcal_n \cap \Kcal_{\varepsilon}(k)} \ind{D_{\Pcal,n}(p) = k} 
%	T_{\Pcal,n}(p),
%\end{equation}
%to denote the number of triangles for nodes in $G_{\Pcal,n}(\alpha,\nu)$ with degree $k$ and $p \in \Kcal_\varepsilon(k)$ and use a similar definition for $\widetilde{T}_{\Pcal}(k,\varepsilon)$ in the graph $G_{\Pcal}(\alpha,\nu)$.

\subsection{Comparing triangles between $G_\Pcal(\alpha,\nu)$ and $G_{\Pcal,n}(\alpha,\nu)$}

We now turn to the task of calculating the expected number of triangles of a node at height $y$, for both the infinite model and the finite box model. Let $p_0 = (0,y)$ and recall that 
\[
	\Exp{T_{\Pcal,n}(p_0)} = \frac{1}{2}\iint_{\Rcal_n^2} T_{\Pcal,n}(p_0,p_1,p_2)
	f_{\alpha,\nu}(x_1,y_1) f_{\alpha,\nu}(x_1,y_1) \, dx_1 \, dx_2 \, dy_1 \, dy_2,
\]
where
\[
	T_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p_1)}.
\]

The difference between the indicator $\ind{p_1 \in B_{\Pcal,n}(p)}$ in the finite box model and $\ind{p_1 \in B_{\Pcal}(p)}$ is that in $G_{\Pcal,n}(\alpha,\nu)$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$. It is clear that for any $0 \le y \le R_n$ we have that $\BallPon{p_0} = \BallPo{p_0} \cap \Rcal_n$. However, when we take another point $p^\prime \in \BallPon{p}$ then it could happen that there are points in the intersection $\BallPon{p} \cap \BallPon{p^\prime}$ that are not in $\BallPo{p} \cap \BallPo{p^\prime}$. Let us denote this region by $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$. Then, any $p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ creates a triangle with $p$ and $p^\prime$ in $G_{\Pcal,n}(\alpha,\nu)$ that is not present in $G_{\Pcal}(\alpha, \nu)$.

Define
\begin{equation}\label{eq:def_tilde_triangle_indicator}
	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal_n}
\end{equation}
Then
\[
	\sum_{p_1,p_2 \in 2^\Pcal_n} T_{\Pcal,n}(p_0,p_1,p_2) - \widetilde{T}_{\Pcal,n}(p_0,p_1,p_2)
	= \sum_{p_1,p_2 \in 2^\Pcal_n} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)}
\]

\begin{figure}[!t]
\centering
\begin{tikzpicture}
	%Define the coordinates 
	%p = (\u,\v) and p^\prime = (\uu, \vv)
	%Box \Rcal_n has width 2\r and height \t
	\pgfmathsetmacro{\u}{0} %0
	\pgfmathsetmacro{\v}{1} %1
	\pgfmathsetmacro{\uu}{1.4} %1.4
	\pgfmathsetmacro{\vv}{0.8} %0.8
	\pgfmathsetmacro{\r}{6}
	\pgfmathsetmacro{\t}{4}

	%The box \Rcal_n
	\draw[line width=1pt] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);

	%Dram both nodes
    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] (p1) at (\u,\v) {};
    \path (p1)+(-0.2,0.2) node {$p$};
    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uu,\vv) {};
    \path (p2)+(-0.2,0.2) node {\color{blue}$p^\prime$};

	%Boundaries p = (\u,\v)

	%Right boundary
	\pgfmathsetmacro{\rightbounduv}{\u+exp((\v)/2)}
	\draw[domain=\rightbounduv:\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-\v});
    %Left boundary
    \pgfmathsetmacro{\leftbounduv}{\u-exp((\v)/2)}
    \draw[domain=\leftbounduv:-\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-\v});

    %Boundaries p^\prime = (\uu,\vv)

    %Right boundary
    \pgfmathsetmacro{\rightbounduuvv}{\uu+exp((\vv)/2)}
    \draw[domain=\rightbounduuvv:\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-\uu)-\vv});
    %Shifted right boundary
    \pgfmathsetmacro{\shiftrightbounduuvv}{\uu+exp((\vv + \t)/2)-2*\r}
    \draw[domain=\shiftrightbounduuvv:-\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+(2*\r-\uu))-\vv});
    %Left boundary 
    \pgfmathsetmacro{\leftbounduuvv}{\uu-exp((\vv)/2)}
    \draw[domain=\leftbounduuvv:-\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\uu-\x)-\vv});
    %Shifted left boundary
    \pgfmathsetmacro{\shiftleftbounduuvv}{\uu-exp((\vv + \t)/2)+2*\r}
    \draw[domain=\shiftleftbounduuvv:\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(2*\r + \uu-\x)-\vv});

    %Define x^\ast(p^\prime) and y^\ast(p^\prime)
    \pgfmathsetmacro{\uuast}{\uu-\r}
    \pgfmathsetmacro{\vvast}{2*ln(\r)-\vv}

    %Define intersection left black and shifted blue curve
    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1 + exp((\vv - \v)/2))}

    %Define h_1(p) = h_2(p)
    \pgfmathsetmacro{\hp}{2*ln(\r-\u)-\v}

    %Define h_1(p^\prime) and h_2(p^\prime)
    \pgfmathsetmacro{\hh}{2*ln(\uu+\r)-\vv}
    \pgfmathsetmacro{\hhh}{2*ln(\r-\uu)-\vv}

    %Highlight area between left black, left blue and shifted right blue line
	\draw[red,line width=1pt,pattern=north west lines, pattern color=red] 
		plot[domain=\uuast:\uast,smooth,variable=\x,red] (\x, {2*ln(\x+(2*\r-\uu))-\vv}) 
		-- 
		plot[domain=\uast:-\r,smooth,variable=\x,red] (\x, {2*ln(-\x)-\v})
		-- 
		(-\r,\hh)
		-- 
		plot[domain=-\r:\uuast,smooth,variable=\x,red] (\x, {2*ln(\uu-\x)-\vv});

%	\draw node[fill, circle, inner sep=0pt, minimum size=4pt, blue] at (\uuast,\vvast) {};
%	\draw node[fill, circle, inner sep=0pt, minimum size=4pt, black] at (\uast,\vast) {};
%	\draw node (f1) at (\uuast,\vvast+0.9) {\color{blue}$(x^\ast(p^\prime), y^\ast(p^\prime))$};
%	\draw node (f2) at (\uast+1,\vast-1.25) {\color{black}$(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$};
%	
%	\draw[->,thick] (f2) -- (\uast+0.1,\vast-0.2);
%	\draw[->,thick,blue] (f1) -- (\uuast,\vvast+0.2);

	 \draw[dashed,line width=1pt,blue] (\uuast,0) -- (\uuast,\vvast);
	 \draw node at (\uuast+0.1,-0.4) {\color{blue}$x^\ast(p^\prime)$};
	 \draw[dashed,line width=1pt,blue] (\r,\vvast) -- (\uuast,\vvast);
	 \draw node at (\r+0.75,\vvast) {\color{blue}$y^\ast(p^\prime)$};
	 \draw[dashed,black,line width=1pt] (-\r,\vast) -- (\uast,\vast);
	 \draw node at (-\r-0.75,\vast) {\color{black}$\hat{y}(p,p^\prime)$};
	 \draw[dashed,black,line width=1pt] (\uast,\vast) -- (\uast,0);
	 \draw node at (\uast-0.1,-0.4) {\color{black}$\hat{x}(p,p^\prime)$};

	 \draw node[fill, circle, inner sep=0pt, minimum size=4pt, blue] at (\uuast,\vvast) {};
	 \draw node[fill, circle, inner sep=0pt, minimum size=4pt, black] at (\uast,\vast) {};

    \draw node at (-\r-0.75,\hh+0.1) {\color{blue}$h_1(p^\prime)$};
    \draw node at (\r+0.75,\hhh-0.1) {\color{blue}$h_2(p^\prime)$};

\end{tikzpicture}
\caption{Example configuration of two points $p$ and $p^\prime$ for which $\BallPon{p} \cap \BallPon{p^\prime}$ is not a subset of $\BallPo{p} \cap \BallPo{p^\prime}$. The red region indicates the area of points belonging to $\BallPon{p} \cap \BallPon{p^\prime}$ but not to $\BallPo{p} \cap \BallPo{p^\prime}$.}
\label{fig:comparing_triangles_diff_intersections}
\end{figure}

Figure \ref{fig:comparing_triangles_diff_intersections} shows an example of a configuration where $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime) \ne \emptyset$. We observe that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime) \ne \emptyset$ because the right boundary of the ball $\BallPon{p^\prime}$ exists the right boundary of the box $\Rcal_n$ and then, since we identified the boundaries, continues from the left so that $\BallPon{p^\prime}$ covers part of the ball $\BallPon{p}$ which would not be covered in the infinite limit model.

To further analyze this, let us introduce some notation. For any $p = (x,y) \in \Rcal_n$ we will define the left and right boundary functions as, respectfully,
\begin{align}
	b_p^-(z) &= \begin{cases}
		2 \log\left(x-z\right) - y &\mbox{if }  -\frac{\pi}{2} e^{R_n/2} \le z \le x - e^{y/2}  \\
		2\log\left(\pi e^{R_n/2} + x - z\right) - y 
			&\mbox{if } x - e^{(y + R_n)/2} + \pi e^{R_n/2} \le z \le \frac{\pi}{2} e^{R_n/2}\\
		0 &\mbox{else}
	\end{cases}\\
	b_p^+(z) &= \begin{cases}
		2 \log\left(z-x\right) - y &\mbox{if } x + e^{y/2} \le z \le \frac{\pi}{2} e^{R_n/2} \\
		2\log\left(\pi e^{R_n/2} + z - x\right) - y 
			&\mbox{if } -\frac{\pi}{2} e^{R_n/2} \le z \le x + e^{(y + R_n)/2} - \pi e^{R_n/2}\\
		0 &\mbox{else}
	\end{cases}
\end{align}
Note that these functions describe the boundaries of the ball $\BallPon{p}$. In particular, $p^\prime \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$. See Figure \ref{fig:comparing_triangles_diff_analysis} for an illustration.

For the remainder of the analysis we restrict ourselves to the case where $x^\prime > 0$. Due to symmetry the situation for $x^\prime < 0$ is the same. There are two important points in the box $\Rcal_n$. These are the intersection between the left boundary of $p^\prime$ and the right boundary of $p^\prime$, as it continues from the left side of the box, and the left boundary of $p$. We denote by $(x^\ast(p^\prime), y^\ast(p^\prime))$ the intersection between the left and right boundary of $p^\prime$ and by $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$ the intersection between the left boundary of $p$ and the right boundary of $p^\prime$ (see also Figure \ref{fig:comparing_triangles_diff_analysis}). After some simple algebra we obtain the following expressions for the coordinates of these two points
\begin{align*}
	x^\ast(p^\prime) &= x^\prime - \frac{\pi}{2} e^{R_n/2}\\
	y^\ast(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{R_n/2}\right) - y^\prime\\
	\hat{x}(p,p^\prime) &= \frac{x^\prime - \pi e^{R_n/2}}{1 + e^{(y^\prime - y)/2}} \\
	\hat{y}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R_n/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)
\end{align*}

The crucial observation is that $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$ as long as the point $(x^\ast(p^\prime), y^\ast(p^\prime))$ is above the left boundary of $p$. This happens exactly when $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$. Therefore the boundary of this event is given by the equation $y^\ast(p^\prime) = b_p^-(x^\ast(p^\prime))$ which reads
\[
	2\log\left(\frac{\pi}{2}e^{R_n/2}\right) - y^\prime = 2\log\left(\frac{\pi}{2} e^{R_n/2} -x^\prime\right) - y.
\]
Solving this equation gives us the function
\begin{equation}
	b^\ast_p(z) = y - 2\log\left(1 - \frac{z}{\frac{\pi}{2} e^{R_n/2}}\right),
\end{equation}
which is displayed by the red curve in Figure \ref{fig:comparing_triangles_diff_analysis}. It holds that $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$ if and only if $y^\prime < b^\ast_p(x^\prime)$ and hence we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$ for all $p^\prime \in \Rcal_n$ for which $y^\prime \ge b^\ast_p(x^\prime)$. We also not that when $y^\prime = b^\ast_p(x^\prime)$ the two points $(x^\ast(p^\prime), y^\ast(p^\prime))$ and $(\hat{x}(p,p^\prime),\hat{y}(p,p^\prime))$ coincide.

\begin{figure}[!t]

\centering
\begin{tikzpicture}
	%Define the coordinates 
	%p = (\u,\v) and p^\prime = (\uu, \vv)
	%Box \Rcal_n has width 2\r and height \t
	\pgfmathsetmacro{\u}{0}
	\pgfmathsetmacro{\v}{1}
	\pgfmathsetmacro{\uu}{1.8}
	\pgfmathsetmacro{\vv}{1.7}
	\pgfmathsetmacro{\r}{6}
	\pgfmathsetmacro{\t}{4}

	%The box \Rcal_n
	\draw[line width=1pt] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);

	%Boundaries p = (\u,\v)

	%Right boundary
	\pgfmathsetmacro{\rightbounduv}{\u+exp((\v)/2)}
	\draw[domain=\rightbounduv:\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-\v});
    %Left boundary
    \pgfmathsetmacro{\leftbounduv}{\u-exp((\v)/2)}
    \draw[domain=\leftbounduv:-\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-\v});

    %Boundaries p^\prime = (\uu,\vv)

    %Right boundary
    \pgfmathsetmacro{\rightbounduuvv}{\uu+exp((\vv)/2)}
    \draw[domain=\rightbounduuvv:\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-\uu)-\vv});
    %Shifted right boundary
    \pgfmathsetmacro{\shiftrightbounduuvv}{\uu+exp((\vv + \t)/2)-2*\r}
    %\draw[domain=\shiftrightbounduuvv:-\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+(2*\r-\uu))-\vv});
    \draw[domain=-\r:\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+(2*\r-\uu))-\vv});
    %Left boundary 
    \pgfmathsetmacro{\leftbounduuvv}{\uu-exp((\vv)/2)}
    \draw[domain=\leftbounduuvv:-\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\uu-\x)-\vv});
    %Shifted left boundary

    %Star boundary
    \pgfmathsetmacro{\starleftbound}{\r*(1-exp(\v/2))}
    \pgfmathsetmacro{\starrightbound}{\r*(1-exp((\v-\t)/2))}
    \draw[domain=\starleftbound:\starrightbound,smooth,variable=\x,red, line width=1pt] plot (\x, {2*ln((\r/(\r-\x)))+\v});

    %Define h_1(p) = h_2(p)
    \pgfmathsetmacro{\hp}{2*ln(\r-\u)-\v}
%    \draw node at (\r+0.75,\hp) {\color{black}$h(y)$};
    \draw node at (\r+1,\hp) {};

    %Define h_1(p^\prime) and h_2(p^\prime)
    \pgfmathsetmacro{\hh}{2*ln(\uu+\r)-\vv}
    \pgfmathsetmacro{\hhh}{2*ln(\r-\uu)-\vv}

%    \draw node at (-\r-0.75,\hh+0.1) {\color{blue}$h_1(p^\prime)$};
%    \draw node at (\r+0.75,\hhh) {\color{blue}$h_2(p^\prime)$};

    %Define x^\ast(p^\prime) and y^\ast(p^\prime), intersection of left and shifted right blue curve
    \pgfmathsetmacro{\uuast}{\uu-\r}
    \pgfmathsetmacro{\vvast}{2*ln(\r)-\vv}

    %Define intersection left black and shifted blue curve
    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1 + exp((\vv - \v)/2))}

%    \draw[dashed,thick,black] (-\r,\hhh) -- (\r,\hhh);
    \draw[dashed,line width=1pt,red] (\uuast,0) -- (\uuast,\vvast);
    \draw node at (\uuast,-0.4) {\color{blue}$x^\ast(p^\prime)$};
    \draw[dashed,line width=1pt,red] (-\r,\vvast) -- (\uuast,\vvast);
    \draw node at (-\r-0.75,\vvast+0.2) {\color{blue}$y^\ast(p^\prime)$};
%    \draw[dashed,black,line width=1pt] (-\r,\vast) -- (\uast,\vast);
    \draw node at (-\r-0.75,\vast-0.2) {\color{black}$\hat{y}(p,p^\prime)$};
%    \draw[dashed,black,line width=1pt] (\uast,\vast) -- (\uast,0);
    \draw node at (\uast,-0.8) {\color{black}$\hat{x}(p,p^\prime)$};

    \draw node[fill, circle, inner sep=0pt, minimum size=4pt, red] at (\uuast,\vvast) {};

   	%Draw both nodes
    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] (p1) at (\u,\v) {};
    \path (p1)+(-0.2,0.2) node {$p$};
    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uu,\vv) {};
    \path (p2)+(-0.2,0.2) node {\color{blue}$p^\prime$};

%    \draw node[fill, circle, inner sep=0pt, minimum size=4pt, black] at (\uast,\vast) {};

%    \draw node at (-7,2.5835) {$h(y)$};

%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
%    \draw[dotted,thick,black] (4.5208,2.0174) -- (6,2.0174);

%    \draw node at (4.5208,-0.5) {$w_x(p,p^\prime)$};
%    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};

%    \draw node at (0,3.5) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
%    \draw node at (-2,1.6) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
%    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
%    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};

\end{tikzpicture}
\caption{???.}
\label{fig:comparing_triangles_diff_analysis}
\end{figure}

This analysis allows us to compute the expected difference in the number of triangles for $\Pcal$ and $\Pcal_n$, for a node with height $y$.

\begin{lemma}\label{lem:clustering_error_T_term}
Let $(k_n)_{n \ge 1}$ be any sequence with $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, for any $0 < \varepsilon < 1$ and $p \in \Kcal_{\varepsilon}(k_n)$, as $n \to \infty$,
\[
	\int_{\Rcal_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\mu, \nu}(x_1,y_1) 
	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
\]
\end{lemma}

The proof of the lemma is not difficult but cumbersome, since it involves computing many different integrals. We postpone this proof till the end of this section and proceed with the main goal, proving Proposition~\ref{prop:convergence_average_clustering_P_n}. But first we state a small lemma about the scaling of $s_\alpha(k_n)$ that will be very useful.

\begin{lemma}\label{lem:scaling_s_alpha}
Let $s_\alpha(k_n)$ be as defined in \eqref{eq:def_scaling_function}. Then for any $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$,
\[
	n^{-(2\alpha - 1)} = \smallO{s_\alpha(k_n)}.
\]
\end{lemma}

\begin{proof}
First let $\frac{1}{2} < \alpha < \frac{3}{4}$. Then
\[
	n^{-(2\alpha - 1)}s_\alpha(k_n)^{-1} = n^{-(2\alpha -1)}k_n^{4\alpha - 2}
	= \smallO{n^{-(2\alpha - 1) + \frac{4\alpha - 2}{2\alpha + 1}}} 
	= \smallO{n^{-\frac{4\alpha^2 - 4\alpha + 1}{2\alpha + 1}}}
	= \smallO{1},
\]
since $4\alpha^2 - 4\alpha + 1 > 0$ for all $\alpha > \frac{1}{2}$. Similarly, for $\alpha \ge \frac{3}{4}$ we have
that $4\alpha^2 > 2$ and hence,
\[
	n^{-(2\alpha - 1)} s_{\alpha}(k_n) = \smallO{n^{-(2\alpha - 1)} k_n} = \smallO{n^{-\frac{4\alpha^2 - 2}{2\alpha + 1}}}
	= \smallO{1}.
\]
\end{proof}

\begin{corollary}\label{cor:clustering_error_T_term}
Let $(k_n)_{n \ge 1}$ be any sequence with $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, for any $0 < \varepsilon < 1$ and $p \in \Kcal_{\varepsilon}(k_n)$, as $n \to \infty$,
\[
	\left|\frac{\Exp{T_{\Pcal,n}(p)}}{\Exp{T_{\Pcal}(p)}} - 1\right| = \bigO{s_\alpha(k_n)^{-1} k_n^{-3(2\alpha - 1)}} =
	\begin{cases}
		\bigO{k_n^{-(2\alpha - 1)}} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
				\bigO{\log(k_n)^{-1} k_n^{-\frac{1}{2}}} &\mbox{if } \alpha = \frac{3}{4},\\
				\bigO{k_n^{-(6\alpha-4)}} &\mbox{if } \alpha > \frac{3}{4}.
	\end{cases}
\]
\end{corollary}

\begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]

\PvdH{incorporate case where $k_n = \bigT{1}$.}

Recall that
\[
	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\int_{\Rcal_n} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}.
\]
By Lemma~\ref{lem:nodes_degree_k_P_n}
\[
	\Exp{N_{\Pcal,n}(k_n)} = (1+o(1)) \alpha n \int_{\R_+} \rho(y,k_n) e^{-\alpha} \dd y,
\]
and hence it is enough to show that
\[
	\int_{\Rcal_n} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y
	= (1 + \smallO{1}) \alpha n \int_{\R_+} \rho(y,k_n) \Exp{T_\Pcal(y)} e^{-\alpha y} \dd x \dd y.
\]

First we note that
\begin{align*}
	\left|T_{\Pcal,n}(p) - T_{\Pcal}(p)\right| = \sum_{p_1, p_2 \in \Rcal_n} \ind{p_1 \in \BallPon{p}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p, p_1)} + \sum_{p_1, p_2 \in \Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2)
\end{align*}
and hence
\begin{align*}
	\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right|
	&\le \int_{\Rcal_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\mu, \nu}(x_1,y_1) 
		\dd x_1 \dd y_1\\
	&\hspace{10pt}+ \iint_{\Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2) f_{\mu, \nu}(x_1,y_1) f_{\mu, \nu}(x_2,y_2)
		\dd x_2 \dd y_2 \dd x_1 \dd y_1. 
\end{align*}

The first integral was taken care of in Lemma \ref{lem:clustering_error_T_term}. For the second integral we have
\begin{align*}
	&\hspace{-30pt}\iint_{\Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2) f_{\mu, \nu}(x_1,y_1) f_{\mu, \nu}(x_2,y_2)
		\dd x_2 \dd y_2 \dd x_1 \dd y_1\\
	&\le \left(\int_{\Rcal \setminus \Rcal_n} \ind{p_1 \in \BallPo{p}} f_{\mu, \nu}(x_1,y_1) \dd x_1 \dd y_1\right)^2\\
	&= \bigO{\left(e^{y/2} \int_{R_n}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}
		= \bigO{e^y n^{-(2\alpha - 1)}},
\end{align*}
from which we conclude that
\[
	\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
	= \bigO{n^{-(2\alpha-1)} e^{y}}.
\]
Next we show that this difference is $\smallO{\Exp{T_\Pcal(p)}}$ when $y \in K_\eps(k_n)$.
Observe that since $\Exp{T_\Pcal(p)} = e^y \Delta_{\Pcal}(y)$, Proposition~\ref{prop:asymptotics_Delta_y_P} implies that $\Exp{T_\Pcal(y)} = \bigT{e^y s_\alpha(e^{y/2})}$ as $y \to \infty$.
Now consider $y \in K_C(k_n)$. Then $e^{y/2} = \bigT{k_n}$ and hence
\[
	\frac{\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right|}{\Exp{T_\Pcal(y)}} =
	\bigO{n^{-(2\alpha - 1)}s_\alpha(k_n)^{-1}\left(\log(k_n)k^{-2} + 1\right)} = \bigO{\left(n^{2\alpha - 1}s_\alpha(k_n)\right)^{-1}} = \smallO{1}, 
\]
where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. It follows that for $y \in \Kcal_\eps(k_n)$ we have
\[
	\Exp{T_{\Pcal,n}(y)} = (1+\smallO{1})\Exp{T_{\Pcal}(y)},
\]
while in general
\[
	\Exp{T_{\Pcal,n}(y)} = \Exp{T_{\Pcal}(y)}\left(1 + \bigO{s_\alpha(e^{y/2})}\right) = \bigO{e^y s_\alpha(e^{y/2})^2}.
\]
Therefore, by first applying a concentration argument and then Lemma~\ref{lem:replace_rho_n_with_rho}, 
\begin{align*}
	&\hspace{-30pt}\int_{\Rcal_n} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
	&= (1+\smallO{1})\int_{\Rcal_n} \rho_n(y,k_n) \Exp{T_\Pcal(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
	&= (1 + \smallO{1}) \int_{\Rcal_n} \rho(y,k_n) \Exp{T_\Pcal(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
	&= (1 + \smallO{1}) \alpha n \int_{\R_+} \rho(y,k_n) \Exp{T_\Pcal(y)} e^{-\alpha y} \dd x \dd y.
\end{align*}
\end{proof}

%\begin{corollary}
%\[
%	\Exp{T_{\Pcal,n}(k_n)} = \begin{cases}
%		\bigT{n k_n^{-3(2\alpha - 1)}} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4}\\
%		\bigT{n \log(k_n) k^{-2\alpha}} &\mbox{if } \alpha = \frac{3}{4} \\
%		\bigT{n k^{-2\alpha}} &\mbox{if } \alpha > \frac{3}{4}.
%	\end{cases}
%\]
%\end{corollary}
%
%\begin{remark}
%Note that for $p_0 \notin \Kcal_\varepsilon(k_n)$, we could have proven that
%\[
%	\left|\Delta_{\Pcal, n}(y) - \Delta_{\Pcal}(y)\right| = \bigO{n^{-\lambda}e^{(\alpha -\frac{1}{2})y}},
%\]
%for some $\lambda > 0$. However, this would have required us to do a more thorough analysis of the integral
%\[
%	\int_{\mathcal{E}_n} \Delta(p_0,p_1,p_2)g_{p_0}(x_1,y_1) g_{p_0}(x_2,y_2) \, dx_2 \, dx_1 \, dy_2 \, dy_1,
%\]
%making the proof more cumbersome. Since for our purpose we only need the $e^{\beta y}$ term, we omitted this additional analysis.
%\end{remark}

%\subsection{Equivalence for local clustering in $G_{\Pcal}(\alpha, \nu)$ and $G_{\Pcal,n}(\alpha,\nu)$}
%
%We now proceed with the proof of Proposition \ref{prop:convergence_average_clustering_P_n}. For this we split 
%$\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - \Exp{c_{\Pcal}^\ast(k_n)}\right|$ into three different terms which each evaluate the difference between the different elements of the local clustering function. We then analyze each term separately. The main tool we use is Lemma \ref{lem:clustering_error_Delta_term} together with the splitting technique we used in the proof of Lemma \ref{lem:asymptotics_integral_outside_K_epsilon}, which considers the integral over $\Kcal_\varepsilon(k_n)$ and $\Rcal_n \setminus \Kcal_\varepsilon(k_n)$ separately. 
%
%\begin{lemma}
%\[
%	\lim_{n \to \infty} \frac{\Exp{\widetilde{T}_{\Pcal,n}(k,\varepsilon)}}{\Exp{T_{\Pcal}(k)}} = 1.
%\]
%\end{lemma}
%
%\begin{proof}[Proof of Proposition \ref{prop:convergence_average_clustering_P_n}]
%
%We give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$. The proof for the other cases are similar.
%
%Let $0 < \varepsilon < 1$ and recall the definition $a_n^\pm = 2\log\left(\frac{(1\pm\varepsilon)k_n}{2\xi_{\alpha,\nu}}\right)$. In addition, recall that
%\[
%	\Exp{c_{\Pcal,n}^\ast(k_n)} = \int_{\Rcal_n} \frac{\Delta_{\Pcal,n}(y) \rho_k(y)}{\Exp{N_{\Pcal,n}(k_n)} \binom{k_n}{2}}  
%    f_{\alpha, \nu}(x,y) \, dx \, dy.
%\]
%
%We now use Lemma \ref{lem:expectation_clustering_P} and \eqref{eq:expectation_clustering_P_n} to write
%\begin{align*}
%	\left|\Exp{c_{\Pcal,n}^\ast(k_n) - c_{\Pcal}^\ast(k_n)}\right|
%	&= \left|\frac{\int_0^{R_n} \Delta_{\Pcal,n}(y) \, \rho_{n,y}(k_n) e^{-\alpha y} \, dy}
%		{\int_0^{R_n} \rho_{n,y}(k_n) e^{-\alpha y} \, dy} 
%		- \frac{\int_0^{\infty} \Delta_{\Pcal}(y) \, \rho_{y}(k_n) e^{-\alpha y} \, dy}
%		{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy}\right|\\
%	&\le \frac{\int_0^{R_n} \left|\Delta_{\Pcal,n}(y) \, \rho_{n,y}(k) - \Delta_{\Pcal}(y) \, \rho_{y}(k)\right| 
%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy} \\
%	&\hspace{10pt}+ \frac{\int_{R_n}^\infty \Delta_{\Pcal}(y) \, \rho_{y}(k) 
%			e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy}\\
%	&\hspace{10pt}+ \frac{\int_0^{R_n} \Delta_{\Pcal,n}(y) \, \rho_{n,y}(k) e^{-\alpha y} \, dy}
%		{\int_0^{R_n}  \rho_{y}(k_n) e^{-\alpha y} \, dy}
%		\left|\frac{\int_0^{R_n}  \rho_{y}(k_n) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{n,y}(k_n) e^{-\alpha y} \, dy}
%		- 1\right|\\
%	&:= I_n^{(1)}(k_n) + I_n^{(2)}(k_n) + I_n^{(3)}(k_n)
%\end{align*}
%We will deal with all three terms separately and show that
%\begin{equation}
%	\lim_{n \to \infty} k_n^{4\alpha - 2} I_n^{(i)}(k_n) = 0 \quad \text{for } i = 1, 2, 3.
%\end{equation} 
%
%For $I_n^{(1)}(k_n)$ we write
%\begin{align}
%	I_n^{(1)}(k_n)	&\le \frac{\int_0^{R_n} \left|\Delta_{\Pcal,n}(y)  - \Delta_{\Pcal}(y) \right| \rho_{y}(k_n)
%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy} 
%        \label{eq:diff_Delta_integral}\\
%	&\hspace{10pt}+ \frac{\int_0^{R_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\Pcal,n}(y) 
%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy}. \label{eq:diff_Poisson_distribution}
%\end{align}
%
%For \eqref{eq:diff_Delta_integral} we use Lemma \ref{lem:clustering_error_Delta_term} to obtain
%\begin{align*}
%	\int_0^{R_n} \left|\Delta_{\Pcal,n}(y)  - \Delta_{\Pcal}(y) \right| \rho_{y}(k_n) e^{-\alpha y} \, dy
%    &\le \bigO{k_n^{-3(2\alpha - 1)}}\int_{a_n^-}^{a_n^+} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
%    &\hspace{10pt}+ \bigO{n^{-(2\alpha - 1)}k^{2\alpha - 1}\int_0^\infty \Delta_\Pcal(y)\rho_{y}(k_n) e^{-\alpha y} 
%    	\, dy}\\
%    &\hspace{10pt}+ \bigO{\frac{1}{n}\int_{\Rcal_n \setminus \Kcal_\varepsilon(k_n)} e^{(\alpha - \frac{1}{2})y} 
%    	\rho_{y}(k_n) f_{\alpha,\nu}(x,y) \, dx \, dy}.
%\end{align*}
%Observe that first term is bounded from above by
%\[
%	\bigO{k_n^{-3(2\alpha - 1)}} \int_0^\infty \rho_y(k_n) e^{-\alpha y} \, dy
%\]
%and recall that $\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy = \Theta\left(k_n^{-(2\alpha + 1)}\right)$. Hence
%\begin{align*}
%	&\hspace{-30pt}k_n^{4\alpha - 2} \, \frac{\int_0^{R_n} \left|\Delta_{\Pcal,n}(y) - \Delta_{\Pcal}(y) 
%		\right| \rho_{y}(k_n) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy}\\
%    &= \bigO{k_n^{4\alpha - 2} k_n^{-3(2\alpha - 1)}} + \bigO{n^{-(2\alpha - 1)}k^{2\alpha - 1}} k_n^{4\alpha - 2}\Exp{c_\Pcal^\ast(k_n)}\\
%	&\hspace{10pt}+ \bigO{k_n^{6\alpha - 1} \frac{1}{n}\int_{\Rcal_n \setminus \Kcal_\varepsilon(k_n)} e^{(\alpha - \frac{1}{2})y} 
%    	\rho_{y}(k_n) f_{\alpha,\nu}(x,y) \, dx \, dy}.
%\end{align*}
%The first term here is $\bigO{k_n^{-(\alpha - \frac{1}{2})}}$ which converges to zero. The second term converges to zero by [Proposition on scaling] and the fact that $n^{-(2\alpha - 1)}k^{2\alpha - 1} = o(1)$. The same holds for the third term by Lemma \ref{lem:asymptotics_integral_outside_K_epsilon}. 
%
%For \eqref{eq:diff_Poisson_distribution} we apply the same splitting technique as in the proof of Lemma \ref{lem:clustering_error_Delta_term}. That is, we take $0 < \varepsilon < 1$, $a_n^+ = 2\log\left((1+\varepsilon)k_n\right)$ and write
%\begin{align*}
%	\int_0^{R_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) e^{-\alpha y} \, dy
%	&= \int_0^{a_n^+} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) e^{-\alpha y} \, dy\\
%	&\hspace{10pt}+ \int_{a_n^+}^{R_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) e^{-\alpha y} \, dy
%\end{align*}
%Next we use Lemma \ref{lem:mu_measure_B} to obtain
%\begin{align*}
%	\rho_{n, y}(k_n) &= \rho_y(k_n) \left((1+\phi_n(y))^{k_n} \left(1 - e^{-\alpha R_n}\right)^{-k_n}
%		e^{-\mu(B(0,y))\left(\phi_n(y) + \frac{(1 + \phi_n(y))e^{-\alpha R_n}}{1 - e^{-\alpha R_n}}\right)}\right).
%\end{align*}
%Using that
%\begin{align*}
%	\max_{0 \le y \le a_n} \hspace{-5pt} \phi_n(y)
%	= O\left(n^{-(2\alpha - 1)(1-\kappa)}\right) \quad \text{and} \quad
%	\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy = \Theta\left(k_n^{-(2\alpha + 1)}\right)
%\end{align*}
%we get for the first integral,
%\begin{align*}
%	&\hspace{-30pt}k_n^{4\alpha - 2}\frac{\int_0^{a_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) 
%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy}\\
%	&= O\left(n^{-(2\alpha - 1)(1-\kappa)} k_n^{4\alpha - 2}\frac{\int_0^\infty \Delta_{\mu}(y) \rho_{y}(k_n) e^{-\alpha y} 
%		\, dy}{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy}\right)\\
%	&= O\left(n^{-(2\alpha - 1)(1-\kappa)}\right).
%\end{align*}
%For the second integral we use that $\phi_n(y) = O(1)$ for all $0 \le y \le R_n$ and hence, using the same argumentation as at the end of the proof of Lemma \ref{lem:clustering_error_Delta_term},
%\begin{align*}
%	&\hspace{-30pt}k_n^{4\alpha - 2}\frac{\int_{a_n}^{R_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) 
%		e^{-\alpha y} \, dy}{\int_0^\infty \rho_y(k_n) \, e^{-\alpha y} \, dy}\\
%	&= O\left(k_n^{4\alpha - 2}\frac{\int_{a_n}^{R_n} \rho_{y}(k_n) \Delta_{\mu}(y) e^{-\alpha y} \, dy}
%		{\int_0^\infty \rho_y(k_n) \, e^{-\alpha y} \, dy}\right)\\
%	&= O\left(k_n^{6\alpha - 1}\rho_{a_n}(k_n)\right) = o(1).
%\end{align*}
%We therefore conclude that $k_n^{4\alpha - 2}I_n^{(1)}(k_n) \to 0$.
%
%Next we consider the second term
%\[
%	I_n^{(2)}(k_n) = \frac{\int_{R_n}^\infty \Delta_{\mu}(y) \, \rho_{y}(k) 
%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy}.
%\]
%Since
%\[
%	\int_{R_n}^\infty \Delta_{\mu}(y) \, \rho_{y}(k) e^{-\alpha y} \, dy 
%	\le \rho_{R_n}(k_n) \int_0^\infty e^{-\alpha y} \, dy = O\left(\rho_(R_n)(k_n)\right) 
%	= O\left(\rho_{a_n}(k_n)\right),
%\]
%it follows from the above computations that
%\[
%	\lim_{n \to \infty} k_n^{4\alpha - 2} \frac{\int_{R_n}^\infty \Delta_{\mu}(y) \, \rho_{y}(k) 
%	e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy} = 0.
%\]
%The proof for $I_n^{(3)}(k_n)$ follows using the same splitting technique and arguments. We therefore omit it.
%\end{proof}

\subsection{Counting missing triangles}

We now come back to computing the expected number of triangles attached to node at height $y$ in $G_{\Pcal,n}(\alpha,\nu)$ that are not present in $G_{\Pcal}(\alpha,\nu)$.

\begin{figure}[!t]

\centering
\begin{tikzpicture}[scale=1.25]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																								  %
%	Shows the three different areas B_n^{(i)} for the computations in Lemma 					  %
%	\label{lem:clustering_error_T_term}			  												  %
%																								  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	%Define the coordinates 
	%p = (\u,\v) and p^\prime = (\uu, \vv)
	%Box \Rcal_n has width 2\r and height \t
	\pgfmathsetmacro{\u}{0}
	\pgfmathsetmacro{\v}{1}
	\pgfmathsetmacro{\uu}{1.8}
	\pgfmathsetmacro{\vv}{1.7}
	\pgfmathsetmacro{\r}{6}
	\pgfmathsetmacro{\t}{4}

	%The box \Rcal_n only positive x
	\draw[line width=1pt] (0,0) -- (\r,0) -- (\r,\t) -- (0,\t) -- (0,0);

	%Boundaries p = (\u,\v)

	%Right boundary
	\pgfmathsetmacro{\rightbounduv}{\u+exp((\v)/2)}
	\draw[domain=\rightbounduv:\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-\v});
    %Left boundary
%    \pgfmathsetmacro{\leftbounduv}{\u-exp((\v)/2)}
%    \draw[domain=\leftbounduv:-\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-\v});

    %Three boundaries for the regions B_n
    \pgfmathsetmacro{\bone}{\r*(1-exp(-\v/2))}
    \pgfmathsetmacro{\btwo}{\r*(exp(-\v/2)-1)}
    %Star boundary
    \pgfmathsetmacro{\bthreeleft}{\r*(1-exp(\v/2))}
    \pgfmathsetmacro{\bthreeright}{\r*(1-exp((\v-\t)/2))}

    \draw[domain=0:\bone,smooth,variable=\x,red,line width=1pt] plot (\x, {\v-2*ln(\r/(\r-\x))});
    \draw[domain=0:\r,smooth,variable=\x,red,line width=1pt] plot (\x, {\v+2*ln(1+(\x/\r))});
    \draw[domain=0:\bthreeright,smooth,variable=\x,red, line width=1pt] plot (\x, {2*ln((\r/(\r-\x)))+\v});

    %Define the top and bottom coordinates of y^prime boundaries
    \pgfmathsetmacro{\ybottom}{\v+2*ln(\r/(\r+exp(\v)))}
    \pgfmathsetmacro{\xbottom}{\r*exp(\v)/(\r + exp(\v))}
    \pgfmathsetmacro{\ytop}{\v+2*ln(\r/(\r-exp(\v)))}
    \pgfmathsetmacro{\xtop}{\r*exp(\v)/(\r - exp(\v))}

    \draw[dashed,line width=1pt,red] (\xbottom,\ybottom) -- (\r,\ybottom);
    \draw[dashed,line width=1pt,red] (\xtop,\ytop) -- (\r,\ytop);
    \draw node at (\r+0.5,\ybottom) {\color{red}$h_\ast(y)$};
    \draw node at (\r+0.5,\ytop) {\color{red}$h^\ast(y)$};

    \draw node at (0.5,\ybottom+0.2) {$B_n^{(1)}$};
    \draw node at (\xbottom,\ybottom+0.75) {$B_n^{(2)}$};
    \draw node at (\xtop,\ytop+0.75) {$B_n^{(3)}$};

    %Define h_1(p) = h_2(p)
    \pgfmathsetmacro{\hp}{2*ln(\r-\u)-\v}

    %Define h_1(p^\prime) and h_2(p^\prime)
    \pgfmathsetmacro{\hh}{2*ln(\uu+\r)-\vv}
    \pgfmathsetmacro{\hhh}{2*ln(\r-\uu)-\vv}

%    \draw node at (-\r-0.75,\hh+0.1) {\color{blue}$h_1(p^\prime)$};
%    \draw node at (\r+0.75,\hhh) {\color{blue}$h_2(p^\prime)$};

   	%Draw node p
    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] (p1) at (\u,\v) {};
    \path (p1)+(-0.2,0.2) node {$p$};

\end{tikzpicture}
\caption{Three different areas $B_n^{(i)}$ used in the proof of Lemma \ref{lem:clustering_error_T_term}.}
\label{fig:comparing_triangles_B_areas}
\end{figure}

\begin{proof}[Proof of Lemma \ref{lem:clustering_error_T_term}]
Due to symmetry it is enough to show that
\begin{equation}\label{eq:clustering_error_T_main}
	\int_0^{R_n}\int_0^{I_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\mu, \nu}(x_1,y_1) 
	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
\end{equation}
The proof goes in two stages. First we compute $\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right)$ by splitting it over three disjoint regimes with respect to $p_1$, with $x_1 \ge 0$. Then we do the integration with respect to $p_1$.

\subsubsection*{Computing $\bm{\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right)}$}

\PvdH{I have currently used that $\alpha < 1$, which is the most difficult case. The case $\alpha = 1$ and $\alpha > 1$ will be added.}

Define the sets
\begin{align*}
	A_n^{(1)} &= \left\{p_1 \in \Rcal_n \, : \, 0 \le y_1 \le y - 2\log(I_n/(I_n-x_1)) \right\},\\
	A_n^{(2)} &= \left\{p_1 \in \Rcal_n \, : \, y - 2\log(I_n/(I_n-x_1)) < y_1 
		\le y + 2 \log\left(1 + \frac{x_1}{I_n}\right)\right\},\\
	A_n^{(3)} &= \left\{p_1 \in \Rcal_n \, : \, y + 2 \log\left(1 + \frac{x_1}{I_n}\right) < y_1 
			\le y + 2 \log\left(\frac{I_n}{I_n-x_1}\right)\right\},
\end{align*}
and let $B_n^{(i)} = \BallPon{p} \cap A_n^{(i)}$, for $i = 1, 2, 3$, see Figure~\ref{fig:comparing_triangles_B_areas}. Here the heights of the two intersections are given by
\begin{align}
	h_\ast(y) &= y + 2 \log\left(\frac{I_n}{I_n + e^y}\right)\\
	h^\ast(y) &= y + 2 \log\left(\frac{I_n}{I_n - e^y}\right).
\end{align}

With these definitions we have that the union $B_n := \bigcup_{i = 1}^n B_n^{(i)}$ denotes the area under the red curve in Figure~\ref{fig:comparing_triangles_diff_analysis} and hence, for all $p_1 \in \Rcal_n\setminus B_n$ with $x_1 \ge 0$ we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1) = \emptyset$. So we only need to consider $p_1 \in B_n$. We shall establish the following result:
\begin{equation}\label{eq:mu_triangle_diff}
	\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = 
	\begin{cases}
		\bigO{I_n^{-2\alpha} e^{\alpha y_1}} &\mbox{if } p_1 \in B_n^{(1)}\\
		\bigO{I_n^{-2\alpha} e^{\alpha y}} &\mbox{if } p_1 \in B_n^{(2)} \cup B_n^{(3)}
	\end{cases}
\end{equation}

Depending on which regime $p_1$ belongs to, the set $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)$ has a different shape. We displayed these shapes in Figure~\ref{fig:shapes_triangle_mismatches} as a visual aid to follow the computations below.

\begin{figure}[!tp]
\centering
\begin{tikzpicture}[scale=5]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																								  %
%	Shows the area T_{\Pcal \Delta \Pcal_n} when h_1(p^\prime) > h_2(p^\prime) > h(y)			  %
%																								  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	%Define the coordinates 
	%p = (\u,\v) and p^\prime = (\uu, \vv)
	%Box \Rcal_n has width 2\r and height \t
	\pgfmathsetmacro{\u}{0}
	\pgfmathsetmacro{\v}{1}
	\pgfmathsetmacro{\uu}{1.4}
	\pgfmathsetmacro{\vv}{0.2}
	\pgfmathsetmacro{\r}{6}
	\pgfmathsetmacro{\t}{4}

    %Define x^\ast(p^\prime) and y^\ast(p^\prime)
    \pgfmathsetmacro{\uuast}{\uu-\r}
    \pgfmathsetmacro{\vvast}{2*ln(\r)-\vv}

    %Define intersection left black and shifted blue curve
    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1 + exp((\vv - \v)/2))}

    %Define h_1(p) = h_2(p)
    \pgfmathsetmacro{\hp}{2*ln(\r-\u)-\v}

    %Define h_1(p^\prime) and h_2(p^\prime)
    \pgfmathsetmacro{\hh}{2*ln(\uu+\r)-\vv}
    \pgfmathsetmacro{\hhh}{2*ln(\r-\uu)-\vv}

    %Draw the boundary left black, left blue and shifted right blue line
	\draw[red,line width=1pt] 
		plot[domain=\uuast:-\r,smooth,variable=\x,red] (\x, {2*ln(\x+(2*\r-\uu))-\vv}) 
		-- 
		(-\r,\hh)
		-- 
		plot[domain=-\r:\uuast,smooth,variable=\x,red] (\x, {2*ln(\uu-\x)-\vv});

	\pgfmathsetmacro{\top}{2*ln(\uu-\uast)-\vv}

	\draw[red, dashed,line width=1pt] (-\r,\vvast) -- (\uuast,\vvast);

    \draw node at (-\r-0.2,\hh+0.1) {\color{blue}$(-\frac{\pi}{2} e^{R_n/2}, h_1(p^\prime))$};
    \draw node at (-\r-0.2,\hhh-0.1) {$(-\frac{\pi}{2} e^{R_n/2}, h_2(p^\prime))$};
    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p^\prime), y^\ast(p^\prime))$};

    \draw node at (-\r+0.3,\vvast+0.2) {$I_n^{(2)}$};
    \draw node at (-\r+0.3,\vvast-0.2) {$I_n^{(1)}$};

    \draw node (f2) at (\uuast-0.3,\hh+0.1) {\color{blue}$b_{p^\prime}^-(z)$};
    \draw node (f3) at (\uuast-0.3,\hhh) {\color{blue}$b_{p^\prime}^+(z)$};
    \path (f2)+(230:0.35) node (f2_arrow) {};
    \path (f3)+(130:0.35) node (f3_arrow) {};
    \draw[->,thick,blue] (f2.south west) -- (f2_arrow);
    \draw[->,thick,blue] (f3.north west) -- (f3_arrow);

	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (-\r,\hhh) {};
	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (-\r,\hh) {};
	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (\uuast,\vvast) {};

\end{tikzpicture}\\
\vspace{20pt}
\begin{tikzpicture}[scale=5]
	%Define the coordinates 
	%p = (\u,\v) and p^\prime = (\uu, \vv)
	%Box \Rcal_n has width 2\r and height \t
	\pgfmathsetmacro{\u}{0}
	\pgfmathsetmacro{\v}{1}
	\pgfmathsetmacro{\uu}{1.4}
	\pgfmathsetmacro{\vv}{0.8}
	\pgfmathsetmacro{\r}{6}
	\pgfmathsetmacro{\t}{4}

    %Define x^\ast(p^\prime) and y^\ast(p^\prime)
    \pgfmathsetmacro{\uuast}{\uu-\r}
    \pgfmathsetmacro{\vvast}{2*ln(\r)-\vv}

    %Define intersection left black and shifted blue curve
    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1 + exp((\vv - \v)/2))}

    %Define h_1(p) = h_2(p)
    \pgfmathsetmacro{\hp}{2*ln(\r-\u)-\v}

    %Define h_1(p^\prime) and h_2(p^\prime)
    \pgfmathsetmacro{\hh}{2*ln(\uu+\r)-\vv}
    \pgfmathsetmacro{\hhh}{2*ln(\r-\uu)-\vv}

    %Draw the boundary left black, left blue and shifted right blue line
	\draw[red,line width=1pt] 
		plot[domain=\uuast:\uast,smooth,variable=\x,red] (\x, {2*ln(\x+(2*\r-\uu))-\vv}) 
		-- 
		plot[domain=\uast:-\r,smooth,variable=\x,red] (\x, {2*ln(-\x)-\v})
		-- 
		(-\r,\hh)
		-- 
		plot[domain=-\r:\uuast,smooth,variable=\x,red] (\x, {2*ln(\uu-\x)-\vv});

	\pgfmathsetmacro{\rb}{\uu + exp((\vv+\hp)/2) -2*\r}

	%\draw[red,dashed,line width=1pt] (\uast,\vast) -- (\uast,\hp);
	\draw[red,dashed,line width=1pt] (-\r,\hp) -- (\rb,\hp);

    \draw node at (-\r-0.2,\hh+0.1) {\color{blue}$(-\frac{\pi}{2} e^{R_n/2}, h_1(p^\prime))$};
    \draw node at (-\r-0.2,\hp-0.1) {$(-\frac{\pi}{2} e^{R_n/2}, h(y))$};
    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p^\prime), y^\ast(p^\prime))$};
    \draw node at (\uast,\vast-0.1) {$(\hat{x}(p,p^\prime), \hat{y}(p, p^\prime))$};

    \draw node at (\uast,\vvast+0.1) {$\mathcal{I}_n^{(1)}$};
    \draw node at (\uast,\hp-0.05) {$\mathcal{I}_n^{(2)}$};
    %\draw node at (\uast+0.1,\hp-0.05) {$\mathcal{I}_n^{(3)}$};

    \draw node (f1) at (-\r-0.05,\hhh) {$b_p^-(z)$};
    \draw node (f2) at (\uast+0.5,\hh+0.1) {\color{blue}$b_{p^\prime}^-(z)$};
    \draw node (f3) at (\uuast-0.3,\hhh) {\color{blue}$b_{p^\prime}^+(z)$};
    \path (f1)+(45:0.35) node (f1_arrow) {};
    \path (f2)+(230:0.35) node (f2_arrow) {};
    \path (f3)+(130:0.35) node (f3_arrow) {};
    \draw[->,thick] (f1.north east) -- (f1_arrow);
    \draw[->,thick,blue] (f2.south west) -- (f2_arrow);
    \draw[->,thick,blue] (f3.north west) -- (f3_arrow);

	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (-\r,\hp) {};
	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (-\r,\hh) {};
	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (\uuast,\vvast) {};
	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (\uast,\vast) {};

\end{tikzpicture}\\
\vspace{20pt}
\begin{tikzpicture}[scale=5]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%																								  %
%	Shows the area T_{\Pcal \Delta \Pcal_n} when h(y) > h_1(p^\prime)							  %
%																								  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	%Define the coordinates 
	%p = (\u,\v) and p^\prime = (\uu, \vv)
	%Box \Rcal_n has width 2\r and height \t
	\pgfmathsetmacro{\u}{0}
	\pgfmathsetmacro{\v}{1}
	\pgfmathsetmacro{\uu}{2.5}
	\pgfmathsetmacro{\vv}{1.8}
	\pgfmathsetmacro{\r}{6}
	\pgfmathsetmacro{\t}{4}

    %Define x^\ast(p^\prime) and y^\ast(p^\prime)
    \pgfmathsetmacro{\uuast}{\uu-\r}
    \pgfmathsetmacro{\vvast}{2*ln(\r)-\vv}

    %Define intersection left black and shifted blue curve
    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1 + exp((\vv - \v)/2))}

    %Define intersection left black and left blue curve
    \pgfmathsetmacro{\utilde}{\uu/(1-exp((\vv-\v)/2))} 
    \pgfmathsetmacro{\vtilde}{2*ln(\uu-\utilde)-\vv}

    %Define h_1(p) = h_2(p)
    \pgfmathsetmacro{\hp}{2*ln(\r-\u)-\v}

    %Define h_1(p^\prime) and h_2(p^\prime)
    \pgfmathsetmacro{\hh}{2*ln(\uu+\r)-\vv}
    \pgfmathsetmacro{\hhh}{2*ln(\r-\uu)-\vv}

    %Draw the boundary left black, left blue and shifted right blue line
	\draw[red,line width=1pt] 
		plot[domain=\utilde:\uuast,smooth,variable=\x,red] (\x, {2*ln(\uu-\x)-\vv})
		--
		plot[domain=\uuast:\uast,smooth,variable=\x,red] (\x, {2*ln(\x+(2*\r-\uu))-\vv})
		--
		plot[domain=\uast:\utilde,smooth,variable=\x,red] (\x, {2*ln(-\x)-\v});

	%Calculate intersection point
	\pgfmathsetmacro{\i}{-exp((\v+\vvast)/2)}
	\draw[red, dashed,line width=1pt] (\i,\vvast) -- (\uuast,\vvast);

    \draw node at (\utilde,\vtilde+0.1) {\color{black}$(\tilde{x}(p,p^\prime), \tilde{y}(p,p^\prime))$};
    \draw node at (\uast,\vast-0.1) {$(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$};
    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p^\prime), y^\ast(p^\prime))$};

    \draw node at (\uuast-0.45,\vvast+0.07) {$\mathcal{I}_n^{(2)}$};
    \draw node at (\uast+0.025,\vvast-0.045) {$\mathcal{I}_n^{(1)}$};

    \draw node (f1) at (\uast-0.7,\vast-0.1) {\color{black}$b_{p}^-(z)$};
    \draw node (f2) at (\uuast-0.2,\vvast+0.5) {\color{blue}$b_{p^\prime}^-(z)$};
    \draw node (f3) at (\uast+0.5,\vast+0.025) {\color{blue}$b_{p^\prime}^+(z)$};
    \path (f1)+(45:0.35) node (f1_arrow) {};
    \path (f2)+(230:0.35) node (f2_arrow) {};
    \path (f3)+(180:0.3) node (f3_arrow) {};
	\draw[->,thick] (f1.north east) -- (f1_arrow);
    \draw[->,thick,blue] (f2.south west) -- (f2_arrow);
    \draw[->,thick,blue] (f3.west) -- (f3_arrow);
%
	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (\utilde,\vtilde) {};
	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (\uast,\vast) {};
	\draw node[red, fill, circle, inner sep=0pt, minimum size=5pt] at (\uuast,\vvast) {};

\end{tikzpicture}
\caption{The different shapes of $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)$ depending on the regime to which $p_1$ belongs. The top figure is for $p_1 \in B_n^{(1)}$, the middle for $p_1 \in B_n^{(2)}$ and the bottom one for $p_1 \in B_n^{(3)}$.}
\label{fig:shapes_triangle_mismatches}
\end{figure}

\paragraph{Regime 1: $0 \le y_1 \le y - 2\log(I_n/(I_n-x_1))$}

In this case the integral over $p_2$ splits into two parts
\begin{align*}
	\mathcal{I}_n^{(1)}(p_1) &:= \int_{h_2(p_1)}^{y^\ast(p_1)} \int_{-I_n}^{x_1 + e^{(y_1+y_2)/2}-2I_n} e^{-\alpha y_2}
		\dd x_2 \dd y_2\\
	\mathcal{I}_n^{(2)}(p_1) &:= \int_{y^\ast(p_1)}^{h_1(p_1)} \int_{x^\ast(p_1)}^{x_1 - e^{(y_1+y_2)/2}} e^{-\alpha y_2}
		\dd x_2 \dd y_2.
\end{align*}

We first compute $\mathcal{I}_n^{(1)}$.
\begin{align*}
	\mathcal{I}_n^{(1)}(p_1) &= \int_{h_2(p_1)}^{y^\ast(p_1)} \left(x_1 + e^{(y_1+y_2)/2} - I_n\right) e^{-\alpha y_2} 
		\dd x_2 \dd y_2\\
	&\le e^{y_1/2} \int_{h_2(p_1)}^{y^\ast(p_1)} e^{-(\alpha-\frac{1}{2}) y_2} \dd y_2\\
	&= \frac{2 e^{y_1/2}}{2\alpha - 1} \left(e^{-(\alpha-\frac{1}{2})h_2(p_1)} - e^{-(\alpha-\frac{1}{2})y^\ast(p_1)}
		\right) \\
	&= \frac{2 e^{\alpha y_1}}{2\alpha - 1} I_n^{-(2\alpha -1)}\left(\left(1 - \frac{x_1}{I_n}\right)^{-(2\alpha - 1)}-1\right)\\
	&= \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}},
\end{align*}
where we used that $x^\prime \le e^{(y+y_1)/2} = \smallO{I_n}$ for all $y_1\le y$ and $y \in \Kcal_{\varepsilon}(k_n)$ so that
\[
	\left(\left(1 - \frac{x_1}{I_n}\right)^{-(2\alpha - 1)}-1\right) = \bigO{\frac{x^\prime}{I_n}} \quad 
	\text{as } n \to \infty.
\]

For $\mathcal{I}_n^{(2)}(p_1)$ we have
\begin{align*}
	\mathcal{I}_n^{(2)}(p_1) &= \int_{y^\ast(p_1)}^{h_1(p_1)} \left(I_n + x_1 - e^{(y_1+y_2)}\right) e^{-\alpha y_2}
		\dd x_2 \dd y_2\\
	&\le 2 I_n \int_{y^\ast(p_1)}^{h_1(p_1)} e^{-\alpha y_2} \dd x_2 \dd y_2\\
	&= \frac{2}{\alpha} I_n \left(I_n^{-2\alpha}e^{\alpha y_1} - \left(I_n + x_1\right)^{-2\alpha} e^{-\alpha y_1}\right)\\
	&= \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}} = \bigO{I_n^{-(2\alpha - 1)} e^{\alpha y_1}}.
\end{align*}

We conclude that for $p_1 \in B_n^{(1)}$:
\[
	\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}},
\]
which establishes the first part of \eqref{eq:mu_triangle_diff}.

\paragraph{Regime 2: $y - 2\log(I_n/(I_n-x_1)) < y_1 \le y + 2 \log\left(1 + \frac{x_1}{I_n}\right)$}

Here we split the integration into three parts (see Figure~\ref{fig:shapes_triangle_mismatches}). Recall that $x^\ast(p,p_1) = x_1 - I_n$. Then, for the first part we have
\begin{align*}
	\mathcal{I}_n^{(1)}(p,p_1) &\le \int_{h(y)}^{h_1(p_1)} \int_{-I_n}^{x^\ast(p,p_1)} f_{\alpha,\nu}(x_2, y_2) 
		\dd x_2 \dd y_2\\
	&= \bigO{x_1 \left(e^{-\alpha h(y)} - e^{-\alpha h_1(p_1)}\right)}\\
	&= \bigO{x_1 I_n^{-2\alpha}\left(e^{\alpha y} - e^{\alpha y_1}\left(1 + \frac{x_1}{I_n}\right)^{-2\alpha}\right)}\\
	&= \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}\left(\left(1 - \frac{x_1}{I_n}\right)^{-2\alpha} 
		- \left(1 + \frac{x_1}{I_n}\right)^{-2\alpha}\right)}\\
	&= \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}} = \bigO{I_n^{-(2\alpha - 1)} e^{\alpha y}}, 
\end{align*}
were we used that $y \le y_1 + 2\log(I_n/(I_n-x_1))$ for $p_1 \in B_n^{(2)}$ for the third line and 
\[
	\left(1 - \frac{x_1}{I_n}\right)^{-2\alpha} - \left(1 + \frac{x_1}{I_n}\right)^{-2\alpha}
	= \bigO{\frac{x_1}{I_n}} = \bigO{1},
\]
for the last line.

For the second part we first compute that 
\begin{align*}
	x_1 + e^{(y_1+y_2)/2} - 2 I_n + e^{(y + y_2)/2} &\le \left(e^{y/2} + e^{y_1/2}\right)e^{y_2/2}\\
	&\le e^{y/2}\left(1 + \frac{I_n}{I_n - e^y}\right)e^{y_2/2} = \bigO{e^{(y+y_2)/2}},
\end{align*}
since $y \in \Kcal_{\varepsilon}(k_n)$ and $k_n = \smallO{\sqrt{n}}$, so that $e^y = \smallO{n} = \smallO{I_n}$. 
Then we have
\begin{align*}
	\mathcal{I}_n^{(2)} &= \int_{\hat{y}(p,p_1)}^{h(y)} \int_{-e^{(y + y_2)/2}}^{x_1 + e^{(y+y_1)/2} - 2 I_n} 
		f_{\alpha,\nu}(x_2, y_2) \dd x_2 \dd y_2\\
	&= \bigO{e^{y/2} \int_{\hat{y}(p,p_1)}^{h(y)} e^{-(\alpha -\frac{1}{2}) y_2} \dd y_2}\\
	&= \bigO{e^{y/2} \left(e^{-(\alpha -\frac{1}{2}) \hat{y}(p,p_1)} - e^{-(\alpha -\frac{1}{2}) h(y)}\right)}\\
	&= \bigO{e^{y/2} \left(\left(\frac{2I_n - x_1}{e^{y/2} + e^{y_1/2}}\right)^{-(2\alpha-1)} 
		- I_n^{-(2\alpha-1)} e^{(\alpha -\frac{1}{2}) y}\right)}\\
	&= \bigO{I_n^{-(2\alpha-1)} e^{\alpha y}},
\end{align*}
where for the last line we first used that $(2I_n - x_1)^{-(2\alpha-1)} \le I_n^{-(2\alpha-1)}$ and then
\[
	\left(\left(e^{y/2} + e^{y_1/2}\right)^{2\alpha-1}- e^{(\alpha -\frac{1}{2}) y}\right)
	\le e^{(\alpha -\frac{1}{2}) y}\left(\left(1 + \sqrt{1+\frac{x_1}{I_n}} \, \right)^{2\alpha - 1} - 1\right)
	= \bigO{e^{(\alpha -\frac{1}{2}) y}}.
\]

It then follows that for $p_1 \in B_n^{(2)}$
\[
	\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-(2\alpha-1)} e^{\alpha y}}.
\]

\paragraph{Regime III $\bm{p_1 \in B_n^{(3)}}$:}

\begin{align*}
	\mathcal{I}_n^{(1)} &= \int_{y^\ast}^{\tilde{y}} \int_{-e^{(y+y_2)/2}}^{x_1-e^{(y_1+y_2)/2}} f_{\alpha, \nu}(x_2,y_2)
		\dd x_2 \dd y_2\\
	&= \bigO{\int_{y^\ast}^{\tilde{y}} x_1 e^{-\alpha y_2} - \left(e^{y_1/2} - e^{y/2}\right)e^{-(\alpha - \frac{1}{2})y_2}
		\dd y_2}\\
	&= \bigO{x_1 \int_{y^\ast}^{\tilde{y}}  e^{-\alpha y_2} \dd y_2}.
\end{align*}

Now 
\begin{align*}
	\int_{y^\ast}^{\tilde{y}}  e^{-\alpha y_2} \dd y_2 
	&= \frac{1}{\alpha}\left(e^{-\alpha y^\ast} - e^{-\alpha \tilde{y}}\right) 
		= \frac{1}{\alpha}\left(I_n^{-2\alpha} e^{\alpha y_1} 
		- \left(\frac{x_1}{e^{y_1/2} - e^{y/2}}\right)^{-2\alpha}\right) \\
	&= \frac{I_n^{-2\alpha} e^{\alpha y_1}}{\alpha}\left(1 - \left(1 - e^{(y - y_1)/2}\right)^{2\alpha}
		\left(\frac{x_1}{I_n}\right)^{-2\alpha}\right) = \bigO{I_n^{-2\alpha} e^{\alpha y_1}},
\end{align*}
and hence we have
\[
	\mathcal{I}_n^{(1)} = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}}.
\]

For the second integral we have
\begin{align*}
	\mathcal{I}_n^{(2)} &= \int_{\hat{y}}^{y^\ast} \int_{-e^{(y+y_2)/2}}^{e^{(y_1 + y_2)/2} + x_1 - 2I_n} 
		f_{\alpha, \nu}(x_2,y_2)\dd x_2 \dd y_2\\
	&= \bigO{\int_{\hat{y}}^{y^\ast} \left(e^{y/2} + e^{y_1/2}\right)e^{-(\alpha - \frac{1}{2})y_2} \dd y_2}\\
	&= \bigO{ e^{y_1/2} \int_{\hat{y}}^{y^\ast}e^{-(\alpha - \frac{1}{2})y_2} \dd y_2}.
\end{align*}

For the integral we have
\begin{align*}
	\int_{\hat{y}}^{y^\ast}e^{-(\alpha - \frac{1}{2})y_2} \dd y_2
	&= \frac{2}{2\alpha - 1} \left(e^{-(\alpha - \frac{1}{2})\hat{y}} - e^{-(\alpha - \frac{1}{2})y^\ast}\right)\\
	&= \frac{2}{2\alpha - 1}\left(\left(\frac{2I_n - x_1}{e^{y/2} + e^{y_1/2}}\right)^{-(2\alpha - 1)} 
		- I_n^{-(2\alpha - 1)} e^{-(\alpha - \frac{1}{2})y_1}\right)\\
	&= \bigO{I_n^{-2\alpha} x_1 e^{-(\alpha - \frac{1}{2})y_1}}
\end{align*}
so that
\[
	\mathcal{I}_n^{(2)} = \bigO{I_n^{-(2\alpha - 1)} e^{(1-\alpha)y_1}} = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
\]
and hence for $p_1 \in B_n^{(3)}$
\[
	\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
	= \bigO{I_n^{-(2\alpha - 1)} e^{\alpha y}}.
\]

\subsubsection*{Integration over $p_1$}

We now proceed with the second part of the computation leading to \eqref{eq:clustering_error_T_main}. Here we will integrate $\mu_{\alpha, \nu}(\mathcal{T}_{\Pcal \Delta \Pcal_n})(p,p_1)$ over the region $B_n := B_n^{(1)} \cup B_n^{(2)} \cup B_n^{(3)}$, see Figure~\ref{fig:comparing_triangles_B_areas}. Let us first identify the boundaries of these areas.

The area $B_n^{(1)}$ is bounded from above by the line given by the equation
\[
	y_1 = y - 2\log\left(\frac{I_n}{I_n - x_1}\right).
\]
Solving this for $x_1$ yields $x_1 = I_n\left(1 - e^{(y_1-y)/2}\right)$ and hence the area $B_n^{(1)}$ is given by
\[
	B_n^{(1)} = \left\{(x_1, y_1) \, : \, 0 \le y_1 \le y, \quad 0 \le x_1 \le I_n\left(1 - e^{(y_1-y)/2}\right) \wedge e^{(y + y_1)/2} \right\}.
\]

In a similar way we have that $B_n^{(2)}$ is bounded from above by line
\[
	y_1 = y + 2\log\left(\frac{I_n}{I_n + x_1}\right),
\]
which yields $x_1 = I_n\left(e^{(y_1 - y)/2} - 1\right)$. The lower red boundary is the upper boundary of $B_n^{(2)}$ and hence we have
\[
	B_n^{(2)} = \left\{(x_1, y_1) \, : \, h_\ast(y) \le y_1 \le h^\ast(y), \,\, I_n\left(1 - e^{(y_1-y)/2}\right) \vee 
	I_n\left(e^{(y_1 - y)/2} - 1\right) \le x_1 \le e^{(y + y_1)/2} \right\}.
\]

We continue is the same way to obtain for $B_n^{(3)}$
\[
	B_n^{(3)} = \left\{(x_1, y_1) \, : \, y \le y_1 \le R_n, \,\,
	I_n\left(1 - e^{(y - y_1)/2}\right) \le x_1 \le I_n\left(e^{(y_1 - y)/2} - 1\right) \wedge e^{(y + y_1)/2} \wedge I_n \right\}.
\]

We these characterizations of the areas we now integrate $\mu_{\alpha, \nu}(\mathcal{T}_{\Pcal \Delta \Pcal_n})(p,p_1)$ over $B_n$, splitting the computations over the three different areas.

\paragraph{$\bm{p_1 \in B_n^{(1)}}:$}

We use that $I_n\left(1 - e^{(y_1-y)/2}\right) \wedge e^{(y + y_1)/2} \le I_n\left(1 - e^{(y_1-y)/2}\right)$ so that
\begin{align*}
	&\hspace{-30pt}\int_{B_n^{(1)}} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
		f_{\alpha,\nu}(x_1,y_1)	\dd x_1 \dd y_1 \\
	&\le  \int_0^y \int_0^{I_n(1-e^{(y_1-y)/2})} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
	&= \bigO{ I_n^{-2\alpha} \int_0^y \int_0^{e^{(y+y_1)/2}}  x_1 \dd x_1 \dd y_1 }\\
	&= \bigO{I_n^{-(2\alpha-1)} \int_0^y \left(1 - e^{(y_1-y)/2}\right)^2 \dd y_1} \\
	&= \bigO{I_n^{-(2\alpha - 1)} y} = \bigO{y n^{-(2\alpha - 1)}}.
\end{align*}

\paragraph{$\bm{p_1 \in B_n^{(2)}}:$}

We will show that
\begin{equation}\label{eq:mu_triangle_diff_2}
	\mu_{\alpha, \nu}(B_n^{(2)}) = \bigO{I_n^{-1} e^{(2-\alpha)y}},
\end{equation}
which together with \eqref{eq:mu_triangle_diff} yields
\begin{align*}
	\int_{B_n^{(2)}} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
		f_{\alpha,\nu}(x_1,y_1)	\dd x_1 \dd y_1
	&= \bigO{\mu_{\alpha, \nu}(B_n^{(2)}) I_n^{-(2\alpha - 1)} e^{\alpha y}}\\
	&= \bigO{I_n^{-2\alpha} e^{2y}}.
\end{align*}

The integration is split into two parts determined by $I_n\left(1 - e^{(y_1-y)/2}\right) \vee 
	I_n\left(e^{(y_1 - y)/2} - 1\right)$:
\begin{align*}
	\mu_{\alpha, \nu}(B_n^{(3)}) &= \int_{h_\ast(y)}^{y} \int_{I_n(1-e^{(y_1-y)/2})}^{e^{(y + y_1)/2}} 
		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
	&\hspace{10pt} + \int_y^{h^\ast(y)} \int_{I_n(e^{(y_1-y)/2}-1)}^{e^{(y + y_1)/2}} 
		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1.
\end{align*}

For the first integral we use that $e^{(y + y_1)/2} - I_n(1-e^{(y_1-y)/2}) \le e^{y_1/2}\left(e^{y/2} + e^{-y/2}\right)$ to obtain
\begin{align*}
	&\hspace{-30pt}\int_{h_\ast(y)}^{y} \int_{I_n(1-e^{(y_1-y)/2})}^{e^{(y + y_1)/2}} f_{\alpha,\nu}(x_1,y_1) 
		\dd x_1 \dd y_1\\
	&= \bigO{e^{y/2} \int_{h_\ast(y)}^{y} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1}\\
	&= \bigO{e^{y/2}\left(e^{-(\alpha - \frac{1}{2})y} - e^{-(\alpha - \frac{1}{2})y} 
		\left(\frac{I_n}{I_n + e^y}\right)^{-(2\alpha - 1)}\right)}\\
	&= \bigO{I_n^{-1} e^{(2-\alpha)y}}.
\end{align*}
For the second integral note that $e^{(y + y_1)/2} - I_n(e^{(y_1-y)/2}-1) \le e^{(y + y_1)/2}$ and hence
\begin{align*}
	&\hspace{-30pt}\int_y^{h^\ast(y)} \int_{I_n(e^{(y_1-y)/2}-1)}^{e^{(y + y_1)/2}} f_{\alpha,\nu}(x_1,y_1) 
		\dd x_1 \dd y_1\\
	&= \bigO{e^{y/2} \int_y^{h^\ast(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1}\\
	&= \bigO{e^{y/2} \left(e^{-(\alpha - \frac{1}{2})y} - e^{-(\alpha - \frac{1}{2})y}
		\left(\frac{I_n}{I_n - e^y}\right)^{-(2\alpha - 1)}\right)}\\
	&= \bigO{I_n^{-1} e^{(2-\alpha)y}},
\end{align*}
so that \eqref{eq:mu_triangle_diff_2} follows.

\paragraph{$\bm{p_1 \in B_n^{(3)}}:$}

For this area we show that 
\begin{equation}\label{eq:mu_triangle_diff_3}
	\mu_{\alpha, \nu}(B_n^{(3)}) = \bigO{e^{(1-\alpha)y}}
\end{equation} 
so that
\begin{align*}
	\int_{B_n^{(3)}} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
		f_{\alpha,\nu}(x_1,y_1)	\dd x_1 \dd y_1
	&= \bigO{\mu_{\alpha, \nu}(B_n^{(2)}) I_n^{-(2\alpha - 1)} e^{\alpha y}}\\
	&= \bigO{I_n^{-(2\alpha-1)} e^{y}}.
\end{align*}

Here the integral is split into three parts:
\begin{align*}
	\mu_{\alpha, \nu}(B_n^{(3)}) &= \int_y^{h^\ast(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n(e^{(y_1-y)/2}-1)}
		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
	&\hspace{10pt}+ \int_{h^\ast(y)}^{h(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{e^{(y+y_1)/2}}
		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
	&\hspace{10pt}+ \int_{h(y)}^{R_n} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n}
		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1.
\end{align*}

Let us first focus on the first integral. Since	$I_n(e^{(y_1-y)/2}-1) - I_n(1-e^{(y-y_1)/2}) \le I_n e^{(y_1-y)/2}$ we get,
using similar arguments as above
\begin{align*}
	\int_y^{h^\ast(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n(e^{(y_1-y)/2}-1)} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
	&= \bigO{I_n e^{-y/2} \int_y^{h^\ast(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1}\\
	&= \bigO{I_n e^{-\alpha y} \left(1 - \left(\frac{I_n}{I_n - e^y}\right)^{-(2\alpha - 1)}\right)}\\
	&= \bigO{e^{(1-\alpha)y}}.
\end{align*}

Proceeding to the second integral, we first note that $e^{(y+y_1)/2} - I_n(1-e^{(y-y_1)/2}) = \bigO{I_n e^{(y_1-y)/2}}$ so that similar calculations as before yield
\begin{align*}
	\int_{h^\ast(y)}^{h(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{e^{(y+y_1)/2}}	f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
	&= \bigO{I_n e^{-y/2} \int_{h^\ast(y)}^{h(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1}
		= \bigO{e^{(1-\alpha)y}}.
\end{align*}

\end{proof}

### 2018-10-17 clustering_infinite_model.tex
small update on motivation and figure 3

@@
 \end{lemma}
+
+\begin{figure}[!t]
+\centering
+\begin{tikzpicture}
+	%Define the coordinates 
+	%p = (\u,\v) and p^\prime = (\uu, \vv)
+	%Box \Rcal_n has width 2\r and height \t
+	\pgfmathsetmacro{\u}{0} %0
+	\pgfmathsetmacro{\v}{0.5} %1
+	\pgfmathsetmacro{\vv}{1.2} %0.8
+	\pgfmathsetmacro{\vvv}{2} %0.8
+	\pgfmathsetmacro{\uuu}{-3} %1.4	
+	\pgfmathsetmacro{\r}{6.5}
+	\pgfmathsetmacro{\t}{4}
+
+	\pgfmathsetmacro{\ubound}{exp((\vv+\vvv)/2)-exp((\v+\vvv)/2)}
+
+	\pgfmathsetmacro{\uu}{3*\ubound/4}
+
+	\pgfmathsetmacro{\leftintvandvvv}{-exp((\v + \vvv)/2)}
+	\pgfmathsetmacro{\rightintvandvvv}{exp((\v + \vvv)/2)}
+	\pgfmathsetmacro{\leftintvvandvvv}{\uu-exp((\vv + \vvv)/2)}
+	\pgfmathsetmacro{\rightintvvandvvv}{\uu+exp((\vv + \vvv)/2)}
+
+	%The box \Rcal_n
+	\draw[line width=1pt,dashed] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);
+
+	%Dram all three nodes
+    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] (p1) at (\u,\v) {};
+    \path (p1)+(-0.2,0.2) node {$p_0$};
+    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uu,\vv) {};
+    \path (p2)+(0.2,0.2) node {\color{blue}$p_1$};
+
+	%Boundaries p_0 = (\u,\v)
+
+	%Right boundary
+	\pgfmathsetmacro{\rightbounduv}{\u+exp((\v)/2)}
+	\draw[domain=\rightbounduv:\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-\v});
+    %Left boundary
+    \pgfmathsetmacro{\leftbounduv}{\u-exp((\v)/2)}
+    \draw[domain=\leftbounduv:-\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-\v});
+
+    %Boundaries p_1 = (\uu,\vv)
+
+    %Right boundary
+    \pgfmathsetmacro{\rightbounduuvv}{\uu+exp((\vv)/2)}
+    \draw[domain=\rightbounduuvv:\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-\uu)-\vv});
+%    %Shifted right boundary
+%    \pgfmathsetmacro{\shiftrightbounduuvv}{\uu+exp((\vv + \t)/2)-2*\r}
+%    \draw[domain=\shiftrightbounduuvv:-\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+(2*\r-\uu))-\vv});
+    %Left boundary 
+    \pgfmathsetmacro{\leftbounduuvv}{\uu-exp((\vv)/2)}
+    \draw[domain=\leftbounduuvv:-\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\uu-\x)-\vv});
+%    %Shifted left boundary
+%    \pgfmathsetmacro{\shiftleftbounduuvv}{\uu-exp((\vv + \t)/2)+2*\r}
+%    \draw[domain=\shiftleftbounduuvv:\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(2*\r + \uu-\x)-\vv});
+
+	\draw [red,dotted,line width=1pt] (\leftintvandvvv,\vvv) -- (\rightintvandvvv,\vvv);
+
+	\draw [red,dotted,line width=1pt] (\leftintvvandvvv,\vvv) -- (\rightintvvandvvv,\vvv);
+
+	\draw [red,line width=1pt] (\leftintvandvvv,\vvv) -- (\rightintvandvvv,\vvv);
+
+    \draw node[fill,black!60!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
+    \path (p2)+(0.25,-0.2) node {\color{black!60!green}$p_2$};
+
+	%Boundaries p_2 = (\uuu,\vvv)
+
+	%Right boundary
+	\pgfmathsetmacro{\rightbounduuuvvv}{\uuu+exp((\vvv)/2)}
+	\draw[domain=\rightbounduuuvvv:\r,smooth,variable=\x,black!60!green,line width=1pt] plot (\x, {2*ln(\x-\uuu)-\vvv});
+    %Left boundary
+    \pgfmathsetmacro{\leftbounduuuvvv}{\uuu-exp((\vvv)/2)}
+    \draw[domain=\leftbounduuuvvv:-\r,smooth,variable=\x,black!60!green,line width=1pt] plot (\x, {2*ln(\uuu-\x)-\vvv});
+
+	\draw node[fill,red, circle, inner sep=0pt, minimum size=3pt] at (\leftintvandvvv,\vvv) {};
+	\path (\leftintvandvvv,\vvv)+(-0.5,-0.5) node[red] {$-e^{\frac{y_0 + y_2}{2}}$};
+	\draw node[fill,red, circle, inner sep=0pt, minimum size=3pt] at (\rightintvandvvv,\vvv) {};
+	\path (\rightintvandvvv,\vvv)+(0,-0.5) node[red] {$e^{\frac{y_0 + y_2}{2}}$};
+
+	\draw node[fill,red, circle, inner sep=0pt, minimum size=3pt] at (\leftintvvandvvv,\vvv) {};
+	\path (\leftintvvandvvv,\vvv)+(0.75,0.5) node[red] {$x_1 - e^{\frac{y_0 + y_2}{2}}$};
+	\draw node[fill,red, circle, inner sep=0pt, minimum size=3pt] at (\rightintvvandvvv,\vvv) {};
+	\path (\rightintvvandvvv,\vvv)+(-0.5,0.5) node[red] {$x_1 + e^{\frac{y_0 + y_2}{2}}$};
+
+\end{tikzpicture}\\
+\vspace{0.5cm}
+\begin{tikzpicture}
+	%Define the coordinates 
+	%p = (\u,\v) and p^\prime = (\uu, \vv)
+	%Box \Rcal_n has width 2\r and height \t
+	\pgfmathsetmacro{\u}{0} %0
+	\pgfmathsetmacro{\v}{0.5} %1
+	\pgfmathsetmacro{\vv}{1.2} %0.8
+	\pgfmathsetmacro{\vvv}{1.8} %0.8
+	\pgfmathsetmacro{\uuu}{2.5} %1.4	
+	\pgfmathsetmacro{\r}{6.5}
+	\pgfmathsetmacro{\t}{4}
+
+	\pgfmathsetmacro{\ubound}{exp((\vv+\vvv)/2)-exp((\v+\vvv)/2)}
+
+	\pgfmathsetmacro{\uu}{5*\ubound/4}
+
+	\pgfmathsetmacro{\leftintvandvvv}{-exp((\v + \vvv)/2)}
+	\pgfmathsetmacro{\rightintvandvvv}{exp((\v + \vvv)/2)}
+	\pgfmathsetmacro{\leftintvvandvvv}{\uu-exp((\vv + \vvv)/2)}
+	\pgfmathsetmacro{\rightintvvandvvv}{\uu+exp((\vv + \vvv)/2)}
+
+	%The box \Rcal_n
+	\draw[line width=1pt,dashed] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);
+
+	%Dram all three nodes
+    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] (p1) at (\u,\v) {};
+    \path (p1)+(-0.2,0.2) node {$p_0$};
+    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uu,\vv) {};
+    \path (p2)+(0.2,0.2) node {\color{blue}$p_1$};
+
+	%Boundaries p_0 = (\u,\v)
+
+	%Right boundary
+	\pgfmathsetmacro{\rightbounduv}{\u+exp((\v)/2)}
+	\draw[domain=\rightbounduv:\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-\v});
+    %Left boundary
+    \pgfmathsetmacro{\leftbounduv}{\u-exp((\v)/2)}
+    \draw[domain=\leftbounduv:-\r,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-\v});
+
+    %Boundaries p_1 = (\uu,\vv)
+
+    %Right boundary
+    \pgfmathsetmacro{\rightbounduuvv}{\uu+exp((\vv)/2)}
+    \draw[domain=\rightbounduuvv:\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-\uu)-\vv});
+    %Left boundary 
+    \pgfmathsetmacro{\leftbounduuvv}{\uu-exp((\vv)/2)}
+    \draw[domain=\leftbounduuvv:-\r,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\uu-\x)-\vv});
+
+	\draw [red,dotted,line width=1pt] (\leftintvandvvv,\vvv) -- (\rightintvandvvv,\vvv);
+
+	\draw [red,dotted,line width=1pt] (\leftintvvandvvv,\vvv) -- (\rightintvvandvvv,\vvv);
+
+	\draw [red,line width=1pt] (\leftintvvandvvv,\vvv) -- (\rightintvandvvv,\vvv);
+
+    \draw node[fill,black!60!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
+    \path (p2)+(-0.2,0.2) node {\color{black!60!green}$p_2$};
+
+	%Boundaries p_2 = (\uuu,\vvv)
+
+	%Right boundary
+	\pgfmathsetmacro{\rightbounduuuvvv}{\uuu+exp((\vvv)/2)}
+	\draw[domain=\rightbounduuuvvv:\r,smooth,variable=\x,black!60!green,line width=1pt] plot (\x, {2*ln(\x-\uuu)-\vvv});
+    %Left boundary
+    \pgfmathsetmacro{\leftbounduuuvvv}{\uuu-exp((\vvv)/2)}
+    \draw[domain=\leftbounduuuvvv:-\r,smooth,variable=\x,black!60!green,line width=1pt] plot (\x, {2*ln(\uuu-\x)-\vvv});
+
+	\draw node[fill,red, circle, inner sep=0pt, minimum size=3pt] at (\leftintvandvvv,\vvv) {};
+	\path (\leftintvandvvv,\vvv)+(-0.5,-0.55) node[red] {$-e^{\frac{y_0 + y_2}{2}}$};
+	\draw node[fill,red, circle, inner sep=0pt, minimum size=3pt] at (\rightintvandvvv,\vvv) {};
+	\path (\rightintvandvvv,\vvv)+(0,-0.55) node[red] {$e^{\frac{y_0 + y_2}{2}}$};
+
+	\draw node[fill,red, circle, inner sep=0pt, minimum size=3pt] at (\leftintvvandvvv,\vvv) {};
+	\path (\leftintvvandvvv,\vvv)+(0.75,0.5) node[red] {$x_1 - e^{\frac{y_0 + y_2}{2}}$};
+	\draw node[fill,red, circle, inner sep=0pt, minimum size=3pt] at (\rightintvvandvvv,\vvv) {};
+	\path (\rightintvvandvvv,\vvv)+(-0.5,0.5) node[red] {$x_1 + e^{\frac{y_0 + y_2}{2}}$};
+
+\end{tikzpicture}
+\caption{Example configuration of two points $p$ and $p^\prime$ for which $\BallPon{p} \cap \BallPon{p^\prime}$ is not a subset of $\BallPo{p} \cap \BallPo{p^\prime}$.
+The red region indicates the area of points belonging to $\BallPon{p} \cap \BallPon{p^\prime}$ but not to $\BallPo{p} \cap \BallPo{p^\prime}$.}
+\end{figure}
 

### 2018-10-17 introduction.tex
small update on motivation and figure 3

@@
 
-\MS{Some ideas:
-\begin{enumerate}
-\item Hyperbolic random graphs as an alternative to Euclidean/standard random geometric graphs
-\end{enumerate}
-}
-
-\PvdH{Add intro on common features of complex networks and modeling of such networks.}
 \MS{I would not write a length introduction to complex networks here (because the paper is quite long already and we do not study networks in general in this paper).
@@
 }
-The main topological features shared among many complex networks are:
+\PvdH{I agree.}
+
+Hyperbolic random graphs were suggested as a suitable model for complex networks by Krioukov et al.~\cite{krioukov2010hyperbolic}, exhibiting the three main characteristics commonly found in complex networks:
 \begin{enumerate}[\upshape 1)]
-\item Broad degree distribution (power-law/scale-free)
-\item Strong clustering (community structure)
-\item Small path lengths (small world phenomenon)
+\item Broad degree distribution (power-law/scale-free),
+\item Strong clustering (community structure),
+\item Small path lengths (small world phenomenon).
 \end{enumerate}
-
-Hyperbolic random graphs were suggested as a suitable model for complex networks by Krioukov et al.~\cite{krioukov2010hyperbolic}.
-Indeed, in their seminal paper they show that these graphs have a power-law degree distribution and exhibit strong clustering.
-In addition it was found that hyperbolic random graphs have doubly logarithmic shortest path lengths~\cite{bringmann2016average} and allow for efficient routing algorithms~\cite{bringmann2017greedy}.
+Indeed, in their seminal paper they show that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
 Many other results regarding hyperbolic random graphs have since been established.
-These include size of the largest component~\cite{BodeFountoulakisMuller2015},~\cite{fountoulakis2018law}, [More?] and number of cliques and largest clique~\cite{blasius2018cliques}.
+One important feature of these graphs is that they allow for efficient routing algorithms~\cite{bringmann2017greedy}.
+Further results include the size of the largest component~\cite{BodeFountoulakisMuller2015},~\cite{fountoulakis2018law}, [More?] and number of cliques and largest clique~\cite{blasius2018cliques}.
 
@@
 The first rigorous mathematical analysis of the local clustering coefficient was done by Gugelmann et al.~\cite{gugelmann2012random}.
-They show~\cite[Theorem 2.1]{gugelmann2012random} that the local clustering coefficient is concentrated around its expectation which is shown to be $\bigT{1}$ as the number of vertices tends to infinity.
+They show~\cite[Theorem 2.1]{gugelmann2012random} that the local clustering coefficient\footnote{Note that in~\cite{gugelmann2012random} this is called the global clustering coefficient.
+However, since this term is more often associated in the literature with the density of triangles compared to the number of paths of length 2, we use the term local clustering coefficient as is done, for instance, in~\cite{candellero2016clustering}.} is concentrated around its expectation which is shown to be $\bigT{1}$ as the number of vertices tends to infinity.
 In particular this results implies that the local clustering coefficient is asymptotically bounded away from zero.
@@
 Finally, our analysis allows us to also prove a convergence result for the local clustering coefficient where the limit can again be explicitly expressed in terms of known special functions.
+
+\PvdH{I recall that J{\'u}lia told me that the results from~\cite{komjathy2018explosion} imply that the local clustering coefficient converges, although they do not mention it in the paper.
+Should we added a comment related to this?}
 
@@
 \includegraphics[scale=0.5]{figures/HyperRGG_N5000L5.eps}
-\caption{Example of a Hyperbolic Random Graph $G_{\H,n}(\alpha, \nu)$ with $\alpha = ??$, $\nu = ??$ and $n = 500$.}
+\caption{Example of a Hyperbolic Random Graph $G_{\H,n}(\alpha, \nu)$ with $\alpha = ??$, $\nu = ??$ and $n = 5000$.
+\PvdH{@Tobias: this figure (HyperRGG\_N5000L5.eps) is taken from the figures you send me. Could you fill in the value of $\alpha$ and $\nu$ you used for the simulation.}
+}
 \label{fig:H_graph_example}
@@
 Also, I thought it was defined as 3 times number of triangles divided by number of length 2 paths and I do not see yet whether this agrees with the definition below.}
-For instance, Let $G$ be a simple graph, with vertex set $V(G)$ and edge set $E(G)$ and denote by $T_G$ the total number of triangles in $G$. Then the global clustering coefficient is defined as
+\PvdH{You were right. I have updated the definition.}
+For instance, Let $G$ be a simple graph, with vertex set $V(G)$ and edge set $E(G)$, denote by $T_G$ and $\Lambda_G$, respectively, the total number of triangles and the total number of paths of length two in $G$.
+Then the \emph{global clustering coefficient} is defined as
 \[
-	c_G = \frac{\T_G}{\binom{E(G)}{2}}.
+	c_G = \frac{3 \T_G}{\Lambda_G}.
 \]
@@
 \end{equation}
-to denote the number of triangles in which node $v$ participates. Then the local clustering coefficient is given by
+to denote the number of triangles in which node $v$ participates. Then the \emph{local clustering coefficient} is given by
 \[
@@
 However, since the local clustering coefficient assigns just one value to the whole network, representing its triangular structure, it is unable to characterize local structural properties involving triangles.
-The local clustering function, on the other hand, measures the fraction of triangles to which nodes of a given degree belong, compared to the maximum number of triangles in which they could participate.
+The local clustering function, on the other hand, measures the fraction of triangles to which nodes of a given degree belong, compared to the maximum number of triangles in which they could participate~\cite{vazquez2002large,serrano2006clustering}.
 It therefore characterizes the triangular structure of nodes in the networks, based on their degree, and gives a more detailed look at the overall structure of the network.
-
-The local clustering function is formally defined as
+The formal definition of the \emph{local clustering function} is
 \begin{equation}\label{eq:def_local_clustering_general}
@@
 
-We note that other versions of the local clustering function have been considered, for instance where nodes with degree larger than $k$ are considered instead of nodes with degree exactly $k$.
+%We note that other versions of the local clustering function have been considered, for instance where nodes with degree larger than $k$ are considered instead of nodes with degree exactly $k$.
 \PvdH{Motivate our choice for this local clustering function.}

### 2018-10-18 clustering_infinite_model.tex
updated figure 3, adjusted computation lemma 3.2 and added text on scaling k_n

@@
 \end{tikzpicture}
-\caption{Example configuration of two points $p$ and $p^\prime$ for which $\BallPon{p} \cap \BallPon{p^\prime}$ is not a subset of $\BallPo{p} \cap \BallPo{p^\prime}$.
-The red region indicates the area of points belonging to $\BallPon{p} \cap \BallPon{p^\prime}$ but not to $\BallPo{p} \cap \BallPo{p^\prime}$.}
+\caption{Situation for the intersections of the connection intervals considered in Lemma~\ref{lem:ordered}, with $y_0 < y_1 <y_2$ fixed and for different cases of $0 \le x_1 \le e^{(y_0 + y_1)/2}$.
+The top figure shows the case where $0 \le x_1 \le e^{(y_1 + y_2)/2} - e^{(y_0 + y_2)/2}$, while the bottom one shows the case $x_1 > e^{(y_1 + y_2)/2} - e^{(y_0 + y_2)/2}$.
+The solid red line indicates the range for $x_2$ such that the points $p_0$, $p_1$ and $p_2$ form a triangle.
+The boundaries of there balls are show in, respectively, black, blue and green.}
+\label{fig:triangle_prob_lemma}
 \end{figure}
@@
 \end{tikzpicture}
-\caption{Situation for the intersections of the connection intervals considered in Lemma~\ref{lem:ordered}, with $y_0 < y_1 <y_2$ and $0 \le x_1 \le e^{(y_0 + y_1)/2}$.
-The regime for $x_2$ in which case a triangle is formed is colored in red on both intervals.
-\PvdH{Maybe show the full connection balls.}}
-\label{fig:triangle_prob_lemma}
 \end{figure}

### 2018-10-18 concentration_argument.tex
updated figure 3, adjusted computation lemma 3.2 and added text on scaling k_n

@@
 \[
-	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 3}{2} e^{-(\alpha - \frac{1}{2})(R_n - y)} 
-		+ \frac{2\alpha - 1}{2}e^{-(\alpha - \frac{1}{2})R_n - y/2},
+	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 1 - 4\pi}{4\pi} e^{-(\alpha - \frac{1}{2})(R_n - y)} 
+		+ \left(\alpha - \frac{1}{2}\right)\pi e^{-(\alpha - \frac{1}{2})R_n - y/2},
 \]
@@
 Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = 4\nu \alpha/(2\alpha - 1)\pi$.
-\PvdH{Check computations below for new $\xi_{\alpha,\nu} = 4\nu \alpha/(2\alpha - 1)\pi$}
 
@@
 		= \nu \alpha e^{R_n/2}\left(e^{-\alpha(R_n - y)} - e^{-\alpha R_n}\right)\\
-	&= \Mu{\BallPo{0,y}} \frac{2\alpha - 1}{2}\left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
+	&= \Mu{\BallPo{0,y}} \frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
 		- e^{-(\alpha - \frac{1}{2})R_n - y/2}\right) \numberthis \label{eq:mu_hyperbolic_ball_part_1}
@@
 	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} 
-	&\le \nu \alpha \int_{0}^{R_n - y} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R_n}\right)
+	&\le \frac{2\nu \alpha}{\pi} \int_{0}^{R_n - y} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R_n}\right)
 		e^{-\alpha y^\prime} \dd y^\prime\\
 	&= \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right) \\
-	&\hspace{10pt}+ \nu \alpha K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
+	&\hspace{10pt}+ \frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
 \end{align*}
@@
 \begin{align*}
-	&\hspace{-30pt}\nu \alpha K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime\\
+	&\hspace{-30pt}\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}
+		\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime\\
 	&= \Mu{\BallPo{0,y}}\begin{cases}
@@
 \[
-	\nu \alpha K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime.
+	\frac{2 \nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime.
 \]

### 2018-10-18 introduction.tex
updated figure 3, adjusted computation lemma 3.2 and added text on scaling k_n

@@
 \paragraph{Maximum scaling for $k_n$ is $n^{\frac{1}{2\alpha +1}}$}
+All our results for clustering in the hyperbolic random graph are valid for any sequence $k_n$ such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
+Although one would like to have results for any sequence $k_n \le n$, it turns out that $n^{1/(2\alpha + 1)}$ is the optimal scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
+To see why this is the case note that by definition of the local clustering function~\eqref{eq:def_local_clustering_general} we have that $c_{\H,n}(k_n) = 0$ if $N_{\H,n}(k_n) = 0$.
+Hence, it follows by Markov's inequality that for any positive function $f$
+\begin{align*}
+	\Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|} 
+	&\ge \Prob{N_{\H,n}(k_n) = 0} \ge 1 - \Exp{N_{\H,n}(k_n)}.
+\end{align*}
+We shall later establish (see Lemma [??] \PvdH{Find the reference for this Lemma}) that $\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}$.
+Therefore if $k_n$ is such that $k_n = \omega\left(n^{\frac{1}{2\alpha + 1}}\right)$ we have
+\[
+	\lim_{n \to \infty} n k_n^{-(2\alpha + 1)} 
+	= \lim_{n \to \infty} \left(n^{-\frac{1}{2\alpha + 1}} k_n\right)^{-(2\alpha + 1)} = 0
+\]
+and hence
+\[
+	\lim_{n \to \infty} \Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|} 
+	\ge \lim_{n \to \infty} 1 - \Exp{N_{\H,n}(k_n)} = \lim_{n \to \infty} 1 - \bigT{n k_n^{-(2\alpha + 1)}} = 1 \ne 0,
+\]
+for any positive function $f$.
+This implies that we cannot expect a result like that of Theorem~\ref{thm:clustering_coefficient_hyperbolic} to hold as soon as $k_n = \omega\left(n^{\frac{1}{2\alpha + 1}}\right)$.
+
 %Maybe, it would make sense to incorporate this statement into theorem \ref{thm:asymptotic_local_clustering_hyperbolic}, i.e.

### 2018-10-18 clustering_infinite_model.tex
cleaned up proof of Theorem 1.5 and realigned formulas in section 4.5

@@
     &= (\xi_{\alpha,\nu})^{2\alpha}\frac{\Gamma(k-2\alpha)}{\Gamma(k+1)}
-    	\left(1 - \frac{\gamma(k-2\alpha, \xi_{\alpha,\nu})}{\Gamma(k - 2\alpha)}\right),
+    	\left(1 - \frac{\Gamma^{-}(k-2\alpha, \xi_{\alpha,\nu})}{\Gamma(k - 2\alpha)}\right),
         \numberthis \label{eq:degree_distribution_P}
 \end{align*}
-where $\Gamma$ denotes the Gamma-function and $\gamma$ the incomplete Gamma-function.
-
-Thus we deduce that, as $k \to \infty$,
+where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{-1}$ the lower-incomplete Gamma-function.
+
+Since $\Gamma^{-}(k-2\alpha, \xi_{\alpha,\nu})\Gamma(k - 2\alpha) \to 0$ \PvdH{Find reference.} and $\Gamma(k-t)/\Gamma(k+1) \sim k^{-(t+1)}$ as $k \to \infty$ we deduce that
 \begin{equation}\label{eq:degree_distribution_P_asymptotics}
@@
 
-By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$,
+By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
 \begin{equation}\label{eq:general_integral_rho_y_k}
 	\int_0^\infty e^{\beta y} \rho_y(k) e^{-\alpha y} \, dy
-    = \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} \frac{\Gamma(k - 2(\beta + \alpha))}{\Gamma(k+1)}
-    	\left(1 - \frac{\gamma(k - 2(\beta + \alpha), \xi_{\alpha,\nu})}{\Gamma(k - 2(\beta + \alpha))}\right).
+    \sim \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
 \end{equation}
@@
 \begin{proposition}[Asymptotic behavior of $\Delta_\Pcal(y)$]\label{prop:asymptotics_Delta_y_P}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}.
-Then there are three, eventually decreasing, functions $\varepsilon_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
-\[
-	\lim_{y \to \infty} \varepsilon_i(y) = 0, 
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}. Then there are three, eventually decreasing, functions $\varphi_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
+\[
+	\lim_{y \to \infty} \varphi_i(y) = 0, 
 \]
@@
 \[
-	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varepsilon_1(y)),
+	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varphi_1(y)),
 \]
@@
 \[
-	\Delta_\Pcal(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varepsilon_2(y)),
+	\Delta_\Pcal(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varphi_2(y)),
 \]
@@
 \[
-	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varepsilon_3(y)).
+	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varphi_3(y)).
 \]
@@
 
-\PvdH{Include concentration argument in this proof.}
 We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$.
 The proofs for the other two cases are similar.
-Let $\varepsilon_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
-\[
-	\xi_1(k_n) = \int_0^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy
+Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
+\[
+	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y
 \]
@@
 \[
-	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho_{y}(k_n) e^{-\alpha y} \, dy
-	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy + \xi_1(k_n).
-\]
-
-Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields
-\[
-	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy 
-    = 2\xi^{6\alpha - 2} \frac{\Gamma(k_n-(6\alpha-2)}{\Gamma(k_n+1)}
-	\left(1 - \frac{\gamma(k_n - (6\alpha - 2), \xi)}{\Gamma(k_n - (6\alpha-2))}\right).
-\]
-Since 
-\[
-	\lim_{n \to \infty} \frac{\gamma(k_n - 2\alpha, \xi)}{\Gamma(k_n - 2\alpha)} = 0,
-\]
-and $\Gamma(k_n - t)/\Gamma(k_n + 1) \sim k_n^{-(t+1)}$ as $n \to \infty$,
-it follows that, as $n \to \infty$,
-\begin{align*}
-	c_\infty(k_n) \sim C_\alpha \xi^{4\alpha - 2} \frac{k_n^{-(6\alpha - 1)}}{k_n^{-(2\alpha - 1)}}
-	+ \frac{\xi^{-2\alpha}\eta_1(k_n)}{2 k_n^{-(2\alpha - 1)}}
-	\sim C_\alpha \xi^{4\alpha - 2} k_n^{-4\alpha + 2} 
-    + \frac{\xi^{-2\alpha}\eta_1(k_n)}{2 k_n^{-(2\alpha - 1)}}.
+	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) e^{-\alpha y} \dd y
+	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y + \epsilon_1(k).
+\]
+
+Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields,
+\begin{equation}\label{eq:asymptotics_clustering_integral}
+	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y 
+	\sim \xi_{\alpha,\nu}^{6\alpha - 2} k^{-(6\alpha - 1)},
+\end{equation}
+as $k \to \infty$. Therefore, by applying the asymptotic scaling for the denominator~\eqref{eq:degree_distribution_P_asymptotics} we get
+\begin{align*}
+	c_\infty(k) &= \frac{\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) e^{-\alpha y} \dd y}
+		{\int_0^\infty \rho_{y}(k) e^{-\alpha y} \dd y} \\
+	&\sim C_\alpha \xi_{\alpha,\nu}^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
+	+ \frac{\epsilon_1(k)}{\xi_{\alpha,\nu}^{2\alpha} k^{-(2\alpha - 1)}}\\
+	&= C_\alpha \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2} 
+    + \xi_{\alpha,\nu}^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
 \end{align*}
@@
 \[
-	\lim_{n \to \infty} k_n^{6\alpha - 1}\xi_1(k_n) = 0.
-\]
-For this let $0 < \varepsilon < 1$, define $a_n = 2\log((1-\varepsilon)k_n)$ and split the integral into two pieces
-\begin{align*}
-	\xi_1(k_n) &= \int_0^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
-	&= \int_0^{a_n} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
-	&\hspace{10pt}+ \int_{a_n}^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
-    	\rho_{y}(k_n) e^{-\alpha y} \, dy.
-\end{align*} 
-For the first integral we use that
-\[
-	k_n^{6\alpha - 1}\rho_{a_n}(k_n) = O\left(\frac{k_n^{6\alpha - 1 + (1-\varepsilon)k_n}}{k_n!} e^{-(1-\varepsilon)k_n}\right) = o(1),
-\]
-so that
-\begin{align*}
-	&\hspace{-30pt}\lim_{n \to \infty} k_n^{6\alpha - 1} \int_0^{a_n} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
-    	\rho_{y}(k_n) e^{-\alpha y} \, dy\\
-	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a_n} \varepsilon_1(y)\right) k_n^{6\alpha - 1} 
-    	\rho_{a_n}(k_n) \int_0^\infty e^{-\alpha y} \, dy = 0.
+	\lim_{k \to \infty} k^{6\alpha - 3}\epsilon_1(k) = 0.
+\]
+For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ and split the integral into two pieces
+\begin{align*}
+	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
+	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
+	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
+    	\rho(y,k) e^{-\alpha y} \dd y.
+\end{align*} 
+For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ and
+\[
+	k^{6\alpha - 3}\rho(a(k),k) = O\left(\frac{k^{6\alpha - 3 + (1-\varphi)k}}{k!} e^{-(1-\varphi)k}\right) = o(1),
+\]
+to obtain
+\begin{align*}
+	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
+    	\rho(y,k) e^{-\alpha y} \dd y\\
+	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
+    	\rho(a(k), k) \int_0^\infty e^{-\alpha y} \dd y = 0.
 \end{align*}
@@
 \[
-	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy \sim k_n^{-(6\alpha - 1)}.
-\] 
-Therefore, using that $\varepsilon_1(y)$ is eventually decreasing and $\lim_{n \to \infty} \varepsilon_1(a_n) = 0$, we obtain
-\begin{align*}
-	&\hspace{-30pt}\lim_{n \to \infty} k_n^{6\alpha - 1} \int_{a_n}^{\infty} \varepsilon_1(y) 
-    	e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
-	&\le \lim_{n \to \infty} \varepsilon_1(a_n) k_n^{6\alpha - 1} \int_0^\infty 
-    	e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy = 0,
+	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
+\] 
+Therefore, using that $\varphi_1(y)$ is eventually decreasing and $\lim_{k \to \infty} \varphi_1(a(k)) = 0$, we obtain
+\begin{align*}
+	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
+    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
+	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
+    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y = 0,
 \end{align*}
@@
 
-\begin{figure}
-\centering
-\begin{tikzpicture}[scale=0.9]
-
-	\draw node at (0,3.5) {\begin{minipage}{5cm}
-		\begin{center}
-		\begin{align*}
-			&\text{I) } e^{\frac{y_0 + y_1}{2}} < e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}} \text{ or}\\
-			&\text{II) } 0 \le x_1 \le e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}}
-		\end{align*}
-		\end{center}
-	\end{minipage}};
-
-	\draw[thick,red] (-2,1) -- (2,1);
-	\draw[thick] (-2,0.8) -- (-2,1.2);
-	\draw[thick] (2,0.8) -- (2,1.2);
-	\draw node at (-2,1.5) {$-e^{\frac{y_0 + y_2}{2}}$};
-	\draw node at (2,1.5) {$e^{\frac{y_0 + y_2}{2}}$};
-
-	\draw[thick] (-3,0) -- (3,0);
-	\draw[thick,red] (-2,0) -- (2,0);
-	\draw[thick,red] (-2,-0.2) -- (-2,0.2);
-	\draw[thick,red] (2,-0.2) -- (2,0.2);
-	\draw[thick] (-3,-0.2) -- (-3,0.2);
-	\draw[thick] (3,-0.2) -- (3,0.2);
-	\draw node at (-3,-0.5) {$x_1 - e^{\frac{y_1 + y_2}{2}}$};
-	\draw node at (3,-0.5) {$x_1 + e^{\frac{y_1 + y_2}{2}}$};
-
-\end{tikzpicture}
-\begin{tikzpicture}[scale=0.9]
-
-	\draw node at (0,3.5) {\begin{minipage}{5cm}
-		\begin{center}
-			$x_1 > e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}}$
-		\end{center}
-	\end{minipage}};
-
-	\draw[thick] (-2,1) -- (2,1);
-	\draw[thick,red] (-1.5,1) -- (2,1);
-	\draw[thick] (-2,0.8) -- (-2,1.2);
-	\draw[thick] (2,0.8) -- (2,1.2);
-	\draw[thick,red] (-1.5,0.8) -- (-1.5,1.2);
-	\draw node at (-2,1.5) {$-e^{\frac{y_0 + y_2}{2}}$};
-	\draw node at (2,1.5) {$e^{\frac{y_0 + y_2}{2}}$};
-
-	\draw[thick] (-1.5,0) -- (3,0);
-	\draw[thick,red] (-1.5,0) -- (2,0);
-	\draw[thick,red] (2,-0.2) -- (2,0.2);
-	\draw[thick] (-1.5,-0.2) -- (-1.5,0.2);
-	\draw[thick] (3,-0.2) -- (3,0.2);
-	\draw node at (-1.5,-0.5) {$x_1 - e^{\frac{y_1 + y_2}{2}}$};
-	\draw node at (3,-0.5) {$x_1 + e^{\frac{y_1 + y_2}{2}}$};
-
-\end{tikzpicture}
-\end{figure}
-
 \begin{proof}
@@
 		= z_0^a \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} \left[ \frac{ z_2^{c+2\alpha-1} }{ c+2\alpha-1 } \right]_{z_0-z_1}^{z_1} \dd z_1\\
-	&= \frac{z_0^a}{c+2\alpha-1} \cdot \left( \int_{z_0/2}^{z_0} z_1^{b+c+4\alpha-3} {\dd}z_1
+	&= \frac{z_0^a}{c+2\alpha-1} \cdot \left( \int_{z_0/2}^{z_0} z_1^{b+c+4\alpha-3} \dd z_1
 	   - \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} (z_0-z_1)^{c+2\alpha-1} {\dd}z_1 \right) \\
-	&= \frac{z_0^{a+b+c+4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
-		- \frac{z_0^{a+b+c+4\alpha-3}}{c+2\alpha-1} \int_{z_0/2}^{z_0}  \left(z_1/z_0\right)^{b+2\alpha-2} 
-	    \left(1-(z_1/z_0)\right)^{c+2\alpha-1} {\dd}z_1\\
+	&= \frac{z_0^{a+b+c+4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} \\
+	&\hspace{10pt}- \frac{z_0^{a+b+c+4\alpha-3}}{c+2\alpha-1} \int_{z_0/2}^{z_0}  \left(z_1/z_0\right)^{b+2\alpha-2} 
+	    \left(1-(z_1/z_0)\right)^{c+2\alpha-1} \dd z_1\\
 	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
 		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1}
-	   \int_{1/2}^1  u^{b+2\alpha-2}(1-u)^{c+2\alpha-1} {\dd} u \\
+	   \int_{1/2}^1  u^{b+2\alpha-2}(1-u)^{c+2\alpha-1} \dd u \\
 	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
@@
 \begin{equation}\label{eq:Delta_P_computation_I22_J}
-	I_{2,2}(y_0) = \frac{1}{4}\left(J_{0,-1,1}^\prime(z_0) + J_{2,-1,-1}^\prime(z_0)
-	+ J_{0,1,-1}^\prime(z_0) + 2J_{1,-1,0}^\prime(z_0) - 2J_{0,0,0}^\prime(z_0) - 2J_{1,0,-1}^\prime(z_0)\right)
+\begin{aligned}
+		I_{2,2}(y_0) &= \frac{1}{4}\left(J_{0,-1,1}^\prime(z_0) + J_{2,-1,-1}^\prime(z_0)
+		+ J_{0,1,-1}^\prime(z_0)\right) \\
+		&\hspace{10pt}+ \frac{1}{2}\left( J_{1,-1,0}^\prime(z_0) - J_{0,0,0}^\prime(z_0) - J_{1,0,-1}^\prime(z_0)\right).
+\end{aligned}
 \end{equation}
@@
 
-\PvdH{Realign formulas to fit them on page.}
-
 We want to compute the limit $\lim_{\alpha \rightarrow 1} \Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0))$.
@@
 \begin{align*}
-z_0^{-2 + 4 \alpha} \frac{(\alpha - 
-	1/2 ) B^-(1/2; 1 + 2 \alpha, 
-	-2 + 2 \alpha)}{2\alpha} = \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
- \left.+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right)  (\alpha-1)+O( (\alpha-1)^2 )
+	&\hspace{-30pt}z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha} \\
+	&= \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
+ 	&\hspace{20pt}\left.+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right)  (\alpha-1)+O( (\alpha-1)^2 )
 \end{align*}
@@
 \begin{align*}
-\frac{d}{d \alpha}\left( z_0^{-2 + 4 \alpha} \frac{(\alpha - 
-	1/2 )}{2\alpha} B^-(1/2; 1 + 2 \alpha, 
-	-2 + 2 \alpha)\right) = \ln(z_0) 4 z_0^{-2+4\alpha} \left(\frac{1}{2}-\frac{1}{4\alpha}\right)B^-(1/2;1+2\alpha,-2+2\alpha)\\
-+z_0^{-2+4\alpha}\frac{1}{4\alpha^2}B^-(1/2;1+2\alpha,-2+2\alpha)+z_0^{-2+4\alpha}\left(\frac{1}{2}-\frac{1}{4\alpha}\right)\int_0^{\frac{1}{2}} \frac{d}{d\alpha}(t^{2\alpha}(1-t)^{2\alpha-3})dt
+	&\hspace{-20pt}\frac{d}{d \alpha}\left( z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 )}{2\alpha} 
+		B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\right) \\
+	&= \ln(z_0) 4 z_0^{-2+4\alpha} \left(\frac{1}{2}-\frac{1}{4\alpha}\right)B^-(1/2;1+2\alpha,-2+2\alpha)\\
+	&+z_0^{-2+4\alpha}\frac{1}{4\alpha^2}B^-(1/2;1+2\alpha,-2+2\alpha)+z_0^{-2+4\alpha}\left(\frac{1}{2}-\frac{1}{4\alpha}\right)\int_0^{\frac{1}{2}} \frac{d}{d\alpha}(t^{2\alpha}(1-t)^{2\alpha-3})dt
 \end{align*}
@@
 &-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) +\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
-&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 -\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 +\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 =0
+&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 -\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 \\ &\hspace{10pt}+\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 =0
 \end{align*}
@@
 \begin{align*}
-&\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) +\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
-&\qquad+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right) \\
-&\qquad- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) \\
-&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} - \frac{z_0^2}{32} \\
-&\qquad-\frac{5}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2-\frac{5z_0^2}{32}+\frac{z_0^2 \ln2}{4}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \\
-&\qquad+\frac{(1-z_0)^2}{4}\ln(1-z_0) -\frac{1}{8}+\frac{z_0}{4}-\frac{z_0^2}{8}\\
-&\qquad+ z_0^2\ln(z_0)-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
-&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} +\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
-&\qquad+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \\
-&\qquad-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
-&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} +\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
-&\qquad+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)) \\
-&\qquad-z_0 \ln z_0-z_0^2(\ln z_0)^2+z_0(1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 \Li_2(z_0))\\
-&\qquad-z_0^2   -\frac{1}{2}  z_0^2\Li_2(1) \\
-&=\frac{9}{4}z_0-\frac{25}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} +\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
-&\qquad-\frac{1}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)-\Li_2(1)+\Li_2(z_0)) \\
-&\qquad-\frac{1}{2}z_0^2(\ln z_0)^2 - \frac{1}{2} z_0(1-z_0) \ln(1-z_0)
-\end{align*}
-where we used that the first integral is
-\begin{align*}
-[1/2 (-2 + 5 t + t^2 - \ln(1 - t)^2 - 2 t \ln t - t^2 \ln t - 
-   \ln(1 - t) (-3 + 2 t + t^2 + 2\ln t) - 2 \Li_2(t))]_0^{\frac{1}{2}} \\
-= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)
-\end{align*}
-and the second one is
-\begin{align*}
-[\frac{1}{-1+ t} (1 + \frac{1}{2}(1 + t) \ln(1 - t) + \frac{1}{2}(1 - t) \ln(
-1 -t)^2 - \frac{1}{2} t \ln(t) +\frac{1}{2} (1 - t) \Li_2(1 -t))]_0^{1-z_0} \\
-=-\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1)
-\end{align*}
+	&\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) 
+		+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
+	&\hspace{10pt}+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+1/2\int_0^{\frac{1}{2}} 
+		\ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right) \\
+	&\hspace{10pt}- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) \\
+	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2
+		+\frac{z_0^2}{8}\ln\frac{z_0}{2} - \frac{z_0^2}{32} \\
+	&\hspace{10pt}-\frac{5}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2-\frac{5z_0^2}{32} +\frac{z_0^2 \ln2}{4}\\
+	&\hspace{10pt}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}\dd t \\
+	&\hspace{10pt}+\frac{(1-z_0)^2}{4}\ln(1-z_0) -\frac{1}{8}+\frac{z_0}{4}-\frac{z_0^2}{8}\\
+	&\hspace{10pt}+ z_0^2\ln(z_0)-z_0 \ln z_0-z_0^2(\ln z_0)^2
+		-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
+	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
+		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
+	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
+		+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \\
+	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
+	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
+		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
+	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
+		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)) \\
+	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2+z_0(1 + \frac{1}{2}(2-z_0) \ln(z_0) 
+		+ \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) \\
+	&\hspace{10pt}+\frac{1}{2}z_0 \Li_2(z_0)) - z_0^2   -\frac{1}{2}  z_0^2\Li_2(1) \\
+	&=\frac{9}{4}z_0-\frac{25}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
+		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
+	&\hspace{10pt}-\frac{1}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
+		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 \\
+	&\hspace{10pt}- \Li_2(1/2)-\Li_2(1)+\Li_2(z_0)) -\frac{1}{2}z_0^2(\ln z_0)^2 - \frac{1}{2} z_0(1-z_0) \ln(1-z_0)
+\end{align*}
+where we used that
+\begin{align*}
+	z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1} \dd t
+	&= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2),
+\end{align*}
+and
+\begin{align*}
+	&z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt\\
+	&= -\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1).
+\end{align*}
+% the first integral is
+%\begin{align*}
+%[1/2 (-2 + 5 t + t^2 - \ln(1 - t)^2 - 2 t \ln t - t^2 \ln t - 
+%   \ln(1 - t) (-3 + 2 t + t^2 + 2\ln t) - 2 \Li_2(t))]_0^{\frac{1}{2}} \\
+%= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)
+%\end{align*}
+%and the second one is
+%\begin{align*}
+%[\frac{1}{-1+ t} (1 + \frac{1}{2}(1 + t) \ln(1 - t) + \frac{1}{2}(1 - t) \ln(
+%1 -t)^2 - \frac{1}{2} t \ln(t) +\frac{1}{2} (1 - t) \Li_2(1 -t))]_0^{1-z_0} \\
+%=-\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1)
+%\end{align*}
 By expanding the squares and collecting terms, the last expression can be simplified to

### 2018-10-19 introduction.tex
Commit by Pim

@@
 
-\MS{I would not write a length introduction to complex networks here (because the paper is quite long already and we do not study networks in general in this paper).
+%\MS{I would not write a length introduction to complex networks here (because the paper is quite long already and we do not study networks in general in this paper).
 So, I would remove the first paragraph/list (or incorporate it as a single sentence in the ensuing paragraph).
 }
-\PvdH{I agree.}
+%\PvdH{I agree.}
 
@@
 \end{enumerate}
-Indeed, in their seminal paper they show that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
-Many other results regarding hyperbolic random graphs have since been established.
-One important feature of these graphs is that they allow for efficient routing algorithms~\cite{bringmann2017greedy}.
-Further results include the size of the largest component~\cite{BodeFountoulakisMuller2015},~\cite{fountoulakis2018law}, [More?] and number of cliques and largest clique~\cite{blasius2018cliques}.
+Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
+Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{BodeFountoulakisMuller2015},~\cite{fountoulakis2018law}, [More?] and the number of cliques and the largest clique~\cite{blasius2018cliques}.
 
@@
 
+\MS{Yes, I think this would probably be good.
+Either after the sentence `the convergence of this coefficient was not proven' add something like, as you say, the results form ..
+imply convergence, although not specifically mentioned there.
+Or drop that sentence about that the convergence was not shown and also rephrase the sentence in 1, to just what is the limit.
+It should just be clear to the reader that we are not claiming the credit for the convergence itself, but mostly for finding the exact limit (in an analytic expression) and with a very strong sense of convergence.
+So, let's better emphasize those last two points and hope that they are good enough.}
+
 \subsection{Outline of the paper}
@@
 Section \ref{sec:proof_outline} contains a detailed high level outline of the proofs of our main results, split up into different propositions.
-The proofs of these propositions can be found in the last four sections while Section~\ref{sec:concentration_argument} contains a crucial technical result regarding that will be used through the other sections.
+The proofs of these propositions can be found in the last four sections.
+Section~\ref{sec:concentration_argument} contains a crucial technical result that will be used in the other sections.
 
@@
 \centering
-\includegraphics[scale=0.5]{figures/HyperRGG_N5000L5.eps}
-\caption{Example of a Hyperbolic Random Graph $G_{\H,n}(\alpha, \nu)$ with $\alpha = ??$, $\nu = ??$ and $n = 5000$.
-\PvdH{@Tobias: this figure (HyperRGG\_N5000L5.eps) is taken from the figures you send me. Could you fill in the value of $\alpha$ and $\nu$ you used for the simulation.}
+\includegraphics[scale=0.3]{figures/KPKVB.png}
+\caption{Example of a Hyperbolic Random Graph $G_{\H,n}(\alpha, \nu)$ with $\alpha = 0.9$, $\nu = 0.2$ and $n = 5000$.
+%\PvdH{@Tobias: this figure (HyperRGG\_N5000L5.eps) is taken from the figures you send me. Could you fill in the value of $\alpha$ and $\nu$ you used for the simulation.}
 }
@@
 Clustering measures for networks consider the fraction of triangles (triples of connected vertices) in the network. 
-\MS{Do we need the definition of the global clustering coefficient?
-Also, I thought it was defined as 3 times number of triangles divided by number of length 2 paths and I do not see yet whether this agrees with the definition below.}
-\PvdH{You were right. I have updated the definition.}
-For instance, Let $G$ be a simple graph, with vertex set $V(G)$ and edge set $E(G)$, denote by $T_G$ and $\Lambda_G$, respectively, the total number of triangles and the total number of paths of length two in $G$.
-Then the \emph{global clustering coefficient} is defined as
+For instance, for a simple graph $G$, with vertex set $V(G)$ and edge set $E(G)$, denote by $T_G$ and $\Lambda_G$, respectively, the total number of triangles and the total number of paths of length two in $G$.
+Then its \emph{global clustering coefficient} is defined as
 \[
@@
 \]
-This coefficient measures the fraction of triangles in the network compared to the total possible number of triangles.
-A different global measure for clustering, \emph{local clustering coefficient} computes the average triangle density per node.
-To define this function, let $D_G(v)$ denote the degree of node $v$ and $N_G(k)$ the number of nodes with degree $k$ in the graph $G$.
+%This coefficient measures the fraction of triangles in the network compared to the total possible number of triangles. 
+A different concept for clustering is defined for each vertex and by taking averages also for the entire graph as well as for all vertices with a specified degree: the \emph{local clustering coefficient} of a vertex $v \in V(G)$ is a real number between zero and one for the extent to which the neighborhood of $v$ resembles a clique.
+If the vertex $v$ has $k\geq 2$ neighbors, there are ${k \choose 2}$ possible edges between them and its local clustering coefficient is the quotient of the number of these pairs that constitute an existing edge in the graph divided by ${k \choose 2}$.
+If the vertex $v$ has no or only one neighbor, its clustering coefficient is set to zero.
+
+To define the local clustering function, let $D_G(v)$ denote the degree of node $v$ and $N_G(k)$ the number of nodes with degree $k$ in the graph $G$.
 In addition let $\T_G(v,v_1,v_2) = \ind{(v,v_1) \in E} \ind{(v, v_2) \in E} \ind{(v_1, v_2) \in E}$ be the indicator that $v, v_1$ and $v_2$ form a triangle and write

### 2018-10-19 clustering_infinite_model.tex
started on Section 4.6. Added task for Markus.

@@
 
-In addition, since $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}}$, with $\xi_{\alpha,\nu} = \frac{4\alpha\BL{\nu}}{(2\alpha - 1)\pi}$, and
+In addition, since $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}}$, with $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{(2\alpha - 1)\pi}$, and
 \[
@@
 \begin{equation}
-	\rho_{p}(k) = \Prob{D_\Pcal(p) = k} = \Prob{\Po(\mu_{\alpha,\nu}(\BallPo{p})) = k},
-\end{equation}
-where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Recall from equation \eqref{eq:mu_B_y_P} that
-\[
-	\mu_{\alpha,\nu}(B(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}},
-\]
-only depends on the $y$-coordinate of $p$. Therefore, we will often write $\rho_y(k)$ instead of $\rho_{p}(k)$.
+	\rho(p,k) = \Prob{D_\Pcal(p) = k} = \Prob{\Po(\mu_{\alpha,\nu}(\BallPo{p})) = k},
+\end{equation}
+where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Recall from equation \eqref{eq:mu_ball_y_P} that
+\[
+	\mu_{\alpha,\nu}(\BallPo{p}) = \xi_{\alpha,\nu} e^{\frac{y}{2}},
+\]
+only depends on the $y$-coordinate of $p$. Therefore, we will often write $\rho(y,k)$ instead of $\rho(p,k)$.
 
@@
     &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_{\xi_{\alpha,\nu}}^{\infty} 
-    	z^{k-2\alpha} e^{-z} \, dz\\
-    &= (\xi_{\alpha,\nu})^{2\alpha}\frac{\Gamma(k-2\alpha)}{\Gamma(k+1)}
-    	\left(1 - \frac{\Gamma^{-}(k-2\alpha, \xi_{\alpha,\nu})}{\Gamma(k - 2\alpha)}\right),
-        \numberthis \label{eq:degree_distribution_P}
-\end{align*}
-where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{-1}$ the lower-incomplete Gamma-function.
-
-Since $\Gamma^{-}(k-2\alpha, \xi_{\alpha,\nu})\Gamma(k - 2\alpha) \to 0$ \PvdH{Find reference.} and $\Gamma(k-t)/\Gamma(k+1) \sim k^{-(t+1)}$ as $k \to \infty$ we deduce that
+    	z^{k - 1 -2\alpha} e^{-z} \, dz\\
+    &= (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)},
+\end{align*}
+where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{+}$ the incomplete Gamma-function.
+We therefore conclude that
+\begin{equation}\label{eq:degree_distribution_P}
+	\Prob{D_\Pcal = k} = (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)}
+\end{equation}
+
+Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(t+1)}$ as $k \to \infty$ \PvdH{Find reference.} we deduce that
 \begin{equation}\label{eq:degree_distribution_P_asymptotics}
-	\Prob{D_\Pcal = k} = \int_0^\infty \rho_{y}(k) e^{-\alpha y} \, dy \sim (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}.
+	\Prob{D_\Pcal = k} \sim (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}
+	\quad \text{as } k \to \infty.
 \end{equation}
@@
 
+\PvdH{@Markus: Please check that your $\xi$ equals $\xi_{\alpha,\nu} := \frac{4\alpha \nu}{(2\alpha - 1)\pi}$ in all computations below. If not please adjust the computations.}
+
 \PvdH{This part is still in the original form and has to be converted to match style and notation.}
 
+Now that we have an expression for $\Delta_{\Pcal}(y)$ we can compute the limit local clustering coefficient $c_\infty$ and the limit local clustering function $c_\infty(k)$, i.e.
+prove Theorem~\ref{thm:exact_expression_c_infty} and Theorem~\ref{thm:exact_expression_local_clustering}.
+
+First we recall that
+\begin{align*}
+p_k := \Pee( D=k ) = \int_0^\infty e^{-\xi e^{y/2}} \frac{(\xi e^{y/2})^k}{k!}\alpha e^{-\alpha y} dy = 2\alpha \int_0^1 e^{-\frac{\xi}{z}} z^{2\alpha -k-1} dz =\frac{2\alpha \xi^{2\alpha}}{k!} \Gamma(k-2\alpha,\xi)
+\end{align*}
+\PvdH{@Markus: This result is taken from your notes. It seems to disagree with~\eqref{eq:degree_distribution_P}. Could you please check the other computations.}
+
 We wish to compute
-
 \[   

### 2018-10-20 introduction.tex
changes to section 1.3-1.5 (new references, clustering function etc., comment on special functions in green)

@@
 The hyperbolic plane is an infinite $2$-dimensional manifold with constant negative curvature.
-Many different representations of the hyperbolic plane exist and we refer to [CITE] for more details.
+Many different representations of the hyperbolic plane exist and we refer to~\cite{Anderson1999} \cite{Katok1992} \cite{Beardon1983} for an introduction to hyperbolic geometry.
 We will work with the \emph{native representation} of the hyperbolic plane which takes the elements of $\R^2$ in polar coordinates $(r,\theta)$ as the underlying set of points and where distances are determined by the hyperbolic law of cosines.
@@
 \]
-as follows from the hyperbolic cosine rule[CITE?].
+as follows from the hyperbolic law of cosines.% rule[CITE?].
 \end{enumerate}
@@
 If the vertex $v$ has no or only one neighbor, its clustering coefficient is set to zero.
+The (average) local clustering coefficient of the graph is the average over the clustering coefficients of all vertices.
+The local clustering function maps a natural number $k$ to the average over the clustering coefficients of all vertices with degree $k$ if there are vertices with degree $k$ and zero otherwise.
 
-To define the local clustering function, let $D_G(v)$ denote the degree of node $v$ and $N_G(k)$ the number of nodes with degree $k$ in the graph $G$.
-In addition let $\T_G(v,v_1,v_2) = \ind{(v,v_1) \in E} \ind{(v, v_2) \in E} \ind{(v_1, v_2) \in E}$ be the indicator that $v, v_1$ and $v_2$ form a triangle and write
+To introduce the notations for these definitions, let $D_G(v)$ denote the degree of vertex $v$ and $N_G(k)$ the number of vertices with degree $k$ in the graph $G$.
+In addition let $$\T_G(v,v_1,v_2) = \ind{(v,v_1) \in E} \ind{(v, v_2) \in E} \ind{(v_1, v_2) \in E}$$ be the indicator that $v, v_1$ and $v_2$ form a triangle and write
 \begin{equation}
@@
 However, since the local clustering coefficient assigns just one value to the whole network, representing its triangular structure, it is unable to characterize local structural properties involving triangles.
-The local clustering function, on the other hand, measures the fraction of triangles to which nodes of a given degree belong, compared to the maximum number of triangles in which they could participate~\cite{vazquez2002large,serrano2006clustering}.
-It therefore characterizes the triangular structure of nodes in the networks, based on their degree, and gives a more detailed look at the overall structure of the network.
+The local clustering function, on the other hand, measures the fraction of triangles to which vertices of a given degree belong, compared to the maximum number of triangles in which they could participate~\cite{vazquez2002large,serrano2006clustering}.
+It describes the triangular structure of vertices in the networks based on their degree and gives a more detailed look at the overall structure of the network.
 The formal definition of the \emph{local clustering function} is
@@
 
+\MS{Here, I would just say that $B(a,b)$ denotes the beta function $B^-(x,a,b)$ the lower incomplete beta function etc.
+and put/refer to the integral representations in the appendix, as already done for the Meijer-G function.}
 %\subsubsection{Special functions}

### 2018-10-21 clustering_infinite_model.tex
fixed errors in bib file and corresponding references in the LaTeX files

@@
 (also called Tricomi's confluent hypergeometric function) has the integral representation 
-$$U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} dt$$ which holds for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $Re(a), Re(z) >0$, see \cite[p.255]{Erdelyi1953}.
+$$U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} dt$$ which holds for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $Re(a), Re(z) >0$, see \cite[p.255]{erdelyi1953higher}.
 Applying the change of variables
@@
 Now, the incomplete $\Gamma$-function has a representation in terms of Meijer's $G$-function $$\Gamma^+(-a-1,\xi/s) = \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}}$$ which holds for any $a\in \R$ and $s>0$ (see appendix; note that for a fixed second argument, the upper incomplete $\Gamma$-function is entire in the first argument, see \cite[pp.
-899, 1032ff.]{Gradshteyn2007}).
+899, 1032ff.]{gradshteyn2015table}).
 Therefore, we get the integral
@@
 \end{align*}
-applying the inversion identity for Meijer's $G$-function (see \cite[p. 209, 5.3.1.(9))]{Erdelyi1953})
+applying the inversion identity for Meijer's $G$-function (see \cite[p. 209, 5.3.1.(9))]{erdelyi1953higher})
 \begin{align*}
@@
 This is the Euler transform of Meijer's $G$-function (see \cite[p.
-214, 5.5.2.(5)]{Erdelyi1953}) and (as the conditions $2+1<2(0+2)$ and $|\arg(\xi^{-1})| < \frac{\pi}{2}$ (as $\xi>0$) and $1-c-b<1-c$ (as $b>0$)  are satisfied) equals
+214, 5.5.2.(5)]{erdelyi1953higher}) and (as the conditions $2+1<2(0+2)$ and $|\arg(\xi^{-1})| < \frac{\pi}{2}$ (as $\xi>0$) and $1-c-b<1-c$ (as $b>0$)  are satisfied) equals
 \begin{align*}

### 2018-10-21 introduction.tex
fixed errors in bib file and corresponding references in the LaTeX files

@@
 Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
-Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{BodeFountoulakisMuller2015},~\cite{fountoulakis2018law}, [More?] and the number of cliques and the largest clique~\cite{blasius2018cliques}.
+Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{bode2015largest},~\cite{fountoulakis2018law}, [More?] and the number of cliques and the largest clique~\cite{blasius2018cliques}.
 
@@
 The hyperbolic plane is an infinite $2$-dimensional manifold with constant negative curvature.
-Many different representations of the hyperbolic plane exist and we refer to~\cite{Anderson1999} \cite{Katok1992} \cite{Beardon1983} for an introduction to hyperbolic geometry.
+Many different representations of the hyperbolic plane exist and we refer to~\cite{anderson2006hyperbolic} \cite{katok1992fuchsian} \cite{beardon2012geometry} for an introduction to hyperbolic geometry.
 We will work with the \emph{native representation} of the hyperbolic plane which takes the elements of $\R^2$ in polar coordinates $(r,\theta)$ as the underlying set of points and where distances are determined by the hyperbolic law of cosines.
@@
 \] 
-see~\cite[p.255 Equation (2)]{erdelyi1953higher}, and let $\MeijerGnew{m}{\ell}{p}{q}{{\bf a}}{{\bf b}}{z}$ denote Meijer's G-Function~\cite{meijer1946g}, see Appendix~\ref{sec:Meijer_G_functions} for more details.
+see~\cite[p.255 Equation (2)]{erdelyi1953higher}, and let $\MeijerGnew{m}{\ell}{p}{q}{{\bf a}}{{\bf b}}{z}$ denote Meijer's G-Function~\cite{meijer1946gfunction}, see Appendix~\ref{sec:Meijer_G_functions} for more details.
 

### 2018-10-24 introduction.tex
Added simulation section.

@@
 \subsection{Simulations}\label{ssec:simulations}
+The simulations of this section (see Figures \ref{fig:c2allnu}, \ref{fig:c4allnu} and \ref{fig:ckvariable}) confirm the formulas from the result section.
+The simulations were obtained by generating the hyperbolic random graph for a given choice of the parameters and number of repetitions and then taking the average over all simulation instances.
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.6]{figures/sim0123c2nualln1000rep20.pdf}
+    %\includegraphics[scale=0.5]{figures/sim0128c4nualln10000rep20.pdf}
+    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n= 2$, for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=1000$ and 20 repetitions.}
+    \label{fig:c2allnu}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.6]{figures/sim0128c4nualln10000rep20.pdf}
+    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n= 4$, for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10 000$ and 20 repetitions.}
+    \label{fig:c4allnu}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.6]{figures/sim1024ck225n10000a0609nu2rep20.pdf}
+    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n$ varying from 2 to 26 on the horizontal axis, for $\nu=2$ and $\alpha=0.6$ (green) and $\alpha=0.9$ (blue); simulations (red dots) with $n=10 000$ and 20 repetitions.}
+    \label{fig:ckvariable}
+\end{figure}

### 2018-10-24 introduction.tex
fix typos in main results section 1.5

@@
 
-With these expressions we define the limit local clustering coefficient as
+With these expressions we define the limiting local clustering coefficient as
 \begin{equation}\label{eq:def_average_clustering_infinite_model}
@@
 \end{equation}
-while the local clustering function limit is defined as
+while the limiting local clustering function is defined as
 \begin{equation}\label{eq:def_c_infty_k}
@@
 
-Our first result shows that the local clustering coefficient in the Hyperbolic random graph converges in expectation to $c_\infty$.
+Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to $c_\infty$.
 
@@
 
-Next we establishes the full expression for the clustering coefficient $c_\infty$ in terms of the special function defined above.
+Next we establish the full expression for the limiting clustering coefficient $c_\infty$ in terms of the special functions defined above.
 
-\begin{theorem}[Exact expression for clustering coefficient limit]\label{thm:exact_expression_c_infty}
+\begin{theorem}[Exact expression for limiting clustering coefficient]\label{thm:exact_expression_c_infty}
 Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, if $\alpha \ne 1$
@@
 
-\begin{theorem}[Exact expression for local clustering function limit]
+\begin{theorem}[Exact expression for limiting local clustering function]
 \label{thm:exact_expression_local_clustering}
@@
 \begin{align*}
-	c_\infty(k) 
-	&= \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma^+(k-6\alpha + 2,\xi_{\alpha,\nu})}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
-		\left(\frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha - 1)^2} + \frac{(\alpha - \frac{1}{2})B^-\left(\frac{1}{2},2\alpha + 1, 2\alpha - 2\right)}{2\alpha(\alpha - 1)}\right)\\
-	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma(2\alpha + 1)}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
-		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}\\
-	&\hspace{10pt}+ \frac{1}{8\alpha(\alpha - 1)}
-		\left(\frac{\xi_{\alpha,\nu}^{k-2\alpha}e^{-\xi}U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu})}
-		{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}-1\right)\\
-	&\hspace{10pt}- \frac{(\alpha - 1/2)^2 \xi_{\alpha,\nu}^2 \Gamma^+(k-2\alpha -2,\xi_{\alpha,\nu})}
-		{4(\alpha - 1)^2 \Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
+c_\infty(k)  =&\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right.
+\\
+&\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
+&\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
+      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
+&\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
+&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
 \end{align*}
+
+%\begin{align*}
+%	c_\infty(k) 
+%	&= \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma^+(k-6\alpha + 2,\xi_{\alpha,\nu})}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
+%		\left(\frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha - 1)^2} + \frac{(\alpha - \frac{1}{2})B^-\left(\frac{1}{2},2\alpha + 1, 2\alpha - 2\right)}{2\alpha(\alpha - 1)}\right)\\
+%	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma(2\alpha + 1)}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
+%		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}\\
+%	&\hspace{10pt}+ \frac{1}{8\alpha(\alpha - 1)}
+%		\left(\frac{\xi_{\alpha,\nu}^{k-2\alpha}e^{-\xi}U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu})}
+%		{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}-1\right)\\
+%	&\hspace{10pt}- \frac{(\alpha - 1/2)^2 \xi_{\alpha,\nu}^2 \Gamma^+(k-2\alpha -2,\xi_{\alpha,\nu})}
+%		{4(\alpha - 1)^2 \Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
+%\end{align*}
 while for $\alpha = 1$
@@
 \begin{equation}\label{eq:def_scaling_function}
-s_\alpha(k_n) = \begin{cases} 
-		k^{4\alpha-1} &\frac{1}{2}<\alpha<\frac{3}{4}, \\
+s_\alpha(k) = \begin{cases} 
+		k^{4\alpha-2} &\frac{1}{2}<\alpha<\frac{3}{4}, \\
 		\frac{k}{\log(k)} & \alpha = \frac{3}{4}, \\

### 2018-10-24 proof_overview.tex
started on Section 4.6. Added task for Markus.
Started merging Nikolaos results into paper

@@
 \end{equation}
-In addition we use $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation 
-\begin{equation}\label{eq:mu_y_P}
+
+Most of the subsequent analysis in this paper will make use of the~\emph{Campbell-Mecke} formula. 
+For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ we have
+\begin{equation}\label{eq:def_Campbell-Mecke}
+\begin{split}
+& \Exp{\sum_{x_1,\ldots, x_r \in \mathcal{P}}^{\neq} h (x_1, \ldots, x_r,
+\mathcal{P} \setminus \{x_1,\ldots, x_r\}) }\\
+& = \int_S \cdots \int_S
+\Exp{h(x_1,\ldots, x_r,\mathcal{P} \setminus \{x_1,\ldots, x_r\}) \lambda (x_1) \cdots \lambda (x_r) dx_1 \cdots dx_r},
+\end{split}
+\end{equation}
+where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$.
+
+Using the Campbell-Mecke formula we can compute the density of the ball $\BallPo{p}$ as
+\begin{equation}\label{eq:mu_ball_y_P}
 	\mu_{\alpha, \nu}(\BallPo{p}) = \int_0^\infty \int_{-\infty}^\infty \ind{|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}}
@@
 \end{equation}
-i.e.
+
+We shall use $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(\BallPo{p})$, i.e.
 \[

### 2018-10-29 clustering_infinite_model.tex

@@
 
-Using the above equation and the transformation of variables $z = \xi_{\alpha,\nu}e^{\frac{y}{2}}$, we compute
-\begin{align*}
-	\int_0^\infty \rho(y,k) e^{-\alpha y} \, dy 
-    &= \frac{1}{\Gamma(k+1)} \int_0^\infty \left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^k 
-    	e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}} e^{-\alpha y} \, dy\\
-    &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_0^\infty 
+Using the above equation and the transformation of variables $z = \xi_{\alpha,\nu}e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
+\begin{align*}
+	\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy 
+    &= \frac{1}{k!} \int_0^\infty \left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^k 
+    	e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy\\
+    &= \frac{\alpha (\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_0^\infty 
     	\left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}}
         \, dy\\
-    &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_{\xi_{\alpha,\nu}}^{\infty} 
-    	z^{k - 1 -2\alpha} e^{-z} \, dz\\
-    &= (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)},
+    &= \frac{2\alpha (\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_{\xi_{\alpha,\nu}}^{\infty} 
+    	z^{k -2\alpha-1} e^{-z} \, dz\\
+    &=2\alpha (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)},
 \end{align*}
@@
 \begin{equation}\label{eq:degree_distribution_P}
-	\Prob{D_\Pcal = k} = (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)}
-\end{equation}
-
-Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(t+1)}$ as $k \to \infty$ \PvdH{Find reference.} we deduce that
+	\Prob{D_\Pcal = k} = 2\alpha (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)}
+\end{equation}
+
+Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$ \PvdH{Find reference.} we deduce that
 \begin{equation}\label{eq:degree_distribution_P_asymptotics}
-	\Prob{D_\Pcal = k} \sim (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}
+	\Prob{D_\Pcal = k} \sim 2\alpha (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}
 	\quad \text{as } k \to \infty.
@@
 \begin{equation}\label{eq:general_integral_rho_y_k}
-	\int_0^\infty e^{\beta y} \rho_y(k) e^{-\alpha y} \, dy
-    \sim \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
+	\int_0^\infty e^{\beta y} \rho_y(k) \alpha e^{-\alpha y} \, dy
+    \sim 2\alpha \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
 \end{equation}
@@
 \[
-	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) e^{-\alpha y} \dd y}.
+	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
 \]
@@
 \[
-	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \, \rho(y,k) e^{-\alpha y} \, dy,
+	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
 \]
@@
 
-\PvdH{@Markus: Please check that your $\xi$ equals $\xi_{\alpha,\nu} := \frac{4\alpha \nu}{(2\alpha - 1)\pi}$ in all computations below. If not please adjust the computations.}
+%\PvdH{@Markus: Please check that your $\xi$ equals $\xi_{\alpha,\nu} := \frac{4\alpha \nu}{(2\alpha - 1)\pi}$ in all computations below. If not please adjust the computations.}
+%Markus: yes, this is the right xi.
 
@@
 \end{align*}
-\PvdH{@Markus: This result is taken from your notes. It seems to disagree with~\eqref{eq:degree_distribution_P}. Could you please check the other computations.}
+%\PvdH{@Markus: This result is taken from your notes. It seems to disagree with~\eqref{eq:degree_distribution_P}. Could you please check the other computations.}
 

### 2018-10-31 concentration_argument.tex
fully merged compations of Nikolaos plus some small edits on section 2

@@
 
-In particular, the average degree of a node at height $y$ is approximately Poisson with mean $\xi_{\alpha,\nu} e^{y/2}$ while we are interested in those nodes with degree $k_n$.
-Since Poisson random variables are well concentrated around their mean, for our analysis we would therefore like to be able the integration to intervals where $e^{y/2} \approx k_n$.
+In particular, the average degree of a node at height $y$ is approximately Poisson with mean $\xi_{\alpha,\nu} e^{y/2}$ and we are mostly interested in those nodes with degree $k_n$.
+Since Poisson random variables are well concentrated around their mean, for our analysis we would therefore like to be able the restrict integration to intervals where $e^{y/2} \approx k_n$.
 Moreover, we want to be able to do this for all three Poisson models $G_{\HP,n}$, $G_{\Pcal,n}$ and $G_\Pcal$ as well as simultaneously deal with the case where $k_n \to \infty$ and $k_n = \bigT{1}$.

### 2018-10-31 introduction.tex
fully merged compations of Nikolaos plus some small edits on section 2

@@
 Section~\ref{sec:concentration_argument} contains a crucial technical result that will be used in the other sections.
+Finally, the Appendix contains a few general results for the hyperbolic random graph and a small section on Meijer's G-function.
 
@@
 \paragraph{Maximum scaling for $k_n$ is $n^{\frac{1}{2\alpha +1}}$}
-All our results for clustering in the hyperbolic random graph are valid for any sequence $k_n$ such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
+All our results for clustering in the hyperbolic random graph are valid for any sequence $k_n$ such that $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$.
 Although one would like to have results for any sequence $k_n \le n$, it turns out that $n^{1/(2\alpha + 1)}$ is the optimal scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
@@
 \end{align*}
-We shall later establish (see Lemma [??] \PvdH{Find the reference for this Lemma}) that $\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}$.
+We shall later establish (see Lemma~\ref{lem:N_k_HP_P}) that $\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}$.
 Therefore if $k_n$ is such that $k_n = \omega\left(n^{\frac{1}{2\alpha + 1}}\right)$ we have
@@
 for any positive function $f$.
-This implies that we cannot expect a result like that of Theorem~\ref{thm:clustering_coefficient_hyperbolic} to hold as soon as $k_n = \omega\left(n^{\frac{1}{2\alpha + 1}}\right)$.
+This implies that we cannot expect a result like that of Theorem~\ref{thm:clustering_coefficient_hyperbolic} to hold as soon as $k_n = \omega\left(n^{\frac{1}{2\alpha + 1}}\right)$, and hence we need $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$.
 

### 2018-10-31 proof_overview.tex
fully merged compations of Nikolaos plus some small edits on section 2

@@
-\section{Overview of the proof strategy for Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}}\label{sec:proof_outline}
+\section{Overview of the proof strategy}\label{sec:proof_outline}
 
-We first give a detailed overview of the structure for the proof of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.
-The proof itself can be found in Section~\ref{ssec:proof_main_results}, where we also prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
+The key result in this paper is Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.
+In particular, it is the key ingredient in the proofs of Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
+Therefore, in this section we first give a detailed overview of the structure for the proof of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.
+The proof itself, based on intermediate propositions, can be found in Section~\ref{ssec:proof_main_results}.
+Here we also prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
+The proves of Theorem~\ref{thm:exact_expression_c_infty} and Theorem~\ref{thm:exact_expression_local_clustering} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P}
+
 Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic} based on the different propositions described below, plus the sections in which theses propositions are proved.

### 2018-11-01 transition.tex
Updated Section 5

@@
 
-\PvdH{The text in this section needs a full overhaul.}
-
-Our focus will however be on substituting $\rho_n(y,k_n)$ with $\rho(y,k_n)$ in integral expressions. We begin with the following useful lemma.
-
-%\begin{lemma}\label{lem:average_degree_P_n}
-%For all $p \in \Rcal_n$, such that $y > 2\log(\pi/2)$,
-%\[
-%	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right)
-%\]
-%where $\phi_n(y) \ge 0$ is given by
-%\[
-%	\phi_n(y) = \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)}e^{-(\alpha-\frac{1}{2})(R_n - y)}
-%	- \frac{(2\alpha - 1)\pi}{4\alpha}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} 
-%	e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(\alpha - \frac{1}{2})R_n - \frac{y}{2}}\right).
-%\]
-%If, on the other hand, $y \le 2 \log(\pi/2)$ then
-%\[
-%	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
-%\]
-%\end{lemma}
-%
-%\begin{proof}
-%First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$.
-We then have that
-%\[
-%	\BallPon{p} = \left\{p^\prime \in \Rcal_n \, : \, |x^\prime|_n \le e^{\frac{y + y^\prime}{2}}\right\},
-%\] 
-%whose boundaries given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$ intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
-%\[
-%	h(y) = R_n + 2 \log\left(\frac{\pi}{2}\right) - y.
-%\]
-%Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R_n$ of the box $\Rcal_n$ while in the other case the full region of the box above $h(y)$ is connected to $p$. 
-%
-%We will first consider the case where $y > 2 \log(\pi/2)$.
-Recall that $\mu_{\alpha,\nu}(B_\Pcal(p)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$ where $\xi_{\alpha,\nu} = \frac{4\alpha \nu}{(2\alpha - 1)\pi}$.
-Then, after some simple algebra, we have that
-%\begin{align*}
-%	\mu_{\alpha,\nu}(B_{\Pcal,n}(p))
-%	&= \int_0^{h(y)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
-%		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
-%	&\hspace{10pt}+ \int_{h(y)}^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
-%		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
-%	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{h(y)} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime
-%		+ \alpha \nu e^{\frac{R_n}{2}} \int_{h(y)}^{R_n} e^{-\alpha y^\prime} \, dy^\prime \\
-%	&= \xi_{\alpha,\nu} e^{\frac{y}{2}}\left(1 - \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} 
-%		e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)\\
-%	&\hspace{10pt}+ \nu e^{\frac{R_n}{2}}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} e^{-\alpha(R_n - y)} 
-%		- e^{-\alpha R_n}\right)\\
-%	&= \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right).
-%\end{align*}
-%Since, for all $\alpha > \frac{1}{2}$,
-%\[
-%	\left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} \ge \frac{(2\alpha - 1)\pi}{4\alpha} \left(\frac{\pi}{2}\right)^{-2\alpha}
-%\]
-%it follows that $\phi_n(y) \ge 0$.
-%
-%When $y \le 2 \log(\pi/2)$ we have
-%\begin{align*}
-%	\mu_{\alpha,\nu}(B_{\Pcal,n}(p))
-%	&= \int_0^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
-%		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
-%	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R_n} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
-%	&= \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
-%\end{align*}
-%\end{proof}
-
-$\phi_n(y) = \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}$. 
-This gives the following useful corollary to Lemma~\ref{lem:average_degree_P_n}.
+Now that we have a complete picture of the behavior of the local clustering coefficient and function in the limit model $G_\Pcal$ we will proceed to relate this to the clustering in the hyperbolic model $G_{\H,n}$.
+The first step is to relate the clustering in the infinite model to that of the finite box model $G_{\Pcal, n}$.
+Recall that $G_{\Pcal,n}$ is obtained by restricting the Poisson Point Process to the box $\Rcal_n = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$, and connecting two points $p_1, p_2 \in \Rcal_n$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$ where we identified the left and right boundary of $\Rcal_n$.
+See Section~\ref{ssec:finite_model} for more details.
+
+In this section we shall compute the asymptotic difference between triangle counts in the finite and infinite model. First we recall the definition of $\Kcal_{C}(k_n)$
+\[
+	\Kcal_C(k_n) = \left\{p \in \R : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
+	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \wedge e^{R_n/2} \right\},	
+\]
+with
+\[
+	\kappa_n := \begin{cases}
+		\log(n) &\mbox{if } k_n = \bigT{1},\\
+		\sqrt{k_n \log(k_n)} &\mbox{else.}
+	\end{cases}
+\]
+In addition we note that the function $\phi_n(y)$ in Lemma~\ref{lem:average_degree_P_n} satisfies
+\[
+	\phi_n(y) = \bigT{e^{-(\alpha - \frac{1}{2})(R_n - y)}},
+\]
+which yields the following useful corollary to Lemma~\ref{lem:average_degree_P_n}.
 
 \begin{corollary}\label{cor:average_degree_P_n_K}
-Let $\alpha > \frac{1}{2}$, $0 < \varepsilon < 1$ and $k_n$ be an increasing sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha - 1}}}$. Then, for all $p \in \Kcal_{\varepsilon}(k_n)$,
+Let $\alpha > \frac{1}{2}$, $C > 0$ and $k_n$ be any sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha - 1}}}$. Then, for all $p \in \Kcal_{C}(k_n)$,
 \[
@@
 \end{corollary}
-
-With this lemma we can now show that we can replace $\rho_n(y,k_n)$ in integral expressions over $\Rcal_n$ with $\rho(y,k_n)$. This will help make the remaining computations easier.
-
-%\begin{lemma}\label{lem:replace_rho_n_with_rho}
-%Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n$ be any increasing sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$.
-Then, for any $h : \R_+ \mapsto \R$ such that $h(y) = \bigO{e^\beta}$ as $y \to \infty$ for some $\beta \in \R$ and $\varepsilon > 2 \sqrt{2 (\beta - \alpha \vee 1)(2\alpha + 1)}$,
-%\[
-%	\int_{\Rcal_n} \rho_n(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
-%	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) e^{\beta y} f_{\alpha,\nu}(x,y) \dd x \dd y.
-%\]
-%\end{lemma}
-%
-%\begin{proof}
-%Similar to the proof of Lemma~\ref{lem:concentration_argument} we define 
-%\[
-%	\lambda_n^\pm = k_n \pm \varepsilon \sqrt{k_n \log(k_n)}, \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right)
-%\] 
-%We will show that as $n \to \infty$,
-%\begin{equation}\label{eq:P_n_nodes_degree_k}
-%	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) e^{(\beta - \alpha) y} \dd y = (1+o(1))\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) e^{(\beta - \alpha) y} \dd y,
-%\end{equation}
-%from which the result follows by a concentration argument.
-%
-%For simplicity we will write
-%\[
-%	\mu_1(y) := \mu_{\alpha,\nu}\left(\BallPo{y}\right) \quad \text{and} \quad 
-%	\mu_2(y) = \mu_{\alpha,\nu}\left(\BallPon{y}\right),
-%\]
-%and recall that $\mu_2(y) = \mu_1(y)(1 - \phi_n(y))$ with $\phi_n(y)$ defined as in Lemma~\ref{lem:average_degree_P_n}. Let us now make a change of variables $y \to z$ such that
-%\[
-%	\mu_2(y) = \mu_1(z).
-%\]
-%and note that since
-%\[
-%	\mu_1^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
-%\]
-%we have
-%\[
-%	z(y) = 2 \log\left(\frac{\mu_1(y)}{\xi_{\alpha,\nu}}\right) + 2 \log\left(1 - \phi_n(y)\right)
-%	= y + 2 \log\left(1 - \phi_n(y)\right).
-%\]
-%
-%Next we note that for any $a_n^- \le y \le a_n^+$
-%\[
-%	\phi_n(a_n^-) \le \phi_n(y) \le \phi_n(a_n^+) 
-%\]
-%which are both $o(1)$, as $n \to \infty$, and hence
-%\begin{equation}
-%	e^{(\beta-\alpha) y} = e^{(\beta-\alpha) z} e^{(\beta-\alpha) \log(1-\phi_n(y))} = e^{(\beta-\alpha) z}\left(1 - \phi_n(y)\right)^{\beta-\alpha}	= (1 + o(1))e^{(\beta-\alpha) z}
-%\end{equation}
-%uniformly for $a_n^- \le y \le a_n^+$. For the derivatives we have $\mu_1^\prime(y) = \mu_1(y)/2$, while $\phi_n^\prime(y) = O(1) \phi_n(y)$ and hence
-%\begin{align*}
-%	\mu_2^\prime(y) = \left(1 - \phi_n(y)\right)\mu_1^\prime(y)  
-%	- \mu_1(y) \phi_n^\prime(y) = \mu_1^\prime(y)\left(1 - o(1)\right),
-%\end{align*}
-%uniformly for $a_n^- \le y \le a_n^+$. Therefore, with this change of variables, and using
-%\[
-%	\hat{a}_n^\pm := z(a_n^\pm) = a_n^\pm + 2\log(1 - \phi_n(a_n^\pm)),
-%\] 
-%we have
-%\begin{align*}
-%	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) e^{(\beta - \alpha)y} \dd y
-%	&=  \int_{a_n^-}^{a_n^+} \Prob{\mathrm{Po}\left(\mu_2(y) = k_n\right)} e^{(\beta-\alpha) y} \dd y\\
-%	&= (1 + \smallO{1})\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\mathrm{Po}\left(\mu_1(z) = k_n\right)}
-%		e^{-\alpha z} \frac{\mu_2^\prime(z)}{\mu_2^{\prime}(z)} \, dz\\
-%	&= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(y,k_n) e^{(\beta-\alpha) z} \, dz.
-%\end{align*}
-%\end{proof}
-
-As a direct consequence of the above lemma we obtain asymptotic result for the number of nodes with degree $k_n$ in $G_{\Pcal,n}(\alpha,\nu)$.
-
-\begin{lemma}\label{lem:nodes_degree_k_P_n}
-Let $k_n$ be an non-decreasing sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then,
-\[
-	\Exp{N_{\Pcal,n}(k_n)} = (1+o(1)) \alpha n \int_{\R_+} \rho(y,k_n) e^{-\alpha} \dd y,
-\]
-so that in particular
-\[
-	\Exp{N_{\Pcal,n}(k_n)} = (1+\smallO{1}) \alpha n k_n^{-(2\alpha + 1)}.
-\]
-\end{lemma}
-
-\begin{proof}
-Since
-\[
-	\Exp{N_{\Pcal,n}(k_n)} = \int_{\Rcal} \rho_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y,
-\]
-and $2 I_n/\pi = n/\nu$, the result follows directly from Lemma~\ref{lem:replace_rho_n_with_rho}.
-\begin{align*}
-	\Exp{N_{\Pcal,n}(k_n)} &= (1+\smallO{1})\int_{\Rcal} \rho(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y\\
-	&= \frac{2 \alpha \nu}{\pi} I_n \int_0^{R_n} \rho(y,k_n) e^{-\alpha} \dd y\\
-	&= \alpha n \int_0^{R_n} \rho(y,k_n) e^{-\alpha} \dd y \\
-	&= (1+\smallO{1}) \alpha n k_n^{-(2\alpha + 1)}.
-\end{align*}
-\end{proof}
-
-%With this inside we define
-%\begin{equation}\label{eq:def_triangle_count_K_epsilon}
-%	\widetilde{T}_{\Pcal,n}(k,\varepsilon) = \sum_{p \in \Pcal_n \cap \Kcal_{\varepsilon}(k)} \ind{D_{\Pcal,n}(p) = k} 
-%	T_{\Pcal,n}(p),
-%\end{equation}
-%to denote the number of triangles for nodes in $G_{\Pcal,n}(\alpha,\nu)$ with degree $k$ and $p \in \Kcal_\varepsilon(k)$ and use a similar definition for $\widetilde{T}_{\Pcal}(k,\varepsilon)$ in the graph $G_{\Pcal}(\alpha,\nu)$.
 
@@
 In particular, $p^\prime \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
-See Figure \ref{fig:comparing_triangles_diff_analysis} for an illustration.
 
@@
 These are the intersection between the left boundary of $p^\prime$ and the right boundary of $p^\prime$, as it continues from the left side of the box, and the left boundary of $p$.
-We denote by $(x^\ast(p^\prime), y^\ast(p^\prime))$ the intersection between the left and right boundary of $p^\prime$ and by $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$ the intersection between the left boundary of $p$ and the right boundary of $p^\prime$ (see also Figure \ref{fig:comparing_triangles_diff_analysis}).
+We denote by $(x^\ast(p^\prime), y^\ast(p^\prime))$ the intersection between the left and right boundary of $p^\prime$ and by $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$ the intersection between the left boundary of $p$ and the right boundary of $p^\prime$, see Figure \ref{fig:comparing_triangles_diff_analysis}.
 After some simple algebra we obtain the following expressions for the coordinates of these two points
@@
 \begin{lemma}\label{lem:clustering_error_T_term}
-Let $(k_n)_{n \ge 1}$ be any sequence with $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, for any $0 < \varepsilon < 1$ and $p \in \Kcal_{\varepsilon}(k_n)$, as $n \to \infty$,
-\[
-	\int_{\Rcal_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\mu, \nu}(x_1,y_1) 
+Let $(k_n)_{n \ge 1}$ be any sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, for some $C > 0$ and $p \in \Kcal_{C}(k_n)$, as $n \to \infty$,
+\[
+	\int_{\Rcal_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\alpha, \nu}(x_1,y_1) 
 	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
@@
 
-\begin{corollary}\label{cor:clustering_error_T_term}
-Let $(k_n)_{n \ge 1}$ be any sequence with $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, for any $0 < \varepsilon < 1$ and $p \in \Kcal_{\varepsilon}(k_n)$, as $n \to \infty$,
-\[
-	\left|\frac{\Exp{T_{\Pcal,n}(p)}}{\Exp{T_{\Pcal}(p)}} - 1\right| = \bigO{s_\alpha(k_n)^{-1} k_n^{-3(2\alpha - 1)}} =
-	\begin{cases}
-		\bigO{k_n^{-(2\alpha - 1)}} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
-				\bigO{\log(k_n)^{-1} k_n^{-\frac{1}{2}}} &\mbox{if } \alpha = \frac{3}{4},\\
-				\bigO{k_n^{-(6\alpha-4)}} &\mbox{if } \alpha > \frac{3}{4}.
-	\end{cases}
-\]
-\end{corollary}
-
 \begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]
 
-\PvdH{incorporate case where $k_n = \bigT{1}$.}
-
 Recall that
 \[
-	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\int_{\Rcal_n} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}.
-\]
-By Lemma~\ref{lem:nodes_degree_k_P_n}
-\[
-	\Exp{N_{\Pcal,n}(k_n)} = (1+o(1)) \alpha n \int_{\R_+} \rho(y,k_n) e^{-\alpha} \dd y,
-\]
-and hence it is enough to show that
-\[
-	\int_{\Rcal_n} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y
-	= (1 + \smallO{1}) \alpha n \int_{\R_+} \rho(y,k_n) \Exp{T_\Pcal(y)} e^{-\alpha y} \dd x \dd y.
-\]
-
-First we note that
+	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\int_{\Rcal_n} \Exp{\ind{D_{\H,n}(y) = k_n} T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}.
+\]
+By Lemma~\ref{lem:average_degree_P_n} and a concentration argument
+\[
+	\Exp{N_{\Pcal,n}(k_n)} = (1+o(1)) \alpha n \int_{0}^\infty \rho(y,k_n) e^{-\alpha} \dd y 
+	= (1+\smallO{1}) \alpha n \Exp{N_{\Pcal}(k_n)},
+\]
+and since $\ind{D_{\H,n}(y) = k_n} T_{\Pcal,n}(y) \le \rho_n(y,k_n) k_n^2$ another concentration argument yields
+\begin{align*}
+	&\hspace{-30pt}\int_{\Rcal_n} \Exp{\ind{D_{\H,n}(y) = k_n} T_{\Pcal,n}(y)} 
+		f_{\alpha,\nu}(x,y) \dd x \dd y\\
+	&= (1+\smallO{1})\int_{\Kcal_C(k_n)} \rho(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
+	&= (1 + \smallO{1}) \alpha n \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha} \dd x \dd y,
+\end{align*}
+with $a_n^\pm = 2\log\left(\frac{k_n \pm C \kappa_n}{\xi_{\alpha,\nu}}\right)$. It now suffices to show that
+\[
+	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha} \dd x \dd y
+	= (1+\smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd x \dd y, 
+\]
+which follows if we can show that
+\[
+	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(y) - T_{\Pcal}(y)}\right| e^{-\alpha} \dd y
+	= \smallO{1} \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd y.
+\]
+
+For this we write
 \begin{align*}
@@
 \end{align*}
-and hence
+so that by the Campbell-Mecke formula~\eqref{eq:def_Campbell-Mecke}
 \begin{align*}
 	\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right|
-	&\le \int_{\Rcal_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\mu, \nu}(x_1,y_1) 
+	&\le \int_{\Rcal_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\alpha, \nu}(x_1,y_1) 
 		\dd x_1 \dd y_1\\
-	&\hspace{10pt}+ \iint_{\Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2) f_{\mu, \nu}(x_1,y_1) f_{\mu, \nu}(x_2,y_2)
+	&\hspace{10pt}+ \iint_{\Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2) f_{\alpha, \nu}(x_1,y_1) f_{\alpha, \nu}(x_2,y_2)
 		\dd x_2 \dd y_2 \dd x_1 \dd y_1. 
@@
 \begin{align*}
-	&\hspace{-30pt}\iint_{\Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2) f_{\mu, \nu}(x_1,y_1) f_{\mu, \nu}(x_2,y_2)
+	&\hspace{-30pt}\iint_{\Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2) f_{\alpha, \nu}(x_1,y_1) f_{\mu, \nu}(x_2,y_2)
 		\dd x_2 \dd y_2 \dd x_1 \dd y_1\\
-	&\le \left(\int_{\Rcal \setminus \Rcal_n} \ind{p_1 \in \BallPo{p}} f_{\mu, \nu}(x_1,y_1) \dd x_1 \dd y_1\right)^2\\
+	&\le \left(\int_{\Rcal \setminus \Rcal_n} \ind{p_1 \in \BallPo{p}} f_{\alpha, \nu}(x_1,y_1) \dd x_1 \dd y_1\right)^2\\
 	&= \bigO{\left(e^{y/2} \int_{R_n}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}
@@
 \]
-Next we show that this difference is $\smallO{\Exp{T_\Pcal(p)}}$ when $y \in K_\eps(k_n)$.
-Observe that since $\Exp{T_\Pcal(p)} = e^y \Delta_{\Pcal}(y)$, Proposition~\ref{prop:asymptotics_Delta_y_P} implies that $\Exp{T_\Pcal(y)} = \bigT{e^y s_\alpha(e^{y/2})}$ as $y \to \infty$.
-Now consider $y \in K_C(k_n)$. Then $e^{y/2} = \bigT{k_n}$ and hence
-\[
-	\frac{\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right|}{\Exp{T_\Pcal(y)}} =
-	\bigO{n^{-(2\alpha - 1)}s_\alpha(k_n)^{-1}\left(\log(k_n)k^{-2} + 1\right)} = \bigO{\left(n^{2\alpha - 1}s_\alpha(k_n)\right)^{-1}} = \smallO{1}, 
-\]
-where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. It follows that for $y \in \Kcal_\eps(k_n)$ we have
-\[
-	\Exp{T_{\Pcal,n}(y)} = (1+\smallO{1})\Exp{T_{\Pcal}(y)},
-\]
-while in general
-\[
-	\Exp{T_{\Pcal,n}(y)} = \Exp{T_{\Pcal}(y)}\left(1 + \bigO{s_\alpha(e^{y/2})}\right) = \bigO{e^y s_\alpha(e^{y/2})^2}.
-\]
-Therefore, by first applying a concentration argument and then Lemma~\ref{lem:replace_rho_n_with_rho}, 
-\begin{align*}
-	&\hspace{-30pt}\int_{\Rcal_n} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
-	&= (1+\smallO{1})\int_{\Rcal_n} \rho_n(y,k_n) \Exp{T_\Pcal(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
-	&= (1 + \smallO{1}) \int_{\Rcal_n} \rho(y,k_n) \Exp{T_\Pcal(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
-	&= (1 + \smallO{1}) \alpha n \int_{\R_+} \rho(y,k_n) \Exp{T_\Pcal(y)} e^{-\alpha y} \dd x \dd y.
-\end{align*}
+Therefore 
+\begin{align*}
+	&\hspace{-30pt}\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| 
+		e^{-\alpha} \dd y\\
+	&= \bigO{1} n^{-(2\alpha - 1)} k_n^2 \int_{0}^\infty \rho(y,k_n) f_{\alpha,\nu}(x,y) \dd y\\
+	&= \bigO{1} n^{-(2\alpha - 1)} k_n^{-2\alpha + 1}.
+\end{align*}
+
+To finish the argument we observe that
+\begin{align*}
+	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd y 
+	&= (1 + \smallO{1})\int_0^\infty \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd y \\
+	&= \bigT{1} \binom{k_n}{2} \int_0^\infty \rho(y,k_n) \Delta_\Pcal(y) e^{-\alpha} \dd y\\
+	&= \bigT{1} k_n^{2} \Exp{N_{\Pcal}(k_n)} c_\infty(k_n)
+		= \bigT{k_n^{-2\alpha + 1} s_\alpha(k_n)}.
+\end{align*}
+Therefore, since $n^{-(2\alpha - 1)} = \smallO{s_\alpha(k_n)}$ by Lemma~\ref{lem:scaling_s_alpha}, we conclude that
+\begin{align*}
+	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| e^{-\alpha} \dd y 
+	&= \smallO{k_n^{-2\alpha + 1} s_\alpha(k_n)} \\
+	&= \smallO{1} \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd y,
+\end{align*}
+which completes the proof.
+
 \end{proof}
@@
 
-\PvdH{I have currently used that $\alpha < 1$, which is the most difficult case. The case $\alpha = 1$ and $\alpha > 1$ will be added.}
-
-Define the sets
+Recall that $I_n = \frac{\pi}{2} e^{R_n/2}$ and define the sets
 \begin{align*}
@@
 \end{align*}
-where we used that $x^\prime \le e^{(y+y_1)/2} = \smallO{I_n}$ for all $y_1\le y$ and $y \in \Kcal_{\varepsilon}(k_n)$ so that
+where we used that $x^\prime \le e^{(y+y_1)/2} = \smallO{I_n}$ for all $y_1\le y$ and $y \in \Kcal_{C}(k_n)$ so that
 \[
@@
 \end{align*}
-since $y \in \Kcal_{\varepsilon}(k_n)$ and $k_n = \smallO{\sqrt{n}}$, so that $e^y = \smallO{n} = \smallO{I_n}$. 
+since $y \in \Kcal_{C}(k_n)$ and $k_n = \smallO{\sqrt{n}}$, so that $e^y = \smallO{n} = \smallO{I_n}$. 
 Then we have

### 2018-11-02 introduction.tex
Major update to Section 1 and 2

--- 2018-10-24 introduction.tex
@@
 The results are obtained by coupling the hyperbolic random graph to an infinite random graph $G_\Pcal(\alpha,\nu)$, which we define in Section~\ref{ssec:infinite_model}, and show that the limit of the local clustering coefficient and function for the hyperbolic random graph are given by those for the infinite model.
-To express these expressions we define for any $y \in \R_+$
-\[
-	\rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k},
-\]
-where $\xi_{\alpha,\nu} = (4\alpha \nu)/(2\alpha - 1)\pi$ and $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$.
-In addition we define the (marginal) probability measures on $\Rcal := \R_+ \times \R$ by
-\[
-	\eta_{y}(x^\prime, y^\prime) = \frac{\alpha \nu e^{-\frac{y}{2}}}{\xi_{\alpha,\nu} \pi} \, \ind{|x^\prime|<e^{(y+y^\prime)/2}} \, e^{-\alpha y^\prime}
-\]	
-and let
-\begin{equation}\label{eq:def_delta_p}
-	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(y, x_1, x_2, y_1, y_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \dd x_1 \dd x_2  \dd y_1  \dd y_2,
-\end{equation}
-where 
-\[
-	T_\Pcal(y, x_1, x_2, y_1, y_2) 
-	= \ind{|x_1| \, \le \, e^{(y+y_1)/2}}\ind{|x_2| \, \le \, e^{(y+y_2)/2}}\ind{|x_1-x_2| \, \le \, e^{(y_1+y_2)/2}}.
-\]
-
-With these expressions we define the limiting local clustering coefficient as
-\begin{equation}\label{eq:def_average_clustering_infinite_model}
-	c_\infty := \alpha \int_0^\infty \Delta_{\Pcal}(y) (1 - \rho(y,0) - \rho(y,1)) e^{-\alpha y} \dd y,
-\end{equation}
-while the limiting local clustering function is defined as
-\begin{equation}\label{eq:def_c_infty_k}
-	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) e^{-\alpha y} \dd y}.
-\end{equation}
-
-Finally to express the local clustering coefficient and function in the infinite limit model we need a couple of special functions.
 
@@
 %\subsubsection{Special functions}
-We let $B(a,b)$ denote the beta-function 
-%\[
-%	B(a,b) = \int_0^1 t^{a-1}(1-t)^{b-1} \, dt
-%\]
-and $B^-(x,a,b)$ the lower incomplete beta-function
-\[
-	B^-(x,a,b) = \int_x^1 t^{a-1}(1-t)^{b-1} \, dt.
-\]
-In addition we write $\Gamma(z)$ for the Gamma function, $\Gamma^+(q,z)$ for the incomplete Gamma function
-\[
-	\Gamma^+(q,z) = \int_z^\infty t^{q - 1} e^{-t} \dd t
-\]
-and define $\Gamma^\ast(q,z) := \Gamma^+(1 + q, z) + \Gamma^+(q, z)$.
+We let $B(a,b)$ denote the beta-function and $B^-(x,a,b)$ the lower incomplete beta-function.
+We also write $\Gamma(z)$ for the Gamma function, $\Gamma^+(q,z)$ for the incomplete Gamma function and define $\Gamma^\ast(q,z) := \Gamma^+(1 + q, z) + \Gamma^+(q, z)$.
 Finally, we write $U(a,b,z)$ for the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $\mathrm{Re}(a), \mathrm{Re}(z) >0$ has the integral representation
@@
 
-\PvdH{@All: I would be nice if we could show with simulations how close $c_{\H,n}$ actually is to $c_\infty$ for reasonably large $n$ in practice.}
-
-Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to $c_\infty$.
+Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to as constant $c_\infty$, which we can explicitly write down in terms of the special function defined above.
 
@@
 \[
-	\lim_{n \to \infty} \Exp{\left|c_{\H,n} - c_\infty\right|} = 0.
+	\lim_{n \to \infty} \Exp{\left|c_{\H,n} - c_\infty\right|} = 0,
 \]
-\end{theorem}
-
-Next we establish the full expression for the limiting clustering coefficient $c_\infty$ in terms of the special functions defined above.
-
-\begin{theorem}[Exact expression for limiting clustering coefficient]\label{thm:exact_expression_c_infty}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, if $\alpha \ne 1$
+where $c_\infty$ is defined for $\alpha \ne 1$ as
 \begin{align*}
@@
 \end{align*}
-while for $\alpha = 1$,
+and for $\alpha = 1$ as
 \begin{align*}
@@
 
-We obtain similar results for the local clustering function. The first states that $c_{\H,n}(k)$ is asymptotically equivalent to $c_\infty(k)$ in an $L^1$ sense.
+For the local clustering function we also obtain convergence in expectation to a function $c_\infty(k)$ which can be explicitly stated using the special functions.
 
 \begin{theorem}[Limit for local clustering function in $G_{\H,n}(\alpha, \nu)$]
-\label{thm:asymptotic_local_clustering_hyperbolic}
+\label{thm:local_clustering_hyperbolic}
 Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, 
 \[
-	\lim_{n \to \infty} \Exp{\left|\frac{c_{\H,n}(k_n)}{c_\infty(k_n)} - 1\right|} = 0.
+	\lim_{n \to \infty} \Exp{\left|\frac{c_{\H,n}(k_n)}{c_\infty(k_n)} - 1\right|} = 0,
 \]
-%where
-%\[
-%	C_{\alpha,\nu} = \begin{cases}
-%		C_\alpha \left(\frac{2\alpha \nu}{\pi\left(\alpha - \frac{1}{2}\right)}\right)^{4\alpha - 2}
-%		&\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
-%		\frac{2\alpha \nu}{\pi\left(\alpha - \frac{1}{4}\right)} &\mbox{if } \alpha = \frac{3}{4},\\
-%		\frac{2\alpha \nu}{\pi\left(\alpha - \frac{3}{4}\right)} &\mbox{if } \alpha \ge \frac{3}{4}
-%	\end{cases} 
-%\]
-%with $C_\alpha$ as defined in \eqref{eq:def_C_alpha}.
-\end{theorem}
-
-Next we give an exact expression for $c_\infty(k)$ in terms of the special functions defined earlier.
-
-\begin{theorem}[Exact expression for limiting local clustering function]
-\label{thm:exact_expression_local_clustering}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, for $\alpha \ne 1$
+where the function $c_\infty(k)$ is defined for $\alpha \ne 1$ as
 \begin{align*}
@@
 \end{align*}
-
-%\begin{align*}
-%	c_\infty(k) 
-%	&= \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma^+(k-6\alpha + 2,\xi_{\alpha,\nu})}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
-%		\left(\frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha - 1)^2} + \frac{(\alpha - \frac{1}{2})B^-\left(\frac{1}{2},2\alpha + 1, 2\alpha - 2\right)}{2\alpha(\alpha - 1)}\right)\\
-%	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma(2\alpha + 1)}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
-%		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}\\
-%	&\hspace{10pt}+ \frac{1}{8\alpha(\alpha - 1)}
-%		\left(\frac{\xi_{\alpha,\nu}^{k-2\alpha}e^{-\xi}U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu})}
-%		{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}-1\right)\\
-%	&\hspace{10pt}- \frac{(\alpha - 1/2)^2 \xi_{\alpha,\nu}^2 \Gamma^+(k-2\alpha -2,\xi_{\alpha,\nu})}
-%		{4(\alpha - 1)^2 \Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
-%\end{align*}
-while for $\alpha = 1$
+and for $\alpha = 1$ as
 \begin{align*}
@@
 
-From the exact expression for $c_\infty(k)$ we obtain its asymptotic behavior as $k \to \infty$. For this we first define, for any $\frac{1}{2} < \alpha < \frac{3}{4}$,
+From the expression for $c_\infty(k)$ we obtain its asymptotic behavior as $k \to \infty$. For this we first define, for any $\frac{1}{2} < \alpha < \frac{3}{4}$,
 \begin{equation}\label{eq:def_C_alpha}
@@
 
-The following is an immediate consequence of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
+The following is an immediate consequence of Theorem~\ref{thm:local_clustering_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
 
@@
 
-\PvdH{@All: It would be nice if we could add some simulations showing this scaling in practice, especially the different regimes.}
-
-The majority of the paper is dedicated to prove Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}, which is based on a sequence of subsequent results for the local clustering function in related random graph models and Theorem~\ref{thm:asymptotics_average_clustering_P}.
+The majority of the paper is dedicated to prove Theorem~\ref{thm:local_clustering_hyperbolic}, which is based on a sequence of subsequent results for the local clustering function in related random graph models and Theorem~\ref{thm:asymptotics_average_clustering_P}.
 The exact flow of the argument is explained in Section \ref{sec:proof_outline}.
-The proof for Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}, using these results, can be found in Section \ref{ssec:proof_main_results}.
+The proof for Theorem~\ref{thm:local_clustering_hyperbolic}, using these results, can be found in Section \ref{ssec:proof_main_results}.
 Here we also give the proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
-The exact result for the local clustering coefficient and function, as well as the proofs of Theorem~\ref{thm:exact_expression_c_infty} and~\ref{thm:asymptotics_average_clustering_P} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
+The proof of Theorem~\ref{thm:asymptotics_average_clustering_P} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
 
@@
 \paragraph{Transition in the scaling of local clustering}
-%Note that Theorem \ref{thm:asymptotic_local_clustering_hyperbolic} implies that for $\frac{1}{2} < \alpha < \frac{3}{4}$ the local clustering $c_{\H,n}(k)$ decays as $k^{-(4\alpha - 2)}$ while for $\alpha > \frac{3}{4}$ it is $k^{-1}$.
+%Note that Theorem \ref{thm:local_clustering_hyperbolic} implies that for $\frac{1}{2} < \alpha < \frac{3}{4}$ the local clustering $c_{\H,n}(k)$ decays as $k^{-(4\alpha - 2)}$ while for $\alpha > \frac{3}{4}$ it is $k^{-1}$.
 
@@
 \end{align*}
-We shall later establish (see Lemma [??] \PvdH{Find the reference for this Lemma}) that $\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}$.
-Therefore if $k_n$ is such that $k_n = \omega\left(n^{\frac{1}{2\alpha + 1}}\right)$ we have
+We shall later establish (see Lemma~\ref{lem:N_k_HP_P}) that $\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}$.
+Therefore if $k_n$ is such that $k_n^{-(2\alpha + 1)} n$ tends to zero as $n \to \infty$ we have that
 \[
-	\lim_{n \to \infty} n k_n^{-(2\alpha + 1)} 
-	= \lim_{n \to \infty} \left(n^{-\frac{1}{2\alpha + 1}} k_n\right)^{-(2\alpha + 1)} = 0
+	\lim_{n \to \infty} \Exp{N_{\H,n}(k_n)} = 0
 \]
@@
 	\lim_{n \to \infty} \Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|} 
-	\ge \lim_{n \to \infty} 1 - \Exp{N_{\H,n}(k_n)} = \lim_{n \to \infty} 1 - \bigT{n k_n^{-(2\alpha + 1)}} = 1 \ne 0,
+	\ge \lim_{n \to \infty} 1 - \Exp{N_{\H,n}(k_n)} = 1 \ne 0,
 \]
 for any positive function $f$.
-This implies that we cannot expect a result like that of Theorem~\ref{thm:clustering_coefficient_hyperbolic} to hold as soon as $k_n = \omega\left(n^{\frac{1}{2\alpha + 1}}\right)$.
+This implies that we cannot expect a result like that of Theorem~\ref{thm:clustering_coefficient_hyperbolic} to hold as soon as $k_n$ is not $\smallO{n^{\frac{1}{2\alpha + 1}}}$.
 
-%Maybe, it would make sense to incorporate this statement into theorem \ref{thm:asymptotic_local_clustering_hyperbolic}, i.e.
+%Maybe, it would make sense to incorporate this statement into theorem \ref{thm:local_clustering_hyperbolic}, i.e.
 that the asymptotic behaviour of $c(k_n)$ is not well-defined for $k_n \gg n^{\frac{1}{2\alpha+1}}$?
@@
 %\paragraph{Local clustering for growing versus fixed degrees}
-%%The main difference between Theorem \ref{thm:fixed_local_clustering_hyperbolic} and Theorem \ref{thm:asymptotic_local_clustering_hyperbolic} is that for fixed degrees $k$ we have a small correction term that depends on the value $k$.
+%%The main difference between Theorem \ref{thm:fixed_local_clustering_hyperbolic} and Theorem \ref{thm:local_clustering_hyperbolic} is that for fixed degrees $k$ we have a small correction term that depends on the value $k$.
 %
@@
 
-%The main difference between Theorem \ref{thm:fixed_local_clustering_hyperbolic} and Theorem \ref{thm:asymptotic_local_clustering_hyperbolic} is that for fixed degrees $k$ we have a small correction term that depends on the value $k$.
+%The main difference between Theorem \ref{thm:fixed_local_clustering_hyperbolic} and Theorem \ref{thm:local_clustering_hyperbolic} is that for fixed degrees $k$ we have a small correction term that depends on the value $k$.
 

### 2018-11-02 proof_overview.tex
Major update to Section 1 and 2

@@
 
-The key result in this paper is Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.
+The key result in this paper is Theorem~\ref{thm:local_clustering_hyperbolic}.
 In particular, it is the key ingredient in the proofs of Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
-Therefore, in this section we first give a detailed overview of the structure for the proof of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.
+Therefore, in this section we first give a detailed overview of the structure for the proof of Theorem~\ref{thm:local_clustering_hyperbolic}.
 The proof itself, based on intermediate propositions, can be found in Section~\ref{ssec:proof_main_results}.
 Here we also prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
-The proves of Theorem~\ref{thm:exact_expression_c_infty} and Theorem~\ref{thm:exact_expression_local_clustering} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P}
+The proof of Theorem~\ref{thm:asymptotics_average_clustering_P} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
 
-Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic} based on the different propositions described below, plus the sections in which theses propositions are proved.
+Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem~\ref{thm:local_clustering_hyperbolic} based on the different propositions described below, plus the sections in which theses propositions are proved.
 
@@
 
-\caption{Overview of the proof strategy for Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}.}
+\caption{Overview of the proof strategy for Theorem \ref{thm:local_clustering_hyperbolic}.}
 \label{fig:overview_proof}
@@
 
-The main idea behind the proof of Theorem \ref{thm:asymptotic_local_clustering_hyperbolic} is to couple the hyperbolic graph $G_{\H, n}(\alpha, \nu)$ with a subgraph of an infinite graph $G_\Pcal(\alpha,\nu)$ (see Section~\ref{ssec:infinite_model}).
+The main idea behind the proof of Theorem \ref{thm:local_clustering_hyperbolic} is to couple the hyperbolic graph $G_{\H, n}(\alpha, \nu)$ with a finite subgraph $G_{\Pcal,n}(\alpha,\nu)$ of an infinite graph $G_\Pcal(\alpha,\nu)$ whose nodes are given by a Poisson Point Process (see Section~\ref{ssec:infinite_model}).
+The infinite graph will then yield the limit expressions for the local clustering coefficient and function.
 A similar approach is used in \cite{fountoulakis2018law} to analyze the size of the largest component in the hyperbolic model and in \cite{komjathy2018explosion} to analyze explosion times in a more general class of models..
@@
 
-Very roughly, the proof falls into three parts: justifying the transitioning from the hyperbolic random graph to the infinite limit model, proving concentration results for local clustering and calculating the expected local clustering coefficient and function in the infinite limit model.
+Very roughly, the proof falls into five parts: 1) replacing the randomly sampled nodes in the hyperbolic graph with a Poisson Point Process, 2) justifying the transitioning from this Poisson version of the hyperbolic random graph to the finite model, 3) proving concentration results for local clustering, 4) show that the limit expression correspond to those in the infinite model and finally 5) calculating the expected local clustering coefficient and function in the infinite limit model.
 
-In this section, we state the required definitions, auxiliary lemmas and propositions and show how to assemble them to obtain Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.
+In this section, we state the required definitions, auxiliary lemmas and propositions and show how to assemble them to obtain Theorem~\ref{thm:local_clustering_hyperbolic}.
 
-\subsection{Infinite limit model}\label{ssec:infinite_model}
+\subsection{Finite box model}\label{ssec:finite_model}
 
-To analyze the limiting expressions for clustering in the hyperbolic random graph $G_{\H,n}(\alpha, \nu)$ we shall use an following infinite graph model which was also considered in~\cite{fountoulakis2018law} to analyze the largest component.
+First we define the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ which we will couple to $G_{\H, n}(\alpha, \nu)$.
+As similar approach was used in~\cite{fountoulakis2018law} to analyze the largest component.
 Define $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and let $\mathcal{P}_{\alpha,\nu}$ be a Poisson point process on $\Rcal$ with intensity function
@@
 
+In addition we denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e. for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
+\begin{equation}\label{eq:def_mu_P}
+	\mu_{\alpha,\nu}(S) = \int_S f_{\alpha,\nu}(x,y) \, dx \, dy,
+\end{equation}
+and for any point $p \in \Rcal$.
+
 We will write $p = (x, y)$ for points in $\Rcal$. Then the \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
@@
 \]
-For a point $p \in \Rcal$, we will write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
-\begin{equation}\label{eq:def_ball_P}
-	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
-\end{equation}
-With this notation we then have that $\BallPo{p} \cap \mathcal{P}$ denotes the set of neighbors of a vertex $p \in G_\Pcal(\alpha,\nu)$.
-We denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e.
-for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
-\begin{equation}\label{eq:def_mu_P}
-	\mu_{\alpha,\nu}(S) = \int_S f_{\alpha,\nu}(x,y) \, dx \, dy,
-\end{equation}
-and for any point $p \in \Rcal$ we let $\eta_p$ be the corresponding probability measure on $\BallPo{p}$ 
-\begin{equation}\label{eq:def_etq_P}
-	\eta_p(S) = \frac{\mu_{\alpha,\nu}(S \cap \BallPo{p})}{\mu_{\alpha,\nu}(\BallPo{p})}.
-\end{equation}
-
-Most of the subsequent analysis in this paper will make use of the~\emph{Campbell-Mecke} formula. 
-For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ we have
-\begin{equation}\label{eq:def_Campbell-Mecke}
-\begin{split}
-& \Exp{\sum_{x_1,\ldots, x_r \in \mathcal{P}}^{\neq} h (x_1, \ldots, x_r,
-\mathcal{P} \setminus \{x_1,\ldots, x_r\}) }\\
-& = \int_S \cdots \int_S
-\Exp{h(x_1,\ldots, x_r,\mathcal{P} \setminus \{x_1,\ldots, x_r\}) \lambda (x_1) \cdots \lambda (x_r) dx_1 \cdots dx_r},
-\end{split}
-\end{equation}
-where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$.
-
-Using the Campbell-Mecke formula we can compute the density of the ball $\BallPo{p}$ as
-\begin{equation}\label{eq:mu_ball_y_P}
-	\mu_{\alpha, \nu}(\BallPo{p}) = \int_0^\infty \int_{-\infty}^\infty \ind{|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}}
-	f_{\alpha,\nu}(x^\prime, y^\prime) \, dx^\prime \, dy^\prime 
-	= \frac{4\alpha \nu}{(2\alpha - 1)\pi} e^{\frac{y}{2}} := \xi_{\alpha,\nu}e^{\frac{y}{2}},
-\end{equation}
-
-We shall use $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(\BallPo{p})$, i.e.
-\[
-	\rho(p,k) = \rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k}.
-\]
-Note that $\rho(y,k)$ denote the probability that a node $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$.
 
@@
 $p_i = (x_i, y_i)$.
+In addition, for a point $p = (x,y)$, we will refer to $y$ as the \emph{height} of $p$.
 \end{remark}
 
-\subsection{Finite box model}
-
-Next we define the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ which we will couple to $G_{\H, n}(\alpha, \nu)$.
-Recall that $R_n = 2\log(n/\nu)$ and that $\Pcal_{\alpha, \nu}$ is a Poisson point process on $\Rcal = \R \times \R_+$, with intensity given by~\eqref{eq:def_intensity_function_f}.
-Now consider the finite box $\Rcal_n = (-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}] \times (0, R_n]$ in $\Rcal$.
+For the definition of the finite graph, recall that $R_n = 2\log(n/\nu)$ and consider the finite box $\Rcal_n = (-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}] \times (0, R_n]$ in $\Rcal$.
 Then the \emph{finite box model} graph $G_{\mathcal{P},n}(\alpha, \nu)$ has vertex set $\mathcal{V}_n := \mathcal{P}_{\alpha, \nu} \cap \Rcal_n$ and edges set such that
@@
 
-Similar to $G_{\Pcal}(\alpha,\nu)$, we define for any $p \in \Rcal_n$, its neighborhood ball
-\[
-	\BallPon{p} = \left\{p^\prime \in \Rcal_n : |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}}\right\}
-\]
-and associated functions $\mu_{\alpha,\nu ,n}$ and $\eta_{p,n}$ and others, by appending an additional subscript $n$. For instance
-\[
-	\mu_{\alpha,\nu,n}(S) = \Mu{S \cap \Rcal_n} \quad \text{and} \quad 
-    \eta_{p,n}(S) = \frac{\mu_{\alpha,\nu ,n}(S \cap \BallPon{p}}{\mu_{\alpha,\nu,n}(\BallPon{p})}
-    = \frac{\Mu{S\cap\BallPon{p}}}{\Mu{\BallPon{p}}}.
-\]
+For a point $p \in \Rcal_n$, we will write $\BallPon{p}$ to denote the \emph{ball} around $p$, i.e.
+\begin{equation}\label{eq:def_ball_P_n}
+	\BallPon{p} = \left\{p^\prime \in \Rcal_n : |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}}\right\}.
+\end{equation}
+With this notation we then have that $\BallPon{p} \cap \PPP$ denotes the set of neighbors of a vertex $p \in G_{\Pcal,n}(\alpha,\nu)$.
 
@@
 The ensuing proposition verifies that this coupling also essentially preserves the local clustering function, i.e.
-that the difference between the local clustering functions in the hyperbolic model and the finite box graph converges to zero faster than the proposed scalings in the main result, Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}.
+that the difference between the local clustering functions in the hyperbolic model and the finite box graph converges to zero faster than the proposed scalings in the main result, Theorem \ref{thm:local_clustering_hyperbolic}.
 Hence, it justifies the transition to the finite box model.
@@
 
-These two results imply that the difference between the local clustering functions in the hyperbolic model and modified version in the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}.
+These two results imply that the difference between the local clustering functions in the hyperbolic model and modified version in the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem \ref{thm:local_clustering_hyperbolic}.
 Hence, to proof this theorem it enough to prove it for $c_{\mathcal{P},n}^\ast(k)$.
+
+\subsection{Infinite limit model}\label{ssec:infinite_model}
+
+To analyze the limiting expressions for clustering in the finite random graph $G_{\Pcal,n}(\alpha, \nu)$ we shall use an infinite graph model which can be understood as taking the finite graph $G_{\Pcal,n}(\alpha,\nu)$ and taking $n \to \infty$.
+Recall that $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and that $\mathcal{P}_{\alpha,\nu}$ is a Poisson point process on $\Rcal$ with intensity function
+\[
+	f_{\alpha,\nu}(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y}.
+\]
+
+The \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
+\[
+	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
+\]
+Similar to the finite graph, we write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
+\begin{equation}\label{eq:def_ball_P}
+	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
+\end{equation}
+
+To analyze expression in the both the finite and infinite model we will make use of the~\emph{Campbell-Mecke} formula. 
+For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ we have
+\begin{equation}\label{eq:def_Campbell-Mecke}
+\begin{split}
+& \Exp{\sum_{x_1,\ldots, x_r \in \mathcal{P}}^{\neq} h (x_1, \ldots, x_r,
+\mathcal{P} \setminus \{x_1,\ldots, x_r\}) }\\
+& = \int_S \cdots \int_S
+\Exp{h(x_1,\ldots, x_r,\mathcal{P} \setminus \{x_1,\ldots, x_r\}) \lambda (x_1) \cdots \lambda (x_r) dx_1 \cdots dx_r},
+\end{split}
+\end{equation}
+where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$.
+
+Using the Campbell-Mecke formula we can compute the density of the ball $\BallPo{p}$ as
+\begin{equation}\label{eq:mu_ball_y_P}
+	\mu_{\alpha, \nu}(\BallPo{p}) = \int_0^\infty \int_{-\infty}^\infty \ind{|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}}
+	f_{\alpha,\nu}(x^\prime, y^\prime) \, dx^\prime \, dy^\prime 
+	= \frac{4\alpha \nu}{(2\alpha - 1)\pi} e^{\frac{y}{2}} := \xi_{\alpha,\nu}e^{\frac{y}{2}},
+\end{equation}
+
+We shall use $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(\BallPo{p})$, i.e.
+\[
+	\rho(p,k) = \rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k}.
+\]
+Note that $\rho(y,k)$ denote the probability that a node $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$, which due to the translation symmetry of the Poisson Point Process in the $x$ direction depends only on the \emph{height} $y$.
+
+\begin{remark}[Degree distributions in the other models]
+Similar to the infinite graph, the degree of a node $p$ in the Poisson hyperbolic graph $G_{\HP,n}$ and the finite random graph $G_{\Pcal,n}$ is distributed as a Poisson random variable with mean $\Mu{\BallHyp{p}}$ and $\Mu{\BallPon{p}}$, respectively.
+Following the notation above we will denote these distributions by $\rho_{\HP,n}(y,k)$ and $\rho_{\Pcal,n}(y,k)$, since these again are independent of the $x$-coordinate of $p$.
+\end{remark}
+
+We can also define a local clustering coefficient and function in this model.
+However, since $G_\Pcal$ has an infinite number of nodes the corresponding definitions are slightly different than for the finite size models.
+Intuitively the local clustering coefficient is the probability that two random neighbors of a randomly sampled node form a triangle, while the local clustering function is the same probability but conditioned on the sampled node having degree $k$.
+
+Again, due to symmetry in the $x$ direction we can assume without loss of generality that a randomly sampled point $p$ is $(0,y)$.
+For any $y \in \R_+$ we define the probability density function on $\Rcal := \R_+ \times \R$ by
+\begin{equation}\label{eq:def_eta_P}
+	\eta_y(x^\prime, y^\prime) = \frac{\ind{p^\prime \in \BallPo{(0,y)}} f_{\alpha,\nu}(x^\prime,y^\prime)}{\mu_{\alpha,\nu}(\BallPo{(0,y)})}.
+\end{equation}
+That is $\eta_y$ is the density $f_{\alpha,\nu}$ restricted to the ball $\BallPo{(0,y)}$, properly normalized.
+Or in other words, it denotes the probability density of a randomly sampled point in $\BallPo{(0,y)}$, i.e.
+a randomly sampled neighbor of $(0,y)$.
+
+We then define
+\begin{equation}\label{eq:def_delta_p}
+	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(y, x_1, x_2, y_1, y_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \dd x_1 \dd x_2  \dd y_1  \dd y_2,
+\end{equation}
+with 
+\[
+	T_\Pcal(y, x_1, x_2, y_1, y_2) 
+	= \ind{|x_1| \, \le \, e^{(y+y_1)/2}}\ind{|x_2| \, \le \, e^{(y+y_2)/2}}\ind{|x_1-x_2| \, \le \, e^{(y_1+y_2)/2}},
+\]
+which is the probability that two randomly sampled points in $\BallPo{(0,y)}$ form a triangle with $(0,y)$.
+
+Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$. \PvdH{Could someone add an intuition or better explanation why this is the case.}
+
+With these expressions we define the limiting local clustering coefficient as
+\begin{equation}\label{eq:def_average_clustering_infinite_model}
+	c_\Pcal := \int_0^\infty \Delta_{\Pcal}(y) (1 - \rho(y,0) - \rho(y,1)) \alpha e^{-\alpha y} \dd y,
+\end{equation}
+while the limiting local clustering function is defined as
+\begin{equation}\label{eq:def_c_infty_k}
+	c_\Pcal(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
+\end{equation}
+
+In Section~\ref{sec:asymptotics_average_clustering_ast_P} we will compute both these quantities and show that $c_\Pcal = c_\infty$ and $c_\Pcal(k) = c_\infty(k)$, where $c_\infty$ and $c_\infty(k)$ are given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}
 
@@
 With this concentration result, we are left with the task to compute the limit of $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$ as $n \to \infty$ and show that it is equivalent to $c_\infty(k_n)$.
-To accomplish this we move to the infinite limit model $G_\Pcal(\alpha,\nu)$.
-The next result shows that the difference between the expected value of the clustering function $c_G^\ast(k)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}.
+To accomplish this we move to the infinite limit model $G_\Pcal(\alpha,\nu)$ and show that the difference between the expected value of the clustering function $c_G^\ast(k)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
 
@@
 \[
-	\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\infty(k_n)\right| = \smallO{s_\alpha(k_n)}.
+	\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\Pcal(k_n)\right| = \smallO{s_\alpha(k_n)}.
 \]
@@
 
-We are now ready to prove our main results, using the propositions stated in the previous sections. We begin with Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}.
+We are now ready to prove our main results, using the propositions stated in the previous sections. We begin with Theorem~\ref{thm:local_clustering_hyperbolic}.
 
-\begin{proof}[Proof of Theorem \ref{thm:asymptotic_local_clustering_hyperbolic}]
+\begin{proof}[Proof of Theorem \ref{thm:local_clustering_hyperbolic}]
 By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
@@
 \begin{proof}[Proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}]
+
+\PvdH{Major errors. FIX!}
+
 First, let $a_n$ be any sequence such that $a_n \to \infty$. Then
@@
 
-Note that Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic} states that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
+Note that Theorem~\ref{thm:local_clustering_hyperbolic} states that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
 \[
@@
 \]
-Then $k_n = \smallO{n^{1/(2\alpha + 1)}}$ and by Theorem~\ref{thm:asymptotic_local_clustering_hyperbolic}
+Then $k_n = \smallO{n^{1/(2\alpha + 1)}}$ and by Theorem~\ref{thm:local_clustering_hyperbolic}
 \[
@@
 \[
-	a_n \arg \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} \to 0.
+	a_n \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} \to 0.
 \]
 
-Then, since $\Exp{N_\Pcal(t)} = \bigT{1}n^{-1} t^{-(2\alpha + 1)}$
+Then, since $\Exp{N_\Pcal(t)} = \bigT{1} t^{-(2\alpha + 1)}$
 \begin{align*}

### 2018-11-02 introduction.tex
Minor update on main results and fixed proof of Theorem 1.1

@@
 \label{thm:local_clustering_hyperbolic}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, 
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n \ge 3$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, 
 \[
@@
 \begin{corollary}[Asymptotic behavior of local clustering function in $G_{\H,n}(\alpha,\nu)$]
+\label{cor:asymptotic_local_clustering_hyperbolic}
 Let $\alpha > \frac{1}{2}$, $\nu > 0$, $(k_n)_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ and $s_\alpha(k)$ defined as in~\eqref{eq:def_scaling_function}.
@@
 
-\paragraph{Transition in the scaling of local clustering}
-%Note that Theorem \ref{thm:local_clustering_hyperbolic} implies that for $\frac{1}{2} < \alpha < \frac{3}{4}$ the local clustering $c_{\H,n}(k)$ decays as $k^{-(4\alpha - 2)}$ while for $\alpha > \frac{3}{4}$ it is $k^{-1}$.
+\paragraph{Uniform convergence}
+
+Our results for the local clustering function in particular imply uniform convergence of $c_{\H,n}(k)$ for all $3 \le k \le a_n$ where $a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. To see this let
+\[
+	b_n = \arg \max_{3 \le k \le a_n} \Exp{\left|\frac{c_{\H ,n}(k)}{c_\infty(k)} - 1\right|}.
+\]
+Then $b_n \le a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ and therefore by Theorem~\ref{thm:local_clustering_hyperbolic}
+\[
+	\lim_{n \to \infty} \max_{3 \le k \le a_n} \Exp{\left|\frac{c_{\H ,n}(k)}{c_\infty(k)} - 1\right|} 
+	= \lim_{n \to \infty}\Exp{\left|\frac{c_{\H ,n}(b_n)}{c_\infty(b_n)} - 1\right|} = 0.
+\]
+The same is true for the result in Corollary~\ref{cor:asymptotic_local_clustering_hyperbolic}.
 
@@
 \end{align*}
-We shall later establish (see Lemma~\ref{lem:N_k_HP_P}) that $\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}$.
+We shall later establish (see Lemma~\ref{lem:N_k_H_P}) that $\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}$.
 Therefore if $k_n$ is such that $k_n^{-(2\alpha + 1)} n$ tends to zero as $n \to \infty$ we have that
@@
 the number of vertices of degree $k_n \gg n^{\frac{1}{2\alpha+1}}$ is zero, such that taking the average over these is not well-defined.
+
+\paragraph{Transition in the scaling of local clustering}
+%Note that Theorem \ref{thm:local_clustering_hyperbolic} implies that for $\frac{1}{2} < \alpha < \frac{3}{4}$ the local clustering $c_{\H,n}(k)$ decays as $k^{-(4\alpha - 2)}$ while for $\alpha > \frac{3}{4}$ it is $k^{-1}$.
 

### 2018-11-02 proof_overview.tex
Minor update on main results and fixed proof of Theorem 1.1

@@
 We can now use this result to prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
+Before we state the proof we summarize some results regarding the degrees in the hyperbolic model.
+The proof of this lemma follows directly from Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson} and Lemma~\ref{lem:N_k_HP_P}, see Section~\ref{sec:coupling_H_P_n}.
+
+\begin{lemma}\label{lem:N_k_H_P}
+Let $\alpha > \frac{1}{2}$ and $k_n$ be a positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then
+\[
+	\lim_{n\to \infty} \Exp{\left|\frac{\Exp{N_{\H,n}(k_n)}}{n \Prob{D_\Pcal = k_n}} - 1\right|} = 0
+\]
+and hence, as $n \to \infty$
+\[
+	\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}.
+\]
+\end{lemma}
 
 \begin{proof}[Proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}]
-
-\PvdH{Major errors. FIX!}
 
@@
 		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
-	&= \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_{\H,n}(t)} c_{\H,n}(t)
+	&= \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t)
 		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}},
 \end{align*}
-where the expectation of last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. We have a similar result for $c_\infty$. Therefore
+where the expectation of last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. Similarly,
+\[
+	c_\Pcal = \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} c_\Pcal(t) + \sum_{t > a_n} \Prob{D_\Pcal = t} c_\Pcal(t)
+\]
+Recall that (see [??]) $c_\infty = c_\Pcal$ and $c_\infty(k) = c_\Pcal(k)$. Therefore
 \begin{align*}
-	\Exp{|c_{\H,n} - c_\infty|}
-	&\le \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}(t) - 	
-		\Exp{N_\Pcal(t)}c_{\infty}(t)\right)\right|}\\ 
+	\Exp{|c_{\H,n} - c_\Pcal|}
+	&\le \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
+		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\ 
 	&\hspace{10pt}+ \Prob{D_{\H,n} > a_n} + \Prob{D_{\Pcal} > a_n},
@@
 \[
-	\lim_{n \to \infty} \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}(t) - 	
-			\Exp{N_\Pcal(t)}c_{\infty}(t)\right)\right|} = 0.
+	\lim_{n \to \infty} \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
+			n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|} = 0.
 \]
@@
 \begin{align*}
-	\Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}(t) - 	
-		\Exp{N_\Pcal(t)}c_{\infty}(t)\right)\right|}
-	&\le \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_\Pcal(t)} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\\
-	&\hspace{10pt}+ \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - N_\Pcal(t)\right|}\Exp{c_\infty(t)},
+	&\hspace{-30pt}\Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
+		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\
+	&\le \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\infty}(t)\right|}\\
+	&\hspace{10pt}+ \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)},
 \end{align*}
@@
 
-Note that Theorem~\ref{thm:local_clustering_hyperbolic} states that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
-\[
-	\lim_{n \to \infty} \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} = 0.
-\]
+Note that Theorem~\ref{thm:local_clustering_hyperbolic} and Lemma~\ref{lem:clustering_ast_H} together state that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
+\begin{equation}\label{eq:convergence_c_H_P}
+	\lim_{n \to \infty} \Exp{\left|c_{\H,n}(k_n) - c_{\Pcal}(k_n)\right|} = 0.
+\end{equation}
 
@@
 \[
-	k_n = \arg \max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}.
+	k_n = \arg \max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|}.
 \]
-Then $k_n = \smallO{n^{1/(2\alpha + 1)}}$ and by Theorem~\ref{thm:local_clustering_hyperbolic}
+Then $k_n = \smallO{n^{1/(2\alpha + 1)}}$ and by~\eqref{eq:convergence_c_H_P}
 \[
-	\max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} = \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} \to 0.
+	\max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|} = \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} \to 0.
 \]
-Similarly we note that
+Similarly we note that by Lemma~\ref{lem:N_k_H_P}
 \[
-	\arg \max_{3 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} \to 0.
+	\max_{3 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
 \]
@@
 \[
-	a_n \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} \to 0.
+	a_n \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
 \]
 
-Then, since $\Exp{N_\Pcal(t)} = \bigT{1} t^{-(2\alpha + 1)}$
+Then, since $\Exp{\Prob{D_\Pcal = t}} = \bigT{1} t^{-(2\alpha + 1)}$
 \begin{align*}
-	&\hspace{-30pt}\frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_\Pcal(t)} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\\
-	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}
+	&\hspace{-30pt}\sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}\\
+	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}
 	= \smallO{1},
 \end{align*}
-while $\Exp{c_\infty(t)} \le 1$ implies that
+while $\Exp{c_\Pcal(t)} \le 1$ implies that
 \begin{align*}
-	&\hspace{-30pt}\frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - N_\Pcal(t)\right|}\Exp{c_\infty(t)} \\
-	&\le \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_\Pcal(t)} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} \\
-	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|} 
-		= \smallO{1}.
+	&\hspace{-30pt}\frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)} \\
+	&\le \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \\
+	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} 
+		\Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} = \smallO{1}.
 \end{align*}

### 2018-11-05 clustering_infinite_model.tex
typo in intro/motivation and missing alphas in section 4.2
Section 4 done (plus some small changes to Section 1.5)

@@
 
-In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\infty$ and $c_{\infty}(k)$, respectively.
-
-We shall first recall some necessary notations for computing the local clustering function in $G_{\Pcal}$ and introduce some new ones.
-
-Recall that for $p\in \R \times \R_+$,
-\[
-	B(p) = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\}.
-\]
-
-Let $T_{\Pcal}(k)$ denote the number of triangles connected to nodes of degree $k$ in $G_{\Pcal}(\alpha, \nu)$, i.e.
-\[
-	T_{\Pcal}(k) = \sum_{p \in \Pcal} \ind{D_\Pcal(p) = k} T(p) = \sum_{p \in \Pcal} \ind{D_\Pcal(p) = k} \sum_{p_1, p_2 \in 2^\Pcal} T(p,p_1,p_2),
-\]
-where $2^{\Pcal}$ is the set of distinct pairs in $\Pcal \times \Pcal$ and
-\[
-	T(p,p_1,p_2) = \ind{p_1 \in B_\Pcal(p)} \ind{p_2 \in B_\Pcal(p)} \ind{p_1 \in B_\Pcal(p_2)},
-\]
-is the indicator that $\{p, p_1, p_2\}$ form a triangle. Then the local clustering function is given by
-\begin{equation}\label{eq:def_local_clustering_P}
-	c_{\Pcal}(k) = \begin{cases} 
-		\frac{T_{\Pcal}(k)}{\binom{k}{2} N_\Pcal(k)} &\mbox{if } N_\Pcal(k) \ge 1\\
-		0 &\mbox{else,}
-		\end{cases}
-\end{equation}
-and the adjusted local clustering by
-\begin{equation}\label{eq:def_local_clustering_ast_P}
-	c_{\Pcal}^\ast(k) = \begin{cases} 
-		\frac{T_{\Pcal}(k)}{\binom{k}{2} \Exp{N_\Pcal(k)}} &\mbox{if } N_\Pcal(k) \ge 1\\
-		0 &\mbox{else,}
-		\end{cases}.
-\end{equation}
-
-To analyze the local clustering we define the conditional expected number of triangles of a vertex $p$ with degree $k$ as
-\[
-	\Delta_{\Pcal}(p,k) = \CExp{\sum_{(p_1, p_2) \in 2^\Pcal} T_\Pcal(p, p_1, p_2)}{D_\Pcal(p) = k}.
-\]
-To compute this expression, let $Z_{1}, Z_{2}$ be two independent random variables on $B_{\Pcal}(p)$, with (marginal) probability measures $\eta_{p} = \frac{\mu|_{B_{\Pcal}(p)}}{\mu(B_{\Pcal}(p))}$.
-Then we define,
-\begin{equation}\label{eq:def_delta_p}
-	\Delta_{\Pcal}(p) = \Prob{ Z_{1} \in \mathcal{B}_{\Pcal}(Z_{2})} %Z_{1} \in \mathcal{B}_{\Pcal}(p), Z_{2} \in \mathcal{B}_{\Pcal}(p),
-\end{equation}
-as the probability that two random neighbors of a point $p \in \mathcal{P}$ are adjacent (note that $\pr = \pr_{\mathcal{P},p}$ denotes the joint probability measure of $Z_1$ and $Z_2$).
-
-We shall often abuse notation and write $\Delta_\Pcal(y)$ to denote $\Delta_\Pcal((0,y))$. %Observe that $\Delta_\Pcal(p)$ is the probability that two random neighbors of $p$ are connected.
-Next we note that conditioned on the Poisson process $\Pcal$ having $k$ points in $\mathcal{B}_{\Pcal}(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$, each with probability measure $\eta_{p}$ and hence
-\[
-	\Delta_{\Pcal}(p,k) = \binom{k}{2} \Delta_\Pcal(p).
-\]
-
-In addition, since $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}}$, with $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{(2\alpha - 1)\pi}$, and
-\[
-	\Delta_{\Pcal}(p) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{p}(x_1,y_1)\eta_{p}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
-\]
-we have that
-\begin{equation}\label{eq:relation_T_vs_Delta_P}
-	\Exp{T_\Pcal(p)} = \xi_{\alpha,\nu}^2 \frac{e^{y}}{2} \Delta_\Pcal(p).
-\end{equation}
-
-\begin{remark}[Notations for the finite graph $G_{\Pcal, n}(\alpha,\nu)$]\label{rmk:notations_clustering_P_n}
-For the finite graph $G_{\Pcal,n}(\alpha, \nu)$ we will use notations similar to those for $G_{\Pcal}(\alpha, \nu)$ where we simply introduce a subscript $n$. For example, 
-\[
-	\Delta_{\Pcal,n}(p) = \pr_{\mathcal{P},p}( Z_{1,n} \in \BallPo{Z_{2,n}}),
-\]
-%Z_{1,n} \in \BallPo{p}, Z_{2,n} \in \BallPo{p},
-where $Z_{1,n}$ and $Z_{2,n}$ are two independent random variables with probability measure \\
-$\eta_{p,n}$.
-\end{remark}
-
-%and define $\epsilon(p_1,p_2)$ to be the indicator that $p_1$ and $p_2$ are neighbors in $G_{\Pcal}(\alpha,\nu)$, i.e.,
-%\[
-%	\epsilon(p_1,p_2) = \begin{cases}
-%		1 &\mbox{if } p_1 \in B(p_2)\\
-%		0 &\mbox{else.}
-%	\end{cases}
-%\]
-%With these definition we then write, 
-%\[
-%	T_\Pcal(p_1,p_2,p_3) = \epsilon_n(p_1,p_2) \epsilon_n(p_2,p_3) \epsilon_n(p_3,p_1),
-%\]
-%to denote the indicator that the tripple $(p_1, p_2, p_3)$ forms a triangle in $G_\Pcal(\alpha,\nu)$ and the triangle counting function as
-%\begin{equation}
-%	T_{\Pcal}(p) = \sum_{p_1, p_2 \in \Pcal} 
-%		\hspace{-5pt} T_\Pcal(p,p_1,p_2).
-%\end{equation}
-%
-%The local clustering function then is
-%\begin{equation}\label{eq:def_local_clustering_P}
-%	c_{\Pcal}(k) = \begin{cases} 
-%		\frac{1}{N_\Pcal(k)}\sum_{p \in \Pcal} \ind{D_\Pcal(p) = k} \frac{T_{\Pcal}(k)}{\binom{k}{2}} &\mbox{if } N_k \ge 1\\
-%		0 &\mbox{else,}
-%		\end{cases}
-%\end{equation}
-%and similarly for $c_{\Pcal}^\ast(k)$.
-%
-%To analyze the local clustering we define the conditional expectation of triangles of a vertex $p$ with degree $k$ as
-%\[
-%	\Delta_{\Pcal}(p,k) = \CExp{\sum_{(p_1, p_2) \in \Pcal} T_\Pcal(p, p_1, p_2)}{p, D_\Pcal(p) = k}.
-%\]
-%To compute this expression, let $Z_{1}, Z_{2}$ be two independent random variables on $B_{\Pcal}(p)$, with probability measure $\eta_{p} = \frac{\mu|_{B_{\Pcal}(p)}}{\mu(B_{\Pcal}(p))}$.
-Then we define,
-%\begin{equation}\label{eq:def_delta_p}
-%	\Delta_{\Pcal}(p) = \CProb{Z_{1} \in B_{\Pcal}(p), Z_{2} \in B_{\Pcal}(p), Z_{1} \in B_{\Pcal}(Z_{2})}{p}
-%\end{equation}
-%We shall often abuse notation and write $\Delta_\Pcal(y)$ to denote $\Delta_\Pcal((0,y))$.
-Observe that $\Delta_\Pcal(p)$ is the probability that two random neighbors of $p$ are connected.
-Next we note that conditioned on the Poisson process $\Pcal$ having $k$ points in $B_{\Pcal}(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$ with probability $\eta_{p}$ and hence
+In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively.
+This is done in several steps.
+Recall that for $p\in \R \times \R_+ := \Rcal$,
+\[
+	\BallPo{p} = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\},
+\]
+denotes the neighborhood ball of $p$. Furthermore we recall the definition of $\Delta_\Pcal$ 
+\[
+	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
+\]
+where $\eta_{y} = \frac{\mu_{\alpha,\nu}|_{\BallPo{(0,y)}}}{\Mu{\BallPo{(0,y)}}}$ is the marginal probability density associated with a randomly sampled neighbor of $(0,y)$.
+
+We already noted that $\Delta_\Pcal(y)$ denotes the probability that two randomly sampled neighbors of $(0,y)$ are connected.
+More precisely, let $Z_{1}, Z_{2}$ be two independent random variables on $\BallPo{(0,y)}$, with (marginal) probability measures $\eta_{y}$.
+Then
+\begin{equation}\label{eq:def_delta_p_alt}
+	\Delta_{\Pcal}(p) = \pr_{\Pcal,p}\left( Z_{1} \in \mathcal{B}_{\Pcal}(Z_{2})\right)
+\end{equation}
+where $\pr_{\Pcal,p}$ denotes the joint probability measure of $Z_1$ and $Z_2$. We shall often abuse notation and write $\Delta_\Pcal(y)$ to denote $\Delta_\Pcal((0,y))$.
+
+%Next we note that conditioned on the Poisson process $\Pcal$ having $k$ points in $\mathcal{B}_{\Pcal}(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$, each with probability measure $\eta_{p}$ and hence
 %\[
@@
 %
-%\begin{remark}[Notations for the finite graph $G_{\Pcal, n}(\alpha,\nu)$]\label{rmk:notations_clustering_P_n}
-%For the finite graph $G_{\Pcal,n}(\alpha, \nu)$ we will use notations similar to those for $G_{\Pcal}(\alpha, \nu)$ where we simply introduce a subscript $n$. For example, 
+%In addition, since $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}}$, with $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{(2\alpha - 1)\pi}$, and
 %\[
-%	\Delta_{\Pcal,n}(p) = \CProb{Z_{1,n} \in \BallPo{p}, Z_{2,n} \in \BallPo{p}, Z_{1,n} \in \BallPo{Z_{2,n}}}{p},
+%	\Delta_{\Pcal}(p) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{p}(x_1,y_1)\eta_{p}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
 %\]
-%where $Z_{1,n}$ and $Z_{2,n}$ are two independent random variables with probability measure \\
-%$\eta_{p,n} = \mu_n|_{\BallPo{p}}/\mu_n(\BallPo{p})$.
-%\end{remark}
+%we have that
+%\begin{equation}\label{eq:relation_T_vs_Delta_P}
+%	\Exp{T_\Pcal(p)} = \xi_{\alpha,\nu}^2 \frac{e^{y}}{2} \Delta_\Pcal(p).
+%\end{equation}
 
@@
 The key ingredient for the proof is a result concerning the asymptotic behavior of $\Delta_\Pcal(y)$ (Proposition \ref{prop:asymptotics_Delta_y_P}) whose proof can be found in Section \ref{ssec:asymptotics_Delta_y_P}.
+The final computations for the exact expressions of $c_\infty$ in Theorem~\ref{thm:clustering_coefficient_hyperbolic} and $c_\infty(k)$ in Theorem~\ref{thm:local_clustering_hyperbolic} can be found in Section~\ref{ssec:exact_expressions_clustering_P}.
 
@@
 \[
-	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y
+	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y
 \]
@@
 \[
-	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) e^{-\alpha y} \dd y
-	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y + \epsilon_1(k).
+	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y + \epsilon_1(k).
 \]
@@
 \begin{equation}\label{eq:asymptotics_clustering_integral}
-	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y 
-	\sim \xi_{\alpha,\nu}^{6\alpha - 2} k^{-(6\alpha - 1)},
+	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y 
+	\sim 2\alpha \xi_{\alpha,\nu}^{6\alpha - 2} k^{-(6\alpha - 1)},
 \end{equation}
@@
 \begin{align*}
-	c_\infty(k) &= \frac{\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) e^{-\alpha y} \dd y}
-		{\int_0^\infty \rho_{y}(k) e^{-\alpha y} \dd y} \\
-	&\sim C_\alpha \xi_{\alpha,\nu}^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
-	+ \frac{\epsilon_1(k)}{\xi_{\alpha,\nu}^{2\alpha} k^{-(2\alpha - 1)}}\\
-	&= C_\alpha \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2} 
-    + \xi_{\alpha,\nu}^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
+	c_\infty(k) &= \frac{\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
+	&\sim C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
+	+ \frac{\epsilon_1(k)}{2\alpha \xi_{\alpha,\nu}^{2\alpha} k^{-(2\alpha - 1)}}\\
+	&= C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2} 
+    + \frac{1}{2\alpha}\xi_{\alpha,\nu}^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
 \end{align*}
@@
 \begin{align*}
-	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
-	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
+	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
+	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
 	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
-    	\rho(y,k) e^{-\alpha y} \dd y.
+    	\rho(y,k) \alpha e^{-\alpha y} \dd y.
 \end{align*} 
@@
 	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
-    	\rho(y,k) e^{-\alpha y} \dd y\\
+    	\rho(y,k) \alpha e^{-\alpha y} \dd y\\
 	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
-    	\rho(a(k), k) \int_0^\infty e^{-\alpha y} \dd y = 0.
+    	\rho(a(k), k) \int_0^\infty \alpha e^{-\alpha y} \dd y = 0.
 \end{align*}
@@
 \[
-	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
+	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
 \] 
@@
 	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
-    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
+    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
 	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
-    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y = 0,
+    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = 0,
 \end{align*}
@@
 \[
-	g(y) := \left(\alpha -\frac{1}{2}\right) e^{-(\alpha-\frac{1}{2})y_1}
-\] 
-and then sampling $x_i$ uniformly in $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$.
+	g(y_i) := \left(\alpha -\frac{1}{2}\right) e^{-(\alpha-\frac{1}{2})y_i}
+\] 
+and then sampling $x_i$ uniformly in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$.
 With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ form a triangle where $x_1$ and $x_2$ are uniform random variables in, respectively, $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.
@@
 \begin{align*}
-	I_1(y_0) &:= \int_{0<y_0<y_1<y_2} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)}  {\dd} y_2 {\dd} y_1 \\ 
-	I_2(y_0) &:= \int_{0<y_1<y_0,y_2} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)} {\dd} y_2 {\dd} y_1 \\ 
+	I_1(y_0) &:= \int_{0<y_0<y_1<y_2} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)}  \dd y_2 \dd y_1 \\ 
+	I_2(y_0) &:= \int_{0<y_1<y_0,y_2} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)} \dd y_2 \dd y_1 \\ 
 \end{align*}
@@
 We want to compute the limit $\lim_{\alpha \rightarrow 1} \Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0))$.
-For this, after factoring out $\frac{1}{\alpha-1}$ we compute the first two terms of the Taylor expansion of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ in $\alpha$ based at $\alpha = 1$.
+For this, after factoring out $\frac{1}{\alpha-1}$ in the expression for $\Delta_{\Pcal}(y)$ we obtained for $\alpha \ne 1$, we compute the first two terms of the Taylor expansion of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ in $\alpha$ based at $\alpha = 1$.
 The constant term of this Taylor expansion is verified to vanish whereas the linear term gives the expression searched (after cancellation with $\frac{1}{\alpha-1}$).
@@
 
-The first summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
-\begin{align*}
--\frac{1}{8 \alpha} = -\frac{1}{8}+\frac{1}{8}(\alpha-1) +O( (\alpha-1)^2)
+The first summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ is,
+\begin{align*}
+	S_1 = -\frac{1}{8 \alpha} = -\frac{1}{8}+\frac{1}{8}(\alpha-1) +O( (\alpha-1)^2)
 \end{align*}
@@
 \begin{align*}
-(\alpha-1/2)z_0 = \frac{1}{2}z_0 +z_0 (\alpha-1)+O( (\alpha-1)^2)
+	S_2 = (\alpha-1/2)z_0 = \frac{1}{2}z_0 +z_0 (\alpha-1)+O( (\alpha-1)^2)
 \end{align*}
@@
 \begin{align*}
-- \frac{(\alpha - 1/2)^2 z_0^2}{4} = -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+O( (\alpha-1)^3)
+	S_3 = - \frac{(\alpha - 1/2)^2 z_0^2}{4} = -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+O( (\alpha-1)^3)
 \end{align*}
@@
 \begin{align*}
-z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha} &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
+	S_4 = z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha} &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
 &\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+O( (\alpha-1)^3)
@@
 \end{align*}
-The fifth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
-\begin{align*}
-	&\hspace{-30pt}z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha} \\
+For the fifth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ we get,
+\begin{align*}
+	S_5 &= z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha} \\
 	&= \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
@@
 \begin{align*}
-\frac{(1 - z_0)^{2 \alpha}}{8 \alpha} = \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1)+O( (\alpha-1)^2 )
-\end{align*}
-The seventh and last summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
-\begin{align*}
-- \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4} = -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
+	S_6 = \frac{(1 - z_0)^{2 \alpha}}{8 \alpha} = \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1)+O( (\alpha-1)^2 )
+\end{align*}
+and finally the seventh and last summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ gives,
+\begin{align*}
+	S_7 = - \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4} = -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
 \left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+O((\alpha-1)^2)
@@
 
-We see that the constant coefficients cancel:
-\begin{align*}
-&-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) +\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
+When adding these terms we see that the constant coefficients cancel:
+\begin{align*}
+& -\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) +\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
 &=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 -\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 \\ &\hspace{10pt}+\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 =0
@@
 \end{align*}
-This finishes the computation.
+which finishes the computation.
 
@@
 
-\subsection{Exact expression for clustering, integrating $\Delta_{\Pcal}(y)$}
-
-%\PvdH{@Markus: Please check that your $\xi$ equals $\xi_{\alpha,\nu} := \frac{4\alpha \nu}{(2\alpha - 1)\pi}$ in all computations below. If not please adjust the computations.}
-%Markus: yes, this is the right xi.
-
-\PvdH{This part is still in the original form and has to be converted to match style and notation.}
-
-Now that we have an expression for $\Delta_{\Pcal}(y)$ we can compute the limit local clustering coefficient $c_\infty$ and the limit local clustering function $c_\infty(k)$, i.e.
-prove Theorem~\ref{thm:exact_expression_c_infty} and Theorem~\ref{thm:exact_expression_local_clustering}.
-
-First we recall that
-\begin{align*}
-p_k := \Pee( D=k ) = \int_0^\infty e^{-\xi e^{y/2}} \frac{(\xi e^{y/2})^k}{k!}\alpha e^{-\alpha y} dy = 2\alpha \int_0^1 e^{-\frac{\xi}{z}} z^{2\alpha -k-1} dz =\frac{2\alpha \xi^{2\alpha}}{k!} \Gamma(k-2\alpha,\xi)
-\end{align*}
-%\PvdH{@Markus: This result is taken from your notes. It seems to disagree with~\eqref{eq:degree_distribution_P}. Could you please check the other computations.}
-
-We wish to compute
-\[   
-	c_\infty = \alpha \int_0^{\infty} \Delta_\Pcal(y) e^{-\alpha y} \left(1-e^{-\xi e^{y/2}} - \xi e^{y/2} 
-	e^{-\xi e^{y_0/2}}\right) \dd y, 
-\]
-
-\noindent
+\subsection{Exact expressions for the local clustering coefficient and function, integrating $\Delta_{\Pcal}(y)$}\label{ssec:exact_expressions_clustering_P}
+
+Now that we have an expression for $\Delta_{\Pcal}(y)$ we can compute the limit local clustering coefficient $c_\Pcal$ and the limit local clustering function $c_\Pcal(k)$ and prove that they equal $c_\infty$ and $c_\infty(k)$ given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}.
+
+First we recall that $\rho(y,k) = (\xi_{\alpha,\nu} e^{y/2})^k/k! \, e^{-\xi_{\alpha,\nu} e^{y/2}}$ and
+\begin{align*}
+	\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y = \frac{2\alpha \xi^{2\alpha}}{k!} \Gamma(k-2\alpha,\xi)
+	:= \rho(k).
+\end{align*}
+We also define
+\[
+	I^{(k)} := \int_0^{\infty} \Delta_\Pcal(y) \alpha e^{-\alpha y} \frac{\left(\xi e^{y/2}\right)^k}{k!} e^{-\xi e^{y/2}} \dd y
+\]
 and
-
-\[ I^{(k)} := 
-\int_0^{\infty} P(y_0) \alpha e^{-\alpha y_0} \frac{\left(\xi e^{y_0/2}\right)^k}{k!} e^{-\xi e^{y_0/2}} {\dd} y_0. \]
-
-\noindent
-(So $c = I$ and $c(k) = I^{(k)} / p_k $ for $k\geq 2$.) \\
-Note that the integral for $I$ can be written as $J - I^{(0)} - I^{(1)}$ where
-
-\[ J := \int_0^{\infty} P(y_0) \alpha e^{-\alpha y_0} {\dd} y_0. \]
-
-\noindent
-Note that, of course, the integrals $I^{(0)}$ and $I^{(1)}$ can be computed even though $c(0)$ and $c(1)$ are technically
-speaking not well-defined.
-
-\noindent
-It seems helpful to change coordinates to $z_0 := e^{-y_0/2}$.
-This gives ${\dd} y_0 = \REMOVEME{-}2 z_0^{-1} {\dd} z_0$, $e^{-\alpha y_0} = z_0^{2\alpha}$.
-Hence
-
-\[ J = 2 \alpha \int_0^1 P(y_0(z_0)) \cdot z_0^{2\alpha-1} {\dd} z_0, \]
-
-\noindent
+\[
+	J := \int_0^\infty \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y.
+\]
+
+Then
+\[   
+	c_\Pcal = J - I^{(1)} - I^{(2)} \quad \text{and} \quad
+	c_\Pcal(k) = \frac{I^{(k)}}{\rho(k)}
+\]
+and hence we first need to compute $J$ and $I^{(k)}$.
+
+For this it will be helpful to change coordinates to $z := e^{-y/2}$. This yields 
+\[ 
+	J = 2 \alpha \int_0^1 \Delta_\Pcal(y) z^{2\alpha-1} \dd z, 
+\]
 and 
-
-\[ I^{(k)} = \frac{2 \alpha \xi^k}{k!} \cdot \int_0^1 P(y_0(z_0)) \cdot z_0^{2\alpha-(k+1)} e^{-\xi/z_0} {\dd} z_0. \]
-
-\noindent
-Given the expression(s) we got for $P(y_0)$, we firstly deal with the case $\alpha \not = 1$.
-% As $J_\alpha$ and $I_\alpha^{(k)}$ (and hence also $c_\alpha$ and $c_\alpha(k)$) are continuous in $\alpha$ by the dominated convergence theorem, we will later obtain the result for $\alpha=1$ by taking the limit $\alpha \rightarrow 1$.
-
-\noindent
-Now we recall that for $\alpha \not =1$, $P(y_0(z_0))$ is in fact a linear combination of terms of the form $z_0^u$, $(1-z_0)^u$ and $z_0^u B^-(1-z_0,v,w)$, so we only need to compute the integrals $J$ and $I^{(k)}$ for these forms.
-
-\vspace{1em}
-
-\noindent
-To work out $J$ we just need to observe that 
-\[ \begin{array}{rcl} 
-\int_0^1 z_0^{u+2\alpha-1} B^-(1-z_0;v,w) {\dd} z_0 
-& = & 
-\left[ \frac{z_0^{u+2\alpha}}{u+2\alpha} B^-(1-z_0;v,w) \right]_0^1 
-+ \frac{1}{u+2\alpha} \int_0^1 z_0^{u+2\alpha+w-1} (1-z_0)^{v-1} {\dd} z_0 \\
-& = & 
-\frac{1}{u+2\alpha} B(u+w+2\alpha,v)
-\end{array} \]
-\noindent
-(using that $\frac{\partial}{\partial z_0} B^-(1-z_0;v,w) = - z_0^{w-1} (1-z_0)^{v-1}$.)
-
-This gives the expression for $J$ (note that it only depends on $\alpha$ but not on $\nu$)
-
+\[ 
+	I^{(k)} = \frac{2 \alpha \xi_{\alpha,\nu}^k}{k!} \cdot \int_0^1 P(y(z)) \cdot z^{2\alpha-(k+1)} e^{-\xi_{\alpha,\nu} z^{-1}} \dd z. 
+\]
+
+We first deal with the case $\alpha \not = 1$.
+We observe from Proposition~\ref{prop:full_expression_delta_P} that for $\alpha \not =1$, $\Delta_\Pcal(y(z))$ is in fact a linear combination of terms of the form $z^u$, $(1-z)^u$ and $z_0^u B^-(1-z_0,v,w)$.
+
+To compute $J$ we observe that, by partial integration, 
+\begin{align*}
+	\int_0^1 z^{u+2\alpha-1} B^-(1-z;v,w) \dd z 
+	&= \left[ \frac{z^{u+2\alpha}}{u+2\alpha} B^-(1-z;v,w) \right]_0^1 
+		+ \frac{1}{u+2\alpha} \int_0^1 z^{u+2\alpha+w-1} (1-z)^{v-1} \dd z \\
+	&= \frac{1}{u+2\alpha} B(u+w+2\alpha,v)
+\end{align*}
+where we used that $\frac{\partial}{\partial z} B^-(1-z;v,w) = - z^{w-1} (1-z)^{v-1}$.
+This takes care of the two integrands involving the Beta function in $\Delta_\Pcal(y)$.
+The other integrals are easily computed and yield the following expression for $J$ (note that it only depends on $\alpha$ but not on $\nu$)
 \begin{align*}
@@
 
-%\begin{figure}
-%	\centering
-%	\includegraphics[scale=0.6]{0817J}
-%	\caption{Plot of $J(\alpha)$ for $\alpha$ between 0.5 and 5 \REMOVEME{(and any $\nu$)}.}
-%\end{figure}
-
-\vspace{1em}
-
-\noindent
-To work out $I^{(k)}$ we first point out that
-
-\[ \begin{array}{rcl} 
-\int_a^b z_0^{u+2\alpha-(k+1)} e^{-\xi z_0^{-1}} {\dd} z_0
-& = & 
-\xi^{u+2\alpha-k} \int_{\xi/b}^{\xi/a} t^{k-1-2\alpha-u} e^{-t} {\dd} t \\
-& = & 
-\xi^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u;\xi/\REMOVEME{b}) - \Gamma^+( k-2\alpha-u; \xi/\REMOVEME{a}) \right), 
-\end{array} \]
-\REMOVEME{
+We proceed to work out $I^{(k)}$.
+For this we will compute the integrals involving terms in $\Delta_\Pcal(y(z))$ of the form $z^u$, $(1-z)^u$ and $B(1-z,v,w)$ separately.
+We first point out that for any $0 \le a < b \le 1$
+\begin{align*}
+	\int_a^b z^{u+2\alpha-(k+1)} e^{-\xi_{\alpha,\nu} z^{-1}} \dd z
+	&= \xi_{\alpha,\nu}^{u+2\alpha-k} \int_{\xi_{\alpha,\nu}/b}^{\xi_{\alpha,\nu}/a} t^{k-1-2\alpha-u} e^{-t} \dd t \\
+	&= \xi_{\alpha,\nu}^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u;\xi_{\alpha,\nu}/b) - \Gamma^+( k-2\alpha-u; \xi_{\alpha,\nu}/a) \right), 
+\end{align*}
 In particular
-\begin{align*}
-\int_0^1 z_0^{u+2\alpha-k-1} e^{-\xi z_0^{-1}} {\dd} z_0 = \xi^{u+2\alpha-k} \Gamma^+(k-2\alpha-u;\xi)
-\end{align*}}
-
-\noindent
+\begin{equation}\label{eq:integral_Delta_P_z}
+	\int_0^1 z^{u+2\alpha-k-1} e^{-\xi_{\alpha,\nu} z^{-1}} \dd z = \xi_{\alpha,\nu}^{u+2\alpha-k} \Gamma^+(k-2\alpha-u;\xi_{\alpha,\nu})
+\end{equation}
 where $\Gamma^+$ denotes the (upper) incomplete gamma function, and we've used the subsitution
-$t = \xi / z_0$ which gives ${\dd} z_0 = -\xi t^{-2} {\dd} t$. (And of course it is understood that 
-$\xi/0 = \infty$.)
-
-The hypergeometric U-function 
-(also called Tricomi's confluent hypergeometric function) has the integral representation 
-$$U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} dt$$ which holds for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $Re(a), Re(z) >0$, see \cite[p.255]{erdelyi1953higher}.
-Applying the change of variables
-$t=\frac{1-s}{s}$ (i.e. $dt = -s^{-2} ds$ and $s = \frac{1}{t+1}$) yields the integral 
-$\int_1^0 e^{-z(-1+\frac{1}{s})} (\frac{1-s}{s})^{a-1} (\frac{1}{s})^{b-a-1} (-s^2)ds = e^z\int_0^1 e^{-z/s} s^{-b}(1-s)^{a-1} ds$, i.e.
+$t = \xi_{\alpha,\nu} / z$ which gives $\dd z = -\xi_{\alpha, \nu} t^{-2} \dd t$. (And of course it is understood that 
+$\xi_{\alpha,\nu}/0 = \infty$). This takes care of the integrals of all terms in $\Delta_\Pcal(y(z))$ of the form $z^{u}$.
+
+Next we will consider the integrals over the terms in $\Delta_\Pcal(y(z))$ of the form $(1-z)^u$.
+For this we need the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which has the integral representation
+\[
+	U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} \dd t
+\] 
+which holds for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $Re(a), Re(z) >0$, see~\cite[p.255]{erdelyi1953higher}.
+Applying the change of variables $t=\frac{1-s}{s}$ (i.e.
+$\dd t = -s^{-2} \dd s$ and $s = \frac{1}{t+1}$) yields
+%yields the integral 
+%$\int_1^0 e^{-z(-1+\frac{1}{s})} (\frac{1-s}{s})^{a-1} (\frac{1}{s})^{b-a-1} (-s^2)ds = e^z\int_0^1 e^{-z/s} s^{-b}(1-s)^{a-1} ds$, i.e.
 \begin{align*}
@@
 \end{align*}
-Plugging in $a=2\alpha+1 >0$, $b=-2\alpha+k+1$, $z=\xi>0$, gives
-\begin{align*}
-\int_0^1 z_0^{2\alpha-k-1} e^{-\xi/z_0} (1-z_0)^{2\alpha} dz_0 = \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi)
-\end{align*}
-
-Let $a, c \in \R$, $\xi, b >0$ positive real numbers. 
+Plugging in $a=2\alpha+1 >0$, $b=-2\alpha+k+1$, $z=\xi_{\alpha,\nu}>0$, then gives
+\begin{equation}\label{eq:integral_Delta_P_1_z}
+	\int_0^1 z_0^{2\alpha-k-1} e^{-\xi_{\alpha,\nu}/z_0} (1-z_0)^{2\alpha} dz_0 = \Gamma(2\alpha+1)e^{-\xi_{\alpha,\nu}} U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu})
+\end{equation}
+
+Finally we need to deal with the terms in $\Delta_\Pcal(y(z))$ that involve the incomplete Beta-function.
+Let $a, c \in \R$, $\xi_{\alpha,\nu}, b >0$ positive real numbers.
 Using the integral definition of the incomplete B-function, the change of variables $s=1-t$ gives:
 \begin{align*}
-\int_0^1 z^a e^{-\xi/z} B^-(1-z;b,c) dz &=\int_0^1 z^a e^{-\xi/z} \int_0^{1-z} t^{b-1} (1-t)^{c-1} dt dz \\
-&=\int_0^1 z^a e^{-\xi/z} \int_z^1 s^{c-1} (1-s)^{b-1} ds dz
-\end{align*}
-Then changing the order of integration and using the substitution $u = \xi/z$  and recognizing the upper incomplete $\Gamma$-function yields
-\begin{align*}
-&=\int_0^1 \int_0^s z^a e^{-\xi/z} dz s^{c-1} (1-s)^{b-1} ds \\
-&=\int_0^1 \int_{\xi/s}^\infty \xi^{a+1} u^{-a-2} e^{-u} du s^{c-1} (1-s)^{b-1} ds \\
-&= \xi^{a+1} \int_0^1 \Gamma^+(-a-1,\xi/s) s^{c-1} (1-s)^{b-1} ds
-\end{align*}
-Now, the incomplete $\Gamma$-function has a representation in terms of Meijer's $G$-function $$\Gamma^+(-a-1,\xi/s) = \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}}$$ which holds for any $a\in \R$ and $s>0$ (see appendix; note that for a fixed second argument, the upper incomplete $\Gamma$-function is entire in the first argument, see \cite[pp.
+	\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} B^-(1-z;b,c) \dd z 
+	&=\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} \int_0^{1-z} t^{b-1} (1-t)^{c-1} \dd t \dd z \\
+	&=\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} \int_z^1 s^{c-1} (1-s)^{b-1} \dd s \dd z
+\end{align*}
+Then changing the order of integration and using the substitution $u = \xi_{\alpha,\nu}/z$  and recognizing the upper incomplete $\Gamma$-function yields
+\begin{align*}
+	&\hspace{-30pt}\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} \int_z^1 s^{c-1} (1-s)^{b-1} \dd s \dd z\\
+	&=\int_0^1 \int_0^s z^a e^{-\xi_{\alpha,\nu}/z} \dd z \, s^{c-1} (1-s)^{b-1} \dd s \\
+	&=\int_0^1 \int_{\xi_{\alpha,\nu}/s}^\infty \xi_{\alpha,\nu}^{a+1} u^{-a-2} e^{-u} \dd u \, s^{c-1} (1-s)^{b-1} \dd s \\
+	&= \xi_{\alpha,\nu}^{a+1} \int_0^1 \Gamma^+(-a-1,\xi_{\alpha,\nu}/s) s^{c-1} (1-s)^{b-1} \dd s.
+		\numberthis \label{eq:integral_gamma_function}
+\end{align*}
+To compute this last integral we make use of the fact that the incomplete $\Gamma$-function has a representation in terms of Meijer's $G$-function (see Lemma~\ref{lem:gamma_meijer_G} in Appendix~\ref{sec:Meijer_G_functions})
+\[
+	\Gamma^+(-a-1,\xi_{\alpha,\nu}/s) = \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi_{\alpha,\nu}}{s}},
+\] 
+which holds for any $a\in \R$ and $s>0$ (that for a fixed second argument, the upper incomplete $\Gamma$-function is entire in the first argument, see \cite[pp.
 899, 1032ff.]{gradshteyn2015table}).
-Therefore, we get the integral
-
+\PvdH{@Markus:What does entire mean?}
+We can now evaluate the integral in~\eqref{eq:integral_gamma_function} using several identities for Meijer's $G$-function. 
 %formula 8.351.3, p. 
  %(see the wolfram functions website \url{http://functions.wolfram.com/06.06.26.0005.01}, it can also be found in the paper \url{https://arxiv.org/pdf/1507.05571}; , so we get the integral
-\begin{align*}
-= \xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}}ds
-\end{align*}
-applying the inversion identity for Meijer's $G$-function (see \cite[p. 209, 5.3.1.(9))]{erdelyi1953higher})
-\begin{align*}
-=\xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{0}{2}{2}{1}{2+a,1}{0}{\frac{s}{\xi}}ds
-\end{align*}
-This is the Euler transform of Meijer's $G$-function (see \cite[p.
-214, 5.5.2.(5)]{erdelyi1953higher}) and (as the conditions $2+1<2(0+2)$ and $|\arg(\xi^{-1})| < \frac{\pi}{2}$ (as $\xi>0$) and $1-c-b<1-c$ (as $b>0$)  are satisfied) equals
-\begin{align*}
-=\xi^{a+1} \Gamma(b) \MeijerG{0}{3}{3}{2}{1-c,2+a,1}{0,1-c-b}{\xi^{-1}}
-\end{align*}
-Using again the inversion identity for Meijer's $G$-function
-\begin{align*}
-=\xi^{a+1} \Gamma(b) \MeijerG{3}{0}{2}{3}{1,b+c}{c,-1-a,0}{\xi}
-\end{align*}
-Plugging in $a= 6\alpha-k-3$, $b=2\alpha$, $c=3-4\alpha$ results in
-\begin{align*}
-=\xi^{6a-k-2} \Gamma(2\alpha) \MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}
-\end{align*}
+First, inserting the expression for the incomplete Gamma-function into~\eqref{eq:integral_gamma_function} gives
+\begin{align*}
+	\xi_{\alpha,\nu}^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi_{\alpha,\nu}}{s}} \dd s
+\end{align*}
+Next we apply the inversion identity for Meijer's $G$-function (see \cite[p. 209, 5.3.1.(9))]{erdelyi1953higher}) to get
+\begin{align*}
+	\xi_{\alpha,\nu}^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{0}{2}{2}{1}{2+a,1}{0}{\frac{s}{\xi_{\alpha,\nu}}} \dd s
+\end{align*}
+This expression is actually the Euler transform of Meijer's $G$-function (see \cite[p.
+214, 5.5.2.(5)]{erdelyi1953higher}) and (as the conditions $2+1<2(0+2)$ and $|\arg(\xi_{\alpha,\nu}^{-1})| < \frac{\pi}{2}$ (as $\xi_{\alpha,\nu}>0$) and $1-c-b<1-c$ (as $b>0$)  are satisfied) it equals
+\begin{align*}
+	\xi_{\alpha,\nu}^{a+1} \Gamma(b) \MeijerG{0}{3}{3}{2}{1-c,2+a,1}{0,1-c-b}{\xi_{\alpha,\nu}^{-1}}
+\end{align*}
+Using again the inversion identity for Meijer's $G$-function we now get
+\begin{align*}
+	\xi_{\alpha,\nu}^{a+1} \Gamma(b) \MeijerG{3}{0}{2}{3}{1,b+c}{c,-1-a,0}{\xi_{\alpha,\nu}}
+\end{align*}
+Finally, plugging in $a= 6\alpha-k-3$, $b=2\alpha$, $c=3-4\alpha$ we obtain
+\begin{equation}\label{eq:integral_Delta_P_Beta}
+	\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} B^-(1-z;b,c) \dd z =
+	\xi_{\alpha,\nu}^{6a-k-2} \Gamma(2\alpha) \MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi_{\alpha,\nu}}
+\end{equation}
 %(note that this agrees with the result in the old approach, after `bringing the power of $\xi$ into Meijer's $G$-function'.)
 
-This allows us to write:
-\begin{align*}
-I^{(k)}&=\frac{\xi^{2\alpha}}{4k!(\alpha-1)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
-&\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
-&\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
-      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
-&\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
-&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
+Using equation~\eqref{eq:integral_Delta_P_z}, \eqref{eq:integral_Delta_P_1_z} and~\eqref{eq:integral_Delta_P_Beta} we get
+\begin{align*}
+	I^{(k)}
+	&=\frac{\xi_{\alpha,\nu}^{2\alpha}}{4k!(\alpha-1)} \left( -\Gamma^+(k - 2 \alpha, \xi_{\alpha,\nu}) 
+		- 2\frac{\alpha (\alpha - 1/2)^2 \xi_{\alpha,\nu}^{2} \Gamma^+(k - 2 \alpha - 2, \xi_{\alpha,\nu})}{(\alpha - 1)} \right. \\ 
+	&\hspace{15pt}\left.+ 8 \alpha (\alpha - 1/2) \xi_{\alpha,\nu} \Gamma^+(k - 2 \alpha - 1,\xi_{\alpha,\nu}) \right.\\ 
+	&\hspace{15pt}\left.+ 4\xi_{\alpha,\nu}^{4\alpha - 2} 
+		\Gamma^+(k - 6 \alpha + 2, \xi_{\alpha,\nu}) \left( 
+		\frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
+	&\hspace{15pt}\left.+ \xi_{\alpha,\nu}^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi_{\alpha,\nu}} 	
+		U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu}) \right. \\ 
+	&\hspace{15pt}\left.- \xi_{\alpha,\nu}^{4\alpha-2} 
+		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi_{\alpha,\nu}}  \right)\\
 \end{align*}%{4\alpha-k+1,6\alpha-k-1}{6\alpha-k-2,2\alpha-k+1,0}
 
-Finally, we compute 
-\begin{align*}
-p_k := \Pee( D=k ) = \int_0^\infty e^{-\xi e^{y/2}} \frac{(\xi e^{y/2})^k}{k!}\alpha e^{-\alpha y} dy = 2\alpha \int_0^1 e^{-\frac{\xi}{z}} z^{2\alpha -k-1} dz =\frac{2\alpha \xi^{2\alpha}}{k!} \Gamma(k-2\alpha,\xi)
-\end{align*}
-%and thus
-%\begin{align*}
-%\GR{p_{\geq 2}} := \Pee( D \geq 2 ) = 1-2\alpha\xi^{2\alpha}(\Gamma(-2\alpha,\xi)-\Gamma(1-2\alpha,\xi))
-%\end{align*}
-and we can write down the average clustering coefficient
-
-\begin{align*}
-c &= J-I^{(0)}-I^{(1)} \\
+With the expressions for $J$ and $I^{(k)}$ and using $\Gamma^\ast(q,z) = \Gamma^+(q+1,z) + \Gamma^+(q,z)$ we now obtain, after some algebra, the expression for $c_\Pcal$
+\begin{align*}
+	c_\Pcal &= J-I^{(0)}-I^{(1)} \\
 	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 
@@
 		4 \alpha}}{(\alpha - 1)^2} \\
-	&\qquad+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
+	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
 	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)} \\
-	&\qquad-\frac{\xi^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+( - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(- 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
-&\qquad\qquad\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+( - 2 \alpha - 1,\xi) \right.\\ 
-&\qquad\qquad\left.+ 4\xi^{4\alpha - 2} \Gamma^+( - 6 \alpha + 2, 
+	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+( - 2 \alpha, \xi_{\alpha,\nu}) - 2\frac{\alpha (\alpha - 1/2)^2 \xi_{\alpha,\nu}^{2} \Gamma^+(- 2 \alpha - 2, \xi_{\alpha,\nu})}{(\alpha - 1)} \right.
+\\
+	&\hspace{10pt}\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi_{\alpha,\nu} \Gamma^+( - 2 \alpha - 1,\xi_{\alpha,\nu}) \right.\\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ 4\xi_{\alpha,\nu}^{4\alpha - 2} \Gamma^+( - 6 \alpha + 2, 
+      \xi_{\alpha,\nu}) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ \xi_{\alpha,\nu}^{-2\alpha} \Gamma(2\alpha+1)e^{-\xi_{\alpha,\nu}} 
+		U(2\alpha+1,1-2\alpha,\xi_{\alpha,\nu}) \right. \\ 
+	&\hspace{10pt}\hspace{10pt}\left.- \xi_{\alpha,\nu}^{4\alpha-2} 
+		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi_{\alpha,\nu}}  \right) \\
+	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+(1 - 2 \alpha, \xi_{\alpha,\nu}) - 
+		2\frac{\alpha (\alpha - 1/2)^2 \xi_{\alpha,\nu}^{2} \Gamma^+( - 2 \alpha - 1, \xi_{\alpha,\nu})}{(\alpha - 1)} \right. \\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi_{\alpha,\nu} \Gamma^+(1 - 2 \alpha - 1,\xi_{\alpha,\nu}) 
+		\right.\\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ 4\xi_{\alpha,\nu}^{4\alpha - 2} \Gamma^+(1 - 6 \alpha + 2, 
+    	\xi_{\alpha,\nu}) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ \xi_{\alpha,\nu}^{1-2\alpha} \Gamma(2\alpha+1)e^{-\xi_{\alpha,\nu}} 
+		U(2\alpha+1,2-2\alpha,\xi_{\alpha,\nu}) \right. \\ 
+	&\hspace{10pt}\hspace{10pt}\left.- \xi_{\alpha,\nu}^{4\alpha-2} 
+		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi_{\alpha,\nu}}  \right)\\
+	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}
+		{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} 
+		+  \frac{2^{-1 - 4 \alpha}}{(\alpha - 1)^2} \\
+	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}
+		{2 (\alpha - 1) (3 \alpha - 1)} \\
+	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{2\alpha} \Gamma^\ast( - 2 \alpha, \xi_{\alpha,\nu})}{4(\alpha-1)}
+		+ \frac{\xi_{\alpha,\nu}^{2\alpha + 2}\alpha (\alpha - 1/2)^2 \Gamma^\ast(- 2 \alpha - 2, \xi_{\alpha,\nu})}
+		{2(\alpha-1)^2} \\
+	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{2\alpha + 1}\alpha (2\alpha - 1) \Gamma^\ast( - 2 \alpha - 1,\xi_{\alpha,\nu})}{(\alpha-1)}
+		- \frac{\xi_{\alpha,\nu}^{6\alpha-2}2^{-4\alpha}(3\alpha - 1)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)^2}\\
+	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{6\alpha - 2}(\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)} \\
+	&\hspace{10pt}- \frac{e^{-\xi_{\alpha,\nu}} \Gamma(2\alpha+1) 
+		\left(U(2\alpha+1,1-2\alpha,\xi_{\alpha,\nu}) + U(2\alpha+1,2-2\alpha,\xi_{\alpha,\nu})\right)}{4(\alpha-1)} \\
+	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{6\alpha - 2} \Gamma(2\alpha+1)\left( 	
+		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi_{\alpha,\nu}}
+		+ \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi_{\alpha,\nu}}\right)}{4(\alpha-1)}.
+\end{align*}
+and note that this equals $c_\infty$ in Theorem~\ref{thm:clustering_coefficient_hyperbolic} when $\alpha \ne 1$.
+
+Similarly, we get
+\begin{align*}
+	c_\Pcal(k) &= \frac{I^{(k)}}{\rho(k)} \\
+	&=\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) 
+		- 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
+	&\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
+	&\hspace{10pt}\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
       \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
-&\qquad\qquad\left.+ \xi^{-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1-2\alpha,\xi) \right. \\ 
-&\qquad\qquad\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi}  \right) \\
-&\qquad-\frac{\xi^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+(1 - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+( - 2 \alpha - 1, \xi)}{(\alpha - 1)} \right. \\ 
-&\qquad\qquad\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(1 - 2 \alpha - 1,\xi) \right.\\ 
-&\qquad\qquad\left.+ 4\xi^{4\alpha - 2} \Gamma^+(1 - 6 \alpha + 2, 
-      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
-&\qquad\qquad\left.+ \xi^{1-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,2-2\alpha,\xi) \right. \\ 
-&\qquad\qquad\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi}  \right)
-\end{align*}
-
+	&\hspace{10pt}\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
+	&\hspace{10pt}\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right),
+\end{align*}
+which equals $c_\infty(k)$ in Theorem~\ref{thm:local_clustering_hyperbolic} when $\alpha \ne 1$.
+
+Finally, to determine the value of $c_\Pcal$ and $c_\Pcal(k)$ for $\alpha=1$, it suffices to find the value of $J$ and $I^{(k)}$ at $\alpha = 1$.
+We can do this by computing the integrals with the expression for $\Delta_\Pcal(y)$ that we found for $\alpha=1$, i.e.
+\begin{align*}
+	J &= 2\alpha\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) - \frac{7+\pi^2}{8}
+		z^2  + \frac{1}{2}z^2 \Li_2(z)\right) z^{2\alpha -1} \dd z \\
+	&=\frac{575-12\pi^2}{576}
+\end{align*}
 and 
 \begin{align*}
-c(k) = \frac{I^{(k)}}{p_k} &=\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right.
-\\
-&\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
-&\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
-      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
-&\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
-&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
-\end{align*}
-
-To determine the value of $c$ and $c(k)$ for $\alpha=1$, it suffices to find the value of $J$ and $I^{(k)}$ at $\alpha = 1$. 
-We can do this by computing those integrals with the expression for $P(y_0)$ that we found for $\alpha=1$, i.e.
-\begin{align*}
-J &= 2\alpha\int_0^1 \left(\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
-z_0^2  + 
-\frac{1}{2}z_0^2 \Li_2(z)\right) z_0^{2\alpha -1} dz_0 \\
-&=\frac{575-12\pi^2}{576}
-\end{align*}
-and 
-\begin{align*}
-I^{(k)} &= \frac{2\alpha \xi^k}{k!}\int_0^1 \left(\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
-z_0^2  + 
-\frac{1}{2}z_0^2 \Li_2(z) \right)z_0^{2\alpha-k-1} e^{-\xi/z_0} dz_0 \\
-&= \frac{2 \eta^k}{k!}\int_0^1 \left(\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
-z_0^2  + 
-\frac{1}{2}z_0^2 \Li_2(z) \right)z_0^{1-k} e^{-\eta/z_0} dz_0 \\
+	I^{(k)} &= \frac{2\alpha \xi_{\alpha,\nu}^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
+		- \frac{7+\pi^2}{8}	z^2  + \frac{1}{2}z^2 \Li_2(z) \right)z^{2\alpha-k-1} e^{-\xi_{\alpha,\nu}/z} \dd z \\
+	&= \frac{2 \eta^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
+		- \frac{7+\pi^2}{8} z^2  + \frac{1}{2}z^2 \Li_2(z) \right)z^{1-k} e^{-\eta/z} \dd z \\
 	&= \frac{9 \eta^k}{2 k!}\eta^{3-k}\Gamma^+(k-3,\eta)-\frac{\eta^k}{k!}\frac{7+\pi^2}{4}\eta^{4-k}\Gamma^+(k-4,\eta)\\
-&+\frac{\eta^k}{2k!}\int_0^1 (1-4z_0+3z_0^2)\ln(1-z_0)z_0^{1-k}e^{-\eta/z_0}dz_0+\frac{\eta^k}{k!}\int_0^1 z_0^{3-k} \Li_2(z) e^{-\eta/z_0}dz_0 \\
+	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}dz+\frac{\eta^k}{k!}\int_0^1 z^{3-k} 
+		\Li_2(z) e^{-\eta/z} \dd z \\
 	&=\frac{9 \eta^3}{2 k!}\Gamma^+(k-3,\eta)-\frac{\eta^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
-&+\frac{\eta^k}{2k!}\int_0^1 (1-4z_0+3z_0^2)\ln(1-z_0)z_0^{1-k}e^{-\eta/z_0}dz_0+\frac{\eta^k}{k!}\int_0^1 z_0^{3-k} \Li_2(z) e^{-\eta/z_0}dz_0
-\end{align*}
-where $\eta = \frac{4\nu}{\pi}$.
+	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}dz+\frac{\eta^k}{k!}\int_0^1 z^{3-k} 
+		\Li_2(z) e^{-\eta/z} \dd z
+\end{align*}
+where $\eta = \frac{4\nu}{\pi}$ and and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function.
+Plugging this into the definitions for $c_\Pcal$ and $c_\Pcal(k)$ yields the expressions $c_\infty$ in Theorem~\ref{thm:clustering_coefficient_hyperbolic} and $c_{\infty}(k)$ in Theorem~\ref{thm:local_clustering_hyperbolic}, respectively.

### 2018-11-05 concentration.tex
fully merged compations of Nikolaos plus some small edits on section 2
Section 4 done (plus some small changes to Section 1.5)

@@
 \begin{proof}[Proof of Proposition \ref{prop:concentration_tilde_T_P_n}]
+
+\PvdH{Include the case $k_n = \bigT{1}$.}
+
 The technical steps of this proof use Lemma \ref{lem:joint_degree_distribution_shift} and Lemma \ref{lem:joint_degree_distribution_P_n}, which deal with the joint degree distribution.
@@
 
-The proofs for the other two cases $I_{0,2}^\ast$ and $I_{0,2}^\ast$ follows similar arguments.
+The proofs for the other two cases $I_{0,2}^\ast$ and $I_{0,2}^\ast$ follow using similar arguments.
 
@@
 \end{proof}
-
-\PvdH{Stopped here with general pass}
 

### 2018-11-05 introduction.tex
typo in intro/motivation and missing alphas in section 4.2
Section 4 done (plus some small changes to Section 1.5)

@@
 However, since this term is more often associated in the literature with the density of triangles compared to the number of paths of length 2, we use the term local clustering coefficient as is done, for instance, in~\cite{candellero2016clustering}.} is concentrated around its expectation which is shown to be $\bigT{1}$ as the number of vertices tends to infinity.
-In particular this results implies that the local clustering coefficient is asymptotically bounded away from zero.
+In particular this result implies that the local clustering coefficient is asymptotically bounded away from zero.
 The convergence of this coefficient was not proven.
@@
 
-The majority of the paper is dedicated to prove Theorem~\ref{thm:local_clustering_hyperbolic}, which is based on a sequence of subsequent results for the local clustering function in related random graph models and Theorem~\ref{thm:asymptotics_average_clustering_P}.
+A major part of this paper is dedicated to prove the convergence result in Theorem~\ref{thm:local_clustering_hyperbolic}, which is based on a sequence of subsequent results for the local clustering function in related random graph models and Theorem~\ref{thm:asymptotics_average_clustering_P}.
 The exact flow of the argument is explained in Section \ref{sec:proof_outline}.
-The proof for Theorem~\ref{thm:local_clustering_hyperbolic}, using these results, can be found in Section \ref{ssec:proof_main_results}.
-Here we also give the proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
-The proof of Theorem~\ref{thm:asymptotics_average_clustering_P} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
+The proof for the convergence result in Theorem~\ref{thm:local_clustering_hyperbolic}, using these results, can be found in Section \ref{ssec:proof_main_results}.
+Here we also give the proof of the convergence result in Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
+Another major part of this paper is the exact computation of the local clustering coefficient and function limit $c_\infty$ and $c_\infty(k)$, which involves careful computations of several involved integrals.
+This is done in Section~\ref{sec:asymptotics_average_clustering_ast_P}, where we also prove Theorem~\ref{thm:asymptotics_average_clustering_P}.
 
@@
 \PvdH{Populate these paragraphs}
+
+\paragraph{Local clustering function for growing versus fixed degrees}
 
@@
 
-\paragraph{Transition in the scaling of local clustering}
+%\paragraph{Transition in the scaling of local clustering}
 %Note that Theorem \ref{thm:local_clustering_hyperbolic} implies that for $\frac{1}{2} < \alpha < \frac{3}{4}$ the local clustering $c_{\H,n}(k)$ decays as $k^{-(4\alpha - 2)}$ while for $\alpha > \frac{3}{4}$ it is $k^{-1}$.
 
-\paragraph{Universality of scaling transition}
+%\paragraph{Universality of scaling transition}
 
-\paragraph{Geometric inhomogeneous random graphs}
-
-%\paragraph{Local clustering for growing versus fixed degrees}
-%%The main difference between Theorem \ref{thm:fixed_local_clustering_hyperbolic} and Theorem \ref{thm:local_clustering_hyperbolic} is that for fixed degrees $k$ we have a small correction term that depends on the value $k$.
-%
-%\MS{We note that the above statements / theorems are disjoint: in one case the degree is fixed corresponding to a constant sequence and in this case the error only depends on $n$, whereas in the other case, the degrees are assumed to be increasing, so in particular unbounded resp.
-tending to infinity and only the leading term in the asymptotic expansion w.r.t.
-$k_n \rightarrow \infty$ is given.
-This allows to study vertices of relatively high degree, e.g.
-close to the maximum degree (note that there are a.a.s.
-no vertices with degree exactly the expected maximum degree of $k_n = n^{\frac{1}{2\alpha}}$).}
-
-%The main difference between Theorem \ref{thm:fixed_local_clustering_hyperbolic} and Theorem \ref{thm:local_clustering_hyperbolic} is that for fixed degrees $k$ we have a small correction term that depends on the value $k$.
+%\paragraph{Geometric inhomogeneous random graphs}
 

### 2018-11-05 paper.tex
cleaned up proof of Theorem 1.5 and realigned formulas in section 4.5
Started merging Nikolaos results into paper
merged more of Nikoloas' computations into paper.
Section 4 done (plus some small changes to Section 1.5)

@@
 \newcommand{\eps}{\varepsilon}						%	varepsilon
-\DeclareMathOperator{\dd}{\, \mathrm{d}\hspace{-1pt}}			%	straight d for integration
+\DeclareMathOperator{\dd}{\mathrm{d}\hspace{-2pt}}			%	straight d for integration
 
@@
 \newcommand{\Po}[0]{\ensuremath{{\mathrm{Po}}}}		%	Poisson random variable
+\newcommand{\PPP}{\ensuremath{\Pcal_{\alpha, \nu}}}	%	Poisson Point Process
 
 \newcommand{\T}{\ensuremath{T}}						%	Symbol for triangles
+
+\newcommand{\dom}[1]{\mathcal{D}_{#1}}
 
@@
 \newcommand{\EdgeDiff}{E_{\H \setminus \mathcal{P}}}
-\newcommand{\expH}{\overline{n}_{\H}(k_n)}
+\newcommand{\expH}{\overline{n}_{\HP}(k_n)}
 \newcommand{\expP}{\overline{n}_{\Pcal}(k_n)}
+\newcommand{\Pop}[2]{\mathrm{Po} (#2;#1)}
+\newcommand{\Nsymdiff}{N_{\H \bigtriangleup \Pcal}(k_n)}
 
@@
 
-\PvdH{Below is a list of high and low level to do items. Please add comments using the commands below.
-
-\noindent Comment commands:\\
-Markus: \textbackslash MS\\
-Nikolaos: \textbackslash NF\\
-Pim: \textbackslash PvdH\\
-Tobias: \textbackslash TM
-
-}
-
-\ToDo{High level list:
-
-\begin{itemize}
-\item Streamline notations and writing of some sections
-\item Finish introduction
-\item Complete bibliography list
-\item Add additional explanation for the Hyperbolic model.
-\item Add additional observations based on our main result
-\end{itemize}
-}
-
 \newpage

### 2018-11-05 proof_overview.tex
Section 4 done (plus some small changes to Section 1.5)

@@
 Here we also prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
-The proof of Theorem~\ref{thm:asymptotics_average_clustering_P} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
+The proof of Theorem~\ref{thm:asymptotics_average_clustering_P} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P} where we also derive the exact expressions for $c_\infty$ and $c_\infty(k)$.
 
@@
 \end{align*}
-This finishes the proof.
+This finishes the first part of the proof. The second part, which derives the exact expression for $c_\Pcal$ can be found in [??] \PvdH{Add reference to section.}
 \end{proof}

### 2018-11-06 proof_overview.tex
explanation for exponential density on page 15

@@
 
-Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$. \PvdH{Could someone add an intuition or better explanation why this is the case.}
+Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$: the distribution function of the radial coordinate of a vertex sampled in the disk is $\frac{\cosh(\alpha  r)-1}{\cosh(\alpha R)-1}$ which is asymptotically equivalent to $e^{\alpha(r-R)} = e^{-\alpha y}$, if $r$ and $R$ are large, resp.
+tending to infinity and $y=R-r$ and because of the minus sign in front of the $r$, the distribution function in $r$ turns into the complementary distribution function of $y$, from which we recognize the exponential distribution with parameter $\alpha$.%\PvdH{Could someone add an intuition or better explanation why this is the case.}
 

### 2018-11-12 introduction.tex
a couple of comments in section 1

@@
 
-\MS{Here, I would just say that $B(a,b)$ denotes the beta function $B^-(x,a,b)$ the lower incomplete beta function etc.
+%\MS{Here, I would just say that $B(a,b)$ denotes the beta function $B^-(x,a,b)$ the lower incomplete beta function etc.
 and put/refer to the integral representations in the appendix, as already done for the Meijer-G function.}
@@
 
-Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to as constant $c_\infty$, which we can explicitly write down in terms of the special function defined above.
+Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to a constant $c_\infty$, which we can explicitly write down in terms of the special functions defined above.
 
 \begin{theorem}[Limit for local clustering coefficient in $G_{\H,n}(\alpha,\nu)$] \label{thm:clustering_coefficient_hyperbolic}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then,
+Let $\alpha > \frac{1}{2}$, $\nu > 0$, and $\xi_{\alpha,\nu} = \frac{4\alpha \nu}{\pi(2\alpha -1)}$. Then,
 \[
@@
 \label{thm:local_clustering_hyperbolic}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n \ge 3$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, 
+Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\xi = \frac{4\alpha\nu}{\pi(2\alpha-1)}$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n \ge 3$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
+Then,
 \[
@@
 			\frac{3 \nu}{\pi} &\mbox{if } \alpha = \frac{3}{4},\\
-			\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha \ge \frac{3}{4},
+			\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha > \frac{3}{4},
 	\end{cases}
@@
 				\frac{3\nu}{\pi} &\mbox{if } \alpha = \frac{3}{4},\\
-				\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha \ge \frac{3}{4},
+				\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha > \frac{3}{4},
 		\end{cases}
 \]
-where $\stackrel{L^1}{\to}$ denotes converges in expectation.
+where $\stackrel{L^1}{\to}$ denotes convergence in expectation.
 \end{corollary}
+\MS{Are you sure all constants are correct? I thought for $\alpha = 3/4$ it might be $6\nu/\pi$. But if you are sure, you can remove this comment of course.}
 
@@
 \paragraph{Local clustering function for growing versus fixed degrees}
+\MS{I'm currently not sure what we should comment here because now Thm 1.2 does cover both cases and the asymptotics in 1.4 appear as a very natural corollary.
+
+However, if we can, then it would be interesting to remark that there is this phase transition in $\alpha$ which appears when the power-law exponent is $2.5=\frac{5}{2}$ and it would be cool if we could give a brief intuitive reason for that or mention that this phase transition point has also been observed in other contexts/models etc.}
 

### 2018-11-14 proof_overview.tex
typos in section 2

@@
 The infinite graph will then yield the limit expressions for the local clustering coefficient and function.
-A similar approach is used in \cite{fountoulakis2018law} to analyze the size of the largest component in the hyperbolic model and in \cite{komjathy2018explosion} to analyze explosion times in a more general class of models..
+A similar approach is used in \cite{fountoulakis2018law} to analyze the size of the largest component in the hyperbolic model and in \cite{komjathy2018explosion} to analyze explosion times in a more general class of models.
 The advantage of the infinite limit model is two-fold.
-First, it simplifies the actual computations, e.g.
+Firstly, it simplifies the actual computations, e.g.
 by replacing hyperbolic densities with exponential densities and the hyperbolic distance with a computationally easier expression.
@@
 
-First we define the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ which we will couple to $G_{\H, n}(\alpha, \nu)$.
-As similar approach was used in~\cite{fountoulakis2018law} to analyze the largest component.
-Define $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and let $\mathcal{P}_{\alpha,\nu}$ be a Poisson point process on $\Rcal$ with intensity function
+First of all we define the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ which we will couple to $G_{\H, n}(\alpha, \nu)$.
+A similar approach was used in~\cite{fountoulakis2018law} to analyze the largest component.
+Define $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and let $\mathcal{P}=\mathcal{P}_{\alpha,\nu}$ be a Poisson point process on $\Rcal$ with intensity function
 \begin{equation}\label{eq:def_intensity_function_f}
@@
 For this we define $G_{\HP,n}(\alpha, \nu)$ to be the hyperbolic random graph where the vertex set is given by $N \stackrel{d}{=} \Po(n)$ points, distributed according to the $(\alpha, R_n)$-quasi uniform distribution~\eqref{eq:def_hyperbolic_point_distribution} defined in Section \ref{ssec:hyperbolic_model}.
-The following two lemmas from \cite{fountoulakis2018law} establishes a coupling between this version of the hyperbolic random graph and the finite box model and relate the hyperbolic neighborhoods to the neighborhood balls $\BallPo{p}$.
+The following two lemmas from \cite{fountoulakis2018law} establish a coupling between this version of the hyperbolic random graph and the finite box model and relate the hyperbolic neighborhoods to the neighborhood balls $\BallPo{p}$.
 The ensuing proposition verifies that this coupling also essentially preserves the local clustering function, i.e.
-that the difference between the local clustering functions in the hyperbolic model and the finite box graph converges to zero faster than the proposed scalings in the main result, Theorem \ref{thm:local_clustering_hyperbolic}.
+that the difference between the local clustering function in the hyperbolic model and the finite box graph converges to zero faster than the proposed scalings in the main result, Theorem \ref{thm:local_clustering_hyperbolic}.
 Hence, it justifies the transition to the finite box model.
@@
 \]
-Note that we have that $\BallHyp{p} \subseteq \mathcal{R}_n$. In particular, a point $p = (x,y) \in \Rcal$ corresponds to $u := \Psi^{-1}(p) = (2 e^{R_n/2} x, R_n - y)$.
+Note that we have that $\BallHyp{p} \subseteq \mathcal{R}_n$. In particular, a point $p = (x,y) \in \Rcal$ corresponds to $u := \Psi^{-1}(p) = (2 e^{-R_n/2} x, R_n - y)$.
 
 Let $u, u^\prime \in \Dcal_R$.
-The hypebolic law of cosines implies that $d_{\H}(u,u^\prime) < R_n$ if and only if their relative angle $\theta(u, u^\prime) := |\theta - \theta^\prime|_{2\pi}$ satisfies $\theta(u, u^\prime) < \theta_{R_n}(r,r^\prime)$, where $\theta_{R_n}(r,r^\prime)$ is the solution of the following equation
+The hyperbolic law of cosines implies that $d_{\H}(u,u^\prime) \leq R_n$ if and only if their relative angle $\theta(u, u^\prime) := |\theta - \theta^\prime|_{2\pi}$ satisfies $\theta(u, u^\prime) \leq \theta_{R_n}(r,r^\prime)$, where $\theta_{R_n}(r,r^\prime)$ is the solution of the following equation
 \[
@@
 \end{equation}
-Then $d_{\H}(u,u^\prime) < R_n$ if and only if $\theta(u, u^\prime) \leq 2 e^{-R_n/2}\Omega(r,r^\prime)$.
+Then $d_{\H}(u,u^\prime) \leq R_n$ if and only if $\theta(u, u^\prime) \leq 2 e^{-R_n/2}\Omega(r,r^\prime)$.
 Under the coupling map $\Psi$, this is equivalent to $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$.
@@
 \begin{equation}\label{eq:tail_inclusion_hyperbolic_ball}
-	r^\prime \leq y = R_n - r \Rightarrow d_H (\Psi^{-1}(p),u^\prime) \leq R_n.
+	r^\prime \leq y = R_n - r \Rightarrow d_{\H} (\Psi^{-1}(p),u^\prime) \leq R_n.
 \end{equation}
@@
 This coupling is however not exact and hence we need to compute the difference in triangle counts between the two models.
-For this, and other computations later on, it will be more convenient to consider the following slight modified version of local clustering,
+For this, and other computations later on, it will be more convenient to consider the following slight modified version of the local clustering function,
 \begin{equation}\label{eq:def_local_clustering_ast_general}
@@
 
-First we show that considering this adjusted version doesn't change anything in terms of the scaling, the proof is given in Section~\ref{ssec:coupling_H_HP}.
+The following lemma justifies working with this modified version, for the proof see Section~\ref{ssec:coupling_H_HP}.
 
@@
 
-We then establish that the adjusted local clustering function in the hyperbolic model $G_{\H,n}(\alpha,\nu)$ behaves similar to that in the Poisson version $G_{\HP, n}(\alpha,\nu)$.
+We then establish that the modified local clustering function in the hyperbolic model $G_{\H,n}(\alpha,\nu)$ behaves similarly to that in the Poisson version $G_{\HP, n}(\alpha,\nu)$.
 
@@
 \end{proposition}
+\MS{I think we can drop the condition to be increasing here and below, also the $n^{1/3}$ should be removed.}
 
-The next step is to show that the modified clustering isn't influenced by the coupling describe above. The proof can be found in Section~\ref{ssec:coupling_HP_ast_P}.
+The next step is to show that the modified clustering is preserved under the coupling described above. The proof can be found in Section~\ref{ssec:coupling_HP_ast_P}.
 
@@
 
-These two results imply that the difference between the local clustering functions in the hyperbolic model and modified version in the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem \ref{thm:local_clustering_hyperbolic}.
-Hence, to proof this theorem it enough to prove it for $c_{\mathcal{P},n}^\ast(k)$.
+These two results imply that the difference between the local clustering function of the hyperbolic random graph and the modified local clustering function of the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem \ref{thm:local_clustering_hyperbolic}.
+Hence, to prove this theorem it is enough to prove it for $c_{\mathcal{P},n}^\ast(k)$.
 

### 2018-11-14 concentration_argument.tex
updated Section 3

--- 2018-10-18 concentration_argument.tex
@@
 
-Many of the computations in this paper will involve integrals where the integrand contains $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$ and $\mu_n(y) \approx e^{y/2}$.
+Many of the computations in this paper will involve integrals whose integrand contains $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$ and $\mu_n(y) \approx e^{y/2}$.
 For instance, the expected adjusted local clustering function $c_\infty(k)$ in $G_\Pcal$ equals
 \[
-	\frac{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \Delta_{\Pcal}(y) e^{-\alpha} \dd y}
-	{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} e^{-\alpha} \dd y},
+	\frac{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \Delta_{\Pcal}(y) \alpha e^{-\alpha} \dd y}
+	{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \alpha e^{-\alpha} \dd y},
 \]
@@
 
-In particular, the average degree of a node at height $y$ is approximately Poisson with mean $\xi_{\alpha,\nu} e^{y/2}$ while we are interested in those nodes with degree $k_n$.
-Since Poisson random variables are well concentrated around their mean, for our analysis we would therefore like to be able the integration to intervals where $e^{y/2} \approx k_n$.
+In particular, we already established that the degree of a node at height $y$ in the infinite model is Poisson with mean $\xi_{\alpha,\nu} e^{y/2}$.
+Since we are mostly interested in those nodes with degree $k_n$ and Poisson random variables are well concentrated around their mean, we would therefore like to be able the restrict integration to intervals where $e^{y/2} \approx k_n$.
 Moreover, we want to be able to do this for all three Poisson models $G_{\HP,n}$, $G_{\Pcal,n}$ and $G_\Pcal$ as well as simultaneously deal with the case where $k_n \to \infty$ and $k_n = \bigT{1}$.
@@
 
-Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with mean $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$. 
+Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with mean $\mu_{\alpha, \nu}(B_\Pcal(y)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$. 
 For any sequence $\{k_n\}_{n \ge 1}$, possibly constant, define
@@
 \end{equation}
-Note that if $k_n = \Omega(\log(n))$ then $e^{y/2} = \bigT{k_n}$ whenever $p \in \Kcal_C(k_n)$. The next lemma states that for a large class of functions $h(y)$ to compute the integral 
+Note that if $k_n = \Omega(\log(n))$ then $e^{y/2} = \bigT{k_n}$ whenever $p \in \Kcal_C(k_n)$. The next lemma states that for a large class of functions $h(y)$, to compute the integral 
 \[
@@
 it is enough to consider integration of $\Kcal_C(k_n)$ instead of $\Rcal_n$.
+More precisely, for any $\ell_n = (1 + \smallO{1})k_n$ it is enough to consider $\Kcal_C(\ell_n)$.
+The flexibility of using $(1+\smallO{1})k_n$ instead of $k_n$ will prove useful in later sections.
 
 \begin{lemma}\label{lem:concentration_argument}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $\{k_n\}_{n \ge 1}$ be any sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$.
-In addition let $\beta < \alpha$ and $h : \R_+ \mapsto \R$ be a any function such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$.
-Then, for any $C > 0$,
+Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\{k_n\}_{n \ge 1}$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$.
+In addition let $\beta < \alpha$ and $h : \R_+ \mapsto \R$ be a any function such that $h(y) = g(y)e^{\beta y}$ with $|g(y)|$ uniformly bounded on $\R_+$.
+Then, if we define for $C > 0$
+\[
+	\lambda_n^\pm = \ell_n \pm C \kappa_n, 
+	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right),
+\] 
+we have
 \begin{equation}\label{eq:error_bound_int_rho_not_K}
 \begin{aligned}
-	&\hspace{-30pt} \int_{\Rcal_n \setminus \Kcal_{C}(k_n)} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y\\
+	\int_{\R_+ \setminus [a_n^-, a_n^+]} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd x \dd y
 	&= \begin{cases}
-		\bigO{n^{1 - \frac{C}{2}}} &\mbox{if } k_n = \bigT{1} \\
-		\bigO{n \left(k_n^{-(1+C^2)/2} + k_n^{-1/2} e^{-\frac{C\sqrt{k_n \log(k_n)}}{2}}\right)} &\mbox{else.}
+		\bigO{\log(n)^{k_n} n^{-\frac{C}{2}}} &\mbox{if } k_n = \bigT{1} \\
+		\bigO{k_n^{-(1+C^2)/2}} &\mbox{else.}
 	\end{cases}
@@
 
-In particular, if $g_n(y)$ is a function such that $g_n(y) = \bigO{n^{-1} k_n^{\beta}}\rho(y,k_n)$ for some $s \in \R$. Then for $C > 0$ large enough we have
+In particular, if $h_n(y)$ is a function such that $h_n(y) = \bigO{n^{-1} k_n^{s} e^{\beta y}}\rho(y,k_n)$ for some $s \in \R$ and $\beta < \alpha$ as $n \to \infty$.
+Then for $C > 0$ large enough we have
 \[
-	\lim_{n \to \infty} \int_{\Rcal_n \setminus \Kcal_{C}(k_n)} g_n(y) f_{\alpha,\nu}(x,y) \dd x\dd y = 0,
+	\lim_{n \to \infty} \int_{\Rcal_n \setminus \Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x\dd y = 0,
 \]
@@
 \[
-	\int_{\Rcal_n} \hspace{-5pt} g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y
-	= (1+\smallO{1}) \int_{\Kcal_{C}(k_n)} \hspace{-5pt} g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
+	\int_{\Rcal_n} \hspace{-5pt} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y
+	= (1+\smallO{1}) \int_{\Kcal_{C}(\ell_n)} \hspace{-5pt} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
 \]
@@
 \begin{proof}
-Define 
+Note that in this case
 \[
-	\lambda_n^\pm = k_n \pm C \kappa_n, 
-	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right).
+	\kappa_n := \begin{cases}
+		\log(n) &\mbox{if } k_n = \bigT{1},\\
+		\sqrt{\ell_n \log(\ell_n)} &\mbox{else.}
+	\end{cases}
 \]
-Then, since $\rho_{y}(k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$
+Then, since $a_n^- < k_n$ and $a_n^+ > k_n$, $\rho_{y}(k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$.
+Therefore, by our assumption on $h(y)$,
 \begin{align*}
-	&\hspace{-20pt}\int_{\Rcal_n \setminus \Kcal_C(k_n)} h(y) \rho_{k_n}(y) 
-		f_{\alpha,\nu}(x,y) \dd x \dd y\\
-    &= \bigO{1} \int_0^{a_n^-} \int_{-I_n}^{I_n} e^{\beta y} \rho_{k_n}(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
-    	+ \int_{a_n^+}^{R_n} \int_{-I_n}^{I_n} e^{\beta y} \rho_{k_n}(y) f_{\alpha,\nu}(x,y) \dd x \dd y \\
-    &= \bigO{n} \int_0^{a_n^-} \rho_{k_n}(y) e^{-(\alpha-\beta) y} \dd y 
-   		+ \bigO{n} \int_{a_n^+}^{R_n} \rho_{k_n}(y) e^{-(\alpha-\beta) y} \dd y\\
-   	&\le \bigO{n}\rho(a_n^-,k_n)\int_0^{a_n^-} e^{-(\alpha-\beta) y} \, \dd y
-   		+ \bigO{n} \rho(y,a_n^+) \int_{a_n^+}^{R_n} e^{-(\alpha-\beta) y} \, \dd y.
+	&\hspace{-20pt}\int_{\R_+ \setminus [a_n^-, a_n^+]} h(y) \rho_{k_n}(y) 
+		\alpha e^{-\alpha y} \dd y\\
+    &= \bigO{1} \int_0^{a_n^-} e^{\beta y} \rho_{k_n}(y) \alpha e^{-\alpha y} \dd y 
+    	+ \bigO{1}\int_{a_n^+}^{R_n} e^{\beta y} \rho_{k_n}(y) \alpha e^{-\alpha y}x \dd y \\
+    &= \bigO{1} \int_0^{a_n^-} \rho_{k_n}(y) e^{-(\alpha-\beta) y} \dd y 
+   		+ \bigO{1} \int_{a_n^+}^{R_n} \rho_{k_n}(y) e^{-(\alpha-\beta) y} \dd y\\
+   	&\le \bigO{1}\rho(a_n^-,k_n)\int_0^{a_n^-} e^{-(\alpha-\beta) y} \, \dd y
+   		+ \bigO{1} \rho(y,a_n^+) \int_{a_n^+}^{R_n} e^{-(\alpha-\beta) y} \, \dd y.
 \end{align*}
-Note that if $k_n = \bigT{1}$ then, for large enough $n$, the first integral is zero, it is $O(1)$ when $k_n \to \infty$. Because $\alpha > \beta$ the second integral is always $\bigO{1}$. Therefore
-
+Note that if $k_n = \bigT{1}$ then, for large enough $n$, the first integral is zero. We conclude that
 \begin{equation}\label{eq:concentration_lemma_integral_bound}
 \begin{aligned}
-	&\hspace{-30pt}\int_{\Rcal_n \setminus \Kcal_C(k_n)} h(y) \rho_{k_n}(y) f_{\alpha,\nu}(x,y) \dd x \dd y \\
+	\int_{\R_+ \setminus [a_n^-, a_n^+]} h(y) \rho_{k_n}(y) \alpha e^{-\alpha y} \dd y
 	&= \begin{cases}
-		\bigO{n} \rho(a_n^+,k_n) &\mbox{if } k_n = \bigT{1},\\
-		\bigO{n} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right) &\mbox{else.}
+		\bigO{1} \rho(a_n^+,k_n) &\mbox{if } k_n = \bigT{1},\\
+		\bigO{1} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right) &\mbox{else.}
 	\end{cases}	
@@
 
-We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^-,k_n)$.
-Note we only need to bound $\rho(a_n^-,k_n)$ when $k_n \to \infty$, in which case $\kappa_n = \sqrt{k_n \log(k_n)}$.
-Using that $k!
-> \sqrt{2\pi} k^{k + 1/2} e^{-k}$ we write
+We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^+,k_n)$.  Using that $k! > \sqrt{2\pi} k^{k + 1/2} e^{-k}$ we write
 \begin{align*}
-	\rho(a_n^-,k_n) &\le \frac{\mu(a_n^-)^{k_n}}{k_n!} e^{-\mu(a_n^-)} 
-		\le (2\pi)^{-1/2} k_n^{-(k_n + 1/2)} e^{-(\mu(a_n^-) - k_n)}\\
+	\rho(a_n^+,k_n) &\le \frac{\Mu{\BallPo{a_n^+}}^{k_n}}{k_n!} e^{-\Mu{\BallPo{a_n^+}}} \\
+	&\le (2\pi)^{-1/2} k_n^{-1/2} \left(\frac{\Mu{\BallPo{a_n^+}}}{k_n}\right)^{k_n} e^{-(\Mu{\BallPo{a_n^+}} - k_n)}\\
 	&= (2\pi)^{-1/2} k_n^{-1/2} 
-		e^{-k_n\left(\frac{\mu(a_n^-)}{k_n} - 1 - \log\left(\frac{\mu(a_n^-)}{k_n}\right)\right)}.
-\end{align*}
-Since 
-\[
-	\frac{\mu(a_n^-)}{k_n} = \frac{\lambda_n^-}{k_n} = 1 - C \frac{\kappa_n}{k_n} = 1 - C \sqrt{\frac{\log(k_n)}{k_n}},
-\]
-and $-x - \log(1 - x) = \Omega(x^2/2)$, we get
-\begin{align*}
-	\rho(a_n^-,k_n) 
-	&\le \sqrt{2\pi} k_n^{-1/2} 
-		e^{-k_n\left(-C \frac{\kappa_n}{k_n} - \log\left(1 + C \frac{\kappa_n}{k_n}\right)\right)}\\
-	&\le (2\pi)^{-1/2} k_n^{-1/2} e^{-\Omega\left(\frac{C^2 \log(k_n)}{2}\right)} = \bigO{k_n^{-(1+C^2)/2}}.
-		\numberthis \label{eq:concentration_lemma_bound_an-}
+		e^{-k_n\left(\frac{\Mu{\BallPo{a_n^+}}}{k_n} - 1 - \log\left(\frac{\Mu{\BallPo{a_n^+}}}{k_n}\right)\right)}.
 \end{align*}
 
-For $a_n^+$ we again use the bound for $k!$ to get
+Let us first consider the case $k_n \to \infty$, in which case $\kappa_n = \sqrt{\ell_n \log(\ell_n)}$. Since 
+\[
+	\frac{\Mu{\BallPo{a_n^+}}}{k_n} = \frac{\lambda_n^-}{k_n} = 1 + \epsilon_n + C \frac{\kappa_n}{k_n} 
+	= 1 + \epsilon_n + C \sqrt{\frac{(1+\epsilon_n)\log((1+\epsilon_n)k_n)}{k_n}},
+\]
+and $x - \log(1 + x) \sim x^2/2$ as $x \to 0$, we get 
 \begin{align*}
-	\rho(a_n^+,k_n) &\le \frac{\mu(a_n^+)^{k_n}}{k_n!} e^{-\mu(a_n^+)} 
-		\le (2\pi)^{-1/2} k_n^{-(k_n + 1/2)} e^{-(\mu(a_n^+) - k_n)}\\
-	&= (2\pi)^{-1/2} k_n^{-1/2} 
-		e^{-k_n\left(\frac{\mu(a_n^+)}{k_n} - 1 - \log\left(\frac{\mu(a_n^+)}{k_n}\right)\right)}.
+	\rho(a_n^+,k_n) 
+	&\le \sqrt{2\pi} k_n^{-1/2} 
+		e^{-k_n\left(\epsilon_n + C \frac{\kappa_n}{k_n} - \log\left(1 + \epsilon_n + C \frac{\kappa_n}{k_n}\right)\right)}\\
+	&\sim (2\pi)^{-1/2} k_n^{-1/2} e^{-\frac{k_n \left(\epsilon_n + C \kappa_n/k_n\right)^2}{2}} \\
+	&= \bigO{k_n^{-(1+C^2)/2}},		\numberthis \label{eq:concentration_lemma_bound_an+}
 \end{align*}
-Since 
+where for the last line we used that
 \[
-	\frac{\mu(a_n^+)}{k_n} = \frac{\lambda_n^+}{k_n} = 1 + C \frac{\kappa_n}{k_n},
+	-k_n \frac{\left(\epsilon_n + C \kappa_n/k_n\right)^2}{2} = -\frac{C^2}{2}\log(k_n) + \bigT{1}.
 \]
-with $\kappa_n/k_n = \omega(1)$ as $n \to \infty$, and $x - \log(1 + x) = \omega(x/2)$ as $x \to \infty$, we get
-\begin{equation}\label{eq:concentration_lemma_bound_an+}
-	\rho(a_n^+,k_n) \le \sqrt{2\pi} k_n^{-1/2} 
-		e^{-k_n\left(C \frac{\kappa_n}{k_n} - \log\left(1 + C \frac{\kappa_n}{k_n}\right)\right)}
-	= \bigO{k_n^{-1/2} e^{-\frac{C \kappa_n}{2}}}.
+Let use now consider the case $k_n = \bigT{1}$. Then $\kappa_n = \log(n)$,
+\[
+	\frac{\Mu{\BallPo{a_n^+}}}{k_n} = \frac{\lambda_n^+}{k_n} = 1 + \epsilon_n + C \frac{\log(n)}{k_n},
+\] 
+and hence
+\begin{equation}\label{eq:concentration_lemma_bound_an+_constant}
+	\rho(a_n^-,k_n) \le \bigO{\log(n)^{k_n} n^{-C}}.
 \end{equation}
 
-Plugging~\eqref{eq:concentration_lemma_bound_an-} and~\eqref{eq:concentration_lemma_bound_an+} into~\eqref{eq:concentration_lemma_integral_bound} yields the result.
-The second statement immediately follows by our choice of $C$.
+Note that for $\rho(a_n^-,k_n)$ we only need to consider the case $k_n \to \infty$. A similar analysis as for $a_n^-$ yields
+\begin{equation}\label{eq:concentration_lemma_bound_an-}
+	\rho(a_n^-,k_n) \le \bigT{1} k_n^{-1/2} e^{-\frac{k_n \left(\epsilon_n - C \kappa_n/k_n\right)^2}{2}} = \bigO{k_n^{-(1+C^2)/2}}.
+\end{equation}
 
-To see that the same holds when we use $\rho_n(y,k_n)$ it satisfies similar bounds as $\rho(y,k_n)$ for $y \in \Rcal_n \setminus \Kcal_\eps(k_n)$ hold for.
-We first note that $\mu_{\alpha, \nu}(\BallPon{y}) = \mu_{\alpha, \nu}(\BallPo{y})(1 - \phi_n(y))$ where $\phi_n(y) = \bigT{e^{-(\alpha - \frac{1}{2})(R_n - y)}}$, see Lemma~\ref{lem:average_degree_P_n}.
-In particular we have that $\mu_{\alpha, \nu}(\BallPon{y})$ is increasing in $y$ and hence for $0 \le y \le a_n^-$
+Plugging~\eqref{eq:concentration_lemma_bound_an-}, \eqref{eq:concentration_lemma_bound_an+} and~\eqref{eq:concentration_lemma_bound_an+_constant} into~\eqref{eq:concentration_lemma_integral_bound} yields the result.
+The second statement immediately follows from the first by choosing a large enough $C$ and observing that
 \[
-	\rho_n(y,k_n) \le \rho_n(a_n^-,k_n) \le \rho(a_n^-,k_n) \le 2 k_n^{-\frac{\varepsilon^2}{4}}.
+	\int_{\Rcal_n \setminus \Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x\dd y
+	\le n \int_{\R_+ \setminus [a_n^-, a_n^+]} h_n(y) \alpha e^{-\alpha y} \dd y.
 \]
-It remains to show that the same holds for $a_n^+ \le y \le R_n$. For this we define 
-\[
-	\lambda_n := \mu_{\alpha, \nu}(\BallPon{a_n^+}) = \left(k_n + C \sqrt{k_n \log(k_n)}\right)
-	\left(1 - \phi_n(a_n^+)\right),
-\] 
-and note that $\lambda_n \ge k_n$ for large enough $n$. Hence
-\begin{align*}
-	\rho_n(y,k_n) &\le \rho_n(a_n^+,k_n) = \Prob{\Po(\mu_{\alpha, \nu}(\BallPon{a_n^+})) = k_n}\\
-	&\le \Prob{\left|\Po(\lambda_n) - \lambda_n\right| \ge k_n - \lambda_n} \le 2e^{-\frac{(k_n - \lambda_n)^2}{2(k_n + \lambda_n)}}.
-\end{align*}
-To finish the argument we observe that $k_n + \lambda_n \le 2k_n$ and $(k_n - \lambda_n)^2 \ge C^2 k_n \log(k_n)$ for $n$ large enough. Therefore
-\[
-	\rho_n(y,k_n) \le 2e^{-\frac{(k_n - \lambda_n)^2}{2(k_n + \lambda_n)}} = \bigO{k_n^{-\frac{C^2}{4}}}
-\] 
-which finishes the proof.
 \end{proof}
@@
 \begin{remark}[Concentration argument]\label{rmk:concentration_argument}
-Lemma~\ref{lem:concentration_argument} will prove very useful in the remainder of this paper since we often have to deal with integrands of the form $g_n(y) f_{\alpha,\nu}(x,y)$ where $g_n(y) = \bigO{n^{-1} k_n^{s}}\rho(y,k_n)$ for some $s \in \R$.
+Lemma~\ref{lem:concentration_argument} will prove very useful in the remainder of this paper since we often have to deal with integrands of the form $g_n(y) f_{\alpha,\nu}(x,y)$ where $g_n(y) = \bigO{n^{-1} k_n^{s}}e^{\beta y}\rho(y,k_n)$ for some $s \in \R$ and $\beta < \alpha$.
 In this case the lemma tells us that for a suitable $C > 0$ we only need to integrate over $\Kcal_C(k_n)$.
@@
 	\int_{\Rcal_n} g_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y 
-	= (1+\smallO{1}) \int_{\Kcal_C(k_n)} \rho(y,k_n) g_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y.
+	= (1+\smallO{1}) \int_{\Kcal_C(k_n)} g_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y.
 \]
+\PvdH{It might be a good idea to add one more example of how the concentration argument is used in the paper.}
 \end{remark}
@@
 
-Next we establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the degree distributions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$ in $G_{\HP,n}$ and $G_{\Pcal,n}$, respectively.
+With the results on the average degrees in the two finite Poisson model, we can now establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the degree distributions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$ in $G_{\HP,n}$ and $G_{\Pcal,n}$, respectively.
+The lemma is stated in a more general form, to make it applicable to slightly other cases later in the paper.
+To understand the general conditions presented in the statement of the lemma we write $\mu_n(y) = \Mu{\BallPon{y}}$ and $\mu(y) = \Mu{\BallPo{y}}$ and recall the result from Lemma~\ref{lem:average_degree_P_n}
+\[
+	\mu_n(y) = \mu(y)(1 - \phi_n(y)).
+\]
+For the error function $\phi_n(y)$ we note that for any $0 < \varepsilon < 1$, as $n \to \infty$, 
+\[
+	\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y) = \smallO{1},
+\]
+while
+\[
+	\frac{\partial \phi_n(y)}{\partial y} = \bigT{\phi_n(y)}.
+\]
+These are exactly the crucial properties of the error function that allow for a concentration argument.
+Moreover, if the integrand also contains a function $g_n(y)$ that is reasonably nice, we can replace the $\rho_{n}(y,k_n)$ in the integrand by $\rho(y,k_n)$.
+In particular, the triangle counting function $\Delta_{\Pcal}(y)$ will satisfy these conditions, see Section~\ref{sec:clustering_Pn_to_P}.
 
 \begin{lemma}\label{lem:concentration_argument_rho_approximation}
-Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any increasing sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$ and $\Kcal_{C}(k_n)$ defined as in~\eqref{eq:def_K_C_set} for some $C > 0$.
-In addition, let $\hat{\mu}_n(y)$ be any function satisfying
+Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and let $\Kcal_{C}(\ell_n)$ be defined as in~\eqref{eq:def_K_C_set}.
+In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is any function satisfying
 \[
@@
 \]
-where $\phi_n^{(i)} : \R_+ \to \R_+$ are such that $\sup_{0 \le y \le R_n} \phi_n(y)^{(i)} = \smallO{1}$.
-Then if we define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, we have, for any $\beta < \alpha$,
+where $\phi_n^{(i)} : \R_+ \to \R_+$ are such that $\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y)^{(i)} = \smallO{1}$ for any $0 < \varepsilon < 1$ and $\partial \phi_n^{(i)}(y)/\partial y = \bigT{\phi_n^{(i)}(y)}$.
+Then the following holds from some $C > 0$ large enough:
+\begin{enumerate}
+\item for any sequence of functions $h_n(y) : \R_+ \mapsto \R$ such that $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s e^{\beta y}}$ for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
 \[
-	\int_{\Rcal_n} \hat{\rho}_n(y,k_n) e^{\beta y} f_{\alpha,\nu}(x,y) \dd x \dd y 
-	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) e^{\beta y} f_{\alpha,\nu}(x,y) \dd x \dd y.
+	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
+	= (1 + o(1)) \int_{\Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
 \]
+\item If, in addition, $h_n(y) = \hat{\rho}_n(y,k_n) g_n(y)$ with $g_n$ satisfying $g_n(y(1+\smallO{1}) = (1+\smallO{1})g_n(y)$, we have,
+\[
+	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
+	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
+\]
+\end{enumerate}
 \end{lemma}
@@
 \[
-	\lambda_n^\pm = k_n \pm \varepsilon \sqrt{k_n \log(k_n)}, \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right),
+	\lambda_n^\pm = \ell_n \pm C \kappa_n, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right).
 \] 
-and for simplicity write
+In addition we fix $\varepsilon > 0$ such that $\varepsilon < \min\{1- \frac{s}{2\alpha(2\alpha + 1)}, 1\}$. Then since $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s}$ we have
+\begin{align*}
+	k_n^s \int_{(1-\varepsilon)R_n}^{R_n} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	&= \bigO{1} \hat{\rho}_n((1-\varepsilon)R_n,k_n) k_n^s e^{-\alpha(1-\varepsilon)R_n} \\
+	&= \bigO{\hat{\rho}_n((1-\varepsilon)R_n,k_n) k_n^s n^{-2\alpha(1 - \varepsilon)}} \\
+	&= \smallO{ \hat{\rho}_n((1-\varepsilon)R_n,k_n) n^{\frac{s}{2\alpha + 1} - 2\alpha(1-\varepsilon)}} = \smallO{1},
+\end{align*}
+where the last step follows by our choice of $\varepsilon$. Hence it is enough to prove both statement on $\Rcal_n((1-\varepsilon)R_n, R_n)$ instead of $\Rcal_n$.
+\PvdH{This is where we use that $s < 2\alpha(2\alpha + 1)$. I think this can be removed by using a more careful bound but I am not sure this is needed.}
+
+For simplicity we write $\mu(y) := \mu_{\alpha,\nu}\left(\BallPo{y}\right)$. For both statements we shall make a change of variables $y \to z$ such that
+\begin{equation}\label{eq:concentration_argument_variable_change}
+	\hat{\mu}_n(y) = \mu(z),
+\end{equation}
+which implies
 \[
-	\mu_1(y) := \mu_{\alpha,\nu}\left(\BallPo{y}\right) \quad \text{and} \quad 
-	\mu_2(y) = \mu_{\alpha,\nu}\left(\BallPon{y}\right).
+	\mu^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
 \]
-Next we notice that for all $y > a_n^+$, $\mu_2(y) \ge \mu_1(a_n^+)(1 - \phi_n^{(1)}) = \omega(k_n)$ and hence
+Observe that since
+\[
+	\mu^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
+\]
+is strictly monotonic in $y$, we have, by our assumptions on $\hat{\mu}_n$, that
+\begin{equation}\label{eq:concentration_argument_z_upper_bound}
+	z(y) \le 2 \log\left(\frac{\mu(y)}{\xi_{\alpha,\nu}}\right) + 2 \log\left(1 + \phi_n^{(2)}(y)\right)
+	= y + 2 \log\left(1 + \phi_n^{(2)}(y)\right),
+\end{equation}
+and similarly
+\begin{equation}\label{eq:concentration_argument_z_lower_bound}
+	z(y) \ge y + 2 \log\left(1 - \phi_n^{(1)}(y)\right) \
+\end{equation}
+Denote by $g^\prime(z)$ the derivative of a function $g$. Then by assumption $(\phi_n^{(i)})^\prime(z) = \bigT{\phi_n^{(i)}(z)}$ and hence
 \begin{align*}
-	\hat{\rho}_n(y,k) &\le \frac{\mu_1(y)^k(1 + \phi_n^{(2)}(y))^k}{k!} e^{-\mu_1(y)} e^{-\mu_1(y)\phi_n^{(2)}(y)}  \\
-	&= \rho(y,k) e^{k \log\left(1 +  \phi_n^{(2)}(y)\right) - \mu_1(y) \phi_n^{(2)}(y)}\\
-	&= \rho(y,k) \bigO{e^{(k - \mu_1(y))\phi_n^{(2)}(y)}}\\
-	&= \rho(y,k) \bigO{e^{-C \kappa_n \phi_n^{(2)}(y)}} = \rho(y,k) \bigO{1}.
-\end{align*}
-Similar we have for all $y < a_n^-$,
-\begin{align*}
-	\hat{\rho}_n(y,k) &\le \frac{\mu_1(y)^k(1 - \phi_n^{(1)}(y))^k}{k!} e^{-\mu_1(y)} e^{\mu_1(y)\phi_n^{(1)}(y)}\\
-	&= \rho(y,k) \bigO{e^{(k + \mu_1(y))\phi_n^{(1)}(y)}} \\
-	&= \rho(y,k) \bigO{e^{-C \kappa_n \phi_n^{(1)}(y)}} = \rho(y,k) \bigO{1}.
+	\hat{\mu}_n^\prime(z) = \mu^\prime(z)\left(1 + o(1)\right).
 \end{align*}
 
-Therefore, by Lemma~\ref{lem:concentration_argument}, it is enough to show that
+\paragraph{Proof of statement 1.} By our assumption on $h_n(y)$ it is enough to show that for sufficiently large $C > 0$,
 \[
-	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha) y} \dd y = (1+o(1))\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) e^{(\beta - \alpha) y} \dd y.
+	\lim_{n \to \infty} k_n^s \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0,
 \]
+and
+\[
+	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0.
+\]
+We shall prove the last statement. The first statement follows using similar computations.
 
-For this let us make a change of variables $y \to z$ such that
-\[
-	\mu_2(y) = \mu_1(z).
-\]
-and note that since
-\[
-	\mu_1^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
-\]
-is strictly monotonic in $y$, we have
-\[
-	z(y) \le 2 \log\left(\frac{\mu_1(y)}{\xi_{\alpha,\nu}}\right) + 2 \log\left(1 + \phi_n^{(2)}(y)\right)
-	= y + 2 \log\left(1 + \phi_n^{(2)}(y)\right),
-\]
-and similarly
-\[
-	z(y) \ge y + 2 \log\left(1 + \phi_n^{(2)}(y)\right).
-\]
-Hence, for all $a_n^- \le y \le a_n^+$,
+By our assumption on $\phi_n^{(2)}(y)$ we have for all $a_n^+ < y \le (1 - \varepsilon)R_n$,
 \begin{equation}
@@
 \end{equation}
-For the derivatives we have, for $a_n^- \le y \le a_n^+$, $\mu_1^\prime(y) = \mu_1(y)/2$, while $(\phi_n^{(i)})^\prime(y) = O(1)$ and hence
+Therefore, with this change of variables~\eqref{eq:concentration_argument_variable_change}, using that $\hat{a}_n^+ := z(a_n^+) = a_n^+(1 + \smallO{1})$ and $z((1-\varepsilon)R_n) = (1-\varepsilon)R_n(1+\smallO{1})$, we have
 \begin{align*}
-	\mu_2^\prime(y) = \mu_1^\prime(y)\left(1 + o(1)\right).
+	k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
+	&=  k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \Prob{\mathrm{Po}\left(\hat{\mu}_n(y) = k_n\right)} 
+		e^{(\beta-\alpha) y} \dd y\\
+	&= (1 + \smallO{1})k_n^s\int_{a_n^+}^{(1-\varepsilon)R_n} \Prob{\mathrm{Po}\left(\mu(z) = k_n\right)}
+		e^{(\beta-\alpha) z} \frac{\hat{\mu}_n^\prime(z)}{\mu^{\prime}(z)} \, dz \\
+	&\le (1 + \smallO{1})k_n^s\int_{a_n^+}^{R_n} \rho(y,k_n)
+			e^{(\beta-\alpha) z} \dd z.
 \end{align*}
-Therefore, with this change of variables, and using
+The result then follows by Lemma~\ref{lem:concentration_argument}.
+
+\paragraph{Proof of statement 2.}
+
+The proof of the second statement follows the same line of reasoning as above. First note that by Lemma~\ref{lem:concentration_argument} and the first statement, it is enough to show that
 \[
-	\hat{a}_n^\pm := z(a_n^\pm) = a_n^\pm(1 + \smallO{1}),
+	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) g_n(y) e^{-\alpha y} \dd y
+	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) g_n(z) e^{-\alpha z} \dd z.
 \] 
-we have
+For this we observe that~\eqref{eq:concentration_argument_z_upper_bound} and~\eqref{eq:concentration_argument_z_lower_bound} imply that $y = z(y) + \smallO{1}$ for $a_n^- \le y \le a_n^+$ and hence, by our assumption on $g_n(y)$ we have that
+\[
+	g_n(y) = g_n(z + \smallO{1}) = (1 + \smallO{1})g_n(z).
+\]
+Therefore, with the change of variables~\eqref{eq:concentration_argument_variable_change} we get
 \begin{align*}
-	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
-	&=  \int_{a_n^-}^{a_n^+} \Prob{\mathrm{Po}\left(\mu_2(y) = k_n\right)} e^{(\beta-\alpha) y} \dd y\\
-	&= (1 + \smallO{1})\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\mathrm{Po}\left(\mu_1(z) = k_n\right)}
-		e^{-\alpha z} \frac{\mu_2^\prime(z)}{\mu_2^{\prime}(z)} \, dz\\
-	&= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(y,k_n) e^{(\beta-\alpha) z} \, dz.
+	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) g_n(y) e^{-\alpha y} \dd y
+	&=  \int_{a_n^-}^{a_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} g_n(y) e^{-\alpha y} \dd y\\
+	&= (1 + \smallO{1})\int_{a_n^-}^{a_n^+}  \Prob{\Po(\mu(z))}
+		g_n(z) e^{-\alpha z} \frac{\hat{\mu}_n^\prime(z)}{\mu^{\prime}(z)} \dd z\\
+	&= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) g_n(z) e^{-\alpha z} \dd z.
 \end{align*}
+
 \end{proof}
 
-Observe that Lemma~\ref{lem:average_degree_P_n} implies that $\Mu{\BallHyp{(0,y)}}$ satisfies the requirements in Lemma~\ref{lem:concentration_argument_rho_approximation}.
-Lemma~\ref{lem:average_degree_hyperbolic} states that $\Mu{\BallPon{0,y}}$ satisfies these requirement when $y \le (1-\eps)R_n$.
-However, since for all $\eps < (2\alpha - 1)/2\alpha$
-\[
-	\Mu{\BallHyp{0,y} \cap \Rcal_n[(1-\eps)R_n, R_n]} = \bigO{e^{\frac{R_n}{2} - \alpha(1-\varepsilon)R_n}}
-	= \bigO{n^{1 - 2\alpha(1 -\eps)}} = \smallO{1},
-\]
-the conclusion of Lemma~\ref{lem:concentration_argument_rho_approximation} still holds for this case. We therefore have the following important Corollary.
+Observe that Lemma~\ref{lem:average_degree_P_n} implies that $\Mu{\BallHyp{(0,y)}}$ satisfies the requirements in Lemma~\ref{lem:concentration_argument_rho_approximation} while Lemma~\ref{lem:average_degree_hyperbolic} states that this holds for $\Mu{\BallPon{0,y}}$.
+We therefore have the following important Corollary.
 
@@
 Let $\hat{\rho}_n(y,k)$ be any of the two distribution functions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$.
-Then, for any function $g_n(y)$ such that $g_n(y) = \bigO{n^{-1} k_n^{s}}\hat{\rho}_n(y,k_n)$, as $n \to \infty$, for some $s \in \R$,
+Then, for any function $g_n(y)$ such that $g_n(y) = \bigO{n^{-1} k_n^{s} e^{\beta y}}\hat{\rho}_n(y,k_n)$, as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
 \[

### 2018-11-15 introduction.tex
more typos in section 2

@@
 \label{thm:local_clustering_hyperbolic}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\xi = \frac{4\alpha\nu}{\pi(2\alpha-1)}$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n \ge 3$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
+Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\xi = \frac{4\alpha\nu}{\pi(2\alpha-1)}$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n \ge \GR{2}$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
 Then,

### 2018-11-15 proof_overview.tex
more typos in section 2

@@
 
-To analyze expression in the both the finite and infinite model we will make use of the~\emph{Campbell-Mecke} formula. 
+To analyze expressions in the both the finite and infinite model we will make use of the~\emph{Campbell-Mecke} formula. 
 For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ we have
@@
 
-Using the Campbell-Mecke formula we can compute the density of the ball $\BallPo{p}$ as
+Using the Campbell-Mecke formula we can compute the intensity measure of the ball $\BallPo{p}$, i.e. the expected number of points falling into it, as
 \begin{equation}\label{eq:mu_ball_y_P}
@@
 \]
-Note that $\rho(y,k)$ denote the probability that a node $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$, which due to the translation symmetry of the Poisson Point Process in the $x$ direction depends only on the \emph{height} $y$.
+Note that $\rho(y,k)$ denotes the probability that a vertex $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$, which due to the translation symmetry of the Poisson Point Process in the $x$ direction depends only on the \emph{height} $y$.
 
@@
 Again, due to symmetry in the $x$ direction we can assume without loss of generality that a randomly sampled point $p$ is $(0,y)$.
-For any $y \in \R_+$ we define the probability density function on $\Rcal := \R_+ \times \R$ by
+For any $y \in \R_+$ we define the probability density function on $\Rcal :=  \R \times \R_+$ by
 \begin{equation}\label{eq:def_eta_P}
@@
 
-In Section~\ref{sec:asymptotics_average_clustering_ast_P} we will compute both these quantities and show that $c_\Pcal = c_\infty$ and $c_\Pcal(k) = c_\infty(k)$, where $c_\infty$ and $c_\infty(k)$ are given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}
+In Section~\ref{sec:asymptotics_average_clustering_ast_P} we will compute both these quantities and show that $c_\Pcal = c_\infty$ and $c_\Pcal(k) = c_\infty(k)$, where $c_\infty$ and $c_\infty(k)$ are given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}.
 
@@
 
-To compute the limit of the adjusted local clustering $c_{\mathcal{P},n}^\ast(k)$ in the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ we first prove in Section~\ref{sec:concentration_c_P_n} that it is concentrated around its mean $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$.
+To compute the limit of the modified local clustering function $c_{\mathcal{P},n}^\ast(k)$ in the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ we first prove in Section~\ref{sec:concentration_c_P_n} that it is concentrated around its expectation $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$.
 
-\begin{proposition}[Concentration local clustering in $G_{\mathcal{P},n}(\alpha, \nu)$]\label{prop:concentration_local_clustering_P_n}
+\begin{proposition}[Concentration local clustering function in $G_{\mathcal{P},n}(\alpha, \nu)$]\label{prop:concentration_local_clustering_P_n}
 Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any non-decreasing sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
@@
 \begin{proposition}[Transition to infinite limit model]\label{prop:convergence_average_clustering_P_n}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any positive sequence tending to infinity and satisfying $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any positive sequence tending to infinity and satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
 \[
@@
 \end{proposition}
+\MS{Is it really necessary that the sequence tends to infinity in the thm above?}
 

### 2018-11-15 proof_overview.tex
rewriting of proof of thm 1.2 in section 2, couple of questions/comments

@@
 \begin{proof}[Proof of Theorem \ref{thm:local_clustering_hyperbolic}]
-By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
+%By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
+%\begin{align*}
+%	&\hspace{-30pt}\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}\\
+%	&\le \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{}c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)}
+%		+ \frac{\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\infty(k_n)\right|}{C_{\alpha,\nu}s_\alpha(k_n)}
+%		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| \\
+%	&= \smallO{1}.
+%\end{align*}
+First of all, due to cancellation of equal terms we can rewrite
 \begin{align*}
-	&\hspace{-30pt}\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}\\
-	&\le \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{}c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)}
-		+ \frac{\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\infty(k_n)\right|}{C_{\alpha,\nu}s_\alpha(k_n)}
-		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| \\
-	&= \smallO{1}.
+    c_{\H,n}(k_n)-c_\infty(k_n) =& c_{\H,n}(k_n)-c_{\H,n}^\ast(k_n)+c_{\H,n}^\ast(k_n)-c_{\HP,n}^\ast(k_n)+c_{\HP,n}^\ast(k_n)-c_{\Pcal,n}^\ast(k_n) \\
+    &+c_{\Pcal,n}^\ast(k_n)-\E c_{\Pcal,n}^\ast(k_n)+\E c_{\Pcal,n}^\ast(k_n)-c_\infty(k_n)
 \end{align*}
+Then, we take absolute values and apply the triangle inequality. By monotonicity of expectation, we can apply it to both sides and obtain
+\begin{align*}
+    \E[|c_{\H,n}(k_n)-c_\infty(k_n)|] \leq & \E[|c_{\H,n}(k_n)-c_{\H,n}^\ast(k_n)|]+\E[|c_{\H,n}^\ast(k_n)-c_{\HP,n}^\ast(k_n)|]\\&+\E[|c_{\HP,n}^\ast(k_n)-c_{\Pcal,n}^\ast(k_n)|] 
+    +\E[|c_{\Pcal,n}^\ast(k_n)-\E c_{\Pcal,n}^\ast(k_n)|]\\&+\E[|\E c_{\Pcal,n}^\ast(k_n)-c_\infty(k_n)|]
+\end{align*}
+At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{s_\alpha(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c_{\Pcal}(k_n) = c_\infty(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
+All of this together yields that:
+\begin{align*}
+    \E[|c_{\H,n}(k_n)-c_\infty(k_n)|] = \smallO{s_\alpha(k_n)} = \smallO{c_\infty(k_n)}
+\end{align*}
+i.e. the statement of the theorem.
+
 %\[
@@
 %\]
-Combining this with Proposition~\ref{prop:couling_c_H_P} yields
-\[
-	\Exp{\left|\frac{c_{\H,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
-	\le \Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|} 
-	+ \frac{\Exp{\left|c_{\H,n}^\ast(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
-\]
-and the result then follows by applying Lemma~\ref{lem:clustering_ast_H}. 
+
+%Combining this with Proposition~\ref{prop:couling_c_H_P} yields
+%\[
+%	\Exp{\left|\frac{c_{\H,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
+%	\le \Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|} 
+%	+ \frac{\Exp{\left|c_{\H,n}^\ast(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
+%\]
+%and the result then follows by applying Lemma~\ref{lem:clustering_ast_H}. 
 \end{proof}
@@
 
+\MS{I think we need to introduce resp. explain $\Prob{D_\Pcal = k_n}$ in the lemma below.}
 \begin{lemma}\label{lem:N_k_H_P}
@@
 \end{align*}
+\MS{Should the summation in $t$ not start from $t=2$?}
 where the expectation of last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. Similarly,

### 2018-11-16 concentration_argument.tex
typos in the proof of thm 1.1. in section 2 and typos in section 3

@@
-\section{Concentration of heights for nodes with degree $k$}\label{sec:concentration_argument}
+\section{Concentration of heights for vertices with degree $k$}\label{sec:concentration_argument}
 
-Many of the computations in this paper will involve integrals whose integrand contains $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$ and $\mu_n(y) \approx e^{y/2}$.
-For instance, the expected adjusted local clustering function $c_\infty(k)$ in $G_\Pcal$ equals
+Many of the computations in this paper will involve integrals whose integrand contains $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and $\mu_n(y) \approx e^{y/2}$.
+For instance, the expected modified local clustering function $c_\infty(k)$ in $G_\Pcal$ equals
 \[
-	\frac{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \Delta_{\Pcal}(y) \alpha e^{-\alpha} \dd y}
-	{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \alpha e^{-\alpha} \dd y},
+	\frac{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \Delta_{\Pcal}(y) \alpha e^{-\alpha y} \dd y}
+	{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \alpha e^{-\alpha y} \dd y},
 \]
@@
 
-Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with mean $\mu_{\alpha, \nu}(B_\Pcal(y)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$. 
+Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(B_\Pcal(y)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$. 
 For any sequence $\{k_n\}_{n \ge 1}$, possibly constant, define
@@
 \begin{equation}\label{eq:def_K_C_set}
-	\Kcal_C(k_n) = \left\{p \in \R : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
+	\Kcal_C(k_n) = \left\{p=(x,y) \in \R \times \R_+ : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
 	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \wedge e^{R_n/2} \right\},
 \end{equation}
-Note that if $k_n = \Omega(\log(n))$ then $e^{y/2} = \bigT{k_n}$ whenever $p \in \Kcal_C(k_n)$. The next lemma states that for a large class of functions $h(y)$, to compute the integral 
+\MS{What does $\vee$ and $\wedge$ mean?}
+
+Note that if $k_n = \Omega(\log(n))$ then $e^{y/2} = \bigT{k_n}$ whenever $p=(x,y) \in \Kcal_C(k_n)$. The next lemma states that for a large class of functions $h(y)$, to compute the integral 
 \[
@@
 Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\{k_n\}_{n \ge 1}$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$.
-In addition let $\beta < \alpha$ and $h : \R_+ \mapsto \R$ be a any function such that $h(y) = g(y)e^{\beta y}$ with $|g(y)|$ uniformly bounded on $\R_+$.
+In addition let $\beta < \alpha$ and $h : \R_+ \rightarrow  \R$ be a any function such that $h(y) = g(y)e^{\beta y}$ with $|g(y)|$ uniformly bounded on $\R_+$.
 Then, if we define for $C > 0$
@@
 
-\subsection{Average degree in the Hyperbolic graph}\label{ssec:average_degree_HP_n}
+\subsection{Average degree in the hyperbolic random graph}\label{ssec:average_degree_HP_n}
 
-Recall that under the coupling between the hyperbolic random graph and the finite box model $|x-x^\prime|_{\pi e^{r_n/2}} \le \Omega(r,r^\prime)$, while the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
+Recall that under the coupling between the hyperbolic random graph and the finite box model $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$, while the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
 \[
@@
 \begin{proof}
-We will split the computation of $\Mu{\BallHyp{0,y}}$ over the case $y^\prime > R_n - y$ and $y^\prime \le R_n - y$ where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
-Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = 4\nu \alpha/(2\alpha - 1)\pi$.
+We will split the computation of $\Mu{\BallHyp{0,y}}$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$ where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
+Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.
 
@@
 \end{align*}
-The last integral depend on the value of $\alpha$,
+The last integral depends on the value of $\alpha$,
 \[
@@
 \]
-If, on the other hand, $y \le 2 \log(\pi/2)$ then
+On the other hand, if $y \le 2 \log(\pi/2)$ then
 \[
@@
 
-\subsection{Concentration argument for Hyperbolic and finite box models}
+\subsection{Concentration argument for hyperbolic and finite box model}
 
-With the results on the average degrees in the two finite Poisson model, we can now establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the degree distributions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$ in $G_{\HP,n}$ and $G_{\Pcal,n}$, respectively.
+With the results on the average degrees in the two finite Poisson models, we can now establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the degree distributions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$ in $G_{\HP,n}$ and $G_{\Pcal,n}$, respectively.
 The lemma is stated in a more general form, to make it applicable to slightly other cases later in the paper.
@@
 where $\phi_n^{(i)} : \R_+ \to \R_+$ are such that $\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y)^{(i)} = \smallO{1}$ for any $0 < \varepsilon < 1$ and $\partial \phi_n^{(i)}(y)/\partial y = \bigT{\phi_n^{(i)}(y)}$.
-Then the following holds from some $C > 0$ large enough:
+Then the following holds for some $C > 0$ large enough:
 \begin{enumerate}
@@
 \begin{proof}
-Similar to the proof of Lemma~\ref{lem:concentration_argument} we define 
+Similarly to the proof of Lemma~\ref{lem:concentration_argument} we define 
 \[
@@
 
-In particular we conclude that, similar to the infinite limit model, concentrations arguments as described in Remark~\ref{rmk:concentration_argument} can be applied in the case of the hyperbolic random graph and finite box model.
+In particular we conclude that, similarly to the infinite limit model, concentration arguments as described in Remark~\ref{rmk:concentration_argument} can be applied in the case of the hyperbolic random graph and finite box model.
 

### 2018-11-16 introduction.tex
typos in the proof of thm 1.1. in section 2 and typos in section 3

@@
 
-Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to a constant $c_\infty$, which we can explicitly write down in terms of the special functions defined above.
+Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to a constant $c_\infty$, which we can explicitly write down in terms of the special functions mentioned above.
 

### 2018-11-16 proof_overview.tex
typos in the proof of thm 1.1. in section 2 and typos in section 3

@@
 \MS{Should the summation in $t$ not start from $t=2$?}
-where the expectation of last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. Similarly,
+where the expectation of the last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. Similarly,
 \[
@@
 \]
-Recall that (see [??]) $c_\infty = c_\Pcal$ and $c_\infty(k) = c_\Pcal(k)$. Therefore
+As derived at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}, $c_\infty = c_\Pcal$ and $c_\infty(k) = c_\Pcal(k)$. Therefore
 \begin{align*}
-	\Exp{|c_{\H,n} - c_\Pcal|}
+	\Exp{|c_{\H,n}-c_\infty|}=\Exp{|c_{\H,n} - c_\Pcal|}
 	&\le \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
@@
 \end{align*}
-and since the last to probabilities are $\smallO{1}$ it is enough to prove that
+and since the last two probabilities are $\smallO{1}$ it is enough to prove that
 \[
@@
 \end{align*}
-This finishes the first part of the proof. The second part, which derives the exact expression for $c_\Pcal$ can be found in [??] \PvdH{Add reference to section.}
+This finishes the proof. %The second part, which derives the exact expression for $c_\Pcal$ can be found in [??] \PvdH{Add reference to section.}
 \end{proof}

### 2018-11-17 concentration.tex
updated sections 5 and 6 with respect to changes in section 3

@@
-\section{Concentration for $c_{\mathcal{P}, n}(k)$ (Proving Proposition \ref{prop:concentration_local_clustering_P_n})}
+\section{Concentration for $c_{\Pcal, n}(k)$ (Proving Proposition \ref{prop:concentration_local_clustering_P_n})}
 \label{sec:concentration_c_P_n}
+
+In this section we establish a concentration result for the local clustering function $c_{\Pcal, n}^\ast(k)$ in the finite model $G_{\Pcal,n}$.
+Similar to the previous section we will focus on those nodes $p = (x,y) \in \Kcal_{C}(k_n)$.
 
@@
 \[
-	\Kcal_C(k) = \left\{p \in \R : \frac{k - C \sqrt{k \log(k)}}{\xi_{\alpha,\nu}} \le e^{\frac{y}{2}}
-		\le \frac{k + C \sqrt{k \log(k)}}{\xi_{\alpha,\nu}} \right\},
+	\Kcal_C(k_n) = \left\{p \in \R : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
+		\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \wedge e^{R_n/2} \right\},
+\]
+with
+\[
+	\kappa_n := \begin{cases}
+		\log(n) &\mbox{if } k_n = \bigT{1},\\
+		\sqrt{k_n \log(k_n)} &\mbox{else.}
+	\end{cases}
 \]
@@
 \begin{equation}\label{eq:def_degree_triangle_count_in_K}
-	\widetilde{T}_{\Pcal,n}(k,C) = \sum_{p \in \Pcal_n \cap K_C(k)} \ind{D_{\Pcal,n}(p) = k} \widetilde{T}_{\Pcal,n}(p),
+	\widetilde{T}_{\Pcal,n}(k, C) = \sum_{p \in \Pcal_n \cap K_C(k)} \ind{D_{\Pcal,n}(p) = k} \widetilde{T}_{\Pcal,n}(p),
 \end{equation}
@@
 \[
-	\widetilde{T}_{\Pcal,n}(p) := \sum_{(p_1, p_2) \in 2^{\Pcal_n}} \widetilde{T}_{\Pcal,n}(p,p_1,p_2).
+	\widetilde{T}_{\Pcal,n}(p) := \sum_{(p_1, p_2) \in \Pcal\setminus (0,y)}^{\ne} \widetilde{T}_{\Pcal,n}(p,p_1,p_2),
 \]
+where the sum is over all distinct pairs $(p_1, p_2) \in \Pcal \setminus \{(0,y)\}$.
 
-By Lemma \ref{lem:clustering_error_T_term} and a concentration argument it follows that for $k_n \to \infty$
-\[
+Next we note that the second result from Corollary~\ref{cor:approximation_triangle_integral} states that
+\begin{equation}\label{eq:asymptotic_equivalence_contraint_triangle_count}
 	\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)} = (1+\smallO{1})\Exp{T_{\Pcal}(k_n)},
-\]
-for a appropriately selected $C > 0$.
-We conclude that the main contribution of triangles of degree $k_n$ is given by $\widetilde{T}_{\Pcal,n}(k_n,C)$.
-Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} we need to show that $\widetilde{T}_{\Pcal,n}(k_n,C)$ is sufficiently concentrated around its mean.
+\end{equation}
+so that we can conclude that the main contribution of triangles of degree $k_n$ is given by $\widetilde{T}_{\Pcal,n}(k_n, C)$.
+Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} it suffices to show that $\widetilde{T}_{\Pcal,n}(k_n,C)$ is sufficiently concentrated around its mean.
+This is done in the following proposition.
 
-\subsection{Proving Proposition \ref{prop:concentration_local_clustering_P_n}}
-
-We start with the concentration result for $\widetilde{T}_{\Pcal,n}(k_n,C)$.
+%\subsection{The proof of Proposition \ref{prop:concentration_local_clustering_P_n}}
+%
+%We start with the concentration result for $\widetilde{T}_{\Pcal,n}(k_n)$.
 
 \begin{proposition}[Concentration $\widetilde{T}_{\Pcal,n}(k_n,C)$]\label{prop:concentration_tilde_T_P_n}
-Let $\alpha > \frac{1}{2}$, $0 < \varepsilon < \min\{2\alpha - 1,1\}$ and let $(k_n)_{n \ge 1}$ be any increasing sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any positive sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then for any $C > 0$, as $n \to \infty$,
 \[
-	\Exp{\widetilde{T}_{\Pcal,n}(k_n, C)^2} = \left(1 + \smallO{1}\right)\Exp{\widetilde{T}_{\Pcal,n}(k_n, C)}^2.
+	\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)^2} = \left(1 + \smallO{1}\right)\Exp{\widetilde{T}_{\Pcal,n}(k_n, C)}^2.
 \]
@@
 
-The proof of this proposition is lengthy and we therefore postpone it till Section \ref{ssec:concentration_tilde_T}.
-The remaining of this section will be devoted to prove Proposition \ref{prop:concentration_local_clustering_P_n}.
-We first show that $\Exp{c_{\Pcal,n}(k_n)} = (1+o(1))\Exp{c^\ast_{\Pcal,n}(k_n)}$.
+We postpone the proof of this proposition postpone till Section \ref{ssec:concentration_tilde_T} and first use it to prove Proposition \ref{prop:concentration_local_clustering_P_n}.
 
-\begin{lemma}\label{lem:L1_convergence_c_Pcal_n}
-Let $\nu > 0$, $\alpha > \frac{1}{2}$ and $k_n = o\left(n^{\frac{1}{2\alpha + 1}}\right)$. Then, as $n \to \infty$,
-\[
-	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
-\]
-\end{lemma}
-
-\begin{proof}
-Let $0 < \delta < 1$ and define the following two events
-\begin{align*}
-	A_n &= \left\{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| \le \Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}\right\}\\
-	B_n &= \left\{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| \le n\right\},
-\end{align*}
-so that
-\[
-	1 = \ind{A_n} + \ind{A_n^c}\ind{B_n} + \ind{B_n^c}.
-\]
-Next we note that on the event $A_n$
-\[
-	\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right| 
-	\le \frac{\Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}}{\Exp{N_{\Pcal,n}(k_n)}+\Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}}
-	\le \Exp{N_{\Pcal,n}(k_n)}^{-\frac{1 - \delta}{2}},
-\]
-and on the event $B_n$
-\[
-	\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right| 
-	\le \frac{n}{\Exp{N_{\Pcal,n}(k_n)} + n} \le 1.
-\]
-Therefore we have
-\begin{align*}
-	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|}
-	&= \Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|}\\
-	&\le \Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n}}\Exp{N_{\Pcal,n}(k_n)}^{-\frac{1 - \delta}{2}} \\
-	&\hspace{10pt}+ \Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}} \\
-	&\hspace{10pt}+ \Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|\ind{B_n^c}}
-\end{align*}
-Since $\Exp{N_{\Pcal,n}(k_n)} \to \infty$, the first term is clearly $\smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}$. For the third term we have
-\begin{align*}
-	\Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|\ind{B_n^c}} 
-	&= \bigO{\Prob{B_n^c}}
-		= \bigO{\Prob{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| > n}}\\
-	&= \bigO{e^{-\frac{n^2}{\Exp{N_{k_n}} + n}}} = \bigO{e^{-n}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
-\end{align*}
-Hence we are left to show that
-\begin{equation}\label{eq:L1_convergence_second_term}
-	\Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
-\end{equation}
-By writing
-\begin{align*}
-	c_{\Pcal, n}^\ast(k_n) = \frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-	+ \frac{T_{\Pcal,n}(k_n,\varepsilon)- \widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-\end{align*}
-and using Lemma~\ref{lem:clustering_error_T_term} we get
-\begin{align*}
-	\Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}}
-	&\le \Exp{\frac{(1+\smallO{1})\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-		\ind{A_n^c}} + \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
-\end{align*}
-For the last step we use H\"{o}lder's inequality and Proposition \ref{prop:concentration_tilde_T_P_n} to get
-\begin{align*}
-	\Exp{\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}\ind{A_n^c}}
-	&\le \Exp{\left(\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}
-		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}\right)^2}^{\frac{1}{2}} \Prob{A_n^c}^{\frac{1}{2}}\\
-	&= \left(1 + \smallO{1}\right) 	
-		\frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-		\Prob{A_n^c}^{\frac{1}{2}}\\
-	&= \bigO{\Exp{c_{\Pcal, n}^\ast(k_n)}}\Prob{A_n^c}^{\frac{1}{2}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}},
-\end{align*}
-since $\Prob{A_n} = o(1)$. This establishes \eqref{eq:L1_convergence_second_term} and hence we conclude that
-\[
-	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
-\]
-\end{proof}
-
-We are now in shape to prove the main result of this section.
+%\begin{lemma}\label{lem:L1_convergence_c_Pcal_n}
+%Let $\nu > 0$, $\alpha > \frac{1}{2}$ and $k_n = o\left(n^{\frac{1}{2\alpha + 1}}\right)$. Then, as $n \to \infty$,
+%\[
+%	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
+%\]
+%\end{lemma}
+%
+%\begin{proof}
+%Let $0 < \delta < 1$ and define the following two events
+%\begin{align*}
+%	A_n &= \left\{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| \le \Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}\right\}\\
+%	B_n &= \left\{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| \le n\right\},
+%\end{align*}
+%so that
+%\[
+%	1 = \ind{A_n} + \ind{A_n^c}\ind{B_n} + \ind{B_n^c}.
+%\]
+%Next we note that on the event $A_n$
+%\[
+%	\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right| 
+%	\le \frac{\Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}}{\Exp{N_{\Pcal,n}(k_n)}+\Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}}
+%	\le \Exp{N_{\Pcal,n}(k_n)}^{-\frac{1 - \delta}{2}},
+%\]
+%and on the event $B_n$
+%\[
+%	\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right| 
+%	\le \frac{n}{\Exp{N_{\Pcal,n}(k_n)} + n} \le 1.
+%\]
+%Therefore we have
+%\begin{align*}
+%	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|}
+%	&= \Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|}\\
+%	&\le \Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n}}\Exp{N_{\Pcal,n}(k_n)}^{-\frac{1 - \delta}{2}} \\
+%	&\hspace{10pt}+ \Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}} \\
+%	&\hspace{10pt}+ \Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|\ind{B_n^c}}
+%\end{align*}
+%Since $\Exp{N_{\Pcal,n}(k_n)} \to \infty$, the first term is clearly $\smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}$. For the third term we have
+%\begin{align*}
+%	\Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|\ind{B_n^c}} 
+%	&= \bigO{\Prob{B_n^c}}
+%		= \bigO{\Prob{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| > n}}\\
+%	&= \bigO{e^{-\frac{n^2}{\Exp{N_{k_n}} + n}}} = \bigO{e^{-n}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
+%\end{align*}
+%Hence we are left to show that
+%\begin{equation}\label{eq:L1_convergence_second_term}
+%	\Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
+%\end{equation}
+%By writing
+%\begin{align*}
+%	c_{\Pcal, n}^\ast(k_n) = \frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
+%	+ \frac{T_{\Pcal,n}(k_n,\varepsilon)- \widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
+%\end{align*}
+%and using Lemma~\ref{lem:clustering_error_T_term} we get
+%\begin{align*}
+%	\Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}}
+%	&\le \Exp{\frac{(1+\smallO{1})\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
+%		\ind{A_n^c}} + \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
+%\end{align*}
+%For the last step we use H\"{o}lder's inequality and Proposition \ref{prop:concentration_tilde_T_P_n} to get
+%\begin{align*}
+%	\Exp{\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}\ind{A_n^c}}
+%	&\le \Exp{\left(\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}
+%		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}\right)^2}^{\frac{1}{2}} \Prob{A_n^c}^{\frac{1}{2}}\\
+%	&= \left(1 + \smallO{1}\right) 	
+%		\frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
+%		\Prob{A_n^c}^{\frac{1}{2}}\\
+%	&= \bigO{\Exp{c_{\Pcal, n}^\ast(k_n)}}\Prob{A_n^c}^{\frac{1}{2}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}},
+%\end{align*}
+%since $\Prob{A_n} = o(1)$. This establishes \eqref{eq:L1_convergence_second_term} and hence we conclude that
+%\[
+%	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
+%\]
+%\end{proof}
 
@@
 \begin{align*}
-	c_{\Pcal, n}^\ast(k_n) = \frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-	+ \frac{\left(T_{\Pcal,n}(k_n)-\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)\right)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}},
+	c_{\Pcal, n}^\ast(k_n) = \frac{\widetilde{T}_{\Pcal,n}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
+	+ \frac{\left(T_{\Pcal,n}(k_n)-\widetilde{T}_{\Pcal,n}(k_n,C)\right)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}},
 \end{align*}
-so that by Lemma \ref{lem:clustering_error_T_term},
-\[
-	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
+so that by~\eqref{eq:asymptotic_equivalence_contraint_triangle_count},
+\begin{equation}\label{eq:concentration_local_clustering_P_n_main}
+	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
 	+ \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}}.
-\]
-Therefore, by Lemma \ref{lem:L1_convergence_c_Pcal_n},
-\begin{align*}
-	\Exp{\left|c_{\Pcal,n}(k_n) - \Exp{c_{\Pcal,n}^\ast(k_n)}\right|}
-	&\le \Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{c_{\Pcal,n}^\ast(k_n)}\right|}
-		+ \Exp{\left|c_{\Pcal,n}(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}\\
-	&= \frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}}
-		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}} + \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}}.
-		\numberthis \label{eq:concentration_local_clustering_P_n_term1}
-\end{align*}
+\end{equation}
+%Therefore, by Lemma \ref{lem:L1_convergence_c_Pcal_n},
+%\begin{align*}
+%	\Exp{\left|c_{\Pcal,n}(k_n) - \Exp{c_{\Pcal,n}^\ast(k_n)}\right|}
+%	&\le \Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{c_{\Pcal,n}^\ast(k_n)}\right|}
+%		+ \Exp{\left|c_{\Pcal,n}(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}\\
+%	&= \frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}}
+%		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}} + \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}}.
+%		\numberthis \label{eq:concentration_local_clustering_P_n_term1}
+%\end{align*}
 Next, we use Proposition \ref{prop:concentration_tilde_T_P_n} to obtain
 \begin{align*}
-	\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}
-	&\le \left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)^2} 
-		- \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}^2\right)^{\frac{1}{2}}\\
-	&= \smallO{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}.
+	\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,C) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}\right|}
+	&\le \left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)^2} 
+		- \Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}^2\right)^{\frac{1}{2}}\\
+	&= \smallO{\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}}.
 \end{align*}
@@
 \end{align*}
-which together with~\eqref{eq:concentration_local_clustering_P_n_term1} finishes the proof.
+which together with~\eqref{eq:concentration_local_clustering_P_n_main} yields the required result.
+\end{proof}
+
+\subsection{Joint neighborhoods and degrees in $G_{\Pcal,n}(\alpha,\nu)$}
+
+To prove Proposition~\ref{prop:concentration_tilde_T_P_n} we need to understand the joint degree distribution in $G_{\Pcal,n}$ and subsequently the joint neighborhoods of two points $p, p^\prime \in \Rcal_n$.
+We perform the analysis in this section.
+The two main results, which will be the crucial technical ingredients for the proof of Proposition~\ref{prop:concentration_tilde_T_P_n}, are Lemma ??
+and Lemma ??.
+
+\subsubsection*{Neighborhoods}
+
+We start with analyzing joint neighborhoods in $G_{\Pcal,n}$.
+Let $p, p^\prime \in \Rcal_n$.
+Then we denote by $\Ncal_{\Pcal,n}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $G_{\Pcal,n}$, i.e.
+those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection.
+In addition we denote by $\Ncal_{\Pcal,n}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$.
+We shall establish lower bounds on the expect number of these disjoint neighbors $\Exp{\Ncal_{\Pcal,n}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors.
+For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large.
+Figure~\ref{fig:representation_disjoint_neighborhoods_P_n}-\ref{fig:representation_disjoint_neighborhoods_P_n_3} show the different situations that occur.
+
+\begin{figure}[p]
+\centering
+\begin{tikzpicture}
+
+	%The box \Rcal_n
+	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
+
+    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
+    \draw node at (-0.2,0.7) {$p$};
+
+    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (1,0.5) {};
+    \draw node at (0.8,0.2) {\color{blue}$p^\prime$};
+
+	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
+    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
+    \draw[domain=2.2840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-1)-0.5});
+    \draw[domain=-0.2840:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(1-\x)-0.5});
+
+    \draw[dashed,thick,black,line width=1pt] (-6,2.5835) -- (6,2.5835);
+
+    \draw node at (-7,2.5835) {$h(y)$};
+    \draw node at (-7,3.3918) {\color{blue}$h_1(p^\prime)$};
+    \draw node at (7,2.7189) {\color{blue}$h_2(p^\prime)$};
+
+    \draw node at (-4,3.5) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
+    \draw node at (4.5,3) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
+    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
+    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+
+\end{tikzpicture}
+\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $G_{\Pcal,n}(\alpha,\nu)$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
+\label{fig:representation_disjoint_neighborhoods_P_n}
+\end{figure}~
+\begin{figure}[p]
+\centering
+\begin{tikzpicture}
+
+	%The box \Rcal_n
+	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
+
+    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
+    \draw node at (-0.2,0.7) {$p$};
+
+    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (2.5,0.5) {};
+    \draw node at (2.3,0.2) {\color{blue}$p^\prime$};
+
+	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
+    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
+    \draw[domain=3.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-2.5)-0.5});
+    \draw[domain=1.2160:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(2.5-\x)-0.5});
+    \draw[domain=0:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+9.5)-0.5});
+
+    \draw[dashed,black,line width=1pt] (-6,2.0055) -- (6,2.0055);
+
+%    \draw node at (-7,2.5835) {$h(y)$};
+    \draw node at (-7,3.7801) {\color{blue}$h_1(p^\prime)$};
+    \draw node at (7,2.0055) {\color{blue}$h_2(p^\prime)$};
+
+%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
+%    \draw[dotted,thick,black] (4.5208,2.0174) -- (6,2.0174);
+
+%    \draw node at (4.5208,-0.5) {$w_x(p,p^\prime)$};
+%    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};
+
+    \draw node at (0,3.5) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
+    \draw node at (-2,1.6) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
+    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
+    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+
+\end{tikzpicture}
+\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $G_{\Pcal,n}(\alpha,\nu)$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
+\label{fig:representation_disjoint_neighborhoods_P_n_2}
+\end{figure}~
+\begin{figure}[p]
+\centering
+\begin{tikzpicture}
+
+	%The box \Rcal_n
+	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
+
+    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
+    \draw node at (-0.2,1.3) {$p$};
+
+    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (4.5,0.5) {};
+    \draw node at (4.3,0.2) {\color{blue}$p^\prime$};
+
+	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
+    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
+    \draw[domain=5.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-4.5)-0.5});
+    \draw[domain=3.2160:-5,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(4.5-\x)-0.5});
+    \draw[domain=2:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+7.5)-0.5});
+
+    \draw[dashed,black,line width=1pt] (-6,0.8563) -- (6,0.8563);
+
+    \draw node at (-7,0.8563) {$h(p,p^\prime)$};
+    \draw node at (7,0.3109) {\color{blue}$h_1(p^\prime)$};
+
+    \draw [decorate,decoration={brace},line width=1pt] (3.2160,-0.1) -- (1.6487,-0.1);
+    \draw node at (2.5,-0.45) {$d(p,p^\prime)$};
+
+    \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
+    \draw node at (2.5298,2) {$x^\ast(p,p^\prime)$};
+
+%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
+%    \draw[dotted,thick,black] (4.5208,2.0174) -- (6,2.0174);
+
+%    \draw node at (4.5208,-0.5) {$w_x(p,p^\prime)$};
+%    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};
+
+    \draw node at (2.3,3.6) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
+    \draw node at (-1,2) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
+    \draw node at (-4.5,2.9) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
+    \draw node at (4.5,2.9) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+
+\end{tikzpicture}
+\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $G_{\Pcal,n}(\alpha,\nu)$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:disjoint_neighbors_P_n_large}.}
+\label{fig:representation_disjoint_neighborhoods_P_n_3}
+\end{figure}
+
+We start by analyzing the shape of the neighborhoods.
+Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal_n$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$ and $y^\prime \le y$.
+To understand the computation it is helpful to have a picture of the different situations.
+Figure \ref{fig:representation_disjoint_neighborhoods_P_n} and Figure \ref{fig:representation_disjoint_neighborhoods_P_n_2} show two different situations for small distance in the $x$-coordinates, in which case the number of disjoint neighbors is small.
+The case where this distance is large, and the number of disjoint neighbors is expected to be large, is show in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+There are several different quantities that are important.
+The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal_n$.
+Note that when $x = 0$ then these height are the same and we denote this by $h(y)$.
+We also need to know the coordinates $h(p,p^\prime)$ and $x^\ast(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$.
+Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, compare Figures \ref{fig:representation_disjoint_neighborhoods_P_n} and \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+The full expressions of all these functions are given below for further reference.
+
+\begin{align}
+	h(y) &= R_n - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
+	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R_n}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
+	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R_n}{2}} - x^\prime\right) - y^\prime 
+		\label{eq:def_height_right_P_n} \\
+%	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
+%		\label{eq:def_x_intersection_close_boundaries}\\
+%	\iota_y(p,p^\prime) &= 2\log\left(\frac{x^\prime - x}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}\right)
+%		\label{eq:def_y_intersection_close_boundaries}\\
+	h((p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
+	x^\ast(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	
+		e^{\frac{y^\prime}{2}}},\\
+	d(p,p^\prime) &= |x - x^\prime| - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
+	\label{eq:def_d_p_p_prime}
+\end{align}
+
+We start with the result for points whose $x$-coordinates are close, which is when $d(p,p^\prime) < 0$.
+
+\begin{lemma}\label{lem:disjoint_neighbors_P_n}
+Let $p, p ^\prime \in \Rcal_n$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
+\begin{align*}
+	\Exp{\Ncal_{\Pcal,n}(p \Delta p^\prime)}
+	&\ge \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
+	&\hspace{10pt}+ \xi_{\alpha, \nu}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
+		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
+\end{align*}
+\end{lemma}
+
+\begin{proof}
+In order to proof the result we will consider the area in between the two left boundaries of the balls $\BallPon{p}$ and
+$\BallPon{p^\prime}$ up to the height $h^\ast := \min\{h(y), h_2(p^\prime)\}$, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n} and Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_2} for reference.
+Note that here we do not need to consider different cases depending on whether $|x - x^\prime| \le e^{(y + y^\prime)/2}$ or $|x - x^\prime| > e^{(y + y^\prime)/2}$.
+
+By the Campbell-Mecke formula we get
+\begin{align*}
+	\Exp{\Ncal_{\Pcal,n}(p \Delta p^\prime)} &=	\Mu{B_{\Pcal,n}(p) \Delta B_{\Pcal,n}(p^\prime)}\\
+	&\ge \int_0^{h^\ast} \int_{x - e^{\frac{y + y_1}{2}}}^{x^\prime - e^{\frac{y^\prime + y_1}{2}}} f_{\alpha,\nu}(x_1,y_1)
+		\, dx_1 \, dy_1 \\
+	&= \frac{\alpha \nu}{\pi}|x^\prime - x| \int_{0}^{h^\ast} e^{-\alpha y_1} dy_1
+		+ \frac{\alpha \nu}{\pi}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right| \int_0^{h^\ast} 
+		e^{-(\alpha-\frac{1}{2})y_1} \, dy_1\\
+	&= \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
+	&\hspace{10pt}+ \xi_{\alpha, \nu}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
+		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
+\end{align*}
+\end{proof}
+
+Now we will consider the case where $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$
+
+\begin{lemma}\label{lem:disjoint_neighbors_P_n_large}
+Let $p, p^\prime \in \Rcal_n$. Then, whenever $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
+\[
+	\Exp{\Ncal_{\Pcal,n}(p\Delta p^\prime)}
+	\ge \left(\mu_{\alpha,\nu}(\BallPon{p}) + \mu_{\alpha,\nu}(\BallPon{p^\prime})\right)
+		\left(1-\phi_n(p,p^\prime)\right).
+\]
+
+\[
+	\phi_n(p,p^\prime) = \xi_{\alpha, \nu}\left( \left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
+	- e^{-(\alpha - \frac{1}{2})R_n}\right)
+\]
+\end{lemma}
+
+\begin{proof}
+We will prove the results by using that
+\[
+	\Exp{\Ncal_{\Pcal,n}(p\Delta p^\prime)} 
+	\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f_{\alpha,\nu}(x_1,y_1) \, dx_1 \, dy_1,
+\]
+and computing the integral on the right. We refer to Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3} for further clarification.
+
+Before we proceed we show that the neighborhoods of $p$ and $p^\prime$ below $h(p,p^\prime)$ are disjoint.
+This is clearly true when $h(p,p^\prime) \le h_2(p^\prime)$ so suppose that $h(p,p^\prime) > h_2(p^\prime)$.
+Then, because we identified the right and left boundaries of the box $\Rcal_n$ the right boundary of $\BallPon{p^\prime}$ continues from the left boundary of the box and is described by the equation
+\[
+	x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}} - \pi e^{\frac{R_n}{2}}.
+\]
+Now, let $x_{\mathrm{right}}^\prime$ and $x_{\mathrm{left}}$ denote the $x$-coordinate of the intersection of the line $h(p,p^\prime)$ with, respectively, the right boundary of $\BallPon{p^\prime}$ and the left boundary of $\BallPon{p}$.
+Then
+\begin{align*}
+	x_{\mathrm{right}}^\prime &= x^\prime + e^{\frac{y^\prime + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+	&= x^\prime + e^{\frac{h(p,p^\prime)}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+		- e{\frac{y + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+	&= x^\prime + |x - x^\prime| - e{\frac{y + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+	&= x - e{\frac{y + h(p,p^\prime)}{2}} + 2|x - x^\prime| - \pi e^{\frac{R_n}{2}}\\
+	&\le x - e{\frac{y + h(p,p^\prime)}{2}} = x_{\mathrm{right}},
+\end{align*}
+and hence the neighborhoods of $p$ and $p^\prime$ below $h(p,p^\prime)$ are disjoint. It then follows that
+\begin{align*}
+	\Exp{\Ncal_{\Pcal,n}(p,p^\prime)} 
+	&\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f_{\alpha,\nu}(x_1,y_1) \, dx_1 \, dy_1\\
+	&= \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+		\left(\ind{p_1 \in \BallPon{p}} + \ind{p_1 \in \BallPon{p^\prime}}\right) 
+		f_{\alpha,\nu}(x_1,y_1) \, dx_1 \, dy_1\\
+	&= \left(\mu_{\alpha,\nu ,n}(\BallPon{p}) + \mu_{\alpha,\nu ,n}(\BallPon{p^\prime})\right)
+		\left(1 - \frac{2\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1\right),
+\end{align*}
+from which the result follows since
+\begin{align*}
+	\frac{2\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1 
+	&= \xi_{\alpha, \nu}\left(e^{-(\alpha - \frac{1}{2})h(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
+	&= \xi_{\alpha, \nu}\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
+		- e^{-(\alpha - \frac{1}{2})R_n}\right).
+\end{align*}
+\end{proof}
+
+%\begin{figure}
+%\centering
+%\begin{tikzpicture}
+%	
+%	%The box \Rcal_n
+%	\draw (-5,0) -- (10,0);
+%	\draw (-5,4) -- (10,4);
+%	
+%	
+%	\draw[domain=1:5,smooth,variable=\x,black] plot (\x, {2*ln(\x)});
+%    \draw[domain=-1:-5,smooth,variable=\x,black] plot (\x, {2*ln(-\x)});
+%    \draw[domain=6:10,smooth,variable=\x,black] plot (\x, {2*ln(\x-5)});
+%    \draw[domain=0:4,smooth,variable=\x,black] plot (\x, {2*ln(5-\x)});
+%    
+%    
+%    
+%    \draw node at (-1,2.5) {$B_{\Pcal}(p) \setminus B_{\Pcal}(p^\prime)$};
+%    
+%    \draw node at (-0.2,3.6) {$x_1 = x^\prime - e^{\frac{y^\prime+y_1}{2}}$};
+%    
+%    \draw node at (2.5,3) {$\Ncal_{\Pcal}(p,p^\prime)$};
+%    
+%    \draw node at (5.2,3.6) {$x_2 = x+e^{\frac{y+y_2}{2}}$};
+%    
+%    \draw node at (6,2.5) {$B_{\Pcal}(p^\prime) \setminus B_{\Pcal}(p)$};
+%    
+%    \draw[dashed,thick] (2.5,1.8326) -- (2.5,0.7);
+%    \draw node at (2.5,0.4) {$w(p,p^\prime)$};
+%    
+%    \draw[dashed,thick] (-3,1.8326) -- (8,1.8326);
+%    \draw node at (-4,1.8326) {$h(p,p^\prime)$};
+%    
+%    \draw [decorate,decoration={brace},line width=1pt] (4,-0.1) -- (1,-0.1);
+%    \draw node at (2.5,-0.45) {$d(p,p^\prime)$};
+%    
+%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,0) {};
+%    \draw node at (0,-0.5) {$p$};
+%    
+%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (5,0) {};
+%    \draw node at (5,-0.5) {$p^\prime$};
+%\end{tikzpicture}
+%\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $G_{\Pcal,n}$ used for the proof of Lemma \ref{lem:common_neighbors_Pcal_n}.}
+%\label{fig:representation_joint_neighborhoods}
+%\end{figure}
+
+Next we consider the number of common neighbors between two nodes $p$ and $p^\prime$ in $G_{\Pcal}$, which we denote by $\Ncal_{\Pcal}(p,p^\prime)$.
+
+\begin{lemma}\label{lem:common_neighbors_Pcal_n}
+Let $p, p^\prime \in \Rcal_n$. Then, whenever $|x - x^\prime| > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
+\[
+	\Exp{\Ncal_{\Pcal,n}(p,p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)\phi_n(p,p^\prime),
+\]
+where
+\[
+	\phi_n(p,p^\prime) = \frac{1 + 2\alpha}{4\alpha}\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
+	+ \frac{2\alpha - 1}{4\alpha}|x^\prime - x|e^{-\alpha R_n} - e^{-(\alpha - \frac{1}{2})R_n}. 
+\]
+\end{lemma}
+
+\begin{proof}
+Assume, without loss of generality, that $y \ge y^\prime$ and $x \le x^\prime$ and consider the boundaries of the balls $\BallPon{p}$ and $\BallPon{p^\prime}$ as drawn in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+The left boundary of $\BallPon{p}$ intersects the right boundary of $\BallPon{p^\prime}$ if an only if $d(p,p^\prime) > 0$.
+We observe from the definition of $d(p,p^\prime)$, \eqref{eq:def_d_p_p_prime}, that this is exactly the condition we imposed in the statement of the lemma.
+The $y$-coordinate of the intersection is then given by
+\[
+	h((p,p^\prime) := 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right).
+\]
+Therefore,
+\begin{align*}
+	\Exp{\Ncal_{\Pcal,n}(p,p^\prime)} 
+	&= \int_{h(p,p^\prime)}^{R_n} \int_{x^\prime - e^{(y^\prime+y_1)/2}}^{x + e^{(y + y_1)/2}}
+		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
+	&= \left(e^{y/2} + e^{y^\prime/2}\right)\frac{\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} 
+		e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\\
+	&\hspace{10pt}- (x^\prime - x) \frac{\alpha \nu}{\pi} \int_{h(p,p^\prime)}^{R_n} e^{-\alpha y_1} \dd y_1.
+\end{align*}
+
+For the first term we get
+\begin{align*}
+	&\hspace{-30pt}\left(e^{y/2} + e^{y^\prime/2}\right)\frac{\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} 
+		e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\\
+	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(
+		e^{-(\alpha - \frac{1}{2})h(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
+	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(\left(\frac{|x^\prime - x|}{e^{y/2} + 	
+		e^{y^\prime/2}}\right)^{-(2\alpha - 1)} - e^{-(\alpha - \frac{1}{2})R_n}\right).
+\end{align*}
+For the other term we compute
+\begin{align*}
+	&\hspace{-30pt}(x^\prime - x) \frac{\alpha \nu}{\pi} \int_{h(p,p^\prime)}^{R_n} e^{-\alpha y_1} \dd y_1\\
+	&= (x^\prime - x) \frac{\nu}{\pi}\left(e^{-\alpha(p,p^\prime)} - e^{-\alpha R_n}\right)\\
+	&= \frac{\nu}{\pi}\left(e^{y/2} + e^{y^\prime/2}\right) \left(
+		\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
+		- (x^\prime - x)e^{-\alpha R_n}\right)\\
+	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(
+		\frac{2\alpha - 1}{4\alpha}\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
+		- \frac{2\alpha - 1}{4\alpha}|x^\prime - x|e^{-\alpha R_n}\right).
+\end{align*}
+Combining these two results and noticing that $\xi_{\alpha, \nu} e^{y/2} = \Mu{\BallPon{p}}$ and similar for $p^\prime$ finishes the proof.
+\end{proof}
+
+\subsubsection*{Degrees}
+
+We now turn to the joint degree distribution of nodes in $G_{\Pcal,n}$. To ease notations we introduce the following short-hand notation for the conditional joint degree distribution
+\[
+	\rho_n(p,p^\prime,k,k^\prime) 
+	:= \Prob{D_{\Pcal,n}(p) = k, D_{\Pcal,n}(p^\prime) = k^\prime}.
+\]
+
+We first establish an almost independence result for integrals over the joint degree distribution $\rho_{n}(p,p^\prime,k,k^\prime)$ for the case where  $p$ and $p^\prime$ are sufficiently separated.
+For this we note that when $|x - x^\prime| \gg e^{y/2} + e^{y^\prime/2}$ it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large}
+\[
+	\Exp{\Ncal_{\Pcal,n}(p \Delta p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)(1 + \smallO{1}),
+\] 
+for $p, p^\prime \in \Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$.
+This implies that the joint neighborhoods are almost independent and hence their degrees must be as well.
+To make this more precise, let $0 < \varepsilon < \min\{(2\alpha - 1)^{-1},1\}$ and define the following two sets
+\begin{align}
+	\mathcal{E}(k_n) &= \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
+			\, : \, |x - x^\prime| > \left(e^{y/2} + e^{y^\prime/2}\right) \log(n)
+		\right\} \label{eq:def_joint_degree_set_E_constant_k} \\
+	\mathcal{E}_{\varepsilon}(k_n) &= \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
+		\, : \, \Exp{\Ncal_{\Pcal,n}(p, p^\prime)} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. \label{eq:def_joint_degree_set_E_growing_k}
+\end{align}
+
+The next result shows that for integrals over either $\mathcal{E}(k_n)$, when $k_n = \bigT{1}$, or $\mathcal{E}_{\varepsilon}(k_n)$, when $k_n \to \infty$, the joint degree distribution satisfies $\rho_n(p,p^\prime,k_n,k_n) = (1 + \smallO{1})\rho(p,k_n)\rho(p^\prime,k_n)$.
+
+\begin{lemma}\label{lem:joint_degree_factorization}
+Let $k_n \to \infty$ be such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ let $h : \R_+ \to \R$ be a uniformly bounded function and set
+\[
+	\mathcal{E}_n := \begin{cases}
+		\mathcal{E}(k_n) &\mbox{if } k_n = \bigT{1}\\
+		\mathcal{E}_\varepsilon(k_n) &\mbox{if } k_n \to \infty.
+	\end{cases}
+\]
+Then, as $n \to \infty$,
+\begin{align*}
+	&\hspace{-30pt}\int_{\mathcal{E}_n} \rho_{n}(p,p^\prime,k_n,k_n) h(y)h(y^\prime) 
+		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&= (1+\smallO{1})\int_{\mathcal{E}_n} \rho(y,k_n)\rho(y^\prime,k_n) h(y)h(y^\prime) 
+		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+\end{align*}
+\end{lemma}
+
+\begin{proof}
+Recall that $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Now define the random variables
+\begin{align*}
+	X_1(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p}\setminus \BallPon{p^\prime}}\right),\\
+	X_2(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p^\prime}\setminus \BallPon{p}}\right),\\
+	X_3(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p} \cup \BallPon{p^\prime}}\right),
+\end{align*}
+and note that
+\begin{align*}
+	\rho_{n}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
+	&= \sum_{t = 0}^\infty \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}.
+\end{align*}
+
+We proceed with the case $k_n \to \infty$.
+
+\noindent {\bf Case $\bm{k_n \to \infty}$:}\\
+Define $\delta_n = k_n^{-\frac{(1-\varepsilon)\varepsilon}{2}}$.
+Then, since $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\Pcal,n}(p,p^\prime)} \ge k_n^{\varepsilon}$ for $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, a Chernoff bound (c.f.
+\eqref{eq:def_chernoff_bound_poisson}) implies that
+\[
+	\Prob{|X_3(p,p^\prime) - \Exp{X_i(p,p^\prime)}| > \delta_n \Exp{X_3(p,p^\prime)}} = \bigO{e^{-k_n^{\varepsilon}}}.
+\]
+If we now define
+\[
+	A_n(p,p^\prime) = \left\{t : (1 - \delta_n) \Exp{X_3(p,p^\prime)} \le t \le (1+\delta_n)\Exp{X_3(p,p^\prime)}\right\},
+\]
+then it follows that
+\begin{align*}
+	&\hspace{-30pt}\sum_{t > \lfloor (1+\delta_n)\Exp{X_3(p,p^\prime)} \rfloor} \Prob{X_3(p,p^\prime) = t} 
+		\Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}\\
+	&\le \Prob{X_3(p,p^\prime) > (1+\delta_n)\Exp{X_3(p,p^\prime)} }\\
+	&\le \Prob{\left|X_3(p,p^\prime) - \Exp{X_3(p,p^\prime)}\right| > \delta_n \Exp{X_3(p,p^\prime)}}\\
+	&= \bigO{e^{-k_n^\varepsilon}},
+\end{align*}
+and similar for the sum over all $t < (1 - \delta_n) \Exp{X_3(p,p^\prime)}$. Hence we conclude that
+\begin{align*}
+	&\hspace{-20pt}\rho_{n}(p,p^\prime,k_n,k_n) \\
+	&= \sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
+		\Prob{X_2(p,p^\prime) = k_n - t} + \bigO{e^{-k_n^\varepsilon}}
+		\numberthis \label{eq:joint_degrees_separation}
+\end{align*}
+
+The idea for the remainder of the proof is to first remove the dependence on $p$ and $p^\prime$ in the summation over $t$ so that
+\[
+	\rho_{n}(p,p^\prime,k_n,k_n) = (1 + \smallO{1})\Prob{X_1(p,p^\prime) = k_n - t_n}
+			\Prob{X_2(p,p^\prime) = k_n - t_n}
+	+ \bigO{e^{-k_n^\varepsilon}},
+\]
+where $t_n = \smallO{k_n}$. Then, since $\Exp{X_1(p,p^\prime)} = \Mu{\BallPon{p}\setminus \BallPon{p^\prime}} = 
+(1 + \smallO{1})\Mu{\BallPon{p}}$, by Lemma~\ref{lem:disjoint_neighbors_P_n_large}, and similar for $X_2$, the proof will follow by applying a concentration argument twice.
+
+To execute this plan we note that $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\Pcal,n}(p,p^\prime)}$.
+Now recall the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n}.
+Then, for $p,p^\prime \in \Kcal_{C}(k_n)$ we have that
+\begin{align*}
+	\phi_n(p,p^\prime) 
+	&\le \frac{1 + 2\alpha}{4\alpha}\left(\frac{k_n^{1 + \varepsilon}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)} 
+	- \left(1-\frac{(2\alpha - 1)\pi}{4\alpha}\right)e^{-(\alpha - \frac{1}{2})R_n}\\
+	&\le \frac{1 + 2\alpha}{4\alpha}\left(\frac{k_n^{1 + \varepsilon}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
+		=\bigT{k_n^{-\varepsilon(2\alpha - 1)}},
+\end{align*}
+where we used that $|x - x^\prime| \le \pi e^{R_n/2}$. In a similar fashion we get
+\begin{align*}
+	\phi_n(p,p^\prime) 
+	&\ge \frac{1 + 2\alpha}{4\alpha}\left(\frac{\pi e^{R_n/2}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
+		+ \frac{2\alpha - 1}{4\alpha} k_n^{1 + \varepsilon}e^{-\alpha R_n} - e^{-(\alpha - \frac{1}{2})R_n}\\
+	&\ge \frac{1 + 2\alpha}{4\alpha}\left(\frac{\pi e^{R_n/2}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
+		- e^{-(\alpha - \frac{1}{2})R_n} = \bigT{k_n^{2\alpha - 1}n^{-(2\alpha - 1)}}.
+\end{align*}
+Therefore, since $\Mu{\BallPo{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$ for $p,p^\prime \in \Kcal_{C}(k_n)$, there exist two $n$-dependent constants 
+\[
+	b_n^- = \bigT{k_n^{2\alpha} n^{-(2\alpha - 1)}} \quad \text{and} \quad
+	b_n^+ = \bigT{k_n^{1 - \varepsilon(2\alpha - 1)}}
+\]
+such that
+\[
+	A_n(p,p^\prime) \subseteq \left\{t \, : \, (1-\delta_n)b_n^- \le t \le (1+\delta_n)b_n^+ \right\} := B_n.
+\]
+If we now define
+\begin{align*}
+	t_n^- &= \arg \min_{t \in B_n} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}\\
+	t_n^+ &= \arg \max_{t \in B_n} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t},
+\end{align*}
+then $t_n^\pm = \smallO{k_n}$ and we get
+\begin{align*}
+	&\hspace{-30pt}\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
+		\Prob{X_2(p,p^\prime) = k_n - t}\\
+	&\le \Prob{X_1(p,p^\prime) = k_n - t_n^+}\Prob{X_2(p,p^\prime) = k_n - t_n^+} 
+		\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t}\\
+	&= \Prob{X_1(p,p^\prime) = k_n - t_n^+}\Prob{X_2(p,p^\prime) = k_n - t_n^+}(1 + \smallO{1}).
+		\numberthis \label{eq:joint_degrees_upper_bound}
+\end{align*}
+and similarly
+\begin{align*}
+	&\hspace{-30pt}\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
+		\Prob{X_2(p,p^\prime) = k_n - t}\\
+	&\ge \Prob{X_1(p,p^\prime) = k_n - t_n^-}\Prob{X_2(p,p^\prime) = k_n - t_n^-}(1 + \smallO{1}).
+		\numberthis \label{eq:joint_degrees_lower_bound}
+\end{align*}
+Next, it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large} that
+\[
+	\Mu{\BallPon{p}}(1 - \phi_n(p,p^\prime))\le \Exp{X_1(p,p^\prime)} \le \Mu{\BallPon{p}},
+\]
+where
+\[
+	\sup_{p,p^\prime \in \mathcal{E}_\varepsilon(k_n)} \phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
+\]
+This implies that on $\mathcal{E}_\varepsilon(k_n)$, $\mu_n^{(1)}(p) := \Exp{X_1(p,p^\prime)}$ satisfies the assumptions of Lemma~\ref{lem:concentration_argument_rho_approximation}.
+The same conclusion holds for $\mu_n^{(2)}(p^\prime)$.
+Therefore, if we write $\hat{\rho}_n^{(i)}(p,k) := \Prob{X_i(p,p^\prime) = k - t_n^\pm}$, the second statement of the Lemma~\ref{lem:concentration_argument_rho_approximation} (applied twice) yields
+\begin{align*}
+	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \hat{\rho}_{n}^{(1)}(p,k_n) \hat{\rho}_{n}^{(2)}(p^\prime,k_n) h(y)h(y^\prime) 
+		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&= (1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
+			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+\end{align*}
+Together with the approximation~\eqref{eq:joint_degrees_separation} and the bounds~\eqref{eq:joint_degrees_upper_bound} and~\eqref{eq:joint_degrees_lower_bound} we get
+\begin{align*}
+	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) h(y) h(y^\prime) f_{\alpha,\nu}(x,y)
+		f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&=(1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
+		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&\hspace{10pt} + \bigO{1} e^{-k_n^{\varepsilon}} \int_{\mathcal{E}_{\varepsilon}(k_n)}
+		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,			
+\end{align*}
+and the result follows since the last term is of smaller order than the first.\\
+\vspace{5pt}
+
+\noindent {\bf Case $\bm{k_n = \bigT{1}}$:}\\
+This proof is very similar to the previous one. Here however, we write
+\begin{align*}
+	\rho_{n}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
+	&= \Prob{X_3(p,p^\prime) = 0}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} 
+		+ \bigO{\Prob{X_3(p,p^\prime) \ge 1}}.
+\end{align*}
+By definition of $\mathcal{E}(k_n)$ and the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n} we get that for $(p,p^\prime) \in \mathcal{E}(k_n)$
+\[
+	\Exp{X_3(p,p^\prime)} \le \bigT{1} \log(n)^{-(2\alpha - 1)} + \bigT{1}e^{-(\alpha - \frac{1}{2})R_n},
+\]
+where we used that in this case $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{1}$ and $|x-x^\prime| \le \bigT{1} e^{R_n/2}$. This implies that
+\[
+	\Prob{X_3(p,p^\prime) \ge 1} \le \Exp{X_{3}(p,p^\prime)} = \bigO{\log(n)^{-(2\alpha - 1)}},
+\] 
+Next we observe that by definition of $\mathcal{E}(k_n)$ the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:disjoint_neighbors_P_n_large} satisfies
+\[
+	\sup_{(p,p^\prime) \in \mathcal{E}(k_n)} \phi_n(p,p^\prime) = \bigO{\log(n)^{-(2\alpha - 1)}}.
+\]
+Therefore we can apply the exact same arguments as for the case $k_n \to \infty$ to obtain
+\begin{align*}
+	&\int_{\mathcal{E}(k_n)} \rho_n(y,y^\prime,k_n,k_N) h(y)h(y^\prime) 
+		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&=(1+\smallO{1})\int_{\mathcal{E}(k_n)} \hspace{-5pt}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} h(y) h(y^\prime) 	
+		f_{\alpha,\nu}(x,y)f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&\hspace{10pt}+ \bigO{1}\log(n)^{-(2\alpha - 1)} \int_{\mathcal{E}(k_n)}
+		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&= (1+\smallO{1})\int_{\mathcal{E}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
+		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,
+\end{align*}
+where we used that
+\[
+	\log(n)^{-(2\alpha - 1)}\int_{\mathcal{E}(k_n)}
+			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime
+\]
+is of smaller order than
+\[
+	\int_{\mathcal{E}_(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
+			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+\]
+\end{proof}
+
+Next we show that when $k_n \to \infty$ and the expected number of disjoint neighbors of $p$ and $p^\prime$ in $\Kcal_{C}(k_n)$ grows only slightly with $k_n$ then any fixed shift in the joint degree distribution does not effect its asymptotic behavior.
+
+\PvdH{The proof of this lemma follows almost the exact same steps as that of the previous one. Is there any way we could merge them?}
+
+\begin{lemma}\label{lem:joint_degree_distribution_shift}
+Let $\alpha > \frac{1}{2}$, $\nu > 0$, $k_n \to \infty$ and fix $\varepsilon > 0$.
+Then for any fixed $i, j, i^\prime, j^\prime \in \mathbb{Z}$ and $p, p^\prime \in \Kcal_{C}(k_n)$ such that $\Exp{\Ncal_{\Pcal,n}(p \Delta p^\prime)} \ge k_n^\varepsilon$,
+\[
+	\rho_n(p,p^\prime,k_n + i,k_n + i^\prime) 
+	= (1 + o(1))\rho_n(p,p^\prime, k_n + j,k_n + j^\prime)  \pm e^{-\Omega(k_n^\varepsilon)}.
+\]
+\end{lemma}
+
+\begin{proof}
+Define
+\begin{align*}
+	X_n = \left|\BallPon{p} \setminus \BallPon{p^\prime}\right|,\\
+	Y_n = \left|\BallPon{p} \cap \BallPon{p^\prime}\right|,\\
+	Z_n = \left|\BallPon{p^\prime} \setminus \BallPon{p}\right|.
+\end{align*}
+Then it follows that $X_n$, $Y_n$ and $Z_n$ are independent Poisson random variables satisfying $\Exp{X_n} + \Exp{Y_n} = \Mu{B_{\Pcal,n}(p)}$ and $\Exp{Z_n} + \Exp{Y_n} = \Mu{B_{\Pcal,n}(p^\prime)}$ while
+\begin{align*}
+	\rho_n(p,p^\prime,k_n + i,k_n + i^\prime) &= \Prob{X_n + Y_n = k + i, Z_n + Y_n = k + i^\prime}\\
+	&= \sum_{\ell = 0}^\infty \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell, Z_n = k + i^\prime - \ell} \\
+	&= \sum_{\ell = 0}^\infty \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell} \Prob{Z_n = k + i^\prime - \ell}.
+\end{align*}
+Next define $\delta_n = k_n^{-\frac{1-\varepsilon}{2}}$, let $n$ be large enough such that $0 < \delta_n < 1$ and note that by a Chernoff bound,
+\[
+	\Prob{|X_n - \Exp{X_n}| > \delta_n \Exp{X_n}} = \bigO{e^{-\frac{\delta_n^2}{4(1+\delta_n)} \Exp{X_n}}},
+\]
+and similar for $Y_n$ and $Z_n$. Finally, we define
+\begin{align*}
+	L_X(k_n) &= \left\{\ell : (1 - \delta_n) \Exp{X_n} \le k + i - \ell \le (1+\delta_n)\Exp{X_n}\right\} \\
+	L_y(k_n) &= \left\{\ell : (1 - \delta_n) \Exp{Y_n} \le \ell \le (1+\delta_n)\Exp{Y_n}\right\}\\
+	L_Z(k_n) &= \left\{\ell : (1 - \delta_n) \Exp{Z_n} \le k + i^\prime - \ell \le (1+\delta_n)\Exp{Z_n}\right\}
+\end{align*}
+We will now make distinguish between the cases $\Exp{Y_n} \le k_n/2$ and $\Exp{Y_n} > k_n/2$.
+
+Let us first assume that $\Exp{Y_n} \le k_n/2$.
+Then, since $p \in \Kcal_{\varepsilon}(k_n)$ and $\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \bigT{e^{y/2}} = \bigT{k_n}$ it follows that $\Exp{X_n} = \Omega(k_n)$ and hence
+\[
+	\Prob{|X_n - \Exp{X_n}| > \delta_n \Exp{X_n}} = \bigO{e^{-\frac{\delta_n^2}{4(1+\delta_n)} \Exp{X_n}}} = e^{-\Omega(k_n^{(1+\varepsilon)/2})} = e^{-\Omega(k_n^{\varepsilon})}.
+\]
+In particular, this implies
+\begin{align*}
+	&\hspace{-30pt}\sum_{\ell \notin L_X} \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell} 
+			\Prob{Z_n = k + i^\prime - \ell}\\
+	&= \bigO{\Prob{|X_n - \Exp{X_n}| > \delta_n \Exp{X_n}}} = e^{-\Omega(k_n^{(1+\varepsilon)/2})}.
+\end{align*}
+Finally we note that, for $\ell \in L_X$, we have
+\begin{equation}\label{eq:fraction_degree_prob}
+	\frac{\Prob{X_n = k + i - \ell}}{\Prob{X_n = k + j - \ell}} = \Exp{X_n}^{i - j} \frac{(k + j - \ell)!}{(k + i - \ell)!}
+	\le (1 + \delta_n)^{2|i - j|}.
+\end{equation}
+and observe that we have similar results for $Z_n$. Therefore,
+\begin{align*}
+	&\hspace{-30pt}\sum_{\ell \in L_X \cap L_Z} \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell} 
+		\Prob{Z_n = k + i^\prime - \ell} \\
+	&\le (1+\delta_n)^{2(j-i) + 2(j^\prime - i^\prime)} \sum_{\ell \in L_x \cap L_Z} 
+			\Prob{Y_n = \ell} \Prob{X_n = k + j - \ell} \Prob{Z_n = k + j^\prime - \ell}\\
+	&= (1+o(1))(1+\delta_n)^{2|i-j| + 2|i^\prime - j^\prime|}\Prob{D_p = k_n + j, D_{p^\prime} = k_n + j^\prime}\\
+	&= (1+o(1))\Prob{D_p = k_n + j, D_{p^\prime} = k_n + j^\prime}
+\end{align*}
+and hence
+\begin{align*}
+	\rho_n(p,p^\prime,k+i,k^\prime+i^\prime)
+	&= (1+o(1))\rho_n(p,p^\prime,k+j,k^\prime+j^\prime) + e^{-\Omega(k_n^\varepsilon)}.
+\end{align*}
+
+Now assume that $\Exp{Y_n} > k_n/2$.
+Then, since $\Exp{\left|\Ncal_{\Pcal,n}(p \Delta p^\prime)\right|} \ge k_n^{\varepsilon}$ it follows that $\Exp{X_n} = \Omega(k_n^\varepsilon)$ or $\Exp{Z_n} = \Omega(k_n^\varepsilon)$.
+Without loss of generality we assume that $\Exp{X_n} = \Omega(k_n^\varepsilon)$.
+Similar to \eqref{eq:fraction_degree_prob} we have for $Y_n$
+\[
+	\frac{\Prob{Y_n = \ell}}{\Prob{Y_n = \ell + j^\prime - i^\prime}} \le (1 + \delta_n)^{2(|i^\prime - j^\prime|)}.
+\]
+Using similar computations as above we then have
+\begin{align*}
+	&\hspace{-30pt}\rho_n(p,p^\prime,k+i,k^\prime+i^\prime) \\
+	&= \sum_{\ell \in L_X \cap L_Y} \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell}
+		\Prob{Z_n = k + i^\prime - \ell}  + e^{-\Omega(k_n^{(1+\varepsilon)/2})}\\
+	&= (1+o(1))\rho_n(p,p^\prime,k+j,k^\prime+j^\prime) + e^{-\Omega(k_n^{(1+\varepsilon)/2})}.
+\end{align*}
 \end{proof}
@@
 \[
-	\widetilde{T}_{\Pcal,n}(k,C)^2 = \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k)}
-		\ind{D_{\Pcal,n}(p), \, D_{\Pcal,n}(p^\prime) = k} 
-		\sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in 2^{\Pcal_n}}
-		T_{\Pcal}(p,p_1,p_2) T_{\Pcal}(p^\prime, p_1^\prime, p_2^\prime),
+	\widetilde{T}_{\Pcal,n}(k,C)^2 = \hspace{-5pt} \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k)}
+		\hspace{-3pt} \ind{D_{\Pcal,n}(p), \, D_{\Pcal,n}(p^\prime) = k} 
+		\sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in \Pcal_n \setminus (0,y)}^{\ne} \hspace{-3pt}
+		\widetilde{T}_{\Pcal}(p,p_1,p_2) \widetilde{T}_{\Pcal}(p^\prime, p_1^\prime, p_2^\prime),
 \]
-with $2^{\Pcal_n}$ denoting the distinct pairs in $\Pcal_n$.
 This expression can be written as the sums of several terms, depending on how $\{p, p_1, p_2\}$ and $\{p^\prime, p_1^\prime, p_2^\prime\}$ intersect.
@@
 \[
-	J_b(p,p^\prime) = \hspace{-10pt} \sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in 2^{\Pcal_n} 
-		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b}
-		\hspace{-5pt} T_{\Pcal,n}(p,p_1,p_2) T_{\Pcal,n}(p^\prime, p_1^\prime, p_2^\prime).
+	J_b(p,p^\prime) = \hspace{-10pt} \sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal_n 
+		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b}^{\ne}
+		\hspace{-5pt} T_{\Pcal,n}(p,p_1,p_2) T_{\Pcal,n}(p^\prime, p_1^\prime, p_2^\prime),
 \]
-Then we have
+with the summation being over all two distinct pairs $(p_1, p_2)$ and $(p_1^\prime, p_2^\prime)$. Then we have
 \[
@@
 
+To prove~\eqref{eq:transition_clustering_main_term} and~\eqref{eq:transition_clustering_error_term} we have to consider the cases $k_n = \bigT{1}$ and $k_n \to \infty$ separately.
+However, each case follows a similar strategy.
+First we define a set $\mathcal{E} \subseteq \Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$ such that outside this set the contributions of $\Exp{I_{a,b}}$ are negligible while on this set the joint degree distribution factorizes.
+These will be the sets defined by~\eqref{eq:def_joint_degree_set_E_constant_k} and~\eqref{eq:def_joint_degree_set_E_growing_k}.
+In particular, for these sets we have that $a = 1$ is not possible and hence we only need to consider the three different cases for $b$.
+For $a =0 = b$, the factorization of the degree distributions will enable us to prove~\eqref{eq:transition_clustering_main_term}.
+For $b = 1, 2$ we derive sufficient bounds for $\Exp{J_b(p,p^\prime)}$ in terms of $k_n$ for $(p,p^\prime)$ in the set $\mathcal{E}$.
+
 \begin{proof}[Proof of Proposition \ref{prop:concentration_tilde_T_P_n}]
 
-\PvdH{Include the case $k_n = \bigT{1}$.}
+Throughout this proof we set $i = |\{p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\} \cap \BallPon{p}|$, $j = |\{p^\prime\} \cap \BallPon{p}|$ and define $i^\prime, j^\prime$ in a similar way by interchanging the primed and non-primed variables.
+In addition, we write $D_{\Pcal,n}(p,p^\prime,k,\ell)$ to denote the indicator that $|\BallPon{p} \cap (\Pcal_n \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = k$ and $|\BallPon{p^\prime} \cap (\Pcal_n \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = \ell$.
+Then,
+\begin{align*}
+	&\Exp{\ind{D_{\Pcal,n}(p) = k_n, D_{\Pcal,n}(p^\prime) = k_n} J_b(p,p^\prime)}\\
+	&= \Exp{\sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal_n 
+		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b}^{\ne}
+			\hspace{-7pt} D_{\Pcal,n}(p,p^\prime, k_n-i,k_n- i^\prime) \,
+			\widetilde{T}_{\Pcal,n}(p,p_1,p_2) \widetilde{T}_{\Pcal,n}(p^\prime, p_1^\prime, p_2^\prime)},
+\end{align*}
+where the sum is over all distinct pairs $(p_1, p_2)$ and $(p_1^\prime, p_2^\prime)$. We also that 
+\[
+	\Exp{T_\Pcal(k_n)} = \bigT{n k_n^{-(2\alpha - 1)} s_\alpha(k_n)}.
+\]
 
-The technical steps of this proof use Lemma \ref{lem:joint_degree_distribution_shift} and Lemma \ref{lem:joint_degree_distribution_P_n}, which deal with the joint degree distribution.
-Let $\Ncal_{\Pcal,n}^c(p,p^\prime)$ denote the number of nodes not connected to both $p$ and $p^\prime$ an fix $0 < \eps < (2\alpha - 1 \wedge 1)$.
-To be able to apply both lemmas, we first show that we only need to consider the case where $\Exp{\left|\Ncal_{\Pcal,n}^c(p,p^\prime)\right|} \ge k_n^{\varepsilon}$ and $|x - x^\prime| > k_n^{1+\eps}$.
-To this end define
+The prove is split over the two cases $k_n = \bigT{1}$ and $k_n \to \infty$.
+
+\subsubsection*{The case $\bm{k_n = \bigT{1}}$}
+
+Take $a_n = 2\log\left((k_n + C\log(n))/\xi_{\alpha, \nu}\right)$ and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}(k_n)$ as defined in~\eqref{eq:def_joint_degree_set_E_constant_k}.
+We will show that the expected difference between $I_{a,b}$ and $I_{a,b}^\ast$ is of smaller order than $\Exp{T_\Pcal(k_n)}^2$ so that we only need to consider $I_{a,b}^\ast$.
+
+Since 
+\[
+	|x - x^\prime| \le \left(e^{y/2} + e^{y^\prime/2}\right)\left(\frac{k_n + C \log(n)}{\xi_{\alpha,\nu}}\right)
+	= \bigO{\log(n)^2}
+\] 
+for all $p,p ^\prime \in \mathcal{E}_C(k_n)^c$, it follows that
+\begin{align*}
+	&\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} \\
+	&\le \int_{\mathcal{E}_{C}(k_n)^c} 
+		\Exp{\ind{D_{\Pcal,n}(p) = k_n - i, \, D_{\Pcal,n}(p^\prime) = k_n - i^\prime} J_b(p,p^\prime)}
+		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{J_b(p,p^\prime)}
+		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)}
+		\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} 
+		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)} 
+		f_{\alpha, \nu}(x,y) \dd x \dd y\right)	
+		\left(\int_0^{a_n} \Delta_\Pcal(y^\prime) e^{-\alpha y^\prime} \dd y^\prime\right) \\
+	&= \bigO{\log(n)^2 s_\alpha(k_n) \Exp{T_\Pcal(k_n)}},
+\end{align*}
+where the last line follows from Corollary~\ref{cor:adjusted_triangle_counting_P_n} and Proposition~\ref{prop:asymptotics_Delta_y_P} which states that for all $0 < y^\prime \le a_n$, $\Delta_\Pcal(y^\prime) = \bigO{s_\alpha(k_n)}$.
+Next we note that $\Exp{T_\Pcal(k_n)} = \bigT{n k_n^{-(2\alpha - 1)} s_\alpha(k_n)}$, hence $\log(n)^2 s_\alpha(k_n) = \smallO{\Exp{T_\Pcal(k_n)}}$ and therefore we conclude that
+\[
+	\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} = \smallO{\Exp{T_\Pcal(k_n)}^2}.
+\]
+
+We now proceed with computing $I_{a,b}^\ast$.
+For this we note that the parts of the neighborhoods $\BallPon{p}$ and $\BallPon{p^\prime}$ where $y_1, y_1^\prime \le h(p,p^\prime)$ are disjoint, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+In particular, this implies that when $b \ne 0$ this can only be if one of the $y_1, y_2, y_1^\prime, y_2^\prime$ exceeds $h(p,p^\prime)$.
+Now we observe that for $(p,p^\prime) \in \mathcal{E}(k_n)$ we have
+\begin{align*}
+	\int_{h(p,p^\prime)}^{R_n}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
+	&= \bigO{e^{y/2} e^{-(\alpha - \frac{1}{2})h(p,p^\prime)}}
+		= \bigO{\log(n)^{-(2\alpha - 1)}},
+\end{align*}
+while
+\begin{align*}
+	\int_0^{h(p,p^\prime)}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
+	&= \bigO{1}.
+\end{align*} 
+Hence if $b \ne 0$ then it follows that $\Exp{J_b} = \bigO{\log(n)^{-(2\alpha - 1)}}$ and we conclude that 
+\[
+	\Exp{I_{a,b}} = \bigO{n^2 \log(n)^{-(2\alpha - 1)}} = \smallO{\Exp{T_\Pcal(k_n)}^2}
+\]
+
+For $I_{0,0}^\ast$ we define
+\[
+	\mathcal{J}_1^\ast = \int_{\Rcal_n^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) 
+			f_{\alpha,\nu}(x_1,y_1)	f_{\alpha,\nu}(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
+\] 
+and define $\mathcal{J}_2^\ast$ in a similar way by interchanging the primed and non-primed variables. Then we get
+\[
+	\Exp{J_0(p,p^\prime)} = \mathcal{J}_1^\ast \mathcal{J}_2^\ast + \bigO{\log(n)^{-(2\alpha - 1)}}.
+\]
+In addition, for $(p,p^\prime) \in \mathcal{E}(k_n)$ Corollary~\ref{cor:adjusted_triangle_counting_P_n} implies that 
+\[
+	\mathcal{J}_1^\ast = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1 + \smallO{1})\binom{k_n}{2} \Delta_\Pcal(y),
+\] 
+and similar for $\mathcal{J}_2^\ast$, while Lemma~\ref{lem:joint_degree_factorization} states that
+\begin{align*}
+	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
+		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+	&= (1+\smallO{1})\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2.
+\end{align*}
+We therefore conclude that
+\begin{align*}
+	\Exp{I_{0,0}^\ast} 
+	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
+		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
+	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
+		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+	&\hspace{10pt}+ \bigO{\log(n)^{-(2\alpha - 1)}n^2} \\
+	&= (1 + \smallO{1}) \binom{k_n}{2}^2 
+		\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2 \\
+	&= (1 + \smallO{1})\Exp{T_\Pcal(k_n)}^2,
+\end{align*}
+which finishes the proof for $k_n = \bigT{1}$
+
+\subsubsection*{The case $\bm{k_n \to \infty}$}
+
+\PvdH{Check this proof!}
+
+Recall the definition of $\mathcal{E}_\varepsilon(k_n)$
 \[
@@
 \]
-and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $p,p^\prime \in \Pcal_n \cap \mathcal{E}_\varepsilon(k_n)$. We first show that
-\begin{eqnarray}\label{eq:I_ab_ast_main}
+let $\mathcal{E}_\varepsilon(k_n)^c$ denote its complement and, similar to the previous case, let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $p,p^\prime \in \Pcal_n \cap \mathcal{E}_\varepsilon(k_n)$.
+We first show that
+\begin{equation}\label{eq:I_ab_ast_main}
 	\Exp{I_{a,b} - I_{a,b}^\ast} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
-\end{eqnarray}
-so that for the remainder of the proof we only need to consider $p, p^\prime \in \mathcal{E}_\varepsilon(k_n)$ and hence, we can apply Lemma \ref{lem:joint_degree_distribution_shift} and Lemma \ref{lem:joint_degree_distribution_P_n} to the joint degree distribution inside the integral.
-
-Note that for all $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ we have that $e^{\frac{y^\ast}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) = \bigT{k_n^2}$, where $y^\ast = \min\{y,y^\prime\}$.
-Hence by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ with $\Exp{\left|\Ncal_{\Pcal,n}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ and $|x-x^\prime| > k_n^{1+\varepsilon}$ that either
-\[
-	|x - x^\prime| + \left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right| = O\left(k_n^\varepsilon\right)
-	\quad \text{or} \quad
-	\Exp{\left|\Ncal_{\Pcal,n}(p\Delta p^\prime)\right|} = \Omega(k_n).
-\]
-In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \notin \mathcal{E}_{\varepsilon}(k_n)$. Therefore, we have
+\end{equation}
+so that for the remainder of the proof we only need to consider $p, p^\prime \in \mathcal{E}_\varepsilon(k_n)$ and hence, we can apply Lemma \ref{lem:joint_degree_factorization}.
+For this we note that by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\Pcal,n}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$.
+In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)^c$.
+Therefore, we have
 \begin{align*}
@@
 
-We will now proceed to establish \eqref{eq:variance_T_I_00} and \eqref{eq:variance_T_I_ab}. We split these up into separate subsections because each term requires different bounding techniques.
+We will now proceed to establish \eqref{eq:variance_T_I_00} and \eqref{eq:variance_T_I_ab}. We start with $I_{0,0}^\ast$
 
-\vspace{5pt}
-
-\paragraph{I) $\bm{I_{0,0}^\ast}$:}
-Let $i = |\{p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\} \cap B_{\Pcal,n}(p)|$ and $j = |\{p^\prime \cap B_{\Pcal,n}(p)\}|$ and let $i^\prime, j^\prime$ be defined, similarly, by interchanging the primed and non-primed variables.
-Then, by Lemma  \ref{lem:joint_degree_distribution_shift} and  Lemma \ref{lem:joint_degree_distribution_P_n}
+By Lemma~\ref{lem:joint_degree_distribution_shift} 
 \[
 	\rho_(p,p^\prime, k_n-i,k_n-i^\prime) = (1+o(1))\rho(p,p^\prime, k_n-j,k_n-j^\prime) 
-	= (1+o(1))\rho_{n}(p, k_n)\rho_{n}(p^\prime,k_n) 
+	= (1+o(1))\rho_{n}(p, p^\prime, k_n, k_n)
 \]
-which now no longer depends on the other four points $p_1, p_2, p_1^\prime, p_2^\prime$. Hence, using the Mecke formula, we get
+which now no longer depends on the other four points $p_1, p_2, p_1^\prime, p_2^\prime$. Hence, using the Campbell-Mecke formula, we get
 \[
-	\Exp{I_{0,0}^\ast} = \frac{1 + \smallO{1}}{4}\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{n}(p, k_n)\rho_{n}(p^\prime,k_n)
+	\Exp{I_{0,0}^\ast} = (1 + \smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{n}(p,p^\prime,k_n, k_n)
 		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y)
@@
 \]
-where the factor $\frac{1}{4}$ is because we consider distinct pairs $(p_1,p_2)$ and $(p_1^\prime, p_2^\prime)$.
 
-Next, by Lemma \ref{lem:clustering_error_T_term} and Proposition~\ref{prop:asymptotics_average_clustering_ast_P} we have for $y \in K_C(k_n)$,
+Next, by Corollary~\ref{cor:adjusted_triangle_counting_P_n} we have for $y \in K_C(k_n)$,
 \[
-	\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal}(p)} = (1 + \smallO{1}) k_n^2 \Delta_{\Pcal}(y)
+	\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal}(p)} = (1 + \smallO{1}) \binom{k_n}{2} \Delta_{\Pcal}(y)
 \] 
-and similar result holds for $p^\prime$. Hence 
+and similar for $p^\prime$. Hence, by Lemma~\ref{lem:joint_degree_factorization} 
 \begin{align*}
-	&\hspace{-10pt}\frac{1 + \smallO{1}}{4} \int_{\mathcal{E}_\varepsilon(k_n)} \rho_{p,p^\prime}(k-j,k-j^\prime)
+	&\hspace{-10pt}(1 + \smallO{1})\int_{\mathcal{E}_\varepsilon(k_n)} \rho_n(p, p^\prime, k_n, k_n)
 		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y)
@@
 	&= (1+\smallO{1})\binom{k_n}{2}^2 \int_{\mathcal{E}_\varepsilon(k_n)} 
-		\rho_{p,p^\prime}(k-j,k-j^\prime) \Delta_{\Pcal}(y) \Delta_\Pcal(y^\prime) 	f_{\alpha,\nu}(x,y) 
+		\rho(y, k_n) \rho(y^\prime, k_n) \Delta_{\Pcal}(y) \Delta_\Pcal(y^\prime) 	f_{\alpha,\nu}(x,y) 
 		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
-	&= (1+\smallO{1}) \left( \binom{k_n}{2} \int_{a_n^-}^{a_n^+}\int_{I_n} \rho_{y,n}(k_n)
+	&= (1+\smallO{1}) \left( \binom{k_n}{2} \int_{a_n^-}^{a_n^+}\int_{I_n} \rho(y,k_n)
 		\Delta_{\Pcal}(y) f_{\alpha,\nu}(x,y) \, dx \, dy\right)^2\\
-	&= (1 + \smallO{1})\left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right)^2,
+	&= (1 + \smallO{1})\left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}\right)^2,
 \end{align*}
@@
 
-\paragraph{II) $\bm{I_{0,1}^\ast}$:}
+Next we consider $I_{0,1}^\ast$. The proofs for the other two cases $I_{1,1}^\ast$ and $I_{0,2}^\ast$ follow using similar arguments and hence we omit them here.
+
 Without loss of generality we will assume that $p_1 = p_1^\prime$.
-Similar to the previous computations, we let $i = |\{p^\prime, p_1, p_2, p_2^\prime\} \cap B_{\Pcal,n}(p)|$ and $j = |\{p^\prime\} \cap B_{\Pcal,n}(p)|$ and let $i^\prime$, $j^\prime$ be defined, similarly, by interchanging the primed and non-primed variables.
+Notice that now $i = |\{p^\prime, p_1, p_2, p_2^\prime\} \cap B_{\Pcal,n}(p)|$ and $j = |\{p^\prime\} \cap B_{\Pcal,n}(p)|$ and $i^\prime$, $j^\prime$ are defined, similarly, by interchanging the primed and non-primed variables.
 Then, if we define
@@
 \begin{align*}
-	\Exp{I_{0,1}^\ast} &= \frac{1+\smallO{1}}{2} \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_n(p,k)\rho_n(p^\prime,k)
+	\Exp{I_{0,1}^\ast} &= (1+\smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_n(p,p^\prime,k_n,k_n)
 			\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)} f_{\alpha,\nu}(x,y)
@@
 \end{align*} 
-where we again used Lemma  \ref{lem:joint_degree_distribution_shift} and  Lemma \ref{lem:joint_degree_distribution_P_n}.
+where we again used Lemma  \ref{lem:joint_degree_distribution_shift}.
 We will show that 
@@
 \begin{align*}
-	\bigO{e^{y}e^{\frac{y^\prime}{2}} \int_{4\log(k_n)}^{a_n^+} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}\\
+	\bigO{e^{y}e^{\frac{y^\prime}{2}} \int_{4\log(k_n)}^{a_n^+} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}
 	&= \bigO{k_n^3 \int_{4\log(k_n)}^{a_n^+} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}\\
@@
 
-The proofs for the other two cases $I_{0,2}^\ast$ and $I_{0,2}^\ast$ follow using similar arguments.
-
 %\paragraph{III) $\bm{I_{0,2}^\ast}$:}

### 2018-11-17 concentration_argument.tex
updated sections 5 and 6 with respect to changes in section 3

@@
 \]
-\item If, in addition, $h_n(y) = \hat{\rho}_n(y,k_n) g_n(y)$ with $g_n$ satisfying $g_n(y(1+\smallO{1}) = (1+\smallO{1})g_n(y)$, we have,
+\item for any uniformly bounded function $h : \R_+ \mapsto \R$,
 \[
-	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
-	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
+	\int_{\Rcal_n} h(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y 
+	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
 \]
@@
 \[
-	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) g_n(y) e^{-\alpha y} \dd y
-	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) g_n(z) e^{-\alpha z} \dd z.
+	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) h(y) e^{-\alpha y} \dd y
+	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z.
 \] 
-For this we observe that~\eqref{eq:concentration_argument_z_upper_bound} and~\eqref{eq:concentration_argument_z_lower_bound} imply that $y = z(y) + \smallO{1}$ for $a_n^- \le y \le a_n^+$ and hence, by our assumption on $g_n(y)$ we have that
-\[
-	g_n(y) = g_n(z + \smallO{1}) = (1 + \smallO{1})g_n(z).
-\]
+For this we observe that~\eqref{eq:concentration_argument_z_upper_bound} and~\eqref{eq:concentration_argument_z_lower_bound} imply that there exists a $b_n \to 0$ such that $y = z(y) + b_n$, uniformly for $a_n^- \le y \le a_n^+$.
+Hence, if we define $g_n(z) = h(z + b_n)$, then $g_n(z)$ is uniformly bounded and converges point wise to $h(z)$.
 Therefore, with the change of variables~\eqref{eq:concentration_argument_variable_change} we get
 \begin{align*}
-	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) g_n(y) e^{-\alpha y} \dd y
-	&=  \int_{a_n^-}^{a_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} g_n(y) e^{-\alpha y} \dd y\\
+	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) h(y) e^{-\alpha y} \dd y
+	&=  \int_{a_n^-}^{a_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(y) e^{-\alpha y} \dd y\\
 	&= (1 + \smallO{1})\int_{a_n^-}^{a_n^+}  \Prob{\Po(\mu(z))}
 		g_n(z) e^{-\alpha z} \frac{\hat{\mu}_n^\prime(z)}{\mu^{\prime}(z)} \dd z\\
-	&= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) g_n(z) e^{-\alpha z} \dd z.
+	&= (1 + \smallO{1})\int_{a_n^-}^{a_n^+}  \Prob{\Po(\mu(z))}
+		g_n(z) e^{-\alpha z} \dd z\\
+	&= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z.
 \end{align*}
-
+where the last line follow by dominated convergence.
 \end{proof}

### 2018-11-17 proof_overview.tex
updated sections 5 and 6 with respect to changes in section 3

@@
 \end{proposition}
-\MS{I think we can drop the condition to be increasing here and below, also the $n^{1/3}$ should be removed.}
+%\MS{I think we can drop the condition to be increasing here and below, also the $n^{1/3}$ should be removed.}
 
@@
 \begin{proposition}[Coupling result for local clustering]\label{prop:couling_c_H_P}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any increasing sequence such that $k_n = \smallO{\min\left\{n^{\frac{1}{2\alpha + 1}}, n^{\frac{1}{3}}\right\}}$. Then, as $n \to \infty$,
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any positive sequence such that $k_n \ge 3$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, as $n \to \infty$,
 \[

### 2018-11-17 transition.tex
updated sections 5 and 6 with respect to changes in section 3

@@
 The first step is to relate the clustering in the infinite model to that of the finite box model $G_{\Pcal, n}$.
-Recall that $G_{\Pcal,n}$ is obtained by restricting the Poisson Point Process to the box $\Rcal_n = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$, and connecting two points $p_1, p_2 \in \Rcal_n$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$ where we identified the left and right boundary of $\Rcal_n$.
+Recall that $G_{\Pcal,n}$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal_n = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ (we write $\Pcal_n$ for this process), and connecting two points $p_1, p_2 \in \Rcal_n$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$ where we identified the left and right boundary of $\Rcal_n$.
 See Section~\ref{ssec:finite_model} for more details.
@@
 \[
-	\sum_{p_1,p_2 \in 2^\Pcal_n} T_{\Pcal,n}(p_0,p_1,p_2) - \widetilde{T}_{\Pcal,n}(p_0,p_1,p_2)
-	= \sum_{p_1,p_2 \in 2^\Pcal_n} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)}
-\]
+	\sum_{p_1,p_2 \in \Pcal_n \setminus (0,y)}^{\ne} T_{\Pcal,n}(p_0,p_1,p_2) - \widetilde{T}_{\Pcal,n}(p_0,p_1,p_2)
+	= \sum_{p_1,p_2 \in \Pcal_n \setminus (0,y)}^{\ne} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)},
+\]
+where the sums are over all distinct pairs $(p_1, p_2) \in \Pcal_n \setminus \{(0,y)\}$.
 
@@
 \[
-	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\int_{\Rcal_n} \Exp{\ind{D_{\H,n}(y) = k_n} T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}.
+	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\int_{\Rcal_n} \Exp{\ind{D_{\Pcal,n}(y) = k_n} T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}.
 \]
@@
 	\Exp{N_{\Pcal,n}(k_n)} = (1+o(1)) \alpha n \int_{0}^\infty \rho(y,k_n) e^{-\alpha} \dd y 
-	= (1+\smallO{1}) \alpha n \Exp{N_{\Pcal}(k_n)},
-\]
-and since $\ind{D_{\H,n}(y) = k_n} T_{\Pcal,n}(y) \le \rho_n(y,k_n) k_n^2$ another concentration argument yields
+	= (1+\smallO{1}) n \Exp{N_{\Pcal}(k_n)},
+\]
+and since $\Exp{\ind{D_{\H,n}(y) = k_n} T_{\Pcal,n}(y)} \le \rho_n(y,k_n) k_n^2$ another concentration argument yields
 \begin{align*}
@@
 		f_{\alpha,\nu}(x,y) \dd x \dd y\\
-	&= (1+\smallO{1})\int_{\Kcal_C(k_n)} \rho(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
-	&= (1 + \smallO{1}) \alpha n \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha} \dd x \dd y,
-\end{align*}
-with $a_n^\pm = 2\log\left(\frac{k_n \pm C \kappa_n}{\xi_{\alpha,\nu}}\right)$. It now suffices to show that
-\[
-	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha} \dd x \dd y
-	= (1+\smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd x \dd y, 
-\]
-which follows if we can show that
-\[
-	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(y) - T_{\Pcal}(y)}\right| e^{-\alpha} \dd y
-	= \smallO{1} \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd y.
-\]
-
-For this we write
+	&= (1+\smallO{1})\int_{\Kcal_C(k_n)} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
+	&= (1 + \smallO{1}) \alpha n \int_{a_n^-}^{a_n^+} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha} \dd x \dd y,
+\end{align*}
+with $a_n^\pm = 2\log\left(\frac{k_n \pm C \kappa_n}{\xi_{\alpha,\nu}}\right)$. Next we note that for $a_n^- \le y \le a_n^-$,
+\[
+	\Exp{T_\Pcal(y)} = \frac{\Mu{\BallPo{y}}^2}{2} \Delta_\Pcal(y) = (1+\smallO{1}) \binom{k_n}{2} \Delta_\Pcal(y)
+\]
+and hence it now suffices to show that
+\[
+	\binom{k_n}{2}^{-1}\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha y} \dd y
+	= (1+\smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Delta_\Pcal(y) e^{-\alpha y} \dd y. 
+\]
+
+We do this in two stages. First we prove that
+\begin{equation}\label{eq:transition_clustering_main_term}
+	\int_{a_n^-}^{a_n^+} \rho_{n}(y,k_n) \Delta_{\Pcal}(y) e^{-\alpha y} \dd y
+	= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Delta_{\Pcal}(y) e^{-\alpha y} \dd y.
+\end{equation}
+Then we show that
+\begin{equation}\label{eq:transition_clustering_error_term}
+	\binom{k_n}{2}^{-1} \int_{a_n^-}^{a_n^+} \rho_n(y,k_n) \left|\Exp{T_{\Pcal,n}(y) - T_{\Pcal}(y)}\right| 
+	e^{-\alpha y} \dd y
+	= \smallO{1} \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Delta_{\Pcal}(y) e^{-\alpha y} \dd y.
+\end{equation}
+
+Since $h(y) := \Delta_\Pcal(y)$ is uniformly bounded \eqref{eq:transition_clustering_main_term} follows directly from the second statement in Lemma~\ref{lem:concentration_argument_rho_approximation}.
+
+For the error term~\eqref{eq:transition_clustering_error_term} we write
 \begin{align*}
@@
 \begin{align*}
-	&\hspace{-30pt}\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| 
+	&\hspace{-30pt}\binom{k_n}{2}^{-1}\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| 
 		e^{-\alpha} \dd y\\
-	&= \bigO{1} n^{-(2\alpha - 1)} k_n^2 \int_{0}^\infty \rho(y,k_n) f_{\alpha,\nu}(x,y) \dd y\\
-	&= \bigO{1} n^{-(2\alpha - 1)} k_n^{-2\alpha + 1}.
-\end{align*}
-
-To finish the argument we observe that
-\begin{align*}
-	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd y 
-	&= (1 + \smallO{1})\int_0^\infty \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd y \\
-	&= \bigT{1} \binom{k_n}{2} \int_0^\infty \rho(y,k_n) \Delta_\Pcal(y) e^{-\alpha} \dd y\\
-	&= \bigT{1} k_n^{2} \Exp{N_{\Pcal}(k_n)} c_\infty(k_n)
-		= \bigT{k_n^{-2\alpha + 1} s_\alpha(k_n)}.
-\end{align*}
-Therefore, since $n^{-(2\alpha - 1)} = \smallO{s_\alpha(k_n)}$ by Lemma~\ref{lem:scaling_s_alpha}, we conclude that
-\begin{align*}
-	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| e^{-\alpha} \dd y 
-	&= \smallO{k_n^{-2\alpha + 1} s_\alpha(k_n)} \\
-	&= \smallO{1} \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Exp{T_{\Pcal}(y)} e^{-\alpha} \dd y,
-\end{align*}
-which completes the proof.
-
+	&= \bigO{1} n^{-(2\alpha - 1)} \int_{0}^\infty \rho(y,k_n) f_{\alpha,\nu}(x,y) \dd y\\
+	&= \bigO{1} n^{-(2\alpha - 1)} k_n^{-(2\alpha + 1)} = \smallO{s_\alpha(k_n) k_n^{-(2\alpha + 1)} },
+\end{align*}
+where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. To finish the argument we observe that
+\begin{align*}
+	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \Delta_\Pcal(y) e^{-\alpha} \dd y
+	&= \bigT{1} \Exp{N_{\Pcal}(k_n)} c_\infty(k_n) = \bigT{ s_\alpha(k_n) k_n^{-(2\alpha + 1)}}.
+\end{align*}
 \end{proof}
 
-%\begin{corollary}
-%\[
-%	\Exp{T_{\Pcal,n}(k_n)} = \begin{cases}
-%		\bigT{n k_n^{-3(2\alpha - 1)}} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4}\\
-%		\bigT{n \log(k_n) k^{-2\alpha}} &\mbox{if } \alpha = \frac{3}{4} \\
-%		\bigT{n k^{-2\alpha}} &\mbox{if } \alpha > \frac{3}{4}.
-%	\end{cases}
-%\]
-%\end{corollary}
-%
-%\begin{remark}
-%Note that for $p_0 \notin \Kcal_\varepsilon(k_n)$, we could have proven that
-%\[
-%	\left|\Delta_{\Pcal, n}(y) - \Delta_{\Pcal}(y)\right| = \bigO{n^{-\lambda}e^{(\alpha -\frac{1}{2})y}},
-%\]
-%for some $\lambda > 0$. However, this would have required us to do a more thorough analysis of the integral
-%\[
-%	\int_{\mathcal{E}_n} \Delta(p_0,p_1,p_2)g_{p_0}(x_1,y_1) g_{p_0}(x_2,y_2) \, dx_2 \, dx_1 \, dy_2 \, dy_1,
-%\]
-%making the proof more cumbersome. Since for our purpose we only need the $e^{\beta y}$ term, we omitted this additional analysis.
-%\end{remark}
-
-%\subsection{Equivalence for local clustering in $G_{\Pcal}(\alpha, \nu)$ and $G_{\Pcal,n}(\alpha,\nu)$}
-%
-%We now proceed with the proof of Proposition \ref{prop:convergence_average_clustering_P_n}. For this we split 
-%$\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - \Exp{c_{\Pcal}^\ast(k_n)}\right|$ into three different terms which each evaluate the difference between the different elements of the local clustering function.
-We then analyze each term separately.
-The main tool we use is Lemma \ref{lem:clustering_error_Delta_term} together with the splitting technique we used in the proof of Lemma \ref{lem:asymptotics_integral_outside_K_epsilon}, which considers the integral over $\Kcal_\varepsilon(k_n)$ and $\Rcal_n \setminus \Kcal_\varepsilon(k_n)$ separately.
-%
-%\begin{lemma}
-%\[
-%	\lim_{n \to \infty} \frac{\Exp{\widetilde{T}_{\Pcal,n}(k,\varepsilon)}}{\Exp{T_{\Pcal}(k)}} = 1.
-%\]
-%\end{lemma}
-%
-%\begin{proof}[Proof of Proposition \ref{prop:convergence_average_clustering_P_n}]
-%
-%We give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$. The proof for the other cases are similar.
-%
-%Let $0 < \varepsilon < 1$ and recall the definition $a_n^\pm = 2\log\left(\frac{(1\pm\varepsilon)k_n}{2\xi_{\alpha,\nu}}\right)$. In addition, recall that
-%\[
-%	\Exp{c_{\Pcal,n}^\ast(k_n)} = \int_{\Rcal_n} \frac{\Delta_{\Pcal,n}(y) \rho_k(y)}{\Exp{N_{\Pcal,n}(k_n)} \binom{k_n}{2}}  
-%    f_{\alpha, \nu}(x,y) \, dx \, dy.
-%\]
-%
-%We now use Lemma \ref{lem:expectation_clustering_P} and \eqref{eq:expectation_clustering_P_n} to write
-%\begin{align*}
-%	\left|\Exp{c_{\Pcal,n}^\ast(k_n) - c_{\Pcal}^\ast(k_n)}\right|
-%	&= \left|\frac{\int_0^{R_n} \Delta_{\Pcal,n}(y) \, \rho_{n,y}(k_n) e^{-\alpha y} \, dy}
-%		{\int_0^{R_n} \rho_{n,y}(k_n) e^{-\alpha y} \, dy} 
-%		- \frac{\int_0^{\infty} \Delta_{\Pcal}(y) \, \rho_{y}(k_n) e^{-\alpha y} \, dy}
-%		{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy}\right|\\
-%	&\le \frac{\int_0^{R_n} \left|\Delta_{\Pcal,n}(y) \, \rho_{n,y}(k) - \Delta_{\Pcal}(y) \, \rho_{y}(k)\right| 
-%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy} \\
-%	&\hspace{10pt}+ \frac{\int_{R_n}^\infty \Delta_{\Pcal}(y) \, \rho_{y}(k) 
-%			e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy}\\
-%	&\hspace{10pt}+ \frac{\int_0^{R_n} \Delta_{\Pcal,n}(y) \, \rho_{n,y}(k) e^{-\alpha y} \, dy}
-%		{\int_0^{R_n}  \rho_{y}(k_n) e^{-\alpha y} \, dy}
-%		\left|\frac{\int_0^{R_n}  \rho_{y}(k_n) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{n,y}(k_n) e^{-\alpha y} \, dy}
-%		- 1\right|\\
-%	&:= I_n^{(1)}(k_n) + I_n^{(2)}(k_n) + I_n^{(3)}(k_n)
-%\end{align*}
-%We will deal with all three terms separately and show that
-%\begin{equation}
-%	\lim_{n \to \infty} k_n^{4\alpha - 2} I_n^{(i)}(k_n) = 0 \quad \text{for } i = 1, 2, 3.
-%\end{equation} 
-%
-%For $I_n^{(1)}(k_n)$ we write
-%\begin{align}
-%	I_n^{(1)}(k_n)	&\le \frac{\int_0^{R_n} \left|\Delta_{\Pcal,n}(y)  - \Delta_{\Pcal}(y) \right| \rho_{y}(k_n)
-%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy} 
-%        \label{eq:diff_Delta_integral}\\
-%	&\hspace{10pt}+ \frac{\int_0^{R_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\Pcal,n}(y) 
-%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy}. \label{eq:diff_Poisson_distribution}
-%\end{align}
-%
-%For \eqref{eq:diff_Delta_integral} we use Lemma \ref{lem:clustering_error_Delta_term} to obtain
-%\begin{align*}
-%	\int_0^{R_n} \left|\Delta_{\Pcal,n}(y)  - \Delta_{\Pcal}(y) \right| \rho_{y}(k_n) e^{-\alpha y} \, dy
-%    &\le \bigO{k_n^{-3(2\alpha - 1)}}\int_{a_n^-}^{a_n^+} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
-%    &\hspace{10pt}+ \bigO{n^{-(2\alpha - 1)}k^{2\alpha - 1}\int_0^\infty \Delta_\Pcal(y)\rho_{y}(k_n) e^{-\alpha y} 
-%    	\, dy}\\
-%    &\hspace{10pt}+ \bigO{\frac{1}{n}\int_{\Rcal_n \setminus \Kcal_\varepsilon(k_n)} e^{(\alpha - \frac{1}{2})y} 
-%    	\rho_{y}(k_n) f_{\alpha,\nu}(x,y) \, dx \, dy}.
-%\end{align*}
-%Observe that first term is bounded from above by
-%\[
-%	\bigO{k_n^{-3(2\alpha - 1)}} \int_0^\infty \rho_y(k_n) e^{-\alpha y} \, dy
-%\]
-%and recall that $\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy = \Theta\left(k_n^{-(2\alpha + 1)}\right)$. Hence
-%\begin{align*}
-%	&\hspace{-30pt}k_n^{4\alpha - 2} \, \frac{\int_0^{R_n} \left|\Delta_{\Pcal,n}(y) - \Delta_{\Pcal}(y) 
-%		\right| \rho_{y}(k_n) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy}\\
-%    &= \bigO{k_n^{4\alpha - 2} k_n^{-3(2\alpha - 1)}} + \bigO{n^{-(2\alpha - 1)}k^{2\alpha - 1}} k_n^{4\alpha - 2}\Exp{c_\Pcal^\ast(k_n)}\\
-%	&\hspace{10pt}+ \bigO{k_n^{6\alpha - 1} \frac{1}{n}\int_{\Rcal_n \setminus \Kcal_\varepsilon(k_n)} e^{(\alpha - \frac{1}{2})y} 
-%    	\rho_{y}(k_n) f_{\alpha,\nu}(x,y) \, dx \, dy}.
-%\end{align*}
-%The first term here is $\bigO{k_n^{-(\alpha - \frac{1}{2})}}$ which converges to zero.
-The second term converges to zero by [Proposition on scaling] and the fact that $n^{-(2\alpha - 1)}k^{2\alpha - 1} = o(1)$.
-The same holds for the third term by Lemma \ref{lem:asymptotics_integral_outside_K_epsilon}.
-%
-%For \eqref{eq:diff_Poisson_distribution} we apply the same splitting technique as in the proof of Lemma \ref{lem:clustering_error_Delta_term}.
-That is, we take $0 < \varepsilon < 1$, $a_n^+ = 2\log\left((1+\varepsilon)k_n\right)$ and write
-%\begin{align*}
-%	\int_0^{R_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) e^{-\alpha y} \, dy
-%	&= \int_0^{a_n^+} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) e^{-\alpha y} \, dy\\
-%	&\hspace{10pt}+ \int_{a_n^+}^{R_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) e^{-\alpha y} \, dy
-%\end{align*}
-%Next we use Lemma \ref{lem:mu_measure_B} to obtain
-%\begin{align*}
-%	\rho_{n, y}(k_n) &= \rho_y(k_n) \left((1+\phi_n(y))^{k_n} \left(1 - e^{-\alpha R_n}\right)^{-k_n}
-%		e^{-\mu(B(0,y))\left(\phi_n(y) + \frac{(1 + \phi_n(y))e^{-\alpha R_n}}{1 - e^{-\alpha R_n}}\right)}\right).
-%\end{align*}
-%Using that
-%\begin{align*}
-%	\max_{0 \le y \le a_n} \hspace{-5pt} \phi_n(y)
-%	= O\left(n^{-(2\alpha - 1)(1-\kappa)}\right) \quad \text{and} \quad
-%	\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy = \Theta\left(k_n^{-(2\alpha + 1)}\right)
-%\end{align*}
-%we get for the first integral,
-%\begin{align*}
-%	&\hspace{-30pt}k_n^{4\alpha - 2}\frac{\int_0^{a_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) 
-%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy}\\
-%	&= O\left(n^{-(2\alpha - 1)(1-\kappa)} k_n^{4\alpha - 2}\frac{\int_0^\infty \Delta_{\mu}(y) \rho_{y}(k_n) e^{-\alpha y} 
-%		\, dy}{\int_0^{\infty} \rho_{y}(k_n) e^{-\alpha y} \, dy}\right)\\
-%	&= O\left(n^{-(2\alpha - 1)(1-\kappa)}\right).
-%\end{align*}
-%For the second integral we use that $\phi_n(y) = O(1)$ for all $0 \le y \le R_n$ and hence, using the same argumentation as at the end of the proof of Lemma \ref{lem:clustering_error_Delta_term},
-%\begin{align*}
-%	&\hspace{-30pt}k_n^{4\alpha - 2}\frac{\int_{a_n}^{R_n} \left|\rho_{n, y}(k) - \rho_{y}(k_n)\right| \Delta_{\mu_n}(y) 
-%		e^{-\alpha y} \, dy}{\int_0^\infty \rho_y(k_n) \, e^{-\alpha y} \, dy}\\
-%	&= O\left(k_n^{4\alpha - 2}\frac{\int_{a_n}^{R_n} \rho_{y}(k_n) \Delta_{\mu}(y) e^{-\alpha y} \, dy}
-%		{\int_0^\infty \rho_y(k_n) \, e^{-\alpha y} \, dy}\right)\\
-%	&= O\left(k_n^{6\alpha - 1}\rho_{a_n}(k_n)\right) = o(1).
-%\end{align*}
-%We therefore conclude that $k_n^{4\alpha - 2}I_n^{(1)}(k_n) \to 0$.
-%
-%Next we consider the second term
-%\[
-%	I_n^{(2)}(k_n) = \frac{\int_{R_n}^\infty \Delta_{\mu}(y) \, \rho_{y}(k) 
-%		e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy}.
-%\]
-%Since
-%\[
-%	\int_{R_n}^\infty \Delta_{\mu}(y) \, \rho_{y}(k) e^{-\alpha y} \, dy 
-%	\le \rho_{R_n}(k_n) \int_0^\infty e^{-\alpha y} \, dy = O\left(\rho_(R_n)(k_n)\right) 
-%	= O\left(\rho_{a_n}(k_n)\right),
-%\]
-%it follows from the above computations that
-%\[
-%	\lim_{n \to \infty} k_n^{4\alpha - 2} \frac{\int_{R_n}^\infty \Delta_{\mu}(y) \, \rho_{y}(k) 
-%	e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) e^{-\alpha y} \, dy} = 0.
-%\]
-%The proof for $I_n^{(3)}(k_n)$ follows using the same splitting technique and arguments. We therefore omit it.
-%\end{proof}
+Observe that the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} yields the following two corollaries, which will be useful later on in Section~\ref{sec:concentration_c_P_n}.
+
+\begin{corollary}\label{cor:adjusted_triangle_counting_P_n}
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $k_n$ be a positive sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, uniformly for all $p \in \Kcal_C(k_n)$, as $n \to \infty$
+\[
+	\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1+\smallO{1})\Exp{T_\Pcal(p)},
+\]
+where
+\[
+	\widetilde{T}_{\Pcal,n}(p) = \sum_{(p_1, p_2) \in \Pcal\setminus p}^{\ne} 
+		\ind{p_1 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal_n}.
+\]
+
+In particular,
+\[
+	\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_n(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y
+	= (1+\smallO{1}) \int_{\Rcal_n} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha, \nu}(x,y) \dd x \dd y. 
+\]
+\end{corollary}
 
@@
 
-Here we split the integration into three parts (see Figure~\ref{fig:shapes_triangle_mismatches}). Recall that $x^\ast(p,p_1) = x_1 - I_n$. Then, for the first part we have
+Here we split the integration into two parts (see Figure~\ref{fig:shapes_triangle_mismatches}). Recall that $x^\ast(p,p_1) = x_1 - I_n$. Then, for the first part we have
 \begin{align*}

### 2018-11-18 clustering_infinite_model.tex
final short pass before sending to Tobias and Nikolaos

@@
 
-Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$ \PvdH{Find reference.} we deduce that
+Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$ \PvdH{@All: Does anyone have a good standard reference for this?} we deduce that
 \begin{equation}\label{eq:degree_distribution_P_asymptotics}
@@
 899, 1032ff.]{gradshteyn2015table}).
-\PvdH{@Markus:What does entire mean?}
+\PvdH{@Markus: What does entire mean?}
 We can now evaluate the integral in~\eqref{eq:integral_gamma_function} using several identities for Meijer's $G$-function. 

### 2018-11-18 concentration.tex
final short pass before sending to Tobias and Nikolaos

@@
 
-Next we note that the second result from Corollary~\ref{cor:approximation_triangle_integral} states that
+Next we note that the second result from Corollary~\ref{cor:adjusted_triangle_counting_P_n} states that
 \begin{equation}\label{eq:asymptotic_equivalence_contraint_triangle_count}
@@
 We perform the analysis in this section.
-The two main results, which will be the crucial technical ingredients for the proof of Proposition~\ref{prop:concentration_tilde_T_P_n}, are Lemma ??
-and Lemma ??.
+The two main results, which will be the crucial technical ingredients for the proof of Proposition~\ref{prop:concentration_tilde_T_P_n}, are Lemma~\ref{lem:joint_degree_factorization} and Lemma~\ref{lem:joint_degree_distribution_shift}.
 
@@
 
-\PvdH{The proof of this lemma follows almost the exact same steps as that of the previous one. Is there any way we could merge them?}
+\PvdH{@All: The proof of this lemma follows almost the exact same steps as that of the previous one. Is there any way we could merge them?}
 
@@
 
-\PvdH{Check this proof!}
-
 Recall the definition of $\mathcal{E}_\varepsilon(k_n)$

### 2018-11-18 concentration_argument.tex
final short pass before sending to Tobias and Nikolaos

@@
 \end{equation}
-\MS{What does $\vee$ and $\wedge$ mean?}
+Where we recall that $a \vee b = \max\{a,b\}$ and $a \wedge b = \min\{a,b\}$.
 
@@
 \]
-\PvdH{It might be a good idea to add one more example of how the concentration argument is used in the paper.}
+\PvdH{ @All:It might be a good idea to add one more example of how the concentration argument is used in the paper. I someone finds a good example we use later on, please add it here.}
 \end{remark}
@@
 where the last step follows by our choice of $\varepsilon$. Hence it is enough to prove both statement on $\Rcal_n((1-\varepsilon)R_n, R_n)$ instead of $\Rcal_n$.
-\PvdH{This is where we use that $s < 2\alpha(2\alpha + 1)$. I think this can be removed by using a more careful bound but I am not sure this is needed.}
+\PvdH{@All: This is where we use that $s < 2\alpha(2\alpha + 1)$. I think this can be removed by using a more careful bound but I am not sure this is needed.}
 

### 2018-11-18 introduction.tex
updated sections 5 and 6 with respect to changes in section 3
final short pass before sending to Tobias and Nikolaos

@@
 Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
-Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{bode2015largest},~\cite{fountoulakis2018law}, [More?] and the number of cliques and the largest clique~\cite{blasius2018cliques}.
+Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{bode2015largest},~\cite{fountoulakis2018law} and the number of cliques and the largest clique~\cite{blasius2018cliques}.
+\PvdH{@All: Does anyone have other suggestions for results to add?}
 
@@
 In particular this result implies that the local clustering coefficient is asymptotically bounded away from zero.
-The convergence of this coefficient was not proven.
+The convergence of this coefficient was however not proven.
 In contrast, the global clustering coefficient was shown~\cite{candellero2016clustering} to converge in probability to some constant which can be explicitly stated as an integral expression, see Theorem 1.2 in \cite{candellero2016clustering}.
@@
 
-\PvdH{I recall that J{\'u}lia told me that the results from~\cite{komjathy2018explosion} imply that the local clustering coefficient converges, although they do not mention it in the paper.
+We remark that it is possible to prove that the local clustering coefficient converges to some limit, using the technical tools in the recent work on explosion times in Geometric Inhomogeneous Random Graphs~\cite{komjathy2018explosion}.
+However, this problem is not explicitly addressed in that paper, nor is there any reason to expect these tools to give us the exact expressions as we do derive in this work.
+
+%\PvdH{I recall that J{\'u}lia told me that the results from~\cite{komjathy2018explosion} imply that the local clustering coefficient converges, although they do not mention it in the paper.
 Should we added a comment related to this?}
 
-\MS{Yes, I think this would probably be good.
+%\MS{Yes, I think this would probably be good.
 Either after the sentence `the convergence of this coefficient was not proven' add something like, as you say, the results form ..
@@
 Section~\ref{sec:concentration_argument} contains a crucial technical result that will be used in the other sections.
-Finally, the Appendix contains a few general results for the hyperbolic random graph and a small section on Meijer's G-function.
+The Appendix contains a small section on Meijer's G-function and some known concentration results we use.
 
@@
 
-%, which without loss of generality we take to be $-1$~[CITE]
-%The \emph{Poincar\'{e} disc model} for the hyperbolic plane is defined by equipping the open unit disc in $\R^2$ with the metric given by the differential form $\dd s^2 = 4 \frac{\dd x^2 + \dd y^2}{(1 - x^2 - y^2)^2}$.
 The hyperbolic plane is an infinite $2$-dimensional manifold with constant negative curvature.
@@
 				&\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
-				\frac{3\nu}{\pi} &\mbox{if } \alpha = \frac{3}{4},\\
+				\frac{6\nu}{\pi} &\mbox{if } \alpha = \frac{3}{4},\\
 				\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha > \frac{3}{4},
@@
 \end{corollary}
-\MS{Are you sure all constants are correct? I thought for $\alpha = 3/4$ it might be $6\nu/\pi$. But if you are sure, you can remove this comment of course.}
+\MS{@Pim: Are you sure all constants are correct? I thought for $\alpha = 3/4$ it might be $6\nu/\pi$. But if you are sure, you can remove this comment of course.}
+\PvdH{@Markus: You might be right. I have updated it and we will later check if you were right.}
 
@@
 \PvdH{Populate these paragraphs}
-
-\paragraph{Local clustering function for growing versus fixed degrees}
-\MS{I'm currently not sure what we should comment here because now Thm 1.2 does cover both cases and the asymptotics in 1.4 appear as a very natural corollary.
-
-However, if we can, then it would be interesting to remark that there is this phase transition in $\alpha$ which appears when the power-law exponent is $2.5=\frac{5}{2}$ and it would be cool if we could give a brief intuitive reason for that or mention that this phase transition point has also been observed in other contexts/models etc.}
 
@@
 
-%Maybe, it would make sense to incorporate this statement into theorem \ref{thm:local_clustering_hyperbolic}, i.e.
-that the asymptotic behaviour of $c(k_n)$ is not well-defined for $k_n \gg n^{\frac{1}{2\alpha+1}}$?
-Resp.
-claim that a.a.s.
-the number of vertices of degree $k_n \gg n^{\frac{1}{2\alpha+1}}$ is zero, such that taking the average over these is not well-defined.
+\paragraph{Transition in the scaling of local clustering}
 
-%\paragraph{Transition in the scaling of local clustering}
-%Note that Theorem \ref{thm:local_clustering_hyperbolic} implies that for $\frac{1}{2} < \alpha < \frac{3}{4}$ the local clustering $c_{\H,n}(k)$ decays as $k^{-(4\alpha - 2)}$ while for $\alpha > \frac{3}{4}$ it is $k^{-1}$.
+\MS{@All: If we can, then it would be interesting to remark that there is this phase transition in $\alpha$ which appears when the power-law exponent is $2.5=\frac{5}{2}$ and it would be cool if we could give a brief intuitive reason for that or mention that this phase transition point has also been observed in other contexts/models etc.}
 
-%\paragraph{Universality of scaling transition}
-
-%\paragraph{Geometric inhomogeneous random graphs}
+\PvdH{@All: I agree with Markus.
+It would be nice to say something on this.
+Maybe we can leave it out of the first arXived version and in the mean time do some research on this.
+We could also ask Remco van der Hofstad.}
 
@@
     \includegraphics[scale=0.6]{figures/sim0123c2nualln1000rep20.pdf}
-    %\includegraphics[scale=0.5]{figures/sim0128c4nualln10000rep20.pdf}
     \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n= 2$, for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=1000$ and 20 repetitions.}

### 2018-11-18 proof_overview.tex
final short pass before sending to Tobias and Nikolaos

@@
 
+We start with some small notational conventions.
+
+\subsection{Notations}
+We adopt standard Landau notations for asymptotic statements. For two functions $f$ and $g$ we write $f(x) = \bigO{g(x)}$ as $x \to \infty$ if
+\[
+	\limsup_{x \to \infty} \frac{|f(x)|}{g(x)} < \infty,
+\]
+while $f(x) = \smallO{g(x)}$ as $x \to \infty$ means
+\[
+	\lim_{x \to \infty} \frac{f(x)}{g(x)} = 0,
+\]
+and $f(x) = \bigT{g(x)}$ as $x \to \infty$ whenever
+\[
+	\limsup_{x \to \infty} \left|\frac{f(x)}{g(x)}\right| > 0 \quad \text{and} \quad
+	\limsup_{x \to \infty} \frac{|f(x)|}{g(x)} < \infty.
+\]
+Moreover we will write $a \vee b$ for $\max\{a,b\}$ and $a \wedge b$ for $\min\{a,b\}$.
+
 \subsection{Finite box model}\label{ssec:finite_model}
@@
 \end{equation}
+
+\PvdH{@All: The choice of $\Omega$ here is slightly problematic, since we also sometimes use $\Omega$ for its asymptotic scaling notation. We should probably change $\Omega$ here.}
+
 Then $d_{\H}(u,u^\prime) \leq R_n$ if and only if $\theta(u, u^\prime) \leq 2 e^{-R_n/2}\Omega(r,r^\prime)$.
@@
 Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$: the distribution function of the radial coordinate of a vertex sampled in the disk is $\frac{\cosh(\alpha  r)-1}{\cosh(\alpha R)-1}$ which is asymptotically equivalent to $e^{\alpha(r-R)} = e^{-\alpha y}$, if $r$ and $R$ are large, resp.
-tending to infinity and $y=R-r$ and because of the minus sign in front of the $r$, the distribution function in $r$ turns into the complementary distribution function of $y$, from which we recognize the exponential distribution with parameter $\alpha$.%\PvdH{Could someone add an intuition or better explanation why this is the case.}
+tending to infinity and $y=R-r$ and because of the minus sign in front of the $r$, the distribution function in $r$ turns into the complementary distribution function of $y$, from which we recognize the exponential distribution with parameter $\alpha$.
+
+\PvdH{@All: This explanation was added by Markus at my request. If someone has a better explanation why this is the case please update this section.}
 
@@
 
+Note that, due to the translation invariance of the Poisson Point Process $\PPP$ in the $x$-direction, $\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y$ denotes the probability that the degree of a random selected node is $k$.
+We shall denote this probability by $\Prob{D_\Pcal = k}$.
+
 In Section~\ref{sec:asymptotics_average_clustering_ast_P} we will compute both these quantities and show that $c_\Pcal = c_\infty$ and $c_\Pcal(k) = c_\infty(k)$, where $c_\infty$ and $c_\infty(k)$ are given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}.
@@
 \begin{proposition}[Concentration local clustering function in $G_{\mathcal{P},n}(\alpha, \nu)$]\label{prop:concentration_local_clustering_P_n}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any non-decreasing sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $k_n$ be any positive sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
 \[
@@
 \begin{proposition}[Transition to infinite limit model]\label{prop:convergence_average_clustering_P_n}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any positive sequence tending to infinity and satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any positive sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
 \[
@@
 \end{proposition}
-\MS{Is it really necessary that the sequence tends to infinity in the thm above?}
 
@@
 
-We are now ready to prove our main results, using the propositions stated in the previous sections. We begin with Theorem~\ref{thm:local_clustering_hyperbolic}.
+We are now ready to prove our main results, using the propositions stated in the previous sections.
+As mentioned before we focus here on the convergence statements.
+The computation of the exact expressions is done in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
+We begin with Theorem~\ref{thm:local_clustering_hyperbolic}.
 
@@
 i.e. the statement of the theorem.
-
 %\[
@@
 
-\MS{I think we need to introduce resp. explain $\Prob{D_\Pcal = k_n}$ in the lemma below.}
+%\MS{I think we need to introduce resp. explain $\Prob{D_\Pcal = k_n}$ in the lemma below.}
+
 \begin{lemma}\label{lem:N_k_H_P}
@@
 		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
-	&= \frac{1}{n} \sum_{t = 3}^{a_n} \sum_{i = 1}^n \ind{D_{\H,n}(i) = t} \frac{T_{\H,n}(i)}{\binom{t}{2}}
+	&= \frac{1}{n} \sum_{t = 2}^{a_n} \sum_{i = 1}^n \ind{D_{\H,n}(i) = t} \frac{T_{\H,n}(i)}{\binom{t}{2}}
 		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
-	&= \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t)
+	&= \frac{1}{n} \sum_{t = 2}^{a_n} \Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t)
 		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}},
 \end{align*}
-\MS{Should the summation in $t$ not start from $t=2$?}
 where the expectation of the last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. Similarly,
 \[
-	c_\Pcal = \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} c_\Pcal(t) + \sum_{t > a_n} \Prob{D_\Pcal = t} c_\Pcal(t)
+	c_\Pcal = \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} c_\Pcal(t) + \sum_{t > a_n} \Prob{D_\Pcal = t} c_\Pcal(t)
 \]
@@
 	\Exp{|c_{\H,n}-c_\infty|}=\Exp{|c_{\H,n} - c_\Pcal|}
-	&\le \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
+	&\le \Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
 		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\ 
@@
 \[
-	\lim_{n \to \infty} \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
+	\lim_{n \to \infty} \Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
 			n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|} = 0.
@@
 \begin{align*}
-	&\hspace{-30pt}\Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
+	&\hspace{-30pt}\Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
 		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\
-	&\le \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\infty}(t)\right|}\\
-	&\hspace{10pt}+ \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)},
+	&\le \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\infty}(t)\right|}\\
+	&\hspace{10pt}+ \frac{1}{n} \sum_{t = 2}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)},
 \end{align*}
@@
 \[
-	k_n = \arg \max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|}.
+	k_n = \arg \max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|}.
 \]
@@
 \[
-	\max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|} = \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} \to 0.
+	\max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|} = \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} \to 0.
 \]
@@
 \[
-	\max_{3 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
+	\max_{2 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
 \]
@@
 	a_n := \left\lfloor \min \left\{
-	\left(\max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\right)^{-1/2},
-	\left(\arg \max_{3 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|}\right)^{-1/2},
+	\left(\max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\right)^{-1/2},
+	\left(\arg \max_{2 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|}\right)^{-1/2},
 	b_n - 1 \right\} \right\rfloor
@@
 \[
-	a_n \max_{3 \le t \le a_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} 
-	\le a_n \max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} \to 0,
+	a_n \max_{2 \le t \le a_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} 
+	\le a_n \max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} \to 0,
 \]
@@
 \[
-	a_n \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
+	a_n \max_{2 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
 \]
@@
 \begin{align*}
-	&\hspace{-30pt}\sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}\\
-	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}
+	&\hspace{-30pt}\sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}\\
+	&\le \bigT{1} 2^{-(2\alpha+1)} a_n \max_{2 \le t \le a_n} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}
 	= \smallO{1},
@@
 \begin{align*}
-	&\hspace{-30pt}\frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)} \\
-	&\le \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \\
-	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} 
+	&\hspace{-30pt}\frac{1}{n} \sum_{t = 2}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)} \\
+	&\le \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \\
+	&\le \bigT{1} 2^{-(2\alpha+1)} a_n \max_{2 \le t \le a_n} 
 		\Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} = \smallO{1}.

### 2019-01-10 clustering_infinite_model.tex
Merging Tobias' comments

@@
 
+\TM{ @Pim and @Nikolaos : if you have not done so already, can you please check the computations in section 4 very very carefully. }
 In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively.
 This is done in several steps.
-Recall that for $p\in \R \times \R_+ := \Rcal$,
+Recall that for $p\in \R \times \R_+ =: \Rcal$,
 \[
@@
 Before we analyze local clustering in the infinite limit model, we first establish some results for its degree distribution.
-We define the probability distribution for the degree of node $p = (x,y)$ as
+\TM{ like "randomly sampled", "degree distribution" is a weird concept for infinite graphs.
+Not sure it even makes sense.
+Better to speak of "degree of a typical node", i.e.
+$x=0$ and $y$ is exponential $\alpha$, independent of the PPP.} We define the probability distribution for the degree of node $p = (x,y)$ \TM{ Indeed, for clarity, we ought to add we add the point $p$ to the PPP, and then study its degree.
+} as
 \begin{equation}
@@
 
-Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$ \PvdH{@All: Does anyone have a good standard reference for this?} we deduce that
+Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$
+\TM{ Typo, bottom should be $\Gamma(k+1)$. } \PvdH{@All: Does anyone have a good standard reference for this?} 
+\TM{ This follows from Stirling's approx, which works also for non-integer values, together with the obvious fact that $\lim_{x\to\infty} \Gamma^x(x,c) / \Gamma(x) = 1$ and some obvious manipulations.
+We ought to provide reference + explanation though.
+Ref for the Stirling approx : De Bruijn, "asymptotic methods in analysis", 3rd edition, section 4.5 } we deduce that
 \begin{equation}\label{eq:degree_distribution_P_asymptotics}
@@
 \end{equation}
+\TM{ $y$ is a subscript here, but is an argument just above. Maybe stick with having it as an argument. }
 
@@
 The proof of this proposition is involved and technical.
-We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.
+We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} \TM{ It is not in section 4.3!!!!
+IN fact I cannot find it in sec 4 alltogether.
+Please fix.
+We do need this worked out explicitly in the paper.
+} and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.
 
@@
 We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$.
-The proofs for the other two cases are similar.
+\TM{ not sure I am happy with this "other cases are similar" approach.
+Especially in a 100 page paper.
+The devil is in the details!
+} The proofs for the other two cases are similar.
 Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
@@
 \]
-For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ and split the integral into two pieces
+For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ \TM{ should there not be a $k/\xi$ inside $\log$ here? (see below) } and split the integral into two pieces
 \begin{align*}
@@
 \end{align*} 
-For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ and
+For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ \TM{ I think that is only true if we change the def as above, in accordance with $a^{\pm}$ earlier. } and
 \[
@@
 \]
+\TM{ again, it seems off. I think we need to take $\xi$ into account here. }
 to obtain
@@
 \end{align*}
-which finishes the proof.
+which finishes the proof. \TM{ PLease elaborate on last line. What is used here? }
 \end{proof}
@@
 
-We derive the following complete asymptotic expansion of $\Delta_{\Pcal}(y)$, from which then the leading terms can be extracted.
+We derive the following explicit expression for $\Delta_{\Pcal}(y)$, from which then the leading terms can be extracted.
 The following result proves Proposition \ref{prop:asymptotics_Delta_y_P}, resp.
 implies it as a corollary after extracting the leading terms.
+\TM{ Extracting the leading terms needs to be done explicitly in the paper!
+If it is already in the paper somewhere, add explicit reference.
+}
+
 \begin{proposition}\label{prop:full_expression_delta_P}
@@
 and then sampling $x_i$ uniformly in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$.
-With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ form a triangle where $x_1$ and $x_2$ are uniform random variables in, respectively, $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.
+With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ form a triangle where $x_1$ and $x_2$ are independent uniform random variables in, respectively, $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.
 
@@
 We proceed by first computing $P(y_0,y_1,y_2)$.
-To compute the integral~\ref{eq:delta_P} it will be convenient to use the change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$.
+To compute the integral~\eqref{eq:delta_P} it will be convenient to use the change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$.
 We will write $y_i(z_i)$ to stress the dependence between $y_i$ and $z_i$.
@@
 Since the Poisson Point Process is translation invariant in the $x$-coordinate we can, without loss of generality, take $x_0 = 0$.
-By definition of the connection rule $P(y_0,y_1,y_2)$ is the probability that $|x_2-x_1| \leq  e^{(y_1+y_2)/2}$ (see figure \ref{fig:triangle_prob_lemma}).
+\TM{ Sentence does not fit with previous discussion, we already said we took $(0,y_0)$ as the central point.
+} By definition of the connection rule $P(y_0,y_1,y_2)$ is the probability that $|x_2-x_1| \leq  e^{(y_1+y_2)/2}$ (see figure \ref{fig:triangle_prob_lemma}).
 Consider $y_0, y_1, y_2$ and $x_1$ fixed.
-Then we are interested in computing the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y+2)/2},x_1+e^{(y_1+y_2)/2}]$ (given by the bottom interval in the Figure~\ref{fig:triangle_prob_lemma}), as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$ (given by the top interval in the Figure~\ref{fig:triangle_prob_lemma}).
+Then we are interested in computing the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y_2)/2},x_1+e^{(y_1+y_2)/2}]$ (given by the bottom interval in the Figure~\ref{fig:triangle_prob_lemma}), as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$ (given by the top interval in the Figure~\ref{fig:triangle_prob_lemma}).
 
@@
 \end{lemma}
+
 \begin{proof}
@@
 $\frac{\alpha-1/2}{2} < \alpha_n - 1/2 < \frac{3\alpha-3/2}{2}$.
-Define $f_n(y_1,y_2) = P(y_0,y_1,y_2) (\alpha_n - 1/2)^2 e^{-(\alpha_n-1/2)(y_1+y_2)}$.
-As the function $x \mapsto x^2$ is increasing in $x$ for $x>0$ and the function $x \mapsto e^{-(y_1+y_2)x}$ is decreasing in $x$ and $P(y_0,y_1,y_2) \in [0,1]$, it holds that $|f_n(y_1,y_2)| \leq (\frac{3\alpha-3/2}{2})^2e^{-(y_1+y_2)\frac{\alpha-1/2}{2}}$ which is integrable over $\R_{\geq 0} \times \R_{\geq 0}$ (with integral equals $\frac{(6\alpha-3)^2}{(2\alpha-1)^2}$).
+Define
+
+$$f_n(y_1,y_2) = P(y_0,y_1,y_2) (\alpha_n - 1/2)^2 e^{-(\alpha_n-1/2)(y_1+y_2)}.$$
+
+As the function $x \mapsto x^2$ is increasing in $x$ for $x>0$ and the function $x \mapsto e^{-(y_1+y_2)x}$ is decreasing in $x$ and $P(y_0,y_1,y_2) \in [0,1]$, it holds that
+
+$$|f_n(y_1,y_2)| \leq \left(\frac{3\alpha-3/2}{2}\right)^2e^{-(y_1+y_2)\frac{\alpha-1/2}{2}}$$
+
+which is integrable over $\R_{\geq 0} \times \R_{\geq 0}$ (with integral equalling $(6\alpha-3)^2/(2\alpha-1)^2$).
 Application of the theorem of dominated convergence and using equation~\eqref{eq:def_delta_p} yields that $\Delta_{\Pcal_{\alpha_n,\nu}}(y_0) \rightarrow \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ which gives the claim as the sequence $(\alpha_n)_n$ was arbitrary.
@@
 To deal with $I_{12}$ we note that $G(z_0,z_1,z_2)$ is a linear combination of monomials of the form $z_0^az_1^bz_2^c$ with 
-$a,b,c \in \{-1,0,1,2\}$ and $a+b+c=0$. Let us consider the integral $J_(a,b,c)(z_0)$
+$a,b,c \in \{-1,0,1,2\}$ and $a+b+c=0$. Let us consider the integral $J_{(a,b,c)}(z_0)$ defined by
+
 \begin{equation}\label{eq:def_Delta_P_computation_int_J_1}
@@
 $B^-$ denotes the (lower) incomplete beta-function.
-Note that since $c \geq -1$, $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators that occur during the integration are all non-zero.
+Note that since $c \geq -1$, $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4},1\}$, the denominators that occur during the integration are all non-zero.
 
@@
 
-We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$ and Lemma~\ref{lem:triangle_prob_y_coordinates} we get
+We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$
+we get
 \begin{align*}
@@
 Their constant terms cancel and after multiplication with $\frac{1}{\alpha-1}$ their linear and quadratic terms become part of the constant and linear term of the overall expansion.
+\TM{ I find this rather hard to follow. Maybe it can be made more clear what is meant. Also, We are describing what will happen next. Say that clearly. }
 
@@
 \end{align*}
-The third summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$, needs a 3-term Taylor expansion after another multiplication with $(\alpha-1)$,
+The third summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$, needs \TM{ ``needs''? Now I am really confused } a 3-term Taylor expansion after another multiplication with $(\alpha-1)$,
 \begin{align*}
@@
 \end{align*}
-The fourth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$, needs a  3-term Taylor expansion after another multiplication with $(\alpha-1)$,
+The fourth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$, needs \TM{ again why need? }a  3-term Taylor expansion after another multiplication with $(\alpha-1)$,
 \begin{align*}
@@
 When adding these terms we see that the constant coefficients cancel:
+\TM{ But wait ... some terms were multiplied with $(\alpha-1)$ others with $(\alpha-1)^2$? 
+I am genuinely lost here.
+What is going on here really needs to explained much better. }
 \begin{align*}
@@
 \begin{align*}
-	\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y = \frac{2\alpha \xi^{2\alpha}}{k!} \Gamma(k-2\alpha,\xi)
+	\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y = \frac{2\alpha \xi^{2\alpha}}{k!} \Gamma^+(k-2\alpha,\xi)
 	:= \rho(k).
@@
 \]
+
+TM{ $P$ should be $\Delta$? }
 

### 2019-01-10 concentration_argument.tex
Merging Tobias' comments

@@
 where $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$. 
+\TM{ Maybe state where $\Delta$ is defined in the paper. }
 
@@
 
-\subsection{Concentration argument for the infinite model}
+\subsection{Concentration \TM{ "of heights"? } argument for the infinite model}
 
@@
 \end{equation}
+\TM{ This is not a good definition.
+There are sequences that neither stay bounded nor tend to infinity, e.q.~odd values equal to 2 even values equal to $\log n$.
+How do you decide for a given $k_n$ which of the two cases you pick.
+To solve this we could either restrict to sequences that are either a) constant or b) tending to infinity; or we could make a cut-off at some specific, slow growing function such as $\log\log\log n$.
+}
 and define further, for any $C > 0$
@@
 \end{equation}
+\TM{ taking max with 0 and min with $R$ do not seem necessary. }
 Where we recall that $a \vee b = \max\{a,b\}$ and $a \wedge b = \min\{a,b\}$.
@@
 \]
-it is enough to consider integration of $\Kcal_C(k_n)$ instead of $\Rcal_n$.
+\TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal_n$. Is this really meant?
+I would have expected we just integrate wrt.~$y$ and replace $f_{\alppha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}
+it is enough to consider integration \BL{over} $\Kcal_C(k_n)$ instead of $\Rcal_n$.
 More precisely, for any $\ell_n = (1 + \smallO{1})k_n$ it is enough to consider $\Kcal_C(\ell_n)$.
@@
 \] 
+\TM{ If $k$ is constant, then $\ell^- < 0$ and hence 
+$a^-$ is undefined! Need to change the definitions. }
+
 we have
@@
 \end{equation}
+\TM{ As before, this is not a proper dichotomy. (unless we assume more about the sequences $k_n$, i.e.~either constant or tending to infinity }
 as $n \to \infty$.
@@
 Then, since $a_n^- < k_n$ and $a_n^+ > k_n$, $\rho_{y}(k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$. 
+\TM{ PLease give more details. }
 Therefore, by our assumption on $h(y)$,
@@
 
-We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^+,k_n)$.  Using that $k! > \sqrt{2\pi} k^{k + 1/2} e^{-k}$ we write
+We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^+,k_n)$.  Using that $k! > \sqrt{2\pi} k^{k + 1/2} e^{-k}$ \TM{ Reference! } we write
 \begin{align*}
-	\rho(a_n^+,k_n) &\le \frac{\Mu{\BallPo{a_n^+}}^{k_n}}{k_n!} e^{-\Mu{\BallPo{a_n^+}}} \\
+	\rho(a_n^+,k_n) &\BL{=} \frac{\Mu{\BallPo{a_n^+}}^{k_n}}{k_n!} e^{-\Mu{\BallPo{a_n^+}}} \\
 	&\le (2\pi)^{-1/2} k_n^{-1/2} \left(\frac{\Mu{\BallPo{a_n^+}}}{k_n}\right)^{k_n} e^{-(\Mu{\BallPo{a_n^+}} - k_n)}\\
@@
 
-Let us first consider the case $k_n \to \infty$, in which case $\kappa_n = \sqrt{\ell_n \log(\ell_n)}$. Since 
+Let us first consider the case $k_n \to \infty$,
+\TM{ again, in general we cannot neatly split into the two cases $k\to\infty$ and $k=\Theta(1)$ } in which case $\kappa_n = \sqrt{\ell_n \log(\ell_n)}$. Since 
 \[
-	\frac{\Mu{\BallPo{a_n^+}}}{k_n} = \frac{\lambda_n^-}{k_n} = 1 + \epsilon_n + C \frac{\kappa_n}{k_n} 
+	\frac{\Mu{\BallPo{a_n^+}}}{k_n} = \frac{\lambda_n^{\BL{+}}}{k_n} = 1 + \epsilon_n + C \frac{\kappa_n}{k_n} 
 	= 1 + \epsilon_n + C \sqrt{\frac{(1+\epsilon_n)\log((1+\epsilon_n)k_n)}{k_n}},
@@
 \begin{remark}[Concentration argument]\label{rmk:concentration_argument}
+\TM{ again, this is a loaded term. I would in the very least change to ``concentration of height'' everywhere }
 Lemma~\ref{lem:concentration_argument} will prove very useful in the remainder of this paper since we often have to deal with integrands of the form $g_n(y) f_{\alpha,\nu}(x,y)$ where $g_n(y) = \bigO{n^{-1} k_n^{s}}e^{\beta y}\rho(y,k_n)$ for some $s \in \R$ and $\beta < \alpha$.
@@
 
+\TM{  the term ``average degree" does not fit very well with what goes on in this section.
+We are considering the expected number of points in a ball, but not yet computing the average degree of the graph.
+}
 Recall that under the coupling between the hyperbolic random graph and the finite box model $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$, while the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
@@
 \]
-for $y + y^\prime < R_n$. This result enables us to determine the measure of a ball around a given point $p=(0,y)$ which will be fairly useful in our subsequent analysis.
+for $y + y^\prime < R_n$.
+\TM{ Say what $K$ is and what the restrictions on $r, r'$ are.
+} This result enables us to determine the measure of a ball around a given point $p=(0,y)$ which will be fairly useful in our subsequent analysis.
 
@@
 \]
+\TM{ maybe remind the reader just before of the rather counter intuitive definition of $\BallHyp{0,y}$, which 
+lives in the box model not in the original hyperbolic disk. }
 where
@@
 \]
+\TM{ We want to say in the lemma where $K$ comes from. (not everyone reads surrounding text, or reads linearly, in a paper as long as this one.) }
 \end{lemma}
@@
 \begin{proof}
-We will split the computation of $\Mu{\BallHyp{0,y}}$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$ where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
+We will split the computation of $\Mu{\BallHyp{0,y}}$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$ \TM{ You have not said what $y^\prime$ is!
+} where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
 Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.
@@
 
+\TM{ same comment Re: average degree. }
 For the finite box model $G_{\Pcal,n}(\alpha, \nu)$ we obtain a similar result for the average degree.
@@
 \]
+\TM{ where did the curly B's go? }
 where $\phi_n(y) \ge 0$ is given by
@@
 \[
-	\BallPon{p} = \left\{p^\prime \in \Rcal_n \, : \, |x^\prime|_n \le e^{\frac{y + y^\prime}{2}}\right\},
+	\BallPon{p} = \left\{p^\prime \in \Rcal_n \, : \, |x^\prime| \le e^{\frac{y + y^\prime}{2}}\right\},
 \] 
+\TM{ There a rogue subscript $n$ in $|x'|_n$ }
 whose boundaries given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$ intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
+\TM{ weird sentence }
 \[
@@
 
-\subsection{Concentration argument for hyperbolic and finite box model}
+\subsection{Concentration \TM{ OF HEIGHTS? }argument for hyperbolic and finite box model}
 
@@
 \begin{enumerate}
-\item for any sequence of functions $h_n(y) : \R_+ \mapsto \R$ such that $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s e^{\beta y}}$ for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
+\item for any sequence of functions $h_n(y) : \R_+ \to \R$ such that $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s e^{\beta y}}$ \TM{ Why not adjust $h$ so that we incorporate $\hat\rho$ in line below.
+Then both items look more similar.
+}  for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
 \[
@@
 \]
-\item for any uniformly bounded function $h : \R_+ \mapsto \R$,
+\item for any uniformly bounded function $h : \R_+ \to \R$,
 \[
@@
 \end{enumerate}
+\TM{ Say in the lemma statement where def of $K_C$ can be found. }
 \end{lemma}
@@
 \] 
+\TM{ Same problem as in L3.1. $\lambda^-$ can be negative, in which case $a^-$ is undefined.}
 In addition we fix $\varepsilon > 0$ such that $\varepsilon < \min\{1- \frac{s}{2\alpha(2\alpha + 1)}, 1\}$. Then since $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s}$ we have
@@
 \end{equation}
-which implies
+which implies \TM{ "implies"? this is just by definition. }
 \[
@@
 \]
+\TM{ repeat of previous eq. Typo or leftover of old version ... ? }
 is strictly monotonic in $y$, we have, by our assumptions on $\hat{\mu}_n$, that
@@
 \end{equation}
-Denote by $g^\prime(z)$ the derivative of a function $g$. Then by assumption $(\phi_n^{(i)})^\prime(z) = \bigT{\phi_n^{(i)}(z)}$ and hence
+\TM{ Please elaborate! Why would $\hat\mu$ be diff'ble anyway? }
+Denote by $g^\prime(z)$ the derivative of a function $g$.
+\TM{ I would remove this last sentence. }
+Then by assumption $(\phi_n^{(i)})^\prime(z) = \bigT{\phi_n^{(i)}(z)}$ and hence
 \begin{align*}
@@
 \]
+\TM{ Why can we change the upper limit of the integral? PLease elaborate (in the paper) }
 We shall prove the last statement. The first statement follows using similar computations.
@@
 \end{align*}
+\TM{ Please elaborate 2nd equlaity. I don't quite follow. }
 The result then follows by Lemma~\ref{lem:concentration_argument}.
@@
 For this we observe that~\eqref{eq:concentration_argument_z_upper_bound} and~\eqref{eq:concentration_argument_z_lower_bound} imply that there exists a $b_n \to 0$ such that $y = z(y) + b_n$, uniformly for $a_n^- \le y \le a_n^+$.
-Hence, if we define $g_n(z) = h(z + b_n)$, then $g_n(z)$ is uniformly bounded and converges point wise to $h(z)$.
-Therefore, with the change of variables~\eqref{eq:concentration_argument_variable_change} we get
+Hence, if we define $g_n(z) = h(z + b_n)$, then $g_n(z)$ is uniformly bounded and converges pointwise to $h(z)$.
+\TM{ I don't quite follow.
+Do we assume $h$ is continuous?
+}Therefore, with the change of variables~\eqref{eq:concentration_argument_variable_change} we get
 \begin{align*}
@@
 \end{align*}
+\TM{ again, please elaborate 2nd eq. (in the paper) }
 where the last line follow by dominated convergence.
@@
 Let $\hat{\rho}_n(y,k)$ be any of the two distribution functions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$.
-Then, for any function $g_n(y)$ such that $g_n(y) = \bigO{n^{-1} k_n^{s} e^{\beta y}}\hat{\rho}_n(y,k_n)$, as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
+Then, for any function $g_n(y)$ such that $g_n(y) = \bigO{n^{-1} k_n^{s} e^{\beta y}}\hat{\rho}_n(y,k_n)$ \TM{ Where did the $n^{-1}$ come from?
+Does not appear in L3.4. }, as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
 \[

### 2019-01-10 introduction.tex
Merging Tobias' comments

@@
 Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
+\TM{ \RD{Remove this reference, and replace with Abdullah-Bode-Fountoulakis!!!!}
+In general the proofs that GIRG = HRG are shaky at best, so I do not want to cite anything that relies on that.
+Of course, in this case Nikoloas & his crew were  first anyway.
+Also, regarding "distances", we probably want to mention graph diameter, studied by Kiwi+Mitsche, Friedrich+Krohmer, M\"uller + Staps.
+}
 Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{bode2015largest},~\cite{fountoulakis2018law} and the number of cliques and the largest clique~\cite{blasius2018cliques}.
 \PvdH{@All: Does anyone have other suggestions for results to add?}
+\TM{ Yes, of course!
+Everything Nikolaos & his crew, and I and my crew, and Kiwi-Mitsche have done on this model.
+This includes 2nd largest componnent, connectivity, spectral gap, diameter, Hamilton cycles & perfect matchings (with Markus, Nikolaos and Mitsche, in preparation but perhaps submitted around the same time as this one.).
+Also there is a recent paper on arxiv by Owada+Yogeshwaran on subgraph counts.}
 
@@
 
+\TM{ I vote to remove this next paragraph. Use of GIRGs is fishy, and also we are not obliged to mention any and all possible alternative approaches. }
 We remark that it is possible to prove that the local clustering coefficient converges to some limit, using the technical tools in the recent work on explosion times in Geometric Inhomogeneous Random Graphs~\cite{komjathy2018explosion}.
@@
 as follows from the hyperbolic law of cosines.% rule[CITE?].
+\TM{ This is only when $r_i+r_j \geq R$! Otherwise the equation does not have a solution as there is no triangle with side lengths $r_i, r_j, R$.}
 \end{enumerate}
@@
 %This coefficient measures the fraction of triangles in the network compared to the total possible number of triangles. 
+\TM{ Do we even need to give this definition? We don't study it, so I would say it suffices to just mention there is another, rival defintion to the one we use.}
 A different concept for clustering is defined for each vertex and by taking averages also for the entire graph as well as for all vertices with a specified degree: the \emph{local clustering coefficient} of a vertex $v \in V(G)$ is a real number between zero and one for the extent to which the neighborhood of $v$ resembles a clique.
 If the vertex $v$ has $k\geq 2$ neighbors, there are ${k \choose 2}$ possible edges between them and its local clustering coefficient is the quotient of the number of these pairs that constitute an existing edge in the graph divided by ${k \choose 2}$.
+\TM{ Here I would add the formula for readability.}
 If the vertex $v$ has no or only one neighbor, its clustering coefficient is set to zero.
@@
 
+\TM{ I would find it natural to define $c(v)$ first and then let $c(G)$ be the average. }
 However, since the local clustering coefficient assigns just one value to the whole network, representing its triangular structure, it is unable to characterize local structural properties involving triangles.
+\TM{ This last sentence seems a bit weird to me, rather abstract. }
 The local clustering function, on the other hand, measures the fraction of triangles to which vertices of a given degree belong, compared to the maximum number of triangles in which they could participate~\cite{vazquez2002large,serrano2006clustering}.
 It describes the triangular structure of vertices in the networks based on their degree and gives a more detailed look at the overall structure of the network.
+\TM{ Similar comment to the previous one. I am not really sure what this means. }
 The formal definition of the \emph{local clustering function} is 
@@
 
+\TM{ Perhaps we should say that, while it may be more natural to consider $c(k)$ to be undefined when $N_k=0$, we use this definition for technical convenience. This way 
+$c(k)$ is a plain vanilla random variable and we can compute expectation and so on without issue, and speak about convergence in probability and what not. }
 %We note that other versions of the local clustering function have been considered, for instance where nodes with degree larger than $k$ are considered instead of nodes with degree exactly $k$.
@@
 When the degree $k$ is a growing function of $n$ we are able to exactly compute the asymptotic behavior of $c_{\H,n}(k)$.
+\TM{ Seems a little strong. We "exactly compute" the leading terms, I would say. }
 
@@
 We let $B(a,b)$ denote the beta-function and $B^-(x,a,b)$ the lower incomplete beta-function.
-We also write $\Gamma(z)$ for the Gamma function, $\Gamma^+(q,z)$ for the incomplete Gamma function and define $\Gamma^\ast(q,z) := \Gamma^+(1 + q, z) + \Gamma^+(q, z)$.
+We also write $\Gamma(z)$ for the Gamma function, $\Gamma^+(q,z)$ for the \TM{ upper } incomplete Gamma function and define $\Gamma^\ast(q,z) := \Gamma^+(1 + q, z) + \Gamma^+(q, z)$.
+\TM{ How useful is this extra definiton?
+If it is just to make the expression in Thm 1.1 neater, then I dont think we need it.
+}
 Finally, we write $U(a,b,z)$ for the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $\mathrm{Re}(a), \mathrm{Re}(z) >0$ has the integral representation
@@
 see~\cite[p.255 Equation (2)]{erdelyi1953higher}, and let $\MeijerGnew{m}{\ell}{p}{q}{{\bf a}}{{\bf b}}{z}$ denote Meijer's G-Function~\cite{meijer1946gfunction}, see Appendix~\ref{sec:Meijer_G_functions} for more details.
+\TM{ Should we not maybe also say what the upper incomplete gamma and lower incomplete beta are then? }
 
@@
 \]
+\TM{ As far as I can tell this is just equivalent to 
+$c(G) \plim c_\infty$. I would prefer to use this more standard notation and terminology, certainly at least here, where we present our main results. }
 where $c_\infty$ is defined for $\alpha \ne 1$ as
@@
 \end{theorem}
+
+\TM{ Do we want to remark something re: closed form expression for the $\alpha=1$ case? }
 
@@
 
+\TM{ I would be tempted to split this thm into two.
+The first states that for $k$ fixed
+$c(k) \plim c_\infty(k)$. Then we say the proof extends to ... the second thm which states that if
+$1 \ll k_n \ll n^{1/(2\alpha+1)}$ then
+$c(k_n) = (1+o(1)) c_\infty(k_n)$ a.a.s. \\
+In fact, maybe it is good to present a separate -- and short -- proof of the constant case.
+The equivalence of the models for constant $k$ can be worked out in a few pages while for the sequence we need 50+ pages of super technical computations.
+What do you think?
+}
+
 From the expression for $c_\infty(k)$ we obtain its asymptotic behavior as $k \to \infty$. For this we first define, for any $\frac{1}{2} < \alpha < \frac{3}{4}$,
@@
 \end{equation}
+\TM{ These exponents are $>0$! (see next comment)}
 
@@
 \end{theorem}
-
+\TM{ There is a typo here. Since you divide by $s$ in this last thm and $s\to\infty$ as the exponents are $>0$ and clustering coefficients are $\in [0,1]$, you would get limiting value zero. }
+\TM{ Also, I dont know if this previous result really deserves the status of ``theorem''. Feels more like a lemma or proposition. } 
 The following is an immediate consequence of Theorem~\ref{thm:local_clustering_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
@@
 \end{corollary}
+
+\TM{ I had not heard of ``convergence in expectation'' before this. I have heard of $L_1$-convergence though. }
 \MS{@Pim: Are you sure all constants are correct? I thought for $\alpha = 3/4$ it might be $6\nu/\pi$. But if you are sure, you can remove this comment of course.}
@@
 
-This result completely characterizes the asymptotic behavior of the local clustering function in Hyperbolic Random Graphs.
+This result completely \TM{ ``completely" is pretty strong. Note also we seem to stay away from 
+$k = \Theta( n^{1/(2\alpha+1)} )$. So unless we change that, there is reason to say we do not to it ``completely''.} 
+characterizes the asymptotic behavior of the local clustering function in Hyperbolic Random Graphs.
 In particular we observe that the conjectured scaling of $k^{-1}$ from~\cite{krioukov2010hyperbolic} only occurs when $\alpha > 3/4$, or equivalently, when the exponent of the pdf of the degree distribution is larger than $5/2$.
@@
 
-Our results for the local clustering function in particular imply uniform convergence of $c_{\H,n}(k)$ for all $3 \le k \le a_n$ where $a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. To see this let
+Our results for the local clustering function in particular imply uniform convergence of $c_{\H,n}(k)$ for all $3 \le k \le a_n$ \TM{ Why 3?
+} where $a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
+To see this let
 \[
@@
 All our results for clustering in the hyperbolic random graph are valid for any sequence $k_n$ such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
-Although one would like to have results for any sequence $k_n \le n$, it turns out that $n^{1/(2\alpha + 1)}$ is the optimal scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
+Although one would like to have results for any sequence $k_n \le n$, it turns out that $n^{1/(2\alpha + 1)}$ is the optimal \TM{ again seems to strong to me } scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
 To see why this is the case note that by definition of the local clustering function~\eqref{eq:def_local_clustering_general} we have that $c_{\H,n}(k_n) = 0$ if $N_{\H,n}(k_n) = 0$.
@@
 
+\TM{ \RD{\bf VERY IMPORTANT:} we need to appropriately cite the vdHofstad-vLeeuwaarden-Stegehuis crew.
+We want to avoid a war.
+(Just between you and me : I do kind of feel theirs is pretty much non-rigorous though.
+I am not sure if there is some way to say their work is ``non-rigorous'' without offending them.) }
+
 \subsection{Simulations}\label{ssec:simulations}
-The simulations of this section (see Figures \ref{fig:c2allnu}, \ref{fig:c4allnu} and \ref{fig:ckvariable}) confirm the formulas from the result section.
+
+\TM{ I think the most important simulation to include is for the ``overall'' clustering coefficient $c(G)$. 
+Can someone please add that? \\
+(The value of $k$ in Figs 2 and 3 seems a bit arbitrary to me btw.) }
+
+The simulations of this section (see Figures \ref{fig:c2allnu}, \ref{fig:c4allnu} and \ref{fig:ckvariable}) confirm \TM{ ``confirm" is too strong.
+Simulations ``seem to be in agreement with the formulas".
+} the formulas from the result section.
 The simulations were obtained by generating the hyperbolic random graph for a given choice of the parameters and number of repetitions and then taking the average over all simulation instances.
@@
 \end{figure}
+
+\TM{ We may want to put the source code in an appendix.
+In fact RuG now officially requires we deposit the source code in some archive. (gasp.) }

### 2019-01-10 paper.tex
a couple of comments in section 1
Merging Tobias' comments

@@
 
-\title{Exact asymptotic expressions for local clustering in hyperbolic random graphs}
+\title{Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph".
+Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}}
 \author[1]{Nikolaos Fountoulakis}
@@
 
-\input{appendix}
+\TM{ Maybe a ``conclusion and further work'' section here,  before the references and appendix? \\
+Also, appendix usually comes after references in my experience.}
 
@@
 
+\input{appendix}
+
 \end{document}

### 2019-01-10 proof_overview.tex
Merging Tobias' comments

@@
 In particular, it is the key ingredient in the proofs of Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
+\TM{ Sounds weird, since Thm 1.3 is just about asymptotics of certain functions. }
 Therefore, in this section we first give a detailed overview of the structure for the proof of Theorem~\ref{thm:local_clustering_hyperbolic}.
@@
 The infinite graph will then yield the limit expressions for the local clustering coefficient and function.
-A similar approach is used in \cite{fountoulakis2018law} to analyze the size of the largest component in the hyperbolic model and in \cite{komjathy2018explosion} to analyze explosion times in a more general class of models.
+\TM{ Our approach builds on the work~\cite{fountoulakis2018law}, where tools were developed to analyze the size of the largest component in the hyperbolic model which can reuse here.}
+\TM{ The Komjathy paper used GIRG, which is fishy. So I say we do not cite that. }
+%and in \cite{komjathy2018explosion} to analyze explosion %times in a more general class of models. 
 The advantage of the infinite limit model is two-fold.
@@
 by replacing hyperbolic densities with exponential densities and the hyperbolic distance with a computationally easier expression.
-Secondly, it directly yields the limit as a result rather than having to determine this later from a long expression depending on $n$.
+Secondly, it directly yields the limit as a result as opposed to some long expression depending on $n$.
 
@@
 
-First of all we define the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ which we will couple to $G_{\H, n}(\alpha, \nu)$.
+First of all we define the \TM{ infinite } graph $G_{\mathcal{P},n}(\alpha, \nu)$ which we will couple to $G_{\H, n}(\alpha, \nu)$.
 A similar approach was used in~\cite{fountoulakis2018law} to analyze the largest component.
@@
 
+\TM{ To me it seems more natural to have a section introducing the infinite model first, rather than sort of doing it here in the beginning and then having to do it again later. }
 In addition we denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e. for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
@@
 In order words, $G_{\mathcal{P},n}(\alpha, \nu)$ is the subgraph of $G_{\mathcal{P}}(\alpha, \nu)$ induced on $\mathcal{V}_n$, where we have identified the boundaries of $(-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}]$ to exclude boundary effects and to make the model symmetric in the horizontal $x$-axis.
+\TM{ So it is NOT an induced subgraph.
+It has edges not in $G_{\mathcal{P}}$.
+Also, ``symmetric in the horizontal $x$-axis'' seems a bit ambiguous.
+I would say something like it is invariant under horizontal translation and reflections in vertical lines.
+}
 
@@
 \begin{equation}\label{eq:def_ball_P_n}
-	\BallPon{p} = \left\{p^\prime \in \Rcal_n : |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}}\right\}.
+	\BallPon{p} = 
+	\left\{p^\prime \in \Rcal_n : |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}}\right\}.
 \end{equation}
@@
 To couple the hyperbolic graph to $G_{\mathcal{P},n}(\alpha, \nu)$ we consider the original hyperbolic graph on a Poisson distributed number of vertices as an intermediate step.
-For this we define $G_{\HP,n}(\alpha, \nu)$ to be the hyperbolic random graph where the vertex set is given by $N \stackrel{d}{=} \Po(n)$ points, distributed according to the $(\alpha, R_n)$-quasi uniform distribution~\eqref{eq:def_hyperbolic_point_distribution} defined in Section \ref{ssec:hyperbolic_model}.
+For this we define $G_{\HP,n}(\alpha, \nu)$ to be the hyperbolic random graph where the vertex set is given by $N \stackrel{d}{=} \Po(n)$ points, \TM{ i.i.d.~and independent of $N$, } distributed according to the $(\alpha, R_n)$-quasi uniform distribution~\eqref{eq:def_hyperbolic_point_distribution} defined in Section \ref{ssec:hyperbolic_model}.
 The following two lemmas from \cite{fountoulakis2018law} establish a coupling between this version of the hyperbolic random graph and the finite box model and relate the hyperbolic neighborhoods to the neighborhood balls $\BallPo{p}$.
@@
 \end{equation}
-Then there exists a coupling such that, a.a.s., $\mathcal{V}_n = \Psi(\mathcal{V}_{\HP,n})$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
+Then there exists a coupling such that, a.a.s.\TM{ Have we defined a.a.s.?
+If no, add it before using it.
+}, $\mathcal{V}_n = \Psi(\mathcal{V}_{\HP,n})$.
+%Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
 %\begin{equation}\label{eq:convergence_miscoupling_hyperbolic_poisson}
@@
 \[
-	\BallHyp{p} := \left\{p^\prime := \Psi(u) \, : \, u \in \Dcal_{R_n} \text{ and } d_\H(\Psi^{-1}(p),u) \le R_n\right\}.
+	\BallHyp{p} := 
+	%\left\{p^\prime := \Psi(u) \, : \, u \in \Dcal_{R_n} \text{ and } d_\H(\Psi^{-1}(p),u) \le R_n\right\}.
+	\BL{\Psi\left[ \left\{ u \in \Dcal_{R_n} : 
+	d_\H(\Psi^{-1}(p),u) \le R_n\right\}\right].}
 \]
@@
 \]
+\TM{ Again, only true for $r+r'>R$!!!! }
 To write this differently, define
@@
 In other words, we have $\Rcal_n ([r, R_n])  \subset \BallHyp{p}$. 
+\TM{ Weird notation : $\Rcal_n ([r, R_n])$. Have not seen it before. Rehrase or introduce. }
 The shape of $\BallHyp{p}$ at the lower parts of $\Rcal_n$ is described by the following lemma which appears in~\cite{fountoulakis2018law}.
@@
 This coupling is however not exact and hence we need to compute the difference in triangle counts between the two models.
-For this, and other computations later on, it will be more convenient to consider the following slight modified version of the local clustering function,
+For this, and other computations later on, it will be more convenient to consider the following slightly modified version of the local clustering function,
 \begin{equation}\label{eq:def_local_clustering_ast_general}
@@
 \end{equation}
+\TM{ Case distinction / second line of definition is not needed. Top expression is automatically zero if $N_k=0$. }
 Notice that the only difference between $c_G(k)$ and $c_G^\ast(k)$ is that we replace $N_G(k)$ by its expectation $\Exp{N_G(k)}$.
@@
 \begin{proposition}\label{prop:clustering_ast_H_Pois}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any increasing sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, as $n \to \infty$,
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any increasing \TM{ Do you really mean to say ``increasing''?
+IN the lemma before and prop.~after, the sequences are more general.
+And if so, increasing = nondecreasing?
+} sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
+Then, as $n \to \infty$,
 \[
@@
 
+\TM{ Maybe we could replace these three with a statement on $|c_{\H,n}(k_n) - c_{\Pcal,n}^\ast(k_n)|$, at least at this point of the paper.
+This is only the high level description and that is all we need for the ``final proof".}
 These two results imply that the difference between the local clustering function of the hyperbolic random graph and the modified local clustering function of the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem \ref{thm:local_clustering_hyperbolic}.
@@
 To analyze the limiting expressions for clustering in the finite random graph $G_{\Pcal,n}(\alpha, \nu)$ we shall use an infinite graph model which can be understood as taking the finite graph $G_{\Pcal,n}(\alpha,\nu)$ and taking $n \to \infty$.
-Recall that $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and that $\mathcal{P}_{\alpha,\nu}$ is a Poisson point process on $\Rcal$ with intensity function
+\TM{ We've already defined the model!
+} Recall that $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and that $\mathcal{P}_{\alpha,\nu}$ is a Poisson point process on $\Rcal$ with intensity function
 \[
@@
 
-To analyze expressions in the both the finite and infinite model we will make use of the~\emph{Campbell-Mecke} formula. 
-For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ we have
+To analyze expressions in the both the finite and infinite model we will make use of the~\emph{Campbell-Mecke} formula. \TM{ This needs a reference! }
+For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ \TM{ Below there is one more argument.
+(a set) } we have
 \begin{equation}\label{eq:def_Campbell-Mecke}
@@
 \end{equation}
-where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$.
+where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$. \TM{ Are you sure this is the Mecke formula? }
 
@@
 \end{equation}
+\TM{ This does not need justification by the Mecke formula. It is just an integral of the intensity over some region. }
 
@@
 \]
-Note that $\rho(y,k)$ denotes the probability that a vertex $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$, which due to the translation symmetry of the Poisson Point Process in the $x$ direction depends only on the \emph{height} $y$.
+Note that $\rho(y,k)$ denotes the probability that a vertex $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$,
+\TM{ This probability is not well-defined as such. What vertex? We have an infinite graph, so ``a random vertex'' does not immediately make sense. 
+The most natural solution, I think, is to say that we {\em add} the point $p$ to the PPP and then consider its degree. This is related to ``Palm theory". }
+which due to the translation symmetry of the Poisson Point Process in the $x$ direction depends only on the \emph{height} $y$.
 
@@
 However, since $G_\Pcal$ has an infinite number of nodes the corresponding definitions are slightly different than for the finite size models.
-Intuitively the local clustering coefficient is the probability that two random neighbors of a randomly sampled node form a triangle, while the local clustering function is the same probability but conditioned on the sampled node having degree $k$.
+Intuitively the local clustering coefficient is the probability that two random neighbors of a randomly sampled node form a triangle , while the local clustering function is the same probability but conditioned on the sampled node having degree $k$.
+\TM{ again "randomly sampled" does not immediately make sense here.
+You may want to say we generate a point $(0,y)$ with $y$
+exponential $\alpha$ distributed and add this to the PPP, which is generated indeptly of $y$.}
 
@@
 \end{equation}
-That is $\eta_y$ is the density $f_{\alpha,\nu}$ restricted to the ball $\BallPo{(0,y)}$, properly normalized.
-Or in other words, it denotes the probability density of a randomly sampled point in $\BallPo{(0,y)}$, i.e.
+That is $\eta_y$ is the density $f_{\alpha,\nu}$ restricted to the ball $\BallPo{(0,y)}$, properly normalized \TM{ to make it a probability distribution}.
+\TM{ It can be interpreted as } the probability density of a randomly sampled point in $\BallPo{(0,y)}$, i.e.
 a randomly sampled neighbor of $(0,y)$.
@@
 	T_\Pcal(y, x_1, x_2, y_1, y_2) 
-	= \ind{|x_1| \, \le \, e^{(y+y_1)/2}}\ind{|x_2| \, \le \, e^{(y+y_2)/2}}\ind{|x_1-x_2| \, \le \, e^{(y_1+y_2)/2}},
+	= \ind{|x_1| \, \le \, e^{(y+y_1)/2}}\ind{|x_2| \, \le \, e^{(y+y_2)/2}}\ind{|x_1-x_2| \, \le \, e^{(y_1+y_2)/2}}.
 \]
-which is the probability that two randomly sampled points in $\BallPo{(0,y)}$ form a triangle with $(0,y)$.
+So $\Delta_{\Pcal}(y)$ is the probability that two randomly sampled points in $\BallPo{(0,y)}$ form a triangle with $(0,y)$.
 
+\TM{ This next bit again suffers from the same issue as above. You cannot "randomly sample a point". }
 Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$: the distribution function of the radial coordinate of a vertex sampled in the disk is $\frac{\cosh(\alpha  r)-1}{\cosh(\alpha R)-1}$ which is asymptotically equivalent to $e^{\alpha(r-R)} = e^{-\alpha y}$, if $r$ and $R$ are large, resp.
@@
 
-Note that, due to the translation invariance of the Poisson Point Process $\PPP$ in the $x$-direction, $\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y$ denotes the probability that the degree of a random selected node is $k$.
+Note that, due to the translation invariance of the Poisson Point Process $\PPP$ in the $x$-direction, $\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y$ denotes the probability that the degree of a random selected \TM{ same issue } node is $k$.
 We shall denote this probability by $\Prob{D_\Pcal = k}$.
@@
 
+\TM{ ``concentration'' is a loaded term in probability. I am not sure this use of the word will not be counterintuitive to many. }
+
 \begin{proposition}[Concentration local clustering function in $G_{\mathcal{P},n}(\alpha, \nu)$]\label{prop:concentration_local_clustering_P_n}
@@
 
-With this concentration result, we are left with the task to compute the limit of $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$ as $n \to \infty$ and show that it is equivalent to $c_\infty(k_n)$.
+\TM{ Assuming this } concentration result, we are left with the task to compute the limit of $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$ as $n \to \infty$ and show that it is equivalent to $c_\infty(k_n)$.
 To accomplish this we move to the infinite limit model $G_\Pcal(\alpha,\nu)$ and show that the difference between the expected value of the clustering function $c_G^\ast(k)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
@@
 \end{proposition}
+
+\TM{ This is only for $c(k)$. Should we not also mean $c$? }
 
@@
 At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{s_\alpha(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c_{\Pcal}(k_n) = c_\infty(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
-All of this together yields that:
+\TM{ Maybe we can have a more clear reference? Now, at this place in the paper this proof feels a bit like cheating since there are almost no details given. } All of this together yields that:
 \begin{align*}
@@
 \end{align*}
+\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point. }
 i.e. the statement of the theorem.
@@
 \]
+\TM{ Did we define $D_\Pcal$ already? }
 and hence, as $n \to \infty$
@@
 \end{align*}
-and since the last two probabilities are $\smallO{1}$ it is enough to prove that
+\TM{ Same comment }
+and since the last two probabilities are $\smallO{1}$ \TM{ We do not seem to have proved this yet at this point in the paper } it is enough to prove that
 \[
@@
 Note that Theorem~\ref{thm:local_clustering_hyperbolic} and Lemma~\ref{lem:clustering_ast_H} together state that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
+
 \begin{equation}\label{eq:convergence_c_H_P}
@@
 
+\TM{ I do not see how this follows from the statements of Thm 1.2 and L2.3. Please elaborate. }
 Let $b_n := \log(n)^{-1} n^{1/(2\alpha + 1)}$ and define the sequence $k_n$ by
@@
 \]
-so that $a_n < b_n = \smallO{n^{1/(2\alpha + 1)}}$, $a_n \to \infty$, 
+\TM{ There seems to be a typo. max should be argmax?
+Also, what is the exponent $-1/2$ doing there? }
+so that $a_n < b_n = \smallO{n^{1/(2\alpha + 1)}}$, $a_n \to \infty$, \TM{ Not with the current def of $a_n$ !!! }
+\
 \[
@@
 \]
+\TM{ LHS and RHS are identical !!! }
 and similarly

### 2019-01-10 transition.tex
final short pass before sending to Tobias and Nikolaos
Merging Tobias' comments

@@
 Recall that $G_{\Pcal,n}$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal_n = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ (we write $\Pcal_n$ for this process), and connecting two points $p_1, p_2 \in \Rcal_n$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$ where we identified the left and right boundary of $\Rcal_n$.
+\TM{ This last bit of the sentence is already contained in the fact we us $|.|_{\pi e^{R_n/2}}$. To me it does not add anything, except possibly confusion. }
 See Section~\ref{ssec:finite_model} for more details.
@@
 \]
+\TM{ Typo : $p\in\R$. Do you mean $\Rcal_n$? Or maybe 
+$\R \time \R^+$? Still not sure that max and min in defn add anything. }
 with
@@
 \]
+\TM{ Same issue as before. }
 In addition we note that the function $\phi_n(y)$ in Lemma~\ref{lem:average_degree_P_n} satisfies
@@
 \begin{corollary}\label{cor:average_degree_P_n_K}
-Let $\alpha > \frac{1}{2}$, $C > 0$ and $k_n$ be any sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha - 1}}}$. Then, for all $p \in \Kcal_{C}(k_n)$,
+Let $\alpha > \frac{1}{2}$, $C > 0$ and $k_n$ be any sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha - 1}}}$. \TM{ Typo? $2\alpha-1$ should be $2\alpha+1$? } 
+Then, for all $p \in \Kcal_{C}(k_n)$,
 \[
@@
 \]
+\TM{ I don't follow. Spell it out. }
+
 \end{corollary}
@@
 \]
-
+\TM{ $p$ is supposed to be $p_0$ I assume. }
 The difference between the indicator $\ind{p_1 \in B_{\Pcal,n}(p)}$ in the finite box model and $\ind{p_1 \in B_{\Pcal}(p)}$ is that in $G_{\Pcal,n}(\alpha,\nu)$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$.
+\TM{ AND we stop at height $y=R_n$!
+(may be significant at some point) }
 It is clear that for any $0 \le y \le R_n$ we have that $\BallPon{p_0} = \BallPo{p_0} \cap \Rcal_n$.
@@
 \end{equation}
+\TM{ $p$ should be $p_0$ I supppose. }
 Then
@@
 \]
+\TM{ Note you cannot really force/assume $p_0 = (0,y)$ is in your PPP $\Pcal_n$.
+(The summation over $\Pcal_n \setminus (0,y)$ suggests this is what you do.) For taking the expectation of sort of thing, Palm theory / Mecke are used typically.
+At this point though you can again still just say we add $p_0$ to the PPP.
+}
 where the sums are over all distinct pairs $(p_1, p_2) \in \Pcal_n \setminus \{(0,y)\}$.
@@
 
-To further analyze this, let us introduce some notation. For any $p = (x,y) \in \Rcal_n$ we will define the left and right boundary functions as, respectfully,
+To further analyze this, let us introduce some notation. For any $p = (x,y) \in \Rcal_n$ we will define the left and right boundary functions as, respectfully,\TM{ respectively? }
 \begin{align}
@@
 Note that these functions describe the boundaries of the ball $\BallPon{p}$.
-In particular, $p^\prime \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
-
-For the remainder of the analysis we restrict ourselves to the case where $x^\prime > 0$.
-Due to symmetry the situation for $x^\prime < 0$ is the same.
+In particular, $p^\prime = \BL{(x^\prime, y^\prime)} \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
+
+For the remainder of the analysis we restrict ourselves to the case where $x^\prime > 0$. Due to symmetry the situation for $x^\prime < 0$ is the same. \TM{ does this not depend on $p$? } 
 There are two important points in the box $\Rcal_n$.
@@
 We denote by $(x^\ast(p^\prime), y^\ast(p^\prime))$ the intersection between the left and right boundary of $p^\prime$ and by $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$ the intersection between the left boundary of $p$ and the right boundary of $p^\prime$, see Figure \ref{fig:comparing_triangles_diff_analysis}.
-After some simple algebra we obtain the following expressions for the coordinates of these two points
+After some simple algebra \TM{ I am not a big fan of writing "after some simple algebra" or similar.
+This is how errors can creep into your argument.
+Maybe we can just give the details?
+} we obtain the following expressions for the coordinates of these two points
 \begin{align*}
@@
 \end{tikzpicture}
-\caption{???.}
+\caption{\PvdH{@All: This still needs a caption.}}
 \label{fig:comparing_triangles_diff_analysis}
@@
 \]
-By Lemma~\ref{lem:average_degree_P_n} and a concentration argument
+By Lemma~\ref{lem:average_degree_P_n} and a concentration argument \TM{ please give more details! }
 \[
@@
 \end{align*}
-with $a_n^\pm = 2\log\left(\frac{k_n \pm C \kappa_n}{\xi_{\alpha,\nu}}\right)$. Next we note that for $a_n^- \le y \le a_n^-$,
+with $a_n^\pm = 2\log\left(\frac{k_n \pm C \kappa_n}{\xi_{\alpha,\nu}}\right)$. \TM{ again, this def has to be adapted. } Next we note that for $a_n^- \le y \le a_n^-$,
 \[
@@
 		\dd x_1 \dd y_1\\
-	&\hspace{10pt}+ \iint_{\Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2) f_{\alpha, \nu}(x_1,y_1) f_{\alpha, \nu}(x_2,y_2)
+	&\hspace{10pt}+ \BL{\int_{\Rcal \setminus \Rcal_n}\int_{\Rcal \setminus \Rcal_n}} T_{\Pcal}(p,p_1,p_2) f_{\alpha, \nu}(x_1,y_1) f_{\alpha, \nu}(x_2,y_2)
 		\dd x_2 \dd y_2 \dd x_1 \dd y_1. 
@@
 
+\TM{ in the 1st integral we could have restricted to
+the ball of $p$, and possibly saved a lot. 
+Does that not help? }
 The first integral was taken care of in Lemma \ref{lem:clustering_error_T_term}. For the second integral we have
@@
 \end{align*}
+\TM{ Typo : $f_{\mu, \nu}$? Also give more details how line 3 follows. }
 from which we conclude that
@@
 \end{align*}
-where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. To finish the argument we observe that
+\TM{ Typo : $e^{-\alpha}$ }
+where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. \TM{ Also justify penultimate step! }
+To finish the argument we observe that
 \begin{align*}
@@
 
+\TM{ Some words spelling this out would help. I don't find it easy to see. Also, in general I think one should avoid saying things like "the proof of such-and-such also gives .." }
 \subsection{Counting missing triangles}

### 2019-01-11 introduction.tex
initial response to some comments in intro

@@
 In general the proofs that GIRG = HRG are shaky at best, so I do not want to cite anything that relies on that.
-Of course, in this case Nikoloas & his crew were  first anyway.
+Of course, in this case Nikoloas \& his crew were  first anyway.
 Also, regarding "distances", we probably want to mention graph diameter, studied by Kiwi+Mitsche, Friedrich+Krohmer, M\"uller + Staps.
@@
 \TM{ Yes, of course!
-Everything Nikolaos & his crew, and I and my crew, and Kiwi-Mitsche have done on this model.
-This includes 2nd largest componnent, connectivity, spectral gap, diameter, Hamilton cycles & perfect matchings (with Markus, Nikolaos and Mitsche, in preparation but perhaps submitted around the same time as this one.).
+Everything Nikolaos\& his crew, and I and my crew, and Kiwi-Mitsche have done on this model.
+This includes 2nd largest componnent, connectivity, spectral gap, diameter, Hamilton cycles \& perfect matchings (with Markus, Nikolaos and Mitsche, in preparation but perhaps submitted around the same time as this one.).
 Also there is a recent paper on arxiv by Owada+Yogeshwaran on subgraph counts.}
@@
 as follows from the hyperbolic law of cosines.% rule[CITE?].
-\TM{ This is only when $r_i+r_j \geq R$! Otherwise the equation does not have a solution as there is no triangle with side lengths $r_i, r_j, R$.}
+\TM{ This is only when $r_i+r_j \geq R$!
+Otherwise the equation does not have a solution as there is no triangle with side lengths $r_i, r_j, R$.}\PvdH{I do not understand this.
+The hyperbolic law of cosines defines the hyperbolic cosine of the distance between points in terms of hyperbolic cosines and sines of their radii and the cosine of their relative angle:
+\[
+	\cosh(d_\H(u_i, u_j)) = \cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}).
+\] 
+Since $\cosh$ is strictly monotonically increasing we have that $\cosh(x) \le \cosh(y) \iff x \le y$ and hence 
+\begin{align*}
+	&d_\H(u_i, u_j) \le R_n \\
+	&\iff \cosh(d_\H(u_i, u_j)) \le \cosh(R_n) \\
+	&\iff \cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R_n)
+\end{align*}
+The approximation for the hyperbolic balls you and Nicolaos derived in Lemma 28 holds only when $r_i + r_j \ge R$.}
 \end{enumerate}
@@
 \TM{ As far as I can tell this is just equivalent to 
-$c(G) \plim c_\infty$. I would prefer to use this more standard notation and terminology, certainly at least here, where we present our main results. }
+$c(G) \plim c_\infty$.
+I would prefer to use this more standard notation and terminology, certainly at least here, where we present our main results.
+} \PvdH{Convergence in expectation implies convergence in probability but is a much stronger notion.
+In addition, for integer valued sequences $a_n$ and $b_n$ we have that $\Exp{|a_n - b_n|} \to 0$ implies that $a_n = b_n$ a.a.s..
+However, when they are real valued this is no longer true in general.}
 where $c_\infty$ is defined for $\alpha \ne 1$ as
@@
 What do you think?
-}
+} \PvdH{I agree with the splitting suggestion.
+However, as I mentioned before, since $c(k_n)/c_\infty(k_n)$ is real-valued our result does not necessarily imply that $c(k_n)/c_\infty(k_n) = 1$ a.a.s..
+I guess this is what you mean with $c(k_n) = (1+o(1)) c_\infty(k_n)$ a.a.s.
+right?}
 

### 2019-01-14 introduction.tex
simulation of overall clustering coefficient

@@
 
-The simulations of this section (see Figures \ref{fig:c2allnu}, \ref{fig:c4allnu} and \ref{fig:ckvariable}) confirm \TM{ ``confirm" is too strong.
-Simulations ``seem to be in agreement with the formulas".
-} the formulas from the result section.
+The simulations of this section (see Figures \ref{fig:c2allnu}, \ref{fig:c4allnu}, \ref{fig:ckvariable} and \ref{fig:cvariable}) appear to be in agreement with the formulas from the result section.
 The simulations were obtained by generating the hyperbolic random graph for a given choice of the parameters and number of repetitions and then taking the average over all simulation instances.
@@
 \end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.6]{figures/SimulationClusteringCoefficientVariousNu.pdf}
+    \caption{Simulation of $c_{\mathbb{H},n}$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=1 000$ and 20 repetitions.}
+    \label{fig:cvariable}
+\end{figure}
 

### 2019-01-19 clustering_infinite_model.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

@@
 \TM{ @Pim and @Nikolaos : if you have not done so already, can you please check the computations in section 4 very very carefully. }
+
+\PvdH{@All: I haven't touched this section yet.}
+
 In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively.
@@
 
-\subsection{Degree distribution in $G_\Pcal(\alpha, \nu)$}
+\subsection{Degree distribution in $G_\Pcal(\alpha, \nu)$}\label{ssec:degrees_infinite_model}
 

### 2019-01-19 concentration.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

@@
 
-\noindent {\bf Case $\bm{k_n = \bigT{1}}$:}\\
-This proof is very similar to the previous one. Here however, we write
-\begin{align*}
-	\rho_{n}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
-	&= \Prob{X_3(p,p^\prime) = 0}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} 
-		+ \bigO{\Prob{X_3(p,p^\prime) \ge 1}}.
-\end{align*}
-By definition of $\mathcal{E}(k_n)$ and the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n} we get that for $(p,p^\prime) \in \mathcal{E}(k_n)$
-\[
-	\Exp{X_3(p,p^\prime)} \le \bigT{1} \log(n)^{-(2\alpha - 1)} + \bigT{1}e^{-(\alpha - \frac{1}{2})R_n},
-\]
-where we used that in this case $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{1}$ and $|x-x^\prime| \le \bigT{1} e^{R_n/2}$. This implies that
-\[
-	\Prob{X_3(p,p^\prime) \ge 1} \le \Exp{X_{3}(p,p^\prime)} = \bigO{\log(n)^{-(2\alpha - 1)}},
-\] 
-Next we observe that by definition of $\mathcal{E}(k_n)$ the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:disjoint_neighbors_P_n_large} satisfies
-\[
-	\sup_{(p,p^\prime) \in \mathcal{E}(k_n)} \phi_n(p,p^\prime) = \bigO{\log(n)^{-(2\alpha - 1)}}.
-\]
-Therefore we can apply the exact same arguments as for the case $k_n \to \infty$ to obtain
-\begin{align*}
-	&\int_{\mathcal{E}(k_n)} \rho_n(y,y^\prime,k_n,k_N) h(y)h(y^\prime) 
-		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-	&=(1+\smallO{1})\int_{\mathcal{E}(k_n)} \hspace{-5pt}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} h(y) h(y^\prime) 	
-		f_{\alpha,\nu}(x,y)f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-	&\hspace{10pt}+ \bigO{1}\log(n)^{-(2\alpha - 1)} \int_{\mathcal{E}(k_n)}
-		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-	&= (1+\smallO{1})\int_{\mathcal{E}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,
-\end{align*}
-where we used that
-\[
-	\log(n)^{-(2\alpha - 1)}\int_{\mathcal{E}(k_n)}
-			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime
-\]
-is of smaller order than
-\[
-	\int_{\mathcal{E}_(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
-\]
+%\noindent {\bf Case $\bm{k_n = \bigT{1}}$:}\\
+%This proof is very similar to the previous one. Here however, we write
+%\begin{align*}
+%	\rho_{n}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
+%	&= \Prob{X_3(p,p^\prime) = 0}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} 
+%		+ \bigO{\Prob{X_3(p,p^\prime) \ge 1}}.
+%\end{align*}
+%By definition of $\mathcal{E}(k_n)$ and the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n} we get that for $(p,p^\prime) \in \mathcal{E}(k_n)$
+%\[
+%	\Exp{X_3(p,p^\prime)} \le \bigT{1} \log(n)^{-(2\alpha - 1)} + \bigT{1}e^{-(\alpha - \frac{1}{2})R_n},
+%\]
+%where we used that in this case $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{1}$ and $|x-x^\prime| \le \bigT{1} e^{R_n/2}$. This implies that
+%\[
+%	\Prob{X_3(p,p^\prime) \ge 1} \le \Exp{X_{3}(p,p^\prime)} = \bigO{\log(n)^{-(2\alpha - 1)}},
+%\] 
+%Next we observe that by definition of $\mathcal{E}(k_n)$ the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:disjoint_neighbors_P_n_large} satisfies
+%\[
+%	\sup_{(p,p^\prime) \in \mathcal{E}(k_n)} \phi_n(p,p^\prime) = \bigO{\log(n)^{-(2\alpha - 1)}}.
+%\]
+%Therefore we can apply the exact same arguments as for the case $k_n \to \infty$ to obtain
+%\begin{align*}
+%	&\int_{\mathcal{E}(k_n)} \rho_n(y,y^\prime,k_n,k_N) h(y)h(y^\prime) 
+%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%	&=(1+\smallO{1})\int_{\mathcal{E}(k_n)} \hspace{-5pt}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} h(y) h(y^\prime) 	
+%		f_{\alpha,\nu}(x,y)f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%	&\hspace{10pt}+ \bigO{1}\log(n)^{-(2\alpha - 1)} \int_{\mathcal{E}(k_n)}
+%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%	&= (1+\smallO{1})\int_{\mathcal{E}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
+%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,
+%\end{align*}
+%where we used that
+%\[
+%	\log(n)^{-(2\alpha - 1)}\int_{\mathcal{E}(k_n)}
+%			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime
+%\]
+%is of smaller order than
+%\[
+%	\int_{\mathcal{E}_(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
+%			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+%\]
 \end{proof}
@@
 
-The prove is split over the two cases $k_n = \bigT{1}$ and $k_n \to \infty$.
-
-\subsubsection*{The case $\bm{k_n = \bigT{1}}$}
-
-Take $a_n = 2\log\left((k_n + C\log(n))/\xi_{\alpha, \nu}\right)$ and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}(k_n)$ as defined in~\eqref{eq:def_joint_degree_set_E_constant_k}.
+%The prove is split over the two cases $k_n = \bigT{1}$ and $k_n \to \infty$. 
+%
+%\subsubsection*{The case $\bm{k_n = \bigT{1}}$}
+%
+%Take $a_n = 2\log\left((k_n + C\log(n))/\xi_{\alpha, \nu}\right)$ and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}(k_n)$ as defined in~\eqref{eq:def_joint_degree_set_E_constant_k}.
 We will show that the expected difference between $I_{a,b}$ and $I_{a,b}^\ast$ is of smaller order than $\Exp{T_\Pcal(k_n)}^2$ so that we only need to consider $I_{a,b}^\ast$.
-
-Since 
-\[
-	|x - x^\prime| \le \left(e^{y/2} + e^{y^\prime/2}\right)\left(\frac{k_n + C \log(n)}{\xi_{\alpha,\nu}}\right)
-	= \bigO{\log(n)^2}
-\] 
-for all $p,p ^\prime \in \mathcal{E}_C(k_n)^c$, it follows that
-\begin{align*}
-	&\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} \\
-	&\le \int_{\mathcal{E}_{C}(k_n)^c} 
-		\Exp{\ind{D_{\Pcal,n}(p) = k_n - i, \, D_{\Pcal,n}(p^\prime) = k_n - i^\prime} J_b(p,p^\prime)}
-		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{J_b(p,p^\prime)}
-		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)}
-		\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} 
-		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)} 
-		f_{\alpha, \nu}(x,y) \dd x \dd y\right)	
-		\left(\int_0^{a_n} \Delta_\Pcal(y^\prime) e^{-\alpha y^\prime} \dd y^\prime\right) \\
-	&= \bigO{\log(n)^2 s_\alpha(k_n) \Exp{T_\Pcal(k_n)}},
-\end{align*}
-where the last line follows from Corollary~\ref{cor:adjusted_triangle_counting_P_n} and Proposition~\ref{prop:asymptotics_Delta_y_P} which states that for all $0 < y^\prime \le a_n$, $\Delta_\Pcal(y^\prime) = \bigO{s_\alpha(k_n)}$.
+%
+%Since 
+%\[
+%	|x - x^\prime| \le \left(e^{y/2} + e^{y^\prime/2}\right)\left(\frac{k_n + C \log(n)}{\xi_{\alpha,\nu}}\right)
+%	= \bigO{\log(n)^2}
+%\] 
+%for all $p,p ^\prime \in \mathcal{E}_C(k_n)^c$, it follows that
+%\begin{align*}
+%	&\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} \\
+%	&\le \int_{\mathcal{E}_{C}(k_n)^c} 
+%		\Exp{\ind{D_{\Pcal,n}(p) = k_n - i, \, D_{\Pcal,n}(p^\prime) = k_n - i^\prime} J_b(p,p^\prime)}
+%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{J_b(p,p^\prime)}
+%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)}
+%		\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} 
+%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)} 
+%		f_{\alpha, \nu}(x,y) \dd x \dd y\right)	
+%		\left(\int_0^{a_n} \Delta_\Pcal(y^\prime) e^{-\alpha y^\prime} \dd y^\prime\right) \\
+%	&= \bigO{\log(n)^2 s_\alpha(k_n) \Exp{T_\Pcal(k_n)}},
+%\end{align*}
+%where the last line follows from Corollary~\ref{cor:adjusted_triangle_counting_P_n} and Proposition~\ref{prop:asymptotics_Delta_y_P} which states that for all $0 < y^\prime \le a_n$, $\Delta_\Pcal(y^\prime) = \bigO{s_\alpha(k_n)}$.
 Next we note that $\Exp{T_\Pcal(k_n)} = \bigT{n k_n^{-(2\alpha - 1)} s_\alpha(k_n)}$, hence $\log(n)^2 s_\alpha(k_n) = \smallO{\Exp{T_\Pcal(k_n)}}$ and therefore we conclude that
-\[
-	\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} = \smallO{\Exp{T_\Pcal(k_n)}^2}.
-\]
-
-We now proceed with computing $I_{a,b}^\ast$.
+%\[
+%	\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} = \smallO{\Exp{T_\Pcal(k_n)}^2}.
+%\]
+%
+%We now proceed with computing $I_{a,b}^\ast$.
 For this we note that the parts of the neighborhoods $\BallPon{p}$ and $\BallPon{p^\prime}$ where $y_1, y_1^\prime \le h(p,p^\prime)$ are disjoint, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3}.
@@
 Now we observe that for $(p,p^\prime) \in \mathcal{E}(k_n)$ we have
-\begin{align*}
-	\int_{h(p,p^\prime)}^{R_n}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
-	&= \bigO{e^{y/2} e^{-(\alpha - \frac{1}{2})h(p,p^\prime)}}
-		= \bigO{\log(n)^{-(2\alpha - 1)}},
-\end{align*}
-while
-\begin{align*}
-	\int_0^{h(p,p^\prime)}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
-	&= \bigO{1}.
-\end{align*} 
-Hence if $b \ne 0$ then it follows that $\Exp{J_b} = \bigO{\log(n)^{-(2\alpha - 1)}}$ and we conclude that 
-\[
-	\Exp{I_{a,b}} = \bigO{n^2 \log(n)^{-(2\alpha - 1)}} = \smallO{\Exp{T_\Pcal(k_n)}^2}
-\]
-
-For $I_{0,0}^\ast$ we define
-\[
-	\mathcal{J}_1^\ast = \int_{\Rcal_n^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) 
-			f_{\alpha,\nu}(x_1,y_1)	f_{\alpha,\nu}(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
-\] 
-and define $\mathcal{J}_2^\ast$ in a similar way by interchanging the primed and non-primed variables. Then we get
-\[
-	\Exp{J_0(p,p^\prime)} = \mathcal{J}_1^\ast \mathcal{J}_2^\ast + \bigO{\log(n)^{-(2\alpha - 1)}}.
-\]
-In addition, for $(p,p^\prime) \in \mathcal{E}(k_n)$ Corollary~\ref{cor:adjusted_triangle_counting_P_n} implies that 
-\[
-	\mathcal{J}_1^\ast = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1 + \smallO{1})\binom{k_n}{2} \Delta_\Pcal(y),
-\] 
-and similar for $\mathcal{J}_2^\ast$, while Lemma~\ref{lem:joint_degree_factorization} states that
-\begin{align*}
-	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
-		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-	&= (1+\smallO{1})\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2.
-\end{align*}
-We therefore conclude that
-\begin{align*}
-	\Exp{I_{0,0}^\ast} 
-	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
-		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
-	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
-		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-	&\hspace{10pt}+ \bigO{\log(n)^{-(2\alpha - 1)}n^2} \\
-	&= (1 + \smallO{1}) \binom{k_n}{2}^2 
-		\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2 \\
-	&= (1 + \smallO{1})\Exp{T_\Pcal(k_n)}^2,
-\end{align*}
-which finishes the proof for $k_n = \bigT{1}$
-
-\subsubsection*{The case $\bm{k_n \to \infty}$}
+%\begin{align*}
+%	\int_{h(p,p^\prime)}^{R_n}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
+%	&= \bigO{e^{y/2} e^{-(\alpha - \frac{1}{2})h(p,p^\prime)}}
+%		= \bigO{\log(n)^{-(2\alpha - 1)}},
+%\end{align*}
+%while
+%\begin{align*}
+%	\int_0^{h(p,p^\prime)}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
+%	&= \bigO{1}.
+%\end{align*} 
+%Hence if $b \ne 0$ then it follows that $\Exp{J_b} = \bigO{\log(n)^{-(2\alpha - 1)}}$ and we conclude that 
+%\[
+%	\Exp{I_{a,b}} = \bigO{n^2 \log(n)^{-(2\alpha - 1)}} = \smallO{\Exp{T_\Pcal(k_n)}^2}
+%\]
+%
+%For $I_{0,0}^\ast$ we define
+%\[
+%	\mathcal{J}_1^\ast = \int_{\Rcal_n^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) 
+%			f_{\alpha,\nu}(x_1,y_1)	f_{\alpha,\nu}(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
+%\] 
+%and define $\mathcal{J}_2^\ast$ in a similar way by interchanging the primed and non-primed variables. Then we get
+%\[
+%	\Exp{J_0(p,p^\prime)} = \mathcal{J}_1^\ast \mathcal{J}_2^\ast + \bigO{\log(n)^{-(2\alpha - 1)}}.
+%\]
+%In addition, for $(p,p^\prime) \in \mathcal{E}(k_n)$ Corollary~\ref{cor:adjusted_triangle_counting_P_n} implies that 
+%\[
+%	\mathcal{J}_1^\ast = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1 + \smallO{1})\binom{k_n}{2} \Delta_\Pcal(y),
+%\] 
+%and similar for $\mathcal{J}_2^\ast$, while Lemma~\ref{lem:joint_degree_factorization} states that
+%\begin{align*}
+%	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
+%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%	&= (1+\smallO{1})\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2.
+%\end{align*}
+%We therefore conclude that
+%\begin{align*}
+%	\Exp{I_{0,0}^\ast} 
+%	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
+%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
+%	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
+%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%	&\hspace{10pt}+ \bigO{\log(n)^{-(2\alpha - 1)}n^2} \\
+%	&= (1 + \smallO{1}) \binom{k_n}{2}^2 
+%		\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2 \\
+%	&= (1 + \smallO{1})\Exp{T_\Pcal(k_n)}^2,
+%\end{align*}
+%which finishes the proof for $k_n = \bigT{1}$
 
@@
 \]
-let $\mathcal{E}_\varepsilon(k_n)^c$ denote its complement and, similar to the previous case, let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $p,p^\prime \in \Pcal_n \cap \mathcal{E}_\varepsilon(k_n)$.
-We first show that
+let $\mathcal{E}_\varepsilon(k_n)^c$ denote its complement and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $p,p^\prime \in \Pcal_n \cap \mathcal{E}_\varepsilon(k_n)$. We first show that
 \begin{equation}\label{eq:I_ab_ast_main}

### 2019-01-19 concentration_argument.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

@@
 
-Many of the computations in this paper will involve integrals whose integrand contains $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and $\mu_n(y) \approx e^{y/2}$.
+Many of the computations in this paper will involve integrals whose integrand contains the function $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and $\mu_n(y) \approx e^{y/2}$.
 For instance, the expected modified local clustering function $c_\infty(k)$ in $G_\Pcal$ equals
@@
 \]
-where $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$. 
-\TM{ Maybe state where $\Delta$ is defined in the paper. }
+where $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ and $\Delta_{\Pcal}(y)$ is defined by~\eqref{eq:def_delta_p}.
 
@@
 
-\subsection{Concentration \TM{ "of heights"? } argument for the infinite model}
+\subsection{Concentration of heights argument for the infinite model}
 
@@
 To solve this we could either restrict to sequences that are either a) constant or b) tending to infinity; or we could make a cut-off at some specific, slow growing function such as $\log\log\log n$.
-}
+}\PvdH{You are right, I overlooked this fact.
+I would opt to go with the setting where we consider only sequences that are either asymptotically bounded or tend to infinity.
+After the new proves are added we can see where we specify this.}
 and define further, for any $C > 0$
 \begin{equation}\label{eq:def_K_C_set}
-	\Kcal_C(k_n) = \left\{p=(x,y) \in \R \times \R_+ : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
-	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \wedge e^{R_n/2} \right\},
+	\Kcal_C(k_n) = \left\{p=(x,y) \in \R \times \R_+ : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \le e^{\frac{y}{2}}
+	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \right\},
 \end{equation}
-\TM{ taking max with 0 and min with $R$ do not seem necessary. }
 Where we recall that $a \vee b = \max\{a,b\}$ and $a \wedge b = \min\{a,b\}$.
@@
 \TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal_n$. Is this really meant?
-I would have expected we just integrate wrt.~$y$ and replace $f_{\alppha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}
+I would have expected we just integrate wrt.~$y$ and replace $f_{\alpha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}\PvdH{I understand this confusion and agree that your suggestion makes more sense here.
+However, I choose this setup to minimize notations later.
+I am for changing the setup to what you are suggesting but I will have to spend some time first on checking how that will effect the definitions in later sections.}
 it is enough to consider integration \BL{over} $\Kcal_C(k_n)$ instead of $\Rcal_n$.
@@
 \[
-	\lambda_n^\pm = \ell_n \pm C \kappa_n, 
+	\lambda_n^\pm = (\ell_n \pm C \kappa_n) \wedge \kappa_n, 
 	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right),
@@
 \TM{ If $k$ is constant, then $\ell^- < 0$ and hence 
-$a^-$ is undefined! Need to change the definitions. }
+$a^-$ is undefined! Need to change the definitions. }\PvdH{You are right. I changed it by taking the minimum with $\kappa_n$.}
 
@@
 \begin{aligned}
-	\int_{\R_+ \setminus [a_n^-, a_n^+]} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd x \dd y
+	\int_{\Rcal_n\setminus \Kcal_{C}(k_n)} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd x \dd y
 	&= \begin{cases}
@@
 
-\subsection{Average degree in the hyperbolic random graph}\label{ssec:average_degree_HP_n}
+\subsection{Expected number of points in balls in the hyperbolic random graph}\label{ssec:average_degree_HP_n}
 
@@
 We are considering the expected number of points in a ball, but not yet computing the average degree of the graph.
-}
-Recall that under the coupling between the hyperbolic random graph and the finite box model $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$, while the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
+}\PvdH{I agree and have changed the header.}
+Recall that under the coupling between the hyperbolic random graph and the finite box model, for two points $p, p^\prime$ with $y + y^\prime < R_n$, $p^\prime \in \BallHyp{p}$ exactly when $|x-x^\prime|_{\pi e^{R_n/2}} \le \Phi(r,r^\prime)$.
+In this setting, the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
 \[
-	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Omega(r, r^\prime) 
+	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Phi(r, r^\prime) 
 		\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
 \]
-for $y + y^\prime < R_n$.
-\TM{ Say what $K$ is and what the restrictions on $r, r'$ are.
-} This result enables us to determine the measure of a ball around a given point $p=(0,y)$ which will be fairly useful in our subsequent analysis.
+for some constant $K$. %\TM{ Say what $K$ is and what the restrictions on $r, r'$ are. } 
+This result enables us to determine the measure of a ball around a given point $p=(0,y)$ which will be fairly useful in our subsequent analysis.
+Recall that the hyperbolic ball $\BallHyp{p}$ is a subset of $\Rcal_n$ and not of the hyperbolic disc $\Dcal_{R_n}$, i.e.
+the balls $\BallHyp{p}$ "live" in the finite box and not the hyperbolic disc.
 
@@
 \]
-\TM{ maybe remind the reader just before of the rather counter intuitive definition of $\BallHyp{0,y}$, which 
-lives in the box model not in the original hyperbolic disk. }
 where
@@
 			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
-			&\mbox{if } \alpha > 3/2.
+			&\mbox{if } \alpha > 3/2,
 		\end{cases}
 \]
-\TM{ We want to say in the lemma where $K$ comes from. (not everyone reads surrounding text, or reads linearly, in a paper as long as this one.) }
+with $K$ being the constant coming from the approximation of $\Phi$ in Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
+%\TM{ We want to say in the lemma where $K$ comes from. (not everyone reads surrounding text, or reads linearly, in a paper as long as this one.) }
 \end{lemma}
@@
 \begin{proof}
-We will split the computation of $\Mu{\BallHyp{0,y}}$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$ \TM{ You have not said what $y^\prime$ is!
-} where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
-Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.
+We perform the computation of $\Mu{\BallHyp{0,y}}$ by splitting the integration with respect to the height $y^\prime$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$, %\TM{ You have not said what $y^\prime$ is!
+}
+where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}. Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.
 
@@
 
-\subsection{Average degree in the finite box model}\label{ssec:average_degree_P_n}
+\subsection{Expected number of points in balls in the finite box model}\label{ssec:average_degree_P_n}
 
-\TM{ same comment Re: average degree. }
+%\TM{ same comment Re: average degree. }
 For the finite box model $G_{\Pcal,n}(\alpha, \nu)$ we obtain a similar result for the average degree.
@@
 \[
-	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right)
+	\mu_{\alpha,\nu}(\BallPon{p}) = \mu_{\alpha,\nu}(\BallPo{p})\left(1 - \phi_n(y)\right)
 \]
-\TM{ where did the curly B's go? }
+\TM{ where did the curly B's go? }\PvdH{Typo. Fixed}
 where $\phi_n(y) \ge 0$ is given by
@@
 \[
-	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
+	\mu_{\alpha,\nu}(\BallPon{p}) = \mu_{\alpha,\nu}(\BallPo{p})\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
 \]
@@
 First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$.
-We then have that
-\[
-	\BallPon{p} = \left\{p^\prime \in \Rcal_n \, : \, |x^\prime| \le e^{\frac{y + y^\prime}{2}}\right\},
-\] 
-\TM{ There a rogue subscript $n$ in $|x'|_n$ }
-whose boundaries given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$ intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
-\TM{ weird sentence }
+We then have that the boundaries of $\BallPon{p}$ are given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$, which intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
 \[
@@
 
-\subsection{Concentration \TM{ OF HEIGHTS? }argument for hyperbolic and finite box model}
+\subsection{Concentration of heights argument for hyperbolic and finite box model}
 
-With the results on the average degrees in the two finite Poisson models, we can now establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the degree distributions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$ in $G_{\HP,n}$ and $G_{\Pcal,n}$, respectively.
+With the results on number of points in the balls in the two finite Poisson models $G_{\HP,n}$ and $G_{\Pcal,n}$, we can now establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the functions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$.
 The lemma is stated in a more general form, to make it applicable to slightly other cases later in the paper.
@@
 Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and let $\Kcal_{C}(\ell_n)$ be defined as in~\eqref{eq:def_K_C_set}.
-In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is any function satisfying
+In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is any differentiable function satisfying
 \[
@@
 \begin{enumerate}
-\item for any sequence of functions $h_n(y) : \R_+ \to \R$ such that $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s e^{\beta y}}$ \TM{ Why not adjust $h$ so that we incorporate $\hat\rho$ in line below.
+\item for any sequence of continuous functions $h_n(y) : \R_+ \to \R$ such that $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s e^{\beta y}}$ \TM{ Why not adjust $h$ so that we incorporate $\hat\rho$ in line below.
 Then both items look more similar.
-}  for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
+}\PvdH{I am not sure what you are suggesting.
+Could you explain a bit more?}  for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
 \[
 	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
-	= (1 + o(1)) \int_{\Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
+	= (1 + o(1)) \int_{\Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y,
 \]
-\item for any uniformly bounded function $h : \R_+ \to \R$,
+with $\Kcal_{C}$ defined in~\eqref{eq:def_K_C_set}
+\item for any continuous and uniformly bounded function $h : \R_+ \to \R$,
 \[
@@
 \end{enumerate}
-\TM{ Say in the lemma statement where def of $K_C$ can be found. }
+%\TM{ Say in the lemma statement where def of $K_C$ can be found. }
 \end{lemma}
@@
 \[
-	\lambda_n^\pm = \ell_n \pm C \kappa_n, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right).
+	\lambda_n^\pm = (\ell_n \pm C \kappa_n) \wedge \kappa_n, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right).
 \] 
-\TM{ Same problem as in L3.1. $\lambda^-$ can be negative, in which case $a^-$ is undefined.}
+%\TM{ Same problem as in L3.1. $\lambda^-$ can be negative, in which case $a^-$ is undefined.}
 In addition we fix $\varepsilon > 0$ such that $\varepsilon < \min\{1- \frac{s}{2\alpha(2\alpha + 1)}, 1\}$. Then since $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s}$ we have
@@
 \end{equation}
-which implies \TM{ "implies"? this is just by definition. }
+and therefore %\TM{ "implies"? this is just by definition. }
 \[
@@
 \]
-Observe that since
-\[
-	\mu^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
-\]
-\TM{ repeat of previous eq. Typo or leftover of old version ... ? }
+Observe that since $\mu^{-1}(y)$
+%\[
+%	\mu^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
+%\]
+%\TM{ repeat of previous eq. Typo or leftover of old version ... ? }
 is strictly monotonic in $y$, we have, by our assumptions on $\hat{\mu}_n$, that
@@
 \end{equation}
-\TM{ Please elaborate! Why would $\hat\mu$ be diff'ble anyway? }
-Denote by $g^\prime(z)$ the derivative of a function $g$.
-\TM{ I would remove this last sentence. }
+\TM{ Please elaborate! Why would $\hat\mu$ be diff'ble anyway? }\PvdH{I have added the diff'ble assumption to the lemma statement}
+%Denote by $g^\prime(z)$ the derivative of a function $g$.
+%\TM{ I would remove this last sentence. }
 Then by assumption $(\phi_n^{(i)})^\prime(z) = \bigT{\phi_n^{(i)}(z)}$ and hence
@@
 \end{align*}
-\TM{ Please elaborate 2nd equlaity. I don't quite follow. }
+\TM{ Please elaborate 2nd equlaity. I don't quite follow. }\PvdH{The fraction $\hat{\mu}_n^\prime(z)/\mu^{\prime}(z)$ comes from the change of variables. Or is this not what you mean?}
 The result then follows by Lemma~\ref{lem:concentration_argument}.
@@
 Do we assume $h$ is continuous?
-}Therefore, with the change of variables~\eqref{eq:concentration_argument_variable_change} we get
+}\PvdH{Yes, we probably should.
+I have added this to the lemma statement.} Therefore, with the change of variables~\eqref{eq:concentration_argument_variable_change} we get
 \begin{align*}
@@
 Then, for any function $g_n(y)$ such that $g_n(y) = \bigO{n^{-1} k_n^{s} e^{\beta y}}\hat{\rho}_n(y,k_n)$ \TM{ Where did the $n^{-1}$ come from?
-Does not appear in L3.4. }, as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
+Does not appear in L3.4.
+}\PvdH{I will elaborate on this once the statement of Lemma~\ref{lem:concentration_argument} is updated}, as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
 \[

### 2019-01-19 introduction.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

@@
 \end{enumerate}
-Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
-\TM{ \RD{Remove this reference, and replace with Abdullah-Bode-Fountoulakis!!!!}
+Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Abdullah et al.~\cite{abdullah2017typical} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
+\TM{
 In general the proofs that GIRG = HRG are shaky at best, so I do not want to cite anything that relies on that.
@@
 This includes 2nd largest componnent, connectivity, spectral gap, diameter, Hamilton cycles \& perfect matchings (with Markus, Nikolaos and Mitsche, in preparation but perhaps submitted around the same time as this one.).
-Also there is a recent paper on arxiv by Owada+Yogeshwaran on subgraph counts.}
+Also there is a recent paper on arxiv by Owada+Yogeshwaran on subgraph counts.}\PvdH{Great, could you add those to the bib file and mention them here.}
 
@@
 
-\TM{ I vote to remove this next paragraph. Use of GIRGs is fishy, and also we are not obliged to mention any and all possible alternative approaches. }
+\TM{ I vote to remove this next paragraph.
+Use of GIRGs is fishy, and also we are not obliged to mention any and all possible alternative approaches.
+}\PvdH{I do not mind if we remove the paragraph.
+However, the results in J\'{u}lias's paper are rigorous so I do not think that is a good reason for removing the paragraph.}
 We remark that it is possible to prove that the local clustering coefficient converges to some limit, using the technical tools in the recent work on explosion times in Geometric Inhomogeneous Random Graphs~\cite{komjathy2018explosion}.
@@
 \subsection{Outline of the paper}
+
+\PvdH{@Tobias and Markus: I haven't update this section yet since it will also depend on your new proofs. Please update it once you have added these to the paper.}
 
@@
 \end{align*}
-The approximation for the hyperbolic balls you and Nicolaos derived in Lemma 28 holds only when $r_i + r_j \ge R$.}
+The approximation for the hyperbolic balls you and Nicolaos derived in Lemma 28 holds only when $r_i + r_j \ge R$.
+There were however some sloppy arguments later in Section~\ref{ssec:coupling_H_P}, regarding the hyperbolic balls, which I corrected.}
 \end{enumerate}
@@
 
-Our results for the local clustering function in particular imply uniform convergence of $c_{\H,n}(k)$ for all $3 \le k \le a_n$ \TM{ Why 3?
-} where $a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
+Our results for the local clustering function in particular imply uniform convergence of $c_{\H,n}(k)$ for all $2 \le k \le a_n$ \TM{ Why 3?
+}\PvdH{Should have been $2$ (corrected) since there are no triangles for node with degree less than $2$.} where $a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
 To see this let

### 2019-01-19 paper.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{tocloft}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Redefines the space between sections in the TOC so that the entire thing fits on one page. 
+% Comment this out when not using the tocloft package
+\setlength{\cftbeforesecskip}{5pt}
 
@@
 
+%Uncomment the part below to remove all comments
+%\renewcommand{\PvdH}[1]{}
+%\renewcommand{\TM}[1]{}
+%\renewcommand{\MS}[1]{}
+%\renewcommand{\NF}[1]{}
+
 \allowdisplaybreaks
@@
 
-\title{Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph".
-Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}}
+\title{Exact asymptotic expressions for local clustering in a hyperbolic model of complex networks.
+\\ \TM{ I prefer not to use the term ``hyperbolic random graph".
+Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}\PvdH{I am not really a fan of the term KPKVB random graph so I implemented the second suggestion.}}
 \author[1]{Nikolaos Fountoulakis}
@@
 
-\input{proof_overview}
+\input{proof_overview_finite_k}
+
+\input{clustering_infinite_model}
+
+\input{proofs_finite_k}
+
+\input{proofs_infinite_k}
 
 \input{concentration_argument}
-
-\input{clustering_infinite_model}
 

### 2019-01-19 proof_overview_finite_k.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

\section{Overview of the proof strategy for fixed $k$}\label{sec:proof_outline}

\PvdH{This section has to be adjusted to include the right references to the new theorems where fixed and diverging $k$ have been separated.}

The key result in this paper is Theorem~\ref{thm:local_clustering_hyperbolic}. In particular, it is the key ingredient in the proofs of Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
\TM{ Sounds weird, since Thm 1.3 is just about asymptotics of certain functions. }

\begin{remark}[Model parameters]
Throughout the remainder of this paper, unless otherwise specified, $\alpha$ and $\nu$ will be real numbers satisfying $\alpha > 1/2$ and $\nu > 0$.
\end{remark}

Our approach builds on the work in~\cite{fountoulakis2018law}, where tools were developed to analyze the size of the largest component in the hyperbolic model which can be reused here. The main idea is to couple the hyperbolic graph $G_{\H, n}(\alpha, \nu)$ with a finite subgraph $G_{\Pcal,n}(\alpha,\nu)$ of an infinite graph $G_\Pcal(\alpha,\nu)$ whose nodes are given by a Poisson Point Process (see Section~\ref{ssec:infinite_model}). The infinite graph will then yield the limit expressions for the local clustering coefficient and function.
\TM{ The Komjathy paper used GIRG, which is fishy. So I say we do not cite that. }
%and in \cite{komjathy2018explosion} to analyze explosion %times in a more general class of models. 
The advantage of the infinite limit model is two-fold. Firstly, it simplifies the actual computations, e.g. by replacing hyperbolic densities with exponential densities and the hyperbolic distance with a computationally easier expression. Secondly, it directly yields the limit as a result as opposed to some long expression depending on $n$.

Very roughly, the proof falls into four parts: 1) replacing the randomly sampled nodes in the hyperbolic graph with a Poisson Point Process, 2) justifying the transitioning from this Poisson version of the hyperbolic random graph to the finite model, 3) show that the limit expression correspond to those in the infinite model and finally 4) calculating the expected local clustering coefficient and function in the infinite limit model. \PvdH{@Tobias and Markus: Please include the references to the new theorems for fixed $k$.} This strategy is executed in Section~\ref{sec:proofs_fixed_k} where we prove Theorems [??].

In this section, we define both the infinite and finite model. We then explain how to transition from local clustering in the finite to the infinite model. Finally, we describe the coupling between our finite model and the hyperbolic model and show how this coupling allows us to relate local clustering between them.

We start with some small notational conventions.

\subsection{Notations}
We adopt standard Landau notations for asymptotic statements. For two functions $f$ and $g$ we write $f(x) = \bigO{g(x)}$ as $x \to \infty$ if
\[
	\limsup_{x \to \infty} \frac{|f(x)|}{g(x)} < \infty,
\]
while $f(x) = \smallO{g(x)}$ as $x \to \infty$ means
\[
	\lim_{x \to \infty} \frac{f(x)}{g(x)} = 0,
\]
and $f(x) = \bigT{g(x)}$ as $x \to \infty$ whenever
\[
	\limsup_{x \to \infty} \left|\frac{f(x)}{g(x)}\right| > 0 \quad \text{and} \quad
	\limsup_{x \to \infty} \frac{|f(x)|}{g(x)} < \infty.
\]
Moreover we will write $a \vee b$ for $\max\{a,b\}$ and $a \wedge b$ for $\min\{a,b\}$.

\subsection{Infinite limit model}\label{ssec:infinite_model}

To define the infinite graph $G_{\mathcal{P}}(\alpha, \nu)$ write $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and let $\mathcal{P}=\mathcal{P}_{\alpha,\nu}$ be a Poisson point process on $\Rcal$ with intensity function
\begin{equation}\label{eq:def_intensity_function_f}
	f_{\alpha,\nu}(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y}.
\end{equation} 
We will write $p = (x, y)$ for points in $\Rcal$.  In addition we denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e. for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
\begin{equation}\label{eq:def_mu_P}
	\mu_{\alpha,\nu}(S) = \int_S f_{\alpha,\nu}(x,y) \, dx \, dy,
\end{equation}

The \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
\[
	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
\]
For any point $p \in \Rcal$, we write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
\begin{equation}\label{eq:def_ball_P}
	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
\end{equation}
With this notation we then have that $\BallPo{p} \cap \PPP$ denotes the set of neighbors of a vertex $p \in G_{\Pcal}(\alpha,\nu)$.

\begin{remark}[Notations for points]\label{rmk:point_notation}
We will be working extensively with expressions in terms of points of $\Pcal_{\alpha, \nu}$, often relating them back to points in the hyperbolic disc $\Dcal_{\Rcal_n}$. Therefore, in the remainder of this paper we will always use $u = (r,\theta)$ to denote points in $\Dcal_{\Rcal_n}$ in polar coordinates while $p = (x,y)$ will denote points in $\Rcal := \mathbb{R} \times \mathbb{R}_+$ in Cartesian coordinates. In addition, when we write $p^\prime \in \mathbb{R} \times \mathbb{R}_+$ we will denote its Cartesian coordinates by $(x^\prime, y^\prime)$ and similarly for $p_i$, $u^\prime$ and $u_i$, e.g. $p_i = (x_i, y_i)$. In addition, for a point $p = (x,y)$, we will refer to $y$ as the \emph{height} of $p$.
\end{remark}

%To analyze the limiting expressions for clustering in the finite random graph $G_{\Pcal,n}(\alpha, \nu)$ we shall use an infinite graph model which can be understood as taking the finite graph $G_{\Pcal,n}(\alpha,\nu)$ and taking $n \to \infty$. Recall that $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and that $\mathcal{P}_{\alpha,\nu}$ is a Poisson point process on $\Rcal$ with intensity function
%\[
%	f_{\alpha,\nu}(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y}.
%\]
%
%The \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
%\[
%	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
%\]
%For a point $p \in \Rcal$, we will write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
%\begin{equation}\label{eq:def_ball_P}
%	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
%\end{equation}

\subsection{Finite box model}\label{ssec:finite_model}

For the definition of the finite graph, recall that $R_n = 2\log(n/\nu)$ and consider the finite box $\Rcal_n = (-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}] \times (0, R_n]$ in $\Rcal$. Then the \emph{finite box model} graph $G_{\mathcal{P},n}(\alpha, \nu)$ has vertex set $\mathcal{V}_n := \mathcal{P}_{\alpha, \nu} \cap \Rcal_n$ and edges set such that
\[
	(p_i, p_j) \in E(G_{\mathcal{P},n}(\alpha, \nu)) \iff |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}},
\]
where $|x|_{\pi e^{R_n/2}} = \inf_{k \in \mathbb{Z}} |x + k \pi e^{R_n/2}|$. This norm means that the boundaries of $(-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}]$ are identified, which is done to exclude boundary effects and make the model invariant under horizontal translation and reflections in vertical lines. The graph $G_{\mathcal{P},n}(\alpha, \nu)$ can thus be seen as a subgraph of $G_{\mathcal{P}}(\alpha, \nu)$ induced on $\mathcal{V}_n$, with some addition edges caused by the identification of the boundaries.

Similar to the infinite graph, for a point $p \in \Rcal_n$ we define the ball $\BallPon{p}$ as
\begin{equation}\label{eq:def_ball_P_n}
	\BallPon{p} = 
	\left\{p^\prime \in \Rcal_n : |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}}\right\}.
\end{equation}

\subsection{Properties of the infinite graph model}

\PvdH{@Tobias: please see if you agree with this setup.} 
The main utility of the infinite graph $G_\Pcal(\alpha, \nu)$ is that we can use it to express limits of properties in the finite model, and eventually the hyperbolic random graphs. To this end we add a "typical" point $p_0 := (0,y) \in \Rcal$, with height $y$ exponentially distributed with rate $\alpha$, and then generate the Poisson Point Process $\Pcal_{\alpha, \nu}$ independently of $y$. Technically, the vertex set of $G_\Pcal(\alpha,\nu)$ then becomes $\Pcal_{\alpha, \nu} \cup p_0$.

A very useful tool to analyze expressions in the both the finite and infinite model is the \emph{Campbell-Mecke Formula}~\cite[Theorem 3.2]{baddeley2007spatial}, which states that for a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and any measurable function $h : S \mapsto \R$,
\begin{equation}\label{eq:def_Campbell-Mecke}
	\Exp{\sum_{p \in \Pcal} h(p)} = \int_S \Exp{h(x)} \dd \lambda(x)
\end{equation}
In essence the results tells us that taking averages of a function over points in a Poisson Points Process simply to integrating the function with respect to the intensity measure. This transformation of summations into integrals is very powerful and we will use this to derive expressions for the degrees and local clustering in the infinite model.
%For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ \TM{ Below there is one more argument. (a set) } we have
%\begin{equation}\label{eq:def_Campbell-Mecke}
%\begin{aligned}
%& \Exp{\sum_{x_1,\ldots, x_r \in \mathcal{P}}^{\neq} h (x_1, \ldots, x_r,
%\mathcal{P} \setminus \{x_1,\ldots, x_r\}) }\\
%& = \int_S \cdots \int_S
%\Exp{h(x_1,\ldots, x_r,\mathcal{P} \setminus \{x_1,\ldots, x_r\}) \lambda (x_1) \cdots \lambda (x_r) dx_1 \cdots dx_r},
%\end{aligned}
%\end{equation}
%where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$. \TM{ Are you sure this is the Mecke formula? }\PvdH{This was indeed incorrect. It is the extended Slivnyak-Mecke theorem.}

\paragraph{Degrees}
If we fix a $y \in \R_+$, then it follow from~\eqref{eq:def_Campbell-Mecke} that the expected number of points in $\BallPo{(0,y)}$ is given by
\[
	\Exp{\sum_{p \in \Pcal} \ind{p \in \BallPo{(0,y)}}} = \mu_{\alpha, \nu}(\BallPo{(0,y)}), 
\] 
which can be computed as,
\begin{equation}\label{eq:mu_ball_y_P}
	\mu_{\alpha, \nu}(\BallPo{(0,y)}) =  \int_0^\infty \int_{-\infty}^\infty \ind{|x^\prime|\le e^{(y + y^\prime)/2}} 
	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x^\prime \dd y^\prime
	= \frac{4\alpha \nu}{(2\alpha - 1)\pi} e^{\frac{y}{2}} := \xi_{\alpha,\nu}e^{\frac{y}{2}}.
\end{equation}

We shall write $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(\BallPo{p})$, i.e.
\[
	\rho(p,k) = \rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k}.
\]
Let us denote by $D_\Pcal$ the degree of the typical vertex $p_0$ in $G_\Pcal(\alpha,\nu)$. Then, since the number of points in $\BallPo{p_0}$ is a Poisson random variable with mean $\Mu{\BallPo{p_0}}$, the distribution of $D_\Pcal$ conditioned on the height $y$ is given by $\rho(y,k)$. Therefore, the degree distribution of the typical point is 
\[
	\Prob{D_\Pcal = k} = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y,
\]
which again can be explicitly computed, see Section~\ref{ssec:degrees_infinite_model}.

\begin{remark}[Degree distributions in the other models]
Similar to the infinite graph, we will consider the degree of a typical point in a Poisson version of the hyperbolic graph $G_{\HP,n}$ and the finite random graph $G_{\Pcal,n}$. These will again be distributed as a Poisson random variable with given means and, following the notation above, we will denote these distributions by $\rho_{\HP,n}(y,k)$ and $\rho_{\Pcal,n}(y,k)$.
\end{remark}

\paragraph{Local clustering}
We can also define a local clustering coefficient and function in the infinite model. 
%However, since $G_\Pcal$ has an infinite number of nodes the corresponding definitions are slightly different than for the finite size models. Intuitively the local clustering coefficient is the probability that two random neighbors of a randomly sampled node form a triangle , while the local clustering function is the same probability but conditioned on the sampled node having degree $k$. \TM{ again "randomly sampled" does not immediately make sense here. You may want to say we generate a point $(0,y)$ with $y$ 
%exponential $\alpha$ distributed and add this to the PPP, which is generated indeptly of $y$.} 
%
%Again, due to symmetry in the $x$ direction we can assume without loss of generality that a randomly sampled point $p$ is $(0,y)$. 
For any $y \in \R_+$ we define the probability density function $\eta_y$ on $\Rcal :=  \R \times \R_+$ by  
\begin{equation}\label{eq:def_eta_P}
	\eta_y(x^\prime, y^\prime) = \frac{\ind{p^\prime \in \BallPo{(0,y)}} f_{\alpha,\nu}(x^\prime,y^\prime)}{\mu_{\alpha,\nu}(\BallPo{(0,y)})}.
\end{equation}
That is $\eta_y$ is the density $f_{\alpha,\nu}$ restricted to the ball $\BallPo{(0,y)}$, properly normalized to make it a probability distribution. It can be interpreted as the probability density of a randomly sampled point in $\BallPo{(0,y)}$, i.e. a randomly sampled neighbor of $(0,y)$ in the infinite model.

We then define
\begin{equation}\label{eq:def_delta_p}
	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(y, x_1, x_2, y_1, y_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \dd x_1 \dd x_2  \dd y_1  \dd y_2,
\end{equation}
with 
\[
	T_\Pcal(y, x_1, x_2, y_1, y_2) 
	= \ind{|x_1| \, \le \, e^{(y+y_1)/2}}\ind{|x_2| \, \le \, e^{(y+y_2)/2}}\ind{|x_1-x_2| \, \le \, e^{(y_1+y_2)/2}}.
\]
Note that $\Delta_{\Pcal}(y)$ is the probability that two randomly sampled points in $\BallPo{(0,y)}$ form a triangle with the vertex $(0,y)$.

%\TM{ This next bit again suffers from the same issue as above. You cannot "randomly sample a point". }
%Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$: the distribution function of the radial coordinate of a vertex sampled in the disk is $\frac{\cosh(\alpha  r)-1}{\cosh(\alpha R)-1}$ which is asymptotically equivalent to $e^{\alpha(r-R)} = e^{-\alpha y}$, if $r$ and $R$ are large, resp. tending to infinity and $y=R-r$ and because of the minus sign in front of the $r$, the distribution function in $r$ turns into the complementary distribution function of $y$, from which we recognize the exponential distribution with parameter $\alpha$.
%
%\PvdH{@All: This explanation was added by Markus at my request. If someone has a better explanation why this is the case please update this section.}

With these expressions we define the limiting local clustering coefficient as
\begin{equation}\label{eq:def_average_clustering_infinite_model}
	c_\Pcal := \int_0^\infty \Delta_{\Pcal}(y) (1 - \rho(y,0) - \rho(y,1)) \alpha e^{-\alpha y} \dd y,
\end{equation}
while the limiting local clustering function is defined as
\begin{equation}\label{eq:def_c_infty_k}
	c_\Pcal(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
\end{equation}

In Section~\ref{sec:asymptotics_average_clustering_ast_P} we will compute both these quantities and show that $c_\Pcal = c_\infty$ and $c_\Pcal(k) = c_\infty(k)$, where $c_\infty$ and $c_\infty(k)$ are given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}.

\subsection{Coupling the hyperbolic model to the finite box model}\label{ssec:coupling_H_P}

The final step of our proof strategy is to couple the hyperbolic graph to $G_{\mathcal{P},n}(\alpha, \nu)$. For this we consider the original hyperbolic graph on a Poisson distributed number of vertices as an intermediate step. We define $G_{\HP,n}(\alpha, \nu)$ to be the hyperbolic random graph where the vertex set is given by $N \stackrel{d}{=} \Po(n)$ points, i.i.d.~and independent of $N$, distributed according to the $(\alpha, R_n)$-quasi uniform distribution~\eqref{eq:def_hyperbolic_point_distribution} defined in Section \ref{ssec:hyperbolic_model}.

First we have to show that replacing uniform sampled points with this Poisson Point Process does not influence the properties of the model, so that we can proceed with the latter.

\PvdH{@Tobias and Markus: I was not sure if you want to state a Lemma here that does this or simply refer to a later section where this is done. So please update this part once you added the proof for fixed $k$.}

The following two lemmas from \cite{fountoulakis2018law} establish a coupling between the Poisson version of the hyperbolic random graph and the finite box model and relate the hyperbolic neighborhoods to the neighborhood balls $\BallPo{p}$. 
%The ensuing proposition verifies that this coupling also essentially preserves the local clustering function, i.e. that the difference between the local clustering function in the hyperbolic model and the finite box graph converges to zero faster than the proposed scalings in the main result, Theorem \ref{thm:local_clustering_hyperbolic}. Hence, it justifies the transition to the finite box model.

\begin{lemma}[{\cite[Lemma 27]{fountoulakis2018law}}]\label{lem:coupling_hyperbolic_poisson}
Let $\mathcal{V}_{\HP, n}$ denote the vertex set of $G_{\HP,n}(\alpha, \nu)$ and $\mathcal{V}_n$ the vertex set of $G_{\Pcal,n}(\alpha, \nu)$. Define the map $\Psi : [0,R_n] \times (-\pi, \pi] \to \mathcal{R}_n$ by
\begin{equation}\label{eq:def_Psi}
	\Psi(r,\theta) = \left(\theta \frac{e^{R_n/2}}{2}, R_n - r\right).
\end{equation}
Then there exists a coupling such that, a.a.s.\TM{ Have we defined a.a.s.? If no, add it before using it. }, $\mathcal{V}_n = \Psi(\mathcal{V}_{\HP,n})$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
%\begin{equation}\label{eq:convergence_miscoupling_hyperbolic_poisson}
%	\Prob{\Ccal_n^c} = \bigO{n^{-(2\alpha - 1)}}. 
%\end{equation}
\end{lemma}

In the remainder of this paper we will write $\BallHyp{p}$ to denote the image under $\Psi$ of the ball of hyperbolic radius $R_n$ around the point $\Psi^{-1}(p)$, i.e. 
\[
	\BallHyp{p} := 
	%\left\{p^\prime := \Psi(u) \, : \, u \in \Dcal_{R_n} \text{ and } d_\H(\Psi^{-1}(p),u) \le R_n\right\}.
	\Psi\left[ \left\{ u \in \Dcal_{R_n} : 
	d_\H(\Psi^{-1}(p),u) \le R_n\right\}\right].
\]
Note that we have that $\BallHyp{p} \subseteq \mathcal{R}_n$. In particular, a point $p = (x,y) \in \Rcal$ corresponds to $u := \Psi^{-1}(p) = (2 e^{-R_n/2} x, R_n - y)$.

Let $u, u^\prime \in \Dcal_R$ and write $\theta(u, u^\prime) := |\theta - \theta^\prime|_{2\pi}$ for their relative angle. If $r + r^\prime < R_n$, it holds for all $0 \le \phi \le 2\pi$ that
\[
	\cosh r \cosh r^\prime - \sinh r \sinh r^\prime \cos \phi \le \cosh(R_n),
\] 
which implies that $d_{\H}(u,u^\prime) \leq R_n$ and hence $u$ and $u^\prime$ are connected. Now consider a point $p \in \mathcal{V}_n$ and write $\Psi^{-1}(p) = (r,\theta)$. Then it follows that for any point $u^\prime \in \Dcal_R$
\begin{equation}\label{eq:tail_inclusion_hyperbolic_ball}
	r^\prime < y = R_n - r \Rightarrow d_{\H} (\Psi^{-1}(p),u^\prime) \leq R_n.
\end{equation}
In other words, we have $(-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}] \times [r, R_n]  \subset \BallHyp{p}$.

When $r + r^\prime > R_n$ the equation 
\[
	\cosh R_n =\cosh r \cosh r^\prime - \sinh r \sinh r^\prime \cos \phi
\]
has two solutions of the form $\theta_{R_n}(r,r^\prime)$ and $2\pi - \theta_{R_n}(r,r^\prime)$ (when $r + r^\prime = R_n$ there is only one solution $\theta_{R_n}(r,r^\prime)$). It then follows that $d_{\H}(u,u^\prime) \leq R_n$ if and only if their relative angle $\theta(u, u^\prime)$ satisfies $\theta(u, u^\prime) \leq \theta_{R_n}(r,r^\prime)$.
To write this differently, define
\begin{equation}\label{eq:def_Omega_hyperbolic}
	\Phi(r,r^\prime) := \frac{1}{2}e^{R_n/2} \arccos\left( \frac{\cosh r \cosh r^\prime - \cosh R_n}
	{\sinh r \sinh r^\prime} \right).
\end{equation}

\PvdH{@All: Since the choice of $\Omega$ here is slightly problematic (we also sometimes use $\Omega$ for its asymptotic scaling notation) I have switched $\Omega \mapsto \Phi$.}

Then if $r + r^\prime > R_n$ we have that $d_{\H}(u,u^\prime) \leq R_n$ if and only if $\theta(u, u^\prime) \leq 2 e^{-R_n/2}\Phi(r,r^\prime)$. Under the coupling map $\Psi$, this is equivalent to $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$. The following lemma, which appears in~\cite{fountoulakis2018law}, gives useful bounds on the function $\Phi(r,r^\prime)$ in the regime $r + r^\prime > R_n$.

\begin{lemma}[{\cite[Lemma 28]{fountoulakis2018law}}]\label{lem:asymptotics_Omega_hyperbolic}
There exists a constant $K>0$ such that, for every $\varepsilon > 0$ and for $R_n$ sufficiently large, the following holds.
For every $r,r^\prime \in [\varepsilon R_n,R_n]$ with $r + r^\prime > R_n$ we have that 
\begin{equation}\label{eq:asymp1}
	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Phi(r, r^\prime) 
	\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
\end{equation}
where $y := R_n - r, y^\prime := R - r^\prime$. 
Moreover:
\begin{equation}\label{eq:asymp2} 
\Phi(r,r^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $r, r^\prime < R_n - K$.} 
\end{equation}
\end{lemma}

A key consequence of Lemma~\ref{lem:asymptotics_Omega_hyperbolic} is that the coupling from Lemma~\ref{lem:coupling_hyperbolic_poisson} preserves edges between points whose heights are small enough, asymptotically.

\begin{lemma}[{\cite[Lemma 30]{fountoulakis2018law}}]\label{lem:coupling_edges}
On the coupling space of Lemma~\ref{lem:coupling_hyperbolic_poisson} the following holds a.a.s.:
\begin{enumerate}
\item for any two points $p_i, p_j \in \Pcal_{\alpha, \nu}$ with $y_i, y_j \le R_n/2$, we have that $(p_i,p_j) \in E(G_{\Pcal,n}) \Rightarrow (\Psi^{-1}(p_i), \Psi^{-1}(p_j)) \in E(G_{\HP,n})$, 
\item for any two points $p_i, p_j \in \Pcal_{\alpha, \nu}$ with $y_i, y_j \le R_n/4$, we have that $(p_i,p_j) \in E(G_{\Pcal,n}) \iff (\Psi^{-1}(p_i), \Psi^{-1}(p_j)) \in E(G_{\HP,n})$.
\end{enumerate}
\end{lemma}

\PvdH{@Tobias and Markus: Please add additional text to explain the usage of these results in your proof for fixed $k$.}

\PvdH{@All: Given that the structure of the proof will change, I removed the section where the proofs of the main results were stated.}

%\subsection{Proof of the main results}\label{ssec:proof_main_results}
%
%
%
%We are now ready to prove our main results, using the propositions stated in the previous sections. As mentioned before we focus here on the convergence statements. The computation of the exact expressions is done in Section~\ref{sec:asymptotics_average_clustering_ast_P}. We begin with Theorem~\ref{thm:local_clustering_hyperbolic}.
%
%\begin{proof}[Proof of Theorem \ref{thm:local_clustering_hyperbolic}]
%%By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
%%\begin{align*}
%%	&\hspace{-30pt}\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}\\
%%	&\le \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{}c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)}
%%		+ \frac{\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\infty(k_n)\right|}{C_{\alpha,\nu}s_\alpha(k_n)}
%%		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| \\
%%	&= \smallO{1}.
%%\end{align*}
%First of all, due to cancellation of equal terms we can rewrite
%\begin{align*}
%    c_{\H,n}(k_n)-c_\infty(k_n) =& c_{\H,n}(k_n)-c_{\H,n}^\ast(k_n)+c_{\H,n}^\ast(k_n)-c_{\HP,n}^\ast(k_n)+c_{\HP,n}^\ast(k_n)-c_{\Pcal,n}^\ast(k_n) \\
%    &+c_{\Pcal,n}^\ast(k_n)-\E c_{\Pcal,n}^\ast(k_n)+\E c_{\Pcal,n}^\ast(k_n)-c_\infty(k_n)
%\end{align*}
%Then, we take absolute values and apply the triangle inequality. By monotonicity of expectation, we can apply it to both sides and obtain
%\begin{align*}
%    \E[|c_{\H,n}(k_n)-c_\infty(k_n)|] \leq & \E[|c_{\H,n}(k_n)-c_{\H,n}^\ast(k_n)|]+\E[|c_{\H,n}^\ast(k_n)-c_{\HP,n}^\ast(k_n)|]\\&+\E[|c_{\HP,n}^\ast(k_n)-c_{\Pcal,n}^\ast(k_n)|] 
%    +\E[|c_{\Pcal,n}^\ast(k_n)-\E c_{\Pcal,n}^\ast(k_n)|]\\&+\E[|\E c_{\Pcal,n}^\ast(k_n)-c_\infty(k_n)|]
%\end{align*}
%At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{s_\alpha(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c_{\Pcal}(k_n) = c_\infty(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
%\TM{ Maybe we can have a more clear reference? Now, at this place in the paper this proof feels a bit like cheating since there are almost no details given. } All of this together yields that:
%\begin{align*}
%    \E[|c_{\H,n}(k_n)-c_\infty(k_n)|] = \smallO{s_\alpha(k_n)} = \smallO{c_\infty(k_n)}
%\end{align*}
%\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point. }
%i.e. the statement of the theorem.
%%\[
%%	\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
%%	\le \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| 
%%	+ \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - c_\infty(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
%%\]
%
%%Combining this with Proposition~\ref{prop:couling_c_H_P} yields
%%\[
%%	\Exp{\left|\frac{c_{\H,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
%%	\le \Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|} 
%%	+ \frac{\Exp{\left|c_{\H,n}^\ast(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
%%\]
%%and the result then follows by applying Lemma~\ref{lem:clustering_ast_H}. 
%\end{proof}
%
%We can now use this result to prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}. Before we state the proof we summarize some results regarding the degrees in the hyperbolic model. The proof of this lemma follows directly from Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson} and Lemma~\ref{lem:N_k_HP_P}, see Section~\ref{sec:coupling_H_P_n}.
%
%%\MS{I think we need to introduce resp. explain $\Prob{D_\Pcal = k_n}$ in the lemma below.}
%
%\begin{lemma}\label{lem:N_k_H_P}
%Let $\alpha > \frac{1}{2}$ and $k_n$ be a positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then
%\[
%	\lim_{n\to \infty} \Exp{\left|\frac{\Exp{N_{\H,n}(k_n)}}{n \Prob{D_\Pcal = k_n}} - 1\right|} = 0
%\]
%\TM{ Did we define $D_\Pcal$ already? }
%and hence, as $n \to \infty$
%\[
%	\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}.
%\]
%\end{lemma}
%
%\begin{proof}[Proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}]
%
%First, let $a_n$ be any sequence such that $a_n \to \infty$. Then
%\begin{align*}
%	c_{\H,n} &= \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) \le a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}
%		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
%	&= \frac{1}{n} \sum_{t = 2}^{a_n} \sum_{i = 1}^n \ind{D_{\H,n}(i) = t} \frac{T_{\H,n}(i)}{\binom{t}{2}}
%		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
%	&= \frac{1}{n} \sum_{t = 2}^{a_n} \Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t)
%		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}},
%\end{align*}
%where the expectation of the last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. Similarly,
%\[
%	c_\Pcal = \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} c_\Pcal(t) + \sum_{t > a_n} \Prob{D_\Pcal = t} c_\Pcal(t)
%\]
%As derived at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}, $c_\infty = c_\Pcal$ and $c_\infty(k) = c_\Pcal(k)$. Therefore
%\begin{align*}
%	\Exp{|c_{\H,n}-c_\infty|}=\Exp{|c_{\H,n} - c_\Pcal|}
%	&\le \Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
%		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\ 
%	&\hspace{10pt}+ \Prob{D_{\H,n} > a_n} + \Prob{D_{\Pcal} > a_n},
%\end{align*}
%\TM{ Same comment }
%and since the last two probabilities are $\smallO{1}$ \TM{ We do not seem to have proved this yet at this point in the paper } it is enough to prove that
%\[
%	\lim_{n \to \infty} \Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
%			n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|} = 0.
%\]
%
%We write
%\begin{align*}
%	&\hspace{-30pt}\Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
%		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\
%	&\le \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\infty}(t)\right|}\\
%	&\hspace{10pt}+ \frac{1}{n} \sum_{t = 2}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)},
%\end{align*}
%and will show that both terms go to zero for some appropriately chosen sequence $a_n$.
%
%Note that Theorem~\ref{thm:local_clustering_hyperbolic} and Lemma~\ref{lem:clustering_ast_H} together state that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
%
%\begin{equation}\label{eq:convergence_c_H_P}
%	\lim_{n \to \infty} \Exp{\left|c_{\H,n}(k_n) - c_{\Pcal}(k_n)\right|} = 0.
%\end{equation}
%
%\TM{ I do not see how this follows from the statements of Thm 1.2 and L2.3. Please elaborate. }
%Let $b_n := \log(n)^{-1} n^{1/(2\alpha + 1)}$ and define the sequence $k_n$ by
%\[
%	k_n = \arg \max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|}.
%\]
%Then $k_n = \smallO{n^{1/(2\alpha + 1)}}$ and by~\eqref{eq:convergence_c_H_P}
%\[
%	\max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|} = \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} \to 0.
%\]
%Similarly we note that by Lemma~\ref{lem:N_k_H_P}
%\[
%	\max_{2 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
%\]
%
%Now define
%\[
%	a_n := \left\lfloor \min \left\{
%	\left(\max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\right)^{-1/2},
%	\left(\max_{2 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|}\right)^{-1/2},
%	b_n - 1 \right\} \right\rfloor
%\]
%\TM{ There seems to be a typo. max should be argmax?
%Also, what is the exponent $-1/2$ doing there? } \PvdH{It was the other way around, argmax should have been max. Since the first to expressions tend to zero, taking them to the power -1/2 make them go to infinity while still making sure that $a_n$ times those expressions tends to zero.}
%so that $a_n < b_n = \smallO{n^{1/(2\alpha + 1)}}$, $a_n \to \infty$,
%\
%\[
%	a_n \max_{2 \le t \le a_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} 
%	\le a_n \max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} \to 0,
%\]
%\TM{ LHS and RHS are identical !!! }\PvdH{They differ by $a_n$ vs $b_n$ in the max.}
%and similarly
%\[
%	a_n \max_{2 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
%\]
%
%Then, since $\Exp{\Prob{D_\Pcal = t}} = \bigT{1} t^{-(2\alpha + 1)}$
%\begin{align*}
%	&\hspace{-30pt}\sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}\\
%	&\le \bigT{1} 2^{-(2\alpha+1)} a_n \max_{2 \le t \le a_n} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}
%	= \smallO{1},
%\end{align*}
%while $\Exp{c_\Pcal(t)} \le 1$ implies that
%\begin{align*}
%	&\hspace{-30pt}\frac{1}{n} \sum_{t = 2}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)} \\
%	&\le \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \\
%	&\le \bigT{1} 2^{-(2\alpha+1)} a_n \max_{2 \le t \le a_n} 
%		\Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} = \smallO{1}.
%\end{align*}
%This finishes the proof. %The second part, which derives the exact expression for $c_\Pcal$ can be found in [??] \PvdH{Add reference to section.}
%\end{proof}

### 2019-01-19 proofs_finite_k.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

\section{Proofs of the main results for fixed $k$}\label{sec:proofs_fixed_k}

### 2019-01-19 proofs_infinite_k.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

--- 2018-11-17 proof_overview.tex
@@
-\section{Overview of the proof strategy}\label{sec:proof_outline}
+\section{Overview of the proof strategy for $k \to \infty$}
 
-The key result in this paper is Theorem~\ref{thm:local_clustering_hyperbolic}.
-In particular, it is the key ingredient in the proofs of Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
-Therefore, in this section we first give a detailed overview of the structure for the proof of Theorem~\ref{thm:local_clustering_hyperbolic}.
-The proof itself, based on intermediate propositions, can be found in Section~\ref{ssec:proof_main_results}.
-Here we also prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
-The proof of Theorem~\ref{thm:asymptotics_average_clustering_P} can be found in Section~\ref{sec:asymptotics_average_clustering_ast_P} where we also derive the exact expressions for $c_\infty$ and $c_\infty(k)$.
+\PvdH{References need to be included once Section 1 is updated.}
 
-Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem~\ref{thm:local_clustering_hyperbolic} based on the different propositions described below, plus the sections in which theses propositions are proved.
+The proofs for Theorems [??] follow the same strategy as outlined in Section~\ref{sec:proof_outline}.
+However, the fact that $k = k_n \to \infty$ as $n \to \infty$, introduces additional technical challenges.
+For example, the coupling we use becomes less exact so that we can no longer use Lemma~\ref{lem:coupling_edges} to conclude that triangle counts in $G_{\HP,n}$ and $G_{\Pcal,n}$ are asymptotically equivalent.
+In this section we explain the challenges with each step and give a detailed overview of the structure for the proof of Theorem [??] using intermediate results for each of the steps.
+Since we are ultimately interested in recovering the scaling of $c_{\H,n}(k_n)$, which Theorem [??] claims is $s_\alpha(k_n)$, we need to show that each step only introduces error terms that are of smaller order, i.e.
+that are $\smallO{s_\alpha(k_n)}$.
+We end this section with the proof of Theorem [??], based on the intermediate results.
+
+\begin{remark}[Diverging $k_n$]
+Throughout the remainder of this paper $\{k_n\}_{n \ge 1}$ will always denote a sequence of integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
+\end{remark}
+
+We start with introducing a slightly modified version of the local clustering function, which will be convenient for computations later,
+\begin{equation}\label{eq:def_local_clustering_ast_general}
+	c_{G}^\ast(k) = \frac{1}{\Exp{N_G(k)}} \sum_{v \in V(G)} \ind{D_G(v) = k} \frac{\T_G(v)}{\binom{k}{2}}.
+\end{equation}
+Notice that the only difference between $c_G(k)$ and $c_G^\ast(k)$ is that we replace $N_G(k)$ by its expectation $\Exp{N_G(k)}$.
+The advantage is that now, the only randomness is in triangle counting.
+In addition, note that since $\Exp{N_G(k)} > 0$ a case distinction for $N_k$ is no longer needed for $c_G^\ast(k)$.
+It is however still relevant since we are eventually interested in $c_G(k)$.
+Following the notational convention, see Remark~\ref{rmk:notation}, throughout the remainder of this paper we write $c_{\HP,n}^\ast(k)$ and $c_{\mathcal{P},n}^\ast(k)$ to denote the modified local clustering function in $G_{\HP,n}(\alpha, \nu)$ and $G_{\mathcal{P},n}(\alpha,\nu)$, respectively.
+
+Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem [??] based on the different propositions described below, plus the sections in which theses propositions are proved.
+Observe that the order in which the intermediate results are proved is reversed with respect to the natural order of reasoning.
+This does not create any circular logic, since each intermediate result is independent of the others.
+We choose this order because results proved in the later stages are helpful to deal with error terms coming up in proofs at earlier stages and hence help streamline those proofs.
 
@@
 	\begin{center}
-	Expected local clustering\\
+	Expected adjusted local clustering\\
 	$\displaystyle \Exp{c_{\Pcal,n}^\ast(k_n)}$
@@
 
-The main idea behind the proof of Theorem \ref{thm:local_clustering_hyperbolic} is to couple the hyperbolic graph $G_{\H, n}(\alpha, \nu)$ with a finite subgraph $G_{\Pcal,n}(\alpha,\nu)$ of an infinite graph $G_\Pcal(\alpha,\nu)$ whose nodes are given by a Poisson Point Process (see Section~\ref{ssec:infinite_model}).
-The infinite graph will then yield the limit expressions for the local clustering coefficient and function.
-A similar approach is used in \cite{fountoulakis2018law} to analyze the size of the largest component in the hyperbolic model and in \cite{komjathy2018explosion} to analyze explosion times in a more general class of models.
-The advantage of the infinite limit model is two-fold.
-Firstly, it simplifies the actual computations, e.g.
-by replacing hyperbolic densities with exponential densities and the hyperbolic distance with a computationally easier expression.
-Secondly, it directly yields the limit as a result rather than having to determine this later from a long expression depending on $n$.
+\subsection{Adjusted clustering and Poisson nodes in hyperbolic graphs}
 
-Very roughly, the proof falls into five parts: 1) replacing the randomly sampled nodes in the hyperbolic graph with a Poisson Point Process, 2) justifying the transitioning from this Poisson version of the hyperbolic random graph to the finite model, 3) proving concentration results for local clustering, 4) show that the limit expression correspond to those in the infinite model and finally 5) calculating the expected local clustering coefficient and function in the infinite limit model.
-
-In this section, we state the required definitions, auxiliary lemmas and propositions and show how to assemble them to obtain Theorem~\ref{thm:local_clustering_hyperbolic}.
-
-\subsection{Finite box model}\label{ssec:finite_model}
-
-First of all we define the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ which we will couple to $G_{\H, n}(\alpha, \nu)$.
-A similar approach was used in~\cite{fountoulakis2018law} to analyze the largest component.
-Define $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and let $\mathcal{P}=\mathcal{P}_{\alpha,\nu}$ be a Poisson point process on $\Rcal$ with intensity function
-\begin{equation}\label{eq:def_intensity_function_f}
-	f_{\alpha,\nu}(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y}.
-\end{equation}
-
-In addition we denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e. for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
-\begin{equation}\label{eq:def_mu_P}
-	\mu_{\alpha,\nu}(S) = \int_S f_{\alpha,\nu}(x,y) \, dx \, dy,
-\end{equation}
-and for any point $p \in \Rcal$.
-
-We will write $p = (x, y)$ for points in $\Rcal$. Then the \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
-\[
-	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
-\]
-
-\begin{remark}[Notations for points]\label{rmk:point_notation}
-We will be working extensively with expressions in terms of points of $\Pcal_{\alpha, \nu}$, often relating them back to points in the hyperbolic disc $\Dcal_{\Rcal_n}$.
-Therefore, in the remainder of this paper we will always use $u = (r,\theta)$ to denote points in $\Dcal_{\Rcal_n}$ in polar coordinates while $p = (x,y)$ will denote points in $\Rcal := \mathbb{R} \times \mathbb{R}_+$ in Cartesian coordinates.
-In addition, when we write $p^\prime \in \mathbb{R} \times \mathbb{R}_+$ we will denote its Cartesian coordinates by $(x^\prime, y^\prime)$ and similarly for $p_i$, $u^\prime$ and $u_i$, e.g.
-$p_i = (x_i, y_i)$.
-In addition, for a point $p = (x,y)$, we will refer to $y$ as the \emph{height} of $p$.
-\end{remark}
-
-For the definition of the finite graph, recall that $R_n = 2\log(n/\nu)$ and consider the finite box $\Rcal_n = (-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}] \times (0, R_n]$ in $\Rcal$.
-Then the \emph{finite box model} graph $G_{\mathcal{P},n}(\alpha, \nu)$ has vertex set $\mathcal{V}_n := \mathcal{P}_{\alpha, \nu} \cap \Rcal_n$ and edges set such that
-\[
-	(p_i, p_j) \in E(G_{\mathcal{P},n}(\alpha, \nu)) \iff |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}},
-\]
-where $|x|_{\pi e^{R_n/2}} = \inf_{k \in \mathbb{Z}} |x + k \pi e^{R_n/2}|$.
-In order words, $G_{\mathcal{P},n}(\alpha, \nu)$ is the subgraph of $G_{\mathcal{P}}(\alpha, \nu)$ induced on $\mathcal{V}_n$, where we have identified the boundaries of $(-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}]$ to exclude boundary effects and to make the model symmetric in the horizontal $x$-axis.
-
-For a point $p \in \Rcal_n$, we will write $\BallPon{p}$ to denote the \emph{ball} around $p$, i.e.
-\begin{equation}\label{eq:def_ball_P_n}
-	\BallPon{p} = \left\{p^\prime \in \Rcal_n : |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}}\right\}.
-\end{equation}
-With this notation we then have that $\BallPon{p} \cap \PPP$ denotes the set of neighbors of a vertex $p \in G_{\Pcal,n}(\alpha,\nu)$.
-
-\subsection{Coupling the hyperbolic model to the finite box model}\label{ssec:coupling_H_P}
-
-To couple the hyperbolic graph to $G_{\mathcal{P},n}(\alpha, \nu)$ we consider the original hyperbolic graph on a Poisson distributed number of vertices as an intermediate step.
-For this we define $G_{\HP,n}(\alpha, \nu)$ to be the hyperbolic random graph where the vertex set is given by $N \stackrel{d}{=} \Po(n)$ points, distributed according to the $(\alpha, R_n)$-quasi uniform distribution~\eqref{eq:def_hyperbolic_point_distribution} defined in Section \ref{ssec:hyperbolic_model}.
-The following two lemmas from \cite{fountoulakis2018law} establish a coupling between this version of the hyperbolic random graph and the finite box model and relate the hyperbolic neighborhoods to the neighborhood balls $\BallPo{p}$.
-The ensuing proposition verifies that this coupling also essentially preserves the local clustering function, i.e.
-that the difference between the local clustering function in the hyperbolic model and the finite box graph converges to zero faster than the proposed scalings in the main result, Theorem \ref{thm:local_clustering_hyperbolic}.
-Hence, it justifies the transition to the finite box model.
-
-\begin{lemma}[{\cite[Lemma 27]{fountoulakis2018law}}]\label{lem:coupling_hyperbolic_poisson}
-Let $\mathcal{V}_{\HP, n}$ denote the vertex set of $G_{\HP,n}(\alpha, \nu)$ and $\mathcal{V}_n$ the vertex set of $G_{\Pcal,n}(\alpha, \nu)$.
-Define the map $\Psi : [0,R_n] \times (-\pi, \pi] \to \mathcal{R}_n$ by
-\begin{equation}\label{eq:def_Psi}
-	\Psi(r,\theta) = \left(\theta \frac{e^{R_n/2}}{2}, R_n - r\right).
-\end{equation}
-Then there exists a coupling such that, a.a.s., $\mathcal{V}_n = \Psi(\mathcal{V}_{\HP,n})$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
-%\begin{equation}\label{eq:convergence_miscoupling_hyperbolic_poisson}
-%	\Prob{\Ccal_n^c} = \bigO{n^{-(2\alpha - 1)}}. 
-%\end{equation}
-\end{lemma}
-
-In the remainder of this paper we will write $\BallHyp{p}$ to denote the image under $\Psi$ of the ball of hyperbolic radius $R_n$ around the point $\Psi^{-1}(p)$, i.e. 
-\[
-	\BallHyp{p} := \left\{p^\prime := \Psi(u) \, : \, u \in \Dcal_{R_n} \text{ and } d_\H(\Psi^{-1}(p),u) \le R_n\right\}.
-\]
-Note that we have that $\BallHyp{p} \subseteq \mathcal{R}_n$. In particular, a point $p = (x,y) \in \Rcal$ corresponds to $u := \Psi^{-1}(p) = (2 e^{-R_n/2} x, R_n - y)$.
-
-Let $u, u^\prime \in \Dcal_R$.
-The hyperbolic law of cosines implies that $d_{\H}(u,u^\prime) \leq R_n$ if and only if their relative angle $\theta(u, u^\prime) := |\theta - \theta^\prime|_{2\pi}$ satisfies $\theta(u, u^\prime) \leq \theta_{R_n}(r,r^\prime)$, where $\theta_{R_n}(r,r^\prime)$ is the solution of the following equation
-\[
-	\cosh R_n =\cosh r \cosh r^\prime - \sinh r \sinh r^\prime \cos \theta_{R_n}(r,r^\prime).
-\]
-To write this differently, define
-\begin{equation}\label{eq:def_Omega_hyperbolic}
-	\Omega(r,r^\prime) := \frac{1}{2}e^{R_n/2} \arccos\left( \frac{\cosh r \cosh r^\prime - \cosh R_n}
-	{\sinh r \sinh r^\prime} \right).
-\end{equation}
-Then $d_{\H}(u,u^\prime) \leq R_n$ if and only if $\theta(u, u^\prime) \leq 2 e^{-R_n/2}\Omega(r,r^\prime)$.
-Under the coupling map $\Psi$, this is equivalent to $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$.
-
-Now consider a point $p \in \mathcal{V}_n$ and write $\Psi^{-1}(p) = (r,\theta)$. Then the triangle inequality implies that
-for any point $u^\prime \in \Dcal_R$
-\begin{equation}\label{eq:tail_inclusion_hyperbolic_ball}
-	r^\prime \leq y = R_n - r \Rightarrow d_{\H} (\Psi^{-1}(p),u^\prime) \leq R_n.
-\end{equation}
-In other words, we have $\Rcal_n ([r, R_n])  \subset \BallHyp{p}$.
-The shape of $\BallHyp{p}$ at the lower parts of $\Rcal_n$ is described by the following lemma which appears in~\cite{fountoulakis2018law}.
-
-\begin{lemma}[{\cite[Lemma 28]{fountoulakis2018law}}]\label{lem:asymptotics_Omega_hyperbolic}
-There exists a constant $K>0$ such that, for every $\varepsilon > 0$ and for $R_n$ sufficiently large, the following holds.
-For every $r,r^\prime \in [\varepsilon R_n,R_n]$ with $r + r^\prime > R_n$ we have that 
-\begin{equation}\label{eq:asymp1}
-	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Omega(r, r^\prime) 
-	\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
-\end{equation}
-where $y := R_n - r, y^\prime := R - r^\prime$. 
-Moreover:
-\begin{equation}\label{eq:asymp2} 
-\Omega(r,r^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $r, r^\prime < R_n - K$.} 
-\end{equation}
-\end{lemma}
-
-This result allows us to couple the neighborhoods in the hyperbolic random graph $G_{\H,n}(\alpha,\nu)$ to those in the finite box model $G_{\Pcal,n}(\alpha,\nu)$.
-This coupling is however not exact and hence we need to compute the difference in triangle counts between the two models.
-For this, and other computations later on, it will be more convenient to consider the following slight modified version of the local clustering function,
-\begin{equation}\label{eq:def_local_clustering_ast_general}
-	c_{G}^\ast(k) = \begin{cases}
-			\frac{1}{\Exp{N_G(k)}} \sum_{v \in V(G)} \ind{D_G(v) = k} \frac{\T_G(v)}{\binom{k}{2}} &\mbox{if } N_G(k) \ge 1\\
-			0 &\mbox{else.}
-		\end{cases}
-\end{equation}
-Notice that the only difference between $c_G(k)$ and $c_G^\ast(k)$ is that we replace $N_G(k)$ by its expectation $\Exp{N_G(k)}$.
-Following the notational convention, see Remark~\ref{rmk:notation}, throughout the remainder of this paper we write $c_{\HP,n}^\ast(k)$ and $c_{\mathcal{P},n}^\ast(k)$ to denote the modified local clustering function in $G_{\HP,n}(\alpha, \nu)$ and $G_{\mathcal{P},n}(\alpha,\nu)$, respectively.
-
-The following lemma justifies working with this modified version, for the proof see Section~\ref{ssec:coupling_H_HP}.
+Recall that the first step for the fixed $k$ case was to show that the transition from the hyperbolic random graph $G_{\H,n}$ to the Poisson version $G_{\HP,n}$ did not influence clustering.
+Here we first make a transition from the local clustering function $c_{\H,n}(k)$ to the adjusted version $c_{\H,n}^\ast(k)$.
+The following lemma justifies working with this modified version.
+The proof uses a concentration result for $\N_{\H,n}(k_n)$ and full details can be found in Section~\ref{ssec:coupling_H_HP}.
 
 \begin{lemma}\label{lem:clustering_ast_H}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, as $n \to \infty$,
+As $n \to \infty$,
 \[
@@
 We then establish that the modified local clustering function in the hyperbolic model $G_{\H,n}(\alpha,\nu)$ behaves similarly to that in the Poisson version $G_{\HP, n}(\alpha,\nu)$.
+This is based on a standard coupling between a Binomial Point Process and Poisson Point Process.
 
 \begin{proposition}\label{prop:clustering_ast_H_Pois}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any increasing sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, as $n \to \infty$,
+As $n \to \infty$,
 \[
@@
 
-The next step is to show that the modified clustering is preserved under the coupling described above. The proof can be found in Section~\ref{ssec:coupling_HP_ast_P}.
+\subsection{Coupling of local clustering between $G_{\HP,n}$ and $G_{\Pcal,n}$}
+
+The next step is to show that the modified clustering is preserved under the coupling described in Section~\ref{ssec:coupling_H_P}.
+The proof can be found in Section~\ref{ssec:coupling_HP_ast_P}.
+This is one of the key technical challenges we face.
+
+To understand why, recall that the degree $k$ of a node is related to its height $y$, roughly speaking, by $k \approx \xi_{\alpha, \nu} e^{y/2}$.
+Therefore, when $k$ is fixed we have that the heights of nodes with that degree are also fixed, in particular $y < R_n/4$ for large enough $n$.
+In addition, the main contribution of triangles would also come from nodes with heights $y^\prime < R_n/4$.
+This allowed us to use Lemma~\ref{lem:coupling_edges} and conclude that the triangles present in the graph $G_{\HP,n}$ where exactly those present in $G_{\Pcal,n}$ and therefore the local clustering function was the same in both models.
+When $k_n \to \infty$ this is no longer true in general.
+For instance, suppose $k_n = n^{\frac{1-\varepsilon}{2\alpha + 1}}$, for some small $0 < \varepsilon < 1$.
+Then the relation $k_n \approx \xi_{\alpha, \nu} e^{y_n/2}$ implies that $y_n \approx \frac{2(1-\varepsilon)}{2\alpha + 1}\log(n) - 2\log(\xi_{\alpha, \nu})$.
+Since
+$R_n/4 = \frac{1}{2}\log(n) - \frac{1}{2}\log(\nu)$ we get that $R_n/4 = \smallO{y_n}$ for all $\alpha > (3 - 4\varepsilon)/2$ and hence $y_n > R_n/4$ for large enough $n$, violating the conditions of Lemma~\ref{lem:coupling_edges}.
+However, by carefully analyzing the difference between the adjusted local clustering function in both models we can still make the same conclusion.
+This is summarized in the following proposition whose proof is found in Section~\ref{ssec:coupling_HP_ast_P}.
 
 \begin{proposition}[Coupling result for local clustering]\label{prop:couling_c_H_P}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $(k_n)_{n\ge 1}$ be any positive sequence such that $k_n \ge 3$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, as $n \to \infty$,
+As $n \to \infty$,
 \[
@@
 
-These two results imply that the difference between the local clustering function of the hyperbolic random graph and the modified local clustering function of the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem \ref{thm:local_clustering_hyperbolic}.
+\TM{ Maybe we could replace these three with a statement on $|c_{\H,n}(k_n) - c_{\Pcal,n}^\ast(k_n)|$, at least at this point of the paper.
+This is only the high level description and that is all we need for the ``final proof".}\PvdH{I would vote for keeping them split, since this allows us to clearly point to the main technical challenge we have to overcome to obtain the final result.}
+These three results together imply that the difference between the local clustering function of the hyperbolic random graph and the modified local clustering function of the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem [??].
 Hence, to prove this theorem it is enough to prove it for $c_{\mathcal{P},n}^\ast(k)$.
-
-\subsection{Infinite limit model}\label{ssec:infinite_model}
-
-To analyze the limiting expressions for clustering in the finite random graph $G_{\Pcal,n}(\alpha, \nu)$ we shall use an infinite graph model which can be understood as taking the finite graph $G_{\Pcal,n}(\alpha,\nu)$ and taking $n \to \infty$.
-Recall that $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and that $\mathcal{P}_{\alpha,\nu}$ is a Poisson point process on $\Rcal$ with intensity function
-\[
-	f_{\alpha,\nu}(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y}.
-\]
-
-The \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
-\[
-	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
-\]
-Similar to the finite graph, we write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
-\begin{equation}\label{eq:def_ball_P}
-	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
-\end{equation}
-
-To analyze expressions in the both the finite and infinite model we will make use of the~\emph{Campbell-Mecke} formula. 
-For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ we have
-\begin{equation}\label{eq:def_Campbell-Mecke}
-\begin{split}
-& \Exp{\sum_{x_1,\ldots, x_r \in \mathcal{P}}^{\neq} h (x_1, \ldots, x_r,
-\mathcal{P} \setminus \{x_1,\ldots, x_r\}) }\\
-& = \int_S \cdots \int_S
-\Exp{h(x_1,\ldots, x_r,\mathcal{P} \setminus \{x_1,\ldots, x_r\}) \lambda (x_1) \cdots \lambda (x_r) dx_1 \cdots dx_r},
-\end{split}
-\end{equation}
-where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$.
-
-Using the Campbell-Mecke formula we can compute the intensity measure of the ball $\BallPo{p}$, i.e. the expected number of points falling into it, as
-\begin{equation}\label{eq:mu_ball_y_P}
-	\mu_{\alpha, \nu}(\BallPo{p}) = \int_0^\infty \int_{-\infty}^\infty \ind{|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}}
-	f_{\alpha,\nu}(x^\prime, y^\prime) \, dx^\prime \, dy^\prime 
-	= \frac{4\alpha \nu}{(2\alpha - 1)\pi} e^{\frac{y}{2}} := \xi_{\alpha,\nu}e^{\frac{y}{2}},
-\end{equation}
-
-We shall use $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(\BallPo{p})$, i.e.
-\[
-	\rho(p,k) = \rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k}.
-\]
-Note that $\rho(y,k)$ denotes the probability that a vertex $(x,y) \in G_{\Pcal}(\alpha,\nu)$ has degree $k$, which due to the translation symmetry of the Poisson Point Process in the $x$ direction depends only on the \emph{height} $y$.
-
-\begin{remark}[Degree distributions in the other models]
-Similar to the infinite graph, the degree of a node $p$ in the Poisson hyperbolic graph $G_{\HP,n}$ and the finite random graph $G_{\Pcal,n}$ is distributed as a Poisson random variable with mean $\Mu{\BallHyp{p}}$ and $\Mu{\BallPon{p}}$, respectively.
-Following the notation above we will denote these distributions by $\rho_{\HP,n}(y,k)$ and $\rho_{\Pcal,n}(y,k)$, since these again are independent of the $x$-coordinate of $p$.
-\end{remark}
-
-We can also define a local clustering coefficient and function in this model.
-However, since $G_\Pcal$ has an infinite number of nodes the corresponding definitions are slightly different than for the finite size models.
-Intuitively the local clustering coefficient is the probability that two random neighbors of a randomly sampled node form a triangle, while the local clustering function is the same probability but conditioned on the sampled node having degree $k$.
-
-Again, due to symmetry in the $x$ direction we can assume without loss of generality that a randomly sampled point $p$ is $(0,y)$.
-For any $y \in \R_+$ we define the probability density function on $\Rcal :=  \R \times \R_+$ by
-\begin{equation}\label{eq:def_eta_P}
-	\eta_y(x^\prime, y^\prime) = \frac{\ind{p^\prime \in \BallPo{(0,y)}} f_{\alpha,\nu}(x^\prime,y^\prime)}{\mu_{\alpha,\nu}(\BallPo{(0,y)})}.
-\end{equation}
-That is $\eta_y$ is the density $f_{\alpha,\nu}$ restricted to the ball $\BallPo{(0,y)}$, properly normalized.
-Or in other words, it denotes the probability density of a randomly sampled point in $\BallPo{(0,y)}$, i.e.
-a randomly sampled neighbor of $(0,y)$.
-
-We then define
-\begin{equation}\label{eq:def_delta_p}
-	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(y, x_1, x_2, y_1, y_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \dd x_1 \dd x_2  \dd y_1  \dd y_2,
-\end{equation}
-with 
-\[
-	T_\Pcal(y, x_1, x_2, y_1, y_2) 
-	= \ind{|x_1| \, \le \, e^{(y+y_1)/2}}\ind{|x_2| \, \le \, e^{(y+y_2)/2}}\ind{|x_1-x_2| \, \le \, e^{(y_1+y_2)/2}},
-\]
-which is the probability that two randomly sampled points in $\BallPo{(0,y)}$ form a triangle with $(0,y)$.
-
-Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$: the distribution function of the radial coordinate of a vertex sampled in the disk is $\frac{\cosh(\alpha  r)-1}{\cosh(\alpha R)-1}$ which is asymptotically equivalent to $e^{\alpha(r-R)} = e^{-\alpha y}$, if $r$ and $R$ are large, resp.
-tending to infinity and $y=R-r$ and because of the minus sign in front of the $r$, the distribution function in $r$ turns into the complementary distribution function of $y$, from which we recognize the exponential distribution with parameter $\alpha$.%\PvdH{Could someone add an intuition or better explanation why this is the case.}
-
-With these expressions we define the limiting local clustering coefficient as
-\begin{equation}\label{eq:def_average_clustering_infinite_model}
-	c_\Pcal := \int_0^\infty \Delta_{\Pcal}(y) (1 - \rho(y,0) - \rho(y,1)) \alpha e^{-\alpha y} \dd y,
-\end{equation}
-while the limiting local clustering function is defined as
-\begin{equation}\label{eq:def_c_infty_k}
-	c_\Pcal(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
-\end{equation}
-
-In Section~\ref{sec:asymptotics_average_clustering_ast_P} we will compute both these quantities and show that $c_\Pcal = c_\infty$ and $c_\Pcal(k) = c_\infty(k)$, where $c_\infty$ and $c_\infty(k)$ are given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}.
 
@@
 
-\begin{proposition}[Concentration local clustering function in $G_{\mathcal{P},n}(\alpha, \nu)$]\label{prop:concentration_local_clustering_P_n}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any non-decreasing sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
+\TM{ ``concentration'' is a loaded term in probability.
+I am not sure this use of the word will not be counterintuitive to many.
+}\PvdH{I am not sure.
+Concentration generally refers to how much a random variable deviates from its expectation.
+This is exactly what this proposition tells us.
+I would therefore vote for keeping this terminology, although I would have no problem with replacing it with an other term if someone has a good suggestion.}
+
+\begin{proposition}[Concentration for local clustering function in $G_{\mathcal{P},n}(\alpha, \nu)$]\label{prop:concentration_local_clustering_P_n}
+As $n \to \infty$,
 \[
@@
 
-With this concentration result, we are left with the task to compute the limit of $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$ as $n \to \infty$ and show that it is equivalent to $c_\infty(k_n)$.
+This result is another one of the technical challenges we face when considering $k_n \to \infty$.
+For the proof, we first identify the specific range of heights that give the main contribution to the triangle count, showing that the triangles coming from nodes with heights outside this range is of smaller order.
+Then we prove a concentration result for the main term, by carefully analyzing the joint neighborhoods of two nodes whose heights fall into the identified range.
+The full details are found in Section~\ref{sec:concentration_c_P_n}.
+
+Assuming this concentration result, we are left with the task to compute the limit of $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$ as $n \to \infty$ and show that it is equivalent to $c_\infty(k_n)$.
 To accomplish this we move to the infinite limit model $G_\Pcal(\alpha,\nu)$ and show that the difference between the expected value of the clustering function $c_G^\ast(k)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
 
-\begin{proposition}[Transition to infinite limit model]\label{prop:convergence_average_clustering_P_n}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any positive sequence tending to infinity and satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then, as $n \to \infty$,
+\begin{proposition}[Transition to the infinite limit model]\label{prop:convergence_average_clustering_P_n}
+As $n \to \infty$,
 \[
@@
 \end{proposition}
-\MS{Is it really necessary that the sequence tends to infinity in the thm above?}
 
-\subsection{Proof of the main results}\label{ssec:proof_main_results}
+\TM{ This is only for $c(k)$. Should we not also mean $c$? }\PvdH{I do not think so. We can prove everything for $c$ once we have the result for $c(k_n)$.}
 
-We are now ready to prove our main results, using the propositions stated in the previous sections. We begin with Theorem~\ref{thm:local_clustering_hyperbolic}.
+Recall that for the finite box model the left and right boundaries of $\Rcal_n$ where identified, so that graph $G_{\Pcal,n}$ contains some additional edge with respect to the induced subgraph of $G_{\Pcal}$ on $\Rcal_n$.
+The prove of Proposition~\ref{prop:convergence_average_clustering_P_n} therefore relies on analyzing the number of triangles coming from these additional edges and showing that their contribution to the local clustering function are of negligible order, see Section~\ref{sec:clustering_Pn_to_P}.
+
+\subsection{Proof of the main results}\label{ssec:proof_main_result_diverging_k}
+
+We are now ready to prove Theorem [??], using the propositions stated in the previous sections.
+As mentioned before, we focus here on the convergence statements.
+The computation of the exact expressions is done in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
+We begin with Theorem~\ref{thm:local_clustering_hyperbolic}.
 
@@
 At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{s_\alpha(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c_{\Pcal}(k_n) = c_\infty(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
-All of this together yields that:
+\TM{ Maybe we can have a more clear reference?
+Now, at this place in the paper this proof feels a bit like cheating since there are almost no details given.
+} \PvdH{I completely agree.
+I think that once the results for fixed $k$ have been included we can include a specific statement at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P} we can refer to.} All of this together yields that:
 \begin{align*}
@@
 \end{align*}
+\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point.
+}\PvdH{We can fix this by proving the scaling of $c_\infty(k)$ in Section~\ref{sec:asymptotics_average_clustering_ast_P}.}
 i.e. the statement of the theorem.
-
 %\[
@@
 \end{proof}
-
-We can now use this result to prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
-Before we state the proof we summarize some results regarding the degrees in the hyperbolic model.
-The proof of this lemma follows directly from Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson} and Lemma~\ref{lem:N_k_HP_P}, see Section~\ref{sec:coupling_H_P_n}.
-
-\MS{I think we need to introduce resp. explain $\Prob{D_\Pcal = k_n}$ in the lemma below.}
-\begin{lemma}\label{lem:N_k_H_P}
-Let $\alpha > \frac{1}{2}$ and $k_n$ be a positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then
-\[
-	\lim_{n\to \infty} \Exp{\left|\frac{\Exp{N_{\H,n}(k_n)}}{n \Prob{D_\Pcal = k_n}} - 1\right|} = 0
-\]
-and hence, as $n \to \infty$
-\[
-	\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}.
-\]
-\end{lemma}
-
-\begin{proof}[Proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}]
-
-First, let $a_n$ be any sequence such that $a_n \to \infty$. Then
-\begin{align*}
-	c_{\H,n} &= \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) \le a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}
-		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
-	&= \frac{1}{n} \sum_{t = 3}^{a_n} \sum_{i = 1}^n \ind{D_{\H,n}(i) = t} \frac{T_{\H,n}(i)}{\binom{t}{2}}
-		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
-	&= \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t)
-		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}},
-\end{align*}
-\MS{Should the summation in $t$ not start from $t=2$?}
-where the expectation of the last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. Similarly,
-\[
-	c_\Pcal = \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} c_\Pcal(t) + \sum_{t > a_n} \Prob{D_\Pcal = t} c_\Pcal(t)
-\]
-As derived at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}, $c_\infty = c_\Pcal$ and $c_\infty(k) = c_\Pcal(k)$. Therefore
-\begin{align*}
-	\Exp{|c_{\H,n}-c_\infty|}=\Exp{|c_{\H,n} - c_\Pcal|}
-	&\le \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
-		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\ 
-	&\hspace{10pt}+ \Prob{D_{\H,n} > a_n} + \Prob{D_{\Pcal} > a_n},
-\end{align*}
-and since the last two probabilities are $\smallO{1}$ it is enough to prove that
-\[
-	\lim_{n \to \infty} \Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
-			n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|} = 0.
-\]
-
-We write
-\begin{align*}
-	&\hspace{-30pt}\Exp{\left|\frac{1}{n} \sum_{t = 3}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
-		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\
-	&\le \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\infty}(t)\right|}\\
-	&\hspace{10pt}+ \frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)},
-\end{align*}
-and will show that both terms go to zero for some appropriately chosen sequence $a_n$.
-
-Note that Theorem~\ref{thm:local_clustering_hyperbolic} and Lemma~\ref{lem:clustering_ast_H} together state that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
-\begin{equation}\label{eq:convergence_c_H_P}
-	\lim_{n \to \infty} \Exp{\left|c_{\H,n}(k_n) - c_{\Pcal}(k_n)\right|} = 0.
-\end{equation}
-
-Let $b_n := \log(n)^{-1} n^{1/(2\alpha + 1)}$ and define the sequence $k_n$ by
-\[
-	k_n = \arg \max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|}.
-\]
-Then $k_n = \smallO{n^{1/(2\alpha + 1)}}$ and by~\eqref{eq:convergence_c_H_P}
-\[
-	\max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|} = \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} \to 0.
-\]
-Similarly we note that by Lemma~\ref{lem:N_k_H_P}
-\[
-	\max_{3 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
-\]
-
-Now define
-\[
-	a_n := \left\lfloor \min \left\{
-	\left(\max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\right)^{-1/2},
-	\left(\arg \max_{3 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|}\right)^{-1/2},
-	b_n - 1 \right\} \right\rfloor
-\]
-so that $a_n < b_n = \smallO{n^{1/(2\alpha + 1)}}$, $a_n \to \infty$, 
-\[
-	a_n \max_{3 \le t \le a_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} 
-	\le a_n \max_{3 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} \to 0,
-\]
-and similarly
-\[
-	a_n \max_{3 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
-\]
-
-Then, since $\Exp{\Prob{D_\Pcal = t}} = \bigT{1} t^{-(2\alpha + 1)}$
-\begin{align*}
-	&\hspace{-30pt}\sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}\\
-	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}
-	= \smallO{1},
-\end{align*}
-while $\Exp{c_\Pcal(t)} \le 1$ implies that
-\begin{align*}
-	&\hspace{-30pt}\frac{1}{n} \sum_{t = 3}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)} \\
-	&\le \sum_{t = 3}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \\
-	&\le \bigT{1} 3^{-(2\alpha+1)} a_n \max_{3 \le t \le a_n} 
-		\Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} = \smallO{1}.
-\end{align*}
-This finishes the proof. %The second part, which derives the exact expression for $c_\Pcal$ can be found in [??] \PvdH{Add reference to section.}
-\end{proof}

### 2019-01-19 transition.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

@@
 The first step is to relate the clustering in the infinite model to that of the finite box model $G_{\Pcal, n}$.
-Recall that $G_{\Pcal,n}$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal_n = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ (we write $\Pcal_n$ for this process), and connecting two points $p_1, p_2 \in \Rcal_n$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$ where we identified the left and right boundary of $\Rcal_n$.
-\TM{ This last bit of the sentence is already contained in the fact we us $|.|_{\pi e^{R_n/2}}$. To me it does not add anything, except possibly confusion. }
+Recall that $G_{\Pcal,n}$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal_n = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ (we write $\Pcal_n$ for this process), and connecting two points $p_1, p_2 \in \Rcal_n$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$.
+We recall that by definition of the norm $|.|_{\pi e^{R_n/2}}$ the left and right boundaries of $\Rcal_n$ are identified.
 See Section~\ref{ssec:finite_model} for more details.
+\TM{ This last bit of the sentence is already contained in the fact we us $|.|_{\pi e^{R_n/2}}$.
+To me it does not add anything, except possibly confusion.
+} \PvdH{I have updated this and just added a reminder of this.}
+
+\begin{remark}[Diverging $k_n$]
+Throughout this section $\{k_n\}_{n \ge 1}$ will denote an sequence of integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
+\end{remark}
 
@@
 \[
-	\Kcal_C(k_n) = \left\{p \in \R : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
-	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \wedge e^{R_n/2} \right\},	
+	\Kcal_C(k_n) = \left\{p \in \Rcal : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi_{\alpha,\nu}} \le e^{\frac{y}{2}}
+	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi_{\alpha,\nu}} \right\},	
 \]
 \TM{ Typo : $p\in\R$. Do you mean $\Rcal_n$? Or maybe 
-$\R \time \R^+$? Still not sure that max and min in defn add anything. }
-with
-\[
-	\kappa_n := \begin{cases}
-		\log(n) &\mbox{if } k_n = \bigT{1},\\
-		\sqrt{k_n \log(k_n)} &\mbox{else.}
-	\end{cases}
-\]
-\TM{ Same issue as before. }
+$\R \times \R^+$? Still not sure that max and min in defn add anything. } \PvdH{It was a typo and is corrected. I have removed the max and min.}
+%with
+%\[
+%	\kappa_n := \begin{cases}
+%		\log(n) &\mbox{if } k_n = \bigT{1},\\
+%		\sqrt{k_n \log(k_n)} &\mbox{else.}
+%	\end{cases}
+%\]
+%\TM{ Same issue as before. }
 In addition we note that the function $\phi_n(y)$ in Lemma~\ref{lem:average_degree_P_n} satisfies
@@
 \]
-which yields the following useful corollary to Lemma~\ref{lem:average_degree_P_n}.
+as $R_n - y \to \infty$.
+Since $e^{y/2} = \bigT{k_n} = \smallO{e^{R_n}}$ as $n \to \infty$, uniformly on $\Kcal_C$, it follows that $\phi_n(y) = \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}$, uniformly on $\Kcal_C$.
+This yields the following useful corollary to Lemma~\ref{lem:average_degree_P_n}.
 
 \begin{corollary}\label{cor:average_degree_P_n_K}
-Let $\alpha > \frac{1}{2}$, $C > 0$ and $k_n$ be any sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha - 1}}}$. \TM{ Typo? $2\alpha-1$ should be $2\alpha+1$? } 
-Then, for all $p \in \Kcal_{C}(k_n)$,
+Let $\alpha > \frac{1}{2}$, $C > 0$. Then, for all $p \in \Kcal_{C}(k_n)$,
 \[
@@
 \]
-\TM{ I don't follow. Spell it out. }
+\TM{ I don't follow. Spell it out. }\PvdH{I added additional explanation above. Please see if this solves the confusion.}
 
@@
 
-We now turn to the task of calculating the expected number of triangles of a node at height $y$, for both the infinite model and the finite box model. Let $p_0 = (0,y)$ and recall that 
+We now turn to the task of calculating the expected number of triangles of a node at height $y$, for both the infinite model and the finite box model.
+Recall that we added a typical point $p_0 = (0,y)$, with exponentially distributed height, to the Poisson Point Process and that
 \[
@@
 \[
-	T_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p_1)}.
-\]
-\TM{ $p$ is supposed to be $p_0$ I assume. }
-The difference between the indicator $\ind{p_1 \in B_{\Pcal,n}(p)}$ in the finite box model and $\ind{p_1 \in B_{\Pcal}(p)}$ is that in $G_{\Pcal,n}(\alpha,\nu)$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$.
-\TM{ AND we stop at height $y=R_n$!
-(may be significant at some point) }
+	T_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_1)}.
+\]
+\TM{ $p$ is supposed to be $p_0$ I assume. }\PvdH{Indeed. It has been corrected.}
+The difference between the indicator $\ind{p_1 \in B_{\Pcal,n}(p)}$ in the finite box model and $\ind{p_1 \in B_{\Pcal}(p)}$ is that in $G_{\Pcal,n}(\alpha,\nu)$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$ and we stop at height $y = R_n$.
 It is clear that for any $0 \le y \le R_n$ we have that $\BallPon{p_0} = \BallPo{p_0} \cap \Rcal_n$.
@@
 \begin{equation}\label{eq:def_tilde_triangle_indicator}
-	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal_n}
+	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal_n}
 \end{equation}
-\TM{ $p$ should be $p_0$ I supppose. }
 Then
 \[
-	\sum_{p_1,p_2 \in \Pcal_n \setminus (0,y)}^{\ne} T_{\Pcal,n}(p_0,p_1,p_2) - \widetilde{T}_{\Pcal,n}(p_0,p_1,p_2)
-	= \sum_{p_1,p_2 \in \Pcal_n \setminus (0,y)}^{\ne} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)},
+	\sum_{p_1,p_2 \in \Pcal_n}^{\ne} T_{\Pcal,n}(p_0,p_1,p_2) - \widetilde{T}_{\Pcal,n}(p_0,p_1,p_2)
+	= \sum_{p_1,p_2 \in \Pcal_n}^{\ne} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)},
 \]
@@
 At this point though you can again still just say we add $p_0$ to the PPP.
-}
-where the sums are over all distinct pairs $(p_1, p_2) \in \Pcal_n \setminus \{(0,y)\}$.
+}\PvdH{I changed the text at the beginning of this section to mention this.
+Since we now consider the point process $\Pcal_n \cup p_0$ the above summation is over $\Pcal_n$.}
+where the sums are over all distinct pairs $(p_1, p_2) \in \Pcal_n$.
 
@@
 
-To further analyze this, let us introduce some notation. For any $p = (x,y) \in \Rcal_n$ we will define the left and right boundary functions as, respectfully,\TM{ respectively? }
+To further analyze this, let us introduce some notation. For any $p = (x,y) \in \Rcal_n$ we will define the left and right boundary functions as, respectively,
 \begin{align}
@@
 
-For the remainder of the analysis we restrict ourselves to the case where $x^\prime > 0$. Due to symmetry the situation for $x^\prime < 0$ is the same. \TM{ does this not depend on $p$? } 
+Since we have identified the left and right boundary of $\Rcal_n$ we can assume, without loss of generality that $x = 0$.
+Due to symmetry it is then enough to restrict the analysis to the case where $x^\prime > 0$.
+\TM{ does this not depend on $p$?
+}\PvdH{I do not think so, because we can always take $p = (0,y)$ due to the invariance in the $x$-direction.
+I have updated the text to better reflect this.}
 There are two important points in the box $\Rcal_n$.

### 2019-02-05 clustering_infinite_model.tex
updated notation and added comments to sections 1-3

--- 2018-11-18 clustering_infinite_model.tex
@@
-\section{Clustering in $G_{\mathcal{P}}(\alpha, \nu)$}\label{sec:asymptotics_average_clustering_ast_P}
-
-In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively.
-This is done in several steps.
-Recall that for $p\in \R \times \R_+ := \Rcal$,
-\[
-	\BallPo{p} = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\},
-\]
-denotes the neighborhood ball of $p$. Furthermore we recall the definition of $\Delta_\Pcal$ 
-\[
-	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
-\]
-where $\eta_{y} = \frac{\mu_{\alpha,\nu}|_{\BallPo{(0,y)}}}{\Mu{\BallPo{(0,y)}}}$ is the marginal probability density associated with a randomly sampled neighbor of $(0,y)$.
-
-We already noted that $\Delta_\Pcal(y)$ denotes the probability that two randomly sampled neighbors of $(0,y)$ are connected.
-More precisely, let $Z_{1}, Z_{2}$ be two independent random variables on $\BallPo{(0,y)}$, with (marginal) probability measures $\eta_{y}$.
-Then
-\begin{equation}\label{eq:def_delta_p_alt}
-	\Delta_{\Pcal}(p) = \pr_{\Pcal,p}\left( Z_{1} \in \mathcal{B}_{\Pcal}(Z_{2})\right)
-\end{equation}
-where $\pr_{\Pcal,p}$ denotes the joint probability measure of $Z_1$ and $Z_2$. We shall often abuse notation and write $\Delta_\Pcal(y)$ to denote $\Delta_\Pcal((0,y))$.
-
-%Next we note that conditioned on the Poisson process $\Pcal$ having $k$ points in $\mathcal{B}_{\Pcal}(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$, each with probability measure $\eta_{p}$ and hence
-%\[
-%	\Delta_{\Pcal}(p,k) = \binom{k}{2} \Delta_\Pcal(p).
-%\]
-%
-%In addition, since $\mu_{\alpha, \nu}(B_\Pcal(p)) = \xi_{\alpha,\nu} e^{\frac{y}{2}}$, with $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{(2\alpha - 1)\pi}$, and
-%\[
-%	\Delta_{\Pcal}(p) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{p}(x_1,y_1)\eta_{p}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
-%\]
-%we have that
-%\begin{equation}\label{eq:relation_T_vs_Delta_P}
-%	\Exp{T_\Pcal(p)} = \xi_{\alpha,\nu}^2 \frac{e^{y}}{2} \Delta_\Pcal(p).
-%\end{equation}
-
-We will start with some preliminary results on the degrees in $G_\Pcal(\alpha, \nu)$.
-The proof of Theorem \ref{thm:asymptotics_average_clustering_P} can be found in Section \ref{ssec:asymptotics_local_clustering_P}.
-The key ingredient for the proof is a result concerning the asymptotic behavior of $\Delta_\Pcal(y)$ (Proposition \ref{prop:asymptotics_Delta_y_P}) whose proof can be found in Section \ref{ssec:asymptotics_Delta_y_P}.
-The final computations for the exact expressions of $c_\infty$ in Theorem~\ref{thm:clustering_coefficient_hyperbolic} and $c_\infty(k)$ in Theorem~\ref{thm:local_clustering_hyperbolic} can be found in Section~\ref{ssec:exact_expressions_clustering_P}.
-
-\subsection{Degree distribution in $G_\Pcal(\alpha, \nu)$}
-
-Before we analyze local clustering in the infinite limit model, we first establish some results for its degree distribution.
-We define the probability distribution for the degree of node $p = (x,y)$ as
+\section{Clustering and the degree of the typical point in $\Ginf$\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
+
+As mentioned earlier, we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of $\GPo$ with certain quantities associated with $\Ginf$.
+We will be considering the Poisson process $\Pcal$ to which we add one additinal point $(0,y)$ on the $y$-axis.
+In some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and independent of $\Pcal$.
+We refer to $(0,y)$ as ``the typical point''.
+
+To provide some intu\"{\i}tion for this definition and name, note that we can alternatively view $\Pcal$ as follows. 
+We take a constant intensity Poisson process on $\eR$ corresponding to the $x$-coordinates, and to each point
+we attach a random ``mark'', corresponding to the $y$-coordinate, where the marks are i.i.d.~exponentially distributed with parameter $\alpha$.
+
+Since $c(G)$ is defined as an average over all vertices of the graph, it is not immediately obvious how to meaningfully define a corresponding notion for infinite graphs, and similarly for the clustering function, the degree sequence, etc.
+We can however without any issues speak of the (expected) clustering coefficient of the typical point, or the expected clustering coefficient given that it has degree k, or the distribution of the degree of the typical point.
+(All considered in the graph obtained from $\Ginf$ by adding the typical point to its vertex set.)
+
+If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we will write
+
+$$ \mu(y) = \mu(p) := \mu(\BallPo{p}). $$
+Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives
+
+$$ \begin{array}{rcl} 
+\mu(y) & = & \int_{\BallPo{p}} f(x',y') \, dx' \,d y'  
+ = \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' \\
+& = & \int_0^\infty 2 e^{(y+y')/2} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dy' 
+ = \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' \\
+& = & \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
+\end{array} $$
+
+\subsection{The degree of the typical point\label{ssec:degrees_infinite_model}}
+
+Before considering clustering we briefly investigate the distribution of the degree of 
+the typical point. 
+For $p = (x,y) \in \eR\times[0,\infty)$ we define
 \begin{equation}
-	\rho(p,k) = \Prob{D_\Pcal(p) = k} = \Prob{\Po(\mu_{\alpha,\nu}(\BallPo{p})) = k},
-\end{equation}
-where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Recall from equation \eqref{eq:mu_ball_y_P} that
-\[
-	\mu_{\alpha,\nu}(\BallPo{p}) = \xi_{\alpha,\nu} e^{\frac{y}{2}},
-\]
-only depends on the $y$-coordinate of $p$. Therefore, we will often write $\rho(y,k)$ instead of $\rho(p,k)$.
-
-Using the above equation and the transformation of variables $z = \xi_{\alpha,\nu}e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
-\begin{align*}
-	\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy 
-    &= \frac{1}{k!} \int_0^\infty \left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^k 
-    	e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy\\
-    &= \frac{\alpha (\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_0^\infty 
-    	\left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}}
+	\rho(p,k) := \Prob{\Po(\mu(y)) = k},
+\end{equation}
+
+where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. 
+We will often write $\rho(y,k)$ instead of $\rho(p,k)$.
+
+Let the random variable $D$ denote the degree of the typical point.
+Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed:
+\begin{equation}\label{eq:def_pk}
+	p_k := \Pee( D=k ) = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
+\end{equation}
+
+Using the transformation of variables $z = \xi e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
+\begin{align*}
+	p_k
+    &= \frac{1}{k!} \int_0^\infty \left(\xi e^{\frac{y}{2}}\right)^k 
+    	e^{-\xi e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy\\
+    &= \frac{\alpha \xi^{2\alpha}}{k!} \int_0^\infty 
+    	\left(\xi e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi e^{\frac{y}{2}}}
         \, dy\\
-    &= \frac{2\alpha (\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_{\xi_{\alpha,\nu}}^{\infty} 
+    &= \frac{2\alpha \xi^{2\alpha}}{k!} \int_{\xi}^{\infty} 
     	z^{k -2\alpha-1} e^{-z} \, dz\\
-    &=2\alpha (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)},
-\end{align*}
-where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{+}$ the incomplete Gamma-function.
-We therefore conclude that
-\begin{equation}\label{eq:degree_distribution_P}
-	\Prob{D_\Pcal = k} = 2\alpha (\xi_{\alpha,\nu})^{2\alpha} \frac{\Gamma^+(k - 2\alpha, \xi_{\alpha,\nu})}{\Gamma(k+1)}
-\end{equation}
-
-Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$ \PvdH{@All: Does anyone have a good standard reference for this?} we deduce that
+    &= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
+\end{align*}
+where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{+}$ the upper incomplete Gamma-function.
+Note that, unsurprisingly, this is identical to the expression Gugelmann et al.~\cite{gugelmann2012random} gave for the limiting degree distribution of $G(n;\alpha,\nu)$.
+Using Stirling's approximation to the gamma function, we find that
+
 \begin{equation}\label{eq:degree_distribution_P_asymptotics}
-	\Prob{D_\Pcal = k} \sim 2\alpha (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}
+	p_k \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha + 1)}
 	\quad \text{as } k \to \infty.
@@
 \begin{equation}\label{eq:general_integral_rho_y_k}
-	\int_0^\infty e^{\beta y} \rho_y(k) \alpha e^{-\alpha y} \, dy
-    \sim 2\alpha \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
-\end{equation}
-
-\subsection{Asymptotic behavior of $c_\infty(k)$}\label{ssec:asymptotics_local_clustering_P}
-
-%\begin{lemma}\label{lem:expectation_clustering_P}
-%Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then
-%\[
-%	\Exp{c_{\Pcal}^\ast(k)} = \frac{\int_0^{\infty} \Delta_{\Pcal}(y) \, 
-%	\rho_{y}(k) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) 
-%	e^{-\alpha y} \, dy}.
-%\]
-%\end{lemma}
-%
-%\begin{proof}
-%By the Palm-Mecke formula, we have
-%\begin{align*}
-%	\Exp{c_{\Pcal}^\ast(k)} &= \frac{1}{\Exp{N_\Pcal(k)}}
-%		\int_0^{\infty} \int_{-\infty}^{\infty} \Exp{\frac{\ind{D_{\Pcal}(p) = k}}{\binom{k}{2}} \sum_{(p_1, p_2) \in \Pcal} T(p,p_1,p_2)} f_{\alpha,\nu}(x,y) \, dx \, dy\\
-%	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} \int_{-\infty}^{\infty} \binom{k}{2}^{-1}
-%		\Delta_{\Pcal}(p,k)\CProb{D_\Pcal(p) = k}{p} f_{\alpha,\nu}(x,y) \, dx \, dy.
-%\end{align*}
-%Conditioned on the Poisson process $\Pcal$ having $k$ points in $B(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$ with probability  distribution $\eta_{p} = \frac{\mu|_{B(p)}}{\mu(B(p))}$.
-Therefore we have
-%\[
-%	\Delta_{\Pcal}(p,k) = \binom{k}{2} T_\Pcal(p),
-%\]
-%and hence, since the entire expression inside the integral does not depend on $x$,
-%\begin{align*}
-%	\Exp{c_{\Gamma, n}^\ast(k)} 
-%	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} \Delta_{\Pcal}(y) \rho_{\mu, y}(k) e^{-\alpha y} \, dy.
-%\end{align*}
-%Finally, we note that
-%\begin{align*}
-%	\Exp{N_\Pcal(k)} &= \Exp{\sum_{p \in \Pcal} \ind{D_\Pcal(p) = k}}
-%	= \int_0^{\infty}\int_{-\infty}^\infty \rho_{\mu, p}(k) f_{\alpha,\nu}(x,y) \, dx \, dy
-%	= \int_0^{\infty} \rho_{\mu, y}(k) e^{-\alpha y} \, dy
-%\end{align*}
-%which completes the proof.
-%\end{proof}
-
-Recall that
-\[
-	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
-\]
-The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
-\[
-	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
-\]
-and in particular the function $\Delta_\Pcal(y)$. The following result establishes the asymptotic behavior of the latter.
-
-\begin{proposition}[Asymptotic behavior of $\Delta_\Pcal(y)$]\label{prop:asymptotics_Delta_y_P}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}. Then there are three, eventually decreasing, functions $\varphi_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
-\[
-	\lim_{y \to \infty} \varphi_i(y) = 0, 
-\]
-such that 
-\begin{enumerate}
-\item for $\frac{1}{2} < \alpha < \frac{3}{4}$,
-\[
-	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varphi_1(y)),
-\]
-\item for $\alpha = \frac{3}{4}$,
-\[
-	\Delta_\Pcal(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varphi_2(y)),
-\]
-\item and for $\alpha > \frac{3}{4}$,
-\[
-	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varphi_3(y)).
-\]
-\end{enumerate}
-\end{proposition}
-
-The proof of this proposition is involved and technical.
-We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.
-
-\begin{proof}[Proof of Theorem \ref{thm:asymptotics_average_clustering_P}]
-
-We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$.
-The proofs for the other two cases are similar.
-Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
-\[
-	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y
-\]
-Then we have that
-\[
-	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y + \epsilon_1(k).
-\]
-
-Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields,
-\begin{equation}\label{eq:asymptotics_clustering_integral}
-	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y 
-	\sim 2\alpha \xi_{\alpha,\nu}^{6\alpha - 2} k^{-(6\alpha - 1)},
-\end{equation}
-as $k \to \infty$. Therefore, by applying the asymptotic scaling for the denominator~\eqref{eq:degree_distribution_P_asymptotics} we get
-\begin{align*}
-	c_\infty(k) &= \frac{\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
-		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
-	&\sim C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
-	+ \frac{\epsilon_1(k)}{2\alpha \xi_{\alpha,\nu}^{2\alpha} k^{-(2\alpha - 1)}}\\
-	&= C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2} 
-    + \frac{1}{2\alpha}\xi_{\alpha,\nu}^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
-\end{align*}
-Hence, to prove the result it is enough to show that
-\[
-	\lim_{k \to \infty} k^{6\alpha - 3}\epsilon_1(k) = 0.
-\]
-For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ and split the integral into two pieces
-\begin{align*}
-	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
-	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
-	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
-    	\rho(y,k) \alpha e^{-\alpha y} \dd y.
-\end{align*} 
-For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ and
-\[
-	k^{6\alpha - 3}\rho(a(k),k) = O\left(\frac{k^{6\alpha - 3 + (1-\varphi)k}}{k!} e^{-(1-\varphi)k}\right) = o(1),
-\]
-to obtain
-\begin{align*}
-	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
-    	\rho(y,k) \alpha e^{-\alpha y} \dd y\\
-	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
-    	\rho(a(k), k) \int_0^\infty \alpha e^{-\alpha y} \dd y = 0.
-\end{align*}
-For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
-\[
-	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
-\] 
-Therefore, using that $\varphi_1(y)$ is eventually decreasing and $\lim_{k \to \infty} \varphi_1(a(k)) = 0$, we obtain
-\begin{align*}
-	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
-    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
-	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
-    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = 0,
-\end{align*}
-which finishes the proof.
-\end{proof}
-
-\subsection{Analyzing $\Delta_\Pcal(y)$, an overview.}\label{ssec:asymptotics_Delta_y_P}
-
-We derive the following complete asymptotic expansion of $\Delta_{\Pcal}(y)$, from which then the leading terms can be extracted.
-The following result proves Proposition \ref{prop:asymptotics_Delta_y_P}, resp.
-implies it as a corollary after extracting the leading terms.
-\begin{proposition}\label{prop:full_expression_delta_P}
-\begin{enumerate}
-	\item If $\alpha \not = 1$, then
-	\begin{align*}
-	 \Delta_{\Pcal}(y) &=-\frac{1}{8 (\alpha - 1) \alpha} + \frac{(\alpha - 1/2) e^{-\frac{1}{2}y}}{\alpha - 1} - \frac{(\alpha - 1/2)^2 e^{-y}}{
+	\int_0^\infty e^{\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
+    \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
+\end{equation}
+
+\subsection{The expected clustering coefficient and function of the typical point}
+
+Let the random variable $C$ denote the clustering coefficient of the typical point $(0,y)$, in the graph obtained from $\Ginf$ by adding $(0,y)$. We {\em define}
+\[
+	\gamma := \Ee C, \quad \gamma(k) := \Ee\left( C | D = k \right).
+\]
+(Where we take the expection over both the Poisson point process $\Pcal$ and $y \isd \text{exp}(\alpha)$, independent of the Poisson process $\Pcal$.) We shall show shortly that these take on the values stated in Theorem~\ref{thm:maincc} and~\ref{thm:mainkfixed}.
+
+For any fixed value $y_0>0$, the set of points inside $\BallPo{(0,y_0)}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{(0,y_0)}}$.
+As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by the experiment where we first pick $N \isd \Po( \mu(y_0) )$ then and we take $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
+(That is, the intesity function of the Poisson point process, but set to zero outside of $\BallPo{(0,y_0)}$ and renormalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{(0,y_0)}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{(0,y_0)}$ chosen according to the mentioned renormalized probability density function.
+This shows that, for every $k\geq 2$:
+\[
+	\Ee\left( C | D=k, y=y_0 \right) 
+	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} 1_{\{u_i\in \BallPo{u_j}\}} \right)
+	= \Exp{1_{\{u_1\in\BallPo{u_2}\}}},
+\]
+where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{(0,y_0)}$ with the above mentioned density.
+Note that this does not depend on the value of $k$. For notational convenience, we'll write 
+\[ 
+	P(y_0) := \Exp{1_{\{u_1\in\BallPo{u_2}\}}},
+\]
+with $u_1, u_2$ as above.
+
+We now observe that 
+\[
+	\gamma(k) = \Ee( C | D=k ) = \int_0^\infty \Ee\left( C | D=k, y=y_0 \right) g_k(y_0) \, d y_0,
+\]
+where $g_k$ denotes the density of $y$ {\em conditional on} $D=k$. That is,
+\[
+	g_k(y_0)  = \frac{\rho(y_0, k) \alpha e^{-\alpha y_0} }{\int_0^\infty \rho(t, k) \alpha e^{-\alpha t} \, d t}
+	= \frac{1}{p_k} \cdot \rho(y_0, k) \alpha e^{-\alpha y_0}.
+\]
+Hence, 
+\begin{equation}\label{eq:gammakint}
+\gamma(k) 
+= \frac{1}{p_k} \cdot \int_0^\infty P(y_0) \rho(y_0,k) \alpha e^{-\alpha y_0} \, d y_0. 
+\end{equation}
+This also gives
+\begin{equation}\label{eq:gammaint}
+\begin{array}{rcl} 
+\gamma 
+& = & \displaystyle \Ee C = \sum_{k\geq 2} \Ee( C | D=k )\Pee( D=k ) \\
+& = & \displaystyle \int_0^\infty P(y_0) \left( \sum_{k=2}^\infty \rho(y_0,k) \right) \alpha e^{-\alpha y_0} \, d y_0 \\
+& = & \displaystyle \int_0^\infty P(y_0) \left(1 - \rho(y_0,0)-\rho(y_0,1)\right) \alpha e^{-\alpha y_0} \, d y_0.
+\end{array}
+\end{equation}
+
+A key step is to derive the following explicit expression for $P(y)$.
+
+\begin{lemma}\label{lem:Paneq1}
+%\begin{enumerate}
+%	\item 
+	If $\alpha \not = 1$, then
+	\begin{align*}
+	 P(y) &=-\frac{1}{8 (\alpha - 1) \alpha} + \frac{(\alpha - 1/2) e^{-\frac{1}{2}y}}{\alpha - 1} - \frac{(\alpha - 1/2)^2 e^{-y}}{
 		4 (\alpha - 1)^2} \\
@@
 	\end{align*}
-	\item If $\alpha = 1$, then
-	\begin{align*}
-	&\Delta_{\Pcal}(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
-e^{-y}  + 
-\frac{1}{2}e^{-y}\Li_2(e^{-y})
-	\end{align*}
-	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
-\end{enumerate}
-\end{proposition}
-
-%We note that $\Delta_{\Pcal}(y_0)$ is the probability that $(x_1,y_1), (x_2,y_2)$ are neighbours, given that they are neighbours of $(0,y_0)$.
-(Here we think of $y_0$ as being fixed during the chance experiment and $(x_1,y_1), (x_2,y_2)$ chosen randomly.)
-
-%The computation can be outlined as follows: First of all, we apply a change of variable $z_i = e^{-y_i/2}$, $i=0,1,2$.
-Then we find an expression for $P(y_0(z_0),y_1(z_1),y_2(z_2))$ depending on several cases in the input variables.
-The two innermost integrals, which we are going to denote by $P(y_0)$, are computed by partitioning the integration domain into four corresponding subdomains.
-
-To derive this result, recall (see~\eqref{eq:def_delta_p}) that $\Delta_{\Pcal}(y)$ is the probability that $Z_1 \in \BallPo{Z_2}$, where $Z_1, Z_2$ are two independent random variables on $\BallPo{0,y}$ with density
-\[
-	\eta_{y}(y^\prime,x^\prime) = \frac{f_{\alpha,\nu}(x^\prime, y^\prime)\ind{(x^\prime, y^\prime \in B_{\Pcal}(0,y)}}{\mu(B_{\Pcal}(0,y))}.
-\]
-
-For notational convenience we will switch to using $y_0$ instead of $y$. Note that the random variables $Z_i = (x_i,y_i)$, for $i = 1,2$, correspond to first sampling $y_i$ according to the density
-\[
-	g(y_i) := \left(\alpha -\frac{1}{2}\right) e^{-(\alpha-\frac{1}{2})y_i}
-\] 
-and then sampling $x_i$ uniformly in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$.
-With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ form a triangle where $x_1$ and $x_2$ are uniform random variables in, respectively, $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.
-
-Then we have that
+% 	\item If $\alpha = 1$, then
+% 	\begin{align*}
+% 	&P(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
+% e^{-y}  + 
+% \frac{1}{2}e^{-y}\Li_2(e^{-y})
+% 	\end{align*}
+% 	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
+%\end{enumerate}
+\end{lemma}
+
+We will prove this lemma in a sequence of steps.
+
+Recall that $P(y_0)$ is the probability that $u_1 = (x_1,y_1), u_2 = (x_2,y_2)$ are neighbours in $\Ginf$, where
+$u_1, u_2$ are i.i.d.~with probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
+In particular
+
+$$ \begin{array}{rcl} 
+\Pee( y_i > t ) 
+& = & 
+\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty \int_{-e^{(s+y_0)/2}}^{e^{(s+y_0)/2}} e^{-\alpha s}\, d s \\
+& = & 
+\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty 2 e^{(s+y_0)/2} \cdot e^{-\alpha s}\, d s \\
+& = & 
+\frac{2 \nu\alpha e^{y_0/2} }{\pi \xi e^{y_0/2} (\alpha-\frac12) }  \cdot e^{(\frac12-\alpha)t} \\
+& = & 
+ e^{(\frac12-\alpha)t},
+\end{array} $$
+
+\noindent
+using that $\mu(y_0) = \xi e^{y_0/2} = \left(\frac{2\alpha\nu}{\pi(\alpha-\frac12)}\right) e^{y_0/2}$.
+Thus, $y_1, y_2$ are exponentially distributed with parameter $\alpha-\frac12$.
+Now note that, for each $t>0$, the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$
+is constant on $[-e^{(t+y_0)/2}, e^{(t+y_0)/2}] \times \{t\}$ and it is 
+vanishes on $(-\infty, -e^{(t+y_0)/2}) \times \{t\} \cup (e^{(t+y_0)/2},\infty)\times\{t\}$.
+
+Hence, given the height $y_i$ of $u_i$, the $x$-coordinate of $u_i$ is uniform in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$. 
+With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ 
+satisfy $|x_1-x_2| \leq e^{(y_1+y_2)/2}$, where $x_1$ and $x_2$ are independent uniform random variables in, respectively, 
+$[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.
+We have that
+
 \begin{align}\label{eq:delta_P}
- \Delta_{\Pcal}(y_0) = (\alpha-1/2)^2 \int_0^\infty \int_0^\infty P(y_0, y_1, y_2) e^{-(\alpha-1/2)(y_1+y_2)} 
+ P(y_0) = (\alpha-1/2)^2 \int_0^\infty \int_0^\infty P(y_0, y_1, y_2) e^{-(\alpha-1/2)(y_1+y_2)} 
  \dd y_2 \dd y_1.
@@
 
-\subsection{Triangle probability for nodes at given heights}
-We proceed by first computing $P(y_0,y_1,y_2)$.
-To compute the integral~\ref{eq:delta_P} it will be convenient to use the change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$.
+\subsubsection{Determining $P(y_0,y_1,y_2)$}
+
+To compute the integral~\eqref{eq:delta_P} it will be convenient to use the 
+change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$. 
 We will write $y_i(z_i)$ to stress the dependence between $y_i$ and $z_i$. 
@@
 We split the proof of this lemma into a couple of smaller pieces. We begin with the following lemma.
+
 \begin{lemma}\label{lem:ordered}
@@
 The solid red line indicates the range for $x_2$ such that the points $p_0$, $p_1$ and $p_2$ form a triangle.
-The boundaries of there balls are show in, respectively, black, blue and green.}
+The boundaries of their neighborhoods are shown in, respectively, black, blue and green.}
 \label{fig:triangle_prob_lemma}
@@
 \begin{proof}
-%pim pass1: $P(y_0,y_1,y_2)$ is the probability that $(x_1,y_1)$ and $(x_2,y_2)$ (which are given by a Poisson process in the upper half-plane) are neighbours of each other, given that they are neighbours of $(0,y_0)$ (see figure \ref{fig:triangle_prob_lemma}).
-By the properties of the Poisson process and our connection rule (which defines the neighourhood area of $(0,y_0)$ in the upper half-plane), given $y_0, y_1, y_2$ we have that $x_i$ is chosen u.a.r.~from $[-e^{y_0/2+y_i/2}, +e^{y_0/2+y_i/2}]$ for $i=1,2$.
-Since the Poisson Point Process is translation invariant in the $x$-coordinate we can, without loss of generality, take $x_0 = 0$.
-By definition of the connection rule $P(y_0,y_1,y_2)$ is the probability that $|x_2-x_1| \leq  e^{(y_1+y_2)/2}$ (see figure \ref{fig:triangle_prob_lemma}).
-Consider $y_0, y_1, y_2$ and $x_1$ fixed.
-Then we are interested in computing the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y+2)/2},x_1+e^{(y_1+y_2)/2}]$ (given by the bottom interval in the Figure~\ref{fig:triangle_prob_lemma}), as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$ (given by the top interval in the Figure~\ref{fig:triangle_prob_lemma}).
-
-%, i.e. the desired probability can be written as
-%\[ 
-%\frac{
-%\Ee_{x_1} \text{length}( [x_1-e^{(y_1+y_2)/2}, x_1+e^{(y_1+y_2)/2}] \cap [-e^{(y_0+y_2)/2}, e^{(y_0+y_2)/2}] )
-%}{
-%2 e^{(y_0+y_2)/2}
-%} \]
-%
-%\noindent
-
-By symmetry, without loss of generality we can consider $x_1$ uniformly at random from $[0,e^{y_0/2+y_1/2}]$. 
-%The probability will be the same.Let us assume for the moment that $y_0 < y_1 < y_2$. 
-Since $y_0 < y_1 < y_2$ we have that $e^{(y_1+y_2)/2} > e^{(y_0+y_2)/2}$ and so, when $x_1 \geq 0$, the ``right half'' of the interval $[-e^{(y_0+y_2)/2}, e^{(y_0+y_2)/2}]$ is always covered by the interval $[x_1-e^{(y_1+y_2)/2}, x_1+e^{(y_1+y_2)/2}]$.
+Note that $P(y_0,y_1,y_2)$ is the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y_2)/2},x_1+e^{(y_1+y_2)/2}]$ , as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$.
+By symmetry considerations, we can take $x_1$ uniformly at random from $[0,e^{y_0/2+y_1/2}]$ as opposed to $[-e^{y_0/2+y_1/2}, e^{y_0/2+y_1/2}]$.
+Figure~\ref{fig:triangle_prob_lemma} show the intersection of the intervals (red line) for two different cases for $x_1 \le e^{(y_0 + y_1)/2}$.
+
+Since $y_0 < y_1 < y_2$ we have that $e^{(y_1+y_2)/2} > e^{(y_0+y_2)/2}$ and so, when $x_1 \geq 0$, the ``right half'' of the 
+interval $[-e^{(y_0+y_2)/2}, e^{(y_0+y_2)/2}]$ is always covered by the interval $[x_1-e^{(y_1+y_2)/2}, x_1+e^{(y_1+y_2)/2}]$.
 If $e^{(y_1+y_2)/2} - e^{(y_0+y_1)/2} \geq e^{(y_0+y_2)/2}$ then the ``left half'' is always covered as well.
@@
 Now consider the case where $e^{(y_1+y_2)/2} - e^{(y_0+y_1)/2} < e^{(y_0+y_2)/2}$. 
-Then, if $x_1 \in [0, e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2}]$ the whole interval $[-e^{(y_0+y_2)/2}, e^{(y_0+y_2)/2}]$ is still covered so that $p_0, p_1$ and $p_2$ form a triangle.
-If, on the other hand $e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2} < x_1 \leq e^{(y_0+y_1)/2}$ then
+Then, if $x_1 \in [0, e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2}]$ the whole interval $[-e^{(y_0+y_2)/2}, e^{(y_0+y_2)/2}]$ is still covered 
+so that $p_0, p_1$ and $p_2$ form a triangle. If, on the other hand $e^{(y_1+y_2)/2} - e^{(y_0+y_2)/2} < x_1 \leq e^{(y_0+y_1)/2}$ then
 the probability that $|x_2-x_1| \leq e^{(y_1+y_2)/2}$ equals
@@
 
-%\begin{lemma}\label{lem:leverage}
-%We have
 %
-%\[ P(y_0, y_1, y_2) = \left(z_0/z_1\right) P(y_1,y_0,y_2) = \left(z_0/z_1\right) P(y_1,y_2,y_0), \]
-%
-%\noindent
-%where $z_i = e^{-y_i/2}$ as before.
-%\end{lemma}
-%
-%
-%
-%\begin{proof}
-%We can think of $P(y_0,y_1,y_2)$ as a multiple of a 3-fold integral of the indicator function
-%\[ 
-%	h(x_0, x_1, x_2) := \ind{ |x_0-x_1| < e^{(y_0+y_1)/2}, |x_0-x_2| < e^{(y_0+y_2)/2}, |x_1-x_2| < e^{(y_1+y_2)/2}}, 
-%\]
-%where $x_0$ is selected uniformly $ x_1, x_2$ range over $\R$. More specifically $x_0$ u.a.r.~from $[-K,+K]$ and $x_i$ u.a.r.~from 
-%$[x_0-e^{(y_0+y_i)/2}, x_0+e^{(y_0+y_i)/2}]$
-%
-%which we make into a 
-%circle by identifying the endpoints and we take $K$ large enough.
-%In more detail: we integrate the indicator function 
-%
-%\[ 
-%	h(x_0, x_1, x_2) := 1_{\{ |x_0-x_1|_{2K} < e^{(y_0+y_1)/2}, |x_0-x_2|_{2K} < e^{(y_0+y_2)/2}, |x_1-x_2|_{2K} < e^{(y_1+y_2)/2} \}}, 
-%\]
-% 
-%(where $|a|_b := \min(|a|, b-|a|)$ for $|a| \leq b$), and we multiply by 
-%$\frac{1}{2K} \cdot \frac{1}{2e^{(y_0+y_1)/2}} \cdot \frac{1}{2e^{(y_0+y_2)/2}}$.
-%(we think of taking $x_0$ u.a.r.~from $[-K,+K]$ and $x_i$ u.a.r.~from 
-%$[x_0-e^{(y_0+y_i)/2}, x_0+e^{(y_0+y_i)/2}]$ -- interpreted modulo $K$ of course, so $K$ is chosen as a real number $>e^{(y_0+y_i)/2}$  s.t.
-the intervals $[x_0-e^{(y_0+y_i)/2},x_0+e^{(y_0+y_i)/2}]$ do not cover the circle).
-%That is:
-%
-%\[ P(y_0, y_1, y_2) = \frac{1}{2K} \cdot \frac{1}{2e^{(y_0+y_1)/2}} \cdot \frac{1}{2e^{(y_0+y_2)/2}} \cdot \int_{[-K,K]^3} f. \]
-%
-%\noindent
-%Completely analogously:
-%
-%\[ P(y_1,y_0,y_2) = \frac{1}{2K} \cdot \frac{1}{2e^{(y_1+y_0)/2}} \cdot \frac{1}{2e^{(y_1+y_2)/2}} \cdot \int_{[-K,K]^3} f
-% = \frac{e^{y_0/2}}{e^{y_1/2}} P(y_0,y_1,y_2) = \frac{z_1}{z_0}  P(y_0,y_1,y_2), \]
-%
-%\noindent
-%proving the first part of the lemma. The second part of the lemma holds as $P(y_1,y_2,y_0)=P(y_1,y_0,y_2)$.
-%\end{proof}
-%
-%\begin{corollary} \label{cor:nonordered}
-%$\text{ }$
-%If $y_1 < \min(y_0,y_2)$ (or equivalently $z_1 > \max(z_0,z_2)$), then 
-%\[ P(y_0,y_1,y_2) = \left\{ 
-%\begin{array}{cl}
-%\frac{z_0}{z_1} & \text{ if } z_1 \geq z_0 + z_2, \\
-%\frac{z_0}{z_1} \cdot (1-G(z_1,z_0,z_2)) & \text{ if } z_1 < z_0+z_2. 
-%\end{array} \right. 
-%\]
-%
-%(Here $z_i := e^{-y_i/2}$ as before.)
-%\end{corollary}
-%
-%Applying the expression found earlier, we find that 
-%
-%\[ \begin{array}{rcl}
-%G(z_1,z_0,z_2)
-%& = & 
-%\frac14 ( z_0^{-1} z_2 + z_0 z_2^{-1} + z_1^2z_0^{-1} z_2^{-1}
-%+ 2 -2z_1z_0^{-1}-2z_1z_2^{-1} ) \\
-%\end{array} \]
-%
-%%\noindent
-%Hence
-%
-%\[ \begin{array}{rcl}
-%    G'(z_0,z_1,z_2) 
-%    & := &  \frac{z_0}{z_1} G(z_1,z_0,z_2) \\
-%    & = & \frac14 ( z_1^{-1} z_2 +z_0^2 z_1^{-1} z_2^{-1} + z_1 z_2^{-1} + 2z_0z_1^{-1} - 2 - 2z_0z_2^{-1} )
-%   \end{array}
-%\]
-%
-%We are now ready to complete the proof of Lemma~\ref{lem:triangle_prob_y_coordinates}.
-%
-%\begin{proof}[Proof of Lemma~\ref{lem:triangle_prob_y_coordinates}]
-%Let $y_i >0$ and $z_i = e^{-y_i/2}$, $i=0,1,2$.
-Then lemma \ref{lem:ordered} gives the expression for $P(y_0(z_0),y_1(z_1),y_2(z_2))$ in the case $y_0<y_1<y_2$, or equivalently $z_0>z_1>z_2$, i.e.
-the first two lines in the claim of the proposition.
-As $P(y_0,y_1,y_2)$ is symmetric in $y_1$ and $y_2$, we can assume $y_1 < y_2$.
-Then, there are two more orderings of $y_0, y_1, y_2$, namely $y_1< y_0< y_2$ and $y_1<y_2<y_0$.
-That either of these orderings holds is equivalent to $y_1 < \min (y_0,y_2)$, or equivalently to $z_1 > \max(z_0,z_2)$.
-For $y_1 < y_0 < y_2$ and $y_1 < y_2<y_0$ we can apply lemma \ref{lem:ordered} to obtain $P(y_1,y_0,y_2)$ and $P(y_1,y_2,y_0)$ which happen to agree due to the symmetry in the last two arguments of the expression found in that lemma.
-Then lemma \ref{lem:leverage} yields $P(y_0,y_1,y_2)$ based on $P(y_1,y_0,y_2)=P(y_1,y_2,y_0)$ and corollary \ref{cor:nonordered} spells this out explicitly and together with the remarks after corollary \ref{cor:nonordered}, we obtain the remaining two lines in the claim of the proposition, which concludes the proof.
-%\end{proof}
-
-\subsection{Computing $\Delta_\Pcal(y_0)$}
-
-Now that we have established the expression for $P(y_0,y_1,y_2)$ we can proceed with computing $\Delta_{\Pcal}(y_0)$, i.e.
-proving Proposition~\ref{prop:full_expression_delta_P}.
-We start with the following observation.
+
+\subsubsection{Integrating over $y_1, y_2$}
+
+Now that we have established the expression for $P(y_0,y_1,y_2)$ we can proceed to compute $P(y_0)$ by integrating over $y_1, y_2$.
+We however start with the following observation.
 
 \begin{lemma}\label{lem:continuity_Delta_function}
-The function $\alpha \mapsto \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ is continuous for all $\alpha > \frac{1}{2}$.
+The function $\alpha \mapsto P_\alpha(y_0)$ is continuous for all $\alpha > \frac{1}{2}$.
 \end{lemma}
+
 \begin{proof}
 This follows from the theorem of dominated convergence:
-Let $\alpha > \frac{1}{2}$ and $(\alpha_n)_{n\in \mathbb{N}}$ a sequence of real numbers converging to $\alpha$, so we can assume $|\alpha_n - \alpha| < \epsilon := \frac{\alpha-1/2}{2}$.
-This means that $-\epsilon < \alpha_n - \alpha < \epsilon$, i.e.
-$\frac{\alpha-1/2}{2} < \alpha_n - 1/2 < \frac{3\alpha-3/2}{2}$.
-Define $f_n(y_1,y_2) = P(y_0,y_1,y_2) (\alpha_n - 1/2)^2 e^{-(\alpha_n-1/2)(y_1+y_2)}$.
-As the function $x \mapsto x^2$ is increasing in $x$ for $x>0$ and the function $x \mapsto e^{-(y_1+y_2)x}$ is decreasing in $x$ and $P(y_0,y_1,y_2) \in [0,1]$, it holds that $|f_n(y_1,y_2)| \leq (\frac{3\alpha-3/2}{2})^2e^{-(y_1+y_2)\frac{\alpha-1/2}{2}}$ which is integrable over $\R_{\geq 0} \times \R_{\geq 0}$ (with integral equals $\frac{(6\alpha-3)^2}{(2\alpha-1)^2}$).
-Application of the theorem of dominated convergence and using equation~\eqref{eq:def_delta_p} yields that $\Delta_{\Pcal_{\alpha_n,\nu}}(y_0) \rightarrow \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ which gives the claim as the sequence $(\alpha_n)_n$ was arbitrary.
+Let $\alpha > \frac{1}{2}$ and $(\alpha_n)_{n\in \mathbb{N}}$ a sequence of real numbers converging to $\alpha$, so we can 
+assume $|\alpha_n - \alpha| < \epsilon := \frac{\alpha-1/2}{2}$. 
+This means that $-\epsilon < \alpha_n - \alpha < \epsilon$, i.e. $\frac{\alpha-1/2}{2} < \alpha_n - 1/2 < \frac{3\alpha-3/2}{2}$. Define
+
+$$f_n(y_1,y_2) = P(y_0,y_1,y_2) (\alpha_n - 1/2)^2 e^{-(\alpha_n-1/2)(y_1+y_2)}.$$
+
+As the function $x \mapsto x^2$ is increasing in $x$ for $x>0$ and the function $x \mapsto e^{-(y_1+y_2)x}$ is decreasing 
+in $x$ and $P(y_0,y_1,y_2) \in [0,1]$, it holds that
+
+$$|f_n(y_1,y_2)| \leq \left(\frac{3\alpha-3/2}{2}\right)^2e^{-(y_1+y_2)\frac{\alpha-1/2}{2}}$$
+
+which is integrable over $\R_{\geq 0} \times \R_{\geq 0}$ (with integral equalling $(6\alpha-3)^2/(2\alpha-1)^2$). 
+Application of the theorem of dominated convergence yields that 
+$P_{\alpha_n}(y_0) \rightarrow P_\alpha(y_0)$ which gives the claim as the 
+sequence $(\alpha_n)_n$ was arbitrary.
 \end{proof}
 
-Due to this lemma we can first assume $\alpha \notin \{ \frac{3}{4},1 \}$, compute $\Delta_{\Pcal}(y_0)$ and then obtain the values of $\Delta_\Pcal(y_0)$ at the remaining two points by taking the corresponding limit in $\alpha$.
+Due to this lemma we can first assume $\alpha \notin \{ \frac{3}{4},1 \}$, compute $P(y_0)$ and then obtain the values of $P(y_0)$ at 
+the remaining two points by taking the corresponding limit in $\alpha$. 
 This strategy is executed below. 
-It involves the computation of several integrals which are involved and will take up the next 7 pages.
-The proof is carefully structured, using headers, to aid the reader.
-
-\begin{proof}[Proof of Proposition~\ref{prop:full_expression_delta_P}]\hfill
-
-\paragraph{When $\bm{\alpha \notin \{3/4,1\}}$}
-Note that when writing $\Delta_{\Pcal}(y_0)$ as in integral as in equation \eqref{eq:def_delta_p}, by symmetry in the integration variables $y_1$ and $y_2$, we can assume that $y_1<y_2$ in which case either $y_0$ or $y_1$ is the smallest height.
-This gives half the value of $\Delta_{\Pcal}(y_0)$ and hence
-\[ 
-	\Delta_\Pcal(y_0) = 2(I_1(y_0) +I_2(y_0)), 
+It involves the computation of several integrals which are involved and will take up a few pages. 
+The proof is structured using headers, to aid the reader.
+
+%\begin{proof}[Proof of Proposition~\ref{prop:full_expression_delta_P}]\hfill
+
+%\paragraph{When $\bm{\alpha \notin \{3/4,1\}}$}
+
+Note that when writing $P(y_0)$ as in integral as in equation \eqref{eq:def_delta_p}, by symmetry in the integration 
+variables $y_1$ and $y_2$, we can assume that $y_1<y_2$ in which case either $y_0$ or $y_1$ is the smallest height. 
+This gives half the value of $P(y_0)$ and hence
+\[ 
+	P(y_0) = 2(I_1(y_0) +I_2(y_0)), 
 \] 
@@
 We proceed with computing each of these two integrals, each of which is split in two parts. 
-The final expressions of those four integrals can be found in~\eqref{eq:Delta_P_computation_I11}, \eqref{eq:Delta_P_computation_I12}, \eqref{eq:Delta_P_computation_I21} and~\eqref{eq:Delta_P_computation_I22}.
+The final expressions of those four integrals can be found 
+in~\eqref{eq:Delta_P_computation_I11}, \eqref{eq:Delta_P_computation_I12}, \eqref{eq:Delta_P_computation_I21} 
+and~\eqref{eq:Delta_P_computation_I22}.
 
@@
 \end{align*}
-As $c \geq -1$ and $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators that occur during the computations above are non-zero.
+As $c \geq -1$ and $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators 
+that occur during the computations above are non-zero.
 
@@
 \end{align*}
-Using some algebra and the identities~\eqref{eq:Delta_P_computation_beta_id_1} and~\eqref{eq:Delta_P_computation_beta_id_2}  this can be reduced to
+Using some algebra and the identities~\eqref{eq:Delta_P_computation_beta_id_1} and~\eqref{eq:Delta_P_computation_beta_id_2}  
+this can be reduced to
 \begin{equation}\label{eq:Delta_P_computation_I22}
@@
 
-%
-%
-%Combining the results for $I_{21}(y_0)$ and $I_{22}(y_0)$ we get
-%\begin{equation}\label{eq:Delta_P_computation_I2}
-%\begin{aligned}
-%	I_2(y_0) = 
-%\end{aligned}
-%\end{equation}
-
 \paragraph{Combining the results for $\bm{I_1(y_0)}$ and $\bm{I_2(y_0)}$}
 
-Combining the results for $I_{11}(y_0), I_{12}(y_0), I_{21}(y_0)$ and $I_{22}(y_0)$ we get, after some algebra, an explicit expression for $\Delta_{\Pcal}(y_0)$ as a linear combination of terms of the form $z_0^u$, $(1-z_0)^u$ and $z_0^u B^-(1-z_0;a,b)$:
-\begin{align*}
-\Delta_{\Pcal}(y_0)=& 2(I_1+I_2) = 8(\alpha- 1/2)^2(I_{1,1}-I_{1,2}+I_{2,1}-I_{2,2}) \\
+Combining the results for $I_{11}(y_0), I_{12}(y_0), I_{21}(y_0)$ and $I_{22}(y_0)$ we get, after some algebra, an explicit expression 
+for $P(y_0)$ as a linear combination of terms of the form $z_0^u$, $(1-z_0)^u$ and $z_0^u B^-(1-z_0;a,b)$: 
+\begin{align*}
+P(y_0)=& 2(I_1+I_2) = 8(\alpha- 1/2)^2(I_{1,1}-I_{1,2}+I_{2,1}-I_{2,2}) \\
 =&8(\alpha-1/2)^2 \left(\frac{1}{2(2\alpha-1)^2 }z_0^{4\alpha -2} \right. \\ 
@@
 Observe that the above expression only contains terms of the form $\alpha - 1$ in the denominator. 
-The only expression of the form $\alpha - 3/4$ is in the lower incomplete beta-function $B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)$ which appears twice in the expression for $\Delta_{\Pcal}(y_0)$.
-
-\paragraph{The case of $\bm{\alpha = 3/4}$}\hfil\\
+The only expression of the form $\alpha - 3/4$ is in the lower incomplete beta-function $B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)$ which 
+appears twice in the expression for $P(y_0)$.
+
+\paragraph{The case of $\bm{\alpha = 3/4}$}\hfill\\
 
 Note that the factor $\alpha-\frac{3}{4}$ does not occur in any denominator of the previously obtained expression. 
-For the lower incomplete beta function, the last argument $3-4\alpha$ is zero for $\alpha=\frac{3}{4}$, however as $z_0 < 1$ the integration domain of the lower incomplete beta function does not touch the singularity at $t=1$ (note $B^-(1-z_0;2\alpha;3-4\alpha) = \int_0^{1-z_0} t^{2\alpha-1} (1-t)^{2-4\alpha}$).
+For the lower incomplete beta function, the last argument $3-4\alpha$ is zero for $\alpha=\frac{3}{4}$, however as $z_0 < 1$ the 
+integration domain of the lower incomplete beta function does not touch the singularity at $t=1$ 
+(note $B^-(1-z_0;2\alpha;3-4\alpha) = \int_0^{1-z_0} t^{2\alpha-1} (1-t)^{2-4\alpha}$). 
 Therefore, the previous expression holds for this case as well.
 
-\paragraph{The case of $\bm{\alpha = 1}$}
-
-We want to compute the limit $\lim_{\alpha \rightarrow 1} \Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0))$.
-For this, after factoring out $\frac{1}{\alpha-1}$ in the expression for $\Delta_{\Pcal}(y)$ we obtained for $\alpha \ne 1$, we compute the first two terms of the Taylor expansion of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ in $\alpha$ based at $\alpha = 1$.
-The constant term of this Taylor expansion is verified to vanish whereas the linear term gives the expression searched (after cancellation with $\frac{1}{\alpha-1}$).
-Note that two terms of $P(y_0(z_0))$ contain $(\alpha-1)^2$ in their denominator, so for those two another $\frac{1}{\alpha-1}$ is factored out and the first three terms of the Taylor expansion are computed.
-Their constant terms cancel and after multiplication with $\frac{1}{\alpha-1}$ their linear and quadratic terms become part of the constant and linear term of the overall expansion.
-
-The first summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ is,
-\begin{align*}
-	S_1 = -\frac{1}{8 \alpha} = -\frac{1}{8}+\frac{1}{8}(\alpha-1) +O( (\alpha-1)^2)
-\end{align*}
-The second summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
-\begin{align*}
-	S_2 = (\alpha-1/2)z_0 = \frac{1}{2}z_0 +z_0 (\alpha-1)+O( (\alpha-1)^2)
-\end{align*}
-The third summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$, needs a 3-term Taylor expansion after another multiplication with $(\alpha-1)$,
-\begin{align*}
-	S_3 = - \frac{(\alpha - 1/2)^2 z_0^2}{4} = -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+O( (\alpha-1)^3)
-\end{align*}
-The fourth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$, needs a  3-term Taylor expansion after another multiplication with $(\alpha-1)$,
-\begin{align*}
-	S_4 = z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha} &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
-&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+O( (\alpha-1)^3)
-\end{align*}
-as
-\begin{align*}
-\frac{d}{d\alpha}\left( \left(\frac{z_0}{2}\right)^{-2+4\alpha} 2^{-3}\left(3-\frac{1}{\alpha}\right) \right) = \left(\frac{z_0}{2}\right)^{-2+4\alpha}2^{-3}\left(4\ln\left(\frac{z_0}{2}\right)\left(3-\frac{1}{\alpha}\right)+\frac{1}{\alpha^2}\right)
-\end{align*}
+%%%\end{proof}
+
+\subsubsection{Computing $\gamma$ and $\gamma(k)$\label{ssec:exact_expressions_clustering_P}}
+
+Now that we have an expression for $P(y_0)$ we can compute $\gamma, \gamma(k)$ by integrating 
+over $y_0$ and prove that they equal the expressions given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and 
+Theorem~\ref{thm:local_clustering_hyperbolic}.
+
+We define
+\[
+	I^{(k)} := 
+	\int_0^{\infty} P(y) \alpha e^{-\alpha y}\rho(y,k) \dd y = 
+	\int_0^{\infty} P(y) \alpha e^{-\alpha y} \frac{\left(\xi e^{y/2}\right)^k}{k!} e^{-\xi e^{y/2}} \dd y
+\]
 and
-\begin{align*}
-\frac{d^2}{d\alpha^2}\left( \left(\frac{z_0}{2}\right)^{-2+4\alpha} 2^{-3}\left(3-\frac{1}{\alpha}\right) \right) = \left( \frac{z_0}{2} \right)^{-2+4\alpha}2^{-3}\left(16\left(\ln\frac{z_0}{2}\right)^2\left(3-\frac{1}{\alpha}\right)+\frac{8\ln(\frac{z_0}{2})}{\alpha^2}-\frac{2}{\alpha^3} \right)
-\end{align*}
-For the fifth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ we get,
-\begin{align*}
-	S_5 &= z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha} \\
-	&= \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
- 	&\hspace{20pt}\left.+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right)  (\alpha-1)+O( (\alpha-1)^2 )
-\end{align*}
-as
-\begin{align*}
-	&\hspace{-20pt}\frac{d}{d \alpha}\left( z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 )}{2\alpha} 
-		B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\right) \\
-	&= \ln(z_0) 4 z_0^{-2+4\alpha} \left(\frac{1}{2}-\frac{1}{4\alpha}\right)B^-(1/2;1+2\alpha,-2+2\alpha)\\
-	&+z_0^{-2+4\alpha}\frac{1}{4\alpha^2}B^-(1/2;1+2\alpha,-2+2\alpha)+z_0^{-2+4\alpha}\left(\frac{1}{2}-\frac{1}{4\alpha}\right)\int_0^{\frac{1}{2}} \frac{d}{d\alpha}(t^{2\alpha}(1-t)^{2\alpha-3})dt
+\[
+	J := \int_0^\infty P(y) \alpha e^{-\alpha y} \dd y.
+\]
+
+Then, recalling~\eqref{eq:gammaint} and~\eqref{eq:gammakint}, we have
+\[   
+	\gamma = J - I^{(1)} - I^{(2)} \quad \text{and} \quad
+	\gamma(k) = \frac{I^{(k)}}{p_k}.
+\]
+
+We will thus compute $J$ and $I^{(k)}$. It will be helpful to change coordinates to $z := e^{-y/2}$. This yields 
+\[ 
+	J = 2 \alpha \int_0^1 P(y) z^{2\alpha-1} \dd z, 
+\]
+and 
+\[ 
+	I^{(k)} = \frac{2 \alpha \xi^k}{k!} \cdot \int_0^1 P(y(z)) \cdot z^{2\alpha-(k+1)} e^{-\xi z^{-1}} \dd z. 
+\]
+
+We shall be assuming $\alpha \not = 1$. 
+We observe from Lemma~\ref{lem:Paneq1} that for $\alpha \not =1$, $P(y(z))$ is in fact a linear combination 
+of terms of the form $z^u$, $(1-z)^u$ and $z_0^u B^-(1-z_0,v,w)$.
+
+To compute $J$ we observe that, by partial integration, 
+\begin{align*}
+	\int_0^1 z^{u+2\alpha-1} B^-(1-z;v,w) \dd z 
+	&= \left[ \frac{z^{u+2\alpha}}{u+2\alpha} B^-(1-z;v,w) \right]_0^1 
+		+ \frac{1}{u+2\alpha} \int_0^1 z^{u+2\alpha+w-1} (1-z)^{v-1} \dd z \\
+	&= \frac{1}{u+2\alpha} B(u+w+2\alpha,v)
+\end{align*}
+where we used that $\frac{\partial}{\partial z} B^-(1-z;v,w) = - z^{w-1} (1-z)^{v-1}$.
+This takes care of the two integrands involving the Beta function in $P(y)$.
+The other integrals are easily computed and yield the following expression for $J$ (note that it only depends on $\alpha$ but not on $\nu$)
+\begin{align*}
+J&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 
+	24 \alpha^5}{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} +  \frac{2^{-1 - 
+		4 \alpha}}{(\alpha - 1)^2} \\
+	&\qquad+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
+	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)}
+\end{align*}
+
+We proceed to work out $I^{(k)}$.
+For this we will compute the integrals involving terms in $P(y(z))$ of the form $z^u$, $(1-z)^u$ and $B(1-z,v,w)$ separately.
+We first point out that for any $0 \le a < b \le 1$
+\begin{align*}
+	\int_a^b z^{u+2\alpha-(k+1)} e^{-\xi z^{-1}} \dd z
+	&= \xi^{u+2\alpha-k} \int_{\xi/b}^{\xi/a} t^{k-1-2\alpha-u} e^{-t} \dd t \\
+	&= \xi^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u;\xi/b) - \Gamma^+( k-2\alpha-u; \xi/a) \right), 
+\end{align*}
+In particular
+\begin{equation}\label{eq:integral_Delta_P_z}
+	\int_0^1 z^{u+2\alpha-k-1} e^{-\xi z^{-1}} \dd z = \xi^{u+2\alpha-k} \Gamma^+(k-2\alpha-u;\xi)
+\end{equation}
+where $\Gamma^+$ denotes the (upper) incomplete gamma function, and we've used the subsitution
+$t = \xi / z$ which gives $\dd z = -\xi_{\alpha, \nu} t^{-2} \dd t$. (And of course it is understood that 
+$\xi/0 = \infty$). This takes care of the integrals of all terms in $P(y(z))$ of the form $z^{u}$.
+
+Next we will consider the integrals over the terms in $P(y(z))$ of the form $(1-z)^u$. For this we need the 
+hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which has the integral representation 
+\[
+	U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} \dd t
+\] 
+which holds for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $Re(a), Re(z) >0$, see~\cite[p.255]{erdelyi1953higher}. 
+Applying the change of variables $t=\frac{1-s}{s}$ (i.e. $\dd t = -s^{-2} \dd s$ and $s = \frac{1}{t+1}$) yields
+%yields the integral 
+%$\int_1^0 e^{-z(-1+\frac{1}{s})} (\frac{1-s}{s})^{a-1} (\frac{1}{s})^{b-a-1} (-s^2)ds = e^z\int_0^1 e^{-z/s} s^{-b}(1-s)^{a-1} ds$, i.e.
+\begin{align*}
+	U(a,b,z) = \frac{e^z}{\Gamma(a)} \int_0^1 s^{-b} (1-s)^{a-1} e^{-z/s} ds
+\end{align*}
+Plugging in $a=2\alpha+1 >0$, $b=-2\alpha+k+1$, $z=\xi>0$, then gives
+\begin{equation}\label{eq:integral_Delta_P_1_z}
+	\int_0^1 z_0^{2\alpha-k-1} e^{-\xi/z_0} (1-z_0)^{2\alpha} dz_0 = \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi)
+\end{equation}
+
+Finally we need to deal with the terms in $P(y(z))$ that involve the incomplete Beta-function. Let $a, c \in \R$, $\xi, b >0$ 
+positive real numbers. Using the integral definition of the incomplete beta function, the change of variables $s=1-t$ gives:
+\begin{align*}
+	\int_0^1 z^a e^{-\xi/z} B^-(1-z;b,c) \dd z 
+	&=\int_0^1 z^a e^{-\xi/z} \int_0^{1-z} t^{b-1} (1-t)^{c-1} \dd t \dd z \\
+	&=\int_0^1 z^a e^{-\xi/z} \int_z^1 s^{c-1} (1-s)^{b-1} \dd s \dd z
+\end{align*}
+Then changing the order of integration and using the substitution $u = \xi/z$  and recognizing the upper incomplete $\Gamma$-function yields
+\begin{align*}
+	&\hspace{-30pt}\int_0^1 z^a e^{-\xi/z} \int_z^1 s^{c-1} (1-s)^{b-1} \dd s \dd z\\
+	&=\int_0^1 \int_0^s z^a e^{-\xi/z} \dd z \, s^{c-1} (1-s)^{b-1} \dd s \\
+	&=\int_0^1 \int_{\xi/s}^\infty \xi^{a+1} u^{-a-2} e^{-u} \dd u \, s^{c-1} (1-s)^{b-1} \dd s \\
+	&= \xi^{a+1} \int_0^1 \Gamma^+(-a-1,\xi/s) s^{c-1} (1-s)^{b-1} \dd s.
+		\numberthis \label{eq:integral_gamma_function}
+\end{align*}
+To compute this last integral we make use of the fact that the incomplete $\Gamma$-function has a representation in terms of 
+Meijer's $G$-function (see Lemma~\ref{lem:gamma_meijer_G} in Appendix~\ref{sec:Meijer_G_functions})
+\[
+	\Gamma^+(-a-1,\xi/s) = \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}},
+\] 
+which holds for any $a\in \R$ and $s>0$ (that for a fixed second argument, the upper incomplete $\Gamma$-function is entire 
+in the first argument, see~\cite[pp. 899, 1032ff.]{gradshteyn2015table}). 
+We can now evaluate the integral in~\eqref{eq:integral_gamma_function} using several identities for Meijer's $G$-function. 
+%formula 8.351.3, p. 
+ %(see the wolfram functions website \url{http://functions.wolfram.com/06.06.26.0005.01}, it can also be found in the paper \url{https://arxiv.org/pdf/1507.05571}; , so we get the integral
+First, inserting the expression for the incomplete Gamma-function into~\eqref{eq:integral_gamma_function} gives
+\begin{align*}
+	\xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}} \dd s
+\end{align*}
+Next we apply the inversion identity for Meijer's $G$-function (see \cite[p. 209, 5.3.1.(9))]{erdelyi1953higher}) to get
+\begin{align*}
+	\xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{0}{2}{2}{1}{2+a,1}{0}{\frac{s}{\xi}} \dd s
+\end{align*}
+This expression is actually the Euler transform of Meijer's $G$-function (see \cite[p.
+214, 5.5.2.(5)]{erdelyi1953higher}) and (as the conditions $2+1<2(0+2)$ and $|\arg(\xi^{-1})| < \frac{\pi}{2}$ (as $\xi>0$) and $1-c-b<1-c$ (as $b>0$)  are satisfied) it equals
+\begin{align*}
+	\xi^{a+1} \Gamma(b) \MeijerG{0}{3}{3}{2}{1-c,2+a,1}{0,1-c-b}{\xi^{-1}}
+\end{align*}
+Using again the inversion identity for Meijer's $G$-function we now get
+\begin{align*}
+	\xi^{a+1} \Gamma(b) \MeijerG{3}{0}{2}{3}{1,b+c}{c,-1-a,0}{\xi}
+\end{align*}
+Finally, plugging in $a= 6\alpha-k-3$, $b=2\alpha$, $c=3-4\alpha$ we obtain
+\begin{equation}\label{eq:integral_Delta_P_Beta}
+	\int_0^1 z^a e^{-\xi/z} B^-(1-z;b,c) \dd z =
+	\xi^{6a-k-2} \Gamma(2\alpha) \MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}
+\end{equation}
+%(note that this agrees with the result in the old approach, after `bringing the power of $\xi$ into Meijer's $G$-function'.)
+
+Using equation~\eqref{eq:integral_Delta_P_z}, \eqref{eq:integral_Delta_P_1_z} and~\eqref{eq:integral_Delta_P_Beta} we get
+\begin{align*}
+	I^{(k)}
+	&=\frac{\xi^{2\alpha}}{4k!(\alpha-1)} \left( -\Gamma^+(k - 2 \alpha, \xi) 
+		- 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
+	&\hspace{15pt}\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
+	&\hspace{15pt}\left.+ 4\xi^{4\alpha - 2} 
+		\Gamma^+(k - 6 \alpha + 2, \xi) \left( 
+		\frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
+	&\hspace{15pt}\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} 	
+		U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
+	&\hspace{15pt}\left.- \xi^{4\alpha-2} 
+		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)\\
+\end{align*}%{4\alpha-k+1,6\alpha-k-1}{6\alpha-k-2,2\alpha-k+1,0}
+
+With the expressions for $J$ and $I^{(k)}$ and using $\Gamma^\ast(q,z) = \Gamma^+(q+1,z) + \Gamma^+(q,z)$ we now obtain, after 
+some algebra, the expression for $c_\Pcal$
+\begin{align*}
+	\gamma &= J-I^{(0)}-I^{(1)} \\
+	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 
+	24 \alpha^5}{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} +  \frac{2^{-1 - 
+		4 \alpha}}{(\alpha - 1)^2} \\
+	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
+	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)} \\
+	&\hspace{10pt}-\frac{\xi^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+( - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} 
+	\Gamma^+(- 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+( - 2 \alpha - 1,\xi) \right.\\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ 4\xi^{4\alpha - 2} \Gamma^+( - 6 \alpha + 2, 
+      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ \xi^{-2\alpha} \Gamma(2\alpha+1)e^{-\xi} 
+		U(2\alpha+1,1-2\alpha,\xi) \right. \\ 
+	&\hspace{10pt}\hspace{10pt}\left.- \xi^{4\alpha-2} 
+		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi}  \right) \\
+	&\hspace{10pt}-\frac{\xi^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+(1 - 2 \alpha, \xi) - 
+		2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+( - 2 \alpha - 1, \xi)}{(\alpha - 1)} \right. \\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(1 - 2 \alpha - 1,\xi) 
+		\right.\\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ 4\xi^{4\alpha - 2} \Gamma^+(1 - 6 \alpha + 2, 
+    	\xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
+	&\hspace{10pt}\hspace{10pt}\left.+ \xi^{1-2\alpha} \Gamma(2\alpha+1)e^{-\xi} 
+		U(2\alpha+1,2-2\alpha,\xi) \right. \\ 
+	&\hspace{10pt}\hspace{10pt}\left.- \xi^{4\alpha-2} 
+		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi}  \right)\\
+	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}
+		{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} 
+		+  \frac{2^{-1 - 4 \alpha}}{(\alpha - 1)^2} \\
+	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}
+		{2 (\alpha - 1) (3 \alpha - 1)} \\
+	&\hspace{10pt}+ \frac{\xi^{2\alpha} \Gamma^\ast( - 2 \alpha, \xi)}{4(\alpha-1)}
+		+ \frac{\xi^{2\alpha + 2}\alpha (\alpha - 1/2)^2 \Gamma^\ast(- 2 \alpha - 2, \xi)}
+		{2(\alpha-1)^2} \\
+	&\hspace{10pt}- \frac{\xi^{2\alpha + 1}\alpha (2\alpha - 1) \Gamma^\ast( - 2 \alpha - 1,\xi)}{(\alpha-1)}
+		- \frac{\xi^{6\alpha-2}2^{-4\alpha}(3\alpha - 1)\Gamma^\ast( - 6 \alpha + 2, \xi)}{(\alpha-1)^2}\\
+	&\hspace{10pt}-\frac{\xi^{6\alpha - 2}(\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\Gamma^\ast( - 6 \alpha + 2, \xi)}{(\alpha-1)} \\
+	&\hspace{10pt}- \frac{e^{-\xi} \Gamma(2\alpha+1) 
+		\left(U(2\alpha+1,1-2\alpha,\xi) + U(2\alpha+1,2-2\alpha,\xi)\right)}{4(\alpha-1)} \\
+	&\hspace{10pt}+ \frac{\xi^{6\alpha - 2} \Gamma(2\alpha+1)\left( 	
+		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi}
+		+ \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi}\right)}{4(\alpha-1)}.
+\end{align*}
+and note that this equals the expression in Theorem~\ref{thm:clustering_coefficient_hyperbolic}. %% when $\alpha \ne 1$.
+
+Similarly, we get
+\begin{align*}
+	\gamma(k) &= \frac{I^{(k)}}{p_k} \\
+	&=\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) 
+		- 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
+	&\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
+	&\hspace{10pt}\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
+      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
+	&\hspace{10pt}\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
+	&\hspace{10pt}\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right),
+\end{align*}
+which equals the expression in Theorem~\ref{thm:local_clustering_hyperbolic}. %% when $\alpha \ne 1$.
+
+\subsubsection{Explicit expressions for $\gamma, \gamma(k)$ when $\alpha=1$.}\label{ssec:alphais1}
+
+Although we've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
+taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$, it is still helpful
+to derive an alternate, more explicit expression.
+This is what we will do in the current section.
+We will prove
+
+\begin{proposition}\label{prop:gammaais1}
+If $\alpha=1$ then 
+\begin{align*} 
+\gamma &= \frac{575 - 12 \pi^2}{576} + \frac{\eta^4(7 + \pi^2)\Gamma^\ast(-4, \eta)}{4}\\
+ 	&\hspace{10pt}- \frac{1}{2} \int_0^1 (1 - 4z + 3z^3)\log(1-z)(z + \eta)e^{-\eta/z} \dd z\\
+ 	&\hspace{10pt}- \int_0^1 \Li_2(z)(z^3 + \eta z^2) e^{-\eta/z} \dd z,		
+ \end{align*}
+and
+\begin{align*}
+ \gamma(k) &= \frac{9 \eta^3}{2 k!} \Gamma^+(k-3,\eta)-\frac{\xi^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
+ 	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
+ 	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
+ \end{align*}
+ with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm 
+ function.
+ %\footnote{Note that the integrals in the expression for $\gamma$ for $\alpha = 1$ exists: for the first 
+ %one note that $1-4z+3z^2=(1-z)(1-3z)$, so the integrand can be bounded by $C(1-z)\log(1-z)$ on $[0,1)$ for some constant $C$, which 
+ %can be continued continuously to the compact interval $[0,1]$ by noting that the limit for $z \rightarrow 1$ is zero, so the 
+ %integrand is bounded on a bounded domain and hence, this integral is finite; for the second integral note 
+ %that $\Li_2(z)$ is bounded by $\Li_2(1)$ on $[0,1]$, which is a series with well-known finite limit, so again the integrand 
+ %is bounded on a bounded domain and hence the second integral is also finite.}.
+\end{proposition}
+
+Naturally, the proof proceeds by proving the analogue of Lemma~\ref{lem:Paneq1}:
+
+\begin{lemma}\label{lem:Pais1}
+If $\alpha = 1$, then
+	\begin{align*}
+	&P(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
+e^{-y}  + 
+\frac{1}{2}e^{-y}\Li_2(e^{-y})
+	\end{align*}
+	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
+\end{lemma}
+
+\begin{proof}
+\TM{\RD{Warning!} this has not been properly proofread by me, or anyone else.}
+We want to compute the limit $\lim_{\alpha \rightarrow 1} P_\alpha(y_0(z_0))$. For $\alpha \neq 1$, we label the terms as follows:
+\begin{align*}
+&P_\alpha(y_0(z_0)) \\
+&= \frac{1}{\alpha-1}\left(s_1(\alpha,z_0)+s_2(\alpha,z_0)+\frac{1}{\alpha-1}(s_3(\alpha,z_0)+s_4(\alpha,z_0)) 
++s_5(\alpha,z_0)+s_6(\alpha,z_0)+s_7(\alpha,z_0)\right)
 \end{align*}
@@
 \begin{align*}
-\int_0^{\frac{1}{2}} \frac{d}{d\alpha}(t^{2\alpha}(1-t)^{2\alpha-3})dt = \int_0^{\frac{1}{2}} \ln(t)2t^{2\alpha}(1-t)^{2\alpha-3}+\ln(1-t)2t^{2\alpha}(1-t)^{2\alpha-3}dt
-\end{align*}
-The sixth summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$,
-\begin{align*}
-	S_6 = \frac{(1 - z_0)^{2 \alpha}}{8 \alpha} = \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1)+O( (\alpha-1)^2 )
-\end{align*}
-and finally the seventh and last summand of $\Delta_\Pcal(y_0(z_0))(\alpha-1)$ gives,
-\begin{align*}
-	S_7 = - \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4} = -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
-\left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+O((\alpha-1)^2)
-\end{align*}
-
-When adding these terms we see that the constant coefficients cancel:
-\begin{align*}
-& -\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) +\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
-&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 -\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 \\ &\hspace{10pt}+\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 =0
-\end{align*}
-The expression for $\alpha=1$ is given by the sum of the linear coefficients:
-\begin{align*}
-	&\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) 
+s_1(\alpha,z_0) &= -\frac{1}{8 \alpha}\\
+s_2(\alpha,z_0) &= (\alpha-1/2)z_0 \\
+s_3(\alpha,z_0) &= - \frac{(\alpha - 1/2)^2 z_0^2}{4}\\
+s_4(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha}\\
+s_5(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha}\\
+s_6(\alpha,z_0) &= \frac{(1 - z_0)^{2 \alpha}}{8 \alpha} \\
+s_7(\alpha,z_0) &= - \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4}
+\end{align*}
+Now, we consider the functions $s_i(\alpha) = s_i(\alpha,z_0)$ as functions of $\alpha$ only and compute their Taylor 
+expansion at $\alpha=1$, for $i\in \{1,2,5,6,7\}$ up to linear and for $i\in \{3,4\}$ up to quadratic order, i.e. we 
+write $s_i(\alpha) = s_i(1)+s_i'(1)(\alpha-1)+o(\alpha-1)$ for $i\in \{1,2,5,6,7\}$ and 
+$s_i(\alpha)=s_i(1)+s_i'(1)(\alpha-1)+\frac{s_i''(1)}{2}(\alpha-1)^2+o((\alpha-1)^2)$ for $i\in \{3,4\}$. Using these expansions, we can rewrite
+\begin{align*}
+&\Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
+s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
+&\left.+\frac{1}{\alpha-1}(s_3(1)+s_4(1)+(s_3'(1)+s_4'(1))(\alpha-1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1)^2 +o((\alpha-1)^2)) \right)
+\end{align*}
+In order to continue, we compute:
+\begin{align*}
+s_1(\alpha) &=-\frac{1}{8}+\frac{1}{8}(\alpha-1)+o(\alpha-1) \\
+s_2(\alpha) &=\frac{1}{2}z_0 +z_0 (\alpha-1)+o(\alpha-1) \\
+s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
+s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
+&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
+s_5(\alpha) &= \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
+ 	&\hspace{20pt}\left.+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right)  (\alpha-1)+o (\alpha-1)\\
+s_6(\alpha) &= \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1)+o(\alpha-1)\\
+s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
+&\qquad \left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+o(\alpha-1)
+\end{align*}
+Based on this we see that
+\begin{align*}
+s_3(1)+s_4(1)=-\frac{1}{16}z_0^2+\frac{1}{16}z_0^2 =0
+\end{align*}
+and
+\begin{align*}
+&\sum_{i\in \{1,2,5,6,7\}} s_i(1) + s_3'(1)+s_4'(1) \\
+&= -\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) 
++\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
+&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 
+-\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 \\ 
+&\hspace{50pt}+\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 \\
+&=0
+\end{align*}
+Finally, it follows that
+\begin{align*}
+\Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)
+\end{align*}
+Therefore, the desired value of $\lim_{\alpha \rightarrow 1} \Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0))$ is given by
+\begin{align*}
+&\sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1))\\
+	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) 
 		+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
@@
 \end{align*}
-% the first integral is
-%\begin{align*}
-%[1/2 (-2 + 5 t + t^2 - \ln(1 - t)^2 - 2 t \ln t - t^2 \ln t - 
-%   \ln(1 - t) (-3 + 2 t + t^2 + 2\ln t) - 2 \Li_2(t))]_0^{\frac{1}{2}} \\
-%= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)
-%\end{align*}
-%and the second one is
-%\begin{align*}
-%[\frac{1}{-1+ t} (1 + \frac{1}{2}(1 + t) \ln(1 - t) + \frac{1}{2}(1 - t) \ln(
-%1 -t)^2 - \frac{1}{2} t \ln(t) +\frac{1}{2} (1 - t) \Li_2(1 -t))]_0^{1-z_0} \\
-%=-\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1)
-%\end{align*}
 By expanding the squares and collecting terms, the last expression can be simplified to
@@
 which finishes the computation.
-
 \end{proof}
 
-\subsection{Exact expressions for the local clustering coefficient and function, integrating $\Delta_{\Pcal}(y)$}\label{ssec:exact_expressions_clustering_P}
-
-Now that we have an expression for $\Delta_{\Pcal}(y)$ we can compute the limit local clustering coefficient $c_\Pcal$ and the limit local clustering function $c_\Pcal(k)$ and prove that they equal $c_\infty$ and $c_\infty(k)$ given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}.
-
-First we recall that $\rho(y,k) = (\xi_{\alpha,\nu} e^{y/2})^k/k! \, e^{-\xi_{\alpha,\nu} e^{y/2}}$ and
-\begin{align*}
-	\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y = \frac{2\alpha \xi^{2\alpha}}{k!} \Gamma(k-2\alpha,\xi)
-	:= \rho(k).
-\end{align*}
-We also define
-\[
-	I^{(k)} := \int_0^{\infty} \Delta_\Pcal(y) \alpha e^{-\alpha y} \frac{\left(\xi e^{y/2}\right)^k}{k!} e^{-\xi e^{y/2}} \dd y
-\]
-and
-\[
-	J := \int_0^\infty \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y.
-\]
-
-Then
-\[   
-	c_\Pcal = J - I^{(1)} - I^{(2)} \quad \text{and} \quad
-	c_\Pcal(k) = \frac{I^{(k)}}{\rho(k)}
-\]
-and hence we first need to compute $J$ and $I^{(k)}$.
-
-For this it will be helpful to change coordinates to $z := e^{-y/2}$. This yields 
-\[ 
-	J = 2 \alpha \int_0^1 \Delta_\Pcal(y) z^{2\alpha-1} \dd z, 
-\]
-and 
-\[ 
-	I^{(k)} = \frac{2 \alpha \xi_{\alpha,\nu}^k}{k!} \cdot \int_0^1 P(y(z)) \cdot z^{2\alpha-(k+1)} e^{-\xi_{\alpha,\nu} z^{-1}} \dd z. 
-\]
-
-We first deal with the case $\alpha \not = 1$.
-We observe from Proposition~\ref{prop:full_expression_delta_P} that for $\alpha \not =1$, $\Delta_\Pcal(y(z))$ is in fact a linear combination of terms of the form $z^u$, $(1-z)^u$ and $z_0^u B^-(1-z_0,v,w)$.
-
-To compute $J$ we observe that, by partial integration, 
-\begin{align*}
-	\int_0^1 z^{u+2\alpha-1} B^-(1-z;v,w) \dd z 
-	&= \left[ \frac{z^{u+2\alpha}}{u+2\alpha} B^-(1-z;v,w) \right]_0^1 
-		+ \frac{1}{u+2\alpha} \int_0^1 z^{u+2\alpha+w-1} (1-z)^{v-1} \dd z \\
-	&= \frac{1}{u+2\alpha} B(u+w+2\alpha,v)
-\end{align*}
-where we used that $\frac{\partial}{\partial z} B^-(1-z;v,w) = - z^{w-1} (1-z)^{v-1}$.
-This takes care of the two integrands involving the Beta function in $\Delta_\Pcal(y)$.
-The other integrals are easily computed and yield the following expression for $J$ (note that it only depends on $\alpha$ but not on $\nu$)
-\begin{align*}
-J&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 
-	24 \alpha^5}{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} +  \frac{2^{-1 - 
-		4 \alpha}}{(\alpha - 1)^2} \\
-	&\qquad+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
-	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)}
-\end{align*}
-
-We proceed to work out $I^{(k)}$.
-For this we will compute the integrals involving terms in $\Delta_\Pcal(y(z))$ of the form $z^u$, $(1-z)^u$ and $B(1-z,v,w)$ separately.
-We first point out that for any $0 \le a < b \le 1$
-\begin{align*}
-	\int_a^b z^{u+2\alpha-(k+1)} e^{-\xi_{\alpha,\nu} z^{-1}} \dd z
-	&= \xi_{\alpha,\nu}^{u+2\alpha-k} \int_{\xi_{\alpha,\nu}/b}^{\xi_{\alpha,\nu}/a} t^{k-1-2\alpha-u} e^{-t} \dd t \\
-	&= \xi_{\alpha,\nu}^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u;\xi_{\alpha,\nu}/b) - \Gamma^+( k-2\alpha-u; \xi_{\alpha,\nu}/a) \right), 
-\end{align*}
-In particular
-\begin{equation}\label{eq:integral_Delta_P_z}
-	\int_0^1 z^{u+2\alpha-k-1} e^{-\xi_{\alpha,\nu} z^{-1}} \dd z = \xi_{\alpha,\nu}^{u+2\alpha-k} \Gamma^+(k-2\alpha-u;\xi_{\alpha,\nu})
-\end{equation}
-where $\Gamma^+$ denotes the (upper) incomplete gamma function, and we've used the subsitution
-$t = \xi_{\alpha,\nu} / z$ which gives $\dd z = -\xi_{\alpha, \nu} t^{-2} \dd t$. (And of course it is understood that 
-$\xi_{\alpha,\nu}/0 = \infty$). This takes care of the integrals of all terms in $\Delta_\Pcal(y(z))$ of the form $z^{u}$.
-
-Next we will consider the integrals over the terms in $\Delta_\Pcal(y(z))$ of the form $(1-z)^u$.
-For this we need the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which has the integral representation
-\[
-	U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} \dd t
-\] 
-which holds for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $Re(a), Re(z) >0$, see~\cite[p.255]{erdelyi1953higher}.
-Applying the change of variables $t=\frac{1-s}{s}$ (i.e.
-$\dd t = -s^{-2} \dd s$ and $s = \frac{1}{t+1}$) yields
-%yields the integral 
-%$\int_1^0 e^{-z(-1+\frac{1}{s})} (\frac{1-s}{s})^{a-1} (\frac{1}{s})^{b-a-1} (-s^2)ds = e^z\int_0^1 e^{-z/s} s^{-b}(1-s)^{a-1} ds$, i.e.
-\begin{align*}
-	U(a,b,z) = \frac{e^z}{\Gamma(a)} \int_0^1 s^{-b} (1-s)^{a-1} e^{-z/s} ds
-\end{align*}
-Plugging in $a=2\alpha+1 >0$, $b=-2\alpha+k+1$, $z=\xi_{\alpha,\nu}>0$, then gives
-\begin{equation}\label{eq:integral_Delta_P_1_z}
-	\int_0^1 z_0^{2\alpha-k-1} e^{-\xi_{\alpha,\nu}/z_0} (1-z_0)^{2\alpha} dz_0 = \Gamma(2\alpha+1)e^{-\xi_{\alpha,\nu}} U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu})
-\end{equation}
-
-Finally we need to deal with the terms in $\Delta_\Pcal(y(z))$ that involve the incomplete Beta-function.
-Let $a, c \in \R$, $\xi_{\alpha,\nu}, b >0$ positive real numbers.
-Using the integral definition of the incomplete B-function, the change of variables $s=1-t$ gives:
-\begin{align*}
-	\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} B^-(1-z;b,c) \dd z 
-	&=\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} \int_0^{1-z} t^{b-1} (1-t)^{c-1} \dd t \dd z \\
-	&=\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} \int_z^1 s^{c-1} (1-s)^{b-1} \dd s \dd z
-\end{align*}
-Then changing the order of integration and using the substitution $u = \xi_{\alpha,\nu}/z$  and recognizing the upper incomplete $\Gamma$-function yields
-\begin{align*}
-	&\hspace{-30pt}\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} \int_z^1 s^{c-1} (1-s)^{b-1} \dd s \dd z\\
-	&=\int_0^1 \int_0^s z^a e^{-\xi_{\alpha,\nu}/z} \dd z \, s^{c-1} (1-s)^{b-1} \dd s \\
-	&=\int_0^1 \int_{\xi_{\alpha,\nu}/s}^\infty \xi_{\alpha,\nu}^{a+1} u^{-a-2} e^{-u} \dd u \, s^{c-1} (1-s)^{b-1} \dd s \\
-	&= \xi_{\alpha,\nu}^{a+1} \int_0^1 \Gamma^+(-a-1,\xi_{\alpha,\nu}/s) s^{c-1} (1-s)^{b-1} \dd s.
-		\numberthis \label{eq:integral_gamma_function}
-\end{align*}
-To compute this last integral we make use of the fact that the incomplete $\Gamma$-function has a representation in terms of Meijer's $G$-function (see Lemma~\ref{lem:gamma_meijer_G} in Appendix~\ref{sec:Meijer_G_functions})
-\[
-	\Gamma^+(-a-1,\xi_{\alpha,\nu}/s) = \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi_{\alpha,\nu}}{s}},
-\] 
-which holds for any $a\in \R$ and $s>0$ (that for a fixed second argument, the upper incomplete $\Gamma$-function is entire in the first argument, see \cite[pp.
-899, 1032ff.]{gradshteyn2015table}).
-\PvdH{@Markus: What does entire mean?}
-We can now evaluate the integral in~\eqref{eq:integral_gamma_function} using several identities for Meijer's $G$-function. 
-%formula 8.351.3, p. 
- %(see the wolfram functions website \url{http://functions.wolfram.com/06.06.26.0005.01}, it can also be found in the paper \url{https://arxiv.org/pdf/1507.05571}; , so we get the integral
-First, inserting the expression for the incomplete Gamma-function into~\eqref{eq:integral_gamma_function} gives
-\begin{align*}
-	\xi_{\alpha,\nu}^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi_{\alpha,\nu}}{s}} \dd s
-\end{align*}
-Next we apply the inversion identity for Meijer's $G$-function (see \cite[p. 209, 5.3.1.(9))]{erdelyi1953higher}) to get
-\begin{align*}
-	\xi_{\alpha,\nu}^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{0}{2}{2}{1}{2+a,1}{0}{\frac{s}{\xi_{\alpha,\nu}}} \dd s
-\end{align*}
-This expression is actually the Euler transform of Meijer's $G$-function (see \cite[p.
-214, 5.5.2.(5)]{erdelyi1953higher}) and (as the conditions $2+1<2(0+2)$ and $|\arg(\xi_{\alpha,\nu}^{-1})| < \frac{\pi}{2}$ (as $\xi_{\alpha,\nu}>0$) and $1-c-b<1-c$ (as $b>0$)  are satisfied) it equals
-\begin{align*}
-	\xi_{\alpha,\nu}^{a+1} \Gamma(b) \MeijerG{0}{3}{3}{2}{1-c,2+a,1}{0,1-c-b}{\xi_{\alpha,\nu}^{-1}}
-\end{align*}
-Using again the inversion identity for Meijer's $G$-function we now get
-\begin{align*}
-	\xi_{\alpha,\nu}^{a+1} \Gamma(b) \MeijerG{3}{0}{2}{3}{1,b+c}{c,-1-a,0}{\xi_{\alpha,\nu}}
-\end{align*}
-Finally, plugging in $a= 6\alpha-k-3$, $b=2\alpha$, $c=3-4\alpha$ we obtain
-\begin{equation}\label{eq:integral_Delta_P_Beta}
-	\int_0^1 z^a e^{-\xi_{\alpha,\nu}/z} B^-(1-z;b,c) \dd z =
-	\xi_{\alpha,\nu}^{6a-k-2} \Gamma(2\alpha) \MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi_{\alpha,\nu}}
-\end{equation}
-%(note that this agrees with the result in the old approach, after `bringing the power of $\xi$ into Meijer's $G$-function'.)
-
-Using equation~\eqref{eq:integral_Delta_P_z}, \eqref{eq:integral_Delta_P_1_z} and~\eqref{eq:integral_Delta_P_Beta} we get
-\begin{align*}
-	I^{(k)}
-	&=\frac{\xi_{\alpha,\nu}^{2\alpha}}{4k!(\alpha-1)} \left( -\Gamma^+(k - 2 \alpha, \xi_{\alpha,\nu}) 
-		- 2\frac{\alpha (\alpha - 1/2)^2 \xi_{\alpha,\nu}^{2} \Gamma^+(k - 2 \alpha - 2, \xi_{\alpha,\nu})}{(\alpha - 1)} \right. \\ 
-	&\hspace{15pt}\left.+ 8 \alpha (\alpha - 1/2) \xi_{\alpha,\nu} \Gamma^+(k - 2 \alpha - 1,\xi_{\alpha,\nu}) \right.\\ 
-	&\hspace{15pt}\left.+ 4\xi_{\alpha,\nu}^{4\alpha - 2} 
-		\Gamma^+(k - 6 \alpha + 2, \xi_{\alpha,\nu}) \left( 
-		\frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
-	&\hspace{15pt}\left.+ \xi_{\alpha,\nu}^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi_{\alpha,\nu}} 	
-		U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu}) \right. \\ 
-	&\hspace{15pt}\left.- \xi_{\alpha,\nu}^{4\alpha-2} 
-		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi_{\alpha,\nu}}  \right)\\
-\end{align*}%{4\alpha-k+1,6\alpha-k-1}{6\alpha-k-2,2\alpha-k+1,0}
-
-With the expressions for $J$ and $I^{(k)}$ and using $\Gamma^\ast(q,z) = \Gamma^+(q+1,z) + \Gamma^+(q,z)$ we now obtain, after some algebra, the expression for $c_\Pcal$
-\begin{align*}
-	c_\Pcal &= J-I^{(0)}-I^{(1)} \\
-	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 
-	24 \alpha^5}{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} +  \frac{2^{-1 - 
-		4 \alpha}}{(\alpha - 1)^2} \\
-	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
-	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)} \\
-	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+( - 2 \alpha, \xi_{\alpha,\nu}) - 2\frac{\alpha (\alpha - 1/2)^2 \xi_{\alpha,\nu}^{2} \Gamma^+(- 2 \alpha - 2, \xi_{\alpha,\nu})}{(\alpha - 1)} \right.
-\\
-	&\hspace{10pt}\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi_{\alpha,\nu} \Gamma^+( - 2 \alpha - 1,\xi_{\alpha,\nu}) \right.\\ 
-	&\hspace{10pt}\hspace{10pt}\left.+ 4\xi_{\alpha,\nu}^{4\alpha - 2} \Gamma^+( - 6 \alpha + 2, 
-      \xi_{\alpha,\nu}) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
-	&\hspace{10pt}\hspace{10pt}\left.+ \xi_{\alpha,\nu}^{-2\alpha} \Gamma(2\alpha+1)e^{-\xi_{\alpha,\nu}} 
-		U(2\alpha+1,1-2\alpha,\xi_{\alpha,\nu}) \right. \\ 
-	&\hspace{10pt}\hspace{10pt}\left.- \xi_{\alpha,\nu}^{4\alpha-2} 
-		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi_{\alpha,\nu}}  \right) \\
-	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+(1 - 2 \alpha, \xi_{\alpha,\nu}) - 
-		2\frac{\alpha (\alpha - 1/2)^2 \xi_{\alpha,\nu}^{2} \Gamma^+( - 2 \alpha - 1, \xi_{\alpha,\nu})}{(\alpha - 1)} \right. \\ 
-	&\hspace{10pt}\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi_{\alpha,\nu} \Gamma^+(1 - 2 \alpha - 1,\xi_{\alpha,\nu}) 
-		\right.\\ 
-	&\hspace{10pt}\hspace{10pt}\left.+ 4\xi_{\alpha,\nu}^{4\alpha - 2} \Gamma^+(1 - 6 \alpha + 2, 
-    	\xi_{\alpha,\nu}) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
-	&\hspace{10pt}\hspace{10pt}\left.+ \xi_{\alpha,\nu}^{1-2\alpha} \Gamma(2\alpha+1)e^{-\xi_{\alpha,\nu}} 
-		U(2\alpha+1,2-2\alpha,\xi_{\alpha,\nu}) \right. \\ 
-	&\hspace{10pt}\hspace{10pt}\left.- \xi_{\alpha,\nu}^{4\alpha-2} 
-		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi_{\alpha,\nu}}  \right)\\
-	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}
-		{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} 
-		+  \frac{2^{-1 - 4 \alpha}}{(\alpha - 1)^2} \\
-	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}
-		{2 (\alpha - 1) (3 \alpha - 1)} \\
-	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{2\alpha} \Gamma^\ast( - 2 \alpha, \xi_{\alpha,\nu})}{4(\alpha-1)}
-		+ \frac{\xi_{\alpha,\nu}^{2\alpha + 2}\alpha (\alpha - 1/2)^2 \Gamma^\ast(- 2 \alpha - 2, \xi_{\alpha,\nu})}
-		{2(\alpha-1)^2} \\
-	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{2\alpha + 1}\alpha (2\alpha - 1) \Gamma^\ast( - 2 \alpha - 1,\xi_{\alpha,\nu})}{(\alpha-1)}
-		- \frac{\xi_{\alpha,\nu}^{6\alpha-2}2^{-4\alpha}(3\alpha - 1)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)^2}\\
-	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{6\alpha - 2}(\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)} \\
-	&\hspace{10pt}- \frac{e^{-\xi_{\alpha,\nu}} \Gamma(2\alpha+1) 
-		\left(U(2\alpha+1,1-2\alpha,\xi_{\alpha,\nu}) + U(2\alpha+1,2-2\alpha,\xi_{\alpha,\nu})\right)}{4(\alpha-1)} \\
-	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{6\alpha - 2} \Gamma(2\alpha+1)\left( 	
-		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi_{\alpha,\nu}}
-		+ \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi_{\alpha,\nu}}\right)}{4(\alpha-1)}.
-\end{align*}
-and note that this equals $c_\infty$ in Theorem~\ref{thm:clustering_coefficient_hyperbolic} when $\alpha \ne 1$.
-
-Similarly, we get
-\begin{align*}
-	c_\Pcal(k) &= \frac{I^{(k)}}{\rho(k)} \\
-	&=\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) 
-		- 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
-	&\hspace{10pt}\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
-	&\hspace{10pt}\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
-      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
-	&\hspace{10pt}\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
-	&\hspace{10pt}\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right),
-\end{align*}
-which equals $c_\infty(k)$ in Theorem~\ref{thm:local_clustering_hyperbolic} when $\alpha \ne 1$.
-
-Finally, to determine the value of $c_\Pcal$ and $c_\Pcal(k)$ for $\alpha=1$, it suffices to find the value of $J$ and $I^{(k)}$ at $\alpha = 1$.
-We can do this by computing the integrals with the expression for $\Delta_\Pcal(y)$ that we found for $\alpha=1$, i.e.
+\begin{proofof}{Proposition~\ref{prop:gammaais1}}
+It suffices to find the value of $J$ and $I^{(k)}$ 
+at $\alpha = 1$. We can do this by computing the integrals with the expression for $P(y)$ that we found for $\alpha=1$, i.e.
 \begin{align*}
@@
 \begin{align*}
-	I^{(k)} &= \frac{2\alpha \xi_{\alpha,\nu}^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
-		- \frac{7+\pi^2}{8}	z^2  + \frac{1}{2}z^2 \Li_2(z) \right)z^{2\alpha-k-1} e^{-\xi_{\alpha,\nu}/z} \dd z \\
+	I^{(k)} &= \frac{2\alpha \xi^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
+		- \frac{7+\pi^2}{8}	z^2  + \frac{1}{2}z^2 \Li_2(z) \right)z^{2\alpha-k-1} e^{-\xi/z} \dd z \\
 	&= \frac{2 \eta^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
@@
 where $\eta = \frac{4\nu}{\pi}$ and and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function. 
-Plugging this into the definitions for $c_\Pcal$ and $c_\Pcal(k)$ yields the expressions $c_\infty$ in Theorem~\ref{thm:clustering_coefficient_hyperbolic} and $c_{\infty}(k)$ in Theorem~\ref{thm:local_clustering_hyperbolic}, respectively.
+Plugging this into ~\eqref{eq:gammaint} and~\eqref{eq:gammakint} yields the expressions in the statement of the proposition.
+\end{proofof}
+
+\subsection{The proof of Proposition~\ref{prop:asymp}\label{ssec:asymptotics_local_clustering_P}}
+
+Recall that
+\[
+	\gamma(k) = \frac{\int_0^\infty \rho(y,k) P(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
+\]
+The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
+\[
+	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
+\]
+and in particular the function $P(y)$.
+We therefore start with establishes the asymptotic behavior of the latter.
+First we combine~\eqref{eq:degree_distribution_P_asymptotics} and~\eqref{eq:general_integral_rho_y_k} to obtain the following scaling result
+\begin{equation}\label{eq:general_clustering_integral_scaling}
+	\frac{\int_0^\infty e^{-\beta y} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	\sim \xi_{\alpha, \nu}^{2\beta} k^{-2\beta}.
+\end{equation}
+
+%\TM{ Here we need a properly spelled out proof of the proposition. (Which Pim was preparing I believe.)}
+
+\begin{proposition}[Asymptotic behavior of $P(y)$]\label{prop:asymptotics_P}
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $c_\alpha$ as defined in Proposition~\ref{prop:asymp} Then, as $y \to \infty$, 
+\begin{enumerate}
+\item for $\frac{1}{2} < \alpha < \frac{3}{4}$,
+\[
+	\Delta_{\Pcal}(y) \sim e^{-\frac{y}{2}(4\alpha - 2)} c_\alpha,
+\]
+\item for $\alpha = \frac{3}{4}$,
+\[
+	\Delta_\Pcal(y) \sim \frac{y}{2} e^{-\frac{y}{2}},
+\]
+\item and for $\alpha > \frac{3}{4}$,
+\[
+	\Delta_{\Pcal}(y) \sim e^{-\frac{y}{2}} \frac{4\alpha - 3}{4(\alpha - 1)}.
+\]
+\end{enumerate}
+\end{proposition}
+
+\begin{proof}
+We shall deal with each of the three cases for $\alpha$ separately.
+
+\paragraph{Proof for \bm{$1/2 < \alpha < 3/4$}}
+By Lemme~\ref{lem:Paneq1} we get that
+\begin{align*}
+	e^{(4\alpha - 2)\frac{y}{2}}P(y) &= \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
+		+ \frac{(\alpha - \frac{1}{2} ) B^-(\frac{1}{2}; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha}
+		- \frac{B^-(1-e^{-\frac{y}{2}}; 2\alpha, 3-4\alpha)}{4(\alpha - 1)} \\
+	&\hspace{10pt}+ \frac{e^{(4\alpha - 2)\frac{y}{2}}}{8(\alpha-1)\alpha}\left((1 - e^{-\frac{y}{2}})^{2\alpha} - 1\right)
+		+ \frac{\alpha-\frac{1}{2}}{\alpha-1} e^{(4\alpha-3)\frac{y}{2}}
+		- \frac{(\alpha - \frac{1}{2})^2}{4(\alpha-1)^2} e^{4(\alpha-1)\frac{y}{2}}.
+\end{align*}
+Because for any $b < 1$, $B^-(1-z,a,b)$ converges to $B^-(a,b) < \infty$ as $z \to 0$, we get that as $y \to \infty$, the first line is asymptotically equivalent to
+\[,
+	\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
+			+ \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha}
+			- \frac{B(2\alpha, 3-4\alpha)}{4(\alpha - 1)} = c_\alpha,
+\]
+as defined in Theorem~\eqref{thm:mainktoinfty}. The proof now follows since for $1/2 < \alpha < 3/4$, the remaining three terms go to zero as $y \to \infty$.
+
+\paragraph{Proof for \bm{$\alpha = 3/4$}}
+
+Similar to the previous case we use Lemma~\ref{lem:Paneq1} to obtain
+\begin{align*}
+	\frac{2}{y} e^{\frac{y}{2}}P(y) 
+	&= \frac{2}{y}\frac{B^-(1-e^{-\frac{y}{2}}, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)}\\
+	&\hspace{10pt} + \frac{2}{y}\frac{e^{\frac{y}{2}}\left((1 - e^{-\frac{y}{2}})^{2\alpha} - 1\right)}{8(\alpha - 1)\alpha}
+		+ \frac{(\alpha - \frac{1}{2})}{(\alpha - 1)y} 
+		-\frac{(\alpha - \frac{1}{2})^2 e^{-\frac{y}{2}}}{4(\alpha - 1)^2 y} \\
+	&\hspace{10pt}+ \frac{2}{y} 
+		\left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
+		+ \frac{(\alpha - \frac{1}{2}) B^-(\frac{1}{2}; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right)
+\end{align*}
+First we note that as $y \to \infty$,
+\begin{equation}\label{eq:asymptotics_Delta_P_auxiliary}
+	e^{\frac{y}{2}}\left(\left(1 - e^{-\frac{y}{2}}\right)^{2\alpha}-1\right) 
+	\sim -2\alpha,
+\end{equation}
+which implies that
+\[
+	\lim_{y \to \infty} \frac{2}{y}\frac{e^{\frac{y}{2}}\left((1 - e^{-\frac{y}{2}})^{2\alpha} - 1\right)}{8(\alpha - 1)\alpha} = 0.
+\]
+It can now conclude that all terms in $\frac{2}{y} e^{\frac{y}{2}}\Delta_{\Pcal}(y)$ except the first one are $\smallO{1}$ as $y \to \infty$.
+By writing $z = e^{-\frac{y}{2}}$ we can rewrite this term as
+\[
+	\frac{2}{y}\frac{B^-(1-e^{-\frac{y}{2}}, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)} 
+	= -\frac{1}{\log(z)}\frac{B^-(1-z, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)}.
+\]
+Since $B^-(1-z,2\alpha,0) \sim - \log(z)$ as $z \to \infty$, see Lemma~\ref{lem:asymptotics_incomplete_beta}, it now follows
+that for $\alpha = 3/4$,
+\[
+	\lim_{y \to \infty} \frac{2}{y}\frac{B^-(1-e^{-\frac{y}{2}}, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)}
+	= \lim_{z \to 0} -\frac{1}{\log(z)}\frac{B^-(1-z, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)} = 1.
+\]
+We therefore conclude that
+\[
+	\frac{2}{y}e^{\frac{y}{2}}P(y) \sim \frac{y}{2} e^{-\frac{y}{2}},
+\]
+as $y \to \infty$.
+
+\paragraph{Proof for \bm{$\alpha > 3/4$}}
+We first deal with the case $\alpha = 1$. Here it follows from Proposition~\ref{prop:gammaais1} that
+\begin{align*}
+	e^{y/2}P(y) &= \frac{9}{4} + \frac{e^{y/2}\log(1-e^{-y/2})}{4} \\
+	&\hspace{10pt}-\log(1-e^{-y/2}) + e^{-y/2}\left(\frac{3}{4}\log(1-e^{-y/2}) - \frac{7 + \pi^2}{8} + 	
+		\frac{1}{2}\mathrm{Li}_2(e^{-y})\right) \\
+	&= 2 + \left(\frac{e^{y/2}\log(1-e^{-y/2})}{4} + 1\right)\\
+	&\hspace{10pt}-\log(1-e^{-y/2}) + e^{-y/2}\left(\frac{3}{4}\log(1-e^{-y/2}) - \frac{7 + \pi^2}{8} + 	
+		\frac{1}{2}\mathrm{Li}_2(e^{-y})\right)
+\end{align*}
+
+Now we will proof all other cases with $\alpha > 3/4$. For simplicity we write
+\[
+	Q_\alpha := \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
+		+ \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha}.
+\]
+Then, by Lemma~\ref{lem:Paneq1} we get
+\begin{align*}
+	e^{y/2} P(y) &= \frac{\alpha - \frac{1}{2}}{\alpha - 1} 
+		+ \frac{e^{\frac{y}{2}}}{8(\alpha - 1)\alpha}\left(\left(1 - e^{-\frac{y}{2}}\right)^{2\alpha}-1\right)\\
+	&\hspace{10pt}- e^{-(4\alpha - 3)\frac{y}{2}}\frac{B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}\\
+	&\hspace{10pt}+ e^{-(4\alpha - 3)\frac{y}{2}}Q_\alpha + \frac{(\alpha-\frac{1}{2})^2}{4(\alpha-1)^2} e^{-\frac{y}{2}}.
+\end{align*}
+The first term is constant while the last two terms go to zero as $y \to \infty$. We will therefore focus on the remain two terms. For the first we have, see~\eqref{eq:asymptotics_Delta_P_auxiliary} 
+\[
+	\frac{e^{\frac{y}{2}}}{8(\alpha - 1)\alpha}\left(\left(1 - e^{-\frac{y}{2}}\right)^{2\alpha}-1\right) 
+	\sim \frac{-2\alpha}{8(\alpha - 1)\alpha} = -\frac{1}{4(\alpha -1)},
+\]
+as $y \to \infty$. Finally, writing $z = e^{-\frac{y}{2}}$ we get that
+\[
+	e^{-(4\alpha - 3)\frac{y}{2}} B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)
+	= z^{4\alpha - 3} B^-(1 - z, 2 \alpha, 3 - 4 \alpha).
+\]
+Therefore it follows, see Lemma~\ref{lem:asymptotics_incomplete_beta}, that
+\[
+	\lim_{y \to \infty} - e^{-(4\alpha - 3)\frac{y}{2}}
+		\frac{B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
+	= \lim_{z \to 0} z^{4\alpha - 3} \frac{B^-(1 - z, 2 \alpha, 3 - 4 \alpha)}{4(\alpha - 1)}
+	= \frac{1}{4(\alpha - 1)(4\alpha - 3)}.
+\]
+We conclude that as $y \to \infty$
+\begin{align*}
+	e^{y/2} P(y) 
+	&\sim \frac{\alpha - \frac{1}{2}}{\alpha - 1} -\frac{1}{4(\alpha -1)} - \frac{1}{4(\alpha - 1)(4\alpha - 3)}
+	= \frac{1 - 3\alpha + 2 \alpha^2}{(\alpha - 1)(\alpha - \frac{3}{4})} 
+	= \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}},
+\end{align*}
+which finishes the proof.
+\end{proof}
+
+With the asymptotic behavior of $P(y)$ we are almost ready to prove Proposition~\ref{prop:asymp}.
+First we will prove a result that will allow us to limit the values of $y$, when performing the integration.
+For this, fix some $C > 0$ and define
+\[
+	a(k)^\pm = 2 \log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
+\] 
+We will prove that, as $k \to \infty$,
+\begin{equation}\label{eq:asymptotics_average_clustering_concentration}
+	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	= (1+\smallO{1}) \int_{a(k)^-}^{a(k)^+} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y.
+\end{equation}
+Note that this implies that for any bounded function $\varphi(y)$ satisfying $\lim_{y \to \infty} |\phi(y)| = 0$,
+\begin{equation}\label{eq:asymptotics_average_clustering_error_term}
+	\int_0^\infty \varphi(y) P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	= \smallO{1} \int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y.
+\end{equation}
+
+To establish~\eqref{eq:asymptotics_average_clustering_concentration} recall that $\mu(y) = \xi e^{\frac{y}{2}}$ and consider $\rho(y,k)$ as a function of $y$.
+Then, since $\mu^\prime(y) = \mu(y)/2$, we get that
+\[
+	\frac{\partial \rho}{\partial y} = \frac{1}{2}\left(k - \mu(y)\right)\rho(y,k),
+\]
+which implies that $\rho(y,k)$ attains its maximum at $\mu(y) = k$.
+Moreover we see that the derivative is strictly positive when $\mu(y) < k$ and strictly negative when $\mu(k) > k$.
+Since $\mu(a(k)^- < k$ and $\mu(a(k)^+) > k$, we conclude that $\rho(y,k)$, as a function of $y$, is strictly increasing on $[0,a(k)^-]$ and strictly decreasing on $[a(k)^+,\infty)$.
+Hence, using that $P(y) \le 1$,
+\begin{align*}
+	&\hspace{-20pt}\int_{\R_+ \setminus [a(k)^-, a(k)^+]} P(y) \rho(y,k) 
+		\alpha e^{-\alpha y} \dd y\\
+    &\le \int_0^{a(k)^-} \rho(y,k) \alpha e^{-\alpha y} \dd y 
+    	+ \int_{a(k)^+}^{\infty}\rho(y,k) \alpha e^{-\alpha y}x \dd y \\
+   	&\le \rho(a(k)^-,k)\int_0^{a(k)^-} e^{-\alpha y} \, \dd y
+   		+ \rho(a(k)^+,k) \int_{a(k)^+}^{\infty} e^{-\alpha y} \, \dd y\\
+   	&= \bigO{1}\left(\rho(a(k)^-,k) + \rho(a(k)^+,k)\right),
+\end{align*}
+as $k \to \infty$. We will show that
+\[
+	\rho(a(k)^\pm,k) = \bigO{k^{-(1+C^2)/2}}.
+\]
+Since the arguments are almost completely identical, we give the prove for $a(k)^+$.
+
+Using Stirling's formula $k! \sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
+\begin{align*}
+	\rho(a_k^+,k) &= \frac{\mu(a_k^+)^{k}}{k!} e^{-\mu(a_k^+)} \\
+	&\sim (2\pi)^{-1/2} k^{-1/2} \left(\frac{\mu(a(k)^+}{k}\right)^{k} e^{-(\mu(a(k)^+ - k)}\\
+	&= (2\pi)^{-1/2} k^{-1/2} 
+		e^{-k\left(\frac{\mu(a_k^+)}{k} - 1 - \log\left(\frac{\mu(a_k^+)}{k}\right)\right)}.
+\end{align*}
+Since 
+\[
+	\frac{\mu(a_k^+)}{k} = 1 + C \sqrt{\frac{\log(k)}{k}}
+\]
+and $x - \log(1 + x) \sim x^2/2$ as $x \to 0$, we get 
+\begin{align*}
+	\rho(a_k^+,k) 
+	&\sim \sqrt{2\pi} k^{-1/2} 
+		e^{-k \left(C \sqrt{\frac{\log(k)}{k}} - \log\left(1 + C \sqrt{\frac{\log(k)}{k}}\right)\right)}\\
+	&\sim (2\pi)^{-1/2} k^{-1/2} e^{-\frac{k \left(C \sqrt{\frac{\log(k)}{k}}\right)^2}{2}} \\
+	&= \bigO{k^{-(1+C^2)/2}}.
+\end{align*}
+
+Since $C > 0$ can be chosen arbitrarily large we conclude that
+\[
+	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	= (1+\smallO{1}) \int_{a^-(k)}^{a^+(k)} \Delta_{\Pcal}(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
+\]
+as $k \to \infty$.
+
+We now proceed with the proof of Proposition~\ref{prop:asymptotics_P}, which is split over the different cases for $\alpha$.
+
+\paragraph{Proof when \bm{$1/2 < \alpha < 3/4$}}
+By Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} it is enough to show that
+\[
+	\frac{\int_0^{\infty} e^{-(4\alpha - 2)y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+	{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
+	\sim \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2}.
+\]
+This follows immediately from~\eqref{eq:general_clustering_integral_scaling} with $\beta = 2\alpha - 1$.
+
+\paragraph{Proof when \bm{$\alpha = 3/4$}}
+Similar to the previous case Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} imply that it is enough to show that
+\[
+	\frac{\int_0^{\infty} P(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+	{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y}
+	\sim \xi_{\alpha,\nu} \log(k) k^{-1},
+\]
+This does not follow immediately from~\eqref{eq:general_clustering_integral_scaling} because of the additional logarithmic term. To establish the above result we first show that
+\begin{equation}\label{eq:average_clustering_proof_34_main}
+	\int_{a(k)^-}^{a(k)^+} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	\sim \log(k) \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y.
+\end{equation}
+For this we establish an upper bound for the left hand side
+\begin{align*}
+	\int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+	&\le \frac{a(k)^+}{2} \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+\end{align*}
+and similarly, a lower bound
+\begin{align*}
+	\int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+	&\ge \frac{a(k)^-}{2} \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+\end{align*}
+Now observe that
+\[
+	\frac{a^\pm(k)}{2} = \log\left(\frac{k \pm \sqrt{k\log(k)}}{\xi_{\alpha, \nu}}\right) \sim \log(k)
+\]
+and therefore it follows that
+\[
+	\limsup_{k \to \infty} \frac{\int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\log(k) \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \le 1.
+\]
+and
+\[
+	\liminf_{k \to \infty} \frac{\int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\log(k) \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \ge 1.
+\]
+This proofs~\eqref{eq:average_clustering_proof_34_main}.
+
+Next we note that by~\eqref{eq:general_clustering_integral_scaling} with $\beta = 1/2$ we have
+\[
+	\frac{\int_0^\infty e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	\sim \xi_{\alpha, \nu}k^{-1}.
+\]
+Therefore, since by~\eqref{eq:asymptotics_average_clustering_concentration},
+\[
+	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y \sim \int_{a(k)^-}^{a(k)^+} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+\]
+it follows from~\eqref{eq:average_clustering_proof_34_main} that
+\begin{align*}
+	\frac{\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y}
+		{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	&\sim \log(k) \frac{\int_0^\infty e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}\\
+	&\sim \xi_{\alpha, \nu}\log(k)k^{-1},
+\end{align*}
+which finishes the proof for this case.
+
+\paragraph{Proof when \bm{$\alpha > 3/4$}}
+
+Again, by Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} it is enough to show that
+\[
+	\frac{\int_0^{\infty} e^{-y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+	{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} 
+	\sim \xi_{\alpha,\nu} k^{-1},
+\]
+which follows from~\eqref{eq:general_clustering_integral_scaling} with $\beta = 1/2$.
+
+% %\begin{lemma}\label{lem:expectation_clustering_P}
+% %Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then
+% %\[
+% %	\Exp{c_{\Pcal}^\ast(k)} = \frac{\int_0^{\infty} P(y) \, 
+% %	\rho_{y}(k) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) 
+% %	e^{-\alpha y} \, dy}.
+% %\]
+% %\end{lemma}
+% %
+% %\begin{proof}
+% %By the Palm-Mecke formula, we have
+% %\begin{align*}
+% %	\Exp{c_{\Pcal}^\ast(k)} &= \frac{1}{\Exp{N_\Pcal(k)}}
+% %		\int_0^{\infty} \int_{-\infty}^{\infty} \Exp{\frac{\ind{D_{\Pcal}(p) = k}}{\binom{k}{2}} \sum_{(p_1, p_2) \in \Pcal} T(p,p_1,p_2)} f_{\alpha,\nu}(x,y) \, dx \, dy\\
+% %	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} \int_{-\infty}^{\infty} \binom{k}{2}^{-1}
+% %		P(p,k)\CProb{D_\Pcal(p) = k}{p} f_{\alpha,\nu}(x,y) \, dx \, dy.
+% %\end{align*}
+% %Conditioned on the Poisson process $\Pcal$ having $k$ points in $B(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$ with probability  distribution $\eta_{p} = \frac{\mu|_{B(p)}}{\mu(B(p))}$.
+Therefore we have
+% %\[
+% %	P(p,k) = \binom{k}{2} T_\Pcal(p),
+% %\]
+% %and hence, since the entire expression inside the integral does not depend on $x$,
+% %\begin{align*}
+% %	\Exp{c_{\Gamma, n}^\ast(k)} 
+% %	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} P(y) \rho_{\mu, y}(k) e^{-\alpha y} \, dy.
+% %\end{align*}
+% %Finally, we note that
+% %\begin{align*}
+% %	\Exp{N_\Pcal(k)} &= \Exp{\sum_{p \in \Pcal} \ind{D_\Pcal(p) = k}}
+% %	= \int_0^{\infty}\int_{-\infty}^\infty \rho_{\mu, p}(k) f_{\alpha,\nu}(x,y) \, dx \, dy
+% %	= \int_0^{\infty} \rho_{\mu, y}(k) e^{-\alpha y} \, dy
+% %\end{align*}
+% %which completes the proof.
+% %\end{proof}
+% 
+% Recall that
+% \[
+% 	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) P(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
+% \]
+% The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
+% \[
+% 	\int_0^{\infty} P(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
+% \]
+% and in particular the function $P(y)$. The following result establishes the asymptotic behavior of the latter.
+% 
+% \begin{proposition}[Asymptotic behavior of $P(y)$]\label{prop:asymptotics_Delta_y_P}
+% Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}.
+Then there are three, eventually decreasing, functions $\varphi_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
+% \[
+% 	\lim_{y \to \infty} \varphi_i(y) = 0, 
+% \]
+% such that 
+% \begin{enumerate}
+% \item for $\frac{1}{2} < \alpha < \frac{3}{4}$,
+% \[
+% 	P(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varphi_1(y)),
+% \]
+% \item for $\alpha = \frac{3}{4}$,
+% \[
+% 	P(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varphi_2(y)),
+% \]
+% \item and for $\alpha > \frac{3}{4}$,
+% \[
+% 	P(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varphi_3(y)).
+% \]
+% \end{enumerate}
+% \end{proposition}
+% 
+% The proof of this proposition is involved and technical. 
+% We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} \TM{ It is not in section 4.3!!!!
+IN fact I cannot find it in sec 4 alltogether.
+Please fix.
+We do need this worked out explicitly in the paper.
+} and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.
+% 
+% 
+% \begin{proof}[Proof of Theorem \ref{thm:asymptotics_average_clustering_P}]
+% 
+% We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$.
+\TM{ not sure I am happy with this "other cases are similar" approach.
+Especially in a 100 page paper.
+The devil is in the details!
+} The proofs for the other two cases are similar.
+Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
+% \[
+% 	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y
+% \]
+% Then we have that
+% \[
+% 	\int_0^{\infty} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+% 	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y + \epsilon_1(k).
+% \]
+% 
+% Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields,
+% \begin{equation}\label{eq:asymptotics_clustering_integral}
+% 	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y 
+% 	\sim 2\alpha \xi^{6\alpha - 2} k^{-(6\alpha - 1)},
+% \end{equation}
+% as $k \to \infty$. Therefore, by applying the asymptotic scaling for the denominator~\eqref{eq:degree_distribution_P_asymptotics} we get
+% \begin{align*}
+% 	c_\infty(k) &= \frac{\int_0^{\infty} P(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+% 		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
+% 	&\sim C_\alpha 2\alpha \xi^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
+% 	+ \frac{\epsilon_1(k)}{2\alpha \xi^{2\alpha} k^{-(2\alpha - 1)}}\\
+% 	&= C_\alpha 2\alpha \xi^{4\alpha - 2} k^{-4\alpha + 2} 
+%     + \frac{1}{2\alpha}\xi^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
+% \end{align*}
+% Hence, to prove the result it is enough to show that
+% \[
+% 	\lim_{k \to \infty} k^{6\alpha - 3}\epsilon_1(k) = 0.
+% \]
+% For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ \TM{ should there not be a $k/\xi$ inside $\log$ here? (see below) } and split the integral into two pieces
+% \begin{align*}
+% 	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
+% 	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
+% 	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
+%     	\rho(y,k) \alpha e^{-\alpha y} \dd y.
+% \end{align*} 
+% For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ \TM{ I think that is only true if we change the def as above, in accordance with $a^{\pm}$ earlier. } and
+% \[
+% 	k^{6\alpha - 3}\rho(a(k),k) = O\left(\frac{k^{6\alpha - 3 + (1-\varphi)k}}{k!} e^{-(1-\varphi)k}\right) = o(1),
+% \]
+% \TM{ again, it seems off. I think we need to take $\xi$ into account here. }
+% to obtain
+% \begin{align*}
+% 	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
+%     	\rho(y,k) \alpha e^{-\alpha y} \dd y\\
+% 	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
+%     	\rho(a(k), k) \int_0^\infty \alpha e^{-\alpha y} \dd y = 0.
+% \end{align*}
+% For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
+% \[
+% 	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
+% \] 
+% Therefore, using that $\varphi_1(y)$ is eventually decreasing and $\lim_{k \to \infty} \varphi_1(a(k)) = 0$, we obtain
+% \begin{align*}
+% 	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
+%     	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
+% 	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
+%     	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = 0,
+% \end{align*}
+% which finishes the proof. \TM{ PLease elaborate on last line. What is used here? }
+% \end{proof}

### 2019-02-05 concentration.tex
updated notation and added comments to sections 1-3

@@
-\section{Concentration for $c_{\Pcal, n}(k)$ (Proving Proposition \ref{prop:concentration_local_clustering_P_n})}
+\section{Concentration for $c(k; \Gbox)$ (Proving Proposition \ref{prop:concentration_local_clustering_P_n})}
 \label{sec:concentration_c_P_n}
 
-In this section we establish a concentration result for the local clustering function $c_{\Pcal, n}^\ast(k)$ in the finite model $G_{\Pcal,n}$.
-Similar to the previous section we will focus on those nodes $p = (x,y) \in \Kcal_{C}(k_n)$.
+In this section we establish a concentration result for the local clustering function $c^\ast(k; \Gbox)$ in the finite model $\Gbox$.
+Similar to the previous section we will focus on typical points $p = (0,y)$ with $y \in \Kcal_{C}(k_n)$.
 
@@
 \[
-	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal_n}.
+	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal}.
 \]
@@
 \[
-	\Kcal_C(k_n) = \left\{p \in \R : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
-		\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \wedge e^{R_n/2} \right\},
+	\Kcal_C(k_n,n) = \left\{p \in \Rcal : \frac{k_n - C \kappa_n}{\xi} \vee 0 \le e^{\frac{y}{2}}
+		\le \frac{k_n + C \kappa_n}{\xi} \right\},
 \]
@@
 \[
-	\kappa_n := \begin{cases}
-		\log(n) &\mbox{if } k_n = \bigT{1},\\
-		\sqrt{k_n \log(k_n)} &\mbox{else.}
-	\end{cases}
+	\kappa_n = \sqrt{k_n \log(k_n)}.
 \]
@@
 \begin{equation}\label{eq:def_degree_triangle_count_in_K}
-	\widetilde{T}_{\Pcal,n}(k, C) = \sum_{p \in \Pcal_n \cap K_C(k)} \ind{D_{\Pcal,n}(p) = k} \widetilde{T}_{\Pcal,n}(p),
+	\widetilde{T}_{\Pcal,n}(k, C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\Pcal,n}(p),
 \end{equation}
@@
 \[
-	\widetilde{T}_{\Pcal,n}(p) := \sum_{(p_1, p_2) \in \Pcal\setminus (0,y)}^{\ne} \widetilde{T}_{\Pcal,n}(p,p_1,p_2),
-\]
-where the sum is over all distinct pairs $(p_1, p_2) \in \Pcal \setminus \{(0,y)\}$.
+	\widetilde{T}_{\Pcal,n}(p) := \sum_{(p_1, p_2) \in \Pcal \setminus p}^{\ne} \widetilde{T}_{\Pcal,n}(p,p_1,p_2),
+\]
+where the sum is over all distinct pairs $(p_1, p_2) \in \Pcal \setminus p$.
 
@@
 %\[
-%	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
+%	\Exp{\left|c^\ast(k_n; \Gbox) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
 %\]
@@
 %\begin{align*}
-%	A_n &= \left\{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| \le \Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}\right\}\\
-%	B_n &= \left\{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| \le n\right\},
+%	A_n &= \left\{\left|N_{\text{box}}(k_n) - \Exp{N_{\text{box}}(k_n)}\right| \le \Exp{N_{\text{box}}(k_n)}^{\frac{1 + \delta}{2}}\right\}\\
+%	B_n &= \left\{\left|N_{\text{box}}(k_n) - \Exp{N_{\text{box}}(k_n)}\right| \le n\right\},
 %\end{align*}
@@
 %\[
-%	\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right| 
-%	\le \frac{\Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}}{\Exp{N_{\Pcal,n}(k_n)}+\Exp{N_{\Pcal,n}(k_n)}^{\frac{1 + \delta}{2}}}
-%	\le \Exp{N_{\Pcal,n}(k_n)}^{-\frac{1 - \delta}{2}},
+%	\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right| 
+%	\le \frac{\Exp{N_{\text{box}}(k_n)}^{\frac{1 + \delta}{2}}}{\Exp{N_{\text{box}}(k_n)}+\Exp{N_{\text{box}}(k_n)}^{\frac{1 + \delta}{2}}}
+%	\le \Exp{N_{\text{box}}(k_n)}^{-\frac{1 - \delta}{2}},
 %\]
@@
 %\[
-%	\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right| 
-%	\le \frac{n}{\Exp{N_{\Pcal,n}(k_n)} + n} \le 1.
+%	\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right| 
+%	\le \frac{n}{\Exp{N_{\text{box}}(k_n)} + n} \le 1.
 %\]
@@
 %\begin{align*}
-%	\Exp{\left|c_{\Pcal, n}^\ast(k_n) - c_{\Pcal, n}(k_n)\right|}
-%	&= \Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|}\\
-%	&\le \Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n}}\Exp{N_{\Pcal,n}(k_n)}^{-\frac{1 - \delta}{2}} \\
-%	&\hspace{10pt}+ \Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}} \\
-%	&\hspace{10pt}+ \Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|\ind{B_n^c}}
-%\end{align*}
-%Since $\Exp{N_{\Pcal,n}(k_n)} \to \infty$, the first term is clearly $\smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}$. For the third term we have
-%\begin{align*}
-%	\Exp{c_{\Pcal, n}^\ast(k_n)\left|\frac{\Exp{N_{\Pcal,n}(k_n)}}{N_{\Pcal,n}(k_n)} - 1\right|\ind{B_n^c}} 
+%	\Exp{\left|c^\ast(k_n; \Gbox) - c_{\Pcal, n}(k_n)\right|}
+%	&= \Exp{c^\ast(k_n; \Gbox)\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right|}\\
+%	&\le \Exp{c^\ast(k_n; \Gbox)\ind{A_n}}\Exp{N_{\text{box}}(k_n)}^{-\frac{1 - \delta}{2}} \\
+%	&\hspace{10pt}+ \Exp{c^\ast(k_n; \Gbox)\ind{A_n^c}\ind{B_n}} \\
+%	&\hspace{10pt}+ \Exp{c^\ast(k_n; \Gbox)\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right|\ind{B_n^c}}
+%\end{align*}
+%Since $\Exp{N_{\text{box}}(k_n)} \to \infty$, the first term is clearly $\smallO{\Exp{c^\ast(k_n; \Gbox)}}$. For the third term we have
+%\begin{align*}
+%	\Exp{c^\ast(k_n; \Gbox)\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right|\ind{B_n^c}} 
 %	&= \bigO{\Prob{B_n^c}}
-%		= \bigO{\Prob{\left|N_{\Pcal,n}(k_n) - \Exp{N_{\Pcal,n}(k_n)}\right| > n}}\\
-%	&= \bigO{e^{-\frac{n^2}{\Exp{N_{k_n}} + n}}} = \bigO{e^{-n}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
+%		= \bigO{\Prob{\left|N_{\text{box}}(k_n) - \Exp{N_{\text{box}}(k_n)}\right| > n}}\\
+%	&= \bigO{e^{-\frac{n^2}{\Exp{N_{k_n}} + n}}} = \bigO{e^{-n}} = \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
 %\end{align*}
@@
 %\begin{equation}\label{eq:L1_convergence_second_term}
-%	\Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
+%	\Exp{c^\ast(k_n; \Gbox)\ind{A_n^c}\ind{B_n}} = \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
 %\end{equation}
@@
 %\begin{align*}
-%	c_{\Pcal, n}^\ast(k_n) = \frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-%	+ \frac{T_{\Pcal,n}(k_n,\varepsilon)- \widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
+%	c^\ast(k_n; \Gbox) = \frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+%	+ \frac{T_{\Pcal,n}(k_n,\varepsilon)- \widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
 %\end{align*}
@@
 %\begin{align*}
-%	\Exp{c_{\Pcal, n}^\ast(k_n)\ind{A_n^c}\ind{B_n}}
-%	&\le \Exp{\frac{(1+\smallO{1})\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-%		\ind{A_n^c}} + \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}}.
+%	\Exp{c^\ast(k_n; \Gbox)\ind{A_n^c}\ind{B_n}}
+%	&\le \Exp{\frac{(1+\smallO{1})\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+%		\ind{A_n^c}} + \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
 %\end{align*}
@@
 %\begin{align*}
-%	\Exp{\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}\ind{A_n^c}}
+%	\Exp{\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\ind{A_n^c}}
 %	&\le \Exp{\left(\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}
-%		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}\right)^2}^{\frac{1}{2}} \Prob{A_n^c}^{\frac{1}{2}}\\
+%		{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right)^2}^{\frac{1}{2}} \Prob{A_n^c}^{\frac{1}{2}}\\
 %	&= \left(1 + \smallO{1}\right) 	
-%		\frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
+%		\frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
 %		\Prob{A_n^c}^{\frac{1}{2}}\\
-%	&= \bigO{\Exp{c_{\Pcal, n}^\ast(k_n)}}\Prob{A_n^c}^{\frac{1}{2}} = \smallO{\Exp{c_{\Pcal, n}^\ast(k_n)}},
+%	&= \bigO{\Exp{c^\ast(k_n; \Gbox)}}\Prob{A_n^c}^{\frac{1}{2}} = \smallO{\Exp{c^\ast(k_n; \Gbox)}},
 %\end{align*}
@@
 \begin{align*}
-	c_{\Pcal, n}^\ast(k_n) = \frac{\widetilde{T}_{\Pcal,n}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-	+ \frac{\left(T_{\Pcal,n}(k_n)-\widetilde{T}_{\Pcal,n}(k_n,C)\right)}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}},
+	c^\ast(k_n; \Gbox) = \frac{\widetilde{T}_{\Pcal,n}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+	+ \frac{\left(T_{\Pcal,n}(k_n)-\widetilde{T}_{\Pcal,n}(k_n,C)\right)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}},
 \end{align*}
@@
 \begin{equation}\label{eq:concentration_local_clustering_P_n_main}
-	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-	+ \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}}.
+	\Exp{c^\ast(k_n; \Gbox)} = \frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+	+ \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
 \end{equation}
@@
 %\begin{align*}
-%	\Exp{\left|c_{\Pcal,n}(k_n) - \Exp{c_{\Pcal,n}^\ast(k_n)}\right|}
-%	&\le \Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{c_{\Pcal,n}^\ast(k_n)}\right|}
-%		+ \Exp{\left|c_{\Pcal,n}(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}\\
+%	\Exp{\left|c_{\Pcal,n}(k_n) - \Exp{c^\ast(k_n; \Gbox)}\right|}
+%	&\le \Exp{\left|c^\ast(k_n; \Gbox) - \Exp{c^\ast(k_n; \Gbox)}\right|}
+%		+ \Exp{\left|c_{\Pcal,n}(k_n) - c^\ast(k_n; \Gbox)\right|}\\
 %	&= \frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}}
-%		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}} + \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}}.
+%		{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}} + \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
 %		\numberthis \label{eq:concentration_local_clustering_P_n_term1}
@@
 \begin{align*}
-	\frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}}
-		{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}
-	&= \smallO{\Exp{c_{\Pcal,n}^\ast(k_n)}},
+	\frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,C) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}\right|}}
+		{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+	&= \smallO{\Exp{c^\ast(k_n; \Gbox)}},
 \end{align*}
@@
 
-\subsection{Joint neighborhoods and degrees in $G_{\Pcal,n}(\alpha,\nu)$}
-
-To prove Proposition~\ref{prop:concentration_tilde_T_P_n} we need to understand the joint degree distribution in $G_{\Pcal,n}$ and subsequently the joint neighborhoods of two points $p, p^\prime \in \Rcal_n$.
+\subsection{Joint neighborhoods and degrees in $\Gbox$}
+
+To prove Proposition~\ref{prop:concentration_tilde_T_P_n} we need to understand the joint degree distribution in $\Gbox$ and subsequently the joint neighborhoods of two points $p, p^\prime \in \Rcal$.
 We perform the analysis in this section.
@@
 
-We start with analyzing joint neighborhoods in $G_{\Pcal,n}$.
-Let $p, p^\prime \in \Rcal_n$.
-Then we denote by $\Ncal_{\Pcal,n}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $G_{\Pcal,n}$, i.e.
+We start with analyzing joint neighborhoods in $\Gbox$.
+Let $p, p^\prime \in \Rcal$.
+Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $\Gbox$, i.e.
 those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection.
-In addition we denote by $\Ncal_{\Pcal,n}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$.
-We shall establish lower bounds on the expect number of these disjoint neighbors $\Exp{\Ncal_{\Pcal,n}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors.
+In addition we denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$.
+We shall establish lower bounds on the expect number of these disjoint neighbors $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors.
 For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large.
@@
 
-	%The box \Rcal_n
+	%The box \Rcal
 	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
@@
 \end{tikzpicture}
-\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $G_{\Pcal,n}(\alpha,\nu)$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
+\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
 \label{fig:representation_disjoint_neighborhoods_P_n}
@@
 \end{tikzpicture}
-\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $G_{\Pcal,n}(\alpha,\nu)$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
+\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
 \label{fig:representation_disjoint_neighborhoods_P_n_2}
@@
 \end{tikzpicture}
-\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $G_{\Pcal,n}(\alpha,\nu)$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:disjoint_neighbors_P_n_large}.}
+\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:disjoint_neighbors_P_n_large}.}
 \label{fig:representation_disjoint_neighborhoods_P_n_3}
@@
 We start by analyzing the shape of the neighborhoods.
-Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal_n$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$ and $y^\prime \le y$.
+Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$ and $y^\prime \le y$.
 To understand the computation it is helpful to have a picture of the different situations.
@@
 There are several different quantities that are important.
-The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal_n$.
+The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal$.
 Note that when $x = 0$ then these height are the same and we denote this by $h(y)$.
@@
 \begin{lemma}\label{lem:disjoint_neighbors_P_n}
-Let $p, p ^\prime \in \Rcal_n$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
-\begin{align*}
-	\Exp{\Ncal_{\Pcal,n}(p \Delta p^\prime)}
+Let $p, p ^\prime \in \Rcal$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
+\begin{align*}
+	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)}
 	&\ge \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
@@
 \begin{align*}
-	\Exp{\Ncal_{\Pcal,n}(p \Delta p^\prime)} &=	\Mu{B_{\Pcal,n}(p) \Delta B_{\Pcal,n}(p^\prime)}\\
-	&\ge \int_0^{h^\ast} \int_{x - e^{\frac{y + y_1}{2}}}^{x^\prime - e^{\frac{y^\prime + y_1}{2}}} f_{\alpha,\nu}(x_1,y_1)
+	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} &=	\Mu{\BallPon{p} \Delta B_{\Pcal,n}(p^\prime)}\\
+	&\ge \int_0^{h^\ast} \int_{x - e^{\frac{y + y_1}{2}}}^{x^\prime - e^{\frac{y^\prime + y_1}{2}}} f(x_1,y_1)
 		\, dx_1 \, dy_1 \\
@@
 \begin{lemma}\label{lem:disjoint_neighbors_P_n_large}
-Let $p, p^\prime \in \Rcal_n$. Then, whenever $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
-\[
-	\Exp{\Ncal_{\Pcal,n}(p\Delta p^\prime)}
-	\ge \left(\mu_{\alpha,\nu}(\BallPon{p}) + \mu_{\alpha,\nu}(\BallPon{p^\prime})\right)
+Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
+\[
+	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}
+	\ge \left(\mu(\BallPon{p}) + \mu(\BallPon{p^\prime})\right)
 		\left(1-\phi_n(p,p^\prime)\right).
@@
 \[
-	\Exp{\Ncal_{\Pcal,n}(p\Delta p^\prime)} 
-	\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f_{\alpha,\nu}(x_1,y_1) \, dx_1 \, dy_1,
+	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)} 
+	\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1,
 \]
@@
 This is clearly true when $h(p,p^\prime) \le h_2(p^\prime)$ so suppose that $h(p,p^\prime) > h_2(p^\prime)$.
-Then, because we identified the right and left boundaries of the box $\Rcal_n$ the right boundary of $\BallPon{p^\prime}$ continues from the left boundary of the box and is described by the equation
+Then, because we identified the right and left boundaries of the box $\Rcal$ the right boundary of $\BallPon{p^\prime}$ continues from the left boundary of the box and is described by the equation
 \[
@@
 \begin{align*}
-	\Exp{\Ncal_{\Pcal,n}(p,p^\prime)} 
+	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
 	&\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
-		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f_{\alpha,\nu}(x_1,y_1) \, dx_1 \, dy_1\\
+		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1\\
 	&= \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
 		\left(\ind{p_1 \in \BallPon{p}} + \ind{p_1 \in \BallPon{p^\prime}}\right) 
-		f_{\alpha,\nu}(x_1,y_1) \, dx_1 \, dy_1\\
+		f(x_1,y_1) \, dx_1 \, dy_1\\
 	&= \left(\mu_{\alpha,\nu ,n}(\BallPon{p}) + \mu_{\alpha,\nu ,n}(\BallPon{p^\prime})\right)
@@
 %	
-%	%The box \Rcal_n
+%	%The box \Rcal
 %	\draw (-5,0) -- (10,0);
@@
 %    
-%    \draw node at (-1,2.5) {$B_{\Pcal}(p) \setminus B_{\Pcal}(p^\prime)$};
+%    \draw node at (-1,2.5) {$\BallPo{p} \setminus B_{\Pcal}(p^\prime)$};
 %    
@@
 %    
-%    \draw node at (6,2.5) {$B_{\Pcal}(p^\prime) \setminus B_{\Pcal}(p)$};
+%    \draw node at (6,2.5) {$B_{\Pcal}(p^\prime) \setminus \BallPo{p}$};
 %    
@@
 %\end{tikzpicture}
-%\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $G_{\Pcal,n}$ used for the proof of Lemma \ref{lem:common_neighbors_Pcal_n}.}
+%\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ used for the proof of Lemma \ref{lem:common_neighbors_Pcal_n}.}
 %\label{fig:representation_joint_neighborhoods}
@@
 
-Next we consider the number of common neighbors between two nodes $p$ and $p^\prime$ in $G_{\Pcal}$, which we denote by $\Ncal_{\Pcal}(p,p^\prime)$.
+Next we consider the number of common neighbors between two nodes $p$ and $p^\prime$ in $\Ginf$, which we denote by $\Ncal_{\Pcal}(p,p^\prime)$.
 
 \begin{lemma}\label{lem:common_neighbors_Pcal_n}
-Let $p, p^\prime \in \Rcal_n$. Then, whenever $|x - x^\prime| > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
-\[
-	\Exp{\Ncal_{\Pcal,n}(p,p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)\phi_n(p,p^\prime),
+Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime| > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
+\[
+	\Exp{\Ncal_{\text{box}}(p,p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)\phi_n(p,p^\prime),
 \]
@@
 \begin{align*}
-	\Exp{\Ncal_{\Pcal,n}(p,p^\prime)} 
+	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
 	&= \int_{h(p,p^\prime)}^{R_n} \int_{x^\prime - e^{(y^\prime+y_1)/2}}^{x + e^{(y + y_1)/2}}
-		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
+		f(x_1,y_1) \dd x_1 \dd y_1\\
 	&= \left(e^{y/2} + e^{y^\prime/2}\right)\frac{\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} 
@@
 
-We now turn to the joint degree distribution of nodes in $G_{\Pcal,n}$. To ease notations we introduce the following short-hand notation for the conditional joint degree distribution
+We now turn to the joint degree distribution of nodes in $\Gbox$. To ease notations we introduce the following short-hand notation for the conditional joint degree distribution
 \[
@@
 \[
-	\Exp{\Ncal_{\Pcal,n}(p \Delta p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)(1 + \smallO{1}),
+	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)(1 + \smallO{1}),
 \] 
@@
 	\mathcal{E}_{\varepsilon}(k_n) &= \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
-		\, : \, \Exp{\Ncal_{\Pcal,n}(p, p^\prime)} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. \label{eq:def_joint_degree_set_E_growing_k}
+		\, : \, \Exp{\Ncal_{\text{box}}(p, p^\prime)} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. \label{eq:def_joint_degree_set_E_growing_k}
 \end{align}
@@
 	&\hspace{-30pt}\int_{\mathcal{E}_n} \rho_{n}(p,p^\prime,k_n,k_n) h(y)h(y^\prime) 
-		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
 	&= (1+\smallO{1})\int_{\mathcal{E}_n} \rho(y,k_n)\rho(y^\prime,k_n) h(y)h(y^\prime) 
-		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
 \end{align*}
@@
 
-We proceed with the case $k_n \to \infty$.
-
-\noindent {\bf Case $\bm{k_n \to \infty}$:}\\
 Define $\delta_n = k_n^{-\frac{(1-\varepsilon)\varepsilon}{2}}$.
-Then, since $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\Pcal,n}(p,p^\prime)} \ge k_n^{\varepsilon}$ for $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, a Chernoff bound (c.f.
+Then, since $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\text{box}}(p,p^\prime)} \ge k_n^{\varepsilon}$ for $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, a Chernoff bound (c.f.
 \eqref{eq:def_chernoff_bound_poisson}) implies that
@@
 
-To execute this plan we note that $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\Pcal,n}(p,p^\prime)}$.
+To execute this plan we note that $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\text{box}}(p,p^\prime)}$.
 Now recall the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n}.
@@
 	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \hat{\rho}_{n}^{(1)}(p,k_n) \hat{\rho}_{n}^{(2)}(p^\prime,k_n) h(y)h(y^\prime) 
-		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
 	&= (1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+			f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
 \end{align*}
@@
 \begin{align*}
-	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) h(y) h(y^\prime) f_{\alpha,\nu}(x,y)
-		f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) h(y) h(y^\prime) f(x,y)
+		f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
 	&=(1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
 	&\hspace{10pt} + \bigO{1} e^{-k_n^{\varepsilon}} \int_{\mathcal{E}_{\varepsilon}(k_n)}
-		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,			
+		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,			
 \end{align*}
@@
 %	&\int_{\mathcal{E}(k_n)} \rho_n(y,y^\prime,k_n,k_N) h(y)h(y^\prime) 
-%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
 %	&=(1+\smallO{1})\int_{\mathcal{E}(k_n)} \hspace{-5pt}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} h(y) h(y^\prime) 	
-%		f_{\alpha,\nu}(x,y)f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%		f(x,y)f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
 %	&\hspace{10pt}+ \bigO{1}\log(n)^{-(2\alpha - 1)} \int_{\mathcal{E}(k_n)}
-%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
 %	&= (1+\smallO{1})\int_{\mathcal{E}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-%		f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,
+%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,
 %\end{align*}
@@
 %	\log(n)^{-(2\alpha - 1)}\int_{\mathcal{E}(k_n)}
-%			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime
+%			f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime
 %\]
@@
 %	\int_{\mathcal{E}_(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-%			f_{\alpha,\nu}(x,y)	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+%			f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
 %\]
@@
 Let $\alpha > \frac{1}{2}$, $\nu > 0$, $k_n \to \infty$ and fix $\varepsilon > 0$.
-Then for any fixed $i, j, i^\prime, j^\prime \in \mathbb{Z}$ and $p, p^\prime \in \Kcal_{C}(k_n)$ such that $\Exp{\Ncal_{\Pcal,n}(p \Delta p^\prime)} \ge k_n^\varepsilon$,
+Then for any fixed $i, j, i^\prime, j^\prime \in \mathbb{Z}$ and $p, p^\prime \in \Kcal_{C}(k_n)$ such that $\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} \ge k_n^\varepsilon$,
 \[
@@
 \end{align*}
-Then it follows that $X_n$, $Y_n$ and $Z_n$ are independent Poisson random variables satisfying $\Exp{X_n} + \Exp{Y_n} = \Mu{B_{\Pcal,n}(p)}$ and $\Exp{Z_n} + \Exp{Y_n} = \Mu{B_{\Pcal,n}(p^\prime)}$ while
+Then it follows that $X_n$, $Y_n$ and $Z_n$ are independent Poisson random variables satisfying $\Exp{X_n} + \Exp{Y_n} = \Mu{\BallPon{p}}$ and $\Exp{Z_n} + \Exp{Y_n} = \Mu{B_{\Pcal,n}(p^\prime)}$ while
 \begin{align*}
@@
 
-Let us first assume that $\Exp{Y_n} \le k_n/2$.
-Then, since $p \in \Kcal_{\varepsilon}(k_n)$ and $\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \bigT{e^{y/2}} = \bigT{k_n}$ it follows that $\Exp{X_n} = \Omega(k_n)$ and hence
+Let us first assume that $\Exp{Y_n} \le k_n/2$. Then, since $p \in \Kcal_{\varepsilon}(k_n)$ and $\mu(\BallPon{p}) = \bigT{e^{y/2}} = \bigT{k_n}$ it follows that $\Exp{X_n} = \Omega(k_n)$ and hence
 \[
@@
 Now assume that $\Exp{Y_n} > k_n/2$.
-Then, since $\Exp{\left|\Ncal_{\Pcal,n}(p \Delta p^\prime)\right|} \ge k_n^{\varepsilon}$ it follows that $\Exp{X_n} = \Omega(k_n^\varepsilon)$ or $\Exp{Z_n} = \Omega(k_n^\varepsilon)$.
+Then, since $\Exp{\left|\Ncal_{\text{box}}(p \Delta p^\prime)\right|} \ge k_n^{\varepsilon}$ it follows that $\Exp{X_n} = \Omega(k_n^\varepsilon)$ or $\Exp{Z_n} = \Omega(k_n^\varepsilon)$.
 Without loss of generality we assume that $\Exp{X_n} = \Omega(k_n^\varepsilon)$.
@@
 \[
-	\widetilde{T}_{\Pcal,n}(k,C) = \sum_{p \in \Pcal_n \cap \Kcal_{C}(k)} \ind{D_{\Pcal,n}(p) = k}
-	\widetilde{T}_{\Pcal,n}(p)
+	\widetilde{T}_{\Pcal,n}(k,C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\Pcal,n}(p)
 \]
@@
 %\[
-%	|x - x^\prime| \le \left(e^{y/2} + e^{y^\prime/2}\right)\left(\frac{k_n + C \log(n)}{\xi_{\alpha,\nu}}\right)
+%	|x - x^\prime| \le \left(e^{y/2} + e^{y^\prime/2}\right)\left(\frac{k_n + C \log(n)}{\xi}\right)
 %	= \bigO{\log(n)^2}
@@
 %		\Exp{\ind{D_{\Pcal,n}(p) = k_n - i, \, D_{\Pcal,n}(p^\prime) = k_n - i^\prime} J_b(p,p^\prime)}
-%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
 %	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{J_b(p,p^\prime)}
-%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
 %	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)}
 %		\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} 
-%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
 %	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)} 
@@
 %\begin{align*}
-%	\int_{h(p,p^\prime)}^{R_n}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
+%	\int_{h(p,p^\prime)}^{R_n}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f(x_1,y_1) \dd x_1 \dd y_1
 %	&= \bigO{e^{y/2} e^{-(\alpha - \frac{1}{2})h(p,p^\prime)}}
@@
 %\begin{align*}
-%	\int_0^{h(p,p^\prime)}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
+%	\int_0^{h(p,p^\prime)}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f(x_1,y_1) \dd x_1 \dd y_1
 %	&= \bigO{1}.
@@
 %\[
-%	\mathcal{J}_1^\ast = \int_{\Rcal_n^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) 
-%			f_{\alpha,\nu}(x_1,y_1)	f_{\alpha,\nu}(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
+%	\mathcal{J}_1^\ast = \int_{\Rcal^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) 
+%			f(x_1,y_1)	f(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
 %\] 
@@
 %	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
-%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&= (1+\smallO{1})\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2.
+%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%	&= (1+\smallO{1})\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f(x,y) \dd x \dd y\right)^2.
 %\end{align*}
@@
 %	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
-%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
+%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
 %	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
-%		f_{\alpha,\nu}(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
 %	&\hspace{10pt}+ \bigO{\log(n)^{-(2\alpha - 1)}n^2} \\
 %	&= (1 + \smallO{1}) \binom{k_n}{2}^2 
-%		\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha,\nu}(x,y) \dd x \dd y\right)^2 \\
+%		\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f(x,y) \dd x \dd y\right)^2 \\
 %	&= (1 + \smallO{1})\Exp{T_\Pcal(k_n)}^2,
@@
 	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
-	\, : \, \Exp{\left|\Ncal_{\Pcal,n}^c(p,p^\prime)\right|} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}
+	\, : \, \Exp{\left|\Ncal_{\text{box}}^c(p,p^\prime)\right|} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}
 \]
@@
 so that for the remainder of the proof we only need to consider $p, p^\prime \in \mathcal{E}_\varepsilon(k_n)$ and hence, we can apply Lemma \ref{lem:joint_degree_factorization}.
-For this we note that by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\Pcal,n}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$.
+For this we note that by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\text{box}}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$.
 In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)^c$.
@@
 	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
-		\Exp{J_b(p,p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+		\Exp{J_b(p,p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
 	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
-		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
 	&= \bigO{\int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}} \rho_{y}(k) 
-		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y) f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy}\\
+		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy}\\
 	&= \bigO{k_n^{1+\varepsilon} \binom{k_n}{2} \left(\int_{a_n^-}^{a_n^+} \Delta_{\Pcal}(y^\prime) 
@@
 	\Exp{I_{0,0}^\ast} = (1 + \smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{n}(p,p^\prime,k_n, k_n)
-		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y)
-		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
+		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f(x,y)
+		f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
 \]
@@
 	&\hspace{-10pt}(1 + \smallO{1})\int_{\mathcal{E}_\varepsilon(k_n)} \rho_n(p, p^\prime, k_n, k_n)
-		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f_{\alpha,\nu}(x,y)
-		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f(x,y)
+		f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
 	&= (1+\smallO{1})\binom{k_n}{2}^2 \int_{\mathcal{E}_\varepsilon(k_n)} 
-		\rho(y, k_n) \rho(y^\prime, k_n) \Delta_{\Pcal}(y) \Delta_\Pcal(y^\prime) 	f_{\alpha,\nu}(x,y) 
-		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+		\rho(y, k_n) \rho(y^\prime, k_n) \Delta_{\Pcal}(y) \Delta_\Pcal(y^\prime) 	f(x,y) 
+		f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
 	&= (1+\smallO{1}) \left( \binom{k_n}{2} \int_{a_n^-}^{a_n^+}\int_{I_n} \rho(y,k_n)
-		\Delta_{\Pcal}(y) f_{\alpha,\nu}(x,y) \, dx \, dy\right)^2\\
+		\Delta_{\Pcal}(y) f(x,y) \, dx \, dy\right)^2\\
 	&= (1 + \smallO{1})\left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}\right)^2,
@@
 Without loss of generality we will assume that $p_1 = p_1^\prime$.
-Notice that now $i = |\{p^\prime, p_1, p_2, p_2^\prime\} \cap B_{\Pcal,n}(p)|$ and $j = |\{p^\prime\} \cap B_{\Pcal,n}(p)|$ and $i^\prime$, $j^\prime$ are defined, similarly, by interchanging the primed and non-primed variables.
+Notice that now $i = |\{p^\prime, p_1, p_2, p_2^\prime\} \cap \BallPon{p}|$ and $j = |\{p^\prime\} \cap \BallPon{p}|$ and $i^\prime$, $j^\prime$ are defined, similarly, by interchanging the primed and non-primed variables.
 Then, if we define
@@
 	\Exp{I_{0,1}^\ast} &= (1+\smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_n(p,p^\prime,k_n,k_n)
-			\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)} f_{\alpha,\nu}(x,y)
-			f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
+			\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)} f(x,y)
+			f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
 \end{align*} 
@@
 %
-%Then, for all $p,p^\prime \in \Rcal_n$ with 
+%Then, for all $p,p^\prime \in \Rcal$ with 
 %\[

### 2019-02-05 concentration_argument.tex
updated notation and added comments to sections 1-3

@@
 
-Many of the computations in this paper will involve integrals whose integrand contains the function $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and $\mu_n(y) \approx e^{y/2}$.
-For instance, the expected modified local clustering function $c_\infty(k)$ in $G_\Pcal$ equals
+In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a(k)^-, a(k)^+]$, with
 \[
-	\frac{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \Delta_{\Pcal}(y) \alpha e^{-\alpha y} \dd y}
-	{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \alpha e^{-\alpha y} \dd y},
+	a(k)^\pm = 2\log\left(\frac{1 \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
 \]
-where $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ and $\Delta_{\Pcal}(y)$ is defined by~\eqref{eq:def_delta_p}.
+The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and $\mu(y) = \mu(B_\Pcal(y)) = \xi e^{y/2}$, and Poisson random variables are well concentrated around their mean, i.e.
+around those values of $y$ for which $\mu(y) \approx k$.
 
-In particular, we already established that the degree of a node at height $y$ in the infinite model is Poisson with mean $\xi_{\alpha,\nu} e^{y/2}$.
-Since we are mostly interested in those nodes with degree $k_n$ and Poisson random variables are well concentrated around their mean, we would therefore like to be able the restrict integration to intervals where $e^{y/2} \approx k_n$.
-Moreover, we want to be able to do this for all three Poisson models $G_{\HP,n}$, $G_{\Pcal,n}$ and $G_\Pcal$ as well as simultaneously deal with the case where $k_n \to \infty$ and $k_n = \bigT{1}$.
-In this section we will establish such a result.
-We start with a concentration lemma for the infinite model (Lemma~\ref{lem:concentration_argument}) and explain in Remark~\ref{rmk:concentration_argument} how such a result will be used throughout the paper.
-To obtain similar results for the other two models we have to first analyze the average degree in these models which we do in Sections~\ref{ssec:average_degree_HP_n} and~\ref{ssec:average_degree_P_n}.
+In the remainder of this paper we will often encounter integrands involving, for some $\mu_n(y)$, the function $\Prob{\Po(\mu_n(y)) = k}$.
+In these case we want to be able to restrict our integration around those heights $y$ for which $\mu_n(y) \approx k_n$.
+We will refer to as \emph{concentration of heights arguments}.
+In this section we establish such results.
+We start with a concentration of heights lemma for the infinite model $\Ginf$ (Lemma~\ref{lem:concentration_argument}) and explain in Remark~\ref{rmk:concentration_argument} how such a result will be used throughout the paper.
+To obtain similar results for the other two models we have to first analyze the expected number of nodes in a typical neighborhood in these models.
+We do in Sections~\ref{ssec:average_degree_HP_n} and~\ref{ssec:average_degree_P_n}.
 We conclude this section with a general result that allows us to extend the concentration lemma for the infinite model to the hyperbolic random graph and finite box model.
@@
 
-Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(B_\Pcal(y)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$. 
-For any sequence $\{k_n\}_{n \ge 1}$, possibly constant, define
-\begin{equation}\label{eq:def_kappa_n}
-	\kappa_n := \begin{cases}
-		\log(n) &\mbox{if } k_n = \bigT{1},\\
-		\sqrt{k_n \log(k_n)} &\mbox{else.}
-	\end{cases}
-\end{equation}
-\TM{ This is not a good definition.
+%Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(B_\Pcal(y)) = \xie^{\frac{y}{2}}$. 
+%We will consider two different types of sequences $\{k_n\}_{n \ge 1}$, those that are asymptotically bounded and those that diverge. We define
+%\begin{equation}\label{eq:def_kappa_n}
+%	\kappa_n := \begin{cases}
+%		\log(n) &\mbox{if } k_n = \bigT{1},\\
+%		\sqrt{k_n \log(k_n)} &\mbox{if } k_n = \omega(1).
+%	\end{cases}
+%\end{equation}
+%\TM{ This is not a good definition.
 There are sequences that neither stay bounded nor tend to infinity, e.q.~odd values equal to 2 even values equal to $\log n$.
@@
 After the new proves are added we can see where we specify this.}
-and define further, for any $C > 0$
+For any positive sequence $a_n \to \infty$ and $C > 0$ we define
 \begin{equation}\label{eq:def_K_C_set}
-	\Kcal_C(k_n) = \left\{p=(x,y) \in \R \times \R_+ : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \le e^{\frac{y}{2}}
-	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \right\},
+	\Kcal_C(a_n) = \left\{y \in \R_+ : \frac{a_n - C \sqrt{a_n \log(a_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
+	\le \frac{a_n + C \sqrt{a_n \log(a_n)}}{\xi} \right\}.
 \end{equation}
-Where we recall that $a \vee b = \max\{a,b\}$ and $a \wedge b = \min\{a,b\}$.
+In addition we define
+\begin{equation}\label{eq:def_K_C_n_set}
+	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R_n] \cap \Kcal_{C}(a_n)),
+\end{equation}
+where $I_n := \frac{\pi}{2}e^{R_n/2}$. In addition, for a sequence $a_n \to \infty$, we shall often use the shorthand notation
+\begin{equation}\label{eq:def_kappa_n}
+	\kappa_n := \sqrt{a_n \log(a_n)}
+\end{equation}
 
-Note that if $k_n = \Omega(\log(n))$ then $e^{y/2} = \bigT{k_n}$ whenever $p=(x,y) \in \Kcal_C(k_n)$. The next lemma states that for a large class of functions $h(y)$, to compute the integral 
+%Where we recall that $a \vee b = \max\{a,b\}$ and $a \wedge b = \min\{a,b\}$.
+
+The next lemma states that for a large class of functions $h(y)$, to compute the integral 
 \[
-	\int_{\Rcal_n} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y
+	\int_{0}^\infty \rho(y,k_n) h(y) e^{-\alpha y} \dd y
 \]
-\TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal_n$. Is this really meant?
-I would have expected we just integrate wrt.~$y$ and replace $f_{\alpha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}\PvdH{I understand this confusion and agree that your suggestion makes more sense here.
+%\TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal_n$. Is this really meant?
+%I would have expected we just integrate wrt.~$y$ and replace $f_{\alpha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}\PvdH{I understand this confusion and agree that your suggestion makes more sense here.
 However, I choose this setup to minimize notations later.
 I am for changing the setup to what you are suggesting but I will have to spend some time first on checking how that will effect the definitions in later sections.}
-it is enough to consider integration \BL{over} $\Kcal_C(k_n)$ instead of $\Rcal_n$.
+it is enough to consider integration over $\Kcal_C(k_n)$ instead of $\R_+$.
 More precisely, for any $\ell_n = (1 + \smallO{1})k_n$ it is enough to consider $\Kcal_C(\ell_n)$.
@@
 \[
-	\lambda_n^\pm = (\ell_n \pm C \kappa_n) \wedge \kappa_n, 
-	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right),
+	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, 
+	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right),
 \] 
-\TM{ If $k$ is constant, then $\ell^- < 0$ and hence 
-$a^-$ is undefined! Need to change the definitions. }\PvdH{You are right. I changed it by taking the minimum with $\kappa_n$.}
-
+%\TM{ If $k$ is constant, then $\ell^- < 0$ and hence 
+%$a^-$ is undefined! Need to change the definitions. }\PvdH{You are right. I changed it by taking the minimum with $\xi$.}
 we have
 \begin{equation}\label{eq:error_bound_int_rho_not_K}
-\begin{aligned}
-	\int_{\Rcal_n\setminus \Kcal_{C}(k_n)} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd x \dd y
-	&= \begin{cases}
-		\bigO{\log(n)^{k_n} n^{-\frac{C}{2}}} &\mbox{if } k_n = \bigT{1} \\
-		\bigO{k_n^{-(1+C^2)/2}} &\mbox{else.}
-	\end{cases}
-\end{aligned}
+	\int_{\R_+ \setminus \Kcal_{C}(\ell_n)} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
+	= \bigO{k_n^{-(1+C^2)/2}}
 \end{equation}
-\TM{ As before, this is not a proper dichotomy. (unless we assume more about the sequences $k_n$, i.e.~either constant or tending to infinity }
+%\TM{ As before, this is not a proper dichotomy. (unless we assume more about the sequences $k_n$, i.e.~either constant or tending to infinity }
 as $n \to \infty$.
@@
 \[
-	\lim_{n \to \infty} \int_{\Rcal_n \setminus \Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x\dd y = 0,
+	\lim_{n \to \infty} \int_{\Rcal_n \setminus \Kcal_{C,n}(\ell_n)} h_n(y) 
+	f_{\alpha, \nu}(x,y) \dd x \dd y = 0,
 \]
@@
 \[
-	\int_{\Rcal_n} \hspace{-5pt} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y
-	= (1+\smallO{1}) \int_{\Kcal_{C}(\ell_n)} \hspace{-5pt} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
+	\int_{\Rcal_n} \hspace{-5pt} h_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y
+	= (1+\smallO{1}) \int_{\Kcal_{C,n}(\ell_n)} \hspace{-5pt} h_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y.
 \]
@@
 \begin{proof}
-Note that in this case
+
+Note that in this case we write
 \[
-	\kappa_n := \begin{cases}
-		\log(n) &\mbox{if } k_n = \bigT{1},\\
-		\sqrt{\ell_n \log(\ell_n)} &\mbox{else.}
-	\end{cases}
+	\kappa_n = \sqrt{\ell_n \log(\ell_n)}.
 \]
-Then, since $a_n^- < k_n$ and $a_n^+ > k_n$, $\rho_{y}(k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$. 
-\TM{ PLease give more details. }
+and recall (see proof of Proposition~\ref{prop:asymp}) that $\rho(y,k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$.
 Therefore, by our assumption on $h(y)$,
 \begin{align*}
-	&\hspace{-20pt}\int_{\R_+ \setminus [a_n^-, a_n^+]} h(y) \rho_{k_n}(y) 
+	&\hspace{-20pt}\int_{\R_+ \setminus [a_n^-, a_n^+]} h(y) \rho(y,k_n) 
 		\alpha e^{-\alpha y} \dd y\\
-    &= \bigO{1} \int_0^{a_n^-} e^{\beta y} \rho_{k_n}(y) \alpha e^{-\alpha y} \dd y 
-    	+ \bigO{1}\int_{a_n^+}^{R_n} e^{\beta y} \rho_{k_n}(y) \alpha e^{-\alpha y}x \dd y \\
-    &= \bigO{1} \int_0^{a_n^-} \rho_{k_n}(y) e^{-(\alpha-\beta) y} \dd y 
-   		+ \bigO{1} \int_{a_n^+}^{R_n} \rho_{k_n}(y) e^{-(\alpha-\beta) y} \dd y\\
+    &= \bigO{1} \int_0^{a_n^-} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y} \dd y 
+    	+ \bigO{1}\int_{a_n^+}^{\infty} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y}x \dd y \\
+    &= \bigO{1} \int_0^{a_n^-} \rho(y,k_n) e^{-(\alpha-\beta) y} \dd y 
+   		+ \bigO{1} \int_{a_n^+}^{\infty} \rho(y,k_n) e^{-(\alpha-\beta) y} \dd y\\
    	&\le \bigO{1}\rho(a_n^-,k_n)\int_0^{a_n^-} e^{-(\alpha-\beta) y} \, \dd y
-   		+ \bigO{1} \rho(y,a_n^+) \int_{a_n^+}^{R_n} e^{-(\alpha-\beta) y} \, \dd y.
+   		+ \bigO{1} \rho(a_n^+,k_n) \int_{a_n^+}^{\infty} e^{-(\alpha-\beta) y} \, \dd y.
 \end{align*}
-Note that if $k_n = \bigT{1}$ then, for large enough $n$, the first integral is zero. We conclude that
+Since $\alpha - \beta > 0$, we conclude that
 \begin{equation}\label{eq:concentration_lemma_integral_bound}
-\begin{aligned}
-	\int_{\R_+ \setminus [a_n^-, a_n^+]} h(y) \rho_{k_n}(y) \alpha e^{-\alpha y} \dd y
-	&= \begin{cases}
-		\bigO{1} \rho(a_n^+,k_n) &\mbox{if } k_n = \bigT{1},\\
-		\bigO{1} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right) &\mbox{else.}
-	\end{cases}	
-\end{aligned}
+	\int_{\R_+ \setminus [a_n^-, a_n^+]} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	= \bigO{1} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right) 
 \end{equation}
 
-We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^+,k_n)$.  Using that $k! > \sqrt{2\pi} k^{k + 1/2} e^{-k}$ \TM{ Reference! } we write
+We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^+,k_n)$.  Using Stirling's approximation $k! \sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
 \begin{align*}
-	\rho(a_n^+,k_n) &\BL{=} \frac{\Mu{\BallPo{a_n^+}}^{k_n}}{k_n!} e^{-\Mu{\BallPo{a_n^+}}} \\
-	&\le (2\pi)^{-1/2} k_n^{-1/2} \left(\frac{\Mu{\BallPo{a_n^+}}}{k_n}\right)^{k_n} e^{-(\Mu{\BallPo{a_n^+}} - k_n)}\\
+	\rho(a_n^+,k_n) &= \frac{\mu(a_n^+)^{k_n}}{k_n!} e^{-\mu(a_n^+)} \\
+	&\sim (2\pi)^{-1/2} k_n^{-1/2} \left(\frac{\mu(a_n^+)}{k_n}\right)^{k_n} e^{-(\mu(a_n^+) - k_n)}\\
 	&= (2\pi)^{-1/2} k_n^{-1/2} 
-		e^{-k_n\left(\frac{\Mu{\BallPo{a_n^+}}}{k_n} - 1 - \log\left(\frac{\Mu{\BallPo{a_n^+}}}{k_n}\right)\right)}.
+		e^{-k_n\left(\frac{\mu(a_n^+)}{k_n} - 1 - \log\left(\frac{\mu(a_n^+)}{k_n}\right)\right)}.
 \end{align*}
 
-Let us first consider the case $k_n \to \infty$,
-\TM{ again, in general we cannot neatly split into the two cases $k\to\infty$ and $k=\Theta(1)$ } in which case $\kappa_n = \sqrt{\ell_n \log(\ell_n)}$. Since 
+Since 
 \[
-	\frac{\Mu{\BallPo{a_n^+}}}{k_n} = \frac{\lambda_n^{\BL{+}}}{k_n} = 1 + \epsilon_n + C \frac{\kappa_n}{k_n} 
+	\frac{\mu(a_n^+)}{k_n} = \frac{\lambda_n^{+}}{k_n} = 1 + \epsilon_n + C \frac{\kappa_n}{k_n} 
 	= 1 + \epsilon_n + C \sqrt{\frac{(1+\epsilon_n)\log((1+\epsilon_n)k_n)}{k_n}},
@@
 \]
-Let use now consider the case $k_n = \bigT{1}$. Then $\kappa_n = \log(n)$,
-\[
-	\frac{\Mu{\BallPo{a_n^+}}}{k_n} = \frac{\lambda_n^+}{k_n} = 1 + \epsilon_n + C \frac{\log(n)}{k_n},
-\] 
-and hence
-\begin{equation}\label{eq:concentration_lemma_bound_an+_constant}
-	\rho(a_n^-,k_n) \le \bigO{\log(n)^{k_n} n^{-C}}.
-\end{equation}
-
-Note that for $\rho(a_n^-,k_n)$ we only need to consider the case $k_n \to \infty$. A similar analysis as for $a_n^-$ yields
+A similar analysis as above yields
 \begin{equation}\label{eq:concentration_lemma_bound_an-}
@@
 
-Plugging~\eqref{eq:concentration_lemma_bound_an-}, \eqref{eq:concentration_lemma_bound_an+} and~\eqref{eq:concentration_lemma_bound_an+_constant} into~\eqref{eq:concentration_lemma_integral_bound} yields the result.
+Plugging~\eqref{eq:concentration_lemma_bound_an-} and~\eqref{eq:concentration_lemma_bound_an+}  into~\eqref{eq:concentration_lemma_integral_bound} yields the result.
 The second statement immediately follows from the first by choosing a large enough $C$ and observing that
 \[
-	\int_{\Rcal_n \setminus \Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x\dd y
+	\int_{\Rcal_n \setminus \Kcal_{C,n}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y
 	\le n \int_{\R_+ \setminus [a_n^-, a_n^+]} h_n(y) \alpha e^{-\alpha y} \dd y.
@@
 
-\begin{remark}[Concentration argument]\label{rmk:concentration_argument}
-\TM{ again, this is a loaded term. I would in the very least change to ``concentration of height'' everywhere }
+\begin{remark}[Concentration of heights argument]\label{rmk:concentration_argument}
+%\TM{ again, this is a loaded term. I would in the very least change to ``concentration of height'' everywhere }
 Lemma~\ref{lem:concentration_argument} will prove very useful in the remainder of this paper since we often have to deal with integrands of the form $g_n(y) f_{\alpha,\nu}(x,y)$ where $g_n(y) = \bigO{n^{-1} k_n^{s}}e^{\beta y}\rho(y,k_n)$ for some $s \in \R$ and $\beta < \alpha$.
 In this case the lemma tells us that for a suitable $C > 0$ we only need to integrate over $\Kcal_C(k_n)$.
-In order words, we may always assume for $g_n(y)$ (for a penalty of $\smallO{1}$) that $k_n - C \kappa_n \le \xi_{\alpha,\nu} e^{y/2} \le k_n + C \kappa_n$.
-We will refer to this as a \emph{concentration argument}, e.g.
-\emph{by a concentration argument}
+In order words, we may always assume for $g_n(y)$ (for a penalty of $\smallO{1}$) that $k_n - C \kappa_n \le \xi e^{y/2} \le k_n + C \kappa_n$.
+We will refer to this as a \emph{concentration of heights argument}, e.g.
+\emph{by a concentration of heights argument}
 \[
-	\int_{\Rcal_n} g_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y 
-	= (1+\smallO{1}) \int_{\Kcal_C(k_n)} g_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y.
+	\int_{\Rcal_n} g_n(y) \rho(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y 
+	= (1+\smallO{1}) n \int_{\Kcal_C(k_n)} g_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
 \]
@@
 \end{remark}
+
+We will later establish similar results for the cases where we consider the hyperbolic and finite box model.
+Here we have to consider Poisson distributions with mean $\mu(\BallHyp{y})$ and $\mu(\BallPon{y})$, respectively.
+For this the following, slightly more general version of Lemma~\ref{lem:concentration_argument} will be important.
+
+\begin{lemma}\label{lem:concentration_argument_rho_approximation}
+Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and let $\Kcal_{C,n}(\ell_n)$ be defined as in~\eqref{eq:def_K_C_n_set}.
+In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ satisfies,
+\[
+	\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y),
+\]
+where $\phi_n(y)$ is a continuous differentiable function such that for some $0 < \varepsilon < 1$
+\[
+	\sup_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| = 0.
+\]
+Then the following holds for some $C > 0$ large enough:
+\begin{enumerate}
+\item For any sequence of continuous functions $h_n(y) : \R_+ \to \R$ such that, uniformly on $(0,R_n]$, $h_n(y) = \bigO{k_n^s e^{\beta y} \hat{\rho}_n(y,k_n)}$, as $n \to \infty$, 
+%\TM{ Why not adjust $h$ so that we incorporate $\hat\rho$ in line below.
+Then both items look more similar.
+}\PvdH{The reason for the bound on $h_n(y)$ in the first statement is that we want to use this for cases where $h_n(y) \le k_n^s \hat{\rho}_n(y,k_n)$ (see for instance the proof of Proposition~\ref{prop:convergence_average_clustering_P_n}.}
+for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
+\[
+	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
+	= (1 + o(1)) \int_{\Kcal_{C,n}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
+\]
+\item For any continuous bounded function $h(y)$,
+\[
+	\int_{\Kcal_{C,n}(\ell_n)} h(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y
+	= (1+\smallO{1}) n \int_{0}^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+\]
+as $n \to \infty$.
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+Similarly to the proof of Lemma~\ref{lem:concentration_argument} we define 
+\[
+	\lambda_n^\pm = (\ell_n \pm C \kappa_n) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
+\] 
+%\TM{ Same problem as in L3.1. $\lambda^-$ can be negative, in which case $a^-$ is undefined.}
+
+In addition we fix $\varepsilon^\ast > 0$ such that $\varepsilon < \min\{1- \frac{s}{2\alpha(2\alpha + 1)},\varepsilon, 1\}$ and. Then since $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s}$ we have
+\begin{align*}
+	k_n^s \int_{(1-\varepsilon^\ast)R_n}^{R_n} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\ast)R_n,k_n) k_n^s e^{-\alpha(1-\varepsilon^\ast)R_n} \\
+	&= \bigO{\hat{\rho}_n((1-\varepsilon^\ast)R_n,k_n) k_n^s n^{-2\alpha(1 - \varepsilon^\ast)}} \\
+	&= \smallO{ \hat{\rho}_n((1-\varepsilon^\ast)R_n,k_n) n^{\frac{s}{2\alpha + 1} - 2\alpha(1-\varepsilon^\ast)}} = \smallO{1},
+\end{align*}
+where the last step follows by our choice of $\varepsilon^\ast$. Hence it is enough to prove both statement on $\Rcal_n((1-\varepsilon)R_n, R_n)$ instead of $\Rcal_n$.
+\PvdH{@All: This is where we use that $s < 2\alpha(2\alpha + 1)$. I think this can be removed by using a more careful bound but I am not sure this is needed.}
+
+\paragraph{Proof of statement 1.}
+Since we already showed that
+\[
+	\lim_{n \to \infty} k_n^s \int_{(1-\varepsilon)R_n}^{R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0,
+\]
+by our assumption on $h_n(y)$, it is enough to show that for sufficiently large $C > 0$,
+\begin{equation}\label{eq:concentration_argument_an_-}
+	\lim_{n \to \infty} k_n^s \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0,
+\end{equation}
+and
+\begin{equation}\label{eq:concentration_argument_an_+}
+	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0.
+\end{equation}
+%\TM{ Why can we change the upper limit of the integral? PLease elaborate (in the paper) }
+
+For simplicity we write $\mu(y) := \mu_{\alpha,\nu}\left(\BallPo{y}\right)$.. Now fix some $0 < \delta < 1$ and let $n$ be large enough such that 
+\begin{enumerate}
+\item $\sup_{0 < y \le (1-\varepsilon)R_n} |\phi_n(y)| < \delta$,
+\item $(\ell_n + C \kappa_n)(1 - \delta) > k_n$ and
+\item $(\ell_n - C \kappa_n)(1 + \delta) < k_n$
+\end{enumerate}
+
+Next, recall that the function $\lambda \mapsto \Prob{\Po(\lambda) = k}$ is monotonic increasing on $[0,k]$ and monotonic decreasing on $[k, \infty)$. Then since for $n$ large enough we have 
+\[
+	\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y)) \ge \mu(y)(1 - \delta) \ge \mu(a_n^+)(1 - \delta)
+	= (\ell_n + C \kappa_n)(1 - \delta) > k_n,
+\]
+it follows that 
+\[
+	\hat{\rho}_n(y,k_n) = \Prob{\Po(\hat{\mu}_n(y)) = k_n} \le \Prob{\Po(\mu(y)(1-\delta)) = k_n},
+\]
+for all $a_n^+ \le y \le (1-\varepsilon)R_n$. By making the change of variables $z = \mu^{-1}(\mu(y)(1-\delta)) = y + 2 \log(1-\delta)$ we then get
+\begin{align*}
+	k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
+	&\le k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \Prob{\Po(\mu(y)(1-\delta)) = k_n} 
+		e^{(\beta-\alpha) y} \dd y\\
+	&= k_n^s (1-\delta)^{\beta - \alpha} \int_{a_n^+ + 2\log(1-\delta)}^{(1-\varepsilon)R_n + 2\log(1-\delta)} 
+		\Prob{\Po(\mu(z)) = k_n} e^{(\beta - \alpha)z} \dd z\\
+	&\le k_n^s (1-\delta)^{\beta - \alpha} \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z.
+\end{align*}
+Since Lemma~\ref{lem:concentration_argument} implies that for large enough $C$,
+\[
+	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z = 0,
+\]
+we have proven~\eqref{eq:concentration_argument_an_+}.
+
+The proof of~\eqref{eq:concentration_argument_an_-} follows the same line of reasoning. This time we use that for $0 \le y \le a_n^-$,
+\[
+	\hat{\mu}_n(y) \le \mu(y)(1 + \delta) \ge \mu(a_n^-)(1 + \delta)
+		= (\ell_n - C \kappa_n)(1 + \delta) < k_n,
+\]
+so that 
+\[
+	\hat{\rho}_n(y,k_n) = \Prob{\Po(\hat{\mu}_n(y)) = k_n} \le \Prob{\Po(\mu(y)(1+\delta)) = k_n}.
+\]
+Making a similar change of variables $z = y + 2 \log(1+\delta)$ we then get
+\begin{align*}
+	k_n^s \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
+	&= k_n^s \int_0^{a_n^-}\Prob{\Po(\mu(y)(1-\delta)) = k_n} 
+		e^{(\beta-\alpha) y} \dd y\\
+	&\le k_n^s (1+\delta)^{\beta - \alpha} \int_0^{a_n^- + 2\log(1+\delta)} 
+		\rho(z,k_n) e^{(\beta - \alpha)z} \dd z,
+\end{align*}
+and~\eqref{eq:concentration_argument_an_-} follows by another application of Lemma~\ref{lem:concentration_argument}.
+
+\paragraph{Proof of statement 2.}
+
+The proof of the second statement follows the same line of reasoning as above. First note that by Lemma~\ref{lem:concentration_argument} and the first statement, it is enough to show that
+\[
+	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) h(y) e^{-\alpha y} \dd y
+	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z.
+\] 
+or equivalently,
+\[
+	\int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z
+	= \left(1 + o(1)\right)\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) h(y) e^{-\alpha y} \dd y.
+\]
+
+Using the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$ and writing $\hat{a}_n^\pm = \hat{\mu}_n^{-1}(\mu(a_n^\pm))$, we get
+\begin{align*}
+	&\hspace{-30pt}\int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z \\
+	&= \int_{a_n^-}^{a_n^+} \Prob{\Po(\mu(z)) = k_n} h(z) e^{-\alpha z} \dd z\\
+	&= \int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(\mu^{-1}(\hat{\mu}_n(y))) e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
+		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
+\end{align*}
+where the fraction is the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.
+
+Now recall that $\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y))$, with $\phi_n(y)$ continuous and differentiable and satisfying
+$\max_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| \to 0$.
+It follows that $\max_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n^\prime(y)| \to 0$ which then implies that $\hat{\mu}_n^\prime(y) = (1 + \smallO{1})\mu^\prime(y)$ as $n \to \infty$, uniformly on $(0,(1-\varepsilon)R_n)$.
+In particular this holds uniformly on $[a_n^-, a_n^+]$.
+Next we note that $\mu^\prime(y) = \mu(y)/2$ from which it follows that uniformly on $[a_n^-, a_n^+]$,
+\[
+	\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))}
+	= \frac{2\hat{\mu}_n^\prime(y)}{\hat{\mu}_n(y)}
+	= \frac{(1 + \smallO{1})2\mu^\prime(y)}{(1 + \smallO{1})\mu(y)}
+	= (1+\smallO{1})
+\]
+In addition, uniformly on $[0,(1-\varepsilon)R_n]$,
+\[
+	\mu^{-1}(\hat{\mu}_n(y)) = 2 \log(\hat{\mu}(y)/\xi) = 2 \log(\mu(y)/\xi) + 2 \log(1 + \smallO{1}) = y + \smallO{1}.
+\]
+Therefore, by assumption on $h(y)$,
+\begin{align*}
+	&\hspace{-30pt}\int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z \\
+	&= (1 + \smallO{1})e^{-\alpha b_n}\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(y + \smallO{1})  
+		e^{-\alpha y} \dd y\\
+	&= (1 + \smallO{1}) \int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(y)  
+		e^{-\alpha y} \dd y \\
+	&= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(y)  
+			e^{-\alpha y} \dd y,
+\end{align*}
+which finishes the proof.
+\end{proof}
 
@@
 }
-where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}. Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.
+where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}. Recall that $\Mu{\BallPo{0,y}} = \xi e^{y/2}$ where $\xi = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.
 
-By~\eqref{eq:tail_inclusion_hyperbolic_ball}, we have $\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])= \Rcal_n([R_n-y,R_n])$. 
+Note that $\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])= \Rcal_n([R_n-y,R_n])$. 
 Thus, 
@@
 %\TM{ same comment Re: average degree. }
-For the finite box model $G_{\Pcal,n}(\alpha, \nu)$ we obtain a similar result for the average degree.
+For the finite box model $\Gbox$ we obtain a similar result for expected size of the balls.
 
@@
 \]
-\TM{ where did the curly B's go? }\PvdH{Typo. Fixed}
+%\TM{ where did the curly B's go? }\PvdH{Typo. Fixed}
 where $\phi_n(y) \ge 0$ is given by
@@
 We will first consider the case where $y > 2 \log(\pi/2)$.
-Recall that $\mu_{\alpha,\nu}(B_\Pcal(p)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$ where $\xi_{\alpha,\nu} = \frac{4\alpha \nu}{(2\alpha - 1)\pi}$.
+Recall that $\mu_{\alpha,\nu}(\BallPo{p}) = \xi e^{\frac{y}{2}}$ where $\xi = \frac{4\alpha \nu}{(2\alpha - 1)\pi}$.
 Then, after some simple algebra, we have that
 \begin{align*}
-	\mu_{\alpha,\nu}(B_{\Pcal,n}(p))
+	\mu_{\alpha,\nu}(\BallPon{p})
 	&= \int_0^{h(y)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
@@
 		+ \alpha \nu e^{\frac{R_n}{2}} \int_{h(y)}^{R_n} e^{-\alpha y^\prime} \, dy^\prime \\
-	&= \xi_{\alpha,\nu} e^{\frac{y}{2}}\left(1 - \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} 
+	&= \xi e^{\frac{y}{2}}\left(1 - \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} 
 		e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)\\
@@
 		- e^{-\alpha R_n}\right)\\
-	&= \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right).
+	&= \mu_{\alpha,\nu}(\BallPo{p})\left(1 - \phi_n(y)\right).
 \end{align*}
@@
 \begin{align*}
-	\mu_{\alpha,\nu}(B_{\Pcal,n}(p))
+	\mu_{\alpha,\nu}(\BallPon{p})
 	&= \int_0^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
@@
 	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R_n} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
-	&= \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
+	&= \mu_{\alpha,\nu}(\BallPo{p})\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
 \end{align*}
@@
 
-With the results on number of points in the balls in the two finite Poisson models $G_{\HP,n}$ and $G_{\Pcal,n}$, we can now establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the functions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$.
-The lemma is stated in a more general form, to make it applicable to slightly other cases later in the paper.
-To understand the general conditions presented in the statement of the lemma we write $\mu_n(y) = \Mu{\BallPon{y}}$ and $\mu(y) = \Mu{\BallPo{y}}$ and recall the result from Lemma~\ref{lem:average_degree_P_n}
-\[
-	\mu_n(y) = \mu(y)(1 - \phi_n(y)).
-\]
-For the error function $\phi_n(y)$ we note that for any $0 < \varepsilon < 1$, as $n \to \infty$, 
-\[
-	\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y) = \smallO{1},
-\]
-while
-\[
-	\frac{\partial \phi_n(y)}{\partial y} = \bigT{\phi_n(y)}.
-\]
-These are exactly the crucial properties of the error function that allow for a concentration argument.
-Moreover, if the integrand also contains a function $g_n(y)$ that is reasonably nice, we can replace the $\rho_{n}(y,k_n)$ in the integrand by $\rho(y,k_n)$.
-In particular, the triangle counting function $\Delta_{\Pcal}(y)$ will satisfy these conditions, see Section~\ref{sec:clustering_Pn_to_P}.
-
-\begin{lemma}\label{lem:concentration_argument_rho_approximation}
-Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and let $\Kcal_{C}(\ell_n)$ be defined as in~\eqref{eq:def_K_C_set}.
-In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is any differentiable function satisfying
-\[
-	\Mu{\BallPo{0,y}}(1 - \phi_n^{(1)}(y)) \le \hat{\mu}_n(y) \le \Mu{\BallPo{0,y}}(1 + \phi_n^{(2)}(y))
-\]
-where $\phi_n^{(i)} : \R_+ \to \R_+$ are such that $\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y)^{(i)} = \smallO{1}$ for any $0 < \varepsilon < 1$ and $\partial \phi_n^{(i)}(y)/\partial y = \bigT{\phi_n^{(i)}(y)}$.
-Then the following holds for some $C > 0$ large enough:
-\begin{enumerate}
-\item for any sequence of continuous functions $h_n(y) : \R_+ \to \R$ such that $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s e^{\beta y}}$ \TM{ Why not adjust $h$ so that we incorporate $\hat\rho$ in line below.
-Then both items look more similar.
-}\PvdH{I am not sure what you are suggesting.
-Could you explain a bit more?}  for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
-\[
-	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
-	= (1 + o(1)) \int_{\Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y,
-\]
-with $\Kcal_{C}$ defined in~\eqref{eq:def_K_C_set}
-\item for any continuous and uniformly bounded function $h : \R_+ \to \R$,
-\[
-	\int_{\Rcal_n} h(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y 
-	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
-\]
-\end{enumerate}
-%\TM{ Say in the lemma statement where def of $K_C$ can be found. }
-\end{lemma}
-
-\begin{proof}
-Similarly to the proof of Lemma~\ref{lem:concentration_argument} we define 
-\[
-	\lambda_n^\pm = (\ell_n \pm C \kappa_n) \wedge \kappa_n, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right).
-\] 
-%\TM{ Same problem as in L3.1. $\lambda^-$ can be negative, in which case $a^-$ is undefined.}
-In addition we fix $\varepsilon > 0$ such that $\varepsilon < \min\{1- \frac{s}{2\alpha(2\alpha + 1)}, 1\}$. Then since $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s}$ we have
-\begin{align*}
-	k_n^s \int_{(1-\varepsilon)R_n}^{R_n} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
-	&= \bigO{1} \hat{\rho}_n((1-\varepsilon)R_n,k_n) k_n^s e^{-\alpha(1-\varepsilon)R_n} \\
-	&= \bigO{\hat{\rho}_n((1-\varepsilon)R_n,k_n) k_n^s n^{-2\alpha(1 - \varepsilon)}} \\
-	&= \smallO{ \hat{\rho}_n((1-\varepsilon)R_n,k_n) n^{\frac{s}{2\alpha + 1} - 2\alpha(1-\varepsilon)}} = \smallO{1},
-\end{align*}
-where the last step follows by our choice of $\varepsilon$. Hence it is enough to prove both statement on $\Rcal_n((1-\varepsilon)R_n, R_n)$ instead of $\Rcal_n$.
-\PvdH{@All: This is where we use that $s < 2\alpha(2\alpha + 1)$. I think this can be removed by using a more careful bound but I am not sure this is needed.}
-
-For simplicity we write $\mu(y) := \mu_{\alpha,\nu}\left(\BallPo{y}\right)$. For both statements we shall make a change of variables $y \to z$ such that
-\begin{equation}\label{eq:concentration_argument_variable_change}
-	\hat{\mu}_n(y) = \mu(z),
-\end{equation}
-and therefore %\TM{ "implies"? this is just by definition. }
-\[
-	\mu^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
-\]
-Observe that since $\mu^{-1}(y)$
-%\[
-%	\mu^{-1}(y) = 2 \log\left(\frac{y}{\xi_{\alpha,\nu}}\right),
-%\]
-%\TM{ repeat of previous eq. Typo or leftover of old version ... ? }
-is strictly monotonic in $y$, we have, by our assumptions on $\hat{\mu}_n$, that
-\begin{equation}\label{eq:concentration_argument_z_upper_bound}
-	z(y) \le 2 \log\left(\frac{\mu(y)}{\xi_{\alpha,\nu}}\right) + 2 \log\left(1 + \phi_n^{(2)}(y)\right)
-	= y + 2 \log\left(1 + \phi_n^{(2)}(y)\right),
-\end{equation}
-and similarly
-\begin{equation}\label{eq:concentration_argument_z_lower_bound}
-	z(y) \ge y + 2 \log\left(1 - \phi_n^{(1)}(y)\right) \
-\end{equation}
-\TM{ Please elaborate! Why would $\hat\mu$ be diff'ble anyway? }\PvdH{I have added the diff'ble assumption to the lemma statement}
-%Denote by $g^\prime(z)$ the derivative of a function $g$.
-%\TM{ I would remove this last sentence. }
-Then by assumption $(\phi_n^{(i)})^\prime(z) = \bigT{\phi_n^{(i)}(z)}$ and hence
-\begin{align*}
-	\hat{\mu}_n^\prime(z) = \mu^\prime(z)\left(1 + o(1)\right).
-\end{align*}
-
-\paragraph{Proof of statement 1.} By our assumption on $h_n(y)$ it is enough to show that for sufficiently large $C > 0$,
-\[
-	\lim_{n \to \infty} k_n^s \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0,
-\]
-and
-\[
-	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0.
-\]
-\TM{ Why can we change the upper limit of the integral? PLease elaborate (in the paper) }
-We shall prove the last statement. The first statement follows using similar computations.
-
-By our assumption on $\phi_n^{(2)}(y)$ we have for all $a_n^+ < y \le (1 - \varepsilon)R_n$,
-\begin{equation}
-	e^{(\beta-\alpha) y} = (1 + o(1))e^{(\beta-\alpha) z}.
-\end{equation}
-Therefore, with this change of variables~\eqref{eq:concentration_argument_variable_change}, using that $\hat{a}_n^+ := z(a_n^+) = a_n^+(1 + \smallO{1})$ and $z((1-\varepsilon)R_n) = (1-\varepsilon)R_n(1+\smallO{1})$, we have
-\begin{align*}
-	k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
-	&=  k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \Prob{\mathrm{Po}\left(\hat{\mu}_n(y) = k_n\right)} 
-		e^{(\beta-\alpha) y} \dd y\\
-	&= (1 + \smallO{1})k_n^s\int_{a_n^+}^{(1-\varepsilon)R_n} \Prob{\mathrm{Po}\left(\mu(z) = k_n\right)}
-		e^{(\beta-\alpha) z} \frac{\hat{\mu}_n^\prime(z)}{\mu^{\prime}(z)} \, dz \\
-	&\le (1 + \smallO{1})k_n^s\int_{a_n^+}^{R_n} \rho(y,k_n)
-			e^{(\beta-\alpha) z} \dd z.
-\end{align*}
-\TM{ Please elaborate 2nd equlaity. I don't quite follow. }\PvdH{The fraction $\hat{\mu}_n^\prime(z)/\mu^{\prime}(z)$ comes from the change of variables. Or is this not what you mean?}
-The result then follows by Lemma~\ref{lem:concentration_argument}.
-
-\paragraph{Proof of statement 2.}
-
-The proof of the second statement follows the same line of reasoning as above. First note that by Lemma~\ref{lem:concentration_argument} and the first statement, it is enough to show that
-\[
-	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) h(y) e^{-\alpha y} \dd y
-	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z.
-\] 
-For this we observe that~\eqref{eq:concentration_argument_z_upper_bound} and~\eqref{eq:concentration_argument_z_lower_bound} imply that there exists a $b_n \to 0$ such that $y = z(y) + b_n$, uniformly for $a_n^- \le y \le a_n^+$.
-Hence, if we define $g_n(z) = h(z + b_n)$, then $g_n(z)$ is uniformly bounded and converges pointwise to $h(z)$.
-\TM{ I don't quite follow.
-Do we assume $h$ is continuous?
-}\PvdH{Yes, we probably should.
-I have added this to the lemma statement.} Therefore, with the change of variables~\eqref{eq:concentration_argument_variable_change} we get
-\begin{align*}
-	\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) h(y) e^{-\alpha y} \dd y
-	&=  \int_{a_n^-}^{a_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(y) e^{-\alpha y} \dd y\\
-	&= (1 + \smallO{1})\int_{a_n^-}^{a_n^+}  \Prob{\Po(\mu(z))}
-		g_n(z) e^{-\alpha z} \frac{\hat{\mu}_n^\prime(z)}{\mu^{\prime}(z)} \dd z\\
-	&= (1 + \smallO{1})\int_{a_n^-}^{a_n^+}  \Prob{\Po(\mu(z))}
-		g_n(z) e^{-\alpha z} \dd z\\
-	&= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z.
-\end{align*}
-\TM{ again, please elaborate 2nd eq. (in the paper) }
-where the last line follow by dominated convergence.
-\end{proof}
-
-Observe that Lemma~\ref{lem:average_degree_P_n} implies that $\Mu{\BallHyp{(0,y)}}$ satisfies the requirements in Lemma~\ref{lem:concentration_argument_rho_approximation} while Lemma~\ref{lem:average_degree_hyperbolic} states that this holds for $\Mu{\BallPon{0,y}}$.
-We therefore have the following important Corollary.
+Let us define $\rho_{\Po}(y,k) = \Prob{\Po(\Mu{\BallHyp{y}}) = k}$ and $\rho_{\text{box}} = \Prob{\Po(\Mu{\BallPon{y}}) = k}$.
+Then since Lemma~\ref{lem:average_degree_P_n} implies that $\Mu{\BallHyp{(y)}}$ satisfies the requirements in Lemma~\ref{lem:concentration_argument_rho_approximation} while Lemma~\ref{lem:average_degree_hyperbolic} states that this holds for $\Mu{\BallPon{0,y}}$, we have the following important Corollary.
 
 \begin{corollary}\label{cor:concentration_argument_other_models}
-Let $\hat{\rho}_n(y,k)$ be any of the two distribution functions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$.
-Then, for any function $g_n(y)$ such that $g_n(y) = \bigO{n^{-1} k_n^{s} e^{\beta y}}\hat{\rho}_n(y,k_n)$ \TM{ Where did the $n^{-1}$ come from?
-Does not appear in L3.4.
-}\PvdH{I will elaborate on this once the statement of Lemma~\ref{lem:concentration_argument} is updated}, as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
-\[
-	\int_{\Rcal_n} g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y
-	= (1+\smallO{1})\int_{\Kcal_C(k_n)} g_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y,
-\]
-for some $C > 0$ large enough.
+The statements of Lemma~\ref{lem:concentration_argument_rho_approximation} holds for the two distribution functions $\rho_{\Po}(y,k)$ and $\rho_{n}(y,k)$. 
 \end{corollary}
 
-In particular we conclude that, similarly to the infinite limit model, concentration arguments as described in Remark~\ref{rmk:concentration_argument} can be applied in the case of the hyperbolic random graph and finite box model.
+%\begin{corollary}\label{cor:concentration_argument_other_models}
+%Let $\hat{\rho}_n(y,k)$ be any of the two distribution functions $\rho_{\Po}(y,k)$ and $\rho_{n}(y,k)$ and let $\Kcal_{C,n}(\kappa_n)$ be defined as in~\eqref{eq:def_K_C_n_set}.
+Then, for any function $g_n(y)$ such that, uniformly on $(0, R_n]$, $g_n(y) = \bigO{k_n^{s} e^{\beta y}}$,
+%%\TM{ Where did the $n^{-1}$ come from? Does not appear in L3.4. }\PvdH{I will elaborate on this once the statement of Lemma~\ref{lem:concentration_argument} is updated}, 
+%as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
+%\[
+%	\int_{\Rcal_n} g_n(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y
+%	= (1+\smallO{1})n\int_{0}^\infty g_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+%\]
+%for some $C > 0$ large enough.
+%\end{corollary}
 
-%\begin{lemma}
-%\[
-%	\Prob{D_{\HP,n}= k_n} = (1 + \smallO{1})\Prob{D_\Pcal = k_n}
-%\]
-%\end{lemma}
+In particular we conclude that, similarly to the infinite limit model, concentration of heights arguments as described in Remark~\ref{rmk:concentration_argument} can be applied in the case of the hyperbolic random graphs and the finite box model.
+
+\begin{remark}[Most frequent use of concentration of argument]
+Note that it follows from Proposition~\ref{prop:asymp} that $P(y)$ satisfies the conditions in the both statements of Lemma~\ref{lem:concentration_argument_rho_approximation}.
+In particular, if $\hat{\rho}_n$ denote either $\rho_{\Po}$ or $\rho_{\text{box}}$, then as $n \to \infty$
+\begin{equation}\label{eq:concentration_heights_argument_Py}
+	\int_{\Rcal_n} P(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x, y) \dd x \dd y
+	= (1 + \smallO{1}) n \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+\end{equation}
+This is the form that will be use most frequently in the remainder of this paper.
+\end{remark}

### 2019-02-05 introduction.tex
updated notation and added comments to sections 1-3

--- 2019-01-11 introduction.tex
@@
-\section{Introduction and results}
+\section{Introduction and main results}
 
-\subsection{Motivation}
+In this paper, we will consider clustering in a model of random graphs that involves points taken randomly in the hyperbolic plane.
+This model was introduced by Krioukov, Papadopoulos, Kitsak, Vahdat and Bogu\~{n}\'a~\cite{krioukov2010hyperbolic} in
+2010 - we abbreviate it as \emph{the KPKVB model}.
+We should however note that the model also goes by several other names in the literature, including {\em hyperbolic random geometric graphs} and {\em random hyperbolic graphs}.
+Krioukov et al.~suggested this model as a suitable model for complex networks.
+It exhibits the three main characteristics usually associated with complex networks: a power-law degree distribution, a non-vanishing clustering coefficient and short graph distances.
 
-%\MS{I would not write a length introduction to complex networks here (because the paper is quite long already and we do not study networks in general in this paper).
-So, I would remove the first paragraph/list (or incorporate it as a single sentence in the ensuing paragraph).
-}
-%\PvdH{I agree.}
+%
+%\subsection{Hyperbolic random graphs}\label{ssec:hyperbolic_model}
 
-Hyperbolic random graphs were suggested as a suitable model for complex networks by Krioukov et al.~\cite{krioukov2010hyperbolic}, exhibiting the three main characteristics commonly found in complex networks:
-\begin{enumerate}[\upshape 1)]
-\item Broad degree distribution (power-law/scale-free),
-\item Strong clustering (community structure),
-\item Small path lengths (small world phenomenon).
-\end{enumerate}
-Indeed, in their seminal paper they showed that these graphs have a power-law degree distribution and exhibit strong clustering, while Bringmann et al.~\cite{bringmann2016average} showed that hyperbolic random graphs have doubly logarithmic shortest path lengths.
-\TM{ \RD{Remove this reference, and replace with Abdullah-Bode-Fountoulakis!!!!}
-In general the proofs that GIRG = HRG are shaky at best, so I do not want to cite anything that relies on that.
-Of course, in this case Nikoloas \& his crew were  first anyway.
-Also, regarding "distances", we probably want to mention graph diameter, studied by Kiwi+Mitsche, Friedrich+Krohmer, M\"uller + Staps.
-}
-Many other results regarding hyperbolic random graphs have since been established: for instance the existence of efficient routing algorithms~\cite{bringmann2017greedy}, the size of the largest component~\cite{bode2015largest},~\cite{fountoulakis2018law} and the number of cliques and the largest clique~\cite{blasius2018cliques}.
-\PvdH{@All: Does anyone have other suggestions for results to add?}
-\TM{ Yes, of course!
-Everything Nikolaos\& his crew, and I and my crew, and Kiwi-Mitsche have done on this model.
-This includes 2nd largest componnent, connectivity, spectral gap, diameter, Hamilton cycles \& perfect matchings (with Markus, Nikolaos and Mitsche, in preparation but perhaps submitted around the same time as this one.).
-Also there is a recent paper on arxiv by Owada+Yogeshwaran on subgraph counts.}
+\PvdH{I would try to refrain from making assumptions about the reader.}
+We start with the definition of the KPKVB model. %As the reader will probably already know, 
+As mentioned, its nodes are situated in the hyperbolic plane $\Haa$, which is a surface with constant Gaussian curvature $-1$.
+This surface has several convenient representations (i.e.~coordinate maps), including the Poincar\'e halfplane model, the Poincar\'e disk model and the Klein disk model.
+A gentle introduction to Gaussian curvature, hyperbolic geometry and these representations of the hyperbolic plane can be found in~\cite{stillwellboek}.
+Throughout this paper we will be working with a representation of the hyperbolic plane using {\em hyperbolic polar coordinates}, sometimes called the {\em native representation}.
+That is, a point $p \in \Haa$ is represented as $(r,\theta)$, where $r$ is the hyperbolic distance between $p$ and the origin $O$ and $\theta$ as the angle between the line segment $Op$ and the positive $x$-axis.
+Here, when mentioning ``the origin'' and the angle between the line segment and the positive $x$-axis, we think of $\Haa$ embedded as the Poincar\'e disk in the ordinary euclidean plane.
 
-The aim of this paper is to study local clustering in hyperbolic random graphs.
-The first rigorous mathematical analysis of the local clustering coefficient was done by Gugelmann et al.~\cite{gugelmann2012random}.
-They show~\cite[Theorem 2.1]{gugelmann2012random} that the local clustering coefficient\footnote{Note that in~\cite{gugelmann2012random} this is called the global clustering coefficient.
-However, since this term is more often associated in the literature with the density of triangles compared to the number of paths of length 2, we use the term local clustering coefficient as is done, for instance, in~\cite{candellero2016clustering}.} is concentrated around its expectation which is shown to be $\bigT{1}$ as the number of vertices tends to infinity.
-In particular this result implies that the local clustering coefficient is asymptotically bounded away from zero.
-The convergence of this coefficient was however not proven.
-In contrast, the global clustering coefficient was shown~\cite{candellero2016clustering} to converge in probability to some constant which can be explicitly stated as an integral expression, see Theorem 1.2 in \cite{candellero2016clustering}.
-The authors mention, however, that their analysis needs significant modification to be able to deal with convergence of the local clustering coefficient.
-
-In addition to the clustering coefficients, an important clustering measure that is often studied is the local clustering function $c(k)$.
-This function computes for any value of $k$ the average of the local clustering coefficient over all vertices of degree $k$.
-A general expression of this function for hyperbolic random graphs is given in \cite[Equation (59)]{krioukov2010hyperbolic}.
-The authors conjecture that as $k$ tends to infinity, $c(k)$ decays as $k^{-1}$, which they observe (Figure 8 in \cite{krioukov2010hyperbolic}) in experiments on the infrastructure of the Internet obtained in~\cite{claffy2009internet}.
-However, despite the importance of the local clustering function and these interesting observations, its behavior in hyperbolic random graphs had not been completely determined and the following crucial questions regarding clustering in hyperbolic random graphs remained open so far:
-\begin{enumerate}[\upshape 1)]
-\item Does the local clustering coefficient converge, and if so, what is the limit?
-\item What is the limit of the local clustering function and how does it scale with the degree?
-\end{enumerate}
-
-In this work we resolve these important open questions.
-We obtain the asymptotic scaling of $c(k)$ as $k \to \infty$, including the leading constant, as well as an exact expression, in terms of known special functions, of the point-wise limit of the local clustering function as the number of vertices tends to infinity.
-Interestingly, the scaling of $c(k)$ depends on the exponent of the degree distribution and is only $k^{-1}$ when this exponent exceeds $5/2$.
-For values less than $5/2$ the scaling is $k^{-s}$ where the value of $s$ depends on the degree distribution exponent.
-Finally, our analysis allows us to also prove a convergence result for the local clustering coefficient where the limit can again be explicitly expressed in terms of known special functions.
-
-\TM{ I vote to remove this next paragraph. Use of GIRGs is fishy, and also we are not obliged to mention any and all possible alternative approaches. }
-We remark that it is possible to prove that the local clustering coefficient converges to some limit, using the technical tools in the recent work on explosion times in Geometric Inhomogeneous Random Graphs~\cite{komjathy2018explosion}.
-However, this problem is not explicitly addressed in that paper, nor is there any reason to expect these tools to give us the exact expressions as we do derive in this work.
-
-%\PvdH{I recall that J{\'u}lia told me that the results from~\cite{komjathy2018explosion} imply that the local clustering coefficient converges, although they do not mention it in the paper.
-Should we added a comment related to this?}
-
-%\MS{Yes, I think this would probably be good.
-Either after the sentence `the convergence of this coefficient was not proven' add something like, as you say, the results form ..
-imply convergence, although not specifically mentioned there.
-Or drop that sentence about that the convergence was not shown and also rephrase the sentence in 1, to just what is the limit.
-It should just be clear to the reader that we are not claiming the credit for the convergence itself, but mostly for finding the exact limit (in an analytic expression) and with a very strong sense of convergence.
-So, let's better emphasize those last two points and hope that they are good enough.}
-
-\subsection{Outline of the paper}
-
-In the next two subsections \ref{ssec:hyperbolic_model} and \ref{ssec:local_clustering} of the introduction, we give the definitions of the hyperbolic random graph and of the local clustering coefficient and function as used in this paper.
-After this we present our main results in Section \ref{ssec:main_results} and discuss several insights that can be obtained from them and in Section \ref{ssec:simulations} show simulations which confirm these results.
-Section \ref{sec:proof_outline} contains a detailed high level outline of the proofs of our main results, split up into different propositions.
-The proofs of these propositions can be found in the last four sections.
-Section~\ref{sec:concentration_argument} contains a crucial technical result that will be used in the other sections.
-The Appendix contains a small section on Meijer's G-function and some known concentration results we use.
-
-\subsection{Hyperbolic random graphs}\label{ssec:hyperbolic_model}
-
-The hyperbolic plane is an infinite $2$-dimensional manifold with constant negative curvature.
-Many different representations of the hyperbolic plane exist and we refer to~\cite{anderson2006hyperbolic} \cite{katok1992fuchsian} \cite{beardon2012geometry} for an introduction to hyperbolic geometry.
-We will work with the \emph{native representation} of the hyperbolic plane which takes the elements of $\R^2$ in polar coordinates $(r,\theta)$ as the underlying set of points and where distances are determined by the hyperbolic law of cosines.
-
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and define $R_n = 2\log(n/\nu)$. Then the hyperbolic random graph $G_{\H,n}(\alpha, \nu)$ is defined as follows:
-\begin{enumerate}
-\item The vertex set if given by $n$ points $u_1, \dots, u_n$ denoted in polar coordinates $(r_i, \theta_i)$, where the angular coordinate $\theta$ is chosen uniformly from $(-\pi,\pi]$ while the radial coordinate $r$ is sampled independently according to the cumulative distribution function
+The KPKVB model has three parameters: the number of vertices $n$, which we think of as going to infinity, and $\alpha > \frac{1}{2}$, $\nu > 0$ which we think of as fixed.
+Given $n, \alpha, \nu$ we define $R = 2\log(n/\nu)$.
+Then the hyperbolic random graph $G(n;\alpha, \nu)$ is defined as follows:
+\begin{itemize}
+\item The vertex set is given by $n$ i.i.d.~points $u_1, \dots, u_n$ denoted in polar coordinates $(r_i, \theta_i)$, where the angular coordinate $\theta$ is chosen uniformly from $(-\pi,\pi]$ while the radial coordinate $r$ is sampled independently according to the cumulative distribution function
 \begin{equation}\label{eq:def_hyperbolic_point_distribution}
-	F_{n,\alpha,\nu}(r) = \begin{cases}
+	F_{\alpha,R}(r) = \begin{cases}
 		0 &\mbox{if } r < 0\\
-		\frac{\cosh(\alpha r)-1}{\cosh(\alpha R_n) - 1} &\mbox{if } 0 \le r \le R_n\\
-		1&\mbox{if } r > R_n
+		\frac{\cosh(\alpha r)-1}{\cosh(\alpha R) - 1} &\mbox{if } 0 \le r \le R\\
+		1&\mbox{if } r > R
 	\end{cases}
 \end{equation}
-\item Any two vertices $u_i=(r_i,\theta_i)$ and $u_j=(r_j,\theta_j)$ are adjacent if and only if $d_\H(u_i,u_j) \le R_n$, where $d_\H$ denotes the distance in the hyperbolic plane, i.e.
+\item Any two vertices $u_i=(r_i,\theta_i)$ and $u_j=(r_j,\theta_j)$ are adjacent if and only if $d_\H(u_i,u_j) \le R$, where $d_\H$ denotes the distance in the hyperbolic plane.
+We will frequently be using that, by the hyperbolic law of cosines, $d_\H(u_i,u_j) \le R$ is equivalent to
 \[
-	\cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R_n),
+	\cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R),
 \]
-as follows from the hyperbolic law of cosines.% rule[CITE?].
-\TM{ This is only when $r_i+r_j \geq R$!
-Otherwise the equation does not have a solution as there is no triangle with side lengths $r_i, r_j, R$.}\PvdH{I do not understand this.
-The hyperbolic law of cosines defines the hyperbolic cosine of the distance between points in terms of hyperbolic cosines and sines of their radii and the cosine of their relative angle:
-\[
-	\cosh(d_\H(u_i, u_j)) = \cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}).
-\] 
-Since $\cosh$ is strictly monotonically increasing we have that $\cosh(x) \le \cosh(y) \iff x \le y$ and hence 
-\begin{align*}
-	&d_\H(u_i, u_j) \le R_n \\
-	&\iff \cosh(d_\H(u_i, u_j)) \le \cosh(R_n) \\
-	&\iff \cosh(r_i) \cosh(r_j) - \sinh(r_i) \sinh( r_j) \cos(|\theta_i-\theta_j|_{2\pi}) \le \cosh(R_n)
-\end{align*}
-The approximation for the hyperbolic balls you and Nicolaos derived in Lemma 28 holds only when $r_i + r_j \ge R$.}
-\end{enumerate}
+where $|a|_{b} = \min( |a|, b - |a|)$ for $-b\leq a\leq b$.
+\end{itemize}
 
@@
 \includegraphics[scale=0.3]{figures/KPKVB.png}
-\caption{Example of a Hyperbolic Random Graph $G_{\H,n}(\alpha, \nu)$ with $\alpha = 0.9$, $\nu = 0.2$ and $n = 5000$.
+\caption{Simulation $G(n;\alpha, \nu)$ with $\alpha = 0.9$, $\nu = 0.2$ and $n = 5000$.
 %\PvdH{@Tobias: this figure (HyperRGG\_N5000L5.eps) is taken from the figures you send me. Could you fill in the value of $\alpha$ and $\nu$ you used for the simulation.}
@@
 
-Figure~\ref{fig:H_graph_example} shows an example of $G_{\H,n}(\alpha, \nu)$.
+\noindent
+Figure~\ref{fig:H_graph_example} shows a computer simulation of $G(n;\alpha, \nu)$.
 
-%We say that the points $u_i \in G_{\H, n}$ are distributed according to a \emph{$(\alpha, R_n)$-quasi uniform distribution}.
+As observed by Krioukov et al~\cite{krioukov2010hyperbolic}, and proved rigorously by Gugelmann et al.~\cite{gugelmann2012random}, the degree sequence of the KPKVB model follows a power-law with exponent $2\alpha+1$.
+% More specifically, if $N_k$ denotes the number of vertices of degree exactly $k$ then Gugelmann et al.~\cite{gugelmann2012random} have shown that
+% 
+% \begin{equation}\label{eq:gugeldegseq} 
+% N_k = (1+o(1)) \cdot n \cdot p_k \quad \text{ a.a.s., }
+% \end{equation}
+% 
+% \noindent
+% where $p_k := 2\alpha \cdot \xi^{2\alpha} \cdot \Gamma^+\left(k - 2\alpha, \xi\right) / k!$
+% with, here and in the rest of the paper, $\xi := \frac{4\alpha\nu}{\pi(2\alpha-1)}$ and 
+% $\Gamma^+(a,b) := \int_b^\infty t^{a-1} e^{-t} \text{d}t$ the 
+% {\em upper incomplete gamma function} and, for $(E_n)_n$ a sequence of events, 
+% $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Pee(E_n)\to 1$.
+%%In particular $X_n = (1+o(1)) Y_n$ is equivalent to $X_n/Y_n \plim 1$.
+%In fact~\eqref{eq:gugeldegseq} was shown in~\cite{gugelmann2012random} to hold not only when $k$ is constant but 
+%also if $k$ depends on $n$ as long as $k = o( n^\delta )$ for a suitable small constant $\delta = \delta( \alpha )$.
+%Standard asymptotic manipulations show that 
+%
+%$$p_k \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha+1)}, $$
+%
+%as $k\to\infty$.
+%\TM{ \RD{We need to add something like the following} : 
+%In Appendix~\ref{} we settle the minor technical point of showing that~\eqref{eq:gugeldegseq} in fact extends 
+%to all $k$ with $k \ll n^{1/(2\alpha+1)}$, while 
+%$N_k = 0$ a.a.s.~whenever $k \gg n^{1/(2\alpha+1)}$. }
+Gugelmann et al~\cite{gugelmann2012random} also showed that the average degree converges in probability to the constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing in the sense that it is bounded below by a positive constant a.a.s.
+Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Pee(E_n)\to 1$.
+%Their work however left open the question of whether the clustering coefficient actually converges in probability.
 
-\subsection{Clustering}\label{ssec:local_clustering}
+Apart from the degree sequence and clustering, the third main characteristic associated with complex networks, ``short distances'', has also been established in the literature.
+In~\cite{abdullah2017typical} it is shown that for $\alpha < 1$ the largest component is what is called an \emph{ultra-small world}: if we randomly sample two vertices of the graph then, a.a.s., conditional on them being in the same component, their graph distance is of order $\log\log n$.
+In~\cite{KiwiMit} and~\cite{ar:FriedKrohmerDiam} a.a.s.~polylogarithmic upper and lower bounds on the graph diameter of the largest component
+are shown, and in~\cite{ar:MullerDiam}, these were sharpened to show that $\log n$ is the correct order of the diameter.
 
-Clustering measures for networks consider the fraction of triangles (triples of connected vertices) in the network. 
-For instance, for a simple graph $G$, with vertex set $V(G)$ and edge set $E(G)$, denote by $T_G$ and $\Lambda_G$, respectively, the total number of triangles and the total number of paths of length two in $G$.
-Then its \emph{global clustering coefficient} is defined as
+Earlier work of the first and third authors with Bode~\cite{bode2015largest} and of the first and third authors~\cite{fountoulakis2018law} has 
+established the ``threshold for a giant component'': when $\alpha < 1$ then there always is a unique component of size linear in $n$ no matter how small 
+$\nu$ (and hence the average degree) is; when $\alpha > 1$ all components are sublinear no matter the value of $\nu$; and when $\alpha=1$ then 
+there is a critical value $\nu_{\text{c}}$ such that for $\nu < \nu_{\text{c}}$ all components are sublinear and for $\nu > \nu_{\text{c}}$ there 
+is a unique linear sized component (all of these statements holding a.a.s.). 
+Whether or not there is a giant component when $\alpha=1$ and $\nu=\nu_{\text{c}}$ remains an open problem.
+In~\cite{KiwiMit} an ~\cite{KiwiMit2017+}, Kiwi and Mitsche considered the size of the second largest component and
+showed that when $\alpha \in (1/2, 1)$, a.a.s., the second largest component has polylogarithmic order with exponent 
+$1/(\alpha -1/2)$.
+
+In another paper of the first and third authors with Bode~\cite{BFMconnRSA} it was shown that $\alpha=1/2$ is the threshold for connectivity:
+for $\alpha < 1/2$ the graph is a.a.s.~connected, for $\alpha>1/2$ the graph is a.a.s.~disconnected and when $\alpha=1/2$ the probability 
+of being connected tends to a continuous, nondecreasing function of $\nu$ which is identically one for $\nu \geq \pi$ and strictly less than one 
+for $\nu < \pi$.
+Friedrich and Krohmer~\cite{blasius2018cliques} studied the size of the largest clique as well as the number of cliques of a given size.
+Bogu\~{n}a et al.~\cite{sustaining} and Bl\"asius et al.~\cite{BlasiusMLE} considered fitting the KPKVB model to data using maximum likelihood 
+estimation.
+Kiwi and Mitsche~\cite{KM18} studied the spectral gap and related properties, and Bl\"asius et al.~\cite{BlasiusTW} considered the treewidth 
+and related parameters of the KPKVB model.
+Recently Owada and Yogeshwaran~\cite{OY} considered subgraph counts, and in particular established a central limit theorem 
+for the number of copies of a fixed tree $T$ in $G(n;\alpha,\nu)$, subject to some restrictions on the parameter $\alpha$.
+
+\subsubsection*{Clustering}
+
+In the literature there are unfortunately two distinct, rival definitions of the {\em clustering coefficient}.
+One of those, sometimes called the {\em global} clustering coefficient, is defined as 
+three times the ratio the number of triangles to the number of paths of length two in the graph.
+Results for this version of the clustering coefficient in the KPKVB model were obtained by Candellero and the first author~\cite{candellero2016clustering} and for the evolution of graphs on more general spaces with negative curvature by the first author in~\cite{F12}.
+
+In this paper we will study the other notion of clustering, the one which is also considered by Krioukov et al.~\cite{krioukov2010hyperbolic} and
+Gugelmann et al.~\cite{gugelmann2012random}. 
+It is sometimes called the {\em local} clustering coefficient, although we should point out that Gugelmann et al.~actually
+call it the global clustering coefficient in their paper.
+For a graph $G$ and a vertex $v\in V(G)$ we define the clustering coefficient {\em of $v$} as:
 \[
-	c_G = \frac{3 \T_G}{\Lambda_G}.
+	c(v) := \left\{\begin{array}{cl}
+		\displaystyle \frac{1}{{\text{deg}(v)\choose 2}} \sum_{u,w\sim v} 1_{\{uw \in E(G)\}} 
+			& \text{ if $\text{deg}(v) \geq 2$, }\\
+		& \\
+        0 & \text{ otherwise,}
+        \end{array}\right.
 \]
-%This coefficient measures the fraction of triangles in the network compared to the total possible number of triangles. 
-\TM{ Do we even need to give this definition? We don't study it, so I would say it suffices to just mention there is another, rival defintion to the one we use.}
-A different concept for clustering is defined for each vertex and by taking averages also for the entire graph as well as for all vertices with a specified degree: the \emph{local clustering coefficient} of a vertex $v \in V(G)$ is a real number between zero and one for the extent to which the neighborhood of $v$ resembles a clique.
-If the vertex $v$ has $k\geq 2$ neighbors, there are ${k \choose 2}$ possible edges between them and its local clustering coefficient is the quotient of the number of these pairs that constitute an existing edge in the graph divided by ${k \choose 2}$.
-\TM{ Here I would add the formula for readability.}
-If the vertex $v$ has no or only one neighbor, its clustering coefficient is set to zero.
-The (average) local clustering coefficient of the graph is the average over the clustering coefficients of all vertices.
-The local clustering function maps a natural number $k$ to the average over the clustering coefficients of all vertices with degree $k$ if there are vertices with degree $k$ and zero otherwise.
+where $E(G)$ denotes the edge set of $G$ and $\text{deg}(v)$ is the degree of vertex $v$.
+That is, provided $v$ has degree at least two, $c(v)$ equals the number of edges that are actually present between the neighbours \PvdH{I think it is neighbors in US English vs neighbours in UK English.
+Is there any specific reason to us the UK version?} of $v$ divided by the
+number of edges that could possibly be present between the neighbours given the degree of $v$.
+The clustering coefficient of $G$ is now defined as the average of $c(v)$ over all vertices $v$:
 
-To introduce the notations for these definitions, let $D_G(v)$ denote the degree of vertex $v$ and $N_G(k)$ the number of vertices with degree $k$ in the graph $G$.
-In addition let $$\T_G(v,v_1,v_2) = \ind{(v,v_1) \in E} \ind{(v, v_2) \in E} \ind{(v_1, v_2) \in E}$$ be the indicator that $v, v_1$ and $v_2$ form a triangle and write
-\begin{equation}
-	\T_G(v) = \sum_{v_1, v_2 \in V(G)} \T_G(v,v_1,v_2),
-\end{equation}
-to denote the number of triangles in which node $v$ participates. Then the \emph{local clustering coefficient} is given by
+$$ c(G) := \frac{1}{|V(G)|} \sum_{v\in V(G)} c(v). $$
+
+As mentioned above, Gugelmann et al.~\cite{gugelmann2012random}, have established that $c(G(n;\alpha,\nu))$ is non-vanishing a.a.s., but they left 
+open the question of convergence.
+Theorem~\ref{thm:maincc} below establishes that the clustering coefficient indeed converges in probability to a constant
+$\gamma$ that we give explicitly as a closed form expression involving $\alpha,\nu$ and several classical special functions.
+
+In addition to the clustering coefficient, we shall also be interested in the {\em clustering function}.
+This assigns to each integer $k$ the value
+
+$$ c(k; G) := \begin{cases}
+		\displaystyle \frac{1}{N_k} \sum_{v \in V(G), \atop \text{deg}(v)=k}  c(v)  &\mbox{ if } N_k \ge 1\\
+		0 &\mbox{else.}
+	\end{cases},
+	$$
+
+\noindent
+where $N_k$ denotes the number of vertices of degree exactly $k$ in $G$.
+In other words, the clustering function assigns to the integer $k$ the average of the local clustering coefficient over all vertices of degree $k$. 
+We remark that, while it might seem natural to consider $c(k)$ to be ``undefined'' when $N_k=0$, we prefer to use the above definition for technical 
+convenience.  This way $c(k; G(n;\alpha,\nu) )$ is a plain vanilla random variable and we can for instance compute its moments without any issues.
+
+A general expression of the clustering function for KPKVB random graphs is given in~\cite[Equation (59)]{krioukov2010hyperbolic}. 
+The authors conjecture that as $k$ tends to infinity, the clustering function decays as $k^{-1}$. They based this prediction 
+on observations (Figure 8 in \cite{krioukov2010hyperbolic}) in experiments on the infrastructure of the Internet obtained 
+in~\cite{claffy2009internet}. 
+Despite these interesting observations and the attention
+the KPKVB model has generated since then, the behaviour of the clustering function in 
+KPKVB random graphs had not been completely determined. In particular it has not been established whether it converges as $n\to\infty$ to some suitable limit function and, 
+how $c(k;G)$ scales with $k$.
+Theorems~\ref{thm:mainkfixed},~\ref{thm:mainktoinfty} and Proposition~\ref{prop:asymp} below settle these questions.
+Theorem~\ref{thm:mainkfixed} shows that for each fixed $k$, the value $c(k;G(n;\alpha,\nu))$ converges in probability to 
+a constant $\gamma(k)$ that we again give explicitly as a closed form expression involving $\alpha,\nu$ and several classical special functions.
+Theorem~\ref{thm:mainktoinfty} extends this result to growing sequences satisfying $k \ll n^{1/(2\alpha+1)}$.
+Propostion~\ref{prop:asymp} clarifies the asymptotics of the limiting function $\gamma(k)$, as $k\to\infty$.
+This depends on the parameter $\alpha$, and $\gamma(k)$ only scales with $k^{-1}$ when $\alpha > 3/4$, 
+which corresponds to the exponent of the degree distribution exceeding $5/2$. 
+So in particular our findings disprove the abovementioned conjecture of Krioukov et al.~\cite{krioukov2010hyperbolic}.
+
+\subsubsection*{Notation}
+
+In the statement of our main results, and throughout the rest of the paper, we will use the following notations. 
+We set 
+$$\xi := \frac{4\alpha\nu}{\pi(2\alpha-1)}. $$
+
+We write $\Gamma(z) := \int_0^\infty t^{z-1} e^{-t}\text{d}t$ for the gamma function, 
+$\Gamma^+(a,b) := \int_b^\infty t^{a-1} e^{-t}\text{d}t$ for the upper incomplete gamma function, 
+ $B(a,b) := \int_0^1 u^{a-1}(1-u)^{b-1}\text{d}u = \Gamma(a)\Gamma(b) / \Gamma(a+b)$ for the beta function and 
+ $B^-(x,a,b) := \int_0^x u^{a-1}(1-u)^{b-1}\text{d}u$ the lower incomplete beta function. 
+We write $U(a,b,z)$ for the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which 
+%for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $\mathrm{Re}(a), \mathrm{Re}(z) >0$ 
+has the integral representation 
 \[
-	c_G = \frac{1}{|V(G)|} \sum_{v \in V(G)} \frac{T_G(v)}{\binom{D_G(v)}{2}}.
+	U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} dt,
 \] 
+see~\cite[p.255 Equation (2)]{erdelyi1953higher}, and let $\MeijerGnew{m}{\ell}{p}{q}{{\bf a}}{{\bf b}}{z}$ denote 
+Meijer's G-Function~\cite{meijer1946gfunction}, see Appendix~\ref{sec:Meijer_G_functions} for more details.
 
-\TM{ I would find it natural to define $c(v)$ first and then let $c(G)$ be the average. }
-However, since the local clustering coefficient assigns just one value to the whole network, representing its triangular structure, it is unable to characterize local structural properties involving triangles.
-\TM{ This last sentence seems a bit weird to me, rather abstract. }
-The local clustering function, on the other hand, measures the fraction of triangles to which vertices of a given degree belong, compared to the maximum number of triangles in which they could participate~\cite{vazquez2002large,serrano2006clustering}.
-It describes the triangular structure of vertices in the networks based on their degree and gives a more detailed look at the overall structure of the network.
-\TM{ Similar comment to the previous one. I am not really sure what this means. }
-The formal definition of the \emph{local clustering function} is 
-\begin{equation}\label{eq:def_local_clustering_general}
-	c_{G}(k) = \begin{cases}
-		\frac{1}{N_G(k)} \sum_{v \in V(G)}  \ind{D_G(v) = k} \frac{\T_G(v)}{\binom{k}{2}} &\mbox{if } N_G(k) \ge 1\\
-		0 &\mbox{else.}
-	\end{cases}
-\end{equation}
-
-\TM{ Perhaps we should say that, while it may be more natural to consider $c(k)$ to be undefined when $N_k=0$, we use this definition for technical convenience. This way 
-$c(k)$ is a plain vanilla random variable and we can compute expectation and so on without issue, and speak about convergence in probability and what not. }
-%We note that other versions of the local clustering function have been considered, for instance where nodes with degree larger than $k$ are considered instead of nodes with degree exactly $k$.
-\PvdH{Motivate our choice for this local clustering function.}
-
-\begin{remark}[Notational convention]\label{rmk:notation}
-In the remainder of this paper we will compare the local clustering function and many other characteristics between several different graph models.
-To make notation less cluttered we will often use a unique subscript to identify the graph with respect to which the specific property refers instead of the full graph description.
-For instance, we shall write $c_{\H,n}(k)$ to denote $c_{G_{\H,n}(\alpha, \nu)}(k)$ and similar, $D_{\H, n}(u)$ for $D_{G_{\H,n}(\alpha, \nu)}(u)$.
-For the infinite model we will use the subscript $\infty$.
-\end{remark}
+For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in probability to $X$, as $n \to \infty$.
+%In addition, $X_n \xrightarrow[n\to\infty]{L^1} X$ denotes convergence in expectation, i.e.
+$\Exp{|X_n - X|} \to 0$ as $n \to \infty$, which is a stronger notion than convergence in probability.
 
@@
 
-We are now ready to state our main results for the clustering coefficient and local clustering function in the hyperbolic random graph.
-When the degree $k$ is a growing function of $n$ we are able to exactly compute the asymptotic behavior of $c_{\H,n}(k)$.
-\TM{ Seems a little strong. We "exactly compute" the leading terms, I would say. }
+\subsubsection{The clustering coefficient}
 
-The results are obtained by coupling the hyperbolic random graph to an infinite random graph $G_\Pcal(\alpha,\nu)$, which we define in Section~\ref{ssec:infinite_model}, and show that the limit of the local clustering coefficient and function for the hyperbolic random graph are given by those for the infinite model.
+Our first result is the following.
 
-%\MS{Here, I would just say that $B(a,b)$ denotes the beta function $B^-(x,a,b)$ the lower incomplete beta function etc.
-and put/refer to the integral representations in the appendix, as already done for the Meijer-G function.}
-%\subsubsection{Special functions}
-We let $B(a,b)$ denote the beta-function and $B^-(x,a,b)$ the lower incomplete beta-function.
-We also write $\Gamma(z)$ for the Gamma function, $\Gamma^+(q,z)$ for the \TM{ upper } incomplete Gamma function and define $\Gamma^\ast(q,z) := \Gamma^+(1 + q, z) + \Gamma^+(q, z)$.
-\TM{ How useful is this extra definiton?
-If it is just to make the expression in Thm 1.1 neater, then I dont think we need it.
-}
-Finally, we write $U(a,b,z)$ for the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which for $a,b,z\in \mathbb{C}$, $b \not \in \mathbb{Z}_{\leq 0}$, $\mathrm{Re}(a), \mathrm{Re}(z) >0$ has the integral representation
+\begin{theorem}\label{thm:clustering_coefficient_hyperbolic}\label{thm:maincc}
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ be fixed. Writing $G_n := G(n;\alpha,\nu)$, we have
 \[
-	U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} dt,
+	c( G_n ) \xrightarrow[n\to\infty]{\Pee} \gamma,
 \]
-see~\cite[p.255 Equation (2)]{erdelyi1953higher}, and let $\MeijerGnew{m}{\ell}{p}{q}{{\bf a}}{{\bf b}}{z}$ denote Meijer's G-Function~\cite{meijer1946gfunction}, see Appendix~\ref{sec:Meijer_G_functions} for more details.
-\TM{ Should we not maybe also say what the upper incomplete gamma and lower incomplete beta are then? }
-
-\subsubsection{Local clustering coefficient}
-
-Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to a constant $c_\infty$, which we can explicitly write down in terms of the special functions mentioned above.
-
-\begin{theorem}[Limit for local clustering coefficient in $G_{\H,n}(\alpha,\nu)$] \label{thm:clustering_coefficient_hyperbolic}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$, and $\xi_{\alpha,\nu} = \frac{4\alpha \nu}{\pi(2\alpha -1)}$. Then,
-\[
-	\lim_{n \to \infty} \Exp{\left|c_{\H,n} - c_\infty\right|} = 0,
-\]
-\TM{ As far as I can tell this is just equivalent to 
-$c(G) \plim c_\infty$.
-I would prefer to use this more standard notation and terminology, certainly at least here, where we present our main results.
-} \PvdH{Convergence in expectation implies convergence in probability but is a much stronger notion.
-In addition, for integer valued sequences $a_n$ and $b_n$ we have that $\Exp{|a_n - b_n|} \to 0$ implies that $a_n = b_n$ a.a.s..
-However, when they are real valued this is no longer true in general.}
-where $c_\infty$ is defined for $\alpha \ne 1$ as
+where $\gamma$ is defined for $\alpha \ne 1$ as
 \begin{align*}
-	c_\infty 
-	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}
-		{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} 
+	\gamma 
+	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} 
 		+  \frac{2^{-1 - 4 \alpha}}{(\alpha - 1)^2} \\
-	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}
-		{2 (\alpha - 1) (3 \alpha - 1)} \\
-	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{2\alpha} \Gamma^\ast( - 2 \alpha, \xi_{\alpha,\nu})}{4(\alpha-1)}
-		+ \frac{\xi_{\alpha,\nu}^{2\alpha + 2}\alpha (\alpha - 1/2)^2 \Gamma^\ast(- 2 \alpha - 2, \xi_{\alpha,\nu})}
+&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)} \\
+%
+&\hspace{10pt}+ \frac{\xi^{2\alpha} \left( \Gamma^+( 1 - 2 \alpha, \xi) + \Gamma^+( - 2 \alpha, \xi)\right) }{4(\alpha-1)} \\
+%
+&\hspace{10pt}+ \frac{\xi^{2\alpha + 2}\alpha (\alpha - 1/2)^2 \left( \Gamma^+(- 2 \alpha - 1, \xi) + \Gamma^+(- 2 \alpha - 2, \xi)\right)}%
 {2(\alpha-1)^2} \\
-	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{2\alpha + 1}\alpha (2\alpha - 1) \Gamma^\ast( - 2 \alpha - 1,\xi_{\alpha,\nu})}{(\alpha-1)}
-		- \frac{\xi_{\alpha,\nu}^{6\alpha-2}2^{-4\alpha}(3\alpha - 1)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)^2}\\
-	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{6\alpha - 2}(\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)} \\
-	&\hspace{10pt}- \frac{e^{-\xi_{\alpha,\nu}} \Gamma(2\alpha+1) 
-		\left(U(2\alpha+1,1-2\alpha,\xi_{\alpha,\nu}) + U(2\alpha+1,2-2\alpha,\xi_{\alpha,\nu})\right)}{4(\alpha-1)} \\
-	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{6\alpha - 2} \Gamma(2\alpha+1)\left( 	
-		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi_{\alpha,\nu}}
-		+ \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi_{\alpha,\nu}}\right)}{4(\alpha-1)},
+%
+&\hspace{10pt}- \frac{\xi^{2\alpha + 1}\alpha (2\alpha - 1) \left( \Gamma^+( - 2\alpha,\xi)+\Gamma^+( - 2 \alpha - 1,\xi) \right)}%
+{(\alpha-1)} \\
+%
+&\hspace{10pt}- \frac{\xi^{6\alpha-2}2^{-4\alpha}(3\alpha - 1)
+\left( \Gamma^+( - 6 \alpha + 3, \xi)+\Gamma^+( - 6 \alpha + 2, \xi) \right)}{(\alpha-1)^2}\\
+%
+&\hspace{10pt}- \frac{\xi^{6\alpha - 2}(\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)%
+\left(\Gamma^+( - 6 \alpha + 3, \xi)+\Gamma^+( - 6 \alpha + 2, \xi)\right)}{(\alpha-1)} \\
+%
+&\hspace{10pt}- \frac{e^{-\xi} \Gamma(2\alpha+1) \left(U(2\alpha+1,1-2\alpha,\xi) + U(2\alpha+1,2-2\alpha,\xi)\right)}{4(\alpha-1)} \\
+%
+&\hspace{10pt}+ \frac{\xi^{6\alpha - 2} \Gamma(2\alpha+1)\left( \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi}
+ 		+ \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi}\right)}{4(\alpha-1)},
 \end{align*}
-and for $\alpha = 1$ as
-\begin{align*}
-	c_\infty &= \frac{575 - 12 \pi^2}{576} + \frac{\eta^4(7 + \pi^2)\Gamma^\ast(-4, \eta)}{4}\\
-	&\hspace{10pt}- \frac{1}{2} \int_0^1 (1 - 4z + 3z^3)\log(1-z)(z + \eta)e^{-\eta/z} \dd z\\
-	&\hspace{10pt}- \int_0^1 \Li_2(z)(z^3 + \eta z^2) e^{-\eta/z} \dd z,		
-\end{align*}
-with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function\footnote{Note that the integrals in the expression for $c_\infty$ for $\alpha = 1$ exists: for the first one note that $1-4z+3z^2=(1-z)(1-3z)$, so the integrand can be bounded by $C(1-z)\log(1-z)$ on $[0,1)$ for some constant $C$, which can be continued continuously to the compact interval $[0,1]$ by noting that the limit for $z \rightarrow 1$ is zero, so the integrand is bounded on a bounded domain and hence, this integral is finite; for the second integral note that $\Li_2(z)$ is bounded by $\Li_2(1)$ on $[0,1]$, which is a series with well-known finite limit, so again the integrand is bounded on a bounded domain and hence the second integral is also finite.}.
+and for $\alpha = 1$ as the $\alpha\to 1$ limit of the above expression. 
+% \begin{align*}
+% 	c_\infty &= \frac{575 - 12 \pi^2}{576} + \frac{\eta^4(7 + \pi^2)\Gamma^\ast(-4, \eta)}{4}\\
+% 	&\hspace{10pt}- \frac{1}{2} \int_0^1 (1 - 4z + 3z^3)\log(1-z)(z + \eta)e^{-\eta/z} \dd z\\
+% 	&\hspace{10pt}- \int_0^1 \Li_2(z)(z^3 + \eta z^2) e^{-\eta/z} \dd z,		
+% \end{align*}
+% with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function\footnote{Note that the integrals in the expression for $c_\infty$ for $\alpha = 1$ exists: for the first one note that $1-4z+3z^2=(1-z)(1-3z)$, so the integrand can be bounded by $C(1-z)\log(1-z)$ on $[0,1)$ for some constant $C$, which can be continued continuously to the compact interval $[0,1]$ by noting that the limit for $z \rightarrow 1$ is zero, so the integrand is bounded on a bounded domain and hence, this integral is finite; for the second integral note that $\Li_2(z)$ is bounded by $\Li_2(1)$ on $[0,1]$, which is a series with well-known finite limit, so again the integrand is bounded on a bounded domain and hence the second integral is also finite.}.
 \end{theorem}
 
-\TM{ Do we want to remark something re: closed form expression for the $\alpha=1$ case? }
+\noindent
+A plot of $\gamma$ can be found in Figure~\ref{fig:gamma}.
 
-\subsubsection{Local clustering function}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[scale=0.6]{figures/SimulationClusteringCoefficientVariousNu.pdf}
+    \caption{Plot of $\gamma$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and 
+    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=1000$ and 20 repetitions.\label{fig:gamma}}
+\end{figure}
 
-For the local clustering function we also obtain convergence in expectation to a function $c_\infty(k)$ which can be explicitly stated using the special functions.
+In the above expression for $\gamma$, a factor $\alpha-1$ occurs in the denominator of each term, but we will see that this
+corresponds to a removable singularity.
+We have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
 
-\begin{theorem}[Limit for local clustering function in $G_{\H,n}(\alpha, \nu)$]
-\label{thm:local_clustering_hyperbolic}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\xi = \frac{4\alpha\nu}{\pi(2\alpha-1)}$ and $(k_n)_{n \ge 1}$ be any positive sequence, possibly constant, such that $k_n \ge \GR{2}$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
-Then,
+\subsubsection{The clustering function}
+
+Our second result in on the clustering function for constant $k$.
+
+\begin{theorem}\label{thm:local_clustering_hyperbolic}\label{thm:mainkfixed}
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $k\geq2$ be fixed. 
+Writing $G_n := G(n;\alpha,\nu)$, we have
+
 \[
-	\lim_{n \to \infty} \Exp{\left|\frac{c_{\H,n}(k_n)}{c_\infty(k_n)} - 1\right|} = 0,
+	c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k),
 \]
-where the function $c_\infty(k)$ is defined for $\alpha \ne 1$ as
+where $\gamma(k)$ is defined for $\alpha \ne 1$ as 
 \begin{align*}
-c_\infty(k)  =&\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right.
-\\
+\gamma(k)  =&\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
 &\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
@@
 \end{align*}
-and for $\alpha = 1$ as
-\begin{align*}
-	c_\infty(k) &= \frac{9 \eta^3}{2 k!} 	
-		\Gamma^+(k-3,\eta)-\frac{\xi_{\alpha,\nu}^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
-	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
-	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
-\end{align*}
-with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function.
+and for $\alpha = 1$ as the $\alpha\to1$ limit of the above expression.
+% \begin{align*}
+% 	c_\infty(k) &= \frac{9 \eta^3}{2 k!} 	
+% 		\Gamma^+(k-3,\eta)-\frac{\xi^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
+% 	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
+% 	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
+% \end{align*}
+% with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function.
 \end{theorem}
 
-\TM{ I would be tempted to split this thm into two.
-The first states that for $k$ fixed
-$c(k) \plim c_\infty(k)$. Then we say the proof extends to ... the second thm which states that if
-$1 \ll k_n \ll n^{1/(2\alpha+1)}$ then
-$c(k_n) = (1+o(1)) c_\infty(k_n)$ a.a.s. \\
-In fact, maybe it is good to present a separate -- and short -- proof of the constant case.
-The equivalence of the models for constant $k$ can be worked out in a few pages while for the sequence we need 50+ pages of super technical computations.
-What do you think?
-} \PvdH{I agree with the splitting suggestion.
-However, as I mentioned before, since $c(k_n)/c_\infty(k_n)$ is real-valued our result does not necessarily imply that $c(k_n)/c_\infty(k_n) = 1$ a.a.s..
-I guess this is what you mean with $c(k_n) = (1+o(1)) c_\infty(k_n)$ a.a.s.
-right?}
-
-From the expression for $c_\infty(k)$ we obtain its asymptotic behavior as $k \to \infty$. For this we first define, for any $\frac{1}{2} < \alpha < \frac{3}{4}$,
-\begin{equation}\label{eq:def_C_alpha}
-	C_\alpha = \frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha-1)^2} 
-	+ \frac{\alpha - \frac{1}{2}}{2(\alpha - 1)\alpha} B^-(\frac{1}{2},2\alpha + 1, 2\alpha - 2)
-	- \frac{1}{4(\alpha - 1)}B(2\alpha, 3\alpha - 4).
-\end{equation}
-Moreover, to simplify the statement we define the scaling function 
-\begin{equation}\label{eq:def_scaling_function}
-s_\alpha(k) = \begin{cases} 
-		k^{4\alpha-2} &\frac{1}{2}<\alpha<\frac{3}{4}, \\
-		\frac{k}{\log(k)} & \alpha = \frac{3}{4}, \\
-		k &\alpha > \frac{3}{4}.
-\end{cases}
-\end{equation}
-\TM{ These exponents are $>0$! (see next comment)}
-
-We now have the following result, where the constant $C_\alpha$ emerges when we consider the local clustering function for $\frac{1}{2} < \alpha < \frac{3}{4}$.
-
-\begin{theorem}[Asymptotic behavior of local clustering function limit]\label{thm:asymptotics_average_clustering_P}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then,
-\[
-	\lim_{k \to \infty} \frac{c_\infty(k)}{s_\alpha(k)} 
-	= \begin{cases}
-			C_\alpha \left(\frac{4\alpha \nu}{\pi\left(2\alpha - 1\right)}\right)^{4\alpha - 2}
-			&\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
-			\frac{3 \nu}{\pi} &\mbox{if } \alpha = \frac{3}{4},\\
-			\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha > \frac{3}{4},
-	\end{cases}
-\]
-with $C_\alpha$ as defined in \eqref{eq:def_C_alpha}.
-\end{theorem}
-\TM{ There is a typo here. Since you divide by $s$ in this last thm and $s\to\infty$ as the exponents are $>0$ and clustering coefficients are $\in [0,1]$, you would get limiting value zero. }
-\TM{ Also, I dont know if this previous result really deserves the status of ``theorem''. Feels more like a lemma or proposition. } 
-The following is an immediate consequence of Theorem~\ref{thm:local_clustering_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
-
-\begin{corollary}[Asymptotic behavior of local clustering function in $G_{\H,n}(\alpha,\nu)$]
-\label{cor:asymptotic_local_clustering_hyperbolic}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$, $(k_n)_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ and $s_\alpha(k)$ defined as in~\eqref{eq:def_scaling_function}.
-Then, as $n \to \infty$,
-\[
-	\frac{c_{\H,n}(k_n)}{s_\alpha(k_n)} \, \stackrel{L^1}{\rightarrow} \, 
-	\begin{cases}
-				C_\alpha \left(\frac{4\alpha \nu}{\pi\left(2\alpha - 1\right)}\right)^{4\alpha - 2}
-				&\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
-				\frac{6\nu}{\pi} &\mbox{if } \alpha = \frac{3}{4},\\
-				\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} &\mbox{if } \alpha > \frac{3}{4},
-		\end{cases}
-\]
-where $\stackrel{L^1}{\to}$ denotes convergence in expectation.
-\end{corollary}
-
-\TM{ I had not heard of ``convergence in expectation'' before this. I have heard of $L_1$-convergence though. }
-\MS{@Pim: Are you sure all constants are correct? I thought for $\alpha = 3/4$ it might be $6\nu/\pi$. But if you are sure, you can remove this comment of course.}
-\PvdH{@Markus: You might be right. I have updated it and we will later check if you were right.}
-
-This result completely \TM{ ``completely" is pretty strong. Note also we seem to stay away from 
-$k = \Theta( n^{1/(2\alpha+1)} )$. So unless we change that, there is reason to say we do not to it ``completely''.} 
-characterizes the asymptotic behavior of the local clustering function in Hyperbolic Random Graphs.
-In particular we observe that the conjectured scaling of $k^{-1}$ from~\cite{krioukov2010hyperbolic} only occurs when $\alpha > 3/4$, or equivalently, when the exponent of the pdf of the degree distribution is larger than $5/2$.
-
-A major part of this paper is dedicated to prove the convergence result in Theorem~\ref{thm:local_clustering_hyperbolic}, which is based on a sequence of subsequent results for the local clustering function in related random graph models and Theorem~\ref{thm:asymptotics_average_clustering_P}.
-The exact flow of the argument is explained in Section \ref{sec:proof_outline}.
-The proof for the convergence result in Theorem~\ref{thm:local_clustering_hyperbolic}, using these results, can be found in Section \ref{ssec:proof_main_results}.
-Here we also give the proof of the convergence result in Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
-Another major part of this paper is the exact computation of the local clustering coefficient and function limit $c_\infty$ and $c_\infty(k)$, which involves careful computations of several involved integrals.
-This is done in Section~\ref{sec:asymptotics_average_clustering_ast_P}, where we also prove Theorem~\ref{thm:asymptotics_average_clustering_P}.
-
-We end this section with some important observations regarding local clustering in hyperbolic random graphs.
-
-\PvdH{Populate these paragraphs}
-
-\paragraph{Uniform convergence}
-
-Our results for the local clustering function in particular imply uniform convergence of $c_{\H,n}(k)$ for all $3 \le k \le a_n$ \TM{ Why 3?
-} where $a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
-To see this let
-\[
-	b_n = \arg \max_{3 \le k \le a_n} \Exp{\left|\frac{c_{\H ,n}(k)}{c_\infty(k)} - 1\right|}.
-\]
-Then $b_n \le a_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ and therefore by Theorem~\ref{thm:local_clustering_hyperbolic}
-\[
-	\lim_{n \to \infty} \max_{3 \le k \le a_n} \Exp{\left|\frac{c_{\H ,n}(k)}{c_\infty(k)} - 1\right|} 
-	= \lim_{n \to \infty}\Exp{\left|\frac{c_{\H ,n}(b_n)}{c_\infty(b_n)} - 1\right|} = 0.
-\]
-The same is true for the result in Corollary~\ref{cor:asymptotic_local_clustering_hyperbolic}.
-
-\paragraph{Maximum scaling for $k_n$ is $n^{\frac{1}{2\alpha +1}}$}
-All our results for clustering in the hyperbolic random graph are valid for any sequence $k_n$ such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$.
-Although one would like to have results for any sequence $k_n \le n$, it turns out that $n^{1/(2\alpha + 1)}$ is the optimal \TM{ again seems to strong to me } scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
-To see why this is the case note that by definition of the local clustering function~\eqref{eq:def_local_clustering_general} we have that $c_{\H,n}(k_n) = 0$ if $N_{\H,n}(k_n) = 0$.
-Hence, it follows by Markov's inequality that for any positive function $f$
-\begin{align*}
-	\Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|} 
-	&\ge \Prob{N_{\H,n}(k_n) = 0} \ge 1 - \Exp{N_{\H,n}(k_n)}.
-\end{align*}
-We shall later establish (see Lemma~\ref{lem:N_k_H_P}) that $\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}$.
-Therefore if $k_n$ is such that $k_n^{-(2\alpha + 1)} n$ tends to zero as $n \to \infty$ we have that
-\[
-	\lim_{n \to \infty} \Exp{N_{\H,n}(k_n)} = 0
-\]
-and hence
-\[
-	\lim_{n \to \infty} \Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|} 
-	\ge \lim_{n \to \infty} 1 - \Exp{N_{\H,n}(k_n)} = 1 \ne 0,
-\]
-for any positive function $f$.
-This implies that we cannot expect a result like that of Theorem~\ref{thm:clustering_coefficient_hyperbolic} to hold as soon as $k_n$ is not $\smallO{n^{\frac{1}{2\alpha + 1}}}$.
-
-\paragraph{Transition in the scaling of local clustering}
-
-\MS{@All: If we can, then it would be interesting to remark that there is this phase transition in $\alpha$ which appears when the power-law exponent is $2.5=\frac{5}{2}$ and it would be cool if we could give a brief intuitive reason for that or mention that this phase transition point has also been observed in other contexts/models etc.}
-
-\PvdH{@All: I agree with Markus.
-It would be nice to say something on this.
-Maybe we can leave it out of the first arXived version and in the mean time do some research on this.
-We could also ask Remco van der Hofstad.}
-
-\TM{ \RD{\bf VERY IMPORTANT:} we need to appropriately cite the vdHofstad-vLeeuwaarden-Stegehuis crew.
-We want to avoid a war.
-(Just between you and me : I do kind of feel theirs is pretty much non-rigorous though.
-I am not sure if there is some way to say their work is ``non-rigorous'' without offending them.) }
-
-\subsection{Simulations}\label{ssec:simulations}
-
-\TM{ I think the most important simulation to include is for the ``overall'' clustering coefficient $c(G)$. 
-Can someone please add that? \\
-(The value of $k$ in Figs 2 and 3 seems a bit arbitrary to me btw.) }
-
-The simulations of this section (see Figures \ref{fig:c2allnu}, \ref{fig:c4allnu} and \ref{fig:ckvariable}) confirm \TM{ ``confirm" is too strong.
-Simulations ``seem to be in agreement with the formulas".
-} the formulas from the result section.
-The simulations were obtained by generating the hyperbolic random graph for a given choice of the parameters and number of repetitions and then taking the average over all simulation instances.
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{figures/sim0123c2nualln1000rep20.pdf}
-    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n= 2$, for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=1000$ and 20 repetitions.}
-    \label{fig:c2allnu}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{figures/sim0128c4nualln10000rep20.pdf}
-    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n= 4$, for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10 000$ and 20 repetitions.}
-    \label{fig:c4allnu}
-\end{figure}
-\begin{figure}
+\noindent
+A plot of $\gamma(k)$ can be found in Figure~\ref{fig:gammak}. %
+%
+%
+\begin{figure}[h!]
     \centering
     \includegraphics[scale=0.6]{figures/sim1024ck225n10000a0609nu2rep20.pdf}
-    \caption{Simulation of $c_{\mathbb{H},n}(k_n)$ for $k_n$ varying from 2 to 26 on the horizontal axis, for $\nu=2$ and $\alpha=0.6$ (green) and $\alpha=0.9$ (blue); simulations (red dots) with $n=10 000$ and 20 repetitions.}
-    \label{fig:ckvariable}
-\end{figure}
+    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 26 on the horizontal axis, for $\nu=2$ and $\alpha=0.6$ 
+    (green) and $\alpha=0.9$ (blue); simulations (red dots) with $n=10000$ and 20 repetitions.\label{fig:gammak}}
+\end{figure}%
+%
+Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a
+removable singularity. Again we have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but
+in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
 
-\TM{ We may want to put the source code in an appendix.
-In fact RuG now officially requires we deposit the source code in some archive. (gasp.) }
+Theorem~\ref{thm:mainkfixed} in fact generalises to increasing sequences $(k_n)_n$.
+
+\begin{theorem}\label{thm:mainktoinfty}
+Let $\alpha>\frac12, \nu>0$ be fixed and let $k_n$ be a sequence 
+satisfying $1 \ll k_n \ll n^{1/(2\alpha+1)}$. Then, writing $G_n := G(n;\alpha,\nu)$, we have
+\[
+	\E[|c(k_n;G_n)-\gamma(k_n)|] = \smallO{\gamma(k_n)},
+\]
+as $n \to \infty$, where $\gamma(.)$ is as in Theorem~\ref{thm:mainkfixed}.
+\end{theorem}
+
+In particular, Theorem~\ref{thm:mainktoinfty} implies that
+\[
+	\frac{c(k_n; G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{L^1} 1,
+\]
+so that the clustering function if the KPKVB model scales as $\gamma(k)$ as $k$ grows.
+
+%We remark that the number of vertices of degree exactly $k$ satisfies $N_k = 0$ a.a.s.~when $k \gg n^{1/(2\alpha+1)}$, see~\TM{ add reference to correct thm / lemma here! }.
+%So the range in the above result is essentially to best possible.
+
+\subsubsection{Scaling of $\gamma(k)$}
+
+To clarify the scaling behaviour of $\gamma(k)$ with $k$ we offer the following result.
+
+\begin{proposition}\label{prop:asymp}
+As $k\to\infty$, we have
+
+$$ \gamma(k) = 
+(1+o(1)) \cdot \left\{ \begin{array}{cl}
+\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} \cdot k^{-1} &\text{ if } \alpha > \frac{3}{4}, \\
+\frac{6 \nu}{\pi} \cdot \frac{\log \log (k/\xi)}{k}& \text{ if } \alpha = \frac{3}{4},\\
+ c_{\alpha} \cdot k^{2-4\alpha} & \text{ if } \frac12 < \alpha < \frac34, 
+\end{array} \right.,
+$$
+where $c_{\alpha} := \left( \frac{3\alpha - 1}{2^{4\alpha+1}\alpha(\alpha-1)^2} 
+	+ \frac{(\alpha - \frac{1}{2})B^-(\frac{1}{2},2\alpha + 1, 2\alpha - 2)}{2(\alpha - 1)\alpha} 
+	- \frac{B(2\alpha, 3\alpha - 4)}{4(\alpha - 1)} \right)  \cdot \xi^{4\alpha-2}$.
+\end{proposition}
+
+In particular this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac34$, and confirms it for $\alpha > \frac34$.
+
+We remark that simultaneously and independently Stegehuis, van der Hofstad and van Leeuwaarden~\cite{stegehuis2018scale} found a similar, but less detailed result on the $k\to\infty$ scaling of the clustering function in the KPKVB model.
+
+\PvdH{I really think we should add a subsection where we discuss the results and their implications.
+Especially the addition $\log(k)$ term for degree distribution exponent $5/2$, and the fact that $n^{1/(2\alpha _ 1)}$ is the best scaling possible for $c(k_n; G_n)$.}
+
+\subsection{Outline of the paper}
+
+In the next section we will recall some useful tools from the literature and define a series of auxiliary random graph models that will be used in the proofs.
+In particular, we relate in a series of steps the KPKVB model to an infinite percolation model $\Ginf$ that was used in previous work of the first and third authors~\cite{fountoulakis2018law} on the largest component of the KPKVB model.
+The value of the limiting constant $\gamma$, respectively limiting clustering function $\gamma(k)$, correspond to the probability that two randomly chosen neighbours of a ``typical point'' in this infinite model are themselves neighbours, respectively the probability of this event conditional on the typical point having exactly $k$ neighbours.
+These probabilities can be expressed as certain integrals, which we solve explicitly in Section~\ref{sec:Ginf}.
+In the same section we also prove Proposition~\ref{prop:asymp}, on the asymptotics of $\gamma(k)$.
+We then proceed to prove Theorems~\ref{thm:maincc} and~\ref{thm:mainkfixed} by relating said probabilities for the typical point of the infinite model to the corresponding clustering coefficient/function in the original KPKVB random graph, using the Campbell-Mecke formula and some other, relatively straightforward considerations.
+
+The remaining sections are devoted to the proof of Theorem~\ref{thm:mainktoinfty}, which turns out to be a lot more involved.

### 2019-02-05 paper.tex
updated notation and added comments to sections 1-3

@@
 
+%\usepackage{showkeys}
 \usepackage{tocloft}
@@
 
-\newcommand{\plim}{\ensuremath{\stackrel{\pr}{\rightarrow}}}	%	Convergence in probability
+\newcommand{\plim}{\ensuremath{\xrightarrow{\Pee}}}	%	Convergence in probability
 \newcommand{\dlim}{\ensuremath{\stackrel{d}{\rightarrow}}}		%	Convergence in distribution
@@
 
-\newcommand{\BallHyp}[1]{\Bcal_{\H,n}\left(#1\right)}		%	The image of the hyperbolic ball around \Psi^{-1}(p)
-\newcommand{\BallPo}[1]{\Bcal_{\Pcal}\left(#1\right)}		%	The neighborhood of a point p in the infinite limit model
-\newcommand{\BallPon}[1]{\Bcal_{\Pcal,n}\left(#1\right)}	%	The neighborhood of a point p in the finit box model
+\newcommand{\BallHyp}[1]{\Bcal\left(#1\right)}		%	The image of the hyperbolic ball around \Psi^{-1}(p)
+\newcommand{\BallPo}[1]{\Bcal_{\infty}\left(#1\right)}		%	The neighborhood of a point p in the infinite limit model
+\newcommand{\BallPon}[1]{\Bcal_{\text{box}}\left(#1\right)}	%	The neighborhood of a point p in the finit box model
 \newcommand{\FatBallHyp}[1]{\check{\Bcal}_{\H,n}(#1)}		%
@@
 
-\newcommand{\Mu}[1]{\mu_{\alpha,\nu}\left(#1\right)}
+\newcommand{\Mu}[1]{\mu\left(#1\right)}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Don't mess with the tobimacros !!!!!							  %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\eR}[0]{\ensuremath{{\mathbb R}}}
+\newcommand{\eN}[0]{\ensuremath{{\mathbb N}}}
 \newcommand{\Ee}[0]{\ensuremath{{\mathbb E}}}
+\newcommand{\Haa}{\ensuremath{{\mathbb H}}}
+\newcommand{\GPo}[0]{\ensuremath{G_{\text{Po}}}}
+\newcommand{\Gbox}[0]{\ensuremath{G_{\text{box}}}}
+\newcommand{\Ginf}[0]{\ensuremath{G_{\infty}}}
+\newcommand{\isd}{\stackrel{\text{d}}{=}}
+\newcommand{\Xcal}{\ensuremath{{\mathcal X}}}
+\newcommand{\Ycal}{\ensuremath{{\mathcal Y}}}
+\newcommand{\Qcal}{\ensuremath{{\mathcal Q}}}
+\newenvironment{proofof}[1]{\vspace{1ex}\noindent{\bf Proof of #1:}}{\hspace*{\fill}$\blacksquare$\vspace{1ex}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title{Exact asymptotic expressions for local clustering in a hyperbolic model of complex networks.
-\\ \TM{ I prefer not to use the term ``hyperbolic random graph".
-Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}\PvdH{I am not really a fan of the term KPKVB random graph so I implemented the second suggestion.}}
-\author[1]{Nikolaos Fountoulakis}
-\author[2]{Pim van der Hoorn}
-\author[3]{Tobias M\"{u}ller}
-\author[3]{Markus Schepers}
+\title{Clustering in a hyperbolic model of complex networks.}
+\author[1]{Nikolaos Fountoulakis\thanks{Research partially supported by the Alan Turing Institute, grant no. EP/N510129/1.}}
+\author[2]{Pim van der Hoorn\thanks{Research partially supported by ARO Grant W911NF-16-1-0391 and W911NF-17-1-0491}}
+\author[3]{Tobias M\"{u}ller\thanks{Research partially supported by NWO grants 639.032.529 and 612.001.409.}}
+\author[3]{Markus Schepers\thanks{Research partially supported by NWO grant 639.032.529.}}
 
-\affil[1]{University of Birmingham, School of Mathematics, United Kingdom}
-\affil[2]{Northeastern University, Department of Physics, United States}
-\affil[3]{University of Groningen, Bernoulli Institute for Mathematics, Computer Science and Artificial Inteligence, The Netherlands}
+\affil[1]{ School of Mathematics, University of Birmingham, United Kingdom.}
+\affil[2]{Department of Physics, Northeastern University, United States.}
+\affil[3]{Bernoulli Institute, University of Groningen, The Netherlands.}
 
@@
 \begin{abstract}
-\PvdH{The abstract will be written at the end.}
+In this paper we consider the clustering coefficient, and clustering function in a random graph model proposed by Krioukov et al.~in 2010.
+In this model, nodes are chosen randomly inside a disk in the hyperbolic plane and two nodes are connected if they are at most a certain hyperbolic distance from each other.
+It has been previously shown that this model has various properties associated with complex networks, including a power-law degree distribution, ``short distances'' and a non-vanishing clustering coefficient.
+The model is specified using three parameters: the number of nodes $n$, which we think of as going to infinity, and $\alpha, \nu > 0$, which we think of as constant.
+Roughly speaking $\alpha$ controls the power law exponent of the degree sequence and $\nu$ the average degree.
+
+Here we show that the clustering coefficient tends in probability \PvdH{Should we state here that convergence is in the stronger notion of expectation ($L_1$)?} to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
+This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant.
+Similarly, we are able to show that $c(k)$, the average clustering over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ given explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
+We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$.
+Our results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should scale with $k^{-1}$ as we let $k$ grow.
+We find that this is true only when $\alpha > \frac34$, while $\gamma(k) = \Theta( k^{2 - 4\alpha})$ if $\alpha < \frac34$ and $\gamma(k) = \Theta( \log(k) / k )$ if $\alpha=\frac34$.
 \end{abstract}
@@
 \newpage
+
+\PvdH{We need to fix the missing references. In addition, I have noticed the use of UK English grammar, which I do not often encounter in papers I read. Is there a specific reason for using this?}
 
@@
 
+\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering and helpful discussions.
+
 \bibliographystyle{plain}

### 2019-02-05 proof_overview_finite_k.tex
updated notation and added comments to sections 1-3

@@
-\section{Overview of the proof strategy for fixed $k$}\label{sec:proof_outline}
+\section{Preliminaries\label{sec:proof_outline}}
 
-\PvdH{This section has to be adjusted to include the right references to the new theorems where fixed and diverging $k$ have been separated.}
+In this section we recall some definitions and tools that we will need in our proofs.
 
-The key result in this paper is Theorem~\ref{thm:local_clustering_hyperbolic}.
-In particular, it is the key ingredient in the proofs of Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:asymptotics_average_clustering_P}.
-\TM{ Sounds weird, since Thm 1.3 is just about asymptotics of certain functions. }
+\subsection{The infinite limit model $\Ginf$\label{ssec:infinite_model}}
 
-\begin{remark}[Model parameters]
-Throughout the remainder of this paper, unless otherwise specified, $\alpha$ and $\nu$ will be real numbers satisfying $\alpha > 1/2$ and $\nu > 0$.
-\end{remark}
+We start by recalling the definition of the infinite limit model from~\cite{fountoulakis2018law}.
+Let $\mathcal{P}=\mathcal{P}_{\alpha,\nu}$ 
+be a Poisson point process on $\eR^2$ with intensity function $f=f_{\alpha,\nu}$ given by
 
-Our approach builds on the work in~\cite{fountoulakis2018law}, where tools were developed to analyze the size of the largest component in the hyperbolic model which can be reused here.
-The main idea is to couple the hyperbolic graph $G_{\H, n}(\alpha, \nu)$ with a finite subgraph $G_{\Pcal,n}(\alpha,\nu)$ of an infinite graph $G_\Pcal(\alpha,\nu)$ whose nodes are given by a Poisson Point Process (see Section~\ref{ssec:infinite_model}).
-The infinite graph will then yield the limit expressions for the local clustering coefficient and function.
-\TM{ The Komjathy paper used GIRG, which is fishy. So I say we do not cite that. }
-%and in \cite{komjathy2018explosion} to analyze explosion %times in a more general class of models. 
-The advantage of the infinite limit model is two-fold.
-Firstly, it simplifies the actual computations, e.g.
-by replacing hyperbolic densities with exponential densities and the hyperbolic distance with a computationally easier expression.
-Secondly, it directly yields the limit as a result as opposed to some long expression depending on $n$.
-
-Very roughly, the proof falls into four parts: 1) replacing the randomly sampled nodes in the hyperbolic graph with a Poisson Point Process, 2) justifying the transitioning from this Poisson version of the hyperbolic random graph to the finite model, 3) show that the limit expression correspond to those in the infinite model and finally 4) calculating the expected local clustering coefficient and function in the infinite limit model.
-\PvdH{@Tobias and Markus: Please include the references to the new theorems for fixed $k$.} This strategy is executed in Section~\ref{sec:proofs_fixed_k} where we prove Theorems [??].
-
-In this section, we define both the infinite and finite model.
-We then explain how to transition from local clustering in the finite to the infinite model.
-Finally, we describe the coupling between our finite model and the hyperbolic model and show how this coupling allows us to relate local clustering between them.
-
-We start with some small notational conventions.
-
-\subsection{Notations}
-We adopt standard Landau notations for asymptotic statements. For two functions $f$ and $g$ we write $f(x) = \bigO{g(x)}$ as $x \to \infty$ if
-\[
-	\limsup_{x \to \infty} \frac{|f(x)|}{g(x)} < \infty,
-\]
-while $f(x) = \smallO{g(x)}$ as $x \to \infty$ means
-\[
-	\lim_{x \to \infty} \frac{f(x)}{g(x)} = 0,
-\]
-and $f(x) = \bigT{g(x)}$ as $x \to \infty$ whenever
-\[
-	\limsup_{x \to \infty} \left|\frac{f(x)}{g(x)}\right| > 0 \quad \text{and} \quad
-	\limsup_{x \to \infty} \frac{|f(x)|}{g(x)} < \infty.
-\]
-Moreover we will write $a \vee b$ for $\max\{a,b\}$ and $a \wedge b$ for $\min\{a,b\}$.
-
-\subsection{Infinite limit model}\label{ssec:infinite_model}
-
-To define the infinite graph $G_{\mathcal{P}}(\alpha, \nu)$ write $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and let $\mathcal{P}=\mathcal{P}_{\alpha,\nu}$ be a Poisson point process on $\Rcal$ with intensity function
 \begin{equation}\label{eq:def_intensity_function_f}
-	f_{\alpha,\nu}(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y}.
-\end{equation} 
-We will write $p = (x, y)$ for points in $\Rcal$.
-In addition we denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu_{\alpha, \nu}$, i.e.
-for every Borel-measurable subset $S \subseteq \mathbb{R} \times \mathbb{R}_+$
-\begin{equation}\label{eq:def_mu_P}
-	\mu_{\alpha,\nu}(S) = \int_S f_{\alpha,\nu}(x,y) \, dx \, dy,
+	f(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y} \cdot 1_{\{y>0\}}.
 \end{equation}
 
-The \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
+The \emph{infinite limit model} $\Ginf = \Ginf(\alpha,\nu)$ has vertex set $\mathcal{P}$ and edge set such that
 \[
-	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
+	pp' \in E(\Ginf) \iff |x - x'| \leq e^{\frac{y + y'}{2}},
 \]
+for $p=(x,y),p'=(x',y')\in\Pcal$.
+
 For any point $p \in \Rcal$, we write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
+
 \begin{equation}\label{eq:def_ball_P}
-	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
+	\BallPo{p} = \{p^\prime \in \eR\times[0,\infty) : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
 \end{equation}
-With this notation we then have that $\BallPo{p} \cap \PPP$ denotes the set of neighbors of a vertex $p \in G_{\Pcal}(\alpha,\nu)$.
 
-\begin{remark}[Notations for points]\label{rmk:point_notation}
-We will be working extensively with expressions in terms of points of $\Pcal_{\alpha, \nu}$, often relating them back to points in the hyperbolic disc $\Dcal_{\Rcal_n}$.
-Therefore, in the remainder of this paper we will always use $u = (r,\theta)$ to denote points in $\Dcal_{\Rcal_n}$ in polar coordinates while $p = (x,y)$ will denote points in $\Rcal := \mathbb{R} \times \mathbb{R}_+$ in Cartesian coordinates.
-In addition, when we write $p^\prime \in \mathbb{R} \times \mathbb{R}_+$ we will denote its Cartesian coordinates by $(x^\prime, y^\prime)$ and similarly for $p_i$, $u^\prime$ and $u_i$, e.g.
-$p_i = (x_i, y_i)$.
-In addition, for a point $p = (x,y)$, we will refer to $y$ as the \emph{height} of $p$.
-\end{remark}
+With this notation we then have that $\BallPo{p} \cap \Pcal$ denotes the set of neighbors of a vertex $p \in \Ginf$.
+We will denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu = \mu_{\alpha, \nu}$, i.e. for every 
+Borel-measurable subset $S \subseteq \eR^2$ we have $\mu(S) = \int_S f(x,y) \, dx \, dy$
 
-%To analyze the limiting expressions for clustering in the finite random graph $G_{\Pcal,n}(\alpha, \nu)$ we shall use an infinite graph model which can be understood as taking the finite graph $G_{\Pcal,n}(\alpha,\nu)$ and taking $n \to \infty$.
-Recall that $\Rcal = \mathbb{R} \times \mathbb{R}_+$ and that $\mathcal{P}_{\alpha,\nu}$ is a Poisson point process on $\Rcal$ with intensity function
-%\[
-%	f_{\alpha,\nu}(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y}.
-%\]
-%
-%The \emph{infinite limit model} $G_{\mathcal{P}}(\alpha, \nu)$ is defined to have vertex set $\mathcal{P}$ and edge set such that
-%\[
-%	(p_i, p_j) \in E(G_{\mathcal{P}}(\alpha, \nu)) \iff |x_i - x_j| \leq e^{\frac{y_i + y_j}{2}}.
-%\]
-%For a point $p \in \Rcal$, we will write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
-%\begin{equation}\label{eq:def_ball_P}
-%	\BallPo{p} = \{p^\prime \in \Rcal : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
-%\end{equation}
+\subsection{The finite box model $\Gbox$\label{ssec:finite_model}}
 
-\subsection{Finite box model}\label{ssec:finite_model}
+For the definition of the finite graph, recall that in the definition of the KPKVB model we set $R = 2\log(n/\nu)$.
+We consider the box $\Rcal = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2}e^{R/2}] \times (0, R]$ in $\eR^2$. 
+Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\mathcal{V} := \mathcal{P} \cap \Rcal$ and edges set such that
+\[
+	pp' \in E(\Gbox(n;\alpha, \nu)) \iff |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}},
+\]
+where $|x|_{r} = \min( |x|, r - |x|)$ for $-r\leq x\leq r$. 
+Using $|.|_{\pi e^{R/2}}$ instead of $|.|$ results in the left and right boundaries of the box $\Rcal$ getting 
+identified, which in particular 
+%excludes boundary effects and 
+makes the model invariant under horizontal shifts and reflections in vertical lines. 
+The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\mathcal{V}_n$, with some addition edges caused by 
+the identification of the boundaries.
 
-For the definition of the finite graph, recall that $R_n = 2\log(n/\nu)$ and consider the finite box $\Rcal_n = (-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}] \times (0, R_n]$ in $\Rcal$.
-Then the \emph{finite box model} graph $G_{\mathcal{P},n}(\alpha, \nu)$ has vertex set $\mathcal{V}_n := \mathcal{P}_{\alpha, \nu} \cap \Rcal_n$ and edges set such that
-\[
-	(p_i, p_j) \in E(G_{\mathcal{P},n}(\alpha, \nu)) \iff |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}},
-\]
-where $|x|_{\pi e^{R_n/2}} = \inf_{k \in \mathbb{Z}} |x + k \pi e^{R_n/2}|$.
-This norm means that the boundaries of $(-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}]$ are identified, which is done to exclude boundary effects and make the model invariant under horizontal translation and reflections in vertical lines.
-The graph $G_{\mathcal{P},n}(\alpha, \nu)$ can thus be seen as a subgraph of $G_{\mathcal{P}}(\alpha, \nu)$ induced on $\mathcal{V}_n$, with some addition edges caused by the identification of the boundaries.
+Similar to the infinite graph, for a point $p \in \Rcal$ we define the ball $\BallPon{p}$ as
 
-Similar to the infinite graph, for a point $p \in \Rcal_n$ we define the ball $\BallPon{p}$ as
 \begin{equation}\label{eq:def_ball_P_n}
 	\BallPon{p} = 
-	\left\{p^\prime \in \Rcal_n : |x_i - x_j|_{\pi e^{R_n/2}} \leq e^{\frac{y_i + y_j}{2}}\right\}.
+	\left\{p' \in \Rcal : |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}}\right\}.
 \end{equation}
 
-\subsection{Properties of the infinite graph model}
+\subsection{The Poissonized KPKVB model $\GPo$}
 
-\PvdH{@Tobias: please see if you agree with this setup.} 
-The main utility of the infinite graph $G_\Pcal(\alpha, \nu)$ is that we can use it to express limits of properties in the finite model, and eventually the hyperbolic random graphs.
-To this end we add a "typical" point $p_0 := (0,y) \in \Rcal$, with height $y$ exponentially distributed with rate $\alpha$, and then generate the Poisson Point Process $\Pcal_{\alpha, \nu}$ independently of $y$.
-Technically, the vertex set of $G_\Pcal(\alpha,\nu)$ then becomes $\Pcal_{\alpha, \nu} \cup p_0$.
+Imagine that we have an infinite supply of i.i.d.~points $p_1, p_2, \dots$ in the hyperbolic plane $\Haa$ chosen according to the $(\alpha, R)$-quasi uniform distribution.
+In the standard KPKVB random graph $G(n;\alpha,\nu)$ we take $p_1,\dots, p_n$ as our vertex set and add edges between points at hyperbolic distance at most $R = 2\log(n/\nu)$.
+In the {\em Poissonized} KPKVB random graph $\GPo := \GPo(n;\alpha,\nu)$, we instead take $N\isd \Po(n)$, a Poisson random variable
+with mean $n$, independent of our i.i.d.~sequence of points and let the vertex set be $p_1,\dots, p_N$ and add edges 
+according to the same rule as before.
+Equivalently, we could say that the vertex set consists of the points of a Poisson point process with intensity function $n g$, where $g$ denotes the probability density of the $(\alpha,R)$-quasi uniform distribution.
+That is,
+\[
+	g(r,\theta) = \frac{\alpha\sinh(\alpha r)}{2\pi(\cosh(\alpha R) - 1)} \cdot 1_{\{0\leq r\leq R, -\pi<\theta\leq \pi\}}.
+\]
 
-A very useful tool to analyze expressions in the both the finite and infinite model is the \emph{Campbell-Mecke Formula}~\cite[Theorem 3.2]{baddeley2007spatial}, which states that for a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and any measurable function $h : S \mapsto \R$,
-\begin{equation}\label{eq:def_Campbell-Mecke}
-	\Exp{\sum_{p \in \Pcal} h(p)} = \int_S \Exp{h(x)} \dd \lambda(x)
-\end{equation}
-In essence the results tells us that taking averages of a function over points in a Poisson Points Process simply to integrating the function with respect to the intensity measure.
-This transformation of summations into integrals is very powerful and we will use this to derive expressions for the degrees and local clustering in the infinite model.
-%For a Poisson point process $\mathcal{P}$ on a measurable space $S$ with intensity $\lambda$ and a measurable non-negative function $h: S^r \rightarrow \mathbb{R}$ \TM{ Below there is one more argument.
-(a set) } we have
-%\begin{equation}\label{eq:def_Campbell-Mecke}
-%\begin{aligned}
-%& \Exp{\sum_{x_1,\ldots, x_r \in \mathcal{P}}^{\neq} h (x_1, \ldots, x_r,
-%\mathcal{P} \setminus \{x_1,\ldots, x_r\}) }\\
-%& = \int_S \cdots \int_S
-%\Exp{h(x_1,\ldots, x_r,\mathcal{P} \setminus \{x_1,\ldots, x_r\}) \lambda (x_1) \cdots \lambda (x_r) dx_1 \cdots dx_r},
-%\end{aligned}
-%\end{equation}
-%where the sum ranges over all distinct $r$-tuples of points of $\mathcal{P}$.
-\TM{ Are you sure this is the Mecke formula?
-}\PvdH{This was indeed incorrect.
-It is the extended Slivnyak-Mecke theorem.}
+Working with the Poissonized model has the advantage that when we take two disjoint regions $A, B$ then the number of points in $A$ and the number of points  in $B$ are independent Poisson-distributed random variables.
+As we will see, and as is to be expected, switching to the Poissonized model does not significantly alter the limiting behaviour of the clustering coefficient and function.
 
-\paragraph{Degrees}
-If we fix a $y \in \R_+$, then it follow from~\eqref{eq:def_Campbell-Mecke} that the expected number of points in $\BallPo{(0,y)}$ is given by
-\[
-	\Exp{\sum_{p \in \Pcal} \ind{p \in \BallPo{(0,y)}}} = \mu_{\alpha, \nu}(\BallPo{(0,y)}), 
-\] 
-which can be computed as,
-\begin{equation}\label{eq:mu_ball_y_P}
-	\mu_{\alpha, \nu}(\BallPo{(0,y)}) =  \int_0^\infty \int_{-\infty}^\infty \ind{|x^\prime|\le e^{(y + y^\prime)/2}} 
-	f_{\alpha,\nu}(x^\prime,y^\prime) \dd x^\prime \dd y^\prime
-	= \frac{4\alpha \nu}{(2\alpha - 1)\pi} e^{\frac{y}{2}} := \xi_{\alpha,\nu}e^{\frac{y}{2}}.
-\end{equation}
+\subsection{Coupling $\GPo$ and $\Gbox$\label{ssec:coupling_H_P}}
 
-We shall write $\rho(p,k)$ and $\rho(y,k)$ (for a point $p=(x,y) \in \mathcal{R}$) to denote the probability mass function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(\BallPo{p})$, i.e.
-\[
-	\rho(p,k) = \rho(y,k) = \Prob{\Po\left(\xi_{\alpha,\nu} e^{y/2}\right) = k}.
-\]
-Let us denote by $D_\Pcal$ the degree of the typical vertex $p_0$ in $G_\Pcal(\alpha,\nu)$.
-Then, since the number of points in $\BallPo{p_0}$ is a Poisson random variable with mean $\Mu{\BallPo{p_0}}$, the distribution of $D_\Pcal$ conditioned on the height $y$ is given by $\rho(y,k)$.
-Therefore, the degree distribution of the typical point is
-\[
-	\Prob{D_\Pcal = k} = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y,
-\]
-which again can be explicitly computed, see Section~\ref{ssec:degrees_infinite_model}.
-
-\begin{remark}[Degree distributions in the other models]
-Similar to the infinite graph, we will consider the degree of a typical point in a Poisson version of the hyperbolic graph $G_{\HP,n}$ and the finite random graph $G_{\Pcal,n}$.
-These will again be distributed as a Poisson random variable with given means and, following the notation above, we will denote these distributions by $\rho_{\HP,n}(y,k)$ and $\rho_{\Pcal,n}(y,k)$.
-\end{remark}
-
-\paragraph{Local clustering}
-We can also define a local clustering coefficient and function in the infinite model. 
-%However, since $G_\Pcal$ has an infinite number of nodes the corresponding definitions are slightly different than for the finite size models.
-Intuitively the local clustering coefficient is the probability that two random neighbors of a randomly sampled node form a triangle , while the local clustering function is the same probability but conditioned on the sampled node having degree $k$.
-\TM{ again "randomly sampled" does not immediately make sense here.
-You may want to say we generate a point $(0,y)$ with $y$
-%exponential $\alpha$ distributed and add this to the PPP, which is generated indeptly of $y$.} 
-%
-%Again, due to symmetry in the $x$ direction we can assume without loss of generality that a randomly sampled point $p$ is $(0,y)$. 
-For any $y \in \R_+$ we define the probability density function $\eta_y$ on $\Rcal :=  \R \times \R_+$ by  
-\begin{equation}\label{eq:def_eta_P}
-	\eta_y(x^\prime, y^\prime) = \frac{\ind{p^\prime \in \BallPo{(0,y)}} f_{\alpha,\nu}(x^\prime,y^\prime)}{\mu_{\alpha,\nu}(\BallPo{(0,y)})}.
-\end{equation}
-That is $\eta_y$ is the density $f_{\alpha,\nu}$ restricted to the ball $\BallPo{(0,y)}$, properly normalized to make it a probability distribution.
-It can be interpreted as the probability density of a randomly sampled point in $\BallPo{(0,y)}$, i.e.
-a randomly sampled neighbor of $(0,y)$ in the infinite model.
-
-We then define
-\begin{equation}\label{eq:def_delta_p}
-	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(y, x_1, x_2, y_1, y_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \dd x_1 \dd x_2  \dd y_1  \dd y_2,
-\end{equation}
-with 
-\[
-	T_\Pcal(y, x_1, x_2, y_1, y_2) 
-	= \ind{|x_1| \, \le \, e^{(y+y_1)/2}}\ind{|x_2| \, \le \, e^{(y+y_2)/2}}\ind{|x_1-x_2| \, \le \, e^{(y_1+y_2)/2}}.
-\]
-Note that $\Delta_{\Pcal}(y)$ is the probability that two randomly sampled points in $\BallPo{(0,y)}$ form a triangle with the vertex $(0,y)$.
-
-%\TM{ This next bit again suffers from the same issue as above. You cannot "randomly sample a point". }
-%Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$: the distribution function of the radial coordinate of a vertex sampled in the disk is $\frac{\cosh(\alpha  r)-1}{\cosh(\alpha R)-1}$ which is asymptotically equivalent to $e^{\alpha(r-R)} = e^{-\alpha y}$, if $r$ and $R$ are large, resp.
-tending to infinity and $y=R-r$ and because of the minus sign in front of the $r$, the distribution function in $r$ turns into the complementary distribution function of $y$, from which we recognize the exponential distribution with parameter $\alpha$.
-%
-%\PvdH{@All: This explanation was added by Markus at my request. If someone has a better explanation why this is the case please update this section.}
-
-With these expressions we define the limiting local clustering coefficient as
-\begin{equation}\label{eq:def_average_clustering_infinite_model}
-	c_\Pcal := \int_0^\infty \Delta_{\Pcal}(y) (1 - \rho(y,0) - \rho(y,1)) \alpha e^{-\alpha y} \dd y,
-\end{equation}
-while the limiting local clustering function is defined as
-\begin{equation}\label{eq:def_c_infty_k}
-	c_\Pcal(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
-\end{equation}
-
-In Section~\ref{sec:asymptotics_average_clustering_ast_P} we will compute both these quantities and show that $c_\Pcal = c_\infty$ and $c_\Pcal(k) = c_\infty(k)$, where $c_\infty$ and $c_\infty(k)$ are given in, respectively, Theorem~\ref{thm:clustering_coefficient_hyperbolic} and Theorem~\ref{thm:local_clustering_hyperbolic}.
-
-\subsection{Coupling the hyperbolic model to the finite box model}\label{ssec:coupling_H_P}
-
-The final step of our proof strategy is to couple the hyperbolic graph to $G_{\mathcal{P},n}(\alpha, \nu)$.
-For this we consider the original hyperbolic graph on a Poisson distributed number of vertices as an intermediate step.
-We define $G_{\HP,n}(\alpha, \nu)$ to be the hyperbolic random graph where the vertex set is given by $N \stackrel{d}{=} \Po(n)$ points, i.i.d.~and independent of $N$, distributed according to the $(\alpha, R_n)$-quasi uniform distribution~\eqref{eq:def_hyperbolic_point_distribution} defined in Section \ref{ssec:hyperbolic_model}.
-
-First we have to show that replacing uniform sampled points with this Poisson Point Process does not influence the properties of the model, so that we can proceed with the latter.
-
-\PvdH{@Tobias and Markus: I was not sure if you want to state a Lemma here that does this or simply refer to a later section where this is done.
-So please update this part once you added the proof for fixed $k$.}
-
-The following two lemmas from \cite{fountoulakis2018law} establish a coupling between the Poisson version of the hyperbolic random graph and the finite box model and relate the hyperbolic neighborhoods to the neighborhood balls $\BallPo{p}$.
-%The ensuing proposition verifies that this coupling also essentially preserves the local clustering function, i.e.
-that the difference between the local clustering function in the hyperbolic model and the finite box graph converges to zero faster than the proposed scalings in the main result, Theorem \ref{thm:local_clustering_hyperbolic}.
-Hence, it justifies the transition to the finite box model.
+The following lemmas from \cite{fountoulakis2018law} establish a useful coupling between the Poissonized KPKVB random graph
+and the finite box model and relate the edge  sets of the two graphs.
 
 \begin{lemma}[{\cite[Lemma 27]{fountoulakis2018law}}]\label{lem:coupling_hyperbolic_poisson}
-Let $\mathcal{V}_{\HP, n}$ denote the vertex set of $G_{\HP,n}(\alpha, \nu)$ and $\mathcal{V}_n$ the vertex set of $G_{\Pcal,n}(\alpha, \nu)$.
-Define the map $\Psi : [0,R_n] \times (-\pi, \pi] \to \mathcal{R}_n$ by
+Let $\mathcal{V}$ denote the vertex set of $\GPo(n;\alpha, \nu)$ and $\mathcal{W}$ the vertex set of $\Gbox(n;\alpha, \nu)$. 
+Define the map $\Psi : [0,R] \times (-\pi, \pi] \to \Rcal$ by
 \begin{equation}\label{eq:def_Psi}
-	\Psi(r,\theta) = \left(\theta \frac{e^{R_n/2}}{2}, R_n - r\right).
+	\Psi(r,\theta) = \left(\theta \frac{e^{R/2}}{2}, R - r\right).
 \end{equation}
-Then there exists a coupling such that, a.a.s.\TM{ Have we defined a.a.s.?
-If no, add it before using it.
-}, $\mathcal{V}_n = \Psi(\mathcal{V}_{\HP,n})$.
-%Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
+Then there exists a coupling such that, a.a.s., $\mathcal{W} = \Psi[\mathcal{V}]$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
 %\begin{equation}\label{eq:convergence_miscoupling_hyperbolic_poisson}
@@
 
-In the remainder of this paper we will write $\BallHyp{p}$ to denote the image under $\Psi$ of the ball of hyperbolic radius $R_n$ around the point $\Psi^{-1}(p)$, i.e. 
+In the remainder of this paper we will write $\BallHyp{p}$ to denote the image under $\Psi$ of the ball of hyperbolic radius $R$ around the point 
+$\Psi^{-1}(p)$, i.e. 
 \[
@@
 	%\left\{p^\prime := \Psi(u) \, : \, u \in \Dcal_{R_n} \text{ and } d_\H(\Psi^{-1}(p),u) \le R_n\right\}.
-	\Psi\left[ \left\{ u \in \Dcal_{R_n} : 
-	d_\H(\Psi^{-1}(p),u) \le R_n\right\}\right].
+	\Psi\left[ \left\{ u \in \Haa : 
+	d_\H(\Psi^{-1}(p),u), d_\H(O,u) \le R \right\}\right].
 \]
-Note that we have that $\BallHyp{p} \subseteq \mathcal{R}_n$. In particular, a point $p = (x,y) \in \Rcal$ corresponds to $u := \Psi^{-1}(p) = (2 e^{-R_n/2} x, R_n - y)$.
 
-Let $u, u^\prime \in \Dcal_R$ and write $\theta(u, u^\prime) := |\theta - \theta^\prime|_{2\pi}$ for their relative angle. If $r + r^\prime < R_n$, it holds for all $0 \le \phi \le 2\pi$ that
-\[
-	\cosh r \cosh r^\prime - \sinh r \sinh r^\prime \cos \phi \le \cosh(R_n),
-\] 
-which implies that $d_{\H}(u,u^\prime) \leq R_n$ and hence $u$ and $u^\prime$ are connected.
-Now consider a point $p \in \mathcal{V}_n$ and write $\Psi^{-1}(p) = (r,\theta)$.
-Then it follows that for any point $u^\prime \in \Dcal_R$
-\begin{equation}\label{eq:tail_inclusion_hyperbolic_ball}
-	r^\prime < y = R_n - r \Rightarrow d_{\H} (\Psi^{-1}(p),u^\prime) \leq R_n.
-\end{equation}
-In other words, we have $(-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2}e^{R_n/2}] \times [r, R_n]  \subset \BallHyp{p}$.
+Under the map $\Psi$, a point $p = (x,y) \in \Rcal$ corresponds to $u := \Psi^{-1}(p) = (2 e^{-R/2} x, R - y)$.
 
-When $r + r^\prime > R_n$ the equation 
-\[
-	\cosh R_n =\cosh r \cosh r^\prime - \sinh r \sinh r^\prime \cos \phi
-\]
-has two solutions of the form $\theta_{R_n}(r,r^\prime)$ and $2\pi - \theta_{R_n}(r,r^\prime)$ (when $r + r^\prime = R_n$ there is only one solution $\theta_{R_n}(r,r^\prime)$).
-It then follows that $d_{\H}(u,u^\prime) \leq R_n$ if and only if their relative angle $\theta(u, u^\prime)$ satisfies $\theta(u, u^\prime) \leq \theta_{R_n}(r,r^\prime)$.
-To write this differently, define
+By the hyperbolic rule of cosines, for two points $p = (x,y) = \Psi( (r,\theta) ), p' = (x',y') = \Psi( (r',\theta') ) \in \Rcal$ we have that
+$p' \in \BallHyp{p}$ iff.~either $r+r'\leq R$ or $r+r'>R$ and
+
+$$
+	\cosh r \cosh r' - \sinh r \sinh r'\cos\left( |\theta-\theta'|_{2\pi} \right) \le \cosh(R),
+$$
+
+\noindent
+This can be reprased as $p'\in \BallHyp{p}$ iff.~either $y+y'\geq R$ or $y+y'<R$ and
+
 \begin{equation}\label{eq:def_Omega_hyperbolic}
-	\Phi(r,r^\prime) := \frac{1}{2}e^{R_n/2} \arccos\left( \frac{\cosh r \cosh r^\prime - \cosh R_n}
-	{\sinh r \sinh r^\prime} \right).
+	|x-x'|_{\pi e^{R/2}} \leq \Phi(r,r') := \frac{1}{2}e^{R/2} \arccos\left( \frac{\cosh r \cosh r' - \cosh R_n}
+	{\sinh r \sinh r'} \right).
 \end{equation}
 
-\PvdH{@All: Since the choice of $\Omega$ here is slightly problematic (we also sometimes use $\Omega$ for its asymptotic scaling notation) I have switched $\Omega \mapsto \Phi$.}
-
-Then if $r + r^\prime > R_n$ we have that $d_{\H}(u,u^\prime) \leq R_n$ if and only if $\theta(u, u^\prime) \leq 2 e^{-R_n/2}\Phi(r,r^\prime)$.
-Under the coupling map $\Psi$, this is equivalent to $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$.
-The following lemma, which appears in~\cite{fountoulakis2018law}, gives useful bounds on the function $\Phi(r,r^\prime)$ in the regime $r + r^\prime > R_n$.
+The following lemma provides useful bounds on the function $\Phi(r,r^\prime)$.
 
 \begin{lemma}[{\cite[Lemma 28]{fountoulakis2018law}}]\label{lem:asymptotics_Omega_hyperbolic}
-There exists a constant $K>0$ such that, for every $\varepsilon > 0$ and for $R_n$ sufficiently large, the following holds.
-For every $r,r^\prime \in [\varepsilon R_n,R_n]$ with $r + r^\prime > R_n$ we have that 
+There exists a constant $K>0$ such that, for every $\varepsilon > 0$ and for $R$ sufficiently large, the following holds.
+For every $r,r^\prime \in [\varepsilon R,R]$ with $r + r^\prime > R$ we have that 
 \begin{equation}\label{eq:asymp1}
-	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Phi(r, r^\prime) 
-	\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
+	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R} \leq \Phi(r, r^\prime) 
+	\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R},
 \end{equation}
-where $y := R_n - r, y^\prime := R - r^\prime$. 
+where $y := R - r, y^\prime := R - r^\prime$. 
 Moreover:
 \begin{equation}\label{eq:asymp2} 
-\Phi(r,r^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $r, r^\prime < R_n - K$.} 
+\Phi(r,r^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $r, r^\prime < R - K$.} 
 \end{equation}
@@
 
-A key consequence of Lemma~\ref{lem:asymptotics_Omega_hyperbolic} is that the coupling from Lemma~\ref{lem:coupling_hyperbolic_poisson} preserves edges between points whose heights are small enough, asymptotically.
+A key consequence of Lemma~\ref{lem:asymptotics_Omega_hyperbolic} is that the coupling from Lemma~\ref{lem:coupling_hyperbolic_poisson} 
+preserves edges between points whose heights are not too large.
 
@@
 \begin{enumerate}
-\item for any two points $p_i, p_j \in \Pcal_{\alpha, \nu}$ with $y_i, y_j \le R_n/2$, we have that $(p_i,p_j) \in E(G_{\Pcal,n}) \Rightarrow (\Psi^{-1}(p_i), \Psi^{-1}(p_j)) \in E(G_{\HP,n})$, 
-\item for any two points $p_i, p_j \in \Pcal_{\alpha, \nu}$ with $y_i, y_j \le R_n/4$, we have that $(p_i,p_j) \in E(G_{\Pcal,n}) \iff (\Psi^{-1}(p_i), \Psi^{-1}(p_j)) \in E(G_{\HP,n})$.
+\item for any two points $p, p' \in \mathcal{W}$ with $y, y'\le R/2$, we have
+
+$$pp' \in E(\Gbox) \Rightarrow \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo), $$
+
+\item for any two points $p, p' \in \mathcal{W}$ with $y, y' \le R/4$, we have that
+
+$$pp' \in E(\Gbox) \iff \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo).$$
+
 \end{enumerate}
@@
 
-\PvdH{@Tobias and Markus: Please add additional text to explain the usage of these results in your proof for fixed $k$.}
+\subsection{The Campbell-Mecke formula}
 
-\PvdH{@All: Given that the structure of the proof will change, I removed the section where the proofs of the main results were stated.}
+\PvdH{We might want to give some more results for Poisson point processes and Poisson random variables. Such as at the end of Section 2.1 in your recent paper on Hamiltonian cycles.}
 
-%\subsection{Proof of the main results}\label{ssec:proof_main_results}
+A very useful tool for analyzing subgraph counts, and their generalizations, in the 
+setting of the Poissonized random geometric graphs, and in particular the Poissonized KPKVB model and the box model is the \emph{Campbell-Mecke formula}.
+We use the incarnation below, which can be found in the monograph~\cite{penrose2003random}, as Theorem 1.6.
+
+\PvdH{I found it extremely hard to see the implications of this theorem.
+I therefore strongly recommend using more explicit version, for instance as in the previous version of the paper, or explicitly state the consequences of this result which will be used here.}
+
+\begin{theorem}[\cite{penrose2003random}]\label{thm:palm}
+Let $\Qcal$ be a Poisson process on $\eR^d$ with intensity function $g$, and suppose that $\lambda := \int g < \infty$.
+Suppose that $h(\Ycal, \Xcal)$ is a bounded measurable function, defined on pairs $(\Ycal,\Xcal)$ with $\Ycal \subseteq \Xcal \subseteq \eR^d$
+and $\Xcal$ finite, such that $h(\Ycal,\Xcal) = 0$ whenever $|\Ycal| \neq j$ (for some $j \in \eN$).
+Then
+\[ \Ee \sum_{\Ycal \subseteq \Qcal} h( \Ycal, \Qcal) = \frac{\lambda^j}{j!} \cdot \Ee h(\{Y_1,\dots, Y_j\}, \{Y_1,\dots, Y_j\} \cup \Qcal ), \]
+\noindent
+where the $Y_i$ are i.i.d.~random variables that are independent of $\Pcal$ and have common probability density function
+$g/\lambda$.
+\end{theorem}
+
+% Let $\mathcal{Q}$ be a point process on a metric space $S$ with density $\rho$. 
+% Let $\mathcal{N} = \mathcal{N} (\mathcal{S})$ be the set of all countable point configurations in $\mathcal{S}$
+% equipped with the $\sigma$-algebra of the point process (that is, for any open subset 
+% $A\subseteq S$ and any non-negative integer $m$ define a basic measurable subset of 
+% $\mathcal{N}$ which consists of all configurations which have exactly $m$ points in $A$). 
+% Now, let $h : S^{k} \times \mathcal{N} \rightarrow \eR$ be a measurable function. 
+% The Palm theory of Poisson point processes on metric spaces~\cite{bk:LastPenrose} yields: 
 % 
+% \begin{equation} \label{eq:Mecke}
+% \E \left( \sum_{p_1, \ldots, p_k \in {\mathcal Q}, \atop \text{distinct}} h(p_1,\ldots, p_k, \mathcal{Q})  \right) =
+% \int_S \cdots \int_S \E (h(x_1,\ldots, x_k, \mathcal{Q})) d\rho (x_1) \cdots d \rho (x_k),
+% \end{equation} 
 % 
-%
-%We are now ready to prove our main results, using the propositions stated in the previous sections.
-As mentioned before we focus here on the convergence statements.
-The computation of the exact expressions is done in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
-We begin with Theorem~\ref{thm:local_clustering_hyperbolic}.
-%
-%\begin{proof}[Proof of Theorem \ref{thm:local_clustering_hyperbolic}]
-%%By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
-%%\begin{align*}
-%%	&\hspace{-30pt}\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}\\
-%%	&\le \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{}c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)}
-%%		+ \frac{\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\infty(k_n)\right|}{C_{\alpha,\nu}s_\alpha(k_n)}
-%%		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| \\
-%%	&= \smallO{1}.
-%%\end{align*}
-%First of all, due to cancellation of equal terms we can rewrite
-%\begin{align*}
-%    c_{\H,n}(k_n)-c_\infty(k_n) =& c_{\H,n}(k_n)-c_{\H,n}^\ast(k_n)+c_{\H,n}^\ast(k_n)-c_{\HP,n}^\ast(k_n)+c_{\HP,n}^\ast(k_n)-c_{\Pcal,n}^\ast(k_n) \\
-%    &+c_{\Pcal,n}^\ast(k_n)-\E c_{\Pcal,n}^\ast(k_n)+\E c_{\Pcal,n}^\ast(k_n)-c_\infty(k_n)
-%\end{align*}
-%Then, we take absolute values and apply the triangle inequality. By monotonicity of expectation, we can apply it to both sides and obtain
-%\begin{align*}
-%    \E[|c_{\H,n}(k_n)-c_\infty(k_n)|] \leq & \E[|c_{\H,n}(k_n)-c_{\H,n}^\ast(k_n)|]+\E[|c_{\H,n}^\ast(k_n)-c_{\HP,n}^\ast(k_n)|]\\&+\E[|c_{\HP,n}^\ast(k_n)-c_{\Pcal,n}^\ast(k_n)|] 
-%    +\E[|c_{\Pcal,n}^\ast(k_n)-\E c_{\Pcal,n}^\ast(k_n)|]\\&+\E[|\E c_{\Pcal,n}^\ast(k_n)-c_\infty(k_n)|]
-%\end{align*}
-%At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{s_\alpha(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c_{\Pcal}(k_n) = c_\infty(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
-%\TM{ Maybe we can have a more clear reference? Now, at this place in the paper this proof feels a bit like cheating since there are almost no details given. } All of this together yields that:
-%\begin{align*}
-%    \E[|c_{\H,n}(k_n)-c_\infty(k_n)|] = \smallO{s_\alpha(k_n)} = \smallO{c_\infty(k_n)}
-%\end{align*}
-%\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point. }
-%i.e. the statement of the theorem.
-%%\[
-%%	\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
-%%	\le \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| 
-%%	+ \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - c_\infty(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
-%%\]
-%
-%%Combining this with Proposition~\ref{prop:couling_c_H_P} yields
-%%\[
-%%	\Exp{\left|\frac{c_{\H,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
-%%	\le \Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|} 
-%%	+ \frac{\Exp{\left|c_{\H,n}^\ast(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
-%%\]
-%%and the result then follows by applying Lemma~\ref{lem:clustering_ast_H}. 
-%\end{proof}
-%
-%We can now use this result to prove Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
-Before we state the proof we summarize some results regarding the degrees in the hyperbolic model.
-The proof of this lemma follows directly from Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson} and Lemma~\ref{lem:N_k_HP_P}, see Section~\ref{sec:coupling_H_P_n}.
-%
-%%\MS{I think we need to introduce resp. explain $\Prob{D_\Pcal = k_n}$ in the lemma below.}
-%
-%\begin{lemma}\label{lem:N_k_H_P}
-%Let $\alpha > \frac{1}{2}$ and $k_n$ be a positive sequence, possibly constant, such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then
-%\[
-%	\lim_{n\to \infty} \Exp{\left|\frac{\Exp{N_{\H,n}(k_n)}}{n \Prob{D_\Pcal = k_n}} - 1\right|} = 0
-%\]
-%\TM{ Did we define $D_\Pcal$ already? }
-%and hence, as $n \to \infty$
-%\[
-%	\Exp{N_{\H,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}}.
-%\]
-%\end{lemma}
-%
-%\begin{proof}[Proof of Theorem~\ref{thm:clustering_coefficient_hyperbolic}]
-%
-%First, let $a_n$ be any sequence such that $a_n \to \infty$. Then
-%\begin{align*}
-%	c_{\H,n} &= \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) \le a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}
-%		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
-%	&= \frac{1}{n} \sum_{t = 2}^{a_n} \sum_{i = 1}^n \ind{D_{\H,n}(i) = t} \frac{T_{\H,n}(i)}{\binom{t}{2}}
-%		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}}\\
-%	&= \frac{1}{n} \sum_{t = 2}^{a_n} \Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t)
-%		+ \frac{1}{n} \sum_{i = 1}^n \ind{D_{\H,n}(i) > a_n} \frac{T_{\H,n}(i)}{\binom{D_{\H,n}(i)}{2}},
-%\end{align*}
-%where the expectation of the last term is bounded from above by $\Prob{D_{\H,n} > a_n}$. Similarly,
-%\[
-%	c_\Pcal = \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} c_\Pcal(t) + \sum_{t > a_n} \Prob{D_\Pcal = t} c_\Pcal(t)
-%\]
-%As derived at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}, $c_\infty = c_\Pcal$ and $c_\infty(k) = c_\Pcal(k)$. Therefore
-%\begin{align*}
-%	\Exp{|c_{\H,n}-c_\infty|}=\Exp{|c_{\H,n} - c_\Pcal|}
-%	&\le \Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
-%		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\ 
-%	&\hspace{10pt}+ \Prob{D_{\H,n} > a_n} + \Prob{D_{\Pcal} > a_n},
-%\end{align*}
-%\TM{ Same comment }
-%and since the last two probabilities are $\smallO{1}$ \TM{ We do not seem to have proved this yet at this point in the paper } it is enough to prove that
-%\[
-%	\lim_{n \to \infty} \Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
-%			n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|} = 0.
-%\]
-%
-%We write
-%\begin{align*}
-%	&\hspace{-30pt}\Exp{\left|\frac{1}{n} \sum_{t = 2}^{a_n} \left(\Exp{N_{\H,n}(t)} c_{\H,n}^\ast(t) - 	
-%		n \Prob{D_\Pcal = t}c_\Pcal(t)\right)\right|}\\
-%	&\le \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\infty}(t)\right|}\\
-%	&\hspace{10pt}+ \frac{1}{n} \sum_{t = 2}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)},
-%\end{align*}
-%and will show that both terms go to zero for some appropriately chosen sequence $a_n$.
-%
-%Note that Theorem~\ref{thm:local_clustering_hyperbolic} and Lemma~\ref{lem:clustering_ast_H} together state that for any sequence $k_n  = \smallO{n^{1/(2\alpha + 1)}}$
-%
-%\begin{equation}\label{eq:convergence_c_H_P}
-%	\lim_{n \to \infty} \Exp{\left|c_{\H,n}(k_n) - c_{\Pcal}(k_n)\right|} = 0.
-%\end{equation}
-%
-%\TM{ I do not see how this follows from the statements of Thm 1.2 and L2.3. Please elaborate. }
-%Let $b_n := \log(n)^{-1} n^{1/(2\alpha + 1)}$ and define the sequence $k_n$ by
-%\[
-%	k_n = \arg \max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|}.
-%\]
-%Then $k_n = \smallO{n^{1/(2\alpha + 1)}}$ and by~\eqref{eq:convergence_c_H_P}
-%\[
-%	\max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\Pcal}(t)\right|} = \Exp{\left|c_{\H,n}(k_n) - c_{\infty}(k_n)\right|} \to 0.
-%\]
-%Similarly we note that by Lemma~\ref{lem:N_k_H_P}
-%\[
-%	\max_{2 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
-%\]
-%
-%Now define
-%\[
-%	a_n := \left\lfloor \min \left\{
-%	\left(\max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|}\right)^{-1/2},
-%	\left(\max_{2 \le t \le b_n} \Exp{\left|\frac{N_{\H,n}(t)}{N_\Pcal(t)} - 1\right|}\right)^{-1/2},
-%	b_n - 1 \right\} \right\rfloor
-%\]
-%\TM{ There seems to be a typo. max should be argmax?
-%Also, what is the exponent $-1/2$ doing there?
-} \PvdH{It was the other way around, argmax should have been max.
-Since the first to expressions tend to zero, taking them to the power -1/2 make them go to infinity while still making sure that $a_n$ times those expressions tends to zero.}
-%so that $a_n < b_n = \smallO{n^{1/(2\alpha + 1)}}$, $a_n \to \infty$,
-%\
-%\[
-%	a_n \max_{2 \le t \le a_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} 
-%	\le a_n \max_{2 \le t \le b_n} \Exp{\left|c_{\H,n}(t) - c_{\infty}(t)\right|} \to 0,
-%\]
-%\TM{ LHS and RHS are identical !!! }\PvdH{They differ by $a_n$ vs $b_n$ in the max.}
-%and similarly
-%\[
-%	a_n \max_{2 \le t \le a_n} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \to 0.
-%\]
-%
-%Then, since $\Exp{\Prob{D_\Pcal = t}} = \bigT{1} t^{-(2\alpha + 1)}$
-%\begin{align*}
-%	&\hspace{-30pt}\sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}\\
-%	&\le \bigT{1} 2^{-(2\alpha+1)} a_n \max_{2 \le t \le a_n} \Exp{\left|c_{\H,n}^\ast(t) - c_{\Pcal}(t)\right|}
-%	= \smallO{1},
-%\end{align*}
-%while $\Exp{c_\Pcal(t)} \le 1$ implies that
-%\begin{align*}
-%	&\hspace{-30pt}\frac{1}{n} \sum_{t = 2}^{a_n} \Exp{\left|N_{\H,n}(t) - n \Prob{D_\Pcal = t}\right|}\Exp{c_\Pcal(t)} \\
-%	&\le \sum_{t = 2}^{a_n} \Prob{D_\Pcal = t} \Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} \\
-%	&\le \bigT{1} 2^{-(2\alpha+1)} a_n \max_{2 \le t \le a_n} 
-%		\Exp{\left|\frac{N_{\H,n}(t)}{n \Prob{D_\Pcal = t}} - 1\right|} = \smallO{1}.
-%\end{align*}
-%This finishes the proof. %The second part, which derives the exact expression for $c_\Pcal$ can be found in [??] \PvdH{Add reference to section.}
-%\end{proof}
+% where the sum ranges over all those $k$-tuples of points which contain no repetitions. 
+% Note that in the RHS, the points $x_1, \dots, x_k$ are not part of $\Qcal$.

### 2019-02-05 proofs_finite_k.tex
updated notation and added comments to sections 1-3

@@
-\section{Proofs of the main results for fixed $k$}\label{sec:proofs_fixed_k}
+\section{Proofs of Theorem~\ref{thm:maincc} and Theorem~\ref{thm:mainkfixed}\label{sec:proofs_fixed_k}}
+
+We will first derive Theorem~\ref{thm:mainkfixed}. It will turn out that Theorem~\ref{thm:maincc} has a quick derivation
+assuming Theorem~\ref{thm:mainkfixed}.
+
+\subsection{The proof of Theorem~\ref{thm:mainkfixed}}
+
+\TM{This is still in need of a serious polish}
+
+We first show we can restrict attention to the Poissonized instead of the standard KPKVB model.
+
+\begin{lemma} Let $\alpha>\frac12,\nu>0, k\geq 2$ be fixed and write $G_n := G(n;\alpha,\nu), G_{n,\text{Po}} := \GPo(n;\alpha,\nu)$.
+Then
+
+$$ c(k; G_n)-c(k; G_{n,\text{Po}}) \xrightarrow[n\to\infty]{\Pee} 0. $$
+\end{lemma}
+
+\begin{proof}
+We use a sprinkling argument. 
+We observe that $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu), G(n;\alpha,\nu)$ 
+and $\GPo(n;\alpha,\nu)$ all live on the same disk (with radius $R = 2\ln \frac{n}{\nu}$).
+We consider the coupling where we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ chosen according
+to the $(\alpha,R)$-quasi uniform distribution, the vertices of $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu)$
+are $u_1,\dots, u_{(1+\epsilon)n}$; the vertices of $G(n;\alpha,\nu)$ are $u_1,\dots, u_n$ and 
+the vertices of $\GPo(n;\alpha,\nu)$ are $u_1,\dots, u_N$ with $N\isd \Po(n)$ indepenent of
+$u_1, u_2, \dots$.
+
+We imagine the situation where we remove $\eps n$ vertices from $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu)$ to obtain
+$G(n;\alpha,\nu)$ and we remove (or add, in the event that $N > (1+\eps)n$) $|(1+\eps)n - N|$ vertices to obtain $\GPo(n;\alpha,\nu)$.
+Note that, by Chebyschev, $\Pee( |N-n| > \eps n ) = o(1)$. So, a.a.s., in both cases we remove no more than $2\eps n$ vertices.
+Now let $X$, respectively $X_{\text{Po}}$, denote the number of vertices that are either themselves removed or have at least one 
+neighbour that is removed.
+
+Let $\overline{D}$ denote the average degree of $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu)$.
+By the results of Gugelmann et al.~\cite{gugelmann2012random} $\overline{D}$ converges in probability
+to a certain constant. In particular, there is a constant $C$ such that $\overline{D} \leq C$ a.a.s.
+
+Now note that, under the coupling described above:
+
+$$ \Ee\left( X | \overline{D} \leq C \right),  \Ee\left( X_{\text{Po}} | \overline{D} \leq C, |N-n|<\eps n \right) \leq (1+C)  2 \eps n. $$
+
+Markov's inequality gives
+
+$$ \Pee( X \geq \sqrt{\eps} n ), \Pee( X_{\text{Po}} \geq \sqrt{\eps} n ) = O( \sqrt{\eps} ). $$
+
+By the results of Gugelmann et al.~on the degree sequence the number of vertices of degree exactly
+$k$ in $G(n;\alpha,\nu)$ equals $(1+o(1)) n p_k$ a.a.s.
+In particular it is $\Omega(n)$ a.a.s.
+
+Since $c(k;G)$ is the average of $c(v)$ over all $v$ of degree $k$, and $0\leq c(v)\leq 1$, we have
+
+$$ \Pee( |c(k;G(n;\alpha,\nu)) - c(k;G((1+\epsilon)n;\alpha,(1+\epsilon)\nu))| > \sqrt{\eps} ) = O(\sqrt\eps), $$
+
+and simlarly for $\GPo$. In particular also 
+$|c(k;G(n;\alpha,\nu)) - c(k;\GPo(n;\alpha,\nu))| > \sqrt{\eps} ) = O(\sqrt\eps)$.
+Sending $\eps\searrow 0$ proves the lemma.
+\end{proof}
+
+\begin{lemma}\label{lem:n1}
+Let $N_1(H)$ denote the number of vertices with height at least $H \in [0,R]$ in the finite box model (with $n$ vertices).
+
+For all $\epsilon >0$, there is $H=H_\epsilon$ such that $\E N_1(H) \leq \epsilon n$.
+\end{lemma}
+\begin{proof}
+By linearity of expectation and the probability mass of a centered disk,
+\begin{align*}
+\E N_1 = n \Pee(B_{R-H}(0)) \leq n e^{-\alpha H}
+\end{align*}
+Now, choose $H$ large enough such that $e^{-\alpha H} \leq \epsilon$.
+\end{proof}
+\begin{lemma}
+Let $N_2(H)$ denote the number of vertices with no neighbour with height above $H \in [0,R]$ in the finite box model (with $n$ vertices).
+
+For all $\epsilon >0$, there is $H=H_\epsilon$ such that $\E N_2 \leq \epsilon n$.
+\end{lemma}
+\begin{proof}
+Let $\epsilon >0$.
+By Lemma~\ref{lem:n1}, there is $H_1$ such that the expected number of vertices with height at least $H_1$ is upper bounded by $\frac{\epsilon}{2}n$.
+So, if we write $N_{\geq H_1}$ for the number of vertices with height at least $H_1$ and $N_{\leq H_1}(H)$ for the number of vertices with height at most $H_1$ and no neighbour with height above $H$, then
+$$N_2(H) \leq N_{\geq H_1} + N_{\leq H_1}(H)$$
+Let $\mu(H)$ denote the expected number of vertices in the neighbourhood ball above $H$ of a vertex with height $H_1$.
+For fixed $H_1$, $\mu(H)$ is a continuous function which is decreasing in $H$ and with $\mu(R)=0$.
+Therefore, there is $H_2$ large enough such that $1-e^{-\mu(H_2)} \leq \frac{\epsilon}{2}$.
+Hence,
+$$\E N_{\leq H_1}(H_2) \leq n (1-e^{-\mu(H_2)}) \leq \frac{\epsilon}{2}$$
+Finally, $\E N_2(H_2) \leq \E N_{\geq H_1} + \E N_{\leq H_1}(H_2) \leq \epsilon n$.
+%For any vertex with height at most $H_1$, the probability mass of the neighbourhood ball $U_v$ of such a vertex $v$ above $H_1$ is upper bounded by $w(H_1)$.
+%The expected number of points in $U_v$ is $\leq \epsilon n$.
+% Write
+%$$N_2 = \sum_{v = 1}^n \1_{\{v\text{ has no neighbour with rad. coord. }<R-H \}} $$
+\end{proof}
+
+\begin{lemma}
+Let $c(k)$ denote the clustering function of the KPKVB random graph for $k \in \N$ and $c_{\leq H}(k)$ denote the average of the clustering coefficient of all vertices with degree $k$ and height $\leq H$ and with no neighbour with height $>H$.
+Then,
+$c(k) = c_{\leq H}(k) + O(\sqrt{\epsilon})$ with probability $\geq 1-O(\sqrt{\epsilon})+o(1)$.
+\end{lemma}
+\begin{proof}
+Let $N(k)$ denote the number of vertices with degree $k$ in KPKVB.
+Let $N_H(k)$ denote the number of vertices with degree $k$ and height $\leq H$ and with no neighbour with height $>H$.
+From the previous two lemmas, it follows that $\E (n- N_H) \leq \epsilon n$ and from this also that $\E (N(k)-N_H(k))\leq \epsilon n$.
+Therefore, by Markov's inequality,
+$$\Pee( n-N_H \geq \sqrt{\epsilon}n) \leq \frac{\E (n-N_H)}{n} \leq \sqrt{\epsilon}$$
+Consider 
+$$c(k)-c_{\leq H}(k) = \frac{1}{N(k)}\sum c(v) - \frac{1}{N_H(k)}\sum c(v) \leq \frac{N(k)-N_H(k)}{N(k)}$$
+So, finally
+$$\Pee( c-c_{\leq H} = O(\sqrt{\epsilon}) ) \geq 1-O(\sqrt{\epsilon})$$
+\end{proof}
+
+\begin{lemma}
+Let $c_{\leq H}(k)$ denote the average over all clustering coefficients of all vertices with degree $k$ and height $\leq H$ and with no neighbour with height $>H$ in the poissonized KPKVB model.
+
+Let $\Delta_H(y)$ denote the probability that two neighbours of $(0,y)$ are adjacent.
+Let $\tau(y,k)$ be the Poisson probability that $(0,y)$ has degree $k$.
+Let $\rho(y)$ denote the truncated exponential density.
+
+Then,
+$c_{\leq H}(k) = (1+o(1))\int_0^H \int_0^H \int_0^H \Delta_H(y) \tau(y,k)\rho(y_1)\rho(y_2)\rho(y) dy_1dy_2 dy$ a.a.s.
+\end{lemma}
+\begin{proof}
+First of all, as for $c_{\leq H}(k)$ all vertices involved have height $\leq H$, we can perform the computations in the box model: As $H$ is constant, for $R$ large enough, vertices with radial coordinates at least $R-H$ will have radial coordinate $\geq \frac{3}{4}R$, such that by Lemma~30(ii) from the paper on the largest component of KPKVB, edges exist between such vertices in the disk if and only if they exist in the box.
+
+Let $N_{trig}(k,H)$ denote the number of tuples $(v,uw)$ for pairwise distinct vertices $v,u,w$ such that $v,u,w$ form a triangle, the radial coordinates of $u,v,w$ are all at least $R-H$ and $v$ has degree $k$ (where $H$ is the cut-off from the first two lemmas).
+So, we have $c_{\leq H}(k) = \frac{N_{trig}(k,H)}{N_H}$.
+
+Let $M_{trig}(k,H)$ denote the number of tuples $(v,u,w)$ for pairwise distinct vertices $v,u,w$ such that $v,u,w$ form a triangle, the radial coordinates of $u,v,w$ are all at least $R-H$ and $v$ has degree $k$.
+Note that $N_{trig}(k,H) = \frac{1}{2}M_{trig}(k,H)$.
+$M_{trig}(k,H)$ can be written as a sum over $3$-tuples:
+\begin{align*}
+M_{trig}(k,H) = \sum_{(v,u,w) \in V_{\not =}^3} h(V,v,u,w)
+\end{align*}
+where $h$ is the indicator function that $v,u,w$ form a triangle, have radial coordinates at least $R-H$ and $v$ has degree $k$.
+Using Mecke's formula, we obtain that 
+\begin{align*}
+\E M_{trig}(k,H) = \int_{E_R} \int_{E_R}\int_{E_R} \E h(V,v,u,w) dvdudw
+\end{align*}
+%Let $V \subset E_R$ denote the vertex set of the finite box model in the box $E_R = (-\frac{\pi}{2}e^{\frac{R}{2}},\frac{\pi}{2}e^{\frac{R}{2}}]\times (0,R]$.
+
+From there, it follows that
+\begin{align*}
+\E c_{\leq H}(k) = \frac{1}{\Pee(D_H=k)} \int_0^H \int_0^H \int_0^H \Delta_{H}(y) \tau(y,k) \rho(y_1)\rho(y_2)dy_1dy_2 dy
+\end{align*}
+For $H\rightarrow \infty$, this converges to the integral obtained in the paper.
+
+In order to complete the proof, we need to show that $\E c_{\leq H}(k)^2 = (1+o(1))(\E c_{\leq H}(k))^2$.
+For this, it is sufficient to show that $\E N_{trig}^2 = (1+o(1))(\E N_{trig})^2$.
+In the box model, we know that two vertices with height at most $H$ and horizontal distance $>2e^H$ cannot be adjacent and their neighbourhood balls are disjoint (w.r.t.
+the connection rule of the box model).
+If the neighbourhood balls are disjoint, then the clustering coefficients of the vertices are independent.
+The horizontal coordinate is uniform in the width of the box which is $\pi e^{\frac{R}{2}}$.
+Therefore, the probability that two vertices have horizontal distance $\leq 2e^H$ is $\leq \frac{2e^H}{\pi e^{\frac{R}{2}}} = o(1)$.
+\end{proof}
+
+\subsection{The proof of Theorem~\ref{thm:maincc}}
+
+\begin{proofof}{Theorem~\ref{thm:maincc}}
+We first note that
+
+$$ \gamma = \Ee C = \sum_{k\geq 2} \Ee\left( C | D=k \right) \Pee( D=k ) = \sum_{k\geq 2} \gamma(k) p_k. $$
+
+Writing $N_k$ for the number of vertices of degree $k$, we have the similar relation
+
+$$ c(G) = \sum_{k\geq 2} c(k;G) \cdot (N_k/n). $$
+
+Theorem~\ref{thm:mainkfixed} establishes that $c(k;G(n;\alpha,\nu))$ converges to $\gamma(k)$ in probability 
+for any fixed $k$. The results of Gugelmann et al.~\cite{gugelmann2012random} on the degree sequence establish 
+that $N_k/n$ converges to $p_k$ in probability, for any fixed $k$.
+The result now follows in a straightforward manner from these observations.
+\end{proofof}

### 2019-02-05 proofs_infinite_k.tex
updated notation and added comments to sections 1-3

@@
 
-The proofs for Theorems [??] follow the same strategy as outlined in Section~\ref{sec:proof_outline}.
+The proof of Theorem~\ref{thm:mainktoinfty} follows the same strategy as outlined in Section~\ref{sec:proof_outline}.
 However, the fact that $k = k_n \to \infty$ as $n \to \infty$, introduces additional technical challenges.
-For example, the coupling we use becomes less exact so that we can no longer use Lemma~\ref{lem:coupling_edges} to conclude that triangle counts in $G_{\HP,n}$ and $G_{\Pcal,n}$ are asymptotically equivalent.
-In this section we explain the challenges with each step and give a detailed overview of the structure for the proof of Theorem [??] using intermediate results for each of the steps.
-Since we are ultimately interested in recovering the scaling of $c_{\H,n}(k_n)$, which Theorem [??] claims is $s_\alpha(k_n)$, we need to show that each step only introduces error terms that are of smaller order, i.e.
-that are $\smallO{s_\alpha(k_n)}$.
-We end this section with the proof of Theorem [??], based on the intermediate results.
+For example, the coupling we use becomes less exact so that we can no longer use Lemma~\ref{lem:coupling_edges} to conclude that triangle counts in $\GPo$ and $\Gbox$ are asymptotically equivalent.
+In this section we explain the challenges with each step and give a detailed overview of the structure for the proof of Theorem~\ref{thm:mainktoinfty} using intermediate results for each of the steps.
+Since we are ultimately interested in recovering the scaling of $c(k_n;G_n)$, which Theorem~\ref{thm:mainktoinfty} claims is $\gamma(k_n)$, we need to show that each step only introduces error terms that are of smaller order, i.e.
+that are $\smallO{\gamma(k_n)}$.
+To this end we define the scaling function
+\begin{equation}\label{eq:def_scaling_function}
+	s(k) = \begin{cases}
+		k^{-(4\alpha - 2)} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
+		\log(k) k^{-1} &\mbox{if } \alpha = \frac{3}{4},\\
+		k^{-1} &\mbox{if } \alpha > \frac{3}{4},
+	\end{cases}
+\end{equation}
+so that $\gamma(k) = \bigT{s(k)}$ as $k \to \infty$. We will end this section with the proof of Theorem~\ref{thm:mainktoinfty}, based on the intermediate results.
 
@@
 \begin{equation}\label{eq:def_local_clustering_ast_general}
-	c_{G}^\ast(k) = \frac{1}{\Exp{N_G(k)}} \sum_{v \in V(G)} \ind{D_G(v) = k} \frac{\T_G(v)}{\binom{k}{2}}.
+	c^\ast(k;G) = \frac{1}{\Exp{N_k}} \sum_{v \in V(G) \atop \text{deg}(v)=k} c(v).
 \end{equation}
-Notice that the only difference between $c_G(k)$ and $c_G^\ast(k)$ is that we replace $N_G(k)$ by its expectation $\Exp{N_G(k)}$.
+Notice that the only difference between $c(k;G)$ and $c^\ast(k;G)$ is that we replace $N_G(k)$ by its expectation $\Exp{N_G(k)}$.
 The advantage is that now, the only randomness is in triangle counting.
-In addition, note that since $\Exp{N_G(k)} > 0$ a case distinction for $N_k$ is no longer needed for $c_G^\ast(k)$.
-It is however still relevant since we are eventually interested in $c_G(k)$.
-Following the notational convention, see Remark~\ref{rmk:notation}, throughout the remainder of this paper we write $c_{\HP,n}^\ast(k)$ and $c_{\mathcal{P},n}^\ast(k)$ to denote the modified local clustering function in $G_{\HP,n}(\alpha, \nu)$ and $G_{\mathcal{P},n}(\alpha,\nu)$, respectively.
+In addition, note that since $\Exp{N_G(k)} > 0$ a case distinction for $N_k$ is no longer needed for $c^\ast(k;G)$.
+It is however still relevant since we are eventually interested in $c(k;G)$.
+Following the notational convention, throughout the remainder of this paper we write $c^\ast(k; \GPo)$ and $c^\ast(k; \Gbox)$ to denote the modified local clustering function in $\GPo$ and $G_{\mathcal{P},n}(\alpha,\nu)$, respectively.
 
-Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem [??] based on the different propositions described below, plus the sections in which theses propositions are proved.
+Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem~\ref{thm:mainktoinfty} based on the different propositions described below, plus the sections in which theses propositions are proved.
 Observe that the order in which the intermediate results are proved is reversed with respect to the natural order of reasoning.
@@
 		\textbf{Hyperbolic graph}\\
-		$G_{\H,n}(\alpha, \nu)$
+		$G_n$
 	\end{center}
@@
 	Local clustering\\
-	$\displaystyle c_{\H,n}(k_n)$
+	$\displaystyle c(k_n;G_n)$
 	\end{center}
@@
 	Adjusted local clustering\\
-	$\displaystyle c_{\H,n}^\ast(k_n)$
+	$\displaystyle c^\ast(k_n;G_n)$
 	\end{center}
@@
 		\textbf{Poisson Hyperbolic graph}\\
-		$G_{\HP,n}(\alpha,\nu)$
+		$\GPo(\alpha,\nu)$
 	\end{center}
@@
 	Adjusted local clustering\\
-	$\displaystyle c_{\HP,n}^\ast(k_n)$
+	$\displaystyle c^\ast(k_n; \GPo)$
 	\end{center}
@@
 		\textbf{Infinite limit model}\\
-		$G_{\Pcal}(\alpha, \nu)$
+		$\Ginf(\alpha, \nu)$
 	\end{center}
@@
 	Clustering limit\\
-	$\displaystyle c_\infty(k_n)$
+	$\displaystyle \gamma(k_n)$
 	\end{center}
@@
 	Adjusted local clustering\\
-	$\displaystyle c_{\Pcal,n}^\ast(k_n)$
+	$\displaystyle c^\ast(k_n; \Gbox)$
 	\end{center}
@@
 	Expected adjusted local clustering\\
-	$\displaystyle \Exp{c_{\Pcal,n}^\ast(k_n)}$
+	$\displaystyle \Exp{c^\ast(k_n; \Gbox)}$
 	\end{center}
@@
 		\textbf{Finite box model}\\
-		$G_{\Pcal,n}(\alpha, \nu)$
+		$\Gbox(\alpha, \nu)$
 	\end{center}
@@
 
-Recall that the first step for the fixed $k$ case was to show that the transition from the hyperbolic random graph $G_{\H,n}$ to the Poisson version $G_{\HP,n}$ did not influence clustering.
-Here we first make a transition from the local clustering function $c_{\H,n}(k)$ to the adjusted version $c_{\H,n}^\ast(k)$.
+Recall that the first step for the fixed $k$ case was to show that the transition from the hyperbolic random graph $G_{\H,n}$ to the Poisson version $\GPo$ did not influence clustering.
+Here we first make a transition from the local clustering function $c_{\H,n}(k)$ to the adjusted version $c^\ast(k; G_n)$.
 The following lemma justifies working with this modified version.
@@
 \[
-	\Exp{\left|c_{\H,n}(k_n) - c_{\H,n}^\ast(k_n)\right|} = \smallO{s_\alpha(k_n)}.
+	\Exp{\left|c(k_n;G_n) - c^\ast(k_n;G_n)\right|} = \smallO{s(k_n)}.
 \]
@@
 \[
-	\Exp{\left|c_{\H,n}^\ast(k_n) - c_{\HP,n}^\ast(k_n)\right|} = \smallO{s_\alpha(k_n)}.
+	\Exp{\left|c^\ast(k_n;G_n) - c^\ast(k_n; \GPo)\right|} = \smallO{s(k_n)}.
 \]
@@
 
-\subsection{Coupling of local clustering between $G_{\HP,n}$ and $G_{\Pcal,n}$}
+\subsection{Coupling of local clustering between $\GPo$ and $\Gbox$}
 
@@
 
-To understand why, recall that the degree $k$ of a node is related to its height $y$, roughly speaking, by $k \approx \xi_{\alpha, \nu} e^{y/2}$.
+To understand why, recall that the degree $k$ of a node is related to its height $y$, roughly speaking, by $k \approx \xi e^{y/2}$.
 Therefore, when $k$ is fixed we have that the heights of nodes with that degree are also fixed, in particular $y < R_n/4$ for large enough $n$.
 In addition, the main contribution of triangles would also come from nodes with heights $y^\prime < R_n/4$.
-This allowed us to use Lemma~\ref{lem:coupling_edges} and conclude that the triangles present in the graph $G_{\HP,n}$ where exactly those present in $G_{\Pcal,n}$ and therefore the local clustering function was the same in both models.
+This allowed us to use Lemma~\ref{lem:coupling_edges} and conclude that the triangles present in the graph $\GPo$ where exactly those present in $\Gbox$ and therefore the local clustering function was the same in both models.
 When $k_n \to \infty$ this is no longer true in general.
 For instance, suppose $k_n = n^{\frac{1-\varepsilon}{2\alpha + 1}}$, for some small $0 < \varepsilon < 1$.
-Then the relation $k_n \approx \xi_{\alpha, \nu} e^{y_n/2}$ implies that $y_n \approx \frac{2(1-\varepsilon)}{2\alpha + 1}\log(n) - 2\log(\xi_{\alpha, \nu})$.
+Then the relation $k_n \approx \xi e^{y_n/2}$ implies that $y_n \approx \frac{2(1-\varepsilon)}{2\alpha + 1}\log(n) - 2\log(\xi)$.
 Since
@@
 \[
-	\Exp{\left|c_{\HP,n}^\ast(k_n) - c_{\Pcal,n}^\ast(k_n)\right|} = \smallO{s_\alpha(k_n)}.
+	\Exp{\left|c^\ast(k_n; \GPo) - c^\ast(k_n; \Gbox)\right|} = \smallO{s(k_n)}.
 \]
@@
 
-\TM{ Maybe we could replace these three with a statement on $|c_{\H,n}(k_n) - c_{\Pcal,n}^\ast(k_n)|$, at least at this point of the paper.
+\TM{ Maybe we could replace these three with a statement on $|c(k_n;G_n) - c^\ast(k_n; \Gbox)|$, at least at this point of the paper.
 This is only the high level description and that is all we need for the ``final proof".}\PvdH{I would vote for keeping them split, since this allows us to clearly point to the main technical challenge we have to overcome to obtain the final result.}
-These three results together imply that the difference between the local clustering function of the hyperbolic random graph and the modified local clustering function of the finite box graph converges to zero faster than the proposed scaling $s_\alpha(k_n)$ in Theorem [??].
-Hence, to prove this theorem it is enough to prove it for $c_{\mathcal{P},n}^\ast(k)$.
+These three results together imply that the difference between the local clustering function of the hyperbolic random graph and the modified local clustering function of the finite box graph converges to zero faster than the proposed scaling $\gamma(k_n)$ in Theorem [??].
+Hence, to prove this theorem it is enough to prove it for $c^\ast(k; \Gbox)$.
 
@@
 
-To compute the limit of the modified local clustering function $c_{\mathcal{P},n}^\ast(k)$ in the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ we first prove in Section~\ref{sec:concentration_c_P_n} that it is concentrated around its expectation $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$.
+To compute the limit of the modified local clustering function $c^\ast(k; \Gbox)$ in the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ we first prove in Section~\ref{sec:concentration_c_P_n} that it is concentrated around its expectation $\Exp{c^\ast(k_n; \Gbox)}$.
 
@@
 \[
-	\Exp{\left|c_{\mathcal{P},n}^\ast(k_n) - \Exp{c_{\mathcal{P},n}^\ast(k_n)}\right|} = \smallO{s_\alpha(k_n)}.
+	\Exp{\left|c^\ast(k_n; \Gbox) - \Exp{c^\ast(k_n; \Gbox)}\right|} = \smallO{s(k_n)}.
 \]
@@
 
-Assuming this concentration result, we are left with the task to compute the limit of $\Exp{c_{\mathcal{P},n}^\ast(k_n)}$ as $n \to \infty$ and show that it is equivalent to $c_\infty(k_n)$.
-To accomplish this we move to the infinite limit model $G_\Pcal(\alpha,\nu)$ and show that the difference between the expected value of the clustering function $c_G^\ast(k)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
+Assuming this concentration result, we are left with the task to compute the limit of $\Exp{c^\ast(k_n; \Gbox)}$ as $n \to \infty$ and show that it is equivalent to $\gamma(k_n)$.
+To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of the clustering function $c^\ast(k;G)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
 
@@
 \[
-	\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\Pcal(k_n)\right| = \smallO{s_\alpha(k_n)}.
+	\left|\Exp{c^\ast(k_n; \Gbox)} - c(k_n;\Ginf)\right| = \smallO{s(k_n)}.
 \]
@@
 
-Recall that for the finite box model the left and right boundaries of $\Rcal_n$ where identified, so that graph $G_{\Pcal,n}$ contains some additional edge with respect to the induced subgraph of $G_{\Pcal}$ on $\Rcal_n$.
+Recall that for the finite box model the left and right boundaries of $\Rcal_n$ where identified, so that graph $\Gbox$ contains some additional edge with respect to the induced subgraph of $\Ginf$ on $\Rcal_n$.
 The prove of Proposition~\ref{prop:convergence_average_clustering_P_n} therefore relies on analyzing the number of triangles coming from these additional edges and showing that their contribution to the local clustering function are of negligible order, see Section~\ref{sec:clustering_Pn_to_P}.
+
+\begin{remark}[Notations different graphs]
+We will use the subscripts $n$, $\Po$, $\text{box}$ and $\infty$ to identify properties of, respectively, the KPKVB mode $G_n$, the Poisson version $\GPo$, the finite box model $\Gbox$ and the infinite model $\Ginf$.
+For example $N_{\Po}(k)$ denotes number of nodes with degree $k$ in $\GPo$ and $\rho_{\text{box}}(y,k) = \Prob{\Po(\mu(\BallPo{y})) = k}$, i.e.
+the degree distribution of a typical point in $\Gbox$.
+\end{remark}
 
@@
 
-We are now ready to prove Theorem [??], using the propositions stated in the previous sections.
-As mentioned before, we focus here on the convergence statements.
-The computation of the exact expressions is done in Section~\ref{sec:asymptotics_average_clustering_ast_P}.
-We begin with Theorem~\ref{thm:local_clustering_hyperbolic}.
+We are now ready to prove Theorem~\ref{thm:mainktoinfty}, using the propositions stated in the previous sections.
 
-\begin{proof}[Proof of Theorem \ref{thm:local_clustering_hyperbolic}]
+\begin{proof}[Proof of Theorem~\ref{thm:mainktoinfty}]
 %By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
 %\begin{align*}
-%	&\hspace{-30pt}\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}\\
-%	&\le \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - \Exp{}c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)}
-%		+ \frac{\left|\Exp{c_{\Pcal,n}^\ast(k_n)} - c_\infty(k_n)\right|}{C_{\alpha,\nu}s_\alpha(k_n)}
-%		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| \\
+%	&\hspace{-30pt}\Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}\\
+%	&\le \frac{\Exp{\left|c^\ast(k_n; \Gbox) - \Exp{}c^\ast(k_n; \Gbox)\right|}}{C_{\alpha,\nu}\gamma(k_n)}
+%		+ \frac{\left|\Exp{c^\ast(k_n; \Gbox)} - \gamma(k_n)\right|}{C_{\alpha,\nu}\gamma(k_n)}
+%		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right| \\
 %	&= \smallO{1}.
@@
 \begin{align*}
-    c_{\H,n}(k_n)-c_\infty(k_n) =& c_{\H,n}(k_n)-c_{\H,n}^\ast(k_n)+c_{\H,n}^\ast(k_n)-c_{\HP,n}^\ast(k_n)+c_{\HP,n}^\ast(k_n)-c_{\Pcal,n}^\ast(k_n) \\
-    &+c_{\Pcal,n}^\ast(k_n)-\E c_{\Pcal,n}^\ast(k_n)+\E c_{\Pcal,n}^\ast(k_n)-c_\infty(k_n)
+    c(k_n;G_n)-\gamma(k_n) =& c(k_n;G_n)-c^\ast(k_n;G_n)+c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)+c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox) \\
+    &+c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)+\E c^\ast(k_n; \Gbox)-\gamma(k_n)
 \end{align*}
@@
 \begin{align*}
-    \E[|c_{\H,n}(k_n)-c_\infty(k_n)|] \leq & \E[|c_{\H,n}(k_n)-c_{\H,n}^\ast(k_n)|]+\E[|c_{\H,n}^\ast(k_n)-c_{\HP,n}^\ast(k_n)|]\\&+\E[|c_{\HP,n}^\ast(k_n)-c_{\Pcal,n}^\ast(k_n)|] 
-    +\E[|c_{\Pcal,n}^\ast(k_n)-\E c_{\Pcal,n}^\ast(k_n)|]\\&+\E[|\E c_{\Pcal,n}^\ast(k_n)-c_\infty(k_n)|]
+    \E[|c(k_n;G_n)-\gamma(k_n)|] \leq & \E[|c(k_n;G_n)-c^\ast(k_n;G_n)|]+\E[|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)|]\\&+\E[|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)|] 
+    +\E[|c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)|]\\&+\E[|\E c^\ast(k_n; \Gbox)-\gamma(k_n)|]
 \end{align*}
-At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{s_\alpha(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c_{\Pcal}(k_n) = c_\infty(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
+At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c(k_n;\Ginf) = \gamma(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
 \TM{ Maybe we can have a more clear reference?
@@
 \begin{align*}
-    \E[|c_{\H,n}(k_n)-c_\infty(k_n)|] = \smallO{s_\alpha(k_n)} = \smallO{c_\infty(k_n)}
+    \E[|c(k_n;G_n)-\gamma(k_n)|] = \smallO{s(k_n)} = \smallO{\gamma(k_n)},
 \end{align*}
-\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point.
+%\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point.
 }\PvdH{We can fix this by proving the scaling of $c_\infty(k)$ in Section~\ref{sec:asymptotics_average_clustering_ast_P}.}
@@
 %\[
-%	\Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
-%	\le \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right| 
-%	+ \frac{\Exp{\left|c_{\Pcal,n}^\ast(k_n) - c_\infty(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
+%	\Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}
+%	\le \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right| 
+%	+ \frac{\Exp{\left|c^\ast(k_n; \Gbox) - \gamma(k_n)\right|}}{C_{\alpha,\nu}\gamma(k_n)} = \smallO{1}.
 %\]
@@
 %\[
-%	\Exp{\left|\frac{c_{\H,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|}
-%	\le \Exp{\left|\frac{c_{\Pcal,n}^\ast(k_n)}{C_{\alpha,\nu}s_\alpha(k_n)} - 1\right|} 
-%	+ \frac{\Exp{\left|c_{\H,n}^\ast(k_n) - c_{\Pcal,n}^\ast(k_n)\right|}}{C_{\alpha,\nu}s_\alpha(k_n)} = \smallO{1}.
+%	\Exp{\left|\frac{c^\ast(k_n;G_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}
+%	\le \Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|} 
+%	+ \frac{\Exp{\left|c^\ast(k_n;G_n) - c^\ast(k_n; \Gbox)\right|}}{C_{\alpha,\nu}\gamma(k_n)} = \smallO{1}.
 %\]

### 2019-02-05 transition.tex
updated notation and added comments to sections 1-3

@@
-\section{From $G_{\mathcal{P}, n}(\alpha, \nu)$ to $G_{\mathcal{P}}(\alpha, \nu)$ (Proving Proposition \ref{prop:convergence_average_clustering_P_n})}\label{sec:clustering_Pn_to_P}
-
-Now that we have a complete picture of the behavior of the local clustering coefficient and function in the limit model $G_\Pcal$ we will proceed to relate this to the clustering in the hyperbolic model $G_{\H,n}$.
-The first step is to relate the clustering in the infinite model to that of the finite box model $G_{\Pcal, n}$.
-Recall that $G_{\Pcal,n}$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal_n = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ (we write $\Pcal_n$ for this process), and connecting two points $p_1, p_2 \in \Rcal_n$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$.
-We recall that by definition of the norm $|.|_{\pi e^{R_n/2}}$ the left and right boundaries of $\Rcal_n$ are identified.
+\section{From $\Gbox$ to $\Ginf$ (Proving Proposition \ref{prop:convergence_average_clustering_P_n})}\label{sec:clustering_Pn_to_P}
+
+In this section we shall relate the clustering in the finite box model $\Gbox$ to that of the infinite model.
+The main goal is to prove Proposition~\ref{prop:convergence_average_clustering_P_n} which states that
+\[
+	\Exp{\left|c^\ast(k_n; \Gbox) - \Exp{c^\ast(k_n; \Gbox)}\right|} = \smallO{s(k_n)}.
+\] 
+Recall that $\Gbox$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ (we write $\Pcal_n$ for this process), and connecting two points $p_1, p_2 \in \Rcal$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$.
+We recall that by definition of the norm $|.|_{\pi e^{R_n/2}}$ the left and right boundaries of $\Rcal$ are identified.
 See Section~\ref{ssec:finite_model} for more details.
@@
 
-\begin{remark}[Diverging $k_n$]
-Throughout this section $\{k_n\}_{n \ge 1}$ will denote an sequence of integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
-\end{remark}
-
 In this section we shall compute the asymptotic difference between triangle counts in the finite and infinite model. First we recall the definition of $\Kcal_{C}(k_n)$
 \[
-	\Kcal_C(k_n) = \left\{p \in \Rcal : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi_{\alpha,\nu}} \le e^{\frac{y}{2}}
-	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi_{\alpha,\nu}} \right\},	
-\]
-\TM{ Typo : $p\in\R$. Do you mean $\Rcal_n$? Or maybe 
+	\Kcal_C(k_n) = \left\{y \in \R_+ : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \le e^{\frac{y}{2}}
+	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\},	
+\]
+\TM{ Typo : $p\in\R$. Do you mean $\Rcal$? Or maybe 
 $\R \times \R^+$? Still not sure that max and min in defn add anything. } \PvdH{It was a typo and is corrected. I have removed the max and min.}
@@
 as $R_n - y \to \infty$.
-Since $e^{y/2} = \bigT{k_n} = \smallO{e^{R_n}}$ as $n \to \infty$, uniformly on $\Kcal_C$, it follows that $\phi_n(y) = \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}$, uniformly on $\Kcal_C$.
+Since $e^{y/2} = \bigT{k_n} = \smallO{e^{R_n}}$ as $n \to \infty$, uniformly on $\Kcal_C(k_n)$, it follows that $\phi_n(y) = \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}$, uniformly on $\Kcal_C$.
 This yields the following useful corollary to Lemma~\ref{lem:average_degree_P_n}.
@@
 \begin{corollary}\label{cor:average_degree_P_n_K}
-Let $\alpha > \frac{1}{2}$, $C > 0$. Then, for all $p \in \Kcal_{C}(k_n)$,
-\[
-	\mu_{\alpha,\nu ,n}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}\right).
+Let $\alpha > \frac{1}{2}$, $C > 0$. Then, for all $y \in \Kcal_{C}(k_n)$,
+\[
+	\mu(\BallPon{y}) = \mu(\BallPo{y})\left(1 - \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}\right).
 \]
@@
 
-\subsection{Comparing triangles between $G_\Pcal(\alpha,\nu)$ and $G_{\Pcal,n}(\alpha,\nu)$}
+\subsection{Comparing triangles between $\Ginf$ and $\Gbox$}
 
 We now turn to the task of calculating the expected number of triangles of a node at height $y$, for both the infinite model and the finite box model.
-Recall that we added a typical point $p_0 = (0,y)$, with exponentially distributed height, to the Poisson Point Process and that
-\[
-	\Exp{T_{\Pcal,n}(p_0)} = \frac{1}{2}\iint_{\Rcal_n^2} T_{\Pcal,n}(p_0,p_1,p_2)
-	f_{\alpha,\nu}(x_1,y_1) f_{\alpha,\nu}(x_1,y_1) \, dx_1 \, dx_2 \, dy_1 \, dy_2,
+Recall that we added a typical point $p_0 = (0,y)$, with exponentially distributed height to the Poisson Point Process.
+Then if we define
+\[
+	T_{\Pcal,n}(p) = \sum^{\ne}_{p_1, p_2 \in \Pcal_n \setminus p} T_{\Pcal,n}(p,p_1,p_2)
 \]
@@
 \]
+it follows that
+\[
+	\Exp{T_{\Pcal,n}(p_0)} = \frac{1}{2}\iint_{\Rcal^2} T_{\Pcal,n}(p_0,p_1,p_2)
+	f(x_1,y_1) f(x_1,y_1) \, dx_1 \, dx_2 \, dy_1 \, dy_2,
+\]
+
 \TM{ $p$ is supposed to be $p_0$ I assume. }\PvdH{Indeed. It has been corrected.}
-The difference between the indicator $\ind{p_1 \in B_{\Pcal,n}(p)}$ in the finite box model and $\ind{p_1 \in B_{\Pcal}(p)}$ is that in $G_{\Pcal,n}(\alpha,\nu)$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$ and we stop at height $y = R_n$.
-It is clear that for any $0 \le y \le R_n$ we have that $\BallPon{p_0} = \BallPo{p_0} \cap \Rcal_n$.
+The difference between the indicator $\ind{p_1 \in \BallPon{p}}$ in the finite box model and $\ind{p_1 \in \BallPo{p}}$ is that in $\Gbox$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$ and we stop at height $y = R_n$.
+It is clear that for any $0 \le y \le R_n$ we have that $\BallPon{p_0} = \BallPo{p_0} \cap \Rcal$.
 However, when we take another point $p^\prime \in \BallPon{p}$ then it could happen that there are points in the intersection $\BallPon{p} \cap \BallPon{p^\prime}$ that are not in $\BallPo{p} \cap \BallPo{p^\prime}$.
 Let us denote this region by $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$.
-Then, any $p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ creates a triangle with $p$ and $p^\prime$ in $G_{\Pcal,n}(\alpha,\nu)$ that is not present in $G_{\Pcal}(\alpha, \nu)$.
+Then, any $p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ creates a triangle with $p$ and $p^\prime$ in $\Gbox$ that is not present in $\Ginf$.
 
@@
 \begin{equation}\label{eq:def_tilde_triangle_indicator}
-	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal_n}
+	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal}
 \end{equation}
@@
 	%p = (\u,\v) and p^\prime = (\uu, \vv)
-	%Box \Rcal_n has width 2\r and height \t
+	%Box \Rcal has width 2\r and height \t
 	\pgfmathsetmacro{\u}{0} %0
@@
 
-	%The box \Rcal_n
+	%The box \Rcal
 	\draw[line width=1pt] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);
@@
 Figure \ref{fig:comparing_triangles_diff_intersections} shows an example of a configuration where $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime) \ne \emptyset$.
-We observe that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime) \ne \emptyset$ because the right boundary of the ball $\BallPon{p^\prime}$ exists the right boundary of the box $\Rcal_n$ and then, since we identified the boundaries, continues from the left so that $\BallPon{p^\prime}$ covers part of the ball $\BallPon{p}$ which would not be covered in the infinite limit model.
-
-To further analyze this, let us introduce some notation. For any $p = (x,y) \in \Rcal_n$ we will define the left and right boundary functions as, respectively,
+We observe that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime) \ne \emptyset$ because the right boundary of the ball $\BallPon{p^\prime}$ exists the right boundary of the box $\Rcal$ and then, since we identified the boundaries, continues from the left so that $\BallPon{p^\prime}$ covers part of the ball $\BallPon{p}$ which would not be covered in the infinite limit model.
+
+To further analyze this, let us introduce some notation. For any $p = (x,y) \in \Rcal$ we will define the left and right boundary functions as, respectively,
 \begin{align}
@@
 Note that these functions describe the boundaries of the ball $\BallPon{p}$.
-In particular, $p^\prime = \BL{(x^\prime, y^\prime)} \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
-
-Since we have identified the left and right boundary of $\Rcal_n$ we can assume, without loss of generality that $x = 0$.
+In particular, $p^\prime = x^\prime, y^\prime) \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
+
+Since we have identified the left and right boundary of $\Rcal$ we can assume, without loss of generality that $x = 0$.
 Due to symmetry it is then enough to restrict the analysis to the case where $x^\prime > 0$.
@@
 I have updated the text to better reflect this.}
-There are two important points in the box $\Rcal_n$.
+There are two important points in the box $\Rcal$.
 These are the intersection between the left boundary of $p^\prime$ and the right boundary of $p^\prime$, as it continues from the left side of the box, and the left boundary of $p$.
-We denote by $(x^\ast(p^\prime), y^\ast(p^\prime))$ the intersection between the left and right boundary of $p^\prime$ and by $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$ the intersection between the left boundary of $p$ and the right boundary of $p^\prime$, see Figure \ref{fig:comparing_triangles_diff_analysis}.
-After some simple algebra \TM{ I am not a big fan of writing "after some simple algebra" or similar.
+We denote by $(x^\ast(p^\prime), y^\ast(p^\prime))$ the intersection between the left and right boundary of $p^\prime$ and by $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$ the intersection between the left boundary of $p$ and the right boundary of $p^\prime$, see Figure \ref{fig:comparing_triangles_diff_intersections}.
+
+Let us derive the expressions for the coordinates of these two points, starting with $(x^\ast(p^\prime), y^\ast(p^\prime))$.
+The $x$-coordinate $x^\ast(p^\prime)$ is the solution to the equation $b_{p^\prime}^+(z) = b_{p^\prime}^-(z)$ for $-\frac{\pi}{2} e^{R_n/2} \le z \le x + e^{(y + R_n)/2} - \pi e^{R_n/2}$.
+This equation becomes
+\[
+	2\log\left(\pi e^{R_n/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x^\prime-z\right) - y^\prime,
+\]
+whose solution is $x^\ast(p^\prime) := x^\prime - \frac{\pi}{2} e^{R_n/2}$.
+Plugging this into either the left or right hand side of the above equation yields the $y$-coordinate $y^\ast(p^\prime) = 2\log\left(\frac{\pi}{2}e^{R_n/2}\right) - y^\prime$.
+In a similar way, the $x$-coordinate $\hat{x}(p,p^\prime)$ is the solution to the equation $b_{p^\prime}^+(z) = b_{p}^-(z)$ for $-\frac{\pi}{2} e^{R_n/2} \le z \le x + e^{(y + R_n)/2} - \pi e^{R_n/2}$, i.e.
+\[
+	2\log\left(\pi e^{R_n/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x-z\right) - y.
+\] 
+This solution is $\frac{x^\prime - \pi e^{R_n/2}}{1 + e^{(y^\prime - y)/2}}$ and again $\hat{y}(p,p^\prime)$ is obtained by plugging the solution into either left or right hand side of the equation, yielding $\hat{y}(p,p^\prime) = 2 \log\left(\frac{\pi e^{R_n/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)$.
+
+To summarize we have:
+% After some simple algebra \TM{ I am not a big fan of writing "after some simple algebra" or similar.
 This is how errors can creep into your argument.
@@
 which is displayed by the red curve in Figure \ref{fig:comparing_triangles_diff_analysis}.
-It holds that $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$ if and only if $y^\prime < b^\ast_p(x^\prime)$ and hence we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$ for all $p^\prime \in \Rcal_n$ for which $y^\prime \ge b^\ast_p(x^\prime)$.
+It holds that $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$ if and only if $y^\prime < b^\ast_p(x^\prime)$ and hence we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$ for all $p^\prime \in \Rcal$ for which $y^\prime \ge b^\ast_p(x^\prime)$.
 We also not that when $y^\prime = b^\ast_p(x^\prime)$ the two points $(x^\ast(p^\prime), y^\ast(p^\prime))$ and $(\hat{x}(p,p^\prime),\hat{y}(p,p^\prime))$ coincide.
@@
 	%p = (\u,\v) and p^\prime = (\uu, \vv)
-	%Box \Rcal_n has width 2\r and height \t
+	%Box \Rcal has width 2\r and height \t
 	\pgfmathsetmacro{\u}{0}
@@
 \end{tikzpicture}
-\caption{\PvdH{@All: This still needs a caption.}}
+\caption{Example for a given $p$ of the boundary function $x^\prime \mapsto b^\ast_p(x^\prime)$, given by the red curve, which determines whether $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$.
+We see that when $y^\prime = b^\ast_p(x^\prime)$ then $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime)) = (x^\ast(p^\prime), y^\ast(\prime))$.}
 \label{fig:comparing_triangles_diff_analysis}
@@
 \begin{lemma}\label{lem:clustering_error_T_term}
-Let $(k_n)_{n \ge 1}$ be any sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, for some $C > 0$ and $p \in \Kcal_{C}(k_n)$, as $n \to \infty$,
-\[
-	\int_{\Rcal_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\alpha, \nu}(x_1,y_1) 
+Let $p_0 = (0,y)$ with $y \in \Kcal_{C}(k_n)$. Then for some $C > 0$, as $n \to \infty$,
+\[
+	\int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)\right) f(x_1,y_1) 
 	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
@@
 We postpone this proof till the end of this section and proceed with the main goal, proving Proposition~\ref{prop:convergence_average_clustering_P_n}.
-But first we state a small lemma about the scaling of $s_\alpha(k_n)$ that will be very useful.
+But first we state a small lemma about the scaling of $s(k_n)$ that will be very useful.
 
 \begin{lemma}\label{lem:scaling_s_alpha}
-Let $s_\alpha(k_n)$ be as defined in \eqref{eq:def_scaling_function}. Then for any $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$,
-\[
-	n^{-(2\alpha - 1)} = \smallO{s_\alpha(k_n)}.
+Let $s(k_n)$ be as defined in \eqref{eq:def_scaling_function}. Then for any $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$,
+\[
+	n^{-(2\alpha - 1)} = \smallO{s(k_n)}.
 \]
@@
 \[
-	n^{-(2\alpha - 1)}s_\alpha(k_n)^{-1} = n^{-(2\alpha -1)}k_n^{4\alpha - 2}
+	n^{-(2\alpha - 1)}s(k_n)^{-1} = n^{-(2\alpha -1)}k_n^{4\alpha - 2}
 	= \smallO{n^{-(2\alpha - 1) + \frac{4\alpha - 2}{2\alpha + 1}}} 
@@
 
+Let $\mathrm{deg}_{\text{box}}(y)$ denote the number of nodes in the ball $\BallPon{y}$ (degree of typical node at height $y$) and similarly $\mathrm{deg}_n(y)$ is the number of nodes in $\BallHyp{y}$.
 Recall that
 \[
-	\Exp{c_{\Pcal,n}^\ast(k_n)} = \frac{\int_{\Rcal_n} \Exp{\ind{D_{\Pcal,n}(y) = k_n} T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y}{\binom{k_n}{2}\Exp{N_{\Pcal,n}(k_n)}}.
-\]
-By Lemma~\ref{lem:average_degree_P_n} and a concentration argument \TM{ please give more details! }
-\[
-	\Exp{N_{\Pcal,n}(k_n)} = (1+o(1)) \alpha n \int_{0}^\infty \rho(y,k_n) e^{-\alpha} \dd y 
-	= (1+\smallO{1}) n \Exp{N_{\Pcal}(k_n)},
-\]
-and since $\Exp{\ind{D_{\H,n}(y) = k_n} T_{\Pcal,n}(y)} \le \rho_n(y,k_n) k_n^2$ another concentration argument yields
-\begin{align*}
-	&\hspace{-30pt}\int_{\Rcal_n} \Exp{\ind{D_{\H,n}(y) = k_n} T_{\Pcal,n}(y)} 
-		f_{\alpha,\nu}(x,y) \dd x \dd y\\
-	&= (1+\smallO{1})\int_{\Kcal_C(k_n)} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y\\
-	&= (1 + \smallO{1}) \alpha n \int_{a_n^-}^{a_n^+} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha} \dd x \dd y,
-\end{align*}
-with $a_n^\pm = 2\log\left(\frac{k_n \pm C \kappa_n}{\xi_{\alpha,\nu}}\right)$. \TM{ again, this def has to be adapted. } Next we note that for $a_n^- \le y \le a_n^-$,
-\[
-	\Exp{T_\Pcal(y)} = \frac{\Mu{\BallPo{y}}^2}{2} \Delta_\Pcal(y) = (1+\smallO{1}) \binom{k_n}{2} \Delta_\Pcal(y)
-\]
+	\Exp{c^\ast(k_n; \Gbox)} = \frac{\int_{\Rcal} \Exp{\ind{\mathrm{deg}_{\text{box}}(y) = k_n} T_{\Pcal,n}(y)} f(x,y) \dd x \dd y}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}},
+\]
+and the definition of $\Kcal_{C,n}(k_n)$
+\[
+	\Kcal_{C,n}(k_n) = \left\{ (x,y) \in \Rcal \, : \, \frac{k_n - C k_n}{\xi} \le e^{\frac{y}{2}}
+		\le \frac{k_n + C \kappa_n}{\xi} \right\},
+\]
+where for $k_n \to \infty$ we defined $\kappa_n := \sqrt{k_n \log(k_n)}$.
+
+Since 
+\[
+	\Exp{N_{\text{box}}(k_n)} = \int_{\Rcal} \rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y,
+\]
+the Corollary~\ref{cor:concentration_argument_other_models}, using the second statement of Lemma~\ref{lem:concentration_argument_rho_approximation}, implies
+\[
+	\Exp{N_{\text{box}}(k_n)} = (1+o(1)) \alpha n \int_{0}^\infty \rho(y,k_n) e^{-\alpha} \dd y 
+	= (1+\smallO{1}) n \Exp{N_{\infty}(k_n)}.
+\]
+Moreover, since $\Exp{\ind{\mathrm{deg}_n(y)(y) = k_n} T_{\Pcal,n}(y)} \le \rho_{\text{box}}(y,k_n) k_n^2$ a concentration of heights argument (cf.
+first statement of Lemma~\ref{lem:concentration_argument_rho_approximation}) yields
+\begin{align*}
+	&\hspace{-30pt}\int_{\Rcal} \Exp{\ind{\mathrm{deg}_n(y) = k_n} T_{\Pcal,n}(y)} 
+		f(x,y) \dd x \dd y\\
+	&= (1+\smallO{1})\int_{\Kcal_{C,n}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{T_{\Pcal,n}(y)} f(x,y) \dd x \dd y\\
+	&= (1 + \smallO{1}) \alpha n \int_{a_n^-}^{a_n^+} \rho_{\text{box}}(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha} \dd x \dd y,
+\end{align*}
+with $a_n^\pm = 2\log\left(\frac{(k_n \pm C \kappa_n) \wedge \xi_{\alpha, \nu}}{\xi}\right)$. %\TM{ again, this def has to be adapted. } 
+Next we note that for $a_n^- \le y \le a_n^+$,
+\begin{equation}\label{eq:relation_E_T_Pcal_vs_Delta_P}
+	\Exp{T_\Pcal(y)} = \frac{\Mu{\BallPo{y}}^2}{2} P(y) = (1+\smallO{1}) \binom{k_n}{2} P(y)
+\end{equation}
 and hence it now suffices to show that
 \[
-	\binom{k_n}{2}^{-1}\int_{a_n^-}^{a_n^+} \rho_n(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha y} \dd y
-	= (1+\smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Delta_\Pcal(y) e^{-\alpha y} \dd y. 
-\]
-
-We do this in two stages. First we prove that
+	\binom{k_n}{2}^{-1}\int_{a_n^-}^{a_n^+} \rho_{\text{box}}(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha y} \dd y
+	= (1+\smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha y} \dd y. 
+\]
+
+We do this in two stages. First note that by a concentration of heights argument
 \begin{equation}\label{eq:transition_clustering_main_term}
-	\int_{a_n^-}^{a_n^+} \rho_{n}(y,k_n) \Delta_{\Pcal}(y) e^{-\alpha y} \dd y
-	= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Delta_{\Pcal}(y) e^{-\alpha y} \dd y.
+	\int_{a_n^-}^{a_n^+} \rho_{n}(y,k_n) P(y) e^{-\alpha y} \dd y
+	= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha y} \dd y.
 \end{equation}
-Then we show that
+It therefore remains toshow that
 \begin{equation}\label{eq:transition_clustering_error_term}
-	\binom{k_n}{2}^{-1} \int_{a_n^-}^{a_n^+} \rho_n(y,k_n) \left|\Exp{T_{\Pcal,n}(y) - T_{\Pcal}(y)}\right| 
+	\binom{k_n}{2}^{-1} \int_{a_n^-}^{a_n^+} \rho_{\text{box}}(y,k_n) \left|\Exp{T_{\Pcal,n}(y) - T_{\Pcal}(y)}\right| 
 	e^{-\alpha y} \dd y
-	= \smallO{1} \int_{a_n^-}^{a_n^+} \rho(y,k_n) \Delta_{\Pcal}(y) e^{-\alpha y} \dd y.
+	= \smallO{1} \int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha y} \dd y.
 \end{equation}
 
-Since $h(y) := \Delta_\Pcal(y)$ is uniformly bounded \eqref{eq:transition_clustering_main_term} follows directly from the second statement in Lemma~\ref{lem:concentration_argument_rho_approximation}.
-
-For the error term~\eqref{eq:transition_clustering_error_term} we write
-\begin{align*}
-	\left|T_{\Pcal,n}(p) - T_{\Pcal}(p)\right| = \sum_{p_1, p_2 \in \Rcal_n} \ind{p_1 \in \BallPon{p}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p, p_1)} + \sum_{p_1, p_2 \in \Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2)
-\end{align*}
-so that by the Campbell-Mecke formula~\eqref{eq:def_Campbell-Mecke}
+For this we write
+\begin{align*}
+	\left|T_{\Pcal,n}(p) - T_{\Pcal}(p)\right| = \sum_{p_1, p_2 \in \Rcal} \ind{p_1 \in \BallPon{p}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p, p_1)} + \sum_{p_1, p_2 \in \Rcal \setminus \Rcal} T_{\Pcal}(p,p_1,p_2)
+\end{align*}
+so that by the Campbell-Mecke formula
 \begin{align*}
 	\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right|
-	&\le \int_{\Rcal_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\alpha, \nu}(x_1,y_1) 
+	&\le \int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f(x_1,y_1) 
 		\dd x_1 \dd y_1\\
-	&\hspace{10pt}+ \BL{\int_{\Rcal \setminus \Rcal_n}\int_{\Rcal \setminus \Rcal_n}} T_{\Pcal}(p,p_1,p_2) f_{\alpha, \nu}(x_1,y_1) f_{\alpha, \nu}(x_2,y_2)
+	&\hspace{10pt}+ \BL{\int_{\Rcal \setminus \Rcal}\int_{\Rcal \setminus \Rcal}} T_{\Pcal}(p,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
 		\dd x_2 \dd y_2 \dd x_1 \dd y_1. 
@@
 
-\TM{ in the 1st integral we could have restricted to
-the ball of $p$, and possibly saved a lot. 
-Does that not help? }
+\TM{ in the 1st integral we could have restricted to the ball of $p$, and possibly saved a lot.
+Does that not help?
+}\PvdH{the first integral is taken care of by another Lemma so it does not matter I think.}
 The first integral was taken care of in Lemma \ref{lem:clustering_error_T_term}. For the second integral we have
 \begin{align*}
-	&\hspace{-30pt}\iint_{\Rcal \setminus \Rcal_n} T_{\Pcal}(p,p_1,p_2) f_{\alpha, \nu}(x_1,y_1) f_{\mu, \nu}(x_2,y_2)
+	&\hspace{-30pt}\iint_{\Rcal \setminus \Rcal} T_{\Pcal}(p,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
 		\dd x_2 \dd y_2 \dd x_1 \dd y_1\\
-	&\le \left(\int_{\Rcal \setminus \Rcal_n} \ind{p_1 \in \BallPo{p}} f_{\alpha, \nu}(x_1,y_1) \dd x_1 \dd y_1\right)^2\\
-	&= \bigO{\left(e^{y/2} \int_{R_n}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}
-		= \bigO{e^y n^{-(2\alpha - 1)}},
-\end{align*}
-\TM{ Typo : $f_{\mu, \nu}$? Also give more details how line 3 follows. }
+	&\le \left(\int_{\Rcal \setminus \Rcal} \ind{p_1 \in \BallPo{p}} f(x_1,y_1) \dd x_1 \dd y_1\right)^2
+		= \bigO{\left(e^{y/2} \int_{R_n}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}\\
+	&= \bigO{e^{y} e^{-(2\alpha-1)R_n}} = \bigO{e^y n^{-(4\alpha - 2)}},
+\end{align*}
+%\TM{ Typo : $f_{\mu, \nu}$? Also give more details how line 3 follows. }
 from which we conclude that
-\[
-	\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
-	= \bigO{n^{-(2\alpha-1)} e^{y}}.
-\]
-Therefore 
+\begin{equation}\label{eq:triangle_count_diff_scaling}
+	\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| = \bigO{y n^{-(2\alpha - 1)} + n^{-(4\alpha-2)} e^{y}}
+	= \bigO{n^{-(4\alpha-2)} e^{y}}.
+\end{equation}
+Therefore, since $e^{y} = \bigO{1} k_n^2$ on $\Kcal_C(k_n)$, 
 \begin{align*}
 	&\hspace{-30pt}\binom{k_n}{2}^{-1}\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| 
-		e^{-\alpha} \dd y\\
-	&= \bigO{1} n^{-(2\alpha - 1)} \int_{0}^\infty \rho(y,k_n) f_{\alpha,\nu}(x,y) \dd y\\
-	&= \bigO{1} n^{-(2\alpha - 1)} k_n^{-(2\alpha + 1)} = \smallO{s_\alpha(k_n) k_n^{-(2\alpha + 1)} },
-\end{align*}
-\TM{ Typo : $e^{-\alpha}$ }
-where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. \TM{ Also justify penultimate step! }
+		e^{-\alpha y} \dd y\\
+	&= \bigO{1} n^{-(4\alpha - 2)} \int_{0}^\infty \rho(y,k_n) e^{-\alpha y} \dd y\\
+	&= \bigO{1} n^{-(4\alpha - 2)} k_n^{-(2\alpha + 1)} = \smallO{s(k_n) k_n^{-(2\alpha + 1)} },
+\end{align*}
+%\TM{ Typo : $e^{-\alpha}$ }
+where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. \TM{ Also justify penultimate step! }\PvdH{What do you mean?}
 To finish the argument we observe that
 \begin{align*}
-	\int_{a_n^-}^{a_n^+} \rho(y,k_n) \Delta_\Pcal(y) e^{-\alpha} \dd y
-	&= \bigT{1} \Exp{N_{\Pcal}(k_n)} c_\infty(k_n) = \bigT{ s_\alpha(k_n) k_n^{-(2\alpha + 1)}}.
+	\int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha} \dd y
+	&= \bigT{1} \Exp{N_{\infty}(k_n)} \gamma(k_n) = \bigT{ s(k_n) k_n^{-(2\alpha + 1)}}.
 \end{align*}
@@
 
-Observe that the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} yields the following two corollaries, which will be useful later on in Section~\ref{sec:concentration_c_P_n}.
+From the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} we can extract the following corollary, which will be useful later on in Section~\ref{sec:concentration_c_P_n}.
 
 \begin{corollary}\label{cor:adjusted_triangle_counting_P_n}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $k_n$ be a positive sequence such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. Then, uniformly for all $p \in \Kcal_C(k_n)$, as $n \to \infty$
-\[
-	\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1+\smallO{1})\Exp{T_\Pcal(p)},
+Uniformly for all $y \in \Kcal_C(k_n)$, as $n \to \infty$
+\[
+	\Exp{\widetilde{T}_{\Pcal,n}(y)} = (1+\smallO{1})\Exp{T_\Pcal(y)},
 \]
@@
 \[
-	\widetilde{T}_{\Pcal,n}(p) = \sum_{(p_1, p_2) \in \Pcal\setminus p}^{\ne} 
-		\ind{p_1 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal,n}(p)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal_n}.
+	\widetilde{T}_{\Pcal,n}(y) = \sum_{(p_1, p_2) \in \Pcal}^{\ne} 
+		\ind{p_1 \in B_{\Pcal,n}(y)}\ind{p_2 \in B_{\Pcal,n}(y)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal}.
 \]
@@
 \[
-	\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_n(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(y)} f_{\alpha,\nu}(x,y) \dd x \dd y
-	= (1+\smallO{1}) \int_{\Rcal_n} \rho(y,k_n) \Delta_\Pcal(y) f_{\alpha, \nu}(x,y) \dd x \dd y. 
+	\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(y)} f(x,y) \dd x \dd y
+	= (1+\smallO{1}) \int_{\Rcal} \rho(y,k_n) P(y) f(x,y) \dd x \dd y. 
 \]
@@
 
-\TM{ Some words spelling this out would help. I don't find it easy to see. Also, in general I think one should avoid saying things like "the proof of such-and-such also gives .." }
+\begin{proof}
+First we note that equation~\eqref{eq:triangle_count_diff_scaling} implies that for $y \in \Kcal_C(k_n)$
+\[
+	\Exp{\left|\widetilde{T}_{\Pcal,n}(y) - T_\Pcal(y)\right|} = \bigO{n^{-(4\alpha - 2)}k_n^2}.
+\]
+Next, equation~\ref{eq:relation_E_T_Pcal_vs_Delta_P} together with Proposition~\ref{prop:asymp} yield
+\[
+	\Exp{T_\Pcal(y)} = (1+\smallO{1})\binom{k_n}{2} P(y) = \bigT{k_n^2 s(k_n)},
+\]
+on $\Kcal_{C}(k_n)$, with $s(k)$ defined by~\eqref{eq:def_scaling_function}. By Lemma~\ref{lem:scaling_s_alpha} we now have that for all $y \in \Kcal_{C}(k_n)$
+\[
+	n^{-(4\alpha - 2)}k_n^2 = \smallO{k_n^2 s(k_n)} = \smallO{\Exp{T_\Pcal(y)}}
+\]
+and hence
+\[
+	\Exp{\widetilde{T}_{\Pcal,n}(y)} = \Exp{T_\Pcal(y)} + \bigO{\Exp{\left|\widetilde{T}_{\Pcal,n}(y) - T_\Pcal(y)\right|}}
+	= (1+\smallO{1})\Exp{T_\Pcal(y)}.
+\]
+
+Using this we derive the second statement as follows 
+\begin{align*}
+	&\hspace{-30pt}\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(y)} 
+		f(x,y) \dd x \dd y\\
+	&=(1 + \smallO{1})\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{T_\Pcal(y)} 
+		f(x,y) \dd x \dd y\\
+	&=(1 + \smallO{1})\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) P(y)f(x,y) \dd x \dd y \\
+	&=(1 + \smallO{1})\int_{\Rcal} \rho_{\text{box}}(y,k_n) P(y)f(x,y) \dd x \dd y
+\end{align*}
+where the third line is due to equation~\eqref{eq:relation_E_T_Pcal_vs_Delta_P} and the last line follows by a concentration of heights argument.
+\end{proof}
+
+%\TM{ Some words spelling this out would help. I don't find it easy to see. Also, in general I think one should avoid saying things like "the proof of such-and-such also gives .." }
 \subsection{Counting missing triangles}
 
-We now come back to computing the expected number of triangles attached to node at height $y$ in $G_{\Pcal,n}(\alpha,\nu)$ that are not present in $G_{\Pcal}(\alpha,\nu)$.
+We now come back to computing the expected number of triangles attached to node at height $y$ in $\Gbox$ that are not present in $\Ginf$.
 
@@
 
-	%The box \Rcal_n only positive x
+	%The box \Rcal only positive x
 	\draw[line width=1pt] (0,0) -- (\r,0) -- (\r,\t) -- (0,\t) -- (0,0);
@@
 \begin{equation}\label{eq:clustering_error_T_main}
-	\int_0^{R_n}\int_0^{I_n} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f_{\mu, \nu}(x_1,y_1) 
+	\int_0^{R_n}\int_0^{I_n} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f(x_1,y_1) 
 	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
@@
 The proof goes in two stages.
-First we compute $\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right)$ by splitting it over three disjoint regimes with respect to $p_1$, with $x_1 \ge 0$.
+First we compute $\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right)$ by splitting it over three disjoint regimes with respect to $p_1$, with $x_1 \ge 0$.
 Then we do the integration with respect to $p_1$.
 
-\subsubsection*{Computing $\bm{\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right)}$}
+\subsubsection*{Computing $\bm{\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right)}$}
 
@@
 \begin{align*}
-	A_n^{(1)} &= \left\{p_1 \in \Rcal_n \, : \, 0 \le y_1 \le y - 2\log(I_n/(I_n-x_1)) \right\},\\
-	A_n^{(2)} &= \left\{p_1 \in \Rcal_n \, : \, y - 2\log(I_n/(I_n-x_1)) < y_1 
+	A_n^{(1)} &= \left\{p_1 \in \Rcal \, : \, 0 \le y_1 \le y - 2\log(I_n/(I_n-x_1)) \right\},\\
+	A_n^{(2)} &= \left\{p_1 \in \Rcal \, : \, y - 2\log(I_n/(I_n-x_1)) < y_1 
 		\le y + 2 \log\left(1 + \frac{x_1}{I_n}\right)\right\},\\
-	A_n^{(3)} &= \left\{p_1 \in \Rcal_n \, : \, y + 2 \log\left(1 + \frac{x_1}{I_n}\right) < y_1 
+	A_n^{(3)} &= \left\{p_1 \in \Rcal \, : \, y + 2 \log\left(1 + \frac{x_1}{I_n}\right) < y_1 
 			\le y + 2 \log\left(\frac{I_n}{I_n-x_1}\right)\right\},
@@
 
-With these definitions we have that the union $B_n := \bigcup_{i = 1}^n B_n^{(i)}$ denotes the area under the red curve in Figure~\ref{fig:comparing_triangles_diff_analysis} and hence, for all $p_1 \in \Rcal_n\setminus B_n$ with $x_1 \ge 0$ we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1) = \emptyset$.
+With these definitions we have that the union $B_n := \bigcup_{i = 1}^n B_n^{(i)}$ denotes the area under the red curve in Figure~\ref{fig:comparing_triangles_diff_analysis} and hence, for all $p_1 \in \Rcal\setminus B_n$ with $x_1 \ge 0$ we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1) = \emptyset$.
 So we only need to consider $p_1 \in B_n$.
@@
 \begin{equation}\label{eq:mu_triangle_diff}
-	\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = 
+	\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = 
 	\begin{cases}
@@
 \[
-	\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}},
+	\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}},
 \]
@@
 \begin{align*}
-	\mathcal{I}_n^{(1)}(p,p_1) &\le \int_{h(y)}^{h_1(p_1)} \int_{-I_n}^{x^\ast(p,p_1)} f_{\alpha,\nu}(x_2, y_2) 
+	\mathcal{I}_n^{(1)}(p,p_1) &\le \int_{h(y)}^{h_1(p_1)} \int_{-I_n}^{x^\ast(p,p_1)} f(x_2, y_2) 
 		\dd x_2 \dd y_2\\
@@
 	\mathcal{I}_n^{(2)} &= \int_{\hat{y}(p,p_1)}^{h(y)} \int_{-e^{(y + y_2)/2}}^{x_1 + e^{(y+y_1)/2} - 2 I_n} 
-		f_{\alpha,\nu}(x_2, y_2) \dd x_2 \dd y_2\\
+		f(x_2, y_2) \dd x_2 \dd y_2\\
 	&= \bigO{e^{y/2} \int_{\hat{y}(p,p_1)}^{h(y)} e^{-(\alpha -\frac{1}{2}) y_2} \dd y_2}\\
@@
 \[
-	\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-(2\alpha-1)} e^{\alpha y}}.
+	\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-(2\alpha-1)} e^{\alpha y}}.
 \]
@@
 \begin{align*}
-	\mathcal{I}_n^{(1)} &= \int_{y^\ast}^{\tilde{y}} \int_{-e^{(y+y_2)/2}}^{x_1-e^{(y_1+y_2)/2}} f_{\alpha, \nu}(x_2,y_2)
+	\mathcal{I}_n^{(1)} &= \int_{y^\ast}^{\tilde{y}} \int_{-e^{(y+y_2)/2}}^{x_1-e^{(y_1+y_2)/2}} f(x_2,y_2)
 		\dd x_2 \dd y_2\\
@@
 	\mathcal{I}_n^{(2)} &= \int_{\hat{y}}^{y^\ast} \int_{-e^{(y+y_2)/2}}^{e^{(y_1 + y_2)/2} + x_1 - 2I_n} 
-		f_{\alpha, \nu}(x_2,y_2)\dd x_2 \dd y_2\\
+		f(x_2,y_2)\dd x_2 \dd y_2\\
 	&= \bigO{\int_{\hat{y}}^{y^\ast} \left(e^{y/2} + e^{y_1/2}\right)e^{-(\alpha - \frac{1}{2})y_2} \dd y_2}\\
@@
 \[
-	\mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
+	\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
 	= \bigO{I_n^{-(2\alpha - 1)} e^{\alpha y}}.
@@
 We now proceed with the second part of the computation leading to \eqref{eq:clustering_error_T_main}.
-Here we will integrate $\mu_{\alpha, \nu}(\mathcal{T}_{\Pcal \Delta \Pcal_n})(p,p_1)$ over the region $B_n := B_n^{(1)} \cup B_n^{(2)} \cup B_n^{(3)}$, see Figure~\ref{fig:comparing_triangles_B_areas}.
+Here we will integrate $\mu(\mathcal{T}_{\Pcal \Delta \Pcal_n})(p,p_1)$ over the region $B_n := B_n^{(1)} \cup B_n^{(2)} \cup B_n^{(3)}$, see Figure~\ref{fig:comparing_triangles_B_areas}.
 Let us first identify the boundaries of these areas.
@@
 
-We these characterizations of the areas we now integrate $\mu_{\alpha, \nu}(\mathcal{T}_{\Pcal \Delta \Pcal_n})(p,p_1)$ over $B_n$, splitting the computations over the three different areas.
+We these characterizations of the areas we now integrate $\mu(\mathcal{T}_{\Pcal \Delta \Pcal_n})(p,p_1)$ over $B_n$, splitting the computations over the three different areas.
 
@@
 \begin{align*}
-	&\hspace{-30pt}\int_{B_n^{(1)}} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
-		f_{\alpha,\nu}(x_1,y_1)	\dd x_1 \dd y_1 \\
-	&\le  \int_0^y \int_0^{I_n(1-e^{(y_1-y)/2})} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
-		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
+	&\hspace{-30pt}\int_{B_n^{(1)}} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
+		f(x_1,y_1)	\dd x_1 \dd y_1 \\
+	&\le  \int_0^y \int_0^{I_n(1-e^{(y_1-y)/2})} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
+		f(x_1,y_1) \dd x_1 \dd y_1\\
 	&= \bigO{ I_n^{-2\alpha} \int_0^y \int_0^{e^{(y+y_1)/2}}  x_1 \dd x_1 \dd y_1 }\\
@@
 \begin{equation}\label{eq:mu_triangle_diff_2}
-	\mu_{\alpha, \nu}(B_n^{(2)}) = \bigO{I_n^{-1} e^{(2-\alpha)y}},
+	\mu(B_n^{(2)}) = \bigO{I_n^{-1} e^{(2-\alpha)y}},
 \end{equation}
@@
 \begin{align*}
-	\int_{B_n^{(2)}} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
-		f_{\alpha,\nu}(x_1,y_1)	\dd x_1 \dd y_1
-	&= \bigO{\mu_{\alpha, \nu}(B_n^{(2)}) I_n^{-(2\alpha - 1)} e^{\alpha y}}\\
+	\int_{B_n^{(2)}} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
+		f(x_1,y_1)	\dd x_1 \dd y_1
+	&= \bigO{\mu(B_n^{(2)}) I_n^{-(2\alpha - 1)} e^{\alpha y}}\\
 	&= \bigO{I_n^{-2\alpha} e^{2y}}.
@@
 \begin{align*}
-	\mu_{\alpha, \nu}(B_n^{(3)}) &= \int_{h_\ast(y)}^{y} \int_{I_n(1-e^{(y_1-y)/2})}^{e^{(y + y_1)/2}} 
-		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
+	\mu(B_n^{(3)}) &= \int_{h_\ast(y)}^{y} \int_{I_n(1-e^{(y_1-y)/2})}^{e^{(y + y_1)/2}} 
+		f(x_1,y_1) \dd x_1 \dd y_1\\
 	&\hspace{10pt} + \int_y^{h^\ast(y)} \int_{I_n(e^{(y_1-y)/2}-1)}^{e^{(y + y_1)/2}} 
-		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1.
+		f(x_1,y_1) \dd x_1 \dd y_1.
 \end{align*}
@@
 \begin{align*}
-	&\hspace{-30pt}\int_{h_\ast(y)}^{y} \int_{I_n(1-e^{(y_1-y)/2})}^{e^{(y + y_1)/2}} f_{\alpha,\nu}(x_1,y_1) 
+	&\hspace{-30pt}\int_{h_\ast(y)}^{y} \int_{I_n(1-e^{(y_1-y)/2})}^{e^{(y + y_1)/2}} f(x_1,y_1) 
 		\dd x_1 \dd y_1\\
@@
 \begin{align*}
-	&\hspace{-30pt}\int_y^{h^\ast(y)} \int_{I_n(e^{(y_1-y)/2}-1)}^{e^{(y + y_1)/2}} f_{\alpha,\nu}(x_1,y_1) 
+	&\hspace{-30pt}\int_y^{h^\ast(y)} \int_{I_n(e^{(y_1-y)/2}-1)}^{e^{(y + y_1)/2}} f(x_1,y_1) 
 		\dd x_1 \dd y_1\\
@@
 \begin{equation}\label{eq:mu_triangle_diff_3}
-	\mu_{\alpha, \nu}(B_n^{(3)}) = \bigO{e^{(1-\alpha)y}}
+	\mu(B_n^{(3)}) = \bigO{e^{(1-\alpha)y}}
 \end{equation} 
@@
 \begin{align*}
-	\int_{B_n^{(3)}} \mu_{\alpha, \nu}\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
-		f_{\alpha,\nu}(x_1,y_1)	\dd x_1 \dd y_1
-	&= \bigO{\mu_{\alpha, \nu}(B_n^{(2)}) I_n^{-(2\alpha - 1)} e^{\alpha y}}\\
+	\int_{B_n^{(3)}} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
+		f(x_1,y_1)	\dd x_1 \dd y_1
+	&= \bigO{\mu(B_n^{(2)}) I_n^{-(2\alpha - 1)} e^{\alpha y}}\\
 	&= \bigO{I_n^{-(2\alpha-1)} e^{y}}.
@@
 \begin{align*}
-	\mu_{\alpha, \nu}(B_n^{(3)}) &= \int_y^{h^\ast(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n(e^{(y_1-y)/2}-1)}
-		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
+	\mu(B_n^{(3)}) &= \int_y^{h^\ast(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n(e^{(y_1-y)/2}-1)}
+		f(x_1,y_1) \dd x_1 \dd y_1\\
 	&\hspace{10pt}+ \int_{h^\ast(y)}^{h(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{e^{(y+y_1)/2}}
-		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1\\
+		f(x_1,y_1) \dd x_1 \dd y_1\\
 	&\hspace{10pt}+ \int_{h(y)}^{R_n} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n}
-		f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1.
+		f(x_1,y_1) \dd x_1 \dd y_1.
 \end{align*}
@@
 \begin{align*}
-	\int_y^{h^\ast(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n(e^{(y_1-y)/2}-1)} f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
+	\int_y^{h^\ast(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n(e^{(y_1-y)/2}-1)} f(x_1,y_1) \dd x_1 \dd y_1
 	&= \bigO{I_n e^{-y/2} \int_y^{h^\ast(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1}\\
@@
 \begin{align*}
-	\int_{h^\ast(y)}^{h(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{e^{(y+y_1)/2}}	f_{\alpha,\nu}(x_1,y_1) \dd x_1 \dd y_1
+	\int_{h^\ast(y)}^{h(y)} \int_{I_n(1-e^{(y-y_1)/2})}^{e^{(y+y_1)/2}}	f(x_1,y_1) \dd x_1 \dd y_1
 	&= \bigO{I_n e^{-y/2} \int_{h^\ast(y)}^{h(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1}

### 2019-02-17 introduction.tex
typos

@@
 
-Our second result in on the clustering function for constant $k$.
+Our second result is on the clustering function for constant $k$.
 
@@
 \]
-so that the clustering function if the KPKVB model scales as $\gamma(k)$ as $k$ grows.
+so that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows.
 

### 2019-02-17 paper.tex
typos

@@
 This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant.
-Similarly, we are able to show that $c(k)$, the average clustering over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ given explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
+Similarly, we are able to show that $c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ given explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
 We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$.

### 2019-02-17 proof_overview_finite_k.tex
typos

@@
 makes the model invariant under horizontal shifts and reflections in vertical lines. 
-The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\mathcal{V}_n$, with some addition edges caused by 
+The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\mathcal{V}_n$, with some additional edges caused by 
 the identification of the boundaries.
@@
 \noindent
-This can be reprased as $p'\in \BallHyp{p}$ iff.~either $y+y'\geq R$ or $y+y'<R$ and
+This can be rephrased as $p'\in \BallHyp{p}$ iff.~either $y+y'\geq R$ or $y+y'<R$ and
 

### 2019-02-21 concentration.tex
typos in section 9.3

@@
 In addition we denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$.
-We shall establish lower bounds on the expect number of these disjoint neighbors $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors.
+We shall establish lower bounds on the expected number of these disjoint neighbors $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors.
 For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large.
@@
 Figure \ref{fig:representation_disjoint_neighborhoods_P_n} and Figure \ref{fig:representation_disjoint_neighborhoods_P_n_2} show two different situations for small distance in the $x$-coordinates, in which case the number of disjoint neighbors is small.
-The case where this distance is large, and the number of disjoint neighbors is expected to be large, is show in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+The case where this distance is large, and the number of disjoint neighbors is expected to be large, is shown in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
 There are several different quantities that are important.
 The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal$.
-Note that when $x = 0$ then these height are the same and we denote this by $h(y)$.
+Note that when $x = 0$ then these heights are the same and we denote this by $h(y)$.
 We also need to know the coordinates $h(p,p^\prime)$ and $x^\ast(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$.
@@
 %		\label{eq:def_y_intersection_close_boundaries}\\
-	h((p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
+	h(p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
 	x^\ast(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	

### 2019-02-21 clustering_infinite_model.tex
typos in section 3

@@
 and in particular the function $P(y)$.
-We therefore start with establishes the asymptotic behavior of the latter.
+We therefore start with establishing the asymptotic behavior of the latter.
 First we combine~\eqref{eq:degree_distribution_P_asymptotics} and~\eqref{eq:general_integral_rho_y_k} to obtain the following scaling result
@@
 \paragraph{Proof for \bm{$1/2 < \alpha < 3/4$}}
-By Lemme~\ref{lem:Paneq1} we get that
+By Lemma~\ref{lem:Paneq1} we get that
 \begin{align*}
@@
 \]
-It can now conclude that all terms in $\frac{2}{y} e^{\frac{y}{2}}\Delta_{\Pcal}(y)$ except the first one are $\smallO{1}$ as $y \to \infty$.
+We can now conclude that all terms in $\frac{2}{y} e^{\frac{y}{2}}\Delta_{\Pcal}(y)$ except the first one are $\smallO{1}$ as $y \to \infty$.
 By writing $z = e^{-\frac{y}{2}}$ we can rewrite this term as
@@
 
-Now we will proof all other cases with $\alpha > 3/4$. For simplicity we write
+Now we will deal with the case $\alpha > 3/4$ and $\alpha \not = 1$. For simplicity we write
 \[
@@
 \end{align*}
-The first term is constant while the last two terms go to zero as $y \to \infty$. We will therefore focus on the remain two terms. For the first we have, see~\eqref{eq:asymptotics_Delta_P_auxiliary} 
+The first term is constant while the last two terms go to zero as $y \to \infty$.
+We will therefore focus on the remaining two terms.
+For the first we have, see~\eqref{eq:asymptotics_Delta_P_auxiliary}
 \[

### 2019-02-21 introduction.tex
new simulation plots in section 1

@@
     \centering
-    \includegraphics[scale=0.6]{figures/SimulationClusteringCoefficientVariousNu.pdf}
+    \includegraphics[scale=0.6]{figures/cn10000nu0512rep100a05to5.pdf}
     \caption{Plot of $\gamma$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and 
-    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=1000$ and 20 repetitions.\label{fig:gamma}}
+    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10000$ and $100$ repetitions.\label{fig:gamma}}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.6]{figures/sim1024ck225n10000a0609nu2rep20.pdf}
-    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 26 on the horizontal axis, for $\nu=2$ and $\alpha=0.6$ 
-    (green) and $\alpha=0.9$ (blue); simulations (red dots) with $n=10000$ and 20 repetitions.\label{fig:gammak}}
+    \includegraphics[scale=0.6]{figures/ckn10000a08nu0512rep100k2to25.pdf}
+    \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 25 on the horizontal axis, for $\alpha=0.8$ and $\nu=\frac{1}{2}$ 
+    (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
 \end{figure}%

### 2019-02-21 clustering_infinite_model.tex
revised sections 6 and 7

@@
 
-\begin{align}\label{eq:delta_P}
+\begin{equation}\label{eq:delta_P}
  P(y_0) = (\alpha-1/2)^2 \int_0^\infty \int_0^\infty P(y_0, y_1, y_2) e^{-(\alpha-1/2)(y_1+y_2)} 
  \dd y_2 \dd y_1.
-\end{align}
+\end{equation}
 
@@
 
-Note that when writing $P(y_0)$ as in integral as in equation \eqref{eq:def_delta_p}, by symmetry in the integration 
+Note that when writing $P(y_0)$ as an integral, see equation~\eqref{eq:delta_P}, by symmetry in the integration 
 variables $y_1$ and $y_2$, we can assume that $y_1<y_2$ in which case either $y_0$ or $y_1$ is the smallest height. 
@@
 		{\dd}z_2{\dd}z_1 \right) \\
-	&=: 4 (\alpha-1/2)^2 ( I_{11}(y_0) - I_{12}(y_0)). \numberthis \label{eq:Delta_P_computation_I11}
+	&=: 4 (\alpha-1/2)^2 ( I_{11}(y_0) - I_{12}(y_0)). 
 \end{align*}
@@
 \begin{align*}
-	I_{11}(y_0) &= \int_0^{z_0} \int_0^{z_1} z_1^{2\alpha-2} z_2^{2\alpha-2} {\dd}z_2{\dd}z_1\\
-	&= \int_0^{z_0} z_1^{2\alpha-2} \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1} \right]_0^{z_1} {\dd}z_1\\
-	&= \frac{1}{2\alpha-1} \cdot \int_0^{z_0} z_1^{4\alpha-3} {\dd}z_1 \\
-	&= \frac{1}{2(2\alpha-1)^2} \cdot z_0^{4\alpha-2}.
+	I_{11}(y_0) &= \int_0^{z_0} \int_0^{z_1} z_1^{2\alpha-2} z_2^{2\alpha-2} {\dd}z_2{\dd}z_1
+		= \int_0^{z_0} z_1^{2\alpha-2} \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1} \right]_0^{z_1} {\dd}z_1\\
+	&= \frac{1}{2\alpha-1} \cdot \int_0^{z_0} z_1^{4\alpha-3} {\dd}z_1
+		= \frac{1}{2(2\alpha-1)^2} \cdot z_0^{4\alpha-2}. \numberthis \label{eq:Delta_P_computation_I11}
 \end{align*}
@@
 		z_2^{2\alpha-2} \dd z_2{\dd}z_1 \right) \\
-	&=: 4 (\alpha-1/2)^2 (I_{21}(y_0) - I_{22}(y_0)). \numberthis \label{eq:Delta_P_computation_I21}
+	&=: 4 (\alpha-1/2)^2 (I_{21}(y_0) - I_{22}(y_0)). 
 \end{align*}
@@
 	&= z_0 \int_{z_0}^1 \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1}\right]_{0}^{z_1} z_1^{2\alpha-3} {\dd}z_1 
-		= \frac{z_0}{2\alpha-1}  \int_{z_0}^1 z_1^{4\alpha-4} {\dd}z_1 \\
-	&= \frac{z_0 - z_0^{4\alpha-2}}{(4\alpha-3)(2\alpha-1)}.
+		= \frac{z_0}{2\alpha-1}  \int_{z_0}^1 z_1^{4\alpha-4} {\dd}z_1
+		= \frac{z_0 - z_0^{4\alpha-2}}{(4\alpha-3)(2\alpha-1)}. \numberthis \label{eq:Delta_P_computation_I21}
 \end{align*}
@@
 With the expressions for $J$ and $I^{(k)}$ and using $\Gamma^\ast(q,z) = \Gamma^+(q+1,z) + \Gamma^+(q,z)$ we now obtain, after 
-some algebra, the expression for $c_\Pcal$
+some algebra, the expression for $\gamma$
 \begin{align*}
@@
 
-Recall that
+Instead of extracting the scaling of $\gamma(k)$ from its explicit expression, it turns out to be more convenient to derive it directly. Recall that
 \[
@@
 \[
-	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
-\]
-and in particular the function $P(y)$.
-We therefore start with establishing the asymptotic behavior of the latter.
-First we combine~\eqref{eq:degree_distribution_P_asymptotics} and~\eqref{eq:general_integral_rho_y_k} to obtain the following scaling result
-\begin{equation}\label{eq:general_clustering_integral_scaling}
-	\frac{\int_0^\infty e^{-\beta y} \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	\sim \xi_{\alpha, \nu}^{2\beta} k^{-2\beta}.
-\end{equation}
+	\int_0^{\infty} P(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
+\]
+and in particular the function $P(y)$. We therefore start with establishing the asymptotic behavior of the latter.
 
@@
 \[
-	\Delta_{\Pcal}(y) \sim e^{-\frac{y}{2}(4\alpha - 2)} c_\alpha,
+	P(y) \sim e^{-\frac{y}{2}(4\alpha - 2)} c_\alpha \xi^{4\alpha - 2},
 \]
@@
 \[
-	\Delta_\Pcal(y) \sim \frac{y}{2} e^{-\frac{y}{2}},
+	P(y) \sim \frac{y}{2} e^{-\frac{y}{2}},
 \]
@@
 \[
-	\Delta_{\Pcal}(y) \sim e^{-\frac{y}{2}} \frac{4\alpha - 3}{4(\alpha - 1)}.
+	P(y) \sim e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}}.
 \]
@@
 Because for any $b < 1$, $B^-(1-z,a,b)$ converges to $B^-(a,b) < \infty$ as $z \to 0$, we get that as $y \to \infty$, the first line is asymptotically equivalent to
-\[,
-	\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
+\[
+	\frac{3 \alpha - 1}{2^{4 \alpha+1} \alpha (\alpha - 1)^2} 
 			+ \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha}
-			- \frac{B(2\alpha, 3-4\alpha)}{4(\alpha - 1)} = c_\alpha,
-\]
-as defined in Theorem~\eqref{thm:mainktoinfty}. The proof now follows since for $1/2 < \alpha < 3/4$, the remaining three terms go to zero as $y \to \infty$.
+			- \frac{B(2\alpha, 3-4\alpha)}{4(\alpha - 1)} = c_\alpha \xi^{-(4\alpha - 2)},
+\]
+with $c_\alpha$ as defined in Proposition~\eqref{prop:asymp}. The proof now follows since for $1/2 < \alpha < 3/4$, the remaining three terms go to zero as $y \to \infty$.
 
@@
 \]
-We can now conclude that all terms in $\frac{2}{y} e^{\frac{y}{2}}\Delta_{\Pcal}(y)$ except the first one are $\smallO{1}$ as $y \to \infty$.
-By writing $z = e^{-\frac{y}{2}}$ we can rewrite this term as
+We can now conclude that all terms in $\frac{2}{y} e^{\frac{y}{2}}P(y)$ except the first one are $\smallO{1}$ as $y \to \infty$. By writing $z = e^{-\frac{y}{2}}$ we can rewrite the first term as
 \[
@@
 \[
-	\frac{2}{y}e^{\frac{y}{2}}P(y) \sim \frac{y}{2} e^{-\frac{y}{2}},
+	P(y) \sim \frac{y}{2} e^{-\frac{y}{2}},
 \]
@@
 \end{align*}
-
-Now we will deal with the case $\alpha > 3/4$ and $\alpha \not = 1$. For simplicity we write
+The last two terms are $\smallO{1}$ as $y \to \infty$, while $2 = (\alpha - 1/2)/(\alpha - 3/4)$ for $\alpha = 1$.
+
+Now we will proof all other cases with $\alpha > 3/4$. For simplicity we write
 \[
@@
 \end{align*}
-The first term is constant while the last two terms go to zero as $y \to \infty$.
-We will therefore focus on the remaining two terms.
-For the first we have, see~\eqref{eq:asymptotics_Delta_P_auxiliary}
+The first term is constant while the last two terms go to zero as $y \to \infty$. We will therefore focus on the remain two terms. For the first we have, see~\eqref{eq:asymptotics_Delta_P_auxiliary} 
 \[
@@
 Therefore it follows, see Lemma~\ref{lem:asymptotics_incomplete_beta}, that
-\[
+\begin{align*}
 	\lim_{y \to \infty} - e^{-(4\alpha - 3)\frac{y}{2}}
 		\frac{B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
-	= \lim_{z \to 0} z^{4\alpha - 3} \frac{B^-(1 - z, 2 \alpha, 3 - 4 \alpha)}{4(\alpha - 1)}
-	= \frac{1}{4(\alpha - 1)(4\alpha - 3)}.
-\]
+	&= \lim_{z \to 0} z^{4\alpha - 3} \frac{B^-(1 - z, 2 \alpha, 3 - 4 \alpha)}{4(\alpha - 1)}\\
+	&= \frac{1}{4(\alpha - 1)(4\alpha - 3)}.
+\end{align*}
 We conclude that as $y \to \infty$
@@
 \] 
-We will prove that, as $k \to \infty$,
+We will show that, as $k \to \infty$,
 \begin{equation}\label{eq:asymptotics_average_clustering_concentration}
@@
 \end{equation}
-Note that this implies that for any bounded function $\varphi(y)$ satisfying $\lim_{y \to \infty} |\phi(y)| = 0$,
-\begin{equation}\label{eq:asymptotics_average_clustering_error_term}
-	\int_0^\infty \varphi(y) P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	= \smallO{1} \int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y.
-\end{equation}
-
-To establish~\eqref{eq:asymptotics_average_clustering_concentration} recall that $\mu(y) = \xi e^{\frac{y}{2}}$ and consider $\rho(y,k)$ as a function of $y$.
+
+To establish~\eqref{eq:asymptotics_average_clustering_concentration} recall that $\mu(y) = \xi e^{\frac{y}{2}}$ and consider $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$ as a function of $y$.
 Then, since $\mu^\prime(y) = \mu(y)/2$, we get that
 \[
-	\frac{\partial \rho}{\partial y} = \frac{1}{2}\left(k - \mu(y)\right)\rho(y,k),
+	\frac{\partial \rho(y,k)}{\partial y} = \frac{1}{2}\left(k - \mu(y)\right)\rho(y,k),
 \]
@@
 Moreover we see that the derivative is strictly positive when $\mu(y) < k$ and strictly negative when $\mu(k) > k$.
-Since $\mu(a(k)^- < k$ and $\mu(a(k)^+) > k$, we conclude that $\rho(y,k)$, as a function of $y$, is strictly increasing on $[0,a(k)^-]$ and strictly decreasing on $[a(k)^+,\infty)$.
+Since $\mu(a(k)^-) < k$ and $\mu(a(k)^+) > k$, we conclude that $\rho(y,k)$, as a function of $y$, is strictly increasing on $[0,a(k)^-]$ and strictly decreasing on $[a(k)^+,\infty)$.
 Hence, using that $P(y) \le 1$,
@@
 \end{align*}
-as $k \to \infty$. We will show that
+as $k \to \infty$. Next we show that
 \[
@@
 \begin{align*}
-	\rho(a_k^+,k) &= \frac{\mu(a_k^+)^{k}}{k!} e^{-\mu(a_k^+)} \\
+	\rho(a(k)^+,k) &= \frac{\mu(a(k)^+)^{k}}{k!} e^{-\mu(a(k)^+)} \\
 	&\sim (2\pi)^{-1/2} k^{-1/2} \left(\frac{\mu(a(k)^+}{k}\right)^{k} e^{-(\mu(a(k)^+ - k)}\\
 	&= (2\pi)^{-1/2} k^{-1/2} 
-		e^{-k\left(\frac{\mu(a_k^+)}{k} - 1 - \log\left(\frac{\mu(a_k^+)}{k}\right)\right)}.
+		e^{-k\left(\frac{\mu(a(k)^+)}{k} - 1 - \log\left(\frac{\mu(a(k)^+)}{k}\right)\right)}.
 \end{align*}
@@
 \[
-	\frac{\mu(a_k^+)}{k} = 1 + C \sqrt{\frac{\log(k)}{k}}
+	\frac{\mu(a(k)^+)}{k} = 1 + C \sqrt{\frac{\log(k)}{k}}
 \]
@@
 \begin{align*}
-	\rho(a_k^+,k) 
+	\rho(a(k)^+,k) 
 	&\sim \sqrt{2\pi} k^{-1/2} 
@@
 	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	= (1+\smallO{1}) \int_{a^-(k)}^{a^+(k)} \Delta_{\Pcal}(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
-\]
-as $k \to \infty$.
-
-We now proceed with the proof of Proposition~\ref{prop:asymptotics_P}, which is split over the different cases for $\alpha$.
+	= (1+\smallO{1}) \int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
+\]
+as $k \to \infty$. Note that this implies that if $P(y) = h(y)(1 + \smallO{1})$ as $y \to \infty$, then 
+\begin{equation}\label{eq:asymptotics_average_clustering_error_term}
+	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	\sim \int_0^\infty h(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
+\end{equation}
+as $y \to \infty$.
+
+We now proceed with the proof of Proposition~\ref{prop:asymp}, which is split over the different cases for $\alpha$.
+First we combine~\eqref{eq:degree_distribution_P_asymptotics} and~\eqref{eq:general_integral_rho_y_k} to obtain the following scaling result
+\begin{equation}\label{eq:general_clustering_integral_scaling}
+	\frac{\int_0^\infty e^{-\beta y} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	\sim \xi_{\alpha, \nu}^{2\beta} k^{-2\beta}.
+\end{equation}
 
 \paragraph{Proof when \bm{$1/2 < \alpha < 3/4$}}
-By Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} it is enough to show that
-\[
-	\frac{\int_0^{\infty} e^{-(4\alpha - 2)y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y}
-	{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
-	\sim \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2}.
-\]
-This follows immediately from~\eqref{eq:general_clustering_integral_scaling} with $\beta = 2\alpha - 1$.
+By Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term}  it follows that as $k \to \infty$,
+\begin{align*}
+	\gamma(k) \sim c_\alpha \xi^{-(4\alpha - 2)} \frac{\int_0^{\infty} e^{-(4\alpha - 2)y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} 
+	\sim c_\alpha k^{-4\alpha + 2}.
+\end{align*}
+where the last line is due to~\eqref{eq:general_clustering_integral_scaling} with $\beta = 2\alpha - 1$.
 
 \paragraph{Proof when \bm{$\alpha = 3/4$}}
-Similar to the previous case Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} imply that it is enough to show that
-\[
-	\frac{\int_0^{\infty} P(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+Similar to the previous case Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} imply that as $k \to \infty$
+\[
+	\gamma(k) = \frac{\int_0^{\infty} P(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
 	{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y}
-	\sim \xi_{\alpha,\nu} \log(k) k^{-1},
-\]
-This does not follow immediately from~\eqref{eq:general_clustering_integral_scaling} because of the additional logarithmic term. To establish the above result we first show that
+	\sim  \frac{\int_0^{\infty} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y}.
+\]
+However, the final step does not follow immediately from~\eqref{eq:general_clustering_integral_scaling} because of the additional logarithmic term. To prove the result we first show that
 \begin{equation}\label{eq:average_clustering_proof_34_main}
 	\int_{a(k)^-}^{a(k)^+} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	\sim \log(k) \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y.
+	\sim \int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y.
 \end{equation}
@@
 \[
-	\frac{a^\pm(k)}{2} = \log\left(\frac{k \pm \sqrt{k\log(k)}}{\xi_{\alpha, \nu}}\right) \sim \log(k)
+	\frac{a(k)^\pm}{2} = \log\left(\frac{k \pm \sqrt{k\log(k)}}{\xi_{\alpha, \nu}}\right) \sim \log(k)
 \]
@@
 	\frac{\int_0^\infty e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	\sim \xi_{\alpha, \nu}k^{-1}.
+	\sim \xi k^{-1}.
 \]
@@
 \]
-it follows from~\eqref{eq:average_clustering_proof_34_main} that
-\begin{align*}
-	\frac{\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y}
+it follows from~\eqref{eq:average_clustering_proof_34_main} that as $k \to \infty$,
+\begin{align*}
+	\gamma(k) &\sim \frac{\int_0^\infty \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+		{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y} \\
+	&\sim \log(k) \frac{\int_0^\infty e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
 	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	&\sim \log(k) \frac{\int_0^\infty e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}\\
-	&\sim \xi_{\alpha, \nu}\log(k)k^{-1},
-\end{align*}
-which finishes the proof for this case.
+	\sim \xi \log(k)k^{-1} = \frac{6\nu}{\pi} \log(k) k^{-1},
+\end{align*}
+when $\alpha = 3/4$.
 
@@
 
-Again, by Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} it is enough to show that
-\[
-	\frac{\int_0^{\infty} e^{-y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y}
-	{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} 
-	\sim \xi_{\alpha,\nu} k^{-1},
-\]
-which follows from~\eqref{eq:general_clustering_integral_scaling} with $\beta = 1/2$.
+Again, by Proposition~\ref{prop:asymptotics_P}, equation~\eqref{eq:asymptotics_average_clustering_error_term} and~\eqref{eq:general_clustering_integral_scaling} with $\beta = 1/2$, it follows that as $k \to \infty$,
+%by Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} it is enough to show that
+\[
+	\gamma(k) \sim \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} \, \frac{\int_0^{\infty} e^{-y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y} {\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} 
+	\sim \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} \, \xi k^{-1} = \frac{8\alpha \nu}{\pi(4\alpha - 3)}.
+\]
 

### 2019-02-21 concentration.tex
revised sections 6 and 7

--- 2019-02-05 concentration.tex
@@
 
-Recall the adjusted triangle count function \eqref{eq:def_tilde_triangle_indicator}
+We define adjusted triangle count function as
 \[
@@
 where the sum is over all distinct pairs $(p_1, p_2) \in \Pcal \setminus p$.
+
+The following results follows from the proof of Proposition~\ref{prop:convergence_average_clustering_P_n}.
+
+\begin{corollary}\label{cor:adjusted_triangle_counting_P_n}
+Let $p_0 = (0,y)$. Then, uniformly for all $y \in \Kcal_C(k_n)$, as $n \to \infty$
+\[
+	\Exp{\widetilde{T}_{\text{box}}(p_0)} = (1+\smallO{1})\Exp{T_{\infty}(p_0)},
+\]
+where
+\[
+	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus p_0}^{\ne} 
+		\ind{p_1 \in \BallPon{p_0}}\ind{p_2 \in \BallPon{p_0}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal}.
+\]
+
+In particular,
+\[
+	\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p_0)} f(x,y) \dd x \dd y
+	= (1+\smallO{1}) n \int_{\Rcal} \rho(y,k_n) P(y) \alpha e^{-\alpha y} \dd y. 
+\]
+\end{corollary}
+
+\begin{proof}
+First we note that equation~\eqref{eq:triangle_count_diff_scaling} implies that uniformly for $y \in \Kcal_C(k_n)$
+\[
+	\Exp{\left|\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)\right|} = \bigO{n^{-(4\alpha - 2)}k_n^2}
+	= \smallO{s(k_n) k_n^2},
+\]
+where the last part is due to Lemma~\ref{lem:scaling_s_alpha}.
+Next, since $\Exp{T_\infty(y)} = \Mu{\BallPo{y}}^2 P(y)/2$, we get
+\[
+	\Exp{\widetilde{T}_{\text{box}}(y)} = \Exp{T_{\infty}(y)} + \Exp{\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)} = \binom{k_n}{2} P(y) + \bigO{s(k_n)k_n^2},
+\]
+uniformly on $\Kcal_{C}(k_n)$. Therefore, we can apply a concentration of height argument to obtain
+\begin{align*}
+	&\hspace{-30pt}\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(y)} 
+		f(x,y) \dd x \dd y\\
+	&=\binom{k_n}{2}^{-1} n \int_{\Kcal_{C}(k_n)} \rho(y,k_n) \left(\binom{k_n}{2} P(y) + \bigO{s(k_n)k_n^2}\right)
+		\alpha e^{-\alpha y} \dd y.....
+\end{align*}
+\PvdH{Finish this proof!}
+\end{proof}
 

### 2019-02-21 concentration_argument.tex
revised sections 6 and 7

@@
 \[
-	a(k)^\pm = 2\log\left(\frac{1 \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
+	a(k)^\pm = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
 \]
-The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and $\mu(y) = \mu(B_\Pcal(y)) = \xi e^{y/2}$, and Poisson random variables are well concentrated around their mean, i.e.
-around those values of $y$ for which $\mu(y) \approx k$.
+The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and Poisson random variables are well concentrated around their mean, i.e.
+around heights $y$ for which $\mu(y) \approx k$.
+Since $\mu(y) = \mu(\BallPo{y}) = \xi e^{y/2}$, this implies that integration with respect to $\rho(y,k)$ is concentrated around $y \approx 2\log(k/\xi)$.
 
-In the remainder of this paper we will often encounter integrands involving, for some $\mu_n(y)$, the function $\Prob{\Po(\mu_n(y)) = k}$.
-In these case we want to be able to restrict our integration around those heights $y$ for which $\mu_n(y) \approx k_n$.
-We will refer to as \emph{concentration of heights arguments}.
+In the remainder of this paper we will often encounter integrands involving the function $\Prob{\Po(\mu_n(y)) = k}$, for some $\mu_n(y)$.
+In these case we want to be able to restrict our integration around those heights $y$ for which $y \approx 2\log(k_n/\xi)$.
+We will refer to such results as \emph{concentration of heights arguments}.
 In this section we establish such results.
 We start with a concentration of heights lemma for the infinite model $\Ginf$ (Lemma~\ref{lem:concentration_argument}) and explain in Remark~\ref{rmk:concentration_argument} how such a result will be used throughout the paper.
-To obtain similar results for the other two models we have to first analyze the expected number of nodes in a typical neighborhood in these models.
-We do in Sections~\ref{ssec:average_degree_HP_n} and~\ref{ssec:average_degree_P_n}.
-We conclude this section with a general result that allows us to extend the concentration lemma for the infinite model to the hyperbolic random graph and finite box model.
+We then establish similar results for the Poissonized KPKVB and finite box model based on a generalization of Lemma~\ref{lem:concentration_argument} obtained in Section~\ref{ssec:general_concentration_lemma}.
+To apply this lemma to $\GPo$ and $\Gbox$ we have to analyze the expected number of nodes in a typical neighborhood in these models, which is done in Sections~\ref{ssec:average_degree_P_n} and~\ref{ssec:average_degree_HP_n}.
 
@@
 After the new proves are added we can see where we specify this.}
-For any positive sequence $a_n \to \infty$ and $C > 0$ we define
-\begin{equation}\label{eq:def_K_C_set}
-	\Kcal_C(a_n) = \left\{y \in \R_+ : \frac{a_n - C \sqrt{a_n \log(a_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
-	\le \frac{a_n + C \sqrt{a_n \log(a_n)}}{\xi} \right\}.
-\end{equation}
-In addition we define
-\begin{equation}\label{eq:def_K_C_n_set}
-	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R_n] \cap \Kcal_{C}(a_n)),
-\end{equation}
-where $I_n := \frac{\pi}{2}e^{R_n/2}$. In addition, for a sequence $a_n \to \infty$, we shall often use the shorthand notation
-\begin{equation}\label{eq:def_kappa_n}
-	\kappa_n := \sqrt{a_n \log(a_n)}
-\end{equation}
 
@@
 
-The next lemma states that for a large class of functions $h(y)$, to compute the integral 
+The next lemma states that for a large class of functions $h(y)$ and $k_n \to \infty$, to compute the integral 
 \[
@@
 I am for changing the setup to what you are suggesting but I will have to spend some time first on checking how that will effect the definitions in later sections.}
-it is enough to consider integration over $\Kcal_C(k_n)$ instead of $\R_+$.
-More precisely, for any $\ell_n = (1 + \smallO{1})k_n$ it is enough to consider $\Kcal_C(\ell_n)$.
-The flexibility of using $(1+\smallO{1})k_n$ instead of $k_n$ will prove useful in later sections.
+it is enough to consider integration over a small interval on which $e^{y/2} \approx k_n$, instead of $\R_+$.
 
 \begin{lemma}\label{lem:concentration_argument}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\{k_n\}_{n \ge 1}$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$.
-In addition let $\beta < \alpha$ and $h : \R_+ \rightarrow  \R$ be a any function such that $h(y) = g(y)e^{\beta y}$ with $|g(y)|$ uniformly bounded on $\R_+$.
-Then, if we define for $C > 0$
+Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\{k_n\}_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n}$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$.
+In addition, define for any constant $C > 0$,
 \[
 	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, 
-	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right),
+	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
 \] 
-%\TM{ If $k$ is constant, then $\ell^- < 0$ and hence 
-%$a^-$ is undefined! Need to change the definitions. }\PvdH{You are right. I changed it by taking the minimum with $\xi$.}
-we have
+Then the following holds.
+\begin{enumerate}
+\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
 \begin{equation}\label{eq:error_bound_int_rho_not_K}
-	\int_{\R_+ \setminus \Kcal_{C}(\ell_n)} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
-	= \bigO{k_n^{-(1+C^2)/2}}
+	\int_{\R_+ \setminus (a_n^-, a_n^+)} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
+	= \bigO{k_n^{-(1+C^2)/2}},
 \end{equation}
-%\TM{ As before, this is not a proper dichotomy. (unless we assume more about the sequences $k_n$, i.e.~either constant or tending to infinity }
 as $n \to \infty$.
-
-In particular, if $h_n(y)$ is a function such that $h_n(y) = \bigO{n^{-1} k_n^{s} e^{\beta y}}\rho(y,k_n)$ for some $s \in \R$ and $\beta < \alpha$ as $n \to \infty$.
-Then for $C > 0$ large enough we have
-\[
-	\lim_{n \to \infty} \int_{\Rcal_n \setminus \Kcal_{C,n}(\ell_n)} h_n(y) 
-	f_{\alpha, \nu}(x,y) \dd x \dd y = 0,
-\]
-or equivalently,
-\[
-	\int_{\Rcal_n} \hspace{-5pt} h_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y
-	= (1+\smallO{1}) \int_{\Kcal_{C,n}(\ell_n)} \hspace{-5pt} h_n(y) f_{\alpha, \nu}(x,y) \dd x \dd y.
-\]
+\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$. Then,
+\begin{equation}\label{eq:concentration_h_rho}
+	\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y^\prime} \dd y^\prime \sim  
+		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
+\end{equation}
+as $n \to \infty$.
+\end{enumerate}
 \end{lemma}
 
-\begin{proof}
+\begin{proof}\hfill
 
-Note that in this case we write
-\[
-	\kappa_n = \sqrt{\ell_n \log(\ell_n)}.
-\]
-and recall (see proof of Proposition~\ref{prop:asymp}) that $\rho(y,k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$.
+\paragraph{Proof of the first statement.}
+Recall (see proof of Proposition~\ref{prop:asymp}) that $\rho(y,k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$.
 Therefore, by our assumption on $h(y)$,
 \begin{align*}
-	&\hspace{-20pt}\int_{\R_+ \setminus [a_n^-, a_n^+]} h(y) \rho(y,k_n) 
+	&\hspace{-20pt}\int_{\R_+ \setminus (a_n^-, a_n^+)} h(y) \rho(y,k_n) 
 		\alpha e^{-\alpha y} \dd y\\
@@
 \begin{equation}\label{eq:concentration_lemma_integral_bound}
-	\int_{\R_+ \setminus [a_n^-, a_n^+]} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	\int_{\R_+ \setminus (a_n^-, a_n^+)} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
 	= \bigO{1} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right) 
@@
 \end{equation} 
+Plugging~\eqref{eq:concentration_lemma_bound_an-} and~\eqref{eq:concentration_lemma_bound_an+}  into~\eqref{eq:concentration_lemma_integral_bound} yields the result.
 
-Plugging~\eqref{eq:concentration_lemma_bound_an-} and~\eqref{eq:concentration_lemma_bound_an+}  into~\eqref{eq:concentration_lemma_integral_bound} yields the result.
-The second statement immediately follows from the first by choosing a large enough $C$ and observing that
+\paragraph{Proof of the second statement.} By the mean value theorem for definite integrals, there exists a $c_n \in (a_n^-, a_n^+)$ such that
 \[
-	\int_{\Rcal_n \setminus \Kcal_{C,n}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y
-	\le n \int_{\R_+ \setminus [a_n^-, a_n^+]} h_n(y) \alpha e^{-\alpha y} \dd y.
+	\int_{a_n^-}^{a_n^+} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	= h(c_n) \int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
 \]
+Since $\int_0^\infty \rho(y,k_n) \alpha e^{-\alpha y} \dd y = \bigT{k_n^{-(2\alpha + 1)}}$, taking any $C > \sqrt{4\alpha + 1}$, \eqref{eq:error_bound_int_rho_not_K} implies that
+\[
+	\int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	= (1 + \smallO{1})\int_0^\infty \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+\]
+from which we conclude that (see~\eqref{eq:degree_distribution_P_asymptotics}),
+\[
+	\int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y = (1 + \smallO{1}) 2\alpha \xi^{2\alpha} k_n^{-(2\alpha + 1)},
+\]
+as $n \to \infty$. Finally, since $c_n \in (a_n^-, a_n^+)$ it follows that
+\[
+	\left|\frac{c_n}{2\log(k_n/\xi)} - 1\right| \le 2 C \sqrt{\frac{\log(k_n)}{k_n}}, 
+\]
+so that $c_n \sim k_n$. Therefore, by assumption on $h$ 
+\[
+	\int_{a_n^-}^{a_n^+} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	\sim h(c_n) 2\alpha \xi^{2\alpha} k_n^{-(2\alpha + 1)} 
+	\sim 2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1),}
+\]
+as $n \to \infty$.
+\end{proof}
+
+Note that we can tune the error in~\eqref{eq:error_bound_int_rho_not_K} by selecting an appropriately large $C > 0$, i.e.
+by restrict the function $h(y)$ inside the integral to an appropriate interval around $2\log(k_n/\xi)$.
+This makes Lemma~\ref{lem:concentration_argument} very powerful.
+Below we list several important corollaries.
+
+\begin{corollary}\label{cor:concentration_of_heights_asymptotics}
+Let $h : \R_+ \to \R$ be any continuous function such that for some $\beta < \alpha$, $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ and $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$.
+Then for any other continuous function $g: \R_+ \to \R$, such that $g(y) \sim h(y)$ as $y \to \infty$
+\begin{equation}\label{eq:concentration_h_sim_rho}
+	\int_0^\infty g(y) \rho(y,k_n) \alpha e^{-\alpha y^\prime} \dd y^\prime \sim  
+		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
+\end{equation}
+as $n \to \infty$.
+\end{corollary}
+
+\begin{proof}
+By assumption, $g$ satisfies the conditions of for the second statement of Lemma~\ref{lem:concentration_argument}. Since in addition $g(2\log(k_n/\xi)) \sim h(2\log(k_n/\xi))$, the result follows.
+\end{proof}
+
+For any positive sequence $a_n \to \infty$ and $C > 0$ we define
+\begin{equation}\label{eq:def_K_C_set}
+	\Kcal_C(a_n) = \left\{y \in \R_+ : \frac{a_n - C \sqrt{a_n \log(a_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
+	\le \frac{a_n + C \sqrt{a_n \log(a_n)}}{\xi} \right\}.
+\end{equation}
+In addition we define
+\begin{equation}\label{eq:def_K_C_n_set}
+	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R_n] \cap \Kcal_{C}(a_n)),
+\end{equation}
+where $I_n := \frac{\pi}{2}e^{R_n/2}$.
+Recall that $\Rcal = (-I_n, I_n] \times [0,R]$.
+The following corollary allows us to bound integrals of function by considering there maximum of $\Kcal_{C}(k_n)$.
+
+\begin{corollary}\label{cor:concentration_heights_bounds_n}
+Let $h_n : \R_+ \to \R_+$ be a sequence of continuous functions which such that for some $s \in \R$ and $\beta < \alpha$, as $n \to \infty$, $h_n(y) = \bigO{k_n^{s} e^{\beta y}}$ and $h_n(y) = \Omega(1)$, uniformly on $0 \le y \le R$.
+Then, as $n \to \infty$,
+\[
+	\int_{\Rcal} h_n(y) \rho(y,k_n) f(x,y) \dd x \dd y 
+	= (1 + \smallO{1}) \, n \int_{\Kcal_{C}(k_n)} h_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+\]
+In particular,
+\[
+	\int_{\Rcal} h_n(y) \rho(y,k_n) f(x,y) \dd x \dd y = \bigO{1} n \, k_n^{-(2\alpha + 1)} \max_{y \in \Kcal_{C}(k_n)} h_n(y),
+\]
+as $n \to \infty$.
+\end{corollary}
+
+\begin{proof}
+The second result follows immediately from the first. For the first result we note that by the first statement of Lemma~\ref{lem:concentration_argument}
+\begin{align*}
+	\int_{[0,R] \setminus (a_n^-, a_n^+)} h_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	&\le \bigO{k_n^s} \int_{\R_+ \setminus (a_n^-, a_n^+)} e^{\beta y } \rho(y,k_n) \alpha e^{-\alpha y} \dd y\\
+	&= \bigO{k_n^{s - (1+C^2)/2}}.
+\end{align*}
+By assumption on $h_n(y)$,
+\[
+	\int_{\Kcal_{C}(k_n)} h_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y 
+	= \bigO{k_n^{s+2\beta}} \int_{\Kcal_{C}(k_n)} \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	= \bigO{k_n^{s+2\beta - (2\alpha + 1)}},
+\]
+and
+\[
+	\int_{\Kcal_{C}(k_n)} h_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y 
+	= \Omega(1) \int_{\Kcal_{C}(k_n)} \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	= \Omega(k_n^{-(2\alpha + 1)}).
+\]
+Hence, by taking $C > 0$ such that $(1+C^2)/2 > \max\{2\alpha + 1 + s, 2\alpha +1 - \beta\}$ we get that
+\[
+	\int_{[0,R] \setminus (a_n^-, a_n^+)} h_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
+	= \smallO{1} \int_{\Kcal_{C}(k_n)} h_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+\]
+The result then follows since
+\[
+	\int_{\Rcal} h_n(y) \rho(y,k_n) f(x,y) \dd x \dd y
+	= n \int_{0}^{R} h_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+\]
+\end{proof}
+
+\begin{corollary}\label{cor:concentration_heights_asymptotics_n}
+Let $h : \R_+ \to \R$ be a continuous function which  satisfies the conditions of Lemma~\ref{lem:concentration_argument} and let $h_n$ be a sequence of functions such that, as $n \to \infty$, $h_n(y) = \Omega(1)$ and $h_n(y) = \bigO{k_n^{s}} h(y)\rho(y,k_n)$, uniformly on $0 \le y \le R$.
+Then,
+\begin{equation}
+	\int_{\Rcal} h_n(y) \rho(y,k_n) f(x,y) \dd x \dd y 
+	\sim 2\alpha \xi^{2\alpha} \, n \, h_n(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
+\end{equation}
+as $n \to \infty$.
+\end{corollary}
+
+\begin{proof}
+The result immediately follows by first applying Corollary~\ref{cor:concentration_heights_bounds_n} and then using the second statement from Lemma~\ref{lem:concentration_argument}.
 \end{proof}
@@
 %\TM{ again, this is a loaded term. I would in the very least change to ``concentration of height'' everywhere }
-Lemma~\ref{lem:concentration_argument} will prove very useful in the remainder of this paper since we often have to deal with integrands of the form $g_n(y) f_{\alpha,\nu}(x,y)$ where $g_n(y) = \bigO{n^{-1} k_n^{s}}e^{\beta y}\rho(y,k_n)$ for some $s \in \R$ and $\beta < \alpha$.
-In this case the lemma tells us that for a suitable $C > 0$ we only need to integrate over $\Kcal_C(k_n)$.
-In order words, we may always assume for $g_n(y)$ (for a penalty of $\smallO{1}$) that $k_n - C \kappa_n \le \xi e^{y/2} \le k_n + C \kappa_n$.
-We will refer to this as a \emph{concentration of heights argument}, e.g.
-\emph{by a concentration of heights argument}
-\[
-	\int_{\Rcal_n} g_n(y) \rho(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y 
-	= (1+\smallO{1}) n \int_{\Kcal_C(k_n)} g_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
-\]
-\PvdH{ @All:It might be a good idea to add one more example of how the concentration argument is used in the paper. I someone finds a good example we use later on, please add it here.}
+All the above corollaries use the same reasoning, namely that when the integrand contains $h_n(y) \rho(y,k_n)$, for some "nice" functions $h_n(y)$, then the main contribution is determined by the integration over $\Kcal_{C}(k_n)$.
+This implies, for instance, that we only need to carefully analyze the functions $h_n(y)$ on $\Kcal_{C}(y)$, while for a certain class of functions we can even simply replace it with $h_n(2\log(k_n/\xi))$.
+We will refer collectively to any of these arguments as a \emph{concentration of heights argument}.
+For example, suppose we know that $h_n(y) = \Omega(1)$ and $h_n(y) = \bigO{k_n^4} e^{\alpha/2 y}$, while $h_n(y) = (1 + \smallO{1}) k_n^2 e^{\alpha/2 y}$, uniformly on $\Kcal_{C}(k_n)$.
+Then by a concentration of heights argument (in this case Corollary~\ref{cor:concentration_heights_asymptotics_n})
+\begin{align*}
+	\int_{\Rcal} h_n(y) \rho(y,k_n) f(x,y) \dd x \dd y 
+	&= (1 + \smallO{1}) 2 \alpha \xi^{2\alpha} \, n \, k_n^2 (k_n/\xi)^{\alpha/2} k_n^{-(2\alpha + 1)} \\
+	&= (1 + \smallO{1}) 2\alpha \xi^{5\alpha/2} \, n \, k_n^{1 + 5\alpha/2}.
+\end{align*}
 \end{remark}
 
-We will later establish similar results for the cases where we consider the hyperbolic and finite box model.
-Here we have to consider Poisson distributions with mean $\mu(\BallHyp{y})$ and $\mu(\BallPon{y})$, respectively.
+\begin{remark}[Proof of Proposition~\ref{prop:asymp} revisited]
+Note that due to Proposition~\ref{prop:asymptotics_P}, the function $P(y)$ from Section~\ref{sec:asymptotics_average_clustering_ast_P} satisfies all the necessary conditions in Corollary~\ref{cor:concentration_of_heights_asymptotics}.
+Hence, Proposition~\ref{prop:asymp} directly follows from Proposition~\ref{prop:asymptotics_P} and a concentration of heights argument (second statement of Lemma~\ref{lem:concentration_argument}).
+\end{remark}
+
+Although powerful, the current versions of the concentration of heights arguments are only valid for the function $\rho(y,k_n) := \Prob{\Po\left(\Mu{\BallPo{y}}\right) = k_n}$, which uses the neighborhoods in the infinite model $\Ginf$.
+Since we will also be working in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, we would like to use concentration of heights arguments when the integrand contains either the function $\rho_{\Po}(y,k_n) := \Prob{\Po\left(\Mu{\BallHyp{y}}\right) = k_n}$ or $\rho_{\text{box}}(y,k_n) := \Prob{\Po\left(\Mu{\BallPon{y}}\right) = k_n}$.
+The next proposition establishes this result and we will spend the rest of this section on its proof.
+
+\begin{proposition}\label{prop:concentration_argument_all}
+The conclusions from Lemmas~\ref{lem:concentration_argument} and Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n} and~\ref{cor:concentration_heights_asymptotics_n} still hold if we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
+\end{proposition}
+
+\subsection{A more general concentration of heights argument}\label{ssec:general_concentration_lemma}
+
+Note that since all three corollaries follow from Lemma~\ref{lem:concentration_argument}, Proposition~\ref{prop:concentration_argument_all} follows if we can prove that the conclusions from this lemma holds when we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
 For this the following, slightly more general version of Lemma~\ref{lem:concentration_argument} will be important.
@@
 \begin{lemma}\label{lem:concentration_argument_rho_approximation}
-Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and let $\Kcal_{C,n}(\ell_n)$ be defined as in~\eqref{eq:def_K_C_n_set}.
+Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n \to \infty$ be such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
+\[
+	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
+\] 
 In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ satisfies, 
@@
 \]
-where $\phi_n(y)$ is a continuous differentiable function such that for some $0 < \varepsilon < 1$
-\[
-	\sup_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| = 0.
-\]
-Then the following holds for some $C > 0$ large enough:
+where $\phi_n(y)$ is a continuous differentiable function such that
+\begin{enumerate}[\upshape i)]
+\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| = 0$,
+\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
+\end{enumerate}
+Then the following holds.
 \begin{enumerate}
-\item For any sequence of continuous functions $h_n(y) : \R_+ \to \R$ such that, uniformly on $(0,R_n]$, $h_n(y) = \bigO{k_n^s e^{\beta y} \hat{\rho}_n(y,k_n)}$, as $n \to \infty$, 
-%\TM{ Why not adjust $h$ so that we incorporate $\hat\rho$ in line below.
-Then both items look more similar.
-}\PvdH{The reason for the bound on $h_n(y)$ in the first statement is that we want to use this for cases where $h_n(y) \le k_n^s \hat{\rho}_n(y,k_n)$ (see for instance the proof of Proposition~\ref{prop:convergence_average_clustering_P_n}.}
-for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
-\[
-	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
-	= (1 + o(1)) \int_{\Kcal_{C,n}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
-\]
-\item For any continuous bounded function $h(y)$,
-\[
-	\int_{\Kcal_{C,n}(\ell_n)} h(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y
-	= (1+\smallO{1}) n \int_{0}^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
-\]
+\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
+\begin{equation}\label{eq:error_bound_int_rho_approx_not_K}
+	\int_{\R_+ \setminus (a_n^-, a_n^+)} \hat{\rho}_n(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
+	= \bigO{k_n^{-(1+C^2)/2}},
+\end{equation}
+as $n \to \infty$.
+\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$. Then,
+\begin{equation}\label{eq:concentration_h_rho_approx}
+	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y^\prime} \dd y^\prime \sim  
+		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
+\end{equation}
 as $n \to \infty$.
@@
 
-\begin{proof}
-Similarly to the proof of Lemma~\ref{lem:concentration_argument} we define 
-\[
-	\lambda_n^\pm = (\ell_n \pm C \kappa_n) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
-\] 
-%\TM{ Same problem as in L3.1. $\lambda^-$ can be negative, in which case $a^-$ is undefined.}
-
-In addition we fix $\varepsilon^\ast > 0$ such that $\varepsilon < \min\{1- \frac{s}{2\alpha(2\alpha + 1)},\varepsilon, 1\}$ and. Then since $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s}$ we have
-\begin{align*}
-	k_n^s \int_{(1-\varepsilon^\ast)R_n}^{R_n} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
-	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\ast)R_n,k_n) k_n^s e^{-\alpha(1-\varepsilon^\ast)R_n} \\
-	&= \bigO{\hat{\rho}_n((1-\varepsilon^\ast)R_n,k_n) k_n^s n^{-2\alpha(1 - \varepsilon^\ast)}} \\
-	&= \smallO{ \hat{\rho}_n((1-\varepsilon^\ast)R_n,k_n) n^{\frac{s}{2\alpha + 1} - 2\alpha(1-\varepsilon^\ast)}} = \smallO{1},
-\end{align*}
-where the last step follows by our choice of $\varepsilon^\ast$. Hence it is enough to prove both statement on $\Rcal_n((1-\varepsilon)R_n, R_n)$ instead of $\Rcal_n$.
-\PvdH{@All: This is where we use that $s < 2\alpha(2\alpha + 1)$. I think this can be removed by using a more careful bound but I am not sure this is needed.}
+\begin{proof} \hfill
 
 \paragraph{Proof of statement 1.}
-Since we already showed that
+Let $0 < \varepsilon < 1$ be such that condition ii) holds and take $\varepsilon^\prime = \min\{\varepsilon,1/3\} < 1/2$.
+We first show that the integration over $(1-\varepsilon^\prime)R \le y \le R$ is negligible.
+
+Since $h(y) = \bigO{e^{\beta y}}$ we have
+\begin{align*}
+	\int_{(1-\varepsilon^\prime)R_n}^{R_n} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\prime)R,k_n) e^{-(\alpha-\beta)(1-\varepsilon^\prime)R} \\
+	&= \bigO{\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) n^{-2(\beta-\alpha)(1-\varepsilon^\prime)}}.
+\end{align*}
+By assumption on $\hat{\mu}_n(y)$ we have that $\hat{\mu}_n((1-\varepsilon^\prime)R) = \bigT{\mu((1-\varepsilon^\prime)R} = \bigT{n^{2(1-\varepsilon^\prime)}}$.
+Since $k_n = \smallO{n}$, by our choice of $\varepsilon^\prime$, $\hat{\mu}_n((1-\varepsilon^\prime)R)/k_n = \omega\left(n^{1 - 2\varepsilon^\prime}\right) \to \infty$ as $n \to \infty$.
+We can now use Stirling's approximation to bound $\hat{\rho}_n((1-\varepsilon^\prime)R,k_n)$ as
+\begin{align*}
+	\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) &= \Prob{\Po(\hat{\mu}_n((1-\varepsilon^\prime)R)) = k_n} \\
+	&= \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)^{k_n}}{k_n!} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)}\\
+	&= \bigO{1} k_n^{-1/2} \left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)^{k_n} e^{k_n - \hat{\mu}_n((1-\varepsilon^\prime)R)}\\
+	&= \bigO{1} k_n^{-1/2} e^{k_n\left(1 - \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)+ \log\left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)}\\
+	&\le \bigO{1} k_n^{-1/2} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)/2},
+\end{align*}
+where the last line follows since $1 - x + \log(x) \le -x/2$ for large enough $x$. We conclude that
 \[
-	\lim_{n \to \infty} k_n^s \int_{(1-\varepsilon)R_n}^{R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0,
+	\int_{(1-\varepsilon^\prime)R_n}^{R_n} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\varepsilon^\prime)} e^{-n^{2(1-\varepsilon^\prime)}}}
+	= \bigO{k_n^{(1+C^2)/2}}.
 \]
-by our assumption on $h_n(y)$, it is enough to show that for sufficiently large $C > 0$,
+
+We are left to show that for sufficiently large $C > 0$,
 \begin{equation}\label{eq:concentration_argument_an_-}
-	\lim_{n \to \infty} k_n^s \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0,
+	 \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}},
 \end{equation}
@@
 \begin{equation}\label{eq:concentration_argument_an_+}
-	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = 0.
+	\int_{a_n^+}^{(1-\varepsilon^\prime)R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}}.
 \end{equation}
@@
 
-For simplicity we write $\mu(y) := \mu_{\alpha,\nu}\left(\BallPo{y}\right)$.. Now fix some $0 < \delta < 1$ and let $n$ be large enough such that 
-\begin{enumerate}
-\item $\sup_{0 < y \le (1-\varepsilon)R_n} |\phi_n(y)| < \delta$,
-\item $(\ell_n + C \kappa_n)(1 - \delta) > k_n$ and
-\item $(\ell_n - C \kappa_n)(1 + \delta) < k_n$
-\end{enumerate}
+For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right)$. Now fix some $0 < \delta < 1$ and let $n$ be large enough such that 
+\[
+\sup_{0 < y \le (1-\varepsilon^\prime)R_n} |\phi_n(y)| < \delta, \quad
+\lambda_n^+(1 - \delta) > k_n \quad \text{and} \quad
+\lambda_n^-(1 + \delta) < k_n.
+\]
 
@@
 \]
-for all $a_n^+ \le y \le (1-\varepsilon)R_n$. By making the change of variables $z = \mu^{-1}(\mu(y)(1-\delta)) = y + 2 \log(1-\delta)$ we then get
+for all $a_n^+ \le y \le (1-\varepsilon^\prime)R_n$. By making the change of variables $z = \mu^{-1}(\mu(y)(1-\delta)) = y + 2 \log(1-\delta)$ we then get
 \begin{align*}
-	k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
-	&\le k_n^s \int_{a_n^+}^{(1-\varepsilon)R_n} \Prob{\Po(\mu(y)(1-\delta)) = k_n} 
+	\int_{a_n^+}^{(1-\varepsilon^\prime)R_n} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
+	&\le \int_{a_n^+}^{(1-\varepsilon^\prime)R_n} \Prob{\Po(\mu(y)(1-\delta)) = k_n} 
 		e^{(\beta-\alpha) y} \dd y\\
-	&= k_n^s (1-\delta)^{\beta - \alpha} \int_{a_n^+ + 2\log(1-\delta)}^{(1-\varepsilon)R_n + 2\log(1-\delta)} 
+	&= (1-\delta)^{\beta - \alpha} \int_{a_n^+ + 2\log(1-\delta)}^{(1-\varepsilon^\prime)R_n + 2\log(1-\delta)} 
 		\Prob{\Po(\mu(z)) = k_n} e^{(\beta - \alpha)z} \dd z\\
-	&\le k_n^s (1-\delta)^{\beta - \alpha} \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z.
+	&= \bigO{1} \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z\\
+	&= \bigO{k_n^{-(1+C^2)/2}},
 \end{align*}
-Since Lemma~\ref{lem:concentration_argument} implies that for large enough $C$,
-\[
-	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z = 0,
-\]
-we have proven~\eqref{eq:concentration_argument_an_+}.
+where the last line is due to Lemma~\ref{lem:concentration_argument}. This proves~\eqref{eq:concentration_argument_an_+}.
+
+%implies that for large enough $C$,
+%\[
+%	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z = 0,
+%\]
+%we have proven~\eqref{eq:concentration_argument_an_+}.
 
@@
 \begin{align*}
-	k_n^s \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
-	&= k_n^s \int_0^{a_n^-}\Prob{\Po(\mu(y)(1-\delta)) = k_n} 
+	\int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
+	&= \int_0^{a_n^-}\Prob{\Po(\mu(y)(1-\delta)) = k_n} 
 		e^{(\beta-\alpha) y} \dd y\\
-	&\le k_n^s (1+\delta)^{\beta - \alpha} \int_0^{a_n^- + 2\log(1+\delta)} 
+	&\le (1+\delta)^{\beta - \alpha} \int_0^{a_n^- + 2\log(1+\delta)} 
 		\rho(z,k_n) e^{(\beta - \alpha)z} \dd z,
 \end{align*}
-and~\eqref{eq:concentration_argument_an_-} follows by another application of Lemma~\ref{lem:concentration_argument}.
+and hence~\eqref{eq:concentration_argument_an_-} follows by another application of Lemma~\ref{lem:concentration_argument}.
 
@@
 
-The proof of the second statement follows the same line of reasoning as above. First note that by Lemma~\ref{lem:concentration_argument} and the first statement, it is enough to show that
+The proof of the second statement follows the same line of reasoning as above. First, by the mean value theorem for definite integrals 
 \[
 	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) h(y) e^{-\alpha y} \dd y
-	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z.
+	= h(c_n) \int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z,
+\]
+for some $c_n \in (a_n^-, a_n^+)$. Since, $c_n \sim 2 \log(k_n/\xi)$, by assumption on $h$, $h(c_n)\sim h(2\log(k_n/\xi))$. Therefore it is enough to show that
+\[
+	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z.
 \] 
@@
 \[
-	\int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z
-	= \left(1 + o(1)\right)\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) h(y) e^{-\alpha y} \dd y.
+	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z
+	= \left(1 + o(1)\right)\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
 \]
@@
 \begin{align*}
-	&\hspace{-30pt}\int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z \\
-	&= \int_{a_n^-}^{a_n^+} \Prob{\Po(\mu(z)) = k_n} h(z) e^{-\alpha z} \dd z\\
-	&= \int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(\mu^{-1}(\hat{\mu}_n(y))) e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
+	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z 
+	&= \int_{a_n^-}^{a_n^+} \Prob{\Po(\mu(z)) = k_n} e^{-\alpha z} \dd z\\
+	&= \int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
 		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
 \end{align*}
-where the fraction is the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.
+where the fraction in the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.
 
-Now recall that $\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y))$, with $\phi_n(y)$ continuous and differentiable and satisfying
-$\max_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| \to 0$.
-It follows that $\max_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n^\prime(y)| \to 0$ which then implies that $\hat{\mu}_n^\prime(y) = (1 + \smallO{1})\mu^\prime(y)$ as $n \to \infty$, uniformly on $(0,(1-\varepsilon)R_n)$.
-In particular this holds uniformly on $[a_n^-, a_n^+]$.
+Now recall that $\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y))$, with $\phi_n(y)$ satisfying conditions i) and ii).
+It then follows $\hat{\mu}_n^\prime(y) = (1 + \smallO{1})\mu^\prime(y)$ as $n \to \infty$, uniformly on $(a_n^-, a_n^+)$.
 Next we note that $\mu^\prime(y) = \mu(y)/2$ from which it follows that uniformly on $[a_n^-, a_n^+]$,
@@
 \]
-In addition, uniformly on $[0,(1-\varepsilon)R_n]$,
-\[
-	\mu^{-1}(\hat{\mu}_n(y)) = 2 \log(\hat{\mu}(y)/\xi) = 2 \log(\mu(y)/\xi) + 2 \log(1 + \smallO{1}) = y + \smallO{1}.
-\]
-Therefore, by assumption on $h(y)$,
+Therefore,
 \begin{align*}
-	&\hspace{-30pt}\int_{a_n^-}^{a_n^+} \rho(z,k_n) h(z) e^{-\alpha z} \dd z \\
-	&= (1 + \smallO{1})e^{-\alpha b_n}\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(y + \smallO{1})  
-		e^{-\alpha y} \dd y\\
-	&= (1 + \smallO{1}) \int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(y)  
-		e^{-\alpha y} \dd y \\
-	&= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} h(y)  
-			e^{-\alpha y} \dd y,
+	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z
+	&= (1 + \smallO{1})\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha y} \dd y\\
+	&= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y\\
+	&= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
 \end{align*}
@@
 
-\subsection{Expected number of points in balls in the hyperbolic random graph}\label{ssec:average_degree_HP_n}
+With this lemma, the proof of Proposition~\ref{prop:concentration_argument_all} follows if we can show that both $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$ are of the form $\rho(y,k_n)(1 + \phi_n(y))$, where $\phi_n(y)$ satisfies the conditions i) and ii).
+We deal with each of these cases separately.
 
-\TM{  the term ``average degree" does not fit very well with what goes on in this section.
-We are considering the expected number of points in a ball, but not yet computing the average degree of the graph.
-}\PvdH{I agree and have changed the header.}
-Recall that under the coupling between the hyperbolic random graph and the finite box model, for two points $p, p^\prime$ with $y + y^\prime < R_n$, $p^\prime \in \BallHyp{p}$ exactly when $|x-x^\prime|_{\pi e^{R_n/2}} \le \Phi(r,r^\prime)$.
-In this setting, the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
-\[
-	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Phi(r, r^\prime) 
-		\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
-\]
-for some constant $K$. %\TM{ Say what $K$ is and what the restrictions on $r, r'$ are. } 
-This result enables us to determine the measure of a ball around a given point $p=(0,y)$ which will be fairly useful in our subsequent analysis.
-Recall that the hyperbolic ball $\BallHyp{p}$ is a subset of $\Rcal_n$ and not of the hyperbolic disc $\Dcal_{R_n}$, i.e.
-the balls $\BallHyp{p}$ "live" in the finite box and not the hyperbolic disc.
+\subsection{Concentration of heights for the finite box model}\label{ssec:average_degree_P_n}
 
-\begin{lemma}\label{lem:average_degree_hyperbolic}
-Let $\eps \in (0, 1)$. Then for all $0 \le y \le (1 - \eps)R_n$
-\[
-	 1 - \phi_{\H,n}^{(1)}(y) - \phi_{\H,n}^{(2)}(y) \le \frac{\Mu{\BallHyp{0,y}}}{\Mu{\BallPo{0,y}}} 
-	 \le 1 - \phi_{\H,n}^{(1)}(y) + \phi_{\H,n}^{(2)}(y),
-\]
-where
-\[
-	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 1 - 4\pi}{4\pi} e^{-(\alpha - \frac{1}{2})(R_n - y)} 
-		+ \left(\alpha - \frac{1}{2}\right)\pi e^{-(\alpha - \frac{1}{2})R_n - y/2},
-\]
-and
-\[
-	\phi_{\H,n}^{(2)}(y) = 
-	+ \begin{cases}
-			\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(R_n - y)}\right)
-			&\mbox{if } 1/2 < \alpha < 3/2,\\
-			\frac{(2\alpha -1)K}{2} (R_n - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
-			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
-			&\mbox{if } \alpha > 3/2,
-		\end{cases}
-\]
-with $K$ being the constant coming from the approximation of $\Phi$ in Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
-%\TM{ We want to say in the lemma where $K$ comes from. (not everyone reads surrounding text, or reads linearly, in a paper as long as this one.) }
-\end{lemma}
-
-\begin{proof}
-We perform the computation of $\Mu{\BallHyp{0,y}}$ by splitting the integration with respect to the height $y^\prime$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$, %\TM{ You have not said what $y^\prime$ is!
-}
-where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}. Recall that $\Mu{\BallPo{0,y}} = \xi e^{y/2}$ where $\xi = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.
-
-Note that $\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])= \Rcal_n([R_n-y,R_n])$. 
-Thus, 
-\begin{align*}
-	&\hspace{-30pt}\Mu{\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])} \\
-	&= \int_{R_n - y}^{R_n} \int_{I_n} f_{\alpha,\nu}(x^\prime, y^\prime) \dd x^\prime \dd y^\prime
-		= \nu \alpha e^{R_n/2}\left(e^{-\alpha(R_n - y)} - e^{-\alpha R_n}\right)\\
-	&= \Mu{\BallPo{0,y}} \frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
-		- e^{-(\alpha - \frac{1}{2})R_n - y/2}\right) \numberthis \label{eq:mu_hyperbolic_ball_part_1}
-\end{align*}
-
-Next we will establish upper and lower bounds on $\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]}$. Using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} we have 
-\begin{align*}
-	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} 
-	&\le \frac{2\nu \alpha}{\pi} \int_{0}^{R_n - y} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R_n}\right)
-		e^{-\alpha y^\prime} \dd y^\prime\\
-	&= \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right) \\
-	&\hspace{10pt}+ \frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
-\end{align*}
-The last integral depends on the value of $\alpha$,
-\[
-	\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
-	= \begin{cases}
-		\frac{2}{3 - 2\alpha}\left(e^{(\frac{3}{2} - \alpha)(R_n - y)} - 1\right) &\mbox{if } 1/2 < \alpha < 3/2,\\
-		R_n - y &\mbox{if } \alpha = 3/2,\\
-		\frac{2}{2\alpha-3}\left(1 - e^{-(\alpha - \frac{3}{2})(R_n - y)}\right) &\mbox{if } \alpha > 3/2.
-	\end{cases}
-\]
-Therefore we get
-\begin{align*}
-	&\hspace{-30pt}\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}
-		\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime\\
-	&= \Mu{\BallPo{0,y}}\begin{cases}
-		\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(R_n - y)}\right)
-		&\mbox{if } 1/2 < \alpha < 3/2,\\
-		\frac{(2\alpha -1)K}{2} (R_n - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
-		\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
-		&\mbox{if } \alpha > 3/2.
-	\end{cases}\\
-	&= \Mu{\BallPo{0,y}} \phi_{\H,n}^{(2)}(y)
-\end{align*}
-and hence
-\[
-	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} = \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(R_n - y)} 
-	+ \phi_{\H,n}^{(2)}(y)\right).
-\]
-Combining this with~\eqref{eq:mu_hyperbolic_ball_part_1} yields the required upper bound.
-
-The lower bound follows by observing that the only difference with the above computations is the change of sign in front of 
-\[
-	\frac{2 \nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime.
-\]
-\end{proof}
-
-\subsection{Expected number of points in balls in the finite box model}\label{ssec:average_degree_P_n}
-
-%\TM{ same comment Re: average degree. }
-For the finite box model $\Gbox$ we obtain a similar result for expected size of the balls.
+The following lemma immediately implies that $\Mu{\BallPon{y}}$ satisfies the conditions of Lemma~\ref{lem:concentration_argument_rho_approximation} and hence that Proposition~\ref{prop:concentration_argument_all} holds for $\rho_{\text{box}}(y,k_n)$.
 
 \begin{lemma}\label{lem:average_degree_P_n}
-For all $p \in \Rcal_n$, such that $y > 2\log(\pi/2)$,
+For all $y > 2\log(\pi/2)$,
 \[
-	\mu_{\alpha,\nu}(\BallPon{p}) = \mu_{\alpha,\nu}(\BallPo{p})\left(1 - \phi_n(y)\right)
+	\Mu{\BallPon{p}} = \Mu{\BallPo{p}}\left(1 - \phi_n(y)\right)
 \]
@@
 
-\subsection{Concentration of heights argument for hyperbolic and finite box model}
+\subsection{Concentration of heights for the KPKVB model}\label{ssec:average_degree_HP_n}
 
-Let us define $\rho_{\Po}(y,k) = \Prob{\Po(\Mu{\BallHyp{y}}) = k}$ and $\rho_{\text{box}} = \Prob{\Po(\Mu{\BallPon{y}}) = k}$.
+%\TM{  the term ``average degree" does not fit very well with what goes on in this section.
+We are considering the expected number of points in a ball, but not yet computing the average degree of the graph.
+}\PvdH{I agree and have changed the header.}
+
+We will now show that a concentration of heights argument also applies to the KPKVB model.
+Due to the hyperbolic distance formula, the computations are however more involved than for the finite box model.
+Recall that under the coupling between the hyperbolic random graph and the finite box model, for two points $p, p^\prime$ with $y + y^\prime < R_n$, $p^\prime \in \BallHyp{p}$ exactly when $|x-x^\prime|_{\pi e^{R_n/2}} \le \Phi(y,y^\prime)$, where we slightly abused notation to write $\Phi(y,y^\prime) = \Phi(R - y, R - y^\prime)$.
+In this setting, the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
+\[
+	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Phi(y, y^\prime) 
+		\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
+\]
+for some constant $K$.
+This result enables us to determine the measure of a ball around a given point $p=(0,y)$.
+Recall that the hyperbolic ball $\BallHyp{p}$ is a subset of $\Rcal_n$ and not of the hyperbolic disc $\Dcal_{R_n}$, i.e.
+the balls $\BallHyp{p}$ "live" in the finite box and not the hyperbolic disc.
+We start with the following preliminary result.
+
+\begin{lemma}\label{lem:hyperbolic_ball_lower_part}
+Let $\Phi(y,y^\prime) := \Phi(R - y,R - y^\prime)$ be defined as in~\eqref{eq:def_Omega_hyperbolic}. Then, for any $0 \le \delta < 1$
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} = 1.
+\]
+\end{lemma}
+
+\begin{proof}
+Recall that $\Mu{\BallPo{0,y}} = \xi e^{y/2}$ where $\xi = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$. Using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} we have 
+\begin{align*}
+	\frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} 
+	&\le \frac{2\nu \alpha}{\pi} \int_{0}^{(1-\delta)(R-y)} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R_n}\right)
+		e^{-\alpha y^\prime} \dd y^\prime\\
+	&= \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(1-\delta)(R_n - y)}\right) \\
+	&\hspace{10pt}+ \frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
+\end{align*}
+
+We first compute the integral, which depends on the value of $\alpha$,
+\[
+	\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
+	= \begin{cases}
+		\frac{2}{3 - 2\alpha}\left(e^{(\frac{3}{2} - \alpha)(1-\delta)(R-y)} - 1\right) &\mbox{if } 1/2 < \alpha < 3/2,\\
+		(1-\delta)(R-y) &\mbox{if } \alpha = 3/2,\\
+		\frac{2}{2\alpha-3}\left(1 - e^{-(\alpha - \frac{3}{2})(1-\delta)(R-y)}\right) &\mbox{if } \alpha > 3/2.
+	\end{cases}
+\]
+Therefore we get
+\begin{align*}
+	&\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}
+		\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime\\
+	&= \Mu{\BallPo{0,y}}\begin{cases}
+		\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)-(\frac{3}{2}-\alpha)\delta(R-y)} 
+			- e^{-(R_n - y)}\right)
+		&\mbox{if } 1/2 < \alpha < 3/2,\\
+		\frac{(2\alpha -1)K}{2} (1-\delta)(R - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
+		\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y) 
+			-(\alpha - \frac{3}{2})(R-y)}\right)
+		&\mbox{if } \alpha > 3/2,
+	\end{cases}
+\end{align*}
+and hence
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1}
+	\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}
+			\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime = 0.
+\]
+Since $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} e^{-(\alpha - \frac{1}{2})(1-\delta)(R_n - y)} = 0$, we conclude that
+\[
+	\limsup_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime)
+		\alpha e^{-\alpha y^\prime} = 1.
+\]
+The proof that this also holds for the limit infimum immediately follows, by observing that the only difference with the above computations is the change of sign in front of 
+\[
+	\frac{2 \nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime.
+\]
+\end{proof}
+
+We can now show that the measure of the balls in the KPKVB model and the infinite model are asymptotically equivalent.
+
+\begin{lemma}\label{lem:average_degree_hyperbolic}
+For any $0 < \varepsilon < 1$
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \frac{\Mu{\BallHyp{0,y}}}{\Mu{\BallPo{0,y}}} = 1.
+\]
+%Let $\eps \in (0, 1)$. Then for all $0 \le y \le (1 - \eps)R_n$
+%\[
+%	 1 - \phi_{\H,n}^{(1)}(y) - \phi_{\H,n}^{(2)}(y) \le \frac{\Mu{\BallHyp{0,y}}}{\Mu{\BallPo{0,y}}} 
+%	 \le 1 - \phi_{\H,n}^{(1)}(y) + \phi_{\H,n}^{(2)}(y),
+%\]
+%where
+%\[
+%	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 1 - 4\pi}{4\pi} e^{-(\alpha - \frac{1}{2})(R_n - y)} 
+%		+ \left(\alpha - \frac{1}{2}\right)\pi e^{-(\alpha - \frac{1}{2})R_n - y/2},
+%\]
+%and
+%\[
+%	\phi_{\H,n}^{(2)}(y) = 
+%	+ \begin{cases}
+%			\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(R_n - y)}\right)
+%			&\mbox{if } 1/2 < \alpha < 3/2,\\
+%			\frac{(2\alpha -1)K}{2} (R_n - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
+%			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
+%			&\mbox{if } \alpha > 3/2,
+%		\end{cases}
+%\]
+%with $K$ being the constant coming from the approximation of $\Phi$ in Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
+%%\TM{ We want to say in the lemma where $K$ comes from. (not everyone reads surrounding text, or reads linearly, in a paper as long as this one.) }
+\end{lemma}
+
+\begin{proof}
+We perform the computation of $\Mu{\BallHyp{0,y}}$ by splitting the integration with respect to the height $y^\prime$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$,
+\[
+	\Mu{\BallHyp{y}} 
+	= \Mu{\BallHyp{y} \cap \Rcal_n ([0,R_n - y))} + \Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}.
+\]
+
+For the first part we have that
+\[
+	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} = \frac{2\nu \alpha}{\pi} \int_0^{R-y} \Phi(y,y^\prime) e^{-\alpha y^\prime}
+	\dd y^\prime.
+\]
+Hence, by applying Lemma~\ref{lem:hyperbolic_ball_lower_part} with $\delta = 0$ we conclude that
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1}
+	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} = 1.
+\]
+
+For the second part we observer that $\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])= \Rcal_n([R_n-y,R_n])$. 
+Thus, 
+\begin{align*}
+	&\hspace{-30pt}\Mu{\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])} \\
+	&= \int_{R_n - y}^{R_n} \int_{I_n} f_{\alpha,\nu}(x^\prime, y^\prime) \dd x^\prime \dd y^\prime
+		= \nu \alpha e^{R_n/2}\left(e^{-\alpha(R_n - y)} - e^{-\alpha R_n}\right)\\
+	&= \Mu{\BallPo{0,y}} \frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
+		- e^{-(\alpha - \frac{1}{2})R_n - y/2}\right), \numberthis \label{eq:mu_hyperbolic_ball_part_1}
+\end{align*}
+from which we conclude that
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} 
+	\Mu{\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])} = 0,
+\]
+which finishes the proof.
+\end{proof}
+
+A direct consequence of Lemma~\ref{lem:average_degree_hyperbolic} is that $\Mu{\BallHyp{y}} = \Mu{\BallPo{y}}(1 + \phi_n(y))$, where $\phi_n(y) := \Mu{\BallHyp{y}}/\Mu{\BallPo{y}} - 1$ satisfies condition i) in Lemma~\ref{lem:concentration_argument_rho_approximation}.
+To show that condition ii) is also satisfied we need to analyze
+\[
+	\phi_n^\prime(y) = 
+	\Mu{\BallPo{y}}^{-1} \frac{\partial}{\partial y} \mu\left(\BallHyp{y}\right) -  \frac{1}{2} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}},
+\]
+where we used that $\frac{\partial}{\partial y}\Mu{\BallPo{y}} = \frac{1}{2}\Mu{\BallPo{y}}$. Again, Lemma~\ref{lem:average_degree_hyperbolic} implies that 
+\[
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R_n} \frac{1}{2} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}}
+	= \frac{1}{2}.
+\]
+The following lemma shows that the same holds for the first term from which we conclude that $\phi_n(y)$ satisfies condition ii) in Lemma~\ref{lem:concentration_argument_rho_approximation} and hence that Proposition~\ref{prop:concentration_argument_all} also holds for $\rho_{\Po}(y,k_n)$.
+
+\begin{lemma}
+For any $0 < \varepsilon < 1$,
+\[
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1}
+	\frac{\partial}{\partial y} \mu\left(\BallHyp{y}\right) 
+	= \frac{1}{2}.
+\]
+\end{lemma}
+
+\begin{proof}
+We again split $\Mu{\BallHyp{y}}$ over the top and bottom part,
+\[
+	\Mu{\BallHyp{y}} 
+	= \Mu{\BallHyp{y} \cap \Rcal_n ([0,R_n - y))} + \Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])},
+\]
+where
+\[
+	\Mu{\BallHyp{y} \cap \Rcal_n ([0,R_n - y))} = \frac{2\alpha \nu}{\pi}\int_0^{R - y} \Phi(y,y^\prime) 
+		e^{-\alpha y^\prime} \dd y^\prime,
+\]
+with $\Phi(y,y^\prime)$ defined as in~\eqref{eq:def_Omega_hyperbolic} and, see~\eqref{eq:mu_hyperbolic_ball_part_1},
+\[
+	\Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}
+	= \xi e^{y/2}\frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
+	- e^{-(\alpha - \frac{1}{2})R_n - y/2}\right).
+\]
+Taking the derivative of the last expression gives
+\begin{align*}
+	&\frac{\partial}{\partial y} \Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}\\
+	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}
+		+ \xi e^{y/2}\frac{2\alpha - 1}{4\pi}\left(
+		\left(\alpha - \frac{1}{2}\right)e^{-(\alpha - \frac{1}{2})(R_n - y)} 
+		+ \frac{1}{2}e^{-(\alpha - \frac{1}{2})R_n - y/2}\right)\\
+	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}\left(1 +
+		\frac{(2\alpha - 1)e^{-(\alpha - \frac{1}{2})(R_n - y)} + e^{-(\alpha - \frac{1}{2})R_n - y/2}}
+		{e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(\alpha - \frac{1}{2})R_n - y/2}}\right).
+\end{align*}
+Since, $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])} = 0$, we are left to show that
+\begin{equation}\label{eq:derivative_mu_hyp_ball_main}
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \frac{2\alpha \nu}{\pi} \frac{\partial}{\partial y} \int_0^{R - y} \Phi(r,r^\prime) e^{-\alpha y^\prime} \dd y^\prime
+	= \frac{1}{2}.
+\end{equation}
+
+We start with some preliminary computations. For convenience we define
+\[
+	\Xi_n(y,y^\prime) = 1 - \frac{\cosh(R- y)\cosh(R-y^\prime) - \cosh(R)}{\sinh(R - y) \sinh(R - y^\prime)},
+\]
+so that
+\[
+	\Phi(R -y, R - y^\prime) = \frac{1}{2}e^{R/2} \arccos\left(1 - \Xi_n(y,y^\prime)\right).
+\]
+Next, following the same calculation as in the proof of~\cite[Lemma 28]{fountoulakis2018law}, we write
+\begin{align*}
+	\Xi(y,y^\prime)
+	&= 2 e^{-(R - y - y^\prime)} \frac{\left(1 - e^{y^\prime - y - R}\right)\left(1 - e^{y - y^\prime - R}\right)}
+		{\left(1 - e^{-2(R - y^\prime)}\right)\left(1 - e^{-2(R- y)}\right)}\\
+	&:= 2 e^{-(R - y - y^\prime)} \frac{h_1(y) h_2(y)}{h_3(y^\prime) h_3(y)},
+\end{align*}
+with
+\[
+	h_1(y) = 1 - e^{y^\prime - y - R}, \quad h_2(y) = 1 - e^{y - y^\prime - R}
+	\quad \text{and} \quad h_3(y) = 1 - e^{-2(R- y)}.
+\]
+We suppressed the dependence on $n$ and, in some cases, on $y^\prime$ for notation convenience.
+
+We make two important observations.
+First, $\Xi(y,y^\prime)$ is an increasing function in both arguments, for $y, y^\prime < R$ and $y + y^\prime < R$.
+Second, for all $y + y^\prime < R$, $h_1(y) \le h_3(y^\prime)$ and $h_2(y) \le h_3(y)$, while $h_3(y), h_3(y^\prime) < 1$, so that
+\begin{equation}\label{eq:derivative_hyp_ball_Xi_bounds}
+	2 e^{-(R - y - y^\prime)}h_1(y) h_2(y) \le \Xi_n(y,y^\prime) \le 2 e^{-(R - y - y^\prime)}.
+\end{equation}
+In particular, there exists a $0 < \delta < 1$ such that $1 \le \Xi(y,y^\prime) \le 2$ for all $0 < y < R$ and $(1-\delta)(R-y) < y^\prime < R$.
+
+Next, taking the derivative of $\Xi_n(y,y^\prime)$ yields,
+\begin{align*}
+	\frac{\partial}{\partial y} \Xi(y,y^\prime) &= \Xi(y,y^\prime) + 2 e^{-(R - y - y^\prime)}
+		\left(\frac{h_1^\prime(y) h_2(y)}{h_3(y^\prime) h_3(y)} + \frac{h_1(y)h_2^\prime(y)}{h_3(y^\prime) h_3(y)}
+		- \frac{h_1(y) h_2(y) h_3^\prime(y)}{h_3(y^\prime) h_3(y)^2}\right)\\
+	&= \Xi(y,y^\prime)\left(1 + \frac{h_1^\prime(y)}{h_1(y)} + \frac{h_2^\prime(y)}{h_2(y)} 
+		- \frac{h_3^\prime(y)}{h_3(y)}\right)\\
+	&:= \Xi(y,y^\prime)\left(1 + \varphi_n(y,y^\prime)\right),
+\end{align*}
+with
+\[
+	\varphi_n(y,y^\prime) = \frac{e^{y^\prime - y- R}}{1 - e^{y^\prime - y - R}} 
+	- \frac{e^{y - y^\prime - R}}{1 - e^{y - y^\prime - R}} - \frac{2e^{-2(R - y)}}{1 - e^{-2(R-y)}}. 
+\]
+Therefore, by the chain rule,
+\begin{align*}
+	\frac{\partial}{\partial y} \Phi(R -y, R - y^\prime)
+	&= \frac{1}{2}e^{R/2} \frac{1}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}} 
+		\frac{\partial}{\partial y} \Xi(y,y^\prime)\\
+	&=  \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}\left(1 + 
+		\varphi_n(y,y^\prime)\right). \numberthis \label{eq:derivative_Phi}
+\end{align*}
+Applying the Leibniz's rule we then get
+\begin{align*}
+	&\hspace{-30pt}\frac{\partial}{\partial y} \int_0^{R - y} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
+	&= - \alpha\Phi(y,R - y)e^{-\alpha(R-y)} + \int_0^{R - y} \frac{\partial}{\partial y}  \Phi(y,y^\prime) 
+		\alpha e^{-\alpha y^\prime} \dd y^\prime\\
+	&= -\frac{\pi}{2}e^{-(\alpha-\frac{1}{2})R_n + \alpha y} + \int_0^{R- y} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+		\left(1 + \varphi_n(y,y^\prime)\right) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
+	&= -\frac{\pi}{2}e^{-(\alpha-\frac{1}{2})R_n + \alpha y}  + \int_0^{(1-\delta)(R- y)} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}
+		{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+		\left(1 + \varphi_n(y,y^\prime)\right) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
+	&\hspace{10pt}+ \int_{(1-\delta)(R- y)}^{R - y} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}
+			{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+			\left(1 + \varphi_n(y,y^\prime)\right) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
+	&:= -I_1(y) + I_2(y) + I_3(y),
+\end{align*}
+with $\delta$ such that $1 \le \Xi(y,y^\prime) \le 2$ for all $0 < y < R$ and $(1-\delta)(R-y) < y^\prime < R$.
+
+We proceed by showing that
+\begin{equation}\label{eq:derivative_hyp_ball_error_1}
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} I_t(y) = 0, \quad \text{for } t = 1,3
+\end{equation}
+while
+\begin{equation}\label{eq:derivative_hyp_ball_main_part}
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} I_2(y) = \frac{1}{2}.
+\end{equation}
+This then implies~\eqref{eq:derivative_mu_hyp_ball_main} and finishes the proof.
+
+Let us first consider $I_1(y)$. Since 
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} I_1(y) 
+	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \frac{\pi}{2\xi} e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
+\]
+
+For $I_3(y)$ we first use that $y^\prime < R - y$ to bound $\varphi(y,y^\prime)$ as follows,
+\[
+	\varphi_n(y,y^\prime) \le \frac{e^{y^\prime - y - R}}{1 - e^{y^\prime - y - R}} \le \frac{e^{-2y}}{1 - e^{-2y}}.
+\]
+This then yields that
+\[
+	I_3(y) \le \frac{\alpha}{2}\left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right)e^{R/2}
+	\int_{(1-\delta)(R- y)}^{R - y} \frac{ \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+	e^{-\alpha y^\prime} \dd y^\prime.
+\]
+Since for all $1 \le x < 2$,
+\[
+	\frac{1}{\sqrt{1- (1-x)^2}} \le \frac{2}{\sqrt{2(2-x)}},
+\]
+and $1 \le \Xi(y,y^\prime) \le 2$, for all $(1-\delta)(R -y) \le y\prime < R-y$ and $y < R$, it follows that
+\begin{align*}
+	&\hspace{-30pt}\int_{(1-\delta)(R- y)}^{R - y} \frac{ \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+		e^{-\alpha y^\prime} \dd y^\prime \\
+	&\le 2 \int_{(1-\delta)(R- y)}^{R - y} \frac{\Xi(y,y^\prime)}{\sqrt{2(2-\Xi(y,y^\prime))}} e^{-\alpha y^\prime} 
+		\dd y^\prime \\
+	&\le 2 e^{-\alpha(R - y)} \int_{(1-\delta)(R- y)}^{R - y} 
+		\frac{e^{-(R - y - y^\prime)}}{\sqrt{1 - e^{-(R - y - y^\prime)}}} e^{\alpha (R - y - y^\prime)} \dd y^\prime.
+\end{align*}
+Making the change of variables $z = e^{-(R - y - y^\prime)}$ ($\dd y^\prime = z^{-1} \dd z$) we get that
+\begin{align*}
+	2 e^{-\alpha(R - y)} \int_{(1-\delta)(R- y)}^{R - y} 
+			\frac{e^{-(R - y - y^\prime)}}{\sqrt{1 - e^{-(R - y - y^\prime)}}} e^{\alpha (R - y - y^\prime)} \dd y^\prime
+	&= 2 e^{-\alpha(R - y)} \int_{e^{-\delta (R - y)}}^{1} \frac{z^{-\alpha}}{\sqrt{1 - z}} \dd z\\
+	&\le 2 e^{-\alpha(R - y)} \sqrt{1 - e^{-\delta (R - y)}}\\
+	&\le 2 e^{-\alpha (R -y)}.
+\end{align*}
+We therefore conclude that
+\[
+	I_3(y) \le \alpha \left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right)e^{-(\alpha -\frac{1}{2})R + \alpha y}.
+\]
+which implies
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} I_3(y) 
+	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \alpha \left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right) e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
+\]
+
+Finally, to show~\eqref{eq:derivative_hyp_ball_main_part} we define 
+\begin{align*}
+	\varphi^-_n &:= \sup_{0 < y \le (1-\varepsilon)R_n} \, \inf_{0 \le y^\prime \le (1 - \delta)(R-y)} 
+		\varphi_n(y,y^\prime)\\
+	\varphi^+_n &:= \sup_{0 < y \le (1-\varepsilon)R_n} \, \sup_{0 \le y^\prime \le (1 - \delta)(R-y)} \varphi_n(y,y^\prime)
+\end{align*}
+and note that since for $0 \le y^\prime \le (1-\delta)(R-y)$,
+\[
+	\frac{e^{-(R + y)}}{1 - e^{-(R+y)}} - \frac{e^{-(R- y)}}{1 - e^{-(R-y)}} - \frac{2e^{-2(R-y)}}{1 - e^{-2(R-y)}}
+	\le \varphi_n(y,y^\prime) \le \frac{e^{-\delta(R-y)}}{1 - e^{-\delta(R-y)}}.
+\] 
+we get $\lim_{n \to \infty} \varphi^\pm_n = 0$.
+Next, recall that $\Phi(y,y^\prime) = \frac{1}{2}e^{R/2}\Xi(y,y^\prime)$.
+Then, since $\Xi(y,y^\prime) < 2$ for all $y^\prime < (1-\delta)(R-y)$ and $y < R$, there exists a $K > 0$ such that (see Lemma~\ref{lem:arccos_approx}),
+\[
+	\frac{1}{2}\Phi(y,y^\prime)\left(1 - \frac{(1+\sqrt{2})\Xi(y,y^\prime)}{1 + \Xi(y,y^\prime)}\right)
+	\le \frac{\frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}} 
+	\le \frac{1}{2}\Phi(y,y^\prime)\left(1 + \frac{(1+K)\Xi(y,y^\prime)}{1 - \Xi(y,y^\prime)}\right)
+\]
+for all $y^\prime < (1-\delta)(R - y)$ and $y < R$. Using that $e^{-(r-y)} \le e^{-(R - y - y^\prime)} \le e^{-\delta(R- y)}$, for $0 < y^\prime < (1-\delta)(R-y)$, we get
+\[
+	1 - \frac{(1+\sqrt{2})\Xi(y,y^\prime)}{1 + \Xi(y,y^\prime)} \ge 1 - 2(1+\sqrt{2})e^{-(R-y)}
+\]
+and
+\[
+	1 + \frac{(1+K)\Xi(y,y^\prime)}{1 - \Xi(y,y^\prime)} 
+	\le 1 + \frac{2(1 + K)e^{-\delta(R - y)}}{1-e^{-\delta(R-y)}}.
+\]
+
+We thus have the following upper and lower bound on $I_2(y)$
+\begin{align*}
+	I_2(y) \le \frac{1}{2} \left(1 + \phi_n^+\right)
+	\left(1 + \frac{2(1 + K)e^{-\delta(R - y)}}{1-e^{-\delta(R-y)}}\right)
+	\int_{0}^{(1-\delta)(R-y)} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime,
+\end{align*}
+and
+\[
+	I_2(y) \ge \frac{1}{2} \left(1 + \phi_n^-\right)\left(1 - 2(1+\sqrt{2})e^{-(R-y)}\right)
+	\int_{0}^{(1-\delta)(R-y)} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime.
+\]
+From this~\eqref{eq:derivative_hyp_ball_main_part} follows since, $\lim_{n \to \infty} \varphi_n^\pm = 0$ and by Lemma~\ref{lem:hyperbolic_ball_lower_part},
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} 
+	\int_{0}^{(1-\delta)(R-y)} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime
+	= 1.
+\] 
+\end{proof}
+
+%\subsection{Concentration of heights argument for hyperbolic and finite box model}
+%
+%Let us define $\rho_{\Po}(y,k) = \Prob{\Po(\Mu{\BallHyp{y}}) = k}$ and $\rho_{\text{box}} = \Prob{\Po(\Mu{\BallPon{y}}) = k}$.
 Then since Lemma~\ref{lem:average_degree_P_n} implies that $\Mu{\BallHyp{(y)}}$ satisfies the requirements in Lemma~\ref{lem:concentration_argument_rho_approximation} while Lemma~\ref{lem:average_degree_hyperbolic} states that this holds for $\Mu{\BallPon{0,y}}$, we have the following important Corollary.
-
-\begin{corollary}\label{cor:concentration_argument_other_models}
-The statements of Lemma~\ref{lem:concentration_argument_rho_approximation} holds for the two distribution functions $\rho_{\Po}(y,k)$ and $\rho_{n}(y,k)$. 
-\end{corollary}
-
+%
 %\begin{corollary}\label{cor:concentration_argument_other_models}
-%Let $\hat{\rho}_n(y,k)$ be any of the two distribution functions $\rho_{\Po}(y,k)$ and $\rho_{n}(y,k)$ and let $\Kcal_{C,n}(\kappa_n)$ be defined as in~\eqref{eq:def_K_C_n_set}.
+%The statements of Lemma~\ref{lem:concentration_argument_rho_approximation} holds for the two distribution functions $\rho_{\Po}(y,k)$ and $\rho_{n}(y,k)$. 
+%\end{corollary}
+%
+%%\begin{corollary}\label{cor:concentration_argument_other_models}
+%%Let $\hat{\rho}_n(y,k)$ be any of the two distribution functions $\rho_{\Po}(y,k)$ and $\rho_{n}(y,k)$ and let $\Kcal_{C,n}(\kappa_n)$ be defined as in~\eqref{eq:def_K_C_n_set}.
 Then, for any function $g_n(y)$ such that, uniformly on $(0, R_n]$, $g_n(y) = \bigO{k_n^{s} e^{\beta y}}$,
-%%\TM{ Where did the $n^{-1}$ come from? Does not appear in L3.4. }\PvdH{I will elaborate on this once the statement of Lemma~\ref{lem:concentration_argument} is updated}, 
-%as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
-%\[
-%	\int_{\Rcal_n} g_n(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y
-%	= (1+\smallO{1})n\int_{0}^\infty g_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
-%\]
-%for some $C > 0$ large enough.
-%\end{corollary}
-
-In particular we conclude that, similarly to the infinite limit model, concentration of heights arguments as described in Remark~\ref{rmk:concentration_argument} can be applied in the case of the hyperbolic random graphs and the finite box model.
-
-\begin{remark}[Most frequent use of concentration of argument]
-Note that it follows from Proposition~\ref{prop:asymp} that $P(y)$ satisfies the conditions in the both statements of Lemma~\ref{lem:concentration_argument_rho_approximation}.
+%%%\TM{ Where did the $n^{-1}$ come from? Does not appear in L3.4. }\PvdH{I will elaborate on this once the statement of Lemma~\ref{lem:concentration_argument} is updated}, 
+%%as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
+%%\[
+%%	\int_{\Rcal_n} g_n(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y
+%%	= (1+\smallO{1})n\int_{0}^\infty g_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+%%\]
+%%for some $C > 0$ large enough.
+%%\end{corollary}
+%
+%In particular we conclude that, similarly to the infinite limit model, concentration of heights arguments as described in Remark~\ref{rmk:concentration_argument} can be applied in the case of the hyperbolic random graphs and the finite box model.
+%
+%\begin{remark}[Most frequent use of concentration of argument]
+%Note that it follows from Proposition~\ref{prop:asymp} that $P(y)$ satisfies the conditions in the both statements of Lemma~\ref{lem:concentration_argument_rho_approximation}.
 In particular, if $\hat{\rho}_n$ denote either $\rho_{\Po}$ or $\rho_{\text{box}}$, then as $n \to \infty$
-\begin{equation}\label{eq:concentration_heights_argument_Py}
-	\int_{\Rcal_n} P(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x, y) \dd x \dd y
-	= (1 + \smallO{1}) n \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
-\end{equation}
-This is the form that will be use most frequently in the remainder of this paper.
-\end{remark}
+%\begin{equation}\label{eq:concentration_heights_argument_Py}
+%	\int_{\Rcal_n} P(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x, y) \dd x \dd y
+%	= (1 + \smallO{1}) n \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+%\end{equation}
+%This is the form that will be use most frequently in the remainder of this paper.
+%\end{remark}

### 2019-02-21 proofs_finite_k.tex
revised sections 6 and 7

@@
 Then 
-
-$$ c(k; G_n)-c(k; G_{n,\text{Po}}) \xrightarrow[n\to\infty]{\Pee} 0. $$
+\[
+	\left|c(k; G_n)-c(k; G_{n,\text{Po}})\right| \xrightarrow[n\to\infty]{\Pee} 0.
+\]
 \end{lemma}
@@
 We observe that $G((1+\epsilon)n;\alpha,(1+\epsilon)\nu), G(n;\alpha,\nu)$ 
-and $\GPo(n;\alpha,\nu)$ all live on the same disk (with radius $R = 2\ln \frac{n}{\nu}$).
+and $\GPo(n;\alpha,\nu)$ all live on the same disk (with radius $R = 2\log\left(\frac{n}{\nu}\right)$).
 We consider the coupling where we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ chosen according
@@
 and simlarly for $\GPo$. In particular also 
-$|c(k;G(n;\alpha,\nu)) - c(k;\GPo(n;\alpha,\nu))| > \sqrt{\eps} ) = O(\sqrt\eps)$.
-Sending $\eps\searrow 0$ proves the lemma.
+$\Prob{|c(k;G(n;\alpha,\nu)) - c(k;\GPo(n;\alpha,\nu))| > \sqrt{\eps} } = O(\sqrt\eps)$.
+Sending $\eps\searrow 0$ proves the lemma. \PvdH{I think we need to be a bit more precise here and set $\varepsilon = \varepsilon_n := Q n^{-1}$.
+}
 \end{proof}
@@
 \begin{align*}
-\E N_1 = n \Pee(B_{R-H}(0)) \leq n e^{-\alpha H}
+\E N_1(H) = n \Pee(B_{R-H}(0)) \leq n e^{-\alpha H}
 \end{align*}
@@
 Hence,
-$$\E N_{\leq H_1}(H_2) \leq n (1-e^{-\mu(H_2)}) \leq \frac{\epsilon}{2}$$
+$$\E N_{\leq H_1}(H_2) \leq n (1-e^{-\mu(H_2)}) \leq n \frac{\epsilon}{2}$$
 Finally, $\E N_2(H_2) \leq \E N_{\geq H_1} + \E N_{\leq H_1}(H_2) \leq \epsilon n$.
@@
 Therefore, by Markov's inequality,
-$$\Pee( n-N_H \geq \sqrt{\epsilon}n) \leq \frac{\E (n-N_H)}{n} \leq \sqrt{\epsilon}$$
+$$\Pee( n-N_H \geq \sqrt{\epsilon}n) \leq \frac{\E (n-N_H)}{n \sqrt{\epsilon}} \leq \sqrt{\epsilon}$$
 Consider 
@@
 Let $\rho(y)$ denote the truncated exponential density.
-
+\PvdH{These notations are not in sync with the rest of the paper.}
 Then,
 $c_{\leq H}(k) = (1+o(1))\int_0^H \int_0^H \int_0^H \Delta_H(y) \tau(y,k)\rho(y_1)\rho(y_2)\rho(y) dy_1dy_2 dy$ a.a.s.
+\PvdH{I do not understand how a.a.s. is proven.}
 \end{lemma}
 \begin{proof}
-First of all, as for $c_{\leq H}(k)$ all vertices involved have height $\leq H$, we can perform the computations in the box model: As $H$ is constant, for $R$ large enough, vertices with radial coordinates at least $R-H$ will have radial coordinate $\geq \frac{3}{4}R$, such that by Lemma~30(ii) from the paper on the largest component of KPKVB, edges exist between such vertices in the disk if and only if they exist in the box.
+First of all, as for $c_{\leq H}(k)$ all vertices involved have height $\leq H$, we can perform the computations in the box model: As $H$ is constant, for $R$ large enough, vertices with radial coordinates at least $R-H$ will have radial coordinate $\geq \frac{3}{4}R$, such that by Lemma~\ref{lem:coupling_edges}, edges exist between such vertices in the disk if and only if they exist in the box.
 
@@
 \end{align*}
+\PvdH{What is $E_R$ and what is $D_H$?}
 %Let $V \subset E_R$ denote the vertex set of the finite box model in the box $E_R = (-\frac{\pi}{2}e^{\frac{R}{2}},\frac{\pi}{2}e^{\frac{R}{2}}]\times (0,R]$.
@@
 
+\PvdH{Where is the proof of Theorem~\ref{thm:mainkfixed}?}
+
 \subsection{The proof of Theorem~\ref{thm:maincc}}

### 2019-02-21 proofs_infinite_k.tex
revised sections 6 and 7

@@
 Assuming this concentration result, we are left with the task to compute the limit of $\Exp{c^\ast(k_n; \Gbox)}$ as $n \to \infty$ and show that it is equivalent to $\gamma(k_n)$.
-To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of the clustering function $c^\ast(k;G)$ in $G_{\mathcal{P},n}(\alpha,\nu)$ and $G_{\mathcal{P}}(\alpha,\nu)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
+To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of $c^\ast(k;\Gbox)$ and $\gamma(k_n)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
 
@@
 \[
-	\left|\Exp{c^\ast(k_n; \Gbox)} - c(k_n;\Ginf)\right| = \smallO{s(k_n)}.
+	\left|\Exp{c^\ast(k_n; \Gbox)} - \gamma(k_n)\right| = \smallO{s(k_n)}.
 \]
@@
 \end{align*}
-At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model where we also used that $c(k_n;\Ginf) = \gamma(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
-\TM{ Maybe we can have a more clear reference?
+At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model.
+%where we also used that $c(k_n;\Ginf) = \gamma(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
+%\TM{ Maybe we can have a more clear reference?
 Now, at this place in the paper this proof feels a bit like cheating since there are almost no details given.
 } \PvdH{I completely agree.
-I think that once the results for fixed $k$ have been included we can include a specific statement at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P} we can refer to.} All of this together yields that:
+I think that once the results for fixed $k$ have been included we can include a specific statement at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P} we can refer to.}
+All of this together yields that:
 \begin{align*}

### 2019-02-21 transition.tex
revised sections 6 and 7

@@
 \[
-	\Exp{\left|c^\ast(k_n; \Gbox) - \Exp{c^\ast(k_n; \Gbox)}\right|} = \smallO{s(k_n)}.
-\] 
-Recall that $\Gbox$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ (we write $\Pcal_n$ for this process), and connecting two points $p_1, p_2 \in \Rcal$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$.
-We recall that by definition of the norm $|.|_{\pi e^{R_n/2}}$ the left and right boundaries of $\Rcal$ are identified.
+	\left|\Exp{c^\ast(k_n; \Gbox)} - \gamma(k_n)\right| = \smallO{s(k_n)}.
+\]
+
+Recall that $\Gbox$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ and connecting two points $p_1, p_2 \in \Rcal$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$.
+We also recall that by definition of the norm $|.|_{\pi e^{R_n/2}}$ the left and right boundaries of $\Rcal$ are identified.
 See Section~\ref{ssec:finite_model} for more details.
-\TM{ This last bit of the sentence is already contained in the fact we us $|.|_{\pi e^{R_n/2}}$.
+Due to this identification of the boundaries some triples of nodes that form triangles in the finite box model do not form a triangle in the infinite model.
+Therefore, to establish the required result we need to compute the asymptotic difference between triangle counts in both models.
+
+%\TM{ This last bit of the sentence is already contained in the fact we us $|.|_{\pi e^{R_n/2}}$.
 To me it does not add anything, except possibly confusion.
@@
 
-In this section we shall compute the asymptotic difference between triangle counts in the finite and infinite model. First we recall the definition of $\Kcal_{C}(k_n)$
-\[
-	\Kcal_C(k_n) = \left\{y \in \R_+ : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \le e^{\frac{y}{2}}
-	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\},	
-\]
-\TM{ Typo : $p\in\R$. Do you mean $\Rcal$? Or maybe 
-$\R \times \R^+$? Still not sure that max and min in defn add anything. } \PvdH{It was a typo and is corrected. I have removed the max and min.}
+%In this section we shall compute the asymptotic difference between triangle counts in the finite box and infinite model. First we recall the definition of $\Kcal_{C}(k_n)$
+%\[
+%	\Kcal_C(k_n) = \left\{y \in \R_+ : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \le e^{\frac{y}{2}}
+%	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\},	
+%\]
+%\TM{ Typo : $p\in\R$. Do you mean $\Rcal$? Or maybe 
+%$\R \times \R^+$? Still not sure that max and min in defn add anything. } \PvdH{It was a typo and is corrected. I have removed the max and min.}
 %with
@@
 %\TM{ Same issue as before. }
-In addition we note that the function $\phi_n(y)$ in Lemma~\ref{lem:average_degree_P_n} satisfies
-\[
-	\phi_n(y) = \bigT{e^{-(\alpha - \frac{1}{2})(R_n - y)}},
-\]
-as $R_n - y \to \infty$.
+%In addition we note that the function $\phi_n(y)$ in Lemma~\ref{lem:average_degree_P_n} satisfies
+%\[
+%	\phi_n(y) = \bigT{e^{-(\alpha - \frac{1}{2})(R_n - y)}},
+%\]
+%as $R_n - y \to \infty$.
 Since $e^{y/2} = \bigT{k_n} = \smallO{e^{R_n}}$ as $n \to \infty$, uniformly on $\Kcal_C(k_n)$, it follows that $\phi_n(y) = \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}$, uniformly on $\Kcal_C$.
 This yields the following useful corollary to Lemma~\ref{lem:average_degree_P_n}.
-
-\begin{corollary}\label{cor:average_degree_P_n_K}
-Let $\alpha > \frac{1}{2}$, $C > 0$. Then, for all $y \in \Kcal_{C}(k_n)$,
-\[
-	\mu(\BallPon{y}) = \mu(\BallPo{y})\left(1 - \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}\right).
-\]
-\TM{ I don't follow. Spell it out. }\PvdH{I added additional explanation above. Please see if this solves the confusion.}
-
-\end{corollary}
+%
+%\begin{corollary}\label{cor:average_degree_P_n_K}
+%Let $\alpha > \frac{1}{2}$, $C > 0$. Then, for all $y \in \Kcal_{C}(k_n)$,
+%\[
+%	\mu(\BallPon{y}) = \mu(\BallPo{y})\left(1 - \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}\right).
+%\]
+%\TM{ I don't follow. Spell it out. }\PvdH{I added additional explanation above. Please see if this solves the confusion.}
+%
+%\end{corollary}
+
+%We now turn to the task of calculating the expected number of triangles of a node at height $y$, for both the infinite model and the finite box model. 
+For any $p \in \R \times \R_+$ we define for the finite box model,
+\[
+	T_{\text{box}}(p) = \sum^{\ne}_{p_1, p_2 \in \Pcal_n \setminus p} T_{\text{box}}(p,p_1,p_2)
+\]
+where the sum is over all distinct pairs in $\Pcal_n \setminus p$ and
+\[
+	T_{\text{box}}(p,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPon{p_1}}.
+\]
+Similarly, for the infinite model we define
+\[
+	T_\infty(y) = \sum_{p_1, p_2 \in \Pcal \setminus \{0,y\}}^{\ne} T_\infty(y,p_1,p_2),
+\]
+where
+\[
+	T_{\infty}(y,p_1,p_2) = \ind{p_1 \in \BallPo{y}}\ind{p_2 \in \BallPo{y}}\ind{p_2 \in \BallPo{p_1}}.
+\]
+We will first relate $\gamma(k_n)$ and $\Exp{c^\ast(k_n; \Gbox)}$ using $T_\infty(y)$ and $T_{\text{box}}(y)$. Recall the definition of $\Kcal_{C}(k_n)$
+\[
+	\Kcal_C(k_n) = \left\{y \in \R_+ : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \le e^{\frac{y}{2}}
+	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\},	
+\]
+
+\begin{lemma}
+Let $\gamma(k_n)$ be defined as in~\eqref{eq:gammakint}. Then as $n \to \infty$
+\begin{equation}\label{eq:alt_gamma_kn}
+	\gamma(k_n) = (1+\smallO{1})\frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_{C}(k_n)} \Exp{T_\infty(y)} \rho(y,k) 
+				\alpha e^{-\alpha y} \dd y. 
+\end{equation}
+Moreover,
+\begin{equation}\label{eq:alt_c_ast_kn}
+	\Exp{c^\ast(k_n;\Gbox)} = (1 + \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y)}
+		\rho(y,k_n) \alpha e^{-\alpha y} \dd y
+\end{equation}
+as $n \to \infty$,
+\end{lemma}
+
+\begin{proof}
+Recall that 
+\[
+	P(y) = \Exp{\ind{u_1 \in \BallPo{u_2}}},
+\]
+where $u_1$ and $u_2$ are independent and distributed according to the probability density \\$\Mu{\BallPo{y}}^{-1} \ind{u_i \in \BallPo{y}} f(x_i, y_i)$.
+It then follows from the Campbell-Mecke formula that
+\begin{align*}
+	\Exp{T_\infty(y)} &= \int \ind{p_1 \in \BallPo{y}}\ind{p_2 \in \BallPo{y}}
+		\ind{p_2 \in \BallPo{p_1}} f(x_1,y_1) f(x_2,y_2) \dd x_1 \dd x_2 \dd y_1 \dd y_2\\
+	&= \Mu{\BallPo{y}}^2 P(y).
+\end{align*}
+It then follows that,
+\begin{align*}
+	\gamma(k_n) &= \frac{1}{p_{k_n}} \cdot \int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y \\
+	&= \frac{1}{p_{k_n}} \int_0^\infty \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) 
+		\alpha e^{-\alpha y_0} \dd y_0\\
+	&= (1+ \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_0^\infty \Exp{T_\infty(y)} \rho(y,k) \alpha e^{-\alpha y} \dd y_0,
+\end{align*}
+where the last line is due to a concentration of heights argument.
+
+For~\eqref{eq:alt_c_ast_kn} we recall that
+\[
+	c^\ast(k_n; \Gbox) = \frac{1}{\Exp{\Nbox(k_n)}} \sum_{p \in \Pcal} c_{\text{box}}(p)\ind{\Dbox(p) = k_n},
+\]
+where $c_{\text{box}}(p)$ can be expressed as
+\[
+	c_{\text{box}}(p) = \frac{1}{\binom{\Dbox(p)}{2}} \sum_{p_1, p_2 \in \Pcal \setminus p}^{\ne} T_{\text{box}}(p,p_1,p_2)
+	= \frac{T_{\text{box}}(p)}{\binom{\Dbox(p)}{2}}.
+\]
+By the Campbell-Mecje formula
+\begin{align*}
+	\Exp{c^\ast(k_n; \Gbox)} 
+	&= \frac{1}{\Exp{\Nbox(k_n)}} \int_{\Rcal} \Exp{c_{\text{box}}(p)\ind{\Dbox(p) = k_n}} f(x,y) \dd x \dd y\\
+	&= \frac{1}{\Exp{\Nbox(k_n)}} \int_{\Rcal} \CExp{c_{\text{box}}(p)}{\Dbox(p) = k_n}\rho_{\text{box}}(p,k_n) 
+		f(x,y) \dd x \dd y\\
+	&= (1+\smallO{1})\frac{n}{\Exp{\Nbox(k_n)}} \int_{\Kcal_C(k_n)} \CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n}
+		\rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+\end{align*}
+where the last line follows from a concentration of heights argument, for which we used that $\CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n} \le \binom{k_n}{2}$.
+To analyze the conditional expectation we observe that, similar to the analysis of $\gamma(k_n)$, conditioned on their being $k_n$ points in $\BallPon{y}$, each points $u_i = (x_i,y_i)$ is independently distributed according to the probability density $\Mu{\BallPon{y}}^{-1} \ind{u_i \in \BallPon{y}} f(x_i,y_i)$.
+Therefore,
+\begin{align*}
+	\CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n}
+	&= \binom{k_n}{2}^{-1} \Exp{\sum_{1 \le i < j \le k_n} \ind{u_i \in \BallPon{u_j}}} \\
+	&= \Exp{u_1 \in \BallPon{u_2}} \\
+	&= \Mu{\BallPon{y}}^{-2} \iint T_{\text{box}}(y,p_1,p_2) f(x_1,y_1) f(x_2,y_2) 
+		\dd x_1 \dd y_1 \dd x_2 \dd y_2\\
+	&= \Mu{\BallPon{y}}^{-2} \Exp{T_{\text{box}}(y)}.
+\end{align*}
+and thus, by applying a concentration of heights argument on $\Mu{\BallPon{y}}^{-2}$,
+\[
+	\Exp{c^\ast(k_n; \Gbox)} = (1 + \smallO{1}) \frac{n \Mu{\BallPon{2\log(k_n/\xi)}}^{-2}}{\Exp{\Nbox(k_n)}} \int_{\Kcal_C(k_n)} \Exp{T_{\text{box}}(y)} \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+\]
+To finish the argument, we first note that $\Mu{\BallPon{2\log(k_n/\xi)}}^{-2} = (1+\smallO{1})k_n^2$, while
+\[
+	\Exp{N_{\text{box}}(k_n)} = \int_{\Rcal} \rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y,
+\]
+so that by a concentration of heights argument,
+\[
+	\Exp{N_{\text{box}}(k_n)} = (1+o(1)) n \int_{0}^\infty \rho(y,k_n) \alpha e^{-\alpha y} \dd y 
+	= (1+\smallO{1}) n p_{k_n}.
+\]
+We therefore conclude that
+\[
+	\Exp{c^\ast(k_n; \Gbox)} = (1 + \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_C(k_n)} 
+		\Exp{T_{\text{box}}(y)} \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+\]
+
+%Next recall the definition of $\Kcal_{C}(k_n)$, see~\eqref{eq:def_K_C_set}, and note that for all $y_0 \in \Kcal_{C}(k_n)$, $\mu(y) = (1+\smallO{1})k_n$.
+Then Lemma~\ref{lem:concentration_argument} implies that, as $n \to \infty$,
+%\begin{align*}
+%	&\hspace{-30pt} \int_0^\infty \Exp{T_\infty(y_0)} \left(\frac{\mu(y)^2}{2}\right)^{-1} \rho(y_0,k) 
+%		\alpha e^{-\alpha y_0} \dd y_0\\
+%	&= (1+ \smallO{1}) \binom{k_n}{2}^{-1} \int_0^\infty \Exp{T_\infty(y_0)} \rho(y_0,k) \alpha e^{-\alpha y_0} \dd y_0,
+%\end{align*}
+%which finishes the proof.
+\end{proof}
+
+%
+%
+%For the finite box model we have, by the Campbell-Mecke formula,
+%\begin{align*}
+%	\Exp{c^\ast(k_n, \Gbox)}
+%	&= \frac{1}{\binom{k_n}{2}\Exp{\Nbox(k_n)}} \int_{\Rcal} \Exp{T_{\text{box}}(p) \ind{\text{deg}(p) = k_n}} f(x,y) 
+%		\dd x \dd y\\
+%	&= \frac{n}{\binom{k_n}{2}N_{\Gbox}(k_n)} \int_0^{R} \CExp{T_{\text{box}}(y_0)}{\text{deg}(y_0) = k_n} 
+%		\rho_{\text{box}}(y,k_n) \alpha e^{-\alpha y_0} \dd y_0,
+%\end{align*}
+%where the last line follows since the Poisson point process is invariant in $x$ and by slightly abusing notation $T_{\text{box}}(y_0) = T_{\text{box}}(0,y_0)$. Next we note that 
+%\[
+%	\Exp{N_{\text{box}}(k_n)} = \int_{\Rcal} \rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y,
+%\]
+%so that by a concentration of heights argument, see Corollary~\ref{cor:concentration_heights_asymptotics_n},
+%\[
+%	\Exp{N_{\text{box}}(k_n)} = (1+o(1)) \alpha n \int_{0}^\infty \rho(y,k_n) e^{-\alpha y} \dd y 
+%	= (1+\smallO{1}) n p_{k_n}.
+%\]
+%Since $\Exp{T_{\text{box}}(y_0)\ind{\text{deg}(y_0) = k_n}} \le \binom{k_n}{2}$, and Another concentration of heights argument yields
+%\[
+%	\int_0^{R} \Exp{T_{\text{box}}(y_0)} \rho_{\text{box}}(y_0,k_n) \alpha e^{-\alpha y_0} \dd y_0
+%	= (1 + \smallO{1}) \int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y_0)} \rho(y_0,k_n) \alpha e^{-\alpha y_0} \dd y_0
+%\]
+%and hence
+%\begin{equation}\label{eq:approx_c_ast_Gbox}
+%	c^\ast(k_n, \Gbox)  = (1 + \smallO{1})\frac{1}{p_{k_n}} \int_{\Kcal_{C}(k_n)} \binom{k_n}{2}^{-1} \Exp{T_{\text{box}}(y_0)} \rho(y_0,k_n) \alpha e^{-\alpha y_0} \dd y_0.
+%\end{equation}
+
+Comparing~\eqref{eq:alt_gamma_kn} and~\eqref{eq:alt_c_ast_kn}, we conclude that to prove Proposition~\ref{prop:convergence_average_clustering_P_n} it is enough to show that
+\begin{equation}\label{eq:triangle_diff_main_term}
+	 \left|\int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y) - T_\infty(y)}
+	\rho(y,k) \alpha e^{-\alpha y} \, d y \right|
+	= \smallO{s(k_n)p_{k_n}k_n^2},
+\end{equation}
+which means we have to compute the expected difference in triangles between both models.
+
+%it follows that
+%\[
+%	\Exp{T_{\text{box}}(p_0)} = \frac{1}{2}\iint_{\Rcal^2} T_{\text{box}}(p_0,p_1,p_2)
+%	f(x_1,y_1) f(x_1,y_1) \, dx_1 \, dx_2 \, dy_1 \, dy_2,
+%\]
+%
+%\TM{ $p$ is supposed to be $p_0$ I assume. }\PvdH{Indeed. It has been corrected.}
 
@@
 
-We now turn to the task of calculating the expected number of triangles of a node at height $y$, for both the infinite model and the finite box model.
-Recall that we added a typical point $p_0 = (0,y)$, with exponentially distributed height to the Poisson Point Process.
-Then if we define
-\[
-	T_{\Pcal,n}(p) = \sum^{\ne}_{p_1, p_2 \in \Pcal_n \setminus p} T_{\Pcal,n}(p,p_1,p_2)
-\]
-where
-\[
-	T_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_1)}.
-\]
-it follows that
-\[
-	\Exp{T_{\Pcal,n}(p_0)} = \frac{1}{2}\iint_{\Rcal^2} T_{\Pcal,n}(p_0,p_1,p_2)
-	f(x_1,y_1) f(x_1,y_1) \, dx_1 \, dx_2 \, dy_1 \, dy_2,
-\]
-
-\TM{ $p$ is supposed to be $p_0$ I assume. }\PvdH{Indeed. It has been corrected.}
-The difference between the indicator $\ind{p_1 \in \BallPon{p}}$ in the finite box model and $\ind{p_1 \in \BallPo{p}}$ is that in $\Gbox$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$ and we stop at height $y = R_n$.
-It is clear that for any $0 \le y \le R_n$ we have that $\BallPon{p_0} = \BallPo{p_0} \cap \Rcal$.
+To analyze $T_{\text{box}}(y_0) - T_\infty(y_0)$ we first reiterate that the difference between the indicator $\ind{p_1 \in \BallPon{p}}$ in the finite box model and $\ind{p_1 \in \BallPo{p}}$ is that in $\Gbox$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$ and we stop at height $y = R_n$.
+It is clear that for any $p = (x,y)$ with $0 \le y \le R_n$ we have that $\BallPon{p} = \BallPo{p} \cap \Rcal$.
 However, when we take another point $p^\prime \in \BallPon{p}$ then it could happen that there are points in the intersection $\BallPon{p} \cap \BallPon{p^\prime}$ that are not in $\BallPo{p} \cap \BallPo{p^\prime}$.
-Let us denote this region by $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$.
+Let us denote this region by $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$, see Figure~\ref{fig:comparing_triangles_diff_intersections} for an example of this region.
 Then, any $p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ creates a triangle with $p$ and $p^\prime$ in $\Gbox$ that is not present in $\Ginf$.
 
-Define
-\begin{equation}\label{eq:def_tilde_triangle_indicator}
-	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal}
+The next result, which is crucial for the proof of Proposition~\ref{prop:convergence_average_clustering_P_n}, computes the expected measure of $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ with respect to $p^\prime$.
+
+\begin{lemma}\label{lem:clustering_error_T_term}
+Let $p_0 = (0,y)$ with $y \in \Kcal_{C}(k_n)$. Then for some $C > 0$, as $n \to \infty$,
+\[
+	\int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)\right) f(x_1,y_1) 
+	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
+\]
+\end{lemma}
+
+The proof of the lemma is not difficult but cumbersome, since it involves computing many different integrals.
+We postpone this proof till the end of this section and proceed with the main goal, proving Proposition~\ref{prop:convergence_average_clustering_P_n}.
+
+First we state a small lemma about the scaling of $s(k_n)$ that will be very useful.
+
+\begin{lemma}\label{lem:scaling_s_alpha}
+Let $s(k_n)$ be as defined in \eqref{eq:def_scaling_function}. Then for any $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$,
+\[
+	n^{-(2\alpha - 1)} = \smallO{s(k_n)}.
+\]
+\end{lemma}
+
+\begin{proof}
+First let $\frac{1}{2} < \alpha < \frac{3}{4}$. Then
+\[
+	n^{-(2\alpha - 1)}s(k_n)^{-1} = n^{-(2\alpha -1)}k_n^{4\alpha - 2}
+	= \smallO{n^{-(2\alpha - 1) + \frac{4\alpha - 2}{2\alpha + 1}}} 
+	= \smallO{n^{-\frac{4\alpha^2 - 4\alpha + 1}{2\alpha + 1}}}
+	= \smallO{1},
+\]
+since $4\alpha^2 - 4\alpha + 1 > 0$ for all $\alpha > \frac{1}{2}$. Similarly, for $\alpha \ge \frac{3}{4}$ we have
+that $4\alpha^2 > 2$ and hence,
+\[
+	n^{-(2\alpha - 1)} s_{\alpha}(k_n) = \smallO{n^{-(2\alpha - 1)} k_n} = \smallO{n^{-\frac{4\alpha^2 - 2}{2\alpha + 1}}}
+	= \smallO{1}.
+\]
+\end{proof}
+
+We now proceed with proving the main result of this section.
+
+\begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]
+
+Let us write $\Rcal^\prime := \R \times \R_+ \setminus \Rcal$ and let $p_0 = (0,y)$ denote the typical point. Then
+\begin{align*}
+	\left|T_{\text{box}}(p_0) - T_{\infty}(p_0)\right| 
+	&= \sum_{p_1, p_2 \in \Pcal }^{\ne} \ind{p_1 \in \BallPon{p_0}} 
+		\ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0, p_1)} 
+		+ \sum_{p_1, p_2 \in \Pcal \cap \Rcal^\prime}^{\ne} T_{\infty}(p_0,p_1,p_2),
+\end{align*}
+so that by the Campbell-Mecke formula
+\begin{align*}
+	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right|
+	&\le \int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)\right) f(x_1,y_1) 
+		\dd x_1 \dd y_1\\
+	&\hspace{10pt}+ \int_{\Rcal^\prime}\int_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
+		\dd x_2 \dd y_2 \dd x_1 \dd y_1. 
+\end{align*}
+
+\TM{ in the 1st integral we could have restricted to the ball of $p$, and possibly saved a lot.
+Does that not help?
+}\PvdH{the first integral is taken care of by another Lemma so it does not matter I think.}
+The first integral was taken care of in Lemma \ref{lem:clustering_error_T_term}. For the second integral we have
+\begin{align*}
+	&\hspace{-30pt}\iint_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
+		\dd x_2 \dd y_2 \dd x_1 \dd y_1\\
+	&\le \left(\int_{\Rcal^\prime} \ind{p_1 \in \BallPo{p_0}} f(x_1,y_1) \dd x_1 \dd y_1\right)^2
+		= \bigO{\left(e^{y/2} \int_{R_n}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}\\
+	&= \bigO{e^{y} e^{-(2\alpha-1)R_n}} = \bigO{e^y n^{-(4\alpha - 2)}}.
+\end{align*}
+%\TM{ Typo : $f_{\mu, \nu}$? Also give more details how line 3 follows. }
+We thus we conclude that,
+\begin{equation}\label{eq:triangle_count_diff_scaling}
+	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| = \bigO{y n^{-(2\alpha - 1)} + n^{-(4\alpha-2)} e^{y}}
+	= \bigO{n^{-(4\alpha-2)} e^{y}}.
 \end{equation}
-Then
-\[
-	\sum_{p_1,p_2 \in \Pcal_n}^{\ne} T_{\Pcal,n}(p_0,p_1,p_2) - \widetilde{T}_{\Pcal,n}(p_0,p_1,p_2)
-	= \sum_{p_1,p_2 \in \Pcal_n}^{\ne} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)},
-\]
-\TM{ Note you cannot really force/assume $p_0 = (0,y)$ is in your PPP $\Pcal_n$.
+
+Therefore, since $e^{y} = \bigO{1} k_n^2$ on $\Kcal_C(k_n)$, 
+\begin{align*}
+	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} \rho(y,k_n) \left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| 
+		e^{-\alpha y_0} \dd y_0\\
+	&= \bigO{1} n^{-(4\alpha - 2)} k_n^2 \int_{0}^\infty \rho(y_0,k_n) e^{-\alpha y_0} \dd y_0\\
+	&= \bigO{1} n^{-(4\alpha - 2)} k_n^2 p_{k_n} = \smallO{s(k_n) p_{k_n} k_n^2},
+\end{align*}
+%\TM{ Typo : $e^{-\alpha}$ }
+where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. This establishes~\eqref{eq:triangle_diff_main_term} and hence finishes the proof.
+%
+% \TM{ Also justify penultimate step! }\PvdH{What do you mean?}
+%To finish the argument we observe that
+%\begin{align*}
+%	\int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha} \dd y
+%	&= \bigT{1} \Exp{N_{\infty}(k_n)} \gamma(k_n) = \bigT{ s(k_n) k_n^{-(2\alpha + 1)}}.
+%\end{align*}
+\end{proof}
+
+%Define
+%\begin{equation}\label{eq:def_tilde_triangle_indicator}
+%	\widetilde{T}_{\text{box}}(p_0,p_1,p_2) = \ind{p_1 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal,n}(p_0)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal}
+%\end{equation}
+%Then
+%\[
+%	\sum_{p_1,p_2 \in \Pcal_n}^{\ne} T_{\text{box}}(p_0,p_1,p_2) - \widetilde{T}_{\text{box}}(p_0,p_1,p_2)
+%	= \sum_{p_1,p_2 \in \Pcal_n}^{\ne} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)},
+%\]
+%where the sums are over all distinct pairs $(p_1, p_2) \in \Pcal_n$.
+
+%\TM{ Note you cannot really force/assume $p_0 = (0,y)$ is in your PPP $\Pcal_n$.
 (The summation over $\Pcal_n \setminus (0,y)$ suggests this is what you do.) For taking the expectation of sort of thing, Palm theory / Mecke are used typically.
@@
 Since we now consider the point process $\Pcal_n \cup p_0$ the above summation is over $\Pcal_n$.}
-where the sums are over all distinct pairs $(p_1, p_2) \in \Pcal_n$.
+
+%\TM{ Some words spelling this out would help. I don't find it easy to see. Also, in general I think one should avoid saying things like "the proof of such-and-such also gives .." }
+\subsection{Counting missing triangles}
+
+We now come back to computing the expected number of triangles attached to node at height $y$ in $\Gbox$ that are not present in $\Ginf$.
 
@@
 
+Recall that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ denotes the region of points which form triangles with $p$ and $p^\prime$ in $\Gbox$ but not in $\Ginf$.
 Figure \ref{fig:comparing_triangles_diff_intersections} shows an example of a configuration where $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime) \ne \emptyset$.
@@
 Note that these functions describe the boundaries of the ball $\BallPon{p}$.
-In particular, $p^\prime = x^\prime, y^\prime) \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
+In particular, $p^\prime = (x^\prime, y^\prime) \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
 
@@
 I have updated the text to better reflect this.}
-There are two important points in the box $\Rcal$.
+For this case there are two important points in the box $\Rcal$.
 These are the intersection between the left boundary of $p^\prime$ and the right boundary of $p^\prime$, as it continues from the left side of the box, and the left boundary of $p$.
@@
 \] 
-This solution is $\frac{x^\prime - \pi e^{R_n/2}}{1 + e^{(y^\prime - y)/2}}$ and again $\hat{y}(p,p^\prime)$ is obtained by plugging the solution into either left or right hand side of the equation, yielding $\hat{y}(p,p^\prime) = 2 \log\left(\frac{\pi e^{R_n/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)$.
+This solution is $\frac{x^\prime - \pi e^{R_n/2}}{1 + e^{(y^\prime - y)/2}}$ and again $\hat{y}(p,p^\prime)$ is obtained by plugging the solution into either the left or right hand side of the equation, yielding $\hat{y}(p,p^\prime) = 2 \log\left(\frac{\pi e^{R_n/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)$.
 
@@
 It holds that $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$ if and only if $y^\prime < b^\ast_p(x^\prime)$ and hence we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$ for all $p^\prime \in \Rcal$ for which $y^\prime \ge b^\ast_p(x^\prime)$.
-We also not that when $y^\prime = b^\ast_p(x^\prime)$ the two points $(x^\ast(p^\prime), y^\ast(p^\prime))$ and $(\hat{x}(p,p^\prime),\hat{y}(p,p^\prime))$ coincide.
+We also note that when $y^\prime = b^\ast_p(x^\prime)$ the two points $(x^\ast(p^\prime), y^\ast(p^\prime))$ and $(\hat{x}(p,p^\prime),\hat{y}(p,p^\prime))$ coincide.
 
@@
 
-This analysis allows us to compute the expected difference in the number of triangles for $\Pcal$ and $\Pcal_n$, for a node with height $y$.
-
-\begin{lemma}\label{lem:clustering_error_T_term}
-Let $p_0 = (0,y)$ with $y \in \Kcal_{C}(k_n)$. Then for some $C > 0$, as $n \to \infty$,
-\[
-	\int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)\right) f(x_1,y_1) 
-	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
-\]
-\end{lemma}
-
-The proof of the lemma is not difficult but cumbersome, since it involves computing many different integrals.
-We postpone this proof till the end of this section and proceed with the main goal, proving Proposition~\ref{prop:convergence_average_clustering_P_n}.
-But first we state a small lemma about the scaling of $s(k_n)$ that will be very useful.
-
-\begin{lemma}\label{lem:scaling_s_alpha}
-Let $s(k_n)$ be as defined in \eqref{eq:def_scaling_function}. Then for any $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$,
-\[
-	n^{-(2\alpha - 1)} = \smallO{s(k_n)}.
-\]
-\end{lemma}
-
-\begin{proof}
-First let $\frac{1}{2} < \alpha < \frac{3}{4}$. Then
-\[
-	n^{-(2\alpha - 1)}s(k_n)^{-1} = n^{-(2\alpha -1)}k_n^{4\alpha - 2}
-	= \smallO{n^{-(2\alpha - 1) + \frac{4\alpha - 2}{2\alpha + 1}}} 
-	= \smallO{n^{-\frac{4\alpha^2 - 4\alpha + 1}{2\alpha + 1}}}
-	= \smallO{1},
-\]
-since $4\alpha^2 - 4\alpha + 1 > 0$ for all $\alpha > \frac{1}{2}$. Similarly, for $\alpha \ge \frac{3}{4}$ we have
-that $4\alpha^2 > 2$ and hence,
-\[
-	n^{-(2\alpha - 1)} s_{\alpha}(k_n) = \smallO{n^{-(2\alpha - 1)} k_n} = \smallO{n^{-\frac{4\alpha^2 - 2}{2\alpha + 1}}}
-	= \smallO{1}.
-\]
-\end{proof}
-
-\begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]
-
-Let $\mathrm{deg}_{\text{box}}(y)$ denote the number of nodes in the ball $\BallPon{y}$ (degree of typical node at height $y$) and similarly $\mathrm{deg}_n(y)$ is the number of nodes in $\BallHyp{y}$.
-Recall that
-\[
-	\Exp{c^\ast(k_n; \Gbox)} = \frac{\int_{\Rcal} \Exp{\ind{\mathrm{deg}_{\text{box}}(y) = k_n} T_{\Pcal,n}(y)} f(x,y) \dd x \dd y}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}},
-\]
-and the definition of $\Kcal_{C,n}(k_n)$
-\[
-	\Kcal_{C,n}(k_n) = \left\{ (x,y) \in \Rcal \, : \, \frac{k_n - C k_n}{\xi} \le e^{\frac{y}{2}}
-		\le \frac{k_n + C \kappa_n}{\xi} \right\},
-\]
-where for $k_n \to \infty$ we defined $\kappa_n := \sqrt{k_n \log(k_n)}$.
-
-Since 
-\[
-	\Exp{N_{\text{box}}(k_n)} = \int_{\Rcal} \rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y,
-\]
-the Corollary~\ref{cor:concentration_argument_other_models}, using the second statement of Lemma~\ref{lem:concentration_argument_rho_approximation}, implies
-\[
-	\Exp{N_{\text{box}}(k_n)} = (1+o(1)) \alpha n \int_{0}^\infty \rho(y,k_n) e^{-\alpha} \dd y 
-	= (1+\smallO{1}) n \Exp{N_{\infty}(k_n)}.
-\]
-Moreover, since $\Exp{\ind{\mathrm{deg}_n(y)(y) = k_n} T_{\Pcal,n}(y)} \le \rho_{\text{box}}(y,k_n) k_n^2$ a concentration of heights argument (cf.
-first statement of Lemma~\ref{lem:concentration_argument_rho_approximation}) yields
-\begin{align*}
-	&\hspace{-30pt}\int_{\Rcal} \Exp{\ind{\mathrm{deg}_n(y) = k_n} T_{\Pcal,n}(y)} 
-		f(x,y) \dd x \dd y\\
-	&= (1+\smallO{1})\int_{\Kcal_{C,n}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{T_{\Pcal,n}(y)} f(x,y) \dd x \dd y\\
-	&= (1 + \smallO{1}) \alpha n \int_{a_n^-}^{a_n^+} \rho_{\text{box}}(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha} \dd x \dd y,
-\end{align*}
-with $a_n^\pm = 2\log\left(\frac{(k_n \pm C \kappa_n) \wedge \xi_{\alpha, \nu}}{\xi}\right)$. %\TM{ again, this def has to be adapted. } 
-Next we note that for $a_n^- \le y \le a_n^+$,
-\begin{equation}\label{eq:relation_E_T_Pcal_vs_Delta_P}
-	\Exp{T_\Pcal(y)} = \frac{\Mu{\BallPo{y}}^2}{2} P(y) = (1+\smallO{1}) \binom{k_n}{2} P(y)
-\end{equation}
-and hence it now suffices to show that
-\[
-	\binom{k_n}{2}^{-1}\int_{a_n^-}^{a_n^+} \rho_{\text{box}}(y,k_n) \Exp{T_{\Pcal,n}(y)} e^{-\alpha y} \dd y
-	= (1+\smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha y} \dd y. 
-\]
-
-We do this in two stages. First note that by a concentration of heights argument
-\begin{equation}\label{eq:transition_clustering_main_term}
-	\int_{a_n^-}^{a_n^+} \rho_{n}(y,k_n) P(y) e^{-\alpha y} \dd y
-	= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha y} \dd y.
-\end{equation}
-It therefore remains toshow that
-\begin{equation}\label{eq:transition_clustering_error_term}
-	\binom{k_n}{2}^{-1} \int_{a_n^-}^{a_n^+} \rho_{\text{box}}(y,k_n) \left|\Exp{T_{\Pcal,n}(y) - T_{\Pcal}(y)}\right| 
-	e^{-\alpha y} \dd y
-	= \smallO{1} \int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha y} \dd y.
-\end{equation}
-
-For this we write
-\begin{align*}
-	\left|T_{\Pcal,n}(p) - T_{\Pcal}(p)\right| = \sum_{p_1, p_2 \in \Rcal} \ind{p_1 \in \BallPon{p}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p, p_1)} + \sum_{p_1, p_2 \in \Rcal \setminus \Rcal} T_{\Pcal}(p,p_1,p_2)
-\end{align*}
-so that by the Campbell-Mecke formula
-\begin{align*}
-	\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right|
-	&\le \int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f(x_1,y_1) 
-		\dd x_1 \dd y_1\\
-	&\hspace{10pt}+ \BL{\int_{\Rcal \setminus \Rcal}\int_{\Rcal \setminus \Rcal}} T_{\Pcal}(p,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
-		\dd x_2 \dd y_2 \dd x_1 \dd y_1. 
-\end{align*}
-
-\TM{ in the 1st integral we could have restricted to the ball of $p$, and possibly saved a lot.
-Does that not help?
-}\PvdH{the first integral is taken care of by another Lemma so it does not matter I think.}
-The first integral was taken care of in Lemma \ref{lem:clustering_error_T_term}. For the second integral we have
-\begin{align*}
-	&\hspace{-30pt}\iint_{\Rcal \setminus \Rcal} T_{\Pcal}(p,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
-		\dd x_2 \dd y_2 \dd x_1 \dd y_1\\
-	&\le \left(\int_{\Rcal \setminus \Rcal} \ind{p_1 \in \BallPo{p}} f(x_1,y_1) \dd x_1 \dd y_1\right)^2
-		= \bigO{\left(e^{y/2} \int_{R_n}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}\\
-	&= \bigO{e^{y} e^{-(2\alpha-1)R_n}} = \bigO{e^y n^{-(4\alpha - 2)}},
-\end{align*}
-%\TM{ Typo : $f_{\mu, \nu}$? Also give more details how line 3 follows. }
-from which we conclude that
-\begin{equation}\label{eq:triangle_count_diff_scaling}
-	\left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| = \bigO{y n^{-(2\alpha - 1)} + n^{-(4\alpha-2)} e^{y}}
-	= \bigO{n^{-(4\alpha-2)} e^{y}}.
-\end{equation}
-Therefore, since $e^{y} = \bigO{1} k_n^2$ on $\Kcal_C(k_n)$, 
-\begin{align*}
-	&\hspace{-30pt}\binom{k_n}{2}^{-1}\int_{a_n^-}^{a_n^+} \rho(y,k_n) \left|\Exp{T_{\Pcal,n}(p) - T_{\Pcal}(p)}\right| 
-		e^{-\alpha y} \dd y\\
-	&= \bigO{1} n^{-(4\alpha - 2)} \int_{0}^\infty \rho(y,k_n) e^{-\alpha y} \dd y\\
-	&= \bigO{1} n^{-(4\alpha - 2)} k_n^{-(2\alpha + 1)} = \smallO{s(k_n) k_n^{-(2\alpha + 1)} },
-\end{align*}
-%\TM{ Typo : $e^{-\alpha}$ }
-where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. \TM{ Also justify penultimate step! }\PvdH{What do you mean?}
-To finish the argument we observe that
-\begin{align*}
-	\int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha} \dd y
-	&= \bigT{1} \Exp{N_{\infty}(k_n)} \gamma(k_n) = \bigT{ s(k_n) k_n^{-(2\alpha + 1)}}.
-\end{align*}
-\end{proof}
-
-From the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} we can extract the following corollary, which will be useful later on in Section~\ref{sec:concentration_c_P_n}.
-
-\begin{corollary}\label{cor:adjusted_triangle_counting_P_n}
-Uniformly for all $y \in \Kcal_C(k_n)$, as $n \to \infty$
-\[
-	\Exp{\widetilde{T}_{\Pcal,n}(y)} = (1+\smallO{1})\Exp{T_\Pcal(y)},
-\]
-where
-\[
-	\widetilde{T}_{\Pcal,n}(y) = \sum_{(p_1, p_2) \in \Pcal}^{\ne} 
-		\ind{p_1 \in B_{\Pcal,n}(y)}\ind{p_2 \in B_{\Pcal,n}(y)}\ind{p_2 \in B_{\Pcal}(p_1) \cap \Rcal}.
-\]
-
-In particular,
-\[
-	\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(y)} f(x,y) \dd x \dd y
-	= (1+\smallO{1}) \int_{\Rcal} \rho(y,k_n) P(y) f(x,y) \dd x \dd y. 
-\]
-\end{corollary}
-
-\begin{proof}
-First we note that equation~\eqref{eq:triangle_count_diff_scaling} implies that for $y \in \Kcal_C(k_n)$
-\[
-	\Exp{\left|\widetilde{T}_{\Pcal,n}(y) - T_\Pcal(y)\right|} = \bigO{n^{-(4\alpha - 2)}k_n^2}.
-\]
-Next, equation~\ref{eq:relation_E_T_Pcal_vs_Delta_P} together with Proposition~\ref{prop:asymp} yield
-\[
-	\Exp{T_\Pcal(y)} = (1+\smallO{1})\binom{k_n}{2} P(y) = \bigT{k_n^2 s(k_n)},
-\]
-on $\Kcal_{C}(k_n)$, with $s(k)$ defined by~\eqref{eq:def_scaling_function}. By Lemma~\ref{lem:scaling_s_alpha} we now have that for all $y \in \Kcal_{C}(k_n)$
-\[
-	n^{-(4\alpha - 2)}k_n^2 = \smallO{k_n^2 s(k_n)} = \smallO{\Exp{T_\Pcal(y)}}
-\]
-and hence
-\[
-	\Exp{\widetilde{T}_{\Pcal,n}(y)} = \Exp{T_\Pcal(y)} + \bigO{\Exp{\left|\widetilde{T}_{\Pcal,n}(y) - T_\Pcal(y)\right|}}
-	= (1+\smallO{1})\Exp{T_\Pcal(y)}.
-\]
-
-Using this we derive the second statement as follows 
-\begin{align*}
-	&\hspace{-30pt}\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(y)} 
-		f(x,y) \dd x \dd y\\
-	&=(1 + \smallO{1})\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{T_\Pcal(y)} 
-		f(x,y) \dd x \dd y\\
-	&=(1 + \smallO{1})\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) P(y)f(x,y) \dd x \dd y \\
-	&=(1 + \smallO{1})\int_{\Rcal} \rho_{\text{box}}(y,k_n) P(y)f(x,y) \dd x \dd y
-\end{align*}
-where the third line is due to equation~\eqref{eq:relation_E_T_Pcal_vs_Delta_P} and the last line follows by a concentration of heights argument.
-\end{proof}
-
-%\TM{ Some words spelling this out would help. I don't find it easy to see. Also, in general I think one should avoid saying things like "the proof of such-and-such also gives .." }
-\subsection{Counting missing triangles}
-
-We now come back to computing the expected number of triangles attached to node at height $y$ in $\Gbox$ that are not present in $\Ginf$.
+This analysis allows us to compute the expected difference in the number of triangles for the finite box model and the infinite model, for a typical node with height $y$, i.e.
+prove Lemma~\ref{lem:clustering_error_T_term}.
 

### 2019-02-21 clustering_infinite_model.tex
no more \Delta in Section 3

@@
 \begin{align*}
-&\Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
+&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
 s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
@@
 \begin{align*}
-\Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)
-\end{align*}
-Therefore, the desired value of $\lim_{\alpha \rightarrow 1} \Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0))$ is given by
+P(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)
+\end{align*}
+Therefore, the desired value of $\lim_{\alpha \rightarrow 1} P(y_0(z_0))$ is given by
 \begin{align*}
@@
 \]
-and in particular the function $P(y)$. We therefore start with establishing the asymptotic behavior of the latter.
+and in particular the function $P(y)$.
+We therefore start with establishing the asymptotic behavior of the latter.
+First we combine~\eqref{eq:degree_distribution_P_asymptotics} and~\eqref{eq:general_integral_rho_y_k} to obtain the following scaling result
+\begin{equation}\label{eq:general_clustering_integral_scaling}
+	\frac{\int_0^\infty e^{-\beta y} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	\sim \xi_{\alpha, \nu}^{2\beta} k^{-2\beta}.
+\end{equation}
 

### 2019-02-22 concentration.tex
revised section 8.1.

--- 2019-02-21 concentration.tex
@@
 
-In this section we establish a concentration result for the local clustering function $c^\ast(k; \Gbox)$ in the finite model $\Gbox$.
+In this section we establish a concentration result for the local clustering function $c^\ast(k; \Gbox)$ in the finite box model $\Gbox$.
 Similar to the previous section we will focus on typical points $p = (0,y)$ with $y \in \Kcal_{C}(k_n)$.
@@
 
-Recall the adjusted triangle count function \eqref{eq:def_tilde_triangle_indicator}
-\[
-	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal}.
-\]
-and the concentration set
-\[
-	\Kcal_C(k_n,n) = \left\{p \in \Rcal : \frac{k_n - C \kappa_n}{\xi} \vee 0 \le e^{\frac{y}{2}}
-		\le \frac{k_n + C \kappa_n}{\xi} \right\},
-\]
-with
-\[
-	\kappa_n = \sqrt{k_n \log(k_n)}.
-\]
-We will define the corresponding triangle degree function
+Recall the adjusted triangle count function
+\[
+	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus p_0}^{\ne} 
+		\widetilde{T}_{\text{box}}(p_0,p_1,p_2).
+\]
+where
+\[
+	\widetilde{T}_{\text{box}}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal},
+\]
+and recall the definition of $\Kcal_{C,n}(k_n)$
+\[
+	\Kcal_{C,n}(k_n) = \left\{p \in \Rcal : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
+		\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\}.
+\]
+
+Slightly abusing notation, we will define the corresponding triangle degree function
 \begin{equation}\label{eq:def_degree_triangle_count_in_K}
-	\widetilde{T}_{\Pcal,n}(k, C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\Pcal,n}(p),
+	\widetilde{T}_{\text{box}}(k, C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p).
 \end{equation}
-where 
-\[
-	\widetilde{T}_{\Pcal,n}(p) := \sum_{(p_1, p_2) \in \Pcal \setminus p}^{\ne} \widetilde{T}_{\Pcal,n}(p,p_1,p_2),
-\]
-where the sum is over all distinct pairs $(p_1, p_2) \in \Pcal \setminus p$.
-
-Next we note that the second result from Corollary~\ref{cor:adjusted_triangle_counting_P_n} states that
-\begin{equation}\label{eq:asymptotic_equivalence_contraint_triangle_count}
-	\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)} = (1+\smallO{1})\Exp{T_{\Pcal}(k_n)},
-\end{equation}
-so that we can conclude that the main contribution of triangles of degree $k_n$ is given by $\widetilde{T}_{\Pcal,n}(k_n, C)$.
-Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} it suffices to show that $\widetilde{T}_{\Pcal,n}(k_n,C)$ is sufficiently concentrated around its mean.
+The idea is that the main contribution of triangles of degree $k_n$ is given by $\widetilde{T}_{\text{box}}(k_n, C)$.
+Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} it suffices to show that $\widetilde{T}_{\text{box}}(k_n,C)$ is sufficiently concentrated around its mean.
 This is done in the following proposition.
@@
 %
-%We start with the concentration result for $\widetilde{T}_{\Pcal,n}(k_n)$.
-
-\begin{proposition}[Concentration $\widetilde{T}_{\Pcal,n}(k_n,C)$]\label{prop:concentration_tilde_T_P_n}
+%We start with the concentration result for $\widetilde{T}_{\text{box}}(k_n)$.
+
+\begin{proposition}[Concentration $\widetilde{T}_{\text{box}}(k_n,C)$]\label{prop:concentration_tilde_T_P_n}
 Let $\alpha > \frac{1}{2}$, $\nu > 0$ and let $(k_n)_{n \ge 1}$ be any positive sequence satisfying $k_n = \smallO{n^{\frac{1}{2\alpha+1}}}$. Then for any $C > 0$, as $n \to \infty$,
 \[
-	\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)^2} = \left(1 + \smallO{1}\right)\Exp{\widetilde{T}_{\Pcal,n}(k_n, C)}^2.
+	\Exp{\widetilde{T}_{\text{box}}(k_n,C)^2} = \left(1 + \smallO{1}\right)\Exp{\widetilde{T}_{\text{box}}(k_n, C)}^2.
 \]
@@
 
-We postpone the proof of this proposition postpone till Section \ref{ssec:concentration_tilde_T} and first use it to prove Proposition \ref{prop:concentration_local_clustering_P_n}.
-
-%\begin{lemma}\label{lem:L1_convergence_c_Pcal_n}
-%Let $\nu > 0$, $\alpha > \frac{1}{2}$ and $k_n = o\left(n^{\frac{1}{2\alpha + 1}}\right)$. Then, as $n \to \infty$,
-%\[
-%	\Exp{\left|c^\ast(k_n; \Gbox) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
-%\]
-%\end{lemma}
-%
-%\begin{proof}
-%Let $0 < \delta < 1$ and define the following two events
-%\begin{align*}
-%	A_n &= \left\{\left|N_{\text{box}}(k_n) - \Exp{N_{\text{box}}(k_n)}\right| \le \Exp{N_{\text{box}}(k_n)}^{\frac{1 + \delta}{2}}\right\}\\
-%	B_n &= \left\{\left|N_{\text{box}}(k_n) - \Exp{N_{\text{box}}(k_n)}\right| \le n\right\},
-%\end{align*}
-%so that
-%\[
-%	1 = \ind{A_n} + \ind{A_n^c}\ind{B_n} + \ind{B_n^c}.
-%\]
-%Next we note that on the event $A_n$
-%\[
-%	\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right| 
-%	\le \frac{\Exp{N_{\text{box}}(k_n)}^{\frac{1 + \delta}{2}}}{\Exp{N_{\text{box}}(k_n)}+\Exp{N_{\text{box}}(k_n)}^{\frac{1 + \delta}{2}}}
-%	\le \Exp{N_{\text{box}}(k_n)}^{-\frac{1 - \delta}{2}},
-%\]
-%and on the event $B_n$
-%\[
-%	\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right| 
-%	\le \frac{n}{\Exp{N_{\text{box}}(k_n)} + n} \le 1.
-%\]
-%Therefore we have
-%\begin{align*}
-%	\Exp{\left|c^\ast(k_n; \Gbox) - c_{\Pcal, n}(k_n)\right|}
-%	&= \Exp{c^\ast(k_n; \Gbox)\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right|}\\
-%	&\le \Exp{c^\ast(k_n; \Gbox)\ind{A_n}}\Exp{N_{\text{box}}(k_n)}^{-\frac{1 - \delta}{2}} \\
-%	&\hspace{10pt}+ \Exp{c^\ast(k_n; \Gbox)\ind{A_n^c}\ind{B_n}} \\
-%	&\hspace{10pt}+ \Exp{c^\ast(k_n; \Gbox)\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right|\ind{B_n^c}}
-%\end{align*}
-%Since $\Exp{N_{\text{box}}(k_n)} \to \infty$, the first term is clearly $\smallO{\Exp{c^\ast(k_n; \Gbox)}}$. For the third term we have
-%\begin{align*}
-%	\Exp{c^\ast(k_n; \Gbox)\left|\frac{\Exp{N_{\text{box}}(k_n)}}{N_{\text{box}}(k_n)} - 1\right|\ind{B_n^c}} 
-%	&= \bigO{\Prob{B_n^c}}
-%		= \bigO{\Prob{\left|N_{\text{box}}(k_n) - \Exp{N_{\text{box}}(k_n)}\right| > n}}\\
-%	&= \bigO{e^{-\frac{n^2}{\Exp{N_{k_n}} + n}}} = \bigO{e^{-n}} = \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
-%\end{align*}
-%Hence we are left to show that
-%\begin{equation}\label{eq:L1_convergence_second_term}
-%	\Exp{c^\ast(k_n; \Gbox)\ind{A_n^c}\ind{B_n}} = \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
-%\end{equation}
-%By writing
-%\begin{align*}
-%	c^\ast(k_n; \Gbox) = \frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
-%	+ \frac{T_{\Pcal,n}(k_n,\varepsilon)- \widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
-%\end{align*}
-%and using Lemma~\ref{lem:clustering_error_T_term} we get
-%\begin{align*}
-%	\Exp{c^\ast(k_n; \Gbox)\ind{A_n^c}\ind{B_n}}
-%	&\le \Exp{\frac{(1+\smallO{1})\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
-%		\ind{A_n^c}} + \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
-%\end{align*}
-%For the last step we use H\"{o}lder's inequality and Proposition \ref{prop:concentration_tilde_T_P_n} to get
-%\begin{align*}
-%	\Exp{\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\ind{A_n^c}}
-%	&\le \Exp{\left(\frac{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}
-%		{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right)^2}^{\frac{1}{2}} \Prob{A_n^c}^{\frac{1}{2}}\\
-%	&= \left(1 + \smallO{1}\right) 	
-%		\frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
-%		\Prob{A_n^c}^{\frac{1}{2}}\\
-%	&= \bigO{\Exp{c^\ast(k_n; \Gbox)}}\Prob{A_n^c}^{\frac{1}{2}} = \smallO{\Exp{c^\ast(k_n; \Gbox)}},
-%\end{align*}
-%since $\Prob{A_n} = o(1)$. This establishes \eqref{eq:L1_convergence_second_term} and hence we conclude that
-%\[
-%	\Exp{\left|c^\ast(k_n; \Gbox) - c_{\Pcal, n}(k_n)\right|} = \smallO{\Exp{c_{\Pcal,n}(k_n)^\ast}}.
-%\]
-%\end{proof}
+We postpone the proof of this proposition till Section~\ref{ssec:concentration_tilde_T} and first use it to prove Proposition~\ref{prop:concentration_local_clustering_P_n}.
 
 \begin{proof}[Proof of Proposition \ref{prop:concentration_local_clustering_P_n}]
-Again, we write
-\begin{align*}
-	c^\ast(k_n; \Gbox) = \frac{\widetilde{T}_{\Pcal,n}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
-	+ \frac{\left(T_{\Pcal,n}(k_n)-\widetilde{T}_{\Pcal,n}(k_n,C)\right)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}},
-\end{align*}
-so that by~\eqref{eq:asymptotic_equivalence_contraint_triangle_count},
-\begin{equation}\label{eq:concentration_local_clustering_P_n_main}
-	\Exp{c^\ast(k_n; \Gbox)} = \frac{\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
-	+ \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
-\end{equation}
-%Therefore, by Lemma \ref{lem:L1_convergence_c_Pcal_n},
-%\begin{align*}
-%	\Exp{\left|c_{\Pcal,n}(k_n) - \Exp{c^\ast(k_n; \Gbox)}\right|}
-%	&\le \Exp{\left|c^\ast(k_n; \Gbox) - \Exp{c^\ast(k_n; \Gbox)}\right|}
-%		+ \Exp{\left|c_{\Pcal,n}(k_n) - c^\ast(k_n; \Gbox)\right|}\\
-%	&= \frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,\varepsilon) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,\varepsilon)}\right|}}
-%		{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}} + \smallO{\Exp{c^\ast(k_n; \Gbox)}}.
-%		\numberthis \label{eq:concentration_local_clustering_P_n_term1}
-%\end{align*}
-Next, we use Proposition \ref{prop:concentration_tilde_T_P_n} to obtain
-\begin{align*}
-	\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,C) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}\right|}
-	&\le \left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)^2} 
-		- \Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}^2\right)^{\frac{1}{2}}\\
-	&= \smallO{\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}}.
+We bound the expectation as follows,
+\begin{align*}
+	\Exp{\left|c^\ast(k_n; \Gbox) - \Exp{c^\ast(k_n; \Gbox)}\right|} 
+	&\le \frac{\Exp{\left|\widetilde{T}_{\text{box}}(k_n,C) - \Exp{\widetilde{T}_{\text{box}}(k_n,C)}\right|}}
+		{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\\
+	&\hspace{10pt} + 2 \Exp{\left|c^\ast(k_n; \Gbox) - \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right|}.
+\end{align*}
+We will show that both terms are $\smallO{s(k_n)}$.
+
+First we note that $\ind{p_2 \in \BallPo{p_1} \cap \Rcal} \le \ind{p_2 \in \BallPon{p_1}}$ and hence $\widetilde{T}_{\text{box}}(p) \le T_{\text{box}}(p)$. This implies that
+\[
+	 \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}} \le c^\ast(k_n; \Gbox). 
+\]
+and therefore
+\[
+	\Exp{\left|c^\ast(k_n; \Gbox) - \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right|}
+	= \Exp{c^\ast(k_n; \Gbox)} 
+	- \frac{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}.
+\]
+For the expectation of $\widetilde{T}_{\text{box}}(k_n,C)$ we use that 
+\[
+	\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n}
+= \binom{k_n}{2} \Mu{\BallPon{y}}^{-2} \Exp{\widetilde{T}_{\text{box}}(p)},
+\] to get
+\begin{align*}
+	\Exp{\widetilde{T}_{\text{box}}(k_n,C)} 
+	&= \int_{\Kcal_{C,n}(k_n)} \CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n}
+		\rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y\\
+	&= (1+\smallO{1}) \binom{k_n}{2} \int_{\Kcal_{C,n}(k_n)} \Mu{\BallPon{y}}^{-2} \Exp{\widetilde{T}_{\text{box}}(y)}
+		\rho_{\text{box}}(y,k_n) \alpha e^{-\alpha y} \dd y\\
+	&= (1+\smallO{1}) \frac{1}{2} \int_{\Kcal_{C,n}(k_n)} \Exp{\widetilde{T}_{\text{box}}(y)}
+			\rho_{\text{box}}(y,k_n) \alpha e^{-\alpha y} \dd y\\
+	&= (1+\smallO{1}) n \binom{k_n}{2} \int_0^\infty P(y) \alpha e^{-\alpha y} \dd y,
+\end{align*}
+where the last line is due to Corollary~\ref{cor:adjusted_triangle_counting_P_n}. Since $\Exp{N_{\text{box}}(k_n)} = (1+\smallO{1}n p_{k_n}$ it follows that
+\[
+	\frac{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+	= (1+\smallO{1}) \frac{\int_0^\infty P(y) \alpha e^{-\alpha y} \dd y}{p_{k_n}}
+	= (1 + \smallO{1}) \gamma(k_n).
+\]
+On the other hand, Proposition~\ref{prop:convergence_average_clustering_P_n} implies that $\Exp{c^\ast(k_n; \Gbox)} = (1+\smallO{1})\gamma(k_n)$ and thus we conclude that
+\[
+	2\Exp{\left|c^\ast(k_n; \Gbox) - \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right|}
+	= \smallO{s(k_n)}.	
+\]
+
+For the remaining term we use Proposition \ref{prop:concentration_tilde_T_P_n} to obtain
+\begin{align*}
+	\Exp{\left|\widetilde{T}_{\text{box}}(k_n,C) - \Exp{\widetilde{T}_{\text{box}}(k_n,C)}\right|}
+	&\le \left(\Exp{\widetilde{T}_{\text{box}}(k_n,C)^2} 
+		- \Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2\right)^{\frac{1}{2}}\\
+	&= \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}.
 \end{align*}
@@
 \begin{align*}
-	\frac{\Exp{\left|\widetilde{T}_{\Pcal,n}(k_n,C) - \Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}\right|}}
+	\frac{\Exp{\left|\widetilde{T}_{\text{box}}(k_n,C) - \Exp{\widetilde{T}_{\text{box}}(k_n,C)}\right|}}
 		{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
-	&= \smallO{\Exp{c^\ast(k_n; \Gbox)}},
-\end{align*}
-which together with~\eqref{eq:concentration_local_clustering_P_n_main} yields the required result.
+	&= \smallO{\frac{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}}
+	= \smallO{s(k_n)},
+\end{align*}
+which finishes the proof.
 \end{proof}
@@
 \[
-	\widetilde{T}_{\Pcal,n}(k,C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\Pcal,n}(p)
+	\widetilde{T}_{\text{box}}(k,C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p)
 \]
@@
 \[
-	\widetilde{T}_{\Pcal,n}(k,C)^2 = \hspace{-5pt} \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k)}
+	\widetilde{T}_{\text{box}}(k,C)^2 = \hspace{-5pt} \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k)}
 		\hspace{-3pt} \ind{D_{\Pcal,n}(p), \, D_{\Pcal,n}(p^\prime) = k} 
@@
 \[
-	\widetilde{T}_{\Pcal,n}(k, C)^2 = \sum_{a = 0}^1 \sum_{b = 0}^2 I_{a,b}.
+	\widetilde{T}_{\text{box}}(k, C)^2 = \sum_{a = 0}^1 \sum_{b = 0}^2 I_{a,b}.
 \]
@@
 \begin{equation}\label{eq:variance_T_I_00}
-	\Exp{I_{0,0}} = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal,n}(k_n)}^2
+	\Exp{I_{0,0}} = (1+\smallO{1})\Exp{\widetilde{T}_{\text{box}}(k_n)}^2
 \end{equation}
@@
 \begin{equation}\label{eq:variance_T_I_ab}
-	\Exp{I_{a,b}} = \smallO{\Exp{\widetilde{T}_{\Pcal,n}(k_n)}^2}.
+	\Exp{I_{a,b}} = \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n)}^2}.
 \end{equation}
-Note that $J_{b}(p,p^\prime) \le J_{0}(p,p^\prime)$ and, since $I_{1,2} = \widetilde{T}_{\Pcal,n}(k_n,C)$, \eqref{eq:variance_T_I_ab} holds for $I_{1,2}$.
+Note that $J_{b}(p,p^\prime) \le J_{0}(p,p^\prime)$ and, since $I_{1,2} = \widetilde{T}_{\text{box}}(k_n,C)$, \eqref{eq:variance_T_I_ab} holds for $I_{1,2}$.
 
@@
 			\hspace{-7pt} D_{\Pcal,n}(p,p^\prime, k_n-i,k_n- i^\prime) \,
-			\widetilde{T}_{\Pcal,n}(p,p_1,p_2) \widetilde{T}_{\Pcal,n}(p^\prime, p_1^\prime, p_2^\prime)},
+			\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime, p_1^\prime, p_2^\prime)},
 \end{align*}
@@
 %		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)}
-%		\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} 
+%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p)}
+%		\Exp{\widetilde{T}_{\text{box}}(p^\prime)} 
 %		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\Pcal,n}(p)} 
+%	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p)} 
 %		f_{\alpha, \nu}(x,y) \dd x \dd y\right)	
@@
 %\[
-%	\mathcal{J}_1^\ast = \int_{\Rcal^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) 
+%	\mathcal{J}_1^\ast = \int_{\Rcal^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\text{box}}(p,p_1,p_2) 
 %			f(x_1,y_1)	f(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
@@
 %\[
-%	\mathcal{J}_1^\ast = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1 + \smallO{1})\binom{k_n}{2} \Delta_\Pcal(y),
+%	\mathcal{J}_1^\ast = (1+\smallO{1})\Exp{\widetilde{T}_{\text{box}}(p)} = (1 + \smallO{1})\binom{k_n}{2} \Delta_\Pcal(y),
 %\] 
@@
 	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
-		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
 	&= \bigO{\int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}} \rho_{y}(k) 
-		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy}\\
+		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy}\\
 	&= \bigO{k_n^{1+\varepsilon} \binom{k_n}{2} \left(\int_{a_n^-}^{a_n^+} \Delta_{\Pcal}(y^\prime) 
@@
 \end{align*}
-which proves \eqref{eq:I_ab_ast_main}. Here we used that $k_n^{2 + \varepsilon} = \smallO{n}$ and $\Exp{T_{\Pcal,n}(k_n)} = \bigT{n k_n^{-(2\alpha - 1)}s_\alpha(k_n)}$ for the last line.
+which proves \eqref{eq:I_ab_ast_main}. Here we used that $k_n^{2 + \varepsilon} = \smallO{n}$ and $\Exp{T_{\Pcal,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}s_\alpha(k_n)}$ for the last line.
 
@@
 	\Exp{I_{0,0}^\ast} = (1 + \smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{n}(p,p^\prime,k_n, k_n)
-		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f(x,y)
+		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y)
 		f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
@@
 \[
-	\Exp{\widetilde{T}_{\Pcal,n}(p)} = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal}(p)} = (1 + \smallO{1}) \binom{k_n}{2} \Delta_{\Pcal}(y)
+	\Exp{\widetilde{T}_{\text{box}}(p)} = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal}(p)} = (1 + \smallO{1}) \binom{k_n}{2} \Delta_{\Pcal}(y)
 \] 
@@
 	&\hspace{-10pt}(1 + \smallO{1})\int_{\mathcal{E}_\varepsilon(k_n)} \rho_n(p, p^\prime, k_n, k_n)
-		\Exp{\widetilde{T}_{\Pcal,n}(p)}\Exp{\widetilde{T}_{\Pcal,n}(p^\prime)} f(x,y)
+		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y)
 		f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
@@
 		\Delta_{\Pcal}(y) f(x,y) \, dx \, dy\right)^2\\
-	&= (1 + \smallO{1})\left(\Exp{\widetilde{T}_{\Pcal,n}(k_n,C)}\right)^2,
+	&= (1 + \smallO{1})\left(\Exp{\widetilde{T}_{\text{box}}(k_n,C)}\right)^2,
 \end{align*}
@@
 \[
-	T^{(0,1)}_{\Pcal,n}(p,p^\prime) = \sum_{(p_1,p_2) \in 2^{\Pcal_n}} \sum_{p_2^\prime \in \Pcal_n} \widetilde{T}_{\Pcal,n}(p,p_1,p_2) \widetilde{T}_{\Pcal,n}(p^\prime,p_1,p_2^\prime),
+	T^{(0,1)}_{\Pcal,n}(p,p^\prime) = \sum_{(p_1,p_2) \in 2^{\Pcal_n}} \sum_{p_2^\prime \in \Pcal_n} \widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime,p_1,p_2^\prime),
 \]
@@
 \] 
-from which \eqref{eq:variance_T_I_ab} follows since $k_n^4 s_\alpha(k_n)^2 = \bigO{\Exp{\widetilde{T}_{\Pcal,n}(p)} \Exp{\widetilde{T}_{\Pcal,n}(p^\prime)}}$ on $\Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$.
+from which \eqref{eq:variance_T_I_ab} follows since $k_n^4 s_\alpha(k_n)^2 = \bigO{\Exp{\widetilde{T}_{\text{box}}(p)} \Exp{\widetilde{T}_{\text{box}}(p^\prime)}}$ on $\Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$.
 
@@
 \begin{align*}
-	\Exp{\widetilde{T}_{\Pcal,n}(p)}
+	\Exp{\widetilde{T}_{\text{box}}(p)}
 		\bigO{e^{\frac{y^\prime}{2}}\int_{b_n}^{a_n^+} e^{-(\alpha -\frac{1}{2})y_2} \, dy_2}
-	&= \bigO{k_n^{1 - \varepsilon}}\Exp{\widetilde{T}_{\Pcal,n}(p)}
+	&= \bigO{k_n^{1 - \varepsilon}}\Exp{\widetilde{T}_{\text{box}}(p)}
 	= \smallO{k_n^4 s_\alpha(k_n)^2}.
@@
 \[
-	\bigO{e^{\frac{y^\prime}{2}} \Exp{\widetilde{T}_{\Pcal,n}(p)}}
-	= \bigO{k_n \Exp{\widetilde{T}_{\Pcal,n}(p)}} = \smallO{k_n^4 s_\alpha(k_n)^2}.
+	\bigO{e^{\frac{y^\prime}{2}} \Exp{\widetilde{T}_{\text{box}}(p)}}
+	= \bigO{k_n \Exp{\widetilde{T}_{\text{box}}(p)}} = \smallO{k_n^4 s_\alpha(k_n)^2}.
 \]

### 2019-02-22 transition.tex
revised section 8.1.

@@
 To analyze $T_{\text{box}}(y_0) - T_\infty(y_0)$ we first reiterate that the difference between the indicator $\ind{p_1 \in \BallPon{p}}$ in the finite box model and $\ind{p_1 \in \BallPo{p}}$ is that in $\Gbox$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$ and we stop at height $y = R_n$.
-It is clear that for any $p = (x,y)$ with $0 \le y \le R_n$ we have that $\BallPon{p} = \BallPo{p} \cap \Rcal$.
-However, when we take another point $p^\prime \in \BallPon{p}$ then it could happen that there are points in the intersection $\BallPon{p} \cap \BallPon{p^\prime}$ that are not in $\BallPo{p} \cap \BallPo{p^\prime}$.
-Let us denote this region by $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$, see Figure~\ref{fig:comparing_triangles_diff_intersections} for an example of this region.
+This induces a difference in triangle counts between both models.
+To see this, note that for any $p = (x,y)$ with $0 \le y \le R_n$ we have that $\BallPon{p} = \BallPo{p} \cap \Rcal$.
+This means that if $p^\prime, p_2 \in \BallPon{p}$ and $p_2 \in \BallPo{p^\prime} \cap \Rcal$ then $p_2 \in \BallPon{p} \cap \BallPon{p^\prime}$ and hence $(p,p^\prime,p_2)$ form a triangle both in $\Gbox$ and $\Ginf$.
+However, it could happen that there are points in the intersection $\BallPon{p} \cap \BallPon{p^\prime}$ that are not in $\BallPo{p} \cap \BallPo{p^\prime}$.
+Let us denote this region by $\mathcal{T}(p \Delta p^\prime)$, see Figure~\ref{fig:comparing_triangles_diff_intersections} for an example of this region.
 Then, any $p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ creates a triangle with $p$ and $p^\prime$ in $\Gbox$ that is not present in $\Ginf$.
+Finally, any point $p_2 \in \BallPo{p} \cap \BallPo{p6\prime}$ with height $y_2 > R$ creates a triangle with $p, p^\prime$ in $\Ginf$ but not in $\Gbox$.
+
+Let us now define the following triangle count function
+\[
+	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus p_0}^{\ne} 
+		\widetilde{T}_{\text{box}}(p_0,p_1,p_2).
+\]
+where
+\[
+	\widetilde{T}_{\text{box}}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal}.
+\]
+Then $\widetilde{T}_{\text{box}}(p_0)$ only counts those triangles attached to $p_0$ that exist in both $\Gbox$ and $\Ginf$ and thus, by definition of the region $\mathcal{T}(p_0,p_1)$,
+\[
+	T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)
+	= \sum_{p_1, p_2 \in \Pcal }^{\ne} \ind{p_1 \in \BallPon{p_0}} 
+			\ind{p_2 \in \mathcal{T}(p_0, p_1)}.
+\]
+%Thus, $\widetilde{T}_{\text{box}}(p_0)$ only count those triangles $(p_0,p_1,p_2)$ that also exist in $\Ginf$.
+%Observe that the difference between $\widetilde{T}_{\text{box}}(p_0)$ and $T_{\text{box}}(p_0)$ is in the last indicator in $\widetilde{T}_{\text{box}}(p_0,p_1,p_2)$.
+counts those points $p_2$ in the box $\Rcal$ that are in the neighborhood $\BallPo{p_1}$ of $p_1$ in the infinite model.
+Thus, $\widetilde{T}_{\text{box}}(p_0)$ only count those triangles $(p_0,p_1,p_2)$ that also exist in $\Ginf$.
 
@@
 \begin{lemma}\label{lem:clustering_error_T_term}
-Let $p_0 = (0,y)$ with $y \in \Kcal_{C}(k_n)$. Then for some $C > 0$, as $n \to \infty$,
-\[
-	\int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)\right) f(x_1,y_1) 
-	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
-\]
+Let $p_0 = (0,y)$ with $y \in \Kcal_{C}(k_n)$. Then as $n \to \infty$,
+\[
+	\Exp{\left|T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right|}
+	= y \, \bigO{n^{-(2\alpha - 1)}} + e^{y}\,\bigO{n^{-(4\alpha-2)}}.
+\]
+%\[
+%	\int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)\right) f(x_1,y_1) 
+%	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
+%\]
 \end{lemma}
@@
 \begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]
-
-Let us write $\Rcal^\prime := \R \times \R_+ \setminus \Rcal$ and let $p_0 = (0,y)$ denote the typical point. Then
+Let us write $\Rcal^\prime := \R \times \R_+ \setminus \Rcal$ and let $p_0 = (0,y)$ denote the typical point.
+Next we recall that it is enough to show~\eqref{eq:triangle_diff_main_term}, so that in particular we have that $y \in \Kcal_{C}(k_n)$.
+
+Now
 \begin{align*}
 	\left|T_{\text{box}}(p_0) - T_{\infty}(p_0)\right| 
-	&= \sum_{p_1, p_2 \in \Pcal }^{\ne} \ind{p_1 \in \BallPon{p_0}} 
-		\ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0, p_1)} 
+	&= \left|T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right| 
 		+ \sum_{p_1, p_2 \in \Pcal \cap \Rcal^\prime}^{\ne} T_{\infty}(p_0,p_1,p_2),
@@
 	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right|
-	&\le \int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)\right) f(x_1,y_1) 
-		\dd x_1 \dd y_1\\
+	&\le \Exp{\left|T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right|}\\
 	&\hspace{10pt}+ \int_{\Rcal^\prime}\int_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
@@
 }\PvdH{the first integral is taken care of by another Lemma so it does not matter I think.}
-The first integral was taken care of in Lemma \ref{lem:clustering_error_T_term}. For the second integral we have
+The part is taken care of by Lemma~\ref{lem:clustering_error_T_term}. For the other integral we have
 \begin{align*}
@@
 %\TM{ Typo : $f_{\mu, \nu}$? Also give more details how line 3 follows. }
-We thus we conclude that,
+We thus we conclude, using Lemma~\ref{lem:clustering_error_T_term}, that,
 \begin{equation}\label{eq:triangle_count_diff_scaling}
-	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| = \bigO{y n^{-(2\alpha - 1)} + n^{-(4\alpha-2)} e^{y}}
-	= \bigO{n^{-(4\alpha-2)} e^{y}}.
+	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| = \bigO{y n^{-(2\alpha - 1)} + n^{-(4\alpha-2)} e^{y}}.
 \end{equation}
-
-Therefore, since $e^{y} = \bigO{1} k_n^2$ on $\Kcal_C(k_n)$, 
+Therefore, since $y = \bigO{\log(k_n)}$ on $\Kcal_C(k_n)$, 
 \begin{align*}
@@
 		e^{-\alpha y_0} \dd y_0\\
-	&= \bigO{1} n^{-(4\alpha - 2)} k_n^2 \int_{0}^\infty \rho(y_0,k_n) e^{-\alpha y_0} \dd y_0\\
-	&= \bigO{1} n^{-(4\alpha - 2)} k_n^2 p_{k_n} = \smallO{s(k_n) p_{k_n} k_n^2},
+	&= \bigO{1} \left(\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)} \right) 
+		\int_{0}^\infty \rho(y_0,k_n) e^{-\alpha y_0} \dd y_0\\
+	&= \bigO{1} \left(\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)} \right) p_{k_n} = \smallO{s(k_n) p_{k_n} k_n^2},
 \end{align*}
 %\TM{ Typo : $e^{-\alpha}$ }
-where the last part follows from Lemma~\ref{lem:scaling_s_alpha}. This establishes~\eqref{eq:triangle_diff_main_term} and hence finishes the proof.
+where the last part follows from Lemma~\ref{lem:scaling_s_alpha} and the fact that $s(k_n)^2 = \smallO{s(k_n)}$. This establishes~\eqref{eq:triangle_diff_main_term} and hence finishes the proof.
 %
@@
 %\end{align*}
+\end{proof}
+
+From the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} we obtain the following useful corollary, which will be used in Section~\ref{sec:concentration_c_P_n}.
+
+\begin{corollary}\label{cor:adjusted_triangle_counting_P_n}
+Let $p_0 = (0,y)$. Then, as $n \to \infty$,
+\[
+	\int_{-I_n}^{I_n}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p_0)} f(x,y) \dd x \dd y
+	= (1+\smallO{1}) n k_n^2 \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y. 
+\]
+In particular,
+\[
+	\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p_0)} f(x,y) \dd x \dd y
+	= \bigT{n k_n^{-(2\alpha - 1)} s(k_n)}.
+\]
+\end{corollary}
+
+\begin{proof}
+We first write
+\[
+	\Exp{\left|\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)\right|} 
+	\le \Exp{\left|T_{\text{box}}(y) - \widetilde{T}_{\text{box}}(y) \right|}
+	+\Exp{\left|T_{\text{box}}(y) - T_{\infty}(y)\right|}.
+\]
+Therefore, Lemma~\ref{lem:clustering_error_T_term} and equation~\eqref{eq:triangle_count_diff_scaling} imply that, uniformly for $y \in \Kcal_C(k_n)$,
+\[
+	\Exp{\left|\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)\right|} = \bigO{\log(k_n)n^{-(2\alpha - 1)}
+	+ k_n^2 n^{-(4\alpha - 2)}}	= \smallO{s(k_n) k_n^2},
+\]
+where the last part is due to Lemma~\ref{lem:scaling_s_alpha}.
+Next, since $\Exp{T_\infty(y)} = \Mu{\BallPo{y}}^2 P(y)$, we get
+\[
+	\Exp{\widetilde{T}_{\text{box}}(y)} = \Exp{T_{\infty}(y)} + \Exp{\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)} 
+	= k_n^2 P(y) + \smallO{s(k_n)k_n^2},
+\]
+uniformly on $\Kcal_{C}(k_n)$. Therefore, we can apply a concentration of height argument to replace $\rho_{\text{box}}(y,k_n)$ with $\rho(y,k_n)$ and thus obtain
+\begin{align*}
+	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(y)} 
+		f(x,y) \dd x \dd y\\
+	&= n k_n^2 \int_{\Kcal_{C}(k_n)} \rho(y,k_n) \left(P(y) + \smallO{s(k_n)}\right)
+		\alpha e^{-\alpha y} \dd y\\
+	&= (1+\smallO{1}) n k_n^2 \int_{\Kcal_{C}(k_n)} P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y\\
+	&= (1+\smallO{1}) n k_n^2 \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+\end{align*}
+where we used that on $\Kcal_{C}(k_n)$, $P(y) = \bigT{s(k_n)}$. This proves the first statement. The second statement follows by observing that
+\[
+	\int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y = p_{k_n} \gamma(k_n)
+	= \bigT{k_n^{-(2\alpha + 1)} s(k_n)}.
+\]
 \end{proof}
@@
 \caption{Example configuration of two points $p$ and $p^\prime$ for which $\BallPon{p} \cap \BallPon{p^\prime}$ is not a subset of $\BallPo{p} \cap \BallPo{p^\prime}$.
-The red region indicates the area of points belonging to $\BallPon{p} \cap \BallPon{p^\prime}$ but not to $\BallPo{p} \cap \BallPo{p^\prime}$.}
+The red region indicates the area belonging to $\BallPon{p} \cap \BallPon{p^\prime}$ but not to $\BallPo{p} \cap \BallPo{p^\prime}$.}
 \label{fig:comparing_triangles_diff_intersections}

### 2019-02-25 paper.tex
revised sections 6 and 7
typos in section 1 and added appendix E for the simulation code

@@
 
+\usepackage{listings}
+\lstset{
+    frame=tb, % draw a frame at the top and bottom of the code block
+    tabsize=4, % tab space width
+    showstringspaces=false, % don't mark spaces in strings
+    numbers=left, % display line numbers on the left
+    commentstyle=\color{green}, % comment color
+    keywordstyle=\color{blue}, % keyword color
+    stringstyle=\color{red} % string color
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\newcommand{\Nbox}{\ensuremath{N_{\text{box}}}}
+\newcommand{\Dbox}{\ensuremath{\text{deg}_{\text{box}}}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-02-27 concentration.tex
finished section 8.2

@@
 
-Recall the adjusted triangle count function
+First we write
+\[
+	c^\ast(k_n ; \Gbox) = \frac{T_{\text{box}}(k_n)}{\binom{k_n}{2}\Exp{\Nbox(k_n)}},
+\]
+where
+\[
+	 T_{\text{box}}(k_n) = \sum_{p \in \Pcal} \ind{\Dbox(p) = k_n} \sum_{p_1, p_2 \in \Pcal \setminus p}^{\ne} 
+	 \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPon{p_1}}
+\]
+In particular, the variance of $c^\ast(k_n ; \Gbox)$ is determined by the variance of $T_{\text{box}}(k_n)$.
+
+Next, recall the adjusted triangle count function
 \[
@@
 \[
-	\widetilde{T}_{\text{box}}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal},
+	\widetilde{T}_{\text{box}}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p_0}}\ind{p_2 \in \BallPon{p_0}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal},
 \]
@@
 \]
-
 Slightly abusing notation, we will define the corresponding triangle degree function
 \begin{equation}\label{eq:def_degree_triangle_count_in_K}
-	\widetilde{T}_{\text{box}}(k, C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p).
+	\widetilde{T}_{\text{box}}(k, C) = \sum_{p \in \Pcal \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p).
 \end{equation}
-The idea is that the main contribution of triangles of degree $k_n$ is given by $\widetilde{T}_{\text{box}}(k_n, C)$.
+The idea is that the main contribution of triangles of degree $k_n$ to $T_{\text{box}}(k_n)$ is given by $\widetilde{T}_{\text{box}}(k_n, C)$.
 Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} it suffices to show that $\widetilde{T}_{\text{box}}(k_n,C)$ is sufficiently concentrated around its mean.
@@
 In addition we denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$.
-We shall establish lower bounds on the expected number of these disjoint neighbors $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors.
+We shall establish lower bounds on the expected number of points in the disjoint neighborhood $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number points in the joint neighborhood.
 For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large.
@@
 
-    \draw node at (-7,0.8563) {$h(p,p^\prime)$};
+    \draw node at (-7,0.8563) {$\hat{y}(p,p^\prime)$};
     \draw node at (7,0.3109) {\color{blue}$h_1(p^\prime)$};
@@
     \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
-    \draw node at (2.5298,2) {$x^\ast(p,p^\prime)$};
+    \draw node at (2.5298,2) {$\hat{x}(p,p^\prime)$};
 
@@
 Figure \ref{fig:representation_disjoint_neighborhoods_P_n} and Figure \ref{fig:representation_disjoint_neighborhoods_P_n_2} show two different situations for small distance in the $x$-coordinates, in which case the number of disjoint neighbors is small.
-The case where this distance is large, and the number of disjoint neighbors is expected to be large, is shown in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+The case where this distance is large, and hence the number of disjoint neighbors is expected to be large, is shown in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
 There are several different quantities that are important.
@@
 Note that when $x = 0$ then these heights are the same and we denote this by $h(y)$.
-We also need to know the coordinates $h(p,p^\prime)$ and $x^\ast(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$.
+We also need to know the coordinates $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$.
 Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, compare Figures \ref{fig:representation_disjoint_neighborhoods_P_n} and \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+The derivation of the expression for these functions is similar to those in Section~\ref{ssec:missing_triangles} and we omit the details here.
 The full expressions of all these functions are given below for further reference.
@@
 %		\label{eq:def_y_intersection_close_boundaries}\\
-	h(p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
-	x^\ast(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	
+	\hat{y}(p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
+	\hat{x}(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	
 		e^{\frac{y^\prime}{2}}},\\
@@
 \begin{lemma}\label{lem:disjoint_neighbors_P_n}
-Let $p, p ^\prime \in \Rcal$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
+Let $p, p ^\prime \in \Rcal$ and denote $y^\ast = \min\{y, y^\prime\}$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
 \begin{align*}
@@
 	&\ge \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
-	&\hspace{10pt}+ \xi_{\alpha, \nu}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
+	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
 		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
@@
 	&= \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
-	&\hspace{10pt}+ \xi_{\alpha, \nu}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
+	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
 		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
@@
 \[
-	\phi_n(p,p^\prime) = \xi_{\alpha, \nu}\left( \left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
+	\phi_n(p,p^\prime) = \xi\left( \left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
 	- e^{-(\alpha - \frac{1}{2})R_n}\right)
@@
 	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)} 
-	\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1,
+	\ge \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1,
 \]
@@
 
-Before we proceed we show that the neighborhoods of $p$ and $p^\prime$ below $h(p,p^\prime)$ are disjoint.
-This is clearly true when $h(p,p^\prime) \le h_2(p^\prime)$ so suppose that $h(p,p^\prime) > h_2(p^\prime)$.
+Before we proceed we show that the neighborhoods of $p$ and $p^\prime$ below $\hat{y}(p,p^\prime)$ are disjoint.
+This is clearly true when $\hat{y}(p,p^\prime) \le h_2(p^\prime)$ so suppose that $\hat{y}(p,p^\prime) > h_2(p^\prime)$.
 Then, because we identified the right and left boundaries of the box $\Rcal$ the right boundary of $\BallPon{p^\prime}$ continues from the left boundary of the box and is described by the equation
@@
 \]
-Now, let $x_{\mathrm{right}}^\prime$ and $x_{\mathrm{left}}$ denote the $x$-coordinate of the intersection of the line $h(p,p^\prime)$ with, respectively, the right boundary of $\BallPon{p^\prime}$ and the left boundary of $\BallPon{p}$.
+Now, let $x_{\mathrm{right}}^\prime$ and $x_{\mathrm{left}}$ denote the $x$-coordinate of the intersection of the line $\hat{y}(p,p^\prime)$ with, respectively, the right boundary of $\BallPon{p^\prime}$ and the left boundary of $\BallPon{p}$.
 Then
 \begin{align*}
-	x_{\mathrm{right}}^\prime &= x^\prime + e^{\frac{y^\prime + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-	&= x^\prime + e^{\frac{h(p,p^\prime)}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-		- e{\frac{y + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-	&= x^\prime + |x - x^\prime| - e{\frac{y + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-	&= x - e{\frac{y + h(p,p^\prime)}{2}} + 2|x - x^\prime| - \pi e^{\frac{R_n}{2}}\\
-	&\le x - e{\frac{y + h(p,p^\prime)}{2}} = x_{\mathrm{right}},
-\end{align*}
-and hence the neighborhoods of $p$ and $p^\prime$ below $h(p,p^\prime)$ are disjoint. It then follows that
+	x_{\mathrm{right}}^\prime &= x^\prime + e^{\frac{y^\prime + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+	&= x^\prime + e^{\frac{\hat{y}(p,p^\prime)}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+		- e^{\frac{y + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+	&= x^\prime + |x - x^\prime| - e{\frac{y + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+	&= x - e^{\frac{y + \hat{y}(p,p^\prime)}{2}} + 2|x - x^\prime| - \pi e^{\frac{R_n}{2}}\\
+	&\le x - e^{\frac{y + \hat{y}(p,p^\prime)}{2}} = x_{\mathrm{left}},
+\end{align*}
+and hence the neighborhoods of $p$ and $p^\prime$ below $\hat{y}(p,p^\prime)$ are disjoint. It then follows that
 \begin{align*}
 	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
-	&\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+	&\ge \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
 		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1\\
-	&= \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+	&= \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
 		\left(\ind{p_1 \in \BallPon{p}} + \ind{p_1 \in \BallPon{p^\prime}}\right) 
@@
 	&= \left(\mu_{\alpha,\nu ,n}(\BallPon{p}) + \mu_{\alpha,\nu ,n}(\BallPon{p^\prime})\right)
-		\left(1 - \frac{2\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1\right),
+		\left(1 - \frac{2\alpha \nu}{\pi}\int_{\hat{y}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1\right),
 \end{align*}
@@
 \begin{align*}
-	\frac{2\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1 
-	&= \xi_{\alpha, \nu}\left(e^{-(\alpha - \frac{1}{2})h(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
-	&= \xi_{\alpha, \nu}\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
+	\frac{2\alpha \nu}{\pi}\int_{\hat{y}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1 
+	&= \xi\left(e^{-(\alpha - \frac{1}{2})\hat{y}(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
+	&= \xi\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
 		- e^{-(\alpha - \frac{1}{2})R_n}\right).
@@
 
-Next we consider the number of common neighbors between two nodes $p$ and $p^\prime$ in $\Ginf$, which we denote by $\Ncal_{\Pcal}(p,p^\prime)$.
+Next we consider the number of common neighbors between two nodes $p$ and $p^\prime$ in $\Gbox$, which we denote by $\Ncal_{\Pcal}(p,p^\prime)$.
 
@@
 		e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\\
-	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(
+	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(
 		e^{-(\alpha - \frac{1}{2})h(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
-	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(\left(\frac{|x^\prime - x|}{e^{y/2} + 	
+	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(\left(\frac{|x^\prime - x|}{e^{y/2} + 	
 		e^{y^\prime/2}}\right)^{-(2\alpha - 1)} - e^{-(\alpha - \frac{1}{2})R_n}\right).
@@
 		- (x^\prime - x)e^{-\alpha R_n}\right)\\
-	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(
+	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(
 		\frac{2\alpha - 1}{4\alpha}\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
@@
 \end{align*}
-Combining these two results and noticing that $\xi_{\alpha, \nu} e^{y/2} = \Mu{\BallPon{p}}$ and similar for $p^\prime$ finishes the proof.
+Combining these two results and noticing that $\xi e^{y/2} = \Mu{\BallPon{p}}$ and similar for $p^\prime$ finishes the proof.
 \end{proof}
@@
 
-We now turn to the joint degree distribution of nodes in $\Gbox$. To ease notations we introduce the following short-hand notation for the conditional joint degree distribution
-\[
-	\rho_n(p,p^\prime,k,k^\prime) 
-	:= \Prob{D_{\Pcal,n}(p) = k, D_{\Pcal,n}(p^\prime) = k^\prime}.
-\]
-
-We first establish an almost independence result for integrals over the joint degree distribution $\rho_{n}(p,p^\prime,k,k^\prime)$ for the case where  $p$ and $p^\prime$ are sufficiently separated.
+We now turn to the joint degree distribution of nodes in $\Gbox$. To ease notations we introduce the following short-hand notation for the joint degree distribution
+\[
+	\rho_{\text{box}}(p,p^\prime,k,k^\prime) 
+	:= \Prob{\Po\left(\Mu{\BallPon{p}}\right) = k, \Po\left(\Mu{\BallPon{p^\prime}}\right) = k^\prime}.
+\]
+
+We first establish an almost independence result for integrals over the joint degree distribution $\rho_{\text{box}}(p,p^\prime,k,k^\prime)$ for the case where  $p$ and $p^\prime$ are sufficiently separated.
 For this we note that when $|x - x^\prime| \gg e^{y/2} + e^{y^\prime/2}$ it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large}
@@
 This implies that the joint neighborhoods are almost independent and hence their degrees must be as well.
-To make this more precise, let $0 < \varepsilon < \min\{(2\alpha - 1)^{-1},1\}$ and define the following two sets
+To make this more precise, let $0 < \varepsilon < \min\{(2\alpha - 1)^{-1},1\}$ and define the following set
 \begin{align}
-	\mathcal{E}(k_n) &= \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
-			\, : \, |x - x^\prime| > \left(e^{y/2} + e^{y^\prime/2}\right) \log(n)
-		\right\} \label{eq:def_joint_degree_set_E_constant_k} \\
-	\mathcal{E}_{\varepsilon}(k_n) &= \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
-		\, : \, \Exp{\Ncal_{\text{box}}(p, p^\prime)} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. \label{eq:def_joint_degree_set_E_growing_k}
+	\mathcal{E}_{\varepsilon}(k_n) &= \left\{(p,p^\prime) \in \Rcal \times \Rcal
+		\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. \label{eq:def_joint_degree_set_E_growing_k}
 \end{align}
@@
 
+\begin{lemma}\label{lem:near_independence_poisson}
+Let $k_n \to \infty$ and $X = \Po(\lambda_1(n))$, $Y = \Po(\lambda_2(n))$, be two Poisson random variables where $\lambda_2(n) = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$ and for some $C > 0$,
+\[
+	k_n - C\sqrt{k_n \log(k_n)} \le \lambda_1(n) + \lambda_2(n) \le k_n + C\sqrt{k_n \log(k_n)}.
+\] 
+Then, if $X_1$ and $X_2$ are two independent copies of $X$,
+\[
+	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} = (1+\smallO{1}) \Prob{X_1 + Y = k_n}\Prob{X_2 + Y = k_n},
+\]
+as $n \to \infty$.
+\end{lemma}
+
+\begin{proof}
+First we write
+\begin{align*}
+	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
+	&= \sum_{t = 0}^\infty \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}.
+\end{align*}
+Now fix a $C_1 > 0$ and define the set
+\[
+	A_n := \left\{t \in \R_+ \, : \, \lambda_2(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \le t 
+	\le \lambda_2(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \right\}.
+\]
+Then by a Chernoff bound (c.f. \eqref{eq:def_chernoff_bound_poisson})
+\begin{align*}
+	&\hspace{-20pt}\sum_{t \in \R_+ \setminus A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
+	&\le \Prob{Y > \lambda_2(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
+		+ \Prob{Y < \lambda_2(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}}\\
+	&= \Prob{\left|\Po(\lambda_2(n)) - \lambda_2(n)\right| > C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
+		= \bigO{k_n^{-\frac{1+C_1^2}{2}}}
+\end{align*}
+and hence
+\[
+	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
+	= \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} + \bigO{k_n^{-(1+C_1^2)/2}}.
+\]
+Now take any $s \in A_n$ so that $|t-s| \le 2 C_1 \sqrt{k_n^{1-\varepsilon}\log(k_n)}$ and note that there exists a $\delta_n$ such that $|\delta_n| \le 2C \sqrt{k_n \log(k_n)}$ and $k_n - t = \lambda_1(n) + \delta_n$.
+It then follows that, uniformly in $t,s$ and $\delta_n$, as $n \to \infty$
+\begin{align*}
+	\frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - s}}
+	&= \frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - t - (s - t)}}\\
+	&= \frac{(k_n - t - (s-t))!}{(k_n - t)!} \lambda_1(n)^{s - t} \\
+	&\sim (k_n - t - (s-t))^{-(s-t)} \lambda_1(n)^{s-t} \\
+	&= \left(\lambda_1(n) + \delta_n - (s-t)\right)^{-(s-t)}\lambda_1(n)^{s-t}\\
+	&= \left(1 + \frac{\delta_n -(s-t)}{\lambda_1(n)}\right)^{s-t}\\
+	&\sim e^{\frac{(s-t)\delta_n}{\lambda_1(n)}} e^{-\frac{(s-t)^2}{\lambda_1(n)}} \sim 1,
+\end{align*}
+where the last line follows since both $\frac{(s-t)\delta_n}{\lambda_1(n)} \to 0$ and $\frac{(s-t)^2}{\lambda_1(n)} \to 0$ as $n \to \infty$. In particular,
+\[
+	\Prob{X_2 = k_n - t} = (1+\smallO{1}) \Prob{X_2 = k_n - s},
+\] 
+uniformly for all $t, s \in A_n$ and therefore, since
+\[
+	1 = \sum_{s = 0}^\infty \Prob{Y = s} = (1+\smallO{1}) \sum_{s \in A_n} \Prob{Y = s},
+\]
+we conclude that
+\begin{align*}
+	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
+	&= (1+\smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} \sum_{s \in A_n} \Prob{Y = s}\\
+	&= (1 + \smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{Y = t} 
+		\sum_{s \in A_n} \Prob{X_2 = k_n - s} \Prob{Y = s}\\
+	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n},
+\end{align*}
+from which the result follows.
+\end{proof}
+
+The above lemma makes it possible to factorize the joint degree distribution $\rho_{\text{box}}(p,p^\prime,k_n,k_n)$ in $\Gbox$, whenever $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$.
+In particular we have the following result.
+
 \begin{lemma}\label{lem:joint_degree_factorization}
-Let $k_n \to \infty$ be such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ let $h : \R_+ \to \R$ be a uniformly bounded function and set
-\[
-	\mathcal{E}_n := \begin{cases}
-		\mathcal{E}(k_n) &\mbox{if } k_n = \bigT{1}\\
-		\mathcal{E}_\varepsilon(k_n) &\mbox{if } k_n \to \infty.
-	\end{cases}
-\]
-Then, as $n \to \infty$,
-\begin{align*}
-	&\hspace{-30pt}\int_{\mathcal{E}_n} \rho_{n}(p,p^\prime,k_n,k_n) h(y)h(y^\prime) 
+Let $k_n \to \infty$ be such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ let $h : \R_+ \to \R$ be a uniformly bounded function. Then, as $n \to \infty$,
+\begin{align*}
+	&\hspace{-30pt}\int_{\mathcal{E}_\varepsilon} \rho_{\text{box}}(p,p^\prime,k_n,k_n) h(y)h(y^\prime) 
 		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-	&= (1+\smallO{1})\int_{\mathcal{E}_n} \rho(y,k_n)\rho(y^\prime,k_n) h(y)h(y^\prime) 
+	&= (1+\smallO{1})\int_{\mathcal{E}_\varepsilon} \rho(y,k_n)\rho(y^\prime,k_n) h(y)h(y^\prime) 
 		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
@@
 	X_2(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p^\prime}\setminus \BallPon{p}}\right),\\
-	X_3(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p} \cup \BallPon{p^\prime}}\right),
-\end{align*}
-and note that
-\begin{align*}
-	\rho_{n}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
-	&= \sum_{t = 0}^\infty \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}.
-\end{align*}
-
-Define $\delta_n = k_n^{-\frac{(1-\varepsilon)\varepsilon}{2}}$.
-Then, since $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\text{box}}(p,p^\prime)} \ge k_n^{\varepsilon}$ for $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, a Chernoff bound (c.f.
+	Y(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p} \cup \BallPon{p^\prime}}\right),
+\end{align*}
+so that
+\begin{align*}
+	\rho_{\text{box}}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k_n, X_2(p,p^\prime) + Y(p,p^\prime) = k_n}.
+\end{align*}
+Next we note that due to symmetry $X_1(p,p^\prime)$ and $X_2(p,p^\prime)$ are independent copies of the same random variable $X(p,p^\prime)$.
+Moreover, on the set $\mathcal{E}_\varepsilon(k_n)$ the random variables $X(p,p^\prime)$ and $Y(p,p^\prime)$ satisfy the conditions of Lemma~\ref{lem:near_independence_poisson}.
+Hence,
+\[
+	\rho_{\text{box}}(p,p^\prime,k_n,k_n)
+	= (1+\smallO{1}) \rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n) + \bigO{k_n^{-\frac{(1+C)^2}{2}}}.
+\]
+where $C > 0$ can be selected arbitrarily large. Since the function $h$ is uniformly bounded it follows that for some large enough $C > 0$,
+\begin{align*}
+	&\int_{\mathcal{E}_\varepsilon(k_n)} k_n^{-\frac{(1+C)^2}{2}} h(y)h(y^\prime) f(x,y) f(x^\prime,y^\prime) \dd x \dd y
+	\dd x^\prime \dd y^\prime \\
+	&= \bigO{1} k_n^{-\frac{(1+C)^2}{2}} \left(\int_\Rcal f(x,y) \dd x \dd y\right)^2 \\
+	&= \smallO{1} \int_{\mathcal{E}_\varepsilon(k_n)} \rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n)
+		h(y)h(y^\prime) f(x,y) f(x^\prime,y^\prime) \dd x \dd y.
+\end{align*}
+Therefore
+\begin{align*}
+	&\int_{\mathcal{E}_\varepsilon(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) h(y)h(y^\prime) f(x,y) f(x^\prime,y^\prime) 
+		\dd x \dd y	\dd x^\prime \dd y^\prime \\
+	&= (1+\smallO{1}) \int_{\mathcal{E}_\varepsilon(k_n)} \rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n)
+		h(y)h(y^\prime) f(x,y) f(x^\prime,y^\prime) \dd x \dd y,
+\end{align*}
+and the result follows by applying a concentration of heights argument twice.
+%Define $\delta_n = k_n^{-\frac{(1-\varepsilon)\varepsilon}{2}}$.
+Then, since $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\text{box}}(p,p^\prime)} \ge k_n^{\varepsilon}$ for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, a Chernoff bound (c.f.
 \eqref{eq:def_chernoff_bound_poisson}) implies that
-\[
-	\Prob{|X_3(p,p^\prime) - \Exp{X_i(p,p^\prime)}| > \delta_n \Exp{X_3(p,p^\prime)}} = \bigO{e^{-k_n^{\varepsilon}}}.
-\]
-If we now define
-\[
-	A_n(p,p^\prime) = \left\{t : (1 - \delta_n) \Exp{X_3(p,p^\prime)} \le t \le (1+\delta_n)\Exp{X_3(p,p^\prime)}\right\},
-\]
-then it follows that
-\begin{align*}
-	&\hspace{-30pt}\sum_{t > \lfloor (1+\delta_n)\Exp{X_3(p,p^\prime)} \rfloor} \Prob{X_3(p,p^\prime) = t} 
-		\Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}\\
-	&\le \Prob{X_3(p,p^\prime) > (1+\delta_n)\Exp{X_3(p,p^\prime)} }\\
-	&\le \Prob{\left|X_3(p,p^\prime) - \Exp{X_3(p,p^\prime)}\right| > \delta_n \Exp{X_3(p,p^\prime)}}\\
-	&= \bigO{e^{-k_n^\varepsilon}},
-\end{align*}
-and similar for the sum over all $t < (1 - \delta_n) \Exp{X_3(p,p^\prime)}$. Hence we conclude that
-\begin{align*}
-	&\hspace{-20pt}\rho_{n}(p,p^\prime,k_n,k_n) \\
-	&= \sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
-		\Prob{X_2(p,p^\prime) = k_n - t} + \bigO{e^{-k_n^\varepsilon}}
-		\numberthis \label{eq:joint_degrees_separation}
-\end{align*}
-
-The idea for the remainder of the proof is to first remove the dependence on $p$ and $p^\prime$ in the summation over $t$ so that
-\[
-	\rho_{n}(p,p^\prime,k_n,k_n) = (1 + \smallO{1})\Prob{X_1(p,p^\prime) = k_n - t_n}
-			\Prob{X_2(p,p^\prime) = k_n - t_n}
-	+ \bigO{e^{-k_n^\varepsilon}},
-\]
-where $t_n = \smallO{k_n}$. Then, since $\Exp{X_1(p,p^\prime)} = \Mu{\BallPon{p}\setminus \BallPon{p^\prime}} = 
-(1 + \smallO{1})\Mu{\BallPon{p}}$, by Lemma~\ref{lem:disjoint_neighbors_P_n_large}, and similar for $X_2$, the proof will follow by applying a concentration argument twice.
-
-To execute this plan we note that $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\text{box}}(p,p^\prime)}$.
+%\[
+%	\Prob{|X_3(p,p^\prime) - \Exp{X_i(p,p^\prime)}| > \delta_n \Exp{X_3(p,p^\prime)}} = \bigO{e^{-k_n^{\varepsilon}}},
+%\]
+%uniformly on $\mathcal{E}_\varepsilon(k_n)$. It now follows that
+%\begin{align*}
+%	&\hspace{-30pt}\sum_{t > \lfloor (1+\delta_n)\Exp{X_3(p,p^\prime)} \rfloor} \Prob{X_3(p,p^\prime) = t} 
+%		\Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}\\
+%	&\le \Prob{X_3(p,p^\prime) > (1+\delta_n)\Exp{X_3(p,p^\prime)} }\\
+%	&\le \Prob{\left|X_3(p,p^\prime) - \Exp{X_3(p,p^\prime)}\right| > \delta_n \Exp{X_3(p,p^\prime)}}\\
+%	&= \bigO{e^{-k_n^\varepsilon}},
+%\end{align*}
+%and similar for the sum over all $t < (1 - \delta_n) \Exp{X_3(p,p^\prime)}$. Hence if we define
+%\[
+%	A_n(p,p^\prime) = \left\{t : (1 - \delta_n) \Exp{X_3(p,p^\prime)} \le t \le (1+\delta_n)\Exp{X_3(p,p^\prime)}\right\},
+%\] 
+%then
+%\begin{align*}
+%	&\hspace{-20pt}\rho_{\text{box}}(p,p^\prime,k_n,k_n) \\
+%	&= \sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
+%		\Prob{X_2(p,p^\prime) = k_n - t} + \bigO{e^{-k_n^\varepsilon}}
+%		\numberthis \label{eq:joint_degrees_separation}
+%\end{align*}
+%
+%The idea for the remainder of the proof is to first remove the dependence on $p$ and $p^\prime$ in the summation over $t$ so that
+%\[
+%	\rho_{\text{box}}(p,p^\prime,k_n,k_n) = (1 + \smallO{1})\Prob{X_1(p,p^\prime) = k_n - t_n}
+%			\Prob{X_2(p,p^\prime) = k_n - t_n}
+%	+ \bigO{e^{-k_n^\varepsilon}},
+%\]
+%where $t_n = \smallO{k_n}$. Then, since $\Exp{X_1(p,p^\prime)} = \Mu{\BallPon{p}\setminus \BallPon{p^\prime}} = 
+%(1 + \smallO{1})\Mu{\BallPon{p}}$, by Lemma~\ref{lem:disjoint_neighbors_P_n_large}, and similar for $X_2$, the proof will follow by applying a concentration argument twice.
+%
+%To execute this plan we note that $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\text{box}}(p,p^\prime)}$.
 Now recall the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n}.
 Then, for $p,p^\prime \in \Kcal_{C}(k_n)$ we have that
-\begin{align*}
-	\phi_n(p,p^\prime) 
-	&\le \frac{1 + 2\alpha}{4\alpha}\left(\frac{k_n^{1 + \varepsilon}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)} 
-	- \left(1-\frac{(2\alpha - 1)\pi}{4\alpha}\right)e^{-(\alpha - \frac{1}{2})R_n}\\
-	&\le \frac{1 + 2\alpha}{4\alpha}\left(\frac{k_n^{1 + \varepsilon}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
-		=\bigT{k_n^{-\varepsilon(2\alpha - 1)}},
-\end{align*}
-where we used that $|x - x^\prime| \le \pi e^{R_n/2}$. In a similar fashion we get
-\begin{align*}
-	\phi_n(p,p^\prime) 
-	&\ge \frac{1 + 2\alpha}{4\alpha}\left(\frac{\pi e^{R_n/2}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
-		+ \frac{2\alpha - 1}{4\alpha} k_n^{1 + \varepsilon}e^{-\alpha R_n} - e^{-(\alpha - \frac{1}{2})R_n}\\
-	&\ge \frac{1 + 2\alpha}{4\alpha}\left(\frac{\pi e^{R_n/2}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
-		- e^{-(\alpha - \frac{1}{2})R_n} = \bigT{k_n^{2\alpha - 1}n^{-(2\alpha - 1)}}.
-\end{align*}
-Therefore, since $\Mu{\BallPo{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$ for $p,p^\prime \in \Kcal_{C}(k_n)$, there exist two $n$-dependent constants 
-\[
-	b_n^- = \bigT{k_n^{2\alpha} n^{-(2\alpha - 1)}} \quad \text{and} \quad
-	b_n^+ = \bigT{k_n^{1 - \varepsilon(2\alpha - 1)}}
-\]
-such that
-\[
-	A_n(p,p^\prime) \subseteq \left\{t \, : \, (1-\delta_n)b_n^- \le t \le (1+\delta_n)b_n^+ \right\} := B_n.
-\]
-If we now define
-\begin{align*}
-	t_n^- &= \arg \min_{t \in B_n} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}\\
-	t_n^+ &= \arg \max_{t \in B_n} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t},
-\end{align*}
-then $t_n^\pm = \smallO{k_n}$ and we get
-\begin{align*}
-	&\hspace{-30pt}\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
-		\Prob{X_2(p,p^\prime) = k_n - t}\\
-	&\le \Prob{X_1(p,p^\prime) = k_n - t_n^+}\Prob{X_2(p,p^\prime) = k_n - t_n^+} 
-		\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t}\\
-	&= \Prob{X_1(p,p^\prime) = k_n - t_n^+}\Prob{X_2(p,p^\prime) = k_n - t_n^+}(1 + \smallO{1}).
-		\numberthis \label{eq:joint_degrees_upper_bound}
-\end{align*}
-and similarly
-\begin{align*}
-	&\hspace{-30pt}\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
-		\Prob{X_2(p,p^\prime) = k_n - t}\\
-	&\ge \Prob{X_1(p,p^\prime) = k_n - t_n^-}\Prob{X_2(p,p^\prime) = k_n - t_n^-}(1 + \smallO{1}).
-		\numberthis \label{eq:joint_degrees_lower_bound}
-\end{align*}
-Next, it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large} that
-\[
-	\Mu{\BallPon{p}}(1 - \phi_n(p,p^\prime))\le \Exp{X_1(p,p^\prime)} \le \Mu{\BallPon{p}},
-\]
-where
-\[
-	\sup_{p,p^\prime \in \mathcal{E}_\varepsilon(k_n)} \phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
-\]
-This implies that on $\mathcal{E}_\varepsilon(k_n)$, $\mu_n^{(1)}(p) := \Exp{X_1(p,p^\prime)}$ satisfies the assumptions of Lemma~\ref{lem:concentration_argument_rho_approximation}.
+%\begin{align*}
+%	\phi_n(p,p^\prime) 
+%	&\le \frac{1 + 2\alpha}{4\alpha}\left(\frac{k_n^{1 + \varepsilon}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)} 
+%	- \left(1-\frac{(2\alpha - 1)\pi}{4\alpha}\right)e^{-(\alpha - \frac{1}{2})R_n}\\
+%	&\le \frac{1 + 2\alpha}{4\alpha}\left(\frac{k_n^{1 + \varepsilon}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
+%		=\bigT{k_n^{-\varepsilon(2\alpha - 1)}},
+%\end{align*}
+%where we used that $|x - x^\prime| \le \pi e^{R_n/2}$. In a similar fashion we get
+%\begin{align*}
+%	\phi_n(p,p^\prime) 
+%	&\ge \frac{1 + 2\alpha}{4\alpha}\left(\frac{\pi e^{R_n/2}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
+%		+ \frac{2\alpha - 1}{4\alpha} k_n^{1 + \varepsilon}e^{-\alpha R_n} - e^{-(\alpha - \frac{1}{2})R_n}\\
+%	&\ge \frac{1 + 2\alpha}{4\alpha}\left(\frac{\pi e^{R_n/2}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
+%		- e^{-(\alpha - \frac{1}{2})R_n} = \bigT{k_n^{2\alpha - 1}n^{-(2\alpha - 1)}}.
+%\end{align*}
+%Therefore, since $\Mu{\BallPo{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$ for $p,p^\prime \in \Kcal_{C}(k_n)$, there exist two $n$-dependent constants 
+%\[
+%	b_n^- = \bigT{k_n^{2\alpha} n^{-(2\alpha - 1)}} \quad \text{and} \quad
+%	b_n^+ = \bigT{k_n^{1 - \varepsilon(2\alpha - 1)}}
+%\]
+%such that
+%\[
+%	A_n(p,p^\prime) \subseteq \left\{t \, : \, (1-\delta_n)b_n^- \le t \le (1+\delta_n)b_n^+ \right\} := B_n.
+%\]
+%If we now define
+%\begin{align*}
+%	t_n^- &= \arg \min_{t \in B_n} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}\\
+%	t_n^+ &= \arg \max_{t \in B_n} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t},
+%\end{align*}
+%then $t_n^\pm = \smallO{k_n}$ and we get
+%\begin{align*}
+%	&\hspace{-30pt}\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
+%		\Prob{X_2(p,p^\prime) = k_n - t}\\
+%	&\le \Prob{X_1(p,p^\prime) = k_n - t_n^+}\Prob{X_2(p,p^\prime) = k_n - t_n^+} 
+%		\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t}\\
+%	&= \Prob{X_1(p,p^\prime) = k_n - t_n^+}\Prob{X_2(p,p^\prime) = k_n - t_n^+}(1 + \smallO{1}).
+%		\numberthis \label{eq:joint_degrees_upper_bound}
+%\end{align*}
+%and similarly
+%\begin{align*}
+%	&\hspace{-30pt}\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
+%		\Prob{X_2(p,p^\prime) = k_n - t}\\
+%	&\ge \Prob{X_1(p,p^\prime) = k_n - t_n^-}\Prob{X_2(p,p^\prime) = k_n - t_n^-}(1 + \smallO{1}).
+%		\numberthis \label{eq:joint_degrees_lower_bound}
+%\end{align*}
+%Next, it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large} that
+%\[
+%	\Mu{\BallPon{p}}(1 - \phi_n(p,p^\prime))\le \Exp{X_1(p,p^\prime)} \le \Mu{\BallPon{p}},
+%\]
+%where
+%\[
+%	\sup_{p,p^\prime \in \mathcal{E}_\varepsilon(k_n)} \phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
+%\]
+%This implies that on $\mathcal{E}_\varepsilon(k_n)$, $\mu_n^{(1)}(p) := \Exp{X_1(p,p^\prime)}$ satisfies the assumptions of Lemma~\ref{lem:concentration_argument_rho_approximation}.
 The same conclusion holds for $\mu_n^{(2)}(p^\prime)$.
-Therefore, if we write $\hat{\rho}_n^{(i)}(p,k) := \Prob{X_i(p,p^\prime) = k - t_n^\pm}$, the second statement of the Lemma~\ref{lem:concentration_argument_rho_approximation} (applied twice) yields
-\begin{align*}
-	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \hat{\rho}_{n}^{(1)}(p,k_n) \hat{\rho}_{n}^{(2)}(p^\prime,k_n) h(y)h(y^\prime) 
-		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-	&= (1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-			f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
-\end{align*}
-Together with the approximation~\eqref{eq:joint_degrees_separation} and the bounds~\eqref{eq:joint_degrees_upper_bound} and~\eqref{eq:joint_degrees_lower_bound} we get
-\begin{align*}
-	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) h(y) h(y^\prime) f(x,y)
-		f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-	&=(1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-	&\hspace{10pt} + \bigO{1} e^{-k_n^{\varepsilon}} \int_{\mathcal{E}_{\varepsilon}(k_n)}
-		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,			
-\end{align*}
-and the result follows since the last term is of smaller order than the first.\\
+%Therefore, if we write $\hat{\rho}_n^{(i)}(p,k) := \Prob{X_i(p,p^\prime) = k - t_n^\pm}$, the second statement of the Lemma~\ref{lem:concentration_argument_rho_approximation} (applied twice) yields
+%\begin{align*}
+%	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \hat{\rho}_{n}^{(1)}(p,k_n) \hat{\rho}_{n}^{(2)}(p^\prime,k_n) h(y)h(y^\prime) 
+%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%	&= (1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
+%			f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+%\end{align*}
+%Together with the approximation~\eqref{eq:joint_degrees_separation} and the bounds~\eqref{eq:joint_degrees_upper_bound} and~\eqref{eq:joint_degrees_lower_bound} we get
+%\begin{align*}
+%	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) h(y) h(y^\prime) f(x,y)
+%		f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%	&=(1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
+%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+%	&\hspace{10pt} + \bigO{1} e^{-k_n^{\varepsilon}} \int_{\mathcal{E}_{\varepsilon}(k_n)}
+%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,			
+%\end{align*}
+%and the result follows since the last term is of smaller order than the first.\\
 \vspace{5pt}
@@
 %\begin{align*}
-%	\rho_{n}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
+%	\rho_{\text{box}}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
 %	&= \Prob{X_3(p,p^\prime) = 0}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} 
@@
 %
-%Take $a_n = 2\log\left((k_n + C\log(n))/\xi_{\alpha, \nu}\right)$ and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}(k_n)$ as defined in~\eqref{eq:def_joint_degree_set_E_constant_k}.
+%Take $a_n = 2\log\left((k_n + C\log(n))/\xi\right)$ and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}(k_n)$ as defined in~\eqref{eq:def_joint_degree_set_E_constant_k}.
 We will show that the expected difference between $I_{a,b}$ and $I_{a,b}^\ast$ is of smaller order than $\Exp{T_\Pcal(k_n)}^2$ so that we only need to consider $I_{a,b}^\ast$.
@@
 %		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{J_b(p,p^\prime)}
+%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{\text{box}}(y,k_n) \Exp{J_b(p,p^\prime)}
 %		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p)}
+%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p)}
 %		\Exp{\widetilde{T}_{\text{box}}(p^\prime)} 
 %		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{n}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p)} 
+%	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p)} 
 %		f_{\alpha, \nu}(x,y) \dd x \dd y\right)	
@@
 %\begin{align*}
-%	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
+%	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
 %		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
@@
 %	\Exp{I_{0,0}^\ast} 
-%	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
+%	&= \int_{\mathcal{E}(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
 %		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
-%	&= \int_{\mathcal{E}(k_n)} \rho_{n}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
+%	&= \int_{\mathcal{E}(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
 %		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
@@
 	\rho_(p,p^\prime, k_n-i,k_n-i^\prime) = (1+o(1))\rho(p,p^\prime, k_n-j,k_n-j^\prime) 
-	= (1+o(1))\rho_{n}(p, p^\prime, k_n, k_n)
+	= (1+o(1))\rho_{\text{box}}(p, p^\prime, k_n, k_n)
 \]
@@
 \[
-	\Exp{I_{0,0}^\ast} = (1 + \smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{n}(p,p^\prime,k_n, k_n)
+	\Exp{I_{0,0}^\ast} = (1 + \smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{\text{box}}(p,p^\prime,k_n, k_n)
 		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y)

### 2019-02-27 introduction.tex
revised sections 6 and 7

@@
 
-As observed by Krioukov et al~\cite{krioukov2010hyperbolic}, and proved rigorously by Gugelmann et al.~\cite{gugelmann2012random}, the degree sequence of the KPKVB model follows a power-law with exponent $2\alpha+1$.
+As observed by Krioukov et al.~\cite{krioukov2010hyperbolic}, and proved rigorously by Gugelmann et al.~\cite{gugelmann2012random}, the degree sequence of the KPKVB model follows a power-law with exponent $2\alpha+1$.
 % More specifically, if $N_k$ denotes the number of vertices of degree exactly $k$ then Gugelmann et al.~\cite{gugelmann2012random} have shown that
@@
 %$N_k = 0$ a.a.s.~whenever $k \gg n^{1/(2\alpha+1)}$. }
-Gugelmann et al~\cite{gugelmann2012random} also showed that the average degree converges in probability to the constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing in the sense that it is bounded below by a positive constant a.a.s.
+Gugelmann et al.~\cite{gugelmann2012random} also showed that the average degree converges in probability to the constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing in the sense that it is bounded below by a positive constant a.a.s.
 Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Pee(E_n)\to 1$.
@@
 Earlier work of the first and third authors with Bode~\cite{bode2015largest} and of the first and third authors~\cite{fountoulakis2018law} has 
-established the ``threshold for a giant component'': when $\alpha < 1$ then there always is a unique component of size linear in $n$ no matter how small 
-$\nu$ (and hence the average degree) is; when $\alpha > 1$ all components are sublinear no matter the value of $\nu$; and when $\alpha=1$ then 
+established the ``threshold for a giant component'': if $\alpha < 1$ then there is a unique component of size linear in $n$ no matter how small 
+$\nu$ (and hence the average degree); if $\alpha > 1$ all components are sublinear no matter the value of $\nu$; and if $\alpha=1$ then 
 there is a critical value $\nu_{\text{c}}$ such that for $\nu < \nu_{\text{c}}$ all components are sublinear and for $\nu > \nu_{\text{c}}$ there 
-is a unique linear sized component (all of these statements holding a.a.s.). 
-Whether or not there is a giant component when $\alpha=1$ and $\nu=\nu_{\text{c}}$ remains an open problem.
-In~\cite{KiwiMit} an ~\cite{KiwiMit2017+}, Kiwi and Mitsche considered the size of the second largest component and
-showed that when $\alpha \in (1/2, 1)$, a.a.s., the second largest component has polylogarithmic order with exponent 
+is a unique linearly sized component (all of these statements holding a.a.s.). 
+Whether or not there is a giant component if $\alpha=1$ and $\nu=\nu_{\text{c}}$ remains an open problem.
+In~\cite{KiwiMit} and~\cite{KiwiMit2017+}, Kiwi and Mitsche considered the size of the second largest component and
+showed that for $\alpha \in (1/2, 1)$, a.a.s., the second largest component has polylogarithmic order with exponent 
 $1/(\alpha -1/2)$.
@@
 One of those, sometimes called the {\em global} clustering coefficient, is defined as 
-three times the ratio the number of triangles to the number of paths of length two in the graph.
+three times the ratio of the number of triangles to the number of paths of length two in the graph.
 Results for this version of the clustering coefficient in the KPKVB model were obtained by Candellero and the first author~\cite{candellero2016clustering} and for the evolution of graphs on more general spaces with negative curvature by the first author in~\cite{F12}.
@@
 	c(v) := \left\{\begin{array}{cl}
-		\displaystyle \frac{1}{{\text{deg}(v)\choose 2}} \sum_{u,w\sim v} 1_{\{uw \in E(G)\}} 
+		\displaystyle \frac{1}{{\text{deg}(v)\choose 2}} \sum_{u,w\sim v} 1_{\{uw \in E(G)\}}, 
 			& \text{ if $\text{deg}(v) \geq 2$, }\\
 		& \\
-        0 & \text{ otherwise,}
+        0, & \text{ otherwise,}
         \end{array}\right.
@@
 $$ c(k; G) := \begin{cases}
-		\displaystyle \frac{1}{N_k} \sum_{v \in V(G), \atop \text{deg}(v)=k}  c(v)  &\mbox{ if } N_k \ge 1\\
-		0 &\mbox{else.}
-	\end{cases},
+		\displaystyle \frac{1}{N_k} \sum_{v \in V(G), \atop \text{deg}(v)=k}  c(v),  &\mbox{ if } N_k \ge 1,\\
+		0, &\mbox{else,}
+	\end{cases}
 	$$
@@
  $B(a,b) := \int_0^1 u^{a-1}(1-u)^{b-1}\text{d}u = \Gamma(a)\Gamma(b) / \Gamma(a+b)$ for the beta function and 
- $B^-(x,a,b) := \int_0^x u^{a-1}(1-u)^{b-1}\text{d}u$ the lower incomplete beta function. 
+ $B^-(x,a,b) := \int_0^x u^{a-1}(1-u)^{b-1}\text{d}u$ for the lower incomplete beta function. 
 We write $U(a,b,z)$ for the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which 
@@
 &\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
-&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
+&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
 \end{align*}
@@
 \frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} \cdot k^{-1} &\text{ if } \alpha > \frac{3}{4}, \\
-\frac{6 \nu}{\pi} \cdot \frac{\log \log (k/\xi)}{k}& \text{ if } \alpha = \frac{3}{4},\\
+\frac{6 \nu}{\pi} \cdot \frac{\log(k)}{k}& \text{ if } \alpha = \frac{3}{4},\\
  c_{\alpha} \cdot k^{2-4\alpha} & \text{ if } \frac12 < \alpha < \frac34, 

### 2019-02-27 proof_overview_finite_k.tex

@@
 \begin{equation}\label{eq:def_intensity_function_f}
-	f(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y} \cdot 1_{\{y>0\}}.
+	f(x,y) = \frac{\alpha \nu}{\pi} e^{-\alpha y} \cdot \1_{\{y>0\}}.
 \end{equation}
@@
 
-For any point $p \in \Rcal$, we write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
+For any point $p \in \R \times (0,\infty)$, we write $\BallPo{p}$ to denote the \emph{ball} around $p$, i.e.
 
 \begin{equation}\label{eq:def_ball_P}
-	\BallPo{p} = \{p^\prime \in \eR\times[0,\infty) : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
+	\BallPo{p} = \{p^\prime \in \eR\times(0,\infty) : |x - x^\prime| \leq e^{\frac{y + y^\prime}{2}}\}.
 \end{equation}
@@
 We consider the box $\Rcal = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2}e^{R/2}] \times (0, R]$ in $\eR^2$. 
-Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\mathcal{V} := \mathcal{P} \cap \Rcal$ and edges set such that
+Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\mathcal{V}_n := \mathcal{P} \cap \Rcal$ and edge set such that
 \[

### 2019-02-28 introduction.tex
update of simulation plots, now with squares

@@
     \centering
-    \includegraphics[scale=0.6]{figures/cn10000nu0512rep100a05to5.pdf}
+    \includegraphics[scale=0.6]{figures/cn10000nu0512rep100a05to5Squares.pdf}
     \caption{Plot of $\gamma$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and 
-    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10000$ and $100$ repetitions.\label{fig:gamma}}
+    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gamma}}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.6]{figures/ckn10000a08nu0512rep100k2to25.pdf}
+    \includegraphics[scale=0.6]{figures/ckn10000a08nu0512rep100k2to25Squares.pdf}
     \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 25 on the horizontal axis, for $\alpha=0.8$ and $\nu=\frac{1}{2}$ 
-    (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (red dots) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
+    (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
 \end{figure}%

### 2019-02-28 clustering_infinite_model.tex
typos in section 3

@@
 $$ \mu(y) = \mu(p) := \mu(\BallPo{p}). $$
-Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives
+Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives, using $\alpha>\frac{1}{2}$,
 
@@
 
-where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. 
+where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$. 
 We will often write $\rho(y,k)$ instead of $\rho(p,k)$.
@@
 Let the random variable $D$ denote the degree of the typical point.
-Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed:
+Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed, for $k \in \N_0$:
 \begin{equation}\label{eq:def_pk}
@@
 \]
-(Where we take the expection over both the Poisson point process $\Pcal$ and $y \isd \text{exp}(\alpha)$, independent of the Poisson process $\Pcal$.) We shall show shortly that these take on the values stated in Theorem~\ref{thm:maincc} and~\ref{thm:mainkfixed}.
+(Where we take the expectation over both the Poisson point process $\Pcal$ and $y \isd \text{exp}(\alpha)$, independently of the Poisson process $\Pcal$.) We shall show shortly that these take on the values stated in Theorem~\ref{thm:maincc} and~\ref{thm:mainkfixed}.
 
 For any fixed value $y_0>0$, the set of points inside $\BallPo{(0,y_0)}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{(0,y_0)}}$.
-As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by the experiment where we first pick $N \isd \Po( \mu(y_0) )$ then and we take $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
-(That is, the intesity function of the Poisson point process, but set to zero outside of $\BallPo{(0,y_0)}$ and renormalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{(0,y_0)}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{(0,y_0)}$ chosen according to the mentioned renormalized probability density function.
+As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by the experiment where we first pick $N \isd \Po( \mu(y_0) )$ and then we take $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
+(That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{(0,y_0)}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{(0,y_0)}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{(0,y_0)}$ chosen according to the mentioned re-normalized probability density function.
 This shows that, for every $k\geq 2$:
@@
 	\Ee\left( C | D=k, y=y_0 \right) 
-	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} 1_{\{u_i\in \BallPo{u_j}\}} \right)
-	= \Exp{1_{\{u_1\in\BallPo{u_2}\}}},
+	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
+	= \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
 \]
 where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{(0,y_0)}$ with the above mentioned density.
-Note that this does not depend on the value of $k$. For notational convenience, we'll write 
-\[ 
-	P(y_0) := \Exp{1_{\{u_1\in\BallPo{u_2}\}}},
+Note that this does not depend on the value of $k$. For notational convenience, we will write 
+\[ 
+	P(y_0) := \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
 \]
@@
 Recall that $P(y_0)$ is the probability that $u_1 = (x_1,y_1), u_2 = (x_2,y_2)$ are neighbours in $\Ginf$, where
-$u_1, u_2$ are i.i.d.~with probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
+$u_1, u_2$ are i.i.d.~with probability density $f \cdot \1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
 In particular
@@
 & = & 
-\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty \int_{-e^{(s+y_0)/2}}^{e^{(s+y_0)/2}} e^{-\alpha s}\, d s \\
+\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty \int_{-e^{(s+y_0)/2}}^{e^{(s+y_0)/2}} e^{-\alpha s}\, d x \, d s \\
 & = & 
@@
 P(y_0(z_0),y_1(z_1),y_2(z_2)) = \begin{cases}
-	1 &\text{ if } z_0 \geq z_1+z_2, z_0 > z_1 > z_2, \\
-	1-G(z_0,z_1,z_2) &\text{ if } z_0 < z_1+z_2, z_0 > z_1 > z_2, \\
-	\frac{z_0}{z_1} &\text{ if } z_1 \geq z_0+z_2, z_1 > \max(z_0,z_2), \\
-	\frac{z_0}{z_1}\left(1-G(z_1,z_0,z_2)\right) &\text{ if } z_1 < z_0+z_2, z_1 > \max(z_0,z_2),
+	1, &\text{ if } z_0 \geq z_1+z_2, z_0 > z_1 > z_2, \\
+	1-G(z_0,z_1,z_2), &\text{ if } z_0 < z_1+z_2, z_0 > z_1 > z_2, \\
+	\frac{z_0}{z_1}, &\text{ if } z_1 \geq z_0+z_2, z_1 > \max(z_0,z_2), \\
+	\frac{z_0}{z_1}\left(1-G(z_1,z_0,z_2)\right), &\text{ if } z_1 < z_0+z_2, z_1 > \max(z_0,z_2),
 \end{cases}
@@
 G(a,b,c) = \frac{1}{4}
-\left( b^{-1}c + bc^{-1} + a^2b^{-1}c^{-1} + 2 - 2ab^{-1}-2ac^{-1}\right)
+\left( b^{-1}c + bc^{-1} + a^2b^{-1}c^{-1} + 2 - 2ab^{-1}-2ac^{-1}\right).
 \end{align*}
@@
 \begin{proof}
-Note that $P(y_0,y_1,y_2)$ is the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y_2)/2},x_1+e^{(y_1+y_2)/2}]$ , as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$.
+Note that $P(y_0,y_1,y_2)$ is the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y_2)/2},x_1+e^{(y_1+y_2)/2}]$, as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$.
 By symmetry considerations, we can take $x_1$ uniformly at random from $[0,e^{y_0/2+y_1/2}]$ as opposed to $[-e^{y_0/2+y_1/2}, e^{y_0/2+y_1/2}]$.
-Figure~\ref{fig:triangle_prob_lemma} show the intersection of the intervals (red line) for two different cases for $x_1 \le e^{(y_0 + y_1)/2}$.
+Figure~\ref{fig:triangle_prob_lemma} shows the intersection of the intervals (red line) for two different cases for $x_1 \le e^{(y_0 + y_1)/2}$.
 
@@
 \begin{align*}
-	P(y_0, y_1, y_2) 
+	P(y_0(z_0), y_1(z_1), y_2(z_2)) 
 	&= 1 - \frac{z_0^2z_1z_2}{4} \cdot \left( z_0^{-1}z_1^{-1}+z_0^{-1}z_2^{-1}-z_1^{-1}z_2^{-1} \right)^2 \\
@@
 \]
-where $x_0$ was set to zero, without loss of generality, and the other two $x_i$ are uniform random variables on $[-e^{(y_0)+y_i)/2}, e^{(y_0+y_i)/2}]$.
+where $x_0$ was set to zero, without loss of generality, and the other two $x_i$ are uniform random variables on $[-e^{(y_0+y_i)/2}, e^{(y_0+y_i)/2}]$.
 When we consider the probability $P(y_1,y_0,y_2)$, this is the 2-fold integral of $h(x_0,0,x_2)$ so that
@@
 
-Applying the change of variables $z_i := e^{-y_i/2}$ and Lemma~\ref{lem:triangle_prob_y_coordinates} gives %${\dd}y_i = -\frac{2{\dd}z_i}{z_i}$ and therefore
+Applying the change of variables $z_i := e^{-y_i/2}$, $i=1,2$, and Lemma~\ref{lem:triangle_prob_y_coordinates} gives %${\dd}y_i = -\frac{2{\dd}z_i}{z_i}$ and therefore
 \begin{align*}
@@
 \begin{align*}
-	J_{a,b,c} 
+	J_{a,b,c}(z_0) 
 	&= z_0^a \int_{z_0/2}^{z_0}\int_{z_0-z_1}^{z_1} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
@@
 \end{align*}
-where we've used the substitution $u := z_1/z_0$ giving $z_0 {\dd} u = {\dd} z_1$ in the penultimate line and
-$B^-$ denotes the (lower) incomplete beta-function.
+where we have used the substitution $u := z_1/z_0$ giving $z_0 {\dd} u = {\dd} z_1$ in the penultimate line and
+$B^-$ denotes the (lower) incomplete beta function.
 Note that since $c \geq -1$, $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4},1\}$, the denominators that occur during the integration are all non-zero.
@@
 
-We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$
+We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$, $i=1,2$,
 we get
 \begin{align*}
-	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0(z_0),y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
+	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0,y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
 		{\dd}z_2{\dd}z_1 \\
@@
 
-We know compute $J_{a,b,c}^\prime(z_0)$
+We now compute $J_{a,b,c}^\prime(z_0)$
 \begin{align*}
@@
 integration domain of the lower incomplete beta function does not touch the singularity at $t=1$ 
-(note $B^-(1-z_0;2\alpha;3-4\alpha) = \int_0^{1-z_0} t^{2\alpha-1} (1-t)^{2-4\alpha}$). 
+(note $B^-(1-z_0;2\alpha,3-4\alpha) = \int_0^{1-z_0} t^{2\alpha-1} (1-t)^{2-4\alpha}dt$). 
 Therefore, the previous expression holds for this case as well.
@@
 We observe from Lemma~\ref{lem:Paneq1} that for $\alpha \not =1$, $P(y(z))$ is in fact a linear combination 
-of terms of the form $z^u$, $(1-z)^u$ and $z_0^u B^-(1-z_0,v,w)$.
-
-To compute $J$ we observe that, by partial integration, 
+of terms of the form $z^u$, $(1-z)^u$ and $z^u B^-(1-z;v,w)$.
+
+To compute $J$ we observe that, by integration by parts, 
 \begin{align*}
@@
 where we used that $\frac{\partial}{\partial z} B^-(1-z;v,w) = - z^{w-1} (1-z)^{v-1}$.
-This takes care of the two integrands involving the Beta function in $P(y)$.
+This takes care of the two integrands involving the beta function in $P(y)$.
 The other integrals are easily computed and yield the following expression for $J$ (note that it only depends on $\alpha$ but not on $\nu$)
@@
 	&= \xi^{u+2\alpha-k} \int_{\xi/b}^{\xi/a} t^{k-1-2\alpha-u} e^{-t} \dd t \\
-	&= \xi^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u;\xi/b) - \Gamma^+( k-2\alpha-u; \xi/a) \right), 
+	&= \xi^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u,\xi/b) - \Gamma^+( k-2\alpha-u, \xi/a) \right), 
 \end{align*}
@@
 \begin{equation}\label{eq:integral_Delta_P_z}
-	\int_0^1 z^{u+2\alpha-k-1} e^{-\xi z^{-1}} \dd z = \xi^{u+2\alpha-k} \Gamma^+(k-2\alpha-u;\xi)
-\end{equation}
-where $\Gamma^+$ denotes the (upper) incomplete gamma function, and we've used the subsitution
-$t = \xi / z$ which gives $\dd z = -\xi_{\alpha, \nu} t^{-2} \dd t$. (And of course it is understood that 
+	\int_0^1 z^{u+2\alpha-k-1} e^{-\xi z^{-1}} \dd z = \xi^{u+2\alpha-k} \Gamma^+(k-2\alpha-u,\xi)
+\end{equation}
+where $\Gamma^+$ denotes the (upper) incomplete gamma function, and we have used the substitution
+$t = \xi / z$ which gives $\dd z = -\xi t^{-2} \dd t$. (And of course it is understood that 
 $\xi/0 = \infty$). This takes care of the integrals of all terms in $P(y(z))$ of the form $z^{u}$.
@@
 
-Finally we need to deal with the terms in $P(y(z))$ that involve the incomplete Beta-function. Let $a, c \in \R$, $\xi, b >0$ 
+Finally we need to deal with the terms in $P(y(z))$ that involve the incomplete beta function. Let $a, c \in \R$, $\xi, b >0$ 
 positive real numbers. Using the integral definition of the incomplete beta function, the change of variables $s=1-t$ gives:
@@
 \end{align*}
-Then changing the order of integration and using the substitution $u = \xi/z$  and recognizing the upper incomplete $\Gamma$-function yields
+Then changing the order of integration and using the substitution $u = \xi/z$  and recognizing the upper incomplete gamma function yields
 \begin{align*}
@@
 \] 
-which holds for any $a\in \R$ and $s>0$ (that for a fixed second argument, the upper incomplete $\Gamma$-function is entire 
+which holds for any $a\in \R$ and $s>0$ (that for a fixed second argument, the upper incomplete gamma function is entire 
 in the first argument, see~\cite[pp. 899, 1032ff.]{gradshteyn2015table}). 

### 2019-02-28 proof_overview_finite_k.tex
typos in section 3

@@
 In the remainder of this paper we will write $\BallHyp{p}$ to denote the image under $\Psi$ of the ball of hyperbolic radius $R$ around the point 
-$\Psi^{-1}(p)$, i.e. 
+$\Psi^{-1}(p)$ for $p \in \Rcal$, i.e. 
 \[
@@
 	\Psi\left[ \left\{ u \in \Haa : 
-	d_\H(\Psi^{-1}(p),u), d_\H(O,u) \le R \right\}\right].
+	d_\H(\Psi^{-1}(p),u), d_\H(O,u) \le R \right\}\right] \subset \Rcal.
 \]
@@
 \begin{equation}\label{eq:def_Omega_hyperbolic}
-	|x-x'|_{\pi e^{R/2}} \leq \Phi(r,r') := \frac{1}{2}e^{R/2} \arccos\left( \frac{\cosh r \cosh r' - \cosh R_n}
+	|x-x'|_{\pi e^{R/2}} \leq \Phi(r,r') := \frac{1}{2}e^{R/2} \arccos\left( \frac{\cosh r \cosh r' - \cosh R}
 	{\sinh r \sinh r'} \right).

### 2019-03-05 proofs_finite_k.tex
update to section 4

--- 2019-01-19 proofs_finite_k.tex
@@
-\section{Proofs of the main results for fixed $k$}\label{sec:proofs_fixed_k}
+\section{Proofs of Theorem~\ref{thm:maincc} and Theorem~\ref{thm:mainkfixed}\label{sec:proofs_fixed_k}}
+
+We will first derive Theorem~\ref{thm:mainkfixed}. It will turn out that Theorem~\ref{thm:maincc} has a quick derivation
+assuming Theorem~\ref{thm:mainkfixed}.
+
+\subsection{Clustering function, proving Theorem~\ref{thm:mainkfixed}}
+In this subsection, we want to show that the clustering function of the KPKVB model $c_n(k) \xrightarrow{\Pee} \gamma(k)$ for a fixed $k$.
+The key idea is that for the poissonized KPKVB model the coupling with the box model is guaranteed to be exact (in the sense that it also preserves edges) for all vertices up to height $H = \frac{R}{4}$ (which is all we need to show the convergence of the clustering function for constant $k$).
+
+The overall proof proceeds in four steps: firstly poissonizing the KPKVB model, secondly truncating the poissonized KPKVB model at height $H=H_n \rightarrow \infty$, thirdly using that the coupling between the poissonized KPKVB and box model is exact when truncated at this height $H$ and finally showing that the clustering function in the truncated box model agrees with the integral for $\gamma(k)$.
+
+We will encouter the following models: we will start with the KPKVB model $G_n = G(n;\alpha,\nu)$, then the Poissonized KPKVB model $\GPo  = G_{Po}(n;\alpha,\nu)$, moving to the truncated Poissonized KPKVB model $\GPoH$ which is the subgraph of $\GPo$ induced on all vertices with height at most $H$ resp.
+radial coordinate at least $R-H$, then the coupling will bring us to the truncated box model $\GboxH$ which is the subgraph of the box model $G_{box}$ induced by all vertices with height at most $H$.
+
+\subsubsection{Poissonization}
+We first show we can restrict attention to the Poissonized instead of the standard KPKVB model.
+
+\begin{lemma}\label{lem:pok} Let $\alpha>\frac12,\nu>0, k\geq 2$ be fixed. % and write $G_n := G(n;\alpha,\nu), G_{n,\text{Po}} := \GPo(n;\alpha,\nu)$.
+Then 
+$$ c(k; G_n)-c(k; \GPo) \xrightarrow[n\to\infty]{\Pee} 0. $$
+\end{lemma}
+
+\begin{proof}
+We consider the coupling where we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ chosen according
+to the $(\alpha,R)$-quasi uniform distribution, the vertices of $G(n;\alpha,\nu)$ are $u_1,\dots, u_n$ and 
+the vertices of $\GPo(n;\alpha,\nu)$ are $u_1,\dots, u_N$ with $N\isd \Po(n)$ independently of
+$u_1, u_2, \dots$.
+
+Due to the coupling, the KPKVB graph or its poissonization is contained in the other, i.e.
+we can use new graph labels $G_1 \subset G_2$; e.g.
+if $N\geq n$, then $G_1 = G(n;\alpha,\nu)$ and $G_2 = \GPo(n;\alpha,\nu)$.
+We write $V_{1,k}$ for the set of vertices of $G_1$ which have $k$ neighbours in $G_1$ and $V_{2,k}$ for the set of vertices of $G_2$ which have $k$ neighbours in $G_2$.
+Write $N_{1,k}=|V_{1,k}|$ and $N_{2,k}=|V_{2,k}|$.
+
+Write $W_1$ for the set of all vertices of $G_1$ which have $k$ neighbours in $G_1$ but no neighbour in $G_2 \backslash G_1$.
+Write $W_2$ for the set of all vertices of $G_1$ which have $k$ neighbours in $G_1$ and at least one neighbour in $G_2 \backslash G_1$.
+Write $W_3$ for the set of all vertices of $G_2$ which have strictly less than $k$ neighbours in $G_1$, but $k$ neighbours in $G_2$.
+
+With this notation, we can rewrite:
+\begin{align*}
+|c(k;G_n)-c(k;\GPo)| &= \left|\sum_{v \in V_{1,k}}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in V_{2,k}}\frac{c_{G_2}(v)}{N_{2,k}}\right| \\
+&=\left|\sum_{v \in W_1}\frac{c_{G_1}(v)}{N_{1,k}}+\sum_{v \in W_2}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in W_1}\frac{c_{G_2}(v)}{N_{2,k}}-\sum_{v \in W_3}\frac{c_{G_2}(v)}{N_{2,k}}\right|
+\end{align*}
+
+For every vertex of $W_1$, the clustering coefficient in $G_1$ and in $G_2$ have the same value. Hence, we can simplify:
+\begin{align*}
+|c(k;G_n)-c(k;\GPo)| &= \left|\sum_{v \in W_1}c_{G_1}(v)\frac{N_{2,k}-N_{1,k}}{N_{1,k}N_{2,k}}+\sum_{v \in W_2}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in W_3}\frac{c_{G_2}(v)}{N_{2,k}}\right|
+\end{align*}
+Using the triangle inequality for the absolute value and the fact that $|c_G(v)|\leq 1$,
+\begin{align*}
+|c(k;G_n)-c(k;\GPo)| &\leq \frac{|W_1| |N_{2,k}-N_{1,k}|}{N_{1,k}N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}}
+\end{align*}
+Using that $|W_1|\leq N_{1,k}$,
+\begin{align*}
+|c(k;G_n)-c(k;\GPo)| &\leq \frac{|N_{2,k}-N_{1,k}|}{N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}}
+\end{align*}
+
+From the Chernoff bound for Poisson random variables, it follows that for any $c>0$, $N \in [n-c\sqrt{n\log n},n+c\sqrt{n\log n}]$ a.a.s..
+This implies that a.a.s.
+the vertex sets of $G_1$ and $G_2$ differ by at most $c\sqrt{n\log n}$ many vertices.
+In particular also $|N_{1,k}-N_{2,k}|,|W_2|,|W_3|=O(\sqrt{n \log n})$ a.a.s.
+
+By the paper by Gugelmann et al.
+it holds that $N_{1,k}$ or $N_{2,k}$ is $\Theta(n)$ a.a.s.
+for fixed degree $k$ and as $|N_{1,k}-N_{2,k}| =O(\sqrt{n\log n})$ a.a.s., it follows that both $N_{1,k},N_{2,k} = \Theta(n)$ a.a.s.
+Putting everything together yields the claim:
+\begin{align*}
+|c(k;G_n)-c(k;\GPo)| &\leq \frac{|N_{2,k}-N_{1,k}|}{N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}} \xrightarrow[n\rightarrow\infty]{\Pee} 0
+\end{align*}
+
+\end{proof}
+
+\subsubsection{Truncation}
+Consider the truncated Poissonized KPKVB model $\GPoH$ with $H =H_n= \frac{R}{4}$.
+%H,R-H tend to infinity and coupling is still exact
+\begin{lemma}\label{lem:n1}
+Let $N_1(H)$ denote the number of vertices with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model $\GPo$. If $H \rightarrow \infty$, then $\E N_1(H) = o(n)$.
+%For all $\epsilon >0$, there is $H_\epsilon$ such that for all $H\geq H_\epsilon$, it holds that $\E N_1(H) \leq \epsilon n$.
+\end{lemma}
+\begin{proof}
+By the Campbell-Mecke formula applied to the vertex set of $\GPo$, by the asymptotic behaviour of $\cosh$ and using $H\rightarrow \infty$,
+\begin{align*}
+\E N_1(H) = n \frac{\cosh(\alpha(R-H))-1}{\cosh(\alpha R) -1} = (1+o(1)) n e^{-\alpha H} = o(n)
+\end{align*}
+\end{proof}
+\begin{lemma}\label{lem:n2}
+Let $N_2(H)$ denote the number of vertices with at least one neighbour with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model.
+If $H \rightarrow \infty$, then $\E N_2(H) = o(n)$.
+\end{lemma}
+\begin{proof}
+Among the vertices with at least one neighbour with radial coordinate at most $R-H$, we distinguish between those that themselves have radial coordinate at most $R-H_0$ and those that themselves have radial coordinate at least $R-H_0$ where $H_0 = \log H$.
+We will show that the expectation of both numbers is sublinear in $n$.
+
+If $H \rightarrow \infty$, then also $H_0 = \log H \rightarrow \infty$.
+Hence by Lemma~\ref{lem:n1}, the expected number of vertices with radial coordinate at most $R-H_0$ (in particular those vertices among them with at least one neighbour with radial coordinate at most $R-H$), $\E N_1(H_0) = o(n)$ is sublinear.
+For a vertex with radial coordinate at least $R-H_0$, the probability that it has a neighbour with radial coordinate at most $R-H$, tends to zero.
+Therefore, by the Campbell-Mecke formula the number of such vertices is sublinear.
+\end{proof}
+
+\begin{lemma}\label{lem:trunc}
+Let $\alpha>\frac{1}{2}$, $\nu>0$ and $k \geq 2$ be fixed. Let $\GPo$ denote the Poissonized KPKVB model and $\GPoH$ denote the truncated Poissonized KPKVB model. Then 
+$$c(k;\GPo)-c(k;\GPoH) \xrightarrow[n \rightarrow \infty]{\Pee} 0.$$
+\end{lemma}
+\begin{proof}
+Let $V_n(k)$ denote the set of all vertices with degree $k$ in the Poissonized KPKVB model $\GPo$ and $V_{n,\leq H}(k)$ the set of all vertices with degree $k$ in the truncated Poissonized KPKVB model $\GPoH$.
+Note that a vertex may have a smaller degree and different clustering coefficient in $\GPo$ and $\GPoH$ (even if it is a vertex of both graphs).
+We write $c_n(v)$ for the clustering coefficient of a vertex $v$ in $\GPo$ and $c_{n,\leq H}(v)$ for the clustering coefficient in $\GPoH$.
+Let $N_n(k)=|V_n(k)|$ denote the number of degree $k$ vertices in $\GPo$.
+Then there is a constant $a_1(k)>0$ such that $N_n(k) \geq a_1(k) n$.
+Let $N_{n,\leq H}(k) = |V_{n,\leq H}(k)|$ be the number of degree $k$ vertices in $\GPoH$.
+
+Using a telescoping sum, we obtain that
+\begin{align*}
+|c(k;\GPo)-c(k;\GPoH)| \leq & \left|c(k;\GPo)-\frac{1}{N_n(k)}\sum_{v \in V_{n,\leq H}(k)} c_n(v)\right|\\
+&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,\leq H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,\leq H}(k)}c_{n,\leq H}(v)\right| \\
+&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,\leq H}(k)} c_{n,\leq H}(v)-c(k;\GPoH)\right| 
+\end{align*}
+Now we use $X_1 := |V_n(k)\backslash V_{n,\leq H}(k)|$, $X_2 := \sum_{v \in V_{n,\leq H}(k)}|c_n(k)-c_{n,\leq H}(k)|$ and $X_3 :=|N_{n,\leq H}(k)-N_n(k)|$ to bound the three differences.
+In the first difference, after factorizing $N_n(k)$, all terms in $V_{n,\leq H}(k)$ cancel and the remaining terms are all bounded by one.
+In the second difference, the sums can be aligned and then the triangle inequality for the absolute value applied.
+In the third difference, the two sums agree.
+Thus, we end up with the upper bound,
+\begin{align*}
+&\leq \frac{X_1}{N_n(k)}+\frac{X_2}{N_n(k)}+\frac{X_3}{N_n(k)}\frac{\sum_{v \in V_{n,\leq H}(k)}c_{n,\leq H}(k)}{N_{n,\leq H}(k)} \\
+&\leq \frac{X_1+X_2+X_3}{N_n(k)} \leq \frac{X_1+X_2+X_3}{a_1(k)n} \\
+%&\leq \frac{|V_n(k)\backslash V_{n,\leq H}(k)|+X_2+|N_{n,\leq H}(k)-N_n(k)|}{a_1(k)n}
+\end{align*}
+using that $c_{n,\leq H}(k) \leq 1$ and $N_n(k) \geq a_1(k)n$ in the last line.
+
+By Lemma~\ref{lem:n1}, we have that $\E X_1 = \E X_3 = o(n)$ and by Lemma~\ref{lem:n2}, we have that $\E X_2 = o(n)$.
+We conclude that $\E |c(k;\GPo)-c(k;\GPoH)| = o(1)$.
+From this, convergence in probability follows by Markov's inequality: for $\epsilon >0$, $\Pee(|c(k;\GPo)-c(k;\GPoH)| \geq \epsilon) \leq \frac{\E|c(k;\GPo)-c(k;\GPoH)|}{\epsilon} = o(1)$.
+\end{proof}
+\subsubsection{Coupling}
+\begin{lemma}\label{lem:coup}
+The clustering function in the truncated Poissonized KPKVB model $\GPoH$ and in the truncated box model $\GboxH$ agree, i.e. $c(k;\GPoH) = c(k;\GboxH)$.
+\end{lemma}
+\begin{proof}
+As all vertices involved have height $\leq H$ resp.
+radial coordinate $\geq R-H$ and as $H\leq \frac{R}{4}$, all vertices involved (in the disk)  will have radial coordinate $\geq \frac{3}{4}R$, such that by Lemma~30(ii) from the paper on the largest component of KPKVB, see Lemma~\ref{lem:coupling_edges}, edges exist between such vertices in the disk if and only if they exist in the box.
+So the two graphs are isomorphic and hence the clustering functions agree.
+\end{proof}
+
+\subsubsection{Deriving the limit integral expression}
+\begin{lemma}\label{lem:lim}
+Let $\alpha > \frac{1}{2}$, $\nu>0$ and $k\geq 2$ be fixed. Then
+$$c(k;\GboxH)\xrightarrow[n\rightarrow\infty]{\Pee}\gamma(k).$$
+\end{lemma}
+%\begin{proof}
+%We will show that $\E c(k;G_{n,Po,H}) \rightarrow \gamma(k)$ as $n\rightarrow\infty$ and $Var(c(k;G_{n,Po,H})) \rightarrow  0$.
+From there, the claim will follow by Chebychev's inequality: Let $\epsilon>0$, then $$\Pee(|c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H})|\geq \epsilon)\leq \frac{Var(c(k;G_{n,Po,H}))}{\epsilon^2} = o(1),$$
+%i.e.
+$c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H}) \xrightarrow[n\rightarrow\infty]{\Pee} 0$, hence also $c(k;G_{n,Po,H})-\gamma(k) = c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H})+\E c(k;G_{n,Po,H})-\gamma(k) \xrightarrow[n\rightarrow\infty]{\Pee} 0$.
+%\end{proof}
+
+Let $\Rcal_H = \Rcal([0,H])$ denote the truncated box.
+For a vertex $v$ of the vertex set $V=V(\GboxH)$, let $h(V,v) = {k \choose 2}^{-1} \sum_{uw \in {\Gamma(v) \choose 2}} \1_{\{uw \in E(\GboxH)\}} \1_{\{ D_{\GboxH}(v)=k\}}$.
+Let $X = \frac{1}{n}\sum_{v \in V(G_{box,H})} h(V(G_{box,H}),v)$.
+Let $Z = \frac{N_{box,H}(k)}{n} = \frac{1}{n}\sum_{v \in \GboxH} \1_{\{D_{\GboxH}(v)=k\}}$.
+Then we have that $c(k;\GboxH) = \frac{X}{Z}$.
+We will show separately that numerator $X$ and denominator $Z$ converge in probability (where the limit of $Z$ is a positive constant).
+From this, the claim of the lemma will follow as convergence in probability is closed under taking quotients.
+
+By the Campbell-Mecke formula, we have
+\begin{align*}
+\E X = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) \mu(dv) = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy
+\end{align*}
+Then, we condition on that the additional vertex $(0,y) \in \Rcal_H$ has degree $k$,
+\begin{align*}
+\E X = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k)\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy
+\end{align*}
+We observe that for $H \rightarrow \infty$, the integrand converges pointwise for $y \in (0,\infty)$ to $P(y)\rho(y,k)\alpha e^{-\alpha y}$ and is always bounded by the integrable function $\alpha e^{-\alpha y}$.
+Therefore, by the theorem of dominated convergence, as $H \rightarrow \infty$,
+\begin{align*}
+\E X \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy
+\end{align*}
+Note that for $X^2$, the summation can be split into off-diagonal (with $v_1 \not = v_2$) and diagonal (with $v_1=v_2$) terms, i.e. write $X^2 = \frac{1}{n^2}(Y_1+Y_2)$ where 
+$$Y_1 = \sum_{v_1 \not = v_2 \in V(G_{box,H})} h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)$$ and $Y_2 = \sum_{v_1 \in V(G_{box,H})} h(V(G_{box,H}),v_1)^2$.
+As $h \leq 1$, $Y_2 \leq n X\leq n$ and so, $\E Y_2 \leq n$, we have by the Campbell-Mecke formula,
+\begin{align*}
+\E Y_1 = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)\mu(dv_1)\mu(dv_2)
+\end{align*}
+If $v_1$ and $v_2$ have horizontal distance $>2e^H$, their neighbourhood balls are disjoint (w.r.t.
+the connection rule of the truncated box model $\GboxH$) and hence, $h(V,v_1)$ and $h(V,v_2)$ are independent.
+The horizontal distance is uniform in $[0,\frac{\pi n}{2\nu}]$.
+Therefore, the probability that two vertices have horizontal distance $\leq 2e^H$ is $\leq \frac{4\nu e^H}{\pi n} = o(1)$.
+Writing $d_H$ for the horizontal distance, we can continue the calculation of the second moment,
+\begin{align*}
+\E Y_1^2 &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ d_H(v_1,v_2)>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)+o(n) \\
+&= (n\E X)^2+o((n\E X)^2)+o(n)
+\end{align*}
+It follows that $\E X^2 = (\E X)^2 + o((\E X)^2)+o(1)$, which implies $Var(X) \rightarrow 0$. We conclude
+$$X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.$$
+In a similar fashion, by the Campbell-Mecke formula,
+\begin{align*}
+\E Z =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy
+\end{align*}
+By the theorem of dominated convergence, it follows that
+\begin{align*}
+\E Z \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy
+\end{align*}
+The statement that $Var(Z) \rightarrow 0$ follows by the same steps as for $X$, just using $h(V,v) = \1_{\{D_{\GboxH}(v)=k\}}$ instead. Hence,
+\begin{align*}
+\E Z \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy
+\end{align*}
+Finally note that 
+\begin{align*}
+\gamma(k) = \frac{\int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy}{\int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy}.
+\end{align*}
+
+\subsubsection{Putting everything together}
+\begin{proofof}{Theorem~\ref{thm:mainkfixed}}
+The overall statement follows from the lemmas together with the fact that convergence in probability is closed under addition.
+Write 
+$$c(k;G_n)-\gamma(k) = c(k;G_n) - c(k;\GPo)+c(k;\GPo)-c(k;\GPoH)+c(k;\GPoH)-\gamma(k).$$ 
+The first difference converges in probability to zero due to the Poissonization Lemma~\ref{lem:pok}, the second difference due to the truncation Lemma~\ref{lem:trunc}, then for the third difference we use $c(k;\GPoH)=c(k;\GboxH)$ from Lemma~\ref{lem:coup} and then Lemma~\ref{lem:lim} on the derivation of the limit integral.
+\end{proofof}
+
+\subsection{Overall clustering coefficient, proving Theorem~\ref{thm:maincc}}
+In this subsection, we want to infer that the clustering coefficient of the KPKVB random graph $c \xrightarrow{\Pee} \gamma$ by only using that $c(k) \xrightarrow{\Pee} \gamma(k)$ for fixed $k$.
+
+\begin{proofof}{Theorem~\ref{thm:maincc}}
+Let $\epsilon >0$.
+First of all, from the paper we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$ (as can be seen e.g.
+via their integral representations), where $p_k$ is the limit degree frequency as obtained by Gugelmann et al.
+for fixed $k$.
+In particular, we know that this series converges (we can use that $\gamma(k)\in [0,1]$ and $\sum_{k=0}^\infty p_k = 1$).
+Therefore, for $\delta >0$ with $\epsilon-2\delta>0$, there is $K_\delta$ such that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$.
+Furthermore, $c_n = \sum_{k=2}^\infty c_n(k)p_n(k)$, so by possibly choosing a larger value for $K_\delta$, we have that $|c_n-\sum_{k=2}^{K_\delta} c_n(k)p_n(k)| \leq \delta$.
+Putting these observations together:
+\begin{align*}
+|c_n-\gamma| &\leq \left|c_n-\sum_{k=2}^{K_\delta}c_n(k)p_n(k)\right|+\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
+ &\leq \delta +\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta 
+\end{align*}
+Therefore, $\Pee(|c_n-\gamma|\geq \epsilon) \leq \Pee(\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta) \rightarrow 0$ because $c_n(k) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p_n(k) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c_n(k)p_n(k) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$.
+%p_k =  = \Theta(k^{-(2\alpha +1)})
+\end{proofof}

### 2019-03-06 proofs_finite_k.tex
corrections to section 4

@@
 
-By the paper by Gugelmann et al.
-it holds that $N_{1,k}$ or $N_{2,k}$ is $\Theta(n)$ a.a.s.
+By the paper by Gugelmann et al.~\cite{gugelmann2012random} it holds that $N_{1,k}$ or $N_{2,k}$ is $\Theta(n)$ a.a.s.
 for fixed degree $k$ and as $|N_{1,k}-N_{2,k}| =O(\sqrt{n\log n})$ a.a.s., it follows that both $N_{1,k},N_{2,k} = \Theta(n)$ a.a.s.
@@
 \begin{proof}
-By the Campbell-Mecke formula applied to the vertex set of $\GPo$, by the asymptotic behaviour of $\cosh$ and using $H\rightarrow \infty$,
+By the Campbell-Mecke formula applied to the vertex set of $\GPo$, by the asymptotic behaviour of $\cosh$ and using that all $R, R-H, H \rightarrow \infty$,
 \begin{align*}
@@
 \begin{proof}
-Let $V_n(k)$ denote the set of all vertices with degree $k$ in the Poissonized KPKVB model $\GPo$ and $V_{n,\leq H}(k)$ the set of all vertices with degree $k$ in the truncated Poissonized KPKVB model $\GPoH$.
+Let $V_n(k)$ denote the set of all vertices with degree $k$ in the Poissonized KPKVB model $\GPo$ and $V_{n,H}(k)$ the set of all vertices with degree $k$ in the truncated Poissonized KPKVB model $\GPoH$.
 Note that a vertex may have a smaller degree and different clustering coefficient in $\GPo$ and $\GPoH$ (even if it is a vertex of both graphs).
-We write $c_n(v)$ for the clustering coefficient of a vertex $v$ in $\GPo$ and $c_{n,\leq H}(v)$ for the clustering coefficient in $\GPoH$.
+We write $c_n(v)$ for the clustering coefficient of a vertex $v$ in $\GPo$ and $c_{n,H}(v)$ for the clustering coefficient in $\GPoH$.
 Let $N_n(k)=|V_n(k)|$ denote the number of degree $k$ vertices in $\GPo$.
-Then there is a constant $a_1(k)>0$ such that $N_n(k) \geq a_1(k) n$.
-Let $N_{n,\leq H}(k) = |V_{n,\leq H}(k)|$ be the number of degree $k$ vertices in $\GPoH$.
+Then as $N_n(k) = \Theta(n k^{-(2\alpha+1)})$ a.a.s., there is a constant $a_1(k)>0$ such that a.a.s.
+$N_n(k) \geq a_1(k) n$.
+Let $N_{n,H}(k) = |V_{n,H}(k)|$ be the number of degree $k$ vertices in $\GPoH$.
 
@@
 \begin{align*}
-|c(k;\GPo)-c(k;\GPoH)| \leq & \left|c(k;\GPo)-\frac{1}{N_n(k)}\sum_{v \in V_{n,\leq H}(k)} c_n(v)\right|\\
-&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,\leq H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,\leq H}(k)}c_{n,\leq H}(v)\right| \\
-&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,\leq H}(k)} c_{n,\leq H}(v)-c(k;\GPoH)\right| 
+|c(k;\GPo)-c(k;\GPoH)| \leq & \left|c(k;\GPo)-\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v)\right|\\
+&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(v)\right| \\
+&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_{n, H}(v)-c(k;\GPoH)\right| 
 \end{align*}
-Now we use $X_1 := |V_n(k)\backslash V_{n,\leq H}(k)|$, $X_2 := \sum_{v \in V_{n,\leq H}(k)}|c_n(k)-c_{n,\leq H}(k)|$ and $X_3 :=|N_{n,\leq H}(k)-N_n(k)|$ to bound the three differences.
-In the first difference, after factorizing $N_n(k)$, all terms in $V_{n,\leq H}(k)$ cancel and the remaining terms are all bounded by one.
-In the second difference, the sums can be aligned and then the triangle inequality for the absolute value applied.
-In the third difference, the two sums agree.
-Thus, we end up with the upper bound,
+Now we use $X_1 := |V_n(k)\backslash V_{n,H}(k)|$, $X_2 := \sum_{v \in V_{n,H}(k)}|c_n(k)-c_{n,H}(k)|$ and $X_3 :=|N_{n,H}(k)-N_n(k)|$ to bound the three differences.
+In the first difference, after factorizing $N_n(k)$, all terms in $V_{n,H}(k)$ cancel and the remaining terms are all bounded by one:
 \begin{align*}
-&\leq \frac{X_1}{N_n(k)}+\frac{X_2}{N_n(k)}+\frac{X_3}{N_n(k)}\frac{\sum_{v \in V_{n,\leq H}(k)}c_{n,\leq H}(k)}{N_{n,\leq H}(k)} \\
-&\leq \frac{X_1+X_2+X_3}{N_n(k)} \leq \frac{X_1+X_2+X_3}{a_1(k)n} \\
-%&\leq \frac{|V_n(k)\backslash V_{n,\leq H}(k)|+X_2+|N_{n,\leq H}(k)-N_n(k)|}{a_1(k)n}
+\left|c(k;\GPo)-\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v)\right| = \left| \frac{1}{N_n(k)}\sum_{v \in V_n \backslash V_{n,H}(k)} c_n(v) \right| \leq \frac{X_1}{N_n(k)}
 \end{align*}
-using that $c_{n,\leq H}(k) \leq 1$ and $N_n(k) \geq a_1(k)n$ in the last line.
+In the second difference, the sums can be aligned and then the triangle inequality for the absolute value applied:
+\begin{align*}
+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(v)\right| \leq \frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} \left|c_n(v)-c_{n,H}(v)\right| =\frac{X_2}{N_n(k)}
+\end{align*}
+In the third difference, we can simplify:
+\begin{align*}
+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_{n, H}(v)-c(k;\GPoH)\right| &= \left|\sum_{v\in V_{n,H}(k)} c_{n,H} \left(\frac{1}{N_n(k)}-\frac{1}{N_{n,H}(k)}\right)\right| \\
+&= \frac{|N_{n,H}(k)-N_n(k)|}{N_n(k)N_{n,H}(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(k)
+\end{align*}
+Thus, we end up with the upper bound, using that $c_{n,H}(k) \leq 1$ and $N_{n,H}(k) = |V_{n,H}(k)|$,
+\begin{align*}
+|c(k;\GPo)-c(k;\GPoH)| \leq \frac{X_1}{N_n(k)}+\frac{X_2}{N_n(k)}+\frac{X_3}{N_n(k)}\frac{\sum_{v \in V_{n,H}(k)}c_{n,\leq H}(k)}{N_{n,H}(k)} \leq \frac{X_1+X_2+X_3}{N_n(k)}
+\end{align*}
+Now using that a.a.s. $N_n(k) \geq a_1(k)n$ gives that a.a.s.
+\begin{align*}
+|c(k;\GPo)-c(k;\GPoH)| \leq \frac{X_1+X_2+X_3}{a_1(k)n} 
+\end{align*}
 
@@
 Let $\Rcal_H = \Rcal([0,H])$ denote the truncated box.
-For a vertex $v$ of the vertex set $V=V(\GboxH)$, let $h(V,v) = {k \choose 2}^{-1} \sum_{uw \in {\Gamma(v) \choose 2}} \1_{\{uw \in E(\GboxH)\}} \1_{\{ D_{\GboxH}(v)=k\}}$.
+For a vertex $v$ of the vertex set $V=V(\GboxH)$, writing $\Gamma(v)$ for the set of all neighbours of vertex $v$, let $$h(V,v) = {k \choose 2}^{-1} \sum_{uw \in {\Gamma(v) \choose 2}} \1_{\{uw \in E(\GboxH)\}} \1_{\{ D_{\GboxH}(v)=k\}}.$$
 Let $X = \frac{1}{n}\sum_{v \in V(G_{box,H})} h(V(G_{box,H}),v)$.
@@
 \begin{align*}
-\E X = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k)\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy
+\E X = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy
 \end{align*}
-We observe that for $H \rightarrow \infty$, the integrand converges pointwise for $y \in (0,\infty)$ to $P(y)\rho(y,k)\alpha e^{-\alpha y}$ and is always bounded by the integrable function $\alpha e^{-\alpha y}$.
+We observe that for $H \rightarrow \infty$, the integrand converges point-wise for $y \in (0,\infty)$ to $P(y)\rho(y,k)\alpha e^{-\alpha y}$ and is always bounded by the integrable function $\alpha e^{-\alpha y}$.
 Therefore, by the theorem of dominated convergence, as $H \rightarrow \infty$,
@@
 \begin{align*}
-\E Y_1 = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)\mu(dv_1)\mu(dv_2)
+\E Y_1 = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)]\mu(dv_1)\mu(dv_2)
 \end{align*}
-If $v_1$ and $v_2$ have horizontal distance $>2e^H$, their neighbourhood balls are disjoint (w.r.t.
-the connection rule of the truncated box model $\GboxH$) and hence, $h(V,v_1)$ and $h(V,v_2)$ are independent.
+If $v_1=(x_1,y_1)$ and $v_2=(x_2,y_2)$ have horizontal distance $>2e^H$, their neighbourhood balls are disjoint w.r.t.
+the connection rule of the truncated box model $\GboxH$.
+To see this, assume that $v_3=(x_3,y_3)$ is adjacent to both $v_1$ and $v_2$, then $|x_1-x_3|\leq e^{\frac{1}{2}(y_1+y_3)}$ and $|x_2-x_3|\leq e^{\frac{1}{2}(y_2+y_3)}$.
+As $y_1, y_2, y_3 \leq H$, it follows that $|x_1-x_3| \leq e^H$ and $|x_2-x_3|\leq e^H$, which implies that $|x_1-x_2| \leq |x_1-x_3|+|x_2-x_3|\leq 2e^H$, contradiction.
+
+Due to the disjointedness of the neighbourhood balls and the properties of the Poisson process $h(V,v_1)$ and $h(V,v_2)$ are independent.
 The horizontal distance is uniform in $[0,\frac{\pi n}{2\nu}]$.
@@
 \begin{align*}
-\E Y_1^2 &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ d_H(v_1,v_2)>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)+o(n) \\
+\E Y_1 &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)\\
+&\qquad+\int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|\leq2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
 &= (n\E X)^2+o((n\E X)^2)+o(n)
@@
 $$X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.$$
-In a similar fashion, by the Campbell-Mecke formula,
+In a similar way, by the Campbell-Mecke formula,
 \begin{align*}
@@
 Let $\epsilon >0$.
-First of all, from the paper we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$ (as can be seen e.g.
-via their integral representations), where $p_k$ is the limit degree frequency as obtained by Gugelmann et al.
-for fixed $k$.
+First of all, from Equations~\ref{eq:def_pk}, \ref{eq:gammakint} and \ref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$.
 In particular, we know that this series converges (we can use that $\gamma(k)\in [0,1]$ and $\sum_{k=0}^\infty p_k = 1$).

### 2019-03-08 concentration.tex
finished with section 8

@@
 \]
-and recall the definition of $\Kcal_{C,n}(k_n)$
-\[
-	\Kcal_{C,n}(k_n) = \left\{p \in \Rcal : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
-		\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\}.
-\]
+and recall the definition of $\Kcal_{C}(k_n)$
+\[
+	\Kcal_{C}(k_n) = \left\{y \in \R_+ : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
+		\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\},
+\]
+and write $\Rcal(k_n,C) = [-I_n,I_n] \times \Kcal_{C}(k_n)$ for the part of the box $\Rcal$ with heights in $\Kcal_{C}(k_n)$.
 Slightly abusing notation, we will define the corresponding triangle degree function
 \begin{equation}\label{eq:def_degree_triangle_count_in_K}
-	\widetilde{T}_{\text{box}}(k, C) = \sum_{p \in \Pcal \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p).
+	\widetilde{T}_{\text{box}}(k_n, C) = \sum_{p \in \Pcal \cap \Rcal(k_n,C)} \ind{\text{deg}_{\text{box}}(p) = k_n} \widetilde{T}_{\text{box}}(p).
 \end{equation}
-The idea is that the main contribution of triangles of degree $k_n$ to $T_{\text{box}}(k_n)$ is given by $\widetilde{T}_{\text{box}}(k_n, C)$.
+The idea is that the main contribution of triangles of degree $k_n$ to the triangle count $T_{\text{box}}(k_n)$ is given by $\widetilde{T}_{\text{box}}(k_n, C)$.
 Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} it suffices to show that $\widetilde{T}_{\text{box}}(k_n,C)$ is sufficiently concentrated around its mean.
-This is done in the following proposition.
+This last part is done in the following proposition.
 
@@
 
-We postpone the proof of this proposition till Section~\ref{ssec:concentration_tilde_T} and first use it to prove Proposition~\ref{prop:concentration_local_clustering_P_n}.
+We first use this result to prove Proposition~\ref{prop:concentration_local_clustering_P_n}.
+The remainder of this section is devoted to prove Proposition~\ref{prop:concentration_tilde_T_P_n}.
+The final proof can be found in Section~\ref{ssec:concentration_tilde_T}.
 
@@
 	\Exp{\widetilde{T}_{\text{box}}(k_n,C)} 
-	&= \int_{\Kcal_{C,n}(k_n)} \CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n}
+	&= \int_{\Rcal(k_n,C)} \CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n}
 		\rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y\\
-	&= (1+\smallO{1}) \binom{k_n}{2} \int_{\Kcal_{C,n}(k_n)} \Mu{\BallPon{y}}^{-2} \Exp{\widetilde{T}_{\text{box}}(y)}
+	&= (1+\smallO{1}) \binom{k_n}{2} \int_{\Rcal(k_n,C)} \Mu{\BallPon{y}}^{-2} \Exp{\widetilde{T}_{\text{box}}(y)}
 		\rho_{\text{box}}(y,k_n) \alpha e^{-\alpha y} \dd y\\
-	&= (1+\smallO{1}) \frac{1}{2} \int_{\Kcal_{C,n}(k_n)} \Exp{\widetilde{T}_{\text{box}}(y)}
+	&= (1+\smallO{1}) \frac{1}{2} \int_{\Rcal(k_n,C)} \Exp{\widetilde{T}_{\text{box}}(y)}
 			\rho_{\text{box}}(y,k_n) \alpha e^{-\alpha y} \dd y\\
-	&= (1+\smallO{1}) n \binom{k_n}{2} \int_0^\infty P(y) \alpha e^{-\alpha y} \dd y,
-\end{align*}
-where the last line is due to Corollary~\ref{cor:adjusted_triangle_counting_P_n}. Since $\Exp{N_{\text{box}}(k_n)} = (1+\smallO{1}n p_{k_n}$ it follows that
+	&= (1+\smallO{1}) n \binom{k_n}{2} \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+\end{align*}
+where the last line is due to Corollary~\ref{cor:adjusted_triangle_counting_P_n}. In particular, since the last integral is $\bigT{k_n^{-(2\alpha + 1)} s(k_n)}$ we conclude that
+\begin{equation}\label{eq:scaling_exected_tilde_T}
+	\Exp{\widetilde{T}_{\text{box}}(k_n,C)} = \bigT{n k_n^{-(2\alpha - 1)}s(k_n)}. 
+\end{equation}
+
+Since $\Exp{N_{\text{box}}(k_n)} = (1+\smallO{1}n p_{k_n}$ it follows that
 \[
@@
 	2\Exp{\left|c^\ast(k_n; \Gbox) - \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right|}
-	= \smallO{s(k_n)}.	
-\]
-
-For the remaining term we use Proposition \ref{prop:concentration_tilde_T_P_n} to obtain
+	= \smallO{\gamma(k_n)} = \smallO{s(k_n)}.	
+\]
+
+For the remaining term we use H\"{o}lder's inequality and Proposition \ref{prop:concentration_tilde_T_P_n} to obtain
 \begin{align*}
@@
 
-To prove Proposition~\ref{prop:concentration_tilde_T_P_n} we need to understand the joint degree distribution in $\Gbox$ and subsequently the joint neighborhoods of two points $p, p^\prime \in \Rcal$.
+To prove Proposition~\ref{prop:concentration_tilde_T_P_n} we need to understand the joint degree distribution in $\Gbox$.
+This subsequently requires us to compute the joint neighborhoods in $\Gbox$ of two points $p, p^\prime \in \Rcal$.
 We perform the analysis in this section.
-The two main results, which will be the crucial technical ingredients for the proof of Proposition~\ref{prop:concentration_tilde_T_P_n}, are Lemma~\ref{lem:joint_degree_factorization} and Lemma~\ref{lem:joint_degree_distribution_shift}.
-
-\subsubsection*{Neighborhoods}
-
-We start with analyzing joint neighborhoods in $\Gbox$.
-Let $p, p^\prime \in \Rcal$.
-Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $\Gbox$, i.e.
+We start with a general result for near independent Poisson random variables.
+
+\begin{lemma}\label{lem:near_independence_poisson}
+Let $k_n \to \infty$ and $X_1 = \Po(\lambda_1(n))$, $X_2 = \Po(\lambda_2(n))$ and $Y = \Po(\lambda_3(n))$, be three Poisson random variables where $\lambda_3(n) = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$ and for some $C > 0$,
+\[
+	k_n - C\sqrt{k_n \log(k_n)} \le \lambda_i(n) + \lambda_3(n) \le k_n + C\sqrt{k_n \log(k_n)},
+\] 
+for $i = 1,2$.Then, as $n \to \infty$
+\[
+	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} = (1+\smallO{1}) \Prob{X_1 + Y = k_n}\Prob{X_2 + Y = k_n}.
+\]
+\end{lemma}
+
+\begin{proof}
+First we write
+\begin{align*}
+	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
+	&= \sum_{t = 0}^\infty \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}.
+\end{align*}
+Now fix a $C_1 > 0$ and define the set
+\[
+	A_n := \left\{t \in \R_+ \, : \, \lambda_3(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \le t 
+	\le \lambda_3(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \right\}.
+\]
+Then by a Chernoff bound (c.f. \eqref{eq:def_chernoff_bound_poisson})
+\begin{align*}
+	&\hspace{-20pt}\sum_{t \in \R_+ \setminus A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
+	&\le \Prob{Y > \lambda_3(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
+		+ \Prob{Y < \lambda_3(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}}\\
+	&= \Prob{\left|\Po(\lambda_3(n)) - \lambda_3(n)\right| > C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
+		\le 2 k_n^{-\frac{C_1}{4}}.
+\end{align*}
+and hence
+\[
+	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
+	= \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} + \bigO{k_n^{-(1+C_1^2)/2}}.
+\]
+Next, for $i=1,2$ we have by assumption on $\lambda_i(n) + \lambda_3(n)$ that
+\begin{align*}
+	\Prob{X_i + Y = k_n} &\ge \frac{\left(k_n + C\sqrt{k_n \log(k_n)}\right)^{k_n}}{k_n!} 
+		e^{-\left(k_n + C\sqrt{k_n \log(k_n)}\right)}\\
+	&\ge e^{-1} k_n^{-1/2} \left(1 + C\sqrt{\frac{\log(k_n)}{k_n}}\right)^{k_n} e^{-C\sqrt{k_n \log(k_n)}}\\
+	&\ge e^{-1} k_n^{-1/2} e^{k_n \log\left(1 + C\sqrt{\frac{\log(k_n)}{k_n}}\right) -C\sqrt{k_n \log(k_n)}}\\
+	&\ge e^{-1} k_n^{-1/2} e^{ -\frac{C^2}{2} \log(k_n)} = e^{-1} k_n^{-\frac{1+C^2}{2}}.
+\end{align*}
+where we also used that $\log(1+x) \ge x - x^2/2$, for $0\le x \le 1$ and $k_n!
+\ge e \sqrt{k_n} k_n^{k_n} e^{-k_n}$.
+Hence, by taking $C_1 > 4(1 + C^2)$ we get that $k_n^{-\frac{C_1}{4}} = \smallO{\Prob{X_1 + Y = k_n}\Prob{X_1 + Y = k_n}}$.
+It remains to show that
+\begin{align*}
+	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
+	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n},
+\end{align*}
+
+For this take any $s \in A_n$ so that $|t-s| \le 2 C_1 \sqrt{k_n^{1-\varepsilon}\log(k_n)}$ and note that there exists a $\delta_n$ satisfying $|\delta_n| \le 2C \sqrt{k_n \log(k_n)}$, for $n$ large enough, such that $k_n - t = \lambda_1(n) + \delta_n$.
+It then follows that, uniformly in $t,s$ and $\delta_n$, as $n \to \infty$
+\begin{align*}
+	\frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - s}}
+	&= \frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - t - (s - t)}}\\
+	&= \frac{(k_n - t - (s-t))!}{(k_n - t)!} \lambda_1(n)^{s - t} \\
+	&\sim (k_n - t - (s-t))^{-(s-t)} \lambda_1(n)^{s-t} \\
+	&= \left(\lambda_1(n) + \delta_n - (s-t)\right)^{-(s-t)}\lambda_1(n)^{s-t}\\
+	&= \left(1 + \frac{\delta_n -(s-t)}{\lambda_1(n)}\right)^{s-t}\\
+	&\sim e^{\frac{(s-t)\delta_n}{\lambda_1(n)}} e^{-\frac{(s-t)^2}{\lambda_1(n)}} \sim 1,
+\end{align*}
+where the last line follows since both $\frac{(s-t)\delta_n}{\lambda_1(n)} \to 0$ and $\frac{(s-t)^2}{\lambda_1(n)} \to 0$ as $n \to \infty$. In particular,
+\[
+	\Prob{X_2 = k_n - t} = (1+\smallO{1}) \Prob{X_2 = k_n - s},
+\] 
+uniformly for all $t, s \in A_n$ and therefore, since
+\[
+	1 = \sum_{s = 0}^\infty \Prob{Y = s} = (1+\smallO{1}) \sum_{s \in A_n} \Prob{Y = s},
+\]
+we conclude that
+\begin{align*}
+	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
+	&= (1+\smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} \sum_{s \in A_n} \Prob{Y = s}\\
+	&= (1 + \smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{Y = t} 
+		\sum_{s \in A_n} \Prob{X_2 = k_n - s} \Prob{Y = s}\\
+	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n},
+\end{align*}
+from which the result follows.
+\end{proof}
+
+To see how this lemma can be applied to analyze the joint degree distribution in $\Gbox$, fix two points $p,p^\prime \in \Rcal$ and denote by 
+\[
+	\rho_{\text{box}}(p,p^\prime,k,k^\prime) 
+	:= \Prob{\Po\left(\Mu{\BallPon{p}}\right) = k, \Po\left(\Mu{\BallPon{p^\prime}}\right) = k^\prime}.
+\]
+the joint degree distribution. Then if we define,
+\begin{align*}
+	X_1(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p}\setminus \BallPon{p^\prime}}\right),\\
+	X_2(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p^\prime}\setminus \BallPon{p}}\right),\\
+	Y(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p} \cap \BallPon{p^\prime}}\right)
+\end{align*}
+it follows that
+\[
+	\rho_{\text{box}}(p,p^\prime,k_n,k_n) = \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k_n, X_2(p,p^\prime) + Y(p,p^\prime) = k_n}.
+\]
+Now, if $y,y^\prime \in \Kcal_{C}(k_n)$ the three Poisson random variables defined above satisfy the condition of Lemma~\ref{lem:near_independence_poisson} regarding the sum $\lambda_i(n) + \lambda_3(n)$.
+Therefore, if in addition $\Mu{\BallPon{p} \cup \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$, we have that
+\[
+	\rho_{\text{box}}(p,p^\prime,k_n,k_n) = (1+\smallO{1})\rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n). 
+\]
+
+To make this more precise, we define, for any $0 < \varepsilon < 1$, the following set
+\begin{equation}\label{eq:def_joint_degree_set_E_growing_k}
+	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
+		\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. 
+\end{equation}
+We will show (see Corollary~\ref{cor:expected_common_neighbors_Ecal_set}) that for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ it holds that $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$ and hence the joint degree distribution factorizes on this set.
+We will use this set later in Section~\ref{ssec:concentration_tilde_T} to prove Proposition~\ref{prop:concentration_tilde_T_P_n}.
+The main idea behind the above result is that if $p$ and $p^\prime$ are sufficiently separated in the $x$-direction, then the overlap of their neighborhoods $\BallPon{p} \cap \BallPon{p^\prime}$ is of smaller order than $\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}$.
+We shall therefore proceed with analyzing the joint neighborhoods in $\Gbox$.
+%
+%
+%The following result shows that for any two points in the set
+%
+%The two main results, which will be the crucial technical ingredients for the proof of Proposition~\ref{prop:concentration_tilde_T_P_n}, are Lemma~\ref{lem:joint_degree_factorization} and Lemma~\ref{lem:joint_degree_distribution_shift}.
+
+\subsubsection*{Joint neighborhoods}
+
+Let $p, p^\prime \in \Rcal$ and denote by
+%Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $\Gbox$, i.e.
 those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection.
-In addition we denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$.
-We shall establish lower bounds on the expected number of points in the disjoint neighborhood $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number points in the joint neighborhood.
+In addition we denote by
+$\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$.
+We shall establish an upper bound on the expected number of joint neighbors when $p$ and $p6\prime$ are sufficiently separated.
+Observe that $\Exp{\Ncal_{\text{box}}(p,p^\prime)} = \Mu{\BallPon{p} \cap \BallPon{p^\prime}}$.
+
+%as well as an asymptotic expression for the expected number points in the joint neighborhood.
 For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large.
 Figure~\ref{fig:representation_disjoint_neighborhoods_P_n}-\ref{fig:representation_disjoint_neighborhoods_P_n_3} show the different situations that occur.
-
-\begin{figure}[p]
+%
+%\begin{figure}[p]
+%\centering
+%\begin{tikzpicture}
+%	
+%	%The box \Rcal
+%	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
+%
+%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
+%    \draw node at (-0.2,0.7) {$p$};
+%    
+%    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (1,0.5) {};
+%    \draw node at (0.8,0.2) {\color{blue}$p^\prime$};
+%	
+%	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
+%    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
+%    \draw[domain=2.2840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-1)-0.5});
+%    \draw[domain=-0.2840:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(1-\x)-0.5});
+%    
+%    \draw[dashed,thick,black,line width=1pt] (-6,2.5835) -- (6,2.5835);
+%    
+%    \draw node at (-7,2.5835) {$h(y)$};
+%    \draw node at (-7,3.3918) {\color{blue}$h_1(p^\prime)$};
+%    \draw node at (7,2.7189) {\color{blue}$h_2(p^\prime)$};
+%    
+%    \draw node at (-4,3.5) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
+%    \draw node at (4.5,3) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
+%    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
+%    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+%
+%\end{tikzpicture}
+%\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
+%\label{fig:representation_disjoint_neighborhoods_P_n}
+%\end{figure}~
+%\begin{figure}[p]
+%\centering
+%\begin{tikzpicture}
+%	
+%	%The box \Rcal
+%	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
+%
+%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
+%    \draw node at (-0.2,0.7) {$p$};
+%    
+%    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (2.5,0.5) {};
+%    \draw node at (2.3,0.2) {\color{blue}$p^\prime$};
+%	
+%	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
+%    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
+%    \draw[domain=3.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-2.5)-0.5});
+%    \draw[domain=1.2160:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(2.5-\x)-0.5});
+%    \draw[domain=0:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+9.5)-0.5});
+%    
+%    \draw[dashed,black,line width=1pt] (-6,2.0055) -- (6,2.0055);
+%    
+%%    \draw node at (-7,2.5835) {$h(y)$};
+%    \draw node at (-7,3.7801) {\color{blue}$h_1(p^\prime)$};
+%    \draw node at (7,2.0055) {\color{blue}$h_2(p^\prime)$};
+%    
+%%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
+%%    \draw[dotted,thick,black] (4.5208,2.0174) -- (6,2.0174);
+%    
+%%    \draw node at (4.5208,-0.5) {$w_x(p,p^\prime)$};
+%%    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};
+%    
+%    \draw node at (0,3.5) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
+%    \draw node at (-2,1.6) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
+%    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
+%    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+%
+%\end{tikzpicture}
+%\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
+%\label{fig:representation_disjoint_neighborhoods_P_n_2}
+%\end{figure}~
+
+\begin{figure}[!ht]
 \centering
@@
 
+	\pgfmathsetmacro{\u}{0} %0
+	\pgfmathsetmacro{\v}{1} %1
+	\pgfmathsetmacro{\uu}{4.5} %1.4
+	\pgfmathsetmacro{\vv}{0.5} %0.8
+	\pgfmathsetmacro{\r}{6}
+	\pgfmathsetmacro{\t}{4}
+
 	%The box \Rcal
-	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
-
-    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
-    \draw node at (-0.2,0.7) {$p$};
-
-    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (1,0.5) {};
-    \draw node at (0.8,0.2) {\color{blue}$p^\prime$};
-
-	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
-    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
-    \draw[domain=2.2840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-1)-0.5});
-    \draw[domain=-0.2840:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(1-\x)-0.5});
-
-    \draw[dashed,thick,black,line width=1pt] (-6,2.5835) -- (6,2.5835);
-
-    \draw node at (-7,2.5835) {$h(y)$};
-    \draw node at (-7,3.3918) {\color{blue}$h_1(p^\prime)$};
-    \draw node at (7,2.7189) {\color{blue}$h_2(p^\prime)$};
-
-    \draw node at (-4,3.5) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
-    \draw node at (4.5,3) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
-    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
-    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
-
-\end{tikzpicture}
-\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
-\label{fig:representation_disjoint_neighborhoods_P_n}
-\end{figure}~
-\begin{figure}[p]
-\centering
-\begin{tikzpicture}
-
-	%The box \Rcal
-	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
-
-    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
-    \draw node at (-0.2,0.7) {$p$};
-
-    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (2.5,0.5) {};
-    \draw node at (2.3,0.2) {\color{blue}$p^\prime$};
-
-	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
-    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
-    \draw[domain=3.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-2.5)-0.5});
-    \draw[domain=1.2160:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(2.5-\x)-0.5});
-    \draw[domain=0:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+9.5)-0.5});
-
-    \draw[dashed,black,line width=1pt] (-6,2.0055) -- (6,2.0055);
-
-%    \draw node at (-7,2.5835) {$h(y)$};
-    \draw node at (-7,3.7801) {\color{blue}$h_1(p^\prime)$};
-    \draw node at (7,2.0055) {\color{blue}$h_2(p^\prime)$};
-
-%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
-%    \draw[dotted,thick,black] (4.5208,2.0174) -- (6,2.0174);
-
-%    \draw node at (4.5208,-0.5) {$w_x(p,p^\prime)$};
-%    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};
-
-    \draw node at (0,3.5) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
-    \draw node at (-2,1.6) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
-    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
-    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
-
-\end{tikzpicture}
-\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
-\label{fig:representation_disjoint_neighborhoods_P_n_2}
-\end{figure}~
-\begin{figure}[p]
-\centering
-\begin{tikzpicture}
-
-	%The box \Rcal
-	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
-
-    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
+	\draw[line width=1pt] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);
+
+    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (\u,\v) {};
     \draw node at (-0.2,1.3) {$p$};
 
-    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (4.5,0.5) {};
+    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (\uu,\vv) {};
     \draw node at (4.3,0.2) {\color{blue}$p^\prime$};
@@
 
-    \draw[dashed,black,line width=1pt] (-6,0.8563) -- (6,0.8563);
-
-    \draw node at (-7,0.8563) {$\hat{y}(p,p^\prime)$};
-    \draw node at (7,0.3109) {\color{blue}$h_1(p^\prime)$};
-
     \draw [decorate,decoration={brace},line width=1pt] (3.2160,-0.1) -- (1.6487,-0.1);
@@
 
-    \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
-    \draw node at (2.5298,2) {$\hat{x}(p,p^\prime)$};
-
+%    \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
+%    \draw node at (2.5298,2) {$\hat{x}(p,p^\prime)$};
+
+    %Define intersection left black and shifted blue curve
+    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
+    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1+exp((\vv-\v)/2))}
+    %Define intersection right black and left blue curve
+    \pgfmathsetmacro{\vvast}{2*ln((\uu)/(exp(\v/2) + exp(\vv/2)))}
+    \pgfmathsetmacro{\uuast}{(\u*exp(\vv/2) + \uu*exp(\v/2))/(exp(\v/2) + exp(\vv/2))}
+    \pgfmathsetmacro{\h}{2*ln(\r)-\v}
 %    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
@@
 %    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};
+
+    \draw node at (\r+0.5,\h) {$h(y)$};
 
@@
 
+	\draw[dashed,black,line width=1pt] (-\r,\vast) -- (\uast,\vast);
+	\draw node at (-\r-1,\vast) {\color{black}$\hat{y}_{\text{left}}(p,p^\prime)$};
+	\draw[dashed,line width=1pt] (\uast,\vast) -- (\uast,0);
+	\draw node at (\uast,-0.5) {$\hat{x}_{\text{left}}(p,p^\prime)$};
+
+	\draw[dashed,black,line width=1pt] (-\r,\vvast) -- (\r,\vvast);
+	\draw node at (\r+1,\vvast) {\color{black}$\hat{y}_{\text{right}}(p,p^\prime)$};
+	\draw[dashed,line width=1pt] (\uuast,\vvast) -- (\uuast,\vvast+1);
+	\draw node at (\uuast,\vvast+1.2) {$\hat{x}_{\text{right}}(p,p^\prime)$};
+
 \end{tikzpicture}
-\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:disjoint_neighbors_P_n_large}.}
+\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:disjoint_neighbors_P_n_large}.
+Note that although here $p^\prime \notin \BallPon{p}$, this is not true in general.
+This situation was merely chosen to improve readability of the figure.}
 \label{fig:representation_disjoint_neighborhoods_P_n_3}
@@
 
-We start by analyzing the shape of the neighborhoods.
-Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$ and $y^\prime \le y$.
-To understand the computation it is helpful to have a picture of the different situations.
-Figure \ref{fig:representation_disjoint_neighborhoods_P_n} and Figure \ref{fig:representation_disjoint_neighborhoods_P_n_2} show two different situations for small distance in the $x$-coordinates, in which case the number of disjoint neighbors is small.
-The case where this distance is large, and hence the number of disjoint neighbors is expected to be large, is shown in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+We start by analyzing the shape of joint neighborhood.
+Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$.
+To understand the computation it is helpful to have a picture.
+Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3} shows such an example.
 There are several different quantities that are important.
-The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal$.
-Note that when $x = 0$ then these heights are the same and we denote this by $h(y)$.
-We also need to know the coordinates $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$.
-Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, compare Figures \ref{fig:representation_disjoint_neighborhoods_P_n} and \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
-The derivation of the expression for these functions is similar to those in Section~\ref{ssec:missing_triangles} and we omit the details here.
+The first are the heights where the left and right boundaries of the ball $\BallPon{p}$ go outside the box $\Rcal$.
+Since $x = 0$ these heights are the same and we denote this by $h(y)$.
+We also need to know the coordinates $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$ and those for the intersection of the left boundary of the neighborhood of $p$ with the right boundary of the neighborhood of $p^\prime$, which we denote by $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$.
+Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, as is the case in Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+The condition $d(p,p^\prime) > 0$ is exactly the right notion for $p$ and $p^\prime$ being sufficiently separated.
+
+Note that $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$ correspond to, respectively, $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ considered in Section~\ref{ssec:missing_triangles}.
+The derivation of $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ is done in a similar manner and we omit the details here.
 The full expressions of all these functions are given below for further reference.
@@
 %		\label{eq:def_y_intersection_close_boundaries}\\
-	\hat{y}(p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
-	\hat{x}(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	
-		e^{\frac{y^\prime}{2}}},\\
+	\hat{y}_{\text{right}}(p,p^\prime) &= 2\log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
+	\hat{x}_{\text{right}}(p,p^\prime) &= \frac{x^\prime}{1 + 	
+		e^{\frac{y^\prime - y}{2}}},\\
+	\hat{y}_{\text{left}}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R_n/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right),\\
+	\hat{x}_{\text{left}}(p,p^\prime) &= \frac{x^\prime - \pi e^{R_n/2}}{1 + e^{\frac{y^\prime - y}{2}}}, \\
 	d(p,p^\prime) &= |x - x^\prime| - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
@@
 
-We start with the result for points whose $x$-coordinates are close, which is when $d(p,p^\prime) < 0$.
-
-\begin{lemma}\label{lem:disjoint_neighbors_P_n}
-Let $p, p ^\prime \in \Rcal$ and denote $y^\ast = \min\{y, y^\prime\}$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
-\begin{align*}
-	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)}
-	&\ge \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
-	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
-		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
-\end{align*}
-\end{lemma}
-
-\begin{proof}
-In order to proof the result we will consider the area in between the two left boundaries of the balls $\BallPon{p}$ and
-$\BallPon{p^\prime}$ up to the height $h^\ast := \min\{h(y), h_2(p^\prime)\}$, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n} and Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_2} for reference.
+%We start with the result for points whose $x$-coordinates are close, which is when $d(p,p^\prime) < 0$.
+%
+%\begin{lemma}\label{lem:disjoint_neighbors_P_n}
+%Let $p, p ^\prime \in \Rcal$ and denote $y^\ast = \min\{y, y^\prime\}$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
+%\begin{align*}
+%	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)}
+%	&\ge \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
+%	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
+%		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
+%\end{align*}
+%\end{lemma}
+%
+%\begin{proof}
+%In order to proof the result we will consider the area in between the two left boundaries of the balls $\BallPon{p}$ and
+%$\BallPon{p^\prime}$ up to the height $h^\ast := \min\{h(y), h_2(p^\prime)\}$, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n} and Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_2} for reference.
 Note that here we do not need to consider different cases depending on whether $|x - x^\prime| \le e^{(y + y^\prime)/2}$ or $|x - x^\prime| > e^{(y + y^\prime)/2}$.
-
-By the Campbell-Mecke formula we get
-\begin{align*}
-	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} &=	\Mu{\BallPon{p} \Delta B_{\Pcal,n}(p^\prime)}\\
-	&\ge \int_0^{h^\ast} \int_{x - e^{\frac{y + y_1}{2}}}^{x^\prime - e^{\frac{y^\prime + y_1}{2}}} f(x_1,y_1)
-		\, dx_1 \, dy_1 \\
-	&= \frac{\alpha \nu}{\pi}|x^\prime - x| \int_{0}^{h^\ast} e^{-\alpha y_1} dy_1
-		+ \frac{\alpha \nu}{\pi}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right| \int_0^{h^\ast} 
-		e^{-(\alpha-\frac{1}{2})y_1} \, dy_1\\
-	&= \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
-	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
-		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
-\end{align*}
-\end{proof}
-
-Now we will consider the case where $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$
-
-\begin{lemma}\label{lem:disjoint_neighbors_P_n_large}
-Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
-\[
-	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}
-	\ge \left(\mu(\BallPon{p}) + \mu(\BallPon{p^\prime})\right)
-		\left(1-\phi_n(p,p^\prime)\right).
-\]
-
-\[
-	\phi_n(p,p^\prime) = \xi\left( \left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
-	- e^{-(\alpha - \frac{1}{2})R_n}\right)
-\]
-\end{lemma}
-
-\begin{proof}
-We will prove the results by using that
-\[
-	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)} 
-	\ge \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1,
-\]
-and computing the integral on the right. We refer to Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3} for further clarification.
-
-Before we proceed we show that the neighborhoods of $p$ and $p^\prime$ below $\hat{y}(p,p^\prime)$ are disjoint.
-This is clearly true when $\hat{y}(p,p^\prime) \le h_2(p^\prime)$ so suppose that $\hat{y}(p,p^\prime) > h_2(p^\prime)$.
+%
+%By the Campbell-Mecke formula we get
+%\begin{align*}
+%	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} &=	\Mu{\BallPon{p} \Delta B_{\Pcal,n}(p^\prime)}\\
+%	&\ge \int_0^{h^\ast} \int_{x - e^{\frac{y + y_1}{2}}}^{x^\prime - e^{\frac{y^\prime + y_1}{2}}} f(x_1,y_1)
+%		\, dx_1 \, dy_1 \\
+%	&= \frac{\alpha \nu}{\pi}|x^\prime - x| \int_{0}^{h^\ast} e^{-\alpha y_1} dy_1
+%		+ \frac{\alpha \nu}{\pi}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right| \int_0^{h^\ast} 
+%		e^{-(\alpha-\frac{1}{2})y_1} \, dy_1\\
+%	&= \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
+%	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
+%		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
+%\end{align*}
+%\end{proof}
+%
+%Now we will consider the case where $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$
+%
+%\begin{lemma}\label{lem:disjoint_neighbors_P_n_large}
+%Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
+%\[
+%	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}
+%	\ge \left(\mu(\BallPon{p}) + \mu(\BallPon{p^\prime})\right)
+%		\left(1-\phi_n(p,p^\prime)\right).
+%\]
+%
+%\[
+%	\phi_n(p,p^\prime) = \xi\left( \left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
+%	- e^{-(\alpha - \frac{1}{2})R_n}\right)
+%\]
+%\end{lemma}
+%
+%\begin{proof}
+%Without loss of generality we take $p = p_0 = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$.
+To state the result for general $p = (x,y)$ we use that $x^\prime = |x - x^\prime|$.
+In particular, we need to keep track of the minus sign in front of $x^\prime$.
+Note that for all $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$ it holds that $\hat{y}_{\text{right}}(p,p^\prime) \le \hat{y}_{\text{left}}(p,p^\prime)$ and hence
+%\[
+%	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)} 
+%	\ge \int_0^{\hat{y}_{\text{right}}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1,
+%\]
+%We shall compute the integral on the right. We refer to Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3} for further clarification. 
+%
+%Before we proceed we show that the neighborhoods of $p$ and $p^\prime$ below $\hat{y}_{\text{right}}(p,p^\prime)$ are disjoint.
+This is clearly true when $\hat{y}_{\text{right}}(p,p^\prime) \le h_2(p^\prime)$ so suppose that $\hat{y}_{\text{right}}(p,p^\prime) > h_2(p^\prime)$.
 Then, because we identified the right and left boundaries of the box $\Rcal$ the right boundary of $\BallPon{p^\prime}$ continues from the left boundary of the box and is described by the equation
-\[
-	x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}} - \pi e^{\frac{R_n}{2}}.
-\]
-Now, let $x_{\mathrm{right}}^\prime$ and $x_{\mathrm{left}}$ denote the $x$-coordinate of the intersection of the line $\hat{y}(p,p^\prime)$ with, respectively, the right boundary of $\BallPon{p^\prime}$ and the left boundary of $\BallPon{p}$.
-Then
-\begin{align*}
-	x_{\mathrm{right}}^\prime &= x^\prime + e^{\frac{y^\prime + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-	&= x^\prime + e^{\frac{\hat{y}(p,p^\prime)}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-		- e^{\frac{y + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-	&= x^\prime + |x - x^\prime| - e{\frac{y + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-	&= x - e^{\frac{y + \hat{y}(p,p^\prime)}{2}} + 2|x - x^\prime| - \pi e^{\frac{R_n}{2}}\\
-	&\le x - e^{\frac{y + \hat{y}(p,p^\prime)}{2}} = x_{\mathrm{left}},
-\end{align*}
-and hence the neighborhoods of $p$ and $p^\prime$ below $\hat{y}(p,p^\prime)$ are disjoint. It then follows that
-\begin{align*}
-	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
-	&\ge \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
-		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1\\
-	&= \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
-		\left(\ind{p_1 \in \BallPon{p}} + \ind{p_1 \in \BallPon{p^\prime}}\right) 
-		f(x_1,y_1) \, dx_1 \, dy_1\\
-	&= \left(\mu_{\alpha,\nu ,n}(\BallPon{p}) + \mu_{\alpha,\nu ,n}(\BallPon{p^\prime})\right)
-		\left(1 - \frac{2\alpha \nu}{\pi}\int_{\hat{y}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1\right),
-\end{align*}
-from which the result follows since
-\begin{align*}
-	\frac{2\alpha \nu}{\pi}\int_{\hat{y}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1 
-	&= \xi\left(e^{-(\alpha - \frac{1}{2})\hat{y}(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
-	&= \xi\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
-		- e^{-(\alpha - \frac{1}{2})R_n}\right).
-\end{align*}
-\end{proof}
+%\[
+%	x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}} - \pi e^{\frac{R_n}{2}}.
+%\]
+%Now, let $x_{\mathrm{right}}^\prime$ and $x_{\mathrm{left}}$ denote the $x$-coordinate of the intersection of the line $\hat{y}_{\text{right}}(p,p^\prime)$ with, respectively, the right boundary of $\BallPon{p^\prime}$ and the left boundary of $\BallPon{p}$.
+Then, since $2x^\prime \le \pi e^{R/2}$,
+%\begin{align*}
+%	x_{\mathrm{right}}^\prime &= x^\prime + e^{\frac{y^\prime + \hat{y}_{\text{right}}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+%	&= x^\prime + e^{\frac{\hat{y}_{\text{right}}(p,p^\prime)}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+%		- e^{\frac{y + \hat{y}_{\text{right}}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+%	&= 2x^\prime - e^{\frac{y + \hat{y}_{\text{right}}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
+%	&\le - e^{\frac{y + \hat{y}_{\text{right}}(p,p^\prime)}{2}} = x_{\mathrm{left}},
+%\end{align*}
+%and hence the neighborhoods of $p$ and $p^\prime$ below $\hat{y}_{\text{right}}(p,p^\prime)$ are disjoint. It then follows that
+%\begin{align*}
+%	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
+%	&\ge \int_0^{\hat{y}_{\text{right}}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+%		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1\\
+%	&= \int_0^{\hat{y}_{\text{right}}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+%		\left(\ind{p_1 \in \BallPon{p}} + \ind{p_1 \in \BallPon{p^\prime}}\right) 
+%		f(x_1,y_1) \, dx_1 \, dy_1\\
+%	&= \left(\mu_{\alpha,\nu ,n}(\BallPon{p}) + \mu_{\alpha,\nu ,n}(\BallPon{p^\prime})\right)
+%		\left(1 - \frac{2\alpha \nu}{\pi}\int_{\hat{y}_{\text{right}}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1\right),
+%\end{align*}
+%from which the result follows since
+%\begin{align*}
+%	\frac{2\alpha \nu}{\pi}\int_{\hat{y}_{\text{right}}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1 
+%	&= \xi\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
+%	&= \xi\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{x^\prime}\right)^{2\alpha - 1}
+%		- e^{-(\alpha - \frac{1}{2})R_n}\right)\\
+%	&= \xi\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{|x - x^\prime|}\right)^{2\alpha - 1}
+%		- e^{-(\alpha - \frac{1}{2})R_n}\right)
+%\end{align*}
+%\end{proof}
 
@@
 
-Next we consider the number of common neighbors between two nodes $p$ and $p^\prime$ in $\Gbox$, which we denote by $\Ncal_{\Pcal}(p,p^\prime)$.
+The following result shows that if $d(p,p^\prime) > 0$, then the expected number of common neighbors is $\smallO{\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}}$.
 
@@
 \[
-	\Exp{\Ncal_{\text{box}}(p,p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)\phi_n(p,p^\prime),
+	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)\phi_n(p,p^\prime),
 \]
@@
 \[
-	\phi_n(p,p^\prime) = \frac{1 + 2\alpha}{4\alpha}\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
-	+ \frac{2\alpha - 1}{4\alpha}|x^\prime - x|e^{-\alpha R_n} - e^{-(\alpha - \frac{1}{2})R_n}. 
+	\phi_n(p,p^\prime) = 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
+	+ \frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
+	e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
+	+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}. 
 \]
@@
 \begin{proof}
-Assume, without loss of generality, that $y \ge y^\prime$ and $x \le x^\prime$ and consider the boundaries of the balls $\BallPon{p}$ and $\BallPon{p^\prime}$ as drawn in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}.
-The left boundary of $\BallPon{p}$ intersects the right boundary of $\BallPon{p^\prime}$ if an only if $d(p,p^\prime) > 0$.
-We observe from the definition of $d(p,p^\prime)$, \eqref{eq:def_d_p_p_prime}, that this is exactly the condition we imposed in the statement of the lemma.
-The $y$-coordinate of the intersection is then given by
-\[
-	h((p,p^\prime) := 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right).
-\]
-Therefore,
+Again, without loss of generality we assume that $p = p_0 = (0,y)$ and $p^\prime = (x^\prime, y^\prime)$ with $0 \le x^\prime \le \frac{\pi}{2} e^{R/2}$. Consider the following two areas
+\begin{align*}
+	A_1 &:= \left\{(x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime), \, 
+		-\frac{\pi}{2} e^{R/2} \wedge - e^{\frac{y + y_1}{2}} \le x_1 \le x^\prime + e^{\frac{y^\prime + y_2}{2}} - \pi e^{R/2} \right\}\\
+	A_2 &:= \left\{(x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime), \,
+			x^\prime - e^{\frac{y^\prime + y_1}{2}} \le x_1 \le \frac{\pi}{2} e^{R/2} \vee e^{\frac{y + y_2}{2}} \right\}.
+\end{align*}
+That is $A_1$ and $A_2$ describe all point $p_1 \in \BallPon{p_0} \cap \BallPon{p}$ with, respectively, $y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime)$ and $y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime)$.
+It now follows that
+\[
+	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \Mu{A_1} + \Mu{A_2},
+\]
+and we will proceed by computing the measures of both sets.
+
+For $A_1$ we have (see also Figure~\ref{fig:comparing_triangles_diff_intersections})
+\begin{align*}
+	\Mu{A_1} &= \int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} 
+		\int_{- e^{\frac{y + y_1}{2}}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} \hspace{-10pt} 
+		f(x_1,y_1) \dd x_1 \dd y_1
+		+ \int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{R/2}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} 
+		\hspace{-10pt}  f(x_1,y_1) \dd x_1 \dd y_1.
+\end{align*}
+For the first integral we get
+\begin{align*}
+	&\hspace{-10pt}\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} 
+		\int_{- e^{\frac{y + y_1}{2}}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} \hspace{-10pt} 
+		f(x_1,y_1) \dd x_1 \dd y_1\\
+	&= \frac{\alpha \nu}{\pi}\left(e^{\frac{y}{2}} + e^{\frac{y}{2}}\right) 	
+		\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1
+		- \frac{\alpha \nu}{\pi}\left(\pi e^{R/2} - x^\prime \right) 
+		\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} e^{-\alpha y_1} \dd y_1\\
+	&= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
+		- e^{-(\alpha - \frac{1}{2})h(y)}\right)
+		- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
+		\left(e^{-\alpha\hat{y}_{\text{left}}(p_0,p^\prime)}
+		- e^{-\alpha h(y)}\right).
+%	&= \frac{2\alpha \nu}{\pi(2\alpha - 1)}\left(e^{\frac{y}{2}} + e^{\frac{y}{2}}\right)
+%		\left(\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
+%		- \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} e^{-(2\alpha - 1)(R-y)}\right)\\
+%	&\hspace{10pt}- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
+%		\left(\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-2\alpha}
+%			- \left(\frac{\pi}{2}\right)^{-2\alpha} e^{-2\alpha(R-y)}\right)
+\end{align*}
+Similarly, the second integral equals
+\begin{align*}
+	&\hspace{-20pt}\int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{R/2}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} 
+		\hspace{-10pt}  f(x_1,y_1) \dd x_1 \dd y_1\\
+	&= \xi e^{\frac{y^\prime}{2}}\left(e^{-(\alpha - \frac{1}{2})h(y)} - e^{-(\alpha - \frac{1}{2})R}\right)
+		- \frac{\nu}{\pi}\left(\pi e^{R/2} - x^\prime\right)
+		\left(e^{-\alpha h(y)}- e^{-\alpha R}\right).
+\end{align*}
+Combining these results yields
+\begin{align*}
+	\Mu{A_1} &= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
+		- \xi e^{\frac{y}{2}} e^{-(\alpha - \frac{1}{2})h(y)}
+		- \xi e^{\frac{y^\prime}{2}} e^{-(\alpha-\frac{1}{2})R} \\
+	&\hspace{10pt}- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
+		e^{-\alpha\hat{y}_{\text{left}}(p_0,p^\prime)}
+		+ \nu e^{R/2}e^{-\alpha h(y)} + \frac{\nu}{\pi}\left(\pi e^{R/2} - x^\prime\right) e^{-\alpha R}\\
+	&\le \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
+		+ \nu e^{R/2}e^{-\alpha h(y)} + \nu e^{-(\alpha - \frac{1}{2}) R}.
+\end{align*}
+
+We now proceed with $A_2$. Here we have
+\begin{align*}
+	\Mu{A_2} &= \int_{\hat{y}_{\text{right}}(p_0,p^\prime)}^{h(y)} 
+		\int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{e^{\frac{y+y_1}{2}}} \hspace{-2pt} 
+		f(x_1,y_1) \dd x_1 \dd y_1
+		+ \int_{h(y)}^{R} \int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{\frac{\pi}{2}e^{R/2}} 
+		\hspace{-2pt}  f(x_1,y_1) \dd x_1 \dd y_1.
+\end{align*}
+Computing each integral separately we get
+\begin{align*}
+	&\hspace{-20pt}\int_{\hat{y}_{\text{right}}(p_0,p^\prime)}^{h(y)} 
+		\int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{e^{\frac{y+y_1}{2}}} \hspace{-2pt} 
+		f(x_1,y_1) \dd x_1 \dd y_1\\
+	&= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} 
+		- e^{-(\alpha - \frac{1}{2})h(y)}\right) 
+		- \frac{\nu}{\pi} x^\prime \left(e^{\alpha \hat{y}_{\text{right}}(p_0,p^\prime)}
+		 - e^{-\alpha h(y)}\right), 
+\end{align*}
+and
+\begin{align*}
+	&\hspace{-20pt}\int_{h(y)}^{R} \int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{\frac{\pi}{2}e^{R/2}} 
+		\hspace{-2pt}  f(x_1,y_1) \dd x_1 \dd y_1\\
+	&= \xi e^{\frac{y^\prime}{2}}\left(e^{-(\alpha - \frac{1}{2})h(y)} - e^{-(\alpha - \frac{1}{2})R}\right)
+		+ \frac{\nu}{\pi}\left(\frac{\pi}{2}e^{R/2} - x^\prime\right)\left(e^{-\alpha h(y)} - e^{-\alpha R}\right).
+\end{align*}
+Combining these results we get
+\begin{align*}
+	\Mu{A_2} &= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} 
+		- \xi e^{\frac{y}{2}}e^{-(\alpha - \frac{1}{2})h(y)} 
+		- \xi e^{\frac{y^\prime}{2}}e^{-(\alpha - \frac{1}{2})R} \\
+	&\hspace{10pt}- \frac{\nu}{\pi} x^\prime e^{-\alpha \hat{y}_{\text{right}}(p_0,p^\prime)}
+		+ \frac{\nu}{2} e^{R/2} e^{-\alpha h(y)} - \frac{\nu}{\pi}\left(\frac{\pi}{2}e^{R/2} - x^\prime\right)
+		e^{-\alpha R}\\
+	&\le \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} + \frac{\nu}{2} e^{R/2} e^{-\alpha h(y)}.
+\end{align*}
+
+Finally, by adding the results for $\Mu{A_1}$ and $\Mu{A_2}$ and using that $\xi e^{\frac{y}{2}} = \Mu{\BallPon{p_0}}$ and 
+$\xi e^{\frac{y^\prime}{2}} = \Mu{\BallPon{p^\prime}}$, we get
 \begin{align*}
 	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
-	&= \int_{h(p,p^\prime)}^{R_n} \int_{x^\prime - e^{(y^\prime+y_1)/2}}^{x + e^{(y + y_1)/2}}
-		f(x_1,y_1) \dd x_1 \dd y_1\\
-	&= \left(e^{y/2} + e^{y^\prime/2}\right)\frac{\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} 
-		e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\\
-	&\hspace{10pt}- (x^\prime - x) \frac{\alpha \nu}{\pi} \int_{h(p,p^\prime)}^{R_n} e^{-\alpha y_1} \dd y_1.
-\end{align*}
-
-For the first term we get
-\begin{align*}
-	&\hspace{-30pt}\left(e^{y/2} + e^{y^\prime/2}\right)\frac{\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} 
-		e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\\
-	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(
-		e^{-(\alpha - \frac{1}{2})h(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
-	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(\left(\frac{|x^\prime - x|}{e^{y/2} + 	
-		e^{y^\prime/2}}\right)^{-(2\alpha - 1)} - e^{-(\alpha - \frac{1}{2})R_n}\right).
-\end{align*}
-For the other term we compute
-\begin{align*}
-	&\hspace{-30pt}(x^\prime - x) \frac{\alpha \nu}{\pi} \int_{h(p,p^\prime)}^{R_n} e^{-\alpha y_1} \dd y_1\\
-	&= (x^\prime - x) \frac{\nu}{\pi}\left(e^{-\alpha(p,p^\prime)} - e^{-\alpha R_n}\right)\\
-	&= \frac{\nu}{\pi}\left(e^{y/2} + e^{y^\prime/2}\right) \left(
-		\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
-		- (x^\prime - x)e^{-\alpha R_n}\right)\\
-	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(
-		\frac{2\alpha - 1}{4\alpha}\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
-		- \frac{2\alpha - 1}{4\alpha}|x^\prime - x|e^{-\alpha R_n}\right).
-\end{align*}
-Combining these two results and noticing that $\xi e^{y/2} = \Mu{\BallPon{p}}$ and similar for $p^\prime$ finishes the proof.
+	&\le \left(\Mu{\BallPon{p_0}} + \Mu{\BallPon{p_0}} \right)
+		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
+		+ e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} \right) \\
+	&\hspace{10pt}+ \frac{3\nu}{2}e^{R/2} e^{-\alpha h(y)}
+		+ \nu e^{-(\alpha -\frac{1}{2}) R}.
+\end{align*}
+Finally we recall that $\hat{y}_{\text{left}}(p_0,p^\prime) \ge \hat{y}_{\text{right}}(p_0,p^\prime)$ for all $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$ and that $h(y) = R - y + 2\log(\pi/\nu)$. Hence
+\begin{align*}
+	&\Exp{\Ncal_{\text{box}}(p,p^\prime)} \\
+	&\le \left(\Mu{\BallPon{p_0}} + \Mu{\BallPon{p_0}} \right) 
+		\left(2e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} +    
+		\frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
+		e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
+		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}
+		\right)
+\end{align*}
+and the result follows by plugging in 
+\[
+	\hat{y}_{\text{right}}(p_0,p^\prime) = 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),
+\]
+and noting that $x^\prime$ is the same as $|x - x^\prime|$, by our generalization step.
+
 \end{proof}
@@
 
-We now turn to the joint degree distribution of nodes in $\Gbox$. To ease notations we introduce the following short-hand notation for the joint degree distribution
-\[
-	\rho_{\text{box}}(p,p^\prime,k,k^\prime) 
-	:= \Prob{\Po\left(\Mu{\BallPon{p}}\right) = k, \Po\left(\Mu{\BallPon{p^\prime}}\right) = k^\prime}.
-\]
-
-We first establish an almost independence result for integrals over the joint degree distribution $\rho_{\text{box}}(p,p^\prime,k,k^\prime)$ for the case where  $p$ and $p^\prime$ are sufficiently separated.
-For this we note that when $|x - x^\prime| \gg e^{y/2} + e^{y^\prime/2}$ it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large}
-\[
-	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)(1 + \smallO{1}),
-\] 
-for $p, p^\prime \in \Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$.
-This implies that the joint neighborhoods are almost independent and hence their degrees must be as well.
-To make this more precise, let $0 < \varepsilon < \min\{(2\alpha - 1)^{-1},1\}$ and define the following set
-\begin{align}
-	\mathcal{E}_{\varepsilon}(k_n) &= \left\{(p,p^\prime) \in \Rcal \times \Rcal
-		\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. \label{eq:def_joint_degree_set_E_growing_k}
-\end{align}
-
-The next result shows that for integrals over either $\mathcal{E}(k_n)$, when $k_n = \bigT{1}$, or $\mathcal{E}_{\varepsilon}(k_n)$, when $k_n \to \infty$, the joint degree distribution satisfies $\rho_n(p,p^\prime,k_n,k_n) = (1 + \smallO{1})\rho(p,k_n)\rho(p^\prime,k_n)$.
-
-\begin{lemma}\label{lem:near_independence_poisson}
-Let $k_n \to \infty$ and $X = \Po(\lambda_1(n))$, $Y = \Po(\lambda_2(n))$, be two Poisson random variables where $\lambda_2(n) = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$ and for some $C > 0$,
-\[
-	k_n - C\sqrt{k_n \log(k_n)} \le \lambda_1(n) + \lambda_2(n) \le k_n + C\sqrt{k_n \log(k_n)}.
-\] 
-Then, if $X_1$ and $X_2$ are two independent copies of $X$,
-\[
-	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} = (1+\smallO{1}) \Prob{X_1 + Y = k_n}\Prob{X_2 + Y = k_n},
-\]
-as $n \to \infty$.
+We now return to the joint degree distribution of nodes in $\Gbox$. Recall the definition of $\mathcal{E}_\varepsilon(k_n)$
+\[
+	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
+			\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. 
+\]
+The following result, which follows from Lemma~\ref{lem:common_neighbors_Pcal_n}, shows that on this set, the expected number of common neighbors is $\smallO{k_n}$.
+
+\begin{lemma}\label{cor:expected_common_neighbors_Ecal_set}
+Fix $0 < \varepsilon < 1$ and let $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. Then for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, as $n \to \infty$,
+\[
+	\Mu{\BallPon{p} \cup \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}.
+\] 
 \end{lemma}
@@
 \begin{proof}
-First we write
-\begin{align*}
-	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
-	&= \sum_{t = 0}^\infty \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}.
-\end{align*}
-Now fix a $C_1 > 0$ and define the set
-\[
-	A_n := \left\{t \in \R_+ \, : \, \lambda_2(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \le t 
-	\le \lambda_2(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \right\}.
-\]
-Then by a Chernoff bound (c.f. \eqref{eq:def_chernoff_bound_poisson})
-\begin{align*}
-	&\hspace{-20pt}\sum_{t \in \R_+ \setminus A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
-	&\le \Prob{Y > \lambda_2(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
-		+ \Prob{Y < \lambda_2(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}}\\
-	&= \Prob{\left|\Po(\lambda_2(n)) - \lambda_2(n)\right| > C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
-		= \bigO{k_n^{-\frac{1+C_1^2}{2}}}
-\end{align*}
-and hence
-\[
-	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
-	= \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} + \bigO{k_n^{-(1+C_1^2)/2}}.
-\]
-Now take any $s \in A_n$ so that $|t-s| \le 2 C_1 \sqrt{k_n^{1-\varepsilon}\log(k_n)}$ and note that there exists a $\delta_n$ such that $|\delta_n| \le 2C \sqrt{k_n \log(k_n)}$ and $k_n - t = \lambda_1(n) + \delta_n$.
-It then follows that, uniformly in $t,s$ and $\delta_n$, as $n \to \infty$
-\begin{align*}
-	\frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - s}}
-	&= \frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - t - (s - t)}}\\
-	&= \frac{(k_n - t - (s-t))!}{(k_n - t)!} \lambda_1(n)^{s - t} \\
-	&\sim (k_n - t - (s-t))^{-(s-t)} \lambda_1(n)^{s-t} \\
-	&= \left(\lambda_1(n) + \delta_n - (s-t)\right)^{-(s-t)}\lambda_1(n)^{s-t}\\
-	&= \left(1 + \frac{\delta_n -(s-t)}{\lambda_1(n)}\right)^{s-t}\\
-	&\sim e^{\frac{(s-t)\delta_n}{\lambda_1(n)}} e^{-\frac{(s-t)^2}{\lambda_1(n)}} \sim 1,
-\end{align*}
-where the last line follows since both $\frac{(s-t)\delta_n}{\lambda_1(n)} \to 0$ and $\frac{(s-t)^2}{\lambda_1(n)} \to 0$ as $n \to \infty$. In particular,
-\[
-	\Prob{X_2 = k_n - t} = (1+\smallO{1}) \Prob{X_2 = k_n - s},
-\] 
-uniformly for all $t, s \in A_n$ and therefore, since
-\[
-	1 = \sum_{s = 0}^\infty \Prob{Y = s} = (1+\smallO{1}) \sum_{s \in A_n} \Prob{Y = s},
-\]
-we conclude that
-\begin{align*}
-	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
-	&= (1+\smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} \sum_{s \in A_n} \Prob{Y = s}\\
-	&= (1 + \smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{Y = t} 
-		\sum_{s \in A_n} \Prob{X_2 = k_n - s} \Prob{Y = s}\\
-	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n},
-\end{align*}
-from which the result follows.
+Since for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ we have $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$, Lemma~\ref{lem:common_neighbors_Pcal_n} implies that
+\[
+	\Mu{\BallPon{p} \cup \BallPon{p^\prime}} \le \bigO{k_n} \phi_n(p,p^\prime),
+\]
+where
+\[
+	\phi_n(p,p^\prime) = 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
+		+ \frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
+		e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
+		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}. 
+\]
+We thus need to show that $\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon}}$.
+For $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, it holds that $e^{y/2}, e^{y^\prime/2} = \bigT{k_n}$ and $|x - x^\prime| > k_n^{1+\varepsilon}$ and hence
+\begin{align*}
+	 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
+	 =	\bigO{k_n^{-\varepsilon(2\alpha - 1)}}
+\end{align*}
+For the second term in $\phi_n(p,p^\prime)$ we use that $e^{\alpha y^\ast} = \bigT{k_n^{2\alpha}}$ and $e^{R} = \bigT{n^2}$ to obtain
+\[
+	\frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
+			e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
+	= \bigO{1} n^{-(2\alpha - 1)} k_n^{2\alpha - 1} = \bigO{n^{-(\alpha - \frac{1}{2})}}.
+\]
+Finally, the third term satisfies $\bigO{n^{-(2\alpha - 1)}k_n^{-1}}$, and we conclude that
+\[
+	\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon(2\alpha - 1)} + n^{-(\alpha - \frac{1}{2})}
+	+ n^{-(2\alpha - 1)}k_n^{-1}} = \bigO{k_n^{-\varepsilon^\prime}},
+\]
+where we used that $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. 
 \end{proof}
 
-The above lemma makes it possible to factorize the joint degree distribution $\rho_{\text{box}}(p,p^\prime,k_n,k_n)$ in $\Gbox$, whenever $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$.
-In particular we have the following result.
+As a corollary we get that on the set $\mathcal{E}_\varepsilon(k_n)$ the joint degree distribution in $\Gbox$ is asymptotically equivalent to the product of the degree distributions.
+We shall however prove a slightly stronger result (Lemma~\ref{lem:joint_degree_factorization}) which also takes care of bounded shifts $\rho_{\text{box}}(p,p^\prime,k_n - t,k_n - t^\prime)$, for some uniformly bounded $t, t^\prime \in \mathbb{Z}$.
+For this we first need the following simple result for Poisson distributions.
+
+\begin{lemma}\label{lem:finite_shifts_poisson}
+Let $k_n \to \infty$ be a sequence of integers and $X = \Po(\lambda_n)$ be a Poisson random variable with mean $\lambda_n$ satisfying
+\[
+		k_n - C\sqrt{k_n \log(k_n)} \le \lambda_n \le k_n + C\sqrt{k_n \log(k_n)}
+\]
+for some $C > 0$. Then, for any $t_n, s_n = O(1)$, as $n \to \infty$,
+\[
+	\Prob{X = k_n - t_n} \sim \Prob{X = k_n - s_n}.
+\]
+\end{lemma}
+
+\begin{proof}
+Note that $k_n > t_n, s_n$ for large enough $n$. Hence, using Stirling's formula, as $n \to \infty$,
+\begin{align*}
+	\frac{\Prob{X = k_n - t_n}}{\Prob{X = k_n - s_n}}
+	&= \frac{(k_n - t_n - (s_n-t_n))!}{(k_n - t_n)!} \lambda_n^{s_n - t_n} \\
+	&\sim \sqrt{\frac{k_n - s_n}{k_n - t_n}} \, \frac{(k_n-s_n)^{k_n - s_n}}{(k_n - t_n)^{k_n - t_n}} \, e^{t_n - s_n} 
+		\lambda_n^{s_n-t_n} \\
+	&= \sqrt{\ell_n} (\ell_n)^{k_n - t_n} e^{t_n - s_n} (k_n - s_n)^{t_n - s_n} \lambda_n^{s_n-t_n}\\
+	&= \sqrt{\ell_n} e^{(k_n - t_n)\log(\ell_n) + t_n - s_n} \left(\frac{k_n - s_n}{\lambda_n}\right)^{s_n - t_n}
+\end{align*}
+where we wrote $\ell_n = (k_n - s_n)/(k_n - t_n)$.
+Note that $\ell_n \to 1$ and hence $\sqrt{\ell_n} \to 1$.
+Moreover, since $(k_n - s_n)/\lambda_n \to 1$ and $|s_n - t_n| = \bigO{1}$ we have that $\left(\frac{k_n - s_n}{\lambda_n}\right)^{s_n - t_n} \sim 1$ Therefore it remains to show that
+\[
+	\lim_{n \to \infty} e^{(k_n - t_n)\log(\ell_n) + t_n - s_n} = 1.
+\] 
+For this we note that for any $x$, such that $|x| \le 1/2$, we have 
+\[
+	x - x^2 \le \log(1+x) \le x.
+\]
+Write $x_n = \ell_n - 1 = \frac{t_n - s_n}{k_n - t_n}$. Then by the assumptions of the lemma, $x_n \to 0$, and thus, for $n$ large enough,
+\[
+	t_n - s_n - \frac{(t_n - s_n)^2}{k_n - t_n}
+	\le (k_n-t)\log\left(\ell_n\right)
+	\le t_n - s_n.
+\]
+In particular
+\[
+	e^{-\frac{(t_n-s_n)^2}{k_n-t_n}}
+	\le e^{(k_n - t_n)\log(\ell_n) + t_n - s_n} \le 1,
+\]
+and the result follows since $\frac{(t_n-s_n)^2}{k_n-t_n} \to 0$.
+\end{proof}
+
+We can now prove the main result of this section.
 
 \begin{lemma}\label{lem:joint_degree_factorization}
-Let $k_n \to \infty$ be such that $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$ let $h : \R_+ \to \R$ be a uniformly bounded function. Then, as $n \to \infty$,
-\begin{align*}
-	&\hspace{-30pt}\int_{\mathcal{E}_\varepsilon} \rho_{\text{box}}(p,p^\prime,k_n,k_n) h(y)h(y^\prime) 
-		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-	&= (1+\smallO{1})\int_{\mathcal{E}_\varepsilon} \rho(y,k_n)\rho(y^\prime,k_n) h(y)h(y^\prime) 
-		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
+Let $0 < \varepsilon < 1$, $k_n \to \infty$ and let $t_n,t^\prime_n, s_n, s_n^\prime \in \mathbb{Z}$ be uniformly bounded.
+Then for any $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, as $n \to \infty$,
+\begin{align*}
+	\rho_{\text{box}}(p,p^\prime,k_n - t_n,k_n - t_n^\prime)
+	&= (1+\smallO{1})\rho_{\text{box}}(p,k_n - s_n)\rho_{\text{box}}(p^\prime,k_n-s_n^\prime).
 \end{align*}
@@
 \begin{proof}
-Recall that $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Now define the random variables
+Define the random variables
 \begin{align*}
@@
 \begin{align*}
-	\rho_{\text{box}}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k_n, X_2(p,p^\prime) + Y(p,p^\prime) = k_n}.
-\end{align*}
-Next we note that due to symmetry $X_1(p,p^\prime)$ and $X_2(p,p^\prime)$ are independent copies of the same random variable $X(p,p^\prime)$.
-Moreover, on the set $\mathcal{E}_\varepsilon(k_n)$ the random variables $X(p,p^\prime)$ and $Y(p,p^\prime)$ satisfy the conditions of Lemma~\ref{lem:near_independence_poisson}.
-Hence,
-\[
-	\rho_{\text{box}}(p,p^\prime,k_n,k_n)
-	= (1+\smallO{1}) \rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n) + \bigO{k_n^{-\frac{(1+C)^2}{2}}}.
-\]
-where $C > 0$ can be selected arbitrarily large. Since the function $h$ is uniformly bounded it follows that for some large enough $C > 0$,
-\begin{align*}
-	&\int_{\mathcal{E}_\varepsilon(k_n)} k_n^{-\frac{(1+C)^2}{2}} h(y)h(y^\prime) f(x,y) f(x^\prime,y^\prime) \dd x \dd y
-	\dd x^\prime \dd y^\prime \\
-	&= \bigO{1} k_n^{-\frac{(1+C)^2}{2}} \left(\int_\Rcal f(x,y) \dd x \dd y\right)^2 \\
-	&= \smallO{1} \int_{\mathcal{E}_\varepsilon(k_n)} \rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n)
-		h(y)h(y^\prime) f(x,y) f(x^\prime,y^\prime) \dd x \dd y.
-\end{align*}
-Therefore
-\begin{align*}
-	&\int_{\mathcal{E}_\varepsilon(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) h(y)h(y^\prime) f(x,y) f(x^\prime,y^\prime) 
-		\dd x \dd y	\dd x^\prime \dd y^\prime \\
-	&= (1+\smallO{1}) \int_{\mathcal{E}_\varepsilon(k_n)} \rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n)
-		h(y)h(y^\prime) f(x,y) f(x^\prime,y^\prime) \dd x \dd y,
-\end{align*}
-and the result follows by applying a concentration of heights argument twice.
-%Define $\delta_n = k_n^{-\frac{(1-\varepsilon)\varepsilon}{2}}$.
-Then, since $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\text{box}}(p,p^\prime)} \ge k_n^{\varepsilon}$ for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, a Chernoff bound (c.f.
-\eqref{eq:def_chernoff_bound_poisson}) implies that
-%\[
-%	\Prob{|X_3(p,p^\prime) - \Exp{X_i(p,p^\prime)}| > \delta_n \Exp{X_3(p,p^\prime)}} = \bigO{e^{-k_n^{\varepsilon}}},
-%\]
-%uniformly on $\mathcal{E}_\varepsilon(k_n)$. It now follows that
-%\begin{align*}
-%	&\hspace{-30pt}\sum_{t > \lfloor (1+\delta_n)\Exp{X_3(p,p^\prime)} \rfloor} \Prob{X_3(p,p^\prime) = t} 
-%		\Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}\\
-%	&\le \Prob{X_3(p,p^\prime) > (1+\delta_n)\Exp{X_3(p,p^\prime)} }\\
-%	&\le \Prob{\left|X_3(p,p^\prime) - \Exp{X_3(p,p^\prime)}\right| > \delta_n \Exp{X_3(p,p^\prime)}}\\
-%	&= \bigO{e^{-k_n^\varepsilon}},
-%\end{align*}
-%and similar for the sum over all $t < (1 - \delta_n) \Exp{X_3(p,p^\prime)}$. Hence if we define
-%\[
-%	A_n(p,p^\prime) = \left\{t : (1 - \delta_n) \Exp{X_3(p,p^\prime)} \le t \le (1+\delta_n)\Exp{X_3(p,p^\prime)}\right\},
-%\] 
-%then
-%\begin{align*}
-%	&\hspace{-20pt}\rho_{\text{box}}(p,p^\prime,k_n,k_n) \\
-%	&= \sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
-%		\Prob{X_2(p,p^\prime) = k_n - t} + \bigO{e^{-k_n^\varepsilon}}
-%		\numberthis \label{eq:joint_degrees_separation}
-%\end{align*}
-%
-%The idea for the remainder of the proof is to first remove the dependence on $p$ and $p^\prime$ in the summation over $t$ so that
-%\[
-%	\rho_{\text{box}}(p,p^\prime,k_n,k_n) = (1 + \smallO{1})\Prob{X_1(p,p^\prime) = k_n - t_n}
-%			\Prob{X_2(p,p^\prime) = k_n - t_n}
-%	+ \bigO{e^{-k_n^\varepsilon}},
-%\]
-%where $t_n = \smallO{k_n}$. Then, since $\Exp{X_1(p,p^\prime)} = \Mu{\BallPon{p}\setminus \BallPon{p^\prime}} = 
-%(1 + \smallO{1})\Mu{\BallPon{p}}$, by Lemma~\ref{lem:disjoint_neighbors_P_n_large}, and similar for $X_2$, the proof will follow by applying a concentration argument twice.
-%
-%To execute this plan we note that $\Exp{X_3(p,p^\prime)} = \Exp{\Ncal_{\text{box}}(p,p^\prime)}$.
-Now recall the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n}.
-Then, for $p,p^\prime \in \Kcal_{C}(k_n)$ we have that
-%\begin{align*}
-%	\phi_n(p,p^\prime) 
-%	&\le \frac{1 + 2\alpha}{4\alpha}\left(\frac{k_n^{1 + \varepsilon}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)} 
-%	- \left(1-\frac{(2\alpha - 1)\pi}{4\alpha}\right)e^{-(\alpha - \frac{1}{2})R_n}\\
-%	&\le \frac{1 + 2\alpha}{4\alpha}\left(\frac{k_n^{1 + \varepsilon}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
-%		=\bigT{k_n^{-\varepsilon(2\alpha - 1)}},
-%\end{align*}
-%where we used that $|x - x^\prime| \le \pi e^{R_n/2}$. In a similar fashion we get
-%\begin{align*}
-%	\phi_n(p,p^\prime) 
-%	&\ge \frac{1 + 2\alpha}{4\alpha}\left(\frac{\pi e^{R_n/2}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
-%		+ \frac{2\alpha - 1}{4\alpha} k_n^{1 + \varepsilon}e^{-\alpha R_n} - e^{-(\alpha - \frac{1}{2})R_n}\\
-%	&\ge \frac{1 + 2\alpha}{4\alpha}\left(\frac{\pi e^{R_n/2}}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
-%		- e^{-(\alpha - \frac{1}{2})R_n} = \bigT{k_n^{2\alpha - 1}n^{-(2\alpha - 1)}}.
-%\end{align*}
-%Therefore, since $\Mu{\BallPo{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$ for $p,p^\prime \in \Kcal_{C}(k_n)$, there exist two $n$-dependent constants 
-%\[
-%	b_n^- = \bigT{k_n^{2\alpha} n^{-(2\alpha - 1)}} \quad \text{and} \quad
-%	b_n^+ = \bigT{k_n^{1 - \varepsilon(2\alpha - 1)}}
-%\]
-%such that
-%\[
-%	A_n(p,p^\prime) \subseteq \left\{t \, : \, (1-\delta_n)b_n^- \le t \le (1+\delta_n)b_n^+ \right\} := B_n.
-%\]
-%If we now define
-%\begin{align*}
-%	t_n^- &= \arg \min_{t \in B_n} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t}\\
-%	t_n^+ &= \arg \max_{t \in B_n} \Prob{X_1(p,p^\prime) = k_n - t}\Prob{X_2(p,p^\prime) = k_n - t},
-%\end{align*}
-%then $t_n^\pm = \smallO{k_n}$ and we get
-%\begin{align*}
-%	&\hspace{-30pt}\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
-%		\Prob{X_2(p,p^\prime) = k_n - t}\\
-%	&\le \Prob{X_1(p,p^\prime) = k_n - t_n^+}\Prob{X_2(p,p^\prime) = k_n - t_n^+} 
-%		\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t}\\
-%	&= \Prob{X_1(p,p^\prime) = k_n - t_n^+}\Prob{X_2(p,p^\prime) = k_n - t_n^+}(1 + \smallO{1}).
-%		\numberthis \label{eq:joint_degrees_upper_bound}
-%\end{align*}
-%and similarly
-%\begin{align*}
-%	&\hspace{-30pt}\sum_{t \in A_n(p,p^\prime)} \Prob{X_3(p,p^\prime) = t} \Prob{X_1(p,p^\prime) = k_n - t}
-%		\Prob{X_2(p,p^\prime) = k_n - t}\\
-%	&\ge \Prob{X_1(p,p^\prime) = k_n - t_n^-}\Prob{X_2(p,p^\prime) = k_n - t_n^-}(1 + \smallO{1}).
-%		\numberthis \label{eq:joint_degrees_lower_bound}
-%\end{align*}
-%Next, it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large} that
-%\[
-%	\Mu{\BallPon{p}}(1 - \phi_n(p,p^\prime))\le \Exp{X_1(p,p^\prime)} \le \Mu{\BallPon{p}},
-%\]
-%where
-%\[
-%	\sup_{p,p^\prime \in \mathcal{E}_\varepsilon(k_n)} \phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
-%\]
-%This implies that on $\mathcal{E}_\varepsilon(k_n)$, $\mu_n^{(1)}(p) := \Exp{X_1(p,p^\prime)}$ satisfies the assumptions of Lemma~\ref{lem:concentration_argument_rho_approximation}.
-The same conclusion holds for $\mu_n^{(2)}(p^\prime)$.
-%Therefore, if we write $\hat{\rho}_n^{(i)}(p,k) := \Prob{X_i(p,p^\prime) = k - t_n^\pm}$, the second statement of the Lemma~\ref{lem:concentration_argument_rho_approximation} (applied twice) yields
-%\begin{align*}
-%	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \hat{\rho}_{n}^{(1)}(p,k_n) \hat{\rho}_{n}^{(2)}(p^\prime,k_n) h(y)h(y^\prime) 
-%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-%	&= (1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-%			f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
-%\end{align*}
-%Together with the approximation~\eqref{eq:joint_degrees_separation} and the bounds~\eqref{eq:joint_degrees_upper_bound} and~\eqref{eq:joint_degrees_lower_bound} we get
-%\begin{align*}
-%	&\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) h(y) h(y^\prime) f(x,y)
-%		f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-%	&=(1 + \smallO{1}) \int_{\mathcal{E}_{\varepsilon}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-%	&\hspace{10pt} + \bigO{1} e^{-k_n^{\varepsilon}} \int_{\mathcal{E}_{\varepsilon}(k_n)}
-%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,			
-%\end{align*}
-%and the result follows since the last term is of smaller order than the first.\\
-\vspace{5pt}
-
-%\noindent {\bf Case $\bm{k_n = \bigT{1}}$:}\\
-%This proof is very similar to the previous one. Here however, we write
-%\begin{align*}
-%	\rho_{\text{box}}(p,p^\prime,k_n,k_n) &= \Prob{X_1(p,p^\prime) + X_3(p,p^\prime) = k_n, X_2(p,p^\prime) + X_3(p,p^\prime) = k_n}\\
-%	&= \Prob{X_3(p,p^\prime) = 0}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} 
-%		+ \bigO{\Prob{X_3(p,p^\prime) \ge 1}}.
-%\end{align*}
-%By definition of $\mathcal{E}(k_n)$ and the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:common_neighbors_Pcal_n} we get that for $(p,p^\prime) \in \mathcal{E}(k_n)$
-%\[
-%	\Exp{X_3(p,p^\prime)} \le \bigT{1} \log(n)^{-(2\alpha - 1)} + \bigT{1}e^{-(\alpha - \frac{1}{2})R_n},
-%\]
-%where we used that in this case $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{1}$ and $|x-x^\prime| \le \bigT{1} e^{R_n/2}$. This implies that
-%\[
-%	\Prob{X_3(p,p^\prime) \ge 1} \le \Exp{X_{3}(p,p^\prime)} = \bigO{\log(n)^{-(2\alpha - 1)}},
-%\] 
-%Next we observe that by definition of $\mathcal{E}(k_n)$ the error function $\phi_n(p,p^\prime)$ from Lemma~\ref{lem:disjoint_neighbors_P_n_large} satisfies
-%\[
-%	\sup_{(p,p^\prime) \in \mathcal{E}(k_n)} \phi_n(p,p^\prime) = \bigO{\log(n)^{-(2\alpha - 1)}}.
-%\]
-%Therefore we can apply the exact same arguments as for the case $k_n \to \infty$ to obtain
-%\begin{align*}
-%	&\int_{\mathcal{E}(k_n)} \rho_n(y,y^\prime,k_n,k_N) h(y)h(y^\prime) 
-%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-%	&=(1+\smallO{1})\int_{\mathcal{E}(k_n)} \hspace{-5pt}\Prob{X_1(p,p^\prime) = k_n}\Prob{X_2(p,p^\prime) = k_n} h(y) h(y^\prime) 	
-%		f(x,y)f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-%	&\hspace{10pt}+ \bigO{1}\log(n)^{-(2\alpha - 1)} \int_{\mathcal{E}(k_n)}
-%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
-%	&= (1+\smallO{1})\int_{\mathcal{E}(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-%		f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime,
-%\end{align*}
-%where we used that
-%\[
-%	\log(n)^{-(2\alpha - 1)}\int_{\mathcal{E}(k_n)}
-%			f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime
-%\]
-%is of smaller order than
-%\[
-%	\int_{\mathcal{E}_(k_n)} \rho(y,k_n) \rho(y^\prime,k_n) h(y)h(y^\prime) 
-%			f(x,y)	f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime.
-%\]
+	\rho_{\text{box}}(p,p^\prime,k_n-t_n,k_n-t_n^\prime) &= \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k_n-t_n, X_2(p,p^\prime) + Y(p,p^\prime) = k_n - t_n^\prime}.
+\end{align*}
+Since by Lemma~\ref{cor:expected_common_neighbors_Ecal_set} $\Mu{\BallPon{p} \cup \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}$, it follows from Lemma~\ref{lem:near_independence_poisson} that
+\[
+	\rho_{\text{box}}(p,p^\prime,k_n-t_n,k_n-t_n^\prime) = (1+\smallO{1})\rho_{\text{box}}(p,k_n-t_n)\rho_{\text{box}}(p^\prime,k_n-t_n^\prime).
+\]
+The result then follows by applying Lemma~\ref{lem:finite_shifts_poisson} twice.
 \end{proof}
 
-Next we show that when $k_n \to \infty$ and the expected number of disjoint neighbors of $p$ and $p^\prime$ in $\Kcal_{C}(k_n)$ grows only slightly with $k_n$ then any fixed shift in the joint degree distribution does not effect its asymptotic behavior.
-
-\PvdH{@All: The proof of this lemma follows almost the exact same steps as that of the previous one. Is there any way we could merge them?}
-
-\begin{lemma}\label{lem:joint_degree_distribution_shift}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$, $k_n \to \infty$ and fix $\varepsilon > 0$.
-Then for any fixed $i, j, i^\prime, j^\prime \in \mathbb{Z}$ and $p, p^\prime \in \Kcal_{C}(k_n)$ such that $\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} \ge k_n^\varepsilon$,
-\[
-	\rho_n(p,p^\prime,k_n + i,k_n + i^\prime) 
-	= (1 + o(1))\rho_n(p,p^\prime, k_n + j,k_n + j^\prime)  \pm e^{-\Omega(k_n^\varepsilon)}.
-\]
-\end{lemma}
-
-\begin{proof}
-Define
-\begin{align*}
-	X_n = \left|\BallPon{p} \setminus \BallPon{p^\prime}\right|,\\
-	Y_n = \left|\BallPon{p} \cap \BallPon{p^\prime}\right|,\\
-	Z_n = \left|\BallPon{p^\prime} \setminus \BallPon{p}\right|.
-\end{align*}
-Then it follows that $X_n$, $Y_n$ and $Z_n$ are independent Poisson random variables satisfying $\Exp{X_n} + \Exp{Y_n} = \Mu{\BallPon{p}}$ and $\Exp{Z_n} + \Exp{Y_n} = \Mu{B_{\Pcal,n}(p^\prime)}$ while
-\begin{align*}
-	\rho_n(p,p^\prime,k_n + i,k_n + i^\prime) &= \Prob{X_n + Y_n = k + i, Z_n + Y_n = k + i^\prime}\\
-	&= \sum_{\ell = 0}^\infty \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell, Z_n = k + i^\prime - \ell} \\
-	&= \sum_{\ell = 0}^\infty \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell} \Prob{Z_n = k + i^\prime - \ell}.
-\end{align*}
-Next define $\delta_n = k_n^{-\frac{1-\varepsilon}{2}}$, let $n$ be large enough such that $0 < \delta_n < 1$ and note that by a Chernoff bound,
-\[
-	\Prob{|X_n - \Exp{X_n}| > \delta_n \Exp{X_n}} = \bigO{e^{-\frac{\delta_n^2}{4(1+\delta_n)} \Exp{X_n}}},
-\]
-and similar for $Y_n$ and $Z_n$. Finally, we define
-\begin{align*}
-	L_X(k_n) &= \left\{\ell : (1 - \delta_n) \Exp{X_n} \le k + i - \ell \le (1+\delta_n)\Exp{X_n}\right\} \\
-	L_y(k_n) &= \left\{\ell : (1 - \delta_n) \Exp{Y_n} \le \ell \le (1+\delta_n)\Exp{Y_n}\right\}\\
-	L_Z(k_n) &= \left\{\ell : (1 - \delta_n) \Exp{Z_n} \le k + i^\prime - \ell \le (1+\delta_n)\Exp{Z_n}\right\}
-\end{align*}
-We will now make distinguish between the cases $\Exp{Y_n} \le k_n/2$ and $\Exp{Y_n} > k_n/2$.
-
-Let us first assume that $\Exp{Y_n} \le k_n/2$. Then, since $p \in \Kcal_{\varepsilon}(k_n)$ and $\mu(\BallPon{p}) = \bigT{e^{y/2}} = \bigT{k_n}$ it follows that $\Exp{X_n} = \Omega(k_n)$ and hence
-\[
-	\Prob{|X_n - \Exp{X_n}| > \delta_n \Exp{X_n}} = \bigO{e^{-\frac{\delta_n^2}{4(1+\delta_n)} \Exp{X_n}}} = e^{-\Omega(k_n^{(1+\varepsilon)/2})} = e^{-\Omega(k_n^{\varepsilon})}.
-\]
-In particular, this implies
-\begin{align*}
-	&\hspace{-30pt}\sum_{\ell \notin L_X} \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell} 
-			\Prob{Z_n = k + i^\prime - \ell}\\
-	&= \bigO{\Prob{|X_n - \Exp{X_n}| > \delta_n \Exp{X_n}}} = e^{-\Omega(k_n^{(1+\varepsilon)/2})}.
-\end{align*}
-Finally we note that, for $\ell \in L_X$, we have
-\begin{equation}\label{eq:fraction_degree_prob}
-	\frac{\Prob{X_n = k + i - \ell}}{\Prob{X_n = k + j - \ell}} = \Exp{X_n}^{i - j} \frac{(k + j - \ell)!}{(k + i - \ell)!}
-	\le (1 + \delta_n)^{2|i - j|}.
-\end{equation}
-and observe that we have similar results for $Z_n$. Therefore,
-\begin{align*}
-	&\hspace{-30pt}\sum_{\ell \in L_X \cap L_Z} \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell} 
-		\Prob{Z_n = k + i^\prime - \ell} \\
-	&\le (1+\delta_n)^{2(j-i) + 2(j^\prime - i^\prime)} \sum_{\ell \in L_x \cap L_Z} 
-			\Prob{Y_n = \ell} \Prob{X_n = k + j - \ell} \Prob{Z_n = k + j^\prime - \ell}\\
-	&= (1+o(1))(1+\delta_n)^{2|i-j| + 2|i^\prime - j^\prime|}\Prob{D_p = k_n + j, D_{p^\prime} = k_n + j^\prime}\\
-	&= (1+o(1))\Prob{D_p = k_n + j, D_{p^\prime} = k_n + j^\prime}
-\end{align*}
-and hence
-\begin{align*}
-	\rho_n(p,p^\prime,k+i,k^\prime+i^\prime)
-	&= (1+o(1))\rho_n(p,p^\prime,k+j,k^\prime+j^\prime) + e^{-\Omega(k_n^\varepsilon)}.
-\end{align*}
-
-Now assume that $\Exp{Y_n} > k_n/2$.
-Then, since $\Exp{\left|\Ncal_{\text{box}}(p \Delta p^\prime)\right|} \ge k_n^{\varepsilon}$ it follows that $\Exp{X_n} = \Omega(k_n^\varepsilon)$ or $\Exp{Z_n} = \Omega(k_n^\varepsilon)$.
-Without loss of generality we assume that $\Exp{X_n} = \Omega(k_n^\varepsilon)$.
-Similar to \eqref{eq:fraction_degree_prob} we have for $Y_n$
-\[
-	\frac{\Prob{Y_n = \ell}}{\Prob{Y_n = \ell + j^\prime - i^\prime}} \le (1 + \delta_n)^{2(|i^\prime - j^\prime|)}.
-\]
-Using similar computations as above we then have
-\begin{align*}
-	&\hspace{-30pt}\rho_n(p,p^\prime,k+i,k^\prime+i^\prime) \\
-	&= \sum_{\ell \in L_X \cap L_Y} \Prob{Y_n = \ell} \Prob{X_n = k + i - \ell}
-		\Prob{Z_n = k + i^\prime - \ell}  + e^{-\Omega(k_n^{(1+\varepsilon)/2})}\\
-	&= (1+o(1))\rho_n(p,p^\prime,k+j,k^\prime+j^\prime) + e^{-\Omega(k_n^{(1+\varepsilon)/2})}.
-\end{align*}
-\end{proof}
-
-\subsection{Concentration for main triangle contribution}\label{ssec:concentration_tilde_T}
+\subsection{Concentration result for main triangle contribution}\label{ssec:concentration_tilde_T}
 
@@
 \[
-	\widetilde{T}_{\text{box}}(k,C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p)
+	\widetilde{T}_{\text{box}}(k_n,C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p)
 \]
@@
 \[
-	\widetilde{T}_{\text{box}}(k,C)^2 = \hspace{-5pt} \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k)}
-		\hspace{-3pt} \ind{D_{\Pcal,n}(p), \, D_{\Pcal,n}(p^\prime) = k} 
-		\sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in \Pcal_n \setminus (0,y)}^{\ne} \hspace{-3pt}
+	\widetilde{T}_{\text{box}}(k_n,C)^2 = \hspace{-5pt} \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k_n)}
+		\hspace{-3pt} \ind{\Dbox(p), \, \Dbox(p^\prime) = k_n} 
+		\sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in \Pcal_n}^{\ne} \hspace{-3pt}
 		\widetilde{T}_{\Pcal}(p,p_1,p_2) \widetilde{T}_{\Pcal}(p^\prime, p_1^\prime, p_2^\prime),
@@
 	I_{a,b} = \hspace{-3pt} \sum_{p, p^\prime \in \Pcal_n \cap \Kcal_C(k) \atop |\{p\} \cap \{p^\prime\}| = a}
-	\hspace{-5pt} \ind{D_{\Pcal,n}(p), \, D_{\Pcal,n}(p^\prime) = k} J_b(p,p^\prime),
+	\hspace{-5pt} \ind{\Dbox(p), \, \Dbox(p^\prime) = k_n} J_b(p,p^\prime),
 \]
@@
 \begin{equation}\label{eq:variance_T_I_00}
-	\Exp{I_{0,0}} = (1+\smallO{1})\Exp{\widetilde{T}_{\text{box}}(k_n)}^2
+	\Exp{I_{0,0}} = (1+\smallO{1})\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2
 \end{equation}
@@
 \begin{equation}\label{eq:variance_T_I_ab}
-	\Exp{I_{a,b}} = \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n)}^2}.
+	\Exp{I_{a,b}} = \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2}.
 \end{equation}
-Note that $J_{b}(p,p^\prime) \le J_{0}(p,p^\prime)$ and, since $I_{1,2} = \widetilde{T}_{\text{box}}(k_n,C)$, \eqref{eq:variance_T_I_ab} holds for $I_{1,2}$.
-
-To prove~\eqref{eq:transition_clustering_main_term} and~\eqref{eq:transition_clustering_error_term} we have to consider the cases $k_n = \bigT{1}$ and $k_n \to \infty$ separately.
+Note $I_{1,2} = \widetilde{T}_{\text{box}}(k_n,C)$ and since~\eqref{eq:scaling_exected_tilde_T} implies that $\Exp{\widetilde{T}_{\text{box}}(k_n,C)} \to \infty$, it follows that \eqref{eq:variance_T_I_ab} holds for $I_{1,2}$.
+
+Recall that $\Rcal(k_n,C) = [-I_n,I_n] \times \Kcal_{C}(k_n)$ and~\eqref{eq:def_joint_degree_set_E_growing_k}
+\[
+	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
+			\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}.
+\]
+Let $\mathcal{E}_\varepsilon(k_n)^c$ the same set but with $|x - x^\prime| \le k_n^{1 + \varepsilon}$ and denote by $I_{a,b}^\ast$ the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$.
+Will split the analysis between $I_{a,b}^\ast$ and $I_{a,b} - I_{a,b}^\ast$.
+The idea for these two cases is that by Lemma~\ref{lem:joint_degree_factorization} it follows that on the set $\mathcal{E}_\varepsilon(k_n)$ and for any uniformly bounded $t, t^\prime \in \mathbb{Z}$, the joint degree distribution factorizes,
+\[
+	\rho_{\text{box}}(p,p^\prime,k_n + t,k_n+t^\prime) = (1 + \smallO{1})\rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p,k_n).
+\]
+In particular this allows us to prove that $\Exp{I_{0,0}^\ast} = (1+\smallO{1})\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2$. 
+On the other hand, the expected number of points in $\mathcal{E}_\varepsilon(k_n)^c$ is $\bigO{k_n^{1+\varepsilon} k_n^{-2\alpha} \Exp{\Nbox(k_n)}} = \smallO{\Exp{\Nbox(k_n)}^2}$, where the latter is the expected number of points in $\Rcal(k_n,C) \times \Rcal(k_n,C)$.
+Hence we expect the contributions coming from $\mathcal{E}_\varepsilon(k_n)^c$ to be negligible.
+
+% and~\eqref{eq:variance_T_I_ab} we have to consider the cases $k_n = \bigT{1}$ and $k_n \to \infty$ separately.
 However, each case follows a similar strategy.
@@
 Throughout this proof we set $i = |\{p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\} \cap \BallPon{p}|$, $j = |\{p^\prime\} \cap \BallPon{p}|$ and define $i^\prime, j^\prime$ in a similar way by interchanging the primed and non-primed variables.
-In addition, we write $D_{\Pcal,n}(p,p^\prime,k,\ell)$ to denote the indicator that $|\BallPon{p} \cap (\Pcal_n \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = k$ and $|\BallPon{p^\prime} \cap (\Pcal_n \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = \ell$.
-Then,
-\begin{align*}
-	&\Exp{\ind{D_{\Pcal,n}(p) = k_n, D_{\Pcal,n}(p^\prime) = k_n} J_b(p,p^\prime)}\\
+In addition, we write $D_{\text{box}}(p,p^\prime,k,\ell)$ to denote the indicator that $|\BallPon{p} \cap (\Pcal_n \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = k$ and $|\BallPon{p^\prime} \cap (\Pcal_n \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = \ell$.
+Then, by the Campbell-Mecke formula
+\begin{align*}
+	&\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n} J_b(p,p^\prime)}\\
 	&= \Exp{\sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal_n 
 		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b}^{\ne}
-			\hspace{-7pt} D_{\Pcal,n}(p,p^\prime, k_n-i,k_n- i^\prime) \,
-			\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime, p_1^\prime, p_2^\prime)},
+			\hspace{-7pt} D_{\text{box}}(p,p^\prime, k_n-i,k_n- i^\prime) \,
+			\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime, p_1^\prime, p_2^\prime)}
 \end{align*}
@@
 
-%The prove is split over the two cases $k_n = \bigT{1}$ and $k_n \to \infty$. 
-%
-%\subsubsection*{The case $\bm{k_n = \bigT{1}}$}
-%
-%Take $a_n = 2\log\left((k_n + C\log(n))/\xi\right)$ and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}(k_n)$ as defined in~\eqref{eq:def_joint_degree_set_E_constant_k}.
-We will show that the expected difference between $I_{a,b}$ and $I_{a,b}^\ast$ is of smaller order than $\Exp{T_\Pcal(k_n)}^2$ so that we only need to consider $I_{a,b}^\ast$.
-%
-%Since 
-%\[
-%	|x - x^\prime| \le \left(e^{y/2} + e^{y^\prime/2}\right)\left(\frac{k_n + C \log(n)}{\xi}\right)
-%	= \bigO{\log(n)^2}
-%\] 
-%for all $p,p ^\prime \in \mathcal{E}_C(k_n)^c$, it follows that
-%\begin{align*}
-%	&\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} \\
-%	&\le \int_{\mathcal{E}_{C}(k_n)^c} 
-%		\Exp{\ind{D_{\Pcal,n}(p) = k_n - i, \, D_{\Pcal,n}(p^\prime) = k_n - i^\prime} J_b(p,p^\prime)}
-%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{\text{box}}(y,k_n) \Exp{J_b(p,p^\prime)}
-%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\le \int_{\mathcal{E}_{C}(k_n)^c} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p)}
-%		\Exp{\widetilde{T}_{\text{box}}(p^\prime)} 
-%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\le \bigO{\log(n)^2} \left(\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p)} 
-%		f_{\alpha, \nu}(x,y) \dd x \dd y\right)	
-%		\left(\int_0^{a_n} \Delta_\Pcal(y^\prime) e^{-\alpha y^\prime} \dd y^\prime\right) \\
-%	&= \bigO{\log(n)^2 s_\alpha(k_n) \Exp{T_\Pcal(k_n)}},
-%\end{align*}
-%where the last line follows from Corollary~\ref{cor:adjusted_triangle_counting_P_n} and Proposition~\ref{prop:asymptotics_Delta_y_P} which states that for all $0 < y^\prime \le a_n$, $\Delta_\Pcal(y^\prime) = \bigO{s_\alpha(k_n)}$.
-Next we note that $\Exp{T_\Pcal(k_n)} = \bigT{n k_n^{-(2\alpha - 1)} s_\alpha(k_n)}$, hence $\log(n)^2 s_\alpha(k_n) = \smallO{\Exp{T_\Pcal(k_n)}}$ and therefore we conclude that
-%\[
-%	\Exp{\left|I_{a,b} - I^\ast_{a,b}\right|} = \smallO{\Exp{T_\Pcal(k_n)}^2}.
-%\]
-%
-%We now proceed with computing $I_{a,b}^\ast$.
-For this we note that the parts of the neighborhoods $\BallPon{p}$ and $\BallPon{p^\prime}$ where $y_1, y_1^\prime \le h(p,p^\prime)$ are disjoint, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3}.
-In particular, this implies that when $b \ne 0$ this can only be if one of the $y_1, y_2, y_1^\prime, y_2^\prime$ exceeds $h(p,p^\prime)$.
-Now we observe that for $(p,p^\prime) \in \mathcal{E}(k_n)$ we have
-%\begin{align*}
-%	\int_{h(p,p^\prime)}^{R_n}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f(x_1,y_1) \dd x_1 \dd y_1
-%	&= \bigO{e^{y/2} e^{-(\alpha - \frac{1}{2})h(p,p^\prime)}}
-%		= \bigO{\log(n)^{-(2\alpha - 1)}},
-%\end{align*}
-%while
-%\begin{align*}
-%	\int_0^{h(p,p^\prime)}\int_{-I_n}^{I_n} \ind{p_1 \in \BallPon{p}} f(x_1,y_1) \dd x_1 \dd y_1
-%	&= \bigO{1}.
-%\end{align*} 
-%Hence if $b \ne 0$ then it follows that $\Exp{J_b} = \bigO{\log(n)^{-(2\alpha - 1)}}$ and we conclude that 
-%\[
-%	\Exp{I_{a,b}} = \bigO{n^2 \log(n)^{-(2\alpha - 1)}} = \smallO{\Exp{T_\Pcal(k_n)}^2}
-%\]
-%
-%For $I_{0,0}^\ast$ we define
-%\[
-%	\mathcal{J}_1^\ast = \int_{\Rcal^2} \ind{0\le y_1, y_2 \le h(p,p^\prime)} \widetilde{T}_{\text{box}}(p,p_1,p_2) 
-%			f(x_1,y_1)	f(x_2,y_2) \dd x_2 \dd x_1 \dd y_2 \dd y_1
-%\] 
-%and define $\mathcal{J}_2^\ast$ in a similar way by interchanging the primed and non-primed variables. Then we get
-%\[
-%	\Exp{J_0(p,p^\prime)} = \mathcal{J}_1^\ast \mathcal{J}_2^\ast + \bigO{\log(n)^{-(2\alpha - 1)}}.
-%\]
-%In addition, for $(p,p^\prime) \in \mathcal{E}(k_n)$ Corollary~\ref{cor:adjusted_triangle_counting_P_n} implies that 
-%\[
-%	\mathcal{J}_1^\ast = (1+\smallO{1})\Exp{\widetilde{T}_{\text{box}}(p)} = (1 + \smallO{1})\binom{k_n}{2} \Delta_\Pcal(y),
-%\] 
-%and similar for $\mathcal{J}_2^\ast$, while Lemma~\ref{lem:joint_degree_factorization} states that
-%\begin{align*}
-%	&\hspace{-30pt}\int_{\mathcal{E}(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
-%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&= (1+\smallO{1})\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f(x,y) \dd x \dd y\right)^2.
-%\end{align*}
-%We therefore conclude that
-%\begin{align*}
-%	\Exp{I_{0,0}^\ast} 
-%	&= \int_{\mathcal{E}(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) \Exp{J_0(p,p^\prime)}
-%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y \\
-%	&= \int_{\mathcal{E}(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n) \Delta_\Pcal(y) \Delta_\Pcal(y^\prime)
-%		f(x,y) f_{\alpha, \nu}(x^\prime, y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
-%	&\hspace{10pt}+ \bigO{\log(n)^{-(2\alpha - 1)}n^2} \\
-%	&= (1 + \smallO{1}) \binom{k_n}{2}^2 
-%		\left(\int_{\Kcal_C(k_n)} \rho(y,k_n) \Delta_\Pcal(y) f(x,y) \dd x \dd y\right)^2 \\
-%	&= (1 + \smallO{1})\Exp{T_\Pcal(k_n)}^2,
-%\end{align*}
-%which finishes the proof for $k_n = \bigT{1}$
-
-Recall the definition of $\mathcal{E}_\varepsilon(k_n)$
-\[
-	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
-	\, : \, \Exp{\left|\Ncal_{\text{box}}^c(p,p^\prime)\right|} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}
-\]
-let $\mathcal{E}_\varepsilon(k_n)^c$ denote its complement and let $I_{a,b}^\ast$ denote the the part of $I_{a,b}$ where $p,p^\prime \in \Pcal_n \cap \mathcal{E}_\varepsilon(k_n)$. We first show that
+We will now proceed to establish \eqref{eq:variance_T_I_00} and \eqref{eq:variance_T_I_ab}.
+
+\paragraph{Computing $\bm{I_{0,0}}$}
+We first show that
 \begin{equation}\label{eq:I_ab_ast_main}
-	\Exp{I_{a,b} - I_{a,b}^\ast} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
+	\Exp{I_{0,0} - I_{0,0}^\ast} = \smallO{\Exp{T_{\text{box}}(k_n,C)}^2},
 \end{equation}
 so that for the remainder of the proof we only need to consider $p, p^\prime \in \mathcal{E}_\varepsilon(k_n)$ and hence, we can apply Lemma \ref{lem:joint_degree_factorization}.
-For this we note that by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\text{box}}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$.
+
+%For this we note that by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\text{box}}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$.
 In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)^c$.
 Therefore, we have
-\begin{align*}
-	&\Exp{I_{a,b} - I_{a,b}^\ast}\\
-	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
-		\Exp{J_b(p,p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
-	&\le \int_{\Kcal_C(k_n)^2 \setminus \mathcal{E}_\varepsilon(k_n)} \rho(p, p^\prime, k - i, k - i^\prime) 
-		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
-	&= \bigO{\int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}} \rho_{y}(k) 
-		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy}\\
-	&= \bigO{k_n^{1+\varepsilon} \binom{k_n}{2} \left(\int_{a_n^-}^{a_n^+} \Delta_{\Pcal}(y^\prime) 
-			e^{-\alpha y^\prime} \, dy^\prime\right) \Exp{T_{\Pcal,n}(k_n)}}\\
-	&= \bigO{k_n^{3 + \varepsilon -2\alpha} s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}}\\
-	&= \smallO{n k_n^{-(2\alpha - 1)}s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}} = \smallO{\Exp{T_{\Pcal,n}(k_n)}^2},
-\end{align*}
-which proves \eqref{eq:I_ab_ast_main}. Here we used that $k_n^{2 + \varepsilon} = \smallO{n}$ and $\Exp{T_{\Pcal,n}(k_n)} = \bigT{n k_n^{-(2\alpha + 1)}s_\alpha(k_n)}$ for the last line.
-
-We will now proceed to establish \eqref{eq:variance_T_I_00} and \eqref{eq:variance_T_I_ab}. We start with $I_{0,0}^\ast$
-
-By Lemma~\ref{lem:joint_degree_distribution_shift} 
-\[
-	\rho_(p,p^\prime, k_n-i,k_n-i^\prime) = (1+o(1))\rho(p,p^\prime, k_n-j,k_n-j^\prime) 
-	= (1+o(1))\rho_{\text{box}}(p, p^\prime, k_n, k_n)
-\]
-which now no longer depends on the other four points $p_1, p_2, p_1^\prime, p_2^\prime$. Hence, using the Campbell-Mecke formula, we get
-\[
-	\Exp{I_{0,0}^\ast} = (1 + \smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{\text{box}}(p,p^\prime,k_n, k_n)
-		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y)
-		f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
-\]
-
-Next, by Corollary~\ref{cor:adjusted_triangle_counting_P_n} we have for $y \in K_C(k_n)$,
-\[
-	\Exp{\widetilde{T}_{\text{box}}(p)} = (1+\smallO{1})\Exp{\widetilde{T}_{\Pcal}(p)} = (1 + \smallO{1}) \binom{k_n}{2} \Delta_{\Pcal}(y)
-\] 
-and similar for $p^\prime$. Hence, by Lemma~\ref{lem:joint_degree_factorization} 
-\begin{align*}
-	&\hspace{-10pt}(1 + \smallO{1})\int_{\mathcal{E}_\varepsilon(k_n)} \rho_n(p, p^\prime, k_n, k_n)
-		\Exp{\widetilde{T}_{\text{box}}(p)}\Exp{\widetilde{T}_{\text{box}}(p^\prime)} f(x,y)
-		f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
-	&= (1+\smallO{1})\binom{k_n}{2}^2 \int_{\mathcal{E}_\varepsilon(k_n)} 
-		\rho(y, k_n) \rho(y^\prime, k_n) \Delta_{\Pcal}(y) \Delta_\Pcal(y^\prime) 	f(x,y) 
-		f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
-	&= (1+\smallO{1}) \left( \binom{k_n}{2} \int_{a_n^-}^{a_n^+}\int_{I_n} \rho(y,k_n)
-		\Delta_{\Pcal}(y) f(x,y) \, dx \, dy\right)^2\\
-	&= (1 + \smallO{1})\left(\Exp{\widetilde{T}_{\text{box}}(k_n,C)}\right)^2,
-\end{align*}
-which proves \eqref{eq:variance_T_I_00}.
-
-Next we consider $I_{0,1}^\ast$. The proofs for the other two cases $I_{1,1}^\ast$ and $I_{0,2}^\ast$ follow using similar arguments and hence we omit them here.
-
-Without loss of generality we will assume that $p_1 = p_1^\prime$.
-Notice that now $i = |\{p^\prime, p_1, p_2, p_2^\prime\} \cap \BallPon{p}|$ and $j = |\{p^\prime\} \cap \BallPon{p}|$ and $i^\prime$, $j^\prime$ are defined, similarly, by interchanging the primed and non-primed variables.
-Then, if we define
-\[
-	T^{(0,1)}_{\Pcal,n}(p,p^\prime) = \sum_{(p_1,p_2) \in 2^{\Pcal_n}} \sum_{p_2^\prime \in \Pcal_n} \widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime,p_1,p_2^\prime),
-\]
-we have
-\begin{align*}
-	\Exp{I_{0,1}^\ast} &= (1+\smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)} \rho_n(p,p^\prime,k_n,k_n)
-			\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)} f(x,y)
-			f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy,
-\end{align*} 
-where we again used Lemma  \ref{lem:joint_degree_distribution_shift}.
-We will show that 
-\[
-	\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)} = \smallO{k_n^4 s_\alpha(k_n)^2},
-\] 
-from which \eqref{eq:variance_T_I_ab} follows since $k_n^4 s_\alpha(k_n)^2 = \bigO{\Exp{\widetilde{T}_{\text{box}}(p)} \Exp{\widetilde{T}_{\text{box}}(p^\prime)}}$ on $\Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$.
-
-First we consider the contribution coming from $y_1 > 4 \log(k_n)$.
-Since the integration of $T_\Pcal(p,p_1,p_2) T_\Pcal(p^\prime,p_1,p_2^\prime)$ over $x_1, x_2$ and $x_2^\prime$ is bounded by $\bigO{e^{y}e^{\frac{y^\prime}{2}} e^{\frac{y_1 + y_2 + y_2^\prime}{2}}}$ it follows that contribution to $\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)}$ is bounded by
-\begin{align*}
-	\bigO{e^{y}e^{\frac{y^\prime}{2}} \int_{4\log(k_n)}^{a_n^+} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}
-	&= \bigO{k_n^3 \int_{4\log(k_n)}^{a_n^+} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}\\
+For $J_0$ we have, using Lemma [??]
+\begin{align*}
+	&\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n} J_0(p,p^\prime)}\\
+	&= \Exp{\sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal \setminus p,p^\prime 
+		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = 0}^{\ne}
+		\hspace{-7pt} D_{\text{box}}(p,p^\prime, k_n-i,k_n- i^\prime) \,
+		\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime, p_1^\prime, p_2^\prime)}\\
+	&= \Exp{D_{\text{box}}(p,p^\prime, k_n-j-2,k_n- j^\prime-2) \, \sum_{p_1,p_2 \in \Pcal \setminus p}^{\ne} 
+		\widetilde{T}_{\text{box}}(p,p_1,p_2)
+		\sum_{p_1^\prime,p_2^\prime \in \Pcal \setminus p^\prime}^{\ne} 
+			\widetilde{T}_{\text{box}}(p^\prime,p_1^\prime,p_2^\prime)}\\
+	&= (1+\smallO{1})\rho_{\text{box}}(p,p^\prime,k_n,k_n) \CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n}
+		\CExp{\widetilde{T}_{\text{box}}(p^\prime)}{\Dbox(p^\prime) = k_n},
+\end{align*}
+Next we recall that for all $y^\prime \in \Kcal_{C}(k_n)$, 
+\[
+	\CExp{\widetilde{T}_{\text{box}}(p^\prime)}{\Dbox(p^\prime) = k_n} = \binom{k_n}{2} \Mu{\BallPon{p^\prime}}^{-2} \Exp{\widetilde{T}_{\text{box}}(p^\prime)} = \bigO{1}k_n^2 P(y^\prime),
+\] 
+where we used that $\Exp{\widetilde{T}_{\text{box}}(p^\prime)} = (1+\smallO{1}) k_n^2 P(y^\prime)$, for all $y^\prime \in \Kcal_{C}(k_n)$.
+Therefore, using that $\rho_{\text{box}}(p,p^\prime,k_n,k_n) \le \rho_{\text{box}}(p,k_n)$,
+\begin{align*}
+	&\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n} J_0(p,p^\prime)}\\
+	&\le \bigO{k_n^2} \rho_{\text{box}}(p,k_n) \CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n} P(y^\prime)
+\end{align*}
+and thus
+\begin{align*}
+	&\Exp{I_{0,0} - I_{0,0}^\ast}\\
+	&= \int_{\mathcal{E}_\varepsilon(k_n)^c}
+		\Exp{\ind{\Dbox(p), \Dbox(p^\prime) = k_n} J_0(p,p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+%	&= \int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}}
+%		\Exp{\ind{\Dbox(p), \Dbox(p^\prime) = k_n} J_0(p,p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+	&\le \bigO{k_n^2} k_n^{1+\varepsilon} \left(\int_{a_n^-}^{a_n^+} P(y^\prime) 
+		e^{-\alpha y^\prime} \, dy^\prime\right) \Exp{\widetilde{T}_{\text{box}}(k_n,C)}\\
+	&= \bigO{k_n^{3 + \varepsilon -2\alpha} s_\alpha(k_n) \Exp{\widetilde{T}_{\text{box}}(k_n,C)}}\\
+	&= \smallO{n k_n^{-(2\alpha - 1)}s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}} 
+		= \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2},
+\end{align*}
+which proves \eqref{eq:I_ab_ast_main}. Here we used that $k_n^{2 + \varepsilon} = \smallO{n}$ and
+\[
+	\Exp{\widetilde{T}_{\text{box}}(k_n,C)} = \bigT{\Exp{\widetilde{T}_{\text{box}}(k_n)}} 
+	= \bigT{n k_n^{-(2\alpha - 1)}s_\alpha(k_n)}
+\] 
+for the last line.
+
+We will now show that
+\[
+	\Exp{I^\ast_{0,0}} = (1+\smallO{1})\Exp{\Exp{T_{\text{box}}(k_n,C)}^2}.
+\]
+We recall that for $(p,p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)$ and any two uniformly bounded $t, t^\prime \in \mathbb{Z}$,
+\[
+	\rho_{\text{box}}(p,p^\prime,k_n + t,k_n+t^\prime) = (1 + \smallO{1})\rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p,k_n).
+\]
+Therefore, by defining $h(y) = \CExp{\widetilde{T}_{\text{box}}(y)}{\Dbox(y) = k_n}$
+\[
+	\Exp{I_{0,0}^\ast} = (1 + \smallO{1})\int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{\text{box}}(p,k_n)
+		\rho_{\text{box}}(p^\prime,k_n)
+		h(y) h(y^\prime) f(x,y)	f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy.
+\]
+The difference with $\Exp{\Exp{T_{\text{box}}(k_n,C)}^2}$ is in that the above integral is over $\mathcal{E}_\varepsilon(k_n)$ instead of $\Rcal(k_n,C) \times \Rcal(k_n,C)$.
+Since the difference between the two sets is
+$\mathcal{E}_\varepsilon(k_n)^c$ and $n k_n^{1+\varepsilon} = \smallO{n^2}$ it follows that
+\begin{align*}
+	&\Exp{\Exp{T_{\text{box}}(k_n,C)}^2}
+		- \int_{\mathcal{E}_{\varepsilon}(k_n)}\rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n)
+		h(y) h(y^\prime) f(x,y)	f(x^\prime,y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+	&= \int_{\mathcal{E}_{\varepsilon}(k_n)^c}\rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n)
+		h(y) h(y^\prime) f(x,y)	f(x^\prime,y^\prime) \dd x^\prime \dd x \dd y^\prime \dd y\\
+	&= \bigO{k_n^{1+\varepsilon}n} 
+		\left(\int_{\Kcal_{C}(k_n)}h(y)\rho_{\text{box}}(y,k_n)\alpha e^{-\alpha y} \dd y\right)^2
+		= \smallO{\Exp{\Exp{T_{\text{box}}(k_n,C)}^2}}.
+\end{align*}
+Thus we conclude that $\Exp{I^\ast_{0,0}} = (1+\smallO{1})\Exp{\Exp{T_{\text{box}}(k_n,C)}^2}$, which finishes the proof of \eqref{eq:variance_T_I_00}.
+
+\paragraph{Computing $\bm{\Exp{I_{0,1}}}$}
+
+We first write
+\begin{equation}\label{eq:bound_E_J1}
+	\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n} J_1}
+	\le \bigO{1} k_n \rho_{\text{box}}(p,p^\prime,k_n,k_n)\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox{p} = k}
+\end{equation}
+Then, using that $\rho_{\text{box}}(p,p^\prime,k_n,k_n) \le \rho_{\text{box}}(p,k_n)$,
+\begin{align*}
+	&\Exp{I_{0,1} - I_{0,1}^\ast}\\
+	&\int_{\mathcal{E}_\varepsilon(k_n)^c}
+		\Exp{\ind{\Dbox(p), \Dbox(p^\prime) = k_n} J_1(p,p^\prime)} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+	&= k_n \int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}}
+		\rho_{\text{box}}(p,k_n)\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox{p} = k} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+	&\le \bigO{k_n^{2+\varepsilon}} \left(\int_{a_n^-}^{a_n^+} e^{-\alpha y^\prime} \, dy^\prime\right) 
+		\Exp{\widetilde{T}_{\text{box}}(k_n,C)}\\
+	&= \bigO{k_n^{2 + \varepsilon - 2\alpha} \Exp{\widetilde{T}_{\text{box}}(k_n,C)}}.
+\end{align*}
+Recall that $\Exp{\widetilde{T}_{\text{box}}(k_n,C)} = \bigT{n k_n^{-(2\alpha - 1)}s(k_n)}$.
+Therefore to show that $\Exp{I_{0,1} - I_{0,1}^\ast} = \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2}$ it suffices to show that $k_n^{2 + \varepsilon - 2\alpha} = \smallO{n k_n^{-(2\alpha - 1)}s(k_n)}$.
+When $\frac{1}{2} < \alpha \le \frac{3}{4}$ we have
+\[
+	\frac{4\alpha - 1 + \varepsilon}{2\alpha + 1} < 1,
+\]
+for $\varepsilon$ small enough. Hence
+\[
+	n^{-1} k_n^{2\alpha - 1} s(k_n)^{-1} k_n^{2 + \varepsilon -2\alpha} = k_n^{4\alpha - 1 + \varepsilon} 
+	= \smallO{n^{-1}n^{\frac{4\alpha - 1 + \varepsilon}{2\alpha + 1}}} = \smallO{1}
+\]
+When $\alpha \ge \frac{3}{4}$,
+\[
+	n^{-1} k_n^{2\alpha - 1} s(k_n)^{-1} k_n^{2 + \varepsilon -2\alpha} = \bigO{\log(k_n)} n^{-1} k_n^{2 + \varepsilon} = \smallO{1},
+\]
+for $\varepsilon$ small enough.
+
+For $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ we assume without loss of generality that $p_1^\prime = p_1 = (x_1,y_1)$, i.e.
+\[
+	J_{0,1} = \sum_{(p_1, p_2) \in \Pcal \setminus p}^{\ne} \widetilde{T}_{\text{box}}(p,p_1,p_2) 
+	\sum_{p_2^\prime \in \Pcal \setminus \{p^\prime, p_1\}} \widetilde{T}_{\text{box}}(p^\prime,p_1,p_2^\prime). 
+\] 
+Now let $Z_{0,1}$ denote the part of $J_{0,1}$ where $y_1 \le 4\log(k_n)$ and $y_2, y_2^\prime \le \varepsilon \log(k_n)$.
+
+We first analyze $\CExp{Z_{0,1}}{\Dbox(p), \Dbox(p^\prime) = k_n}$. When $y_1 \le 4\log(k_n)$ and both $y_2, y_2^\prime \le \varepsilon \log(k_n)$ we have that
+\[
+	|x_2 - x_2^\prime| \le |x_1 - x_2| + |x_1 - x_2^\prime| \le e^{\frac{y_1}{2}}\left(e^{\frac{y_2}{2}} + e^{\frac{y_2^\prime}{2}}\right) \le 2k_n^{2+\varepsilon}
+\]
+whenever $\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime,p_1,p_2^\prime) > 0$ while both $|x - x_2|, |x^\prime - x_2^\prime| = \bigO{k_n^{1 + \varepsilon}}$.
+Hence it follows that $\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime,p_1,p_2^\prime) > 0$ implies that
+\[
+	|x - x^\prime| \le |x - x_2| + |x_2 - x_2^\prime| + |x_2^\prime - x^\prime| = \bigO{k_n^{2 + \varepsilon}}.
+\]
+Next, by integrating only over $x_2^\prime$ and $y_2^\prime $ we get that $\CExp{Z_{0,1}}{\Dbox(p), \Dbox(p^\prime) = k_n}$ 
+\begin{align*}
+	\CExp{Z_{0,1}}{\Dbox(p), \Dbox(p^\prime) = k_n} &=
+	\bigO{e^{\frac{y^\prime}{2}}\ind{|x-x^\prime|\le k_n^{2 + \varepsilon}} 
+		\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) =k_n}}\\
+	&= \bigO{k_n \CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) =k_n}}.
+\end{align*}
+Thus
+\begin{align*}
+	&\int_{\mathcal{E}_\varepsilon(k_n)} \rho_{\text{box}}(p,p^\prime,k_n,k_n)
+		\CExp{Z_{0,1}}{\Dbox(p), \Dbox(p^\prime) = k_n} f(x,y) f(x^\prime,y^\prime) \dd x \dd y \dd x^\prime \dd y^\prime\\
+	&= \bigO{k_n^{3+\varepsilon}} \Exp{\widetilde{T}_{\text{box}}(k_n,C)} 
+		\int_{\Kcal_{C}(k_n)}\rho_{\text{box}}(y^\prime,k_n) e^{-\alpha y^\prime} \dd y^\prime\\
+	&= \bigO{k_n^{2+\varepsilon} k_n^{-2\alpha} \Exp{\widetilde{T}_{\text{box}}(k_n,C)} } 
+		= \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2}, 
+\end{align*}
+where the last line follow from the analysis done for $\Exp{I_{0,0}-I_{0,0}^\ast}$.
+
+It now remains to consider $J_{0,1} - Z_{0,1} := Z_{0,1}^\ast$. We will show that 
+\begin{equation}\label{eq:expectation_J01}
+	\CExp{Z_{0,1}^\ast}{\Dbox(p), \Dbox(p^\prime) = k_n} = \smallO{k_n^4 s(k_n)^2}.
+\end{equation} 
+Using that the joint degree distribution factorizes on $\mathcal{E}_\varepsilon(k_n)$ this then implies that
+\begin{align*}
+	\Exp{I_{0,1}^\ast}
+%	&= \bigO{1} \int_{\mathcal{E}_\varepsilon(k_n)} \rho_{\text{box}}(p,k_n) \rho_{\text{box}}(p^\prime,k_n) \CExp{J_{0,1}}{\Dbox(p), \Dbox(p^\prime) = k_n} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy \\
+	&= \smallO{k_n^4 s(k_n)^2} \left(\int_{\Rcal(k_n,C)} \rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y \right)^2\\ 
+	&= \smallO{\left(n s(k_n) k_n^{-2\alpha + 1}\right)^2} = \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2},
+\end{align*}
+which finished the proof of~\eqref{eq:variance_T_I_ab} for $a = 0, b = 1$.
+
+We first consider the part with $y_1 > 4\log(k_n)$.
+Since the integration over $x_1, x_2$ and $x_2^\prime$ of $\CExp{Z_{0,1}^\ast}{\Dbox(p), \Dbox(p^\prime) = k_n}$ is bounded by $\bigO{e^{y}e^{\frac{y^\prime}{2}}}$ we get that the contribution to $\CExp{Z_{0,1}^\ast}{\Dbox(p), \Dbox(p^\prime) = k_n}$ with $y > 4\log(k_n)$ and $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ is
+\begin{align*}
+	\bigO{e^{y}e^{\frac{y^\prime}{2}} \int_{4\log(k_n)}^{R} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}
+	&= \bigO{k_n^3 \int_{4\log(k_n)}^{R} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1}\\
 	&= \bigO{k_n^{3 - (4\alpha - 2)}} = \smallO{k_n^4 s_\alpha(k_n)^2}.
 \end{align*}
-
-To deal with the case where $y_1 \le 4\log(k_n)$ we define $b_n = 2\varepsilon\log(k_n))$ and will consider different cases for $\Exp{T^\ast_{\Pcal,n}(p,p^\prime)}$, depending on whether $y_2 \le b_n$ or $y_2 > b_n$ and similar for $y_2^\prime$.
-
-When $y_1 \le 4\log(k_n)$ and $y_2 > b_n$, the contribution to $\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)}$ is bounded by
+Here the last step follows since for $\frac{1}{2} < \alpha < \frac{3}{4}$
+\[
+	k_n^{3 - (4\alpha - 2) - 4} s(k_n)^{-2} 
+	= k_n^{3 - (4\alpha - 2) - 4 + 2(4\alpha - 2)} = k_n^{-5 + 4\alpha} = \smallO{1},
+\]
+while for $\alpha = \frac{3}{4}$
+\[
+	k_n^{3 - (4\alpha - 2) - 4} s(k_n)^{-2} 
+	= \bigO{\log(k_n)^{-2}} k_n^{3 - (4\alpha - 2) - 2} = \bigO{\log(k_n)^{-2}} = \smallO{1},
+\]
+and for $\alpha > \frac{3}{4}$
+\[
+	k_n^{3 - (4\alpha - 2) - 4} s(k_n)^{-2} = k_n^{3 - (4\alpha - 2) - 2} = \smallO{1}.
+\]
+
+Next we consider the case where $y_1 \le 4\log(k_n)$ and at least one of $y_2, y_2^\prime$ is larger than $\varepsilon \log(k_n)$.
+Due to symmetry it is enough to consider the case with $y_2 > \varepsilon \log(k_n)$.
+Here the contribution to $\CExp{Z_{0,1}^\ast}{\Dbox(p), \Dbox(p^\prime) = k_n}$ is
 \begin{align*}
 	\Exp{\widetilde{T}_{\text{box}}(p)}
-		\bigO{e^{\frac{y^\prime}{2}}\int_{b_n}^{a_n^+} e^{-(\alpha -\frac{1}{2})y_2} \, dy_2}
-	&= \bigO{k_n^{1 - \varepsilon}}\Exp{\widetilde{T}_{\text{box}}(p)}
-	= \smallO{k_n^4 s_\alpha(k_n)^2}.
-\end{align*}
-Due to the symmetry in $p_2$ and $p_2^\prime$ the same results holds for the cases where $y_2 > b_n$.
-
-Finally, when $y_1 \le 4\log(k_n)$ and both $y_2, y_2^\prime \le b_n$ we have that
-\[
-	|x_2 - x_2^\prime| \le |x_1 - x_2| + |x_1 - x_2^\prime| \le e^{\frac{y_1}{2}}\left(e^{\frac{y_2}{2}} + e^{\frac{y_2^\prime}{2}}\right) \le 2k_n^{2+\varepsilon}
-\]
-whenever $T_\Pcal(p,p_1,p_2) T_\Pcal(p^\prime,p_1,p_2^\prime) > 0$ while both $|x - x_2|, |x^\prime - x_2^\prime| = \bigO{k_n^{1 + \varepsilon}}$. Hence it follows that
-\[
-	|x - x^\prime| \le |x - x_2| + |x_2 - x_2^\prime| + |x_2^\prime - x^\prime| = \bigO{k_n^{2 + \varepsilon}}.
-\]
-Next, by integrating only over $x_2^\prime$ and $y_2^\prime $ we get the contribution to $\Exp{T^{(0,1)}_{\Pcal,n}(p,p^\prime)}$ for this regime is bounded by
-\[
-	\bigO{e^{\frac{y^\prime}{2}} \Exp{\widetilde{T}_{\text{box}}(p)}}
-	= \bigO{k_n \Exp{\widetilde{T}_{\text{box}}(p)}} = \smallO{k_n^4 s_\alpha(k_n)^2}.
-\]
-
-%\paragraph{III) $\bm{I_{0,2}^\ast}$:}
-%
-%\paragraph{IV) $\bm{I_{1,1}^\ast}$:}
+		\bigO{e^{\frac{y^\prime}{2}}\int_{\varepsilon \log(k_n)}^{R} e^{-(\alpha -\frac{1}{2})y_2} \, dy_2}
+	&= \bigO{k_n^{1 - \varepsilon(\alpha -\frac{1}{2})}}\Exp{\widetilde{T}_{\text{box}}(p)}\\
+	&= \bigO{k_n^{3 - \varepsilon(\alpha -\frac{1}{2})} s(k_n)} = \smallO{k_n^4 s(k_n)^2}.
+\end{align*}
+The last line follows since $k_n^{-1} = \smallO{s(k_n)}$ for $\frac{1}{2} < \alpha < \frac{3}{4}$ and $k_n^{-1} = \bigO{s(k_n)}$ for $\alpha \ge \frac{3}{4}$.
+
+\paragraph{Computing $\bm{\Exp{I_{0,2}}}$} In this case we have
+\[
+	\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n}J_2} = (1+\smallO{1})\rho_{\text{box}}(p,p^\prime,k_n,k_n)
+	\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n}.
+\]
+We then use that $\rho_{\text{box}}(p,p^\prime,k_n,k_n) \le \rho_{\text{box}}(p,k_n)$ to obtain
+\begin{align*}
+	\Exp{I_{0,2}-I_{0,2}^\ast} 
+	&= \bigO{k_n^{1+\varepsilon}} \left(\int_{\Kcal_{C}(k_n)} e^{-\alpha y^\prime} \dd y^\prime\right) 
+		\Exp{\widetilde{T}_{\text{box}}(k_n,C)}\\
+	&= \bigO{k_n^{\varepsilon -(2\alpha - 1)}}\Exp{\widetilde{T}_{\text{box}}(k_n,C)}
+		= \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}
+\end{align*}
+were the last line follows since $\Exp{\widetilde{T}_{\text{box}}(k_n,C)} = \bigT{n k_n^{-(2\alpha - 1)}s(k_n)}$ and $k_n^{\varepsilon}n^{-1} = \smallO{s(k_n)}$.
+
+For the other term we use that the degree distribution factorizes. This gives
+\begin{align*}
+	\Exp{I_{0,2}^\ast} 
+	&= \bigO{1}\left(\int_{\Rcal(k_n,C)} \rho_{\text{box}}(y^\prime,k_n) f(x^\prime,y^\prime) 
+		\dd x^\prime \dd y^\prime \right)\Exp{\widetilde{T}_{\text{box}}(k_n,C)}\\
+	&= \bigO{n k_n^{-(2\alpha + 1)}}\Exp{\widetilde{T}_{\text{box}}(k_n,C)}
+		= \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2},
+\end{align*}
+where we use that $k_n^{-2} = \smallO{s(k_n)}$.
+
+\paragraph{Computing $\bm{\Exp{I_{1,1}}}$}
+
+Using~\eqref{eq:expectation_J01} we get
+\begin{align*}
+	\Exp{I_{1,1}}
+	&= \bigO{k_n} \int_{\Rcal(k_n,C)} \rho_{\text{box}}(y,k_n) \CExp{\widetilde{T}_{\text{box}}}{\Dbox(p) = k_n}
+		f(x,y) \dd x \dd y\\
+	&= \bigO{k_n}\Exp{\widetilde{T}_{\text{box}}(k_n,C)}.
+\end{align*}
+Now observe that for $\frac{1}{2} < \alpha < \frac{3}{4}$
+\[
+	k_n n^{-1} n^{-1} k_n^{-(2\alpha -1)} s(k_n)^{-1} = k_n^{6\alpha - 2} n^{-1}
+	= \bigO{n^{\frac{4\alpha - 3}{2\alpha + 1}}} = \smallO{1},
+\]
+while for $\alpha \ge \frac{3}{4}$
+\[
+	k_n n^{-1} n^{-1} k_n^{-(2\alpha -1)} s(k_n)^{-1} = \bigO{n^{-1} k_n^{-(2\alpha - 1)}} = \smallO{1}.
+\]
+We conclude that $k_n = \smallO{n k^{-(2\alpha - 1)}s(k_n)}$ and hence $\Exp{I_{1,1}} = \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2}$.
 
 \end{proof}
-
-%\subsubsection{The case where $k_n = \bigO{1}$}
-%
-%Let $0 < \varepsilon < 1$, $\delta_n = (\varepsilon/k_n)^2$ and define
-%\[
-%	a_n = -\frac{1}{\alpha} \log\left(\delta_n\right)
-%\]
-%
-%Then, for all $p,p^\prime \in \Rcal$ with 
-%\[
-%	|x-x^\prime| > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)\max\{e^{\frac{a_n}{2}},e^{\frac{y^\ast}{2}}\}
-%	:= b_n(p,p^\prime)
-%\] 
-%we have that $h(p,p^\prime) > a_n$ and hence the neighborhoods of $p$ and $p^\prime$ below height $a_n$ are disjoint.

### 2019-03-08 transition.tex
finished section 8.2
finished with section 8

@@
 \end{align*}
-where the last line follows from a concentration of heights argument, for which we used that $\CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n} \le \binom{k_n}{2}$.
+where the last line follows from a concentration of heights argument, for which we used that $\CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n} \le 1$.
 To analyze the conditional expectation we observe that, similar to the analysis of $\gamma(k_n)$, conditioned on their being $k_n$ points in $\BallPon{y}$, each points $u_i = (x_i,y_i)$ is independently distributed according to the probability density $\Mu{\BallPon{y}}^{-1} \ind{u_i \in \BallPon{y}} f(x_i,y_i)$.
@@
 %\TM{ Some words spelling this out would help. I don't find it easy to see. Also, in general I think one should avoid saying things like "the proof of such-and-such also gives .." }
-\subsection{Counting missing triangles}
+\subsection{Counting missing triangles}\label{ssec:missing_triangles}
 

### 2019-03-08 proofs_finite_k.tex

@@
 &\qquad+\int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|\leq2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
-&= (n\E X)^2+o((n\E X)^2)+o(n)
+&= (1+o(1))\int_{} \int_{\Rcal_H\times \Rcal_H} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
+&= (1+o(1)) (n\E X)^2%+o((n\E X)^2)+o(n)
 \end{align*}
-It follows that $\E X^2 = (\E X)^2 + o((\E X)^2)+o(1)$, which implies $Var(X) \rightarrow 0$. We conclude
+It follows that $\E X^2 = (1+o(1))(\E X)^2$, which implies $Var(X) \rightarrow 0$. We conclude
 $$X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.$$

### 2019-03-10 concentration.tex
finished with section 9.2

@@
 \end{equation}
+and with that a different clustering function.
+\begin{equation}\label{eq:def_tilde_c_box}
+	\widetilde{c}_{\text{box}}(k_n) = \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+\end{equation}
 The idea is that the main contribution of triangles of degree $k_n$ to the triangle count $T_{\text{box}}(k_n)$ is given by $\widetilde{T}_{\text{box}}(k_n, C)$.
@@
 		{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\\
-	&\hspace{10pt} + 2 \Exp{\left|c^\ast(k_n; \Gbox) - \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right|}.
+	&\hspace{10pt} + 2 \Exp{\left|c^\ast(k_n; \Gbox) - \widetilde{c}_{\text{box}}(k_n)\right|}.
 \end{align*}
@@
 \[
-	 \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}} \le c^\ast(k_n; \Gbox). 
+	 \widetilde{c}_{\text{box}}(k_n) = \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}} \le c^\ast(k_n; \Gbox). 
 \]
@@
 \[
-	\Exp{\left|c^\ast(k_n; \Gbox) - \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right|}
-	= \Exp{c^\ast(k_n; \Gbox)} 
-	- \frac{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}.
+	\Exp{\left|c^\ast(k_n; \Gbox) - \widetilde{c}_{\text{box}}(k_n)\right|}
+	= \Exp{c^\ast(k_n; \Gbox)} - \widetilde{c}_{\text{box}}(k_n).
 \]
@@
 = \binom{k_n}{2} \Mu{\BallPon{y}}^{-2} \Exp{\widetilde{T}_{\text{box}}(p)},
-\] to get
+\] 
+to get
 \begin{align*}
@@
 \[
-	\frac{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+	\widetilde{c}_{\text{box}}(k_n) = \frac{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
 	= (1+\smallO{1}) \frac{\int_0^\infty P(y) \alpha e^{-\alpha y} \dd y}{p_{k_n}}
@@
 \[
-	2\Exp{\left|c^\ast(k_n; \Gbox) - \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}\right|}
+	2\Exp{\left|c^\ast(k_n; \Gbox) - \widetilde{c}_{\text{box}}(k_n)\right|}
 	= \smallO{\gamma(k_n)} = \smallO{s(k_n)}.	
@@
 \end{proof}
+
+We note that the above proof establishes the following important result
+
+\begin{corollary}\label{cor:c_ast_box_2_tilde_c_box}
+Let $k_n \to \infty$. Then, as $n \to \infty$,
+\[
+	\Exp{\left|c^\ast(k_n; \Gbox) - \widetilde{c}_{\text{box}}(k_n)\right|} = \smallO{s(k_n)}.
+\]
+\end{corollary}
 
@@
 Therefore, we have
-For $J_0$ we have, using Lemma [??]
+For $J_0$ we have, using Lemma~\ref{lem:joint_degree_factorization}
 \begin{align*}

### 2019-03-11 introduction.tex
pass over Sectoin 1-2.4 and fixed most references

@@
 
-\PvdH{I would try to refrain from making assumptions about the reader.}
-We start with the definition of the KPKVB model. %As the reader will probably already know, 
+We start with the definition of the KPKVB model.
 As mentioned, its nodes are situated in the hyperbolic plane $\Haa$, which is a surface with constant Gaussian curvature $-1$.
 This surface has several convenient representations (i.e.~coordinate maps), including the Poincar\'e halfplane model, the Poincar\'e disk model and the Klein disk model.
-A gentle introduction to Gaussian curvature, hyperbolic geometry and these representations of the hyperbolic plane can be found in~\cite{stillwellboek}.
+A gentle introduction to Gaussian curvature, hyperbolic geometry and these representations of the hyperbolic plane can be found in~\cite{stillwell2012geometry}.
 Throughout this paper we will be working with a representation of the hyperbolic plane using {\em hyperbolic polar coordinates}, sometimes called the {\em native representation}.
-That is, a point $p \in \Haa$ is represented as $(r,\theta)$, where $r$ is the hyperbolic distance between $p$ and the origin $O$ and $\theta$ as the angle between the line segment $Op$ and the positive $x$-axis.
+That is, a point $u \in \Haa$ is represented as $(r,\theta)$, where $r$ is the hyperbolic distance between $u$ and the origin $O$ and $\theta$ as the angle between the line segment $Ou$ and the positive $x$-axis.
 Here, when mentioning ``the origin'' and the angle between the line segment and the positive $x$-axis, we think of $\Haa$ embedded as the Poincar\'e disk in the ordinary euclidean plane.
@@
 Gugelmann et al.~\cite{gugelmann2012random} also showed that the average degree converges in probability to the constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing in the sense that it is bounded below by a positive constant a.a.s.
-Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Pee(E_n)\to 1$.
+Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Pee(E_n)\to 1$ as $n \to \infty$.
 %Their work however left open the question of whether the clustering coefficient actually converges in probability.
@@
 In~\cite{abdullah2017typical} it is shown that for $\alpha < 1$ the largest component is what is called an \emph{ultra-small world}: if we randomly sample two vertices of the graph then, a.a.s., conditional on them being in the same component, their graph distance is of order $\log\log n$.
-In~\cite{KiwiMit} and~\cite{ar:FriedKrohmerDiam} a.a.s.~polylogarithmic upper and lower bounds on the graph diameter of the largest component
-are shown, and in~\cite{ar:MullerDiam}, these were sharpened to show that $\log n$ is the correct order of the diameter.
+In~\cite{kiwi2015bound} and~\cite{friedrich2018diameter} a.a.s.~polylogarithmic upper and lower bounds on the graph diameter of the largest component are shown, and in~\cite{muller2017diameter}, these were sharpened to show that $\log n$ is the correct order of the diameter.
 
-Earlier work of the first and third authors with Bode~\cite{bode2015largest} and of the first and third authors~\cite{fountoulakis2018law} has 
-established the ``threshold for a giant component'': if $\alpha < 1$ then there is a unique component of size linear in $n$ no matter how small 
-$\nu$ (and hence the average degree); if $\alpha > 1$ all components are sublinear no matter the value of $\nu$; and if $\alpha=1$ then 
-there is a critical value $\nu_{\text{c}}$ such that for $\nu < \nu_{\text{c}}$ all components are sublinear and for $\nu > \nu_{\text{c}}$ there 
-is a unique linearly sized component (all of these statements holding a.a.s.). 
+Earlier work of the first and third authors with Bode~\cite{bode2015largest} and of the first and third authors~\cite{fountoulakis2018law} has established the ``threshold for a giant component'': if $\alpha < 1$ then there is a unique component of size linear in $n$ no matter how small $\nu$ (i.e.
+the average degree); if $\alpha > 1$ all components are sublinear no matter the value of $\nu$; and if $\alpha=1$ then there is a critical value $\nu_{\text{c}}$ such that for $\nu < \nu_{\text{c}}$ all components are sublinear and for $\nu > \nu_{\text{c}}$ there is a unique linearly sized component (all of these statements holding a.a.s.).
 Whether or not there is a giant component if $\alpha=1$ and $\nu=\nu_{\text{c}}$ remains an open problem.
-In~\cite{KiwiMit} and~\cite{KiwiMit2017+}, Kiwi and Mitsche considered the size of the second largest component and
-showed that for $\alpha \in (1/2, 1)$, a.a.s., the second largest component has polylogarithmic order with exponent 
-$1/(\alpha -1/2)$.
+In~\cite{kiwi2015bound} and~\cite{kiwi2017second}, Kiwi and Mitsche considered the size of the second largest component and showed that for $\alpha \in (1/2, 1)$, a.a.s., the second largest component has polylogarithmic order with exponent $1/(\alpha -1/2)$.
 
-In another paper of the first and third authors with Bode~\cite{BFMconnRSA} it was shown that $\alpha=1/2$ is the threshold for connectivity:
-for $\alpha < 1/2$ the graph is a.a.s.~connected, for $\alpha>1/2$ the graph is a.a.s.~disconnected and when $\alpha=1/2$ the probability 
-of being connected tends to a continuous, nondecreasing function of $\nu$ which is identically one for $\nu \geq \pi$ and strictly less than one 
-for $\nu < \pi$.
+In another paper of the first and third authors with Bode~\cite{bode2016probability} it was shown that $\alpha=1/2$ is the threshold for connectivity: for $\alpha < 1/2$ the graph is a.a.s.~connected, for $\alpha>1/2$ the graph is a.a.s.~disconnected and when $\alpha=1/2$ the probability of being connected tends to a continuous, nondecreasing function of $\nu$ which is identically one for $\nu \geq \pi$ and strictly less than one for $\nu < \pi$.
 Friedrich and Krohmer~\cite{blasius2018cliques} studied the size of the largest clique as well as the number of cliques of a given size.
-Bogu\~{n}a et al.~\cite{sustaining} and Bl\"asius et al.~\cite{BlasiusMLE} considered fitting the KPKVB model to data using maximum likelihood 
-estimation.
-Kiwi and Mitsche~\cite{KM18} studied the spectral gap and related properties, and Bl\"asius et al.~\cite{BlasiusTW} considered the treewidth 
-and related parameters of the KPKVB model.
-Recently Owada and Yogeshwaran~\cite{OY} considered subgraph counts, and in particular established a central limit theorem 
-for the number of copies of a fixed tree $T$ in $G(n;\alpha,\nu)$, subject to some restrictions on the parameter $\alpha$.
+Bogu\~{n}a et al.~\cite{boguna2010sustaining} and Bl\"asius et al.~\cite{BlasiusMLE} considered fitting the KPKVB model to data using maximum likelihood estimation.
+Kiwi and Mitsche~\cite{kiwi2018spectral} studied the spectral gap and related properties, and Bl\"asius et al.\cite{blasius2016hyperbolic} considered the tree-width and related parameters of the KPKVB model.
+Recently Owada and Yogeshwaran~\cite{owada2018sub} considered subgraph counts, and in particular established a central limit theorem for the number of copies of a fixed tree $T$ in $G(n;\alpha,\nu)$, subject to some restrictions on the parameter $\alpha$.
 
@@
 
+In this work we study the clustering coefficient in the KPKVB model.
 In the literature there are unfortunately two distinct, rival definitions of the {\em clustering coefficient}.
-One of those, sometimes called the {\em global} clustering coefficient, is defined as 
-three times the ratio of the number of triangles to the number of paths of length two in the graph.
-Results for this version of the clustering coefficient in the KPKVB model were obtained by Candellero and the first author~\cite{candellero2016clustering} and for the evolution of graphs on more general spaces with negative curvature by the first author in~\cite{F12}.
+One of those, sometimes called the {\em global} clustering coefficient, is defined as three times the ratio of the number of triangles to the number of paths of length two in the graph.
+Results for this version of the clustering coefficient in the KPKVB model were obtained by Candellero and the first author~\cite{candellero2016clustering} and for the evolution of graphs on more general spaces with negative curvature by the first author in~\cite{fountoulakis2012evolution}.
 
-In this paper we will study the other notion of clustering, the one which is also considered by Krioukov et al.~\cite{krioukov2010hyperbolic} and
-Gugelmann et al.~\cite{gugelmann2012random}. 
-It is sometimes called the {\em local} clustering coefficient, although we should point out that Gugelmann et al.~actually
-call it the global clustering coefficient in their paper.
+We will study the other notion of clustering, the one which is also considered by Krioukov et al.~\cite{krioukov2010hyperbolic} and Gugelmann et al.~\cite{gugelmann2012random}.
+It is sometimes called the {\em local} clustering coefficient, although we should point out that Gugelmann et al.~actually call it the global clustering coefficient in their paper.
 For a graph $G$ and a vertex $v\in V(G)$ we define the clustering coefficient {\em of $v$} as:
@@
 That is, provided $v$ has degree at least two, $c(v)$ equals the number of edges that are actually present between the neighbours \PvdH{I think it is neighbors in US English vs neighbours in UK English.
-Is there any specific reason to us the UK version?} of $v$ divided by the
-number of edges that could possibly be present between the neighbours given the degree of $v$.
+Is there any specific reason to us the UK version?} of $v$ divided by the number of edges that could possibly be present between the neighbours given the degree of $v$.
 The clustering coefficient of $G$ is now defined as the average of $c(v)$ over all vertices $v$:
+\[
+	c(G) := \frac{1}{|V(G)|} \sum_{v\in V(G)} c(v).
+\]
 
-$$ c(G) := \frac{1}{|V(G)|} \sum_{v\in V(G)} c(v). $$
-
-As mentioned above, Gugelmann et al.~\cite{gugelmann2012random}, have established that $c(G(n;\alpha,\nu))$ is non-vanishing a.a.s., but they left 
-open the question of convergence.
-Theorem~\ref{thm:maincc} below establishes that the clustering coefficient indeed converges in probability to a constant
-$\gamma$ that we give explicitly as a closed form expression involving $\alpha,\nu$ and several classical special functions.
+As mentioned above, Gugelmann et al.~\cite{gugelmann2012random}, have established that $c(G(n;\alpha,\nu))$ is non-vanishing a.a.s., but they left open the question of convergence.
+Theorem~\ref{thm:maincc} below establishes that the clustering coefficient indeed converges in probability to a constant $\gamma$ that we give explicitly as a closed form expression involving $\alpha,\nu$ and several classical special functions.
 
@@
 This assigns to each integer $k$ the value
-
-$$ c(k; G) := \begin{cases}
+\[ 
+	c(k; G) := \begin{cases}
 		\displaystyle \frac{1}{N_k} \sum_{v \in V(G), \atop \text{deg}(v)=k}  c(v),  &\mbox{ if } N_k \ge 1,\\
@@
 	\end{cases}
-	$$
-
-\noindent
+\]
 where $N_k$ denotes the number of vertices of degree exactly $k$ in $G$.
@@
 A general expression of the clustering function for KPKVB random graphs is given in~\cite[Equation (59)]{krioukov2010hyperbolic}.
-The authors conjecture that as $k$ tends to infinity, the clustering function decays as $k^{-1}$. They based this prediction 
-on observations (Figure 8 in \cite{krioukov2010hyperbolic}) in experiments on the infrastructure of the Internet obtained 
-in~\cite{claffy2009internet}. 
-Despite these interesting observations and the attention
-the KPKVB model has generated since then, the behaviour of the clustering function in 
-KPKVB random graphs had not been completely determined. In particular it has not been established whether it converges as $n\to\infty$ to some suitable limit function and, 
-how $c(k;G)$ scales with $k$.
+The authors conjecture that as $k$ tends to infinity, the clustering function decays as $k^{-1}$.
+They based this prediction on observations (Figure 8 in \cite{krioukov2010hyperbolic}) in experiments on the infrastructure of the Internet obtained in~\cite{claffy2009internet}.
+Despite these interesting observations and the attention the KPKVB model has generated since then, the behaviour of the clustering function in KPKVB random graphs had not been completely determined.
+In particular it has not been established whether it converges as $n\to\infty$ to some suitable limit function, nor how $c(k;G)$ scales with $k$.
 Theorems~\ref{thm:mainkfixed},~\ref{thm:mainktoinfty} and Proposition~\ref{prop:asymp} below settle these questions.
-Theorem~\ref{thm:mainkfixed} shows that for each fixed $k$, the value $c(k;G(n;\alpha,\nu))$ converges in probability to 
-a constant $\gamma(k)$ that we again give explicitly as a closed form expression involving $\alpha,\nu$ and several classical special functions.
+Theorem~\ref{thm:mainkfixed} shows that for each fixed $k$, the value $c(k;G(n;\alpha,\nu))$ converges in probability to a constant $\gamma(k)$ that we again give explicitly as a closed form expression involving $\alpha,\nu$ and several classical special functions.
 Theorem~\ref{thm:mainktoinfty} extends this result to growing sequences satisfying $k \ll n^{1/(2\alpha+1)}$.
-Propostion~\ref{prop:asymp} clarifies the asymptotics of the limiting function $\gamma(k)$, as $k\to\infty$.
-This depends on the parameter $\alpha$, and $\gamma(k)$ only scales with $k^{-1}$ when $\alpha > 3/4$, 
-which corresponds to the exponent of the degree distribution exceeding $5/2$. 
+Proposition~\ref{prop:asymp} clarifies the asymptotic behavior of the limiting function $\gamma(k)$, as $k\to\infty$.
+This depends on the parameter $\alpha$, and $\gamma(k)$ only scales with $k^{-1}$ when $\alpha > 3/4$, which corresponds to the exponent of the degree distribution exceeding $5/2$.
 So in particular our findings disprove the abovementioned conjecture of Krioukov et al.~\cite{krioukov2010hyperbolic}.
@@
 %
-Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a
-removable singularity. Again we have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but
-in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
+Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a removable singularity.
+Again, we have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
 
@@
 \begin{theorem}\label{thm:mainktoinfty}
-Let $\alpha>\frac12, \nu>0$ be fixed and let $k_n$ be a sequence 
+Let $\alpha>\frac12, \nu>0$ be fixed and let $k_n$ be a sequence of integers
 satisfying $1 \ll k_n \ll n^{1/(2\alpha+1)}$. Then, writing $G_n := G(n;\alpha,\nu)$, we have
@@
 \]
-as $n \to \infty$, where $\gamma(.)$ is as in Theorem~\ref{thm:mainkfixed}.
+as $n \to \infty$, where $\gamma(\cdot)$ is as in Theorem~\ref{thm:mainkfixed}.
 \end{theorem}
@@
 so that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows.
+
+\PvdH{ToDo: add remark on maximum scaling for $k_n$.}
 
@@
 
-\PvdH{I really think we should add a subsection where we discuss the results and their implications.
-Especially the addition $\log(k)$ term for degree distribution exponent $5/2$, and the fact that $n^{1/(2\alpha _ 1)}$ is the best scaling possible for $c(k_n; G_n)$.}
-
 \subsection{Outline of the paper}
@@
 The remaining sections are devoted to the proof of Theorem~\ref{thm:mainktoinfty}, which turns out to be a lot more involved.
+In particular, since we push the possible scaling of $k_n$ to its maximum, a great deal of work is needed to properly control the arising error terms.

### 2019-03-11 paper.tex
update to section 4
finished with section 9.2
pass over Sectoin 1-2.4 and fixed most references

@@
 \newcommand{\BallPon}[1]{\Bcal_{\text{box}}\left(#1\right)}	%	The neighborhood of a point p in the finit box model
-\newcommand{\FatBallHyp}[1]{\check{\Bcal}_{\H,n}(#1)}		%
-\newcommand{\BallSym}[1]{\Bcal_{\H \bigtriangleup \Pcal}\left(#1\right)}	%	Symmetric difference between balls in the 
+\newcommand{\FatBallHyp}[1]{\check{\Bcal}_{\Po}(#1)}		%
+\newcommand{\BallSym}[1]{\Bcal_{\Po \bigtriangleup \infty}\left(#1\right)}	%	Symmetric difference between balls in the 
 																			%	hyperbolic and infinite limit model
-\newcommand{\BallInter}[1]{\Bcal_{\H \cap \Pcal}\left(#1\right)}
+\newcommand{\BallInter}[1]{\Bcal_{\Po \cap \text{box}}\left(#1\right)}
 
@@
 \newcommand{\EdgeDiff}{E_{\H \setminus \mathcal{P}}}
-\newcommand{\expH}{\overline{n}_{\HP}(k_n)}
-\newcommand{\expP}{\overline{n}_{\Pcal}(k_n)}
+\newcommand{\expH}{\overline{n}_{\Po}(k_n)}
+\newcommand{\expP}{\overline{n}_{\infty}(k_n)}
 \newcommand{\Pop}[2]{\mathrm{Po} (#2;#1)}
@@
 \newcommand{\Dbox}{\ensuremath{\text{deg}_{\text{box}}}}
+\newcommand{\Vbox}{\ensuremath{\mathcal{V}_{\text{box}}}}
+\newcommand{\VPo}{\ensuremath{\mathcal{V}_{\Po}}}
 
@@
 \newcommand{\Gbox}[0]{\ensuremath{G_{\text{box}}}}
+\newcommand{\GPoH}{\ensuremath{G_{Po,H}}}
+\newcommand{\GboxH}{\ensuremath{G_{box,H}}}
 \newcommand{\Ginf}[0]{\ensuremath{G_{\infty}}}
@@
 We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$.
-Our results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should scale with $k^{-1}$ as we let $k$ grow.
-We find that this is true only when $\alpha > \frac34$, while $\gamma(k) = \Theta( k^{2 - 4\alpha})$ if $\alpha < \frac34$ and $\gamma(k) = \Theta( \log(k) / k )$ if $\alpha=\frac34$.
+Our results show that $\gamma(k)$ scales differently, as $k$ grows, for different ranges of $\alpha$.
+More precisely, $\gamma(k) = \Theta( k^{2 - 4\alpha})$ if $\frac{1}{2} < \alpha < \frac{3}{4}$, $\gamma(k) = \Theta( \log(k) / k )$ if $\alpha=\frac{3}{4}$ and $\gamma = \bigT{k^{-1}}$ when $\alpha > \frac{3}{4}$.
+These results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale with $k^{-1}$ as we let $k$ grow.
 \end{abstract}

### 2019-03-11 proof_overview_finite_k.tex
pass over Sectoin 1-2.4 and fixed most references

@@
 We start by recalling the definition of the infinite limit model from~\cite{fountoulakis2018law}.
-Let $\mathcal{P}=\mathcal{P}_{\alpha,\nu}$ 
-be a Poisson point process on $\eR^2$ with intensity function $f=f_{\alpha,\nu}$ given by
+Let $\mathcal{P}=\mathcal{P}_{\alpha,\nu}$ be a Poisson point process on $\eR^2$ with intensity function $f=f_{\alpha,\nu}$ given by
 
@@
 We will denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu = \mu_{\alpha, \nu}$, i.e. for every 
-Borel-measurable subset $S \subseteq \eR^2$ we have $\mu(S) = \int_S f(x,y) \, dx \, dy$
+Borel-measurable subset $S \subseteq \eR^2$ we have $\mu(S) = \int_S f(x,y) \dd x \dd y$
 
@@
 We consider the box $\Rcal = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2}e^{R/2}] \times (0, R]$ in $\eR^2$. 
-Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\mathcal{V}_n := \mathcal{P} \cap \Rcal$ and edge set such that
+Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\Vbox := \mathcal{P} \cap \Rcal$ and edge set such that
 \[
@@
 where $|x|_{r} = \min( |x|, r - |x|)$ for $-r\leq x\leq r$.
-Using $|.|_{\pi e^{R/2}}$ instead of $|.|$ results in the left and right boundaries of the box $\Rcal$ getting 
-identified, which in particular 
-%excludes boundary effects and 
-makes the model invariant under horizontal shifts and reflections in vertical lines. 
-The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\mathcal{V}_n$, with some additional edges caused by 
-the identification of the boundaries.
+Using $|.|_{\pi e^{R/2}}$ instead of $|.|$ results in the left and right boundaries of the box $\Rcal$ getting identified, which in particular makes the model invariant under horizontal shifts and reflections in vertical lines.
+The graph $\Gbox$ can thus be seen as a subgraph of $\Ginf$ induced on $\Vbox$, with some additional edges caused by the identification of the boundaries.
 
 Similar to the infinite graph, for a point $p \in \Rcal$ we define the ball $\BallPon{p}$ as
-
 \begin{equation}\label{eq:def_ball_P_n}
@@
 
-Imagine that we have an infinite supply of i.i.d.~points $p_1, p_2, \dots$ in the hyperbolic plane $\Haa$ chosen according to the $(\alpha, R)$-quasi uniform distribution.
-In the standard KPKVB random graph $G(n;\alpha,\nu)$ we take $p_1,\dots, p_n$ as our vertex set and add edges between points at hyperbolic distance at most $R = 2\log(n/\nu)$.
+Imagine that we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ in the hyperbolic plane $\Haa$ chosen according to the $(\alpha, R)$-quasi uniform distribution.
+In the standard KPKVB random graph $G(n;\alpha,\nu)$ we take $u_1,\dots, u_n$ as our vertex set and add edges between points at hyperbolic distance at most $R = 2\log(n/\nu)$.
 In the {\em Poissonized} KPKVB random graph $\GPo := \GPo(n;\alpha,\nu)$, we instead take $N\isd \Po(n)$, a Poisson random variable
-with mean $n$, independent of our i.i.d.~sequence of points and let the vertex set be $p_1,\dots, p_N$ and add edges 
+with mean $n$, independent of our i.i.d.~sequence of points and let the vertex set be $u_1,\dots, u_N$ and add edges 
 according to the same rule as before.
@@
 \begin{lemma}[{\cite[Lemma 27]{fountoulakis2018law}}]\label{lem:coupling_hyperbolic_poisson}
-Let $\mathcal{V}$ denote the vertex set of $\GPo(n;\alpha, \nu)$ and $\mathcal{W}$ the vertex set of $\Gbox(n;\alpha, \nu)$. 
+Let $\VPo$ denote the vertex set of $\GPo(n;\alpha, \nu)$ and $\Vbox$ the vertex set of $\Gbox(n;\alpha, \nu)$. 
 Define the map $\Psi : [0,R] \times (-\pi, \pi] \to \Rcal$ by
@@
 \end{equation}
-Then there exists a coupling such that, a.a.s., $\mathcal{W} = \Psi[\mathcal{V}]$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
+Then there exists a coupling such that, a.a.s., $\Vbox = \Psi[\VPo]$. %Moreover, if $\Ccal_n$ is the event that ${\cal V}_n = \Psi\left(\mathcal{V}_{\HP,n}\right)$ then
 %\begin{equation}\label{eq:convergence_miscoupling_hyperbolic_poisson}
@@
 
-By the hyperbolic rule of cosines, for two points $p = (x,y) = \Psi( (r,\theta) ), p' = (x',y') = \Psi( (r',\theta') ) \in \Rcal$ we have that
-$p' \in \BallHyp{p}$ iff.~either $r+r'\leq R$ or $r+r'>R$ and
-
-$$
+By the hyperbolic rule of cosines, for two points $p = (x,y) = \Psi( (r,\theta) ), p' = (x',y') = \Psi( (r',\theta') ) \in \Rcal$ we have that $p' \in \BallHyp{p}$ iff.~either $r+r'\leq R$ or $r+r'>R$ and
+\[
 	\cosh r \cosh r' - \sinh r \sinh r'\cos\left( |\theta-\theta'|_{2\pi} \right) \le \cosh(R),
-$$
-
-\noindent
+\]
 This can be rephrased as $p'\in \BallHyp{p}$ iff.~either $y+y'\geq R$ or $y+y'<R$ and
@@
 \begin{equation}\label{eq:def_Omega_hyperbolic}
-	|x-x'|_{\pi e^{R/2}} \leq \Phi(r,r') := \frac{1}{2}e^{R/2} \arccos\left( \frac{\cosh r \cosh r' - \cosh R}
-	{\sinh r \sinh r'} \right).
+	|x-x'|_{\pi e^{R/2}} \leq \Phi(y,y^\prime) := \frac{1}{2}e^{R/2} \arccos\left( \frac{\cosh(R-y) \cosh(R-y^\prime) - \cosh R}{\sinh(R-y) \sinh(R-y^\prime)} \right).
 \end{equation}
@@
 The following lemma provides useful bounds on the function $\Phi(r,r^\prime)$.
+Note that in~\cite{fountoulakis2018law} the function $\Phi$ is written in terms of where $r := R - y, r^\prime := R - y^\prime$.
 
@@
 There exists a constant $K>0$ such that, for every $\varepsilon > 0$ and for $R$ sufficiently large, the following holds.
-For every $r,r^\prime \in [\varepsilon R,R]$ with $r + r^\prime > R$ we have that 
+For every $r,r^\prime \in [\varepsilon R,R]$ with $y + y^\prime < R$ we have that 
 \begin{equation}\label{eq:asymp1}
-	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R} \leq \Phi(r, r^\prime) 
+	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R} \leq \Phi(y, y^\prime) 
 	\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R},
 \end{equation}
-where $y := R - r, y^\prime := R - r^\prime$. 
 Moreover:
 \begin{equation}\label{eq:asymp2} 
-\Phi(r,r^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $r, r^\prime < R - K$.} 
+\Phi(y,y^\prime) \geq e^{\frac12(y+y^\prime)} \quad \text{if \quad $y, y^\prime > K$.} 
 \end{equation}
@@
 
-A key consequence of Lemma~\ref{lem:asymptotics_Omega_hyperbolic} is that the coupling from Lemma~\ref{lem:coupling_hyperbolic_poisson} 
-preserves edges between points whose heights are not too large.
+A key consequence of Lemma~\ref{lem:asymptotics_Omega_hyperbolic} is that the coupling from Lemma~\ref{lem:coupling_hyperbolic_poisson} preserves edges between points whose heights are not too large.
 
@@
 \begin{enumerate}
-\item for any two points $p, p' \in \mathcal{W}$ with $y, y'\le R/2$, we have
-
-$$pp' \in E(\Gbox) \Rightarrow \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo), $$
-
-\item for any two points $p, p' \in \mathcal{W}$ with $y, y' \le R/4$, we have that
-
-$$pp' \in E(\Gbox) \iff \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo).$$
+\item for any two points $p, p' \in \Vbox$ with $y, y'\le R/2$, we have 
+\[
+	pp' \in E(\Gbox) \Rightarrow \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo),
+\]
+\item for any two points $p, p' \in \Vbox$ with $y, y' \le R/4$, we have that 
+\[
+	pp' \in E(\Gbox) \iff \Psi^{-1}(p)\Psi^{-1}(p') \in E(\GPo).
+\]
 

### 2019-03-12 concentration_argument.tex
improvements to section 4.2 and typos in Lemma 6.6

@@
 
-Note that since all three corollaries follow from Lemma~\ref{lem:concentration_argument}, Proposition~\ref{prop:concentration_argument_all} follows if we can prove that the conclusions from this lemma holds when we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
+Note that since all three corollaries follow from Lemma~\ref{lem:concentration_argument}, Proposition~\ref{prop:concentration_argument_all} follows if we can prove that the conclusions from this lemma hold when we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
 For this the following, slightly more general version of Lemma~\ref{lem:concentration_argument} will be important.
@@
 \begin{lemma}\label{lem:concentration_argument_rho_approximation}
-Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n \to \infty$ be such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
+Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n \to \infty$ such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
 \[
@@
 \]
-where $\phi_n(y)$ is a continuous differentiable function such that
+where $\phi_n(y)$ is a continuously differentiable function such that
 \begin{enumerate}[\upshape i)]
@@
 as $n \to \infty$.
-\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$. Then,
+\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$, then,
 \begin{equation}\label{eq:concentration_h_rho_approx}
-	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y^\prime} \dd y^\prime \sim  
+	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
 		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},

### 2019-03-12 proofs_finite_k.tex
improvements to section 4.2 and typos in Lemma 6.6

@@
 \subsection{Overall clustering coefficient, proving Theorem~\ref{thm:maincc}}
-In this subsection, we want to infer that the clustering coefficient of the KPKVB random graph $c \xrightarrow{\Pee} \gamma$ by only using that $c(k) \xrightarrow{\Pee} \gamma(k)$ for fixed $k$.
+In this subsection, we want to infer that the clustering coefficient of the KPKVB random graph $c(G_n) \xrightarrow{\Pee} \gamma$ by using that $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for fixed $k$.
 
 \begin{proofof}{Theorem~\ref{thm:maincc}}
-Let $\epsilon >0$.
-First of all, from Equations~\ref{eq:def_pk}, \ref{eq:gammakint} and \ref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$.
-In particular, we know that this series converges (we can use that $\gamma(k)\in [0,1]$ and $\sum_{k=0}^\infty p_k = 1$).
-Therefore, for $\delta >0$ with $\epsilon-2\delta>0$, there is $K_\delta$ such that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$.
-Furthermore, $c_n = \sum_{k=2}^\infty c_n(k)p_n(k)$, so by possibly choosing a larger value for $K_\delta$, we have that $|c_n-\sum_{k=2}^{K_\delta} c_n(k)p_n(k)| \leq \delta$.
+Let $\epsilon >2\delta >0$.
+As the $p_k$ form the probability mass function of an $\N_0$-valued random variable, we have that $\sum_{k=0}^\infty p_k = 1$, which implies that there is $K_\delta >0$ such that $1-\delta < \sum_{k=0}^{K_\delta} p_k \leq 1$.
+From Equations~\ref{eq:def_pk}, \ref{eq:gammakint} and \ref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$. 
+From this, it follows that $(1-\delta)\gamma < \sum_{k=2}^{K_\delta} \gamma(k) p_k \leq 1$ and hence that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$.
+Write $p(k;G_n)=\frac{N_n(k)}{n}$ for the fraction of degree $k$ vertices in the KPKVB model.
+From the definition of the clustering coefficient and function, it follows immediately that $c(G_n) = \sum_{k=2}^\infty c(k;G_n)p(k;G_n)$.
+By the initial observation, it follows again that $(1-\delta)c(k;G_n) < \sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \leq 1$, and hence, $|c(G_n)-\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n)| \leq \delta$.
 Putting these observations together:
 \begin{align*}
-|c_n-\gamma| &\leq \left|c_n-\sum_{k=2}^{K_\delta}c_n(k)p_n(k)\right|+\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
- &\leq \delta +\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta 
+|c(G_n)-\gamma| &\leq \left|c(G_n)-\sum_{k=2}^{K_\delta}c(k;G_n)p(k;G_n)\right|+\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
+ &\leq \delta +\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta 
 \end{align*}
-Therefore, $\Pee(|c_n-\gamma|\geq \epsilon) \leq \Pee(\left|\sum_{k=2}^{K_\delta} c_n(k)p_n(k) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta) \rightarrow 0$ because $c_n(k) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p_n(k) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c_n(k)p_n(k) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$.
+Therefore, $\Pee(|c(G_n)-\gamma|\geq \epsilon) \leq \Pee(\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta) \rightarrow 0$ because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$.
 %p_k =  = \Theta(k^{-(2\alpha +1)})

### 2019-03-13 proofs_infinite_k.tex
finished with section 9.2
finished section 9.3. Fixed the binomial Poisson coupling proof

@@
 
-The proof of Theorem~\ref{thm:mainktoinfty} follows the same strategy as outlined in Section~\ref{sec:proof_outline}.
+The proof of Theorem~\ref{thm:mainktoinfty} follows the same strategy as outlined in Section~\ref{sec:proof_outline} and executed in Section~\ref{sec:proofs_fixed_k}.
 However, the fact that $k = k_n \to \infty$ as $n \to \infty$, introduces additional technical challenges.
@@
 
-\subsection{Adjusted clustering and Poisson nodes in hyperbolic graphs}
+\subsection{Adjusted clustering and Poisson nodes in hyperbolic graphs}\label{ssec:KPKVB_to_GPo_infinite_k}
 

### 2019-03-13 introduction.tex
added observation section and changed the campbell-mecke section

@@
 This assigns to each integer $k$ the value
-\[ 
+\begin{equation}\label{eq:def_clustering_function}
 	c(k; G) := \begin{cases}
@@
 	\end{cases}
-\]
+\end{equation}
 where $N_k$ denotes the number of vertices of degree exactly $k$ in $G$.
@@
 For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in probability to $X$, as $n \to \infty$.
-%In addition, $X_n \xrightarrow[n\to\infty]{L^1} X$ denotes convergence in expectation, i.e.
-$\Exp{|X_n - X|} \to 0$ as $n \to \infty$, which is a stronger notion than convergence in probability.
+
+%We further adopt standard notations on asymptotic behavior of functions and sequences.
+That is, for two functions $f$ and $g$, we write $f(n) = \smallO{g(n)}$ as $n \to \infty$ if $\limsup_{n \to \infty} f(n)/g(n) = 0$ and $f(n) = \bigO{g(n)}$ as $n \to \infty$ if $\limsup_{n \to \infty} |f(n)|/g(n) < \infty$.
+Furthermore, $f(n) = \Omega(g(n))$ as $n \to \infty$ if $\limsup_{n \to \infty} |f(n)/g(n)| > 0$ and $f(n) = \omega(g(n))$ as $n \to \infty$ if $\limsup_{n \to \infty} |f(n)/g(n)| = \infty$.
+Finally, $f(n) = \bigT{g(n)}$ as $n \to \infty$ if $f(n) = \bigO{g(n)}$ and $g(n) = \Omega(f(n))$.
+
+ %In addition, $X_n \xrightarrow[n\to\infty]{L^1} X$ denotes convergence in expectation, i.e. $\Exp{|X_n - X|} \to 0$ as $n \to \infty$, which is a stronger notion than convergence in probability.
 
@@
 \]
-as $n \to \infty$, where $\gamma(\cdot)$ is as in Theorem~\ref{thm:mainkfixed}.
+as $n \to \infty$, where $\gamma(\cdot)$ is as in Theorem~\ref{thm:mainkfixed}. In particular
+\[
+	\lim_{n \to \infty} \Exp{\left|\frac{c(k_n; G_n)}{\gamma(k_n)}- 1 \right|} = 0.
+\]
 \end{theorem}
-
-In particular, Theorem~\ref{thm:mainktoinfty} implies that
-\[
-	\frac{c(k_n; G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{L^1} 1,
-\]
-so that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows.
-
-\PvdH{ToDo: add remark on maximum scaling for $k_n$.}
 
@@
 
-In particular this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac34$, and confirms it for $\alpha > \frac34$.
+Note that Theorem~\ref{thm:mainktoinfty} implies that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows, whose scaling is given in the above result.
+In particular, this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac34$, and confirms it for $\alpha > \frac34$.
 
 We remark that simultaneously and independently Stegehuis, van der Hofstad and van Leeuwaarden~\cite{stegehuis2018scale} found a similar, but less detailed result on the $k\to\infty$ scaling of the clustering function in the KPKVB model.
+
+\subsection{Observations}
+
+There are a few other observation to be made regarding our results.
+
+\paragraph{Uniform convergence.}
+
+Our results for the local clustering function in particular imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. To see this let
+\[
+	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k_n; G_n)}{\gamma(k)} - 1\right|}.
+\]
+Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:local_clustering_hyperbolic}
+\[
+	\lim_{n \to \infty} \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|} 
+	= \lim_{n \to \infty}\Exp{\left|\frac{c(b_n; G_n)}{\gamma(b_n)} - 1\right|} = 0.
+\]
+
+\paragraph{Near maximum scaling for $k_n$.}
+Our results for the clustering function in the KPKVB model are valid for any sequence of integers $k_n \to \infty$ such that $k_n \ll n^{\frac{1}{2\alpha + 1}}$.
+Although one would like to have results for any sequence $k_n \le n$, it turns out that $n^{1/(2\alpha + 1)}$ is the near maximum scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
+To see why this is the case note that by definition of the local clustering function~\eqref{eq:def_clustering_function} we have that $c(k_n; G_n) = 0$ if $N_{n}(k_n) = 0$, where $N_n(k_n)$ denote the number of vertices in a KPKVB graph $G(n; \alpha, \nu)$ with degree $k_n$.
+It follows by Markov's inequality that for any positive function $f : \R_+ \to \R_+$
+\begin{align*}
+	\Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|} 
+	&\ge \Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|\ind{N_n(k_n) = 0}}\\ 
+	&\ge \Prob{N_{n}(k_n) = 0} \ge 1 - \Exp{N_{\H,n}(k_n)}.
+\end{align*}
+We shall later establish (see Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson}) that $\Exp{N_n(k_n)}$ scales as $n k_n^{-(2\alpha + 1)}$.
+Therefore if $k_n$ is such that $k_n^{-(2\alpha + 1)} n$ tends to zero as $n \to \infty$ we have that
+\[
+	\lim_{n \to \infty} \Exp{N_{n}(k_n)} = 0
+\]
+and hence
+\[
+	\lim_{n \to \infty} \Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|} 
+	\ge \lim_{n \to \infty} 1 - \Exp{N_{n}(k_n)} = 1 \ne 0,
+\]
+for any positive function $f$. This implies that we cannot expect a result like that of Theorem~\ref{thm:mainktoinfty} to hold as soon as $k_n \gg n^{\frac{1}{2\alpha + 1}}$.
+
+\paragraph{Transition in scaling at $\bm{\alpha = 3/4}$.}
+
+\PvdH{We should try and add something here. Not necessarily needed for the submission to arXiv though.}
 
@@
 The remaining sections are devoted to the proof of Theorem~\ref{thm:mainktoinfty}, which turns out to be a lot more involved.
-In particular, since we push the possible scaling of $k_n$ to its maximum, a great deal of work is needed to properly control the arising error terms.
+The main reason for this is that we push the possible scaling of $k_n$ to its maximum and hence a great deal of work is needed to properly control the arising error terms and make sure these are of smaller order than $\gamma(k_n)$.
+
+Finally, the Appendix includes some technical results on Meijer's G-function, Chernoff bounds for Poisson and Binomial random variables and the code used for simulations.

### 2019-03-13 proof_overview_finite_k.tex
finished section 9.3. Fixed the binomial Poisson coupling proof
added observation section and changed the campbell-mecke section

@@
 That is,
-\[
+\begin{equation}\label{eq:def_quasi_uniform_density}
 	g(r,\theta) = \frac{\alpha\sinh(\alpha r)}{2\pi(\cosh(\alpha R) - 1)} \cdot 1_{\{0\leq r\leq R, -\pi<\theta\leq \pi\}}.
-\]
+\end{equation}
 
@@
 
-\PvdH{We might want to give some more results for Poisson point processes and Poisson random variables. Such as at the end of Section 2.1 in your recent paper on Hamiltonian cycles.}
-
 A very useful tool for analyzing subgraph counts, and their generalizations, in the 
 setting of the Poissonized random geometric graphs, and in particular the Poissonized KPKVB model and the box model is the \emph{Campbell-Mecke formula}.
-We use the incarnation below, which can be found in the monograph~\cite{penrose2003random}, as Theorem 1.6.
+We use a specific incarnation, which follows from Palm theory of Poisson point processes on metric spaces, see~\cite{last2017lectures}.
+For this consider a Poisson point process $\Pcal$ on some metric space $\mathcal{M}$ with density $\mu$ and let $\mathcal{N}$ denote the set of all possible point configurations in $\mathcal{M}$, equipped with the sigma algebra of the process $\Pcal$.
+Then, for any integer $k$ and measurable function $h : \R^k \times \mathcal{N} \to \R$,
+\begin{equation}\label{eq:def_campbell_mecke}
+	\Exp{\sum_{p_1, \dots, p_k \in \Pcal}^{\ne} h(p_1, \dots, p_k, \Pcal)}
+	= \int_{\mathcal{S}} \dots \int_{\mathcal{S}} \Exp{h(x_1,\dots, x_k, \Pcal} \dd \mu(x_1) \dots \dd \mu(x_k),
+\end{equation}
+where the sum is over all distinct point $p_1, \dots, p_k \in \Pcal$.
 
-\PvdH{I found it extremely hard to see the implications of this theorem.
+%To see this result in action consider the finite box model $\Gbox$. Then 
+%\[
+%	\Exp{\Nbox(k)} = \Exp{\sum_{p \in \Pcal} \ind{\Dbox(p) = k}}
+%	= \int_\Rcal \Prob{\Dbox(p) = k} f(x,y) \dd x \dd y.
+%\]
+
+%
+%
+%We use the incarnation below, which can be found in the monograph~\cite{penrose2003random}, as Theorem 1.6.
+%
+%\PvdH{I found it extremely hard to see the implications of this theorem.
 I therefore strongly recommend using more explicit version, for instance as in the previous version of the paper, or explicitly state the consequences of this result which will be used here.}
-
-\begin{theorem}[\cite{penrose2003random}]\label{thm:palm}
-Let $\Qcal$ be a Poisson process on $\eR^d$ with intensity function $g$, and suppose that $\lambda := \int g < \infty$.
-Suppose that $h(\Ycal, \Xcal)$ is a bounded measurable function, defined on pairs $(\Ycal,\Xcal)$ with $\Ycal \subseteq \Xcal \subseteq \eR^d$
-and $\Xcal$ finite, such that $h(\Ycal,\Xcal) = 0$ whenever $|\Ycal| \neq j$ (for some $j \in \eN$).
-Then
-\[ \Ee \sum_{\Ycal \subseteq \Qcal} h( \Ycal, \Qcal) = \frac{\lambda^j}{j!} \cdot \Ee h(\{Y_1,\dots, Y_j\}, \{Y_1,\dots, Y_j\} \cup \Qcal ), \]
-\noindent
-where the $Y_i$ are i.i.d.~random variables that are independent of $\Pcal$ and have common probability density function
-$g/\lambda$.
-\end{theorem}
+%
+%\begin{theorem}[\cite{penrose2003random}]\label{thm:palm}
+%Let $\Qcal$ be a Poisson process on $\eR^d$ with intensity function $g$, and suppose that $\lambda := \int g < \infty$.
+%Suppose that $h(\Ycal, \Xcal)$ is a bounded measurable function, defined on pairs $(\Ycal,\Xcal)$ with $\Ycal \subseteq \Xcal \subseteq \eR^d$
+%and $\Xcal$ finite, such that $h(\Ycal,\Xcal) = 0$ whenever $|\Ycal| \neq j$ (for some $j \in \eN$).
+%Then
+%\[ \Ee \sum_{\Ycal \subseteq \Qcal} h( \Ycal, \Qcal) = \frac{\lambda^j}{j!} \cdot \Ee h(\{Y_1,\dots, Y_j\}, \{Y_1,\dots, Y_j\} \cup \Qcal ), \]
+%\noindent
+%where the $Y_i$ are i.i.d.~random variables that are independent of $\Pcal$ and have common probability density function
+%$g/\lambda$.
+%\end{theorem}
 

### 2019-03-13 clustering_infinite_model.tex
finished revision of sections 5 and 6 and Appendix D

@@
 As mentioned earlier, we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of $\GPo$ with certain quantities associated with $\Ginf$.
-We will be considering the Poisson process $\Pcal$ to which we add one additinal point $(0,y)$ on the $y$-axis.
+We will be considering the Poisson process $\Pcal$ to which we add one additional point $(0,y)$ on the $y$-axis.
 In some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and independent of $\Pcal$.
@@
 
-To provide some intu\"{\i}tion for this definition and name, note that we can alternatively view $\Pcal$ as follows. 
+To provide some intuition for this definition and name, note that we can alternatively view $\Pcal$ as follows. 
 We take a constant intensity Poisson process on $\eR$ corresponding to the $x$-coordinates, and to each point
@@
 If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we will write
-
-$$ \mu(y) = \mu(p) := \mu(\BallPo{p}). $$
+\[ 
+	\mu(y) = \mu(p) := \mu(\BallPo{p}).
+\]
 Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives, using $\alpha>\frac{1}{2}$,
-
-$$ \begin{array}{rcl} 
-\mu(y) & = & \int_{\BallPo{p}} f(x',y') \, dx' \,d y'  
+\begin{align*}
+	\mu(y) &= \int_{\BallPo{p}} f(x',y') \, dx' \,d y'  
  		= \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' \\
-& = & \int_0^\infty 2 e^{(y+y')/2} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dy' 
+	&= \int_0^\infty 2 e^{(y+y')/2} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dy' 
  		= \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' \\
-& = & \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
-\end{array} $$
+	&= \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
+\end{align*}
 
@@
 
-Before considering clustering we briefly investigate the distribution of the degree of 
-the typical point. 
+Before considering clustering we briefly investigate the distribution of the degree of the typical point. 
 For $p = (x,y) \in \eR\times[0,\infty)$ we define
-\begin{equation}
-	\rho(p,k) := \Prob{\Po(\mu(y)) = k},
-\end{equation}
-
-where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$. 
-We will often write $\rho(y,k)$ instead of $\rho(p,k)$.
+\begin{equation}\label{eq:def_degree_inf_model}
+	\rho(p,k) := \Prob{\Po(\Mu{p}) = k},
+\end{equation}
+where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$. We will often write $\rho(y,k)$ instead of $\rho(p,k)$.
 
@@
     &= \frac{1}{k!} \int_0^\infty \left(\xi e^{\frac{y}{2}}\right)^k 
-    	e^{-\xi e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy\\
-    &= \frac{\alpha \xi^{2\alpha}}{k!} \int_0^\infty 
+    	e^{-\xi e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy
+    	= \frac{\alpha \xi^{2\alpha}}{k!} \int_0^\infty 
     	\left(\xi e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi e^{\frac{y}{2}}}
@@
     &= \frac{2\alpha \xi^{2\alpha}}{k!} \int_{\xi}^{\infty} 
-    	z^{k -2\alpha-1} e^{-z} \, dz\\
-    &= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
+    	z^{k -2\alpha-1} e^{-z} \, dz
+    	= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
 \end{align*}
@@
 
-Let the random variable $C$ denote the clustering coefficient of the typical point $(0,y)$, in the graph obtained from $\Ginf$ by adding $(0,y)$. We {\em define}
+Let the random variable $C$ denote the clustering coefficient of the typical point $(0,y)$, in the graph obtained from $\Ginf$ by adding $(0,y)$. We now {\em define}
 \[
@@
 For any fixed value $y_0>0$, the set of points inside $\BallPo{(0,y_0)}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{(0,y_0)}}$.
-As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by the experiment where we first pick $N \isd \Po( \mu(y_0) )$ and then we take $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
+As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by first picking $N \isd \Po( \mu(y_0) )$ and then taking $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
 (That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{(0,y_0)}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{(0,y_0)}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{(0,y_0)}$ chosen according to the mentioned re-normalized probability density function.
@@
 In particular
-
-$$ \begin{array}{rcl} 
-\Pee( y_i > t ) 
-& = & 
-\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty \int_{-e^{(s+y_0)/2}}^{e^{(s+y_0)/2}} e^{-\alpha s}\, d x \, d s \\
-& = & 
-\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty 2 e^{(s+y_0)/2} \cdot e^{-\alpha s}\, d s \\
-& = & 
-\frac{2 \nu\alpha e^{y_0/2} }{\pi \xi e^{y_0/2} (\alpha-\frac12) }  \cdot e^{(\frac12-\alpha)t} \\
-& = & 
- e^{(\frac12-\alpha)t},
-\end{array} $$
-
-\noindent
+\begin{align*}
+	\Prob{y_i > t} &= \frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty \int_{-e^{(y+y_0)/2}}^{e^{(y+y_0)/2}} e^{-\alpha y}
+		\dd x \dd y
+		= \frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty 2 e^{(y+y_0)/2} \cdot e^{-\alpha y} \dd y \\
+	&= \frac{2 \nu\alpha e^{y_0/2} }{\pi \xi e^{y_0/2} (\alpha-\frac{1}{2}) }  \cdot e^{(\frac{1}{2}-\alpha)t}
+		= e^{(\frac{1}{2}-\alpha)t},
+\end{align*}
 using that $\mu(y_0) = \xi e^{y_0/2} = \left(\frac{2\alpha\nu}{\pi(\alpha-\frac12)}\right) e^{y_0/2}$.

### 2019-03-13 concentration_argument.tex
finished revision of sections 5 and 6 and Appendix D

@@
 
-In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a(k)^-, a(k)^+]$, with
-\[
-	a(k)^\pm = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
-\]
-The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and Poisson random variables are well concentrated around their mean, i.e.
-around heights $y$ for which $\mu(y) \approx k$.
-Since $\mu(y) = \mu(\BallPo{y}) = \xi e^{y/2}$, this implies that integration with respect to $\rho(y,k)$ is concentrated around $y \approx 2\log(k/\xi)$.
+Here we show that if we integrate with respect to a function $\hat{\rho}_n(y,k_n) = \Prob{\Po(\mu_n(y)) = k_n}$ then we may restrict integration with respect to the \emph{height} $y$ to an interval on which $\mu_n(y) = \bigT{k_n}$.
+We will refer to such a result as a \emph{concentration of heights} result.
+In addition, if $\mu_n(y)$ is equivalent to $\mu(y)$ on this interval, then we may replace $\hat{\rho}_n(y,k_n)$ in the integral with $\rho(y,k_n) = \Prob{\Po(\mu(y)) = k_n}$ (the degree distribution of the typical point in $\Ginf$).
 
-In the remainder of this paper we will often encounter integrands involving the function $\Prob{\Po(\mu_n(y)) = k}$, for some $\mu_n(y)$.
-In these case we want to be able to restrict our integration around those heights $y$ for which $y \approx 2\log(k_n/\xi)$.
-We will refer to such results as \emph{concentration of heights arguments}.
-In this section we establish such results.
-We start with a concentration of heights lemma for the infinite model $\Ginf$ (Lemma~\ref{lem:concentration_argument}) and explain in Remark~\ref{rmk:concentration_argument} how such a result will be used throughout the paper.
-We then establish similar results for the Poissonized KPKVB and finite box model based on a generalization of Lemma~\ref{lem:concentration_argument} obtained in Section~\ref{ssec:general_concentration_lemma}.
-To apply this lemma to $\GPo$ and $\Gbox$ we have to analyze the expected number of nodes in a typical neighborhood in these models, which is done in Sections~\ref{ssec:average_degree_P_n} and~\ref{ssec:average_degree_HP_n}.
+We start with a concentration of heights result for the infinite model $\Ginf$ (Lemma~\ref{lem:concentration_argument}) and explain in Remark~\ref{rmk:concentration_argument} how such a result will be used throughout the paper.
+We then present a generalization of this result (Lemma~\ref{lem:concentration_argument}) and use this to establish concentration of heights results for the Poissonized KPKVB $\GPo$ and finite box model $\Gbox$.
+
+Finally we provide a general result that allow to substitute $\hat{\rho}_n(y,k_n)$ in the integrand with $\rho(y,k_n)$ and show that this holds in particular for the degree distributions in $\GPo$ and $\Gbox$, given by, respectively $\rho_{\Po}(y,k_n) := \Prob{\Po(\Mu{\BallHyp{y}}) = k_n}$ and $\rho_{\text{box}}(y,k_n) := \Prob{\Po(\Mu{\BallPon{y}}) = k_n}$.
 
@@
 \]
-%\TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal_n$. Is this really meant?
+%\TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal$. Is this really meant?
 %I would have expected we just integrate wrt.~$y$ and replace $f_{\alpha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}\PvdH{I understand this confusion and agree that your suggestion makes more sense here.
@@
 Note that we can tune the error in~\eqref{eq:error_bound_int_rho_not_K} by selecting an appropriately large $C > 0$, i.e.
-by restrict the function $h(y)$ inside the integral to an appropriate interval around $2\log(k_n/\xi)$.
+by restricting the function $h(y)$ inside the integral to an appropriate interval around $2\log(k_n/\xi)$.
 This makes Lemma~\ref{lem:concentration_argument} very powerful.
@@
 \begin{proof}
-By assumption, $g$ satisfies the conditions of for the second statement of Lemma~\ref{lem:concentration_argument}. Since in addition $g(2\log(k_n/\xi)) \sim h(2\log(k_n/\xi))$, the result follows.
+By assumption, $g$ satisfies the conditions of the second statement of Lemma~\ref{lem:concentration_argument}. Since in addition $g(2\log(k_n/\xi)) \sim h(2\log(k_n/\xi))$, the result follows.
 \end{proof}
 
-For any positive sequence $a_n \to \infty$ and $C > 0$ we define
-\begin{equation}\label{eq:def_K_C_set}
-	\Kcal_C(a_n) = \left\{y \in \R_+ : \frac{a_n - C \sqrt{a_n \log(a_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
-	\le \frac{a_n + C \sqrt{a_n \log(a_n)}}{\xi} \right\}.
-\end{equation}
-In addition we define
-\begin{equation}\label{eq:def_K_C_n_set}
-	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R_n] \cap \Kcal_{C}(a_n)),
-\end{equation}
-where $I_n := \frac{\pi}{2}e^{R_n/2}$.
-Recall that $\Rcal = (-I_n, I_n] \times [0,R]$.
+%For any positive sequence $a_n \to \infty$ and $C > 0$ we define
+%\begin{equation}\label{eq:def_K_C_set}
+%	\Kcal_C(a_n) = \left\{y \in \R_+ : \frac{a_n - C \sqrt{a_n \log(a_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
+%	\le \frac{a_n + C \sqrt{a_n \log(a_n)}}{\xi} \right\}.
+%\end{equation}
+%In addition we define
+%\begin{equation}\label{eq:def_K_C_n_set}
+%	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R_n] \cap \Kcal_{C}(a_n)),
+%\end{equation}
+%where $I_n := \frac{\pi}{2}e^{R_n/2}$. Recall that $\Rcal = (-I_n, I_n] \times [0,R]$. 
 The following corollary allows us to bound integrals of function by considering there maximum of $\Kcal_{C}(k_n)$.
@@
 
+For functions $h_n(y) = k_n^s h(y)$ we obtain an asymptotic equivalent expression for the associated integral.
+
 \begin{corollary}\label{cor:concentration_heights_asymptotics_n}
@@
 \begin{remark}[Proof of Proposition~\ref{prop:asymp} revisited]
-Note that due to Proposition~\ref{prop:asymptotics_P}, the function $P(y)$ from Section~\ref{sec:asymptotics_average_clustering_ast_P} satisfies all the necessary conditions in Corollary~\ref{cor:concentration_of_heights_asymptotics}.
-Hence, Proposition~\ref{prop:asymp} directly follows from Proposition~\ref{prop:asymptotics_P} and a concentration of heights argument (second statement of Lemma~\ref{lem:concentration_argument}).
+Note that due to Proposition~\ref{prop:asymptotics_P}, the function $P(y)$ from Section~\ref{sec:asymptotics_average_clustering_ast_P} satisfies all the necessary conditions in Corollary~\ref{cor:concentration_of_heights_asymptotics} with
+\[
+	h(y) := \begin{cases}
+		e^{-\frac{y}{2}(4\alpha - 2)} c_\alpha \xi^{4\alpha - 2} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
+		\frac{y}{2} e^{-\frac{y}{2}} &\mbox{if } \alpha = \frac{3}{4},\\
+		e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} &\mbox{if } \alpha > \frac{3}{4}.
+	\end{cases}
+\] 
+Hence, Proposition~\ref{prop:asymp} directly follows from Proposition~\ref{prop:asymptotics_P} and a concentration of heights argument (Corollary~\ref{cor:concentration_of_heights_asymptotics}).
 \end{remark}
 
-Although powerful, the current versions of the concentration of heights arguments are only valid for the function $\rho(y,k_n) := \Prob{\Po\left(\Mu{\BallPo{y}}\right) = k_n}$, which uses the neighborhoods in the infinite model $\Ginf$.
-Since we will also be working in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, we would like to use concentration of heights arguments when the integrand contains either the function $\rho_{\Po}(y,k_n) := \Prob{\Po\left(\Mu{\BallHyp{y}}\right) = k_n}$ or $\rho_{\text{box}}(y,k_n) := \Prob{\Po\left(\Mu{\BallPon{y}}\right) = k_n}$.
-The next proposition establishes this result and we will spend the rest of this section on its proof.
-
-\begin{proposition}\label{prop:concentration_argument_all}
-The conclusions from Lemmas~\ref{lem:concentration_argument} and Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n} and~\ref{cor:concentration_heights_asymptotics_n} still hold if we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
-\end{proposition}
+%
+%
+%The next proposition establishes this result and we will spend the rest of this section on its proof.
+%
+%\begin{proposition}\label{prop:concentration_argument_all}
+%The conclusions from Lemmas~\ref{lem:concentration_argument} and Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n} and~\ref{cor:concentration_heights_asymptotics_n} still hold if we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
+%\end{proposition}
 
@@
 
+Although powerful, the current versions of the concentration of heights arguments are only valid for the function $\rho(y,k_n) := \Prob{\Po\left(\Mu{\BallPo{y}}\right) = k_n}$, which uses the neighborhoods in the infinite model $\Ginf$.
+Since we will also be working in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, we would like to use concentration of heights arguments when the integrand contains either the function $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
+To establish these result we first prove a more general version of Lemma~\ref{lem:concentration_argument}.
+
 \begin{lemma}\label{lem:concentration_argument_rho_approximation}
@@
 \] 
-In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ satisfies, 
-\[
-	\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y),
-\]
-where $\phi_n(y)$ is a continuously differentiable function such that
+In addition, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, with $\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y)$ and 
+where $\phi_n(y)$ is a differentiable function satisfying:
 \begin{enumerate}[\upshape i)]
@@
 \end{enumerate}
-Then the following holds.
+Then the following holds:
 \begin{enumerate}
@@
 	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
-		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
+		\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
 \end{equation}
@@
 
-With this lemma, the proof of Proposition~\ref{prop:concentration_argument_all} follows if we can show that both $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$ are of the form $\rho(y,k_n)(1 + \phi_n(y))$, where $\phi_n(y)$ satisfies the conditions i) and ii).
-We deal with each of these cases separately.
+To apply this lemma to $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$ we need to show that both these functions are of the form $\rho(y,k_n)(1 + \phi_n(y))$, where $\phi_n(y)$ satisfies the conditions i) and ii) in Lemma~\ref{lem:concentration_argument_rho_approximation}.
+We will do this in the next two sections and establish that the results from Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n}
+and~\ref{cor:concentration_heights_asymptotics_n} hold when we replace $\rho(y,k_n)$ with either $\rho_{\text{box}}(y,k_n)$
+or $\rho_{\Po}(y,k_n)$.
+
+\begin{remark}[Generalized concentration of heights arguments]
+Since the results from Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n} and~\ref{cor:concentration_heights_asymptotics_n} hold for any of the three functions $\rho(y,k_n)$, $\rho_{\text{box}}(y,k_n)$ and $\rho_{\Po}(y,k_n)$, we will will refer only to one of these three when using a concentration of heights argument of for any of the three models $\GPo$, $\Gbox$ and $\Ginf$.
+\end{remark}
 
@@
 
-The following lemma immediately implies that $\Mu{\BallPon{y}}$ satisfies the conditions of Lemma~\ref{lem:concentration_argument_rho_approximation} and hence that Proposition~\ref{prop:concentration_argument_all} holds for $\rho_{\text{box}}(y,k_n)$.
+The following lemma immediately implies that $\Mu{\BallPon{y}}$ satisfies the conditions of Lemma~\ref{lem:concentration_argument_rho_approximation}.
 
@@
 \]
-Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R_n$ of the box $\Rcal_n$ while in the other case the full region of the box above $h(y)$ is connected to $p$.
+Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R_n$ of the box $\Rcal$ while in the other case the full region of the box above $h(y)$ is connected to $p$.
 
@@
 
+The following is now immediate.
+
+\begin{corollary}\label{cor:concentration_of_heights_Gbox}
+The statement in Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n}
+and~\ref{cor:concentration_heights_asymptotics_n} hold when we replace $\rho(y,k_n)$ with $\rho_{\text{box}}(y,k_n)$.
+\end{corollary}
+
 \subsection{Concentration of heights for the KPKVB model}\label{ssec:average_degree_HP_n}
@@
 Due to the hyperbolic distance formula, the computations are however more involved than for the finite box model.
-Recall that under the coupling between the hyperbolic random graph and the finite box model, for two points $p, p^\prime$ with $y + y^\prime < R_n$, $p^\prime \in \BallHyp{p}$ exactly when $|x-x^\prime|_{\pi e^{R_n/2}} \le \Phi(y,y^\prime)$, where we slightly abused notation to write $\Phi(y,y^\prime) = \Phi(R - y, R - y^\prime)$.
+Recall that under the coupling between the hyperbolic random graph and the finite box model, for two points $p, p^\prime$ with $y + y^\prime < R_n$, $p^\prime \in \BallHyp{p}$ exactly when $|x-x^\prime|_{\pi e^{R_n/2}} \le \Phi(y,y^\prime)$.
 In this setting, the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
@@
 This result enables us to determine the measure of a ball around a given point $p=(0,y)$.
-Recall that the hyperbolic ball $\BallHyp{p}$ is a subset of $\Rcal_n$ and not of the hyperbolic disc $\Dcal_{R_n}$, i.e.
+Recall that the hyperbolic ball $\BallHyp{p}$ is a subset of $\Rcal$ and not of the hyperbolic disc $\Dcal_{R_n}$, i.e.
 the balls $\BallHyp{p}$ "live" in the finite box and not the hyperbolic disc.
@@
 \begin{lemma}\label{lem:hyperbolic_ball_lower_part}
-Let $\Phi(y,y^\prime) := \Phi(R - y,R - y^\prime)$ be defined as in~\eqref{eq:def_Omega_hyperbolic}. Then, for any $0 \le \delta < 1$
+Let $\Phi(y,y^\prime)$ be defined as in~\eqref{eq:def_Omega_hyperbolic}. Then, for any $0 \le \delta < 1$
 \[
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \frac{\Mu{\BallHyp{0,y}}}{\Mu{\BallPo{0,y}}} = 1.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}} = 1.
 \]
@@
 	\Mu{\BallHyp{y}} 
-	= \Mu{\BallHyp{y} \cap \Rcal_n ([0,R_n - y))} + \Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}.
+	= \Mu{\BallHyp{y} \cap \Rcal ([0,R_n - y))} + \Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}.
 \]
@@
 \[
-	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} = \frac{2\nu \alpha}{\pi} \int_0^{R-y} \Phi(y,y^\prime) e^{-\alpha y^\prime}
+	\Mu{\BallHyp{(0,y)} \cap\Rcal[(0,R_n-y)]} = \frac{2\nu \alpha}{\pi} \int_0^{R-y} \Phi(y,y^\prime) e^{-\alpha y^\prime}
 	\dd y^\prime.
@@
 	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1}
-	\Mu{\BallHyp{(0,y)} \cap\Rcal_n[(0,R_n-y)]} = 1.
+	\Mu{\BallHyp{(0,y)} \cap\Rcal[(0,R_n-y)]} = 1.
 \]
 
-For the second part we observer that $\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])= \Rcal_n([R_n-y,R_n])$. 
+For the second part we observer that $\BallHyp{(0,y)} \cap \Rcal ([R_n - y, R_n])= \Rcal([R_n-y,R_n])$. 
 Thus, 
 \begin{align*}
-	&\hspace{-30pt}\Mu{\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])} \\
+	&\hspace{-30pt}\Mu{\BallHyp{(0,y)} \cap \Rcal ([R_n - y, R_n])} \\
 	&= \int_{R_n - y}^{R_n} \int_{I_n} f_{\alpha,\nu}(x^\prime, y^\prime) \dd x^\prime \dd y^\prime
@@
 	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} 
-	\Mu{\BallHyp{(0,y)} \cap \Rcal_n ([R_n - y, R_n])} = 0,
+	\Mu{\BallHyp{(0,y)} \cap \Rcal ([R_n - y, R_n])} = 0,
 \]
@@
 \]
-The following lemma shows that the same holds for the first term from which we conclude that $\phi_n(y)$ satisfies condition ii) in Lemma~\ref{lem:concentration_argument_rho_approximation} and hence that Proposition~\ref{prop:concentration_argument_all} also holds for $\rho_{\Po}(y,k_n)$.
+The following lemma shows that the same holds for the first term from which we conclude that $\phi_n(y)$ satisfies condition ii) in Lemma~\ref{lem:concentration_argument_rho_approximation}.
 
@@
 	\Mu{\BallHyp{y}} 
-	= \Mu{\BallHyp{y} \cap \Rcal_n ([0,R_n - y))} + \Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])},
+	= \Mu{\BallHyp{y} \cap \Rcal ([0,R_n - y))} + \Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])},
 \]
@@
 \[
-	\Mu{\BallHyp{y} \cap \Rcal_n ([0,R_n - y))} = \frac{2\alpha \nu}{\pi}\int_0^{R - y} \Phi(y,y^\prime) 
+	\Mu{\BallHyp{y} \cap \Rcal ([0,R_n - y))} = \frac{2\alpha \nu}{\pi}\int_0^{R - y} \Phi(y,y^\prime) 
 		e^{-\alpha y^\prime} \dd y^\prime,
@@
 \[
-	\Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}
+	\Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}
 	= \xi e^{y/2}\frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
@@
 \begin{align*}
-	&\frac{\partial}{\partial y} \Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}\\
-	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}
+	&\frac{\partial}{\partial y} \Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}\\
+	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}
 		+ \xi e^{y/2}\frac{2\alpha - 1}{4\pi}\left(
@@
 		+ \frac{1}{2}e^{-(\alpha - \frac{1}{2})R_n - y/2}\right)\\
-	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])}\left(1 +
+	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}\left(1 +
 		\frac{(2\alpha - 1)e^{-(\alpha - \frac{1}{2})(R_n - y)} + e^{-(\alpha - \frac{1}{2})R_n - y/2}}
@@
 \end{align*}
-Since, $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \Mu{\BallHyp{y} \cap \Rcal_n ([R_n - y, R_n])} = 0$, we are left to show that
+Since, $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])} = 0$, we are left to show that
 \begin{equation}\label{eq:derivative_mu_hyp_ball_main}
@@
 
-We thus have the following upper and lower bound on $I_2(y)$
+We thus have the following upper and lower bound for $I_2(y)$
 \begin{align*}
@@
 
-%\subsection{Concentration of heights argument for hyperbolic and finite box model}
-%
-%Let us define $\rho_{\Po}(y,k) = \Prob{\Po(\Mu{\BallHyp{y}}) = k}$ and $\rho_{\text{box}} = \Prob{\Po(\Mu{\BallPon{y}}) = k}$.
-Then since Lemma~\ref{lem:average_degree_P_n} implies that $\Mu{\BallHyp{(y)}}$ satisfies the requirements in Lemma~\ref{lem:concentration_argument_rho_approximation} while Lemma~\ref{lem:average_degree_hyperbolic} states that this holds for $\Mu{\BallPon{0,y}}$, we have the following important Corollary.
-%
-%\begin{corollary}\label{cor:concentration_argument_other_models}
-%The statements of Lemma~\ref{lem:concentration_argument_rho_approximation} holds for the two distribution functions $\rho_{\Po}(y,k)$ and $\rho_{n}(y,k)$. 
-%\end{corollary}
-%
-%%\begin{corollary}\label{cor:concentration_argument_other_models}
-%%Let $\hat{\rho}_n(y,k)$ be any of the two distribution functions $\rho_{\Po}(y,k)$ and $\rho_{n}(y,k)$ and let $\Kcal_{C,n}(\kappa_n)$ be defined as in~\eqref{eq:def_K_C_n_set}.
-Then, for any function $g_n(y)$ such that, uniformly on $(0, R_n]$, $g_n(y) = \bigO{k_n^{s} e^{\beta y}}$,
-%%%\TM{ Where did the $n^{-1}$ come from? Does not appear in L3.4. }\PvdH{I will elaborate on this once the statement of Lemma~\ref{lem:concentration_argument} is updated}, 
-%%as $n \to \infty$, for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$,
-%%\[
-%%	\int_{\Rcal_n} g_n(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y
-%%	= (1+\smallO{1})n\int_{0}^\infty g_n(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
-%%\]
-%%for some $C > 0$ large enough.
-%%\end{corollary}
-%
-%In particular we conclude that, similarly to the infinite limit model, concentration of heights arguments as described in Remark~\ref{rmk:concentration_argument} can be applied in the case of the hyperbolic random graphs and the finite box model.
-%
-%\begin{remark}[Most frequent use of concentration of argument]
-%Note that it follows from Proposition~\ref{prop:asymp} that $P(y)$ satisfies the conditions in the both statements of Lemma~\ref{lem:concentration_argument_rho_approximation}.
-In particular, if $\hat{\rho}_n$ denote either $\rho_{\Po}$ or $\rho_{\text{box}}$, then as $n \to \infty$
-%\begin{equation}\label{eq:concentration_heights_argument_Py}
-%	\int_{\Rcal_n} P(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x, y) \dd x \dd y
-%	= (1 + \smallO{1}) n \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
-%\end{equation}
-%This is the form that will be use most frequently in the remainder of this paper.
-%\end{remark}
+We now conclude that similar to Corollary~\ref{cor:concentration_of_heights_Gbox}, the concentration of heights results also hold for $\rho_{\Po}(y,k_n)$.
+
+\begin{corollary}\label{cor:concentration_of_heights_GPo}
+The statement in Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n}
+and~\ref{cor:concentration_heights_asymptotics_n} hold when we replace $\rho(y,k_n)$ with $\rho_{\Po}(y,k_n)$.
+\end{corollary}

### 2019-03-13 proofs_infinite_k.tex
finished revision of sections 5 and 6 and Appendix D

@@
 
-\PvdH{References need to be included once Section 1 is updated.}
+The proof of Theorem~\ref{thm:mainktoinfty} follows the same strategy as outlined in Section~\ref{sec:proof_outline} and executed in Section~\ref{sec:proofs_fixed_k}.
+However, the fact that $k = k_n \to \infty$ as $n \to \infty$, introduces significant technical challenges, especially for $k_n$ close the the maximum scale $n^{\frac{1}{2\alpha + 1}}$.
+For example, the coupling between $\GPo$ and $\Gbox$ we use becomes less exact so that we can no longer use Lemma~\ref{lem:coupling_edges} to conclude that triangle counts in $\GPo$ and $\Gbox$ are asymptotically equivalent.
+Moreover, since we are ultimately interested in recovering the scaling of $c(k_n;G_n)$, which Theorem~\ref{thm:mainktoinfty} claims is $\gamma(k_n)$, we need to show that each step in the strategy outlined in Section~\ref{sec:proof_outline} only introduces error terms that are of smaller order, i.e.
+that are $\smallO{\gamma(k_n)}$.
+This will turn out to require a great deal of care in bounding all error terms we encounter.
 
-The proof of Theorem~\ref{thm:mainktoinfty} follows the same strategy as outlined in Section~\ref{sec:proof_outline} and executed in Section~\ref{sec:proofs_fixed_k}.
-However, the fact that $k = k_n \to \infty$ as $n \to \infty$, introduces additional technical challenges.
-For example, the coupling we use becomes less exact so that we can no longer use Lemma~\ref{lem:coupling_edges} to conclude that triangle counts in $\GPo$ and $\Gbox$ are asymptotically equivalent.
 In this section we explain the challenges with each step and give a detailed overview of the structure for the proof of Theorem~\ref{thm:mainktoinfty} using intermediate results for each of the steps.
-Since we are ultimately interested in recovering the scaling of $c(k_n;G_n)$, which Theorem~\ref{thm:mainktoinfty} claims is $\gamma(k_n)$, we need to show that each step only introduces error terms that are of smaller order, i.e.
-that are $\smallO{\gamma(k_n)}$.
 To this end we define the scaling function
@@
 \begin{remark}[Diverging $k_n$]
-Throughout the remainder of this paper $\{k_n\}_{n \ge 1}$ will always denote a sequence of integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
+Throughout the remainder of this paper, unless stated otherwise, $\{k_n\}_{n \ge 1}$ will always denote a sequence of integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
 \end{remark}
@@
 \end{equation}
-Notice that the only difference between $c(k;G)$ and $c^\ast(k;G)$ is that we replace $N_G(k)$ by its expectation $\Exp{N_G(k)}$.
-The advantage is that now, the only randomness is in triangle counting.
-In addition, note that since $\Exp{N_G(k)} > 0$ a case distinction for $N_k$ is no longer needed for $c^\ast(k;G)$.
+Notice that the only difference between $c(k;G)$ and $c^\ast(k;G)$ is that we replace $N_k$ by its expectation $\Exp{N_k}$.
+The advantage is that now, the only randomness is in the formation of triangles.
+In addition, note that since $\Exp{N_k} > 0$ a case distinction for $N_k$ is no longer needed for $c^\ast(k;G)$.
 It is however still relevant since we are eventually interested in $c(k;G)$.
@@
 We choose this order because results proved in the later stages are helpful to deal with error terms coming up in proofs at earlier stages and hence help streamline those proofs.
+Below briefly describe each of the intermediate steps leading up to the proof of Theorem~\ref{thm:mainktoinfty}.
+We start with an observation on the dependence between the degree of a point $p = (x,y)$ and its height $y$.
+
+\subsection{Restricting the height for vertices with degree $k_n$}
+
+In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a(k)^-, a(k)^+]$, with
+\[
+	a(k)^\pm = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
+\]
+The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and Poisson random variables are well concentrated around their mean, i.e.
+around heights $y$ for which $\mu(y) \approx k$.
+Since $\mu(y) = \mu(\BallPo{y}) = \xi e^{y/2}$, this implies that integration with respect to $\rho(y,k)$ is concentrated around $y \approx 2\log(k/\xi)$.
+In the remainder of this paper we will often encounter integrands involving the function $\Prob{\Po(\mu_n(y)) = k}$, for some $\mu_n(y)$ which is asymptoticly equivalent to $\mu(y)$.
+In these case we also want to be able to restrict our integration around those heights $y$ for which $y \approx 2\log(k_n/\xi)$.
+Such results are established in Section~\ref{sec:concentration_argument}.
+Moreover, we prove that if $\mu_n$ corresponds to either $\Mu{\BallHyp{y}}$ or $\Mu{\BallPon{y}}$, then for a certain classs of functions $h$
+\[
+	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y 
+	= (1+\smallO{1}) \int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+\]
+i.e. we may replace $\hat{\rho}_n(y,k_n)$ in the integrand with $\rho(y,k_n)$.
 
@@
 	\begin{center}
-		\textbf{Hyperbolic graph}\\
-		$G_n$
+		\textbf{KPKVB graph}\\
+		$G_n = G(n; \alpha, \nu)$
 	\end{center}
@@
 
-\path (c_ast_hyp.south)+(0,-3) node (pois_hyp_header) {\begin{minipage}[c]{13em}
+\path (c_ast_hyp.south)+(0,-3) node (pois_hyp_header) {\begin{minipage}[c]{14em}
 	\begin{center}
-		\textbf{Poisson Hyperbolic graph}\\
-		$\GPo(\alpha,\nu)$
+		\textbf{Poissonized KPKVB graph}\\
+		$\GPo = \GPo(n;\alpha,\nu)$
 	\end{center}
@@
 
-\path (pois_hyp_header.north)+(-2,1) node (pois_hyp_text) [textblock] {\begin{minipage}[c]{7em}
+\path (pois_hyp_header.north)+(-2,1.5) node (pois_hyp_text) [textblock] {\begin{minipage}[c]{7em}
 	\begin{center}
@@
 	\begin{center}
-	Adjusted local clustering\\
+	Adjusted clustering function\\
 	$\displaystyle c^\ast(k_n; \GPo)$
@@
 		\textbf{Infinite limit model}\\
-		$\Ginf(\alpha, \nu)$
+		$\Ginf= \Ginf(\alpha, \nu)$
 	\end{center}
@@
 
-\path (c_infty.south)+(2,-0.75) node (exp_c_pois_text) [textblock] {\begin{minipage}[c]{7em}
+\path (c_infty.south)+(2,-1.5) node (exp_c_pois_text) [textblock] {\begin{minipage}[c]{7em}
 	\begin{center}
@@
 	\begin{center}
-	Adjusted local clustering\\
+	Adjusted clustering function\\
 	$\displaystyle c^\ast(k_n; \Gbox)$
@@
 
-\path (c_ast_pois_n.south)+(-4.25,-0.5) node (c_ast_pois_n_text) [textblock] {\begin{minipage}[c]{7em}
+\path (c_ast_pois_n.south)+(-4,-0.5) node (c_ast_pois_n_text) [textblock] {\begin{minipage}[c]{7em}
 	\begin{center}
@@
 	\begin{center}
-		\textbf{Finite box model}\\
-		$\Gbox(\alpha, \nu)$
+		\textbf{Finite box graph}\\
+		$\Gbox = \Gbox(n; \alpha, \nu)$
 	\end{center}
@@
 
-\path (pois_hyp_header)+(-2.5,0.75) node (pois_hyp_a) {};
-\path (c_ast_pois_hyp)+(2.5,-1) node (pois_hyp_b) {};
+\path (pois_hyp_header)+(-2.75,0.75) node (pois_hyp_a) {};
+\path (c_ast_pois_hyp)+(2.75,-1) node (pois_hyp_b) {};
 \path[rounded corners, draw=black, dashed, thick, fill=black!20] (pois_hyp_a) rectangle (pois_hyp_b);
@@
 
-\path (exp_c_pois_n)+(-2.5,2) node (pois_n_a) {};
-\path (c_ast_pois_n)+(2.5,-1) node (pois_n_b) {};
+\path (exp_c_pois_n)+(-2.75,2) node (pois_n_a) {};
+\path (c_ast_pois_n)+(2.75,-1) node (pois_n_b) {};
 \path[rounded corners, draw=black, dashed, thick, fill=black!20] (pois_n_a) rectangle (pois_n_b);
@@
 
-\caption{Overview of the proof strategy for Theorem \ref{thm:local_clustering_hyperbolic}.}
+\caption{Overview of the proof strategy for Theorem \ref{thm:local_clustering_hyperbolic}.
+The left column denote the models in which the true hyperbolic balls are used while the right column contains the models that use an approximation of these.
+The most important part is the transition between these to setting which is accomplished by Proposition~\ref{prop:couling_c_H_P}.}
 \label{fig:overview_proof}
@@
 
-\subsection{Adjusted clustering and Poisson nodes in hyperbolic graphs}\label{ssec:KPKVB_to_GPo_infinite_k}
+\subsection{Adjusted clustering and the Poissonized KPKVB model}\label{ssec:KPKVB_to_GPo_infinite_k}
 
-Recall that the first step for the fixed $k$ case was to show that the transition from the hyperbolic random graph $G_{\H,n}$ to the Poisson version $\GPo$ did not influence clustering.
-Here we first make a transition from the local clustering function $c_{\H,n}(k)$ to the adjusted version $c^\ast(k; G_n)$.
+Recall that the first step for the fixed $k$ case was to show that the transition from the KPKVB graph $G_n = G(n;\alpha,\nu)$ to the Poissonized version $\GPo$ did not influence clustering.
+Here we first make a transition from the local clustering function $c(k_n; G_n)$ to the adjusted version $c^\ast(k_n; G_n)$.
 The following lemma justifies working with this modified version.
-The proof uses a concentration result for $\N_{\H,n}(k_n)$ and full details can be found in Section~\ref{ssec:coupling_H_HP}.
+The proof uses a concentration result for $\N_{n}(k_n)$ and full details can be found in Section~\ref{ssec:coupling_H_HP}.
 
@@
 
-We then establish that the modified local clustering function in the hyperbolic model $G_{\H,n}(\alpha,\nu)$ behaves similarly to that in the Poisson version $G_{\HP, n}(\alpha,\nu)$.
-This is based on a standard coupling between a Binomial Point Process and Poisson Point Process.
+We then establish that the modified local clustering function for KPKVB graphs $G_n$ behaves similarly to that in the $\GPo$.
+The proof, found in Section~\ref{ssec:coupling_H_HP}, is based on a standard coupling between a Binomial Point Process and Poisson Point Process.
 
@@
 \end{proposition}
-%\MS{I think we can drop the condition to be increasing here and below, also the $n^{1/3}$ should be removed.}
 
@@
 The proof can be found in Section~\ref{ssec:coupling_HP_ast_P}.
-This is one of the key technical challenges we face.
+This step is one of the key technical challenges we face in proving Theorem~\ref{thm:mainktoinfty}.
 
 To understand why, recall that the degree $k$ of a node is related to its height $y$, roughly speaking, by $k \approx \xi e^{y/2}$.
-Therefore, when $k$ is fixed we have that the heights of nodes with that degree are also fixed, in particular $y < R_n/4$ for large enough $n$.
-In addition, the main contribution of triangles would also come from nodes with heights $y^\prime < R_n/4$.
+Therefore, when $k$ is fixed we have that the heights of nodes with that degree are also fixed, in particular $y < R/4$ for large enough $n$.
+In addition, the main contribution of triangles would also come from nodes with heights $y^\prime < R/4$.
 This allowed us to use Lemma~\ref{lem:coupling_edges} and conclude that the triangles present in the graph $\GPo$ where exactly those present in $\Gbox$ and therefore the local clustering function was the same in both models.
@@
 Since
-$R_n/4 = \frac{1}{2}\log(n) - \frac{1}{2}\log(\nu)$ we get that $R_n/4 = \smallO{y_n}$ for all $\alpha > (3 - 4\varepsilon)/2$ and hence $y_n > R_n/4$ for large enough $n$, violating the conditions of Lemma~\ref{lem:coupling_edges}.
+$R/4 = \frac{1}{2}\log(n) - \frac{1}{2}\log(\nu)$ we get that $R/4 = \smallO{y_n}$ for all $\alpha > (3 - 4\varepsilon)/2$ and hence $y_n > R/4$ for large enough $n$, violating the conditions of Lemma~\ref{lem:coupling_edges}.
 However, by carefully analyzing the difference between the adjusted local clustering function in both models we can still make the same conclusion.
@@
 
-\begin{proposition}[Coupling result for local clustering]\label{prop:couling_c_H_P}
+\begin{proposition}[Coupling result for adjusted clustering function]\label{prop:couling_c_H_P}
 As $n \to \infty$,
@@
 This is only the high level description and that is all we need for the ``final proof".}\PvdH{I would vote for keeping them split, since this allows us to clearly point to the main technical challenge we have to overcome to obtain the final result.}
-These three results together imply that the difference between the local clustering function of the hyperbolic random graph and the modified local clustering function of the finite box graph converges to zero faster than the proposed scaling $\gamma(k_n)$ in Theorem [??].
+
+Together, the three results described so far imply that the difference between the clustering function for a KPKVB graph and the adjusted clustering function for the finite box graph $\Gbox$ converges to zero faster than the proposed scaling $\gamma(k_n)$ in Theorem~\ref{thm:mainktoinfty}.
 Hence, to prove this theorem it is enough to prove it for $c^\ast(k; \Gbox)$.
 
-\subsection{From the finite to the infinite model}
+\subsection{From the finite box to the infinite model}
 
-To compute the limit of the modified local clustering function $c^\ast(k; \Gbox)$ in the finite graph $G_{\mathcal{P},n}(\alpha, \nu)$ we first prove in Section~\ref{sec:concentration_c_P_n} that it is concentrated around its expectation $\Exp{c^\ast(k_n; \Gbox)}$.
+To compute the limit of the adjusted clustering function $c^\ast(k; \Gbox)$ we first prove in Section~\ref{sec:concentration_c_P_n} that it is concentrated around its mean $\Exp{c^\ast(k_n; \Gbox)}$.
 
@@
 
-\begin{proposition}[Concentration for local clustering function in $G_{\mathcal{P},n}(\alpha, \nu)$]\label{prop:concentration_local_clustering_P_n}
+\begin{proposition}[Concentration for adjusted clustering function in $\Gbox$]\label{prop:concentration_local_clustering_P_n}
 As $n \to \infty$,
@@
 
-This result is another one of the technical challenges we face when considering $k_n \to \infty$.
+This result represents another technical challenge we face when considering $k_n \to \infty$.
 For the proof, we first identify the specific range of heights that give the main contribution to the triangle count, showing that the triangles coming from nodes with heights outside this range is of smaller order.
@@
 
-Assuming this concentration result, we are left with the task to compute the limit of $\Exp{c^\ast(k_n; \Gbox)}$ as $n \to \infty$ and show that it is equivalent to $\gamma(k_n)$.
+Assuming this concentration result, we are left to compute the limit of $\Exp{c^\ast(k_n; \Gbox)}$ as $n \to \infty$ and show that it is equivalent to $\gamma(k_n)$.
 To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of $c^\ast(k;\Gbox)$ and $\gamma(k_n)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
@@
 
-\TM{ This is only for $c(k)$. Should we not also mean $c$? }\PvdH{I do not think so. We can prove everything for $c$ once we have the result for $c(k_n)$.}
-
 Recall that for the finite box model the left and right boundaries of $\Rcal_n$ where identified, so that graph $\Gbox$ contains some additional edge with respect to the induced subgraph of $\Ginf$ on $\Rcal_n$.
-The prove of Proposition~\ref{prop:convergence_average_clustering_P_n} therefore relies on analyzing the number of triangles coming from these additional edges and showing that their contribution to the local clustering function are of negligible order, see Section~\ref{sec:clustering_Pn_to_P}.
+The proof of Proposition~\ref{prop:convergence_average_clustering_P_n} therefore relies on analyzing the number of triangles coming from these additional edges and showing that their contribution to the clustering function are of negligible order, see Section~\ref{sec:clustering_Pn_to_P}.
 
@@
 For example $N_{\Po}(k)$ denotes number of nodes with degree $k$ in $\GPo$ and $\rho_{\text{box}}(y,k) = \Prob{\Po(\mu(\BallPo{y})) = k}$, i.e.
-the degree distribution of a typical point in $\Gbox$.
+the degree distribution in $\Gbox$ for a point $p = (x,y)$.
 \end{remark}
@@
 
-We are now ready to prove Theorem~\ref{thm:mainktoinfty}, using the propositions stated in the previous sections.
+We are now ready to prove Theorem~\ref{thm:mainktoinfty}, using the results stated in the previous sections.
 
 \begin{proof}[Proof of Theorem~\ref{thm:mainktoinfty}]
-%By applying Proposition~\ref{prop:convergence_average_clustering_P_n}, Proposition~\ref{prop:convergence_average_clustering_P_n} and Theorem~\ref{thm:asymptotics_average_clustering_P} we get
-%\begin{align*}
-%	&\hspace{-30pt}\Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}\\
-%	&\le \frac{\Exp{\left|c^\ast(k_n; \Gbox) - \Exp{}c^\ast(k_n; \Gbox)\right|}}{C_{\alpha,\nu}\gamma(k_n)}
-%		+ \frac{\left|\Exp{c^\ast(k_n; \Gbox)} - \gamma(k_n)\right|}{C_{\alpha,\nu}\gamma(k_n)}
-%		+ \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right| \\
-%	&= \smallO{1}.
-%\end{align*}
-First of all, due to cancellation of equal terms we can rewrite
+Note that the second of the theorem follows immediately from the first.
+
+To prove the first statement, we rewrite $c(k_n; G_n)$ as
 \begin{align*}
-    c(k_n;G_n)-\gamma(k_n) =& c(k_n;G_n)-c^\ast(k_n;G_n)+c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)+c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox) \\
-    &+c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)+\E c^\ast(k_n; \Gbox)-\gamma(k_n)
+    c(k_n;G_n)-\gamma(k_n) &= \left(c(k_n;G_n)-c^\ast(k_n;G_n)\right)
+    	+ \left(c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)\right)\\
+    &\hspace{10pt}+ \left(c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right)
+    	+ \left(c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)\right)\\
+    &\hspace{10pt}+ \E c^\ast(k_n; \Gbox)-\gamma(k_n)
 \end{align*}
@@
 \begin{align*}
-    \E[|c(k_n;G_n)-\gamma(k_n)|] \leq & \E[|c(k_n;G_n)-c^\ast(k_n;G_n)|]+\E[|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)|]\\&+\E[|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)|] 
-    +\E[|c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)|]\\&+\E[|\E c^\ast(k_n; \Gbox)-\gamma(k_n)|]
+    \Exp{\left|c(k_n;G_n)-\gamma(k_n)\right|} 
+    &\le \Exp{\left|c(k_n;G_n)-c^\ast(k_n;G_n)\right|}
+    	+\Exp{\left|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)\right|}\\
+    &\hspace{10pt}+ \Exp{\left|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right|} 
+    	+ \Exp{\left|c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)\right|}\\
+    &+ \left|\Exp{c^\ast(k_n; \Gbox)}-\gamma(k_n)\right|
 \end{align*}
-At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the disk in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling from the disk to the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model.
-%where we also used that $c(k_n;\Ginf) = \gamma(k_n)$ as obtained at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P}.
-%\TM{ Maybe we can have a more clear reference?
-Now, at this place in the paper this proof feels a bit like cheating since there are almost no details given.
-} \PvdH{I completely agree.
-I think that once the results for fixed $k$ have been included we can include a specific statement at the end of Section~\ref{sec:asymptotics_average_clustering_ast_P} we can refer to.}
+At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling between the Poissonized KPKVB and the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model.
+
 All of this together yields that:
 \begin{align*}
-    \E[|c(k_n;G_n)-\gamma(k_n)|] = \smallO{s(k_n)} = \smallO{\gamma(k_n)},
+    \Exp{\left|c(k_n;G_n)-\gamma(k_n)\right|} = \smallO{s(k_n)} = \smallO{\gamma(k_n)},
 \end{align*}
-%\TM{ Last equality seems to rely on Thm 1.3, which is not yet proven at this point.
-}\PvdH{We can fix this by proving the scaling of $c_\infty(k)$ in Section~\ref{sec:asymptotics_average_clustering_ast_P}.}
-i.e. the statement of the theorem.
-%\[
-%	\Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}
-%	\le \left|\frac{c_{\infty}(k_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right| 
-%	+ \frac{\Exp{\left|c^\ast(k_n; \Gbox) - \gamma(k_n)\right|}}{C_{\alpha,\nu}\gamma(k_n)} = \smallO{1}.
-%\]
-
-%Combining this with Proposition~\ref{prop:couling_c_H_P} yields
-%\[
-%	\Exp{\left|\frac{c^\ast(k_n;G_n)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|}
-%	\le \Exp{\left|\frac{c^\ast(k_n; \Gbox)}{C_{\alpha,\nu}\gamma(k_n)} - 1\right|} 
-%	+ \frac{\Exp{\left|c^\ast(k_n;G_n) - c^\ast(k_n; \Gbox)\right|}}{C_{\alpha,\nu}\gamma(k_n)} = \smallO{1}.
-%\]
-%and the result then follows by applying Lemma~\ref{lem:clustering_ast_H}. 
+which establishes the first statement of the theorem and finishes the proof.  
 \end{proof}

### 2019-03-18 concentration_argument.tex
Updates from Overleaf

@@
 \begin{lemma}\label{lem:concentration_argument}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\{k_n\}_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n}$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$.
+Let $\alpha > \frac{1}{2}$, $\nu > 0$, $(k_n)_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n}$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$.
 In addition, define for any constant $C > 0$,
@@
 \begin{equation}\label{eq:concentration_h_rho}
-	\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y^\prime} \dd y^\prime \sim  
+	\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
 		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
@@
     &= \bigO{1} \int_0^{a_n^-} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y} \dd y 
-    	+ \bigO{1}\int_{a_n^+}^{\infty} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y}x \dd y \\
+    	+ \bigO{1}\int_{a_n^+}^{\infty} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y} \dd y \\
     &= \bigO{1} \int_0^{a_n^-} \rho(y,k_n) e^{-(\alpha-\beta) y} \dd y 
@@
 \]
-and $x - \log(1 + x) \sim x^2/2$ as $x \to 0$, we get 
+and as $x - \log(1 + x) \sim x^2/2$ as $x \to 0$, we get 
 \begin{align*}

### 2019-03-21 clustering_infinite_model.tex
beta integral detail in computation for alpha =1

@@
 +\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
-&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 
--\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 \\ 
-&\hspace{50pt}+\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 \\
+&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\left(\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2\right) 
++\left(-\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2\right) \\ 
+&\hspace{50pt}+\left(\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}\right)+\left(\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0\right) \\
 &=0
 \end{align*}
+using that %$B^-(\frac{1}{2};3,0)=-\frac{5}{8}+\ln 2$ and $B^-(1-z_0;2,-1)=-1+z_0^{-1}+\ln z_0$.
+\begin{align*}
+B^-(\frac{1}{2};3,0)&=\int_0^\frac{1}{2}t^2(1-t)^-1dt=\int_\frac{1}{2}^1 (1-s)^2 s^{-1}ds\\
+&=\int_\frac{1}{2}^1 s^{-1}-2+sds = -2+\frac{1}{2}-\ln\frac{1}{2}+1-\frac{1}{8}=-\frac{5}{8}+\ln 2
+\end{align*}
+and
+\begin{align*}
+B^-(1-z_0;2,-1)&=\int_0^{1-z_0} t(1-t)^{-2}dt = \int_{z_0}^1 (1-s)s^{-2}ds \\
+&=\int_{z_0}^1 s^{-2}-s^{-1}ds = -1+z_0^{-1}+\ln z_0.
+\end{align*}
+
 Finally, it follows that

### 2019-03-25 clustering_infinite_model.tex
processed most of Nikoloas comments for sections 1-3

--- 2019-03-13 clustering_infinite_model.tex
@@
 Since $c(G)$ is defined as an average over all vertices of the graph, it is not immediately obvious how to meaningfully define a corresponding notion for infinite graphs, and similarly for the clustering function, the degree sequence, etc.
-We can however without any issues speak of the (expected) clustering coefficient of the typical point, or the expected clustering coefficient given that it has degree k, or the distribution of the degree of the typical point.
+We can however without any issues speak of the (expected) clustering coefficient of the typical point, or the expected clustering coefficient given that it has degree $k$, or the distribution of the degree of the typical point.
 (All considered in the graph obtained from $\Ginf$ by adding the typical point to its vertex set.)
@@
 \begin{equation}\label{eq:def_pk}
-	p_k := \Pee( D=k ) = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
+	p_k :=  \Prob{D = k} = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
 \end{equation}
@@
 \[
-	\gamma := \Ee C, \quad \gamma(k) := \Ee\left( C | D = k \right).
+	\gamma := \Exp{C}, \quad \gamma(k) := \CExp{C}{D = k}.
 \]
@@
 \[
-	\Ee\left( C | D=k, y=y_0 \right) 
+	\CExp{C}{D=k, y=y_0} 
 	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
@@
 \[
-	\gamma(k) = \Ee( C | D=k ) = \int_0^\infty \Ee\left( C | D=k, y=y_0 \right) g_k(y_0) \, d y_0,
+	\gamma(k) = \CExp{C}{D=k} = \int_0^\infty \CExp{C}{D=k, y=y_0} g_k(y_0) \, d y_0,
 \]
@@
 \gamma 
-& = & \displaystyle \Ee C = \sum_{k\geq 2} \Ee( C | D=k )\Pee( D=k ) \\
+& = & \displaystyle \Exp{C} = \sum_{k\geq 2} \CExp{ C }{ D=k }\Prob{ D=k } \\
 & = & \displaystyle \int_0^\infty P(y_0) \left( \sum_{k=2}^\infty \rho(y_0,k) \right) \alpha e^{-\alpha y_0} \, d y_0 \\
@@
 	&+ 
-	(e^{-\frac{1}{2}y})^{4\alpha -2} \left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} + \frac{(\alpha - 
-		1/2 ) B^-(1/2; 1 + 2 \alpha, 
-		-2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right) \\
+	(e^{-\frac{1}{2}y})^{4\alpha -2} \left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
+		+ \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right) \\
 	&+ \frac{(1 - 
@@
 With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ 
-satisfy $|x_1-x_2| \leq e^{(y_1+y_2)/2}$, where $x_1$ and $x_2$ are independent uniform random variables in, respectively, 
-$[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.
-We have that
-
+satisfy \\ $|x_1-x_2| \leq e^{(y_1+y_2)/2}$, where $x_1$ and $x_2$ are independent uniform random variables in the intervals
+$[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$, respectively. We have that
 \begin{equation}\label{eq:delta_P}
@@
 The solid red line indicates the range for $x_2$ such that the points $p_0$, $p_1$ and $p_2$ form a triangle.
-The boundaries of their neighborhoods are shown in, respectively, black, blue and green.}
+The boundaries of their neighbourhoods are shown in, respectively, black, blue and green.}
 \label{fig:triangle_prob_lemma}
@@
 	&= 1 - \frac{1}{2e^{y_0+y_1/2+y_2/2} } \int_0^{ e^{(y_0+y_1)/2}+e^{(y_0+y_2)/2}-e^{(y_1+y_2)/2} } x_1 \dd x_1 \\
-	&= 1 - \frac{ \left( e^{(y_0+y_1)/2}+e^{(y_0+y_2)/2}-e^{(y_1+y_2)/2} \right)^2 }{ 4 e^{y_0+y_1/2+y_2/2} },
+	&= 1 - \frac{ \left( e^{(y_0+y_1)/2}+e^{(y_0+y_2)/2}-e^{(y_1+y_2)/2} \right)^2 }{ 4 e^{y_0+y_1/2+y_2/2} }.
 \end{align*}
@@
 
-Applying the change of variables $z_i := e^{-y_i/2}$, $i=1,2$, and Lemma~\ref{lem:triangle_prob_y_coordinates} gives %${\dd}y_i = -\frac{2{\dd}z_i}{z_i}$ and therefore
+Applying the change of variables $z_i := e^{-y_i/2}$, $i=1,2$, and Lemma~\ref{lem:triangle_prob_y_coordinates} gives 
 \begin{align*}
 	I_1(y_0) &=	4 (\alpha-1/2)^2 \cdot \int_{z_0>z_1>z_2>0} P(y_0,y_1(z),y_2(z)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
-		{\dd}z_2{\dd}z_1 \\
+		\dd z_2\dd z_1 \\
 	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{z_0>z_1>z_2>0} 1 \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
-		{\dd}z_2{\dd}z_1 \right. \\
+		\dd z_2 \dd z_1 \right. \\
 	&\hspace{10pt} \left. - \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} G(z_0,z_1,z_2) \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
-		{\dd}z_2{\dd}z_1 \right) \\
+		\dd z_2 \dd z_1 \right) \\
 	&=: 4 (\alpha-1/2)^2 ( I_{11}(y_0) - I_{12}(y_0)). 
@@
 \begin{align*}
-	I_{11}(y_0) &= \int_0^{z_0} \int_0^{z_1} z_1^{2\alpha-2} z_2^{2\alpha-2} {\dd}z_2{\dd}z_1
-		= \int_0^{z_0} z_1^{2\alpha-2} \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1} \right]_0^{z_1} {\dd}z_1\\
-	&= \frac{1}{2\alpha-1} \cdot \int_0^{z_0} z_1^{4\alpha-3} {\dd}z_1
+	I_{11}(y_0) &= \int_0^{z_0} \int_0^{z_1} z_1^{2\alpha-2} z_2^{2\alpha-2} \dd z_2 \dd z_1
+		= \int_0^{z_0} z_1^{2\alpha-2} \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1} \right]_0^{z_1} \dd z_1\\
+	&= \frac{1}{2\alpha-1} \cdot \int_0^{z_0} z_1^{4\alpha-3} \dd z_1
 		= \frac{1}{2(2\alpha-1)^2} \cdot z_0^{4\alpha-2}. \numberthis \label{eq:Delta_P_computation_I11}
@@
 \begin{equation}\label{eq:def_Delta_P_computation_int_J_1}
-	J_{a,b,c}(z_0) := z_0^a \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1.
+	J_{a,b,c}(z_0) := z_0^a \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2\dd z_1.
 \end{equation}
@@
 	J_{a,b,c}(z_0) 
-	&= z_0^a \int_{z_0/2}^{z_0}\int_{z_0-z_1}^{z_1} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
+	&= z_0^a \int_{z_0/2}^{z_0}\int_{z_0-z_1}^{z_1} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1
 		= z_0^a \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} \left[ \frac{ z_2^{c+2\alpha-1} }{ c+2\alpha-1 } \right]_{z_0-z_1}^{z_1} \dd z_1\\
 	&= \frac{z_0^a}{c+2\alpha-1} \cdot \left( \int_{z_0/2}^{z_0} z_1^{b+c+4\alpha-3} \dd z_1
-	   - \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} (z_0-z_1)^{c+2\alpha-1} {\dd}z_1 \right) \\
+	   - \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} (z_0-z_1)^{c+2\alpha-1} \dd z_1 \right) \\
 	&= \frac{z_0^{a+b+c+4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} \\
@@
 \end{align*}
-where we have used the substitution $u := z_1/z_0$ giving $z_0 {\dd} u = {\dd} z_1$ in the penultimate line and
+where we have used the substitution $u := z_1/z_0$ giving $z_0 \dd u = \dd z_1$ in the penultimate line and
 $B^-$ denotes the (lower) incomplete beta function.
@@
    		\alpha (-\frac{41}{128} + \frac{13}{16}  2^{-4\alpha}) 
-   		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} a^4\right) 
+   		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} \alpha^4\right) 
    		z_0^{4 \alpha-2} }{4(\alpha-1/2)^2 (\alpha-1)^2 (\alpha-3/4) \alpha} \\
@@
 		+ \alpha (-\frac{41}{128} + \frac{13}{16}  2^{-4\alpha})  
-		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} a^4\right) 
+		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} \alpha^4\right) 
 		z_0^{4 \alpha-2} }{4(\alpha-1/2)^2 (\alpha-1)^2 (\alpha-3/4) \alpha} \\
@@
 		+ \alpha (-\frac{41}{128} + \frac{13}{16}  2^{-4\alpha})
-		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} a^4\right) 
+		+ \alpha^2 (\frac{5}{8} - \frac{3}{4} 2^{-4\alpha}) - \frac{15}{32}\alpha^3 +\frac{1}{8} \alpha^4\right) 
 		z_0^{4 \alpha-2} }{4(\alpha-1/2)^2 (\alpha-1)^2 (\alpha-3/4) \alpha} \\
@@
 	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0,y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
-		{\dd}z_2{\dd}z_1 \\
+		\dd z_2 \dd z_1 \\
 	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{1>z_1>z_0,z_2>0}  z_0 z_1^{2\alpha-3} z_2^{2\alpha-2} 
-		{\dd}z_2{\dd}z_1 \right. \\
+		 \dd z_2 \dd z_1 \right. \\
 	&\hspace{10pt}\left. - \int_{{1>z_1>z_0,z_2>0}\atop{z_1 < z_0+z_2}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
-		z_2^{2\alpha-2} \dd z_2{\dd}z_1 \right) \\
+		z_2^{2\alpha-2} \dd z_2 \dd z_1 \right) \\
 	&=: 4 (\alpha-1/2)^2 (I_{21}(y_0) - I_{22}(y_0)). 
@@
 
-We proceed with the easy integral:
-\begin{align*}
-	I_{21}(y_0) &= z_0 \int_{1>z_1>\max(z_2,z_0);z_0,z_2>0} z_1^{2\alpha-3} z_2^{2\alpha-2} {\dd}z_2{\dd}z_1   
-		= z_0 \int_{z_0}^1 \int_{0}^{z_1} z_1^{2\alpha-3} z_2^{2\alpha-2} {\dd}z_2{\dd}z_1\\
-	&= z_0 \int_{z_0}^1 \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1}\right]_{0}^{z_1} z_1^{2\alpha-3} {\dd}z_1 
-		= \frac{z_0}{2\alpha-1}  \int_{z_0}^1 z_1^{4\alpha-4} {\dd}z_1
+We start with the easy integral:
+\begin{align*}
+	I_{21}(y_0) &= z_0 \int_{1>z_1>\max(z_2,z_0);z_0,z_2>0} z_1^{2\alpha-3} z_2^{2\alpha-2}  \dd z_2 \dd z_1   
+		= z_0 \int_{z_0}^1 \int_{0}^{z_1} z_1^{2\alpha-3} z_2^{2\alpha-2}  \dd z_2 \dd z_1\\
+	&= z_0 \int_{z_0}^1 \left[ \frac{z_2^{2\alpha-1}}{2\alpha-1}\right]_{0}^{z_1} z_1^{2\alpha-3} \dd z_1 
+		= \frac{z_0}{2\alpha-1}  \int_{z_0}^1 z_1^{4\alpha-4} \dd z_1
 		= \frac{z_0 - z_0^{4\alpha-2}}{(4\alpha-3)(2\alpha-1)}. \numberthis \label{eq:Delta_P_computation_I21}
@@
 
-To deal with $I_{22}(y_0)$ we consider the integral function
-\[
-	J_{a,b,c}^\prime(z_0) := z_0^a \int_{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\atop{z_1 < z_0+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
-\]
-and note that
+To deal with $I_{22}(y_0)$ we consider the function
+\[
+	J_{a,b,c}^\prime(z_0) := z_0^a \int_{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\atop{z_1 < z_0+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1
+\]
+and write
 \begin{equation}\label{eq:Delta_P_computation_I22_J}
@@
 	J_{a,b,c}^\prime(z_0) 
-	&= z_0^a \int_{z_0}^1 \int_{z_1-z_0}^{z_1}  z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd} z_2 {\dd} z_1  \\
- 	&= z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1}  z_1^{b+2\alpha-2}( z_1^{c+2\alpha-1}-(z_1-z_0)^{c+2\alpha-1})  {\dd} z_1  \\
+	&= z_0^a \int_{z_0}^1 \int_{z_1-z_0}^{z_1}  z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1  \\
+ 	&= z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1}  z_1^{b+2\alpha-2}( z_1^{c+2\alpha-1}-(z_1-z_0)^{c+2\alpha-1})  \dd z_1  \\
  	&=z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1} z_1^{b+c+4\alpha-3} {\dd } z_1 -z_0^{a} \int_{z_0}^1 	
- 		\frac{1}{c+2\alpha-1}z_1^{b+2\alpha-2}(z_1-z_0)^{c+2\alpha-1}  {\dd} z_1  \\
+ 		\frac{1}{c+2\alpha-1}z_1^{b+2\alpha-2}(z_1-z_0)^{c+2\alpha-1}  \dd z_1  \\
  	&= z_0^a  \frac{1}{(c+2\alpha-1)(b+c+4\alpha-2)}(1-z_0^{b+c+4\alpha-2}) \\
@@
 \begin{align*}
- \int_{z_0}^{1} z_1^x (z_1-z_0)^y {\dd} z_1 
- &= \int_0^{1-z_0} (s+z_0)^x s^y {\dd} s \\
- &= z_0^{x+y} \int_0^{1-z_0} \left( (s/z_0) + 1 \right)^x (s/z_0)^y {\dd} s \\
- &= z_0^{x+y+1} \int_{0}^{1/z_0 -1 } (t+1)^x t^y {\dd} t \\
- &= z_0^{x+y+1} \int_0^{1-z_0} u^y (1-u)^{-(x+y+2)} {\dd} u \\
+ \int_{z_0}^{1} z_1^x (z_1-z_0)^y \dd z_1 
+ &= \int_0^{1-z_0} (s+z_0)^x s^y \dd s \\
+ &= z_0^{x+y} \int_0^{1-z_0} \left( (s/z_0) + 1 \right)^x (s/z_0)^y \dd s \\
+ &= z_0^{x+y+1} \int_{0}^{1/z_0 -1 } (t+1)^x t^y \dd t \\
+ &= z_0^{x+y+1} \int_0^{1-z_0} u^y (1-u)^{-(x+y+2)} \dd u \\
  &= z_0^{x+y+1} B^-(1-z_0; y+1,-x-y-1 ).
@@
 	&\qquad+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + 
-	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)}
+	B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}{2 (\alpha - 1) (3 \alpha - 1)}.
 \end{align*}
@@
 	&= \xi^{u+2\alpha-k} \int_{\xi/b}^{\xi/a} t^{k-1-2\alpha-u} e^{-t} \dd t \\
-	&= \xi^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u,\xi/b) - \Gamma^+( k-2\alpha-u, \xi/a) \right), 
+	&= \xi^{u+2\alpha-k} \left( \Gamma^+( k-2\alpha-u,\xi/b) - \Gamma^+( k-2\alpha-u, \xi/a) \right).
 \end{align*}
@@
 \begin{equation}\label{eq:integral_Delta_P_z}
-	\int_0^1 z^{u+2\alpha-k-1} e^{-\xi z^{-1}} \dd z = \xi^{u+2\alpha-k} \Gamma^+(k-2\alpha-u,\xi)
+	\int_0^1 z^{u+2\alpha-k-1} e^{-\xi z^{-1}} \dd z = \xi^{u+2\alpha-k} \Gamma^+(k-2\alpha-u,\xi).
 \end{equation}
@@
 \[
-	U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} \dd t
+	U(a,b,z) = \frac{1}{\Gamma(a)} \int_0^\infty e^{-zt} t^{a-1} (1+t)^{b-a-1} \dd t.
 \] 
@@
 \end{align*}
-Plugging in $a=2\alpha+1 >0$, $b=-2\alpha+k+1$, $z=\xi>0$, then gives
+Setting $a=2\alpha+1 >0$, $b=-2\alpha+k+1$, $z=\xi>0$, then gives
 \begin{equation}\label{eq:integral_Delta_P_1_z}
-	\int_0^1 z_0^{2\alpha-k-1} e^{-\xi/z_0} (1-z_0)^{2\alpha} dz_0 = \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi)
+	\int_0^1 z_0^{2\alpha-k-1} e^{-\xi/z_0} (1-z_0)^{2\alpha} dz_0 = \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi).
 \end{equation}
@@
 	&=\int_0^1 z^a e^{-\xi/z} \int_0^{1-z} t^{b-1} (1-t)^{c-1} \dd t \dd z \\
-	&=\int_0^1 z^a e^{-\xi/z} \int_z^1 s^{c-1} (1-s)^{b-1} \dd s \dd z
+	&=\int_0^1 z^a e^{-\xi/z} \int_z^1 s^{c-1} (1-s)^{b-1} \dd s \dd z.
 \end{align*}
@@
 \[
-	\Gamma^+(-a-1,\xi/s) = \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}},
+	\Gamma^+(-a-1,\xi/s) = \MeijerGnew{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}},
 \] 
@@
 \begin{align*}
-	\xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}} \dd s
+	\xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerGnew{2}{0}{1}{2}{1}{-a-1,0}{\frac{\xi}{s}} \dd s.
 \end{align*}
@@
 \begin{align*}
-	\xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerG{0}{2}{2}{1}{2+a,1}{0}{\frac{s}{\xi}} \dd s
+	\xi^{a+1} \int_0^1 s^{c-1} (1-s)^{b-1} \MeijerGnew{0}{2}{2}{1}{2+a,1}{0}{\frac{s}{\xi}} \dd s.
 \end{align*}
@@
 \begin{align*}
-	\xi^{a+1} \Gamma(b) \MeijerG{0}{3}{3}{2}{1-c,2+a,1}{0,1-c-b}{\xi^{-1}}
+	\xi^{a+1} \Gamma(b) \MeijerGnew{0}{3}{3}{2}{1-c,2+a,1}{0,1-c-b}{\xi^{-1}}.
 \end{align*}
@@
 \begin{align*}
-	\xi^{a+1} \Gamma(b) \MeijerG{3}{0}{2}{3}{1,b+c}{c,-1-a,0}{\xi}
+	\xi^{a+1} \Gamma(b) \MeijerGnew{3}{0}{2}{3}{1,b+c}{c,-1-a,0}{\xi}.
 \end{align*}
@@
 	\int_0^1 z^a e^{-\xi/z} B^-(1-z;b,c) \dd z =
-	\xi^{6a-k-2} \Gamma(2\alpha) \MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}
+	\xi^{6a-k-2} \Gamma(2\alpha) \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}.
 \end{equation}
@@
 	&\hspace{15pt}\left.- \xi^{4\alpha-2} 
-		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)\\
+		\Gamma(2\alpha+1)\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)\\
 \end{align*}%{4\alpha-k+1,6\alpha-k-1}{6\alpha-k-2,2\alpha-k+1,0}
@@
 	&\hspace{10pt}\hspace{10pt}\left.- \xi^{4\alpha-2} 
-		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi}  \right) \\
+		\Gamma(2\alpha+1)\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi}  \right) \\
 	&\hspace{10pt}-\frac{\xi^{2\alpha}}{4(\alpha-1)} \left( -\Gamma^+(1 - 2 \alpha, \xi) - 
@@
 	&\hspace{10pt}\hspace{10pt}\left.- \xi^{4\alpha-2} 
-		\Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi}  \right)\\
+		\Gamma(2\alpha+1)\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi}  \right)\\
 	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}
@@
 \end{align*}
-and note that this equals the expression in Theorem~\ref{thm:clustering_coefficient_hyperbolic}. %% when $\alpha \ne 1$.
+which is the expression in Theorem~\ref{thm:clustering_coefficient_hyperbolic}.
 
@@
 	&\hspace{10pt}\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
-	&\hspace{10pt}\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right),
+	&\hspace{10pt}\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right),
 \end{align*}
@@
 taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$, it is still helpful
-to derive an alternate, more explicit expression.
+to derive an alternative, more explicit expression.
 This is what we will do in the current section.
@@
 We want to compute the limit $\lim_{\alpha \rightarrow 1} P_\alpha(y_0(z_0))$. For $\alpha \neq 1$, we label the terms as follows:
+%\begin{align*}
+%&P_\alpha(y_0(z_0)) \\
+%&= \frac{1}{\alpha-1}\left(s_1(\alpha,z_0)+s_2(\alpha,z_0)+s_3(\alpha,z_0)+s_4(\alpha,z_0) 
+%+s_5(\alpha,z_0)+s_6(\alpha,z_0)+s_7(\alpha,z_0)\right)
+%\end{align*}
 \begin{align*}
@@
 $s_i(\alpha)=s_i(1)+s_i'(1)(\alpha-1)+\frac{s_i''(1)}{2}(\alpha-1)^2+o((\alpha-1)^2)$ for $i\in \{3,4\}$. Using these expansions, we can rewrite
+%\begin{align*}
+%&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
+%s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
+%&\left.+\frac{1}{\alpha-1}(s_3(1)+s_4(1)+(s_3'(1)+s_4'(1))(\alpha-1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1)^2 +o((\alpha-1)^2)) \right)
+%\end{align*}
 \begin{align*}
@@
 s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
-&\left.+\frac{1}{\alpha-1}(s_3(1)+s_4(1)+(s_3'(1)+s_4'(1))(\alpha-1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1)^2 +o((\alpha-1)^2)) \right)
+&\left.+\frac{s_3(1)+s_4(1)}{\alpha-1} + s_3'(1)+s_4'(1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1) +o((\alpha-1)) \right)
 \end{align*}
@@
 s_2(\alpha) &=\frac{1}{2}z_0 +z_0 (\alpha-1)+o(\alpha-1) \\
-s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
+%s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
+s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{2}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
+%s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
+%&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
 s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
-&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
-s_5(\alpha) &= \frac{z_0^2}{4} B^-(1/2;3,0) + z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) \right. \\
- 	&\hspace{20pt}\left.+1/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right)  (\alpha-1)+o (\alpha-1)\\
-s_6(\alpha) &= \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1)+o(\alpha-1)\\
-s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
-&\qquad \left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+o(\alpha-1)
+&\qquad+\frac{z_0^2}{8}\left(8\left(\ln\frac{z_0}{2}\right)^2+2\ln\frac{z_0}{2} - \frac{1}{2}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
+s_5(\alpha) &= \frac{z_0^2}{4} B^-(1/2;3,0) +o(\alpha-1) \\
+	&\hspace{10pt}+ z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) +1/2\int_0^{\frac{1}{2}} \ln(t(1-t))t^2(1-t)^{-1} \dd t \right)  (\alpha-1)+o (\alpha-1)\\
+s_6(\alpha) &= \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1 + \smallO{a-1})\\
+%s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
+%&\qquad \left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+o(\alpha-1)
+s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) +o(\alpha-1) \\
+	&\hspace{10pt}- z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) 
+		+\int_0^{1-z_0} t(1-t)^{-2}\ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} \dd t \right) (\alpha-1).
 \end{align*}
@@
 +\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
-&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2 
--\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2 \\ 
-&\hspace{50pt}+\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}+\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0 \\
-&=0
-\end{align*}
-Finally, it follows that
+&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\left(\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2\right) 
++\left(-\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2\right) \\ 
+&\hspace{50pt}+\left(\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}\right)+\left(\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0\right) &=0,
+\end{align*}
+using that %$B^-(\frac{1}{2};3,0)=-\frac{5}{8}+\ln 2$ and $B^-(1-z_0;2,-1)=-1+z_0^{-1}+\ln z_0$.
+\begin{align*}
+B^-(\frac{1}{2};3,0)&=\int_0^\frac{1}{2}t^2(1-t)^-1dt=\int_\frac{1}{2}^1 (1-s)^2 s^{-1}ds\\
+&=\int_\frac{1}{2}^1 s^{-1}-2+sds = -2+\frac{1}{2}-\ln\frac{1}{2}+1-\frac{1}{8}=-\frac{5}{8}+\ln 2
+\end{align*}
+and
+\begin{align*}
+B^-(1-z_0;2,-1)&=\int_0^{1-z_0} t(1-t)^{-2}dt = \int_{z_0}^1 (1-s)s^{-2}ds \\
+&=\int_{z_0}^1 s^{-2}-s^{-1}ds = -1+z_0^{-1}+\ln z_0.
+\end{align*}
+
+Finally, it follows that as $\alpha \to 1$,
 \begin{align*}
@@
 		+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
-	&\hspace{10pt}+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+1/2\int_0^{\frac{1}{2}} 
-		\ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \right) \\
-	&\hspace{10pt}- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) \\
+	&\hspace{10pt}+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+ \frac{1}{2}\int_0^{\frac{1}{2}} 
+		\ln(t(1-t)) \, t^2(1-t)^{-1} \dd t \right) \\
+	&\hspace{10pt}- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0}\ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} 
+		\dd t \right) \\
 	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2
@@
 	&\hspace{10pt}-\frac{5}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2-\frac{5z_0^2}{32} +\frac{z_0^2 \ln2}{4}\\
-	&\hspace{10pt}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}\dd t \\
+	&\hspace{10pt}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t(1-t)) \, t^2(1-t)^{-1}\dd t \\
 	&\hspace{10pt}+\frac{(1-z_0)^2}{4}\ln(1-z_0) -\frac{1}{8}+\frac{z_0}{4}-\frac{z_0^2}{8}\\
 	&\hspace{10pt}+ z_0^2\ln(z_0)-z_0 \ln z_0-z_0^2(\ln z_0)^2
-		-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
+		-z_0^2\int_0^{1-z_0} \ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2}  \dd t \\
 	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
@@
 	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
-		+z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1}dt \\
-	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \\
+		+z_0^2/2\int_0^{\frac{1}{2}} \ln(t(1-t)) \, t^2(1-t)^{-1} \dd t \\
+	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} \ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} \dd t \\
 	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
@@
 \begin{align*}
-	&z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt\\
-	&= -\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1).
+	&z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2} \dd t\\
+	&= -\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 \Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1).
 \end{align*}
@@
 	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	\sim \xi_{\alpha, \nu}^{2\beta} k^{-2\beta}.
+	\sim \xi^{2\beta} k^{-2\beta}.
 \end{equation}
@@
 \end{align*}
-Because for any $b < 1$, $B^-(1-z,a,b)$ converges to $B^-(a,b) < \infty$ as $z \to 0$, we get that as $y \to \infty$, the first line is asymptotically equivalent to
+Because for any $b < 1$, $B^-(1-z: a,b)$ converges to $B(a,b) < \infty$ as $z \to 0$, we get that as $y \to \infty$, the first line is asymptotically equivalent to
 \[
@@
 
-Similar to the previous case we use Lemma~\ref{lem:Paneq1} to obtain
+Similar to the previous case we use Lemma~\ref{lem:Paneq1} to obtain (evaluating the expressions for $\alpha = 3/4$)
 \begin{align*}
 	\frac{2}{y} e^{\frac{y}{2}}P(y) 
-	&= \frac{2}{y}\frac{B^-(1-e^{-\frac{y}{2}}, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)}\\
-	&\hspace{10pt} + \frac{2}{y}\frac{e^{\frac{y}{2}}\left((1 - e^{-\frac{y}{2}})^{2\alpha} - 1\right)}{8(\alpha - 1)\alpha}
-		+ \frac{(\alpha - \frac{1}{2})}{(\alpha - 1)y} 
-		-\frac{(\alpha - \frac{1}{2})^2 e^{-\frac{y}{2}}}{4(\alpha - 1)^2 y} \\
+	&= \frac{2}{y}B^-(1-e^{-\frac{y}{2}}; 3/2, 0)
+		- \frac{4}{y}\frac{e^{\frac{y}{2}}\left((1 - e^{-\frac{y}{2}})^{3/2} - 1\right)}{3}
+		- \frac{1}{y} - \frac{ e^{-\frac{y}{2}}}{4 y} \\
 	&\hspace{10pt}+ \frac{2}{y} 
-		\left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
-		+ \frac{(\alpha - \frac{1}{2}) B^-(\frac{1}{2}; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right)
+		\left(\frac{5}{3} 
+		- \frac{2 B^-(\frac{1}{2}; 5/2, -1/2)}{3}\right)
 \end{align*}
@@
 \begin{equation}\label{eq:asymptotics_Delta_P_auxiliary}
-	e^{\frac{y}{2}}\left(\left(1 - e^{-\frac{y}{2}}\right)^{2\alpha}-1\right) 
-	\sim -2\alpha,
+	e^{\frac{y}{2}}\left(\left(1 - e^{-\frac{y}{2}}\right)^{3/2}-1\right) 
+	\sim -\frac{3}{2},
 \end{equation}
@@
 \[
-	\lim_{y \to \infty} \frac{2}{y}\frac{e^{\frac{y}{2}}\left((1 - e^{-\frac{y}{2}})^{2\alpha} - 1\right)}{8(\alpha - 1)\alpha} = 0.
+	\lim_{y \to \infty} \frac{4}{y}\frac{e^{\frac{y}{2}}\left((1 - e^{-\frac{y}{2}})^{3/2} - 1\right)}{3} = 0.
 \]
@@
 \[
-	\frac{2}{y}\frac{B^-(1-e^{-\frac{y}{2}}, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)} 
-	= -\frac{1}{\log(z)}\frac{B^-(1-z, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)}.
-\]
-Since $B^-(1-z,2\alpha,0) \sim - \log(z)$ as $z \to \infty$, see Lemma~\ref{lem:asymptotics_incomplete_beta}, it now follows
+	\frac{2}{y}B^-(1-e^{-\frac{y}{2}}; 3/2, 0) 
+	= -\frac{B^-(1-z; 3/2, 0)}{\log(z)} .
+\]
+Since $B^-(1-z,3/2,0) \sim - \log(z)$ as $z \to 0$, see Lemma~\ref{lem:asymptotics_incomplete_beta}, it now follows
 that for $\alpha = 3/4$,
 \[
-	\lim_{y \to \infty} \frac{2}{y}\frac{B^-(1-e^{-\frac{y}{2}}, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)}
-	= \lim_{z \to 0} -\frac{1}{\log(z)}\frac{B^-(1-z, 2\alpha, 3 - 4\alpha)}{4(\alpha - 1)} = 1.
+	\lim_{y \to \infty} \frac{2}{y} B^-(1-e^{-\frac{y}{2}}; 3/2, 0)
+	= \lim_{z \to 0} -\frac{1}{\log(z)} B^-(1-z; 3/2, 0) = 1.
 \]
@@
 		\frac{B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
-	&= \lim_{z \to 0} z^{4\alpha - 3} \frac{B^-(1 - z, 2 \alpha, 3 - 4 \alpha)}{4(\alpha - 1)}\\
+	&= \lim_{z \to 0} z^{4\alpha - 3} \frac{B^-(1 - z; 2 \alpha, 3 - 4 \alpha)}{4(\alpha - 1)}\\
 	&= \frac{1}{4(\alpha - 1)(4\alpha - 3)}.
@@
 \[
-	a(k)^\pm = 2 \log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
+	a^\pm(k) = 2 \log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
 \] 
@@
 	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	= (1+\smallO{1}) \int_{a(k)^-}^{a(k)^+} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y.
+	= (1+\smallO{1}) \int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y.
 \end{equation}
@@
 which implies that $\rho(y,k)$ attains its maximum at $\mu(y) = k$.
-Moreover we see that the derivative is strictly positive when $\mu(y) < k$ and strictly negative when $\mu(k) > k$.
-Since $\mu(a(k)^-) < k$ and $\mu(a(k)^+) > k$, we conclude that $\rho(y,k)$, as a function of $y$, is strictly increasing on $[0,a(k)^-]$ and strictly decreasing on $[a(k)^+,\infty)$.
+Moreover we see that the derivative is strictly positive when $\mu(y) < k$ and strictly negative when $\mu(y) > k$.
+Since $\mu(a^-(k)) < k$ and $\mu(a^+(k)) > k$, we conclude that $\rho(y,k)$, as a function of $y$, is strictly increasing on $[0,a^-(k)]$ and strictly decreasing on $[a^+(k),\infty)$.
 Hence, using that $P(y) \le 1$,
 \begin{align*}
-	&\hspace{-20pt}\int_{\R_+ \setminus [a(k)^-, a(k)^+]} P(y) \rho(y,k) 
+	&\hspace{-20pt}\int_{\R_+ \setminus [a^-(k), a^+(k)]} P(y) \rho(y,k) 
 		\alpha e^{-\alpha y} \dd y\\
-    &\le \int_0^{a(k)^-} \rho(y,k) \alpha e^{-\alpha y} \dd y 
-    	+ \int_{a(k)^+}^{\infty}\rho(y,k) \alpha e^{-\alpha y}x \dd y \\
-   	&\le \rho(a(k)^-,k)\int_0^{a(k)^-} e^{-\alpha y} \, \dd y
-   		+ \rho(a(k)^+,k) \int_{a(k)^+}^{\infty} e^{-\alpha y} \, \dd y\\
-   	&= \bigO{1}\left(\rho(a(k)^-,k) + \rho(a(k)^+,k)\right),
+    &\le \int_0^{a^-(k)} \rho(y,k) \alpha e^{-\alpha y} \dd y 
+    	+ \int_{a^+(k)}^{\infty}\rho(y,k) \alpha e^{-\alpha y}x \dd y \\
+   	&\le \rho(a^-(k),k)\int_0^{a^-(k)} e^{-\alpha y} \, \dd y
+   		+ \rho(a^+(k),k) \int_{a^+(k)}^{\infty} e^{-\alpha y} \, \dd y\\
+   	&= \bigO{1}\left(\rho(a^-(k),k) + \rho(a^+(k),k)\right),
 \end{align*}
@@
 \[
-	\rho(a(k)^\pm,k) = \bigO{k^{-(1+C^2)/2}}.
-\]
-Since the arguments are almost completely identical, we give the prove for $a(k)^+$.
+	\rho(a^\pm(k),k) = \bigO{k^{-(1+C^2)/2}}.
+\]
+Since the arguments are almost completely identical, we give the prove for $a^+(k)$.
 
@@
 \begin{align*}
-	\rho(a(k)^+,k) &= \frac{\mu(a(k)^+)^{k}}{k!} e^{-\mu(a(k)^+)} \\
-	&\sim (2\pi)^{-1/2} k^{-1/2} \left(\frac{\mu(a(k)^+}{k}\right)^{k} e^{-(\mu(a(k)^+ - k)}\\
+	\rho(a^+(k),k) &= \frac{\mu(a^+(k))^{k}}{k!} e^{-\mu(a^+(k))} \\
+	&\sim (2\pi)^{-1/2} k^{-1/2} \left(\frac{\mu(a^+(k))}{k}\right)^{k} e^{-(\mu(a^+(k) - k)}\\
 	&= (2\pi)^{-1/2} k^{-1/2} 
-		e^{-k\left(\frac{\mu(a(k)^+)}{k} - 1 - \log\left(\frac{\mu(a(k)^+)}{k}\right)\right)}.
-\end{align*}
-Since 
-\[
-	\frac{\mu(a(k)^+)}{k} = 1 + C \sqrt{\frac{\log(k)}{k}}
+		e^{-k\left(\frac{\mu(a^+(k))}{k} - 1 - \log\left(\frac{\mu(a^+(k))}{k}\right)\right)}.
+\end{align*}
+Since, for sufficiently large $k$,
+\[
+	\frac{\mu(a^+(k))}{k} = 1 + C \sqrt{\frac{\log(k)}{k}}
 \]
@@
 \begin{align*}
-	\rho(a(k)^+,k) 
+	\rho(a^+(k),k) 
 	&\sim \sqrt{2\pi} k^{-1/2} 
@@
 \]
-as $k \to \infty$. Note that this implies that if $P(y) = h(y)(1 + \smallO{1})$ as $y \to \infty$, then 
+as $k \to \infty$. Note that this implies that if $P(y) = h(y)(1 + \smallO{1})$, uniformly in $y$, as $y \to \infty$, then 
 \begin{equation}\label{eq:asymptotics_average_clustering_error_term}
@@
 We now proceed with the proof of Proposition~\ref{prop:asymp}, which is split over the different cases for $\alpha$.
-First we combine~\eqref{eq:degree_distribution_P_asymptotics} and~\eqref{eq:general_integral_rho_y_k} to obtain the following scaling result
-\begin{equation}\label{eq:general_clustering_integral_scaling}
-	\frac{\int_0^\infty e^{-\beta y} \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	\sim \xi_{\alpha, \nu}^{2\beta} k^{-2\beta}.
-\end{equation}
 
@@
 \begin{equation}\label{eq:average_clustering_proof_34_main}
-	\int_{a(k)^-}^{a(k)^+} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	\sim \int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y.
+	\int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	\sim \int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y.
 \end{equation}
@@
 \begin{align*}
-	\int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
-	&\le \frac{a(k)^+}{2} \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+	\int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+	&\le \frac{a^+(k)}{2} \int_{a^-(k)}^{a^+(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
 \end{align*}
@@
 \begin{align*}
-	\int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
-	&\ge \frac{a(k)^-}{2} \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
-\end{align*}
-Now observe that
-\[
-	\frac{a(k)^\pm}{2} = \log\left(\frac{k \pm \sqrt{k\log(k)}}{\xi_{\alpha, \nu}}\right) \sim \log(k)
+	\int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+	&\ge \frac{a^-(k)}{2} \int_{a^-(k)}^{a^+(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+\end{align*}
+Now observe that as $k \to \infty$,
+\[
+	\frac{a^\pm(k)}{2} = \log\left(\frac{k \pm \sqrt{k\log(k)}}{\xi_{\alpha, \nu}}\right) \sim \log(k)
 \]
@@
 \[
-	\limsup_{k \to \infty} \frac{\int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	{\log(k) \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \le 1.
+	\limsup_{k \to \infty} \frac{\int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\log(k) \int_{a^-(k)}^{a^+(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \le 1.
 \]
@@
 \[
-	\liminf_{k \to \infty} \frac{\int_{a(k)^-}^{a(k)^+} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	{\log(k) \int_{a(k)^-}^{a(k)^+} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \ge 1.
-\]
-This proofs~\eqref{eq:average_clustering_proof_34_main}.
+	\liminf_{k \to \infty} \frac{\int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\log(k) \int_{a^-(k)}^{a^+(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \ge 1.
+\]
+This proves~\eqref{eq:average_clustering_proof_34_main}.
 
@@
 \[
-	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y \sim \int_{a(k)^-}^{a(k)^+} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y \sim \int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
 \]
@@
 \[
-	\gamma(k) \sim \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} \, \frac{\int_0^{\infty} e^{-y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y} {\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} 
+	\gamma(k) \sim \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} \, \frac{\int_0^{\infty} e^{-y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y} {\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y} 
 	\sim \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} \, \xi k^{-1} = \frac{8\alpha \nu}{\pi(4\alpha - 3)}.

### 2019-03-25 concentration.tex
processed most of Nikoloas comments for sections 1-3

@@
 
-\subsection{Joint neighborhoods and degrees in $\Gbox$}
+\subsection{Joint neighbourhoods and degrees in $\Gbox$}
 
 To prove Proposition~\ref{prop:concentration_tilde_T_P_n} we need to understand the joint degree distribution in $\Gbox$.
-This subsequently requires us to compute the joint neighborhoods in $\Gbox$ of two points $p, p^\prime \in \Rcal$.
+This subsequently requires us to compute the joint neighbourhoods in $\Gbox$ of two points $p, p^\prime \in \Rcal$.
 We perform the analysis in this section.
@@
 \end{equation}
-We will show (see Corollary~\ref{cor:expected_common_neighbors_Ecal_set}) that for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ it holds that $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$ and hence the joint degree distribution factorizes on this set.
+We will show (see Corollary~\ref{cor:expected_common_neighbours_Ecal_set}) that for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ it holds that $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$ and hence the joint degree distribution factorizes on this set.
 We will use this set later in Section~\ref{ssec:concentration_tilde_T} to prove Proposition~\ref{prop:concentration_tilde_T_P_n}.
-The main idea behind the above result is that if $p$ and $p^\prime$ are sufficiently separated in the $x$-direction, then the overlap of their neighborhoods $\BallPon{p} \cap \BallPon{p^\prime}$ is of smaller order than $\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}$.
-We shall therefore proceed with analyzing the joint neighborhoods in $\Gbox$.
+The main idea behind the above result is that if $p$ and $p^\prime$ are sufficiently separated in the $x$-direction, then the overlap of their neighbourhoods $\BallPon{p} \cap \BallPon{p^\prime}$ is of smaller order than $\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}$.
+We shall therefore proceed with analyzing the joint neighbourhoods in $\Gbox$.
 %
@@
 
-\subsubsection*{Joint neighborhoods}
+\subsubsection*{Joint neighbourhoods}
 
 Let $p, p^\prime \in \Rcal$ and denote by
-%Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $\Gbox$, i.e.
+%Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbours of $p$ and $p^\prime$ in $\Gbox$, i.e.
 those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection.
 In addition we denote by
-$\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$.
-We shall establish an upper bound on the expected number of joint neighbors when $p$ and $p6\prime$ are sufficiently separated.
+$\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbours of $p$ and $p^\prime$.
+We shall establish an upper bound on the expected number of joint neighbours when $p$ and $p6\prime$ are sufficiently separated.
 Observe that $\Exp{\Ncal_{\text{box}}(p,p^\prime)} = \Mu{\BallPon{p} \cap \BallPon{p^\prime}}$.
 
-%as well as an asymptotic expression for the expected number points in the joint neighborhood.
+%as well as an asymptotic expression for the expected number points in the joint neighbourhood.
 For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large.
-Figure~\ref{fig:representation_disjoint_neighborhoods_P_n}-\ref{fig:representation_disjoint_neighborhoods_P_n_3} show the different situations that occur.
+Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n}-\ref{fig:representation_disjoint_neighbourhoods_P_n_3} show the different situations that occur.
 %
@@
 %\end{tikzpicture}
-%\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
-%\label{fig:representation_disjoint_neighborhoods_P_n}
+%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbours_P_n} and Lemma~\ref{lem:common_neighbours_Pcal_n}.}
+%\label{fig:representation_disjoint_neighbourhoods_P_n}
 %\end{figure}~
@@
 %\end{tikzpicture}
-%\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbors_P_n} and Lemma~\ref{lem:common_neighbors_Pcal_n}.}
-%\label{fig:representation_disjoint_neighborhoods_P_n_2}
+%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbours_P_n} and Lemma~\ref{lem:common_neighbours_Pcal_n}.}
+%\label{fig:representation_disjoint_neighbourhoods_P_n_2}
 %\end{figure}~
@@
 \end{tikzpicture}
-\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:disjoint_neighbors_P_n_large}.
+\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:disjoint_neighbours_P_n_large}.
 Note that although here $p^\prime \notin \BallPon{p}$, this is not true in general.
 This situation was merely chosen to improve readability of the figure.}
-\label{fig:representation_disjoint_neighborhoods_P_n_3}
+\label{fig:representation_disjoint_neighbourhoods_P_n_3}
 \end{figure}
 
-We start by analyzing the shape of joint neighborhood.
+We start by analyzing the shape of joint neighbourhood.
 Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$.
 To understand the computation it is helpful to have a picture.
-Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3} shows such an example.
+Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n_3} shows such an example.
 There are several different quantities that are important.
@@
 Since $x = 0$ these heights are the same and we denote this by $h(y)$.
-We also need to know the coordinates $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$ and those for the intersection of the left boundary of the neighborhood of $p$ with the right boundary of the neighborhood of $p^\prime$, which we denote by $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$.
-Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, as is the case in Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3}.
+We also need to know the coordinates $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ of the intersection of the right boundary of the neighbourhood of $p$ with the left boundary of the neighbourhood of $p^\prime$ and those for the intersection of the left boundary of the neighbourhood of $p$ with the right boundary of the neighbourhood of $p^\prime$, which we denote by $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$.
+Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighbourhoods do not intersect, as is the case in Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n_3}.
 The condition $d(p,p^\prime) > 0$ is exactly the right notion for $p$ and $p^\prime$ being sufficiently separated.
@@
 %
-%\begin{lemma}\label{lem:disjoint_neighbors_P_n}
+%\begin{lemma}\label{lem:disjoint_neighbours_P_n}
 %Let $p, p ^\prime \in \Rcal$ and denote $y^\ast = \min\{y, y^\prime\}$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
@@
 %In order to proof the result we will consider the area in between the two left boundaries of the balls $\BallPon{p}$ and
-%$\BallPon{p^\prime}$ up to the height $h^\ast := \min\{h(y), h_2(p^\prime)\}$, see Figure~\ref{fig:representation_disjoint_neighborhoods_P_n} and Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_2} for reference.
+%$\BallPon{p^\prime}$ up to the height $h^\ast := \min\{h(y), h_2(p^\prime)\}$, see Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n} and Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n_2} for reference.
 Note that here we do not need to consider different cases depending on whether $|x - x^\prime| \le e^{(y + y^\prime)/2}$ or $|x - x^\prime| > e^{(y + y^\prime)/2}$.
@@
 %
-%\begin{lemma}\label{lem:disjoint_neighbors_P_n_large}
+%\begin{lemma}\label{lem:disjoint_neighbours_P_n_large}
 %Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
@@
 %\]
-%We shall compute the integral on the right. We refer to Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3} for further clarification. 
-%
-%Before we proceed we show that the neighborhoods of $p$ and $p^\prime$ below $\hat{y}_{\text{right}}(p,p^\prime)$ are disjoint.
+%We shall compute the integral on the right. We refer to Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n_3} for further clarification. 
+%
+%Before we proceed we show that the neighbourhoods of $p$ and $p^\prime$ below $\hat{y}_{\text{right}}(p,p^\prime)$ are disjoint.
 This is clearly true when $\hat{y}_{\text{right}}(p,p^\prime) \le h_2(p^\prime)$ so suppose that $\hat{y}_{\text{right}}(p,p^\prime) > h_2(p^\prime)$.
@@
 %\end{align*}
-%and hence the neighborhoods of $p$ and $p^\prime$ below $\hat{y}_{\text{right}}(p,p^\prime)$ are disjoint. It then follows that
+%and hence the neighbourhoods of $p$ and $p^\prime$ below $\hat{y}_{\text{right}}(p,p^\prime)$ are disjoint. It then follows that
 %\begin{align*}
@@
 %\end{tikzpicture}
-%\caption{Schematic representation of the neighborhoods of $p$ and $p^\prime$ in $\Gbox$ used for the proof of Lemma \ref{lem:common_neighbors_Pcal_n}.}
-%\label{fig:representation_joint_neighborhoods}
+%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ used for the proof of Lemma \ref{lem:common_neighbours_Pcal_n}.}
+%\label{fig:representation_joint_neighbourhoods}
 %\end{figure}
 
-The following result shows that if $d(p,p^\prime) > 0$, then the expected number of common neighbors is $\smallO{\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}}$.
-
-\begin{lemma}\label{lem:common_neighbors_Pcal_n}
+The following result shows that if $d(p,p^\prime) > 0$, then the expected number of common neighbours is $\smallO{\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}}$.
+
+\begin{lemma}\label{lem:common_neighbours_Pcal_n}
 Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime| > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
@@
 \]
-The following result, which follows from Lemma~\ref{lem:common_neighbors_Pcal_n}, shows that on this set, the expected number of common neighbors is $\smallO{k_n}$.
-
-\begin{lemma}\label{cor:expected_common_neighbors_Ecal_set}
+The following result, which follows from Lemma~\ref{lem:common_neighbours_Pcal_n}, shows that on this set, the expected number of common neighbours is $\smallO{k_n}$.
+
+\begin{lemma}\label{cor:expected_common_neighbours_Ecal_set}
 Fix $0 < \varepsilon < 1$ and let $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. Then for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, as $n \to \infty$,
@@
 \begin{proof}
-Since for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ we have $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$, Lemma~\ref{lem:common_neighbors_Pcal_n} implies that
+Since for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ we have $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$, Lemma~\ref{lem:common_neighbours_Pcal_n} implies that
 \[
@@
 \end{align*}
-Since by Lemma~\ref{cor:expected_common_neighbors_Ecal_set} $\Mu{\BallPon{p} \cup \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}$, it follows from Lemma~\ref{lem:near_independence_poisson} that
+Since by Lemma~\ref{cor:expected_common_neighbours_Ecal_set} $\Mu{\BallPon{p} \cup \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}$, it follows from Lemma~\ref{lem:near_independence_poisson} that
 \[
@@
 
-%For this we note that by Lemma \ref{lem:disjoint_neighbors_P_n} and Lemma \ref{lem:disjoint_neighbors_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\text{box}}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$.
+%For this we note that by Lemma \ref{lem:disjoint_neighbours_P_n} and Lemma \ref{lem:disjoint_neighbours_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\text{box}}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$.
 In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)^c$.

### 2019-03-25 concentration_argument.tex
processed most of Nikoloas comments for sections 1-3

@@
 
-Although powerful, the current versions of the concentration of heights arguments are only valid for the function $\rho(y,k_n) := \Prob{\Po\left(\Mu{\BallPo{y}}\right) = k_n}$, which uses the neighborhoods in the infinite model $\Ginf$.
+Although powerful, the current versions of the concentration of heights arguments are only valid for the function $\rho(y,k_n) := \Prob{\Po\left(\Mu{\BallPo{y}}\right) = k_n}$, which uses the neighbourhoods in the infinite model $\Ginf$.
 Since we will also be working in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, we would like to use concentration of heights arguments when the integrand contains either the function $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.

### 2019-03-25 introduction.tex
processed most of Nikoloas comments for sections 1-3

@@
 As mentioned, its nodes are situated in the hyperbolic plane $\Haa$, which is a surface with constant Gaussian curvature $-1$.
-This surface has several convenient representations (i.e.~coordinate maps), including the Poincar\'e halfplane model, the Poincar\'e disk model and the Klein disk model.
+This surface has several convenient representations (i.e.~coordinate maps), such as the Poincar\'e halfplane model, the Poincar\'e disk model and the Klein disk model.
 A gentle introduction to Gaussian curvature, hyperbolic geometry and these representations of the hyperbolic plane can be found in~\cite{stillwell2012geometry}.
@@
 \begin{itemize}
-\item The vertex set is given by $n$ i.i.d.~points $u_1, \dots, u_n$ denoted in polar coordinates $(r_i, \theta_i)$, where the angular coordinate $\theta$ is chosen uniformly from $(-\pi,\pi]$ while the radial coordinate $r$ is sampled independently according to the cumulative distribution function
+\item The vertex set is given by $n$ i.i.d.~points $u_1, \dots, u_n$ denoted in polar coordinates $u_i = (r_i, \theta_i)$, where the angular coordinate $\theta$ is chosen uniformly from $(-\pi,\pi]$ while the radial coordinate $r$ is sampled independently according to the cumulative distribution function
 \begin{equation}\label{eq:def_hyperbolic_point_distribution}
@@
 Friedrich and Krohmer~\cite{blasius2018cliques} studied the size of the largest clique as well as the number of cliques of a given size.
-Bogu\~{n}a et al.~\cite{boguna2010sustaining} and Bl\"asius et al.~\cite{BlasiusMLE} considered fitting the KPKVB model to data using maximum likelihood estimation.
+Bogu\~{n}a et al.~\cite{boguna2010sustaining} and Bl\"asius et al.~\cite{blasius2018efficient} considered fitting the KPKVB model to data using maximum likelihood estimation.
 Kiwi and Mitsche~\cite{kiwi2018spectral} studied the spectral gap and related properties, and Bl\"asius et al.\cite{blasius2016hyperbolic} considered the tree-width and related parameters of the KPKVB model.
@@
 where $E(G)$ denotes the edge set of $G$ and $\text{deg}(v)$ is the degree of vertex $v$.
-That is, provided $v$ has degree at least two, $c(v)$ equals the number of edges that are actually present between the neighbours \PvdH{I think it is neighbors in US English vs neighbours in UK English.
-Is there any specific reason to us the UK version?} of $v$ divided by the number of edges that could possibly be present between the neighbours given the degree of $v$.
+That is, provided $v$ has degree at least two, $c(v)$ equals the number of edges that are actually present between the neighbours of $v$ divided by the number of edges that could possibly be present between the neighbours given the degree of $v$.
 The clustering coefficient of $G$ is now defined as the average of $c(v)$ over all vertices $v$:
@@
 In addition to the clustering coefficient, we shall also be interested in the {\em clustering function}.
-This assigns to each integer $k$ the value
+This assigns to each non-negative integer $k$ the value
 \begin{equation}\label{eq:def_clustering_function}
 	c(k; G) := \begin{cases}
-		\displaystyle \frac{1}{N_k} \sum_{v \in V(G), \atop \text{deg}(v)=k}  c(v),  &\mbox{ if } N_k \ge 1,\\
+		\displaystyle \frac{1}{N(k)} \sum_{v \in V(G), \atop \text{deg}(v)=k}  c(v),  &\mbox{ if } N(k) \ge 1,\\
 		0, &\mbox{else,}
@@
 \end{equation}
-where $N_k$ denotes the number of vertices of degree exactly $k$ in $G$.
+where $N(k)$ denotes the number of vertices of degree exactly $k$ in $G$.
 In other words, the clustering function assigns to the integer $k$ the average of the local clustering coefficient over all vertices of degree $k$.
-We remark that, while it might seem natural to consider $c(k)$ to be ``undefined'' when $N_k=0$, we prefer to use the above definition for technical
+We remark that, while it might seem natural to consider $c(k)$ to be ``undefined'' when $N(k)=0$, we prefer to use the above definition for technical
 convenience.  This way $c(k; G(n;\alpha,\nu) )$ is a plain vanilla random variable and we can for instance compute its moments without any issues.
@@
  $B(a,b) := \int_0^1 u^{a-1}(1-u)^{b-1}\text{d}u = \Gamma(a)\Gamma(b) / \Gamma(a+b)$ for the beta function and 
- $B^-(x,a,b) := \int_0^x u^{a-1}(1-u)^{b-1}\text{d}u$ for the lower incomplete beta function. 
+ $B^-(x ; a,b) := \int_0^x u^{a-1}(1-u)^{b-1}\text{d}u$ for the lower incomplete beta function. 
 We write $U(a,b,z)$ for the hypergeometric U-function (also called Tricomi's confluent hypergeometric function), which 
@@
 
-Theorem~\ref{thm:mainkfixed} in fact generalises to increasing sequences $(k_n)_n$.
+Theorem~\ref{thm:mainkfixed} in fact generalises to increasing sequences $(k_n)_{n \ge 1}$.
 
@@
 Note that Theorem~\ref{thm:mainktoinfty} implies that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows, whose scaling is given in the above result.
-In particular, this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac34$, and confirms it for $\alpha > \frac34$.
+In particular, this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac34$, and confirms it only for $\alpha > \frac34$.
 
@@
 \begin{align*}
-	\Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|} 
-	&\ge \Exp{\left|\frac{c_{\H,n}(k_n)}{f(k_n)} - 1\right|\ind{N_n(k_n) = 0}}\\ 
-	&\ge \Prob{N_{n}(k_n) = 0} \ge 1 - \Exp{N_{\H,n}(k_n)}.
+	\Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|} 
+	&\ge \Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|\ind{N_n(k_n) = 0}}\\ 
+	&\ge \Prob{N_{n}(k_n) = 0} \ge 1 - \Exp{N_n(k_n)}.
 \end{align*}
@@
 	\lim_{n \to \infty} \Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|} 
-	\ge \lim_{n \to \infty} 1 - \Exp{N_{n}(k_n)} = 1 \ne 0,
+	\ge 1 - \lim_{n \to \infty} \Exp{N_{n}(k_n)} = 1 \ne 0,
 \]

### 2019-03-25 paper.tex
finished section 9.3. Fixed the binomial Poisson coupling proof
processed most of Nikoloas comments for sections 1-3

@@
 \newcommand{\Nsymdiff}{N_{\H \bigtriangleup \Pcal}(k_n)}
+\renewcommand{\deg}{\mathrm{deg}}
 
@@
 The model is specified using three parameters: the number of nodes $n$, which we think of as going to infinity, and $\alpha, \nu > 0$, which we think of as constant.
-Roughly speaking $\alpha$ controls the power law exponent of the degree sequence and $\nu$ the average degree.
+Roughly speaking, the parameter $\alpha$ controls the power law exponent of the degree sequence and $\nu$ the average degree.
 
-Here we show that the clustering coefficient tends in probability \PvdH{Should we state here that convergence is in the stronger notion of expectation ($L_1$)?} to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
+Here we show that the clustering coefficient tends in probability to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
 This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant.
@@
 \newpage
-
-\PvdH{We need to fix the missing references. In addition, I have noticed the use of UK English grammar, which I do not often encounter in papers I read. Is there a specific reason for using this?}
 

### 2019-03-25 proof_overview_finite_k.tex
processed most of Nikoloas comments for sections 1-3

@@
 
-With this notation we then have that $\BallPo{p} \cap \Pcal$ denotes the set of neighbors of a vertex $p \in \Ginf$.
+With this notation we then have that $\BallPo{p} \cap \Pcal$ denotes the set of neighbours of a vertex $p \in \Ginf$.
 We will denote the intensity measure of the Poisson process $\mathcal{P}$ by $\mu = \mu_{\alpha, \nu}$, i.e. for every 
-Borel-measurable subset $S \subseteq \eR^2$ we have $\mu(S) = \int_S f(x,y) \dd x \dd y$
+Borel-measurable subset $S \subseteq \eR^2$ we have $\mu(S) = \int_S f(x,y) \dd x \dd y$.
 
@@
 setting of the Poissonized random geometric graphs, and in particular the Poissonized KPKVB model and the box model is the \emph{Campbell-Mecke formula}.
-We use a specific incarnation, which follows from Palm theory of Poisson point processes on metric spaces, see~\cite{last2017lectures}.
+We use a specific incarnation, which follows from the Palm theory of Poisson point processes on metric spaces, see~\cite{last2017lectures}.
 For this consider a Poisson point process $\Pcal$ on some metric space $\mathcal{M}$ with density $\mu$ and let $\mathcal{N}$ denote the set of all possible point configurations in $\mathcal{M}$, equipped with the sigma algebra of the process $\Pcal$.
-Then, for any integer $k$ and measurable function $h : \R^k \times \mathcal{N} \to \R$,
+Then, for any natural number $k$ and measurable function $h : \R^k \times \mathcal{N} \to \R$,
 \begin{equation}\label{eq:def_campbell_mecke}
 	\Exp{\sum_{p_1, \dots, p_k \in \Pcal}^{\ne} h(p_1, \dots, p_k, \Pcal)}
-	= \int_{\mathcal{S}} \dots \int_{\mathcal{S}} \Exp{h(x_1,\dots, x_k, \Pcal} \dd \mu(x_1) \dots \dd \mu(x_k),
+	= \int_{\mathcal{M}} \dots \int_{\mathcal{M}} \Exp{h(x_1,\dots, x_k, \Pcal} \dd \mu(x_1) \dots \dd \mu(x_k),
 \end{equation}

### 2019-03-25 proofs_infinite_k.tex
processed most of Nikoloas comments for sections 1-3

@@
 For the proof, we first identify the specific range of heights that give the main contribution to the triangle count, showing that the triangles coming from nodes with heights outside this range is of smaller order.
-Then we prove a concentration result for the main term, by carefully analyzing the joint neighborhoods of two nodes whose heights fall into the identified range.
+Then we prove a concentration result for the main term, by carefully analyzing the joint neighbourhoods of two nodes whose heights fall into the identified range.
 The full details are found in Section~\ref{sec:concentration_c_P_n}.

### 2019-04-02 proofs_finite_k.tex
implementation of Nikolaos comments in section 4.

@@
 we can use new graph labels $G_1 \subset G_2$; e.g.
-if $N\geq n$, then $G_1 = G(n;\alpha,\nu)$ and $G_2 = \GPo(n;\alpha,\nu)$.
+if $N\geq n$, then $G_1 \stackrel{d}{=} G(n;\alpha,\nu)$ and $G_2 \stackrel{d}{=} \GPo(n;\alpha,\nu)$.
 We write $V_{1,k}$ for the set of vertices of $G_1$ which have $k$ neighbours in $G_1$ and $V_{2,k}$ for the set of vertices of $G_2$ which have $k$ neighbours in $G_2$.
@@
 |c(k;G_n)-c(k;\GPo)| &= \left|\sum_{v \in V_{1,k}}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in V_{2,k}}\frac{c_{G_2}(v)}{N_{2,k}}\right| \\
-&=\left|\sum_{v \in W_1}\frac{c_{G_1}(v)}{N_{1,k}}+\sum_{v \in W_2}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in W_1}\frac{c_{G_2}(v)}{N_{2,k}}-\sum_{v \in W_3}\frac{c_{G_2}(v)}{N_{2,k}}\right|
+&=\left|\sum_{v \in W_1}\frac{c_{G_1}(v)}{N_{1,k}}+\sum_{v \in W_2}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in W_1}\frac{c_{G_2}(v)}{N_{2,k}}-\sum_{v \in W_3}\frac{c_{G_2}(v)}{N_{2,k}}\right|.
 \end{align*}
@@
 \begin{align*}
-|c(k;G_n)-c(k;\GPo)| &= \left|\sum_{v \in W_1}c_{G_1}(v)\frac{N_{2,k}-N_{1,k}}{N_{1,k}N_{2,k}}+\sum_{v \in W_2}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in W_3}\frac{c_{G_2}(v)}{N_{2,k}}\right|
+|c(k;G_n)-c(k;\GPo)| &= \left|\sum_{v \in W_1}c_{G_1}(v)\frac{N_{2,k}-N_{1,k}}{N_{1,k}N_{2,k}}+\sum_{v \in W_2}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in W_3}\frac{c_{G_2}(v)}{N_{2,k}}\right|.
 \end{align*}
@@
 \begin{align*}
-|c(k;G_n)-c(k;\GPo)| &\leq \frac{|W_1| |N_{2,k}-N_{1,k}|}{N_{1,k}N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}}
+|c(k;G_n)-c(k;\GPo)| &\leq \frac{|W_1| |N_{2,k}-N_{1,k}|}{N_{1,k}N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}}.
 \end{align*}
@@
 \begin{align*}
-|c(k;G_n)-c(k;\GPo)| &\leq \frac{|N_{2,k}-N_{1,k}|}{N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}}
+|c(k;G_n)-c(k;\GPo)| &\leq \frac{|N_{2,k}-N_{1,k}|}{N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}}.
 \end{align*}
@@
 \begin{align*}
-|c(k;G_n)-c(k;\GPo)| &\leq \frac{|N_{2,k}-N_{1,k}|}{N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}} \xrightarrow[n\rightarrow\infty]{\Pee} 0
+|c(k;G_n)-c(k;\GPo)| &\leq \frac{|N_{2,k}-N_{1,k}|}{N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}} \xrightarrow[n\rightarrow\infty]{\Pee} 0.
 \end{align*}
@@
 \begin{lemma}\label{lem:n1}
-Let $N_1(H)$ denote the number of vertices with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model $\GPo$. If $H \rightarrow \infty$, then $\E N_1(H) = o(n)$.
+Let $N_1(H)$ denote the number of vertices with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model $\GPo$. Then $\E N_1(H) = o(n)$.%If $H \rightarrow \infty$, 
 %For all $\epsilon >0$, there is $H_\epsilon$ such that for all $H\geq H_\epsilon$, it holds that $\E N_1(H) \leq \epsilon n$.
@@
 \begin{proof}
-By the Campbell-Mecke formula applied to the vertex set of $\GPo$, by the asymptotic behaviour of $\cosh$ and using that all $R, R-H, H \rightarrow \infty$,
+By the Poisson distribution of the number of points inside the disk with radius $R-H$, by the asymptotic behaviour of $\cosh$ and using that all $R, R-H, H \rightarrow \infty$,
 \begin{align*}
@@
 
-If $H \rightarrow \infty$, then also $H_0 = \log H \rightarrow \infty$.
+Since $H \rightarrow \infty$ we also have that $H_0 = \log H \rightarrow \infty$.
 Hence by Lemma~\ref{lem:n1}, the expected number of vertices with radial coordinate at most $R-H_0$ (in particular those vertices among them with at least one neighbour with radial coordinate at most $R-H$), $\E N_1(H_0) = o(n)$ is sublinear.
@@
 &+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(v)\right| \\
-&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_{n, H}(v)-c(k;\GPoH)\right| 
+&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_{n, H}(v)-c(k;\GPoH)\right|. 
 \end{align*}
@@
 \begin{align*}
-\left|c(k;\GPo)-\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v)\right| = \left| \frac{1}{N_n(k)}\sum_{v \in V_n \backslash V_{n,H}(k)} c_n(v) \right| \leq \frac{X_1}{N_n(k)}
+\left|c(k;\GPo)-\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v)\right| = \left| \frac{1}{N_n(k)}\sum_{v \in V_n \backslash V_{n,H}(k)} c_n(v) \right| \leq \frac{X_1}{N_n(k)}.
 \end{align*}
@@
 \begin{align*}
-\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(v)\right| \leq \frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} \left|c_n(v)-c_{n,H}(v)\right| =\frac{X_2}{N_n(k)}
+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(v)\right| \leq \frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} \left|c_n(v)-c_{n,H}(v)\right| =\frac{X_2}{N_n(k)}.
 \end{align*}
@@
 \left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_{n, H}(v)-c(k;\GPoH)\right| &= \left|\sum_{v\in V_{n,H}(k)} c_{n,H} \left(\frac{1}{N_n(k)}-\frac{1}{N_{n,H}(k)}\right)\right| \\
-&= \frac{|N_{n,H}(k)-N_n(k)|}{N_n(k)N_{n,H}(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(k)
+&= \frac{|N_{n,H}(k)-N_n(k)|}{N_n(k)N_{n,H}(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(k).
 \end{align*}
@@
 \begin{align*}
-|c(k;\GPo)-c(k;\GPoH)| \leq \frac{X_1}{N_n(k)}+\frac{X_2}{N_n(k)}+\frac{X_3}{N_n(k)}\frac{\sum_{v \in V_{n,H}(k)}c_{n,\leq H}(k)}{N_{n,H}(k)} \leq \frac{X_1+X_2+X_3}{N_n(k)}
+|c(k;\GPo)-c(k;\GPoH)| \leq \frac{X_1}{N_n(k)}+\frac{X_2}{N_n(k)}+\frac{X_3}{N_n(k)}\frac{\sum_{v \in V_{n,H}(k)}c_{n,\leq H}(k)}{N_{n,H}(k)} \leq \frac{X_1+X_2+X_3}{N_n(k)}.
 \end{align*}
@@
 \begin{align*}
-|c(k;\GPo)-c(k;\GPoH)| \leq \frac{X_1+X_2+X_3}{a_1(k)n} 
+|c(k;\GPo)-c(k;\GPoH)| \leq \frac{X_1+X_2+X_3}{a_1(k)n}.
 \end{align*}
@@
 As all vertices involved have height $\leq H$ resp.
-radial coordinate $\geq R-H$ and as $H\leq \frac{R}{4}$, all vertices involved (in the disk)  will have radial coordinate $\geq \frac{3}{4}R$, such that by Lemma~30(ii) from the paper on the largest component of KPKVB, see Lemma~\ref{lem:coupling_edges}, edges exist between such vertices in the disk if and only if they exist in the box.
+radial coordinate $\geq R-H$ and as $H\leq \frac{R}{4}$, all vertices involved (in the disk)  will have radial coordinate $\geq \frac{3}{4}R$, therefore by Lemma~\ref{lem:coupling_edges}, edges exist between such vertices in the disk if and only if they exist in the box.
 So the two graphs are isomorphic and hence the clustering functions agree.
@@
 \begin{align*}
-\E X = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) \mu(dv) = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy
+\E X = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) \mu(dv) = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy.
 \end{align*}
-Then, we condition on that the additional vertex $(0,y) \in \Rcal_H$ has degree $k$,
+Then, we condition on the additional vertex $(0,y) \in \Rcal_H$ having degree $k$,
 \begin{align*}
-\E X = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy
+\E X = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy.
 \end{align*}
@@
 \begin{align*}
-\E X \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy
+\E X \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
 \end{align*}
@@
 \begin{align*}
-\E Y_1 = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)]\mu(dv_1)\mu(dv_2)
+\E Y_1 = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)]\mu(dv_1)\mu(dv_2).
 \end{align*}
-If $v_1=(x_1,y_1)$ and $v_2=(x_2,y_2)$ have horizontal distance $>2e^H$, their neighbourhood balls are disjoint w.r.t.
+If $v_1=(x_1,y_1)$ and $v_2=(x_2,y_2)$ have horizontal distance $|x_1-x_2|>2e^H$, their neighbourhood balls are disjoint w.r.t.
 the connection rule of the truncated box model $\GboxH$.
-To see this, assume that $v_3=(x_3,y_3)$ is adjacent to both $v_1$ and $v_2$, then $|x_1-x_3|\leq e^{\frac{1}{2}(y_1+y_3)}$ and $|x_2-x_3|\leq e^{\frac{1}{2}(y_2+y_3)}$.
+To see this, assume that $v_3=(x_3,y_3)$ is adjacent to both $v_1$ and $v_2$.
+Then $|x_1-x_3|\leq e^{\frac{1}{2}(y_1+y_3)}$ and $|x_2-x_3|\leq e^{\frac{1}{2}(y_2+y_3)}$.
 As $y_1, y_2, y_3 \leq H$, it follows that $|x_1-x_3| \leq e^H$ and $|x_2-x_3|\leq e^H$, which implies that $|x_1-x_2| \leq |x_1-x_3|+|x_2-x_3|\leq 2e^H$, contradiction.
@@
 &= (1+o(1))\int_{} \int_{\Rcal_H\times \Rcal_H} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
-&= (1+o(1)) (n\E X)^2%+o((n\E X)^2)+o(n)
+&= (1+o(1)) (n\E X)^2.
 \end{align*}
-It follows that $\E X^2 = (1+o(1))(\E X)^2$, which implies $Var(X) \rightarrow 0$. We conclude
+It follows that $\E X^2 = (1+o(1))(\E X)^2$, which implies $Var(X) \rightarrow 0$ using that $\E X$ tends to a constant (see above). We conclude
 $$X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.$$
@@
 \begin{align*}
-\E Z =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy
+\E Z =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy.
 \end{align*}
@@
 \begin{align*}
-\E Z \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy
+\E Z \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
 \end{align*}
@@
 \begin{align*}
-\E Z \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy
+\E Z \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
 \end{align*}
@@
 As the $p_k$ form the probability mass function of an $\N_0$-valued random variable, we have that $\sum_{k=0}^\infty p_k = 1$, which implies that there is $K_\delta >0$ such that $1-\delta < \sum_{k=0}^{K_\delta} p_k \leq 1$.
-From Equations~\ref{eq:def_pk}, \ref{eq:gammakint} and \ref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$. 
+From Equations~\eqref{eq:def_pk}, \eqref{eq:gammakint} and \eqref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$. 
 From this, it follows that $(1-\delta)\gamma < \sum_{k=2}^{K_\delta} \gamma(k) p_k \leq 1$ and hence that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$.
@@
 |c(G_n)-\gamma| &\leq \left|c(G_n)-\sum_{k=2}^{K_\delta}c(k;G_n)p(k;G_n)\right|+\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
- &\leq \delta +\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta 
+ &\leq \delta +\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta. 
 \end{align*}
-Therefore, $\Pee(|c(G_n)-\gamma|\geq \epsilon) \leq \Pee(\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta) \rightarrow 0$ because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$.
+Therefore, $\Pee(|c(G_n)-\gamma|\geq \epsilon) \leq \Prob{\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta} \rightarrow 0$ because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$.
 %p_k =  = \Theta(k^{-(2\alpha +1)})

### 2019-05-01 concentration_argument.tex
processed most of Nikolaos comments on sections 5-7

@@
 
-Here we show that if we integrate with respect to a function $\hat{\rho}_n(y,k_n) = \Prob{\Po(\mu_n(y)) = k_n}$ then we may restrict integration with respect to the \emph{height} $y$ to an interval on which $\mu_n(y) = \bigT{k_n}$.
+Here we show that if we integrate with respect to the function $\hat{\rho}_n(y,k_n) = \Prob{\Po(\mu_n(y)) = k_n}$ then we may restrict integration with respect to the \emph{height} $y$ to an interval on which $\mu_n(y) = \bigT{k_n}$.
 We will refer to such a result as a \emph{concentration of heights} result.
@@
 as $n \to \infty$.
-\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$. Then,
+\item If in addition $C > \sqrt{4\alpha + 1}$ and $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$. Then, 
 \begin{equation}\label{eq:concentration_h_rho}
@@
 	\int_{\R_+ \setminus (a_n^-, a_n^+)} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
-	= \bigO{1} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right) 
+	= \bigO{1} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right).
 \end{equation}
 
-We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^+,k_n)$.  Using Stirling's approximation $k! \sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
+We shall now bound the terms $\rho(a_n^\pm,k_n)$.
+We explicitly show the bound for $\rho(a_n^+,k_n)$, the computation for $\rho(a_n^-,k_n)$ is similar.
+Using Stirling's approximation $k!
+\sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
 \begin{align*}
@@
 \]
-so that $c_n \sim k_n$. Therefore, by assumption on $h$ 
+so that $c_n \sim 2\log(k_n/\xi)$. Therefore, by assumption on $h$ 
 \[
@@
 \begin{equation}\label{eq:concentration_h_sim_rho}
-	\int_0^\infty g(y) \rho(y,k_n) \alpha e^{-\alpha y^\prime} \dd y^\prime \sim  
+	\int_0^\infty g(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
 		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
@@
 
-%For any positive sequence $a_n \to \infty$ and $C > 0$ we define
-%\begin{equation}\label{eq:def_K_C_set}
-%	\Kcal_C(a_n) = \left\{y \in \R_+ : \frac{a_n - C \sqrt{a_n \log(a_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
-%	\le \frac{a_n + C \sqrt{a_n \log(a_n)}}{\xi} \right\}.
-%\end{equation}
+For any $C > 0$ we define
+\begin{equation}\label{eq:def_K_C_set}
+	\Kcal_C(k_n) = \left\{y \in \R_+ : \frac{k_n - C \sqrt{a_n \log(k_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
+	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\}.
+\end{equation}
 %In addition we define
 %\begin{equation}\label{eq:def_K_C_n_set}
-%	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R_n] \cap \Kcal_{C}(a_n)),
+%	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R] \cap \Kcal_{C}(a_n)),
 %\end{equation}
-%where $I_n := \frac{\pi}{2}e^{R_n/2}$. Recall that $\Rcal = (-I_n, I_n] \times [0,R]$. 
-The following corollary allows us to bound integrals of function by considering there maximum of $\Kcal_{C}(k_n)$.
+%where $I_n := \frac{\pi}{2}e^{R/2}$. Recall that $\Rcal = (-I_n, I_n] \times [0,R]$. 
+The following corollary allows us to bound integrals of functions $h_n(y)$ by considering their maximum of $\Kcal_{C}(k_n)$.
 
@@
 We will refer collectively to any of these arguments as a \emph{concentration of heights argument}.
-For example, suppose we know that $h_n(y) = \Omega(1)$ and $h_n(y) = \bigO{k_n^4} e^{\alpha/2 y}$, while $h_n(y) = (1 + \smallO{1}) k_n^2 e^{\alpha/2 y}$, uniformly on $\Kcal_{C}(k_n)$.
-Then by a concentration of heights argument (in this case Corollary~\ref{cor:concentration_heights_asymptotics_n})
+For example, suppose we know that $h_n(y) = \Omega(1)$ and we can obtain some general crude bound $h_n(y) = \bigO{k_n^s} e^{\alpha/2 y}$ for some $s > 0$ for $y \in \R_+$.
+Then, if we can obtain a more precise bound $h_n(y) = (1 + \smallO{1}) k_n^2 e^{\alpha/2 y}$ uniformly on $\Kcal_{C}(k_n)$, by a concentration of heights argument (in this case Corollary~\ref{cor:concentration_heights_asymptotics_n})
 \begin{align*}
@@
 \begin{enumerate}[\upshape i)]
-\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| = 0$,
+\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} |\phi_n(y)| = 0$,
 \item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
@@
 \begin{align*}
-	\int_{(1-\varepsilon^\prime)R_n}^{R_n} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
 	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\prime)R,k_n) e^{-(\alpha-\beta)(1-\varepsilon^\prime)R} \\
@@
 \[
-	\int_{(1-\varepsilon^\prime)R_n}^{R_n} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
 	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\varepsilon^\prime)} e^{-n^{2(1-\varepsilon^\prime)}}}
@@
 \begin{equation}\label{eq:concentration_argument_an_+}
-	\int_{a_n^+}^{(1-\varepsilon^\prime)R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}}.
+	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}}.
 \end{equation}
@@
 \[
-\sup_{0 < y \le (1-\varepsilon^\prime)R_n} |\phi_n(y)| < \delta, \quad
+\sup_{0 < y \le (1-\varepsilon^\prime)R} |\phi_n(y)| < \delta, \quad
 \lambda_n^+(1 - \delta) > k_n \quad \text{and} \quad
@@
 \]
-for all $a_n^+ \le y \le (1-\varepsilon^\prime)R_n$. By making the change of variables $z = \mu^{-1}(\mu(y)(1-\delta)) = y + 2 \log(1-\delta)$ we then get
+for all $a_n^+ \le y \le (1-\varepsilon^\prime)R$. By making the change of variables $z = \mu^{-1}(\mu(y)(1-\delta)) = y + 2 \log(1-\delta)$ we then get
 \begin{align*}
-	\int_{a_n^+}^{(1-\varepsilon^\prime)R_n} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
-	&\le \int_{a_n^+}^{(1-\varepsilon^\prime)R_n} \Prob{\Po(\mu(y)(1-\delta)) = k_n} 
+	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
+	&\le \int_{a_n^+}^{(1-\varepsilon^\prime)R} \Prob{\Po(\mu(y)(1-\delta)) = k_n} 
 		e^{(\beta-\alpha) y} \dd y\\
-	&= (1-\delta)^{\beta - \alpha} \int_{a_n^+ + 2\log(1-\delta)}^{(1-\varepsilon^\prime)R_n + 2\log(1-\delta)} 
+	&= (1-\delta)^{\beta - \alpha} \int_{a_n^+ + 2\log(1-\delta)}^{(1-\varepsilon^\prime)R + 2\log(1-\delta)} 
 		\Prob{\Po(\mu(z)) = k_n} e^{(\beta - \alpha)z} \dd z\\
@@
 \[
-	\phi_n(y) = \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)}e^{-(\alpha-\frac{1}{2})(R_n - y)}
+	\phi_n(y) = \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)}e^{-(\alpha-\frac{1}{2})(R - y)}
 	- \frac{(2\alpha - 1)\pi}{4\alpha}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} 
-	e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(\alpha - \frac{1}{2})R_n - \frac{y}{2}}\right).
+	e^{-(\alpha - \frac{1}{2})(R - y)} - e^{-(\alpha - \frac{1}{2})R - \frac{y}{2}}\right).
 \]
@@
 \[
-	\mu_{\alpha,\nu}(\BallPon{p}) = \mu_{\alpha,\nu}(\BallPo{p})\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
+	\mu(\BallPon{p}) = \mu(\BallPo{p})\left(1 - e^{-(\alpha - \frac{1}{2})R}\right).
 \]
@@
 \begin{proof}
-First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$.
-We then have that the boundaries of $\BallPon{p}$ are given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$, which intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
+First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R}{2}}, \frac{\pi}{2}e^{\frac{R}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$.
+We then have that the boundaries of $\BallPon{p}$ are given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$, which intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R}{2}}, \frac{\pi}{2}e^{\frac{R}{2}}]$ at height
 \[
-	h(y) = R_n + 2 \log\left(\frac{\pi}{2}\right) - y.
+	h(y) = R + 2 \log\left(\frac{\pi}{2}\right) - y.
 \]
-Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R_n$ of the box $\Rcal$ while in the other case the full region of the box above $h(y)$ is connected to $p$.
+Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R$ of the box $\Rcal$ while in the other case the full region of the box above $h(y)$ is connected to $p$.
 
 We will first consider the case where $y > 2 \log(\pi/2)$.
-Recall that $\mu_{\alpha,\nu}(\BallPo{p}) = \xi e^{\frac{y}{2}}$ where $\xi = \frac{4\alpha \nu}{(2\alpha - 1)\pi}$.
+Recall that $\mu(\BallPo{p}) = \xi e^{\frac{y}{2}}$ where $\xi = \frac{4\alpha \nu}{(2\alpha - 1)\pi}$.
 Then, after some simple algebra, we have that
 \begin{align*}
-	\mu_{\alpha,\nu}(\BallPon{p})
-	&= \int_0^{h(y)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+	\mu(\BallPon{p})
+	&= \int_0^{h(y)} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
 		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
-	&\hspace{10pt}+ \int_{h(y)}^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+	&\hspace{10pt}+ \int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
 		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
 	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{h(y)} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime
-		+ \alpha \nu e^{\frac{R_n}{2}} \int_{h(y)}^{R_n} e^{-\alpha y^\prime} \, dy^\prime \\
+		+ \alpha \nu e^{\frac{R}{2}} \int_{h(y)}^{R} e^{-\alpha y^\prime} \, dy^\prime \\
 	&= \xi e^{\frac{y}{2}}\left(1 - \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} 
-		e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)\\
-	&\hspace{10pt}+ \nu e^{\frac{R_n}{2}}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} e^{-\alpha(R_n - y)} 
-		- e^{-\alpha R_n}\right)\\
-	&= \mu_{\alpha,\nu}(\BallPo{p})\left(1 - \phi_n(y)\right).
+		e^{-(\alpha - \frac{1}{2})(R - y)}\right)\\
+	&\hspace{10pt}+ \nu e^{\frac{R}{2}}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} e^{-\alpha(R - y)} 
+		- e^{-\alpha R}\right)\\
+	&= \mu(\BallPo{p})\left(1 - \phi_n(y)\right).
 \end{align*}
@@
 \begin{align*}
-	\mu_{\alpha,\nu}(\BallPon{p})
-	&= \int_0^{R_n} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
+	\mu(\BallPon{p})
+	&= \int_0^{R} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
 		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
-	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R_n} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
-	&= \mu_{\alpha,\nu}(\BallPo{p})\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
+	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
+	&= \mu(\BallPo{p})\left(1 - e^{-(\alpha - \frac{1}{2})R}\right).
 \end{align*}
@@
 
-The following is now immediate.
+Let us now define
+\[
+	\rho_{\mathrm{box}}(y,k) = \Prob{\Po(\mu(\BallPon{y})) = k}.
+\]
+The following is then immediate.
+
+\PvdH{Check if we need to define this earlier.}
 
 \begin{corollary}\label{cor:concentration_of_heights_Gbox}
-The statement in Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n}
+The statements in Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n}
 and~\ref{cor:concentration_heights_asymptotics_n} hold when we replace $\rho(y,k_n)$ with $\rho_{\text{box}}(y,k_n)$.
@@
 Due to the hyperbolic distance formula, the computations are however more involved than for the finite box model.
-Recall that under the coupling between the hyperbolic random graph and the finite box model, for two points $p, p^\prime$ with $y + y^\prime < R_n$, $p^\prime \in \BallHyp{p}$ exactly when $|x-x^\prime|_{\pi e^{R_n/2}} \le \Phi(y,y^\prime)$.
+Recall that under the coupling between the hyperbolic random graph and the finite box model, for two points $p, p^\prime$ with $y + y^\prime < R$, $p^\prime \in \BallHyp{p}$ exactly when $|x-x^\prime|_{\pi e^{R/2}} \le \Phi(y,y^\prime)$.
 In this setting, the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that
 \[
-	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Phi(y, y^\prime) 
-		\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
+	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R} \leq \Phi(y, y^\prime) 
+		\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R},
 \]
@@
 This result enables us to determine the measure of a ball around a given point $p=(0,y)$.
-Recall that the hyperbolic ball $\BallHyp{p}$ is a subset of $\Rcal$ and not of the hyperbolic disc $\Dcal_{R_n}$, i.e.
-the balls $\BallHyp{p}$ "live" in the finite box and not the hyperbolic disc.
+Recall that the hyperbolic ball $\BallHyp{p}$ is a subset of $\Rcal$ and not of the hyperbolic disc $\Dcal_{R}$, i.e.
+the balls $\BallHyp{p}$ ``live" in the finite box and not on the hyperbolic disc.
 We start with the following preliminary result.
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} = 1.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} = 1.
 \]
@@
 	\frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} 
-	&\le \frac{2\nu \alpha}{\pi} \int_{0}^{(1-\delta)(R-y)} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R_n}\right)
+	&\le \frac{2\nu \alpha}{\pi} \int_{0}^{(1-\delta)(R-y)} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R}\right)
 		e^{-\alpha y^\prime} \dd y^\prime\\
-	&= \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(1-\delta)(R_n - y)}\right) \\
-	&\hspace{10pt}+ \frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
+	&= \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(1-\delta)(R - y)}\right) \\
+	&\hspace{10pt}+ \frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
 \end{align*}
@@
 \begin{align*}
-	&\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}
+	&\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}
 		\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime\\
 	&= \Mu{\BallPo{0,y}}\begin{cases}
-		\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)-(\frac{3}{2}-\alpha)\delta(R-y)} 
-			- e^{-(R_n - y)}\right)
+		\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R - y)-(\frac{3}{2}-\alpha)\delta(R-y)} 
+			- e^{-(R - y)}\right)
 		&\mbox{if } 1/2 < \alpha < 3/2,\\
-		\frac{(2\alpha -1)K}{2} (1-\delta)(R - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
-		\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y) 
+		\frac{(2\alpha -1)K}{2} (1-\delta)(R - y)e^{-(R - y)} &\mbox{if } \alpha = 3/2,\\
+		\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R - y)} - e^{-(\alpha - \frac{1}{2})(R - y) 
 			-(\alpha - \frac{3}{2})(R-y)}\right)
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1}
-	\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1}
+	\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}
 			\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime = 0.
 \]
-Since $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} e^{-(\alpha - \frac{1}{2})(1-\delta)(R_n - y)} = 0$, we conclude that
+Since $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} e^{-(\alpha - \frac{1}{2})(1-\delta)(R - y)} = 0$, we conclude that
 \[
-	\limsup_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime)
+	\limsup_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime)
 		\alpha e^{-\alpha y^\prime} = 1.
@@
 \[
-	\frac{2 \nu \alpha}{\pi} K e^{\frac{3 y}{2} - R_n}\int_0^{R_n-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime.
+	\frac{2 \nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}\int_0^{R-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime.
 \]
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}} = 1.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}} = 1.
 \]
-%Let $\eps \in (0, 1)$. Then for all $0 \le y \le (1 - \eps)R_n$
+%Let $\eps \in (0, 1)$. Then for all $0 \le y \le (1 - \eps)R$
 %\[
@@
 %\[
-%	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 1 - 4\pi}{4\pi} e^{-(\alpha - \frac{1}{2})(R_n - y)} 
-%		+ \left(\alpha - \frac{1}{2}\right)\pi e^{-(\alpha - \frac{1}{2})R_n - y/2},
+%	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 1 - 4\pi}{4\pi} e^{-(\alpha - \frac{1}{2})(R - y)} 
+%		+ \left(\alpha - \frac{1}{2}\right)\pi e^{-(\alpha - \frac{1}{2})R - y/2},
 %\]
@@
 %	+ \begin{cases}
-%			\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(R_n - y)}\right)
+%			\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R - y)} - e^{-(R - y)}\right)
 %			&\mbox{if } 1/2 < \alpha < 3/2,\\
-%			\frac{(2\alpha -1)K}{2} (R_n - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
-%			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
+%			\frac{(2\alpha -1)K}{2} (R - y)e^{-(R - y)} &\mbox{if } \alpha = 3/2,\\
+%			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R - y)} - e^{-(\alpha - \frac{1}{2})(R - y)}\right)
 %			&\mbox{if } \alpha > 3/2,
@@
 \begin{proof}
-We perform the computation of $\Mu{\BallHyp{0,y}}$ by splitting the integration with respect to the height $y^\prime$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$,
+We perform the computation of $\Mu{\BallHyp{0,y}}$ by splitting the integration with respect to the height $y^\prime$ into the cases $y^\prime > R - y$ and $y^\prime \le R - y$,
 \[
 	\Mu{\BallHyp{y}} 
-	= \Mu{\BallHyp{y} \cap \Rcal ([0,R_n - y))} + \Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}.
+	= \Mu{\BallHyp{y} \cap \Rcal ([0,R - y))} + \Mu{\BallHyp{y} \cap \Rcal ([R - y, R])}.
 \]
@@
 \[
-	\Mu{\BallHyp{(0,y)} \cap\Rcal[(0,R_n-y)]} = \frac{2\nu \alpha}{\pi} \int_0^{R-y} \Phi(y,y^\prime) e^{-\alpha y^\prime}
+	\Mu{\BallHyp{(0,y)} \cap\Rcal[(0,R-y)]} = \frac{2\nu \alpha}{\pi} \int_0^{R-y} \Phi(y,y^\prime) e^{-\alpha y^\prime}
 	\dd y^\prime.
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1}
-	\Mu{\BallHyp{(0,y)} \cap\Rcal[(0,R_n-y)]} = 1.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1}
+	\Mu{\BallHyp{(0,y)} \cap\Rcal[(0,R-y)]} = 1.
 \]
 
-For the second part we observer that $\BallHyp{(0,y)} \cap \Rcal ([R_n - y, R_n])= \Rcal([R_n-y,R_n])$. 
+For the second part we observer that $\BallHyp{(0,y)} \cap \Rcal ([R - y, R])= \Rcal([R-y,R])$. 
 Thus, 
 \begin{align*}
-	&\hspace{-30pt}\Mu{\BallHyp{(0,y)} \cap \Rcal ([R_n - y, R_n])} \\
-	&= \int_{R_n - y}^{R_n} \int_{I_n} f_{\alpha,\nu}(x^\prime, y^\prime) \dd x^\prime \dd y^\prime
-		= \nu \alpha e^{R_n/2}\left(e^{-\alpha(R_n - y)} - e^{-\alpha R_n}\right)\\
-	&= \Mu{\BallPo{0,y}} \frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
-		- e^{-(\alpha - \frac{1}{2})R_n - y/2}\right), \numberthis \label{eq:mu_hyperbolic_ball_part_1}
+	&\hspace{-30pt}\Mu{\BallHyp{(0,y)} \cap \Rcal ([R - y, R])} \\
+	&= \int_{R - y}^{R} \int_{I_n} f_{\alpha,\nu}(x^\prime, y^\prime) \dd x^\prime \dd y^\prime
+		= \nu \alpha e^{R/2}\left(e^{-\alpha(R - y)} - e^{-\alpha R}\right)\\
+	&= \Mu{\BallPo{0,y}} \frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R - y)}
+		- e^{-(\alpha - \frac{1}{2})R - y/2}\right), \numberthis \label{eq:mu_hyperbolic_ball_part_1}
 \end{align*}
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} 
-	\Mu{\BallHyp{(0,y)} \cap \Rcal ([R_n - y, R_n])} = 0,
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} 
+	\Mu{\BallHyp{(0,y)} \cap \Rcal ([R - y, R])} = 0,
 \]
@@
 \[
-	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R_n} \frac{1}{2} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}}
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \frac{1}{2} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}}
 	= \frac{1}{2}.
@@
 \[
-	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1}
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1}
 	\frac{\partial}{\partial y} \mu\left(\BallHyp{y}\right) 
@@
 	\Mu{\BallHyp{y}} 
-	= \Mu{\BallHyp{y} \cap \Rcal ([0,R_n - y))} + \Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])},
+	= \Mu{\BallHyp{y} \cap \Rcal ([0,R - y))} + \Mu{\BallHyp{y} \cap \Rcal ([R - y, R])},
 \]
@@
 \[
-	\Mu{\BallHyp{y} \cap \Rcal ([0,R_n - y))} = \frac{2\alpha \nu}{\pi}\int_0^{R - y} \Phi(y,y^\prime) 
+	\Mu{\BallHyp{y} \cap \Rcal ([0,R - y))} = \frac{2\alpha \nu}{\pi}\int_0^{R - y} \Phi(y,y^\prime) 
 		e^{-\alpha y^\prime} \dd y^\prime,
@@
 \[
-	\Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}
-	= \xi e^{y/2}\frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R_n - y)}
-	- e^{-(\alpha - \frac{1}{2})R_n - y/2}\right).
+	\Mu{\BallHyp{y} \cap \Rcal ([R - y, R])}
+	= \xi e^{y/2}\frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R - y)}
+	- e^{-(\alpha - \frac{1}{2})R - y/2}\right).
 \]
@@
 \begin{align*}
-	&\frac{\partial}{\partial y} \Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}\\
-	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}
+	&\frac{\partial}{\partial y} \Mu{\BallHyp{y} \cap \Rcal ([R - y, R])}\\
+	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal ([R - y, R])}
 		+ \xi e^{y/2}\frac{2\alpha - 1}{4\pi}\left(
-		\left(\alpha - \frac{1}{2}\right)e^{-(\alpha - \frac{1}{2})(R_n - y)} 
-		+ \frac{1}{2}e^{-(\alpha - \frac{1}{2})R_n - y/2}\right)\\
-	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])}\left(1 +
-		\frac{(2\alpha - 1)e^{-(\alpha - \frac{1}{2})(R_n - y)} + e^{-(\alpha - \frac{1}{2})R_n - y/2}}
-		{e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(\alpha - \frac{1}{2})R_n - y/2}}\right).
+		\left(\alpha - \frac{1}{2}\right)e^{-(\alpha - \frac{1}{2})(R - y)} 
+		+ \frac{1}{2}e^{-(\alpha - \frac{1}{2})R - y/2}\right)\\
+	&= \frac{1}{2}\Mu{\BallHyp{y} \cap \Rcal ([R - y, R])}\left(1 +
+		\frac{(2\alpha - 1)e^{-(\alpha - \frac{1}{2})(R - y)} + e^{-(\alpha - \frac{1}{2})R - y/2}}
+		{e^{-(\alpha - \frac{1}{2})(R - y)} - e^{-(\alpha - \frac{1}{2})R - y/2}}\right).
 \end{align*}
-Since, $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \Mu{\BallHyp{y} \cap \Rcal ([R_n - y, R_n])} = 0$, we are left to show that
+Since, $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \Mu{\BallHyp{y} \cap \Rcal ([R - y, R])} = 0$, we are left to show that
 \begin{equation}\label{eq:derivative_mu_hyp_ball_main}
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \frac{2\alpha \nu}{\pi} \frac{\partial}{\partial y} \int_0^{R - y} \Phi(r,r^\prime) e^{-\alpha y^\prime} \dd y^\prime
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \frac{2\alpha \nu}{\pi} \frac{\partial}{\partial y} \int_0^{R - y} \Phi(r,r^\prime) e^{-\alpha y^\prime} \dd y^\prime
 	= \frac{1}{2}.
@@
 \[
-	\Xi_n(y,y^\prime) = 1 - \frac{\cosh(R- y)\cosh(R-y^\prime) - \cosh(R)}{\sinh(R - y) \sinh(R - y^\prime)},
+	\Xi(y,y^\prime) = 1 - \frac{\cosh(R- y)\cosh(R-y^\prime) - \cosh(R)}{\sinh(R - y) \sinh(R - y^\prime)},
 \]
@@
 \[
-	\Phi(R -y, R - y^\prime) = \frac{1}{2}e^{R/2} \arccos\left(1 - \Xi_n(y,y^\prime)\right).
+	\Phi(R -y, R - y^\prime) = \frac{1}{2}e^{R/2} \arccos\left(1 - \Xi(y,y^\prime)\right).
 \]
@@
 \begin{equation}\label{eq:derivative_hyp_ball_Xi_bounds}
-	2 e^{-(R - y - y^\prime)}h_1(y) h_2(y) \le \Xi_n(y,y^\prime) \le 2 e^{-(R - y - y^\prime)}.
+	2 e^{-(R - y - y^\prime)}h_1(y) h_2(y) \le \Xi(y,y^\prime) \le 2 e^{-(R - y - y^\prime)}.
 \end{equation}
@@
 
-Next, taking the derivative of $\Xi_n(y,y^\prime)$ yields,
+Next, taking the derivative of $\Xi(y,y^\prime)$ yields,
 \begin{align*}
@@
 		\alpha e^{-\alpha y^\prime} \dd y^\prime\\
-	&= -\frac{\pi}{2}e^{-(\alpha-\frac{1}{2})R_n + \alpha y} + \int_0^{R- y} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+	&= -\frac{\pi}{2}e^{-(\alpha-\frac{1}{2})R + \alpha y} + \int_0^{R- y} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
 		\left(1 + \varphi_n(y,y^\prime)\right) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
-	&= -\frac{\pi}{2}e^{-(\alpha-\frac{1}{2})R_n + \alpha y}  + \int_0^{(1-\delta)(R- y)} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}
+	&= -\frac{\pi}{2}e^{-(\alpha-\frac{1}{2})R + \alpha y}  + \int_0^{(1-\delta)(R- y)} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}
 		{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
@@
 \begin{equation}\label{eq:derivative_hyp_ball_error_1}
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} I_t(y) = 0, \quad \text{for } t = 1,3
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} I_t(y) = 0, \quad \text{for } t = 1,3
 \end{equation}
@@
 \begin{equation}\label{eq:derivative_hyp_ball_main_part}
-	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} I_2(y) = \frac{1}{2}.
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} I_2(y) = \frac{1}{2}.
 \end{equation}
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} I_1(y) 
-	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \frac{\pi}{2\xi} e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} I_1(y) 
+	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \frac{\pi}{2\xi} e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
 \]
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} I_3(y) 
-	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \alpha \left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right) e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} I_3(y) 
+	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \alpha \left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right) e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
 \]
@@
 \begin{align*}
-	\varphi^-_n &:= \sup_{0 < y \le (1-\varepsilon)R_n} \, \inf_{0 \le y^\prime \le (1 - \delta)(R-y)} 
+	\varphi^-_n &:= \sup_{0 < y \le (1-\varepsilon)R} \, \inf_{0 \le y^\prime \le (1 - \delta)(R-y)} 
 		\varphi_n(y,y^\prime)\\
-	\varphi^+_n &:= \sup_{0 < y \le (1-\varepsilon)R_n} \, \sup_{0 \le y^\prime \le (1 - \delta)(R-y)} \varphi_n(y,y^\prime)
+	\varphi^+_n &:= \sup_{0 < y \le (1-\varepsilon)R} \, \sup_{0 \le y^\prime \le (1 - \delta)(R-y)} \varphi_n(y,y^\prime)
 \end{align*}
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R_n} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} 
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} 
 	\int_{0}^{(1-\delta)(R-y)} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime

### 2019-05-01 proofs_infinite_k.tex
processed most of Nikolaos comments on sections 5-7

@@
 
-In this section we explain the challenges with each step and give a detailed overview of the structure for the proof of Theorem~\ref{thm:mainktoinfty} using intermediate results for each of the steps.
+In this section we explain the challenges associated with each step and give a detailed overview of the structure for the proof of Theorem~\ref{thm:mainktoinfty} using intermediate results for each of the steps.
 To this end we define the scaling function
@@
 
-In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a(k)^-, a(k)^+]$, with
+In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a^-(k), a^+(k)]$, with
 \[
-	a(k)^\pm = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
+	a^\pm(k) = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
 \]
@@
 Since $\mu(y) = \mu(\BallPo{y}) = \xi e^{y/2}$, this implies that integration with respect to $\rho(y,k)$ is concentrated around $y \approx 2\log(k/\xi)$.
-In the remainder of this paper we will often encounter integrands involving the function $\Prob{\Po(\mu_n(y)) = k}$, for some $\mu_n(y)$ which is asymptoticly equivalent to $\mu(y)$.
-In these case we also want to be able to restrict our integration around those heights $y$ for which $y \approx 2\log(k_n/\xi)$.
+In the remainder of this paper we will often encounter integrands involving the function $\Prob{\Po(\mu_n(y)) = k_n} := \hat{\rho}_n(y,k_n)$, for some $\mu_n(y)$ which is asymptoticly equivalent to $\mu(y)$.
+In these cases we also want to be able to restrict our integration around those heights $y$ for which $y \approx 2\log(k_n/\xi)$.
 Such results are established in Section~\ref{sec:concentration_argument}.
@@
 The following lemma justifies working with this modified version.
-The proof uses a concentration result for $\N_{n}(k_n)$ and full details can be found in Section~\ref{ssec:coupling_H_HP}.
+The proof uses a concentration result for $N_{n}(k_n)$ and full details can be found in Section~\ref{ssec:coupling_H_HP}.
 
@@
 
-Assuming this concentration result, we are left to compute the limit of $\Exp{c^\ast(k_n; \Gbox)}$ as $n \to \infty$ and show that it is equivalent to $\gamma(k_n)$.
+Assuming this concentration result, we are left to compute expectation $\Exp{c^\ast(k_n; \Gbox)}$ and show that it is asymptotically equivalent to $\gamma(k_n)$ as $n \to \infty$.
 To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of $c^\ast(k;\Gbox)$ and $\gamma(k_n)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.

### 2019-05-01 transition.tex
processed most of Nikoloas comments for sections 1-3
processed most of Nikolaos comments on sections 5-7

@@
 
-Recall that $\Gbox$ is obtained by restricting the Poisson Point Process $\PPP$ to the box $\Rcal = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ and connecting two points $p_1, p_2 \in \Rcal$ if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$.
+Recall that $\Gbox$ is obtained by restricting the Poisson point process $\PPP$ to the box $\Rcal = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ and connecting two points $p_1, p_2 \in \Rcal$ if and only if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$.
 We also recall that by definition of the norm $|.|_{\pi e^{R_n/2}}$ the left and right boundaries of $\Rcal$ are identified.
 See Section~\ref{ssec:finite_model} for more details.
-Due to this identification of the boundaries some triples of nodes that form triangles in the finite box model do not form a triangle in the infinite model.
+Due to this identification of the boundaries some triples of nodes that form a triangle in the finite box model do not form a triangle in the infinite model.
 Therefore, to establish the required result we need to compute the asymptotic difference between triangle counts in both models.
@@
 \[
-	T_{\text{box}}(p) = \sum^{\ne}_{p_1, p_2 \in \Pcal_n \setminus p} T_{\text{box}}(p,p_1,p_2)
-\]
-where the sum is over all distinct pairs in $\Pcal_n \setminus p$ and
+	T_{\text{box}}(p) = \sum^{\ne}_{p_1, p_2 \in \Pcal \setminus \{p\}} T_{\text{box}}(p,p_1,p_2)
+\]
+where the sum is over all distinct pairs in $\Pcal \setminus p$ and
 \[
@@
 \[
-	T_\infty(y) = \sum_{p_1, p_2 \in \Pcal \setminus \{0,y\}}^{\ne} T_\infty(y,p_1,p_2),
+	T_\infty(y) = \sum_{p_1, p_2 \in \Pcal \setminus (0,y)}^{\ne} T_\infty(y,p_1,p_2),
 \]
@@
 \]
+Here we slightly abuse notation and write $\BallPo{y}$ for $\BallPo{(0,y)}$. We will adopt this notational convention throughout the remainder of this section, to keep notation concise.
+
 We will first relate $\gamma(k_n)$ and $\Exp{c^\ast(k_n; \Gbox)}$ using $T_\infty(y)$ and $T_{\text{box}}(y)$. Recall the definition of $\Kcal_{C}(k_n)$
@@
 where the last line follows from a concentration of heights argument, for which we used that $\CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n} \le 1$.
-To analyze the conditional expectation we observe that, similar to the analysis of $\gamma(k_n)$, conditioned on their being $k_n$ points in $\BallPon{y}$, each points $u_i = (x_i,y_i)$ is independently distributed according to the probability density $\Mu{\BallPon{y}}^{-1} \ind{u_i \in \BallPon{y}} f(x_i,y_i)$.
+To analyze the conditional expectation we observe that, similar to the analysis of $\gamma(k_n)$, conditioned on there being $k_n$ points in $\BallPon{y}$, each point $u_i = (x_i,y_i)$ is independently distributed according to the probability density $\Mu{\BallPon{y}}^{-1} \ind{u_i \in \BallPon{y}} f(x_i,y_i)$.
 Therefore,
@@
 However, it could happen that there are points in the intersection $\BallPon{p} \cap \BallPon{p^\prime}$ that are not in $\BallPo{p} \cap \BallPo{p^\prime}$.
-Let us denote this region by $\mathcal{T}(p \Delta p^\prime)$, see Figure~\ref{fig:comparing_triangles_diff_intersections} for an example of this region.
-Then, any $p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ creates a triangle with $p$ and $p^\prime$ in $\Gbox$ that is not present in $\Ginf$.
-Finally, any point $p_2 \in \BallPo{p} \cap \BallPo{p6\prime}$ with height $y_2 > R$ creates a triangle with $p, p^\prime$ in $\Ginf$ but not in $\Gbox$.
+Let us denote this region by $\mathcal{T}(p,p^\prime)$, see Figure~\ref{fig:comparing_triangles_diff_intersections} for an example of this region.
+Then, any $p_2 \in \mathcal{T}(p,p^\prime)$ creates a triangle with $p$ and $p^\prime$ in $\Gbox$ that is not present in $\Ginf$.
+Finally, any point $p_2 \in \BallPo{p} \cap \BallPo{p^\prime}$ with height $y_2 > R$ creates a triangle with $p, p^\prime$ in $\Ginf$ but not in $\Gbox$.
 
@@
 \[
-	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus p_0}^{\ne} 
+	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus \{p_0\}}^{\ne} 
 		\widetilde{T}_{\text{box}}(p_0,p_1,p_2).
@@
 	T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)
-	= \sum_{p_1, p_2 \in \Pcal }^{\ne} \ind{p_1 \in \BallPon{p_0}} 
+	= \sum_{p_1, p_2 \in \Pcal \setminus \{p_0\}}^{\ne} \ind{p_1 \in \BallPon{p_0}} 
 			\ind{p_2 \in \mathcal{T}(p_0, p_1)}.
@@
 %Observe that the difference between $\widetilde{T}_{\text{box}}(p_0)$ and $T_{\text{box}}(p_0)$ is in the last indicator in $\widetilde{T}_{\text{box}}(p_0,p_1,p_2)$.
-counts those points $p_2$ in the box $\Rcal$ that are in the neighborhood $\BallPo{p_1}$ of $p_1$ in the infinite model.
+counts those points $p_2$ in the box $\Rcal$ that are in the neighbourhood $\BallPo{p_1}$ of $p_1$ in the infinite model.
 Thus, $\widetilde{T}_{\text{box}}(p_0)$ only count those triangles $(p_0,p_1,p_2)$ that also exist in $\Ginf$.
 
-The next result, which is crucial for the proof of Proposition~\ref{prop:convergence_average_clustering_P_n}, computes the expected measure of $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ with respect to $p^\prime$.
+The next result, which is crucial for the proof of Proposition~\ref{prop:convergence_average_clustering_P_n}, computes the expected measure of $\mathcal{T}(p,p^\prime)$ with respect to $p^\prime$.
 
@@
 %\[
-%	\int_{\Rcal} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)\right) f(x_1,y_1) 
+%	\int_{\Rcal} \mu\left(\mathcal{T}(p,p^\prime)(p_0,p_1)\right) f(x_1,y_1) 
 %	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
@@
 \begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]
-Let us write $\Rcal^\prime := \R \times \R_+ \setminus \Rcal$ and let $p_0 = (0,y)$ denote the typical point.
+Let us write $\Rcal^\prime := (\R \times \R_+) \setminus \Rcal$ and let $p_0 = (0,y)$ denote the typical point.
 Next we recall that it is enough to show~\eqref{eq:triangle_diff_main_term}, so that in particular we have that $y \in \Kcal_{C}(k_n)$.
@@
 }\PvdH{the first integral is taken care of by another Lemma so it does not matter I think.}
-The part is taken care of by Lemma~\ref{lem:clustering_error_T_term}. For the other integral we have
+The first part is taken care of by Lemma~\ref{lem:clustering_error_T_term}. For the other integral we have
 \begin{align*}
@@
 %\TM{ Typo : $f_{\mu, \nu}$? Also give more details how line 3 follows. }
-We thus we conclude, using Lemma~\ref{lem:clustering_error_T_term}, that,
+Thus we conclude, using Lemma~\ref{lem:clustering_error_T_term}, that,
 \begin{equation}\label{eq:triangle_count_diff_scaling}
@@
 \end{equation}
-Therefore, since $y = \bigO{\log(k_n)}$ on $\Kcal_C(k_n)$, 
-\begin{align*}
-	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} \rho(y,k_n) \left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| 
+Therefore, on $\Kcal_C(k_n)$, 
+\begin{align*}
+	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} \rho(y_0,k_n) \left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| 
 		e^{-\alpha y_0} \dd y_0\\
@@
 
-From the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} we obtain the following useful corollary, which will be used in Section~\ref{sec:concentration_c_P_n}.
+From the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} we obtain the following useful corollary, which will be used in Section~\ref{sec:concentration_c_P_n}. Recall that
+\[
+	\rho_{\mathrm{box}}(y,k_n) = \Prob{\Po(\mu(\BallPon{y})) = k_n},
+\]
+denote the degree distribution of a point $p_0 = (0,y)$ in $\Gbox$.
 
@@
 %\[
-%	\sum_{p_1,p_2 \in \Pcal_n}^{\ne} T_{\text{box}}(p_0,p_1,p_2) - \widetilde{T}_{\text{box}}(p_0,p_1,p_2)
-%	= \sum_{p_1,p_2 \in \Pcal_n}^{\ne} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}_{\Pcal \Delta \Pcal_n}(p_0,p_1)},
+%	\sum_{p_1,p_2 \in \Pcal}^{\ne} T_{\text{box}}(p_0,p_1,p_2) - \widetilde{T}_{\text{box}}(p_0,p_1,p_2)
+%	= \sum_{p_1,p_2 \in \Pcal}^{\ne} \ind{p_1 \in \BallPon{p_0}} \ind{p_2 \in \mathcal{T}(p,p^\prime)(p_0,p_1)},
 %\]
-%where the sums are over all distinct pairs $(p_1, p_2) \in \Pcal_n$.
-
-%\TM{ Note you cannot really force/assume $p_0 = (0,y)$ is in your PPP $\Pcal_n$.
-(The summation over $\Pcal_n \setminus (0,y)$ suggests this is what you do.) For taking the expectation of sort of thing, Palm theory / Mecke are used typically.
+%where the sums are over all distinct pairs $(p_1, p_2) \in \Pcal$.
+
+%\TM{ Note you cannot really force/assume $p_0 = (0,y)$ is in your PPP $\Pcal$.
+(The summation over $\Pcal \setminus (0,y)$ suggests this is what you do.) For taking the expectation of sort of thing, Palm theory / Mecke are used typically.
 At this point though you can again still just say we add $p_0$ to the PPP.
 }\PvdH{I changed the text at the beginning of this section to mention this.
-Since we now consider the point process $\Pcal_n \cup p_0$ the above summation is over $\Pcal_n$.}
+Since we now consider the point process $\Pcal \cup p_0$ the above summation is over $\Pcal$.}
 
@@
 
-We now come back to computing the expected number of triangles attached to node at height $y$ in $\Gbox$ that are not present in $\Ginf$.
+We now come back to computing the expected number of triangles attached to a node at height $y$ in $\Gbox$ that are not present in $\Ginf$.
 
@@
 
-Recall that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime)$ denotes the region of points which form triangles with $p$ and $p^\prime$ in $\Gbox$ but not in $\Ginf$.
-Figure \ref{fig:comparing_triangles_diff_intersections} shows an example of a configuration where $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime) \ne \emptyset$.
-We observe that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p^\prime) \ne \emptyset$ because the right boundary of the ball $\BallPon{p^\prime}$ exists the right boundary of the box $\Rcal$ and then, since we identified the boundaries, continues from the left so that $\BallPon{p^\prime}$ covers part of the ball $\BallPon{p}$ which would not be covered in the infinite limit model.
+Recall that $\mathcal{T}(p,p^\prime)$ denotes the region of points which form triangles with $p$ and $p^\prime$ in $\Gbox$ but not in $\Ginf$.
+Figure \ref{fig:comparing_triangles_diff_intersections} shows an example of a configuration where $\mathcal{T}(p,p^\prime) \ne \emptyset$.
+We observe that $\mathcal{T}(p,p^\prime) \ne \emptyset$ because the right boundary of the ball $\BallPon{p^\prime}$ exits the right boundary of the box $\Rcal$ and then, since we identified the boundaries, continues from the left so that $\BallPon{p^\prime}$ covers part of the ball $\BallPon{p}$ which would not be covered in the infinite limit model.
 
@@
 			&\mbox{if } x - e^{(y + R_n)/2} + \pi e^{R_n/2} \le z \le \frac{\pi}{2} e^{R_n/2}\\
-		0 &\mbox{else}
+		0 &\mbox{otherwise}
 	\end{cases}\\
@@
 			&\mbox{if } -\frac{\pi}{2} e^{R_n/2} \le z \le x + e^{(y + R_n)/2} - \pi e^{R_n/2}\\
-		0 &\mbox{else}
+		0 &\mbox{otherwise}
 	\end{cases}
@@
 
-The crucial observation is that $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$ as long as the point $(x^\ast(p^\prime), y^\ast(p^\prime))$ is above the left boundary of $p$.
+The crucial observation is that $\mathcal{T}(p,p^\prime) = \emptyset$ as long as the point $(x^\ast(p^\prime), y^\ast(p^\prime))$ is above the left boundary of $p$.
 This happens exactly when $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$.
@@
 which is displayed by the red curve in Figure \ref{fig:comparing_triangles_diff_analysis}.
-It holds that $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$ if and only if $y^\prime < b^\ast_p(x^\prime)$ and hence we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$ for all $p^\prime \in \Rcal$ for which $y^\prime \ge b^\ast_p(x^\prime)$.
+It holds that $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$ if and only if $y^\prime < b^\ast_p(x^\prime)$ and hence we have that $\mathcal{T}(p,p^\prime) = \emptyset$ for all $p^\prime \in \Rcal$ for which $y^\prime \ge b^\ast_p(x^\prime)$.
 We also note that when $y^\prime = b^\ast_p(x^\prime)$ the two points $(x^\ast(p^\prime), y^\ast(p^\prime))$ and $(\hat{x}(p,p^\prime),\hat{y}(p,p^\prime))$ coincide.
@@
 \end{tikzpicture}
-\caption{Example for a given $p$ of the boundary function $x^\prime \mapsto b^\ast_p(x^\prime)$, given by the red curve, which determines whether $\mathcal{T}_{\Pcal \Delta \Pcal_n} = \emptyset$.
+\caption{Example for a given $p$ of the boundary function $x^\prime \mapsto b^\ast_p(x^\prime)$, given by the red curve, which determines whether $\mathcal{T}(p,p^\prime) = \emptyset$.
 We see that when $y^\prime = b^\ast_p(x^\prime)$ then $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime)) = (x^\ast(p^\prime), y^\ast(\prime))$.}
@@
 \begin{equation}\label{eq:clustering_error_T_main}
-	\int_0^{R_n}\int_0^{I_n} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) f(x_1,y_1) 
+	\int_0^{R_n}\int_0^{I_n} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) f(x_1,y_1) 
 	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
@@
 The proof goes in two stages.
-First we compute $\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right)$ by splitting it over three disjoint regimes with respect to $p_1$, with $x_1 \ge 0$.
+First we compute $\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right)$ by splitting it over three disjoint regimes with respect to $p_1$, with $x_1 \ge 0$.
 Then we do the integration with respect to $p_1$.
 
-\subsubsection*{Computing $\bm{\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right)}$}
+\subsubsection*{Computing $\bm{\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right)}$}
 
@@
 \begin{align*}
-	A_n^{(1)} &= \left\{p_1 \in \Rcal \, : \, 0 \le y_1 \le y - 2\log(I_n/(I_n-x_1)) \right\},\\
-	A_n^{(2)} &= \left\{p_1 \in \Rcal \, : \, y - 2\log(I_n/(I_n-x_1)) < y_1 
+	A_n^{(1)} &= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, 0 \le y_1 \le y - 2\log(I_n/(I_n-x_1)) \right\},\\
+	A_n^{(2)} &= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, y - 2\log(I_n/(I_n-x_1)) < y_1 
 		\le y + 2 \log\left(1 + \frac{x_1}{I_n}\right)\right\},\\
-	A_n^{(3)} &= \left\{p_1 \in \Rcal \, : \, y + 2 \log\left(1 + \frac{x_1}{I_n}\right) < y_1 
+	A_n^{(3)} &= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, y + 2 \log\left(1 + \frac{x_1}{I_n}\right) < y_1 
 			\le y + 2 \log\left(\frac{I_n}{I_n-x_1}\right)\right\},
@@
 
-With these definitions we have that the union $B_n := \bigcup_{i = 1}^n B_n^{(i)}$ denotes the area under the red curve in Figure~\ref{fig:comparing_triangles_diff_analysis} and hence, for all $p_1 \in \Rcal\setminus B_n$ with $x_1 \ge 0$ we have that $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1) = \emptyset$.
+With these definitions we have that the union $B_n := \bigcup_{i = 1}^n B_n^{(i)}$ denotes the area under the red curve in Figure~\ref{fig:comparing_triangles_diff_analysis} and hence, for all $p_1 \in \Rcal\setminus B_n$ with $x_1 \ge 0$ we have that $\mathcal{T}(p,p^\prime)(p,p_1) = \emptyset$.
 So we only need to consider $p_1 \in B_n$.
@@
 \begin{equation}\label{eq:mu_triangle_diff}
-	\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = 
+	\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) = 
 	\begin{cases}
@@
 
-Depending on which regime $p_1$ belongs to, the set $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)$ has a different shape.
+Depending on which set $p_1$ belongs to, the set $\mathcal{T}(p,p^\prime)(p,p_1)$ has a different shape.
 We displayed these shapes in Figure~\ref{fig:shapes_triangle_mismatches} as a visual aid to follow the computations below.
@@
 %																								  %
-%	Shows the area T_{\Pcal \Delta \Pcal_n} when h_1(p^\prime) > h_2(p^\prime) > h(y)			  %
+%	Shows the area T_{\Pcal \Delta \Pcal} when h_1(p^\prime) > h_2(p^\prime) > h(y)			  %
 %																								  %
@@
 %																								  %
-%	Shows the area T_{\Pcal \Delta \Pcal_n} when h(y) > h_1(p^\prime)							  %
+%	Shows the area T_{\Pcal \Delta \Pcal} when h(y) > h_1(p^\prime)							  %
 %																								  %
@@
 \end{tikzpicture}
-\caption{The different shapes of $\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)$ depending on the regime to which $p_1$ belongs.
+\caption{The different shapes of $\mathcal{T}(p,p^\prime)(p,p_1)$ depending on the regime to which $p_1$ belongs.
 The top figure is for $p_1 \in B_n^{(1)}$, the middle for $p_1 \in B_n^{(2)}$ and the bottom one for $p_1 \in B_n^{(3)}$.}
@@
 	\mathcal{I}_n^{(1)}(p_1) &= \int_{h_2(p_1)}^{y^\ast(p_1)} \left(x_1 + e^{(y_1+y_2)/2} - I_n\right) e^{-\alpha y_2} 
-		\dd x_2 \dd y_2\\
+		\dd y_2\\
 	&\le e^{y_1/2} \int_{h_2(p_1)}^{y^\ast(p_1)} e^{-(\alpha-\frac{1}{2}) y_2} \dd y_2\\
@@
 \end{align*}
-where we used that $x^\prime \le e^{(y+y_1)/2} = \smallO{I_n}$ for all $y_1\le y$ and $y \in \Kcal_{C}(k_n)$ so that
+where we used that $x_1 \le e^{(y+y_1)/2} = \smallO{I_n}$ for all $y_1\le y$ and $y \in \Kcal_{C}(k_n)$ so that
 \[
@@
 	\mathcal{I}_n^{(2)}(p_1) &= \int_{y^\ast(p_1)}^{h_1(p_1)} \left(I_n + x_1 - e^{(y_1+y_2)}\right) e^{-\alpha y_2}
-		\dd x_2 \dd y_2\\
+		\dd y_2\\
 	&\le 2 I_n \int_{y^\ast(p_1)}^{h_1(p_1)} e^{-\alpha y_2} \dd x_2 \dd y_2\\
@@
 \[
-	\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}},
+	\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}},
 \]
@@
 \[
-	\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-(2\alpha-1)} e^{\alpha y}}.
-\]
-
-\paragraph{Regime III $\bm{p_1 \in B_n^{(3)}}$:}
+	\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) = \bigO{I_n^{-(2\alpha-1)} e^{\alpha y}}.
+\]
+
+\paragraph{Regime 3:}
 
@@
 \[
-	\mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
+	\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
 	= \bigO{I_n^{-(2\alpha - 1)} e^{\alpha y}}.
@@
 We now proceed with the second part of the computation leading to \eqref{eq:clustering_error_T_main}.
-Here we will integrate $\mu(\mathcal{T}_{\Pcal \Delta \Pcal_n})(p,p_1)$ over the region $B_n := B_n^{(1)} \cup B_n^{(2)} \cup B_n^{(3)}$, see Figure~\ref{fig:comparing_triangles_B_areas}.
+Here we will integrate $\mu(\mathcal{T}(p,p^\prime))(p,p_1)$ over the region $B_n := B_n^{(1)} \cup B_n^{(2)} \cup B_n^{(3)}$, see Figure~\ref{fig:comparing_triangles_B_areas}.
 Let us first identify the boundaries of these areas.
@@
 
-We continue is the same way to obtain for $B_n^{(3)}$
+We continue in the same way for $B_n^{(3)}$
 \[
@@
 
-We these characterizations of the areas we now integrate $\mu(\mathcal{T}_{\Pcal \Delta \Pcal_n})(p,p_1)$ over $B_n$, splitting the computations over the three different areas.
+We these characterizations of the areas we now integrate $\mu(\mathcal{T}(p,p^\prime))(p,p_1)$ over $B_n$, splitting the computations over the three different areas.
 
@@
 \begin{align*}
-	&\hspace{-30pt}\int_{B_n^{(1)}} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
+	&\hspace{-30pt}\int_{B_n^{(1)}} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) 
 		f(x_1,y_1)	\dd x_1 \dd y_1 \\
-	&\le  \int_0^y \int_0^{I_n(1-e^{(y_1-y)/2})} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
+	&\le  \int_0^y \int_0^{I_n(1-e^{(y_1-y)/2})} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) 
 		f(x_1,y_1) \dd x_1 \dd y_1\\
@@
 \begin{align*}
-	\int_{B_n^{(2)}} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
+	\int_{B_n^{(2)}} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) 
 		f(x_1,y_1)	\dd x_1 \dd y_1
@@
 
-For this area we show that 
+For this case we show that 
 \begin{equation}\label{eq:mu_triangle_diff_3}
@@
 \begin{align*}
-	\int_{B_n^{(3)}} \mu\left(\mathcal{T}_{\Pcal \Delta \Pcal_n}(p,p_1)\right) 
+	\int_{B_n^{(3)}} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) 
 		f(x_1,y_1)	\dd x_1 \dd y_1

### 2019-05-28 concentration.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

@@
 
-First we write
+Recall that $\Nbox(k_n)$ denotes the number of vertices in $\Gbox$ with degree $k_n$. We first write
 \[
@@
 \[
-	 T_{\text{box}}(k_n) = \sum_{p \in \Pcal} \ind{\Dbox(p) = k_n} \sum_{p_1, p_2 \in \Pcal \setminus p}^{\ne} 
+	 T_{\text{box}}(k_n) = \sum_{p \in \Pcal} \ind{\Dbox(p) = k_n} \sum_({p_1, p_2) \in \Pcal \setminus \{p\}}^{\ne} 
 	 \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPon{p_1}}
@@
 \]
-and recall the definition of $\Kcal_{C}(k_n)$
+as well as the definition of $\Kcal_{C}(k_n)$
 \[
@@
 \begin{equation}\label{eq:def_tilde_c_box}
-	\widetilde{c}_{\text{box}}(k_n) = \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
+	\widetilde{c}_{\text{box}}(k_n) = \frac{\widetilde{T}_{\text{box}}(k_n,C)}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}.
 \end{equation}
@@
 We first use this result to prove Proposition~\ref{prop:concentration_local_clustering_P_n}.
-The remainder of this section is devoted to prove Proposition~\ref{prop:concentration_tilde_T_P_n}.
+The remainder of this section is devoted to the proof of Proposition~\ref{prop:concentration_tilde_T_P_n}.
 The final proof can be found in Section~\ref{ssec:concentration_tilde_T}.
@@
 	\Exp{\left|c^\ast(k_n; \Gbox) - \widetilde{c}_{\text{box}}(k_n)\right|}
-	= \Exp{c^\ast(k_n; \Gbox)} - \widetilde{c}_{\text{box}}(k_n).
+	= \Exp{c^\ast(k_n; \Gbox)} - \Exp{\widetilde{c}_{\text{box}}(k_n)}.
 \]
@@
 \[
-	\Exp{\left|c^\ast(k_n; \Gbox) - \widetilde{c}_{\text{box}}(k_n)\right|} = \smallO{s(k_n)}.
+	\Exp{\left|c^\ast(k_n; \Gbox) - \widetilde{c}_{\mathrm{box}}(k_n)\right|} = \smallO{s(k_n)}.
 \]
@@
 To prove Proposition~\ref{prop:concentration_tilde_T_P_n} we need to understand the joint degree distribution in $\Gbox$.
-This subsequently requires us to compute the joint neighbourhoods in $\Gbox$ of two points $p, p^\prime \in \Rcal$.
-We perform the analysis in this section.
+This subsequently requires us to analyse the joint neighbourhoods in $\Gbox$ of two points $p, p^\prime \in \Rcal$.
 We start with a general result for near independent Poisson random variables.
@@
 	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
-	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n},
+	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n}.
 \end{align*}
@@
 To see how this lemma can be applied to analyze the joint degree distribution in $\Gbox$, fix two points $p,p^\prime \in \Rcal$ and denote by 
-\[
+\begin{equation}\label{eq:def_joint_degree_distribution}
 	\rho_{\text{box}}(p,p^\prime,k,k^\prime) 
 	:= \Prob{\Po\left(\Mu{\BallPon{p}}\right) = k, \Po\left(\Mu{\BallPon{p^\prime}}\right) = k^\prime}.
-\]
+\end{equation}
 the joint degree distribution. Then if we define,
@@
 Now, if $y,y^\prime \in \Kcal_{C}(k_n)$ the three Poisson random variables defined above satisfy the condition of Lemma~\ref{lem:near_independence_poisson} regarding the sum $\lambda_i(n) + \lambda_3(n)$.
-Therefore, if in addition $\Mu{\BallPon{p} \cup \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$, we have that
+Therefore, if in addition $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$, we have that
 \[
@@
 	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
-		\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. 
+		\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}, 
 \end{equation}
+where $|x|_n = \min\{|x|, \pi e^{R/2} - |x|\}$ denotes the norm on the finite box $\Rcal$ where the left and right boundaries are identified.
 We will show (see Corollary~\ref{cor:expected_common_neighbours_Ecal_set}) that for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ it holds that $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$ and hence the joint degree distribution factorizes on this set.
@@
 
-\subsubsection*{Joint neighbourhoods}
+\subsubsection*{Common neighbourhoods}
 
@@
 In addition we denote by
-$\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbours of $p$ and $p^\prime$.
-We shall establish an upper bound on the expected number of joint neighbours when $p$ and $p6\prime$ are sufficiently separated.
+$\Ncal_{\text{box}}(p,p^\prime)$ the number of common neighbours of $p$ and $p^\prime$.
+We shall establish an upper bound on the expected number of joint neighbours when $p$ and $p^\prime$ are sufficiently separated.
 Observe that $\Exp{\Ncal_{\text{box}}(p,p^\prime)} = \Mu{\BallPon{p} \cap \BallPon{p^\prime}}$.
@@
 \end{tikzpicture}
-\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:disjoint_neighbours_P_n_large}.
+\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:common_neighbours_Pcal_n}.
 Note that although here $p^\prime \notin \BallPon{p}$, this is not true in general.
@@
 There are several different quantities that are important.
-The first are the heights where the left and right boundaries of the ball $\BallPon{p}$ go outside the box $\Rcal$.
-Since $x = 0$ these heights are the same and we denote this by $h(y)$.
+The first are the heights where the left and right boundaries of the ball $\BallPon{p}$ hit the boundaries of the box $\Rcal$.
+Since $x = 0$ these heights are the same and we denote their common value by $h(y)$.
 We also need to know the coordinates $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ of the intersection of the right boundary of the neighbourhood of $p$ with the left boundary of the neighbourhood of $p^\prime$ and those for the intersection of the left boundary of the neighbourhood of $p$ with the right boundary of the neighbourhood of $p^\prime$, which we denote by $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$.
@@
 \begin{align}
-	h(y) &= R_n - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
-	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R_n}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
-	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R_n}{2}} - x^\prime\right) - y^\prime 
+	h(y) &= R - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
+	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
+	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R}{2}} - x^\prime\right) - y^\prime 
 		\label{eq:def_height_right_P_n} \\
@@
 		e^{\frac{y^\prime - y}{2}}},\\
-	\hat{y}_{\text{left}}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R_n/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right),\\
-	\hat{x}_{\text{left}}(p,p^\prime) &= \frac{x^\prime - \pi e^{R_n/2}}{1 + e^{\frac{y^\prime - y}{2}}}, \\
-	d(p,p^\prime) &= |x - x^\prime| - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
+	\hat{y}_{\text{left}}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),\\
+	\hat{x}_{\text{left}}(p,p^\prime) &= \frac{x^\prime - \pi e^{R/2}}{1 + e^{\frac{y^\prime - y}{2}}}, \\
+	d(p,p^\prime) &= |x - x^\prime|_n - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
 	\label{eq:def_d_p_p_prime}
@@
 
-%We start with the result for points whose $x$-coordinates are close, which is when $d(p,p^\prime) < 0$.
-%
-%\begin{lemma}\label{lem:disjoint_neighbours_P_n}
-%Let $p, p ^\prime \in \Rcal$ and denote $y^\ast = \min\{y, y^\prime\}$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
-%\begin{align*}
-%	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)}
-%	&\ge \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
-%	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
-%		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
-%\end{align*}
-%\end{lemma}
-%
-%\begin{proof}
-%In order to proof the result we will consider the area in between the two left boundaries of the balls $\BallPon{p}$ and
-%$\BallPon{p^\prime}$ up to the height $h^\ast := \min\{h(y), h_2(p^\prime)\}$, see Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n} and Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n_2} for reference.
-Note that here we do not need to consider different cases depending on whether $|x - x^\prime| \le e^{(y + y^\prime)/2}$ or $|x - x^\prime| > e^{(y + y^\prime)/2}$.
-%
-%By the Campbell-Mecke formula we get
-%\begin{align*}
-%	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} &=	\Mu{\BallPon{p} \Delta B_{\Pcal,n}(p^\prime)}\\
-%	&\ge \int_0^{h^\ast} \int_{x - e^{\frac{y + y_1}{2}}}^{x^\prime - e^{\frac{y^\prime + y_1}{2}}} f(x_1,y_1)
-%		\, dx_1 \, dy_1 \\
-%	&= \frac{\alpha \nu}{\pi}|x^\prime - x| \int_{0}^{h^\ast} e^{-\alpha y_1} dy_1
-%		+ \frac{\alpha \nu}{\pi}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right| \int_0^{h^\ast} 
-%		e^{-(\alpha-\frac{1}{2})y_1} \, dy_1\\
-%	&= \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
-%	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
-%		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
-%\end{align*}
-%\end{proof}
-%
-%Now we will consider the case where $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$
-%
-%\begin{lemma}\label{lem:disjoint_neighbours_P_n_large}
-%Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
-%\[
-%	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}
-%	\ge \left(\mu(\BallPon{p}) + \mu(\BallPon{p^\prime})\right)
-%		\left(1-\phi_n(p,p^\prime)\right).
-%\]
-%
-%\[
-%	\phi_n(p,p^\prime) = \xi\left( \left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
-%	- e^{-(\alpha - \frac{1}{2})R_n}\right)
-%\]
-%\end{lemma}
-%
-%\begin{proof}
-%Without loss of generality we take $p = p_0 = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$.
-To state the result for general $p = (x,y)$ we use that $x^\prime = |x - x^\prime|$.
-In particular, we need to keep track of the minus sign in front of $x^\prime$.
-Note that for all $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$ it holds that $\hat{y}_{\text{right}}(p,p^\prime) \le \hat{y}_{\text{left}}(p,p^\prime)$ and hence
-%\[
-%	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)} 
-%	\ge \int_0^{\hat{y}_{\text{right}}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1,
-%\]
-%We shall compute the integral on the right. We refer to Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n_3} for further clarification. 
-%
-%Before we proceed we show that the neighbourhoods of $p$ and $p^\prime$ below $\hat{y}_{\text{right}}(p,p^\prime)$ are disjoint.
-This is clearly true when $\hat{y}_{\text{right}}(p,p^\prime) \le h_2(p^\prime)$ so suppose that $\hat{y}_{\text{right}}(p,p^\prime) > h_2(p^\prime)$.
-Then, because we identified the right and left boundaries of the box $\Rcal$ the right boundary of $\BallPon{p^\prime}$ continues from the left boundary of the box and is described by the equation
-%\[
-%	x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}} - \pi e^{\frac{R_n}{2}}.
-%\]
-%Now, let $x_{\mathrm{right}}^\prime$ and $x_{\mathrm{left}}$ denote the $x$-coordinate of the intersection of the line $\hat{y}_{\text{right}}(p,p^\prime)$ with, respectively, the right boundary of $\BallPon{p^\prime}$ and the left boundary of $\BallPon{p}$.
-Then, since $2x^\prime \le \pi e^{R/2}$,
-%\begin{align*}
-%	x_{\mathrm{right}}^\prime &= x^\prime + e^{\frac{y^\prime + \hat{y}_{\text{right}}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-%	&= x^\prime + e^{\frac{\hat{y}_{\text{right}}(p,p^\prime)}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-%		- e^{\frac{y + \hat{y}_{\text{right}}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-%	&= 2x^\prime - e^{\frac{y + \hat{y}_{\text{right}}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
-%	&\le - e^{\frac{y + \hat{y}_{\text{right}}(p,p^\prime)}{2}} = x_{\mathrm{left}},
-%\end{align*}
-%and hence the neighbourhoods of $p$ and $p^\prime$ below $\hat{y}_{\text{right}}(p,p^\prime)$ are disjoint. It then follows that
-%\begin{align*}
-%	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
-%	&\ge \int_0^{\hat{y}_{\text{right}}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
-%		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1\\
-%	&= \int_0^{\hat{y}_{\text{right}}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
-%		\left(\ind{p_1 \in \BallPon{p}} + \ind{p_1 \in \BallPon{p^\prime}}\right) 
-%		f(x_1,y_1) \, dx_1 \, dy_1\\
-%	&= \left(\mu_{\alpha,\nu ,n}(\BallPon{p}) + \mu_{\alpha,\nu ,n}(\BallPon{p^\prime})\right)
-%		\left(1 - \frac{2\alpha \nu}{\pi}\int_{\hat{y}_{\text{right}}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1\right),
-%\end{align*}
-%from which the result follows since
-%\begin{align*}
-%	\frac{2\alpha \nu}{\pi}\int_{\hat{y}_{\text{right}}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1 
-%	&= \xi\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
-%	&= \xi\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{x^\prime}\right)^{2\alpha - 1}
-%		- e^{-(\alpha - \frac{1}{2})R_n}\right)\\
-%	&= \xi\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{|x - x^\prime|}\right)^{2\alpha - 1}
-%		- e^{-(\alpha - \frac{1}{2})R_n}\right)
-%\end{align*}
-%\end{proof}
-
-%\begin{figure}
-%\centering
-%\begin{tikzpicture}
-%	
-%	%The box \Rcal
-%	\draw (-5,0) -- (10,0);
-%	\draw (-5,4) -- (10,4);
-%	
-%	
-%	\draw[domain=1:5,smooth,variable=\x,black] plot (\x, {2*ln(\x)});
-%    \draw[domain=-1:-5,smooth,variable=\x,black] plot (\x, {2*ln(-\x)});
-%    \draw[domain=6:10,smooth,variable=\x,black] plot (\x, {2*ln(\x-5)});
-%    \draw[domain=0:4,smooth,variable=\x,black] plot (\x, {2*ln(5-\x)});
-%    
-%    
-%    
-%    \draw node at (-1,2.5) {$\BallPo{p} \setminus B_{\Pcal}(p^\prime)$};
-%    
-%    \draw node at (-0.2,3.6) {$x_1 = x^\prime - e^{\frac{y^\prime+y_1}{2}}$};
-%    
-%    \draw node at (2.5,3) {$\Ncal_{\Pcal}(p,p^\prime)$};
-%    
-%    \draw node at (5.2,3.6) {$x_2 = x+e^{\frac{y+y_2}{2}}$};
-%    
-%    \draw node at (6,2.5) {$B_{\Pcal}(p^\prime) \setminus \BallPo{p}$};
-%    
-%    \draw[dashed,thick] (2.5,1.8326) -- (2.5,0.7);
-%    \draw node at (2.5,0.4) {$w(p,p^\prime)$};
-%    
-%    \draw[dashed,thick] (-3,1.8326) -- (8,1.8326);
-%    \draw node at (-4,1.8326) {$h(p,p^\prime)$};
-%    
-%    \draw [decorate,decoration={brace},line width=1pt] (4,-0.1) -- (1,-0.1);
-%    \draw node at (2.5,-0.45) {$d(p,p^\prime)$};
-%    
-%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,0) {};
-%    \draw node at (0,-0.5) {$p$};
-%    
-%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (5,0) {};
-%    \draw node at (5,-0.5) {$p^\prime$};
-%\end{tikzpicture}
-%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ used for the proof of Lemma \ref{lem:common_neighbours_Pcal_n}.}
-%\label{fig:representation_joint_neighbourhoods}
-%\end{figure}
-
 The following result shows that if $d(p,p^\prime) > 0$, then the expected number of common neighbours is $\smallO{\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}}$.
@@
 \begin{lemma}\label{lem:common_neighbours_Pcal_n}
-Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime| > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
+Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime|_n > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
 \[
@@
 \begin{align*}
-	A_1 &:= \left\{(x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime), \, 
-		-\frac{\pi}{2} e^{R/2} \wedge - e^{\frac{y + y_1}{2}} \le x_1 \le x^\prime + e^{\frac{y^\prime + y_2}{2}} - \pi e^{R/2} \right\}\\
-	A_2 &:= \left\{(x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime), \,
-			x^\prime - e^{\frac{y^\prime + y_1}{2}} \le x_1 \le \frac{\pi}{2} e^{R/2} \vee e^{\frac{y + y_2}{2}} \right\}.
-\end{align*}
-That is $A_1$ and $A_2$ describe all point $p_1 \in \BallPon{p_0} \cap \BallPon{p}$ with, respectively, $y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime)$ and $y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime)$.
+	A_1 &:= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime), \, 
+		-\frac{\pi}{2} e^{R/2} \vee - e^{\frac{y + y_1}{2}} \le x_1 \le x^\prime + e^{\frac{y^\prime + y_2}{2}} - \pi e^{R/2} \right\}\\
+	A_2 &:= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime), \,
+			x^\prime - e^{\frac{y^\prime + y_1}{2}} \le x_1 \le \frac{\pi}{2} e^{R/2} \wedge e^{\frac{y + y_2}{2}} \right\}.
+\end{align*}
+That is $A_1$ and $A_2$ describe all points $p_1 \in \BallPon{p_0} \cap \BallPon{p}$ with $y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime)$ and $y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime)$, respectively.
 It now follows that
@@
 \begin{align*}
-	&\hspace{-10pt}\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} 
+	&\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} 
 		\int_{- e^{\frac{y + y_1}{2}}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} \hspace{-10pt} 
 		f(x_1,y_1) \dd x_1 \dd y_1\\
-	&= \frac{\alpha \nu}{\pi}\left(e^{\frac{y}{2}} + e^{\frac{y}{2}}\right) 	
+	&= \frac{\alpha \nu}{\pi}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) 	
 		\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1
@@
 \end{align*}
-Combining these results yields
+Adding these expressions yields
 \begin{align*}
@@
 	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
-	&\le \left(\Mu{\BallPon{p_0}} + \Mu{\BallPon{p_0}} \right)
-		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
-		+ e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} \right) \\
+	&\le \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}} \right)
+		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p,p^\prime)}
+		+ e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p,p^\prime)} \right) \\
 	&\hspace{10pt}+ \frac{3\nu}{2}e^{R/2} e^{-\alpha h(y)}
@@
 \end{align*}
-Finally we recall that $\hat{y}_{\text{left}}(p_0,p^\prime) \ge \hat{y}_{\text{right}}(p_0,p^\prime)$ for all $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$ and that $h(y) = R - y + 2\log(\pi/\nu)$. Hence
+To finish the argument we recall that $\hat{y}_{\text{left}}(p,p^\prime) \ge \hat{y}_{\text{right}}(p,p^\prime)$ for all $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$ and that $h(y) = R - y + 2\log(\pi/\nu)$.
+Hence
 \begin{align*}
 	&\Exp{\Ncal_{\text{box}}(p,p^\prime)} \\
-	&\le \left(\Mu{\BallPon{p_0}} + \Mu{\BallPon{p_0}} \right) 
-		\left(2e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} +    
+	&\le \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}} \right) 
+		\left(2e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p,p^\prime)} +    
 		\frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
 		e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
-		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}
+		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{\xi(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}})}
 		\right)
@@
 \[
-	\hat{y}_{\text{right}}(p_0,p^\prime) = 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),
+	\hat{y}_{\text{right}}(p,p^\prime) = 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),
 \]
@@
 	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
-			\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. 
+			\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}. 
 \]
@@
 \[
-	\Mu{\BallPon{p} \cup \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}.
+	\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}.
 \] 
@@
 \[
-	\Mu{\BallPon{p} \cup \BallPon{p^\prime}} \le \bigO{k_n} \phi_n(p,p^\prime),
+	\Mu{\BallPon{p} \cap \BallPon{p^\prime}} \le \bigO{k_n} \phi_n(p,p^\prime),
 \]
@@
 	 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
-	 =	\bigO{k_n^{-\varepsilon(2\alpha - 1)}}
+	 =	\bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
 \end{align*}
@@
 As a corollary we get that on the set $\mathcal{E}_\varepsilon(k_n)$ the joint degree distribution in $\Gbox$ is asymptotically equivalent to the product of the degree distributions.
-We shall however prove a slightly stronger result (Lemma~\ref{lem:joint_degree_factorization}) which also takes care of bounded shifts $\rho_{\text{box}}(p,p^\prime,k_n - t,k_n - t^\prime)$, for some uniformly bounded $t, t^\prime \in \mathbb{Z}$.
+We shall however prove a slightly stronger result (Lemma~\ref{lem:joint_degree_factorization}) which also takes care of bounded shifts in the joint degree distribution $\rho_{\text{box}}(p,p^\prime,k_n - t,k_n - t^\prime)$, for some uniformly bounded $t, t^\prime \in \mathbb{Z}$.
 For this we first need the following simple result for Poisson distributions.
@@
 \begin{lemma}\label{lem:finite_shifts_poisson}
-Let $k_n \to \infty$ be a sequence of integers and $X = \Po(\lambda_n)$ be a Poisson random variable with mean $\lambda_n$ satisfying
+Let $k_n \to \infty$ be a sequence of non-negative integers and $X = \Po(\lambda_n)$ be a Poisson random variable with mean $\lambda_n$ satisfying
 \[
@@
 	&= \sqrt{\ell_n} (\ell_n)^{k_n - t_n} e^{t_n - s_n} (k_n - s_n)^{t_n - s_n} \lambda_n^{s_n-t_n}\\
-	&= \sqrt{\ell_n} e^{(k_n - t_n)\log(\ell_n) + t_n - s_n} \left(\frac{k_n - s_n}{\lambda_n}\right)^{s_n - t_n}
+	&= \sqrt{\ell_n} e^{(k_n - t_n)\log(\ell_n) + t_n - s_n} \left(\frac{k_n - s_n}{\lambda_n}\right)^{t_n - s_n}
 \end{align*}
@@
 Note that $\ell_n \to 1$ and hence $\sqrt{\ell_n} \to 1$.
-Moreover, since $(k_n - s_n)/\lambda_n \to 1$ and $|s_n - t_n| = \bigO{1}$ we have that $\left(\frac{k_n - s_n}{\lambda_n}\right)^{s_n - t_n} \sim 1$ Therefore it remains to show that
+Moreover, since $(k_n - s_n)/\lambda_n \to 1$ and $|s_n - t_n| = \bigO{1}$ we have that $\left(\frac{k_n - s_n}{\lambda_n}\right)^{t_n - s_n} \sim 1$ Therefore it remains to show that
 \[
@@
 \begin{align*}
-	\rho_{\text{box}}(p,p^\prime,k_n - t_n,k_n - t_n^\prime)
-	&= (1+\smallO{1})\rho_{\text{box}}(p,k_n - s_n)\rho_{\text{box}}(p^\prime,k_n-s_n^\prime).
+	\rho_{\mathrm{box}}(p,p^\prime,k_n - t_n,k_n - t_n^\prime)
+	&= (1+\smallO{1})\rho_{\mathrm{box}}(p,k_n - s_n)\rho_{\mathrm{box}}(p^\prime,k_n-s_n^\prime).
 \end{align*}
@@
 \end{align*}
-Since by Lemma~\ref{cor:expected_common_neighbours_Ecal_set} $\Mu{\BallPon{p} \cup \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}$, it follows from Lemma~\ref{lem:near_independence_poisson} that
+Since by Lemma~\ref{cor:expected_common_neighbours_Ecal_set} $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}$, it follows from Lemma~\ref{lem:near_independence_poisson} that
 \[
@@
 \]
-This expression can be written as the sums of several terms, depending on how $\{p, p_1, p_2\}$ and $\{p^\prime, p_1^\prime, p_2^\prime\}$ intersect.
+This expression can be written as the sum of several terms, depending on how $\{p, p_1, p_2\}$ and $\{p^\prime, p_1^\prime, p_2^\prime\}$ intersect.
 To this end we define, for $a \in \{0,1\}$ and $b \in \{0,1,2\}$,
@@
 \]
-with the summation being over all two distinct pairs $(p_1, p_2)$ and $(p_1^\prime, p_2^\prime)$. Then we have
+with the sum taken over all two distinct pairs $(p_1, p_2)$ and $(p_1^\prime, p_2^\prime)$. Then we have
 \[
@@
 	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
-			\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}.
-\]
-Let $\mathcal{E}_\varepsilon(k_n)^c$ the same set but with $|x - x^\prime| \le k_n^{1 + \varepsilon}$ and denote by $I_{a,b}^\ast$ the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$.
+			\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}.
+\]
+Let $\mathcal{E}_\varepsilon(k_n)^c$ be the same set but with $|x - x^\prime|_n \le k_n^{1 + \varepsilon}$ and denote by $I_{a,b}^\ast$ the the part of $I_{a,b}$ where $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$.
 Will split the analysis between $I_{a,b}^\ast$ and $I_{a,b} - I_{a,b}^\ast$.
@@
 
-% and~\eqref{eq:variance_T_I_ab} we have to consider the cases $k_n = \bigT{1}$ and $k_n \to \infty$ separately.
-However, each case follows a similar strategy.
-First we define a set $\mathcal{E} \subseteq \Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$ such that outside this set the contributions of $\Exp{I_{a,b}}$ are negligible while on this set the joint degree distribution factorizes.
-These will be the sets defined by~\eqref{eq:def_joint_degree_set_E_constant_k} and~\eqref{eq:def_joint_degree_set_E_growing_k}.
-In particular, for these sets we have that $a = 1$ is not possible and hence we only need to consider the three different cases for $b$.
-For $a =0 = b$, the factorization of the degree distributions will enable us to prove~\eqref{eq:transition_clustering_main_term}.
-For $b = 1, 2$ we derive sufficient bounds for $\Exp{J_b(p,p^\prime)}$ in terms of $k_n$ for $(p,p^\prime)$ in the set $\mathcal{E}$.
-
 \begin{proof}[Proof of Proposition \ref{prop:concentration_tilde_T_P_n}]
@@
 Throughout this proof we set $i = |\{p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\} \cap \BallPon{p}|$, $j = |\{p^\prime\} \cap \BallPon{p}|$ and define $i^\prime, j^\prime$ in a similar way by interchanging the primed and non-primed variables.
-In addition, we write $D_{\text{box}}(p,p^\prime,k,\ell)$ to denote the indicator that $|\BallPon{p} \cap (\Pcal_n \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = k$ and $|\BallPon{p^\prime} \cap (\Pcal_n \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = \ell$.
+In addition, we write $\widetilde{D}_{\text{box}}(p,p^\prime,k,\ell)$ to denote the indicator that $|\BallPon{p} \cap (\Pcal \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = k$ and $|\BallPon{p^\prime} \cap (\Pcal \setminus \{p, p^\prime, p_1, p_2, p_1^\prime, p_2^\prime\})| = \ell$.
+Note that this also depend on $\{p_1, p_2, p_1^\prime, p_2^\prime\}$ but we suppressed this to keep notation concise.
+Similarly we write $D_{\text{box}}(p,p^\prime,k,\ell)$ to denote the indicator that $|\BallPon{p} \cap (\Pcal \setminus \{p, p^\prime\})| = k$ and $|\BallPon{p^\prime} \cap (\Pcal \setminus \{p, p^\prime\})| = \ell$, which now only depends on $p$ and $p^\prime$.
 Then, by the Campbell-Mecke formula
@@
 		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b}^{\ne}
-			\hspace{-7pt} D_{\text{box}}(p,p^\prime, k_n-i,k_n- i^\prime) \,
+			\hspace{-7pt} \widetilde{D}_{\text{box}}(p,p^\prime, k_n-i,k_n- i^\prime) \,
 			\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime, p_1^\prime, p_2^\prime)}
 \end{align*}
-where the sum is over all distinct pairs $(p_1, p_2)$ and $(p_1^\prime, p_2^\prime)$. We also that 
+where the sum is over all distinct pairs $(p_1, p_2)$ and $(p_1^\prime, p_2^\prime)$. We also know that 
 \[
@@
 
-%For this we note that by Lemma \ref{lem:disjoint_neighbours_P_n} and Lemma \ref{lem:disjoint_neighbours_P_n_large} we have for $p,p^\prime \in \Kcal_{\varepsilon}(k_n)$ that $\Exp{\left|\Ncal_{\text{box}}(p\Delta p^\prime)\right|} \le k_n^{\varepsilon}$ implies that eventually and $|x-x^\prime| \le k_n^{1+\varepsilon}$.
-In particular $|x - x^\prime| \le k_n^{1+\varepsilon}$ for all $(p, p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)^c$.
-Therefore, we have
 For $J_0$ we have, using Lemma~\ref{lem:joint_degree_factorization}
@@
 	&\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n} J_0(p,p^\prime)}\\
-	&= \Exp{\sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal \setminus p,p^\prime 
+	&= \Exp{\sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal \setminus \{p,p^\prime\} 
 		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = 0}^{\ne}
-		\hspace{-7pt} D_{\text{box}}(p,p^\prime, k_n-i,k_n- i^\prime) \,
+		\hspace{-7pt} \widetilde{D}_{\text{box}}(p,p^\prime, k_n-i,k_n- i^\prime) \,
 		\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime, p_1^\prime, p_2^\prime)}\\
@@
 \end{align*}
-Next we recall that for all $y^\prime \in \Kcal_{C}(k_n)$, 
+Next we recall that for all $y^\prime \in \Kcal_{C}(k_n)$ (see~\eqref{eq:def_K_C_set}), 
 \[
@@
 \] 
-where we used that $\Exp{\widetilde{T}_{\text{box}}(p^\prime)} = (1+\smallO{1}) k_n^2 P(y^\prime)$, for all $y^\prime \in \Kcal_{C}(k_n)$.
+where $p^\prime = (x^\prime, y^\prime)$ and we used that $\Exp{\widetilde{T}_{\text{box}}(p^\prime)} = (1+\smallO{1}) k_n^2 P(y^\prime)$, for all $y^\prime \in \Kcal_{C}(k_n)$.
 Therefore, using that $\rho_{\text{box}}(p,p^\prime,k_n,k_n) \le \rho_{\text{box}}(p,k_n)$,
@@
 	&= \bigO{k_n^{3 + \varepsilon -2\alpha} s_\alpha(k_n) \Exp{\widetilde{T}_{\text{box}}(k_n,C)}}\\
-	&= \smallO{n k_n^{-(2\alpha - 1)}s_\alpha(k_n) \Exp{T_{\Pcal,n}(k_n)}} 
+	&= \smallO{n k_n^{-(2\alpha - 1)}s_\alpha(k_n) \Exp{\widetilde{T}_{\text{box}}(k_n,C)}} 
 		= \smallO{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}^2},
@@
 \]
-We recall that for $(p,p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)$ and any two uniformly bounded $t, t^\prime \in \mathbb{Z}$,
+Recall the result from Lemma~\ref{lem:joint_degree_factorization}, that for $(p,p^\prime) \in \mathcal{E}_{\varepsilon}(k_n)$ and any two uniformly bounded $t, t^\prime \in \mathbb{Z}$,
 \[
@@
 	\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n} J_1}
-	\le \bigO{1} k_n \rho_{\text{box}}(p,p^\prime,k_n,k_n)\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox{p} = k}
+	\le \bigO{1} k_n \rho_{\text{box}}(p,p^\prime,k_n,k_n)\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n}
 \end{equation}
@@
 	&= k_n \int_{\Kcal_C(k_n)^2} \ind{|x-x^\prime| \le k_n^{1 + \varepsilon}}
-		\rho_{\text{box}}(p,k_n)\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox{p} = k} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
+		\rho_{\text{box}}(p,k_n)\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) = k_n} f(x,y) f(x^\prime,y^\prime) \, dx^\prime \, dx \, dy^\prime \, dy\\
 	&\le \bigO{k_n^{2+\varepsilon}} \left(\int_{a_n^-}^{a_n^+} e^{-\alpha y^\prime} \, dy^\prime\right) 
@@
 \[
-	n^{-1} k_n^{2\alpha - 1} s(k_n)^{-1} k_n^{2 + \varepsilon -2\alpha} = k_n^{4\alpha - 1 + \varepsilon} 
+	n^{-1} k_n^{2\alpha - 1} s(k_n)^{-1} k_n^{2 + \varepsilon -2\alpha} = n^{-1} k_n^{4\alpha - 1 + \varepsilon} 
 	= \smallO{n^{-1}n^{\frac{4\alpha - 1 + \varepsilon}{2\alpha + 1}}} = \smallO{1}
@@
 \[
-	J_{0,1} = \sum_{(p_1, p_2) \in \Pcal \setminus p}^{\ne} \widetilde{T}_{\text{box}}(p,p_1,p_2) 
+	J_{0,1} = \sum_{(p_1, p_2) \in \Pcal \setminus \{p\}}^{\ne} \widetilde{T}_{\text{box}}(p,p_1,p_2) 
 	\sum_{p_2^\prime \in \Pcal \setminus \{p^\prime, p_1\}} \widetilde{T}_{\text{box}}(p^\prime,p_1,p_2^\prime). 
@@
 \]
-Next, by integrating only over $x_2^\prime$ and $y_2^\prime $ we get that $\CExp{Z_{0,1}}{\Dbox(p), \Dbox(p^\prime) = k_n}$ 
+Next, by integrating only over $x_2^\prime$ and $y_2^\prime $ we get
 \begin{align*}
 	\CExp{Z_{0,1}}{\Dbox(p), \Dbox(p^\prime) = k_n} &=
-	\bigO{e^{\frac{y^\prime}{2}}\ind{|x-x^\prime|\le k_n^{2 + \varepsilon}} 
+	\bigO{e^{\frac{y^\prime}{2}}\ind{|x-x^\prime|\le \bigO{1}k_n^{2 + \varepsilon}} 
 		\CExp{\widetilde{T}_{\text{box}}(p)}{\Dbox(p) =k_n}}\\
@@
 \end{align*}
-where the last line follow from the analysis done for $\Exp{I_{0,0}-I_{0,0}^\ast}$.
+where the last line follows from the analysis done for $\Exp{I_{0,0}-I_{0,0}^\ast}$.
 
@@
 
-For the other term we use that the degree distribution factorizes. This gives
+For the other term we use the fact that the degree distribution factorizes;
 \begin{align*}
@@
 \end{align*}
-where we use that $k_n^{-2} = \smallO{s(k_n)}$.
+where we also used that $k_n^{-2} = \smallO{s(k_n)}$.
 
@@
 \[
-	k_n n^{-1} n^{-1} k_n^{-(2\alpha -1)} s(k_n)^{-1} = k_n^{6\alpha - 2} n^{-1}
+	k_n n^{-1} k_n^{(2\alpha -1)} s(k_n)^{-1} = k_n^{6\alpha - 2} n^{-1}
 	= \bigO{n^{\frac{4\alpha - 3}{2\alpha + 1}}} = \smallO{1},
@@
 \[
-	k_n n^{-1} n^{-1} k_n^{-(2\alpha -1)} s(k_n)^{-1} = \bigO{n^{-1} k_n^{-(2\alpha - 1)}} = \smallO{1}.
+	k_n  n^{-1} k_n^{(2\alpha -1)} s(k_n)^{-1} = \bigO{n^{-1} k_n^{-(2\alpha - 1)}} = \smallO{1}.
 \]

### 2019-05-28 concentration_argument.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

@@
 
-Note that since all three corollaries follow from Lemma~\ref{lem:concentration_argument}, Proposition~\ref{prop:concentration_argument_all} follows if we can prove that the conclusions from this lemma hold when we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
-For this the following, slightly more general version of Lemma~\ref{lem:concentration_argument} will be important.
-
 Although powerful, the current versions of the concentration of heights arguments are only valid for the function $\rho(y,k_n) := \Prob{\Po\left(\Mu{\BallPo{y}}\right) = k_n}$, which uses the neighbourhoods in the infinite model $\Ginf$.
-Since we will also be working in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, we would like to use concentration of heights arguments when the integrand contains either the function $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
+Since we will also be working in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, we would like to use concentration of heights arguments for the degree distribution function in these models.
+To be more precise, let us define
+\[
+	\rho_{\Po}(y,k) = \Prob{\Po(\mu(\BallHyp{y})) = k}
+\] 
+and
+\[
+	\rho_{\mathrm{box}}(y,k) = \Prob{\Po(\mu(\BallPon{y})) = k}
+\] 
+Then we want when Lemma~\ref{lem:concentration_argument} to remain true if we replace $\rho(y,k_n)$ with either the function $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$.
 To establish these result we first prove a more general version of Lemma~\ref{lem:concentration_argument}.
@@
 \] 
-In addition, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, with $\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y)$ and 
-where $\phi_n(y)$ is a differentiable function satisfying:
-\begin{enumerate}[\upshape i)]
-\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} |\phi_n(y)| = 0$,
-\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
-\end{enumerate}
+In addition, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is a differentiable function that satisfies for some $0 < \varepsilon < 1$
+\begin{align*}
+	&\mathrm{i)} \, \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} \frac{\hat{\mu}_n(y)}{\mu(\BallPo{y})} = 1
+	\quad \text{and}
+	&&\mathrm{ii)} \, \lim_{n \to \infty}  \sup_{0 \le y \le (1 - \varepsilon)R} \frac{\hat{\mu}_n^\prime(y)}{\mu(\BallPo{y})} = \frac{1}{2}.
+\end{align*}
+%
+%
+% with $\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y)$ and 
+%where $\phi_n(y)$ is a differentiable function satisfying:
+%\begin{enumerate}[\upshape i)]
+%\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} |\phi_n(y)| = 0$,
+%\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
+%\end{enumerate}
 Then the following holds:
@@
 
+For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right) = \xi e^{y/2}$ throughout the proof. Observe that $\mu^\prime(y) = \mu(y)/2$ and $\mu^{-1}(y z) = \mu^{-1(y)} + \mu^{-1}(z)$.
+
+%We note that the statement will follow from Lemma~\ref{lem:concentration_argument} if we can show that
+%\[
+%	\int_0^R \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+%	= \left(1 + o(1)\right) \int_0^R \rho(z,k_n) e^{-\alpha z} \dd z.
+%\] 
+%or equivalently,
+%\[
+%	\int_0^R \rho(z,k_n) e^{-\alpha z} \dd z
+%	= \left(1 + o(1)\right)\int_0^R \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
+%\]
+%
+%We will do this in two steps.
+%
+%Therefore, what is left is to show that
+%\[
+%	\int_0^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+%	= \left(1 + o(1)\right) \int_0^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z.
+%\] 
+%or equivalently,
+%\[
+%	\int_0^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z
+%	= \left(1 + o(1)\right)\int_0^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
+%\]
+%
+%Using the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$ and writing $\hat{a}_n^\pm = \hat{\mu}_n^{-1}(\mu(a_n^\pm))$ and $\hat{R}_{\varepsilon^\prime} := \hat{\mu}_n^{-1}(\mu((1-\varepsilon^\prime)R))$, we get
+%\begin{align*}
+%	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z 
+%	&= \int_{a_n^+}^{(1-\varepsilon^\prime)R} \Prob{\Po(\mu(z)) = k_n} e^{-\alpha z} \dd z\\
+%	&= \int_{\hat{a}_n^+}^{\hat{R}_{\varepsilon^\prime}} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
+%		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
+%\end{align*}
+%where the fraction in the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.
+
 \paragraph{Proof of statement 1.}
-Let $0 < \varepsilon < 1$ be such that condition ii) holds and take $\varepsilon^\prime = \min\{\varepsilon,1/3\} < 1/2$.
-We first show that the integration over $(1-\varepsilon^\prime)R \le y \le R$ is negligible.
+
+Let $0 < \varepsilon < 1$ be such that conditions i) and ii) hold, take $\varepsilon^\prime = \min\{\varepsilon/3,1/3\} < 1/2$ and let $\delta > 0$ be such that $\hat{\mu}_n(\delta) \ge \xi$.
+We first show that we can restrict to integration over $(\delta, (1-\varepsilon^\prime)R)$ that the integration over $(1-\varepsilon^\prime)R \le y \le R$ is negligible.
 
@@
 	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\prime)R,k_n) e^{-(\alpha-\beta)(1-\varepsilon^\prime)R} \\
-	&= \bigO{\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) n^{-2(\beta-\alpha)(1-\varepsilon^\prime)}}.
+	&= \bigO{\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) n^{-2(\alpha-\beta)(1-\varepsilon^\prime)}}.
 \end{align*}
-By assumption on $\hat{\mu}_n(y)$ we have that $\hat{\mu}_n((1-\varepsilon^\prime)R) = \bigT{\mu((1-\varepsilon^\prime)R} = \bigT{n^{2(1-\varepsilon^\prime)}}$.
-Since $k_n = \smallO{n}$, by our choice of $\varepsilon^\prime$, $\hat{\mu}_n((1-\varepsilon^\prime)R)/k_n = \omega\left(n^{1 - 2\varepsilon^\prime}\right) \to \infty$ as $n \to \infty$.
+By construction $\varepsilon^\prime < \varepsilon$, and hence by condition i) we have that $\hat{\mu}_n((1-\varepsilon^\prime)R) = \bigT{\mu((1-\varepsilon^\prime)R} = \bigT{n^{2(1-\varepsilon^\prime)}}$.
+Therefore, since $k_n = \smallO{n}$, it follows that $\hat{\mu}_n((1-\varepsilon^\prime)R)/k_n = \omega\left(n^{1 - 2\varepsilon^\prime}\right) \to \infty$ as $n \to \infty$.
 We can now use Stirling's approximation to bound $\hat{\rho}_n((1-\varepsilon^\prime)R,k_n)$ as
@@
 	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\varepsilon^\prime)} e^{-n^{2(1-\varepsilon^\prime)}}}
-	= \bigO{k_n^{(1+C^2)/2}}.
+	= \bigO{k_n^{-(1+C^2)/2}}.
 \]
 
-We are left to show that for sufficiently large $C > 0$,
+In a similar fashion we get that
+\begin{align*}
+	\int_0^\delta h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	&= \bigO{1} \hat{\rho}_n(\delta, k_n) \\
+	&= \bigO{1} k_n^{-1/2} e^{-k_n(\log(k_n)-\hat{\mu}_n(\delta))} = \bigO{k_n^{-(1+C^2)/2}}.
+\end{align*}
+
+We are thus left to show that for sufficiently large $C > 0$,
 \begin{equation}\label{eq:concentration_argument_an_-}
-	 \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}},
+	 \int_\delta^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}},
 \end{equation}
@@
 \end{equation}
-%\TM{ Why can we change the upper limit of the integral? PLease elaborate (in the paper) }
+To prove this we first establish a result that will also help with proving statement 2.
 
-For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right)$. Now fix some $0 < \delta < 1$ and let $n$ be large enough such that 
+Let $(a, b) \subseteq (\delta,(1-\varepsilon^\prime)R)$ and consider the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$.
+Then, writing $\hat{a} = \hat{\mu}_n^{-1}(\mu(a))$ and similar for $\hat{b}$, we get
+\begin{align*}
+	\int_{a}^{b} \rho(z,k_n) e^{-\alpha z} \dd z 
+	&= \int_{a}^{b} \Prob{\Po(\mu(z)) = k_n} e^{-\alpha z} \dd z\\
+	&= \int_{\hat{a}}^{\hat{b}} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
+		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
+\end{align*}
+where the fraction in the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.
+
+Now recall that $\hat{\mu}_n(y)$ satisfies conditions i) and ii). Since $\mu^\prime(y) = \mu(y)/2$ it follows that, uniformly on $(a,b)$,
 \[
-\sup_{0 < y \le (1-\varepsilon^\prime)R} |\phi_n(y)| < \delta, \quad
-\lambda_n^+(1 - \delta) > k_n \quad \text{and} \quad
-\lambda_n^-(1 + \delta) < k_n.
+	\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))}
+	= \frac{2\hat{\mu}_n^\prime(y)}{\hat{\mu}_n(y)}
+	= \frac{(1 + \smallO{1})2\hat{\mu}_n^\prime(y)}{(1 + \smallO{1})\mu(y)}
+	= (1+\smallO{1}).
 \]
+Moreover, we have
+\[
+	e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} = e^{-\alpha (y + \mu^{-1}(1+\smallO{1}))} = (1+\smallO{1})e^{-\alpha y},
+\]
+uniformly on $(a,b)$. These results then imply
+\begin{equation}\label{eq:equivalence_integral_rho_change_variables}
+	\int_{a}^{b} \rho(z,k_n) e^{-\alpha z} \dd z 
+	= (1+\smallO{1}) \int_{\hat{a}}^{\hat{b}} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
+\end{equation}
 
-Next, recall that the function $\lambda \mapsto \Prob{\Po(\lambda) = k}$ is monotonic increasing on $[0,k]$ and monotonic decreasing on $[k, \infty)$. Then since for $n$ large enough we have 
+Now, using~\eqref{eq:equivalence_integral_rho_change_variables} with $a = \mu^{-1}(\hat{\mu}_n(\delta))$ and $b = \mu^{-1}(\hat{\mu}_n(a_n^-)$ we get
+\begin{align*}
+	\int_a^b \rho(y,k_n) e^{(\beta-\alpha) y} \dd y
+	&= (1+\smallO{1}) \int_{\delta}^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y.
+\end{align*}
+Since $\mu^{-1}(\hat{\mu}_n(a_n^-) = (1+\smallO{1})a_n^-$ and $b \ge 0$ the left hand side is
 \[
-	\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y)) \ge \mu(y)(1 - \delta) \ge \mu(a_n^+)(1 - \delta)
-	= (\ell_n + C \kappa_n)(1 - \delta) > k_n,
+	\bigO{1} \int_0^{a_n^-} \rho(y,k_n) e^{(\beta-\alpha) y} \dd y,
 \]
-it follows that 
-\[
-	\hat{\rho}_n(y,k_n) = \Prob{\Po(\hat{\mu}_n(y)) = k_n} \le \Prob{\Po(\mu(y)(1-\delta)) = k_n},
-\]
-for all $a_n^+ \le y \le (1-\varepsilon^\prime)R$. By making the change of variables $z = \mu^{-1}(\mu(y)(1-\delta)) = y + 2 \log(1-\delta)$ we then get
-\begin{align*}
-	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
-	&\le \int_{a_n^+}^{(1-\varepsilon^\prime)R} \Prob{\Po(\mu(y)(1-\delta)) = k_n} 
-		e^{(\beta-\alpha) y} \dd y\\
-	&= (1-\delta)^{\beta - \alpha} \int_{a_n^+ + 2\log(1-\delta)}^{(1-\varepsilon^\prime)R + 2\log(1-\delta)} 
-		\Prob{\Po(\mu(z)) = k_n} e^{(\beta - \alpha)z} \dd z\\
-	&= \bigO{1} \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z\\
-	&= \bigO{k_n^{-(1+C^2)/2}},
-\end{align*}
-where the last line is due to Lemma~\ref{lem:concentration_argument}. This proves~\eqref{eq:concentration_argument_an_+}.
-
-%implies that for large enough $C$,
-%\[
-%	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z = 0,
-%\]
-%we have proven~\eqref{eq:concentration_argument_an_+}.
-
-The proof of~\eqref{eq:concentration_argument_an_-} follows the same line of reasoning. This time we use that for $0 \le y \le a_n^-$,
-\[
-	\hat{\mu}_n(y) \le \mu(y)(1 + \delta) \ge \mu(a_n^-)(1 + \delta)
-		= (\ell_n - C \kappa_n)(1 + \delta) < k_n,
-\]
-so that 
-\[
-	\hat{\rho}_n(y,k_n) = \Prob{\Po(\hat{\mu}_n(y)) = k_n} \le \Prob{\Po(\mu(y)(1+\delta)) = k_n}.
-\]
-Making a similar change of variables $z = y + 2 \log(1+\delta)$ we then get
-\begin{align*}
-	\int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
-	&= \int_0^{a_n^-}\Prob{\Po(\mu(y)(1-\delta)) = k_n} 
-		e^{(\beta-\alpha) y} \dd y\\
-	&\le (1+\delta)^{\beta - \alpha} \int_0^{a_n^- + 2\log(1+\delta)} 
-		\rho(z,k_n) e^{(\beta - \alpha)z} \dd z,
-\end{align*}
-and hence~\eqref{eq:concentration_argument_an_-} follows by another application of Lemma~\ref{lem:concentration_argument}.
+and hence~\eqref{eq:concentration_argument_an_-} follows from Lemma~\ref{lem:concentration_argument}. The proof of~\eqref{eq:concentration_argument_an_+} follows in a similar way.
 
@@
 
-The proof of the second statement follows the same line of reasoning as above. First, by the mean value theorem for definite integrals 
+The proof of the second statement follows the same line of reasoning as above, using~\eqref{eq:equivalence_integral_rho_change_variables}.
+First, the mean value theorem for definite integrals implies that
 \[
 	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) h(y) e^{-\alpha y} \dd y
-	= h(c_n) \int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z,
+	= h(c_n) \int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y,
 \]
-for some $c_n \in (a_n^-, a_n^+)$. Since, $c_n \sim 2 \log(k_n/\xi)$, by assumption on $h$, $h(c_n)\sim h(2\log(k_n/\xi))$. Therefore it is enough to show that
+for some $c_n \in (a_n^-, a_n^+)$. Since, $c_n \sim 2 \log(k_n/\xi)$, by assumption on $h$, $h(c_n)\sim h(2\log(k_n/\xi))$. 
+Therefore it is enough to show that
 \[
@@
 \] 
-or equivalently,
-\[
-	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z
-	= \left(1 + o(1)\right)\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
-\]
-
-Using the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$ and writing $\hat{a}_n^\pm = \hat{\mu}_n^{-1}(\mu(a_n^\pm))$, we get
-\begin{align*}
-	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z 
-	&= \int_{a_n^-}^{a_n^+} \Prob{\Po(\mu(z)) = k_n} e^{-\alpha z} \dd z\\
-	&= \int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
-		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
-\end{align*}
-where the fraction in the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.
-
-Now recall that $\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y))$, with $\phi_n(y)$ satisfying conditions i) and ii).
-It then follows $\hat{\mu}_n^\prime(y) = (1 + \smallO{1})\mu^\prime(y)$ as $n \to \infty$, uniformly on $(a_n^-, a_n^+)$.
-Next we note that $\mu^\prime(y) = \mu(y)/2$ from which it follows that uniformly on $[a_n^-, a_n^+]$,
-\[
-	\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))}
-	= \frac{2\hat{\mu}_n^\prime(y)}{\hat{\mu}_n(y)}
-	= \frac{(1 + \smallO{1})2\mu^\prime(y)}{(1 + \smallO{1})\mu(y)}
-	= (1+\smallO{1})
-\]
-Therefore,
-\begin{align*}
-	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z
-	&= (1 + \smallO{1})\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha y} \dd y\\
-	&= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y\\
-	&= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
-\end{align*}
-which finishes the proof.
+This however follows immediately from~\eqref{eq:equivalence_integral_rho_change_variables} by picking $a = \mu^{-1}(\hat{\mu}_n(a_n^-))$ and $b = \mu^{-1}(\hat{\mu}_n(a_n^+))$.
 \end{proof}
 
-To apply this lemma to $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$ we need to show that both these functions are of the form $\rho(y,k_n)(1 + \phi_n(y))$, where $\phi_n(y)$ satisfies the conditions i) and ii) in Lemma~\ref{lem:concentration_argument_rho_approximation}.
+To apply this lemma to $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$ we need to show that both these functions satisfies the conditions i) and ii) in Lemma~\ref{lem:concentration_argument_rho_approximation}.
 We will do this in the next two sections and establish that the results from Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n}
@@
 or $\rho_{\Po}(y,k_n)$.
-
-\begin{remark}[Generalized concentration of heights arguments]
-Since the results from Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n} and~\ref{cor:concentration_heights_asymptotics_n} hold for any of the three functions $\rho(y,k_n)$, $\rho_{\text{box}}(y,k_n)$ and $\rho_{\Po}(y,k_n)$, we will will refer only to one of these three when using a concentration of heights argument of for any of the three models $\GPo$, $\Gbox$ and $\Ginf$.
-\end{remark}
 
@@
 
-Let us now define
-\[
-	\rho_{\mathrm{box}}(y,k) = \Prob{\Po(\mu(\BallPon{y})) = k}.
-\]
-The following is then immediate.
-
-\PvdH{Check if we need to define this earlier.}
+From the definition of $\phi_n(y)$ in Lemma~\ref{lem:average_degree_P_n} it is immediate that $\rho_{\mathrm{box}}(y,k)$ satisfies the conditions for $\hat{\rho}_n(y,k)$ in Lemma~\ref{lem:concentration_argument_rho_approximation}.
+We thus have the following corollary.
 
@@
 \end{corollary}
+
+\begin{remark}[Generalized concentration of heights arguments]
+Since the results from Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n} and~\ref{cor:concentration_heights_asymptotics_n} hold for any of the three functions $\rho(y,k_n)$, $\rho_{\text{box}}(y,k_n)$ and $\rho_{\Po}(y,k_n)$, we will will refer only to one of these three when using a concentration of heights argument of for any of the three models $\GPo$, $\Gbox$ and $\Ginf$.
+\end{remark}

### 2019-05-28 introduction.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

@@
 It exhibits the three main characteristics usually associated with complex networks: a power-law degree distribution, a non-vanishing clustering coefficient and short graph distances.
-
-%
-%\subsection{Hyperbolic random graphs}\label{ssec:hyperbolic_model}
 
@@
 Gugelmann et al.~\cite{gugelmann2012random} also showed that the average degree converges in probability to the constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing in the sense that it is bounded below by a positive constant a.a.s.
-Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Pee(E_n)\to 1$ as $n \to \infty$.
+Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Prob{E_n} \to 1$ as $n \to \infty$.
+Here the events $E_n$ might be defined in different probability spaces, in which case $\Pee$ will the corresponding probability measure.
 %Their work however left open the question of whether the clustering coefficient actually converges in probability.
@@
 Despite these interesting observations and the attention the KPKVB model has generated since then, the behaviour of the clustering function in KPKVB random graphs had not been completely determined.
-In particular it has not been established whether it converges as $n\to\infty$ to some suitable limit function, nor how $c(k;G)$ scales with $k$.
+In particular it has not been established whether it converges as $n\to\infty$ to some suitable limit function, nor how $c(k;G(n; \alpha,\nu))$ scales with $k$.
 Theorems~\ref{thm:mainkfixed},~\ref{thm:mainktoinfty} and Proposition~\ref{prop:asymp} below settle these questions.
@@
 \begin{theorem}\label{thm:mainktoinfty}
-Let $\alpha>\frac12, \nu>0$ be fixed and let $k_n$ be a sequence of integers
+Let $\alpha>\frac12, \nu>0$ be fixed and let $k_n$ be a sequence of non-negative integers
 satisfying $1 \ll k_n \ll n^{1/(2\alpha+1)}$. Then, writing $G_n := G(n;\alpha,\nu)$, we have
@@
 \end{theorem}
-
-%We remark that the number of vertices of degree exactly $k$ satisfies $N_k = 0$ a.a.s.~when $k \gg n^{1/(2\alpha+1)}$, see~\TM{ add reference to correct thm / lemma here! }.
-%So the range in the above result is essentially to best possible.
 
@@
 Note that Theorem~\ref{thm:mainktoinfty} implies that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows, whose scaling is given in the above result.
-In particular, this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac34$, and confirms it only for $\alpha > \frac34$.
+In particular, this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac{3}{4}$, and confirms it only for $\alpha > \frac{3}{4}$.
 
-We remark that simultaneously and independently Stegehuis, van der Hofstad and van Leeuwaarden~\cite{stegehuis2018scale} found a similar, but less detailed result on the $k\to\infty$ scaling of the clustering function in the KPKVB model.
+We remark that simultaneously and independently Stegehuis, van der Hofstad and van Leeuwaarden~\cite{stegehuis2019scale} used a completely different technique to obtain a similar, though less detailed, result on the $k\to\infty$ scaling of the clustering function in the KPKVB model.
 
@@
 \[
-	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k_n; G_n)}{\gamma(k)} - 1\right|}.
+	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|}.
 \]
-Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:local_clustering_hyperbolic}
+Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainktoinfty}
 \[
@@
 \paragraph{Near maximum scaling for $k_n$.}
-Our results for the clustering function in the KPKVB model are valid for any sequence of integers $k_n \to \infty$ such that $k_n \ll n^{\frac{1}{2\alpha + 1}}$.
-Although one would like to have results for any sequence $k_n \le n$, it turns out that $n^{1/(2\alpha + 1)}$ is the near maximum scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
-To see why this is the case note that by definition of the local clustering function~\eqref{eq:def_clustering_function} we have that $c(k_n; G_n) = 0$ if $N_{n}(k_n) = 0$, where $N_n(k_n)$ denote the number of vertices in a KPKVB graph $G(n; \alpha, \nu)$ with degree $k_n$.
+Our results for the clustering function in the KPKVB model are valid for any sequence of non-negative integers $k_n \to \infty$ such that $k_n \ll n^{\frac{1}{2\alpha + 1}}$.
+Although one would like to have results for any sequence $k_n \le n-1$, it turns out that $n^{1/(2\alpha + 1)}$ is the near maximum scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
+To see why this is the case note that by definition of the local clustering function~\eqref{eq:def_clustering_function} we have that $c(k_n; G_n) = 0$ if $N_{n}(k_n) = 0$, where $N_n(k_n)$ denotes the number of vertices in a KPKVB graph $G(n; \alpha, \nu)$ with degree $k_n$.
 It follows by Markov's inequality that for any positive function $f : \R_+ \to \R_+$
@@
 
-\PvdH{We should try and add something here. Not necessarily needed for the submission to arXiv though.}
+It follows from Proposition~\ref{prop:asymp} that there is a transition in the scaling of the local clustering function at $\alpha = 3/4$.
+This corresponds to an exponent $5/2$ for the probability mass function of the degree distribution.
+This transition is different from those often observed for networks with scale-free degree distributions, where transitions occur at integer values of the exponent.
+At this point, it is unclear what the underlying reason is for the appearance of the transition at this half exponent.
+Interestingly, a similar transition point has also been observed for both majority vote models~\cite{chen2015critical} and flocking dynamics~\cite{miguel2018effects} on networks with scale-free degree degree distributions.
 

### 2019-05-28 paper.tex
processed most of Nikolaos comments on sections 5-7
included all comments from Nikolaos and made final changes. Ready for Tobias.

@@
 % Comment this out when not using the tocloft package
-\setlength{\cftbeforesecskip}{5pt}
+\setlength{\cftbeforesecskip}{7pt}
 
@@
 \newcommand{\expH}{\overline{n}_{\Po}(k_n)}
-\newcommand{\expP}{\overline{n}_{\infty}(k_n)}
+\newcommand{\expP}{\overline{n}_{\mathrm{box}}(k_n)}
 \newcommand{\Pop}[2]{\mathrm{Po} (#2;#1)}
@@
 \newcommand{\Haa}{\ensuremath{{\mathbb H}}}
-\newcommand{\GPo}[0]{\ensuremath{G_{\text{Po}}}}
-\newcommand{\Gbox}[0]{\ensuremath{G_{\text{box}}}}
+\newcommand{\GPo}[0]{\ensuremath{G_{\Po}}}
+\newcommand{\Gbox}[0]{\ensuremath{G_{\mathrm{box}}}}
 \newcommand{\GPoH}{\ensuremath{G_{Po,H}}}
@@
 This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant.
-Similarly, we are able to show that $c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ given explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
+Similarly, we are able to show that $c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ which we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
 We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$.
 Our results show that $\gamma(k)$ scales differently, as $k$ grows, for different ranges of $\alpha$.
-More precisely, $\gamma(k) = \Theta( k^{2 - 4\alpha})$ if $\frac{1}{2} < \alpha < \frac{3}{4}$, $\gamma(k) = \Theta( \log(k) / k )$ if $\alpha=\frac{3}{4}$ and $\gamma = \bigT{k^{-1}}$ when $\alpha > \frac{3}{4}$.
+More precisely, there exists constants $Q_{\alpha,\nu}$ depending on $\alpha$ and $\nu$, such that as $k \to \infty$, $\gamma(k) \sim Q_{\alpha,\nu} k^{2 - 4\alpha}$ if $\frac{1}{2} < \alpha < \frac{3}{4}$, $\gamma(k) \sim Q_{\alpha,\nu} \log(k) k^{-1} $ if $\alpha=\frac{3}{4}$ and $\gamma = Q_{\alpha,\nu} k^{-1}$ when $\alpha > \frac{3}{4}$.
 These results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale with $k^{-1}$ as we let $k$ grow.
@@
 
-\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering and helpful discussions.
+\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model and his helpful insights during discussions of the topic.
 

### 2019-05-28 proof_overview_finite_k.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

@@
 In the standard KPKVB random graph $G(n;\alpha,\nu)$ we take $u_1,\dots, u_n$ as our vertex set and add edges between points at hyperbolic distance at most $R = 2\log(n/\nu)$.
-In the {\em Poissonized} KPKVB random graph $\GPo := \GPo(n;\alpha,\nu)$, we instead take $N\isd \Po(n)$, a Poisson random variable
+In the \emph{Poissonized} KPKVB random graph $\GPo := \GPo(n;\alpha,\nu)$, we instead take $N\isd \Po(n)$, a Poisson random variable
 with mean $n$, independent of our i.i.d.~sequence of points and let the vertex set be $u_1,\dots, u_N$ and add edges 
@@
 	\BallHyp{p} := 
-	%\left\{p^\prime := \Psi(u) \, : \, u \in \Dcal_{R_n} \text{ and } d_\H(\Psi^{-1}(p),u) \le R_n\right\}.
+	%\left\{p^\prime := \Psi(u) \, : \, u \in \Dcal_{R} \text{ and } d_\H(\Psi^{-1}(p),u) \le R\right\}.
 	\Psi\left[ \left\{ u \in \Haa : 
@@
 \end{lemma}
+
+\begin{remark}[Notion convention for points]
+We will often be working with the finite box graph $\GPo$ or the infinite graph $\Ginf$, whose nodes are points in $\R \times \R_+$.
+For any point $p \in \R \times \R_+$ we will always use $p = (x,y)$.
+When considering different points $p,p^\prime \in \R \times \R_+$, we will use primed coordinates to refer to $p^\prime$, i.e.
+$p^\prime = (x^\prime ,y^\prime)$, and similar with subscripts, i.e.
+$p_i = (x_i,y_i)$.
+\end{remark}
 

### 2019-05-28 proofs_finite_k.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

@@
 \begin{lemma}\label{lem:n1}
-Let $N_1(H)$ denote the number of vertices with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model $\GPo$. Then $\E N_1(H) = o(n)$.%If $H \rightarrow \infty$, 
+Let $N_1(H)$ denote the number of vertices with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model $\GPo$. Then $\Exp{N_1(H)} = o(n)$.%If $H \rightarrow \infty$, 
 %For all $\epsilon >0$, there is $H_\epsilon$ such that for all $H\geq H_\epsilon$, it holds that $\E N_1(H) \leq \epsilon n$.
@@
 \begin{align*}
-\E N_1(H) = n \frac{\cosh(\alpha(R-H))-1}{\cosh(\alpha R) -1} = (1+o(1)) n e^{-\alpha H} = o(n)
+\Exp{N_1(H)} = n \frac{\cosh(\alpha(R-H))-1}{\cosh(\alpha R) -1} = (1+o(1)) n e^{-\alpha H} = o(n)
 \end{align*}
@@
 Let $N_2(H)$ denote the number of vertices with at least one neighbour with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model.
-If $H \rightarrow \infty$, then $\E N_2(H) = o(n)$.
+If $H \rightarrow \infty$, then $\Exp{N_2(H)} = o(n)$.
 \end{lemma}
@@
 Since $H \rightarrow \infty$ we also have that $H_0 = \log H \rightarrow \infty$.
-Hence by Lemma~\ref{lem:n1}, the expected number of vertices with radial coordinate at most $R-H_0$ (in particular those vertices among them with at least one neighbour with radial coordinate at most $R-H$), $\E N_1(H_0) = o(n)$ is sublinear.
+Hence by Lemma~\ref{lem:n1}, the expected number of vertices with radial coordinate at most $R-H_0$ (in particular those vertices among them with at least one neighbour with radial coordinate at most $R-H$), $\Exp{ N_1(H_0) = o(n)}$ is sublinear.
 For a vertex with radial coordinate at least $R-H_0$, the probability that it has a neighbour with radial coordinate at most $R-H$, tends to zero.
@@
 
-By Lemma~\ref{lem:n1}, we have that $\E X_1 = \E X_3 = o(n)$ and by Lemma~\ref{lem:n2}, we have that $\E X_2 = o(n)$.
+By Lemma~\ref{lem:n1}, we have that $\Exp{ X_1} = \Exp{ X_3} = o(n)$ and by Lemma~\ref{lem:n2}, we have that $\Exp{ X_2} = o(n)$.
 We conclude that $\E |c(k;\GPo)-c(k;\GPoH)| = o(1)$.
-From this, convergence in probability follows by Markov's inequality: for $\epsilon >0$, $\Pee(|c(k;\GPo)-c(k;\GPoH)| \geq \epsilon) \leq \frac{\E|c(k;\GPo)-c(k;\GPoH)|}{\epsilon} = o(1)$.
+From this, convergence in probability follows by Markov's inequality: for $\epsilon >0$,
+\[
+	\Pee(|c(k;\GPo)-c(k;\GPoH)| \geq \epsilon) \leq \frac{\E|c(k;\GPo)-c(k;\GPoH)|}{\epsilon} = o(1).
+\]
 \end{proof}
@@
 \begin{align*}
-\E X = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) \mu(dv) = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy.
+\Exp{ X} = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) \mu(dv) = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy.
 \end{align*}
@@
 \begin{align*}
-\E X = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy.
+\Exp{ X} = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy.
 \end{align*}
@@
 \begin{align*}
-\E X \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
+\Exp{X} \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
 \end{align*}
 Note that for $X^2$, the summation can be split into off-diagonal (with $v_1 \not = v_2$) and diagonal (with $v_1=v_2$) terms, i.e. write $X^2 = \frac{1}{n^2}(Y_1+Y_2)$ where 
-$$Y_1 = \sum_{v_1 \not = v_2 \in V(G_{box,H})} h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)$$ and $Y_2 = \sum_{v_1 \in V(G_{box,H})} h(V(G_{box,H}),v_1)^2$.
-As $h \leq 1$, $Y_2 \leq n X\leq n$ and so, $\E Y_2 \leq n$, we have by the Campbell-Mecke formula,
+\[
+	Y_1 = \sum_{v_1 \not = v_2 \in V(G_{box,H})} h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2),
+\] 
+and $Y_2 = \sum_{v_1 \in V(G_{box,H})} h(V(G_{box,H}),v_1)^2$. As $h \leq 1$, $Y_2 \leq n X\leq n$ and so, $\E Y_2 \leq n$, we have by the Campbell-Mecke formula,
 \begin{align*}
-\E Y_1 = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)]\mu(dv_1)\mu(dv_2).
+\Exp{Y_1} = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)]\mu(dv_1)\mu(dv_2).
 \end{align*}
@@
 \begin{align*}
-\E Y_1 &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)\\
+\Exp{ Y_1} &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)\\
 &\qquad+\int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|\leq2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
@@
 \end{align*}
-It follows that $\E X^2 = (1+o(1))(\E X)^2$, which implies $Var(X) \rightarrow 0$ using that $\E X$ tends to a constant (see above). We conclude
-$$X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.$$
+It follows that $\Exp{ X^2} = (1+o(1))\Exp{ X}^2$, which implies $Var(X) \rightarrow 0$ using that $\Exp{ X}$ tends to a constant (see above). We conclude
+\[
+	X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
+\]
 In a similar way, by the Campbell-Mecke formula,
 \begin{align*}
-\E Z =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy.
+\Exp{Z} =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy.
 \end{align*}
@@
 \begin{align*}
-\E Z \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
+\Exp{ Z} \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
 \end{align*}
@@
 \begin{align*}
-\E Z \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
+\Exp{ Z} \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
 \end{align*}
@@
 \end{align*}
-Therefore, $\Pee(|c(G_n)-\gamma|\geq \epsilon) \leq \Prob{\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta} \rightarrow 0$ because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$.
-%p_k =  = \Theta(k^{-(2\alpha +1)})
+Therefore, 
+\[
+	\Prob{|c(G_n)-\gamma|\geq \epsilon} \leq \Prob{\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta} \rightarrow 0,
+\] 
+because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that 
+\[
+	\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k.
+\]
 \end{proofof}

### 2019-05-28 proofs_infinite_k.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

@@
 \begin{remark}[Diverging $k_n$]
-Throughout the remainder of this paper, unless stated otherwise, $\{k_n\}_{n \ge 1}$ will always denote a sequence of integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
+Throughout the remainder of this paper, unless stated otherwise, $\{k_n\}_{n \ge 1}$ will always denote a sequence of non-negative integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
 \end{remark}

### 2019-05-28 transition.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

@@
 
-Recall that $\Gbox$ is obtained by restricting the Poisson point process $\PPP$ to the box $\Rcal = (-I_n, I_n] \times (0, R_n]$, with $I_n = \frac{\pi}{2} e^{R_n/2}$ and connecting two points $p_1, p_2 \in \Rcal$ if and only if $|x_1 - x_2|_{\pi e^{R_n/2}} \le e^{(y_1 + y_2)/2}$.
-We also recall that by definition of the norm $|.|_{\pi e^{R_n/2}}$ the left and right boundaries of $\Rcal$ are identified.
+Recall that $\Gbox$ is obtained by restricting the Poisson point process $\PPP$ to the box $\Rcal = (-I_n, I_n] \times (0, R]$, with $I_n = \frac{\pi}{2} e^{R/2}$ and connecting two points $p_1, p_2 \in \Rcal$ if and only if $|x_1 - x_2|_{\pi e^{R/2}} \le e^{(y_1 + y_2)/2}$.
+We also recall that by definition of the norm $|.|_{\pi e^{R/2}}$ the left and right boundaries of $\Rcal$ are identified.
 See Section~\ref{ssec:finite_model} for more details.
@@
 Therefore, to establish the required result we need to compute the asymptotic difference between triangle counts in both models.
-
-%\TM{ This last bit of the sentence is already contained in the fact we us $|.|_{\pi e^{R_n/2}}$.
+To keep notation concise we write $|\cdot|_n$ for the norm $|\cdot|_{\pi e^{R/2}}$.
+
+%\TM{ This last bit of the sentence is already contained in the fact we us $|.|_{\pi e^{R/2}}$.
 To me it does not add anything, except possibly confusion.
@@
 %\[
-%	\phi_n(y) = \bigT{e^{-(\alpha - \frac{1}{2})(R_n - y)}},
+%	\phi_n(y) = \bigT{e^{-(\alpha - \frac{1}{2})(R - y)}},
 %\]
-%as $R_n - y \to \infty$.
-Since $e^{y/2} = \bigT{k_n} = \smallO{e^{R_n}}$ as $n \to \infty$, uniformly on $\Kcal_C(k_n)$, it follows that $\phi_n(y) = \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}$, uniformly on $\Kcal_C$.
+%as $R - y \to \infty$.
+Since $e^{y/2} = \bigT{k_n} = \smallO{e^{R}}$ as $n \to \infty$, uniformly on $\Kcal_C(k_n)$, it follows that $\phi_n(y) = \bigT{k_n^{2\alpha - 1} n^{-(2\alpha - 1)}}$, uniformly on $\Kcal_C$.
 This yields the following useful corollary to Lemma~\ref{lem:average_degree_P_n}.
@@
 \]
-Here we slightly abuse notation and write $\BallPo{y}$ for $\BallPo{(0,y)}$. We will adopt this notational convention throughout the remainder of this section, to keep notation concise.
+Here we slightly abuse notation and write $\BallPo{y}$ for $\BallPo{(0,y)}$.
+We will adopt this notational convention throughout the remainder of this section, to keep notation concise.
+We further write $\Nbox(k)$ to denote the number of vertices with degree $k$ in $\Gbox$.
 
@@
 
-To analyze $T_{\text{box}}(y_0) - T_\infty(y_0)$ we first reiterate that the difference between the indicator $\ind{p_1 \in \BallPon{p}}$ in the finite box model and $\ind{p_1 \in \BallPo{p}}$ is that in $\Gbox$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R_n/2}, \frac{\pi}{2} e^{R_n/2}]$ and we stop at height $y = R_n$.
+To analyze $T_{\text{box}}(y_0) - T_\infty(y_0)$ we first reiterate that the difference between the indicator $\ind{p_1 \in \BallPon{p}}$ in the finite box model and $\ind{p_1 \in \BallPo{p}}$ is that in $\Gbox$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2} e^{R/2}]$ and we stop at height $y = R$.
 This induces a difference in triangle counts between both models.
-To see this, note that for any $p = (x,y)$ with $0 \le y \le R_n$ we have that $\BallPon{p} = \BallPo{p} \cap \Rcal$.
+To see this, note that for any $p = (x,y)$ with $0 \le y \le R$ we have that $\BallPon{p} = \BallPo{p} \cap \Rcal$.
 This means that if $p^\prime, p_2 \in \BallPon{p}$ and $p_2 \in \BallPo{p^\prime} \cap \Rcal$ then $p_2 \in \BallPon{p} \cap \BallPon{p^\prime}$ and hence $(p,p^\prime,p_2)$ form a triangle both in $\Gbox$ and $\Ginf$.
@@
 
-\TM{ in the 1st integral we could have restricted to the ball of $p$, and possibly saved a lot.
+%\TM{ in the 1st integral we could have restricted to the ball of $p$, and possibly saved a lot.
 Does that not help?
@@
 	&\le \left(\int_{\Rcal^\prime} \ind{p_1 \in \BallPo{p_0}} f(x_1,y_1) \dd x_1 \dd y_1\right)^2
-		= \bigO{\left(e^{y/2} \int_{R_n}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}\\
-	&= \bigO{e^{y} e^{-(2\alpha-1)R_n}} = \bigO{e^y n^{-(4\alpha - 2)}}.
+		= \bigO{\left(e^{y/2} \int_{R}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}\\
+	&= \bigO{e^{y} e^{-(2\alpha-1)R}} = \bigO{e^y n^{-(4\alpha - 2)}}.
 \end{align*}
@@
 	b_p^-(z) &= \begin{cases}
-		2 \log\left(x-z\right) - y &\mbox{if }  -\frac{\pi}{2} e^{R_n/2} \le z \le x - e^{y/2}  \\
-		2\log\left(\pi e^{R_n/2} + x - z\right) - y 
-			&\mbox{if } x - e^{(y + R_n)/2} + \pi e^{R_n/2} \le z \le \frac{\pi}{2} e^{R_n/2}\\
+		2 \log\left(x-z\right) - y &\mbox{if }  -\frac{\pi}{2} e^{R/2} \le z \le x - e^{y/2}  \\
+		2\log\left(\pi e^{R/2} + x - z\right) - y 
+			&\mbox{if } x - e^{(y + R)/2} + \pi e^{R/2} \le z \le \frac{\pi}{2} e^{R/2}\\
 		0 &\mbox{otherwise}
@@
 	b_p^+(z) &= \begin{cases}
-		2 \log\left(z-x\right) - y &\mbox{if } x + e^{y/2} \le z \le \frac{\pi}{2} e^{R_n/2} \\
-		2\log\left(\pi e^{R_n/2} + z - x\right) - y 
-			&\mbox{if } -\frac{\pi}{2} e^{R_n/2} \le z \le x + e^{(y + R_n)/2} - \pi e^{R_n/2}\\
+		2 \log\left(z-x\right) - y &\mbox{if } x + e^{y/2} \le z \le \frac{\pi}{2} e^{R/2} \\
+		2\log\left(\pi e^{R/2} + z - x\right) - y 
+			&\mbox{if } -\frac{\pi}{2} e^{R/2} \le z \le x + e^{(y + R)/2} - \pi e^{R/2}\\
 		0 &\mbox{otherwise}
@@
 Let us derive the expressions for the coordinates of these two points, starting with $(x^\ast(p^\prime), y^\ast(p^\prime))$.
-The $x$-coordinate $x^\ast(p^\prime)$ is the solution to the equation $b_{p^\prime}^+(z) = b_{p^\prime}^-(z)$ for $-\frac{\pi}{2} e^{R_n/2} \le z \le x + e^{(y + R_n)/2} - \pi e^{R_n/2}$.
+The $x$-coordinate $x^\ast(p^\prime)$ is the solution to the equation $b_{p^\prime}^+(z) = b_{p^\prime}^-(z)$ for $-\frac{\pi}{2} e^{R/2} \le z \le x + e^{(y + R)/2} - \pi e^{R/2}$.
 This equation becomes
 \[
-	2\log\left(\pi e^{R_n/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x^\prime-z\right) - y^\prime,
-\]
-whose solution is $x^\ast(p^\prime) := x^\prime - \frac{\pi}{2} e^{R_n/2}$.
-Plugging this into either the left or right hand side of the above equation yields the $y$-coordinate $y^\ast(p^\prime) = 2\log\left(\frac{\pi}{2}e^{R_n/2}\right) - y^\prime$.
-In a similar way, the $x$-coordinate $\hat{x}(p,p^\prime)$ is the solution to the equation $b_{p^\prime}^+(z) = b_{p}^-(z)$ for $-\frac{\pi}{2} e^{R_n/2} \le z \le x + e^{(y + R_n)/2} - \pi e^{R_n/2}$, i.e.
-\[
-	2\log\left(\pi e^{R_n/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x-z\right) - y.
-\] 
-This solution is $\frac{x^\prime - \pi e^{R_n/2}}{1 + e^{(y^\prime - y)/2}}$ and again $\hat{y}(p,p^\prime)$ is obtained by plugging the solution into either the left or right hand side of the equation, yielding $\hat{y}(p,p^\prime) = 2 \log\left(\frac{\pi e^{R_n/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)$.
+	2\log\left(\pi e^{R/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x^\prime-z\right) - y^\prime,
+\]
+whose solution is $x^\ast(p^\prime) := x^\prime - \frac{\pi}{2} e^{R/2}$.
+Plugging this into either the left or right hand side of the above equation yields the $y$-coordinate $y^\ast(p^\prime) = 2\log\left(\frac{\pi}{2}e^{R/2}\right) - y^\prime$.
+In a similar way, the $x$-coordinate $\hat{x}(p,p^\prime)$ is the solution to the equation $b_{p^\prime}^+(z) = b_{p}^-(z)$ for $-\frac{\pi}{2} e^{R/2} \le z \le x + e^{(y + R)/2} - \pi e^{R/2}$, i.e.
+\[
+	2\log\left(\pi e^{R/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x-z\right) - y.
+\] 
+This solution is $\frac{x^\prime - \pi e^{R/2}}{1 + e^{(y^\prime - y)/2}}$ and again $\hat{y}(p,p^\prime)$ is obtained by plugging the solution into either the left or right hand side of the equation, yielding $\hat{y}(p,p^\prime) = 2 \log\left(\frac{\pi e^{R/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)$.
 
@@
 \begin{align*}
-	x^\ast(p^\prime) &= x^\prime - \frac{\pi}{2} e^{R_n/2}\\
-	y^\ast(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{R_n/2}\right) - y^\prime\\
-	\hat{x}(p,p^\prime) &= \frac{x^\prime - \pi e^{R_n/2}}{1 + e^{(y^\prime - y)/2}} \\
-	\hat{y}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R_n/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)
+	x^\ast(p^\prime) &= x^\prime - \frac{\pi}{2} e^{R/2}\\
+	y^\ast(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{R/2}\right) - y^\prime\\
+	\hat{x}(p,p^\prime) &= \frac{x^\prime - \pi e^{R/2}}{1 + e^{(y^\prime - y)/2}} \\
+	\hat{y}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)
 \end{align*}
@@
 \[
-	2\log\left(\frac{\pi}{2}e^{R_n/2}\right) - y^\prime = 2\log\left(\frac{\pi}{2} e^{R_n/2} -x^\prime\right) - y.
+	2\log\left(\frac{\pi}{2}e^{R/2}\right) - y^\prime = 2\log\left(\frac{\pi}{2} e^{R/2} -x^\prime\right) - y.
 \]
@@
 \begin{equation}
-	b^\ast_p(z) = y - 2\log\left(1 - \frac{z}{\frac{\pi}{2} e^{R_n/2}}\right),
+	b^\ast_p(z) = y - 2\log\left(1 - \frac{z}{\frac{\pi}{2} e^{R/2}}\right),
 \end{equation}
@@
 \begin{equation}\label{eq:clustering_error_T_main}
-	\int_0^{R_n}\int_0^{I_n} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) f(x_1,y_1) 
+	\int_0^{R}\int_0^{I_n} \mu\left(\mathcal{T}(p,p_1)\right) f(x_1,y_1) 
 	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
@@
 The proof goes in two stages.
-First we compute $\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right)$ by splitting it over three disjoint regimes with respect to $p_1$, with $x_1 \ge 0$.
+First we compute $\mu\left(\mathcal{T}(p,p_1)\right)$ by splitting it over three disjoint regimes with respect to $p_1$, with $x_1 \ge 0$.
 Then we do the integration with respect to $p_1$.
 
-\subsubsection*{Computing $\bm{\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right)}$}
-
-Recall that $I_n = \frac{\pi}{2} e^{R_n/2}$ and define the sets
+\subsubsection*{Computing $\bm{\mu\left(\mathcal{T}(p,p_1)\right)}$}
+
+Recall that $I_n = \frac{\pi}{2} e^{R/2}$ and define the sets
 \begin{align*}
@@
 
-With these definitions we have that the union $B_n := \bigcup_{i = 1}^n B_n^{(i)}$ denotes the area under the red curve in Figure~\ref{fig:comparing_triangles_diff_analysis} and hence, for all $p_1 \in \Rcal\setminus B_n$ with $x_1 \ge 0$ we have that $\mathcal{T}(p,p^\prime)(p,p_1) = \emptyset$.
+With these definitions we have that the union $B_n := \bigcup_{i = 1}^n B_n^{(i)}$ denotes the area under the red curve in Figure~\ref{fig:comparing_triangles_diff_analysis} and hence, for all $p_1 \in \Rcal\setminus B_n$ with $x_1 \ge 0$ we have that $\mathcal{T}(p,p_1) = \emptyset$.
 So we only need to consider $p_1 \in B_n$.
@@
 \begin{equation}\label{eq:mu_triangle_diff}
-	\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) = 
+	\mu\left(\mathcal{T}(p,p_1)\right) = 
 	\begin{cases}
@@
 
-Depending on which set $p_1$ belongs to, the set $\mathcal{T}(p,p^\prime)(p,p_1)$ has a different shape.
+Depending on which set $p_1$ belongs to, the set $\mathcal{T}(p,p_1)$ has a different shape.
 We displayed these shapes in Figure~\ref{fig:shapes_triangle_mismatches} as a visual aid to follow the computations below.
@@
 
-    \draw node at (-\r-0.2,\hh+0.1) {\color{blue}$(-\frac{\pi}{2} e^{R_n/2}, h_1(p^\prime))$};
-    \draw node at (-\r-0.2,\hhh-0.1) {$(-\frac{\pi}{2} e^{R_n/2}, h_2(p^\prime))$};
-    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p^\prime), y^\ast(p^\prime))$};
+    \draw node at (-\r-0.2,\hh+0.1) {\color{blue}$(-\frac{\pi}{2} e^{R/2}, h_1(p_1))$};
+    \draw node at (-\r-0.2,\hhh-0.1) {$(-\frac{\pi}{2} e^{R/2}, h_2(p_1))$};
+    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p_1), y^\ast(p_1))$};
+
+    \draw node at (\uuast-2,\vvast) {$\bm{p_1 \in B^{(1)}_n}$};
 
@@
 
-    \draw node (f2) at (\uuast-0.3,\hh+0.1) {\color{blue}$b_{p^\prime}^-(z)$};
-    \draw node (f3) at (\uuast-0.3,\hhh) {\color{blue}$b_{p^\prime}^+(z)$};
+    \draw node (f2) at (\uuast-0.3,\hh+0.1) {\color{blue}$b_{p_1}^-(z)$};
+    \draw node (f3) at (\uuast-0.3,\hhh) {\color{blue}$b_{p_1}^+(z)$};
     \path (f2)+(230:0.35) node (f2_arrow) {};
@@
 
-    \draw node at (-\r-0.2,\hh+0.1) {\color{blue}$(-\frac{\pi}{2} e^{R_n/2}, h_1(p^\prime))$};
-    \draw node at (-\r-0.2,\hp-0.1) {$(-\frac{\pi}{2} e^{R_n/2}, h(y))$};
-    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p^\prime), y^\ast(p^\prime))$};
-    \draw node at (\uast,\vast-0.1) {$(\hat{x}(p,p^\prime), \hat{y}(p, p^\prime))$};
+    \draw node at (-\r-0.2,\hh+0.1) {\color{blue}$(-\frac{\pi}{2} e^{R/2}, h_1(p_1))$};
+    \draw node at (-\r-0.2,\hp-0.1) {$(-\frac{\pi}{2} e^{R/2}, h(y))$};
+    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p_1), y^\ast(p_1))$};
+    \draw node at (\uast,\vast-0.1) {$(\hat{x}(p,p_1), \hat{y}(p, p_1))$};
+
+    \draw node at (\uuast-2,\vvast) {$\bm{p_1 \in B^{(2)}_n}$};
 
@@
     \draw node (f1) at (-\r-0.05,\hhh) {$b_p^-(z)$};
-    \draw node (f2) at (\uast+0.5,\hh+0.1) {\color{blue}$b_{p^\prime}^-(z)$};
-    \draw node (f3) at (\uuast-0.3,\hhh) {\color{blue}$b_{p^\prime}^+(z)$};
+    \draw node (f2) at (\uast+0.5,\hh+0.1) {\color{blue}$b_{p_1}^-(z)$};
+    \draw node (f3) at (\uuast-0.3,\hhh) {\color{blue}$b_{p_1}^+(z)$};
     \path (f1)+(45:0.35) node (f1_arrow) {};
@@
 
-    \draw node at (\utilde,\vtilde+0.1) {\color{black}$(\tilde{x}(p,p^\prime), \tilde{y}(p,p^\prime))$};
-    \draw node at (\uast,\vast-0.1) {$(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$};
-    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p^\prime), y^\ast(p^\prime))$};
-
-    \draw node at (\uuast-0.45,\vvast+0.07) {$\mathcal{I}_n^{(2)}$};
-    \draw node at (\uast+0.025,\vvast-0.045) {$\mathcal{I}_n^{(1)}$};
+    \draw node at (\utilde,\vtilde+0.1) {\color{black}$(\tilde{x}(p,p_1), \tilde{y}(p,p_1))$};
+    \draw node at (\uast,\vast-0.1) {$(\hat{x}(p,p_1), \hat{y}(p,p_1))$};
+    \draw node at (\uuast+0.2,\vvast+0.1) {\color{blue}$(x^\ast(p_1), y^\ast(p_1))$};
+
+   \draw node at (\uuast-2,\vvast) {$\bm{p_1 \in B^{(3)}_n}$};
+
+    \draw node at (\uuast-0.45,\vvast+0.07) {$\mathcal{I}_n^{(1)}$};
+    \draw node at (\uast+0.025,\vvast-0.045) {$\mathcal{I}_n^{(2)}$};
 
     \draw node (f1) at (\uast-0.7,\vast-0.1) {\color{black}$b_{p}^-(z)$};
-    \draw node (f2) at (\uuast-0.2,\vvast+0.5) {\color{blue}$b_{p^\prime}^-(z)$};
-    \draw node (f3) at (\uast+0.5,\vast+0.025) {\color{blue}$b_{p^\prime}^+(z)$};
+    \draw node (f2) at (\uuast-0.2,\vvast+0.5) {\color{blue}$b_{p_1}^-(z)$};
+    \draw node (f3) at (\uast+0.5,\vast+0.025) {\color{blue}$b_{p_1}^+(z)$};
     \path (f1)+(45:0.35) node (f1_arrow) {};
@@
 \end{tikzpicture}
-\caption{The different shapes of $\mathcal{T}(p,p^\prime)(p,p_1)$ depending on the regime to which $p_1$ belongs.
+\caption{The different shapes of $\mathcal{T}(p,p_1)$ depending on the regime to which $p_1$ belongs.
 The top figure is for $p_1 \in B_n^{(1)}$, the middle for $p_1 \in B_n^{(2)}$ and the bottom one for $p_1 \in B_n^{(3)}$.}
@@
 
-\paragraph{Regime 1: $0 \le y_1 \le y - 2\log(I_n/(I_n-x_1))$}
+\paragraph{Case $p_1 \in B_n^{(1)}$: $0 \le y_1 \le y - 2\log(I_n/(I_n-x_1))$}
 
@@
 \[
-	\left(\left(1 - \frac{x_1}{I_n}\right)^{-(2\alpha - 1)}-1\right) = \bigO{\frac{x^\prime}{I_n}} \quad 
+	\left(\left(1 - \frac{x_1}{I_n}\right)^{-(2\alpha - 1)}-1\right) = \bigO{\frac{x_1}{I_n}} \quad 
 	\text{as } n \to \infty.
@@
 \[
-	\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}},
+	\mu\left(\mathcal{T}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y_1}},
 \]
@@
 
-\paragraph{Regime 2: $y - 2\log(I_n/(I_n-x_1)) < y_1 \le y + 2 \log\left(1 + \frac{x_1}{I_n}\right)$}
+\paragraph{Case $p_1 \in B_n^{(2)}$: $y - 2\log(I_n/(I_n-x_1)) < y_1 \le y + 2 \log\left(1 + \frac{x_1}{I_n}\right)$}
 
@@
 
-For the second part we first compute that 
+For the second part we first us the upper bound on $y_1$ to compute that 
 \begin{align*}
 	x_1 + e^{(y_1+y_2)/2} - 2 I_n + e^{(y + y_2)/2} &\le \left(e^{y/2} + e^{y_1/2}\right)e^{y_2/2}\\
-	&\le e^{y/2}\left(1 + \frac{I_n}{I_n - e^y}\right)e^{y_2/2} = \bigO{e^{(y+y_2)/2}},
-\end{align*}
-since $y \in \Kcal_{C}(k_n)$ and $k_n = \smallO{\sqrt{n}}$, so that $e^y = \smallO{n} = \smallO{I_n}$. 
-Then we have
+	&\le e^{y/2}\left(2 + \frac{x_1}{I_n}\right)e^{y_2/2} = \bigO{e^{(y+y_2)/2}},
+\end{align*}
+since $|x_1| \le I_n$. Then we have
 \begin{align*}
@@
 \[
-	\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) = \bigO{I_n^{-(2\alpha-1)} e^{\alpha y}}.
-\]
-
-\paragraph{Regime 3:}
+	\mu\left(\mathcal{T}(p,p_1)\right) = \bigO{I_n^{-(2\alpha-1)} e^{\alpha y}}.
+\]
+
+\paragraph{Case $p_1 \in B_n^{(3)}$: $y +2\log(1+x_1/I_n) < y_1 \le y + 2\log(I_n/(I_n-x_1))$}
 
@@
 
-For the second integral we have
+For the second integral we have, using that $y \le y_1$ for $p_1 \in B_n^{(3)}$,
 \begin{align*}
@@
 \begin{align*}
-	\int_{\hat{y}}^{y^\ast}e^{-(\alpha - \frac{1}{2})y_2} \dd y_2
-	&= \frac{2}{2\alpha - 1} \left(e^{-(\alpha - \frac{1}{2})\hat{y}} - e^{-(\alpha - \frac{1}{2})y^\ast}\right)\\
+	&\hspace{-30pt}\int_{\hat{y}}^{y^\ast}e^{-(\alpha - \frac{1}{2})y_2} \dd y_2
+		= \frac{2}{2\alpha - 1} \left(e^{-(\alpha - \frac{1}{2})\hat{y}} - e^{-(\alpha - \frac{1}{2})y^\ast}\right)\\
 	&= \frac{2}{2\alpha - 1}\left(\left(\frac{2I_n - x_1}{e^{y/2} + e^{y_1/2}}\right)^{-(2\alpha - 1)} 
-		- I_n^{-(2\alpha - 1)} e^{-(\alpha - \frac{1}{2})y_1}\right)\\
-	&= \bigO{I_n^{-2\alpha} x_1 e^{-(\alpha - \frac{1}{2})y_1}}
-\end{align*}
-so that
-\[
-	\mathcal{I}_n^{(2)} = \bigO{I_n^{-(2\alpha - 1)} e^{(1-\alpha)y_1}} = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
+		- I_n^{-(2\alpha - 1)} e^{(\alpha - \frac{1}{2})y_1}\right) = \bigO{I_n^{-(2\alpha-1)} e^{(\alpha - \frac{1}{2})y_1}},
+\end{align*}
+where we used the upper bound on $y_1$ and the fact that $2I_n - x_1 = \bigT{I_n}$ for all $x_1 \in [-I_n,I_n]$. We conclude that
+\[
+	\mathcal{I}_n^{(2)} = \bigO{I_n^{-(2\alpha-1)} x_1 e^{\alpha y}}
 \]
@@
 \[
-	\mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
+	\mu\left(\mathcal{T}(p,p_1)\right) = \bigO{I_n^{-2\alpha} x_1 e^{\alpha y}}
 	= \bigO{I_n^{-(2\alpha - 1)} e^{\alpha y}}.
@@
 
-\subsubsection*{Integration over $p_1$}
+\subsubsection*{Integration $\mu(\mathcal{T}(p,p_1))$ with respect to $p_1$}
 
@@
 \[
-	B_n^{(3)} = \left\{(x_1, y_1) \, : \, y \le y_1 \le R_n, \,\,
+	B_n^{(3)} = \left\{(x_1, y_1) \, : \, y \le y_1 \le R, \,\,
 	I_n\left(1 - e^{(y - y_1)/2}\right) \le x_1 \le I_n\left(e^{(y_1 - y)/2} - 1\right) \wedge e^{(y + y_1)/2} \wedge I_n \right\}.
@@
 
-We these characterizations of the areas we now integrate $\mu(\mathcal{T}(p,p^\prime))(p,p_1)$ over $B_n$, splitting the computations over the three different areas.
-
-\paragraph{$\bm{p_1 \in B_n^{(1)}}:$}
+We these characterizations of the areas we now integrate $\mu(\mathcal{T}(p,p_1))$ over $B_n$, splitting the computations over the three different areas.
+
+\paragraph{Integration over $\bm{B_n^{(1)}}:$}
 
@@
 \begin{align*}
-	&\hspace{-30pt}\int_{B_n^{(1)}} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) 
+	&\hspace{-30pt}\int_{B_n^{(1)}} \mu\left(\mathcal{T}(p,p_1)\right) 
 		f(x_1,y_1)	\dd x_1 \dd y_1 \\
-	&\le  \int_0^y \int_0^{I_n(1-e^{(y_1-y)/2})} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) 
+	&\le  \int_0^y \int_0^{I_n(1-e^{(y_1-y)/2})} \mu\left(\mathcal{T}(p,p_1)\right) 
 		f(x_1,y_1) \dd x_1 \dd y_1\\
@@
 
-\paragraph{$\bm{p_1 \in B_n^{(2)}}:$}
+\paragraph{Integration over $\bm{B_n^{(2)}}:$}
 
@@
 \begin{align*}
-	\int_{B_n^{(2)}} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) 
+	\int_{B_n^{(2)}} \mu\left(\mathcal{T}(p,p_1)\right) 
 		f(x_1,y_1)	\dd x_1 \dd y_1
@@
 
-\paragraph{$\bm{p_1 \in B_n^{(3)}}:$}
+\paragraph{Integration over $\bm{B_n^{(3)}}:$}
 
@@
 \begin{align*}
-	\int_{B_n^{(3)}} \mu\left(\mathcal{T}(p,p^\prime)(p,p_1)\right) 
+	\int_{B_n^{(3)}} \mu\left(\mathcal{T}(p,p_1)\right) 
 		f(x_1,y_1)	\dd x_1 \dd y_1
@@
 		f(x_1,y_1) \dd x_1 \dd y_1\\
-	&\hspace{10pt}+ \int_{h(y)}^{R_n} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n}
+	&\hspace{10pt}+ \int_{h(y)}^{R} \int_{I_n(1-e^{(y-y_1)/2})}^{I_n}
 		f(x_1,y_1) \dd x_1 \dd y_1.

### 2019-05-28 proofs_infinite_k.tex
commented out the in-text-comments

@@
 
-\TM{ Maybe we could replace these three with a statement on $|c(k_n;G_n) - c^\ast(k_n; \Gbox)|$, at least at this point of the paper.
+%\TM{ Maybe we could replace these three with a statement on $|c(k_n;G_n) - c^\ast(k_n; \Gbox)|$, at least at this point of the paper.
 This is only the high level description and that is all we need for the ``final proof".}\PvdH{I would vote for keeping them split, since this allows us to clearly point to the main technical challenge we have to overcome to obtain the final result.}
@@
 
-\TM{ ``concentration'' is a loaded term in probability.
+%\TM{ ``concentration'' is a loaded term in probability.
 I am not sure this use of the word will not be counterintuitive to many.

### 2019-10-02 concentration_argument.tex
updated Lemma 6.8 and 6.9

@@
 
-%Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(B_\Pcal(y)) = \xie^{\frac{y}{2}}$. 
-%We will consider two different types of sequences $\{k_n\}_{n \ge 1}$, those that are asymptotically bounded and those that diverge. We define
-%\begin{equation}\label{eq:def_kappa_n}
-%	\kappa_n := \begin{cases}
-%		\log(n) &\mbox{if } k_n = \bigT{1},\\
-%		\sqrt{k_n \log(k_n)} &\mbox{if } k_n = \omega(1).
-%	\end{cases}
-%\end{equation}
-%\TM{ This is not a good definition.
-There are sequences that neither stay bounded nor tend to infinity, e.q.~odd values equal to 2 even values equal to $\log n$.
-How do you decide for a given $k_n$ which of the two cases you pick.
-To solve this we could either restrict to sequences that are either a) constant or b) tending to infinity; or we could make a cut-off at some specific, slow growing function such as $\log\log\log n$.
-}\PvdH{You are right, I overlooked this fact.
-I would opt to go with the setting where we consider only sequences that are either asymptotically bounded or tend to infinity.
-After the new proves are added we can see where we specify this.}
-
-%Where we recall that $a \vee b = \max\{a,b\}$ and $a \wedge b = \min\{a,b\}$.
-
 The next lemma states that for a large class of functions $h(y)$ and $k_n \to \infty$, to compute the integral 
@@
 \]
-%\TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal$. Is this really meant?
-%I would have expected we just integrate wrt.~$y$ and replace $f_{\alpha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}\PvdH{I understand this confusion and agree that your suggestion makes more sense here.
-However, I choose this setup to minimize notations later.
-I am for changing the setup to what you are suggesting but I will have to spend some time first on checking how that will effect the definitions in later sections.}
 it is enough to consider integration over a small interval on which $e^{y/2} \approx k_n$, instead of $\R_+$.
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} = 1.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \left|\Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} \dd y^\prime  - 1\right| = 0.
 \]
@@
 \begin{proof}
-Recall that $\Mu{\BallPo{0,y}} = \xi e^{y/2}$ where $\xi = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$. Using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} we have 
+Recall that $\Mu{\BallPo{0,y}} = \xi e^{y/2}$ where $\xi = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$ and that by Lemma~\ref{lem:asymptotics_Omega_hyperbolic}
+\[
+	\left|\Phi(y,y^\prime) - e^{\frac{y+y^\prime}{2}}\right| \le K e^{\frac{3}{2}(y+y^\prime) - R},
+\]
+for all $y + y^\prime < R$. Also,
+\[
+	\Mu{\BallPo{y}} = \frac{2 \nu \alpha}{\pi}\int_0^\infty e^{\frac{y + y^\prime}{2}} e^{-\alpha y^\prime} \dd y^\prime. 
+\]
+
+Therefore we have 
 \begin{align*}
-	\frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} 
-	&\le \frac{2\nu \alpha}{\pi} \int_{0}^{(1-\delta)(R-y)} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R}\right)
+	&\left|\Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} 
+		\dd y^\prime  - 1\right|\\
+	&= \frac{1}{\Mu{\BallPo{y}}}\left|\frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) 
+		e^{-\alpha y^\prime} \dd y^\prime 
+		- \frac{2\nu \alpha}{\pi} \int_0^\infty e^{\frac{y + y^\prime}{2}} e^{-\alpha y^\prime} \dd y^\prime\right|\\
+	&\le \frac{2\nu \alpha}{\pi \Mu{\BallPo{y}}} \int_0^{(1-\delta)(R-y)}\left|\Phi(y,y^\prime) - 
+		e^{\frac{y + y^\prime}{2}} \right| e^{-\alpha y^\prime} \dd y^\prime
+		+ \frac{2\nu \alpha}{\pi \Mu{\BallPo{y}}} \int_{(1-\delta)(R-y)}^\infty e^{\frac{y + y^\prime}{2}} 
 		e^{-\alpha y^\prime} \dd y^\prime\\
-	&= \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(1-\delta)(R - y)}\right) \\
-	&\hspace{10pt}+ \frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
+	&\le \frac{2 K \nu \alpha}{\pi \Mu{\BallPo{y}}} e^{\frac{3}{2}y - R} \int_0^{(1-\delta)(R-y)} 	
+		e^{(\frac{3}{2}-\alpha)y^\prime} \dd y^\prime +  e^{-(\alpha-\frac{1}{2})(1-\delta)(R-y)}.
 \end{align*}
-
-We first compute the integral, which depends on the value of $\alpha$,
+%\begin{align*}
+%	\frac{2\nu \alpha}{\pi} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime) e^{-\alpha y^\prime} 
+%	&\le \frac{2\nu \alpha}{\pi} \int_{0}^{(1-\delta)(R-y)} \left(e^{\frac{y + y^\prime}{2}} + K e^{\frac{3}{2}(y + y^\prime) - R}\right)
+%		e^{-\alpha y^\prime} \dd y^\prime\\
+%	&= \Mu{\BallPo{0,y}}\left(1 - e^{-(\alpha - \frac{1}{2})(1-\delta)(R - y)}\right) \\
+%	&\hspace{10pt}+ \frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime
+%\end{align*}
+For the last term it holds that
+\[
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R}  e^{-(\alpha-\frac{1}{2})(1-\delta)(R-y)} = 0.
+\]
+We first compute the integral in the first term, which depends on the value of $\alpha$,
 \[
@@
 \]
-Therefore we get
+This implies that
 \begin{align*}
-	&\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}
+	&\frac{2 K \nu \alpha}{\pi \Mu{\BallPo{y}}} e^{\frac{3 y}{2} - R}
 		\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime\\
-	&= \Mu{\BallPo{0,y}}\begin{cases}
+	&= \begin{cases}
 		\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R - y)-(\frac{3}{2}-\alpha)\delta(R-y)} 
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1}
-	\frac{2\nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}
-			\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime = 0.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R}
+	\frac{2 K \nu \alpha}{\pi \Mu{\BallPo{y}}} e^{\frac{3 y}{2} - R}
+			\int_0^{(1-\delta)(R-y)} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime = 0,
 \]
-Since $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} e^{-(\alpha - \frac{1}{2})(1-\delta)(R - y)} = 0$, we conclude that
-\[
-	\limsup_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \int_0^{(1-\delta)(R-y)} \Phi(y,y^\prime)
-		\alpha e^{-\alpha y^\prime} = 1.
-\]
-The proof that this also holds for the limit infimum immediately follows, by observing that the only difference with the above computations is the change of sign in front of 
-\[
-	\frac{2 \nu \alpha}{\pi} K e^{\frac{3 y}{2} - R}\int_0^{R-y} e^{(\frac{3}{2} - \alpha)y^\prime} \dd y^\prime.
-\]
+which completes the proof.
 \end{proof}
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}} = 1.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \left|\frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}} - 1\right| = 0.
 \]
-%Let $\eps \in (0, 1)$. Then for all $0 \le y \le (1 - \eps)R$
-%\[
-%	 1 - \phi_{\H,n}^{(1)}(y) - \phi_{\H,n}^{(2)}(y) \le \frac{\Mu{\BallHyp{0,y}}}{\Mu{\BallPo{0,y}}} 
-%	 \le 1 - \phi_{\H,n}^{(1)}(y) + \phi_{\H,n}^{(2)}(y),
-%\]
-%where
-%\[
-%	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 1 - 4\pi}{4\pi} e^{-(\alpha - \frac{1}{2})(R - y)} 
-%		+ \left(\alpha - \frac{1}{2}\right)\pi e^{-(\alpha - \frac{1}{2})R - y/2},
-%\]
-%and
-%\[
-%	\phi_{\H,n}^{(2)}(y) = 
-%	+ \begin{cases}
-%			\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R - y)} - e^{-(R - y)}\right)
-%			&\mbox{if } 1/2 < \alpha < 3/2,\\
-%			\frac{(2\alpha -1)K}{2} (R - y)e^{-(R - y)} &\mbox{if } \alpha = 3/2,\\
-%			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R - y)} - e^{-(\alpha - \frac{1}{2})(R - y)}\right)
-%			&\mbox{if } \alpha > 3/2,
-%		\end{cases}
-%\]
-%with $K$ being the constant coming from the approximation of $\Phi$ in Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
-%%\TM{ We want to say in the lemma where $K$ comes from. (not everyone reads surrounding text, or reads linearly, in a paper as long as this one.) }
 \end{lemma}
@@
 \begin{proof}
-We perform the computation of $\Mu{\BallHyp{0,y}}$ by splitting the integration with respect to the height $y^\prime$ into the cases $y^\prime > R - y$ and $y^\prime \le R - y$,
+We perform the computation of $\Mu{\BallHyp{y}}$ by splitting the integration with respect to the height $y^\prime$ into the cases $y^\prime > R - y$ and $y^\prime \le R - y$,
 \[
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1}
-	\Mu{\BallHyp{(0,y)} \cap\Rcal[(0,R-y)]} = 1.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \left|
+	\frac{\Mu{\BallHyp{(y)} \cap\Rcal[(0,R-y)]}}{\Mu{\BallPo{y}}} - 1\right| = 0.
 \]
 
-For the second part we observer that $\BallHyp{(0,y)} \cap \Rcal ([R - y, R])= \Rcal([R-y,R])$. 
+For the second part we observer that $\BallHyp{(y)} \cap \Rcal ([R - y, R])= \Rcal([R-y,R])$. 
 Thus, 
 \begin{align*}
-	&\hspace{-30pt}\Mu{\BallHyp{(0,y)} \cap \Rcal ([R - y, R])} \\
+	&\hspace{-30pt}\Mu{\BallHyp{(y)} \cap \Rcal ([R - y, R])} \\
 	&= \int_{R - y}^{R} \int_{I_n} f_{\alpha,\nu}(x^\prime, y^\prime) \dd x^\prime \dd y^\prime
 		= \nu \alpha e^{R/2}\left(e^{-\alpha(R - y)} - e^{-\alpha R}\right)\\
-	&= \Mu{\BallPo{0,y}} \frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R - y)}
+	&= \Mu{\BallPo{y}} \frac{2\alpha - 1}{4\pi} \left( e^{-(\alpha - \frac{1}{2})(R - y)}
 		- e^{-(\alpha - \frac{1}{2})R - y/2}\right), \numberthis \label{eq:mu_hyperbolic_ball_part_1}
@@
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} 
-	\Mu{\BallHyp{(0,y)} \cap \Rcal ([R - y, R])} = 0,
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \frac{\Mu{\BallHyp{(0,y)} \cap \Rcal ([R - y, R])}}{\Mu{\BallPo{y}}} = 0,
 \]

### 2020-01-02 clustering_infinite_model.tex
version 1.6

@@
 
-As mentioned earlier, we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of $\GPo$ with certain quantities associated with $\Ginf$.
-We will be considering the Poisson process $\Pcal$ to which we add one additional point $(0,y)$ on the $y$-axis.
-In some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and independent of $\Pcal$.
-We refer to $(0,y)$ as ``the typical point''.
-
-To provide some intuition for this definition and name, note that we can alternatively view $\Pcal$ as follows. 
-We take a constant intensity Poisson process on $\eR$ corresponding to the $x$-coordinates, and to each point
-we attach a random ``mark'', corresponding to the $y$-coordinate, where the marks are i.i.d.~exponentially distributed with parameter $\alpha$.
+Similar to the proof for the degrees we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of $\GPo$ with certain quantities associated with $\Ginf$.
+Recall that a \emph{typical point} is a point $p_0 = (0,y)$, where in some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and independent of $\Pcal$.
 
@@
 \end{align*}
-
-\subsection{The degree of the typical point\label{ssec:degrees_infinite_model}}
-
-Before considering clustering we briefly investigate the distribution of the degree of the typical point. 
-For $p = (x,y) \in \eR\times[0,\infty)$ we define
-\begin{equation}\label{eq:def_degree_inf_model}
-	\rho(p,k) := \Prob{\Po(\Mu{p}) = k},
-\end{equation}
-where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$. We will often write $\rho(y,k)$ instead of $\rho(p,k)$.
-
-Let the random variable $D$ denote the degree of the typical point.
-Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed, for $k \in \N_0$:
-\begin{equation}\label{eq:def_pk}
-	p_k :=  \Prob{D = k} = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
-\end{equation}
-
-Using the transformation of variables $z = \xi e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
-\begin{align*}
-	p_k
-    &= \frac{1}{k!} \int_0^\infty \left(\xi e^{\frac{y}{2}}\right)^k 
-    	e^{-\xi e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy
-    	= \frac{\alpha \xi^{2\alpha}}{k!} \int_0^\infty 
-    	\left(\xi e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi e^{\frac{y}{2}}}
-        \, dy\\
-    &= \frac{2\alpha \xi^{2\alpha}}{k!} \int_{\xi}^{\infty} 
-    	z^{k -2\alpha-1} e^{-z} \, dz
-    	= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
-\end{align*}
-where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{+}$ the upper incomplete Gamma-function.
-Note that, unsurprisingly, this is identical to the expression Gugelmann et al.~\cite{gugelmann2012random} gave for the limiting degree distribution of $G(n;\alpha,\nu)$.
-Using Stirling's approximation to the gamma function, we find that
-
-\begin{equation}\label{eq:degree_distribution_P_asymptotics}
-	p_k \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha + 1)}
-	\quad \text{as } k \to \infty.
-\end{equation}
-
-By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
-\begin{equation}\label{eq:general_integral_rho_y_k}
-	\int_0^\infty e^{\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
-    \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
-\end{equation}
 
@@
 First we will prove a result that will allow us to limit the values of $y$, when performing the integration.
-For this, fix some $C > 0$ and define
-\[
-	a^\pm(k) = 2 \log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
-\] 
+For this, recall that for any $C > 0$ we defined
+\[
+	y_{k,C}^\pm = 2 \log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
+\] 
+Since $P(y) \le 1$ by the concentration of heights results (Proposition~\ref{prop:concentration_height_general}) we have that
 We will show that, as $k \to \infty$,
@@
 	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	= (1+\smallO{1}) \int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y.
-\end{equation}
-
-To establish~\eqref{eq:asymptotics_average_clustering_concentration} recall that $\mu(y) = \xi e^{\frac{y}{2}}$ and consider $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$ as a function of $y$.
+	= (1+\smallO{1}) \int_{y_{k,C}^-}^{y_{k,C}^+} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y.
+\end{equation}
+
+Note that this implies that if $P(y) = h(y)(1 + \smallO{1})$, uniformly in $y$, as $y \to \infty$, then 
+\begin{equation}\label{eq:asymptotics_average_clustering_error_term}
+	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	\sim \int_0^\infty h(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
+\end{equation}
+as $y \to \infty$.
+
+%To establish~\eqref{eq:asymptotics_average_clustering_concentration} recall that $\mu(y) = \xi e^{\frac{y}{2}}$ and consider $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$ as a function of $y$.
 Then, since $\mu^\prime(y) = \mu(y)/2$, we get that
-\[
-	\frac{\partial \rho(y,k)}{\partial y} = \frac{1}{2}\left(k - \mu(y)\right)\rho(y,k),
-\]
-which implies that $\rho(y,k)$ attains its maximum at $\mu(y) = k$.
+%\[
+%	\frac{\partial \rho(y,k)}{\partial y} = \frac{1}{2}\left(k - \mu(y)\right)\rho(y,k),
+%\]
+%which implies that $\rho(y,k)$ attains its maximum at $\mu(y) = k$.
 Moreover we see that the derivative is strictly positive when $\mu(y) < k$ and strictly negative when $\mu(y) > k$.
@@
 Hence, using that $P(y) \le 1$,
-\begin{align*}
-	&\hspace{-20pt}\int_{\R_+ \setminus [a^-(k), a^+(k)]} P(y) \rho(y,k) 
-		\alpha e^{-\alpha y} \dd y\\
-    &\le \int_0^{a^-(k)} \rho(y,k) \alpha e^{-\alpha y} \dd y 
-    	+ \int_{a^+(k)}^{\infty}\rho(y,k) \alpha e^{-\alpha y}x \dd y \\
-   	&\le \rho(a^-(k),k)\int_0^{a^-(k)} e^{-\alpha y} \, \dd y
-   		+ \rho(a^+(k),k) \int_{a^+(k)}^{\infty} e^{-\alpha y} \, \dd y\\
-   	&= \bigO{1}\left(\rho(a^-(k),k) + \rho(a^+(k),k)\right),
-\end{align*}
-as $k \to \infty$. Next we show that
-\[
-	\rho(a^\pm(k),k) = \bigO{k^{-(1+C^2)/2}}.
-\]
-Since the arguments are almost completely identical, we give the prove for $a^+(k)$.
-
-Using Stirling's formula $k! \sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
-\begin{align*}
-	\rho(a^+(k),k) &= \frac{\mu(a^+(k))^{k}}{k!} e^{-\mu(a^+(k))} \\
-	&\sim (2\pi)^{-1/2} k^{-1/2} \left(\frac{\mu(a^+(k))}{k}\right)^{k} e^{-(\mu(a^+(k) - k)}\\
-	&= (2\pi)^{-1/2} k^{-1/2} 
-		e^{-k\left(\frac{\mu(a^+(k))}{k} - 1 - \log\left(\frac{\mu(a^+(k))}{k}\right)\right)}.
-\end{align*}
-Since, for sufficiently large $k$,
-\[
-	\frac{\mu(a^+(k))}{k} = 1 + C \sqrt{\frac{\log(k)}{k}}
-\]
-and $x - \log(1 + x) \sim x^2/2$ as $x \to 0$, we get 
-\begin{align*}
-	\rho(a^+(k),k) 
-	&\sim \sqrt{2\pi} k^{-1/2} 
-		e^{-k \left(C \sqrt{\frac{\log(k)}{k}} - \log\left(1 + C \sqrt{\frac{\log(k)}{k}}\right)\right)}\\
-	&\sim (2\pi)^{-1/2} k^{-1/2} e^{-\frac{k \left(C \sqrt{\frac{\log(k)}{k}}\right)^2}{2}} \\
-	&= \bigO{k^{-(1+C^2)/2}}.
-\end{align*}
-
-Since $C > 0$ can be chosen arbitrarily large we conclude that
-\[
-	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	= (1+\smallO{1}) \int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
-\]
-as $k \to \infty$. Note that this implies that if $P(y) = h(y)(1 + \smallO{1})$, uniformly in $y$, as $y \to \infty$, then 
-\begin{equation}\label{eq:asymptotics_average_clustering_error_term}
-	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	\sim \int_0^\infty h(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
-\end{equation}
-as $y \to \infty$.
+%\begin{align*}
+%	&\hspace{-20pt}\int_{\R_+ \setminus [a^-(k), a^+(k)]} P(y) \rho(y,k) 
+%		\alpha e^{-\alpha y} \dd y\\
+%    &\le \int_0^{a^-(k)} \rho(y,k) \alpha e^{-\alpha y} \dd y 
+%    	+ \int_{a^+(k)}^{\infty}\rho(y,k) \alpha e^{-\alpha y}x \dd y \\
+%   	&\le \rho(a^-(k),k)\int_0^{a^-(k)} e^{-\alpha y} \, \dd y
+%   		+ \rho(a^+(k),k) \int_{a^+(k)}^{\infty} e^{-\alpha y} \, \dd y\\
+%   	&= \bigO{1}\left(\rho(a^-(k),k) + \rho(a^+(k),k)\right),
+%\end{align*}
+%as $k \to \infty$. Next we show that
+%\[
+%	\rho(a^\pm(k),k) = \bigO{k^{-(1+C^2)/2}}.
+%\]
+%Since the arguments are almost completely identical, we give the prove for $a^+(k)$.
+%
+%Using Stirling's formula $k! \sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
+%\begin{align*}
+%	\rho(a^+(k),k) &= \frac{\mu(a^+(k))^{k}}{k!} e^{-\mu(a^+(k))} \\
+%	&\sim (2\pi)^{-1/2} k^{-1/2} \left(\frac{\mu(a^+(k))}{k}\right)^{k} e^{-(\mu(a^+(k) - k)}\\
+%	&= (2\pi)^{-1/2} k^{-1/2} 
+%		e^{-k\left(\frac{\mu(a^+(k))}{k} - 1 - \log\left(\frac{\mu(a^+(k))}{k}\right)\right)}.
+%\end{align*}
+%Since, for sufficiently large $k$,
+%\[
+%	\frac{\mu(a^+(k))}{k} = 1 + C \sqrt{\frac{\log(k)}{k}}
+%\]
+%and $x - \log(1 + x) \sim x^2/2$ as $x \to 0$, we get 
+%\begin{align*}
+%	\rho(a^+(k),k) 
+%	&\sim \sqrt{2\pi} k^{-1/2} 
+%		e^{-k \left(C \sqrt{\frac{\log(k)}{k}} - \log\left(1 + C \sqrt{\frac{\log(k)}{k}}\right)\right)}\\
+%	&\sim (2\pi)^{-1/2} k^{-1/2} e^{-\frac{k \left(C \sqrt{\frac{\log(k)}{k}}\right)^2}{2}} \\
+%	&= \bigO{k^{-(1+C^2)/2}}.
+%\end{align*}
+%
+%Since $C > 0$ can be chosen arbitrarily large we conclude that
+%\[
+%	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+%	= (1+\smallO{1}) \int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
+%\]
+%as $k \to \infty$.
 

### 2020-01-02 concentration.tex
version 1.6

@@
 
-\subsection{Joint neighbourhoods and degrees in $\Gbox$}
-
-To prove Proposition~\ref{prop:concentration_tilde_T_P_n} we need to understand the joint degree distribution in $\Gbox$.
-This subsequently requires us to analyse the joint neighbourhoods in $\Gbox$ of two points $p, p^\prime \in \Rcal$.
-We start with a general result for near independent Poisson random variables.
-
-\begin{lemma}\label{lem:near_independence_poisson}
-Let $k_n \to \infty$ and $X_1 = \Po(\lambda_1(n))$, $X_2 = \Po(\lambda_2(n))$ and $Y = \Po(\lambda_3(n))$, be three Poisson random variables where $\lambda_3(n) = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$ and for some $C > 0$,
-\[
-	k_n - C\sqrt{k_n \log(k_n)} \le \lambda_i(n) + \lambda_3(n) \le k_n + C\sqrt{k_n \log(k_n)},
-\] 
-for $i = 1,2$.Then, as $n \to \infty$
-\[
-	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} = (1+\smallO{1}) \Prob{X_1 + Y = k_n}\Prob{X_2 + Y = k_n}.
-\]
-\end{lemma}
-
-\begin{proof}
-First we write
-\begin{align*}
-	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
-	&= \sum_{t = 0}^\infty \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}.
-\end{align*}
-Now fix a $C_1 > 0$ and define the set
-\[
-	A_n := \left\{t \in \R_+ \, : \, \lambda_3(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \le t 
-	\le \lambda_3(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \right\}.
-\]
-Then by a Chernoff bound (c.f. \eqref{eq:def_chernoff_bound_poisson})
-\begin{align*}
-	&\hspace{-20pt}\sum_{t \in \R_+ \setminus A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
-	&\le \Prob{Y > \lambda_3(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
-		+ \Prob{Y < \lambda_3(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}}\\
-	&= \Prob{\left|\Po(\lambda_3(n)) - \lambda_3(n)\right| > C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
-		\le 2 k_n^{-\frac{C_1}{4}}.
-\end{align*}
-and hence
-\[
-	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
-	= \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} + \bigO{k_n^{-(1+C_1^2)/2}}.
-\]
-Next, for $i=1,2$ we have by assumption on $\lambda_i(n) + \lambda_3(n)$ that
-\begin{align*}
-	\Prob{X_i + Y = k_n} &\ge \frac{\left(k_n + C\sqrt{k_n \log(k_n)}\right)^{k_n}}{k_n!} 
-		e^{-\left(k_n + C\sqrt{k_n \log(k_n)}\right)}\\
-	&\ge e^{-1} k_n^{-1/2} \left(1 + C\sqrt{\frac{\log(k_n)}{k_n}}\right)^{k_n} e^{-C\sqrt{k_n \log(k_n)}}\\
-	&\ge e^{-1} k_n^{-1/2} e^{k_n \log\left(1 + C\sqrt{\frac{\log(k_n)}{k_n}}\right) -C\sqrt{k_n \log(k_n)}}\\
-	&\ge e^{-1} k_n^{-1/2} e^{ -\frac{C^2}{2} \log(k_n)} = e^{-1} k_n^{-\frac{1+C^2}{2}}.
-\end{align*}
-where we also used that $\log(1+x) \ge x - x^2/2$, for $0\le x \le 1$ and $k_n!
+\subsection{Joint degrees in $\Gbox$}
+
+%\begin{lemma}\label{lem:near_independence_poisson}
+%Let $k_n \to \infty$ and $X_1 = \Po(\lambda_1(n))$, $X_2 = \Po(\lambda_2(n))$ and $Y = \Po(\lambda_3(n))$, be three Poisson random variables where $\lambda_3(n) = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$ and for some $C > 0$,
+%\[
+%	k_n - C\sqrt{k_n \log(k_n)} \le \lambda_i(n) + \lambda_3(n) \le k_n + C\sqrt{k_n \log(k_n)},
+%\] 
+%for $i = 1,2$.Then, as $n \to \infty$
+%\[
+%	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} = (1+\smallO{1}) \Prob{X_1 + Y = k_n}\Prob{X_2 + Y = k_n}.
+%\]
+%\end{lemma}
+
+%\begin{proof}
+%First we write
+%\begin{align*}
+%	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
+%	&= \sum_{t = 0}^\infty \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}.
+%\end{align*}
+%Now fix a $C_1 > 0$ and define the set
+%\[
+%	A_n := \left\{t \in \R_+ \, : \, \lambda_3(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \le t 
+%	\le \lambda_3(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)} \right\}.
+%\]
+%Then by a Chernoff bound (c.f. \eqref{eq:def_chernoff_bound_poisson})
+%\begin{align*}
+%	&\hspace{-20pt}\sum_{t \in \R_+ \setminus A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
+%	&\le \Prob{Y > \lambda_3(n) + C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
+%		+ \Prob{Y < \lambda_3(n) - C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}}\\
+%	&= \Prob{\left|\Po(\lambda_3(n)) - \lambda_3(n)\right| > C_1\sqrt{k_n^{1-\varepsilon}\log(k_n)}} 
+%		\le 2 k_n^{-\frac{C_1}{4}}.
+%\end{align*}
+%and hence
+%\[
+%	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} 
+%	= \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} + \bigO{k_n^{-(1+C_1^2)/2}}.
+%\]
+%Next, for $i=1,2$ we have by assumption on $\lambda_i(n) + \lambda_3(n)$ that
+%\begin{align*}
+%	\Prob{X_i + Y = k_n} &\ge \frac{\left(k_n + C\sqrt{k_n \log(k_n)}\right)^{k_n}}{k_n!} 
+%		e^{-\left(k_n + C\sqrt{k_n \log(k_n)}\right)}\\
+%	&\ge e^{-1} k_n^{-1/2} \left(1 + C\sqrt{\frac{\log(k_n)}{k_n}}\right)^{k_n} e^{-C\sqrt{k_n \log(k_n)}}\\
+%	&\ge e^{-1} k_n^{-1/2} e^{k_n \log\left(1 + C\sqrt{\frac{\log(k_n)}{k_n}}\right) -C\sqrt{k_n \log(k_n)}}\\
+%	&\ge e^{-1} k_n^{-1/2} e^{ -\frac{C^2}{2} \log(k_n)} = e^{-1} k_n^{-\frac{1+C^2}{2}}.
+%\end{align*}
+%where we also used that $\log(1+x) \ge x - x^2/2$, for $0\le x \le 1$ and $k_n!
 \ge e \sqrt{k_n} k_n^{k_n} e^{-k_n}$.
@@
 It remains to show that
-\begin{align*}
-	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
-	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n}.
-\end{align*}
-
-For this take any $s \in A_n$ so that $|t-s| \le 2 C_1 \sqrt{k_n^{1-\varepsilon}\log(k_n)}$ and note that there exists a $\delta_n$ satisfying $|\delta_n| \le 2C \sqrt{k_n \log(k_n)}$, for $n$ large enough, such that $k_n - t = \lambda_1(n) + \delta_n$.
+%\begin{align*}
+%	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
+%	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n}.
+%\end{align*}
+%
+%For this take any $s \in A_n$ so that $|t-s| \le 2 C_1 \sqrt{k_n^{1-\varepsilon}\log(k_n)}$ and note that there exists a $\delta_n$ satisfying $|\delta_n| \le 2C \sqrt{k_n \log(k_n)}$, for $n$ large enough, such that $k_n - t = \lambda_1(n) + \delta_n$.
 It then follows that, uniformly in $t,s$ and $\delta_n$, as $n \to \infty$
-\begin{align*}
-	\frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - s}}
-	&= \frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - t - (s - t)}}\\
-	&= \frac{(k_n - t - (s-t))!}{(k_n - t)!} \lambda_1(n)^{s - t} \\
-	&\sim (k_n - t - (s-t))^{-(s-t)} \lambda_1(n)^{s-t} \\
-	&= \left(\lambda_1(n) + \delta_n - (s-t)\right)^{-(s-t)}\lambda_1(n)^{s-t}\\
-	&= \left(1 + \frac{\delta_n -(s-t)}{\lambda_1(n)}\right)^{s-t}\\
-	&\sim e^{\frac{(s-t)\delta_n}{\lambda_1(n)}} e^{-\frac{(s-t)^2}{\lambda_1(n)}} \sim 1,
-\end{align*}
-where the last line follows since both $\frac{(s-t)\delta_n}{\lambda_1(n)} \to 0$ and $\frac{(s-t)^2}{\lambda_1(n)} \to 0$ as $n \to \infty$. In particular,
-\[
-	\Prob{X_2 = k_n - t} = (1+\smallO{1}) \Prob{X_2 = k_n - s},
-\] 
-uniformly for all $t, s \in A_n$ and therefore, since
-\[
-	1 = \sum_{s = 0}^\infty \Prob{Y = s} = (1+\smallO{1}) \sum_{s \in A_n} \Prob{Y = s},
-\]
-we conclude that
-\begin{align*}
-	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
-	&= (1+\smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} \sum_{s \in A_n} \Prob{Y = s}\\
-	&= (1 + \smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{Y = t} 
-		\sum_{s \in A_n} \Prob{X_2 = k_n - s} \Prob{Y = s}\\
-	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n},
-\end{align*}
-from which the result follows.
-\end{proof}
-
-To see how this lemma can be applied to analyze the joint degree distribution in $\Gbox$, fix two points $p,p^\prime \in \Rcal$ and denote by 
-\begin{equation}\label{eq:def_joint_degree_distribution}
+%\begin{align*}
+%	\frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - s}}
+%	&= \frac{\Prob{X_2 = k_n - t}}{\Prob{X_2 = k_n - t - (s - t)}}\\
+%	&= \frac{(k_n - t - (s-t))!}{(k_n - t)!} \lambda_1(n)^{s - t} \\
+%	&\sim (k_n - t - (s-t))^{-(s-t)} \lambda_1(n)^{s-t} \\
+%	&= \left(\lambda_1(n) + \delta_n - (s-t)\right)^{-(s-t)}\lambda_1(n)^{s-t}\\
+%	&= \left(1 + \frac{\delta_n -(s-t)}{\lambda_1(n)}\right)^{s-t}\\
+%	&\sim e^{\frac{(s-t)\delta_n}{\lambda_1(n)}} e^{-\frac{(s-t)^2}{\lambda_1(n)}} \sim 1,
+%\end{align*}
+%where the last line follows since both $\frac{(s-t)\delta_n}{\lambda_1(n)} \to 0$ and $\frac{(s-t)^2}{\lambda_1(n)} \to 0$ as $n \to \infty$. In particular,
+%\[
+%	\Prob{X_2 = k_n - t} = (1+\smallO{1}) \Prob{X_2 = k_n - s},
+%\] 
+%uniformly for all $t, s \in A_n$ and therefore, since
+%\[
+%	1 = \sum_{s = 0}^\infty \Prob{Y = s} = (1+\smallO{1}) \sum_{s \in A_n} \Prob{Y = s},
+%\]
+%we conclude that
+%\begin{align*}
+%	&\hspace{-20pt}\sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t}\\
+%	&= (1+\smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{X_2 = k_n - t}\Prob{Y = t} \sum_{s \in A_n} \Prob{Y = s}\\
+%	&= (1 + \smallO{1}) \sum_{t \in A_n} \Prob{X_1 = k_n - t}\Prob{Y = t} 
+%		\sum_{s \in A_n} \Prob{X_2 = k_n - s} \Prob{Y = s}\\
+%	&= (1 + \smallO{1}) \Prob{X_1 + Y = k_n} \Prob{X_2 + Y = k_n},
+%\end{align*}
+%from which the result follows.
+%\end{proof}
+
+To prove Proposition~\ref{prop:concentration_tilde_T_P_n} will use results from Section~\ref{ssec:joint_degrees_GPo} regarding the joint degree distribution in $\Gbox$.
+For any two points $p,p^\prime \in \Rcal$ we will denote by
+\begin{equation}\label{eq:def_joint_degree_distribution_2}
 	\rho_{\text{box}}(p,p^\prime,k,k^\prime) 
@@
 \end{equation}
-the joint degree distribution. Then if we define,
-\begin{align*}
-	X_1(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p}\setminus \BallPon{p^\prime}}\right),\\
-	X_2(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p^\prime}\setminus \BallPon{p}}\right),\\
-	Y(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p} \cap \BallPon{p^\prime}}\right)
-\end{align*}
-it follows that
-\[
-	\rho_{\text{box}}(p,p^\prime,k_n,k_n) = \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k_n, X_2(p,p^\prime) + Y(p,p^\prime) = k_n}.
-\]
-Now, if $y,y^\prime \in \Kcal_{C}(k_n)$ the three Poisson random variables defined above satisfy the condition of Lemma~\ref{lem:near_independence_poisson} regarding the sum $\lambda_i(n) + \lambda_3(n)$.
+the joint degree distribution.
+
+%hen if we define,
+%\begin{align*}
+%	X_1(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p}\setminus \BallPon{p^\prime}}\right),\\
+%	X_2(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p^\prime}\setminus \BallPon{p}}\right),\\
+%	Y(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p} \cap \BallPon{p^\prime}}\right)
+%\end{align*}
+%it follows that
+%\[
+%	\rho_{\text{box}}(p,p^\prime,k_n,k_n) = \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k_n, X_2(p,p^\prime) + Y(p,p^\prime) = k_n}.
+%\]
+%Now, if $y,y^\prime \in \Kcal_{C}(k_n)$ the three Poisson random variables defined above satisfy the condition of Lemma~\ref{lem:near_independence_poisson} regarding the sum $\lambda_i(n) + \lambda_3(n)$.
 Therefore, if in addition $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$, we have that
-\[
-	\rho_{\text{box}}(p,p^\prime,k_n,k_n) = (1+\smallO{1})\rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n). 
-\]
-
-To make this more precise, we define, for any $0 < \varepsilon < 1$, the following set
-\begin{equation}\label{eq:def_joint_degree_set_E_growing_k}
-	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
-		\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}, 
-\end{equation}
-where $|x|_n = \min\{|x|, \pi e^{R/2} - |x|\}$ denotes the norm on the finite box $\Rcal$ where the left and right boundaries are identified.
+%\[
+%	\rho_{\text{box}}(p,p^\prime,k_n,k_n) = (1+\smallO{1})\rho_{\text{box}}(p,k_n)\rho_{\text{box}}(p^\prime,k_n). 
+%\]
+%
+%To make this more precise, we define, for any $0 < \varepsilon < 1$, the following set
+%\begin{equation}\label{eq:def_joint_degree_set_E_growing_k}
+%	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
+%		\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}, 
+%\end{equation}
+%where $|x|_n = \min\{|x|, \pi e^{R/2} - |x|\}$ denotes the norm on the finite box $\Rcal$ where the left and right boundaries are identified.
 We will show (see Corollary~\ref{cor:expected_common_neighbours_Ecal_set}) that for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ it holds that $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$ and hence the joint degree distribution factorizes on this set.
@@
 
-\subsubsection*{Common neighbourhoods}
-
-Let $p, p^\prime \in \Rcal$ and denote by
-%Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbours of $p$ and $p^\prime$ in $\Gbox$, i.e.
+%\subsubsection*{Common neighbourhoods}
+%
+%Let $p, p^\prime \in \Rcal$ and denote by
+%%Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbours of $p$ and $p^\prime$ in $\Gbox$, i.e.
 those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection.
 In addition we denote by
-$\Ncal_{\text{box}}(p,p^\prime)$ the number of common neighbours of $p$ and $p^\prime$.
+%$\Ncal_{\text{box}}(p,p^\prime)$ the number of common neighbours of $p$ and $p^\prime$.
 We shall establish an upper bound on the expected number of joint neighbours when $p$ and $p^\prime$ are sufficiently separated.
 Observe that $\Exp{\Ncal_{\text{box}}(p,p^\prime)} = \Mu{\BallPon{p} \cap \BallPon{p^\prime}}$.
-
-%as well as an asymptotic expression for the expected number points in the joint neighbourhood.
+%
+%%as well as an asymptotic expression for the expected number points in the joint neighbourhood.
 For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large.
 Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n}-\ref{fig:representation_disjoint_neighbourhoods_P_n_3} show the different situations that occur.
-%
-%\begin{figure}[p]
+%%
+%%\begin{figure}[p]
+%%\centering
+%%\begin{tikzpicture}
+%%	
+%%	%The box \Rcal
+%%	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
+%%
+%%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
+%%    \draw node at (-0.2,0.7) {$p$};
+%%    
+%%    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (1,0.5) {};
+%%    \draw node at (0.8,0.2) {\color{blue}$p^\prime$};
+%%	
+%%	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
+%%    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
+%%    \draw[domain=2.2840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-1)-0.5});
+%%    \draw[domain=-0.2840:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(1-\x)-0.5});
+%%    
+%%    \draw[dashed,thick,black,line width=1pt] (-6,2.5835) -- (6,2.5835);
+%%    
+%%    \draw node at (-7,2.5835) {$h(y)$};
+%%    \draw node at (-7,3.3918) {\color{blue}$h_1(p^\prime)$};
+%%    \draw node at (7,2.7189) {\color{blue}$h_2(p^\prime)$};
+%%    
+%%    \draw node at (-4,3.5) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
+%%    \draw node at (4.5,3) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
+%%    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
+%%    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+%%
+%%\end{tikzpicture}
+%%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbours_P_n} and Lemma~\ref{lem:common_neighbours_Pcal_n}.}
+%%\label{fig:representation_disjoint_neighbourhoods_P_n}
+%%\end{figure}~
+%%\begin{figure}[p]
+%%\centering
+%%\begin{tikzpicture}
+%%	
+%%	%The box \Rcal
+%%	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
+%%
+%%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
+%%    \draw node at (-0.2,0.7) {$p$};
+%%    
+%%    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (2.5,0.5) {};
+%%    \draw node at (2.3,0.2) {\color{blue}$p^\prime$};
+%%	
+%%	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
+%%    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
+%%    \draw[domain=3.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-2.5)-0.5});
+%%    \draw[domain=1.2160:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(2.5-\x)-0.5});
+%%    \draw[domain=0:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+9.5)-0.5});
+%%    
+%%    \draw[dashed,black,line width=1pt] (-6,2.0055) -- (6,2.0055);
+%%    
+%%%    \draw node at (-7,2.5835) {$h(y)$};
+%%    \draw node at (-7,3.7801) {\color{blue}$h_1(p^\prime)$};
+%%    \draw node at (7,2.0055) {\color{blue}$h_2(p^\prime)$};
+%%    
+%%%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
+%%%    \draw[dotted,thick,black] (4.5208,2.0174) -- (6,2.0174);
+%%    
+%%%    \draw node at (4.5208,-0.5) {$w_x(p,p^\prime)$};
+%%%    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};
+%%    
+%%    \draw node at (0,3.5) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
+%%    \draw node at (-2,1.6) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
+%%    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
+%%    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+%%
+%%\end{tikzpicture}
+%%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbours_P_n} and Lemma~\ref{lem:common_neighbours_Pcal_n}.}
+%%\label{fig:representation_disjoint_neighbourhoods_P_n_2}
+%%\end{figure}~
+%
+%\begin{figure}[!ht]
 %\centering
@@
 %	
+%
+%	\pgfmathsetmacro{\u}{0} %0
+%	\pgfmathsetmacro{\v}{1} %1
+%	\pgfmathsetmacro{\uu}{4.5} %1.4
+%	\pgfmathsetmacro{\vv}{0.5} %0.8
+%	\pgfmathsetmacro{\r}{6}
+%	\pgfmathsetmacro{\t}{4}
+%	
 %	%The box \Rcal
-%	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
-%
-%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
-%    \draw node at (-0.2,0.7) {$p$};
-%    
-%    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (1,0.5) {};
-%    \draw node at (0.8,0.2) {\color{blue}$p^\prime$};
+%	\draw[line width=1pt] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);
+%	
+%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (\u,\v) {};
+%    \draw node at (-0.2,1.3) {$p$};
+%    
+%    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (\uu,\vv) {};
+%    \draw node at (4.3,0.2) {\color{blue}$p^\prime$};
 %	
@@
 %    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
-%    \draw[domain=2.2840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-1)-0.5});
-%    \draw[domain=-0.2840:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(1-\x)-0.5});
-%    
-%    \draw[dashed,thick,black,line width=1pt] (-6,2.5835) -- (6,2.5835);
-%    
-%    \draw node at (-7,2.5835) {$h(y)$};
-%    \draw node at (-7,3.3918) {\color{blue}$h_1(p^\prime)$};
-%    \draw node at (7,2.7189) {\color{blue}$h_2(p^\prime)$};
-%    
-%    \draw node at (-4,3.5) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
-%    \draw node at (4.5,3) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
-%    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
-%    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
-%
-%\end{tikzpicture}
-%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x-x^\prime| \le e^{\frac{y + y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbours_P_n} and Lemma~\ref{lem:common_neighbours_Pcal_n}.}
-%\label{fig:representation_disjoint_neighbourhoods_P_n}
-%\end{figure}~
-%\begin{figure}[p]
-%\centering
-%\begin{tikzpicture}
-%	
-%	%The box \Rcal
-%	\draw[line width=1pt] (-6,0) -- (6,0) -- (6,4) -- (-6,4) -- (-6,0);
-%
-%    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (0,1) {};
-%    \draw node at (-0.2,0.7) {$p$};
-%    
-%    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (2.5,0.5) {};
-%    \draw node at (2.3,0.2) {\color{blue}$p^\prime$};
-%	
-%	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
-%    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
-%    \draw[domain=3.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-2.5)-0.5});
-%    \draw[domain=1.2160:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(2.5-\x)-0.5});
-%    \draw[domain=0:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+9.5)-0.5});
-%    
-%    \draw[dashed,black,line width=1pt] (-6,2.0055) -- (6,2.0055);
-%    
-%%    \draw node at (-7,2.5835) {$h(y)$};
-%    \draw node at (-7,3.7801) {\color{blue}$h_1(p^\prime)$};
-%    \draw node at (7,2.0055) {\color{blue}$h_2(p^\prime)$};
-%    
+%    \draw[domain=5.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-4.5)-0.5});
+%    \draw[domain=3.2160:-5,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(4.5-\x)-0.5});
+%    \draw[domain=2:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+7.5)-0.5});
+%    
+%    
+%    
+%    \draw [decorate,decoration={brace},line width=1pt] (3.2160,-0.1) -- (1.6487,-0.1);
+%    \draw node at (2.5,-0.45) {$d(p,p^\prime)$};
+%    
+%%    \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
+%%    \draw node at (2.5298,2) {$\hat{x}(p,p^\prime)$};
+%    
+%    %Define intersection left black and shifted blue curve
+%    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
+%    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1+exp((\vv-\v)/2))}
+%    %Define intersection right black and left blue curve
+%    \pgfmathsetmacro{\vvast}{2*ln((\uu)/(exp(\v/2) + exp(\vv/2)))}
+%    \pgfmathsetmacro{\uuast}{(\u*exp(\vv/2) + \uu*exp(\v/2))/(exp(\v/2) + exp(\vv/2))}
+%    \pgfmathsetmacro{\h}{2*ln(\r)-\v}
 %%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
@@
 %    
-%    \draw node at (0,3.5) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
-%    \draw node at (-2,1.6) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
-%    \draw node at (-4.5,1) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
-%    \draw node at (2,1.5) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+%    \draw node at (\r+0.5,\h) {$h(y)$};
+%    
+%    \draw node at (2.3,3.6) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
+%    \draw node at (-1,2) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
+%    \draw node at (-4.5,2.9) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
+%    \draw node at (4.5,2.9) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
+%	
+%	
+%	\draw[dashed,black,line width=1pt] (-\r,\vast) -- (\uast,\vast);
+%	\draw node at (-\r-1,\vast) {\color{black}$\hat{y}_{\text{left}}(p,p^\prime)$};
+%	\draw[dashed,line width=1pt] (\uast,\vast) -- (\uast,0);
+%	\draw node at (\uast,-0.5) {$\hat{x}_{\text{left}}(p,p^\prime)$};
+%
+%	\draw[dashed,black,line width=1pt] (-\r,\vvast) -- (\r,\vvast);
+%	\draw node at (\r+1,\vvast) {\color{black}$\hat{y}_{\text{right}}(p,p^\prime)$};
+%	\draw[dashed,line width=1pt] (\uuast,\vvast) -- (\uuast,\vvast+1);
+%	\draw node at (\uuast,\vvast+1.2) {$\hat{x}_{\text{right}}(p,p^\prime)$};
+%	
 %	
 %\end{tikzpicture}
-%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $e^{\frac{y + y^\prime}{2}} < |x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma~\ref{lem:disjoint_neighbours_P_n} and Lemma~\ref{lem:common_neighbours_Pcal_n}.}
-%\label{fig:representation_disjoint_neighbourhoods_P_n_2}
-%\end{figure}~
-
-\begin{figure}[!ht]
-\centering
-\begin{tikzpicture}
-
-	\pgfmathsetmacro{\u}{0} %0
-	\pgfmathsetmacro{\v}{1} %1
-	\pgfmathsetmacro{\uu}{4.5} %1.4
-	\pgfmathsetmacro{\vv}{0.5} %0.8
-	\pgfmathsetmacro{\r}{6}
-	\pgfmathsetmacro{\t}{4}
-
-	%The box \Rcal
-	\draw[line width=1pt] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);
-
-    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (\u,\v) {};
-    \draw node at (-0.2,1.3) {$p$};
-
-    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (\uu,\vv) {};
-    \draw node at (4.3,0.2) {\color{blue}$p^\prime$};
-
-	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
-    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
-    \draw[domain=5.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-4.5)-0.5});
-    \draw[domain=3.2160:-5,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(4.5-\x)-0.5});
-    \draw[domain=2:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+7.5)-0.5});
-
-    \draw [decorate,decoration={brace},line width=1pt] (3.2160,-0.1) -- (1.6487,-0.1);
-    \draw node at (2.5,-0.45) {$d(p,p^\prime)$};
-
-%    \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
-%    \draw node at (2.5298,2) {$\hat{x}(p,p^\prime)$};
-
-    %Define intersection left black and shifted blue curve
-    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
-    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1+exp((\vv-\v)/2))}
-    %Define intersection right black and left blue curve
-    \pgfmathsetmacro{\vvast}{2*ln((\uu)/(exp(\v/2) + exp(\vv/2)))}
-    \pgfmathsetmacro{\uuast}{(\u*exp(\vv/2) + \uu*exp(\v/2))/(exp(\v/2) + exp(\vv/2))}
-    \pgfmathsetmacro{\h}{2*ln(\r)-\v}
-%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
-%    \draw[dotted,thick,black] (4.5208,2.0174) -- (6,2.0174);
-
-%    \draw node at (4.5208,-0.5) {$w_x(p,p^\prime)$};
-%    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};
-
-    \draw node at (\r+0.5,\h) {$h(y)$};
-
-    \draw node at (2.3,3.6) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
-    \draw node at (-1,2) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
-    \draw node at (-4.5,2.9) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
-    \draw node at (4.5,2.9) {$x_1 = x + e^{\frac{y + y_1}{2}}$};
-
-	\draw[dashed,black,line width=1pt] (-\r,\vast) -- (\uast,\vast);
-	\draw node at (-\r-1,\vast) {\color{black}$\hat{y}_{\text{left}}(p,p^\prime)$};
-	\draw[dashed,line width=1pt] (\uast,\vast) -- (\uast,0);
-	\draw node at (\uast,-0.5) {$\hat{x}_{\text{left}}(p,p^\prime)$};
-
-	\draw[dashed,black,line width=1pt] (-\r,\vvast) -- (\r,\vvast);
-	\draw node at (\r+1,\vvast) {\color{black}$\hat{y}_{\text{right}}(p,p^\prime)$};
-	\draw[dashed,line width=1pt] (\uuast,\vvast) -- (\uuast,\vvast+1);
-	\draw node at (\uuast,\vvast+1.2) {$\hat{x}_{\text{right}}(p,p^\prime)$};
-
-\end{tikzpicture}
-\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:common_neighbours_Pcal_n}.
+%\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:common_neighbours_Pcal_n}.
 Note that although here $p^\prime \notin \BallPon{p}$, this is not true in general.
 This situation was merely chosen to improve readability of the figure.}
-\label{fig:representation_disjoint_neighbourhoods_P_n_3}
-\end{figure}
-
-We start by analyzing the shape of joint neighbourhood.
+%\label{fig:representation_disjoint_neighbourhoods_P_n_3}
+%\end{figure}
+%
+%
+%We start by analyzing the shape of joint neighbourhood.
 Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$.
@@
 The condition $d(p,p^\prime) > 0$ is exactly the right notion for $p$ and $p^\prime$ being sufficiently separated.
-
-Note that $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$ correspond to, respectively, $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ considered in Section~\ref{ssec:missing_triangles}.
+%
+%Note that $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$ correspond to, respectively, $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ considered in Section~\ref{ssec:missing_triangles}.
 The derivation of $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ is done in a similar manner and we omit the details here.
 The full expressions of all these functions are given below for further reference.
-
-\begin{align}
-	h(y) &= R - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
-	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
-	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R}{2}} - x^\prime\right) - y^\prime 
-		\label{eq:def_height_right_P_n} \\
-%	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
-%		\label{eq:def_x_intersection_close_boundaries}\\
-%	\iota_y(p,p^\prime) &= 2\log\left(\frac{x^\prime - x}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}\right)
-%		\label{eq:def_y_intersection_close_boundaries}\\
-	\hat{y}_{\text{right}}(p,p^\prime) &= 2\log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
-	\hat{x}_{\text{right}}(p,p^\prime) &= \frac{x^\prime}{1 + 	
-		e^{\frac{y^\prime - y}{2}}},\\
-	\hat{y}_{\text{left}}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),\\
-	\hat{x}_{\text{left}}(p,p^\prime) &= \frac{x^\prime - \pi e^{R/2}}{1 + e^{\frac{y^\prime - y}{2}}}, \\
-	d(p,p^\prime) &= |x - x^\prime|_n - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
-	\label{eq:def_d_p_p_prime}
-\end{align}
-
-The following result shows that if $d(p,p^\prime) > 0$, then the expected number of common neighbours is $\smallO{\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}}$.
-
-\begin{lemma}\label{lem:common_neighbours_Pcal_n}
-Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime|_n > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
-\[
-	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)\phi_n(p,p^\prime),
+%
+%\begin{align}
+%	h(y) &= R - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
+%	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
+%	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R}{2}} - x^\prime\right) - y^\prime 
+%		\label{eq:def_height_right_P_n} \\
+%%	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
+%%		\label{eq:def_x_intersection_close_boundaries}\\
+%%	\iota_y(p,p^\prime) &= 2\log\left(\frac{x^\prime - x}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}\right)
+%%		\label{eq:def_y_intersection_close_boundaries}\\
+%	\hat{y}_{\text{right}}(p,p^\prime) &= 2\log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
+%	\hat{x}_{\text{right}}(p,p^\prime) &= \frac{x^\prime}{1 + 	
+%		e^{\frac{y^\prime - y}{2}}},\\
+%	\hat{y}_{\text{left}}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),\\
+%	\hat{x}_{\text{left}}(p,p^\prime) &= \frac{x^\prime - \pi e^{R/2}}{1 + e^{\frac{y^\prime - y}{2}}}, \\
+%	d(p,p^\prime) &= |x - x^\prime|_n - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
+%	\label{eq:def_d_p_p_prime}
+%\end{align}
+%
+%The following result shows that if $d(p,p^\prime) > 0$, then the expected number of common neighbours is $\smallO{\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}}$.
+%
+%\begin{lemma}\label{lem:common_neighbours_Pcal_n}
+%Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime|_n > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
+%\[
+%	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \Mu{\BallPon{p}}
+%	\left(\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}  
+%	+ \frac{\nu}{\xi} e^{-(\alpha - \frac{1}{2})(R-y)}\right).
+%\]
+%\end{lemma}
+%
+%\begin{proof}
+%Again, without loss of generality we assume that $p = p_0 = (0,y)$ and $p^\prime = (x^\prime, y^\prime)$ with $0 \le x^\prime \le \frac{\pi}{2} e^{R/2}$.
+Note that since $0 < x^\prime \le \frac{\pi}{2} e^{R/2}$,$ \hat{y}_{\mathrm{right}}(p,p^\prime) \le \hat{y}_{\mathrm{left}}(p,p^\prime)$.
+We write $\hat{y}$ for $\hat{y}_{\mathrm{right}}(p,p^\prime)$ and observe that below $\hat{y}$ the balls $\BallPon{p}$ and $\BallPon{p^\prime}$ are disjoint.
+Therefore, if we define
+%\begin{align*}
+%	A &:= \left\{p_1 = (x_1,y_1) \in \Rcal \cap \BallPon{p} \, : \, y_1 \ge \hat{y} \right\},
+%\end{align*}
+%then
+%\[
+%	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \Mu{A}.
+%\]
+%We proceed with computing the right hand side
+%\begin{align*}
+%	\Mu{A} &= \int_{\hat{y}}^{h(y)} 
+%		\int_{- e^{\frac{y + y_1}{2}}}^{e^{\frac{y^\prime+y_1}{2}}} 
+%		f(x_1,y_1) \dd x_1 \dd y_1
+%		+ \int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{R/2}}^{\frac{\pi}{2} e^{R/2}} 
+%		\hspace{-10pt}  f(x_1,y_1) \dd x_1 \dd y_1 \\
+%	&= \frac{2\alpha \nu}{\pi}e^{\frac{y}{2}}
+%		\int_{\hat{y}}^{h(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1 
+%		+ \alpha \nu e^{R/2} \int_{h(y)}^R e^{-\alpha y_1} \dd y_1\\
+%	&\le \xi\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) e^{-(\alpha-\frac{1}{2})\hat{y}}
+%		+ \nu e^{R/2} e^{-\alpha h(y)} \\
+%	&= \Mu{\BallPon{p}}\left(
+%		e^{-(\alpha-\frac{1}{2})\hat{y}} + \frac{\nu}{\xi} e^{-(\alpha - \frac{1}{2})(R-y)}\right).
+%\end{align*}
+%%Consider the following two areas
+%%\begin{align*}
+%%	A_1 &:= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime), \, 
+%%		-\frac{\pi}{2} e^{R/2} \vee - e^{\frac{y + y_1}{2}} \le x_1 \le x^\prime + e^{\frac{y^\prime + y_2}{2}} - \pi e^{R/2} \right\}\\
+%%	A_2 &:= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime), \,
+%%			x^\prime - e^{\frac{y^\prime + y_1}{2}} \le x_1 \le \frac{\pi}{2} e^{R/2} \wedge e^{\frac{y + y_2}{2}} \right\}.
+%%\end{align*}
+%%That is $A_1$ and $A_2$ describe all points $p_1 \in \BallPon{p_0} \cap \BallPon{p}$ with $y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime)$ and $y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime)$, respectively.
+It now follows that
+%%\[
+%%	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \Mu{A_1} + \Mu{A_2},
+%%\]
+%%and we will proceed by computing the measures of both sets. 
+%%
+%%For $A_1$ we have (see also Figure~\ref{fig:comparing_triangles_diff_intersections})
+%%\begin{align*}
+%%	\Mu{A_1} &= \int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} 
+%%		\int_{- e^{\frac{y + y_1}{2}}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} \hspace{-10pt} 
+%%		f(x_1,y_1) \dd x_1 \dd y_1
+%%		+ \int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{R/2}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} 
+%%		\hspace{-10pt}  f(x_1,y_1) \dd x_1 \dd y_1.
+%%\end{align*}
+%%For the first integral we get
+%%\begin{align*}
+%%	&\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} 
+%%		\int_{- e^{\frac{y + y_1}{2}}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} \hspace{-10pt} 
+%%		f(x_1,y_1) \dd x_1 \dd y_1\\
+%%	&= \frac{\alpha \nu}{\pi}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) 	
+%%		\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1
+%%		- \frac{\alpha \nu}{\pi}\left(\pi e^{R/2} - x^\prime \right) 
+%%		\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} e^{-\alpha y_1} \dd y_1\\
+%%	&= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+%%		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
+%%		- e^{-(\alpha - \frac{1}{2})h(y)}\right)
+%%		- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
+%%		\left(e^{-\alpha\hat{y}_{\text{left}}(p_0,p^\prime)}
+%%		- e^{-\alpha h(y)}\right).
+%%%	&= \frac{2\alpha \nu}{\pi(2\alpha - 1)}\left(e^{\frac{y}{2}} + e^{\frac{y}{2}}\right)
+%%%		\left(\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
+%%%		- \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} e^{-(2\alpha - 1)(R-y)}\right)\\
+%%%	&\hspace{10pt}- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
+%%%		\left(\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-2\alpha}
+%%%			- \left(\frac{\pi}{2}\right)^{-2\alpha} e^{-2\alpha(R-y)}\right)
+%%\end{align*}
+%%Similarly, the second integral equals
+%%\begin{align*}
+%%	&\hspace{-20pt}\int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{R/2}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} 
+%%		\hspace{-10pt}  f(x_1,y_1) \dd x_1 \dd y_1\\
+%%	&= \xi e^{\frac{y^\prime}{2}}\left(e^{-(\alpha - \frac{1}{2})h(y)} - e^{-(\alpha - \frac{1}{2})R}\right)
+%%		- \frac{\nu}{\pi}\left(\pi e^{R/2} - x^\prime\right)
+%%		\left(e^{-\alpha h(y)}- e^{-\alpha R}\right).
+%%\end{align*}
+%%Adding these expressions yields
+%%\begin{align*}
+%%	\Mu{A_1} &= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+%%		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
+%%		- \xi e^{\frac{y}{2}} e^{-(\alpha - \frac{1}{2})h(y)}
+%%		- \xi e^{\frac{y^\prime}{2}} e^{-(\alpha-\frac{1}{2})R} \\
+%%	&\hspace{10pt}- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
+%%		e^{-\alpha\hat{y}_{\text{left}}(p_0,p^\prime)}
+%%		+ \nu e^{R/2}e^{-\alpha h(y)} + \frac{\nu}{\pi}\left(\pi e^{R/2} - x^\prime\right) e^{-\alpha R}\\
+%%	&\le \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+%%		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
+%%		+ \nu e^{R/2}e^{-\alpha h(y)} + \nu e^{-(\alpha - \frac{1}{2}) R}.
+%%\end{align*}
+%%
+%%We now proceed with $A_2$. Here we have
+%%\begin{align*}
+%%	\Mu{A_2} &= \int_{\hat{y}_{\text{right}}(p_0,p^\prime)}^{h(y)} 
+%%		\int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{e^{\frac{y+y_1}{2}}} \hspace{-2pt} 
+%%		f(x_1,y_1) \dd x_1 \dd y_1
+%%		+ \int_{h(y)}^{R} \int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{\frac{\pi}{2}e^{R/2}} 
+%%		\hspace{-2pt}  f(x_1,y_1) \dd x_1 \dd y_1.
+%%\end{align*}
+%%Computing each integral separately we get
+%%\begin{align*}
+%%	&\hspace{-20pt}\int_{\hat{y}_{\text{right}}(p_0,p^\prime)}^{h(y)} 
+%%		\int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{e^{\frac{y+y_1}{2}}} \hspace{-2pt} 
+%%		f(x_1,y_1) \dd x_1 \dd y_1\\
+%%	&= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+%%		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} 
+%%		- e^{-(\alpha - \frac{1}{2})h(y)}\right) 
+%%		- \frac{\nu}{\pi} x^\prime \left(e^{\alpha \hat{y}_{\text{right}}(p_0,p^\prime)}
+%%		 - e^{-\alpha h(y)}\right), 
+%%\end{align*}
+%%and
+%%\begin{align*}
+%%	&\hspace{-20pt}\int_{h(y)}^{R} \int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{\frac{\pi}{2}e^{R/2}} 
+%%		\hspace{-2pt}  f(x_1,y_1) \dd x_1 \dd y_1\\
+%%	&= \xi e^{\frac{y^\prime}{2}}\left(e^{-(\alpha - \frac{1}{2})h(y)} - e^{-(\alpha - \frac{1}{2})R}\right)
+%%		+ \frac{\nu}{\pi}\left(\frac{\pi}{2}e^{R/2} - x^\prime\right)\left(e^{-\alpha h(y)} - e^{-\alpha R}\right).
+%%\end{align*}
+%%Combining these results we get
+%%\begin{align*}
+%%	\Mu{A_2} &= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+%%		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} 
+%%		- \xi e^{\frac{y}{2}}e^{-(\alpha - \frac{1}{2})h(y)} 
+%%		- \xi e^{\frac{y^\prime}{2}}e^{-(\alpha - \frac{1}{2})R} \\
+%%	&\hspace{10pt}- \frac{\nu}{\pi} x^\prime e^{-\alpha \hat{y}_{\text{right}}(p_0,p^\prime)}
+%%		+ \frac{\nu}{2} e^{R/2} e^{-\alpha h(y)} - \frac{\nu}{\pi}\left(\frac{\pi}{2}e^{R/2} - x^\prime\right)
+%%		e^{-\alpha R}\\
+%%	&\le \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
+%%		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} + \frac{\nu}{2} e^{R/2} e^{-\alpha h(y)}.
+%%\end{align*}
+%%
+%%Finally, by adding the results for $\Mu{A_1}$ and $\Mu{A_2}$ and using that $\xi e^{\frac{y}{2}} = \Mu{\BallPon{p_0}}$ and 
+%%$\xi e^{\frac{y^\prime}{2}} = \Mu{\BallPon{p^\prime}}$, we get
+%%\begin{align*}
+%%	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
+%%	&\le \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}} \right)
+%%		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p,p^\prime)}
+%%		+ e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p,p^\prime)} \right) \\
+%%	&\hspace{10pt}+ \frac{3\nu}{2}e^{R/2} e^{-\alpha h(y)}
+%%		+ \nu e^{-(\alpha -\frac{1}{2}) R}.
+%%\end{align*}
+%%To finish the argument we recall that $\hat{y}_{\text{left}}(p,p^\prime) \ge \hat{y}_{\text{right}}(p,p^\prime)$ for all $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$ and that $h(y) = R - y + 2\log(\pi/\nu)$.
+Hence
+%%\begin{align*}
+%%	&\Exp{\Ncal_{\text{box}}(p,p^\prime)} \\
+%%	&\le \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}} \right) 
+%%		\left(2e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p,p^\prime)} +    
+%%		\frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
+%%		e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
+%%		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{\xi(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}})}
+%%		\right)
+%%\end{align*}
+%The result follows by plugging in 
+%\[
+%	\hat{y} := \hat{y}_{\text{right}}(p,p^\prime) = 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),
+%\]
+%and noting that $x^\prime$ is the same as $|x - x^\prime|$, by our generalization step.
+%
+%\end{proof}
+
+%We also prove a similar result for the Poissonized KPKVB model $\GPo$.
+%
+%\begin{lemma}\label{lem:common_neighbours_KPKVB}
+%Let $0 < \varepsilon < 1$, $p, p^\prime \in \Rcal$ with $y,y^\prime \le (1-\varepsilon)R$ and denote by $\Ncal_{\Po}(p,p^\prime)$ the number of joint neighbours of $p, p^\prime$ in $\GPo$.
+Then, whenever $|x - x^\prime|_n > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)\left(1 + \frac{\pi^2 K}{4}\right)$,
+%\[
+%	\Exp{\Ncal_{\Po}(p,p^\prime)} \le \Mu{\BallHyp{p}}
+%	\left(e^{(2\alpha - 1)\lambda} \left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}  
+%	+ \frac{\nu}{\xi} e^{-(\alpha - \frac{1}{2})(R-y)}\right),
+%\]
+%where
+%\[
+%	\lambda = \log\left(1 + \frac{\pi^2 K}{4}\right),
+%\]
+%with $K$ the constant from Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
+%\end{lemma}
+%
+%\begin{proof}
+%We will proceed in a similar fashion as for Lemma~\ref{lem:common_neighbours_Pcal_n}.
+That is we will bound the expected number of common neighbours by the number of neighbors of $p$ whose $y$-coordinate is above the intersection of the right boundary of $\BallHyp{p}$ and the left boundary of $\BallHyp{p^\prime}$.
+Denote by $\hat{y}$ the height of this intersection point.
+Then
+%\begin{align*}
+%	\Exp{\Ncal_{\Po}(p,p^\prime)} &\le \frac{2\alpha \nu}{\pi} \int_{\hat{y}}^{R-y} \Phi(y,y_1) e^{-\alpha y_1} \dd y_1
+%		+ \alpha \nu e^{R/2} \int_{R-y}^{R} e^{-\alpha y_1} \dd y_1.
+%\end{align*} 
+%The second integral is bounded by $\frac{\nu}{\xi} \Mu{\BallPon{y}} e^{-(\alpha - \frac{1}{2})(R-y)}$. We bound the first integral using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} as
+%\begin{align*}
+%	\frac{2\alpha \nu}{\pi} \int_{\hat{y}}^{R-y} \Phi(y,y_1) e^{-\alpha y_1} \dd y_1
+%	&\le \frac{2\alpha \nu}{\pi} \int_{\hat{y}}^{R-y} \left(e^{\frac{y+y_1}{2}} + K e^{\frac{3}{2}(y + y_1)-R}\right) 
+%		e^{-\alpha y_1} \dd y_1 \\
+%	&\le \frac{2\alpha \nu}{\pi} (1+K)e^{\frac{y}{2}} \int_{\hat{y}}^{R-y} e^{-(\alpha - \frac{1}{2}) y_1} \dd y_1\\
+%	&\le (1 + K)\Mu{\BallPon{p}}  e^{-(\alpha - \frac{1}{2})\hat{y}},
+%\end{align*}
+%where we used that $\frac{3y_1}{2} \le R - y + \frac{y_1}{2}$ for all $y_1 \le R-y$ for the second line. 
+%
+%It remains to compute $\hat{y}$, for which we will establish the following bound
+%\begin{equation}\label{eq:joint_neighbors_KPKVB_intersection}
+%	\hat{y} \ge 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right) - 2\lambda.
+%\end{equation}
+%
+%To show~\eqref{eq:joint_neighbors_KPKVB_intersection} we note that for any point $y_1 \ge \hat{y}$, the corresponding $x$-coordinate of the left boundary of $\BallHyp{p^\prime}$ must be to the left of that of the ball $\BallHyp{p}$, i.e.
+%$x^\prime - \Phi(y^\prime, y_1) \le \Phi(y,y_1)$. Therefore it is enough to show that for all 
+%\[
+%	y_1 \le 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right) - 2\lambda
+%\]
+%it holds that $\Phi(y,y_1) \le x^\prime - \Phi(y^\prime, y_1)$, with $\lambda$ as defined in the statement of the lemma.
+Note that by assumption on $|x - x^\prime|$ the above upper bound is non-negative.
+Using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} it suffices to prove that for all such $y_1$,
+%\[
+%	e^{\frac{y + y_1}{2}} + K e^{\frac{3}{2}(y + y_1) - R} \le x^\prime - e^{\frac{y^\prime + y_1}{2}}
+%	- K e^{\frac{3}{2}(y^\prime + y_1) - R},
+%\]
+%which is equivalent to
+%\[
+%	\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) e^{\frac{y_1}{2}} 
+%	+ K e^{-R} \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)^3 e^{\frac{3 y_1}{2}} \le x^\prime.
+%\]
+%Plugging the upper bound for $y_1$ into the left hand side and using that $(e^{y/2} + e^{y^\prime/2})^3 \ge e^{3y/2} + e^{3y^\prime/2}$, we obtain
+%\begin{align*}
+%	\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) e^{\frac{y_1}{2}} 
+%		+ K e^{-R} \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)^3 e^{\frac{3 y_1}{2}}
+%	&\le x^\prime e^{-\lambda} + K e^{-R} (x^\prime)^3 e^{-3\lambda}
+%		\le x^\prime \left(e^{-\lambda} + \frac{\pi^2 K}{4} e^{-3\lambda}\right)\\
+%	&\le x^\prime e^{-\lambda} \left(1 + \frac{\pi^2 K}{4}\right) = x^\prime,
+%\end{align*} 
+%where we also used that $x^\prime \le \frac{\pi}{2} e^{-R/2}$.
+%\end{proof}
+
+Recall the definition of $\mathcal{E}_\varepsilon(k_n)$
+from Section~\ref{ssec:joint_degrees_GPo},
+\[
+	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
+			\, : \, y,y^\prime \in [y_{k_n,C}^-, y_{k_N,C}^+] \text{ and } |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\},
 \]
@@
 \[
-	\phi_n(p,p^\prime) = 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
-	+ \frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
-	e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
-	+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}. 
-\]
-\end{lemma}
-
-\begin{proof}
-Again, without loss of generality we assume that $p = p_0 = (0,y)$ and $p^\prime = (x^\prime, y^\prime)$ with $0 \le x^\prime \le \frac{\pi}{2} e^{R/2}$. Consider the following two areas
-\begin{align*}
-	A_1 &:= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime), \, 
-		-\frac{\pi}{2} e^{R/2} \vee - e^{\frac{y + y_1}{2}} \le x_1 \le x^\prime + e^{\frac{y^\prime + y_2}{2}} - \pi e^{R/2} \right\}\\
-	A_2 &:= \left\{p_1 = (x_1,y_1) \in \Rcal \, : \, y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime), \,
-			x^\prime - e^{\frac{y^\prime + y_1}{2}} \le x_1 \le \frac{\pi}{2} e^{R/2} \wedge e^{\frac{y + y_2}{2}} \right\}.
-\end{align*}
-That is $A_1$ and $A_2$ describe all points $p_1 \in \BallPon{p_0} \cap \BallPon{p}$ with $y_1 \ge \hat{y}_{\text{left}}(p_0,p^\prime)$ and $y_1 \ge \hat{y}_{\text{right}}(p_0,p^\prime)$, respectively.
-It now follows that
-\[
-	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \Mu{A_1} + \Mu{A_2},
-\]
-and we will proceed by computing the measures of both sets.
-
-For $A_1$ we have (see also Figure~\ref{fig:comparing_triangles_diff_intersections})
-\begin{align*}
-	\Mu{A_1} &= \int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} 
-		\int_{- e^{\frac{y + y_1}{2}}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} \hspace{-10pt} 
-		f(x_1,y_1) \dd x_1 \dd y_1
-		+ \int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{R/2}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} 
-		\hspace{-10pt}  f(x_1,y_1) \dd x_1 \dd y_1.
-\end{align*}
-For the first integral we get
-\begin{align*}
-	&\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} 
-		\int_{- e^{\frac{y + y_1}{2}}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} \hspace{-10pt} 
-		f(x_1,y_1) \dd x_1 \dd y_1\\
-	&= \frac{\alpha \nu}{\pi}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) 	
-		\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1
-		- \frac{\alpha \nu}{\pi}\left(\pi e^{R/2} - x^\prime \right) 
-		\int_{\hat{y}_{\text{left}}(p_0,p^\prime)}^{h(y)} e^{-\alpha y_1} \dd y_1\\
-	&= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
-		- e^{-(\alpha - \frac{1}{2})h(y)}\right)
-		- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
-		\left(e^{-\alpha\hat{y}_{\text{left}}(p_0,p^\prime)}
-		- e^{-\alpha h(y)}\right).
-%	&= \frac{2\alpha \nu}{\pi(2\alpha - 1)}\left(e^{\frac{y}{2}} + e^{\frac{y}{2}}\right)
-%		\left(\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
-%		- \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} e^{-(2\alpha - 1)(R-y)}\right)\\
-%	&\hspace{10pt}- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
-%		\left(\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-2\alpha}
-%			- \left(\frac{\pi}{2}\right)^{-2\alpha} e^{-2\alpha(R-y)}\right)
-\end{align*}
-Similarly, the second integral equals
-\begin{align*}
-	&\hspace{-20pt}\int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{R/2}}^{x^\prime + e^{\frac{y^\prime+y_1}{2}} - \pi e^{R/2}} 
-		\hspace{-10pt}  f(x_1,y_1) \dd x_1 \dd y_1\\
-	&= \xi e^{\frac{y^\prime}{2}}\left(e^{-(\alpha - \frac{1}{2})h(y)} - e^{-(\alpha - \frac{1}{2})R}\right)
-		- \frac{\nu}{\pi}\left(\pi e^{R/2} - x^\prime\right)
-		\left(e^{-\alpha h(y)}- e^{-\alpha R}\right).
-\end{align*}
-Adding these expressions yields
-\begin{align*}
-	\Mu{A_1} &= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
-		- \xi e^{\frac{y}{2}} e^{-(\alpha - \frac{1}{2})h(y)}
-		- \xi e^{\frac{y^\prime}{2}} e^{-(\alpha-\frac{1}{2})R} \\
-	&\hspace{10pt}- \frac{\nu}{\pi} \left(\pi e^{R/2} - x^\prime\right)
-		e^{-\alpha\hat{y}_{\text{left}}(p_0,p^\prime)}
-		+ \nu e^{R/2}e^{-\alpha h(y)} + \frac{\nu}{\pi}\left(\pi e^{R/2} - x^\prime\right) e^{-\alpha R}\\
-	&\le \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p_0,p^\prime)}
-		+ \nu e^{R/2}e^{-\alpha h(y)} + \nu e^{-(\alpha - \frac{1}{2}) R}.
-\end{align*}
-
-We now proceed with $A_2$. Here we have
-\begin{align*}
-	\Mu{A_2} &= \int_{\hat{y}_{\text{right}}(p_0,p^\prime)}^{h(y)} 
-		\int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{e^{\frac{y+y_1}{2}}} \hspace{-2pt} 
-		f(x_1,y_1) \dd x_1 \dd y_1
-		+ \int_{h(y)}^{R} \int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{\frac{\pi}{2}e^{R/2}} 
-		\hspace{-2pt}  f(x_1,y_1) \dd x_1 \dd y_1.
-\end{align*}
-Computing each integral separately we get
-\begin{align*}
-	&\hspace{-20pt}\int_{\hat{y}_{\text{right}}(p_0,p^\prime)}^{h(y)} 
-		\int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{e^{\frac{y+y_1}{2}}} \hspace{-2pt} 
-		f(x_1,y_1) \dd x_1 \dd y_1\\
-	&= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} 
-		- e^{-(\alpha - \frac{1}{2})h(y)}\right) 
-		- \frac{\nu}{\pi} x^\prime \left(e^{\alpha \hat{y}_{\text{right}}(p_0,p^\prime)}
-		 - e^{-\alpha h(y)}\right), 
-\end{align*}
-and
-\begin{align*}
-	&\hspace{-20pt}\int_{h(y)}^{R} \int_{x^\prime - e^{\frac{y^\prime + y_1}{2}}}^{\frac{\pi}{2}e^{R/2}} 
-		\hspace{-2pt}  f(x_1,y_1) \dd x_1 \dd y_1\\
-	&= \xi e^{\frac{y^\prime}{2}}\left(e^{-(\alpha - \frac{1}{2})h(y)} - e^{-(\alpha - \frac{1}{2})R}\right)
-		+ \frac{\nu}{\pi}\left(\frac{\pi}{2}e^{R/2} - x^\prime\right)\left(e^{-\alpha h(y)} - e^{-\alpha R}\right).
-\end{align*}
-Combining these results we get
-\begin{align*}
-	\Mu{A_2} &= \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} 
-		- \xi e^{\frac{y}{2}}e^{-(\alpha - \frac{1}{2})h(y)} 
-		- \xi e^{\frac{y^\prime}{2}}e^{-(\alpha - \frac{1}{2})R} \\
-	&\hspace{10pt}- \frac{\nu}{\pi} x^\prime e^{-\alpha \hat{y}_{\text{right}}(p_0,p^\prime)}
-		+ \frac{\nu}{2} e^{R/2} e^{-\alpha h(y)} - \frac{\nu}{\pi}\left(\frac{\pi}{2}e^{R/2} - x^\prime\right)
-		e^{-\alpha R}\\
-	&\le \xi \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
-		e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p_0,p^\prime)} + \frac{\nu}{2} e^{R/2} e^{-\alpha h(y)}.
-\end{align*}
-
-Finally, by adding the results for $\Mu{A_1}$ and $\Mu{A_2}$ and using that $\xi e^{\frac{y}{2}} = \Mu{\BallPon{p_0}}$ and 
-$\xi e^{\frac{y^\prime}{2}} = \Mu{\BallPon{p^\prime}}$, we get
-\begin{align*}
-	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
-	&\le \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}} \right)
-		\left(e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{left}}(p,p^\prime)}
-		+ e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p,p^\prime)} \right) \\
-	&\hspace{10pt}+ \frac{3\nu}{2}e^{R/2} e^{-\alpha h(y)}
-		+ \nu e^{-(\alpha -\frac{1}{2}) R}.
-\end{align*}
-To finish the argument we recall that $\hat{y}_{\text{left}}(p,p^\prime) \ge \hat{y}_{\text{right}}(p,p^\prime)$ for all $0 \le x^\prime \le \frac{\pi}{2}e^{R/2}$ and that $h(y) = R - y + 2\log(\pi/\nu)$.
-Hence
-\begin{align*}
-	&\Exp{\Ncal_{\text{box}}(p,p^\prime)} \\
-	&\le \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}} \right) 
-		\left(2e^{-(\alpha - \frac{1}{2})\hat{y}_{\text{right}}(p,p^\prime)} +    
-		\frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
-		e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
-		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{\xi(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}})}
-		\right)
-\end{align*}
-and the result follows by plugging in 
-\[
-	\hat{y}_{\text{right}}(p,p^\prime) = 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),
-\]
-and noting that $x^\prime$ is the same as $|x - x^\prime|$, by our generalization step.
-
-\end{proof}
-
-\subsubsection*{Degrees}
-
-We now return to the joint degree distribution of nodes in $\Gbox$. Recall the definition of $\mathcal{E}_\varepsilon(k_n)$
-\[
-	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \Rcal \times \Rcal
-			\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}. 
-\]
-The following result, which follows from Lemma~\ref{lem:common_neighbours_Pcal_n}, shows that on this set, the expected number of common neighbours is $\smallO{k_n}$.
-
-\begin{lemma}\label{cor:expected_common_neighbours_Ecal_set}
-Fix $0 < \varepsilon < 1$ and let $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. Then for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, as $n \to \infty$,
-\[
-	\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}.
-\] 
-\end{lemma}
-
-\begin{proof}
-Since for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ we have $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$, Lemma~\ref{lem:common_neighbours_Pcal_n} implies that
-\[
-	\Mu{\BallPon{p} \cap \BallPon{p^\prime}} \le \bigO{k_n} \phi_n(p,p^\prime),
-\]
-where
-\[
-	\phi_n(p,p^\prime) = 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
-		+ \frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
-		e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
-		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}. 
-\]
-We thus need to show that $\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon}}$.
+	y_{k,C}^\pm = 2 \log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi}\right),
+\]
+as defined in~\eqref{eq:def_y_k_C}.
+Furthermore, we recall that by Lemma~\ref{lem:probdegFact} the joint degree distribution of two point $p, p^\prime \in \mathcal{E}_{\varepsilon}(k_N)$ factorizes, i.e.
+on the set $\mathcal{E}_\varepsilon(k_n)$ the joint degree distribution in $\Gbox$ is asymptotically equivalent to the product of the degree distributions.
+We shall now prove a slightly stronger result (Lemma~\ref{lem:joint_degree_factorization}) which also takes care of bounded shifts in the joint degree distribution $\rho_{\text{box}}(p,p^\prime,k_n - t,k_n - t^\prime)$, for some uniformly bounded $t, t^\prime \in \mathbb{Z}$.
+For this we first need the following simple result for Poisson distributions.
+
+%The following result, which follows from Lemma~\ref{lem:common_neighbours_Pcal_n}, shows that on this set, the expected number of common neighbours is $\smallO{k_n}$.
+
+%\begin{lemma}\label{cor:expected_common_neighbours_Ecal_set}
+%Fix $0 < \varepsilon < 1$ and let $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. Then for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, as $n \to \infty$,
+%\[
+%	\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}.
+%\] 
+%\end{lemma}
+%
+%\begin{proof}
+%Since for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ we have $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$, Lemma~\ref{lem:common_neighbours_Pcal_n} implies that
+%\[
+%	\Mu{\BallPon{p} \cap \BallPon{p^\prime}} \le \bigO{k_n} \phi_n(p,p^\prime),
+%\]
+%where
+%\[
+%	\phi_n(p,p^\prime) = 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
+%		+ \frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
+%		e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
+%		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}. 
+%\]
+%We thus need to show that $\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon}}$.
 For $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, it holds that $e^{y/2}, e^{y^\prime/2} = \bigT{k_n}$ and $|x - x^\prime| > k_n^{1+\varepsilon}$ and hence
-\begin{align*}
-	 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
-	 =	\bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
-\end{align*}
-For the second term in $\phi_n(p,p^\prime)$ we use that $e^{\alpha y^\ast} = \bigT{k_n^{2\alpha}}$ and $e^{R} = \bigT{n^2}$ to obtain
-\[
-	\frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
-			e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
-	= \bigO{1} n^{-(2\alpha - 1)} k_n^{2\alpha - 1} = \bigO{n^{-(\alpha - \frac{1}{2})}}.
-\]
-Finally, the third term satisfies $\bigO{n^{-(2\alpha - 1)}k_n^{-1}}$, and we conclude that
-\[
-	\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon(2\alpha - 1)} + n^{-(\alpha - \frac{1}{2})}
-	+ n^{-(2\alpha - 1)}k_n^{-1}} = \bigO{k_n^{-\varepsilon^\prime}},
-\]
-where we used that $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. 
-\end{proof}
-
-As a corollary we get that on the set $\mathcal{E}_\varepsilon(k_n)$ the joint degree distribution in $\Gbox$ is asymptotically equivalent to the product of the degree distributions.
-We shall however prove a slightly stronger result (Lemma~\ref{lem:joint_degree_factorization}) which also takes care of bounded shifts in the joint degree distribution $\rho_{\text{box}}(p,p^\prime,k_n - t,k_n - t^\prime)$, for some uniformly bounded $t, t^\prime \in \mathbb{Z}$.
-For this we first need the following simple result for Poisson distributions.
+%\begin{align*}
+%	 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
+%	 =	\bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
+%\end{align*}
+%For the second term in $\phi_n(p,p^\prime)$ we use that $e^{\alpha y^\ast} = \bigT{k_n^{2\alpha}}$ and $e^{R} = \bigT{n^2}$ to obtain
+%\[
+%	\frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
+%			e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
+%	= \bigO{1} n^{-(2\alpha - 1)} k_n^{2\alpha - 1} = \bigO{n^{-(\alpha - \frac{1}{2})}}.
+%\]
+%Finally, the third term satisfies $\bigO{n^{-(2\alpha - 1)}k_n^{-1}}$, and we conclude that
+%\[
+%	\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon(2\alpha - 1)} + n^{-(\alpha - \frac{1}{2})}
+%	+ n^{-(2\alpha - 1)}k_n^{-1}} = \bigO{k_n^{-\varepsilon^\prime}},
+%\]
+%where we used that $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. 
+%\end{proof}
+%
+%It is clear that using Lemma~\ref{lem:common_neighbours_KPKVB} instead of Lemma~\ref{lem:common_neighbours_Pcal_n}, the above proof applies to the Poissonized KPKVB model, yielding the following result.
+%
+%\begin{lemma}\label{cor:expected_common_neighbours_KPKVB}
+%Fix $0 < \varepsilon < 1$ and let $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. Then for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, as $n \to \infty$,
+%\[
+%	\Mu{\BallHyp{p} \cap \BallHyp{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}.
+%\] 
+%\end{lemma}
 
@@
 \end{align*}
-Since by Lemma~\ref{cor:expected_common_neighbours_Ecal_set} $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}$, it follows from Lemma~\ref{lem:near_independence_poisson} that
+Since by Lemma~\ref{cor:expected_common_neighbours_Ecal_set} $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}$, it follows from Lemma~\ref{lem:probdegFact} that
 \[

### 2020-01-02 concentration_argument.tex
version 1.6

@@
 \begin{lemma}\label{lem:concentration_argument_rho_approximation}
-Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n \to \infty$ such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
+Let $\alpha > \frac{1}{2}, \nu > 0$ and $0 < \varepsilon < 1$.
+Furthermore, let $k_n \to \infty$ such that $k_n = \bigO{n^{1-\varepsilon}}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
 \[
-	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
+	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right),
 \] 
-In addition, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is a differentiable function that satisfies for some $0 < \varepsilon < 1$
+for some $C > 0$. Finally, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is a differentiable function that satisfies for some $0 < \varepsilon^\prime < 1$
 \begin{align*}
-	&\mathrm{i)} \, \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} \frac{\hat{\mu}_n(y)}{\mu(\BallPo{y})} = 1
+	&\mathrm{i)} \, \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon^\prime)R} 
+		\left|\frac{\hat{\mu}_n(y)}{\mu(\BallPo{y})} - 1\right| = 0
 	\quad \text{and}
-	&&\mathrm{ii)} \, \lim_{n \to \infty}  \sup_{0 \le y \le (1 - \varepsilon)R} \frac{\hat{\mu}_n^\prime(y)}{\mu(\BallPo{y})} = \frac{1}{2}.
+	&&\mathrm{ii)} \, \lim_{n \to \infty}  \sup_{0 \le y \le (1 - \varepsilon^\prime)R} 	
+		\left|\frac{\hat{\mu}_n^\prime(y)}{\mu(\BallPo{y})} - \frac{1}{2}\right| = 0.
 \end{align*}
-%
-%
-% with $\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y)$ and 
-%where $\phi_n(y)$ is a differentiable function satisfying:
-%\begin{enumerate}[\upshape i)]
-%\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} |\phi_n(y)| = 0$,
-%\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
-%\end{enumerate}
-Then the following holds:
+Then the following holds for $C > 0$ large enough:
 \begin{enumerate}
@@
 
-For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right) = \xi e^{y/2}$ throughout the proof. Observe that $\mu^\prime(y) = \mu(y)/2$ and $\mu^{-1}(y z) = \mu^{-1(y)} + \mu^{-1}(z)$.
-
-%We note that the statement will follow from Lemma~\ref{lem:concentration_argument} if we can show that
-%\[
-%	\int_0^R \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
-%	= \left(1 + o(1)\right) \int_0^R \rho(z,k_n) e^{-\alpha z} \dd z.
-%\] 
-%or equivalently,
-%\[
-%	\int_0^R \rho(z,k_n) e^{-\alpha z} \dd z
-%	= \left(1 + o(1)\right)\int_0^R \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
-%\]
-%
-%We will do this in two steps.
-%
-%Therefore, what is left is to show that
-%\[
-%	\int_0^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
-%	= \left(1 + o(1)\right) \int_0^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z.
-%\] 
-%or equivalently,
-%\[
-%	\int_0^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z
-%	= \left(1 + o(1)\right)\int_0^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
-%\]
-%
-%Using the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$ and writing $\hat{a}_n^\pm = \hat{\mu}_n^{-1}(\mu(a_n^\pm))$ and $\hat{R}_{\varepsilon^\prime} := \hat{\mu}_n^{-1}(\mu((1-\varepsilon^\prime)R))$, we get
-%\begin{align*}
-%	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z 
-%	&= \int_{a_n^+}^{(1-\varepsilon^\prime)R} \Prob{\Po(\mu(z)) = k_n} e^{-\alpha z} \dd z\\
-%	&= \int_{\hat{a}_n^+}^{\hat{R}_{\varepsilon^\prime}} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
-%		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
-%\end{align*}
-%where the fraction in the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.
+For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right) = \xi e^{y/2}$ throughout the proof. Observe that $\mu^\prime(y) = \mu(y)/2$ and $\mu^{-1}(y z) = \mu^{-1}(y) + \mu^{-1}(z)$.
 
@@
 
-Let $0 < \varepsilon < 1$ be such that conditions i) and ii) hold, take $\varepsilon^\prime = \min\{\varepsilon/3,1/3\} < 1/2$ and let $\delta > 0$ be such that $\hat{\mu}_n(\delta) \ge \xi$.
-We first show that we can restrict to integration over $(\delta, (1-\varepsilon^\prime)R)$ that the integration over $(1-\varepsilon^\prime)R \le y \le R$ is negligible.
+Let $0 < \varepsilon < 1$ be such that conditions i) and ii) hold, 
+Take any $0 < \delta < \min\{\varepsilon, \varepsilon^\prime/3,1/3\} < 1/2$ and let $Q > 0$ be such that $\hat{\mu}_n(Q) \ge \xi$.
+We first show that we can restrict to integration over $(Q, (1-\delta)R)$, starting with showing that the integration over $(1-\delta)R \le y \le R$ is negligible.
 
-Since $h(y) = \bigO{e^{\beta y}}$ we have
+By construction $\delta < \varepsilon^\prime$, and hence by condition i) we have that $\hat{\mu}_n((1-\delta)R) = \bigT{\mu((1-\delta)R} = \bigT{n^{(1-\delta)}}$.
+Therefore, since $\delta<\varepsilon$ and $k_n = \bigO{n^{1-\varepsilon}}$, it follows that $\hat{\mu}_n((1-\delta)R)/k_n = \omega\left(n^{\varepsilon - \delta}\right)$ as $n \to \infty$.
+In particular $\hat{\mu}((1-\delta)R) = \omega{k_n}$ and hence $\hat{\rho}_n(y,k_n) \le \hat{\rho}((1-\delta)R,k_n)$ for all $y \ge (1-\delta)R$.
+It now follow that
 \begin{align*}
-	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
-	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\prime)R,k_n) e^{-(\alpha-\beta)(1-\varepsilon^\prime)R} \\
-	&= \bigO{\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) n^{-2(\alpha-\beta)(1-\varepsilon^\prime)}}.
+	\int_{(1-\delta)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	&= \bigO{1} \hat{\rho}_n((1-\delta)R,k_n) e^{-(\alpha-\beta)(1-\delta)R} \\
+	&= \bigO{\hat{\rho}_n((1-\delta)R,k_n) n^{-2(\alpha-\beta)(1-\delta)}},
 \end{align*}
-By construction $\varepsilon^\prime < \varepsilon$, and hence by condition i) we have that $\hat{\mu}_n((1-\varepsilon^\prime)R) = \bigT{\mu((1-\varepsilon^\prime)R} = \bigT{n^{2(1-\varepsilon^\prime)}}$.
-Therefore, since $k_n = \smallO{n}$, it follows that $\hat{\mu}_n((1-\varepsilon^\prime)R)/k_n = \omega\left(n^{1 - 2\varepsilon^\prime}\right) \to \infty$ as $n \to \infty$.
-We can now use Stirling's approximation to bound $\hat{\rho}_n((1-\varepsilon^\prime)R,k_n)$ as
+where we used that that $h(y) = \bigO{e^{\beta y}}$.
+Using Stirling's approximation to bound $\hat{\rho}_n((1-\delta)R,k_n)$ we get
 \begin{align*}
-	\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) &= \Prob{\Po(\hat{\mu}_n((1-\varepsilon^\prime)R)) = k_n} \\
-	&= \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)^{k_n}}{k_n!} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)}\\
-	&= \bigO{1} k_n^{-1/2} \left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)^{k_n} e^{k_n - \hat{\mu}_n((1-\varepsilon^\prime)R)}\\
-	&= \bigO{1} k_n^{-1/2} e^{k_n\left(1 - \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)+ \log\left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)}\\
-	&\le \bigO{1} k_n^{-1/2} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)/2},
+	\hat{\rho}_n((1-\delta)R,k_n) &= \Prob{\Po(\hat{\mu}_n((1-\delta)R)) = k_n} \\
+	&= \frac{\hat{\mu}_n((1-\delta)R)^{k_n}}{k_n!} e^{-\hat{\mu}_n((1-\delta)R)}\\
+	&= \bigO{1} k_n^{-1/2} \left(\frac{\hat{\mu}_n((1-\delta)R)}{k_n}\right)^{k_n} e^{k_n - \hat{\mu}_n((1-\delta)R)}\\
+	&= \bigO{1} k_n^{-1/2} e^{k_n\left(1 - \frac{\hat{\mu}_n((1-\delta)R)}{k_n}+ \log\left(\frac{\hat{\mu}_n((1-\delta)R)}{k_n}\right)\right)}\\
+	&\le \bigO{1} k_n^{-1/2} e^{-\hat{\mu}_n((1-\delta)R)/2},
 \end{align*}
-where the last line follows since $1 - x + \log(x) \le -x/2$ for large enough $x$. We conclude that
+where the last line follows since $1 - x + \log(x) \le -x/2$ for large enough $x$ and $\hat{\mu}_n((1-\delta)R)/k_n \to \infty$. We thus conclude that for any $C > 0$
 \[
-	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
-	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\varepsilon^\prime)} e^{-n^{2(1-\varepsilon^\prime)}}}
+	\int_{(1-\delta)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\delta)} e^{-n^{(1-\delta)}}}
 	= \bigO{k_n^{-(1+C^2)/2}}.
@@
 
-In a similar fashion we get that
+For the range $(0,Q)$ we have, for any $C > 0$,
 \begin{align*}
-	\int_0^\delta h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
-	&= \bigO{1} \hat{\rho}_n(\delta, k_n) \\
-	&= \bigO{1} k_n^{-1/2} e^{-k_n(\log(k_n)-\hat{\mu}_n(\delta))} = \bigO{k_n^{-(1+C^2)/2}}.
+	\int_0^Q h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
+	&= \bigO{1} \hat{\rho}_n(Q, k_n) \\
+	&= \bigO{1} k_n^{-1/2} e^{-k_n(\log(k_n)-\hat{\mu}_n(Q))} = \bigO{k_n^{-(1+C^2)/2}}.
 \end{align*}
@@
 
-Let $(a, b) \subseteq (\delta,(1-\varepsilon^\prime)R)$ and consider the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$.
-Then, writing $\hat{a} = \hat{\mu}_n^{-1}(\mu(a))$ and similar for $\hat{b}$, we get
+Let $(a, b) \subseteq (Q,(1-\delta)R)$ and consider the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$. Then, writing $\hat{a} = \hat{\mu}_n^{-1}(\mu(a))$ and similar for $\hat{b}$, we get
 \begin{align*}
@@
 
-Now, using~\eqref{eq:equivalence_integral_rho_change_variables} with $a = \mu^{-1}(\hat{\mu}_n(\delta))$ and $b = \mu^{-1}(\hat{\mu}_n(a_n^-)$ we get
+Now, using~\eqref{eq:equivalence_integral_rho_change_variables} with $a = \mu^{-1}(\hat{\mu}_n(Q))$ and $b = \mu^{-1}(\hat{\mu}_n(a_n^-)$ we get
 \begin{align*}
 	\int_a^b \rho(y,k_n) e^{(\beta-\alpha) y} \dd y
-	&= (1+\smallO{1}) \int_{\delta}^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y.
+	&= (1+\smallO{1}) \int_{Q}^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y.
 \end{align*}
@@
 \]
-for some $c_n \in (a_n^-, a_n^+)$. Since, $c_n \sim 2 \log(k_n/\xi)$, by assumption on $h$, $h(c_n)\sim h(2\log(k_n/\xi))$. 
+for some $c_n \in (a_n^-, a_n^+)$. Since $c_n \sim 2 \log(k_n/\xi)$, $h(c_n)\sim h(2\log(k_n/\xi))$ by assumption on $h$. 
 Therefore it is enough to show that
@@
 \[
-	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \frac{1}{2} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}}
-	= \frac{1}{2}.
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \left|\frac{1}{2} \frac{\Mu{\BallHyp{y}}}{\Mu{\BallPo{y}}}
+	- \frac{1}{2}\right| = 0.
 \]
@@
 \[
-	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1}
-	\frac{\partial}{\partial y} \mu\left(\BallHyp{y}\right) 
-	= \frac{1}{2}.
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \left|\Mu{\BallPo{y}}^{-1}
+	\frac{\partial}{\partial y} \mu\left(\BallHyp{y}\right) - \frac{1}{2}\right| = 0.
 \]
@@
 \begin{equation}\label{eq:derivative_mu_hyp_ball_main}
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \frac{2\alpha \nu}{\pi} \frac{\partial}{\partial y} \int_0^{R - y} \Phi(r,r^\prime) e^{-\alpha y^\prime} \dd y^\prime
-	= \frac{1}{2}.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \left|\Mu{\BallPo{y}}^{-1} \frac{2\alpha \nu}{\pi} \frac{\partial}{\partial y} \int_0^{R - y} \Phi(y,y^\prime) e^{-\alpha y^\prime} \dd y^\prime
+	- \frac{1}{2}\right| = 0.
 \end{equation}
@@
 \[
-	\Phi(R -y, R - y^\prime) = \frac{1}{2}e^{R/2} \arccos\left(1 - \Xi(y,y^\prime)\right).
+	\Phi(y, y^\prime) = \frac{1}{2}e^{R/2} \arccos\left(1 - \Xi(y,y^\prime)\right).
 \]
@@
 \end{equation}
-In particular, there exists a $0 < \delta < 1$ such that $1 \le \Xi(y,y^\prime) \le 2$ for all $0 < y < R$ and $(1-\delta)(R-y) < y^\prime < R$.
+In particular, since $R-y$ is an increrasing function of $n$ uniformly on $0 < y < (1-\varepsilon)R$, there exists a $0 < \delta < 1$ such that $1/2 \le \Xi(y,y^\prime) < 2$ for all $y + y^\prime < R$ and $(1-\delta)(R-y) < y^\prime < R$ and $n$ large enough.
 
@@
 \begin{align*}
-	\frac{\partial}{\partial y} \Phi(R -y, R - y^\prime)
+	\frac{\partial}{\partial y} \Phi(y, y^\prime)
 	&= \frac{1}{2}e^{R/2} \frac{1}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}} 
@@
 \begin{align*}
-	&\hspace{-30pt}\frac{\partial}{\partial y} \int_0^{R - y} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
-	&= - \alpha\Phi(y,R - y)e^{-\alpha(R-y)} + \int_0^{R - y} \frac{\partial}{\partial y}  \Phi(y,y^\prime) 
-		\alpha e^{-\alpha y^\prime} \dd y^\prime\\
-	&= -\frac{\pi}{2}e^{-(\alpha-\frac{1}{2})R + \alpha y} + \int_0^{R- y} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
-		\left(1 + \varphi_n(y,y^\prime)\right) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
-	&= -\frac{\pi}{2}e^{-(\alpha-\frac{1}{2})R + \alpha y}  + \int_0^{(1-\delta)(R- y)} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}
+	&\hspace{-30pt}\frac{\partial}{\partial y} \int_0^{R - y} \Phi(y,y^\prime) e^{-\alpha y^\prime} \dd y^\prime\\
+	&= - \Phi(y,R - y)e^{-\alpha(R-y)} + \int_0^{R - y} \frac{\partial}{\partial y}  \Phi(y,y^\prime) 
+		 e^{-\alpha y^\prime} \dd y^\prime\\
+	&= -\frac{1}{2}e^{-(\alpha-\frac{1}{2})R + \alpha y} + \int_0^{R- y} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+		\left(1 + \varphi_n(y,y^\prime)\right) e^{-\alpha y^\prime} \dd y^\prime\\
+	&= -\frac{1}{2}e^{-(\alpha-\frac{1}{2})R + \alpha y}  + \int_0^{(1-\delta)(R- y)} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}
 		{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
-		\left(1 + \varphi_n(y,y^\prime)\right) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
+		\left(1 + \varphi_n(y,y^\prime)\right) e^{-\alpha y^\prime} \dd y^\prime\\
 	&\hspace{10pt}+ \int_{(1-\delta)(R- y)}^{R - y} \frac{ \frac{1}{2}e^{R/2} \Xi(y,y^\prime)}
 			{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
-			\left(1 + \varphi_n(y,y^\prime)\right) \alpha e^{-\alpha y^\prime} \dd y^\prime\\
+			\left(1 + \varphi_n(y,y^\prime)\right) e^{-\alpha y^\prime} \dd y^\prime\\
 	&:= -I_1(y) + I_2(y) + I_3(y),
 \end{align*}
-with $\delta$ such that $1 \le \Xi(y,y^\prime) \le 2$ for all $0 < y < R$ and $(1-\delta)(R-y) < y^\prime < R$.
+with $0 \le \delta < 1$ such that $0 < \Xi(y,y^\prime) < 2$ for all $0 < y < R$ and $(1-\delta)(R-y) < y^\prime < R$.
 
@@
 \begin{equation}\label{eq:derivative_hyp_ball_error_1}
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} I_t(y) = 0, \quad \text{for } t = 1,3
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \left|\frac{I_t(y)}{\Mu{\BallPo{y}}}\right| 
+	= 0, \quad \text{for } t = 1,3
 \end{equation}
@@
 \begin{equation}\label{eq:derivative_hyp_ball_main_part}
-	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} I_2(y) = \frac{1}{2}.
+	\lim_{n \to \infty} \sup_{0 \le y \le (1-\varepsilon)R} \left|\frac{2\nu \alpha}{\pi \Mu{\BallPo{y}}} I_2(y) - \frac{1}{2}\right| = 0.
 \end{equation}
@@
 
-Let us first consider $I_1(y)$. Since 
+For $I_1(y)$ we have 
 \[
 	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} I_1(y) 
-	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \frac{\pi}{2\xi} e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
+	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \frac{1}{2\xi} e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
 \]
@@
 \[
-	I_3(y) \le \frac{\alpha}{2}\left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right)e^{R/2}
+	I_3(y) \le \frac{1}{2}\left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right)e^{R/2}
 	\int_{(1-\delta)(R- y)}^{R - y} \frac{ \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
@@
 \]
-Since for all $1 \le x < 2$,
+To bound the integral we recall that $0 < \Xi(y,y^\prime) \le 2e^{-(R-y-y^\prime)} < 2$ and for all $1/2 \le x < 2$,
 \[
-	\frac{1}{\sqrt{1- (1-x)^2}} \le \frac{2}{\sqrt{2(2-x)}},
-\]
-and $1 \le \Xi(y,y^\prime) \le 2$, for all $(1-\delta)(R -y) \le y\prime < R-y$ and $y < R$, it follows that
+	\frac{1}{\sqrt{1- (1-x)^2}} \le \frac{2}{\sqrt{2-x}},
+\]a
+where the right hand side is a monotonic increasing function.
+Therefore
 \begin{align*}
-	&\hspace{-30pt}\int_{(1-\delta)(R- y)}^{R - y} \frac{ \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
-		e^{-\alpha y^\prime} \dd y^\prime \\
-	&\le 2 \int_{(1-\delta)(R- y)}^{R - y} \frac{\Xi(y,y^\prime)}{\sqrt{2(2-\Xi(y,y^\prime))}} e^{-\alpha y^\prime} 
+	\int_{(1-\delta)(R- y)}^{R - y} \frac{ \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+		e^{-\alpha y^\prime} \dd y^\prime
+	&\le 2 \int_{(1-\delta)(R- y)}^{R - y} \frac{\Xi(y,y^\prime)}{\sqrt{(2-\Xi(y,y^\prime))}} e^{-\alpha y^\prime} 
 		\dd y^\prime \\
-	&\le 2 e^{-\alpha(R - y)} \int_{(1-\delta)(R- y)}^{R - y} 
-		\frac{e^{-(R - y - y^\prime)}}{\sqrt{1 - e^{-(R - y - y^\prime)}}} e^{\alpha (R - y - y^\prime)} \dd y^\prime.
+	&\le \sqrt{2} e^{-\alpha(R - y)} \int_{(1-\delta)(R- y)}^{R - y} 
+		\frac{e^{-(R - y - y^\prime)}}{\sqrt{1 - e^{-(R - y - y^\prime)}}} e^{\alpha (R - y - y^\prime)} \dd y^\prime,
 \end{align*}
@@
 \begin{align*}
-	2 e^{-\alpha(R - y)} \int_{(1-\delta)(R- y)}^{R - y} 
-			\frac{e^{-(R - y - y^\prime)}}{\sqrt{1 - e^{-(R - y - y^\prime)}}} e^{\alpha (R - y - y^\prime)} \dd y^\prime
-	&= 2 e^{-\alpha(R - y)} \int_{e^{-\delta (R - y)}}^{1} \frac{z^{-\alpha}}{\sqrt{1 - z}} \dd z\\
-	&\le 2 e^{-\alpha(R - y)} \sqrt{1 - e^{-\delta (R - y)}}\\
-	&\le 2 e^{-\alpha (R -y)}.
+	&\hspace{-20pt}\sqrt{2} e^{-\alpha(R - y)} \int_{(1-\delta)(R- y)}^{R - y} 
+			\frac{e^{-(R - y - y^\prime)}}{\sqrt{1 - e^{-(R - y - y^\prime)}}} e^{\alpha (R - y - y^\prime)} \dd y^\prime\\
+	&= \sqrt{2} e^{-\alpha(R - y)} \int_{e^{-\delta (R - y)}}^{1} \frac{z^{-\alpha}}{\sqrt{1 - z}} \dd z
+		\le \sqrt{2} e^{-\alpha(R - y)} \sqrt{1 - e^{-\delta (R - y)}}
+		\le \sqrt{2} e^{-\alpha (R -y)}.
 \end{align*}
@@
 \[
-	I_3(y) \le \alpha \left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right)e^{-(\alpha -\frac{1}{2})R + \alpha y}.
+	I_3(y) \le \frac{1}{\sqrt{2}} \left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right)e^{-(\alpha -\frac{1}{2})R + \alpha y}.
 \]
-which implies
+which implies~\eqref{eq:derivative_hyp_ball_error_1} for $t=3$.
+
+Finally, to show~\eqref{eq:derivative_hyp_ball_main_part} we first write
+\begin{align*}
+	\left|\frac{2\alpha \nu}{\pi \Mu{\BallPo{y}}} I_2(y) - \frac{1}{2}\right|
+	&\le \left|\frac{2\alpha \nu}{\pi \Mu{\BallPo{y}}}  \int_0^{(1-\delta)(R- y)} \frac{\Phi(y,y^\prime)}{2} 
+		e^{-\alpha y^\prime} \dd y^\prime - \frac{1}{2}\right| \\
+	&\hspace{10pt}+ \frac{2\alpha \nu}{\pi \Mu{\BallPo{y}}}\left|\int_0^{(1-\delta)(R- y)} 
+		\frac{\Phi(y,y^\prime)}{2} e^{-\alpha y^\prime} \dd y^\prime - I_2(y)\right|.
+\end{align*}
+By Lemma~\ref{lem:hyperbolic_ball_lower_part},
 \[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} I_3(y) 
-	\le \lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \alpha \left(1 + \frac{e^{-2y}}{1 - e^{-2y}}\right) e^{-(\alpha - \frac{1}{2})(R - y)} = 0.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \left|\frac{2\nu \alpha}{\pi \Mu{\BallPo{y}}} 
+	\int_{0}^{(1-\delta)(R-y)} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime
+	- 1\right| = 0,
 \] 
+and thus it suffices to show that the $\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R}$ of the second term goes to zero.
 
-Finally, to show~\eqref{eq:derivative_hyp_ball_main_part} we define 
+Recalling the definition of $I_2(y)$ we have
 \begin{align*}
-	\varphi^-_n &:= \sup_{0 < y \le (1-\varepsilon)R} \, \inf_{0 \le y^\prime \le (1 - \delta)(R-y)} 
-		\varphi_n(y,y^\prime)\\
-	\varphi^+_n &:= \sup_{0 < y \le (1-\varepsilon)R} \, \sup_{0 \le y^\prime \le (1 - \delta)(R-y)} \varphi_n(y,y^\prime)
+	&\hspace{-30pt}\left|\int_0^{(1-\delta)(R- y)} \frac{\Phi(y,y^\prime)}{2} e^{-\alpha y^\prime} \dd y^\prime 
+		- I_2(y)\right|\\
+	&\le \int_0^{(1-\delta)(R- y)} \left|\frac{\Phi(y,y^\prime)}{2}- \frac{\frac{1}{2}e^{R/2} \Xi(y,y^\prime)}
+		{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}(1+\varphi_n(y,y^\prime)\right|e^{-\alpha y^\prime} \dd y^\prime.
+		\numberthis \label{eq:derivative_hyp_ball_final_error}
 \end{align*}
-and note that since for $0 \le y^\prime \le (1-\delta)(R-y)$,
+We will oroceed to bound the term inside the integral. For this we first note that for $0 \le y^\prime \le (1-\delta)(R-y)$,
 \[
-	\frac{e^{-(R + y)}}{1 - e^{-(R+y)}} - \frac{e^{-(R- y)}}{1 - e^{-(R-y)}} - \frac{2e^{-2(R-y)}}{1 - e^{-2(R-y)}}
-	\le \varphi_n(y,y^\prime) \le \frac{e^{-\delta(R-y)}}{1 - e^{-\delta(R-y)}}.
+	\varphi_n(y,y^\prime) \le \frac{e^{-\delta(R-y)}}{1 - e^{-\delta(R-y)}}.
 \]
-we get $\lim_{n \to \infty} \varphi^\pm_n = 0$.
-Next, recall that $\Phi(y,y^\prime) = \frac{1}{2}e^{R/2}\Xi(y,y^\prime)$.
-Then, since $\Xi(y,y^\prime) < 2$ for all $y^\prime < (1-\delta)(R-y)$ and $y < R$, there exists a $K > 0$ such that (see Lemma~\ref{lem:arccos_approx}),
+and recall that $\Xi(y,y^\prime) \le 2 e^{-(R-y-y^\prime)}$.
+Moreover, since $x/\sqrt{1-(1-x)^2} = x/\sqrt{2x-x^2}$ is an increasing function and $e^{-(R - y - y^\prime)} \le e^{-\delta(R- y)}$ for $0 < y^\prime < (1-\delta)(R-y)$,
 \[
-	\frac{1}{2}\Phi(y,y^\prime)\left(1 - \frac{(1+\sqrt{2})\Xi(y,y^\prime)}{1 + \Xi(y,y^\prime)}\right)
-	\le \frac{\frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}} 
-	\le \frac{1}{2}\Phi(y,y^\prime)\left(1 + \frac{(1+K)\Xi(y,y^\prime)}{1 - \Xi(y,y^\prime)}\right)
+	\frac{\frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}
+	\le e^{R/2} \frac{e^{-\delta(R-y)}}{\sqrt{2e^{-\delta(R-y)} - e^{-2\delta(R-y)}}}.
 \]
-for all $y^\prime < (1-\delta)(R - y)$ and $y < R$. Using that $e^{-(r-y)} \le e^{-(R - y - y^\prime)} \le e^{-\delta(R- y)}$, for $0 < y^\prime < (1-\delta)(R-y)$, we get
+Next, recall that $\Phi(y,y^\prime) = \frac{1}{2}e^{R/2}\arccos(1-\Xi(y,y^\prime))$.
+Then, since $\Xi(y,y^\prime) < 1$ for all $y^\prime < (1-\delta)(R-y)$, $y < R$ and $n$ large enough, we have (see Lemma~\ref{lem:arccos_approx}),
 \[
-	1 - \frac{(1+\sqrt{2})\Xi(y,y^\prime)}{1 + \Xi(y,y^\prime)} \ge 1 - 2(1+\sqrt{2})e^{-(R-y)}
+	\left|\frac{1}{2}\Phi(y,y^\prime) - \frac{\frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}}\right| \le \frac{1}{2}\Phi(y,y^\prime) \Xi(y,y^\prime).
 \]
-and
+for all $y^\prime < (1-\delta)(R - y)$ and $y < R$. Togehter these facts imply that for $n$ large enough
+\begin{align*}
+	&\hspace{-30pt}\left|\frac{\Phi(y,y)}{2} - \frac{\frac{1}{2}e^{R/2} \Xi(y,y^\prime)}{\sqrt{1 - \left(1 - 	
+		\Xi(y,y^\prime)\right)^2}}(1+\varphi_n(y,y^\prime))\right|\\
+	&\le \frac{\Phi(y,y^\prime)\Xi(y,y^\prime)}{2} 
+		+ \frac{\frac{1}{2}e^{R/2} \Xi(y,y^\prime) \varphi_n(y,y^\prime)}
+		{\sqrt{1 - \left(1 - \Xi(y,y^\prime)\right)^2}} \\
+	&\le e^{-\delta(R-y)} \Phi(y,y^\prime) + \frac{e^{-\delta(R-y)}}{1-e^{-\delta(R-y)}}
+		\frac{e^{R/2} e^{-\delta(R-y)}}{\sqrt{2e^{-\delta(R-y)} - e^{-2\delta(R-y)}}}\\
+	&\le e^{-\delta(R-y)} \Phi(y,y^\prime) + \frac{e^{\frac{R}{2}}e^{-\frac{3}{2}\delta(R-y)}}
+		{\left(1 - e^{-\delta(R-y)}\right)^{3/2}}
+\end{align*}
+
+Plugging this into~\eqref{eq:derivative_hyp_ball_final_error} yields
+\begin{align*}
+	&\hspace{-30pt}\left|\int_0^{(1-\delta)(R- y)} \frac{\Phi(y,y^\prime)}{2} e^{-\alpha y^\prime} \dd y^\prime 
+			- I_2(y)\right|\\
+	&\le \int_0^{(1-\delta)(R- y)} \left(e^{-\delta(R-y)} \Phi(y,y^\prime) + 
+		\frac{e^{\frac{R}{2}}e^{-\frac{3}{2}\delta(R-y)}}{\left(1 - e^{-\delta(R-y)}\right)^{3/2}}\right)
+		e^{-\alpha y^\prime} \dd y^\prime \\
+	&\le e^{-\delta(R-y)} \Mu{\BallPo{y}} + e^{\frac{y}{2}} \frac{e^{-(\alpha - \frac{1}{2} - (\alpha - \frac{3}{2})\delta)(R-y)}}
+		{\alpha \left(1 - e^{-\delta(R-y)}\right)^{3/2}}
+\end{align*}
+To finish the argument we note that $R-y > 0$ for all $0 < y \le (1-\varepsilon)R$ and observe that $\delta < 1$ implies that $(\alpha - \frac{1}{2} - (\alpha - \frac{3}{2})\delta > 1$.
+Since $\Mu{\BallPo{y}} = \bigT{e^{\frac{y}{2}}}$ it the
+then follows that
 \[
-	1 + \frac{(1+K)\Xi(y,y^\prime)}{1 - \Xi(y,y^\prime)} 
-	\le 1 + \frac{2(1 + K)e^{-\delta(R - y)}}{1-e^{-\delta(R-y)}}.
+	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \frac{2\alpha \nu}{\pi \Mu{\BallPo{y}}}
+	\left|\int_0^{(1-\delta)(R- y)} \frac{\Phi(y,y^\prime)}{2} e^{-\alpha y^\prime} \dd y^\prime - I_2(y)\right| = 0,
 \]
-
-We thus have the following upper and lower bound for $I_2(y)$
-\begin{align*}
-	I_2(y) \le \frac{1}{2} \left(1 + \phi_n^+\right)
-	\left(1 + \frac{2(1 + K)e^{-\delta(R - y)}}{1-e^{-\delta(R-y)}}\right)
-	\int_{0}^{(1-\delta)(R-y)} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime,
-\end{align*}
-and
-\[
-	I_2(y) \ge \frac{1}{2} \left(1 + \phi_n^-\right)\left(1 - 2(1+\sqrt{2})e^{-(R-y)}\right)
-	\int_{0}^{(1-\delta)(R-y)} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime.
-\]
-From this~\eqref{eq:derivative_hyp_ball_main_part} follows since, $\lim_{n \to \infty} \varphi_n^\pm = 0$ and by Lemma~\ref{lem:hyperbolic_ball_lower_part},
-\[
-	\lim_{n \to \infty} \sup_{0 < y \le (1-\varepsilon)R} \Mu{\BallPo{y}}^{-1} \frac{2\nu \alpha}{\pi} 
-	\int_{0}^{(1-\delta)(R-y)} \Phi(y,y^\prime) \alpha e^{-\alpha y^\prime} \dd y^\prime
-	= 1.
-\] 
+which completes the proof.
 \end{proof}

### 2020-01-02 hyperbolic_degrees.tex
version 1.6

\section{Degrees in the KPKVK model: proof of Theorem~\ref{thm:degrees_hyperbolic}}

\subsection{Proof overview}

As mentioned earlier, we plan to make use of the Campbell-Mecke formula for comparing the degree distribution in $\GPo$ with that of a \emph{typical point} in $\Ginf$. For this we will be considering the Poisson process $\Pcal$ to which we add one additional point $(0,y)$ on the $y$-axis. In some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and independent of $\Pcal$.
We refer to $(0,y)$ as ``the typical point''.

To provide some intuition for this definition and name, note that we can alternatively view $\Pcal$ as follows. 
We take a constant intensity Poisson process on $\eR$ corresponding to the $x$-coordinates, and to each point
we attach a random ``mark'', corresponding to the $y$-coordinate, where the marks are i.i.d.~exponentially distributed with parameter $\alpha$. By translation invariance of Poisson point process, each point will behave as $(0,y)$ with $y$ exponentially distributed with parameter $\alpha$, the typical point of the process.

We first compute the degree distribution of the typical point in $\Ginf$ and show that this equals 
\[
	p_k = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
\]
We then relate this to the Poissonized KPKVB model $\GPo$ by showing in Section~\ref{ssec:expected_degrees_GPo} that for any $1 \le k_n \le n -1$ with $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$, $\Exp{N_{\Po}(k_n)} = (1+\smallO{1}) n p_{k_n}$ and more generally,
\[
	\Exp{\binom{N_{\Po}(k_n)}{r}} = (1+\smallO{1}) \frac{\Exp{N_{\Po}(k_n)}^r}{r!},
\]
for any integer $r \ge 1$ in Section~\ref{ssec:factorial_moments_GPo}. The latter result requires us to analyze the joint degree distribution in $\GPo$, which we do in Section~\ref{ssec:joint_degrees_GPo}. The above result in particular implies concentration of $N_{\Po}(k_n)$ from which the result on the degree distribution in $\GPo$ follows for $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$. When $k_n = (1+\smallO{1}) c n^{\frac{1}{2\alpha + 1}}$ we use the above result to show that the fraction of degree $k_n$ nodes in $\GPo$ converges to a Poisson distribution.

To extend these results to $G_n$ we couple the construction of the KPKVB model to that of the Poissonized version $\GPo$ in Section~\ref{ssec:coupling_Gn_GPo} to show that a.a.s, $N_n(k_n) = (1+\smallO{1}) N_{\Po}(k_n)$. With these results we then proof Theorem~\ref{thm:degrees_hyperbolic} in Section~\ref{ssec:proof_thm_degrees}.

We will also establish all the above mention results for the finite box model $\Gbox$, since the proofs only require small alterations and we will need these results later on when analyzing the clustering coefficient and function.

\subsection{The degree of the typical point in $\Ginf$}\label{ssec:degrees_infinite_model}

We start with investigating the distribution of the degree of the typical point. (Considered in the graph obtained from $\Ginf$ by adding the typical point to its vertex set.)

If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we will write
\[ 
	\mu(y) = \mu(p) := \mu(\BallPo{p}).
\]
Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives, using $\alpha>\frac{1}{2}$,
\begin{align*}
	\mu(y) &= \int_{\BallPo{p}} f(x',y') \, dx' \,d y'  
 		= \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' \\
	&= \int_0^\infty 2 e^{(y+y')/2} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dy' 
 		= \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' \\
	&= \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
\end{align*}

For $p = (x,y) \in \eR\times[0,\infty)$ we define
\begin{equation}\label{eq:def_degree_inf_model}
	\rho(p,k) := \Prob{\Po(\Mu{p}) = k},
\end{equation}
where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$. When $p = (0,y)$ we often write $\rho(y,k)$ instead of $\rho(p,k)$.

Let the random variable $D$ denote the degree of the typical point. Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed, for $k \in \N_0$:
\begin{equation}\label{eq:def_pk}
	p_k :=  \Prob{D = k} = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
\end{equation}

Using the transformation of variables $z = \xi e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
\begin{align*}
	p_k
    &= \frac{1}{k!} \int_0^\infty \left(\xi e^{\frac{y}{2}}\right)^k 
    	e^{-\xi e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy
    	= \frac{\alpha \xi^{2\alpha}}{k!} \int_0^\infty 
    	\left(\xi e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi e^{\frac{y}{2}}}
        \, dy\\
    &= \frac{2\alpha \xi^{2\alpha}}{k!} \int_{\xi}^{\infty} 
    	z^{k -2\alpha-1} e^{-z} \, dz
    	= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
\end{align*}
where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{+}$ the upper incomplete Gamma-function.
Note that, unsurprisingly, this is identical to the expression Gugelmann et al.~\cite{gugelmann2012random} gave for the limiting degree distribution of $G(n;\alpha,\nu)$. Using Stirling's approximation to the gamma function, we find that

\begin{equation}\label{eq:degree_distribution_P_asymptotics}
	p_k \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha + 1)}
	\quad \text{as } k \to \infty.
\end{equation}

By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
    \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
\end{equation}

\subsection{Expected degrees in $\Gbox$ and $\GPo$}\label{ssec:expected_degrees_GPo}

We proceed with the expected degrees in the finite box and Poissonized KPKVB model. Recall the definition of the neighbourhood balls $\BallPon{y}$ and $\BallHyp{y}$ of a point $(0,y)$ in, respectively $\Gbox$ and $\GPo$. We introduce the short hand notation
\[
	\mu_{\Po}(y) := \Mu{\BallHyp{y}} \quad \text{and} \quad \mu_{\mathrm{box}}(y) := \Mu{\BallPon{y}}.
\]
Observe that

Our first results relate these measures to the measure $\mu(y)$ on the infinite model $\Ginf$.

\begin{lemma}[Expected degree given height in $\GPo$]\label{lem:average_degree_P_n}
Let $\alpha > \frac{1}{2}$, $\varepsilon >0$ and $0 \leq y \leq (1-\epsilon)R$. Then as $n \to \infty$, uniformly in $y$,
\[
	\mu_{\Po}(y) = (1+\smallO{1}) \mu(y).
\]
\end{lemma}

\begin{proof}
Recall that when $y^\prime \ge R - y$ then $p^\prime \in \BallHyp{y}$ while for $y^\prime < R - y$ this is true when~\eqref{eq:def_Omega_hyperbolic} holds. We does split the integral for $\mu_{Po,n}(y)$ accordingly, into two integrals $I_1$ and $I_2$,
\begin{align*}
\mu_{\Po}(y) 
&= \int_0^{R-y} 2\Phi(y,y_1)\frac{\alpha\nu}{\pi}e^{-\alpha y_1} dy_1+\int_{R-y}^R \frac{\pi n}{\nu} \frac{\alpha \nu}{\pi}e^{-\alpha y_1}dy_1 =: I_1+I_2.
\end{align*}
Firstly, we will show that the second integral $I_2=o(\mu(y))$ and then we will show that $I_1 = (1+o(1))\mu(y)$ (both with  convergence uniform in $0\leq y\leq (1-\epsilon)R$).

For the second integral $I_2$, we compute
\begin{align*}
I_2 &= \int_{R-y}^R \frac{\pi n}{\nu} \frac{\alpha \nu}{\pi}e^{-\alpha y_1}dy_1 =n(e^{-\alpha(R-y)}-e^{-\alpha R}) =ne^{-\alpha R}(e^{\alpha y} -1) =n^{1-2\alpha}\nu^{2\alpha}(e^{\alpha y} -1). 	%&= o(\xi e^{\frac{y}{2}})=o(\mu(y)).
\end{align*}
To see that $n^{1-2\alpha}\nu^{2\alpha}(e^{\alpha y} -1) = o(\mu(y))$, recall that $\mu(y)=\xi e^{\frac{y}{2}}$. So, we need to show that
\begin{align*}
\frac{n^{1-2\alpha}\nu^{2\alpha}(e^{\alpha y} -1)}{\xi e^{\frac{y}{2}}} = o(1)
\end{align*}
or equivalently that
\begin{align*}
\frac{e^{\alpha y}-1}{\xi e^{\frac{y}{2}}}=\smallO{n^{2\alpha-1}}.
\end{align*}
For this, note that
\begin{align*}
\frac{e^{\alpha y}-1}{\xi e^{\frac{y}{2}}}=\bigO{e^{\alpha y-\frac{y}{2}}} = \bigO{e^{\left(\alpha-\frac{1}{2}\right)y}}.
\end{align*}
As $y \leq (1-\epsilon)R =(1-\epsilon)2\ln \frac{n}{\nu}$ and $\alpha > \frac{1}{2}$, we have 
\[
	e^{\left(\alpha-\frac{1}{2}\right)y} \leq e^{\left(\alpha-\frac{1}{2}\right)(1-\epsilon)R} = \left(\frac{n}{\nu}\right)^{2\left(\alpha-\frac{1}{2}\right)(1-\epsilon)} = \smallO{n^{2\alpha-1}},
\]
where the convergence is uniform in $y$, $0\leq y\leq (1-\epsilon)R$, as the last upper bound does not depend on $y$.

For the first integral $I_1$, we first recall from Lemma~\ref{lem:asymptotics_Omega_hyperbolic} that there is a positive constant $K$ such that for any $\varepsilon >0$, for all $y_1, y_2 \in [0,(1-\varepsilon)R]$, $y_1+y_2 <R$, we have (for $\Phi(y_1,y_2)$ from Equation~\ref{eq:def_Omega_hyperbolic})
\[
	e^{\frac{1}{2}(y_1+y_2)} - Ke^{\frac{3}{2}(y_1+y_2)-R} \leq \Phi(y_1,y_2) \leq e^{\frac{1}{2}(y_1+y_2)} + Ke^{\frac{3}{2}(y_1+y_2)-R}.
\]
Thus we define a main and error term of $I_1$ as
\begin{align*}
I_{1,main} &=\int_0^{R-y} 2e^{\frac{y+y_1}{2}}\frac{\alpha\nu}{\pi}e^{-\alpha y_1}dy_1, \\
I_{1,error} &= \int_0^{R-y} 2Ke^{\frac{3}{2}(y+y_1)-R} \frac{\alpha\nu}{\pi} e^{-\alpha y_1} dy_1.
\end{align*}
From the error bounds for $\Phi$ as given in Lemma~\ref{lem:asymptotics_Omega_hyperbolic}, it follows that
$$I_{1,main}-I_{1,error} \leq I_1 \leq I_{1,main}+I_{1,error}. $$
We will firstly show that $I_{1,main} =(1+o(1))\mu(y) $ and then that $I_{1,error} = o(\mu(y))$.

For the main term, we obtain, as $R-y \geq \epsilon R \rightarrow \infty$, uniformly in $0\leq y\leq (1-\epsilon)R$,
\begin{align*}
I_{1,main} &= \int_0^{R-y} 2e^{\frac{y+y_1}{2}}\frac{\alpha\nu}{\pi}e^{-\alpha y_1}dy_1 
		= \frac{2\alpha\nu}{\pi}e^{\frac{y}{2}}\int_0^{R-y} e^{\left(\frac{1}{2}-\alpha\right)y_1}dy_1\\
	&=\frac{2\alpha\nu}{\pi\left(\alpha-\frac{1}{2}\right)}e^{\frac{y}{2}}
		\left(1-e^{\left(\frac{1}{2}-\alpha\right)(R-y)}\right)
		=(1+o(1))\xi e^{\frac{y}{2}} = (1+o(1))\mu(y).
\end{align*}
%\PvdH{It is not clear to the reader what the error term is. Please be specific, for example writing it out and using equation numbers.}

For the error term, we obtain, for $\alpha \not = \frac{3}{2}$, uniformly in $0\leq y\leq (1-\epsilon)R$,
\begin{align*}
I_{1,error}=\int_0^{R-y} 2Ke^{\frac{3}{2}(y+y_1)-R} \frac{\alpha\nu}{\pi} e^{-\alpha y_1} dy_1 &= 2K\frac{\alpha\nu}{\pi} e^{\frac{3}{2}y-R} \int_0^{R-y} e^{\left(\frac{3}{2}-\alpha\right)y_1}dy_1 \\
&= \frac{2K\alpha\nu}{\pi\left(\frac{3}{2}-\alpha\right)}e^{\frac{3}{2}y-R} \left(e^{\left(\frac{3}{2}-\alpha\right)(R-y)}-1\right)\\
&= \frac{2K\alpha\nu}{\pi\left(\frac{3}{2}-\alpha\right)}e^{\frac{1}{2}y} \left(e^{\left(\frac{1}{2}-\alpha\right)(R-y)}-e^{-(R-y)}\right) =o\left(\xi e^{\frac{y}{2}}\right).
\end{align*}
For the error term with $\alpha=\frac{3}{2}$, uniformly in $0\leq y\leq (1-\epsilon)R$,
\begin{align*}
\int_0^{R-y} 3Ke^{\frac{3}{2}(y+y_1)-R} \frac{\nu}{\pi} e^{-\frac{3}{2} y_1} dy_1 &= 3K\frac{\nu}{\pi} e^{\frac{3}{2}y-R} \int_0^{R-y} dy_1 = \frac{3K\nu}{\pi}e^{\frac{3}{2}y-R} (R-y) =o\left(\xi e^{\frac{y}{2}}\right).
\end{align*}
We conclude that $I_{1,error} = o(\mu(y))$ and hence $I_{1,main}\pm I_{1,error} = (1+o(1))\mu(y)$, which finishes the proof.
\end{proof}

\begin{lemma}[Expected degree given height in $\Gbox$]\label{lem:average_degree_G_box}
Let $\alpha > \frac{1}{2}$, $\varepsilon >0$ and $0 \leq y \leq (1-\epsilon)R$. Then as $n \to \infty$, uniformly in $y$,
\[
	\mu_{\mathrm{box}}(y) = (1+\smallO{1}) \mu(y).
\]
\end{lemma}

\begin{proof}
First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R}{2}}, \frac{\pi}{2}e^{\frac{R}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$. We then have that the boundaries of $\BallPon{p}$ are given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$, which intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R}{2}}, \frac{\pi}{2}e^{\frac{R}{2}}]$ at height
\[
	h(y) = R + 2 \log\left(\frac{\pi}{2}\right) - y.
\]
Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R$ of the box $\Rcal$ while in the other case the full region of the box above $h(y)$ is connected to $p$.

We will first consider the case where $y \le 2 \log(\pi/2)$. Here we have
\begin{align*}
	\mu(\BallPon{p})
	&= \int_0^{R} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
	&= \mu(y)\left(1 - e^{-(\alpha - \frac{1}{2})R}\right),
\end{align*}
where the error term is $\smallO{1}$, uniformly in $y$.

Now let $y > 2 \log(\pi/2)$ and recall that $\mu(y) = \xi e^{\frac{y}{2}}$ where $\xi = \frac{4\alpha \nu}{(2\alpha - 1)\pi}$. Then, after some simple algebra, we have that
\begin{align*}
	\mu_{\mathrm{box}}(y)
	&= \int_0^{h(y)} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime
		+ \int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{h(y)} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime
		+ \alpha \nu e^{\frac{R}{2}} \int_{h(y)}^{R} e^{-\alpha y^\prime} \, dy^\prime \\
	&= \xi e^{\frac{y}{2}}\left(1 - \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} 
		e^{-(\alpha - \frac{1}{2})(R - y)}\right)
	+ \nu e^{\frac{R}{2}}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} e^{-\alpha(R - y)} 
		- e^{-\alpha R}\right)\\
	&= \mu(y)\left(1 - \phi_n(y) \right).
\end{align*}
where 
\[
	\phi_n(y) :=  \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} \hspace{-3pt} e^{-(\alpha - \frac{1}{2})(R - y)}
				+ \frac{\nu}{\xi}e^{-(\alpha - \frac{1}{2})R - \frac{y}{2}} - \frac{\nu}{\xi}\left(\frac{\pi}{2}\right)^{-2\alpha} e^{-(\alpha-\frac{1}{2})(R - y)}.
\]
Since $R - y \ge \varepsilon R$ we have that $|\phi_n(y)|$ is uniformly bounded by
$\bigO{e^{-(\alpha - \frac{1}{2})\varepsilon R}}$, which is $\smallO{1}$ for $\alpha > \frac{1}{2}$. 
\end{proof}

We can now use a concentration of heights argument to show that the integration of the Poisson probabilities $\Prob{\Po(\mu_{\Po}(y)) = k_n}$ over $0 \le y \le (1-\varepsilon) R$ is asymptotically equivalent to $p_{k_n}$. And the same holds if we instead consider $\mu_{\mathrm{box}}(y)$.

\begin{lemma}\label{lem:degree_integral}
Let $0 < \varepsilon < 1$. Then for all $0 \le k_n \le n - 1$, as $n \to \infty$,
\begin{equation}\label{eq:degree_integral_BallHyp}
	\int_0^{(1-\varepsilon)R} \Prob{\Po(\Mu{\BallHyp{y}} = k_n} \alpha e^{-\alpha y} \dd y
	= (1+\smallO{1}) p_{k_n},
\end{equation}
where
\begin{equation}\label{eq:def_average_degree_Gbox_phi}
	p_{k_n} = \int_0^\infty \Pee(Po(\xi e^{\frac{y}{2}})=k_n)\alpha e^{-\alpha y}dy.
\end{equation}
Moreover, the same holds if we replace $\Mu{\BallHyp{y}}$ with $\Mu{\BallPon{y}}$ in~\eqref{eq:degree_integral_BallHyp}.
\end{lemma}

\begin{proof}
We will show that
\[
	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po,n}(y)) = k_n} \alpha e^{-\alpha y} \dd y
	= (1+o(1))\int_0^\infty \Pee(Po(\xi e^{\frac{z}{2}})=k_n) \alpha e^{-\alpha z} \dd z.
\]
This implies the result because the last integral equals $(1+o(1))2\alpha \xi^{2\alpha} k_n^{-(2\alpha+1)} = (1+o(1))p_{k_n}$.

Define the function $z(y)=2\ln\frac{\mu_{Po,n}(y)}{\xi}$ (note that $z(y)$ is well-defined as $\mu_{Po,n}(y)\geq 0$ and that $z(y)$ is bijective because $\mu_{Po,n}(y)$ is strictly monotone increasing and continuous, see Lemma~3.3. in \cite{gugelmann2012random}). By rearranging, we have that
\begin{align*}
\mu_{Po,n}(y) = \xi e^{\frac{z(y)}{2}}.
\end{align*}
From Lemma~\ref{lem:average_degree_P_n}, it follows that uniformly for all $0\leq y\leq (1-\varepsilon)R$, $\xi e^{\frac{y}{2}} = (1+o(1))\mu_{Po,n}(y) = (1+o(1))\xi e^{\frac{z(y)}{2}}$, and hence that
\begin{align*}
e^{-\alpha y} = (1+o(1))e^{-\alpha z(y)}.
\end{align*}
Next we need a similar result regarding the derivative of $\mu_{\Po}(y)$, i.e.
\[
	\mu_{Po}^\prime(y) = (1+o(1))\frac{1}{2}\mu(y) = (1+o(1))\frac{1}{2}\mu_{Po}(y)
	= (1+\smallO{1}) \mu^\prime(y),
\]
uniformly for $0 \leq  y \leq (1-\varepsilon)R$. This result is given by Lemma~\ref{lem:derivative_mu_Po} in the Appendix. The lemma is placed there since the proof is a straightforward though cumbersome use of function analysis and we do not want to break the flow of the argument.

We now have that
\[
	z^\prime(y) = \frac{2\mu_{Po}^\prime(y)}{\mu_{Po,n}(y)} = 1+o(1).
\]
which implies that
\begin{align*}
	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po}(y))=k_n} \alpha e^{-\alpha y}dy 
	= (1+o(1)) \int_0^{(1-\varepsilon)R} \Prob{\Po(\xi e^{\frac{z(y)}{2}})=k_n}\alpha e^{-\alpha z(y)} z^\prime(y) dy.
\end{align*}
We now apply integration by substitution to the integral, i.e. use the new variable $z=z(y)$, to obtain 
\begin{align*}
	\int_{z(0)}^{z((1-\varepsilon)R)} \Prob{\Po(\xi e^{\frac{z}{2}})=k_n}\alpha e^{-\alpha z} dz
	= \int_{z(0)}^{z((1-\varepsilon)R)} \Prob{\Po(\mu(z))=k_n}\alpha e^{-\alpha z} dz.
\end{align*}

Note that since the function $y \mapsto 2\ln \frac{y}{\xi}$ is monotone increasing it follows that for large enough $n$, 
$\Kcal_C(k_n)\subset [z(0),z((1-\epsilon)R)]$. Therefore, by a concentration of heights argument (Proposition~\ref{prop:concentration_height_general}) it follows that
\begin{align*}
	\int_{z(0)}^{z((1-\varepsilon)R)} \Prob{\Po(\xi e^{\frac{z}{2}})=k_n}\alpha e^{-\alpha z} dz 
	&= (1+o(1))\int_0^\infty \Pee(Po(\mu(z))=k_n)\alpha e^{-\alpha z}dz.
\end{align*}
and hence
\[
	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po}(y))=k_n} \alpha e^{-\alpha y}dy
	= (1+o(1))\int_0^\infty \Pee(Po(\mu(z))=k_n)\alpha e^{-\alpha z}dz,
\]
which finishes the proof for $\mu_{Po}(y)$.

The proof for $\mu_{\mathrm{box}}(y)$ follows similar arguments. First, we define $z(y) = 2 \log (\mu_{\mathrm{box}}(y)/\xi)$ and use Lemma~\ref{lem:average_degree_G_box} instead of Lemma~\ref{lem:average_degree_P_n} to establish that $e^{-\alpha y} = (1+\smallO{1})e^{-\alpha z(y)}$. For the derivative $z^\prime(y)$ we recall from the proof of Lemma~\ref{lem:average_degree_G_box} that $\mu_{\mathrm{box}}(y) = (1 + \phi_n(y)) \mu(y)$ with $\phi_n(y)$ given by~\eqref{eq:def_average_degree_Gbox_phi}. The derivative of $\phi_n(y)$ can be uniformly bounded by $\smallO{1}$ for $0 \le y \le (1-\varepsilon)R$. Hence we get $\mu_{\mathrm{box}}^\prime(y) = (1+\smallO{1}) \mu^\prime(y)$ and thus $z^\prime(y) = 1 + \smallO{1}$ uniformly for $0 \le y \le (1-\varepsilon)R$. We can now apply the same change of variables to arrive at the required statement.

\end{proof}

The main result of this section now follows almost immediately.

\begin{lemma}[First moment of number of degree $k$ vertices]\label{lem:expnnkn}
Let $N_{Po}(k)$ and $\Nbox(k)$ denote the number of vertices with degree $k$ vertices in the poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, respectively. Consider a sequence of integers $k_n\rightarrow\infty$ with $0 \leq k_n \leq n-1$.	If $k_n = O\left(n^{\frac{1}{2\alpha+1}}\right)$, then as $n \to \infty$,
\[
	\Exp{N_{Po}(k_n)} =(1+o(1)) n p_{k_n} \quad \text{and} \quad \Exp{\Nbox(k_n)} =(1+o(1)) n p_{k_n}.
\]
Moreover, if $k_n \gg n^{\frac{1}{2\alpha + 1}}$ then
\[
	\Exp{N_{\Po}(k_n)} = \smallO{1} \quad \text{and} \quad \Exp{\Nbox(k_n)} = \smallO{1}
\]
\end{lemma}

\begin{proof}
We shall consider $\GPo$. The proof of the statements for $\Gbox$ follows using the same arguments and we omit it here.

Let $D_{\Po}(p)$ denote the degree of a node $p \in \GPo$. Then since $N_{Po}(k_n)= \sum_{v\in V(\GPo)}\1_{\{D_{\GPo}(v)=k_n\}}$ and $\Prob{D_{\Po}(p) = k}$ is invariant under translations in the $x$-axis, we can apply the Campbell-Mecke formula to obtain
\begin{align*}
	\Exp{N_{Po}(k_n)} 
	&= \int_0^R \Prob{\Po(\mu_{\Po}(y)) = k_n} \frac{\pi n}{\nu}\frac{\alpha \nu}{\pi} e^{-\alpha y}dy \\
	&=n \int_0^R \Prob{\Po(\mu_{\Po}(y)) = k_n} \alpha e^{-\alpha y}dy \\
	&=n\left( \int_0^{(1-\epsilon)R} \Prob{\Po(\mu_{\Po}(y)) = k_n} \alpha e^{-\alpha y}dy
		+ \int_{(1-\varepsilon)R}^R \Prob{\Po(\mu_{\Po}(y)) = k_n} \alpha e^{-\alpha y}dy \right),
%		\numberthis \label{eq:enpoknsplit}
\end{align*}
where $0 < \varepsilon < 1$ is a constant to be chosen later.
Note that
\begin{align*}
	\int_{(1-\varepsilon)R}^R \Prob{\Po(\mu_{\Po}(y)) = k_n}\alpha e^{-\alpha y}dy 
	\le \int_{(1-\varepsilon)R}^R \alpha e^{-\alpha y}dy 
	= \Theta(e^{-\alpha (1-\varepsilon) R}) = \Theta(n^{-2\alpha(1-\varepsilon)}) .%= o(k_n^{-(2\alpha+1)})
\end{align*}

Now first consider the case where $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$. Then, for $\alpha > \frac{1}{2}$ and $0 < \varepsilon < \frac{1}{2\alpha} - 1$, we have $2\alpha(1-\varepsilon)>1$. Therefore, $\frac{2\alpha (1-\varepsilon)}{2\alpha+1}>\frac{1}{2\alpha+1}$ and thus
$k_n = \bigO{n^{\frac{1}{2\alpha+1}}} = \smallO{n^{\frac{2\alpha(1-\varepsilon)}{2\alpha+1}}}$. This implies that $k_n^{-(2\alpha+1)} \gg n^{-2\alpha(1-\varepsilon)}$ or, stated differently, $\Theta(n^{-2\alpha(1-\varepsilon)}) = \smallO{k_n^{-(2\alpha+1)}}$. The first statement of the lemma now follows from Lemma~\ref{lem:degree_integral}.

When $k_n \gg n^{\frac{1}{2\alpha + 1}}$, Lemma~\ref{lem:degree_integral} implies that
\[
	n \int_0^{(1-\varepsilon)R} \Pee(Po(\mu_{Po}(y))=k_n) \alpha e^{-\alpha y}dy
	= (1+\smallO{1}) n p_{k_n} = \bigO{n k^{-(2\alpha + 1}} = \smallO{1}.
\]
On the other hand,
\[
	n \int_{(1-\varepsilon)R}^R \Pee(Po(\mu_{Po}(y))=k_n) \alpha e^{-\alpha y}dy = \bigO{n^{1 - 2\alpha(1-\varepsilon)}}.
\]
which is $\smallO{1}$ since by our choice $2\alpha(1-\varepsilon) > 1$. Thus the second claim of the lemma follows.
\end{proof}

\subsection{Joint degrees in $\Gbox$ and $\GPo$}\label{ssec:joint_degrees_GPo}

To prove the factorization of higher moments of $N_{\Po}(k_n)$ and $\Nbox(k_n)$ we first have to understand the joint degree distribution in $\GPo$ $\Gbox$, respectively. This subsequently requires us to analyze the joint neighbourhoods of two points $p, p^\prime$ in these models. To explaining the proof strategy we will use the finite box model, since the formulas there are slightly easier. The results for the Poissonized KPKVB model $\GPo$ follow the same idea.

%We start with a general result for near independent Poisson random variables.
%
%\begin{lemma}\label{lem:near_independence_poisson}
%Let $k_n \to \infty$ and $X_1 = \Po(\lambda_1(n))$, $X_2 = \Po(\lambda_2(n))$ and $Y = \Po(\lambda_3(n))$, be three Poisson random variables where $\lambda_3(n) = \bigO{k_n^{1-\varepsilon}}$, for some $0 < \varepsilon < 1$ and for some $C > 0$,
%\[
%	k_n - C\sqrt{k_n \log(k_n)} \le \lambda_i(n) + \lambda_3(n) \le k_n + C\sqrt{k_n \log(k_n)},
%\] 
%for $i = 1,2$.Then, as $n \to \infty$
%\[
%	\Prob{X_1 + Y = k_n, X_2 + Y = k_n} = (1+\smallO{1}) \Prob{X_1 + Y = k_n}\Prob{X_2 + Y = k_n},
%\]
%where the error term $\smallO{1}$ only depends on $k_n, \varepsilon$ and $C$.
%\end{lemma}
%
%The proof can be found in the Appendix. To see how this lemma can be applied

For $r\in \N$ and $p_1, \dots, p_r \in \Rcal$, we write $\Gbox\cup \{p_1,\dots,p_r\}$ for the finite box model obtained by adding $p_1,\dots,p_r$ to the vertex set of the graph and adding all corresponding edges according to the connection rule. Then we define, for any positive integer $s$ and $V \subset \{p_1,\dots,p_s\}$,
\begin{equation}\label{eq:def_joint_degree_distribution}
\varphi_{\mathrm{box}}(V, k ; p_1,\dots,p_s) = \Prob{\text{every }p\in V\text{ has degree }k\text{ in }\Gbox \cup \{p_1,\dots,p_s\}}.
\end{equation}
In particular, for two points $p, p^\prime \in \Rcal$ and $V = \{p,p^\prime\}$, $\varphi_{\mathrm{box}}(V, k ;p,p^\prime)$ is the joint degree distribution of $p, p^\prime $ in $\Gbox$. We will use similar notation for the Poissonize KPKVB model. That is, $\GPo \cup \{p_1,\dots,p_r\}$ denotes the Poissonized KPKVB model obtained by adding $p_1,\dots,p_r$ to the vertex set of the graph and adding all corresponding edges and $\varphi_{\Po}(V, k ; p_1,\dots,p_s)$ the corresponding joint degree function.

If we define,
\begin{align*}
	X_1(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p}\setminus \BallPon{p^\prime}}\right),\\
	X_2(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p^\prime}\setminus \BallPon{p}}\right),\\
	Y(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p} \cap \BallPon{p^\prime}}\right)
\end{align*}
then each of these are independent Poisson random variables, while
\[
	\varphi_{\mathrm{box}}(\{p,p^\prime\}, k ;p,p^\prime) 
	= \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k_n, X_2(p,p^\prime) + Y(p,p^\prime) = k_n}.
\]
Recall the definition of $y_{k_n,C}^\pm$ from equation~\eqref{eq:def_y_k_C}. We will show (see Lemma~\ref{cor:expected_common_neighbours_Ecal_set}) that for any two points $p, p^\prime$ whose $y$-coordinate is in $[y_{k_n, C}^-, y_{k_n,C}^+]$ and whose $x$-coordinates are sufficiently separated, it holds that $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$. Since the mean of $X_1$ and $X_2$ for such two points is $k_n$, the contribution of the Poisson random variable $Y(p,p^\prime)$ to theirs degrees becomes negligible as $k_n \to \infty$ and hence the joint degree distribution will factorizes on this set. The main idea is that if $p$ and $p^\prime$ are sufficiently separated in the $x$-direction, then the overlap of their neighbourhoods $\BallPon{p} \cap \BallPon{p^\prime}$ is of smaller order than $\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}$. We now proceed with analyzing theses joint neighbourhoods.

Let $p, p^\prime \in \Rcal$ and denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of common neighbours of $p$ and $p^\prime$ in $\Gbox \cup \{p,p^\prime\}$. We shall establish an upper bound on the expected number of joint neighbours when $p$ and $p^\prime$ are sufficiently separated. Observe that $\Exp{\Ncal_{\text{box}}(p,p^\prime)} = \Mu{\BallPon{p} \cap \BallPon{p^\prime}}$.

\begin{figure}[!ht]
\centering
\begin{tikzpicture}

	\pgfmathsetmacro{\u}{0} %0
	\pgfmathsetmacro{\v}{1} %1
	\pgfmathsetmacro{\uu}{4.5} %1.4
	\pgfmathsetmacro{\vv}{0.5} %0.8
	\pgfmathsetmacro{\r}{6}
	\pgfmathsetmacro{\t}{4}

	%The box \Rcal
	\draw[line width=1pt] (-\r,0) -- (\r,0) -- (\r,\t) -- (-\r,\t) -- (-\r,0);

    \draw node[fill, circle, inner sep=0pt, minimum size=5pt] at (\u,\v) {};
    \draw node at (-0.2,1.3) {$p$};

    \draw node[fill,blue, circle, inner sep=0pt, minimum size=5pt] at (\uu,\vv) {};
    \draw node at (4.3,0.2) {\color{blue}$p^\prime$};

	\draw[domain=1.6487:6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(\x)-1});
    \draw[domain=-1.6487:-6,smooth,variable=\x,black,line width=1pt] plot (\x, {2*ln(-\x)-1});
    \draw[domain=5.7840:6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x-4.5)-0.5});
    \draw[domain=3.2160:-5,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(4.5-\x)-0.5});
    \draw[domain=2:-6,smooth,variable=\x,blue,line width=1pt] plot (\x, {2*ln(\x+7.5)-0.5});

    \draw [decorate,decoration={brace},line width=1pt] (3.2160,-0.1) -- (1.6487,-0.1);
    \draw node at (2.5,-0.45) {$d(p,p^\prime)$};

%    \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
%    \draw node at (2.5298,2) {$\hat{x}(p,p^\prime)$};

    %Define intersection left black and shifted blue curve
    \pgfmathsetmacro{\vast}{2*ln((2*\r - \uu)/(exp(\v/2) + exp(\vv/2)))}
    \pgfmathsetmacro{\uast}{(\uu - 2*\r)/(1+exp((\vv-\v)/2))}
    %Define intersection right black and left blue curve
    \pgfmathsetmacro{\vvast}{2*ln((\uu)/(exp(\v/2) + exp(\vv/2)))}
    \pgfmathsetmacro{\uuast}{(\u*exp(\vv/2) + \uu*exp(\v/2))/(exp(\v/2) + exp(\vv/2))}
    \pgfmathsetmacro{\h}{2*ln(\r)-\v}
%    \draw[dotted,thick,black] (4.5208,2.0174) -- (4.5208,0);
%    \draw[dotted,thick,black] (4.5208,2.0174) -- (6,2.0174);

%    \draw node at (4.5208,-0.5) {$w_x(p,p^\prime)$};
%    \draw node at (7,2.0174) {$w_y(p,p^\prime)$};

    \draw node at (\r+0.5,\h) {$h(y)$};

    \draw node at (2.3,3.6) {\color{blue}$x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}}$};
    \draw node at (-1,2) {\color{blue}$x_1 = x^\prime - e^{\frac{y^\prime + y_1}{2}}$};
    \draw node at (-4.5,2.9) {$x_1 = x - e^{\frac{y + y_1}{2}}$};
    \draw node at (4.5,2.9) {$x_1 = x + e^{\frac{y + y_1}{2}}$};

	\draw[dashed,black,line width=1pt] (-\r,\vast) -- (\uast,\vast);
	\draw node at (-\r-1,\vast) {\color{black}$\hat{y}_{\text{left}}(p,p^\prime)$};
	\draw[dashed,line width=1pt] (\uast,\vast) -- (\uast,0);
	\draw node at (\uast,-0.5) {$\hat{x}_{\text{left}}(p,p^\prime)$};

	\draw[dashed,black,line width=1pt] (-\r,\vvast) -- (\r,\vvast);
	\draw node at (\r+1,\vvast) {\color{black}$\hat{y}_{\text{right}}(p,p^\prime)$};
	\draw[dashed,line width=1pt] (\uuast,\vvast) -- (\uuast,\vvast+1);
	\draw node at (\uuast,\vvast+1.2) {$\hat{x}_{\text{right}}(p,p^\prime)$};

\end{tikzpicture}
\caption{Schematic representation of the neighbourhoods of $p$ and $p^\prime$ in $\Gbox$ when $|x - x^\prime| > e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$ used for the proof of Lemma \ref{lem:common_neighbours_Pcal_n}. Note that although here $p^\prime \notin \BallPon{p}$, this is not true in general. This situation was merely chosen to improve readability of the figure.}
\label{fig:representation_disjoint_neighbourhoods_P_n_3}
\end{figure}

We start by analyzing the shape of joint neighbourhood. Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$. To understand the computation it is helpful to have a picture. Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n_3} shows such an example. There are several different quantities that are important. The first are the heights where the left and right boundaries of the ball $\BallPon{p}$ hit the boundaries of the box $\Rcal$. Since $x = 0$ these heights are the same and we denote their common value by $h(y)$. We also need to know the coordinates $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ of the intersection of the right boundary of the neighbourhood of $p$ with the left boundary of the neighbourhood of $p^\prime$ and those for the intersection of the left boundary of the neighbourhood of $p$ with the right boundary of the neighbourhood of $p^\prime$, which we denote by $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$. Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighbourhoods do not intersect, as is the case in Figure~\ref{fig:representation_disjoint_neighbourhoods_P_n_3}. The condition $d(p,p^\prime) > 0$ is exactly the right notion for $p$ and $p^\prime$ being sufficiently separated.

Note that $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$ correspond to, respectively, $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ considered in Section~\ref{ssec:missing_triangles}. The derivation of $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ is done in a similar manner and we omit the details here. The full expressions of all these functions are given below for further reference.

\begin{align}
	h(y) &= R - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R}{2}} - x^\prime\right) - y^\prime 
		\label{eq:def_height_right_P_n} \\
%	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
%		\label{eq:def_x_intersection_close_boundaries}\\
%	\iota_y(p,p^\prime) &= 2\log\left(\frac{x^\prime - x}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}\right)
%		\label{eq:def_y_intersection_close_boundaries}\\
	\hat{y}_{\text{right}}(p,p^\prime) &= 2\log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
	\hat{x}_{\text{right}}(p,p^\prime) &= \frac{x^\prime}{1 + 	
		e^{\frac{y^\prime - y}{2}}},\\
	\hat{y}_{\text{left}}(p,p^\prime) &= 2 \log\left(\frac{\pi e^{R/2} - x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),\\
	\hat{x}_{\text{left}}(p,p^\prime) &= \frac{x^\prime - \pi e^{R/2}}{1 + e^{\frac{y^\prime - y}{2}}}, \\
	d(p,p^\prime) &= |x - x^\prime|_n - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
	\label{eq:def_d_p_p_prime}
\end{align}

The following result shows that if $d(p,p^\prime) > 0$, then the expected number of common neighbours is $\smallO{\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}}$.

\begin{lemma}\label{lem:common_neighbours_Pcal_n}
Let $p, p^\prime \in \Rcal$. Then, whenever $|x - x^\prime|_n > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)$,
\[
	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \Mu{\BallPon{p}}
	\left(\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}  
	+ \frac{\nu}{\xi} e^{-(\alpha - \frac{1}{2})(R-y)}\right).
\]
\end{lemma}

\begin{proof}
Again, without loss of generality we assume that $p = p_0 = (0,y)$ and $p^\prime = (x^\prime, y^\prime)$ with $0 \le x^\prime \le \frac{\pi}{2} e^{R/2}$. Note that since $0 < x^\prime \le \frac{\pi}{2} e^{R/2}$,$ \hat{y}_{\mathrm{right}}(p,p^\prime) \le \hat{y}_{\mathrm{left}}(p,p^\prime)$. We write $\hat{y}$ for $\hat{y}_{\mathrm{right}}(p,p^\prime)$ and observe that below $\hat{y}$ the balls $\BallPon{p}$ and $\BallPon{p^\prime}$ are disjoint. Therefore, if we define $A := \left\{p_1 = (x_1,y_1) \in \Rcal \cap \BallPon{p} \, : \, y_1 \ge \hat{y} \right\}$. Then
\[
	\Exp{\Ncal_{\text{box}}(p,p^\prime)} \le \Mu{A}.
\]
We proceed with computing the right hand side
\begin{align*}
	\Mu{A} &= \int_{\hat{y}}^{h(y)} 
		\int_{- e^{\frac{y + y_1}{2}}}^{e^{\frac{y^\prime+y_1}{2}}} 
		f(x_1,y_1) \dd x_1 \dd y_1
		+ \int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{R/2}}^{\frac{\pi}{2} e^{R/2}} 
		\hspace{-10pt}  f(x_1,y_1) \dd x_1 \dd y_1 \\
	&= \frac{2\alpha \nu}{\pi}e^{\frac{y}{2}}
		\int_{\hat{y}}^{h(y)} e^{-(\alpha - \frac{1}{2})y_1} \dd y_1 
		+ \alpha \nu e^{R/2} \int_{h(y)}^R e^{-\alpha y_1} \dd y_1\\
	&\le \xi\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) e^{-(\alpha-\frac{1}{2})\hat{y}}
		+ \nu e^{R/2} e^{-\alpha h(y)} \\
	&= \Mu{\BallPon{p}}\left(
		e^{-(\alpha-\frac{1}{2})\hat{y}} + \frac{\nu}{\xi} e^{-(\alpha - \frac{1}{2})(R-y)}\right).
\end{align*}
The result follows by plugging in 
\[
	\hat{y} := \hat{y}_{\text{right}}(p,p^\prime) = 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right),
\]
and noting that $x^\prime$ is the same as $|x - x^\prime|$, by our generalization step.

\end{proof}

We can also prove a similar result for the Poissonized KPKVB model $\GPo$, denoting by $\Ncal_{\Po}(p,p^\prime)$ the number of joint neighbours in $\GPo \cup \{p,p^\prime\}$.

\begin{lemma}\label{lem:common_neighbours_KPKVB}
Let $0 < \varepsilon < 1$, $p, p^\prime \in \Rcal$ with $y,y^\prime \le (1-\varepsilon)R$ and denote by $\Ncal_{\Po}(p,p^\prime)$ the number of joint neighbours of $p, p^\prime$ in $\GPo$. Then, whenever $|x - x^\prime|_n > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)\left(1 + \frac{\pi^2 K}{4}\right)$,
\[
	\Exp{\Ncal_{\Po}(p,p^\prime)} \le \Mu{\BallHyp{p}}
	\left(e^{(2\alpha - 1)\lambda} \left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}  
	+ \frac{\nu}{\xi} e^{-(\alpha - \frac{1}{2})(R-y)}\right),
\]
where
\[
	\lambda = \log\left(1 + \frac{\pi^2 K}{4}\right),
\]
with $K$ the constant from Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
\end{lemma}

\begin{proof}
We will proceed in a similar fashion as for Lemma~\ref{lem:common_neighbours_Pcal_n}. That is we will bound the expected number of common neighbours by the number of neighbors of $p$ whose $y$-coordinate is above the intersection of the right boundary of $\BallHyp{p}$ and the left boundary of $\BallHyp{p^\prime}$. Denote by $\hat{y}$ the height of this intersection point. Then
\begin{align*}
	\Exp{\Ncal_{\Po}(p,p^\prime)} &\le \frac{2\alpha \nu}{\pi} \int_{\hat{y}}^{R-y} \Phi(y,y_1) e^{-\alpha y_1} \dd y_1
		+ \alpha \nu e^{R/2} \int_{R-y}^{R} e^{-\alpha y_1} \dd y_1.
\end{align*} 
The second integral is bounded by $\frac{\nu}{\xi} \Mu{\BallPon{y}} e^{-(\alpha - \frac{1}{2})(R-y)}$. We bound the first integral using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} as
\begin{align*}
	\frac{2\alpha \nu}{\pi} \int_{\hat{y}}^{R-y} \Phi(y,y_1) e^{-\alpha y_1} \dd y_1
	&\le \frac{2\alpha \nu}{\pi} \int_{\hat{y}}^{R-y} \left(e^{\frac{y+y_1}{2}} + K e^{\frac{3}{2}(y + y_1)-R}\right) 
		e^{-\alpha y_1} \dd y_1 \\
	&\le \frac{2\alpha \nu}{\pi} (1+K)e^{\frac{y}{2}} \int_{\hat{y}}^{R-y} e^{-(\alpha - \frac{1}{2}) y_1} \dd y_1\\
	&\le (1 + K)\Mu{\BallPon{p}}  e^{-(\alpha - \frac{1}{2})\hat{y}},
\end{align*}
where we used that $\frac{3y_1}{2} \le R - y + \frac{y_1}{2}$ for all $y_1 \le R-y$ for the second line.

It remains to compute $\hat{y}$, for which we will establish the following bound
\begin{equation}\label{eq:joint_neighbors_KPKVB_intersection}
	\hat{y} \ge 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right) - 2\lambda.
\end{equation}

To show~\eqref{eq:joint_neighbors_KPKVB_intersection} we note that for any point $y_1 \ge \hat{y}$, the corresponding $x$-coordinate of the left boundary of $\BallHyp{p^\prime}$ must be to the left of that of the ball $\BallHyp{p}$, i.e.
$x^\prime - \Phi(y^\prime, y_1) \le \Phi(y,y_1)$. Therefore it is enough to show that for all 
\[
	y_1 \le 2 \log\left(\frac{x^\prime}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right) - 2\lambda
\]
it holds that $\Phi(y,y_1) \le x^\prime - \Phi(y^\prime, y_1)$, with $\lambda$ as defined in the statement of the lemma. Note that by assumption on $|x - x^\prime|$ the above upper bound is non-negative. Using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} it suffices to prove that for all such $y_1$,
\[
	e^{\frac{y + y_1}{2}} + K e^{\frac{3}{2}(y + y_1) - R} \le x^\prime - e^{\frac{y^\prime + y_1}{2}}
	- K e^{\frac{3}{2}(y^\prime + y_1) - R},
\]
which is equivalent to
\[
	\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) e^{\frac{y_1}{2}} 
	+ K e^{-R} \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)^3 e^{\frac{3 y_1}{2}} \le x^\prime.
\]
Plugging the upper bound for $y_1$ into the left hand side and using that $(e^{y/2} + e^{y^\prime/2})^3 \ge e^{3y/2} + e^{3y^\prime/2}$, we obtain
\begin{align*}
	\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right) e^{\frac{y_1}{2}} 
		+ K e^{-R} \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)^3 e^{\frac{3 y_1}{2}}
	&\le x^\prime e^{-\lambda} + K e^{-R} (x^\prime)^3 e^{-3\lambda}
		\le x^\prime \left(e^{-\lambda} + \frac{\pi^2 K}{4} e^{-3\lambda}\right)\\
	&\le x^\prime e^{-\lambda} \left(1 + \frac{\pi^2 K}{4}\right) = x^\prime,
\end{align*} 
where we also used that $x^\prime \le \frac{\pi}{2} e^{-R/2}$.
\end{proof}

Recall the definition of the stripe $\stripknc = \Rcal \cap (\R_+ \times [y_{k_n,C}^-, y_{k_n,C}^+])$ from~\eqref{eq:def_stripe} and define, for any $0 < \varepsilon < 1$, the following set
\begin{equation}\label{eq:def_joint_degree_set_E_growing_k}
	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \stripknc
		\, : \,  |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}, 
\end{equation}
where $|x|_n = \min\{|x|, \pi e^{R/2} - |x|\}$ denotes the norm on the finite box $\Rcal$ where the left and right boundaries are identified. Then for any two points $p,p^\prime \in \mathcal{E}_\varepsilon(k_n)$ the expect number of joint neighbours is $\smallO{k_n}$.

\begin{lemma}\label{cor:expected_common_neighbours_Ecal_set}
Fix $0 < \varepsilon < 1$ and let $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. Then for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, as $n \to \infty$,
\[
	\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}.
\] 
\end{lemma}

\begin{proof}
Since for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$ we have $\Mu{\BallPon{p}}, \Mu{\BallPon{p^\prime}} = \bigT{k_n}$, Lemma~\ref{lem:common_neighbours_Pcal_n} implies that
\[
	\Mu{\BallPon{p} \cap \BallPon{p^\prime}} \le \bigO{k_n} \phi_n(p,p^\prime),
\]
where
\[
	\phi_n(p,p^\prime) = 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
		+ \frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
		e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
		+ \frac{\nu e^{-(\alpha - \frac{1}{2})R}}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}. 
\]
We thus need to show that $\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon}}$. For $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, it holds that $e^{y/2}, e^{y^\prime/2} = \bigT{k_n}$ and $|x - x^\prime| > k_n^{1+\varepsilon}$ and hence
\begin{align*}
	 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
	 =	\bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
\end{align*}
For the second term in $\phi_n(p,p^\prime)$ we use that $e^{\alpha y^\ast} = \bigT{k_n^{2\alpha}}$ and $e^{R} = \bigT{n^2}$ to obtain
\[
	\frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
			e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)}
	= \bigO{1} n^{-(2\alpha - 1)} k_n^{2\alpha - 1} = \bigO{n^{-(\alpha - \frac{1}{2})}}.
\]
Finally, the third term satisfies $\bigO{n^{-(2\alpha - 1)}k_n^{-1}}$, and we conclude that
\[
	\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon(2\alpha - 1)} + n^{-(\alpha - \frac{1}{2})}
	+ n^{-(2\alpha - 1)}k_n^{-1}} = \bigO{k_n^{-\varepsilon^\prime}},
\]
where we used that $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. 
\end{proof}

It is clear that using Lemma~\ref{lem:common_neighbours_KPKVB} instead of Lemma~\ref{lem:common_neighbours_Pcal_n}, the above proof applies to the Poissonized KPKVB model, yielding the following result.

\begin{lemma}\label{cor:expected_common_neighbours_KPKVB}
Fix $0 < \varepsilon < 1$ and let $\varepsilon^\prime = \min\{\varepsilon(2\alpha - 1),\varepsilon\}$. Then for all $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, as $n \to \infty$,
\[
	\Mu{\BallHyp{p} \cap \BallHyp{p^\prime}} = \bigO{k_n^{1-\varepsilon^\prime}}.
\] 
\end{lemma}

Let us now define the \emph{stripe}
\begin{equation}\label{eq:def_stripe}
	\stripknc = \Rcal \cap (\R_+ \times \Kcal_C(k_n)).
\end{equation} 
Consider a fixed number of points $p_1, \dots, p_r$. Then, if their $x$-coordinates are sufficient far apart and their $y$ coordinates lie with in the strip $\stripknc$, their degrees are asymptotically independent.

\begin{lemma}[Asymptotic factorization of degree probabilities]\label{lem:probdegFact}
Let $C, C^\prime>0$ and $r,s$ be positive integers with $r+1\leq s$. Fix $0<\varepsilon<1$. Then, it holds uniformly for all $(v_1,\dots,v_s) \in \left(\stripknc\right)^{s} = \stripknc \times \dots \times \stripknc$, satisfying $|x_{v_i}-x_{v_{r+1}}|\geq k_n^{1+\varepsilon}$ for all  $1\leq i \leq r$,  that
\[
	\varphi(\{v_1,\dots,v_{r+1}\};v_1,\dots,v_s)
	=(1+o(1))\varphi(\{v_1,\dots,v_r\};v_1,\dots,v_s)\varphi(\{v_{r+1}\};v_1,\dots,v_s)+\bigO{k_n^{-C^\prime}},
\]
where $\varphi$ is either $\varphi_{\Po}$ or $\varphi_{\mathrm{box}}$.
(Here uniformity means that the $\smallO{1}$ and $\bigO{k_n}$ terms do not depend on $v_1,\dots,v_{s}$.)
\end{lemma}

\begin{proof}
Let $H=\GPo \cup\{p_1,\dots,p_s\}$ or $H=\Gbox \cup \{p_1,\dots,p_s\}$ and $1\leq r\leq s$. For $1\leq j \leq r$, let $Y_j$ be the number of vertices of $H$ which are adjacent to both $p_j$ and $p_{r+1}$. Let $X_j$ be the number of vertices of $H$ which are adjacent to $p_j$, but not to $p_{r+1}$. Then, $X_j+Y_j= D_{H}(p_j)$ is the degree of $p_j$ in $H$.

Now let $X_{r+1}$ be the number of vertices of $H$ which are adjacent to $p_{r+1}$, but to none of $p_1,\dots,p_r$. Let $Y_{r+1}$ be the number of vertices of $H$ which are adjacent to $p_{r+1}$, and at least one of $p_1,\dots,p_r$. Then, $X_{r+1}+Y_{r+1}=D_H(p_{r+1})$ is the degree of $p_{r+1}$ in $H$. By definition, we therefore have
\begin{align*}
\varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s)&=\Prob{X_1+Y_1=\dots=X_{r+1}+Y_{r+1}=k_n}, \\
\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)&=\Prob{X_1+Y_1=\dots=X_r+Y_r=k_n}, \\
\varphi(\{p_{r+1}\};p_1,\dots,p_s)&=\Prob{X_{r+1}+Y_{r+1}=k_n},
\end{align*}
and the claim of the lemma is that
\begin{equation}\label{eq:probdegfact_main}
	\begin{aligned}
		&\Prob{X_1+Y_1=\dots=X_{r+1}+Y_{r+1}=k_n} \\
		&= (1+o(1))\Prob{X_1+Y_1=\dots=X_r+Y_r=k_n}\Prob{X_{r+1}+Y_{r+1}=k_n}+\bigO{k_n^{-C}}.
	\end{aligned}
\end{equation}

To prove~\eqref{eq:probdegfact_main} let $\varepsilon'=\min(\varepsilon,\varepsilon(2\alpha-1))\in (0,1)$. Since for $1\leq i \leq r$, it is given that $|x_{p_i}-x_{p_{r+1}}|\geq k_n^{1+\varepsilon}$, it then follows from Lemma~\ref{lem:common_neighbours_KPKVB} that $\E[Y_j] = \bigO{k_n^{1-\varepsilon'}}$. To prove the result for $\Gbox$ we use Lemma~\ref{lem:common_neighbours_Pcal_n}. The rest of the proof is independent of which of the two models we consider and only uses that $\E[Y_j] = \bigO{k_n^{1-\varepsilon'}}$.

As $Y_{r+1} \leq Y_1+\dots+Y_r$, we also have $\mu:=\Exp{Y_{r+1}} = \bigO{k_n^{1-\varepsilon'}}$. In particular, there is $c_0>0$ such that $c_0\sqrt{k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}}\geq c_1\sqrt{\mu\ln\mu}$ (where $c_1=\sqrt{\frac{2C}{1-\varepsilon'}}$, which is well-defined because $1-\varepsilon'>0$). Now define
\begin{align*}
A_n=[\mu-c_0\sqrt{k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}},\mu+c_0\sqrt{k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}}]\cap \N_0.%=[\mu-c\sqrt{\mu\ln \mu},\mu+c\sqrt{\mu\ln \mu}].
\end{align*}
By equation~\eqref{eq:def_chernoff_bound_poisson_C}, we have
\begin{align*}
	\Prob{Y_{r+1} \not \in A_n} 
	= \Prob{|Y_{r+1}-\mu|\geq c_0\sqrt{k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}}}
	\le \Prob{|Y_{r+1}-\mu|\geq c_1\sqrt{\mu\ln\mu}}
	=\bigO{k_n^{-\frac{(1-\varepsilon')c_1^2}{2}}}.
\end{align*}
As by definition $c_1$ satisfies $\frac{(1-\varepsilon')c_1^2}{2}=C$, this implies that for the event $S_n = \{Y_{r+1}\in A_n\}$,
\[
	\Prob{S_n^c}=\bigO{k_n^{-C}}.
\]
Beginning with the left-hand side of the claim of the lemma, the law of total probability applied to the events $\{Y_{r+1}=y_{r+1}\}$, for all $y_{r+1}\in A_n$, and $S_n^c$ implies that
\begin{align*}
	&\Prob{X_1+Y_1=\dots=X_{r+1}+Y_{r+1}=k_n} \\
	&=\sum_{y_{r+1}\in A_n} \Prob{X_1+Y_1=\dots=X_{r+1}+y_{r+1}=k_n|Y_{r+1}=y_{r+1}}\Prob{Y_{r+1}=y_{r+1}}\\ 
	&\hspace{10pt}+ \Prob{X_1+Y_1=\dots=X_{r+1}+Y_{r+1}=k_n|S_n^c} \Prob{S_n^c}\\
	&=\sum_{y_{r+1}\in A_n} \Prob{X_1+Y_1=\dots=X_{r+1}+y_{r+1}=k_n|Y_{r+1}=y_{r+1}} 
		\Prob{Y_{r+1}=y_{r+1}}+\bigO{k_n^{-C}}.
\end{align*}
As $X_{r+1}$ is independent of $X_1, \dots, X_r, Y_1, \dots, Y_r$ by the properties of a Poisson process (as $X_{r+1}$ counts the number of points in a set which is disjoint to what $X_1,\dots,X_r, Y_1, \dots, Y_r$ are counting), it follows that
\begin{align*}%\label{eq:afterindep}
	&\Prob{X_1+Y_1=\dots=X_{r+1}+Y_{r+1}=k_n} \\
	&=\sum_{y_{r+1} \in A_n} \Prob{X_1+Y_1=\dots=X_{r}+Y_r=k_n|Y_{r+1}=y_{r+1}}
		\Prob{X_{r+1}+y_{r+1}=k_n} \Prob{Y_{r+1}=y_{r+1}}\\
	&\hspace{10pt} +\bigO{k_n^{-C}}.
\end{align*}
We will now show that uniformly for all $y_{r+1}, s \in A_n$, it holds that,
\begin{align}\label{eq:yrp1tos}
	\Prob{X_{r+1}=k_n-y_{r+1}} = (1+o(1))\Prob{X_{r+1}=k_n-s}.
\end{align}
To see this, observe that for all $y_{r+1},s\in A_n$, we have that $|y_{r+1}-s|\leq 2c\sqrt{k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}}$. Denote the expectation of $X_{r+1}$ by $\lambda$, write $\delta_n = k_n-y_{r+1}-\lambda$ and note that
\begin{align*}
	\frac{\Prob{X_{r+1}=k_n-y_{r+1}}}{\Prob{X_{r+1}=k_n-s}} 
	&= \frac{\Prob{X_{r+1}=k_n-y_{r+1}}}{\Prob{X_{r+1}=k_n-y_{r+1}+(y_{r+1}-s)}}\\
	&=\frac{(k_n-y_{r+1}+(y_{r+1}-s))!}{(k_n-y_{r+1})!}\lambda^{s-y_{r+1}}
\end{align*}
We will now use that $\frac{(a+b)!}{a!} = (1+o(1))(a+b)^b$ for $b^2=o(a)$, applied to $a=k_n-y_{r+1}$ and $b=y_{r+1}-s$. To see this auxiliary fact, note that by Stirling's approximation to the factorial, it follows that
\begin{align*}
	\frac{(a+b)!}{a!}=(1+o(1))\frac{(a+b)^{a+b+\frac{1}{2}}e^{-a-b}}{a^{a+\frac{1}{2}}e^{-a}}
	=(1+o(1))\left(1+\frac{b}{a}\right)^{a+\frac{1}{2}}(a+b)^b e^{-b}.
\end{align*}
Since $1+\frac{b}{a}\leq e^{\frac{b}{a}}$, it holds that $(1+\frac{b}{a})^a \leq e^b$. Furthermore, as $\ln(1+x)\geq x-\frac{x^2}{2}$ (for $x\in (-1,1)$), we have that $(1+\frac{b}{a})^a =e^{a\ln(1+\frac{b}{a})}\geq e^{a(\frac{b}{a}-\frac{b^2}{2a})} =e^{b-\frac{b^2}{2a}}=(1+o(1))e^{b}$ because $b^2=o(a)$. Finally, $b^2=o(a)$ also implies that $(1+\frac{b}{a})^\frac{1}{2}=1+o(1)$. This finishes the proof of the auxiliary fact and we can continue with
\begin{align*}
	&=(1+o(1)) (k_n-y_{r+1}+(y_{r+1}-s))^{y_{r+1}-s} \lambda^{s-y_{r+1}} \\
	&=(1+o(1)) (\lambda+\delta_n+(y_{r+1}-s))^{y_{r+1}-s} \lambda^{s-y_{r+1}} \\
	&=(1+o(1))\left(1+\frac{\delta_n+(y_{r+1}-s)}{\lambda}\right)^{y_{r+1}-s} \\
	&=(1+o(1)) e^{\frac{\delta_n(y_{r+1}-s)}{\lambda}} e^{\frac{(y_{r+1}-s)^2}{\lambda}} = 1+o(1),
\end{align*}
where the last line follows since $\delta_n, |y_{r+1}-s| \leq 2c_0\sqrt{k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}}$ and $\lambda=\Theta(k_n)$ and therefore, with convergence uniform in $y_{r+1},s$,
\[
	\frac{\delta_n(y_{r+1}-s)}{\lambda}, \frac{(y_{r+1}-s)^2}{\lambda} \leq \frac{4c_0^2 k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}}{\lambda}  \rightarrow 0.
\]
As $\Prob{S_n^c}=\bigO{k_n^{-C}}$, we have
\begin{align*}
	1=\sum_{s\in A_n}\Prob{Y_{r+1}=s}+\bigO{k_n^{-C}}.
\end{align*}
From~\eqref{eq:yrp1tos}, it then follows that
\begin{align*}
	\Prob{X_{r+1}=k_n-y_{r+1}} 
	&=\Prob{X_{r+1}=k_n-y_{r+1}} \sum_{s\in A_n} \Prob{Y_{r+1}=s}+\bigO{k_n^{-C}}\\
	&= (1+o(1)) \sum_{s\in A_n} \Prob{Y_{r+1}=s} \Prob{X_{r+1}=k_n-s}+\bigO{k_n^{-C}} \\
	&=(1+o(1))\sum_{s\in A_n} \Prob{X_{r+1}+Y_{r+1}=k_n, Y_{r+1}=s}+\bigO{k_n^{-C}} \\
	&=(1+o(1))\Prob{X_{r+1}+Y_{r+1}=k_n, Y_{r+1}\in A_n}+\bigO{k_n^{-C}} \\
	&=(1+o(1))\left(\Prob{X_{r+1}+Y_{r+1}=k_n}-\Prob{X_{r+1}+Y_{r+1}=k_n, Y_{r+1}\not \in A_n}\right)+\bigO{k_n^{-C}} \\
	&=(1+o(1))\Prob{X_{r+1}+Y_{r+1}=k_n}+\bigO{k_n^{-C}}.
\end{align*}
Note that $\Prob{X_{r+1}+Y_{r+1}=k_n}$ no longer depends on $y_{r+1}$ and neither does the $\bigO{k_n^{-C}}$ error term. Therefore we have
\begin{align*}
	&\Prob{X_1+Y_1=\dots=X_{r+1}+Y_{r+1}=k_n} \\
	&\sum_{y_{r+1} \in A_n} \Prob{X_1+Y_1=\dots=X_{r}+Y_r=k_n|Y_{r+1}=y_{r+1}} 	
		\Prob{X_{r+1}+y_{r+1}=k_n}\Prob{Y_{r+1}=y_{r+1}}+\bigO{k_n^{-C}}\\
	&=(1+o(1))\Prob{X_{r+1}+Y_{r+1}=k_n}\sum_{y_{r+1} \in A_n} 	
		\Prob{X_1+Y_1=\dots=X_{r}+Y_r=k_n|Y_{r+1}=y_{r+1}}\Prob{Y_{r+1}=y_{r+1}}\\
	&\hspace{10pt}+\bigO{k_n^{-C}}.
\end{align*}
For the last summation we have
\begin{align*}
	&\sum_{y_{r+1} \in A_n} \Prob{X_1+Y_1=\dots=X_{r}+Y_r=k_n|Y_{r+1}=y_{r+1}}\Prob{Y_{r+1}=y_{r+1}} \\
	&= \Prob{X_1+Y_1=\dots=X_r+Y_r=k_n,Y_{r+1}\in A_n} \\
	&= (1+o(1))\Prob{X_1+Y_1=\dots=X_r+Y_r=k_n}+\bigO{k_n^{-C}}.
\end{align*}
Finally, plugging this into the previous step gives 
\begin{align*}
	&\Prob{X_1+Y_1=\dots=X_{r+1}+Y_{r+1}=k_n} \\
	&=(1+o(1))\Prob{X_{r+1}+Y_{r+1}=k_n}\sum_{y_{r+1} \in A_n} 	
		\Prob{X_1+Y_1=\dots=X_{r}+Y_r=k_n|Y_{r+1}=y_{r+1}}\Prob{Y_{r+1}=y_{r+1}}\\
	&\hspace{10pt}+\bigO{k_n^{-C}} \\
	&=(1+o(1))\Prob{X_{r+1}+Y_{r+1}=k_n}\Prob{X_1+Y_1=\dots=X_r+Y_r=k_n}+\bigO{k_n^{-C}}.
\end{align*}
which establishes~\eqref{eq:probdegfact_main} and thus the claim of the lemma.
\end{proof}

\subsection{Factorial moments of degrees}\label{ssec:factorial_moments_GPo}

Now that we have analyzed the joint neighbourhoods and degree distributions in both the Poissonized KPKVB and finite box model, we can show convergence of the factorial moments of the number of nodes of degree $k$ in both models.

\begin{lemma}[Factorial moments]\label{lem:factmoment}
Recall that $N_{Po}(k)$ denotes the number of degree $k$ vertices in $\GPo$. % and $k_n \rightarrow \infty$ as 
For any positive integer $r$, it holds that
\[
	\Exp{{N_{Po}(k_n) \choose r}} =(1+o(1)) \frac{(\Exp{ N_{Po}(k_n)})^r}{r!}.
\]
\end{lemma}

The proof of this result requires the following technical lemma which states that the integration of the joint degree distribution can be factorized.

\begin{lemma}[Factorization of degrees]
	\label{lem:asympind}
	Let $\varphi$ be either $\varphi_{\mathrm{box}}$ or $\varphi_{\Po}$. Then we have that
	\begin{align*}
	&\int_\Rcal \cdots \int_\Rcal \varphi(\{p_1,\dots,p_r \};p_1,\dots,p_r) 
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r \\
	&= (1+o(1))\left(\int_\Rcal  \varphi(\{p_1\};p_1) f(x,y) \dd x \dd y\right)^r .
	\end{align*}
\end{lemma}

\begin{proof}
Let $C>r(2\alpha+1)$ and define the set $A = (\Rcal \times \cdots \times\Rcal) \backslash (\stripknc \times \cdots\times \stripknc)$. We will first show that the contribution of the integration of $\varphi$ over this range is negligible.

For $(p_1,\dots,p_r) \in (\Rcal \times \cdots \times\Rcal) \backslash (\stripknc \times \cdots\times \stripknc)$, there is a $j$, $1\leq j\leq r$, such that $y_j \not \in [y_{k_n,c}^-,y_{k_n,c}^+]$, so that the Chernoff bound (see in~\ref{eq:chernoff_bound_degrees}) yields that $\Prob{D_{\GPo}(v_j)=k_n } = \bigO{k_n^{-C}}$. As, for $1\leq j\leq r$, the event $\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}$ implies the event $\{D_{\GPo}(v_j)=k_n\}$, it follows that $\Prob{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n} = \bigO{k_n^{-C}}$ and hence,
\begin{align*}
	\int_A \Pee(D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n) f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r  
	= O\left(n^r k_n^{-C}\right).
\end{align*}

Next we note that by the concentration of heights (Proposition~\ref{prop:concentration_height_general}) it follows that
\begin{align*}
	\int_{\stripknc} \varphi(\{p_1\};p_1) f(x,y) \dd x \dd y 
	&= (1+\smallO{1}) \int_\Rcal  \varphi(\{p_1\};p_1) f(x,y) \dd x \dd y
	&= (1+\smallO{1}) 2\alpha \xi^{2\alpha} n k_n^{-(2\alpha + 1)} \numberthis \label{eq:integration_average_degree_stripe}
\end{align*}
Since for $C>r(2\alpha+1)$ it holds that $n^r k_n^{-C} = \smallO{\left(n k_n^{-(2\alpha + 1)}\right)^r}$ it now suffices to show that
\begin{align*}
	&\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r \};p_1,\dots,p_r) 
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r \\
	&= (1+o(1))\left(\int_{\stripknc}  \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r.
\end{align*}

We will prove this using induction. More precisely, for every fixed positive integer $s$, we will show by induction on $r$, $1\leq r\leq s$, that for all $p_{r+1},\dots,p_s \in \stripknc$, it holds that
\begin{align*}
	&\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r\\
	&= (1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r .
\end{align*}
Note that for $r=s$ this the claim of the lemma. Throughout the proof $H$ is either $\GPo \cup\{p_1,\dots,p_s\}$ or $\Gbox \cup \{p_1,\dots,p_s\}$, depending on whether $\varphi$ is, respectively, $\varphi_{\Po}$ or $\varphi_{\mathrm{box}}$.

For $r=1$, we only need to show that uniformly for $p_1 \in \stripknc$,
\begin{align*}
\varphi(\{p_1\};p_1,\dots,p_s) = (1+o(1))\varphi(\{p_1\};p_1).
\end{align*}
To see this, note that as $p_1\in \stripknc$, the expected degree of $p_1$ in $\GPo$ is $\Theta(k_n)$. Assume that $p_1$ is adjacent to $s'<s$ many vertices among $v_2,\dots,p_s$. Then, as $s'<s$ is bounded and $k_n \rightarrow \infty$ as $n\rightarrow \infty$,  we have that
\begin{align*}
\Pee(D_{\GPo}(p_1)=k_n-s') = (1+o(1))\Pee(D_{\GPo}(p_1)=k_n).
\end{align*}
So, we have the base case of the induction,
\begin{align*}
\varphi(\{p_1\};p_1,\dots,p_s)&=\Pee(D_H(p_1)=k_n)
= \Pee(D_{\GPo}(p_1)=k_n-s')\\
&= (1+o(1))\Pee(D_{\GPo}(p_1)=k_n)=(1+o(1))\varphi(\{p_1\};p_1).
\end{align*}
Assuming the claim holds for integer $r <s$, we will show that it holds for $r+1$.

Let $p_{r+2},\dots,p_s\in \stripknc$ (if $r+2>s$, this definition is void and the corresponding points will never be used in the proof).
Fix $0<\epsilon<1$ small enough s.t. $\frac{1}{2}+\epsilon<\alpha$. Define the region that the $(r+1)$-th vertex $p_{r+1}$ is far apart from all other vertices horizontally,
$$\Fcal_\epsilon(k_n)=\{(p_1,\dots,p_{r+1}) \in \left(\stripknc\right)^{r+1}: \forall 1\leq i \leq r: |x_{p_i}-x_{p_{r+1}}|\geq k_n^{1+\epsilon}\}.$$

We will split the integration into this region and its complement $\Fcal_\epsilon(k_n)^c = \left(\stripknc\right)^{r+1} \backslash \Fcal_\epsilon(k_n)$.

Firstly, we derive an upper bound for the complement $\Fcal_\epsilon(k_n)^c$.	Note that $$\varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s) \leq \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)$$
and so,
\begin{align*}
	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s)
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
	&\leq \int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}.
\end{align*}

For $(p_1,\dots,p_{r+1})\in \Fcal_\epsilon(k_n)^c$, we have that $(p_1,\dots,p_r) \in \left(\stripknc\right)^r$ and $p_{r+1}=(x_{r+1},y_{r+1})$ satisfies $y_{k_n,c}^-\leq y_{r+1}\leq y_{k_n,c}^+$ and $x_{r+1}$ falls into an interval $I_n$ of length $2k_n^{1+\epsilon}$.
As the integrand $\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)$ is constant in $x_{r+1}$, we can upper bound the corresponding integration  w.r.t. $\mu_n(dp_{r+1})$ resp. $dy_{r+1}$ as follows,
\begin{align*}
	&\int_{\{(x_{r+1},y_{r+1})\in\stripknc: x_{r+1}\in I_n\}} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s) 
		f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1} \\
	&= \int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \int_{I_n} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)\frac{\alpha \nu}{\pi} e^{-\alpha y_{r+1}} dx_{r+1}dy_{r+1} \\
	&\leq 2k_n^{1+\epsilon} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)\int_{y_{k_n,c}^-}^{y_{k_n,c}^+}  \frac{\alpha \nu}{\pi} e^{-\alpha y_{r+1}} dy_{r+1}.
\end{align*}
Furthermore, we have that
\begin{align*}
\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} e^{-\alpha y_1}dy_1 \leq \int_{y_{k_n,c}^-}^\infty e^{-\alpha y_1}dy_1 = \bigO{e^{-\alpha y_{k_n,c}^-}} = \bigO{\left( \frac{k_n-c\sqrt{k_n\ln k_n}}{\xi}\right)^{-2\alpha}} = \bigO{k_n^{-2\alpha}}.
\end{align*}
We have thus established that
\begin{align*}
	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
	&\leq \bigO{k_n^{1+\epsilon} k_n^{-2\alpha}}\int_{\stripknc} \cdots \int_{\stripknc} 
		\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s) f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}.
\end{align*}
By applying the induction hypothesis to the $r$-fold integral, we obtain the upper bound
\begin{align}\label{eq:indhyp}
&=\bigO{k_n^{1+\epsilon-2\alpha}}\left(\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r .
\end{align}
Finally, we use that $k_n^{1+\epsilon-2\alpha} = \smallO{\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)}$. To see this, we will firstly show that $k_n^{1+\epsilon-2\alpha} = \smallO{nk_n^{-(2\alpha+1)}}$ and then apply~\eqref{eq:integration_average_degree_stripe}, which says that
\begin{align*}
\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1 = \bigT{n k_n^{-(2\alpha+1)}}.
\end{align*}
By our choice of $\epsilon$, we have that $\frac{1}{2}+\epsilon<\alpha$, which implies that $\frac{2+\epsilon}{1+2\alpha}<1$, and hence, using $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$,
\begin{align*}
\frac{k_n^{1+\epsilon-2\alpha}}{nk_n^{-(2\alpha+1)}} = n^{-1} k_n^{2+\epsilon} = \bigO{n^{-1} n^{\frac{2+\epsilon}{1+2\alpha}}} = \smallO{n^{-1}n}= \smallO{1}.
\end{align*}
Having shown that $k_n^{1+\epsilon-2\alpha} = \smallO{\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)}$, we therefore conclude from~\eqref{eq:indhyp} that
\begin{align*}
	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
	&=\smallO{\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)}\left(\int_{\stripknc} \varphi(\{p_1\};p_1) 
		f(x_1,y_1) \dd x_1 \dd y_1\right)^r  \\
	&=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\};p_1)f(x_1,y_1) \dd x_1 \dd y_1\right)^{r+1}}.
\end{align*}

For the integration over $\Fcal_\epsilon(k_n)$, recall that by Lemma~\ref{lem:probdegFact}, $$\varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s)=(1+o(1))\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)\varphi(\{p_{r+1}\};p_1,\dots,p_s)+\bigO{k_n^{-C}}.$$% =(1+o(1)) \varphi(p_1,\dots,p_r)\varphi(y_{r+1}).$$

This implies that
\begin{align*}
	&\int \int_{\Fcal_\epsilon(k_n)} \varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s) 
		 f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
	&=(1+o(1))\int \int_{\Fcal_\epsilon(k_n)} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s) 
		\varphi(\{p_{r+1}\};p_1,\dots,p_s) f(x_1,y_1) \dd x_1 \dd y_1 \cdots \\
	&\hspace{10pt} \times f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
	&\hspace{10pt}+\bigO{k_n^{-C}}\int \int_{\Fcal_\epsilon(k_n)} 
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1} =:M+E.
\end{align*}
To finish the induction step we have to show that
\begin{align*}
M=(1+o(1)) \left(\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)\right)^{r+1}
\end{align*}
and
\begin{align*}
E=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)\right)^{r+1}}.
\end{align*}

For $M$, note that we can factorize to integration over $p_1,\dots,p_r$ and over $p_{r+1}$.

Furthermore, we note that the condition $(p_1,\dots,p_{r+1})\in \Fcal_\epsilon(k_n)$ implies that (writing $p_{r+1}=(x_{r+1},y_{r+1})$) the horizontal coordinate $x_{r+1}$ falls into an interval $I_n$ of length $L_n$, satisfying
\[
	\frac{\pi n}{\nu}-2rk_n^{1+\epsilon}\leq L_n\leq \frac{\pi n}{\nu}-2k_n^{1+\epsilon}.
\]
As $k_n^{1+\epsilon} = \bigO{n^{\frac{1+\epsilon}{2\alpha+1}}} = o(n)$ for $\epsilon<1$ and $\alpha>\frac{1}{2}$, this shows that the length of the integration range in $x_{r+1}$ satisfies $L_n=(1+o(1))\frac{\pi n}{\nu}$. Thus, we have that
\begin{align*}
	M &= (1+o(1))\int_{I_n}\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \varphi(\{p_{r+1}\};p_1,\dots,p_s)
		\frac{\alpha\nu}{\pi} e^{-\alpha y_{r+1}}dy_{r+1}dx_{r+1}\\
	&\hspace{15pt} \times \int_{\stripknc} \cdots \int_{\stripknc} 
		\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}\\
	&=(1+o(1))n\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \varphi(\{p_{r+1}\};p_1,\dots,p_s)\alpha e^{-\alpha y_{r+1}}dy_{r+1}\\
	&\hspace{15pt} \times \int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}\\
	&=(1+o(1))\int_{\stripknc} \varphi(\{p_{r+1}\};p_1,\dots,p_s)\mu_n(dp_1)\\
	&\hspace{15pt} \times\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}.
\end{align*}
By applying the base case of the induction to the first factor and the induction hypothesis to the second one, we have derived that
\begin{align*}
M&=(1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1 \right)^{r+1}.
\end{align*}
Finally, for $E$ we observe that
\begin{align*}
	E=\bigO{k_n^{-C}}\int \int_{\Fcal_\epsilon(k_n)} 
	f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1} 
	= \bigO{k_n^{-C}}(1+o(1))n^{r+1}.
\end{align*}
Recall that again by~\eqref{eq:integration_average_degree_stripe},
\begin{align*}
\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1 = \bigT{n k_n^{-(2\alpha+1)}},
\end{align*}
which implies that
\begin{align*}
\left(\int_{\stripknc} \varphi(\{p_1\};p_1)f(x_1,y_1) \dd x_1 \dd y_1\right)^{r+1} 
= \bigT{n^{r+1}k_n^{-r(2\alpha+1)}}.
\end{align*}
For $C>r(2\alpha+1)$, we can conclude that indeed
\begin{align*}
E = \bigO{n^{r+1}k_n^{-C}}=\smallO{n^{r+1}k_n^{-r(2\alpha+1)}}=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)\right)^{r+1}}.
\end{align*}
\end{proof}

We now proof the result for the factorial moments.

\begin{proof}[Proof of Lemma~\ref{lem:factmoment}]
First of all, we observe that
\begin{align*}
{N_{\Po}(k_n) \choose r} = \frac{1}{r!} \sum_{v_1,\dots,v_r\in V(\GPo)}^{\not = } \1_{\{D_{\GPo}(v_1)=\dots=D_{\GPo}(v_r)=k_n\}}.
\end{align*}
This can be seen by induction on $r$. For $r=1$, the claim is clear. Assuming it holds for $r\geq 1$, by the induction hypothesis,
\begin{align*}
&{N_{\Po}(k_n) \choose r+1} = {N_{\Po}(k_n) \choose r} \frac{N_{\Po}(k_n)-r}{r+1} \\
&= \frac{1}{(r+1)!}\sum_{v_1,\dots,v_r\in V(\GPo)}^{\not = } \1_{\{D_{\GPo}(v_1)=\dots=D_{\GPo}(v_r)=k_n\}} (N_{\Po}(k_n)-r).
\end{align*}
Now, we can write
$$N_{\Po}(k_n) = \sum_{\stackrel{v_{r+1} \in V(\GPo),}{v_{r+1} \not \in\{ v_1,\dots,v_r\}} } \1_{\{D_{\GPo}(v_{r+1})=k_n\}}+\sum_{v_{r+1} \in \{v_1,\dots,v_r\}}\1_{\{D_{\GPo}(v_{r+1})=k_n\}}.$$
The first sum leads to the right-hand side of the claim for $r+1$, whereas the second sum will cancel with the $-r$.

By the Campbell-Mecke formula 
\begin{align*}
	&\Exp{ {N_{\Po}(k_n) \choose r}}=\frac{1}{r!} \E\left[ \sum_{v_1,\dots,v_r\in V(\GPo)}^{\not = }  
		\1_{\{D_{\GPo}(v_1)=\dots=D_{\GPo}(v_r)=k_n\}}\right] \\
	&=\frac{1}{r!} \int_\Rcal \cdots \int_\Rcal \varphi_{\Po}(\{p_1,\dots,p_r\},p_1,\dots,p_r)
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r},
\end{align*}
where we integrate over $r$ additional points which we can think of as being added independently and with the same distribution as the vertices of the poissonized KPKVB model $\GPo$ in the upper half-plane coordinates.

With $r=1$, it follows that
\[
	\Exp{N_{\Po}(k_n)} = \int_\Rcal \Pee(v_1 \text{ has degree }k_n\text{ in }G(\VPo\cup \{v_1\})) \mu_n(dv_1),
\]
which yields that the right-hand side of the claim of the lemma can be rewritten as
\[
	\frac{1}{r!}(\Exp{N_{\Po}(k_n)})^r = \frac{1}{r!}\left(\int_\Rcal \Pee(v_1 \text{ has degree }k_n\text{ in }G(\VPo\cup \{v_1\})) \mu_n(dv_1)\right)^r.
\]

Using Lemma~\ref{lem:asympind}, we conclude that
\begin{align*}
	&\hspace{-20pt}\Exp{ { N_{\Po}(k_n) \choose r}} \\
	&= \frac{1}{r!} \int_\Rcal \cdots \int_\Rcal 
		\varphi_{\Po}(\{p_1,\dots,p_r\},p_1,\dots,p_r) 
		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r} \\
	&= (1+o(1))\frac{1}{r!}\left(\int_\Rcal \varphi_{\Po}(\{p_1\},p_1) f(x_1,y_1) \dd x_1 \dd y_1 \right)^r \\
	&= (1+o(1))\frac{1}{r!}(\Exp{N_{\Po}(k_n)})^r.
\end{align*}
\end{proof}

\subsection{Coupling $G_n$ to $\GPo$}\label{ssec:coupling_Gn_GPo}

In the previous sections we have established results for the degrees and the factorial moments of the degree $k_n$ nodes in the Poissonized KPKVB and finite box model. Our intended result, however, was for the degree distribution in the original KPKVB model. In order to extend the result for the Poissonized KPKVB model to the original model we will use a coupling argument to show that the expected difference between the number of degree $k_n$ nodes is negligible.

\begin{lemma}\label{lem:diff_Nk_hyperbolic_binomial_poisson}
As $n \rightarrow \infty$, it holds that
\[
\Exp{\left|N_{n}(k_n)-N_{Po}(k_n)\right|} = \smallO{\Exp{N_{Po}(k_n)}}.
\]
\end{lemma}

\begin{proof}
We couple both models by taking an infinite supply of i.i.d.~points $u_1, u_2, \dots$ chosen according
to the $(\alpha,R)$-quasi uniform distribution and letting the vertices of $G(n;\alpha,\nu)$ be $u_1,\dots, u_n$ and
the vertices of $\GPo(n;\alpha,\nu)$ be $u_1,\dots, u_N$ with $N\isd \Po(n)$ independently of
$u_1, u_2, \dots$. Thus, under this coupling, the only difference between $G_n = G(n;\alpha,\nu)$ and $\GPo = \GPo(n;\alpha,\nu)$ is the number of points. Note that since $N$ is Poisson with mean $n$, it follows from the Chernoff bound (see also equation (135) in the paper) that we may assume that $n - C\sqrt{n \log n} \le N \le n + C \sqrt{n \log n}$. To keep notation simple we will suppress this conditioning in the derivations.

Clearly, if $N = n$ the graphs are the same. So we will consider the two cases $n - C\sqrt{n \log n} \le N < n$ and $n < N \le n + C \sqrt{n \log n}$. We will prove the latter case. The other case uses similar arguments and hence we omit the details here.

If $n < N \le n + C \sqrt{n \log n}$ then the $G_n$ has less vertices that $\GPo$. Write $V_n(k_n)$ and $V_{\Po}(k_n)$ to denote the set of vertices that have degree $k_n$ in $G_n$ and $G_{\Po}$, respectively. Then since the vertices $u_{n+1}, \dots, u_N$ are not present in $G_n$,
\begin{align*}
	\left|N_n(k_n) - N_{\Po}(k_n)\right| &= \sum_{i = 1}^N \1_{\left\{u_i \in V_n(k_n) \Delta V_{\Po}(k_n)\right\}}\\
	&= \sum_{i = 1}^n \1_{\left\{u_i \in V_n(k_n) \Delta V_{\Po}(k_n)\right\}}
		+ \sum_{i = n+1}^N \1_{\left\{u_i \in V_{\Po}(k_n)\right\}}.
\end{align*}
Let $D_{\Po}$ denote the degree in the Poissonized KPKVB model of a point $u$ placed according to the $(\alpha,R)$-quasi uniform distribution. Then, using the Campbell-Mecke formula, the expectation of the second summation equals
\begin{align*}
	(N-n) \Prob{D_{\Po} = k_n} &= (N-n) \int_0^R \Prob{\Po(\mu_{\Po,n}(y)) = k_n} \alpha e^{-\alpha y} \dd y\\
	&\le (1+o(1)) C \sqrt{n \log n} p_{k_n} = \smallO{\Exp{N_{\Po}(k_n)}}.
\end{align*}
Therefore it remains to consider the first summation.

Let $D_n(u)$ and $D_{\Po}(u)$ denote the degree of a point $u$ in $G_n$ and $G_{\Po}$, respectively. Then there are two scenarios to consider: 1) either $D_n(u_i) = k_n$ and $D_{\Po}(u_i) \ne k_n$ or 2) $D_n(u_i) \ne k_n$ and $D_{\Po}(u_i) = k_n$. In the first case, since $u_i$ is present in both graphs it follows that $D_{\Po}(u_i) > k_n$. Similarly, for the second case it must hold that $D_n(u_i) < k_n$. Hence we have
\begin{align*}
	&\hspace{-30pt}\sum_{i = 1}^n \1_{\left\{u_i \in V_n(k_n) \Delta V_{\Po}(k_n)\right\}}\\
	&= \sum_{i = 1}^n \1_{\left\{d_n(u_i) = k_n, D_{\Po}(u_i) > k_n\right\}}
		+ \sum_{i = 1}^n \1_{\left\{d_n(u_i) < k_n, D_{\Po}(u_i) = k_n\right\}}.
\end{align*}

Let us first consider the second summation, i.e. the case where the node has degree smaller than $k_n$ in $G_n$. Taking the expectation gives $n \Prob{D_n < k_n, D_{\Po} = k_n}$, where $D_n$ denotes the degree in the KPKVB model of a point $u$ placed according to the $(\alpha,R)$-quasi uniform distribution. We now observe that because the points $u_1, \dots, u_N$ used to couple the graphs are independent, we can view the graph $G_n$ as being obtained from $\GPo$ by removing $N-n$ points, uniformly at random. Therefore if a point has degree $k_n$ in $\GPo$ but smaller degree in $G_n$, this means that at least one of its neighbors was removed. Denote by $Z(n)$ a random variable with a Hypergeometric distribution, for taking $N-n$ draws from a population of size $N$, where there are $k_n$ good objects. That is, $Z(n)$ denote the number of removed neighbors of a node $u$ with degree $k_n$ in $\GPo$. We then have
\begin{align*}
	\Prob{D_n < k_n, D_{\Po} = k_n} &= \Prob{Z(n) > 1}\Prob{D_{\Po} = k_n}\\
	&\le \Exp{Z(n)} \Prob{D_{\Po} = k_n} = \frac{(N-n) k_n}{N} \Prob{D_{\Po} = k_n}.
\end{align*}
Because $\alpha > 1/2$ and $k_n = \bigO{n^{\frac{1}{2\alpha+ 1}}}$ it holds that $k_n = \smallO{\sqrt{\frac{n}{\log n}}}$. Since $N = \bigT{n}$ and $N - n \le \bigO{\sqrt{n \log n}}$ it then follows that $\frac{(N-n) k_n}{N} = \smallO{1}$, from which we conclude that
\begin{align*}
	\Exp{\sum_{i = 1}^n \1_{\left\{d_n(u_i) < k_n, D_{\Po}(u_i) = k_n\right\}}}
	&= n \Prob{D_n < k_n, D_{\Po} = k_n}\\
	&\le \smallO{1} n \Prob{D_{\Po} = k_n} = \smallO{\Exp{N_{\Po}(k_n)}}.
\end{align*}

We now proceed with the other summation, for the case where a vertex has degree $k_n$ in $G_n$ but larger degree in $G_{\Po}$. Since the degree of $u$ in $\GPo$ can be a most $N-n$ larger we have
\[
	\Prob{D_n(u) = k_n, D_{\Po}(u) > k_n} = \sum_{t = 1}^{N - n} \Prob{D_n(u) = k_n, D_{\Po}(u) = k_n + t}.
\]
Using that the graph $G_n$ can be seen as being obtained from $\GPo$ by removing $N-n$ points uniformly at random, a point with degree $k_n + t$ in $G_{\Po}$ can only have degree $k_n$ in $G_n$ if exactly $t$ of its neighbors where removed. Let us therefore denote by $Z(n,t)$ a random variable with a Hypergeometric distribution, for taking $N-n$ draws from a population of size $N$, where there are $k_n + t$ good objects. Then
\[
	\Prob{D_n(u) = k_n, D_{\Po}(u) = k_n + t} = \Prob{Z(n,t) = t}\Prob{D_{\Po} = k_n + t}.
\]

Recall that, for any $0 < \varepsilon < 1$
\begin{align*}
	\Prob{D_{\Po} = k_n + t} &= \int_0^R \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy\\
	&= \int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy \\
	&\hspace{10pt}+ \int_{(1-\varepsilon)R}^R \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy
\end{align*}
By Lemma~\ref{lem:degree_integral} the first part is $(1+o(1)) p_{k_n + t}$ while the second part is $O(n^{-2\alpha(1-\varepsilon)})$ and hence
\[
	\Prob{D_{\Po} = k_n + t} \le \bigO{1}\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right).
\]
In addition we have that $\Prob{Z(n,t) = t} \le \bigO{1} \frac{\Exp{Z(n,t)}}{t}$. We thus obtain
\begin{align*}
	\sum_{t = 1}^{N-n} \Prob{Z(n,t) = t}\Prob{D_{\Po} = k_n + t}
	&\le \bigO{1} \sum_{t = 1}^{N-n} \frac{\Exp{Z(n,t)}}{t}\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)\\
	&= \bigO{1} \sum_{t = 1}^{N-n} \frac{(N-m)(k_n + t)}{N}\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)\\
	&= \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n} \frac{k_n}{t}
		\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)\\
	&\hspace{10pt}+ \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n}
		\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right),
\end{align*}
where we used that $\frac{N-n}{N} = \bigO{\sqrt{\frac{\log n}{n}}}$.

We will show that both summations are $\smallO{p_{k_n}}$. For the first summation we recall that $\frac{k_n (\log n)^{3/2}}{\sqrt{n}} = \smallO{1}$ for $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$, while for $\varepsilon > 0$ small enough $n^{-2\alpha(1-\varepsilon)} = \smallO{k_n^{-(2\alpha + 1)}} = \smallO{p_{k_n}}$. Hence, since $p_{k_n + t} \le p_{k_n}$,
\begin{align*}
	\bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n} \frac{k_n}{t}
		\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)
	&\le \bigO{ k_n \sqrt{\frac{\log n}{n}} p_{k_n}} \sum_{t = 1}^{N - m} \frac{1}{t}\\
	&= \bigO{\frac{k_n (\log n)^{3/2}}{\sqrt{n}}} p_{k_n} = \smallO{p_{k_n}}.
\end{align*}

For the other summation we use that
\[
	\sum_{t = 1}^{N-n} p_{k_n + t} \le \sum_{t = 1}^\infty p_{k_n + t}
	\le \bigO{k_n^{-2\alpha}} = \bigO{k_n p_{k_n}},
\]
together with the fact that for $\varepsilon$ small enough, $\log(n) n^{-2\alpha(1-\varepsilon)} = \smallO{k_n^{-(2\alpha + 1)}} = \smallO{p_{k_n}}$. This implies that
\begin{align*}
	\bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n}
		\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)
	&\le \bigO{\sqrt{\frac{\log n}{n}} k_n p_{k_n}} + \bigO{(N-n)\sqrt{\frac{\log n}{n}} n^{-2\alpha(1-\varepsilon)}}\\
	&\le \smallO{p_{k_n}} + \bigO{(\log n) n^{-2\alpha(1-\varepsilon)}} = \smallO{p_{k_n}}.
\end{align*}

It now follows that
\begin{align*}
	n \Prob{D_n(u) = k_n, D_{\Po}(u) > k_n}
	&= \sum_{t = 1}^{N-n} \Prob{D_n = k_n, D_{\Po} = k_n + t}\\
	&= n \sum_{t = 1}^{N-n} \Prob{Z(n,t) = t}\Prob{D_{\Po} = k_n + t}\\
	&= n \, \smallO{\Prob{D_{\Po} = k_n}} = \smallO{\Exp{N_{\Po}(k_n)}},
\end{align*}
which finishes the proof for the case where $N > n$.
\end{proof}

%\subsection{First moment for large degrees}\label{ssec:moments_larges_degrees_GPo}
%
%B
%
%\begin{lemma}\label{lem:firstmomlargedegs}
%Let $\alpha>\frac{1}{2}$ and $N_n(k)$ denote the number vertices in the KPKVB model $G(n;\alpha,\nu)$ with degree $k$. Consider a sequence of integers $(k_n)$ with $0 \leq k_n \leq n-1$ and $k_n \gg n^{\frac{1}{2\alpha+1}}$. Then, $\Exp{N_n(k_n)} = o(1)$.
%\end{lemma}
%
%\begin{proof}
%First we observe that as the poissonized KPKVB model $\GPo$ has the same intensity measure as the original KPKVB model with a fixed number $n$ of points, the expected degree of a vertex of the KPKVB model with radial coordinate $r=R-y$ is given by $\mu_{\Po,n}(y)$ and hence,
%\[
%	\Exp{N_n(k_n)} = n \int_0^R \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)/n) = k_n} \frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy.
%\]
%Fix $0 < \varepsilon < \frac{4\alpha - 1}{4\alpha + 2} \wedge \frac{2\alpha - 1}{2\alpha}$. We first show that we only need to consider integration up to $y \le (1-\varepsilon)R$. By our choice of $\varepsilon$, $2\alpha(1-\varepsilon) > 1$, so that
%\[
%	\frac{\cosh(\alpha \varepsilon R) - 1}{\cosh(\alpha R) - 1}
%	= \bigO{n^{-2\alpha (1 - \varepsilon)}} = \smallO{n^{-1}}.
%\]
%This implies
%\[
%	n \int_{(1-\varepsilon)R}^R \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)/n) = k_n}
%	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy
%	\le n \frac{\cosh(\alpha \epsilon R)}{\cosh(\alpha R)-1} = \smallO{1},
%\]
%and thus it is enough to show that
%\[
%	n \int_0^{(1-\varepsilon)R} \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)) = k_n}
%	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy = \smallO{1}.
%\]
%Note that for all $0 \le y \le (1-\varepsilon)R$ we have
%\[
%	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} = (1+\smallO{1}) \alpha e^{-\alpha y}.
%\]
%Hence, by bounding the Binomial probability (see Lemma~\ref{lem:binomial_poisson_bound})
%\begin{align*}
%	&\hspace{-20pt} n \int_0^{(1-\varepsilon)R} \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)) = k_n}
%		\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy\\
%	&\le (1+\smallO{1}) \frac{e}{\sqrt{2\pi}} \sqrt{\frac{n}{n-k_n}}
%		n \int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po,n}(y)) = k_n} \alpha e^{-\alpha y} dy \\
%	&\le (1+\smallO{1}) \frac{e}{\sqrt{2\pi}} \sqrt{\frac{n}{n-k_n}} n p_{k_n}
%	= \bigO{\sqrt{\frac{n}{n-k_n}} n k_n^{-(2\alpha + 1)}}.
%\end{align*}
%We shall now consider two cases: $n^{\frac{1}{2\alpha + 1}} \ll k_n < n^{1-\varepsilon}$ and $n^{1-\varepsilon} \le k_n \le n - 1$.
%
%If $n^{\frac{1}{2\alpha + 1}} \ll k_n < n^{1-\varepsilon}$ then $\sqrt{\frac{n}{n-k_n}} = 1 + \smallO{1}$ and hence
%\[
%	\sqrt{\frac{n}{n-k_n}} n k_n^{-(2\alpha + 1)} = \bigO{n k_n^{-(2\alpha + 1)}} = \smallO{1}.
%\]
%
%For $k_n \ge n^{1 - \varepsilon}$ we have, by our choice of $\varepsilon$, that $\frac{3}{2} - (2\alpha + 1)(1-\varepsilon) < 0$, and thus
%\[
%	\sqrt{\frac{n}{n-k_n}} n k_n^{-(2\alpha + 1)} = \bigO{n^{\frac{3}{2}} k_n^{-(2\alpha + 1)}}
%	= \bigO{n^{\frac{3}{2} - (2\alpha + 1)(1-\varepsilon)}} = \smallO{1}.
%\]
%\end{proof}

\subsection{Proof of Theorem~\ref{thm:degrees_hyperbolic}}\label{ssec:proof_thm_degrees}

We now have all necessary ingredient to proof the main result on the degrees, Theorem~\ref{thm:degree_hyperbolic}.

\begin{proof}[Proof of Theorem~\ref{thm:degrees_hyperbolic}] \hfill\\
\begin{enumerate}[\upshape (i)]
\item  First we recall that the statements regarding $p_k$ and its asymptotic behavior follow from Equation~\ref{eq:def_pk} and Equation~\ref{eq:degree_distribution_P_asymptotics}.

By Lemma~\ref{lem:expnnkn},
\[
\Exp{{ N_{Po}(k_n) }}=(1+o(1))n p_{k_n}.
\]
Using Lemma~\ref{lem:factmoment} with $r=2$ we have that $\Exp{{N_{Po}(k_n) \choose 2}} = (1+o(1))\frac{(\Exp{ N_{Po}(k_n)})^2}{2}$, which implies $\Exp{N_{Po}(k_n)^2} = 2\Exp{{N_{Po}(k_n) \choose 2}} +\Exp{N_{Po}(k_n)} = (1+o(1))(\Exp{ N_{Po}(k_n)})^2 +o((\Exp{N_{Po}(k_n)})^2)$ (because $\Exp{N_{Po}(k_n)} = (1+o(1)) np_{k_n} \rightarrow \infty$). Hence, by Chebychev for any $\epsilon >0$,
\[
	\Prob{|N_{Po}(k_n)-\Exp{N_{Po}(k_n)}|\geq \epsilon \Exp{N_{Po}(k_n)}}
	\leq \frac{Var(N_{Po}(k_n))}{\epsilon^2 (\Exp{ N_{Po}(k_n)})^2} = o(1).
\]
As $N_n(k_n)=N_{Po}(k_n)+N_n(k_n)-N_{Po}(k_n) = N_{Po}(k_n)\pm |N_n(k_n)-N_{Po}(k_n)|$ (where the sign depends on whether $N_n(k_n)>N_{Po}(k_n)$ or not), due to Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson}, we have that
\[
	\Exp{N_n(k_n)} = \Exp{N_{Po}(k_n)} \pm \Exp{ |N_n(k_n)-N_{Po}(k_n)|} = (1+o(1))\Exp{N_{Po}(k_n)} = (1+o(1))n p_{k_n}.
\]

\item Let $\zeta = 2\alpha \xi^{2\alpha}c^{-(2\alpha+1)} \in \R$.
The proof consists of showing that $\Exp{{N_{Po}(k_n) \choose r} } \rightarrow \frac{\zeta^r}{r!}$ for every positive integer $r$ and then applying \cite[Theorem 8.3.1]{alon2016probabilistic}.

If $k_n=(1+o(1))c n^{\frac{1}{2\alpha+1}}$, then by Lemma~\ref{lem:expnnkn},
\begin{align*}
	\Exp{N_{Po}(k_n)} &= (1+o(1))2\alpha \xi^{2\alpha} n (1+o(1))^{-(2\alpha+1)} c^{-(2\alpha+1)}n^{-1} \\
	&= (1+o(1))2\alpha \xi^{2\alpha} c^{-(2\alpha+1)}=(1+o(1))\zeta,
\end{align*}
which implies $\Exp{N_{Po}(k_n)} \rightarrow \zeta$ (as $\zeta$ is a positive constant). From Lemma~\ref{lem:factmoment}, it then follows that $\Exp{{N_{Po}(k_n) \choose r}} =(1+o(1))\frac{(\Exp{ N_{Po}(k_n)})^r}{r!}\rightarrow \frac{\zeta^r}{r!}$. Thus, it follows from \cite[Theorem 8.3.1]{alon2016probabilistic} that $N_{Po}(k_n) \xrightarrow{d} Po(\zeta)$.

Finally, since $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$, by Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson}, $\Exp{| N_n(k_n) - N_{Po}(k_n)|} = o(\Exp{N_{Po}(k_n)}) = o(\zeta)$, from which it follows that $\Prob{|N_n(k_n)-N_{Po}(k_n)|\geq 1} \leq \Exp{ |N_n(k_n)-N_{Po}(k_n)|} = o(\zeta)$. Hence, it also holds that $N_n(k_n) \xrightarrow{d} Po(\zeta)$.

\item We will show that in this case $\E[N_n(k_n)] = o(1)$. This then implies, by Markov's inequality,
\[
	\Prob{N_n(k_n)>0}\leq \E[N_n(k_n)] = o(1).
\]

First we observe that as the poissonized KPKVB model $\GPo$ has the same intensity measure as the original KPKVB model with a fixed number $n$ of points, the expected degree of a vertex of the KPKVB model with radial coordinate $r=R-y$ is given by $\mu_{\Po,n}(y)$ and hence,
\[
	\Exp{N_n(k_n)} = n \int_0^R \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)/n) = k_n} \frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy.
\]
Fix $0 < \varepsilon < \frac{4\alpha - 1}{4\alpha + 2} \wedge \frac{2\alpha - 1}{2\alpha}$. We first show that we only need to consider integration up to $y \le (1-\varepsilon)R$. By our choice of $\varepsilon$, $2\alpha(1-\varepsilon) > 1$, so that
\[
	\frac{\cosh(\alpha \varepsilon R) - 1}{\cosh(\alpha R) - 1}
	= \bigO{n^{-2\alpha (1 - \varepsilon)}} = \smallO{n^{-1}}.
\]
This implies
\[
	n \int_{(1-\varepsilon)R}^R \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)/n) = k_n}
	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy
	\le n \frac{\cosh(\alpha \epsilon R)}{\cosh(\alpha R)-1} = \smallO{1},
\]
and thus it is enough to show that
\[
	n \int_0^{(1-\varepsilon)R} \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)) = k_n}
	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy = \smallO{1}.
\]
Note that for all $0 \le y \le (1-\varepsilon)R$ we have
\[
	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} = (1+\smallO{1}) \alpha e^{-\alpha y}.
\]
Hence, by bounding the Binomial probability (see Lemma~\ref{lem:binomial_poisson_bound})
\begin{align*}
	&\hspace{-20pt} n \int_0^{(1-\varepsilon)R} \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)) = k_n}
		\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy\\
	&\le (1+\smallO{1}) \frac{e}{\sqrt{2\pi}} \sqrt{\frac{n}{n-k_n}}
		n \int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po,n}(y)) = k_n} \alpha e^{-\alpha y} dy \\
	&\le (1+\smallO{1}) \frac{e}{\sqrt{2\pi}} \sqrt{\frac{n}{n-k_n}} n p_{k_n}
	= \bigO{\sqrt{\frac{n}{n-k_n}} n k_n^{-(2\alpha + 1)}}.
\end{align*}
We shall now consider two cases: $n^{\frac{1}{2\alpha + 1}} \ll k_n < n^{1-\varepsilon}$ and $n^{1-\varepsilon} \le k_n \le n - 1$.

If $n^{\frac{1}{2\alpha + 1}} \ll k_n < n^{1-\varepsilon}$ then $\sqrt{\frac{n}{n-k_n}} = 1 + \smallO{1}$ and hence
\[
	\sqrt{\frac{n}{n-k_n}} n k_n^{-(2\alpha + 1)} = \bigO{n k_n^{-(2\alpha + 1)}} = \smallO{1}.
\]

For $k_n \ge n^{1 - \varepsilon}$ we have, by our choice of $\varepsilon$, that $\frac{3}{2} - (2\alpha + 1)(1-\varepsilon) < 0$, and thus
\[
	\sqrt{\frac{n}{n-k_n}} n k_n^{-(2\alpha + 1)} = \bigO{n^{\frac{3}{2}} k_n^{-(2\alpha + 1)}}
	= \bigO{n^{\frac{3}{2} - (2\alpha + 1)(1-\varepsilon)}} = \smallO{1}.
\]
\end{enumerate}
\end{proof}

### 2020-01-02 introduction.tex
version 1.6

@@
 
-We start with the definition of the KPKVB model.
+\subsection{KPKVB model}
+We start with the definition of the model.
 As mentioned, its nodes are situated in the hyperbolic plane $\Haa$, which is a surface with constant Gaussian curvature $-1$.
@@
 
+Here we summarize our main results regarding the degrees and clustering in the KPKVB model.
+
+\subsubsection{Degrees}
+
+The first rigorous result on the degree distribution in the KPKVB model was given in~\cite{gugelmann2012random}, where they analyzed the fraction of nodes with degree $k$.
+Although their results allowed $k = k_n$ to scale with $n$ as $k_n = n^\delta$, it did not cover the full range $1 \le k_n \le n-1$.
+Our main result for the degrees gives this full characterization of the degree distribution.
+
+\begin{theorem}\label{thm:degrees_hyperbolic}
+Let $\alpha >\frac{1}{2}$, denote by $N_n(k)$ the number of vertices with degree $k$ in the KPKVB model $G(n;\alpha,\nu)$ and consider a sequence of integers $k_n$ with $0 \leq k_n \leq n-1$.
+\begin{enumerate}
+\item If $k_n =\smallO{n^{\frac{1}{2\alpha+1}}}$ as $n\rightarrow \infty$, then a.a.s.
+\[
+	N_n(k_n) =(1+o(1)) n p_{k_n},
+\]
+where
+\[
+	p_{k_n} = \int_0^\infty \Pee(Po(\xi e^{\frac{y}{2}})=k_n)\alpha e^{-\alpha y}dy,
+\]
+and $p_{k_n}=\frac{2\alpha \xi^{2\alpha}\Gamma^+(k_n-2\alpha,\xi)}{k_n!}=(1+o(1)) 2\alpha \xi^{2\alpha} k_n^{-(2\alpha+1)}$ as $k_n \rightarrow \infty$.
+\item If $k_n = (1+o(1))c n^{\frac{1}{2\alpha+1}}$ for some fixed $c >0$, then
+\[
+	N_n(k_n) \xrightarrow[n\rightarrow\infty]{d} \operatorname{Po}(2\alpha \xi^{2\alpha} c^{-(2\alpha+1)}).
+\]
+\item If $k_n \gg n^{\frac{1}{2\alpha+1}}$, then a.a.s. $N_n(k_n) = 0$.
+\end{enumerate}
+\end{theorem}
+
+The first result of Theorem~\ref{thm:degrees_hyperbolic} states that the fraction of nodes of degree $k_n$ converges to $p_{k_n}$.
+Not surprisingly, the limit distribution is the same as found in~\cite{gugelmann2012random}.
+However, their this result was proved only for $k_n \le n^{\delta^\prime}$, where $\delta^\prime < \min\left\{\frac{2\alpha-1}{4\alpha(2\alpha +1)}, \frac{2(2\alpha -1)}{5(2\alpha + 1)}\right\} < \frac{1}{2\alpha + 1}$.
+Therefore, our result extends theirs by showing that this converges holds all the way till $n^{\frac{1}{2\alpha + 1}}$ .
+Moreover, we establish what happens at the boundary, where $k_n$ scales as $n^{\frac{1}{2\alpha + 1}}$ and show that this scaling is indeed the bound for the distribution since $N_n(k_n) = 0$ a.a.s.
+when $k_n$ grows faster than $n^{\frac{1}{2\alpha + 1}}$.
+
 \subsubsection{The clustering coefficient}
 
-Our first result is the following.
+Our first result on the clustering shows the convergence of the local clustering coefficient in the KPKVB model and establishes the limit exactly.
 
@@
 	c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k),
+\]
+\[
+	\lim_{n \to \infty} \Exp{\left|\frac{c(k;G_n)}{\gamma(k)} - 1\right|} = 0.
 \]
@@
 
-There are a few other observation to be made regarding our results.
+There are a few other observation to be made regarding our results on clustering.
 

### 2020-01-02 paper.tex
version 1.6

@@
 \newcommand{\Po}[0]{\ensuremath{{\mathrm{Po}}}}		%	Poisson random variable
-\newcommand{\PPP}{\ensuremath{\Pcal_{\alpha, \nu}}}	%	Poisson Point Process
+\newcommand{\PPP}{\ensuremath{\Pcal}}	%	Poisson Point Process
 
@@
 
+\newcommand{\strip}{\mathcal{S}_{k_n}}
+\newcommand{\stripkn}{\mathcal{S}_{k_n}}
+\newcommand{\stripk}{\mathcal{S}_{k}}
+\newcommand{\stripknc}{\mathcal{S}_{k_n,C}}
+\newcommand{\stripkc}{\mathcal{S}_{k,C}}
+
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}	%	Use to insert equation number 
@@
 \newcommand{\Nbox}{\ensuremath{N_{\text{box}}}}
-\newcommand{\Dbox}{\ensuremath{\text{deg}_{\text{box}}}}
-\newcommand{\Vbox}{\ensuremath{\mathcal{V}_{\text{box}}}}
-\newcommand{\VPo}{\ensuremath{\mathcal{V}_{\Po}}}
+\newcommand{\Dbox}{\ensuremath{D_{\Gbox}}}
+\newcommand{\Vbox}{\ensuremath{V_{\text{box}}}}
+\newcommand{\VPo}{\ensuremath{V_{\Po}}}
 
@@
 \newcommand{\Ycal}{\ensuremath{{\mathcal Y}}}
+\newcommand{\Fcal}{\ensuremath{\mathcal{F}}}
 \newcommand{\Qcal}{\ensuremath{{\mathcal Q}}}
@@
 Here we show that the clustering coefficient tends in probability to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
-This improves over earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant.
+This improves earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant.
 Similarly, we are able to show that $c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ which we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
@@
 
-\input{proof_overview_finite_k}
+\input{preliminaries}
+
+\input{hyperbolic_degrees}
 
@@
 \input{proofs_infinite_k}
-
-\input{concentration_argument}
 

### 2020-01-02 preliminaries.tex
version 1.6

--- 2019-05-28 proof_overview_finite_k.tex
@@
 
+\subsection{Concentration of heights}
+
+When analyzing degrees and clustering in the Poissonized KPKVB and related models we often encounter expressions of the form
+\begin{equation}\label{eq:example_poisson_integral}
+	\int_{0}^R \Prob{\Po(\hat{\mu}(y)) = k_n} h(y) e^{-\alpha y} \dd y,
+\end{equation}
+where $h(y)$ is some function and $\hat{\mu}(y)$ is $\Mu{\BallHyp{y}}$, $\Mu{\BallPon{y}}$ or $\Mu{\BallPo{y}}$.
+We will often have to either bound the behavior of such integrals as $k_n \to \infty$ or establish their asymptotic behavior.
+For this we will utilize that Poisson random variables are well concentrated around their mean.
+
+In particular, if $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$, we have the following Chernoff bound (c.f. \cite[Lemma 1.2]{penrose2003random})
+\begin{equation}\label{eq:def_chernoff_bound_poisson}
+	\Prob{\left|\mathrm{Po}(\lambda) - \lambda\right| \ge x} \le 2e^{-\frac{x^2}{2(\lambda + x)}}.
+\end{equation}
+In particular, if $\lambda = \lambda_n \to \infty$, then for any $C>0$,
+\begin{equation}\label{eq:def_chernoff_bound_poisson_C}
+	\Prob{\left|\mathrm{Po}(\lambda_n) - \lambda_n\right| \ge C \sqrt{\lambda_n\log(\lambda_n)}} \le \bigO{\lambda_n^{-\frac{C^2}{2}}}.
+\end{equation}
+
+For our application these Chernoff bounds imply that if $y$ is such that $\hat{\mu}(y)$ is far from $k_n$ then $\Prob{\Po(\hat{\mu}(y)) = k_n}$ becomes very small.
+To be more specific, we define for any $k \ge 0$ and $C > 0$,
+\begin{equation}\label{eq:def_y_k_C}
+	y_{k,C}^\pm = 2 \log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi}\right),
+\end{equation}
+where we set $y_{k,C}^- = 0$ if $k - C \sqrt{k \log(k)} < \xi$. For convenience we write $\Kcal_C(k_n) := [y_{k_n,C}^-, y_{k_n,C}^+]$. Then we can show that for all $y$ outside $\Kcal_C(k_n)$
+\begin{equation}\label{eq:chernoff_bound_degrees}
+	\Prob{\Po(\hat{\mu}(y)) = k_n} \le \bigO{k_n^{-\frac{C^2}{2}}}.
+\end{equation}
+Since we can select $C$ to be as big as we want we can make this error as small as needed.
+This implies that then the main contribution to the integral~\eqref{eq:example_poisson_integral} comes from those `'heights" $y$ that are in the interval $\Kcal_C(k_n)$.
+In other words, the main contribution is concentrated around the heights $y$ for which $\mu(y) = k_n$.
+We thus refer to this as the concentration of heights result.
+More precisely, we prove the following.
+
+\begin{proposition}[Concentration of heights]\label{prop:concentration_height_general}
+Let $\alpha > \frac{1}{2}$, $\nu > 0$, $(k_n)_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n}$.
+Furthermore, let $\hat{\mu}(y)$ denoting either $\Mu{\BallHyp{y}}$, $\Mu{\BallPon{y}}$ or $\Mu{\BallPo{y}}$.
+Then for any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, it holds that
+\begin{equation}\label{eq:error_bound_int_rho_not_K}
+	\int_0^\infty \hspace{-3pt} h(y) \Prob{\Po(\hat{\mu}(y)) = k_n} \alpha e^{-\alpha y} \dd y
+	\sim \int_{\Kcal_C(k_n)} \hspace{-8pt} h(y) \Prob{\Po(\hat{\mu}(y)) = k_n} \alpha e^{-\alpha y} \dd y,
+\end{equation}
+as $n \to \infty$.
+\end{proposition}
+
+The key implication of Proposition~\ref{prop:concentration_height_general} is that if the function $h(y)$ does not increase too fast, then we can restrict integration to the interval $\Kcal_C(y)$.
+The full details associated with these concentration of heights and the proof of Proposition~\ref{prop:concentration_height_general} can be found in the Section~\ref{sec:concentration_argument} of the Appendix.
+
 %To see this result in action consider the finite box model $\Gbox$. Then 

### 2020-01-02 proofs_infinite_k.tex
version 1.6

@@
 
-\subsection{Restricting the height for vertices with degree $k_n$}
-
-In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a^-(k), a^+(k)]$, with
-\[
-	a^\pm(k) = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
-\]
-The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and Poisson random variables are well concentrated around their mean, i.e.
+%\subsection{Restricting the height for vertices with degree $k_n$}
+%
+%In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a^-(k), a^+(k)]$, with
+%\[
+%	a^\pm(k) = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
+%\]
+%The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and Poisson random variables are well concentrated around their mean, i.e.
 around heights $y$ for which $\mu(y) \approx k$.
@@
 Moreover, we prove that if $\mu_n$ corresponds to either $\Mu{\BallHyp{y}}$ or $\Mu{\BallPon{y}}$, then for a certain classs of functions $h$
-\[
-	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y 
-	= (1+\smallO{1}) \int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
-\]
-i.e. we may replace $\hat{\rho}_n(y,k_n)$ in the integrand with $\rho(y,k_n)$.
+%\[
+%	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y 
+%	= (1+\smallO{1}) \int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+%\]
+%i.e. we may replace $\hat{\rho}_n(y,k_n)$ in the integrand with $\rho(y,k_n)$.
 
@@
 
-\begin{remark}[Notations different graphs]
+\begin{remark}[Notations for different graphs]
 We will use the subscripts $n$, $\Po$, $\text{box}$ and $\infty$ to identify properties of, respectively, the KPKVB mode $G_n$, the Poisson version $\GPo$, the finite box model $\Gbox$ and the infinite model $\Ginf$.
-For example $N_{\Po}(k)$ denotes number of nodes with degree $k$ in $\GPo$ and $\rho_{\text{box}}(y,k) = \Prob{\Po(\mu(\BallPo{y})) = k}$, i.e.
+For example $N_{\Po}(k)$ denotes number of nodes with degree $k$ in $\GPo$ and $\rho_{\text{box}}(y,k) = \Prob{\Po(\mu(\BallPon{y})) = k}$, i.e.
 the degree distribution in $\Gbox$ for a point $p = (x,y)$.

### 2020-01-02 transition.tex
commented out the in-text-comments
version 1.6

@@
 We will adopt this notational convention throughout the remainder of this section, to keep notation concise.
-We further write $\Nbox(k)$ to denote the number of vertices with degree $k$ in $\Gbox$.
-
-We will first relate $\gamma(k_n)$ and $\Exp{c^\ast(k_n; \Gbox)}$ using $T_\infty(y)$ and $T_{\text{box}}(y)$. Recall the definition of $\Kcal_{C}(k_n)$
-\[
-	\Kcal_C(k_n) = \left\{y \in \R_+ : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \le e^{\frac{y}{2}}
-	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\},	
-\]
+We also recall that $\Nbox(k)$ denotes the number of vertices with degree $k$ in $\Gbox$.
+
+We will first relate $\gamma(k_n)$ to an integral expression involving $T_\infty(y)$ and $\Exp{c^\ast(k_n;\Gbox)}$ to one involving $\Exp{T_{\text{box}}(y)}$.
+Recall the definition of $y_{k,C}^\pm$ from~\eqref{eq:def_y_k_C} and the interval $\Kcal_{C}(k_n) = [y_{k_n,C}^-, y_{k_n,C}^+]$.
+Note that for any $y \in \Kcal_C(k_n)$ it holds that as
+\begin{equation}\label{eq:def_K_C_set}
+	\frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \le e^{\frac{y}{2}}
+	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi}	
+\end{equation}
+and thus $k_n - C \sqrt{k_n \log(k_n)} \le \mu(y) \le k_n + C \sqrt{k_n \log(k_n)}$.
 
@@
 	\Exp{c^\ast(k_n;\Gbox)} = (1 + \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y)}
-		\rho(y,k_n) \alpha e^{-\alpha y} \dd y
+		\rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y
 \end{equation}
@@
 \begin{align*}
-	\gamma(k_n) &= \frac{1}{p_{k_n}} \cdot \int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y \\
-	&= \frac{1}{p_{k_n}} \int_0^\infty \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) 
-		\alpha e^{-\alpha y_0} \dd y_0\\
-	&= (1+ \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_0^\infty \Exp{T_\infty(y)} \rho(y,k) \alpha e^{-\alpha y} \dd y_0,
-\end{align*}
-where the last line is due to a concentration of heights argument.
+	\gamma(k_n) &= \frac{1}{p_{k_n}} \cdot \int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	= \frac{1}{p_{k_n}} \int_0^\infty \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) 
+		\alpha e^{-\alpha y} \dd y.
+\end{align*}
+
+Because $\Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} = \bigO{1}$, uniformly in $y \in \R_+$ and $\mu(y) = (1+\smallO{1}) k_n$ uniformly for $y \in \Kcal_C(k_n)$, by the concentration of heights (Proposition~\ref{prop:concentration_height_general})
+\begin{align*}
+	&\hspace{-30pt} \frac{1}{p_{k_n}} 
+		\int_0^\infty \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) \alpha e^{-\alpha y} \dd y \\
+	&= (1+\smallO{1}) \frac{1}{p_{k_n}} 
+		\int_{\Kcal_C(k_n)} \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) \alpha e^{-\alpha y} \dd y \\
+	&= (1+ \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_C(k_n)} \Exp{T_\infty(y)} \rho(y,k) \alpha e^{-\alpha y} \dd y.
+\end{align*}
 
@@
 	&= (1+\smallO{1})\frac{n}{\Exp{\Nbox(k_n)}} \int_{\Kcal_C(k_n)} \CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n}
-		\rho(y,k_n) \alpha e^{-\alpha y} \dd y,
-\end{align*}
-where the last line follows from a concentration of heights argument, for which we used that $\CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n} \le 1$.
+		\rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y,
+\end{align*}
+where the last line follows from the concentration of heights, for which we used the upper bound $\CExp{c_{\text{box}}(y)}{\Dbox(y) = k_n} \le 1$.
+
 To analyze the conditional expectation we observe that, similar to the analysis of $\gamma(k_n)$, conditioned on there being $k_n$ points in $\BallPon{y}$, each point $u_i = (x_i,y_i)$ is independently distributed according to the probability density $\Mu{\BallPon{y}}^{-1} \ind{u_i \in \BallPon{y}} f(x_i,y_i)$.
@@
 \[
-	\Exp{c^\ast(k_n; \Gbox)} = (1 + \smallO{1}) \frac{n \Mu{\BallPon{2\log(k_n/\xi)}}^{-2}}{\Exp{\Nbox(k_n)}} \int_{\Kcal_C(k_n)} \Exp{T_{\text{box}}(y)} \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+	\Exp{c^\ast(k_n; \Gbox)} = (1 + \smallO{1}) \frac{n \Mu{\BallPon{2\log(k_n/\xi)}}^{-2}}{\Exp{\Nbox(k_n)}} \int_{\Kcal_C(k_n)} \Exp{T_{\text{box}}(y)} \rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y.
 \]
@@
 \[
-	\Exp{N_{\text{box}}(k_n)} = \int_{\Rcal} \rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y,
-\]
-so that by a concentration of heights argument,
-\[
-	\Exp{N_{\text{box}}(k_n)} = (1+o(1)) n \int_{0}^\infty \rho(y,k_n) \alpha e^{-\alpha y} \dd y 
-	= (1+\smallO{1}) n p_{k_n}.
-\]
-We therefore conclude that
+	\Exp{N_{\text{box}}(k_n)} = (1+\smallO{1}) n p_{k_n}
+\]
+by Lemma~\ref{lem:average_degree_G_box}. We therefore conclude that
 \[
 	\Exp{c^\ast(k_n; \Gbox)} = (1 + \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_C(k_n)} 
-		\Exp{T_{\text{box}}(y)} \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
-\]
-
-%Next recall the definition of $\Kcal_{C}(k_n)$, see~\eqref{eq:def_K_C_set}, and note that for all $y_0 \in \Kcal_{C}(k_n)$, $\mu(y) = (1+\smallO{1})k_n$.
-Then Lemma~\ref{lem:concentration_argument} implies that, as $n \to \infty$,
-%\begin{align*}
-%	&\hspace{-30pt} \int_0^\infty \Exp{T_\infty(y_0)} \left(\frac{\mu(y)^2}{2}\right)^{-1} \rho(y_0,k) 
-%		\alpha e^{-\alpha y_0} \dd y_0\\
-%	&= (1+ \smallO{1}) \binom{k_n}{2}^{-1} \int_0^\infty \Exp{T_\infty(y_0)} \rho(y_0,k) \alpha e^{-\alpha y_0} \dd y_0,
-%\end{align*}
-%which finishes the proof.
+		\Exp{T_{\text{box}}(y)} \rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y.
+\]
 \end{proof}
 
-%
-%
-%For the finite box model we have, by the Campbell-Mecke formula,
-%\begin{align*}
-%	\Exp{c^\ast(k_n, \Gbox)}
-%	&= \frac{1}{\binom{k_n}{2}\Exp{\Nbox(k_n)}} \int_{\Rcal} \Exp{T_{\text{box}}(p) \ind{\text{deg}(p) = k_n}} f(x,y) 
-%		\dd x \dd y\\
-%	&= \frac{n}{\binom{k_n}{2}N_{\Gbox}(k_n)} \int_0^{R} \CExp{T_{\text{box}}(y_0)}{\text{deg}(y_0) = k_n} 
-%		\rho_{\text{box}}(y,k_n) \alpha e^{-\alpha y_0} \dd y_0,
-%\end{align*}
-%where the last line follows since the Poisson point process is invariant in $x$ and by slightly abusing notation $T_{\text{box}}(y_0) = T_{\text{box}}(0,y_0)$. Next we note that 
-%\[
-%	\Exp{N_{\text{box}}(k_n)} = \int_{\Rcal} \rho_{\text{box}}(y,k_n) f(x,y) \dd x \dd y,
-%\]
-%so that by a concentration of heights argument, see Corollary~\ref{cor:concentration_heights_asymptotics_n},
-%\[
-%	\Exp{N_{\text{box}}(k_n)} = (1+o(1)) \alpha n \int_{0}^\infty \rho(y,k_n) e^{-\alpha y} \dd y 
-%	= (1+\smallO{1}) n p_{k_n}.
-%\]
-%Since $\Exp{T_{\text{box}}(y_0)\ind{\text{deg}(y_0) = k_n}} \le \binom{k_n}{2}$, and Another concentration of heights argument yields
-%\[
-%	\int_0^{R} \Exp{T_{\text{box}}(y_0)} \rho_{\text{box}}(y_0,k_n) \alpha e^{-\alpha y_0} \dd y_0
-%	= (1 + \smallO{1}) \int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y_0)} \rho(y_0,k_n) \alpha e^{-\alpha y_0} \dd y_0
-%\]
-%and hence
-%\begin{equation}\label{eq:approx_c_ast_Gbox}
-%	c^\ast(k_n, \Gbox)  = (1 + \smallO{1})\frac{1}{p_{k_n}} \int_{\Kcal_{C}(k_n)} \binom{k_n}{2}^{-1} \Exp{T_{\text{box}}(y_0)} \rho(y_0,k_n) \alpha e^{-\alpha y_0} \dd y_0.
+As a result of this lemma we only need to compare the difference in triangles between both models for height in the interval $\Kcal_C(k_n)$. This will significantly help the analysis.
+
+%Comparing~\eqref{eq:alt_gamma_kn} and~\eqref{eq:alt_c_ast_kn}, we conclude that to prove Proposition~\ref{prop:convergence_average_clustering_P_n} it is enough to show that
+%\begin{equation}\label{eq:triangle_diff_main_term}
+%	 \left|\int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y) - T_\infty(y)}
+%	\rho(y,k) \alpha e^{-\alpha y} \, d y \right|
+%	= \smallO{s(k_n)p_{k_n}k_n^2},
 %\end{equation}
-
-Comparing~\eqref{eq:alt_gamma_kn} and~\eqref{eq:alt_c_ast_kn}, we conclude that to prove Proposition~\ref{prop:convergence_average_clustering_P_n} it is enough to show that
-\begin{equation}\label{eq:triangle_diff_main_term}
-	 \left|\int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y) - T_\infty(y)}
-	\rho(y,k) \alpha e^{-\alpha y} \, d y \right|
-	= \smallO{s(k_n)p_{k_n}k_n^2},
-\end{equation}
-which means we have to compute the expected difference in triangles between both models.
+%which means we have to compute the expected difference in triangles between both models.
 
@@
 We postpone this proof till the end of this section and proceed with the main goal, proving Proposition~\ref{prop:convergence_average_clustering_P_n}.
-
 First we state a small lemma about the scaling of $s(k_n)$ that will be very useful.
@@
 
-We now proceed with proving the main result of this section.
-
-\begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]
-Let us write $\Rcal^\prime := (\R \times \R_+) \setminus \Rcal$ and let $p_0 = (0,y)$ denote the typical point.
-Next we recall that it is enough to show~\eqref{eq:triangle_diff_main_term}, so that in particular we have that $y \in \Kcal_{C}(k_n)$.
-
-Now
-\begin{align*}
-	\left|T_{\text{box}}(p_0) - T_{\infty}(p_0)\right| 
-	&= \left|T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right| 
-		+ \sum_{p_1, p_2 \in \Pcal \cap \Rcal^\prime}^{\ne} T_{\infty}(p_0,p_1,p_2),
-\end{align*}
-so that by the Campbell-Mecke formula
+The first key implication of Lemma~\ref{lem:clustering_error_T_term} is that the triangle count in the finite box model is equivalent to $k_n^2 P(y)$, where $P(y)$ is defined in [??].
+
+\begin{lemma}\label{lem:appox_triangle_count_box}
+Let $p_0 = (0,y)$. Then uniformly for $y \in \Kcal_C(k_n)$,
+\[
+	\Exp{T_{\mathrm{box}}(p_0)} = (1+\smallO{1})k_n^2 P(y) + \smallO{s(k_n) k_n^2},
+\]
+as $n \to \infty$.
+\end{lemma}
+
+\begin{proof}
+Recall that $\Exp{T_\infty(y)} = \mu(y)^2 P(y) = (1+\smallO{1})k_n^2 P(y)$ on $\Kcal_C(k_n)$. We will show that
+\[
+	\Exp{\left|\Exp{T_{\mathrm{box}}(p_0)} - T_\infty(y)\right|} = \smallO{s(k_n) k_n^2},
+\]
+which implies the result.
+
+Define $\Rcal^\prime := (\R \times \R_+) \setminus \Rcal$. Then we can write
+\begin{align*}
+	\left|T_{\mathrm{box}}(p_0) - T_\infty(y)\right|
+	&\le \left|T_{\mathrm{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right| 
+		+ \left|\widetilde{T}_{\text{box}}(p_0) - T_\infty(y)\right|\\
+	&= \left|T_{\mathrm{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right| 
+		+ \sum_{p_1, p_2 \in \Pcal \cap \Rcal^\prime}^{\ne} T_{\infty}(p_0,p_1,p_2).
+\end{align*}
+Then by the Campbell-Mecke formula
 \begin{align*}
@@
 \end{equation}
+
 Therefore, on $\Kcal_C(k_n)$, 
 \begin{align*}
-	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} \rho(y_0,k_n) \left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| 
-		e^{-\alpha y_0} \dd y_0\\
-	&= \bigO{1} \left(\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)} \right) 
-		\int_{0}^\infty \rho(y_0,k_n) e^{-\alpha y_0} \dd y_0\\
-	&= \bigO{1} \left(\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)} \right) p_{k_n} = \smallO{s(k_n) p_{k_n} k_n^2},
-\end{align*}
-%\TM{ Typo : $e^{-\alpha}$ }
-where the last part follows from Lemma~\ref{lem:scaling_s_alpha} and the fact that $s(k_n)^2 = \smallO{s(k_n)}$. This establishes~\eqref{eq:triangle_diff_main_term} and hence finishes the proof.
+	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| 
+	&= \bigO{\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)}} \\
+	&= \bigO{\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)}} = \smallO{s(k_n) k_n^2},
+\end{align*}
+where the last part follows from Lemma~\ref{lem:scaling_s_alpha} and the fact that $s(k_n)^2 = \smallO{s(k_n)}$.
+\end{proof}
+
+We can now prove the main result of this section.
+
+\begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]
+First, by Lemma~\ref{lem:appox_triangle_count_box} and~\eqref{eq:alt_c_ast_kn} we have
+\begin{align*}
+	\Exp{c^\ast(k_n;\Gbox)} &= (1 + \smallO{1}) \frac{1}{p_{k_n}} \int_{\Kcal_{C}(k_n)} P(y)
+		\rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y \\
+	&\hspace{10pt}+ \smallO{s(k_n)}	\frac{1}{p_{k_n}} \int_{\Kcal_{C}(k_n)} P(y)
+			\rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y.
+\end{align*}
+By Lemma~\ref{lem:degree_integral} the integral in the second term is $(1+\smallO{1}) p_{k_n}$ and thus the second term is $\smallO{s(k_n)} = \smallO{\gamma(k_n)}$.
+Hence it remain to prove that the first term is $(1+\smallO{1}) \gamma(y)$.
+Using~\eqref{eq:alt_gamma_kn} it is enough to show that
+\[
+	\int_{\Kcal_{C}(k_n)} P(y) \rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y
+	= (1+\smallO{1}) \int_{\Kcal_{C}(k_n)} P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
+\]
+Now recall the substitution of variables from the proof of Lemma~\ref{lem:degree_integral}: $z(y) = 2 \log(\mu_{\mathrm{box}}(y)/\xi)$.
+We will apply this change of variables to the right hand side in the above equation.
+This yields
+\begin{align*}
+	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} P(y) \rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y\\
+	&= (1+\smallO{1}) \int_{\Kcal_C(k_n)} P(z(y) - 2\log(1+\smallO{1})) \rho(z(y),k_n) 
+		z^\prime(y) \alpha e^{-\alpha z(y)} \dd y\\
+	&= (1+\smallO{1}) \int_{\Kcal_C(k_n)} P(z - 2\log(1+\smallO{1})) \rho(z,k_n) \alpha e^{-\alpha z} \dd z.
+\end{align*}
+Next we recall that by Proposition~\ref{prop:asymptotics_P}
+\[
+	P(y) \sim \begin{cases}
+		e^{-\frac{y}{2}(4\alpha - 2)} c_\alpha \xi^{4\alpha - 2} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4}\\
+		\frac{y}{2} e^{-\frac{y}{2}} &\mbox{if } \alpha = \frac{3}{4}\\
+		e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} &\mbox{if } \alpha > \frac{3}{4}.
+	\end{cases}
+\]
+In particular, this implies that $P(z - 2\log(1+\smallO{1})) = (1+\smallO{1})P(z)$, uniformly on $\Kcal_C(k_n)$. We therefore conclude that
+\[
+	\int_{\Kcal_{C}(k_n)} P(y) \rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y
+		= (1+\smallO{1}) \int_{\Kcal_{C}(k_n)} P(z) \rho(z,k_n) \alpha e^{-\alpha z} \dd z,
+\]
+which finishes the proof.
 %
-% \TM{ Also justify penultimate step! }\PvdH{What do you mean?}
-%To finish the argument we observe that
+%
+%
+%
+%Let us write $\Rcal^\prime := (\R \times \R_+) \setminus \Rcal$ and let $p_0 = (0,y)$ denote the typical point.
+Next we recall that it is enough to show~\eqref{eq:triangle_diff_main_term}, so that in particular we have that $y \in \Kcal_{C}(k_n)$.
+%
+%Now
 %\begin{align*}
-%	\int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha} \dd y
-%	&= \bigT{1} \Exp{N_{\infty}(k_n)} \gamma(k_n) = \bigT{ s(k_n) k_n^{-(2\alpha + 1)}}.
+%	\left|T_{\text{box}}(p_0) - T_{\infty}(p_0)\right| 
+%	&= \left|T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right| 
+%		+ \sum_{p_1, p_2 \in \Pcal \cap \Rcal^\prime}^{\ne} T_{\infty}(p_0,p_1,p_2),
 %\end{align*}
+%so that by the Campbell-Mecke formula
+%\begin{align*}
+%	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right|
+%	&\le \Exp{\left|T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right|}\\
+%	&\hspace{10pt}+ \int_{\Rcal^\prime}\int_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
+%		\dd x_2 \dd y_2 \dd x_1 \dd y_1. 
+%\end{align*}
+%
+%%\TM{ in the 1st integral we could have restricted to the ball of $p$, and possibly saved a lot.
+Does that not help?
+}\PvdH{the first integral is taken care of by another Lemma so it does not matter I think.}
+%The first part is taken care of by Lemma~\ref{lem:clustering_error_T_term}. For the other integral we have
+%\begin{align*}
+%	&\hspace{-30pt}\iint_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
+%		\dd x_2 \dd y_2 \dd x_1 \dd y_1\\
+%	&\le \left(\int_{\Rcal^\prime} \ind{p_1 \in \BallPo{p_0}} f(x_1,y_1) \dd x_1 \dd y_1\right)^2
+%		= \bigO{\left(e^{y/2} \int_{R}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}\\
+%	&= \bigO{e^{y} e^{-(2\alpha-1)R}} = \bigO{e^y n^{-(4\alpha - 2)}}.
+%\end{align*}
+%%\TM{ Typo : $f_{\mu, \nu}$? Also give more details how line 3 follows. }
+%Thus we conclude, using Lemma~\ref{lem:clustering_error_T_term}, that,
+%\begin{equation}\label{eq:triangle_count_diff_scaling}
+%	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| = \bigO{y n^{-(2\alpha - 1)} + n^{-(4\alpha-2)} e^{y}}.
+%\end{equation}
+%Therefore, on $\Kcal_C(k_n)$, 
+%\begin{align*}
+%	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} \rho(y_0,k_n) \left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right| 
+%		e^{-\alpha y_0} \dd y_0\\
+%	&= \bigO{1} \left(\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)} \right) 
+%		\int_{0}^\infty \rho(y_0,k_n) e^{-\alpha y_0} \dd y_0\\
+%	&= \bigO{1} \left(\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)} \right) p_{k_n} = \smallO{s(k_n) p_{k_n} k_n^2},
+%\end{align*}
+%%\TM{ Typo : $e^{-\alpha}$ }
+%where the last part follows from Lemma~\ref{lem:scaling_s_alpha} and the fact that $s(k_n)^2 = \smallO{s(k_n)}$. This establishes~\eqref{eq:triangle_diff_main_term} and hence finishes the proof.
+%%
+%% \TM{ Also justify penultimate step! }\PvdH{What do you mean?}
+%%To finish the argument we observe that
+%%\begin{align*}
+%%	\int_{a_n^-}^{a_n^+} \rho(y,k_n) P(y) e^{-\alpha} \dd y
+%%	&= \bigT{1} \Exp{N_{\infty}(k_n)} \gamma(k_n) = \bigT{ s(k_n) k_n^{-(2\alpha + 1)}}.
+%%\end{align*}
 \end{proof}
 
-From the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} we obtain the following useful corollary, which will be used in Section~\ref{sec:concentration_c_P_n}. Recall that
-\[
-	\rho_{\mathrm{box}}(y,k_n) = \Prob{\Po(\mu(\BallPon{y})) = k_n},
-\]
-denote the degree distribution of a point $p_0 = (0,y)$ in $\Gbox$.
+From the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} we immediately obtain the following useful corollary, which will be used in Section~\ref{sec:concentration_c_P_n}.
 
@@
 
-\begin{proof}
-We first write
-\[
-	\Exp{\left|\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)\right|} 
-	\le \Exp{\left|T_{\text{box}}(y) - \widetilde{T}_{\text{box}}(y) \right|}
-	+\Exp{\left|T_{\text{box}}(y) - T_{\infty}(y)\right|}.
-\]
-Therefore, Lemma~\ref{lem:clustering_error_T_term} and equation~\eqref{eq:triangle_count_diff_scaling} imply that, uniformly for $y \in \Kcal_C(k_n)$,
-\[
-	\Exp{\left|\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)\right|} = \bigO{\log(k_n)n^{-(2\alpha - 1)}
-	+ k_n^2 n^{-(4\alpha - 2)}}	= \smallO{s(k_n) k_n^2},
-\]
-where the last part is due to Lemma~\ref{lem:scaling_s_alpha}.
-Next, since $\Exp{T_\infty(y)} = \Mu{\BallPo{y}}^2 P(y)$, we get
-\[
-	\Exp{\widetilde{T}_{\text{box}}(y)} = \Exp{T_{\infty}(y)} + \Exp{\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)} 
-	= k_n^2 P(y) + \smallO{s(k_n)k_n^2},
-\]
-uniformly on $\Kcal_{C}(k_n)$. Therefore, we can apply a concentration of height argument to replace $\rho_{\text{box}}(y,k_n)$ with $\rho(y,k_n)$ and thus obtain
-\begin{align*}
-	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(y)} 
-		f(x,y) \dd x \dd y\\
-	&= n k_n^2 \int_{\Kcal_{C}(k_n)} \rho(y,k_n) \left(P(y) + \smallO{s(k_n)}\right)
-		\alpha e^{-\alpha y} \dd y\\
-	&= (1+\smallO{1}) n k_n^2 \int_{\Kcal_{C}(k_n)} P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y\\
-	&= (1+\smallO{1}) n k_n^2 \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
-\end{align*}
-where we used that on $\Kcal_{C}(k_n)$, $P(y) = \bigT{s(k_n)}$. This proves the first statement. The second statement follows by observing that
-\[
-	\int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y = p_{k_n} \gamma(k_n)
-	= \bigT{k_n^{-(2\alpha + 1)} s(k_n)}.
-\]
-\end{proof}
+%\begin{proof}
+%We first write
+%\[
+%	\Exp{\left|\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)\right|} 
+%	\le \Exp{\left|T_{\text{box}}(y) - \widetilde{T}_{\text{box}}(y) \right|}
+%	+\Exp{\left|T_{\text{box}}(y) - T_{\infty}(y)\right|}.
+%\]
+%Therefore, Lemma~\ref{lem:clustering_error_T_term} and equation~\eqref{eq:triangle_count_diff_scaling} imply that, uniformly for $y \in \Kcal_C(k_n)$,
+%\[
+%	\Exp{\left|\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)\right|} = \bigO{\log(k_n)n^{-(2\alpha - 1)}
+%	+ k_n^2 n^{-(4\alpha - 2)}}	= \smallO{s(k_n) k_n^2},
+%\]
+%where the last part is due to Lemma~\ref{lem:scaling_s_alpha}.
+%Next, since $\Exp{T_\infty(y)} = \Mu{\BallPo{y}}^2 P(y)$, we get
+%\[
+%	\Exp{\widetilde{T}_{\text{box}}(y)} = \Exp{T_{\infty}(y)} + \Exp{\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)} 
+%	= k_n^2 P(y) + \smallO{s(k_n)k_n^2},
+%\]
+%uniformly on $\Kcal_{C}(k_n)$. Therefore, we can apply a concentration of height argument to replace $\rho_{\text{box}}(y,k_n)$ with $\rho(y,k_n)$ and thus obtain
+%\begin{align*}
+%	&\hspace{-30pt}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(y)} 
+%		f(x,y) \dd x \dd y\\
+%	&= n k_n^2 \int_{\Kcal_{C}(k_n)} \rho(y,k_n) \left(P(y) + \smallO{s(k_n)}\right)
+%		\alpha e^{-\alpha y} \dd y\\
+%	&= (1+\smallO{1}) n k_n^2 \int_{\Kcal_{C}(k_n)} P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y\\
+%	&= (1+\smallO{1}) n k_n^2 \int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
+%\end{align*}
+%where we used that on $\Kcal_{C}(k_n)$, $P(y) = \bigT{s(k_n)}$. This proves the first statement. The second statement follows by observing that
+%\[
+%	\int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y = p_{k_n} \gamma(k_n)
+%	= \bigT{k_n^{-(2\alpha + 1)} s(k_n)}.
+%\]
+%\end{proof}
 
@@
 Due to symmetry it is then enough to restrict the analysis to the case where $x^\prime > 0$.
-\TM{ does this not depend on $p$?
-}\PvdH{I do not think so, because we can always take $p = (0,y)$ due to the invariance in the $x$-direction.
-I have updated the text to better reflect this.}
+%\TM{ does this not depend on $p$? }\PvdH{I do not think so, because we can always take $p = (0,y)$ due to the invariance in the $x$-direction. I have updated the text to better reflect this.} 
 For this case there are two important points in the box $\Rcal$.

### 2020-01-03 hyperbolic_degrees.tex
updated section 3

@@
 
+Since the new contribution of Theorem~\ref{thm:degrees_hyperbolic} concerns the cases where the degree $k_n \to \infty$, we will assume that this holds throughout this section.
+
 \subsection{Proof overview}
 
-As mentioned earlier, we plan to make use of the Campbell-Mecke formula for comparing the degree distribution in $\GPo$ with that of a \emph{typical point} in $\Ginf$.
+We start by using the Campbell-Mecke formula to compare the degree distribution in $\GPo$ with that of a \emph{typical point} in $\Ginf$.
 For this we will be considering the Poisson process $\Pcal$ to which we add one additional point $(0,y)$ on the $y$-axis.
@@
 \]
-We then relate this to the Poissonized KPKVB model $\GPo$ by showing in Section~\ref{ssec:expected_degrees_GPo} that for any $1 \le k_n \le n -1$ with $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$, $\Exp{N_{\Po}(k_n)} = (1+\smallO{1}) n p_{k_n}$ and more generally,
-\[
+We then relate this to the Poissonized KPKVB model $\GPo$.
+More precisely, let $N_{\Po}(k)$ denote the set of degree $k$ vertices in $\GPo$.
+We then show in Section~\ref{ssec:expected_degrees_GPo} that for any $1 \ll k_n \le n -1$ with $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$, $\Exp{N_{\Po}(k_n)} = (1+\smallO{1}) n p_{k_n}$ and more generally,
+\begin{equation}\label{eq:def_factorial_moments_GPo}
 	\Exp{\binom{N_{\Po}(k_n)}{r}} = (1+\smallO{1}) \frac{\Exp{N_{\Po}(k_n)}^r}{r!},
-\]
+\end{equation}
 for any integer $r \ge 1$ in Section~\ref{ssec:factorial_moments_GPo}.
@@
 To extend these results to $G_n$ we couple the construction of the KPKVB model to that of the Poissonized version $\GPo$ in Section~\ref{ssec:coupling_Gn_GPo} to show that a.a.s, $N_n(k_n) = (1+\smallO{1}) N_{\Po}(k_n)$.
-With these results we then proof Theorem~\ref{thm:degrees_hyperbolic} in Section~\ref{ssec:proof_thm_degrees}.
+With these results we then prove Theorem~\ref{thm:degrees_hyperbolic} in Section~\ref{ssec:proof_thm_degrees}.
 
@@
 \begin{align*}
-	\mu(y) &= \int_{\BallPo{p}} f(x',y') \, dx' \,d y'  
- 		= \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' \\
-	&= \int_0^\infty 2 e^{(y+y')/2} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dy' 
- 		= \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' \\
-	&= \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
+	\mu(y) &= \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' 
+		= \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' 
+		= \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
 \end{align*}
@@
 \end{align*}
-where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{+}$ the upper incomplete Gamma-function.
+where we recall that $\Gamma^{+}$ denotes the upper incomplete Gamma-function.
 Note that, unsurprisingly, this is identical to the expression Gugelmann et al.~\cite{gugelmann2012random} gave for the limiting degree distribution of $G(n;\alpha,\nu)$.
@@
 \]
-Observe that
-
-Our first results relate these measures to the measure $\mu(y)$ on the infinite model $\Ginf$.
+
+Our first results relate these measures to the measure $\mu(y)$, of the ball $\BallPo{y}$ in the infinite model $\Ginf$.
 
@@
 
-For the first integral $I_1$, we first recall from Lemma~\ref{lem:asymptotics_Omega_hyperbolic} that there is a positive constant $K$ such that for any $\varepsilon >0$, for all $y_1, y_2 \in [0,(1-\varepsilon)R]$, $y_1+y_2 <R$, we have (for $\Phi(y_1,y_2)$ from Equation~\ref{eq:def_Omega_hyperbolic})
+For the first integral $I_1$, we first recall from Lemma~\ref{lem:asymptotics_Omega_hyperbolic} that there is a positive constant $K$ such that for any $\varepsilon >0$, for all $y_1, y_2 \in [0,(1-\varepsilon)R]$, $y_1+y_2 <R$, we have
 \[
@@
 \]
-Thus we define a main and error term of $I_1$ as
+We thus define the main and error term of $I_1$ as
 \begin{align*}
@@
 	\mu(\BallPon{p})
-	&= \int_0^{R} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
-		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
+	&= \int_0^{R} \int_{-e^{\frac{y+y^\prime}{2}}}^{e^{\frac{y+y^\prime}{2}}} 
+		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
 	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
@@
 And the same holds if we instead consider $\mu_{\mathrm{box}}(y)$.
+The proof contains some technical elements that are contained in the Appendix to not hinder the flow of the argument.
 
@@
 \[
-	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po,n}(y)) = k_n} \alpha e^{-\alpha y} \dd y
-	= (1+o(1))\int_0^\infty \Pee(Po(\xi e^{\frac{z}{2}})=k_n) \alpha e^{-\alpha z} \dd z.
+	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{\Po}(y)) = k_n} \alpha e^{-\alpha y} \dd y
+	= (1+o(1))\int_0^\infty \Pee(\Po(\xi e^{\frac{z}{2}})=k_n) \alpha e^{-\alpha z} \dd z.
 \]
@@
 
-Define the function $z(y)=2\ln\frac{\mu_{Po,n}(y)}{\xi}$ (note that $z(y)$ is well-defined as $\mu_{Po,n}(y)\geq 0$ and that $z(y)$ is bijective because $\mu_{Po,n}(y)$ is strictly monotone increasing and continuous, see Lemma~3.3.
+Define the function $z(y)=2\ln\frac{\mu_{\Po}(y)}{\xi}$ (note that $z(y)$ is well-defined as $\mu_{Po,n}(y)\geq 0$ and that $z(y)$ is bijective because $\mu_{\Po}(y)$ is strictly monotone increasing and continuous, see Lemma~3.3.
 in \cite{gugelmann2012random}).
@@
 \begin{align*}
-\mu_{Po,n}(y) = \xi e^{\frac{z(y)}{2}}.
-\end{align*}
-From Lemma~\ref{lem:average_degree_P_n}, it follows that uniformly for all $0\leq y\leq (1-\varepsilon)R$, $\xi e^{\frac{y}{2}} = (1+o(1))\mu_{Po,n}(y) = (1+o(1))\xi e^{\frac{z(y)}{2}}$, and hence that
+\mu_{\Po}(y) = \xi e^{\frac{z(y)}{2}}.
+\end{align*}
+From Lemma~\ref{lem:average_degree_P_n}, it follows that uniformly for all $0\leq y\leq (1-\varepsilon)R$, $\xi e^{\frac{y}{2}} = (1+o(1))\mu_{\Po}(y) = (1+o(1))\xi e^{\frac{z(y)}{2}}$, and hence that
 \begin{align*}
@@
 \[
-	\mu_{Po}^\prime(y) = (1+o(1))\frac{1}{2}\mu(y) = (1+o(1))\frac{1}{2}\mu_{Po}(y)
+	\mu_{\Po}^\prime(y) = (1+o(1))\frac{1}{2}\mu(y) = (1+o(1))\frac{1}{2}\mu_{\Po}(y)
 	= (1+\smallO{1}) \mu^\prime(y),
@@
 \[
-	z^\prime(y) = \frac{2\mu_{Po}^\prime(y)}{\mu_{Po,n}(y)} = 1+o(1).
+	z^\prime(y) = \frac{2\mu_{\Po}^\prime(y)}{\mu_{\Po}(y)} = 1+o(1).
 \]
@@
 \begin{align*}
-	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po}(y))=k_n} \alpha e^{-\alpha y}dy 
+	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{\Po}(y))=k_n} \alpha e^{-\alpha y}dy 
 	= (1+o(1)) \int_0^{(1-\varepsilon)R} \Prob{\Po(\xi e^{\frac{z(y)}{2}})=k_n}\alpha e^{-\alpha z(y)} z^\prime(y) dy.
@@
 \begin{align*}
-	\int_{z(0)}^{z((1-\varepsilon)R)} \Prob{\Po(\xi e^{\frac{z}{2}})=k_n}\alpha e^{-\alpha z} dz 
+	\int_{z(0)}^{z((1-\varepsilon)R)} \Prob{\Po(\mu(z))=k_n}\alpha e^{-\alpha z} dz 
 	&= (1+o(1))\int_0^\infty \Pee(Po(\mu(z))=k_n)\alpha e^{-\alpha z}dz.
@@
 \[
-	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po}(y))=k_n} \alpha e^{-\alpha y}dy
+	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{\Po}(y))=k_n} \alpha e^{-\alpha y}dy
 	= (1+o(1))\int_0^\infty \Pee(Po(\mu(z))=k_n)\alpha e^{-\alpha z}dz,
 \]
-which finishes the proof for $\mu_{Po}(y)$.
+which finishes the proof for $\mu_{\Po}(y)$.
 
@@
 Hence we get $\mu_{\mathrm{box}}^\prime(y) = (1+\smallO{1}) \mu^\prime(y)$ and thus $z^\prime(y) = 1 + \smallO{1}$ uniformly for $0 \le y \le (1-\varepsilon)R$.
-We can now apply the same change of variables to arrive at the required statement.
+We can now apply the same change of variables and a concentration of heights argument to arrive at the required statement.
 
@@
 
-To prove the factorization of higher moments of $N_{\Po}(k_n)$ and $\Nbox(k_n)$ we first have to understand the joint degree distribution in $\GPo$ $\Gbox$, respectively.
+To prove the factorization of higher moments of $N_{\Po}(k_n)$ and $\Nbox(k_n)$ as in~\eqref{eq:def_factorial_moments_GPo}, we first have to understand the joint degree distribution in $\GPo$ and $\Gbox$, respectively.
 This subsequently requires us to analyze the joint neighbourhoods of two points $p, p^\prime$ in these models.
@@
 In particular, for two points $p, p^\prime \in \Rcal$ and $V = \{p,p^\prime\}$, $\varphi_{\mathrm{box}}(V, k ;p,p^\prime)$ is the joint degree distribution of $p, p^\prime $ in $\Gbox$.
-We will use similar notation for the Poissonize KPKVB model.
+We will use similar notation for the Poissonized KPKVB model.
 That is, $\GPo \cup \{p_1,\dots,p_r\}$ denotes the Poissonized KPKVB model obtained by adding $p_1,\dots,p_r$ to the vertex set of the graph and adding all corresponding edges and $\varphi_{\Po}(V, k ; p_1,\dots,p_s)$ the corresponding joint degree function.
@@
 	\varphi_{\mathrm{box}}(\{p,p^\prime\}, k ;p,p^\prime) 
-	= \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k_n, X_2(p,p^\prime) + Y(p,p^\prime) = k_n}.
+	= \Prob{X_1(p,p^\prime) + Y(p,p^\prime) = k, X_2(p,p^\prime) + Y(p,p^\prime) = k_n}.
 \]
 Recall the definition of $y_{k_n,C}^\pm$ from equation~\eqref{eq:def_y_k_C}.
-We will show (see Lemma~\ref{cor:expected_common_neighbours_Ecal_set}) that for any two points $p, p^\prime$ whose $y$-coordinate is in $[y_{k_n, C}^-, y_{k_n,C}^+]$ and whose $x$-coordinates are sufficiently separated, it holds that $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$.
-Since the mean of $X_1$ and $X_2$ for such two points is $k_n$, the contribution of the Poisson random variable $Y(p,p^\prime)$ to theirs degrees becomes negligible as $k_n \to \infty$ and hence the joint degree distribution will factorizes on this set.
+We will show (see Lemma~\ref{cor:expected_common_neighbours_Ecal_set}) that for any two points $p, p^\prime$ whose $y$-coordinate is in $\Kcal_C(k_n)$ and whose $x$-coordinates are sufficiently separated, it holds that $\Mu{\BallPon{p} \cap \BallPon{p^\prime}} = \bigO{k_n^{1-\varepsilon}}$.
+Since the mean of $X_1$ and $X_2$ for such two points is $k_n$, the contribution of the Poisson random variable $Y(p,p^\prime)$ to their degrees becomes negligible as $k_n \to \infty$ and hence the joint degree distribution will factorizes on this set.
 The main idea is that if $p$ and $p^\prime$ are sufficiently separated in the $x$-direction, then the overlap of their neighbourhoods $\BallPon{p} \cap \BallPon{p^\prime}$ is of smaller order than $\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}$.
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
 \centering
@@
 
-We start by analyzing the shape of joint neighbourhood.
+We start by analyzing the shape of the joint neighbourhood.
 Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$.
@@
 
-Note that $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$ correspond to, respectively, $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ considered in Section~\ref{ssec:missing_triangles}.
-The derivation of $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ is done in a similar manner and we omit the details here.
-The full expressions of all these functions are given below for further reference.
+We start by deriving expressions for these important coordinates.
+For this we introduce some notation.
+For any $p = (x,y) \in \Rcal$ we will define the left and right boundary functions as, respectively,
+\begin{align}
+	b_p^-(z) &= \begin{cases}
+		2 \log\left(x-z\right) - y &\mbox{if }  -\frac{\pi}{2} e^{R/2} \le z \le x - e^{y/2}  \\
+		2\log\left(\pi e^{R/2} + x - z\right) - y 
+			&\mbox{if } x - e^{(y + R)/2} + \pi e^{R/2} \le z \le \frac{\pi}{2} e^{R/2}\\
+		0 &\mbox{otherwise}
+	\end{cases}\\
+	b_p^+(z) &= \begin{cases}
+		2 \log\left(z-x\right) - y &\mbox{if } x + e^{y/2} \le z \le \frac{\pi}{2} e^{R/2} \\
+		2\log\left(\pi e^{R/2} + z - x\right) - y 
+			&\mbox{if } -\frac{\pi}{2} e^{R/2} \le z \le x + e^{(y + R)/2} - \pi e^{R/2}\\
+		0 &\mbox{otherwise}
+	\end{cases}
+\end{align}
+Note that these functions describe the boundaries of the ball $\BallPon{p}$.
+In particular, $p^\prime = (x^\prime, y^\prime) \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
+
+We shall derive the expressions for the point $(\hat{x}_{\text{left}}(p,p^\prime), \hat{y}_{\text{left}}(p,p^\prime))$.
+The $x$-coordinate $\hat{x}_{\text{left}}(p,p^\prime)$ is the solution to the equation $b_{p}^+(z) = b_{p^\prime}^-(z)$ for $-\frac{\pi}{2} e^{R/2} \le z \le + e^{y/2}$.
+This equation becomes
+\[
+	2\log\left(\pi e^{R/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x^\prime-z\right) - y^\prime,
+\]
+whose solution is $\frac{x^\prime - \pi e^{R/2}}{1 + e^{(y^\prime - y)/2}}$.
+Plugging this into either the left or right hand side of the above equation yields the $y$-coordinate $\hat{y}_{\text{left}}(p,p^\prime) = 2 \log\left(\frac{\pi e^{R/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)$.
+The expressions for $\hat{x}_{\text{right}}(p,p^\prime$ and $\hat{y}_{\text{right}}(p,p^\prime)$ are derived in a similar way.
+The expression for $d(p,p^\prime)$ follows as the difference $b_{p^\prime}^-(x^\prime - e^{y^\prime/2}) - b_p^+(e^{y/2})$.
+
+The full expressions of all coordinates are given below for further reference.
 
@@
 	h(y) &= R - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
-	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
-	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R}{2}} - x^\prime\right) - y^\prime 
-		\label{eq:def_height_right_P_n} \\
+%	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
+%	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R}{2}} - x^\prime\right) - y^\prime 
+%		\label{eq:def_height_right_P_n} \\
 %	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
@@
 Again, without loss of generality we assume that $p = p_0 = (0,y)$ and $p^\prime = (x^\prime, y^\prime)$ with $0 \le x^\prime \le \frac{\pi}{2} e^{R/2}$.
-Note that since $0 < x^\prime \le \frac{\pi}{2} e^{R/2}$,$ \hat{y}_{\mathrm{right}}(p,p^\prime) \le \hat{y}_{\mathrm{left}}(p,p^\prime)$.
+Note that since $0 < x^\prime \le \frac{\pi}{2} e^{R/2}$, $ \hat{y}_{\mathrm{right}}(p,p^\prime) \le \hat{y}_{\mathrm{left}}(p,p^\prime)$.
 We write $\hat{y}$ for $\hat{y}_{\mathrm{right}}(p,p^\prime)$ and observe that below $\hat{y}$ the balls $\BallPon{p}$ and $\BallPon{p^\prime}$ are disjoint.
@@
 \begin{lemma}\label{lem:common_neighbours_KPKVB}
-Let $0 < \varepsilon < 1$, $p, p^\prime \in \Rcal$ with $y,y^\prime \le (1-\varepsilon)R$ and denote by $\Ncal_{\Po}(p,p^\prime)$ the number of joint neighbours of $p, p^\prime$ in $\GPo$.
+Let $0 < \varepsilon < 1$, $p, p^\prime \in \Rcal$ with $y,y^\prime \le (1-\varepsilon)R$, denote by $\Ncal_{\Po}(p,p^\prime)$ the number of joint neighbours of $p, p^\prime$ in $\GPo$ and let $K$ be the constant from Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
 Then, whenever $|x - x^\prime|_n > \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)\left(1 + \frac{\pi^2 K}{4}\right)$,
@@
 \[
-	\lambda = \log\left(1 + \frac{\pi^2 K}{4}\right),
-\]
-with $K$ the constant from Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
+	\lambda = \log\left(1 + \frac{\pi^2 K}{4}\right).
+\]
 \end{lemma}
@@
 We will proceed in a similar fashion as for Lemma~\ref{lem:common_neighbours_Pcal_n}.
-That is we will bound the expected number of common neighbours by the number of neighbors of $p$ whose $y$-coordinate is above the intersection of the right boundary of $\BallHyp{p}$ and the left boundary of $\BallHyp{p^\prime}$.
+That is, we will bound the expected number of common neighbours by the number of neighbors of $p$ whose $y$-coordinate is above the intersection of the right boundary of $\BallHyp{p}$ and the left boundary of $\BallHyp{p^\prime}$.
 Denote by $\hat{y}$ the height of this intersection point.
@@
 it holds that $\Phi(y,y_1) \le x^\prime - \Phi(y^\prime, y_1)$, with $\lambda$ as defined in the statement of the lemma.
-Note that by assumption on $|x - x^\prime|$ the above upper bound is non-negative.
+Note that by assumption on $x^\prime := |x - x^\prime|_n$ (since we can take $x = 0$) the above upper bound is non-negative.
 Using Lemma~\ref{lem:asymptotics_Omega_hyperbolic} it suffices to prove that for all such $y_1$,
@@
 
-Recall the definition of the stripe $\stripknc = \Rcal \cap (\R_+ \times [y_{k_n,C}^-, y_{k_n,C}^+])$ from~\eqref{eq:def_stripe} and define, for any $0 < \varepsilon < 1$, the following set
+Let us now define the \emph{stripe}
+\begin{equation}\label{eq:def_stripe}
+	\stripknc = \Rcal \cap (\R_+ \times \Kcal_C(k_n)).
+\end{equation} 
+and in addition define, for any $0 < \varepsilon < 1$, the following set
 \begin{equation}\label{eq:def_joint_degree_set_E_growing_k}
@@
 \[
-	\phi_n(p,p^\prime) = 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
+	\phi_n(p,p^\prime) = 2\left(\frac{|x - x^\prime|_n}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)} 
 		+ \frac{3 \nu^{2\alpha + 1}e^{-(\alpha - \frac{1}{2})R} e^{\alpha y}}{2 \pi^{2\alpha}\left(
@@
 \]
-We thus need to show that $\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon}}$.
-For $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, it holds that $e^{y/2}, e^{y^\prime/2} = \bigT{k_n}$ and $|x - x^\prime| > k_n^{1+\varepsilon}$ and hence
-\begin{align*}
-	 2\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
+We thus need to show that $\phi_n(p,p^\prime) = \bigO{k_n^{-\varepsilon^\prime}}$.
+For $(p,p^\prime) \in \mathcal{E}_\varepsilon(k_n)$, it holds that $e^{y/2}, e^{y^\prime/2} = \bigT{k_n}$ and $|x - x^\prime|_n > k_n^{1+\varepsilon}$ and hence
+\begin{align*}
+	 2\left(\frac{|x - x^\prime|_n}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)^{-(2\alpha - 1)}
 	 =	\bigO{k_n^{-\varepsilon(2\alpha - 1)}}.
@@
 
-Let us now define the \emph{stripe}
-\begin{equation}\label{eq:def_stripe}
-	\stripknc = \Rcal \cap (\R_+ \times \Kcal_C(k_n)).
-\end{equation} 
+Recall the definition of the stripe $\stripknc = \Rcal \cap (\R_+ \times [y_{k_n,C}^-, y_{k_n,C}^+])$ from~\eqref{eq:def_stripe}.
 Consider a fixed number of points $p_1, \dots, p_r$.
-Then, if their $x$-coordinates are sufficient far apart and their $y$ coordinates lie with in the strip $\stripknc$, their degrees are asymptotically independent.
+Then, if their $x$-coordinates are sufficient far apart and their $y$ coordinates lie within the stripe $\stripknc$, their degrees are asymptotically independent.
 
@@
 To prove~\eqref{eq:probdegfact_main} let $\varepsilon'=\min(\varepsilon,\varepsilon(2\alpha-1))\in (0,1)$.
-Since for $1\leq i \leq r$, it is given that $|x_{p_i}-x_{p_{r+1}}|\geq k_n^{1+\varepsilon}$, it then follows from Lemma~\ref{lem:common_neighbours_KPKVB} that $\E[Y_j] = \bigO{k_n^{1-\varepsilon'}}$.
-To prove the result for $\Gbox$ we use Lemma~\ref{lem:common_neighbours_Pcal_n}.
+Since for $1\leq i \leq r$, it is given that $|x_{p_i}-x_{p_{r+1}}|\geq k_n^{1+\varepsilon}$, then in the case where $H = \GPo \cup\{p_1,\dots,p_s\}$ it follows from Lemma~\ref{lem:common_neighbours_KPKVB} that $\E[Y_j] = \bigO{k_n^{1-\varepsilon'}}$.
+When $H=\Gbox \cup \{p_1,\dots,p_s\}$ we get the same result using Lemma~\ref{lem:common_neighbours_Pcal_n}.
 The rest of the proof is independent of which of the two models we consider and only uses that $\E[Y_j] = \bigO{k_n^{1-\varepsilon'}}$.
@@
 	\Prob{Y_{r+1} \not \in A_n} 
-	= \Prob{|Y_{r+1}-\mu|\geq c_0\sqrt{k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}}}
-	\le \Prob{|Y_{r+1}-\mu|\geq c_1\sqrt{\mu\ln\mu}}
+	&= \Prob{|Y_{r+1}-\mu|\geq c_0\sqrt{k_n^{1-\varepsilon'}\ln k_n^{1-\varepsilon'}}}\\
+	&\le \Prob{|Y_{r+1}-\mu|\geq c_1\sqrt{\mu\ln\mu}}
 	=\bigO{k_n^{-\frac{(1-\varepsilon')c_1^2}{2}}}.
@@
 \end{align*}
-As $X_{r+1}$ is independent of $X_1, \dots, X_r, Y_1, \dots, Y_r$ by the properties of a Poisson process (as $X_{r+1}$ counts the number of points in a set which is disjoint to what $X_1,\dots,X_r, Y_1, \dots, Y_r$ are counting), it follows that
+As $X_{r+1}$ is independent of $X_1, \dots, X_r, Y_1, \dots, Y_r$ by the properties of a Poisson process (as $X_{r+1}$ counts the number of points in a set which is disjoint of $X_1,\dots,X_r, Y_1, \dots, Y_r$), it follows that
 \begin{align*}%\label{eq:afterindep}
@@
 \begin{align*}
+	\frac{\Prob{X_{r+1}=k_n-y_{r+1}}}{\Prob{X_{r+1}=k_n-s}}
 	&=(1+o(1)) (k_n-y_{r+1}+(y_{r+1}-s))^{y_{r+1}-s} \lambda^{s-y_{r+1}} \\
@@
 \begin{lemma}[Factorial moments]\label{lem:factmoment}
-Recall that $N_{Po}(k)$ denotes the number of degree $k$ vertices in $\GPo$. % and $k_n \rightarrow \infty$ as 
-For any positive integer $r$, it holds that
+Recall that $N_{Po}(k)$ denotes the number of degree $k$ vertices in $\GPo$. Then, for any positive integer $r$ and $k_n \rightarrow \infty$, it holds that
 \[
@@
 	\begin{align*}
-	&\int_\Rcal \cdots \int_\Rcal \varphi(\{p_1,\dots,p_r \};p_1,\dots,p_r) 
+	&\int_\Rcal \cdots \int_\Rcal \varphi(\{p_1,\dots,p_r \}, k_n ;p_1,\dots,p_r) 
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r \\
-	&= (1+o(1))\left(\int_\Rcal  \varphi(\{p_1\};p_1) f(x,y) \dd x \dd y\right)^r .
+	&= (1+o(1))\left(\int_\Rcal  \varphi(\{p_1\}, k_n ;p_1) f(x,y) \dd x \dd y\right)^r .
 	\end{align*}
@@
 \begin{align*}
-	\int_{\stripknc} \varphi(\{p_1\};p_1) f(x,y) \dd x \dd y 
-	&= (1+\smallO{1}) \int_\Rcal  \varphi(\{p_1\};p_1) f(x,y) \dd x \dd y
+	\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x,y) \dd x \dd y 
+	&= (1+\smallO{1}) \int_\Rcal  \varphi(\{p_1\}, k_n ;p_1) f(x,y) \dd x \dd y\\
 	&= (1+\smallO{1}) 2\alpha \xi^{2\alpha} n k_n^{-(2\alpha + 1)} \numberthis \label{eq:integration_average_degree_stripe}
@@
 \begin{align*}
-	&\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r \};p_1,\dots,p_r) 
+	&\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r \}, k_n ;p_1,\dots,p_r) 
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r \\
-	&= (1+o(1))\left(\int_{\stripknc}  \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r.
+	&= (1+o(1))\left(\int_{\stripknc}  \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r.
 \end{align*}
@@
 \begin{align*}
-	&\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
+	&\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r\\
-	&= (1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r .
-\end{align*}
-Note that for $r=s$ this the claim of the lemma.
+	&= (1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r .
+\end{align*}
+Note that for $r=s$ this is the claim of the lemma.
 Throughout the proof $H$ is either $\GPo \cup\{p_1,\dots,p_s\}$ or $\Gbox \cup \{p_1,\dots,p_s\}$, depending on whether $\varphi$ is, respectively, $\varphi_{\Po}$ or $\varphi_{\mathrm{box}}$.
@@
 \begin{align*}
-\varphi(\{p_1\};p_1,\dots,p_s) = (1+o(1))\varphi(\{p_1\};p_1).
+\varphi(\{p_1\}, k_n ;p_1,\dots,p_s) = (1+o(1))\varphi(\{p_1\}, k_n ;p_1).
 \end{align*}
 To see this, note that as $p_1\in \stripknc$, the expected degree of $p_1$ in $\GPo$ is $\Theta(k_n)$.
-Assume that $p_1$ is adjacent to $s'<s$ many vertices among $v_2,\dots,p_s$.
+Assume that $p_1$ is adjacent to $s'<s$ many vertices among $p_2,\dots,p_s$.
 Then, as $s'<s$ is bounded and $k_n \rightarrow \infty$ as $n\rightarrow \infty$,  we have that
@@
 \begin{align*}
-\varphi(\{p_1\};p_1,\dots,p_s)&=\Pee(D_H(p_1)=k_n)
+\varphi(\{p_1\}, k_n ;p_1,\dots,p_s)&=\Pee(D_H(p_1)=k_n)
 = \Pee(D_{\GPo}(p_1)=k_n-s')\\
-&= (1+o(1))\Pee(D_{\GPo}(p_1)=k_n)=(1+o(1))\varphi(\{p_1\};p_1).
+&= (1+o(1))\Pee(D_{\GPo}(p_1)=k_n)=(1+o(1))\varphi(\{p_1\}, k_n ;p_1).
 \end{align*}
@@
 
-Firstly, we derive an upper bound for the complement $\Fcal_\epsilon(k_n)^c$.	Note that $$\varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s) \leq \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)$$
+Firstly, we derive an upper bound for the complement $\Fcal_\epsilon(k_n)^c$. Note that 
+\[
+	\varphi(\{p_1,\dots,p_{r+1}\}, k_n ;p_1,\dots,p_s) \leq \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s),
+\]
 and so,
 \begin{align*}
-	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s)
+	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_{r+1}\}, k_n ;p_1,\dots,p_s)
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
-	&\leq \int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
+	&\leq \int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}.
@@
 For $(p_1,\dots,p_{r+1})\in \Fcal_\epsilon(k_n)^c$, we have that $(p_1,\dots,p_r) \in \left(\stripknc\right)^r$ and $p_{r+1}=(x_{r+1},y_{r+1})$ satisfies $y_{k_n,c}^-\leq y_{r+1}\leq y_{k_n,c}^+$ and $x_{r+1}$ falls into an interval $I_n$ of length $2k_n^{1+\epsilon}$.
-As the integrand $\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)$ is constant in $x_{r+1}$, we can upper bound the corresponding integration  w.r.t. $\mu_n(dp_{r+1})$ resp. $dy_{r+1}$ as follows,
-\begin{align*}
-	&\int_{\{(x_{r+1},y_{r+1})\in\stripknc: x_{r+1}\in I_n\}} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s) 
+As the integrand $\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)$ is constant in $x_{r+1}$, we can upper bound the corresponding integration as follows,
+\begin{align*}
+	&\int_{\{(x_{r+1},y_{r+1})\in\stripknc: x_{r+1}\in I_n\}} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s) 
 		f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1} \\
-	&= \int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \int_{I_n} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)\frac{\alpha \nu}{\pi} e^{-\alpha y_{r+1}} dx_{r+1}dy_{r+1} \\
-	&\leq 2k_n^{1+\epsilon} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)\int_{y_{k_n,c}^-}^{y_{k_n,c}^+}  \frac{\alpha \nu}{\pi} e^{-\alpha y_{r+1}} dy_{r+1}.
+	&= \int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \int_{I_n} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)\frac{\alpha \nu}{\pi} e^{-\alpha y_{r+1}} dx_{r+1}dy_{r+1} \\
+	&\leq 2k_n^{1+\epsilon} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)\int_{y_{k_n,c}^-}^{y_{k_n,c}^+}  \frac{\alpha \nu}{\pi} e^{-\alpha y_{r+1}} dy_{r+1}.
 \end{align*}
@@
 \begin{align*}
-\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} e^{-\alpha y_1}dy_1 \leq \int_{y_{k_n,c}^-}^\infty e^{-\alpha y_1}dy_1 = \bigO{e^{-\alpha y_{k_n,c}^-}} = \bigO{\left( \frac{k_n-c\sqrt{k_n\ln k_n}}{\xi}\right)^{-2\alpha}} = \bigO{k_n^{-2\alpha}}.
+\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} e^{-\alpha y_{r+1}}dy_{r+1} \leq \int_{y_{k_n,c}^-}^\infty e^{-\alpha y_{r+1}}dy_{r+1} = \bigO{e^{-\alpha y_{k_n,c}^-}} = \bigO{\left( \frac{k_n-c\sqrt{k_n\ln k_n}}{\xi}\right)^{-2\alpha}} = \bigO{k_n^{-2\alpha}}.
 \end{align*}
@@
 \begin{align*}
-	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
+	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
 	&\leq \bigO{k_n^{1+\epsilon} k_n^{-2\alpha}}\int_{\stripknc} \cdots \int_{\stripknc} 
-		\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s) f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}.
-\end{align*}
-By applying the induction hypothesis to the $r$-fold integral, we obtain the upper bound
+		\varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s) f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}.
+\end{align*}
+The $r$-fold integral can the bounded from above using the induction hypothesis as
 \begin{align}\label{eq:indhyp}
-&=\bigO{k_n^{1+\epsilon-2\alpha}}\left(\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r .
+	\bigO{k_n^{1+\epsilon-2\alpha}}\left(\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r .
 \end{align}
@@
 \begin{align*}
-	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
+	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
-	&=\smallO{\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)}\left(\int_{\stripknc} \varphi(\{p_1\};p_1) 
-		f(x_1,y_1) \dd x_1 \dd y_1\right)^r  \\
-	&=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\};p_1)f(x_1,y_1) \dd x_1 \dd y_1\right)^{r+1}}.
-\end{align*}
-
-For the integration over $\Fcal_\epsilon(k_n)$, recall that by Lemma~\ref{lem:probdegFact}, $$\varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s)=(1+o(1))\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)\varphi(\{p_{r+1}\};p_1,\dots,p_s)+\bigO{k_n^{-C}}.$$% =(1+o(1)) \varphi(p_1,\dots,p_r)\varphi(y_{r+1}).$$
-
+	&=\smallO{\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)\mu_n(dp_1)}
+		\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r  \\
+	&=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)f(x_1,y_1) \dd x_1 \dd y_1\right)^{r+1}}.
+\end{align*}
+
+For the integration over $\Fcal_\epsilon(k_n)$, recall that by Lemma~\ref{lem:probdegFact}, \[
+	\varphi(\{p_1,\dots,p_{r+1}\}, k_n ;p_1,\dots,p_s)
+	=(1+o(1))\varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
+	\varphi(\{p_{r+1}\}, k_n ;p_1,\dots,p_s)+\bigO{k_n^{-C}}.
+\]
 This implies that
 \begin{align*}
-	&\int \int_{\Fcal_\epsilon(k_n)} \varphi(\{p_1,\dots,p_{r+1}\};p_1,\dots,p_s) 
+	&\int \int_{\Fcal_\epsilon(k_n)} \varphi(\{p_1,\dots,p_{r+1}\}, k_n ;p_1,\dots,p_s) 
 		 f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
-	&=(1+o(1))\int \int_{\Fcal_\epsilon(k_n)} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s) 
+	&=(1+o(1))\int \int_{\Fcal_\epsilon(k_n)} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s) 
 		\varphi(\{p_{r+1}\};p_1,\dots,p_s) f(x_1,y_1) \dd x_1 \dd y_1 \cdots \\
@@
 \begin{align*}
-M=(1+o(1)) \left(\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)\right)^{r+1}
+M=(1+o(1)) \left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)\mu_n(dp_1)\right)^{r+1}
 \end{align*}
@@
 \begin{align*}
-E=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)\right)^{r+1}}.
+E=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)\mu_n(dp_1)\right)^{r+1}}.
 \end{align*}
@@
 \begin{align*}
-	M &= (1+o(1))\int_{I_n}\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \varphi(\{p_{r+1}\};p_1,\dots,p_s)
+	M &= (1+o(1))\int_{I_n}\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \varphi(\{p_{r+1}\}, k_n ;p_1,\dots,p_s)
 		\frac{\alpha\nu}{\pi} e^{-\alpha y_{r+1}}dy_{r+1}dx_{r+1}\\
 	&\hspace{15pt} \times \int_{\stripknc} \cdots \int_{\stripknc} 
-		\varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}\\
-	&=(1+o(1))n\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \varphi(\{p_{r+1}\};p_1,\dots,p_s)\alpha e^{-\alpha y_{r+1}}dy_{r+1}\\
+		\varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}\\
+	&=(1+o(1))n\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \varphi(\{p_{r+1}\}, k_n ;p_1,\dots,p_s)\alpha e^{-\alpha y_{r+1}}dy_{r+1}\\
 	&\hspace{15pt} \times \int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}\\
-	&=(1+o(1))\int_{\stripknc} \varphi(\{p_{r+1}\};p_1,\dots,p_s)\mu_n(dp_1)\\
-	&\hspace{15pt} \times\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
+	&=(1+o(1))\int_{\stripknc} \varphi(\{p_{r+1}\}, k_n ;p_1,\dots,p_s)\mu_n(dp_1)\\
+	&\hspace{15pt} \times\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}.
@@
 \begin{align*}
-M&=(1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1 \right)^{r+1}.
+M&=(1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1 \right)^{r+1}.
 \end{align*}
@@
 \begin{align*}
-\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1 = \bigT{n k_n^{-(2\alpha+1)}},
+\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1 = \bigT{n k_n^{-(2\alpha+1)}},
 \end{align*}
@@
 \begin{align*}
-\left(\int_{\stripknc} \varphi(\{p_1\};p_1)f(x_1,y_1) \dd x_1 \dd y_1\right)^{r+1} 
+\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)f(x_1,y_1) \dd x_1 \dd y_1\right)^{r+1} 
 = \bigT{n^{r+1}k_n^{-r(2\alpha+1)}}.
@@
 \begin{align*}
-E = \bigO{n^{r+1}k_n^{-C}}=\smallO{n^{r+1}k_n^{-r(2\alpha+1)}}=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\};p_1)\mu_n(dp_1)\right)^{r+1}}.
+E = \bigO{n^{r+1}k_n^{-C}}=\smallO{n^{r+1}k_n^{-r(2\alpha+1)}}=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)\mu_n(dp_1)\right)^{r+1}}.
 \end{align*}
@@
 \begin{proof}[Proof of Lemma~\ref{lem:factmoment}]
+We give the proof for the Poissonized KPKVB model. The proof for the finite box model $\Gbox$ follows using similar arguments.
+
 First of all, we observe that
 \begin{align*}
-{N_{\Po}(k_n) \choose r} = \frac{1}{r!} \sum_{v_1,\dots,v_r\in V(\GPo)}^{\not = } \1_{\{D_{\GPo}(v_1)=\dots=D_{\GPo}(v_r)=k_n\}}.
+{N_{\Po}(k_n) \choose r} = \frac{1}{r!} \sum_{p_1,\dots,p_r\in V(\GPo)}^{\not = } \1_{\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}}.
 \end{align*}
@@
 &{N_{\Po}(k_n) \choose r+1} = {N_{\Po}(k_n) \choose r} \frac{N_{\Po}(k_n)-r}{r+1} \\
-&= \frac{1}{(r+1)!}\sum_{v_1,\dots,v_r\in V(\GPo)}^{\not = } \1_{\{D_{\GPo}(v_1)=\dots=D_{\GPo}(v_r)=k_n\}} (N_{\Po}(k_n)-r).
+&= \frac{1}{(r+1)!}\sum_{p_1,\dots,p_r\in V(\GPo)}^{\not = } \1_{\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}} (N_{\Po}(k_n)-r).
 \end{align*}
 Now, we can write
-$$N_{\Po}(k_n) = \sum_{\stackrel{v_{r+1} \in V(\GPo),}{v_{r+1} \not \in\{ v_1,\dots,v_r\}} } \1_{\{D_{\GPo}(v_{r+1})=k_n\}}+\sum_{v_{r+1} \in \{v_1,\dots,v_r\}}\1_{\{D_{\GPo}(v_{r+1})=k_n\}}.$$
+\[
+	N_{\Po}(k_n) = \sum_{\stackrel{p_{r+1} \in V(\GPo),}{p_{r+1} \not \in\{ p_1,\dots,p_r\}} } \1_{\{D_{\GPo}(p_{r+1})=k_n\}}+\sum_{p_{r+1} \in \{p_1,\dots,p_r\}}\1_{\{D_{\GPo}(p_{r+1})=k_n\}}.
+\]
 The first sum leads to the right-hand side of the claim for $r+1$, whereas the second sum will cancel with the $-r$.
@@
 \begin{align*}
-	&\Exp{ {N_{\Po}(k_n) \choose r}}=\frac{1}{r!} \E\left[ \sum_{v_1,\dots,v_r\in V(\GPo)}^{\not = }  
-		\1_{\{D_{\GPo}(v_1)=\dots=D_{\GPo}(v_r)=k_n\}}\right] \\
+	&\Exp{ {N_{\Po}(k_n) \choose r}}=\frac{1}{r!} \E\left[ \sum_{p_1,\dots,p_r\in V(\GPo)}^{\not = }  
+		\1_{\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}}\right] \\
 	&=\frac{1}{r!} \int_\Rcal \cdots \int_\Rcal \varphi_{\Po}(\{p_1,\dots,p_r\},p_1,\dots,p_r)
@@
 \[
-	\Exp{N_{\Po}(k_n)} = \int_\Rcal \Pee(v_1 \text{ has degree }k_n\text{ in }G(\VPo\cup \{v_1\})) \mu_n(dv_1),
+	\Exp{N_{\Po}(k_n)} = \int_\Rcal \phi_{\Po}(\{p_1\}, k_n ; p_1) f(x_1,y_1) \dd x_1 \dd y_1,
 \]
@@
 \[
-	\frac{1}{r!}(\Exp{N_{\Po}(k_n)})^r = \frac{1}{r!}\left(\int_\Rcal \Pee(v_1 \text{ has degree }k_n\text{ in }G(\VPo\cup \{v_1\})) \mu_n(dv_1)\right)^r.
+	\frac{1}{r!}(\Exp{N_{\Po}(k_n)})^r = \frac{1}{r!}\left(\int_\Rcal \phi_{\Po}(\{p_1\}, k_n; p_1) f(x_1,y_1) \dd x_1 \dd y_1,\right)^r.
 \]
@@
 	&= \frac{1}{r!} \int_\Rcal \cdots \int_\Rcal 
-		\varphi_{\Po}(\{p_1,\dots,p_r\},p_1,\dots,p_r) 
+		\varphi_{\Po}(\{p_1,\dots,p_r\}, k_n; p_1,\dots,p_r) 
 		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r} \\
-	&= (1+o(1))\frac{1}{r!}\left(\int_\Rcal \varphi_{\Po}(\{p_1\},p_1) f(x_1,y_1) \dd x_1 \dd y_1 \right)^r \\
+	&= (1+o(1))\frac{1}{r!}\left(\int_\Rcal \varphi_{\Po}(\{p_1\}, k_n;p_1) f(x_1,y_1) \dd x_1 \dd y_1 \right)^r \\
 	&= (1+o(1))\frac{1}{r!}(\Exp{N_{\Po}(k_n)})^r.
@@
 \begin{lemma}\label{lem:diff_Nk_hyperbolic_binomial_poisson}
-As $n \rightarrow \infty$, it holds that
+As $n \rightarrow \infty$, it holds that for $0 \le k_n \le n - 1$,
 \[
@@
 
-We now have all necessary ingredient to proof the main result on the degrees, Theorem~\ref{thm:degree_hyperbolic}.
-
-\begin{proof}[Proof of Theorem~\ref{thm:degrees_hyperbolic}] \hfill\\
+We now have all necessary ingredient to proof the main result on the degrees, Theorem~\ref{thm:degrees_hyperbolic}.
+
+\begin{proof}[Proof of Theorem~\ref{thm:degrees_hyperbolic}]
+
+Recall that we shall only give the proof for the case where $k_n \to \infty$, since result (i) for fixed $k = \bigO{1}$ follows from~\cite{gugelmann2012random}.
+
 \begin{enumerate}[\upshape (i)]
@@
 
-\item We will show that in this case $\E[N_n(k_n)] = o(1)$. This then implies, by Markov's inequality,
-\[
-	\Prob{N_n(k_n)>0}\leq \E[N_n(k_n)] = o(1).
-\]
-
-First we observe that as the poissonized KPKVB model $\GPo$ has the same intensity measure as the original KPKVB model with a fixed number $n$ of points, the expected degree of a vertex of the KPKVB model with radial coordinate $r=R-y$ is given by $\mu_{\Po,n}(y)$ and hence,
-\[
-	\Exp{N_n(k_n)} = n \int_0^R \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)/n) = k_n} \frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy.
+\item We will show that in this case $\Exp{N_n(k_n)} = o(1)$. This then implies, by Markov's inequality,
+\[
+	\Prob{N_n(k_n)>0}\leq \Exp{N_n(k_n)} = o(1).
+\]
+
+First we observe that as the poissonized KPKVB model $\GPo$ has the same intensity measure as the original KPKVB model with a fixed number $n$ of points, the expected degree of a vertex of the KPKVB model with radial coordinate $r=R-y$ is given by $\mu_{\Po}(y)$ and hence,
+\[
+	\Exp{N_n(k_n)} = n \int_0^R \Prob{\mathrm{Bin}(n-1,\mu_{\Po}(y)/n) = k_n} 
+	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy.
 \]
@@
 \[
-	n \int_{(1-\varepsilon)R}^R \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)/n) = k_n}
+	n \int_{(1-\varepsilon)R}^R \Prob{\mathrm{Bin}(n-1,\mu_{\Po}(y)/n) = k_n}
 	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy
@@
 \[
-	n \int_0^{(1-\varepsilon)R} \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)) = k_n}
+	n \int_0^{(1-\varepsilon)R} \Prob{\mathrm{Bin}(n-1,\mu_{\Po}(y)) = k_n}
 	\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy = \smallO{1}.
@@
 \begin{align*}
-	&\hspace{-20pt} n \int_0^{(1-\varepsilon)R} \Prob{\mathrm{Bin}(n-1,\mu_{\Po,n}(y)) = k_n}
+	&\hspace{-20pt} n \int_0^{(1-\varepsilon)R} \Prob{\mathrm{Bin}(n-1,\mu_{\Po}(y)) = k_n}
 		\frac{\alpha \sinh(\alpha (R-y))}{\cosh(\alpha R)-1} dy\\
 	&\le (1+\smallO{1}) \frac{e}{\sqrt{2\pi}} \sqrt{\frac{n}{n-k_n}}
-		n \int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po,n}(y)) = k_n} \alpha e^{-\alpha y} dy \\
+		n \int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po}(y)) = k_n} \alpha e^{-\alpha y} dy \\
 	&\le (1+\smallO{1}) \frac{e}{\sqrt{2\pi}} \sqrt{\frac{n}{n-k_n}} n p_{k_n}

### 2020-01-03 clustering_infinite_model.tex
updated section 3
updated section 4

@@
-\section{Clustering and the degree of the typical point in $\Ginf$\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
+\section{Clustering of the typical point in $\Ginf$\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
 
@@
 Since $c(G)$ is defined as an average over all vertices of the graph, it is not immediately obvious how to meaningfully define a corresponding notion for infinite graphs, and similarly for the clustering function, the degree sequence, etc.
-We can however without any issues speak of the (expected) clustering coefficient of the typical point, or the expected clustering coefficient given that it has degree $k$, or the distribution of the degree of the typical point.
+We can however without any issues speak of the (expected) clustering coefficient of the typical point or the expected clustering coefficient given that it has degree $k$.
 (All considered in the graph obtained from $\Ginf$ by adding the typical point to its vertex set.)
 
-If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we will write
+If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we write
 \[ 
@@
 \]
-Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives, using $\alpha>\frac{1}{2}$,
-\begin{align*}
-	\mu(y) &= \int_{\BallPo{p}} f(x',y') \, dx' \,d y'  
- 		= \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' \\
-	&= \int_0^\infty 2 e^{(y+y')/2} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dy' 
- 		= \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' \\
-	&= \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
-\end{align*}
+Recall that $\mu(y) = \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}$. When $p = (0,y)$ we also write $\BallPo{y} = \BallPo{p}$.
 
@@
 
-For any fixed value $y_0>0$, the set of points inside $\BallPo{(0,y_0)}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{(0,y_0)}}$.
-As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by first picking $N \isd \Po( \mu(y_0) )$ and then taking $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
-(That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{(0,y_0)}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{(0,y_0)}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{(0,y_0)}$ chosen according to the mentioned re-normalized probability density function.
+For any fixed value $y_0>0$, the set of points inside $\BallPo{y_0}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{y_0}}$.
+As $\mu(\BallPo{y_0}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by first picking $N \isd \Po( \mu(y_0) )$ and then taking $N$ i.i.d.~points in $\BallPo{y_0}$ according to the probability density $f \cdot 1_{\BallPo{y_0}} / \mu(y_0)$.
+(That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{y_0}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{y_0}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{y_0}$ chosen according to the mentioned re-normalized probability density function.
 This shows that, for every $k\geq 2$:
@@
 \]
-where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{(0,y_0)}$ with the above mentioned density.
+where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{y_0}$ with the above mentioned density.
 Note that this does not depend on the value of $k$. For notational convenience, we will write 
@@
 	g_k(y_0)  = \frac{\rho(y_0, k) \alpha e^{-\alpha y_0} }{\int_0^\infty \rho(t, k) \alpha e^{-\alpha t} \, d t}
-	= \frac{1}{p_k} \cdot \rho(y_0, k) \alpha e^{-\alpha y_0}.
-\]
-Hence, 
+	= \frac{1}{p_k} \cdot \rho(y_0, k) \alpha e^{-\alpha y_0},
+\]
+where we recall that $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$ denotes the probability that a Poisson random variable with mean $\mu(y)$ is $k$. Hence, 
 \begin{equation}\label{eq:gammakint}
@@
 Recall that $P(y_0)$ is the probability that $u_1 = (x_1,y_1), u_2 = (x_2,y_2)$ are neighbours in $\Ginf$, where
-$u_1, u_2$ are i.i.d.~with probability density $f \cdot \1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
+$u_1, u_2$ are i.i.d.~with probability density $f \cdot \1_{\BallPo{y_0}} / \mu(y_0)$.
 In particular
@@
 Thus, $y_1, y_2$ are exponentially distributed with parameter $\alpha-\frac12$.
-Now note that, for each $t>0$, the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$
+Now note that, for each $t>0$, the probability density $f \cdot 1_{\BallPo{y_0}} / \mu(y_0)$
 is constant on $[-e^{(t+y_0)/2}, e^{(t+y_0)/2}] \times \{t\}$ and it is 
@@
 Hence, given the height $y_i$ of $u_i$, the $x$-coordinate of $u_i$ is uniform in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$. 
-With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ 
+With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $y_0, (x_1,y_1), (x_2,y_2)$ 
 satisfy \\ $|x_1-x_2| \leq e^{(y_1+y_2)/2}$, where $x_1$ and $x_2$ are independent uniform random variables in the intervals
-$[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$, respectively. We have that
+$[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$, respectively. We then have that
 \begin{equation}\label{eq:delta_P}
@@
 taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$, it is still helpful
-to derive an alternative, more explicit expression.
-This is what we will do in the current section.
-We will prove
+to derive an alternative, more explicit expression. This is what we will do in the current section.
+
+Recall that $\Gamma^\ast(q,z) = \Gamma^+(q+1,z) + \Gamma^+(q,z)$. We will prove the following.
 
@@
 function.
- %\footnote{Note that the integrals in the expression for $\gamma$ for $\alpha = 1$ exists: for the first 
- %one note that $1-4z+3z^2=(1-z)(1-3z)$, so the integrand can be bounded by $C(1-z)\log(1-z)$ on $[0,1)$ for some constant $C$, which 
- %can be continued continuously to the compact interval $[0,1]$ by noting that the limit for $z \rightarrow 1$ is zero, so the 
- %integrand is bounded on a bounded domain and hence, this integral is finite; for the second integral note 
- %that $\Li_2(z)$ is bounded by $\Li_2(1)$ on $[0,1]$, which is a series with well-known finite limit, so again the integrand 
- %is bounded on a bounded domain and hence the second integral is also finite.}.
 \end{proposition}
@@
 \begin{proof}
-\TM{\RD{Warning!} this has not been properly proofread by me, or anyone else.}
 We want to compute the limit $\lim_{\alpha \rightarrow 1} P_\alpha(y_0(z_0))$. For $\alpha \neq 1$, we label the terms as follows:
@@
 
-Instead of extracting the scaling of $\gamma(k)$ from its explicit expression, it turns out to be more convenient to derive it directly. Recall that
+Instead of extracting the scaling of $\gamma(k)$ from its explicit expression, it turns out to be more convenient to derive it using $P(y)$. Recall that
 \[
@@
 
-\paragraph{Proof for \bm{$1/2 < \alpha < 3/4$}}
+\paragraph{\bm{$1/2 < \alpha < 3/4$}}
 By Lemma~\ref{lem:Paneq1} we get that
@@
 \end{align*}
+Now consider again variable $z = e^{-y/2}$ and not that $z \to 0$ as $y \to \infty$.
 Because for any $b < 1$, $B^-(1-z: a,b)$ converges to $B(a,b) < \infty$ as $z \to 0$, we get that as $y \to \infty$, the first line is asymptotically equivalent to
@@
 \]
-with $c_\alpha$ as defined in Proposition~\eqref{prop:asymp}. The proof now follows since for $1/2 < \alpha < 3/4$, the remaining three terms go to zero as $y \to \infty$.
-
-\paragraph{Proof for \bm{$\alpha = 3/4$}}
+with $c_\alpha$ as defined in Proposition~\eqref{prop:asymp}.
+The proof now follows since for $1/2 < \alpha < 3/4$, the remaining three terms go to zero as $y \to \infty$.
+For the first of these terms this is true since
+\[
+	e^{(4\alpha - 2)\frac{y}{2}}\left((1 - e^{-\frac{y}{2}})^{2\alpha} - 1\right) = \bigO{e^{(4\alpha - 2)\frac{y}{2}}e^{-\frac{y}{2}}}
+	= \bigO{e^{(4\alpha - 3) \frac{y}{2}}} = \smallO{1}
+\]
+as $y \to \infty$ and $1/2 < \alpha < 3/4$.
+
+\paragraph{\bm{$\alpha = 3/4$}}
 
@@
 
-\paragraph{Proof for \bm{$\alpha > 3/4$}}
-We first deal with the case $\alpha = 1$. Here it follows from Proposition~\ref{prop:gammaais1} that
+\paragraph{\bm{$\alpha > 3/4$}}
+We first deal with the case $\alpha = 1$. Here it follows from Lemma~\ref{lem:Pais1} that
 \begin{align*}
@@
 		\frac{1}{2}\mathrm{Li}_2(e^{-y})\right) \\
-	&= 2 + \left(\frac{e^{y/2}\log(1-e^{-y/2})}{4} + 1\right)\\
+	&= 2 + \frac{1}{4}\left(e^{y/2}\log(1-e^{-y/2}) + 1\right)\\
 	&\hspace{10pt}-\log(1-e^{-y/2}) + e^{-y/2}\left(\frac{3}{4}\log(1-e^{-y/2}) - \frac{7 + \pi^2}{8} + 	
@@
 \end{align*}
-The last two terms are $\smallO{1}$ as $y \to \infty$, while $2 = (\alpha - 1/2)/(\alpha - 3/4)$ for $\alpha = 1$.
+The last three terms are $\smallO{1}$ as $y \to \infty$, while $2 = (\alpha - 1/2)/(\alpha - 3/4)$ for $\alpha = 1$.
 
@@
 
-With the asymptotic behavior of $P(y)$ we are almost ready to prove Proposition~\ref{prop:asymp}.
-First we will prove a result that will allow us to limit the values of $y$, when performing the integration.
-For this, recall that for any $C > 0$ we defined
+With the asymptotic behavior of $P(y)$ we are ready to prove Proposition~\ref{prop:asymp}. Recall that for any $C > 0$ we defined
 \[
@@
 \] 
-Since $P(y) \le 1$ by the concentration of heights results (Proposition~\ref{prop:concentration_height_general}) we have that
-We will show that, as $k \to \infty$,
+and $\Kcal_C(k) = [y_{k,C}^-, y_{k,C}^+]$. Since $P(y) \le 1$ by the concentration of heights results (Proposition~\ref{prop:concentration_height_general}) we have that, as $k \to \infty$,
 \begin{equation}\label{eq:asymptotics_average_clustering_concentration}
@@
 
-Note that this implies that if $P(y) = h(y)(1 + \smallO{1})$, uniformly in $y$, as $y \to \infty$, then 
+Note that this implies that if $P(y) = h(y)(1 + \smallO{1})$ as $y \to \infty$, then 
 \begin{equation}\label{eq:asymptotics_average_clustering_error_term}
@@
 
-%To establish~\eqref{eq:asymptotics_average_clustering_concentration} recall that $\mu(y) = \xi e^{\frac{y}{2}}$ and consider $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$ as a function of $y$.
-Then, since $\mu^\prime(y) = \mu(y)/2$, we get that
-%\[
-%	\frac{\partial \rho(y,k)}{\partial y} = \frac{1}{2}\left(k - \mu(y)\right)\rho(y,k),
-%\]
-%which implies that $\rho(y,k)$ attains its maximum at $\mu(y) = k$.
-Moreover we see that the derivative is strictly positive when $\mu(y) < k$ and strictly negative when $\mu(y) > k$.
-Since $\mu(a^-(k)) < k$ and $\mu(a^+(k)) > k$, we conclude that $\rho(y,k)$, as a function of $y$, is strictly increasing on $[0,a^-(k)]$ and strictly decreasing on $[a^+(k),\infty)$.
-Hence, using that $P(y) \le 1$,
-%\begin{align*}
-%	&\hspace{-20pt}\int_{\R_+ \setminus [a^-(k), a^+(k)]} P(y) \rho(y,k) 
-%		\alpha e^{-\alpha y} \dd y\\
-%    &\le \int_0^{a^-(k)} \rho(y,k) \alpha e^{-\alpha y} \dd y 
-%    	+ \int_{a^+(k)}^{\infty}\rho(y,k) \alpha e^{-\alpha y}x \dd y \\
-%   	&\le \rho(a^-(k),k)\int_0^{a^-(k)} e^{-\alpha y} \, \dd y
-%   		+ \rho(a^+(k),k) \int_{a^+(k)}^{\infty} e^{-\alpha y} \, \dd y\\
-%   	&= \bigO{1}\left(\rho(a^-(k),k) + \rho(a^+(k),k)\right),
-%\end{align*}
-%as $k \to \infty$. Next we show that
-%\[
-%	\rho(a^\pm(k),k) = \bigO{k^{-(1+C^2)/2}}.
-%\]
-%Since the arguments are almost completely identical, we give the prove for $a^+(k)$.
-%
-%Using Stirling's formula $k! \sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
-%\begin{align*}
-%	\rho(a^+(k),k) &= \frac{\mu(a^+(k))^{k}}{k!} e^{-\mu(a^+(k))} \\
-%	&\sim (2\pi)^{-1/2} k^{-1/2} \left(\frac{\mu(a^+(k))}{k}\right)^{k} e^{-(\mu(a^+(k) - k)}\\
-%	&= (2\pi)^{-1/2} k^{-1/2} 
-%		e^{-k\left(\frac{\mu(a^+(k))}{k} - 1 - \log\left(\frac{\mu(a^+(k))}{k}\right)\right)}.
-%\end{align*}
-%Since, for sufficiently large $k$,
-%\[
-%	\frac{\mu(a^+(k))}{k} = 1 + C \sqrt{\frac{\log(k)}{k}}
-%\]
-%and $x - \log(1 + x) \sim x^2/2$ as $x \to 0$, we get 
-%\begin{align*}
-%	\rho(a^+(k),k) 
-%	&\sim \sqrt{2\pi} k^{-1/2} 
-%		e^{-k \left(C \sqrt{\frac{\log(k)}{k}} - \log\left(1 + C \sqrt{\frac{\log(k)}{k}}\right)\right)}\\
-%	&\sim (2\pi)^{-1/2} k^{-1/2} e^{-\frac{k \left(C \sqrt{\frac{\log(k)}{k}}\right)^2}{2}} \\
-%	&= \bigO{k^{-(1+C^2)/2}}.
-%\end{align*}
-%
-%Since $C > 0$ can be chosen arbitrarily large we conclude that
-%\[
-%	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-%	= (1+\smallO{1}) \int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y,
-%\]
-%as $k \to \infty$.
-
-We now proceed with the proof of Proposition~\ref{prop:asymp}, which is split over the different cases for $\alpha$.
-
-\paragraph{Proof when \bm{$1/2 < \alpha < 3/4$}}
+\begin{proof}[Proof of Proposition~\ref{prop:asymp}]
+We split the proof over the different cases for $\alpha$.
+
+\paragraph{\bm{$1/2 < \alpha < 3/4$}}
 By Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term}  it follows that as $k \to \infty$,
@@
 
-\paragraph{Proof when \bm{$\alpha = 3/4$}}
+\paragraph{\bm{$\alpha = 3/4$}}
 Similar to the previous case Proposition~\ref{prop:asymptotics_P} and~\eqref{eq:asymptotics_average_clustering_error_term} imply that as $k \to \infty$
@@
 \]
-However, the final step does not follow immediately from~\eqref{eq:general_clustering_integral_scaling} because of the additional logarithmic term. To prove the result we first show that
+However, the final step does not follow immediately from~\eqref{eq:general_clustering_integral_scaling} because of the additional logarithmic term. 
+%To prove the result we first show that
+%\begin{equation}\label{eq:average_clustering_proof_34_main}
+%	\int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+%	\sim \int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y.
+%\end{equation}
+To deal with this we observe the following upper and lower bound
+\begin{align*}
+	\int_{\Kcal_C(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+	&\le \frac{y_{k,C}^+}{2} \int_{\Kcal_C(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+\end{align*}
+and similarly, a lower bound
+\begin{align*}
+	\int_{\Kcal_C(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+	&\ge \frac{y_{k,C}^-}{2} \int_{\Kcal_C(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+\end{align*}
+Now observe that as $k \to \infty$,
+\[
+	\frac{y_{k,C}^\pm}{2} = \log\left(\frac{k \pm \sqrt{k\log(k)}}{\xi}\right) \sim \log(k)
+\]
+It follows that
+\[
+	\limsup_{k \to \infty} \frac{\int_{\Kcal_C(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\log(k) \int_{\Kcal_C(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \le 1.
+\]
+and
+\[
+	\liminf_{k \to \infty} \frac{\int_{\Kcal_C(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
+	{\log(k) \int_{\Kcal_C(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \ge 1,
+\]
+which imply
 \begin{equation}\label{eq:average_clustering_proof_34_main}
-	\int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	\sim \int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y.
-\end{equation}
-For this we establish an upper bound for the left hand side
-\begin{align*}
-	\int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
-	&\le \frac{a^+(k)}{2} \int_{a^-(k)}^{a^+(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
-\end{align*}
-and similarly, a lower bound
-\begin{align*}
-	\int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
-	&\ge \frac{a^-(k)}{2} \int_{a^-(k)}^{a^+(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
-\end{align*}
-Now observe that as $k \to \infty$,
-\[
-	\frac{a^\pm(k)}{2} = \log\left(\frac{k \pm \sqrt{k\log(k)}}{\xi_{\alpha, \nu}}\right) \sim \log(k)
-\]
-and therefore it follows that
-\[
-	\limsup_{k \to \infty} \frac{\int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	{\log(k) \int_{a^-(k)}^{a^+(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \le 1.
-\]
-and
-\[
-	\liminf_{k \to \infty} \frac{\int_{a^-(k)}^{a^+(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	{\log(k) \int_{a^-(k)}^{a^+(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y} \ge 1.
-\]
-This proves~\eqref{eq:average_clustering_proof_34_main}.
-
-Next we note that by~\eqref{eq:general_clustering_integral_scaling} with $\beta = 1/2$ we have
+	\int_{\Kcal_C(k)} \frac{y}{2} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y
+	\sim \log(k) \int_{\Kcal_C(k)} e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y,
+\end{equation}
+as $k \to \infty$.
+
+Since~\eqref{eq:general_clustering_integral_scaling} with $\beta = 1/2$ implies
 \[
 	\frac{\int_0^\infty e^{-y/2} \rho(y,k) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
-	\sim \xi k^{-1}.
-\]
-Therefore, since by~\eqref{eq:asymptotics_average_clustering_concentration},
-\[
-	\int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y \sim \int_{a^-(k)}^{a^+(k)} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	\sim \xi k^{-1},
 \]
@@
 
-\paragraph{Proof when \bm{$\alpha > 3/4$}}
+\paragraph{\bm{$\alpha > 3/4$}}
 
@@
 \]
-
-% %\begin{lemma}\label{lem:expectation_clustering_P}
-% %Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then
-% %\[
-% %	\Exp{c_{\Pcal}^\ast(k)} = \frac{\int_0^{\infty} P(y) \, 
-% %	\rho_{y}(k) e^{-\alpha y} \, dy}{\int_0^{\infty} \rho_{y}(k) 
-% %	e^{-\alpha y} \, dy}.
-% %\]
-% %\end{lemma}
-% %
-% %\begin{proof}
-% %By the Palm-Mecke formula, we have
-% %\begin{align*}
-% %	\Exp{c_{\Pcal}^\ast(k)} &= \frac{1}{\Exp{N_\Pcal(k)}}
-% %		\int_0^{\infty} \int_{-\infty}^{\infty} \Exp{\frac{\ind{D_{\Pcal}(p) = k}}{\binom{k}{2}} \sum_{(p_1, p_2) \in \Pcal} T(p,p_1,p_2)} f_{\alpha,\nu}(x,y) \, dx \, dy\\
-% %	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} \int_{-\infty}^{\infty} \binom{k}{2}^{-1}
-% %		P(p,k)\CProb{D_\Pcal(p) = k}{p} f_{\alpha,\nu}(x,y) \, dx \, dy.
-% %\end{align*}
-% %Conditioned on the Poisson process $\Pcal$ having $k$ points in $B(p)$, the points are independent random variables $Z_{1}, \dots, Z_{k}$ with probability  distribution $\eta_{p} = \frac{\mu|_{B(p)}}{\mu(B(p))}$.
-Therefore we have
-% %\[
-% %	P(p,k) = \binom{k}{2} T_\Pcal(p),
-% %\]
-% %and hence, since the entire expression inside the integral does not depend on $x$,
-% %\begin{align*}
-% %	\Exp{c_{\Gamma, n}^\ast(k)} 
-% %	&= \frac{1}{\Exp{N_\Pcal(k)}} \int_0^{\infty} P(y) \rho_{\mu, y}(k) e^{-\alpha y} \, dy.
-% %\end{align*}
-% %Finally, we note that
-% %\begin{align*}
-% %	\Exp{N_\Pcal(k)} &= \Exp{\sum_{p \in \Pcal} \ind{D_\Pcal(p) = k}}
-% %	= \int_0^{\infty}\int_{-\infty}^\infty \rho_{\mu, p}(k) f_{\alpha,\nu}(x,y) \, dx \, dy
-% %	= \int_0^{\infty} \rho_{\mu, y}(k) e^{-\alpha y} \, dy
-% %\end{align*}
-% %which completes the proof.
-% %\end{proof}
-% 
-% Recall that
-% \[
-% 	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) P(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
-% \]
-% The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
-% \[
-% 	\int_0^{\infty} P(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
-% \]
-% and in particular the function $P(y)$. The following result establishes the asymptotic behavior of the latter.
-% 
-% \begin{proposition}[Asymptotic behavior of $P(y)$]\label{prop:asymptotics_Delta_y_P}
-% Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}.
-Then there are three, eventually decreasing, functions $\varphi_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
-% \[
-% 	\lim_{y \to \infty} \varphi_i(y) = 0, 
-% \]
-% such that 
-% \begin{enumerate}
-% \item for $\frac{1}{2} < \alpha < \frac{3}{4}$,
-% \[
-% 	P(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varphi_1(y)),
-% \]
-% \item for $\alpha = \frac{3}{4}$,
-% \[
-% 	P(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varphi_2(y)),
-% \]
-% \item and for $\alpha > \frac{3}{4}$,
-% \[
-% 	P(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varphi_3(y)).
-% \]
-% \end{enumerate}
-% \end{proposition}
-% 
-% The proof of this proposition is involved and technical. 
-% We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} \TM{ It is not in section 4.3!!!!
-IN fact I cannot find it in sec 4 alltogether.
-Please fix.
-We do need this worked out explicitly in the paper.
-} and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.
-% 
-% 
-% \begin{proof}[Proof of Theorem \ref{thm:asymptotics_average_clustering_P}]
-% 
-% We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$.
-\TM{ not sure I am happy with this "other cases are similar" approach.
-Especially in a 100 page paper.
-The devil is in the details!
-} The proofs for the other two cases are similar.
-Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
-% \[
-% 	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y
-% \]
-% Then we have that
-% \[
-% 	\int_0^{\infty} P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-% 	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y + \epsilon_1(k).
-% \]
-% 
-% Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields,
-% \begin{equation}\label{eq:asymptotics_clustering_integral}
-% 	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y 
-% 	\sim 2\alpha \xi^{6\alpha - 2} k^{-(6\alpha - 1)},
-% \end{equation}
-% as $k \to \infty$. Therefore, by applying the asymptotic scaling for the denominator~\eqref{eq:degree_distribution_P_asymptotics} we get
-% \begin{align*}
-% 	c_\infty(k) &= \frac{\int_0^{\infty} P(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
-% 		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
-% 	&\sim C_\alpha 2\alpha \xi^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
-% 	+ \frac{\epsilon_1(k)}{2\alpha \xi^{2\alpha} k^{-(2\alpha - 1)}}\\
-% 	&= C_\alpha 2\alpha \xi^{4\alpha - 2} k^{-4\alpha + 2} 
-%     + \frac{1}{2\alpha}\xi^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
-% \end{align*}
-% Hence, to prove the result it is enough to show that
-% \[
-% 	\lim_{k \to \infty} k^{6\alpha - 3}\epsilon_1(k) = 0.
-% \]
-% For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ \TM{ should there not be a $k/\xi$ inside $\log$ here? (see below) } and split the integral into two pieces
-% \begin{align*}
-% 	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
-% 	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
-% 	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
-%     	\rho(y,k) \alpha e^{-\alpha y} \dd y.
-% \end{align*} 
-% For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ \TM{ I think that is only true if we change the def as above, in accordance with $a^{\pm}$ earlier. } and
-% \[
-% 	k^{6\alpha - 3}\rho(a(k),k) = O\left(\frac{k^{6\alpha - 3 + (1-\varphi)k}}{k!} e^{-(1-\varphi)k}\right) = o(1),
-% \]
-% \TM{ again, it seems off. I think we need to take $\xi$ into account here. }
-% to obtain
-% \begin{align*}
-% 	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
-%     	\rho(y,k) \alpha e^{-\alpha y} \dd y\\
-% 	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
-%     	\rho(a(k), k) \int_0^\infty \alpha e^{-\alpha y} \dd y = 0.
-% \end{align*}
-% For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
-% \[
-% 	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
-% \] 
-% Therefore, using that $\varphi_1(y)$ is eventually decreasing and $\lim_{k \to \infty} \varphi_1(a(k)) = 0$, we obtain
-% \begin{align*}
-% 	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
-%     	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
-% 	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
-%     	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = 0,
-% \end{align*}
-% which finishes the proof. \TM{ PLease elaborate on last line. What is used here? }
-% \end{proof}
+\end{proof}

### 2020-03-10 clustering_infinite_model.tex
Edits by Tobias

@@
-\section{Clustering of the typical point in $\Ginf$\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
-
-Similar to the proof for the degrees we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of $\GPo$ with certain quantities associated with $\Ginf$.
-Recall that a \emph{typical point} is a point $p_0 = (0,y)$, where in some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and independent of $\Pcal$.
-
-Since $c(G)$ is defined as an average over all vertices of the graph, it is not immediately obvious how to meaningfully define a corresponding notion for infinite graphs, and similarly for the clustering function, the degree sequence, etc.
-We can however without any issues speak of the (expected) clustering coefficient of the typical point or the expected clustering coefficient given that it has degree $k$.
+\section{Clustering and the degree of the typical point in $\Ginf$\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
+
+As alluded to earlier, we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of the (poissonized) KPKVB random graph 
+with certain quantities associated with $\Ginf$.
+We will be considering the Poisson process $\Pcal$ to which we add one additional point $(0,y)$ on the $y$-axis.
+In some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and
+independent of $\Pcal$.
+We refer to $(0,y)$ as ``the typical point''.
+
+To provide some intu\"{\i}tion for this definition and name, note that we can alternatively view $\Pcal$ as follows. 
+We take a constant intensity Poisson process on $\eR$ corresponding to the $x$-coordinates, and to each point
+we attach a random ``mark'', corresponding to the $y$-coordinate, where the marks are i.i.d.~exponentially distributed with parameter $\alpha$.
+
+Since $c(G)$ is defined as an average over all vertices of the graph, it is not immediately obvious how to meaningfully define 
+a corresponding notion for infinite graphs, and similarly for the clustering function, the degree sequence, etc.
+We can however without any issues speak of the (expected) clustering coefficient of the typical point, or the expected clustering
+coefficient given that it has degree k, or the distribution of the degree of the typical point.
 (All considered in the graph obtained from $\Ginf$ by adding the typical point to its vertex set.)
 
-If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we write
-\[ 
-	\mu(y) = \mu(p) := \mu(\BallPo{p}).
-\]
-Recall that $\mu(y) = \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}$. When $p = (0,y)$ we also write $\BallPo{y} = \BallPo{p}$.
-
-\subsection{The expected clustering coefficient and function of the typical point}
+If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we will write
+
+$$ \mu(y) = \mu(p) := \mu(\BallPo{p}). $$
+
+Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives
+
+$$ \begin{array}{rcl} 
+\mu(y) & = & \int_{\BallPo{p}} f(x',y') \, dx' \,d y'  
+ = \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' \\
+& = & \int_0^\infty 2 e^{(y+y')/2} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dy' 
+ = \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' \\
+& = & \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
+\end{array} $$
+
+\subsection{The degree of the typical point\label{ssec:degrees_infinite_model}}
+
+Before considering clustering we briefly investigate the distribution of the degree of 
+the typical point. 
+For $p = (x,y) \in \eR\times[0,\infty)$ we define
+\begin{equation}
+	\rho(p,k) := \Prob{\Po(\mu(y)) = k},
+\end{equation}
+
+where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. 
+We will often write $\rho(y,k)$ instead of $\rho(p,k)$.
+
+Let the random variable $D$ denote the degree of the typical point.
+Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed:
+
+$$ \pmf(k) := \Pee( D=k ) = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy. $$
+
+\noindent
+(Note that here we {\em define} $\pi(k)$ as the probability that the degree of the typical point equals $k$.)
+Using the transformation of variables $z = \xi e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
+\begin{align*}
+	\pmf(k)
+    &= \frac{1}{k!} \int_0^\infty \left(\xi e^{\frac{y}{2}}\right)^k 
+    	e^{-\xi e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy\\
+    &= \frac{\alpha \xi^{2\alpha}}{k!} \int_0^\infty 
+    	\left(\xi e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi e^{\frac{y}{2}}}
+        \, dy\\
+    &= \frac{2\alpha \xi^{2\alpha}}{k!} \int_{\xi}^{\infty} 
+    	z^{k -2\alpha-1} e^{-z} \, dz\\
+    &= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
+\end{align*}
+where we recall that $\Gamma$ denotes the gamma-function and $\Gamma^{+}$ the upper incomplete gamma-function.
+Note that, unsurprisingly, this is identical to the expression Gugelmann et al.~\cite{gugelmann2012random} gave for the limiting 
+degree distribution of $G(n;\alpha,\nu)$.
+Using Stirling's approximation to the gamma function, we find that
+
+\begin{equation}\label{eq:degree_distribution_P_asymptotics}
+	\pmf(k) \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha + 1)}
+	\quad \text{as } k \to \infty.
+\end{equation}
+
+By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
+
+\begin{equation}\label{eq:general_integral_rho_y_k}
+	\int_0^\infty e^{\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
+    \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
+\end{equation}
+
+\subsection{The expected clustering coefficient of the typical point\label{sec:42}}
 
@@
 	g_k(y_0)  = \frac{\rho(y_0, k) \alpha e^{-\alpha y_0} }{\int_0^\infty \rho(t, k) \alpha e^{-\alpha t} \, d t}
-	= \frac{1}{p_k} \cdot \rho(y_0, k) \alpha e^{-\alpha y_0},
+	= \frac{1}{\pmf(k)} \cdot \rho(y_0, k) \alpha e^{-\alpha y_0},
 \]
@@
 \gamma(k) 
-= \frac{1}{p_k} \cdot \int_0^\infty P(y_0) \rho(y_0,k) \alpha e^{-\alpha y_0} \, d y_0. 
+= \frac{1}{\pmf(k)} \cdot \int_0^\infty P(y_0) \rho(y_0,k) \alpha e^{-\alpha y_0} \, d y_0. 
 \end{equation}
@@
 	\gamma = J - I^{(1)} - I^{(2)} \quad \text{and} \quad
-	\gamma(k) = \frac{I^{(k)}}{p_k}.
+	\gamma(k) = \frac{I^{(k)}}{\pmf(k)}.
 \]
@@
 \begin{align*}
-	\gamma(k) &= \frac{I^{(k)}}{p_k} \\
+	\gamma(k) &= \frac{I^{(k)}}{\pmf(k)} \\
 	&=\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) 
@@
 \]
-The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
+The asymptotic behavior for the denominator is given by~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
 \[
@@
 \begin{proposition}[Asymptotic behavior of $P(y)$]\label{prop:asymptotics_P}
-Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $c_\alpha$ as defined in Proposition~\ref{prop:asymp} Then, as $y \to \infty$, 
+Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $c_{\alpha,\nu}$ as defined in Proposition~\ref{prop:asymp} Then, as $y \to \infty$, 
 \begin{enumerate}
@@
 \[
-	P(y) \sim e^{-\frac{y}{2}(4\alpha - 2)} c_\alpha \xi^{4\alpha - 2},
+	P(y) \sim e^{-\frac{y}{2}(4\alpha - 2)} c_{\alpha,\nu} \xi^{4\alpha - 2},
 \]
@@
 			+ \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha}
-			- \frac{B(2\alpha, 3-4\alpha)}{4(\alpha - 1)} = c_\alpha \xi^{-(4\alpha - 2)},
-\]
-with $c_\alpha$ as defined in Proposition~\eqref{prop:asymp}.
+			- \frac{B(2\alpha, 3-4\alpha)}{4(\alpha - 1)} = c_{\alpha,\nu} \xi^{-(4\alpha - 2)},
+\]
+with $c_{\alpha,\nu}$ as defined in Proposition~\eqref{prop:asymp}.
 The proof now follows since for $1/2 < \alpha < 3/4$, the remaining three terms go to zero as $y \to \infty$.
@@
 \begin{align*}
-	\gamma(k) \sim c_\alpha \xi^{-(4\alpha - 2)} \frac{\int_0^{\infty} e^{-(4\alpha - 2)y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y}
+	\gamma(k) \sim c_{\alpha,\nu} \xi^{-(4\alpha - 2)} \frac{\int_0^{\infty} e^{-(4\alpha - 2)y/2} \rho(y,k) \alpha  e^{-\alpha y} \dd y}
 		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} 
-	\sim c_\alpha k^{-4\alpha + 2}.
+	\sim c_{\alpha,\nu} k^{-4\alpha + 2}.
 \end{align*}

### 2020-03-10 hyperbolic_degrees.tex
Edits by Tobias

@@
-\section{Degrees in the KPKVK model: proof of Theorem~\ref{thm:degrees_hyperbolic}}
-
-Since the new contribution of Theorem~\ref{thm:degrees_hyperbolic} concerns the cases where the degree $k_n \to \infty$, we will assume that this holds throughout this section.
+\section{Degrees when $k\to\infty$: proof of Theorem~\ref{thm:degrees_hyperbolic}\label{sec:degrees}}
+
+Since the new contribution of Theorem~\ref{thm:degrees_hyperbolic} concerns the cases where the degree $k_n \to \infty$, we 
+will assume that this holds throughout this section.
 
@@
 
-We start by using the Campbell-Mecke formula to compare the degree distribution in $\GPo$ with that of a \emph{typical point} in $\Ginf$.
-For this we will be considering the Poisson process $\Pcal$ to which we add one additional point $(0,y)$ on the $y$-axis.
-In some computations the height $y$ will be fixed, but eventually we shall take it exponentially distributed with parameter $\alpha$, and independent of $\Pcal$.
-We refer to $(0,y)$ as ``the typical point''.
-
-To provide some intuition for this definition and name, note that we can alternatively view $\Pcal$ as follows. 
-We take a constant intensity Poisson process on $\eR$ corresponding to the $x$-coordinates, and to each point
-we attach a random ``mark'', corresponding to the $y$-coordinate, where the marks are i.i.d.~exponentially distributed with parameter $\alpha$.
-By translation invariance of Poisson point process, each point will behave as $(0,y)$ with $y$ exponentially distributed with parameter $\alpha$, the typical point of the process.
-
-We first compute the degree distribution of the typical point in $\Ginf$ and show that this equals 
-\[
-	p_k = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
-\]
-We then relate this to the Poissonized KPKVB model $\GPo$.
+We start by using the Campbell-Mecke formula to compare the degree distribution in $\GPo$ with that of the typical point in $\Ginf$. 
+As we've already seen this equals 
+\[
+	\pmf(k) = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
+\]
+We will relate this to the Poissonized KPKVB model $\GPo$. 
 More precisely, let $N_{\Po}(k)$ denote the set of degree $k$ vertices in $\GPo$. 
-We then show in Section~\ref{ssec:expected_degrees_GPo} that for any $1 \ll k_n \le n -1$ with $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$, $\Exp{N_{\Po}(k_n)} = (1+\smallO{1}) n p_{k_n}$ and more generally,
+We then show in Section~\ref{ssec:expected_degrees_GPo} that for any $1 \ll k_n \le n -1$ with 
+$k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$, $\Exp{N_{\Po}(k_n)} = (1+\smallO{1}) n \pmf(k_n)$ and more generally,
+
 \begin{equation}\label{eq:def_factorial_moments_GPo}
@@
 \end{equation}
+
+\noindent
 for any integer $r \ge 1$ in Section~\ref{ssec:factorial_moments_GPo}. 
@@
 
-We will also establish all the above mention results for the finite box model $\Gbox$, since the proofs only require small alterations and we will need these results later on when analyzing the clustering coefficient and function.
-
-\subsection{The degree of the typical point in $\Ginf$}\label{ssec:degrees_infinite_model}
-
-We start with investigating the distribution of the degree of the typical point. (Considered in the graph obtained from $\Ginf$ by adding the typical point to its vertex set.)
-
-If $p = (x,y) \in \eR\times[0,\infty)$ is a point, not necessarily part of the Poisson process, then we will write
-\[ 
-	\mu(y) = \mu(p) := \mu(\BallPo{p}).
-\]
-Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives, using $\alpha>\frac{1}{2}$,
-\begin{align*}
-	\mu(y) &= \int_0^\infty \int_{-e^{(y+y')/2}}^{e^{(y+y')/2}} \frac{\alpha \nu}{\pi} e^{-\alpha y'} \, dx' \, dy' 
-		= \frac{2\alpha \nu e^{y/2}}{\pi} \int_0^\infty e^{(\frac12-\alpha)y'} \, dy' 
-		= \frac{2\alpha \nu e^{y/2}}{\pi(\alpha-\frac12)} = \xi e^{y/2}.
-\end{align*}
-
-For $p = (x,y) \in \eR\times[0,\infty)$ we define
-\begin{equation}\label{eq:def_degree_inf_model}
-	\rho(p,k) := \Prob{\Po(\Mu{p}) = k},
-\end{equation}
-where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$. When $p = (0,y)$ we often write $\rho(y,k)$ instead of $\rho(p,k)$.
-
-Let the random variable $D$ denote the degree of the typical point.
-Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed, for $k \in \N_0$:
-\begin{equation}\label{eq:def_pk}
-	p_k :=  \Prob{D = k} = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
-\end{equation}
-
-Using the transformation of variables $z = \xi e^{\frac{y}{2}}$ (so $dy = \frac{2}{z}dz$), we compute
-\begin{align*}
-	p_k
-    &= \frac{1}{k!} \int_0^\infty \left(\xi e^{\frac{y}{2}}\right)^k 
-    	e^{-\xi e^{\frac{y}{2}}} \alpha e^{-\alpha y} \, dy
-    	= \frac{\alpha \xi^{2\alpha}}{k!} \int_0^\infty 
-    	\left(\xi e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi e^{\frac{y}{2}}}
-        \, dy\\
-    &= \frac{2\alpha \xi^{2\alpha}}{k!} \int_{\xi}^{\infty} 
-    	z^{k -2\alpha-1} e^{-z} \, dz
-    	= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
-\end{align*}
-where we recall that $\Gamma^{+}$ denotes the upper incomplete Gamma-function.
-Note that, unsurprisingly, this is identical to the expression Gugelmann et al.~\cite{gugelmann2012random} gave for the limiting degree distribution of $G(n;\alpha,\nu)$.
-Using Stirling's approximation to the gamma function, we find that
-
-\begin{equation}\label{eq:degree_distribution_P_asymptotics}
-	p_k \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha + 1)}
-	\quad \text{as } k \to \infty.
-\end{equation}
-
-By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
-\begin{equation}\label{eq:general_integral_rho_y_k}
-	\int_0^\infty e^{\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
-    \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
-\end{equation}
+We will also establish all the above mentioned results for the finite box model $\Gbox$, since the proofs only require small 
+alterations and we will need these results later on when analyzing the clustering coefficient and function.
 
@@
 
-We can now use a concentration of heights argument to show that the integration of the Poisson probabilities $\Prob{\Po(\mu_{\Po}(y)) = k_n}$ over $0 \le y \le (1-\varepsilon) R$ is asymptotically equivalent to $p_{k_n}$.
+We can now use a concentration of heights argument to show that the integration of the Poisson probabilities $\Prob{\Po(\mu_{\Po}(y)) = k_n}$ over $0 \le y \le (1-\varepsilon) R$ is asymptotically equivalent to $\pmf(k_n)$.
 And the same holds if we instead consider $\mu_{\mathrm{box}}(y)$.
@@
 Let $0 < \varepsilon < 1$. Then for all $0 \le k_n \le n - 1$, as $n \to \infty$,
+
 \begin{equation}\label{eq:degree_integral_BallHyp}
 	\int_0^{(1-\varepsilon)R} \Prob{\Po(\Mu{\BallHyp{y}} = k_n} \alpha e^{-\alpha y} \dd y
-	= (1+\smallO{1}) p_{k_n},
+	= (1+\smallO{1}) \pmf(k_n).
 \end{equation}
-where
-\begin{equation}\label{eq:def_average_degree_Gbox_phi}
-	p_{k_n} = \int_0^\infty \Pee(Po(\xi e^{\frac{y}{2}})=k_n)\alpha e^{-\alpha y}dy.
-\end{equation}
+
 Moreover, the same holds if we replace $\Mu{\BallHyp{y}}$ with $\Mu{\BallPon{y}}$ in~\eqref{eq:degree_integral_BallHyp}.
@@
 \]
-This implies the result because the last integral equals $(1+o(1))2\alpha \xi^{2\alpha} k_n^{-(2\alpha+1)} = (1+o(1))p_{k_n}$.
+This implies the result because the last integral equals $(1+o(1))2\alpha \xi^{2\alpha} k_n^{-(2\alpha+1)} = (1+o(1))\pmf(k_n)$.
 
@@
 \[
-	\Exp{N_{Po}(k_n)} =(1+o(1)) n p_{k_n} \quad \text{and} \quad \Exp{\Nbox(k_n)} =(1+o(1)) n p_{k_n}.
+	\Exp{N_{Po}(k_n)} =(1+o(1)) n \pmf(k_n) \quad \text{and} \quad \Exp{\Nbox(k_n)} =(1+o(1)) n \pmf(k_n).
 \]
@@
 \[
-	\Exp{N_{\Po}(k_n)} = \smallO{1} \quad \text{and} \quad \Exp{\Nbox(k_n)} = \smallO{1}
+	\Exp{N_{\Po}(k_n)} = \smallO{1} \quad \text{and} \quad \Exp{\Nbox(k_n)} = \smallO{1}.
 \]
@@
 	n \int_0^{(1-\varepsilon)R} \Pee(Po(\mu_{Po}(y))=k_n) \alpha e^{-\alpha y}dy
-	= (1+\smallO{1}) n p_{k_n} = \bigO{n k^{-(2\alpha + 1}} = \smallO{1}.
+	= (1+\smallO{1}) n \pmf(k_n)= \bigO{n k^{-(2\alpha + 1}} = \smallO{1}.
 \]
@@
 \begin{lemma}[Asymptotic factorization of degree probabilities]\label{lem:probdegFact}
+Let $(k_n)$ be a sequence of integers with $0\leq k_n \leq n-1$, $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$ and $k_n \rightarrow \infty$.
 Let $C, C^\prime>0$ and $r,s$ be positive integers with $r+1\leq s$.
@@
 We will now use that $\frac{(a+b)!}{a!} = (1+o(1))(a+b)^b$ for $b^2=o(a)$, applied to $a=k_n-y_{r+1}$ and $b=y_{r+1}-s$.
-To see this auxiliary fact, note that by Stirling's approximation to the factorial, it follows that
+To see this auxiliary fact, note that by Stirling's approximation to the factorial (see e.g.~\cite{Dutkay2013},~\cite{Nanjundiah1959}), it follows that
 \begin{align*}
@@
 \begin{lemma}[Factorial moments]\label{lem:factmoment}
-Recall that $N_{Po}(k)$ denotes the number of degree $k$ vertices in $\GPo$. Then, for any positive integer $r$ and $k_n \rightarrow \infty$, it holds that
+Recall that $N_{Po}(k)$ denotes the number of degree $k$ vertices in $\GPo$.
+Let $(k_n)$ be a sequence of integers with $0\leq k_n \leq n-1$, $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$ and $k_n \rightarrow \infty$.
+Then, for any positive integer $r$, it holds that
 \[
@@
 	\label{lem:asympind}
+	Let $(k_n)$ be a sequence of integers with $0\leq k_n \leq n-1$, $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$ and $k_n \rightarrow \infty$.
+
 	Let $\varphi$ be either $\varphi_{\mathrm{box}}$ or $\varphi_{\Po}$. Then we have that
@@
 \begin{align*}
-{N_{\Po}(k_n) \choose r} = \frac{1}{r!} \sum_{p_1,\dots,p_r\in V(\GPo)}^{\not = } \1_{\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}}.
+{N_{\Po}(k_n) \choose r} = \frac{1}{r!} \sum_{p_1,\dots,p_r\in V(\GPo), \atop \text{distinct}} \1_{\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}}.
 \end{align*}
@@
 &{N_{\Po}(k_n) \choose r+1} = {N_{\Po}(k_n) \choose r} \frac{N_{\Po}(k_n)-r}{r+1} \\
-&= \frac{1}{(r+1)!}\sum_{p_1,\dots,p_r\in V(\GPo)}^{\not = } \1_{\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}} (N_{\Po}(k_n)-r).
+&= \frac{1}{(r+1)!}\sum_{p_1,\dots,p_r\in V(\GPo), \atop \text{distinct}} \1_{\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}} (N_{\Po}(k_n)-r).
 \end{align*}
@@
 \begin{align*}
-	&\Exp{ {N_{\Po}(k_n) \choose r}}=\frac{1}{r!} \E\left[ \sum_{p_1,\dots,p_r\in V(\GPo)}^{\not = }  
+	&\Exp{ {N_{\Po}(k_n) \choose r}}=\frac{1}{r!} \E\left[ \sum_{p_1,\dots,p_r\in V(\GPo), \atop \text{distinct}}  
 		\1_{\{D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n\}}\right] \\
@@
 \end{align*}
-where we integrate over $r$ additional points which we can think of as being added independently and with the same distribution as the vertices of the poissonized KPKVB model $\GPo$ in the upper half-plane coordinates.
+where we integrate over $r$ additional points which we can think of as being added independently and with the same distribution as the vertices of the Poissonized KPKVB model $\GPo$ in the upper half-plane coordinates.
 
@@
 \[
-	\Exp{N_{\Po}(k_n)} = \int_\Rcal \phi_{\Po}(\{p_1\}, k_n ; p_1) f(x_1,y_1) \dd x_1 \dd y_1,
+	\Exp{N_{\Po}(k_n)} = \int_\Rcal \varphi_{\Po}(\{p_1\}, k_n ; p_1) f(x_1,y_1) \dd x_1 \dd y_1,
 \]
@@
 \end{align*}
-By Lemma~\ref{lem:degree_integral} the first part is $(1+o(1)) p_{k_n + t}$ while the second part is $O(n^{-2\alpha(1-\varepsilon)})$ and hence
-\[
-	\Prob{D_{\Po} = k_n + t} \le \bigO{1}\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right).
+By Lemma~\ref{lem:degree_integral} the first part is $(1+o(1)) \pmf(k_n + t)$ while the second part is $O(n^{-2\alpha(1-\varepsilon)})$ and hence
+\[
+	\Prob{D_{\Po} = k_n + t} \le \bigO{1}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right).
 \]
@@
 	\sum_{t = 1}^{N-n} \Prob{Z(n,t) = t}\Prob{D_{\Po} = k_n + t}
-	&\le \bigO{1} \sum_{t = 1}^{N-n} \frac{\Exp{Z(n,t)}}{t}\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)\\
-	&= \bigO{1} \sum_{t = 1}^{N-n} \frac{(N-m)(k_n + t)}{N}\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)\\
+	&\le \bigO{1} \sum_{t = 1}^{N-n} \frac{\Exp{Z(n,t)}}{t}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
+	&= \bigO{1} \sum_{t = 1}^{N-n} \frac{(N-m)(k_n + t)}{N}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
 	&= \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n} \frac{k_n}{t}
-		\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)\\
+		\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
 	&\hspace{10pt}+ \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n}
-		\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right),
+		\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right),
 \end{align*}
@@
 
-We will show that both summations are $\smallO{p_{k_n}}$.
-For the first summation we recall that $\frac{k_n (\log n)^{3/2}}{\sqrt{n}} = \smallO{1}$ for $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$, while for $\varepsilon > 0$ small enough $n^{-2\alpha(1-\varepsilon)} = \smallO{k_n^{-(2\alpha + 1)}} = \smallO{p_{k_n}}$.
-Hence, since $p_{k_n + t} \le p_{k_n}$,
+We will show that both summations are $\smallO{\pmf(k_n)}$.
+For the first summation we recall that $\frac{k_n (\log n)^{3/2}}{\sqrt{n}} = \smallO{1}$ for $k_n = \bigO{n^{\frac{1}{2\alpha + 1}}}$, while for $\varepsilon > 0$ small enough $n^{-2\alpha(1-\varepsilon)} = \smallO{k_n^{-(2\alpha + 1)}} = \smallO{\pmf(k_n)}$.
+Hence, since $\pmf(k_n + t)\le \pmf(k_n)$,
 \begin{align*}
 	\bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n} \frac{k_n}{t}
-		\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)
-	&\le \bigO{ k_n \sqrt{\frac{\log n}{n}} p_{k_n}} \sum_{t = 1}^{N - m} \frac{1}{t}\\
-	&= \bigO{\frac{k_n (\log n)^{3/2}}{\sqrt{n}}} p_{k_n} = \smallO{p_{k_n}}.
+		\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)
+	&\le \bigO{ k_n \sqrt{\frac{\log n}{n}} \pmf(k_n)} \sum_{t = 1}^{N - m} \frac{1}{t}\\
+	&= \bigO{\frac{k_n (\log n)^{3/2}}{\sqrt{n}}} \pmf(k_n) = \smallO{\pmf(k_n)}.
 \end{align*}
@@
 \[
-	\sum_{t = 1}^{N-n} p_{k_n + t} \le \sum_{t = 1}^\infty p_{k_n + t}
-	\le \bigO{k_n^{-2\alpha}} = \bigO{k_n p_{k_n}},
-\]
-together with the fact that for $\varepsilon$ small enough, $\log(n) n^{-2\alpha(1-\varepsilon)} = \smallO{k_n^{-(2\alpha + 1)}} = \smallO{p_{k_n}}$. This implies that
+	\sum_{t = 1}^{N-n} \pmf(k_n + t) \le \sum_{t = 1}^\infty \pmf(k_n + t)
+	\le \bigO{k_n^{-2\alpha}} = \bigO{k_n \pmf(k_n)},
+\]
+together with the fact that for $\varepsilon$ small enough, $\log(n) n^{-2\alpha(1-\varepsilon)} = \smallO{k_n^{-(2\alpha + 1)}} = \smallO{\pmf(k_n)}$. This implies that
 \begin{align*}
 	\bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n}
-		\left(p_{k_n + t} + n^{-2\alpha(1-\varepsilon)}\right)
-	&\le \bigO{\sqrt{\frac{\log n}{n}} k_n p_{k_n}} + \bigO{(N-n)\sqrt{\frac{\log n}{n}} n^{-2\alpha(1-\varepsilon)}}\\
-	&\le \smallO{p_{k_n}} + \bigO{(\log n) n^{-2\alpha(1-\varepsilon)}} = \smallO{p_{k_n}}.
+		\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)
+	&\le \bigO{\sqrt{\frac{\log n}{n}} k_n \pmf(k_n)} + \bigO{(N-n)\sqrt{\frac{\log n}{n}} n^{-2\alpha(1-\varepsilon)}}\\
+	&\le \smallO{\pmf(k_n)} + \bigO{(\log n) n^{-2\alpha(1-\varepsilon)}} = \smallO{\pmf(k_n)}.
 \end{align*}
@@
 
-We now have all necessary ingredient to proof the main result on the degrees, Theorem~\ref{thm:degrees_hyperbolic}.
+We now have all necessary ingredients to prove the main result on the degrees, Theorem~\ref{thm:degrees_hyperbolic}.
 
@@
 \begin{enumerate}[\upshape (i)]
-\item  First we recall that the statements regarding $p_k$ and its asymptotic behavior follow from Equation~\ref{eq:def_pk} and Equation~\ref{eq:degree_distribution_P_asymptotics}.
+\item  First we recall that the statements regarding $\pmf(k)$ and its asymptotic behavior follow from Equation~\ref{eq:def_pk} and Equation~\ref{eq:degree_distribution_P_asymptotics}.
 
@@
 \[
-\Exp{{ N_{Po}(k_n) }}=(1+o(1))n p_{k_n}.
-\]
-Using Lemma~\ref{lem:factmoment} with $r=2$ we have that $\Exp{{N_{Po}(k_n) \choose 2}} = (1+o(1))\frac{(\Exp{ N_{Po}(k_n)})^2}{2}$, which implies $\Exp{N_{Po}(k_n)^2} = 2\Exp{{N_{Po}(k_n) \choose 2}} +\Exp{N_{Po}(k_n)} = (1+o(1))(\Exp{ N_{Po}(k_n)})^2 +o((\Exp{N_{Po}(k_n)})^2)$ (because $\Exp{N_{Po}(k_n)} = (1+o(1)) np_{k_n} \rightarrow \infty$).
+\Exp{{ N_{Po}(k_n) }}=(1+o(1))n \pmf(k_n).
+\]
+Using Lemma~\ref{lem:factmoment} with $r=2$ we have that $\Exp{{N_{Po}(k_n) \choose 2}} = (1+o(1))\frac{(\Exp{ N_{Po}(k_n)})^2}{2}$, which implies $\Exp{N_{Po}(k_n)^2} = 2\Exp{{N_{Po}(k_n) \choose 2}} +\Exp{N_{Po}(k_n)} = (1+o(1))(\Exp{ N_{Po}(k_n)})^2 +o((\Exp{N_{Po}(k_n)})^2)$ (because $\Exp{N_{Po}(k_n)} = (1+o(1)) n\pmf(k_n) \rightarrow \infty$).
 Hence, by Chebychev for any $\epsilon >0$,
@@
 \[
-	\Exp{N_n(k_n)} = \Exp{N_{Po}(k_n)} \pm \Exp{ |N_n(k_n)-N_{Po}(k_n)|} = (1+o(1))\Exp{N_{Po}(k_n)} = (1+o(1))n p_{k_n}.
+	\Exp{N_n(k_n)} = \Exp{N_{Po}(k_n)} \pm \Exp{ |N_n(k_n)-N_{Po}(k_n)|} = (1+o(1))\Exp{N_{Po}(k_n)} = (1+o(1))n \pmf(k_n).
 \]
@@
 \item Let $\zeta = 2\alpha \xi^{2\alpha}c^{-(2\alpha+1)} \in \R$.
-The proof consists of showing that $\Exp{{N_{Po}(k_n) \choose r} } \rightarrow \frac{\zeta^r}{r!}$ for every positive integer $r$ and then applying \cite[Theorem 8.3.1]{alon2016probabilistic}.
+The proof consists of showing that $\Exp{{N_{Po}(k_n) \choose r} } \rightarrow \frac{\zeta^r}{r!}$ for every positive integer $r$.% and then applying \cite[Theorem 8.3.1]{alon2016probabilistic}.
 
@@
 From Lemma~\ref{lem:factmoment}, it then follows that $\Exp{{N_{Po}(k_n) \choose r}} =(1+o(1))\frac{(\Exp{ N_{Po}(k_n)})^r}{r!}\rightarrow \frac{\zeta^r}{r!}$.
-Thus, it follows from \cite[Theorem 8.3.1]{alon2016probabilistic} that $N_{Po}(k_n) \xrightarrow{d} Po(\zeta)$.
+Thus, it follows from \cite[Theorem 8.3.1]{alon2016probabilistic} that $N_{Po}(k_n) \xrightarrow{d} Po(\zeta)$ for the Poissonized version.
 
 Finally, since $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$, by Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson}, $\Exp{| N_n(k_n) - N_{Po}(k_n)|} = o(\Exp{N_{Po}(k_n)}) = o(\zeta)$, from which it follows that $\Prob{|N_n(k_n)-N_{Po}(k_n)|\geq 1} \leq \Exp{ |N_n(k_n)-N_{Po}(k_n)|} = o(\zeta)$.
-Hence, it also holds that $N_n(k_n) \xrightarrow{d} Po(\zeta)$.
+Hence, it also holds in the original KPKVB model that $N_n(k_n) \xrightarrow{d} Po(\zeta)$.
 
@@
 		n \int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po}(y)) = k_n} \alpha e^{-\alpha y} dy \\
-	&\le (1+\smallO{1}) \frac{e}{\sqrt{2\pi}} \sqrt{\frac{n}{n-k_n}} n p_{k_n}
+	&\le (1+\smallO{1}) \frac{e}{\sqrt{2\pi}} \sqrt{\frac{n}{n-k_n}} n \pmf(k_n)
 	= \bigO{\sqrt{\frac{n}{n-k_n}} n k_n^{-(2\alpha + 1)}}.

### 2020-03-10 introduction.tex
Edits by Tobias

--- 2019-05-28 introduction.tex
@@
 \includegraphics[scale=0.3]{figures/KPKVB.png}
-\caption{Simulation $G(n;\alpha, \nu)$ with $\alpha = 0.9$, $\nu = 0.2$ and $n = 5000$.
-%\PvdH{@Tobias: this figure (HyperRGG\_N5000L5.eps) is taken from the figures you send me. Could you fill in the value of $\alpha$ and $\nu$ you used for the simulation.}
-}
+\caption{Simulation $G(n;\alpha, \nu)$ with $\alpha = 0.9$, $\nu = 0.2$ and $n = 5000$.}
 \label{fig:H_graph_example}
@@
 
-As observed by Krioukov et al.~\cite{krioukov2010hyperbolic}, and proved rigorously by Gugelmann et al.~\cite{gugelmann2012random}, the degree sequence of the KPKVB model follows a power-law with exponent $2\alpha+1$.
-% More specifically, if $N_k$ denotes the number of vertices of degree exactly $k$ then Gugelmann et al.~\cite{gugelmann2012random} have shown that
-% 
-% \begin{equation}\label{eq:gugeldegseq} 
-% N_k = (1+o(1)) \cdot n \cdot p_k \quad \text{ a.a.s., }
-% \end{equation}
-% 
-% \noindent
-% where $p_k := 2\alpha \cdot \xi^{2\alpha} \cdot \Gamma^+\left(k - 2\alpha, \xi\right) / k!$
-% with, here and in the rest of the paper, $\xi := \frac{4\alpha\nu}{\pi(2\alpha-1)}$ and 
-% $\Gamma^+(a,b) := \int_b^\infty t^{a-1} e^{-t} \text{d}t$ the 
-% {\em upper incomplete gamma function} and, for $(E_n)_n$ a sequence of events, 
-% $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Pee(E_n)\to 1$.
-%%In particular $X_n = (1+o(1)) Y_n$ is equivalent to $X_n/Y_n \plim 1$.
-%In fact~\eqref{eq:gugeldegseq} was shown in~\cite{gugelmann2012random} to hold not only when $k$ is constant but 
-%also if $k$ depends on $n$ as long as $k = o( n^\delta )$ for a suitable small constant $\delta = \delta( \alpha )$.
-%Standard asymptotic manipulations show that 
-%
-%$$p_k \sim 2\alpha\xi^{2\alpha} k^{-(2\alpha+1)}, $$
-%
-%as $k\to\infty$.
-%\TM{ \RD{We need to add something like the following} : 
-%In Appendix~\ref{} we settle the minor technical point of showing that~\eqref{eq:gugeldegseq} in fact extends 
-%to all $k$ with $k \ll n^{1/(2\alpha+1)}$, while 
-%$N_k = 0$ a.a.s.~whenever $k \gg n^{1/(2\alpha+1)}$. }
-Gugelmann et al.~\cite{gugelmann2012random} also showed that the average degree converges in probability to the constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing in the sense that it is bounded below by a positive constant a.a.s.
-Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means that $\Prob{E_n} \to 1$ as $n \to \infty$.
-Here the events $E_n$ might be defined in different probability spaces, in which case $\Pee$ will the corresponding probability measure.
-%Their work however left open the question of whether the clustering coefficient actually converges in probability.
+As observed by Krioukov et al.~\cite{krioukov2010hyperbolic}, and proved rigorously by Gugelmann et al.~\cite{gugelmann2012random}, the 
+degree sequence of the KPKVB model follows a power-law with exponent $2\alpha+1$.
+Gugelmann et al.~\cite{gugelmann2012random} also showed that the average degree converges in probability to the 
+constant $8\nu\alpha^2/ \pi (2\alpha-1)^2$, and they showed that the (local) clustering coefficient is non-vanishing 
+in the sense that it is bounded below by a positive constant a.a.s. 
+Here, and in the rest of the paper, for a sequence $(E_n)_n$ of events, $E_n$ {\em asymptotically almost surely} (a.a.s.) means 
+that $\Prob{E_n} \to 1$ as $n \to \infty$.
 
-Apart from the degree sequence and clustering, the third main characteristic associated with complex networks, ``short distances'', has also been established in the literature.
-In~\cite{abdullah2017typical} it is shown that for $\alpha < 1$ the largest component is what is called an \emph{ultra-small world}: if we randomly sample two vertices of the graph then, a.a.s., conditional on them being in the same component, their graph distance is of order $\log\log n$.
-In~\cite{kiwi2015bound} and~\cite{friedrich2018diameter} a.a.s.~polylogarithmic upper and lower bounds on the graph diameter of the largest component are shown, and in~\cite{muller2017diameter}, these were sharpened to show that $\log n$ is the correct order of the diameter.
+Apart from the degree sequence and clustering, the third main characteristic associated with complex networks, ``short distances'', has 
+also been established in the literature. In~\cite{abdullah2017typical} it is shown that for $\alpha < 1$ the largest component 
+is what is called an \emph{ultra-small world}: if we randomly sample two vertices of the graph then, a.a.s., conditional on them 
+being in the same component, their graph distance is of order $\log\log n$. 
+In~\cite{kiwi2015bound} and~\cite{friedrich2018diameter} a.a.s.~polylogarithmic upper and lower bounds on the graph diameter of 
+the largest component are shown, and in~\cite{muller2017diameter}, these were sharpened to show that $\log n$ is the correct order of 
+the diameter.
 
@@
 
-For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in probability to $X$, as $n \to \infty$.
+For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in 
+probability to $X$, and we write $X_n \xrightarrow[n\to\infty]{L_1} X$ if $X_n$ converges to $X$ in the $L_1$ sense 
+(i.e.~if $\Ee |X_n-X| \to 0$.)
 
@@
 
-Our first result is the following.
+Our first main result shows the convergence of the local clustering coefficient in the KPKVB model and 
+establishes the limit exactly.
 
@@
 In the above expression for $\gamma$, a factor $\alpha-1$ occurs in the denominator of each term, but we will see that this
-corresponds to a removable singularity.
-We have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
+corresponds to a removable singularity. We have not been able to find a closed form expression in terms of standard functions in the case 
+when $\alpha=1$, but in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
 
@@
 
-Our second result is on the clustering function for constant $k$.
+Our second main result is on the clustering function for constant $k$.
 
@@
 and for $\alpha = 1$ as the $\alpha\to1$ limit of the above expression.
-% \begin{align*}
-% 	c_\infty(k) &= \frac{9 \eta^3}{2 k!} 	
-% 		\Gamma^+(k-3,\eta)-\frac{\xi^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
-% 	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
-% 	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
-% \end{align*}
-% with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function.
 \end{theorem}
@@
 %
-\begin{figure}[h!]
+\begin{figure}[H]
     \centering
@@
 Again, we remark that the above expression for $\gamma(k)$ appears to have a singularity at $\alpha=1$, but this will turn out to be a removable singularity. 
-Again, we have not been able to find a closed form expression in terms of known functions in the case when $\alpha=1$, but in Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
+Again, we have not been able to find a closed form expression in terms of standard functions in the case when $\alpha=1$, but in 
+Section~\ref{ssec:alphais1} we do provide an explicit expression involving integrals.
 
@@
 satisfying $1 \ll k_n \ll n^{1/(2\alpha+1)}$. Then, writing $G_n := G(n;\alpha,\nu)$, we have
-\[
-	\E[|c(k_n;G_n)-\gamma(k_n)|] = \smallO{\gamma(k_n)},
-\]
-as $n \to \infty$, where $\gamma(\cdot)$ is as in Theorem~\ref{thm:mainkfixed}. In particular
-\[
-	\lim_{n \to \infty} \Exp{\left|\frac{c(k_n; G_n)}{\gamma(k_n)}- 1 \right|} = 0.
-\]
+
+$$ \frac{c(k_n;G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{L_1} 1. $$
+
 \end{theorem}
+
+\noindent
+The conclusion of Theorem~\ref{thm:mainktoinfty} is slightly stronger than $c(k_n; G_n)/\gamma(k_n) 
+\xrightarrow[n\to\infty]{\Pee} 1$, which might alternatively be written as $c(k_n;G_n) = (1+o(1)) \gamma(k_n)$ a.a.s., using notation that is common in the random graphs community.
 
@@
 
-To clarify the scaling behaviour of $\gamma(k)$ with $k$ we offer the following result.
+To clarify the scaling behaviour of $\gamma(k)$ we offer the following result.
 
@@
 $$ \gamma(k) = 
-(1+o(1)) \cdot \left\{ \begin{array}{cl}
-\frac{8\alpha \nu}{\pi\left(4\alpha - 3\right)} \cdot k^{-1} &\text{ if } \alpha > \frac{3}{4}, \\
-\frac{6 \nu}{\pi} \cdot \frac{\log(k)}{k}& \text{ if } \alpha = \frac{3}{4},\\
- c_{\alpha} \cdot k^{2-4\alpha} & \text{ if } \frac12 < \alpha < \frac34, 
+\left\{ \begin{array}{ll}
+(c_{\alpha,\nu}+o(1)) \cdot k^{-1} &\text{ if } \alpha > \frac{3}{4}, \\
+(c_{\alpha,\nu}+o(1)) \cdot \frac{\log(k)}{k}& \text{ if } \alpha = \frac{3}{4},\\
+(c_{\alpha,\nu}+o(1)) \cdot k^{2-4\alpha} & \text{ if } \frac12 < \alpha < \frac34, 
 \end{array} \right.,
 $$
-where $c_{\alpha} := \left( \frac{3\alpha - 1}{2^{4\alpha+1}\alpha(\alpha-1)^2} 
+where
+
+$$ c_{\alpha,\nu} := 
+\left\{ \begin{array}{cl}
+8\alpha \nu / (\pi\left(4\alpha - 3\right)) & \text{ if } \alpha > \frac{3}{4}, \\
+6 \nu / \pi & \text{ if } \alpha = \frac{3}{4},\\
+ \left( \frac{3\alpha - 1}{2^{4\alpha+1}\alpha(\alpha-1)^2} 
 	+ \frac{(\alpha - \frac{1}{2})B^-(\frac{1}{2},2\alpha + 1, 2\alpha - 2)}{2(\alpha - 1)\alpha} 
-	- \frac{B(2\alpha, 3\alpha - 4)}{4(\alpha - 1)} \right)  \cdot \xi^{4\alpha-2}$.
+	- \frac{B(2\alpha, 3\alpha - 4)}{4(\alpha - 1)} \right)  \cdot \xi^{4\alpha-2} 
+	& \text{ if } \frac12 < \alpha < \frac34.
+\end{array} \right. $$
 \end{proposition}
 
-Note that Theorem~\ref{thm:mainktoinfty} implies that the clustering function of the KPKVB model scales as $\gamma(k)$ as $k$ grows, whose scaling is given in the above result.
-In particular, this contradicts the scaling conjectured in~\cite{krioukov2010hyperbolic} for $\alpha \leq \frac{3}{4}$, and confirms it only for $\alpha > \frac{3}{4}$.
+Theorem~\ref{thm:mainktoinfty} states that the clustering function of the KPKVB model scales as $\gamma(k)$ as the number of vertices $n\to\infty$, and
+Proposition~\ref{prop:asymp} makes clear how $\gamma(k)$ behaves as $k$ grows.
+In particular, these results contradict the scaling conjectured in~\cite{krioukov2010hyperbolic} for 
+$\alpha \leq \frac{3}{4}$, and confirms it only for $\alpha > \frac{3}{4}$.
 
@@
 
-\subsection{Observations}
+\subsection{Additional observations and results}
 
-There are a few other observation to be made regarding our results.
+There are a few additional remarks we would like to make regarding our results.
 
-\paragraph{Uniform convergence.}
+\subsubsection{The degree distribution and the range of $k_n$ in Theorem~\ref{thm:mainktoinfty}}
 
-Our results for the local clustering function in particular imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. To see this let
+The reader may already have observed that, with a power law exponent of $2\alpha+1$ for the probability mass function of 
+the degree sequence, we would expect $\Theta( n \cdot k^{-(1+2\alpha)} ) = o(1)$ vertices of degree {\em exactly} $k$ whenever
+$k \gg n^{1/(1+2\alpha)}$.
+
+This is the reason why in Theorem~\ref{thm:mainktoinfty} we restrict ourselves to 
+sequences $k_n$ with $k_n \ll n^{1/(1+2\alpha)}$. 
+When  $k_n \gg n^{1/(1+2\alpha)}$ there are no vertices of degree exactly $k_n$ a.a.s., which in particular
+implies that the clustering function equals zero a.a.s.~for any such sequence $k_n$.
+%When $k_n$ is of the same order as $n^{1/(1+2\alpha)}$ then the probability that there are no vertices of degree exactly $k_n$
+%stays bounded away from zero.
+
+As mentioned previously, Gugelmann et al.~\cite{gugelmann2012random} gave a mathematically rigorous result on the degree sequence, which can of course be rephrased as a result on the number of nodes with degree exactly $k$.
+Their results allow $k = k_n$ to grow with $n$, but unfortunately require that $k_n \leq n^\delta$ with 
+$\delta < \min\left\{\frac{2\alpha-1}{4\alpha(2\alpha +1)}, \frac{2(2\alpha -1)}{5(2\alpha + 1)}\right\} < \frac{1}{2\alpha + 1}$.
+For completeness we offer the following result, which extends that of Gugelmann et al.~to the full range $1 \le k_n \le n-1$.
+
+\begin{theorem}\label{thm:degrees_hyperbolic}
+Let $\alpha >\frac{1}{2}, \nu > 0$, denote by $N_n(k)$ the number of vertices with degree $k$ in the KPKVB model $G(n;\alpha,\nu)$ and 
+consider a sequence of integers $(k_n)_n$ with $0 \leq k_n \leq n-1$.
+\begin{enumerate}
+\item If $k_n \ll n^{\frac{1}{2\alpha+1}} $ as $n\rightarrow \infty$, then a.a.s.
+
+$$N_n(k_n) = (1+o(1)) \cdot n \cdot \pmf(k_n),$$
+
+where $\pmf(k_n) = 2\alpha \xi^{2\alpha}\Gamma^+(k_n-2\alpha,\xi)/k_n!$.
+
+\item If $k_n = (1+o(1))c n^{\frac{1}{2\alpha+1}}$ for some fixed $c >0$, then
+
+$$ N_n(k_n) \xrightarrow[n\rightarrow\infty]{d} \operatorname{Po}(2\alpha \xi^{2\alpha} c^{-(2\alpha+1)}). $$
+
+\item If $k_n \gg n^{\frac{1}{2\alpha+1}}$, then a.a.s. $N_n(k_n) = 0$.
+\end{enumerate}
+\end{theorem}
+
+\subsubsection{Transition in scaling at $\alpha = 3/4$.}
+
+Proposition~\ref{prop:asymp} demonstrates that there is a transition in the scaling of the local clustering 
+function at $\alpha = 3/4$. 
+This corresponds to an exponent $5/2$ for the probability mass function of the degree distribution. 
+This transition is different from those often observed for networks with scale-free degree distributions, where transitions occur at
+integer values of the exponent. 
+At this point, it is unclear what the underlying reason is for the appearance of the transition at this particular half integer 
+exponent. 
+Interestingly, a similar transition point has also been observed for both majority vote models~\cite{chen2015critical} and 
+flocking dynamics~\cite{miguel2018effects} on networks with scale-free degree degree distributions.
+
+\subsubsection{Uniform convergence.}
+
+Our results for the local clustering function in fact imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ 
+where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. 
+To see this we first observe that for {\em fixed} $k$, the statement $c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k)$
+is equivalent to $c(k;G_n)/\gamma(k) \xrightarrow[n\to\infty]{L_1} 1$.
+Now let
 \[
@@
 \]
-Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainktoinfty}
+Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainkfixed} and Theorem~\ref{thm:mainktoinfty}
 \[
@@
 
-\paragraph{Near maximum scaling for $k_n$.}
-Our results for the clustering function in the KPKVB model are valid for any sequence of non-negative integers $k_n \to \infty$ such that $k_n \ll n^{\frac{1}{2\alpha + 1}}$.
-Although one would like to have results for any sequence $k_n \le n-1$, it turns out that $n^{1/(2\alpha + 1)}$ is the near maximum scaling for which Theorem~\ref{thm:clustering_coefficient_hyperbolic} can be true.
-To see why this is the case note that by definition of the local clustering function~\eqref{eq:def_clustering_function} we have that $c(k_n; G_n) = 0$ if $N_{n}(k_n) = 0$, where $N_n(k_n)$ denotes the number of vertices in a KPKVB graph $G(n; \alpha, \nu)$ with degree $k_n$.
-It follows by Markov's inequality that for any positive function $f : \R_+ \to \R_+$
-\begin{align*}
-	\Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|} 
-	&\ge \Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|\ind{N_n(k_n) = 0}}\\ 
-	&\ge \Prob{N_{n}(k_n) = 0} \ge 1 - \Exp{N_n(k_n)}.
-\end{align*}
-We shall later establish (see Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson}) that $\Exp{N_n(k_n)}$ scales as $n k_n^{-(2\alpha + 1)}$.
-Therefore if $k_n$ is such that $k_n^{-(2\alpha + 1)} n$ tends to zero as $n \to \infty$ we have that
-\[
-	\lim_{n \to \infty} \Exp{N_{n}(k_n)} = 0
-\]
-and hence
-\[
-	\lim_{n \to \infty} \Exp{\left|\frac{c(k_n; G_n)}{f(k_n)} - 1\right|} 
-	\ge 1 - \lim_{n \to \infty} \Exp{N_{n}(k_n)} = 1 \ne 0,
-\]
-for any positive function $f$. This implies that we cannot expect a result like that of Theorem~\ref{thm:mainktoinfty} to hold as soon as $k_n \gg n^{\frac{1}{2\alpha + 1}}$.
-
-\paragraph{Transition in scaling at $\bm{\alpha = 3/4}$.}
-
-It follows from Proposition~\ref{prop:asymp} that there is a transition in the scaling of the local clustering function at $\alpha = 3/4$.
-This corresponds to an exponent $5/2$ for the probability mass function of the degree distribution.
-This transition is different from those often observed for networks with scale-free degree distributions, where transitions occur at integer values of the exponent.
-At this point, it is unclear what the underlying reason is for the appearance of the transition at this half exponent.
-Interestingly, a similar transition point has also been observed for both majority vote models~\cite{chen2015critical} and flocking dynamics~\cite{miguel2018effects} on networks with scale-free degree degree distributions.
-
 \subsection{Outline of the paper}
 
-In the next section we will recall some useful tools from the literature and define a series of auxiliary random graph models that will be used in the proofs.
-In particular, we relate in a series of steps the KPKVB model to an infinite percolation model $\Ginf$ that was used in previous work of the first and third authors~\cite{fountoulakis2018law} on the largest component of the KPKVB model.
-The value of the limiting constant $\gamma$, respectively limiting clustering function $\gamma(k)$, correspond to the probability that two randomly chosen neighbours of a ``typical point'' in this infinite model are themselves neighbours, respectively the probability of this event conditional on the typical point having exactly $k$ neighbours.
-These probabilities can be expressed as certain integrals, which we solve explicitly in Section~\ref{sec:Ginf}.
+In the next section we will recall some useful tools from the literature and define a series of auxiliary random graph models 
+that will be used in the proofs. In particular, we relate in a series of steps the KPKVB model to an infinite percolation model 
+$\Ginf$ that was used in previous work of the first and third authors~\cite{fountoulakis2018law} on the largest component 
+of the KPKVB model. 
+The value of the limiting constant $\gamma$, respectively limiting clustering function $\gamma(k)$, correspond to the probability 
+that two randomly chosen neighbours of a ``typical point'' in this infinite model are themselves neighbours, respectively the 
+probability of this event conditional on the typical point having exactly $k$ neighbours. These probabilities can be expressed as 
+certain integrals, which we solve explicitly in Section~\ref{sec:Ginf}. 
 In the same section we also prove Proposition~\ref{prop:asymp}, on the asymptotics of $\gamma(k)$. 
-We then proceed to prove Theorems~\ref{thm:maincc} and~\ref{thm:mainkfixed} by relating said probabilities for the typical point of the infinite model to the corresponding clustering coefficient/function in the original KPKVB random graph, using the Campbell-Mecke formula and some other, relatively straightforward considerations.
+We then proceed to prove Theorems~\ref{thm:maincc} and~\ref{thm:mainkfixed} by relating said probabilities for the typical point 
+of the infinite model to the corresponding clustering coefficient/function in the original KPKVB random graph, using the Campbell-Mecke 
+formula and some other, relatively straightforward considerations.
 
-The remaining sections are devoted to the proof of Theorem~\ref{thm:mainktoinfty}, which turns out to be a lot more involved.
-The main reason for this is that we push the possible scaling of $k_n$ to its maximum and hence a great deal of work is needed to properly control the arising error terms and make sure these are of smaller order than $\gamma(k_n)$.
+In Section~\ref{sec:degrees} we prove Theorem~\ref{thm:degrees_hyperbolic}, which also doubles as a warm-up for the proof 
+of Theorem~\ref{thm:mainktoinfty} of the clustering function for growing $k$.
+The remaining sections are devoted to the proof of Theorem~\ref{thm:mainktoinfty}, which turns out to be technically involved.
+The main reason for this is that when we push $k_n$ close to the maximum possible value, a great deal of work is needed 
+to properly control the arising error terms.
 
-Finally, the Appendix includes some technical results on Meijer's G-function, Chernoff bounds for Poisson and Binomial random variables and the code used for simulations.
+The Appendix includes some auxiliary results on Meijer's G-function, Chernoff bounds for Poisson and Binomial 
+random variables and the code used for simulations.

### 2020-03-10 paper.tex
Edits by Tobias

@@
 \usepackage{tocloft}
-
 \usepackage{enumerate}
@@
 \newcommand{\BallSym}[1]{\Bcal_{\Po \bigtriangleup \infty}\left(#1\right)}	%	Symmetric difference between balls in the 
+\newcommand{\BallH}[1]{\Bcal_{H}\left(#1\right)}	 % Ball up to height H.
 %	hyperbolic and infinite limit model
@@
 \newcommand{\eR}[0]{\ensuremath{{\mathbb R}}}
+\newcommand{\pmf}[0]{\ensuremath{{\pi}}}
 \newcommand{\eN}[0]{\ensuremath{{\mathbb N}}}
@@
 \newcommand{\Gbox}[0]{\ensuremath{G_{\mathrm{box}}}}
-\newcommand{\GPoH}{\ensuremath{G_{Po,H}}}
-\newcommand{\GboxH}{\ensuremath{G_{box,H}}}
+%\newcommand{\GboxH}[0]{\ensuremath{G_{\mathrm{box},\leq R/4}}}
+\newcommand{\GboxH}[0]{\ensuremath{G_{\mathrm{box}-}}}
+%\newcommand{\GboxH}[0]{\ensuremath{G_{-}}}
 \newcommand{\Ginf}[0]{\ensuremath{G_{\infty}}}
@@
 \newcommand{\Qcal}{\ensuremath{{\mathcal Q}}}
-\newenvironment{proofof}[1]{\vspace{1ex}\noindent{\bf Proof of #1:}}{\hspace*{\fill}$\blacksquare$\vspace{1ex}}
+\newenvironment{proofof}[1]{\vspace{1ex}\noindent{\bf Proof of #1.}}{\hspace*{\fill}$\blacksquare$\vspace{1ex}}
+\renewenvironment{proof}{\vspace{1ex}\noindent{\bf Proof.}}{\hspace*{\fill}$\blacksquare$\vspace{1ex}}
+\DeclareMathOperator{\Var}{Var}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this paper we consider the clustering coefficient, and clustering function in a random graph model proposed by Krioukov et al.~in 2010. 
-In this model, nodes are chosen randomly inside a disk in the hyperbolic plane and two nodes are connected if they are at most a certain hyperbolic distance from each other.
-It has been previously shown that this model has various properties associated with complex networks, including a power-law degree distribution, ``short distances'' and a non-vanishing clustering coefficient.
-The model is specified using three parameters: the number of nodes $n$, which we think of as going to infinity, and $\alpha, \nu > 0$, which we think of as constant.
-Roughly speaking, the parameter $\alpha$ controls the power law exponent of the degree sequence and $\nu$ the average degree.
+In this model, nodes are chosen randomly inside a disk in the hyperbolic plane and two nodes are connected if they are at most a certain 
+hyperbolic distance from each other. It has been previously shown that this model has various properties associated with complex networks, 
+including a power-law degree distribution, ``short distances'' and a non-vanishing clustering coefficient. 
+The model is specified using three parameters: the number of nodes $n$, which we think of as going to infinity, and $\alpha, \nu > 0$, 
+which we think of as constant. Roughly speaking, the parameter $\alpha$ controls the power law exponent of the degree sequence 
+and $\nu$ the average degree.
 
-Here we show that the clustering coefficient tends in probability to a constant $\gamma$ that we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
-This improves earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero with high probability, but left open the issue of convergence to a limiting constant.
-Similarly, we are able to show that $c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit $\gamma(k)$ which we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions.
+Here we show that the clustering coefficient tends in probability to a constant $\gamma$ that we give explicitly as a closed form 
+expression in terms of $\alpha, \nu$ and certain special functions. 
+This improves earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero 
+with high probability, but left open the issue of convergence to a limiting constant. Similarly, we are able to show that 
+$c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit 
+$\gamma(k)$ which we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. 
 We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$. 
 Our results show that $\gamma(k)$ scales differently, as $k$ grows, for different ranges of $\alpha$. 
-More precisely, there exists constants $Q_{\alpha,\nu}$ depending on $\alpha$ and $\nu$, such that as $k \to \infty$, $\gamma(k) \sim Q_{\alpha,\nu} k^{2 - 4\alpha}$ if $\frac{1}{2} < \alpha < \frac{3}{4}$, $\gamma(k) \sim Q_{\alpha,\nu} \log(k) k^{-1} $ if $\alpha=\frac{3}{4}$ and $\gamma = Q_{\alpha,\nu} k^{-1}$ when $\alpha > \frac{3}{4}$.
-These results contradict a prediction of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale with $k^{-1}$ as we let $k$ grow.
+More precisely, there exists constants $c_{\alpha,\nu}$ depending on $\alpha$ and $\nu$, such that as $k \to \infty$, 
+$\gamma(k) \sim c_{\alpha,\nu} \cdot k^{2 - 4\alpha}$ if $\frac{1}{2} < \alpha < \frac{3}{4}$, 
+$\gamma(k) \sim c_{\alpha,\nu} \cdot \log(k) \cdot k^{-1} $ 
+if $\alpha=\frac{3}{4}$ and $\gamma(k) \sim c_{\alpha,\nu} \cdot k^{-1}$ when $\alpha > \frac{3}{4}$. 
+These results contradict a conjecture of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale 
+with $k^{-1}$ as we let $k$ grow. 
 \end{abstract}
@@
 
-\input{hyperbolic_degrees}
-
 \input{clustering_infinite_model}
@@
 \input{proofs_finite_k}
+
+\input{hyperbolic_degrees}
 
@@
 
-\TM{ Maybe a ``conclusion and further work'' section here,  before the references and appendix? \\
-Also, appendix usually comes after references in my experience.}
-
-\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model and his helpful insights during discussions of the topic.
+\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model 
+and his helpful insights during discussions of the topic.
 

### 2020-03-10 preliminaries.tex
Edits by Tobias

@@
 
-For the definition of the finite graph, recall that in the definition of the KPKVB model we set $R = 2\log(n/\nu)$.
+Recall that in the definition of the KPKVB model we set $R = 2\log(n/\nu)$.
 We consider the box $\Rcal = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2}e^{R/2}] \times (0, R]$ in $\eR^2$. 
-Then the \emph{finite box model} $\Gbox := \Gbox(n;\alpha, \nu)$ has vertex set $\Vbox := \mathcal{P} \cap \Rcal$ and edge set such that
+Then the \emph{finite box model} $\Gbox = \Gbox(n;\alpha, \nu)$ has vertex set $\Vbox := \mathcal{P} \cap \Rcal$ and edge set such that
 \[
-	pp' \in E(\Gbox(n;\alpha, \nu)) \iff |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}},
+	pp' \in E(\Gbox) \iff |x - x'|_{\pi e^{R/2}} \leq e^{\frac{y + y'}{2}},
 \]
@@
 
-\begin{remark}[Notion convention for points]
-We will often be working with the finite box graph $\GPo$ or the infinite graph $\Ginf$, whose nodes are points in $\R \times \R_+$.
-For any point $p \in \R \times \R_+$ we will always use $p = (x,y)$.
-When considering different points $p,p^\prime \in \R \times \R_+$, we will use primed coordinates to refer to $p^\prime$, i.e.
-$p^\prime = (x^\prime ,y^\prime)$, and similar with subscripts, i.e.
-$p_i = (x_i,y_i)$.
+\begin{remark}[Notational convention for points]
+We will often be working with the finite box graph $\GPo$ or the infinite graph $\Ginf$, whose nodes are points 
+in $\R \times \R_+$. For any point $p \in \R \times \R_+$ we will always use $p = (x,y)$. 
+When considering different points $p,p^\prime \in \R \times \R_+$, we will use primed coordinates to refer 
+to $p^\prime$, i.e. $p^\prime = (x^\prime ,y^\prime)$, and similar with subscripts, i.e. $p_i = (x_i,y_i)$.
 \end{remark}
@@
 
-A very useful tool for analyzing subgraph counts, and their generalizations, in the 
-setting of the Poissonized random geometric graphs, and in particular the Poissonized KPKVB model and the box model is the \emph{Campbell-Mecke formula}.
-We use a specific incarnation, which follows from the Palm theory of Poisson point processes on metric spaces, see~\cite{last2017lectures}.
-For this consider a Poisson point process $\Pcal$ on some metric space $\mathcal{M}$ with density $\mu$ and let $\mathcal{N}$ denote the set of all possible point configurations in $\mathcal{M}$, equipped with the sigma algebra of the process $\Pcal$.
+A useful tool for analyzing subgraph counts, and their generalizations, in the 
+setting of Poissonized random geometric graphs, and in particular the Poissonized KPKVB model and the box 
+model is the \emph{Campbell-Mecke formula}. 
+We use a specific incarnation, which follows from the Palm theory of Poisson point processes on metric 
+spaces, see~\cite{last2017lectures}. For this consider a Poisson point process $\Pcal$ on some metric 
+space $\mathcal{M}$ with density $\mu$ and let $\mathcal{N}$ denote the set of all possible point configurations 
+in $\mathcal{M}$, equipped with the sigma algebra of the process $\Pcal$. 
 Then, for any natural number $k$ and measurable function $h : \R^k \times \mathcal{N} \to \R$,
+
 \begin{equation}\label{eq:def_campbell_mecke}
-	\Exp{\sum_{p_1, \dots, p_k \in \Pcal}^{\ne} h(p_1, \dots, p_k, \Pcal)}
-	= \int_{\mathcal{M}} \dots \int_{\mathcal{M}} \Exp{h(x_1,\dots, x_k, \Pcal} \dd \mu(x_1) \dots \dd \mu(x_k),
+\begin{array}{c}
+\displaystyle	\Exp{\sum_{p_1, \dots, p_k \in \Pcal, \atop \text{distinct}} h(p_1, \dots, p_k, \Pcal)} \\
+= \\
+\displaystyle \int_{\mathcal{M}} \dots \int_{\mathcal{M}} \Exp{h(x_1,\dots, x_k, \Pcal\cup\{x_1,\dots,x_k\})} \mu(dx_1)\dots\mu(dx_k).
+\end{array}
 \end{equation}
-where the sum is over all distinct point $p_1, \dots, p_k \in \Pcal$.
 
@@
 \end{equation}
-where we set $y_{k,C}^- = 0$ if $k - C \sqrt{k \log(k)} < \xi$. For convenience we write $\Kcal_C(k_n) := [y_{k_n,C}^-, y_{k_n,C}^+]$. Then we can show that for all $y$ outside $\Kcal_C(k_n)$
+where we set $y_{k,C}^- = 0$ if $k - C \sqrt{k \log(k)} < \xi$ and likewise if $k + C \sqrt{k \log(k)} < \xi$ we set $y_{k,C}^+=0$, but  note that as we consider $k\rightarrow\infty$, we can assume that this case does not occur.
+For convenience we write $\Kcal_C(k_n) := [y_{k_n,C}^-, y_{k_n,C}^+]$.
+Then we can show that for all $y$ outside $\Kcal_C(k_n)$
 \begin{equation}\label{eq:chernoff_bound_degrees}

### 2020-03-10 proofs_finite_k.tex
Edits by Tobias

--- 2019-03-12 proofs_finite_k.tex
@@
 
-\subsection{Clustering function, proving Theorem~\ref{thm:mainkfixed}}
-In this subsection, we want to show that the clustering function of the KPKVB model $c_n(k) \xrightarrow{\Pee} \gamma(k)$ for a fixed $k$.
-The key idea is that for the poissonized KPKVB model the coupling with the box model is guaranteed to be exact (in the sense that it also preserves edges) for all vertices up to height $H = \frac{R}{4}$ (which is all we need to show the convergence of the clustering function for constant $k$).
+\subsection{Clustering function for fixed $k$, proving Theorem~\ref{thm:mainkfixed}}
 
-The overall proof proceeds in four steps: firstly poissonizing the KPKVB model, secondly truncating the poissonized KPKVB model at height $H=H_n \rightarrow \infty$, thirdly using that the coupling between the poissonized KPKVB and box model is exact when truncated at this height $H$ and finally showing that the clustering function in the truncated box model agrees with the integral for $\gamma(k)$.
+We will now show that the clustering function of the KPKVB model $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for a fixed $k$. 
+The key ideas are that the coupling of the poissonized KPKVB model with the box model is guaranteed to be exact 
+(in the sense that it also preserves edges) for all vertices up to height $R/4$; and that when computing 
+the expected value clustering function $c(k;G)$ in the subgraph of the box model induced by all vertices up to height $R/4$
+using the Campbell-Mecke formula we obtain integrals that are very similar to the expressions we found earlier for $\gamma(k)$.
+%, the conditional expectation of 
+%clustering coefficient of the typical point in the infinite limit model $\Ginf$ conditioned on the typical point having degree $k$.
 
-We will encouter the following models: we will start with the KPKVB model $G_n = G(n;\alpha,\nu)$, then the Poissonized KPKVB model $\GPo  = G_{Po}(n;\alpha,\nu)$, moving to the truncated Poissonized KPKVB model $\GPoH$ which is the subgraph of $\GPo$ induced on all vertices with height at most $H$ resp.
-radial coordinate at least $R-H$, then the coupling will bring us to the truncated box model $\GboxH$ which is the subgraph of the box model $G_{box}$ induced by all vertices with height at most $H$.
+We will repeatedly rely on the following observation.
 
-\subsubsection{Poissonization}
-We first show we can restrict attention to the Poissonized instead of the standard KPKVB model.
+\begin{lemma}\label{lem:ckGckH}
+Let $k\geq 2$ and let $G, H$ be graphs such that $G$ is an induced subgraph of $H$, or vice versa.
+Then
 
-\begin{lemma}\label{lem:pok} Let $\alpha>\frac12,\nu>0, k\geq 2$ be fixed. % and write $G_n := G(n;\alpha,\nu), G_{n,\text{Po}} := \GPo(n;\alpha,\nu)$.
-Then 
-$$ c(k; G_n)-c(k; \GPo) \xrightarrow[n\to\infty]{\Pee} 0. $$
+$$ \left| c(k;G) - c(k;H) \right| \leq \frac{6|E(G)\Delta E(H)|}{N_G(k) - 2|E(G)\Delta E(H)|}, $$
+
+\noindent
+provided $N_G(k) > 2|E(G)\Delta E(H)|$.
 \end{lemma}
@@
 \begin{proof} 
-We consider the coupling where we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ chosen according
-to the $(\alpha,R)$-quasi uniform distribution, the vertices of $G(n;\alpha,\nu)$ are $u_1,\dots, u_n$ and 
-the vertices of $\GPo(n;\alpha,\nu)$ are $u_1,\dots, u_N$ with $N\isd \Po(n)$ independently of
+We observe that
+
+$$ \begin{array}{rcl} 
+|c(k; G)-c(k;H)| 
+& = & \displaystyle
+\left| \sum_{v\in V(G), \atop\text{deg}_G(v)=k} \frac{c_G(v)}{N_G(k)} - 
+\sum_{v\in V(H), \atop\text{deg}_{H}(v)=k} \frac{c_{H}(v)}{N_{H}(k)} \right| \\[8ex]
+& = & \displaystyle 
+\left| \frac{1}{N_G(k)} \left( \sum_{v\in V(G)\setminus V(H), \atop\text{deg}_G(v)=k} c_G(v)
++ \sum_{v\in V(G)\cap V(H), \atop{\text{deg}_G(v)=k, \atop\text{deg}_{H}(v)\neq k}} c_G(v) \right) \right. \\
+& & \displaystyle
+- \frac{1}{N_{H}(k)} \left(\sum_{v\in V(H)\setminus V(G), \atop\text{deg}_{H}(v)=k} c_{H}(v)
++ \sum_{v\in V(G)\cap V(H), \atop{\text{deg}_G(v)\neq k, \atop\text{deg}_{H}(v)=k}} c_{H}(v) \right) \\
+& & \displaystyle  
+\left. + \left(\frac{1}{N_G(k)}-\frac{1}{N_{H}(k)} \right) \cdot 
+\left( \sum_{v \in V(G)\cap V(H), \atop\text{deg}_G(v)=\text{deg}_{H}(v)=k}
+c_G(v) \right) \right| \\[8ex]
+ & \leq & \displaystyle
+ \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + 
+ \frac{|N_{H}(k) - N_G(k)|}{N_G(k)\cdot N_{H}(k)} \cdot N_{H}(k) \\[5ex]
+ & = & \displaystyle 
+ \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + \frac{|N_{H}(k) - N_G(k)|}{N_G(k)} \\[5ex]
+ & \leq & \displaystyle
+ \frac{2|E(G)\Delta E(H)|}{N_G(k)} + \frac{2|E(G)\Delta E(H)|}{N_{H}(k)} + \frac{2|E(G)\Delta E(H)|}{N_G(k)} \\[5ex]
+ & \leq & \displaystyle
+\frac{6 |E(G)\Delta E(H)|}{N_G(k)-2|E(G)\Delta E(H)|}.
+\end{array} $$
+
+\noindent
+(In the second line we use that $\text{deg}_G(v) = \text{deg}_{H}(v)$ in fact 
+implies that $c_G(v) = c_{H}(v)$ since one of $G,H$ is an induced subgraph of the other. 
+In the third line we use that clustering coefficients $c_G(v), c_H(v)$ take values in $[0,1]$, and if either 
+$\text{deg}_{G}(v) \neq \text{deg}_{H}(v)$ or $v \in V(G)\Delta V(H)$ and $v$ has degree $K$ in whichever of $G, H$ it belongs to 
+then at least one edge of $E(G)\Delta E(H)$ is incident with $v$, and that every edge in 
+$E(G)\Delta E(H)$ only affects the status of its two incident vertices.
+For the fifth line we used that $|N_G(k)-N_H(k)| \leq |\{ v\in V(G) : \text{deg}_G(v) = k \} \Delta 
+\{ v\in V(H) : \text{deg}_H(v) = k \}| \leq 2|E(G)\Delta E(H)|$ for similar reasons.
+In the last line we used that $N_H(k) \geq N_G(k) - |N_G(k)-N_H(k)| \geq N_G(k) - 2|E(G)\Delta E(H)|$.)
+\end{proof}
+
+\begin{lemma}\label{lem:NDGnGPo}
+%Under the standard coupling of $G_n$ and $\GPo$, we have 
+$|E(G_n) \Delta E(\GPo) | = o(n)$ a.a.s. 
+\end{lemma}
+
+\begin{proof}
+Let us fix some $\eps>0$ and write
+
+$$G_- := G((1-\eps)n, \alpha, (1-\eps)\nu ), \quad G_+ := G((1+\eps)n, \alpha, (1+\eps)\nu ). $$
+
+\noindent
+(We ignore rounding issues, i.e.~the issue that $(1-\eps)n, (1+\eps)n$ may not be integers, 
+to avoid notational burden. We leave the straightforward details of adapting our arguments below to deal with it to the reader.)
+
+Observe that the vertices of $G_-, G_+, G_n, \GPo$ all live on the same hyperbolic disk, of radius 
+$R = 2\ln(n/\nu)$. 
+We consider the standard coupling where we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ chosen according
+to the $(\alpha,R)$-quasi uniform distribution, the vertices of $G_n = G(n;\alpha,\nu)$ are $u_1,\dots, u_n$, 
+the vertices of $G_-$ are $u_1,\dots, u_{(1-\eps)n}$, the vertices of $G_+$ are $u_1,\dots, u_{(1+\eps)n}$ and 
+the vertices of $\GPo$ are $u_1,\dots, u_N$ with $N\isd \Po(n)$ independently of
 $u_1, u_2, \dots$.
 
-Due to the coupling, the KPKVB graph or its poissonization is contained in the other, i.e.
-we can use new graph labels $G_1 \subset G_2$; e.g.
-if $N\geq n$, then $G_1 = G(n;\alpha,\nu)$ and $G_2 = \GPo(n;\alpha,\nu)$.
-We write $V_{1,k}$ for the set of vertices of $G_1$ which have $k$ neighbours in $G_1$ and $V_{2,k}$ for the set of vertices of $G_2$ which have $k$ neighbours in $G_2$.
-Write $N_{1,k}=|V_{1,k}|$ and $N_{2,k}=|V_{2,k}|$.
+As $N\isd\Po(n)$, by Chebyschev's inequality, we have that $|N-n| < \eps n$ a.a.s.
+So in particular, under our coupling we have $G_- \subseteq G_n, \GPo \subseteq G_+$ a.a.s. 
+We now point out that, by the results of Gugelmann et al.~on the average degree (\cite{gugelmann2012random}, Theorem 2.3), 
+we have
 
-Write $W_1$ for the set of all vertices of $G_1$ which have $k$ neighbours in $G_1$ but no neighbour in $G_2 \backslash G_1$.
-Write $W_2$ for the set of all vertices of $G_1$ which have $k$ neighbours in $G_1$ and at least one neighbour in $G_2 \backslash G_1$.
-Write $W_3$ for the set of all vertices of $G_2$ which have strictly less than $k$ neighbours in $G_1$, but $k$ neighbours in $G_2$.
+$$|E(G_-)| = (1-\eps)^2\cdot \frac{4\nu\alpha^2}{\pi(2\alpha-1)^2} \cdot n + o(n), \quad 
+|E(G_+)| = (1+\eps)^2 \cdot \frac{4\nu\alpha^2}{\pi(2\alpha-1)^2} \cdot n + o(n) \quad \text{ a.a.s. } $$
 
-With this notation, we can rewrite:
-\begin{align*}
-|c(k;G_n)-c(k;\GPo)| &= \left|\sum_{v \in V_{1,k}}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in V_{2,k}}\frac{c_{G_2}(v)}{N_{2,k}}\right| \\
-&=\left|\sum_{v \in W_1}\frac{c_{G_1}(v)}{N_{1,k}}+\sum_{v \in W_2}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in W_1}\frac{c_{G_2}(v)}{N_{2,k}}-\sum_{v \in W_3}\frac{c_{G_2}(v)}{N_{2,k}}\right|
-\end{align*}
+%$G_-$ hand $G_+$ both have $4\nu\alpha^2/\pi(2\alpha-1)^2 \cdot n + o(n)$ many edges (a.a.s.).
+It follows that
 
-For every vertex of $W_1$, the clustering coefficient in $G_1$ and in $G_2$ have the same value. Hence, we can simplify:
-\begin{align*}
-|c(k;G_n)-c(k;\GPo)| &= \left|\sum_{v \in W_1}c_{G_1}(v)\frac{N_{2,k}-N_{1,k}}{N_{1,k}N_{2,k}}+\sum_{v \in W_2}\frac{c_{G_1}(v)}{N_{1,k}}-\sum_{v \in W_3}\frac{c_{G_2}(v)}{N_{2,k}}\right|
-\end{align*}
-Using the triangle inequality for the absolute value and the fact that $|c_G(v)|\leq 1$,
-\begin{align*}
-|c(k;G_n)-c(k;\GPo)| &\leq \frac{|W_1| |N_{2,k}-N_{1,k}|}{N_{1,k}N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}}
-\end{align*}
-Using that $|W_1|\leq N_{1,k}$,
-\begin{align*}
-|c(k;G_n)-c(k;\GPo)| &\leq \frac{|N_{2,k}-N_{1,k}|}{N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}}
-\end{align*}
+$$ | E(G_n) \Delta E(\GPo) | \leq |E(G_+)\setminus E(G_-)|
+= \eps \cdot \frac{16\nu\alpha^2}{\pi(2\alpha-1)^2}\cdot n + o(n) \text{ a.a.s. }
+$$
 
-From the Chernoff bound for Poisson random variables, it follows that for any $c>0$, $N \in [n-c\sqrt{n\log n},n+c\sqrt{n\log n}]$ a.a.s..
-This implies that a.a.s.
-the vertex sets of $G_1$ and $G_2$ differ by at most $c\sqrt{n\log n}$ many vertices.
-In particular also $|N_{1,k}-N_{2,k}|,|W_2|,|W_3|=O(\sqrt{n \log n})$ a.a.s.
-
-By the paper by Gugelmann et al.~\cite{gugelmann2012random} it holds that $N_{1,k}$ or $N_{2,k}$ is $\Theta(n)$ a.a.s.
-for fixed degree $k$ and as $|N_{1,k}-N_{2,k}| =O(\sqrt{n\log n})$ a.a.s., it follows that both $N_{1,k},N_{2,k} = \Theta(n)$ a.a.s.
-Putting everything together yields the claim:
-\begin{align*}
-|c(k;G_n)-c(k;\GPo)| &\leq \frac{|N_{2,k}-N_{1,k}|}{N_{2,k}}+\frac{|W_2|}{N_{1,k}}+\frac{|W_3|}{N_{2,k}} \xrightarrow[n\rightarrow\infty]{\Pee} 0
-\end{align*}
-
+This holds for every fixed $\eps>0$. Sending $\eps\searrow 0$, concludes the proof of the lemma.
 \end{proof}
 
-\subsubsection{Truncation}
-Consider the truncated Poissonized KPKVB model $\GPoH$ with $H =H_n= \frac{R}{4}$.
-%H,R-H tend to infinity and coupling is still exact
-\begin{lemma}\label{lem:n1}
-Let $N_1(H)$ denote the number of vertices with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model $\GPo$. If $H \rightarrow \infty$, then $\E N_1(H) = o(n)$.
-%For all $\epsilon >0$, there is $H_\epsilon$ such that for all $H\geq H_\epsilon$, it holds that $\E N_1(H) \leq \epsilon n$.
+Next, let us recall that by the results of Gugelmann et al.~on the degree sequence
+(\cite{gugelmann2012random}, Theorem 2.2) we have that
+
+\begin{equation}\label{eq:gugeldegseqaap} 
+\frac{N_{G_n}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k), 
+\end{equation}
+
+\noindent
+for every fixed $k$.
+In particular $N_{G_n}(k) = \Omega(n)$ a.a.s. Combining this with lemmas~\ref{lem:ckGckH} and~\ref{lem:NDGnGPo} we obtain:
+
+\begin{corollary}\label{cor:pok} 
+%Under the standard coupling of $G_n$ and $\GPo$, we have
+For every kixed $k\geq 2$, we have
+
+$$ c(k; G_n)-c(k; \GPo) \xrightarrow[n\to\infty]{\Pee} 0, $$
+
+%\noindent
+%for every fixed $k\geq 2$.
+\end{corollary}
+
+Since $N_{G_n}(k) - 2|E(G_n)\Delta E(\GPo)| \leq N_{\GPo}(k) \leq N_{G_n}(k) + 2|E(G_n)\Delta E(\GPo)|$ for all $k\geq 1$,
+we can also conclude from~\eqref{eq:gugeldegseqaap} and Lemma~\ref{lem:NDGnGPo} that:
+
+\begin{corollary}\label{cor:NGPok} 
+For every fixed $k\geq 0$ we have
+
+$$ \frac{N_{\GPo}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$
+
+\end{corollary}
+
+\noindent
+(The case $k=0$ follows from all the other cases together with the fact that the $\pmf(k)$ sum to one.)
+
+In the remainder of this section, we'll denote by $\GboxH$ the subgraph of $\Gbox$ induced by all 
+vertices $(x,y) \in \Vbox = \Pcal \cap \Rcal$ of height at most $R/4$.
+
+\begin{lemma}
+Under the coupling provided by Lemma~\ref{lem:coupling_hyperbolic_poisson}, a.a.s., 
+$\GboxH$ is an induced subgraph of $\GPo$ and $|E(\GPo) \setminus E(\GboxH)| = o(n)$.
 \end{lemma}
+
 \begin{proof}
-By the Campbell-Mecke formula applied to the vertex set of $\GPo$, by the asymptotic behaviour of $\cosh$ and using that all $R, R-H, H \rightarrow \infty$,
-\begin{align*}
-\E N_1(H) = n \frac{\cosh(\alpha(R-H))-1}{\cosh(\alpha R) -1} = (1+o(1)) n e^{-\alpha H} = o(n)
-\end{align*}
-\end{proof}
-\begin{lemma}\label{lem:n2}
-Let $N_2(H)$ denote the number of vertices with at least one neighbour with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model.
-If $H \rightarrow \infty$, then $\E N_2(H) = o(n)$.
-\end{lemma}
-\begin{proof}
-Among the vertices with at least one neighbour with radial coordinate at most $R-H$, we distinguish between those that themselves have radial coordinate at most $R-H_0$ and those that themselves have radial coordinate at least $R-H_0$ where $H_0 = \log H$.
-We will show that the expectation of both numbers is sublinear in $n$.
+We remind the reader that under the coupling of Lemma~\ref{lem:coupling_hyperbolic_poisson}, 
+we can view $\Gbox$ and $\GPo$ as having the same vertex set $\Vbox = \Pcal \cap \Rcal$; and 
+two points $p = (x,y), p' = (x',y') \in \Vbox$ are joined by an edge in $\Gbox$ if 
+$|x-x'|_{\pi e^{R/2}} \leq e^{(y+y')/2}$, while $p,p'$ are joined by an edge in $\GPo$ 
+if either $y+y'\geq R$ or $y+y'<R$ and $|x-x'|_{\pi e^{R/2}} \leq \Phi(y,y')$ with $\Phi$ as provided by~\eqref{eq:def_Omega_hyperbolic}.
+It follows immediately from Lemma~\ref{lem:coupling_edges} that $\GboxH$ is an induced subgraph of $\GPo$, a.a.s., as claimed.
 
-If $H \rightarrow \infty$, then also $H_0 = \log H \rightarrow \infty$.
-Hence by Lemma~\ref{lem:n1}, the expected number of vertices with radial coordinate at most $R-H_0$ (in particular those vertices among them with at least one neighbour with radial coordinate at most $R-H$), $\E N_1(H_0) = o(n)$ is sublinear.
-For a vertex with radial coordinate at least $R-H_0$, the probability that it has a neighbour with radial coordinate at most $R-H$, tends to zero.
-Therefore, by the Campbell-Mecke formula the number of such vertices is sublinear.
+Fix $\eps > 0$, and let $X$ denote the number points of $\Vbox$ with $y$-coordinate $\geq (1-\eps) R$. 
+Then $X$ is a Poisson random variable with mean
+
+$$ \begin{array}{rcl} 
+\Ee X 
+& = & \displaystyle \mu\left( (-\frac{\pi}{2} e^{R/2},\frac{\pi}{2} e^{R/2}] \times [(1-\eps) R,R] \right)
+= \int_{-\frac{\pi}{2} e^{R/2}}^{\frac{\pi}{2} e^{R/2}}\int_{(1-\eps)R}^R \left(\frac{\nu\alpha}{\pi}\right) e^{-\alpha y}\;dy\;dx \\[4ex]
+& = & O( e^{R/2-(1-\eps)\alpha R} ) = o(1), 
+\end{array} $$
+
+\noindent
+the last equality holding provided $\eps$ was chosen sufficiently small (using that $\alpha > 1/2$).
+We conclude that, a.a.s., there are no vertices of height $\geq (1-\eps) R$.
+
+Let $Y$ denote the number of pairs of vertices $p = (x,y), p'=(x',y') \in \Vbox$ with $y+y' \geq R$.
+Then, by the Campbell-Mecke formula
+
+$$ \begin{array}{rcl} \Ee Y 
+& = & \displaystyle
+\int_\Rcal\int_\Rcal 1_{\{y+y'\geq R\}} \mu(dp')\mu(dp) \\[4ex]
+& = & \displaystyle
+\int_{-\frac{\pi}{2}e^{R/2}}^{\frac{\pi}{2}e^{R/2}}\int_0^R
+\int_{-\frac{\pi}{2}e^{R/2}}^{\frac{\pi}{2}e^{R/2}}\int_{R-y}^R \left(\frac{\nu\alpha}{\pi}\right)^2 e^{-\alpha(y+y')}dy'dx'dydx \\[4ex]
+%= n^2 \int_0^R \int_{R-y}^R \alpha^2 e^{-\alpha(y+y')}dy'dy
+& = & O( R e^{(1-\alpha)R} ) = o( n ),
+\end{array} $$
+
+\noindent
+the last equality holding because $\alpha > 1/2$ and $n = \nu e^{R/2}$.
+In particular, by Markov's inequality, $Y = o(n)$ a.a.s.
+
+Now let $Z$ denote the number of pairs of vertices $p = (x,y), p'=(x',y')$
+for which $y+y'<R, y < (1-\eps)R, R/4 \leq y' < (1-\eps)R$ and $|x-x'|_{\pi e^{R/2}} < \Phi(y,y')$.
+By Lemma~\ref{lem:asymptotics_Omega_hyperbolic} we have that $\Phi(y,y') = O( e^{(y+y')/2} )$ 
+for all such $y,y'$.
+By Campbell-Mecke we can write
+
+$$ \begin{array}{rcl} 
+\Ee Z 
+& = & \displaystyle
+\int_{-\frac{\pi}{2}e^{R/2}}^{\frac{\pi}{2}e^{R/2}}\int_0^{(1-\eps)R}
+\int_{-\frac{\pi}{2}e^{R/2}}^{\frac{\pi}{2}e^{R/2}}\int_{R/4}^{(1-\eps)R} 
+1_{\{|x-x'|_{\pi e^{R/2}}<\Phi(y,y'), y+y'<R\}}\left(\frac{\nu\alpha}{\pi}\right)^2 e^{-\alpha(y+y')}dy'dxdydx' \\[4ex]
+& = & \displaystyle
+O\left( e^{R/2} \int_0^{(1-\eps)R} \int_{R/4}^{(1-\eps)R} e^{(1/2-\alpha)(y+y')} dy'dy \right) \\[4ex]
+& = & \displaystyle
+O\left( e^{R/2 + (1/2-\alpha) R/4} \right) = o(n).
+\end{array} $$
+
+\noindent
+Hence also $Z = o(n)$ a.a.s.
+
+This concludes the proof as we've now shown that under the stated coupling, a.a.s., $\GboxH$ and $\GPo$ differ by only $o(n)$ edges.
 \end{proof}
 
-\begin{lemma}\label{lem:trunc}
-Let $\alpha>\frac{1}{2}$, $\nu>0$ and $k \geq 2$ be fixed. Let $\GPo$ denote the Poissonized KPKVB model and $\GPoH$ denote the truncated Poissonized KPKVB model. Then 
-$$c(k;\GPo)-c(k;\GPoH) \xrightarrow[n \rightarrow \infty]{\Pee} 0.$$
+Analogously to Corollaries~\ref{cor:pok} and~\ref{cor:NGPok} we obtain:
+
+\begin{corollary}\label{cor:GPoHdegseq}
+For every fixed $k$ we have
+
+$$\frac{N_{\GboxH}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$
+
+\end{corollary}
+
+\begin{corollary}\label{cor:GPoGboxH}
+For every fixed $k\geq 2$ we have
+
+$$c(k;\GPo) - c(k;\GboxH) \xrightarrow[n \rightarrow \infty]{\Pee} 0. $$
+
+\end{corollary}
+
+\begin{lemma}\label{lem:ckGboxH} 
+For every fixed $k\geq 2$ we have
+
+ $$ c(k;\GboxH) \xrightarrow[n \rightarrow \infty]{\Pee}  \gamma(k). $$
+
  \end{lemma}
+
  \begin{proof}
-Let $V_n(k)$ denote the set of all vertices with degree $k$ in the Poissonized KPKVB model $\GPo$ and $V_{n,H}(k)$ the set of all vertices with degree $k$ in the truncated Poissonized KPKVB model $\GPoH$.
-Note that a vertex may have a smaller degree and different clustering coefficient in $\GPo$ and $\GPoH$ (even if it is a vertex of both graphs).
-We write $c_n(v)$ for the clustering coefficient of a vertex $v$ in $\GPo$ and $c_{n,H}(v)$ for the clustering coefficient in $\GPoH$.
-Let $N_n(k)=|V_n(k)|$ denote the number of degree $k$ vertices in $\GPo$.
-Then as $N_n(k) = \Theta(n k^{-(2\alpha+1)})$ a.a.s., there is a constant $a_1(k)>0$ such that a.a.s.
-$N_n(k) \geq a_1(k) n$.
-Let $N_{n,H}(k) = |V_{n,H}(k)|$ be the number of degree $k$ vertices in $\GPoH$.
+ We write $\Rcal_- := \Rcal \cap (\eR\times[0,R/4]) = (-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2} e^{R/2}] \times [0,R/4]$ and set
 
-Using a telescoping sum, we obtain that
-\begin{align*}
-|c(k;\GPo)-c(k;\GPoH)| \leq & \left|c(k;\GPo)-\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v)\right|\\
-&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(v)\right| \\
-&+\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_{n, H}(v)-c(k;\GPoH)\right| 
-\end{align*}
-Now we use $X_1 := |V_n(k)\backslash V_{n,H}(k)|$, $X_2 := \sum_{v \in V_{n,H}(k)}|c_n(k)-c_{n,H}(k)|$ and $X_3 :=|N_{n,H}(k)-N_n(k)|$ to bound the three differences.
-In the first difference, after factorizing $N_n(k)$, all terms in $V_{n,H}(k)$ cancel and the remaining terms are all bounded by one:
-\begin{align*}
-\left|c(k;\GPo)-\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v)\right| = \left| \frac{1}{N_n(k)}\sum_{v \in V_n \backslash V_{n,H}(k)} c_n(v) \right| \leq \frac{X_1}{N_n(k)}
-\end{align*}
-In the second difference, the sums can be aligned and then the triangle inequality for the absolute value applied:
-\begin{align*}
-\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_n(v) -\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(v)\right| \leq \frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} \left|c_n(v)-c_{n,H}(v)\right| =\frac{X_2}{N_n(k)}
-\end{align*}
-In the third difference, we can simplify:
-\begin{align*}
-\left|\frac{1}{N_n(k)}\sum_{v \in V_{n,H}(k)} c_{n, H}(v)-c(k;\GPoH)\right| &= \left|\sum_{v\in V_{n,H}(k)} c_{n,H} \left(\frac{1}{N_n(k)}-\frac{1}{N_{n,H}(k)}\right)\right| \\
-&= \frac{|N_{n,H}(k)-N_n(k)|}{N_n(k)N_{n,H}(k)}\sum_{v \in V_{n,H}(k)}c_{n,H}(k)
-\end{align*}
-Thus, we end up with the upper bound, using that $c_{n,H}(k) \leq 1$ and $N_{n,H}(k) = |V_{n,H}(k)|$,
-\begin{align*}
-|c(k;\GPo)-c(k;\GPoH)| \leq \frac{X_1}{N_n(k)}+\frac{X_2}{N_n(k)}+\frac{X_3}{N_n(k)}\frac{\sum_{v \in V_{n,H}(k)}c_{n,\leq H}(k)}{N_{n,H}(k)} \leq \frac{X_1+X_2+X_3}{N_n(k)}
-\end{align*}
-Now using that a.a.s. $N_n(k) \geq a_1(k)n$ gives that a.a.s.
-\begin{align*}
-|c(k;\GPo)-c(k;\GPoH)| \leq \frac{X_1+X_2+X_3}{a_1(k)n} 
-\end{align*}
+ $$ 
+ X := \sum_{v \in N_{\GboxH}(k)} c(v) = \sum_{v \in \Pcal \cap \Rcal_-} c_{\GboxH}(v) \cdot 1_{\{\text{deg}_{\GboxH}(v)=k\}}.
+ $$
 
-By Lemma~\ref{lem:n1}, we have that $\E X_1 = \E X_3 = o(n)$ and by Lemma~\ref{lem:n2}, we have that $\E X_2 = o(n)$.
-We conclude that $\E |c(k;\GPo)-c(k;\GPoH)| = o(1)$.
-From this, convergence in probability follows by Markov's inequality: for $\epsilon >0$, $\Pee(|c(k;\GPo)-c(k;\GPoH)| \geq \epsilon) \leq \frac{\E|c(k;\GPo)-c(k;\GPoH)|}{\epsilon} = o(1)$.
-\end{proof}
-\subsubsection{Coupling}
-\begin{lemma}\label{lem:coup}
-The clustering function in the truncated Poissonized KPKVB model $\GPoH$ and in the truncated box model $\GboxH$ agree, i.e. $c(k;\GPoH) = c(k;\GboxH)$.
-\end{lemma}
-\begin{proof}
-As all vertices involved have height $\leq H$ resp.
-radial coordinate $\geq R-H$ and as $H\leq \frac{R}{4}$, all vertices involved (in the disk)  will have radial coordinate $\geq \frac{3}{4}R$, such that by Lemma~30(ii) from the paper on the largest component of KPKVB, see Lemma~\ref{lem:coupling_edges}, edges exist between such vertices in the disk if and only if they exist in the box.
-So the two graphs are isomorphic and hence the clustering functions agree.
+ \noindent
+ By the Campbell-Mecke formula
+
+ $$ \Ee X = \int_{\Rcal_-} 
+ \Ee_\Pcal\left[ c_{\GboxH^z}(z) \cdot 1_{\{\text{deg}_{\GboxH^z}(z)=k\}}\right] \mu(dz), $$
+
+ \noindent
+ where $\GboxH^z$ denotes the graph we get by adding $z$ as an additional vertex to $\GboxH$, and adding edges between $z$ and the other 
+ vertices as per the connection rule (for $\Gbox$).
+ Spelling out the intensity measure $\mu$, plus symmetry considerations, gives
+
+ $$ \begin{array}{rcl}
+     \Ee X 
+     & = & \displaystyle 
+     \int_{-\frac{\pi}{2}e^{R/2}}^{\frac{\pi}{2}e^{R/2}} \int_0^{R/4}
+     \Ee_\Pcal\left[ c_{\GboxH^{(x,y)}}((x,y)) \cdot 1_{\{\text{deg}_{\GboxH^{(x,y)}}((x,y))=k\}}\right] 
+     \left(\frac{\nu\alpha}{\pi}\right) e^{-\alpha y}\;dy\;dx \\[6ex]
+     & = & \displaystyle
+     n \dot \int_0^{R/4}
+     \Ee_\Pcal\left[ c_{\GboxH^{(0,y)}}((0,y)) \cdot 1_{\{\text{deg}_{\GboxH^{(0,y)}}((0,y))=k\}}\right] 
+     \alpha e^{-\alpha y}\;d y \\[6ex]
+     & = & \displaystyle
+     n \cdot \int_0^{R/4} \Ee_\Pcal\left[ c_{\GboxH^{(0,y_0)}}((0,y_0)) {\Big|} \text{deg}_{\GboxH^{(0,y_0)}}((0,y_0))=k \right] \cdot \\[6ex]
+     & & \displaystyle \hspace{6ex} 
+     %\cdot 
+     \Pee\left[ \text{deg}_{\GboxH^{(0,y_0)}}((0,y_0))=k  \right] \alpha e^{-\alpha y_0} \;dy_0.
+    \end{array}
+$$
+
+\noindent
+The random variable $\text{deg}_{\GboxH^{(0,y_0)}}((0,y_0))$ follows a Poisson distribution with mean
+
+$$ \begin{array}{rcl} 
+\Ee\left[ \text{deg}_{\GboxH^{(0,y_0)}}((0,y_0))\right] 
+& = & \displaystyle  
+\mu(\BallPo{(0,y_0)}\cap\Rcal_-) 
+= \int_0^{R/4} \int_{-e^{(y+y_0)/2}}^{e^{(y+y_0)/2}} \left(\frac{\nu\alpha}{\pi}\right) e^{-\alpha y}\;dx\;dy \\
+& = & \xi e^{y_0/2} \cdot (1-e^{(1/2-\alpha)R/4}). 
+\end{array} $$
+
+\noindent
+Hence, for every fixed $y_0$ and $k$, we have that
+
+$$ \Pee\left[ \text{deg}_{\GboxH^{(0,y_0)}}((0,y_0))=k\right] %= \Pee( \Po( \mu(\BallH{(0,y_0)}) = k ) 
+\xrightarrow[n\to\infty]{} 
+%\Pee( \Po( \mu(\BallPo{(0,y_0)})) = k ) = 
+\Pee( \Po(\xi e^{y_0/2})=k ) = \rho(y_0,k).$$
+
+%\noindent
+%with $D$ denoting the (unrestricted) degree of the typical point in the limit model $\Ginf$.
+
+Next we remark that, analogously to the argument given in the beginning of Section~\ref{sec:42}, we have
+
+$$ %\Ee[ c_{\GboxH^{(0,y_0)}}((0,y_0)) | \text{deg}_{\GboxH^{(0,y_0)}}((0,y_0))=k ] 
+\Ee\left[ c_{\GboxH^{(0,y_0)}}((0,y_0)) {\Big|} \text{deg}_{\GboxH^{(0,y_0)}}((0,y_0))=k \right] 
+= \Pee( w_1 \in \BallPo{w_2} ) =: P_n(y_0), $$
+
+\noindent
+with $w_1 = (x_1, y_1), w_2 = (x_2, y_2)$ chosen independently from $\BallPo{(0,y_0)} \cap \Rcal_-$ according to the probability 
+measure we get by renormalizing $\mu$, i.e.~with pdf $f_\mu \cdot 1_{\BallPo{(0,y_0)} \cap \Rcal_-} / \mu(\BallPo{(0,y_0)}\cap \Rcal_-)$.
+By considerations completely analogous to those following Lemma~\ref{lem:Paneq1}, the random variables $y_1, y_2$ both follow
+a truncated exponential distribution with parameter $\alpha - 1/2$ truncated at height $R/4$
+(i.e.~with density $1_{\{y_i \leq R/4\}} \cdot (\alpha-1/2) e^{(1/2-\alpha)y_i} / (1-e^{(1/2-\alpha)R/4})$) and, given the 
+values of $y_0, y_1, y_2$, each $x_i$ is chosen uniformly on the interval $[-e^{(y_0+y_i)/2}, e^{(y_0,y_i)/2}]$.
+In particular
+
+$$ P_n(y_0) = 
+\left(\frac{\alpha-1/2}{1-e^{(1/2-\alpha)R/4}}\right)^2 \int_0^{R/4}\int_0^{R/4} P(y_0, y_1, y_2) e^{(1/2-\alpha)(y_1+y_2)}\;dy_1\;dy_2,
+$$
+
+\noindent
+with $P(.,.,y.)$ as defined in the paragraph following Lemma~\ref{lem:Paneq1}.
+(That is, $P(y_0, y_1, y_2)$ is the probability that $|x_1-x_2| < e^{(y_1+y_2)/2}$, where $x_1, x_2$ are independent with $x_i$ uniform 
+on the interval $[-e^{(y_0+y_i)/2}, e^{(y_0+y_i)/2}]$). 
+It follows that, for any fixed $y_0$, we have
+
+$$ P_n(y_0) \xrightarrow[n\to\infty]{} 
+(\alpha-1/2)^2\int_0^\infty\int_0^\infty P(y_0, y_1, y_2) e^{(1/2-\alpha)(y_1+y_2)}\;dy_1\;dy_2 = P(y_0). $$
+
+\noindent
+(Applying monotone convergence to justify the convergence of the integral as $n \to \infty$.)
+
+Since (expected) clustering coefficients and probabilities are between zero and one and $\alpha e^{\alpha y_0}$ is integrable, we can now apply the dominated 
+convergence theorem to obtain that
+
+\begin{equation}\label{eq:EXn} 
+\frac{\Ee X}{n} \xrightarrow[n\to\infty]{} \int_0^\infty P(y_0) \rho(y_0,k)\alpha e^{-\alpha y_0}\;dy_0 = \pmf(k) \cdot \gamma(k).  
+\end{equation}
+
+\noindent
+(Applying~\eqref{eq:gammakint} for the last equality.)
+
+Next, we turn attention to $X(X-1) = \sum_{u\neq v \in N_{\GboxH}(k)} c(v)c(u)$.
+Another application of Cambell-Mecke shows that
+
+$$
+\Ee X(X-1) 
+= 
+\int_{\Rcal_-}\int_{\Rcal_-} \Ee\left[ c_{\GboxH^{z,z'}}(z)c_{\GboxH^{z,z'}}(z') \cdot 
+1_{\{\text{deg}_{\GboxH^{z,z'}}(z)=\text{deg}_{\GboxH^{z,z'}}(z')=k\}}\right]\mu(dz)\mu(dz'),
+$$
+
+\noindent
+with $\GboxH^{z,z'}$ denoting the graph we get by adding $z, z'$ as additional vertices to $\GboxH$.
+Now note that if $z=(x,y)$ and $z'=(x',y')$ satisfy $|x-x'|_{\pi e^{R/2}} > 2 e^{R/4}$ then 
+the neighbourhoods of $z,z'$ are determined by the points of the Poisson process $\Pcal$ in disjoint areas
+of the plane.
+This implies that, provided $|x-x'|_{\pi e^{R/2}} > 2 e^{R/4}$:
+
+\begin{equation}\label{eq:noot1} 
+\begin{array}{c} 
+\Ee\left[ c_{\GboxH^{z,z'}}(z)c_{\GboxH^{z,z'}}(z') \cdot 
+1_{\{\text{deg}_{\GboxH^{z,z'}}(z)=\text{deg}_{\GboxH^{z,z'}}(z')=k\}}\right] \\
+= \\
+\Ee\left[ c_{\GboxH^{z}}(z) \cdot 
+1_{\{\text{deg}_{\GboxH^{z}}(z)=k\}}\right] \cdot 
+\Ee\left[ c_{\GboxH^{z'}}(z') \cdot 
+1_{\{\text{deg}_{\GboxH^{z'}}(z')=k\}}\right].
+\end{array} 
+\end{equation}
+
+\noindent
+On the other hand, the LHS of~\eqref{eq:noot1} is always between zero and one, also if $|x-x'|_{\pi e^{R/2}} \leq 2 e^{R/4}$. 
+We may conclude that
+
+$$ \begin{array}{rcl} 
+\Ee X(X-1) 
+& \leq & \displaystyle  
+\int_{\Rcal_-}\int_{\Rcal_-} \Ee\left[ c_{\GboxH^{z}}(z) \cdot 
+1_{\{\text{deg}_{\GboxH^{z}}(z)=k\}}\right] %\\
+%& & \displaystyle 
+\cdot 
+\Ee\left[ c_{\GboxH^{z'}}(z') \cdot 
+1_{\{\text{deg}_{\GboxH^{z'}}(z')=k\}}\right] \mu(dz)\mu(dz') \\[8ex]
+& & \displaystyle 
++ \int_{\Rcal_-}\int_{\Rcal_-} 1_{\{|x-x'|\leq 2e^{R/4}\}} \mu(dz)\mu(dz') \\[8ex]
+& = & \displaystyle
+\left( \int_{\Rcal_-} \Ee\left[ c_{\GboxH^z}(z) \cdot 1_{\{\text{deg}_{\GboxH^z}(z)=k\}}\right] \mu(dz) \right)^2
++ O( e^{3R/4} ) \\[8ex] 
+& = & \displaystyle
+\left(\Ee X\right)^2 + O( n^{3/2} ).
+\end{array} $$
+
+\noindent
+Combining this with~\eqref{eq:EXn}, it follows that 
+$\Var X = \Ee X(X-1) + \Ee X - \left(\Ee X\right)^2 = o\left( \left(\Ee X\right)^2 \right)$.
+ By Chebyschev's inequality, we therefore have
+
+ $$ X = n \cdot \gamma(k) \cdot \pmf(k) + o(n) \text{ a.a.s. } $$
+
+In combination with Corollary~\ref{cor:GPoHdegseq} we can conclude that
+
+$$ c(k;\GboxH) = \frac{X}{N_{\GboxH(k)}} \xrightarrow[n\to\infty]{\Pee} \gamma(k), $$
+
+\noindent
+as desired.
  \end{proof}
 
-\subsubsection{Deriving the limit integral expression}
-\begin{lemma}\label{lem:lim}
-Let $\alpha > \frac{1}{2}$, $\nu>0$ and $k\geq 2$ be fixed. Then
-$$c(k;\GboxH)\xrightarrow[n\rightarrow\infty]{\Pee}\gamma(k).$$
-\end{lemma}
-%\begin{proof}
-%We will show that $\E c(k;G_{n,Po,H}) \rightarrow \gamma(k)$ as $n\rightarrow\infty$ and $Var(c(k;G_{n,Po,H})) \rightarrow  0$.
-From there, the claim will follow by Chebychev's inequality: Let $\epsilon>0$, then $$\Pee(|c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H})|\geq \epsilon)\leq \frac{Var(c(k;G_{n,Po,H}))}{\epsilon^2} = o(1),$$
-%i.e.
-$c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H}) \xrightarrow[n\rightarrow\infty]{\Pee} 0$, hence also $c(k;G_{n,Po,H})-\gamma(k) = c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H})+\E c(k;G_{n,Po,H})-\gamma(k) \xrightarrow[n\rightarrow\infty]{\Pee} 0$.
-%\end{proof}
-
-Let $\Rcal_H = \Rcal([0,H])$ denote the truncated box.
-For a vertex $v$ of the vertex set $V=V(\GboxH)$, writing $\Gamma(v)$ for the set of all neighbours of vertex $v$, let $$h(V,v) = {k \choose 2}^{-1} \sum_{uw \in {\Gamma(v) \choose 2}} \1_{\{uw \in E(\GboxH)\}} \1_{\{ D_{\GboxH}(v)=k\}}.$$
-Let $X = \frac{1}{n}\sum_{v \in V(G_{box,H})} h(V(G_{box,H}),v)$.
-Let $Z = \frac{N_{box,H}(k)}{n} = \frac{1}{n}\sum_{v \in \GboxH} \1_{\{D_{\GboxH}(v)=k\}}$.
-Then we have that $c(k;\GboxH) = \frac{X}{Z}$.
-We will show separately that numerator $X$ and denominator $Z$ converge in probability (where the limit of $Z$ is a positive constant).
-From this, the claim of the lemma will follow as convergence in probability is closed under taking quotients.
-
-By the Campbell-Mecke formula, we have
-\begin{align*}
-\E X = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) \mu(dv) = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy
-\end{align*}
-Then, we condition on that the additional vertex $(0,y) \in \Rcal_H$ has degree $k$,
-\begin{align*}
-\E X = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy
-\end{align*}
-We observe that for $H \rightarrow \infty$, the integrand converges point-wise for $y \in (0,\infty)$ to $P(y)\rho(y,k)\alpha e^{-\alpha y}$ and is always bounded by the integrable function $\alpha e^{-\alpha y}$.
-Therefore, by the theorem of dominated convergence, as $H \rightarrow \infty$,
-\begin{align*}
-\E X \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy
-\end{align*}
-Note that for $X^2$, the summation can be split into off-diagonal (with $v_1 \not = v_2$) and diagonal (with $v_1=v_2$) terms, i.e. write $X^2 = \frac{1}{n^2}(Y_1+Y_2)$ where 
-$$Y_1 = \sum_{v_1 \not = v_2 \in V(G_{box,H})} h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)$$ and $Y_2 = \sum_{v_1 \in V(G_{box,H})} h(V(G_{box,H}),v_1)^2$.
-As $h \leq 1$, $Y_2 \leq n X\leq n$ and so, $\E Y_2 \leq n$, we have by the Campbell-Mecke formula,
-\begin{align*}
-\E Y_1 = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)]\mu(dv_1)\mu(dv_2)
-\end{align*}
-If $v_1=(x_1,y_1)$ and $v_2=(x_2,y_2)$ have horizontal distance $>2e^H$, their neighbourhood balls are disjoint w.r.t.
-the connection rule of the truncated box model $\GboxH$.
-To see this, assume that $v_3=(x_3,y_3)$ is adjacent to both $v_1$ and $v_2$, then $|x_1-x_3|\leq e^{\frac{1}{2}(y_1+y_3)}$ and $|x_2-x_3|\leq e^{\frac{1}{2}(y_2+y_3)}$.
-As $y_1, y_2, y_3 \leq H$, it follows that $|x_1-x_3| \leq e^H$ and $|x_2-x_3|\leq e^H$, which implies that $|x_1-x_2| \leq |x_1-x_3|+|x_2-x_3|\leq 2e^H$, contradiction.
-
-Due to the disjointedness of the neighbourhood balls and the properties of the Poisson process $h(V,v_1)$ and $h(V,v_2)$ are independent.
-The horizontal distance is uniform in $[0,\frac{\pi n}{2\nu}]$.
-Therefore, the probability that two vertices have horizontal distance $\leq 2e^H$ is $\leq \frac{4\nu e^H}{\pi n} = o(1)$.
-Writing $d_H$ for the horizontal distance, we can continue the calculation of the second moment,
-\begin{align*}
-\E Y_1 &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)\\
-&\qquad+\int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|\leq2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
-&= (1+o(1))\int_{} \int_{\Rcal_H\times \Rcal_H} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
-&= (1+o(1)) (n\E X)^2%+o((n\E X)^2)+o(n)
-\end{align*}
-It follows that $\E X^2 = (1+o(1))(\E X)^2$, which implies $Var(X) \rightarrow 0$. We conclude
-$$X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.$$
-In a similar way, by the Campbell-Mecke formula,
-\begin{align*}
-\E Z =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy
-\end{align*}
-By the theorem of dominated convergence, it follows that
-\begin{align*}
-\E Z \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy
-\end{align*}
-The statement that $Var(Z) \rightarrow 0$ follows by the same steps as for $X$, just using $h(V,v) = \1_{\{D_{\GboxH}(v)=k\}}$ instead. Hence,
-\begin{align*}
-\E Z \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy
-\end{align*}
-Finally note that 
-\begin{align*}
-\gamma(k) = \frac{\int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy}{\int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy}.
-\end{align*}
-
-\subsubsection{Putting everything together}
 \begin{proofof}{Theorem~\ref{thm:mainkfixed}}
-The overall statement follows from the lemmas together with the fact that convergence in probability is closed under addition.
-Write 
-$$c(k;G_n)-\gamma(k) = c(k;G_n) - c(k;\GPo)+c(k;\GPo)-c(k;\GPoH)+c(k;\GPoH)-\gamma(k).$$ 
-The first difference converges in probability to zero due to the Poissonization Lemma~\ref{lem:pok}, the second difference due to the truncation Lemma~\ref{lem:trunc}, then for the third difference we use $c(k;\GPoH)=c(k;\GboxH)$ from Lemma~\ref{lem:coup} and then Lemma~\ref{lem:lim} on the derivation of the limit integral.
+For completeness, we point out that Theorem~\ref{thm:mainkfixed} follows immediately from 
+Corollaries~\ref{cor:pok},~\ref{cor:GPoGboxH} and Lemma~\ref{lem:ckGboxH}.
 \end{proofof}
@@
 \subsection{Overall clustering coefficient, proving Theorem~\ref{thm:maincc}}
-In this subsection, we want to infer that the clustering coefficient of the KPKVB random graph $c(G_n) \xrightarrow{\Pee} \gamma$ by using that $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for fixed $k$.
+
+% 
+% 
+% 
+% In this subsection, we will infer that the clustering coefficient of the KPKVB random graph 
+% $c(G_n) \xrightarrow{\Pee} \gamma$ by using that $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ and $N_{G_n}(k)/n \xrightarrow{\Pee} \pmf(k)$ 
+% for all fixed $k$.
 
 \begin{proofof}{Theorem~\ref{thm:maincc}}
-Let $\epsilon >2\delta >0$.
-As the $p_k$ form the probability mass function of an $\N_0$-valued random variable, we have that $\sum_{k=0}^\infty p_k = 1$, which implies that there is $K_\delta >0$ such that $1-\delta < \sum_{k=0}^{K_\delta} p_k \leq 1$.
-From Equations~\ref{eq:def_pk}, \ref{eq:gammakint} and \ref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$. 
-From this, it follows that $(1-\delta)\gamma < \sum_{k=2}^{K_\delta} \gamma(k) p_k \leq 1$ and hence that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$.
-Write $p(k;G_n)=\frac{N_n(k)}{n}$ for the fraction of degree $k$ vertices in the KPKVB model.
-From the definition of the clustering coefficient and function, it follows immediately that $c(G_n) = \sum_{k=2}^\infty c(k;G_n)p(k;G_n)$.
-By the initial observation, it follows again that $(1-\delta)c(k;G_n) < \sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \leq 1$, and hence, $|c(G_n)-\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n)| \leq \delta$.
-Putting these observations together:
-\begin{align*}
-|c(G_n)-\gamma| &\leq \left|c(G_n)-\sum_{k=2}^{K_\delta}c(k;G_n)p(k;G_n)\right|+\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
- &\leq \delta +\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta 
-\end{align*}
-Therefore, $\Pee(|c(G_n)-\gamma|\geq \epsilon) \leq \Pee(\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta) \rightarrow 0$ because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$.
-%p_k =  = \Theta(k^{-(2\alpha +1)})
+Recall in Section~\ref{sec:Ginf},  we {\em defined} $\pmf(k) := \Pee(D=k), \gamma := \Ee C, \gamma(k) := \Ee(C|D=k)$ with $D$ the degree
+and $C$ the clustering coefficient of the ``typical point'' in the infinite limit model $\Ginf$. We can write
+
+$$ \gamma = \Ee C = \sum_{k\geq 2} \Ee\left( C | D=k \right) \Pee( D=k ) = \sum_{k\geq 2} \gamma(k) \cdot \pmf(k). $$
+
+For the KPKVB random graph, or any graph for that matter, we have the similar relation
+
+$$ c(G_n) = \sum_{k\geq 2} c(k;G_n) \cdot (N_{G_n}(k)/n). $$
+
+By Theorem~\ref{thm:mainkfixed} and~\eqref{eq:gugeldegseqaap} we have, for any fixed $K\geq 2$:
+
+\begin{equation}\label{eq:slutskyUB} 
+ c(G_n) \geq \sum_{k=2}^K c(k;G_n) \cdot (N_{G_n}(k)/n) \xrightarrow[n\to\infty]{\Pee} \sum_{k=2}^K \gamma(k)\cdot \pmf(k), 
+\end{equation}
+
+\noindent
+where Slutsky's theorem justifies the convergence in probability.
+On the other hand we have
+
+\begin{equation}\label{eq:slutskyLB} 
+c(G_n) \leq \sum_{k=2}^K c(k;G_n) \cdot (N_{G_n}(k)/n) + \sum_{k>K} (N_{G_n}(k)/n)
+\xrightarrow[n\to\infty]{\Pee} \sum_{k=2}^K \gamma(k)\cdot \pmf(k) + \sum_{k>K} \pmf(k), 
+\end{equation}
+
+\noindent
+where the convergence in probability can be justified using Slutksy's theorem together 
+with the fact that $\sum_{k=0}^\infty \pmf(k) = 1$ (one convenient way to convince oneself that this is true, is to note that 
+$D$, the degree of the typical point, is a.s.~finite). In more detail,
+
+$$\sum_{k>K} (N_{G_n}(k)/n) 
+= 1 - \sum_{k=0}^K (N_{G_n}(k)/n) \xrightarrow[n\to\infty]{\Pee} 1 - \sum_{k=0}^K \pmf(k) = \sum_{k>K} \pmf(k). $$
+
+The result follows from~\eqref{eq:slutskyLB} and~\eqref{eq:slutskyUB}, by sending $K\to\infty$. 
 \end{proofof}

### 2020-03-10 proofs_infinite_k.tex
Edits by Tobias

@@
-\section{Overview of the proof strategy for $k \to \infty$}
+\section{Clustering when $k\to\infty$ : overview of the proof strategy}
 
@@
 \begin{equation}\label{eq:def_local_clustering_ast_general}
-	c^\ast(k;G) = \frac{1}{\Exp{N_k}} \sum_{v \in V(G) \atop \text{deg}(v)=k} c(v).
+	c^\ast(k;G) = \frac{1}{\Exp{N(k)}} \sum_{v \in V(G) \atop \text{deg}(v)=k} c(v).
 \end{equation}
-Notice that the only difference between $c(k;G)$ and $c^\ast(k;G)$ is that we replace $N_k$ by its expectation $\Exp{N_k}$.
+Notice that the only difference between $c(k;G)$ and $c^\ast(k;G)$ is that we replace $N(k)$ by its expectation $\Exp{N(k)}$.
 The advantage is that now, the only randomness is in the formation of triangles.
-In addition, note that since $\Exp{N_k} > 0$ a case distinction for $N_k$ is no longer needed for $c^\ast(k;G)$.
+In addition, note that since $\Exp{N(k)} > 0$ a case distinction for $N(k)$ is no longer needed for $c^\ast(k;G)$.
 It is however still relevant since we are eventually interested in $c(k;G)$.
@@
 
-We then establish that the modified local clustering function for KPKVB graphs $G_n$ behaves similarly to that in the $\GPo$.
+We then establish that the modified local clustering function for KPKVB graphs $G_n$ behaves similarly to that in $\GPo$.
 The proof, found in Section~\ref{ssec:coupling_H_HP}, is based on a standard coupling between a Binomial Point Process and Poisson Point Process.

### 2020-03-10 transition.tex
updated section 3
Edits by Tobias

@@
 \[
-	T_{\text{box}}(p) = \sum^{\ne}_{p_1, p_2 \in \Pcal \setminus \{p\}} T_{\text{box}}(p,p_1,p_2)
+	T_{\text{box}}(p) = \sum_{p_1, p_2 \in \Pcal \setminus \{p\}, \atop \text{distinct}} T_{\text{box}}(p,p_1,p_2)
 \]
@@
 \[
-	T_\infty(y) = \sum_{p_1, p_2 \in \Pcal \setminus (0,y)}^{\ne} T_\infty(y,p_1,p_2),
+	T_\infty(y) = \sum_{p_1, p_2 \in \Pcal \setminus (0,y), \atop \text{distinct}} T_\infty(y,p_1,p_2),
 \]
@@
 \begin{equation}\label{eq:alt_gamma_kn}
-	\gamma(k_n) = (1+\smallO{1})\frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_{C}(k_n)} \Exp{T_\infty(y)} \rho(y,k) 
+	\gamma(k_n) = (1+\smallO{1})\frac{1}{k_n^2 \pmf(k_n)} \int_{\Kcal_{C}(k_n)} \Exp{T_\infty(y)} \rho(y,k) 
 				\alpha e^{-\alpha y} \dd y. 
@@
 \begin{equation}\label{eq:alt_c_ast_kn}
-	\Exp{c^\ast(k_n;\Gbox)} = (1 + \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y)}
+	\Exp{c^\ast(k_n;\Gbox)} = (1 + \smallO{1}) \frac{1}{k_n^2 \pmf(k_n)} \int_{\Kcal_{C}(k_n)} \Exp{T_{\text{box}}(y)}
 		\rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y
@@
 \begin{align*}
-	\gamma(k_n) &= \frac{1}{p_{k_n}} \cdot \int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
-	= \frac{1}{p_{k_n}} \int_0^\infty \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) 
+	\gamma(k_n) &= \frac{1}{\pmf(k_n)} \cdot \int_0^\infty P(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
+	= \frac{1}{\pmf(k_n)} \int_0^\infty \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) 
 		\alpha e^{-\alpha y} \dd y.
@@
 \begin{align*}
-	&\hspace{-30pt} \frac{1}{p_{k_n}} 
+	&\hspace{-30pt} \frac{1}{\pmf(k_n)} 
 		\int_0^\infty \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) \alpha e^{-\alpha y} \dd y \\
-	&= (1+\smallO{1}) \frac{1}{p_{k_n}} 
+	&= (1+\smallO{1}) \frac{1}{\pmf(k_n)} 
 		\int_{\Kcal_C(k_n)} \Exp{T_\infty(y)} \Mu{\BallPo{y}}^{-2} \rho(y,k) \alpha e^{-\alpha y} \dd y \\
-	&= (1+ \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_C(k_n)} \Exp{T_\infty(y)} \rho(y,k) \alpha e^{-\alpha y} \dd y.
+	&= (1+ \smallO{1}) \frac{1}{k_n^2 \pmf(k_n)} \int_{\Kcal_C(k_n)} \Exp{T_\infty(y)} \rho(y,k) \alpha e^{-\alpha y} \dd y.
 \end{align*}
@@
 \[
-	c_{\text{box}}(p) = \frac{1}{\binom{\Dbox(p)}{2}} \sum_{p_1, p_2 \in \Pcal \setminus p}^{\ne} T_{\text{box}}(p,p_1,p_2)
+	c_{\text{box}}(p) = \frac{1}{\binom{\Dbox(p)}{2}} \sum_{p_1, p_2 \in \Pcal \setminus p, \atop \text{distinct}} T_{\text{box}}(p,p_1,p_2)
 	= \frac{T_{\text{box}}(p)}{\binom{\Dbox(p)}{2}}.
 \]
-By the Campbell-Mecje formula
+By the Campbell-Mecke formula
 \begin{align*}
@@
 \[
-	\Exp{N_{\text{box}}(k_n)} = (1+\smallO{1}) n p_{k_n}
+	\Exp{N_{\text{box}}(k_n)} = (1+\smallO{1}) n \pmf(k_n)
 \]
@@
 \[
-	\Exp{c^\ast(k_n; \Gbox)} = (1 + \smallO{1}) \frac{1}{k_n^2 p_{k_n}} \int_{\Kcal_C(k_n)} 
+	\Exp{c^\ast(k_n; \Gbox)} = (1 + \smallO{1}) \frac{1}{k_n^2 \pmf(k_n)} \int_{\Kcal_C(k_n)} 
 		\Exp{T_{\text{box}}(y)} \rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y.
@@
 %	\rho(y,k) \alpha e^{-\alpha y} \, d y \right|
-%	= \smallO{s(k_n)p_{k_n}k_n^2},
+%	= \smallO{s(k_n)\pmf(k_n)k_n^2},
 %\end{equation}
@@
 \[
-	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus \{p_0\}}^{\ne} 
+	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus \{p_0\}, \atop \text{distinct}}
 		\widetilde{T}_{\text{box}}(p_0,p_1,p_2).
@@
 	T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)
-	= \sum_{p_1, p_2 \in \Pcal \setminus \{p_0\}}^{\ne} \ind{p_1 \in \BallPon{p_0}} 
+	= \sum_{p_1, p_2 \in \Pcal \setminus \{p_0\}, \atop \text{distinct}} \ind{p_1 \in \BallPon{p_0}} 
 			\ind{p_2 \in \mathcal{T}(p_0, p_1)}.
@@
 	&= \left|T_{\mathrm{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right| 
-		+ \sum_{p_1, p_2 \in \Pcal \cap \Rcal^\prime}^{\ne} T_{\infty}(p_0,p_1,p_2).
+		+ \sum_{p_1, p_2 \in \Pcal \cap \Rcal^\prime, \atop \text{distinct}} T_{\infty}(p_0,p_1,p_2).
 \end{align*}
@@
 \begin{align*}
-	\Exp{c^\ast(k_n;\Gbox)} &= (1 + \smallO{1}) \frac{1}{p_{k_n}} \int_{\Kcal_{C}(k_n)} P(y)
+	\Exp{c^\ast(k_n;\Gbox)} &= (1 + \smallO{1}) \frac{1}{\pmf(k_n)} \int_{\Kcal_{C}(k_n)} P(y)
 		\rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y \\
-	&\hspace{10pt}+ \smallO{s(k_n)}	\frac{1}{p_{k_n}} \int_{\Kcal_{C}(k_n)} P(y)
+	&\hspace{10pt}+ \smallO{s(k_n)}	\frac{1}{\pmf(k_n)} \int_{\Kcal_{C}(k_n)} P(y)
 			\rho_{\mathrm{box}}(y,k_n) \alpha e^{-\alpha y} \dd y.
 \end{align*}
-By Lemma~\ref{lem:degree_integral} the integral in the second term is $(1+\smallO{1}) p_{k_n}$ and thus the second term is $\smallO{s(k_n)} = \smallO{\gamma(k_n)}$.
+By Lemma~\ref{lem:degree_integral} the integral in the second term is $(1+\smallO{1}) \pmf(k_n)$ and thus the second term is $\smallO{s(k_n)} = \smallO{\gamma(k_n)}$.
 Hence it remain to prove that the first term is $(1+\smallO{1}) \gamma(y)$.
@@
 %		\int_{0}^\infty \rho(y_0,k_n) e^{-\alpha y_0} \dd y_0\\
-%	&= \bigO{1} \left(\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)} \right) p_{k_n} = \smallO{s(k_n) p_{k_n} k_n^2},
+%	&= \bigO{1} \left(\log(k_n) n^{-(2\alpha - 1)} + k_n^2 n^{-(4\alpha - 2)} \right) \pmf(k_n) = \smallO{s(k_n) \pmf(k_n) k_n^2},
 %\end{align*}
@@
 %\[
-%	\int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y = p_{k_n} \gamma(k_n)
+%	\int_0^\infty P(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y = \pmf(k_n) \gamma(k_n)
 %	= \bigT{k_n^{-(2\alpha + 1)} s(k_n)}.
@@
 We observe that $\mathcal{T}(p,p^\prime) \ne \emptyset$ because the right boundary of the ball $\BallPon{p^\prime}$ exits the right boundary of the box $\Rcal$ and then, since we identified the boundaries, continues from the left so that $\BallPon{p^\prime}$ covers part of the ball $\BallPon{p}$ which would not be covered in the infinite limit model.
+
+%Note that $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$ correspond to, respectively, $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ considered in Section~\ref{ssec:missing_triangles}.
+The derivation of $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ is done in a similar manner and we omit the details here.
 

### 2020-03-10 hyperbolic_degrees.tex
merging with tobias edits

@@
 	&= \int_0^{R} \int_{-e^{\frac{y+y^\prime}{2}}}^{e^{\frac{y+y^\prime}{2}}} 
-		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
+		f(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
 	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{R} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime\\
@@
 	&= \int_0^{h(y)} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
-		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime
+		\ind{|x^\prime| \le e^{\frac{y+y^\prime}{2}}} f(x^\prime,y^\prime) \, dx^\prime \, dy^\prime
 		+ \int_{h(y)}^{R} \int_{-\frac{\pi}{2}e^{\frac{R}{2}}}^{\frac{\pi}{2}e^{\frac{R}{2}}} 
-		f_{\alpha,\nu}(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
+		f(x^\prime,y^\prime) \, dx^\prime \, dy^\prime\\
 	&= \frac{2 \alpha \nu}{\pi} e^{\frac{y}{2}} \int_0^{h(y)} e^{-(\alpha - \frac{1}{2})y^\prime} \, dy^\prime
@@
 		0 &\mbox{otherwise}
-	\end{cases}\\
+	\end{cases} \label{eq:def_left_boundary_Bp} \\ 
 	b_p^+(z) &= \begin{cases}
@@
 	&\int_\Rcal \cdots \int_\Rcal \varphi(\{p_1,\dots,p_r \}, k_n ;p_1,\dots,p_r) 
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r \\
-	&= (1+o(1))\left(\int_\Rcal  \varphi(\{p_1\}, k_n ;p_1) f(x,y) \dd x \dd y\right)^r .
+		 \dd \mu(p_1) \cdots \dd \mu(p_r) \\
+	&= (1+o(1))\left(\int_\Rcal  \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p)\right)^r .
 	\end{align*}
@@
 \begin{align*}
-	\int_A \Pee(D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n) f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r  
-	= O\left(n^r k_n^{-C}\right).
+	\int_A \Pee(D_{\GPo}(p_1)=\dots=D_{\GPo}(p_r)=k_n) \dd \mu(p_1) \cdots \dd \mu(p_r)	= O\left(n^r k_n^{-C}\right).
 \end{align*}
@@
 \begin{align*}
-	\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x,y) \dd x \dd y 
-	&= (1+\smallO{1}) \int_\Rcal  \varphi(\{p_1\}, k_n ;p_1) f(x,y) \dd x \dd y\\
+	\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1) 
+	&= (1+\smallO{1}) \int_\Rcal  \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1) \\
 	&= (1+\smallO{1}) 2\alpha \xi^{2\alpha} n k_n^{-(2\alpha + 1)} \numberthis \label{eq:integration_average_degree_stripe}
@@
 	&\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r \}, k_n ;p_1,\dots,p_r) 
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r \\
-	&= (1+o(1))\left(\int_{\stripknc}  \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r.
+		\dd \mu(p_1)\cdots \dd \mu(p_r) \\
+	&= (1+o(1))\left(\int_{\stripknc}  \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1) \right)^r.
 \end{align*}
@@
 	&\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_r,y_r)\dd x_r \dd y_r\\
-	&= (1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r .
+		\dd \mu(p_1) \cdots \dd \mu(p_r)\\
+	&= (1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1)\right)^r .
 \end{align*}
@@
 	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_{r+1}\}, k_n ;p_1,\dots,p_s)
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
+		\dd \mu(p_1) \cdots \dd \mu(p_{r+1})\\
 	&\leq \int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}.
+		\dd \mu(p_1) \cdots \dd \mu(p_{r+1}).
 \end{align*}
@@
 	&\int_{\{(x_{r+1},y_{r+1})\in\stripknc: x_{r+1}\in I_n\}} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s) 
-		f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1} \\
+		\dd \mu(p_{r+1}) \\
 	&= \int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \int_{I_n} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)\frac{\alpha \nu}{\pi} e^{-\alpha y_{r+1}} dx_{r+1}dy_{r+1} \\
@@
 \begin{align*}
-\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} e^{-\alpha y_{r+1}}dy_{r+1} \leq \int_{y_{k_n,c}^-}^\infty e^{-\alpha y_{r+1}}dy_{r+1} = \bigO{e^{-\alpha y_{k_n,c}^-}} = \bigO{\left( \frac{k_n-c\sqrt{k_n\ln k_n}}{\xi}\right)^{-2\alpha}} = \bigO{k_n^{-2\alpha}}.
+	\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} e^{-\alpha y_{r+1}}dy_{r+1} 
+	\leq \int_{y_{k_n,c}^-}^\infty e^{-\alpha y_{r+1}}dy_{r+1} 
+	= \bigO{e^{-\alpha y_{k_n,c}^-}} = \bigO{\left( \frac{k_n-c\sqrt{k_n\ln k_n}}{\xi}\right)^{-2\alpha}} 
+	= \bigO{k_n^{-2\alpha}}.
 \end{align*}
@@
 	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
+		\dd \mu(p_1) \cdots \dd \mu(p_{r+1})\\
 	&\leq \bigO{k_n^{1+\epsilon} k_n^{-2\alpha}}\int_{\stripknc} \cdots \int_{\stripknc} 
-		\varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s) f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}.
+		\varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s) \dd \mu(p_1) \cdots \dd \mu(p_{r}).
 \end{align*}
@@
 \begin{align}\label{eq:indhyp}
-	\bigO{k_n^{1+\epsilon-2\alpha}}\left(\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r .
+	\bigO{k_n^{1+\epsilon-2\alpha}}\left(\int_{\stripknc} \varphi(\{p_1\};p_1) \dd \mu(p_1) \right)^r .
 \end{align}
@@
 \begin{align*}
-\int_{\stripknc} \varphi(\{p_1\};p_1) f(x_1,y_1) \dd x_1 \dd y_1 = \bigT{n k_n^{-(2\alpha+1)}}.
+\int_{\stripknc} \varphi(\{p_1\};p_1) \dd \mu(p_1) = \bigT{n k_n^{-(2\alpha+1)}}.
 \end{align*}
@@
 	&\int \int_{\Fcal_\epsilon(k_n)^c} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
+		\dd \mu(p_1) \cdots \dd \mu(p_{r+1})\\
 	&=\smallO{\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)\mu_n(dp_1)}
-		\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1\right)^r  \\
-	&=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)f(x_1,y_1) \dd x_1 \dd y_1\right)^{r+1}}.
+		\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1) \right)^r  \\
+	&=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1)\right)^{r+1}}.
 \end{align*}
@@
 	&\int \int_{\Fcal_\epsilon(k_n)} \varphi(\{p_1,\dots,p_{r+1}\}, k_n ;p_1,\dots,p_s) 
-		 f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
+		 \dd \mu(p_1) \cdots \dd \mu(p_{r+1})\\
 	&=(1+o(1))\int \int_{\Fcal_\epsilon(k_n)} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s) 
-		\varphi(\{p_{r+1}\};p_1,\dots,p_s) f(x_1,y_1) \dd x_1 \dd y_1 \cdots \\
-	&\hspace{10pt} \times f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1}\\
+		\varphi(\{p_{r+1}\};p_1,\dots,p_s) \dd \mu(p_1) \cdots \dd \mu(p_{r+1}) \\
 	&\hspace{10pt}+\bigO{k_n^{-C}}\int \int_{\Fcal_\epsilon(k_n)} 
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1} =:M+E.
+		\dd \mu(p_1) \cdots \dd \mu(p_{r+1}) =:M+E.
 \end{align*}
@@
 	&\hspace{15pt} \times \int_{\stripknc} \cdots \int_{\stripknc} 
-		\varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}\\
+		\varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s) \dd \mu(p_1) \cdots \dd \mu(p_{r})\\
 	&=(1+o(1))n\int_{y_{k_n,c}^-}^{y_{k_n,c}^+} \varphi(\{p_{r+1}\}, k_n ;p_1,\dots,p_s)\alpha e^{-\alpha y_{r+1}}dy_{r+1}\\
 	&\hspace{15pt} \times \int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\};p_1,\dots,p_s)
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}\\
+		\dd \mu(p_1) \cdots \dd \mu(p_{r})\\
 	&=(1+o(1))\int_{\stripknc} \varphi(\{p_{r+1}\}, k_n ;p_1,\dots,p_s)\mu_n(dp_1)\\
 	&\hspace{15pt} \times\int_{\stripknc} \cdots \int_{\stripknc} \varphi(\{p_1,\dots,p_r\}, k_n ;p_1,\dots,p_s)
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r}.
+		\dd \mu(p_1) \cdots \dd \mu(p_{r}).
 \end{align*}
@@
 \begin{align*}
-M&=(1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1 \right)^{r+1}.
+M&=(1+o(1))\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1) \right)^{r+1}.
 \end{align*}
@@
 \begin{align*}
-	E=\bigO{k_n^{-C}}\int \int_{\Fcal_\epsilon(k_n)} 
-	f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r+1},y_{r+1})\dd x_{r+1} \dd y_{r+1} 
-	= \bigO{k_n^{-C}}(1+o(1))n^{r+1}.
+	E=\bigO{k_n^{-C}}\int \int_{\Fcal_\epsilon(k_n)} \dd \mu(p_1) \cdots \dd \mu(p_{r+1}) = \bigO{k_n^{-C}}(1+o(1))n^{r+1}.
 \end{align*}
@@
 \begin{align*}
-\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) f(x_1,y_1) \dd x_1 \dd y_1 = \bigT{n k_n^{-(2\alpha+1)}},
+\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1) = \bigT{n k_n^{-(2\alpha+1)}},
 \end{align*}
@@
 \begin{align*}
-\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)f(x_1,y_1) \dd x_1 \dd y_1\right)^{r+1} 
+\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1) \right)^{r+1} 
 = \bigT{n^{r+1}k_n^{-r(2\alpha+1)}}.
@@
 \begin{align*}
-E = \bigO{n^{r+1}k_n^{-C}}=\smallO{n^{r+1}k_n^{-r(2\alpha+1)}}=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1)\mu_n(dp_1)\right)^{r+1}}.
+E = \bigO{n^{r+1}k_n^{-C}}=\smallO{n^{r+1}k_n^{-r(2\alpha+1)}}=\smallO{\left(\int_{\stripknc} \varphi(\{p_1\}, k_n ;p_1) \dd \mu(p_1)\right)^{r+1}}.
 \end{align*}
@@
 	&=\frac{1}{r!} \int_\Rcal \cdots \int_\Rcal \varphi_{\Po}(\{p_1,\dots,p_r\},p_1,\dots,p_r)
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r},
+		\dd \mu(p_1) \cdots \dd \mu(p_{r}),
 \end{align*}
@@
 	\Exp{N_{\Po}(k_n)} = \int_\Rcal \varphi_{\Po}(\{p_1\}, k_n ; p_1) f(x_1,y_1) \dd x_1 \dd y_1,
+%=======
+%	\Exp{N_{\Po}(k_n)} = \int_\Rcal \phi_{\Po}(\{p_1\}, k_n ; p_1) \dd \mu(p_1),
+%>>>>>>> Stashed changes
 \]
@@
 \[
-	\frac{1}{r!}(\Exp{N_{\Po}(k_n)})^r = \frac{1}{r!}\left(\int_\Rcal \phi_{\Po}(\{p_1\}, k_n; p_1) f(x_1,y_1) \dd x_1 \dd y_1,\right)^r.
+	\frac{1}{r!}(\Exp{N_{\Po}(k_n)})^r = \frac{1}{r!}\left(\int_\Rcal \phi_{\Po}(\{p_1\}, k_n; p_1) \dd \mu(p_1)\right)^r.
 \]
@@
 \begin{align*}
-	&\hspace{-20pt}\Exp{ { N_{\Po}(k_n) \choose r}} \\
+	\Exp{ { N_{\Po}(k_n) \choose r}} 
 	&= \frac{1}{r!} \int_\Rcal \cdots \int_\Rcal 
 		\varphi_{\Po}(\{p_1,\dots,p_r\}, k_n; p_1,\dots,p_r) 
-		f(x_1,y_1) \dd x_1 \dd y_1 \cdots f(x_{r},y_{r})\dd x_{r} \dd y_{r} \\
+		\dd \mu(p_1) \cdots \dd \mu(p_{r}) \\
 	&= (1+o(1))\frac{1}{r!}\left(\int_\Rcal \varphi_{\Po}(\{p_1\}, k_n;p_1) f(x_1,y_1) \dd x_1 \dd y_1 \right)^r \\
@@
 	&\hspace{-30pt}\sum_{i = 1}^n \1_{\left\{u_i \in V_n(k_n) \Delta V_{\Po}(k_n)\right\}}\\
-	&= \sum_{i = 1}^n \1_{\left\{d_n(u_i) = k_n, D_{\Po}(u_i) > k_n\right\}}
-		+ \sum_{i = 1}^n \1_{\left\{d_n(u_i) < k_n, D_{\Po}(u_i) = k_n\right\}}.
+	&= \sum_{i = 1}^n \1_{\left\{D_n(u_i) = k_n, D_{\Po}(u_i) > k_n\right\}}
+		+ \sum_{i = 1}^n \1_{\left\{D_n(u_i) < k_n, D_{\Po}(u_i) = k_n\right\}}.
 \end{align*}

### 2020-03-10 proofs_finite_k.tex
merging with tobias edits

@@
 \subsection{Clustering function for fixed $k$, proving Theorem~\ref{thm:mainkfixed}}
+%=======
+%\subsection{Clustering function, proving Theorem~\ref{thm:mainkfixed}}
+%In this subsection, we want to show that the clustering function of the KPKVB model $c(k; G(n;\alpha,\nu)) \xrightarrow{\Pee} \gamma(k)$ for any fixed $k$.
+The key idea is that for the poissonized KPKVB model the coupling with the box model is guaranteed to be exact (in the sense that it also preserves edges) for all vertices up to height $H = \frac{R}{4}$ (which is all we need to show the convergence of the clustering function for constant $k$).
+%>>>>>>> Stashed changes
 
@@
 %clustering coefficient of the typical point in the infinite limit model $\Ginf$ conditioned on the typical point having degree $k$.
+
+%=======
+%We will encounter the following models: we will start with the KPKVB model $G_n = G(n;\alpha,\nu)$, then the Poissonized KPKVB model $\GPo  = G_{Po}(n;\alpha,\nu)$, moving to the truncated Poissonized KPKVB model $\GPoH$ which is the subgraph of $\GPo$ induced on all vertices with height at most $H$ resp.
+radial coordinate at least $R-H$, then the coupling will bring us to the truncated box model $\GboxH$ which is the subgraph of the box model $G_{box}$ induced by all vertices with height at most $H$.
+%>>>>>>> Stashed changes
 
@@
 
+%=======
+%\subsubsection{Deriving the limit integral expression}
+%\begin{lemma}\label{lem:lim}
+%Let $\alpha > \frac{1}{2}$, $\nu>0$ and $k\geq 2$ be fixed. Then
+%$$c(k;\GboxH)\xrightarrow[n\rightarrow\infty]{\Pee}\gamma(k).$$
+%\end{lemma}
+%%\begin{proof}
+%%We will show that $\E c(k;G_{n,Po,H}) \rightarrow \gamma(k)$ as $n\rightarrow\infty$ and $Var(c(k;G_{n,Po,H})) \rightarrow  0$.
+From there, the claim will follow by Chebychev's inequality: Let $\epsilon>0$, then $$\Pee(|c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H})|\geq \epsilon)\leq \frac{Var(c(k;G_{n,Po,H}))}{\epsilon^2} = o(1),$$
+%%i.e.
+$c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H}) \xrightarrow[n\rightarrow\infty]{\Pee} 0$, hence also $c(k;G_{n,Po,H})-\gamma(k) = c(k;G_{n,Po,H})-\E c(k;G_{n,Po,H})+\E c(k;G_{n,Po,H})-\gamma(k) \xrightarrow[n\rightarrow\infty]{\Pee} 0$.
+%%\end{proof}
+%
+%Let $\Rcal_H = \Rcal([0,H])$ denote the truncated box.
+%For a point $p \in H$ corresponding to a vertex $v \in V=V(\GboxH)$, let 
+%\[
+%	h(V,p) = {k \choose 2}^{-1} \sum_{p_1,p_2 \in \BallPon{p}}^{\ne} \1_{\{((p_1, p_2) \in E(\GboxH)\}} \1_{\{ D_{\GboxH}(v)=k\}}.
+%\]
+%Let $X = \frac{1}{n}\sum_{p \in V \cap \Pcal} h(V(G_{box,H}),p)$.
+Let $Z = \frac{N_{box,H}(k)}{n} = \frac{1}{n}\sum_{p \in V \cap \Pcal} \1_{\{D_{\GboxH}(v)=k\}}$.
+Then we have that $c(k;\GboxH) = \frac{X}{Z}$.
+We will show separately that numerator $X$ and denominator $Z$ converge in probability (where the limit of $Z$ is a positive constant).
+From this, the claim of the lemma will follow as convergence in probability is closed under taking quotients.
+%
+%
+%
+%By the Campbell-Mecke formula, we have
+%\begin{align*}
+%\Exp{ X} = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) f(x,y) \dd x \dd y = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy.
+%\end{align*}
+%Then, we condition on the additional vertex $(0,y) \in \Rcal_H$ having degree $k$,
+%\begin{align*}
+%\Exp{ X} = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy.
+%\end{align*}
+%We observe that for $H \rightarrow \infty$, the integrand converges point-wise for $y \in (0,\infty)$ to $P(y)\rho(y,k)\alpha e^{-\alpha y}$ and is always bounded by the integrable function $\alpha e^{-\alpha y}$.
+%Therefore, by the theorem of dominated convergence, as $H \rightarrow \infty$,
+%\begin{align*}
+%\Exp{X} \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
+%\end{align*}
+%Note that for $X^2$, the summation can be split into off-diagonal (with $v_1 \not = v_2$) and diagonal (with $v_1=v_2$) terms, i.e. write $X^2 = \frac{1}{n^2}(Y_1+Y_2)$ where 
+%\[
+%	Y_1 = \sum_{p_1, p_1 \in V(G_{box,H})}^{\ne} h(V(G_{box,H}),p_1)h(V(G_{box,H}),p_2),
+%\] 
+%and $Y_2 = \sum_{p_1 \in V(G_{box,H})} h(V(G_{box,H}),p_1)^2$. As $h \leq 1$, $Y_2 \leq n X\leq n$ and so, $\E Y_2 \leq n$, we have by the Campbell-Mecke formula,
+%\begin{align*}
+%\Exp{Y_1} = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),p_1)h(V(G_{box,H}),p_2)] f(x_1,y_1) f(x_2,y_2) \dd x_1 \dd y_2 \dd x_2 \dd y_2.
+%\end{align*}
+%If $v_1=(x_1,y_1)$ and $v_2=(x_2,y_2)$ have horizontal distance $|x_1-x_2|>2e^H$, their neighbourhood balls are disjoint w.r.t.
+the connection rule of the truncated box model $\GboxH$.
+To see this, assume that $v_3=(x_3,y_3)$ is adjacent to both $v_1$ and $v_2$.
+Then $|x_1-x_3|\leq e^{\frac{1}{2}(y_1+y_3)}$ and $|x_2-x_3|\leq e^{\frac{1}{2}(y_2+y_3)}$.
+As $y_1, y_2, y_3 \leq H$, it follows that $|x_1-x_3| \leq e^H$ and $|x_2-x_3|\leq e^H$, which implies that $|x_1-x_2| \leq |x_1-x_3|+|x_2-x_3|\leq 2e^H$, contradiction.
+%
+%Due to the disjointedness of the neighbourhood balls and the properties of the Poisson process $h(V,v_1)$ and $h(V,v_2)$ are independent.
+The horizontal distance is uniform in $[0,\frac{\pi n}{2\nu}]$.
+Therefore, the probability that two vertices have horizontal distance $\leq 2e^H$ is $\leq \frac{4\nu e^H}{\pi n} = o(1)$.
+Writing $d_H$ for the horizontal distance, we can continue the calculation of the second moment,
+%\begin{align*}
+%\Exp{ Y_1} &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)\\
+%&\qquad+\int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|\leq2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
+%&= (1+o(1))\int_{} \int_{\Rcal_H\times \Rcal_H} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
+%&= (1+o(1)) (n\E X)^2.
+%\end{align*}
+%It follows that $\Exp{ X^2} = (1+o(1))\Exp{ X}^2$, which implies $Var(X) \rightarrow 0$ using that $\Exp{ X}$ tends to a constant (see above). We conclude
+%\[
+%	X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
+%\]
+%In a similar way, by the Campbell-Mecke formula,
+%\begin{align*}
+%\Exp{Z} =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy.
+%\end{align*}
+%By the theorem of dominated convergence, it follows that
+%\begin{align*}
+%\Exp{ Z} \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
+%\end{align*}
+%The statement that $Var(Z) \rightarrow 0$ follows by the same steps as for $X$, just using $h(V,v) = \1_{\{D_{\GboxH}(v)=k\}}$ instead. Hence,
+%\begin{align*}
+%\Exp{ Z} \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
+%\end{align*}
+%Finally note that 
+%\begin{align*}
+%\gamma(k) = \frac{\int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy}{\int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy}.
+%\end{align*}
+%
+%\subsubsection{Putting everything together}
+%>>>>>>> Stashed changes
 \begin{proofof}{Theorem~\ref{thm:mainkfixed}}

### 2020-03-10 clustering_infinite_model.tex
merging with tobias edits
Updates from Overleaf

@@
 
-As alluded to earlier, we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of the (poissonized) KPKVB random graph 
+As alluded to earlier, we plan to make use of the Campbell-Mecke formula for comparing the clustering coefficient and function of the (Poissonized) KPKVB random graph 
 with certain quantities associated with $\Ginf$.
@@
 
-\begin{proof}[Proof of Lemma~\ref{lem:triangle_prob_y_coordinates}]
+\begin{proofof}{Lemma~\ref{lem:triangle_prob_y_coordinates}}
 Let $y_i >0$ and $z_i = e^{-y_i/2}$, $i=0,1,2$.
@@
 The expression for $P(y_0,y_1,y_2)$ then follows from~\eqref{eq:symmetry_relation_triangle_prob}.
-\end{proof}
+\end{proofof}
 
@@
 	\end{align*}
-	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
+	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dilogarithm function.
 \end{lemma}

### 2020-03-10 hyperbolic_degrees.tex
Updates from Overleaf

--- 2020-03-10 hyperbolic_degrees.tex
@@
 \begin{lemma}[First moment of number of degree $k$ vertices]\label{lem:expnnkn}
-Let $N_{Po}(k)$ and $\Nbox(k)$ denote the number of vertices with degree $k$ vertices in the poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, respectively.
+Let $N_{Po}(k)$ and $\Nbox(k)$ denote the number of vertices with degree $k$ vertices in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, respectively.
 Consider a sequence of integers $k_n\rightarrow\infty$ with $0 \leq k_n \leq n-1$.	If $k_n = O\left(n^{\frac{1}{2\alpha+1}}\right)$, then as $n \to \infty$,
@@
 
-First we observe that as the poissonized KPKVB model $\GPo$ has the same intensity measure as the original KPKVB model with a fixed number $n$ of points, the expected degree of a vertex of the KPKVB model with radial coordinate $r=R-y$ is given by $\mu_{\Po}(y)$ and hence,
+First we observe that as the Poissonized KPKVB model $\GPo$ has the same intensity measure as the original KPKVB model with a fixed number $n$ of points, the expected degree of a vertex of the KPKVB model with radial coordinate $r=R-y$ is given by $\mu_{\Po}(y)$ and hence,
 \[

### 2020-03-10 introduction.tex
Updates from Overleaf

@@
 As mentioned, its nodes are situated in the hyperbolic plane $\Haa$, which is a surface with constant Gaussian curvature $-1$.
-This surface has several convenient representations (i.e.~coordinate maps), such as the Poincar\'e halfplane model, the Poincar\'e disk model and the Klein disk model.
+This surface has several convenient representations (i.e.~coordinate maps), such as the Poincar\'e half-plane model, the Poincar\'e disk model and the Klein disk model.
 A gentle introduction to Gaussian curvature, hyperbolic geometry and these representations of the hyperbolic plane can be found in~\cite{stillwell2012geometry}.
@@
 
-In another paper of the first and third authors with Bode~\cite{bode2016probability} it was shown that $\alpha=1/2$ is the threshold for connectivity: for $\alpha < 1/2$ the graph is a.a.s.~connected, for $\alpha>1/2$ the graph is a.a.s.~disconnected and when $\alpha=1/2$ the probability of being connected tends to a continuous, nondecreasing function of $\nu$ which is identically one for $\nu \geq \pi$ and strictly less than one for $\nu < \pi$.
+In another paper of the first and third authors with Bode~\cite{bode2016probability} it was shown that $\alpha=1/2$ is the threshold for connectivity: for $\alpha < 1/2$ the graph is a.a.s.~connected, for $\alpha>1/2$ the graph is a.a.s.~disconnected and when $\alpha=1/2$ the probability of being connected tends to a continuous, non-decreasing function of $\nu$ which is identically one for $\nu \geq \pi$ and strictly less than one for $\nu < \pi$.
 Friedrich and Krohmer~\cite{blasius2018cliques} studied the size of the largest clique as well as the number of cliques of a given size.
@@
 This depends on the parameter $\alpha$, and $\gamma(k)$ only scales with $k^{-1}$ when $\alpha > 3/4$, which corresponds to the exponent of the degree distribution exceeding $5/2$.
-So in particular our findings disprove the abovementioned conjecture of Krioukov et al.~\cite{krioukov2010hyperbolic}.
+So in particular our findings disprove the above-mentioned conjecture of Krioukov et al.~\cite{krioukov2010hyperbolic}.
 
@@
 \noindent
-A plot of $\gamma$ can be found in Figure~\ref{fig:gamma}.
+A plot of $\gamma$ can be found in Figure~\ref{fig:gamma}. The figure also shows the results of computer simulations that appear to be in agreement with our findings.
 
@@
     \caption{Plot of $\gamma$ for $\alpha$ varying from $0.5$ to $5$ on the horizontal axis and 
-    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gamma}}
+    for $\nu=\frac{1}{2}$ (blue), $\nu=1$ (purple), $\nu=2$ (green). Simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gamma}}
 \end{figure}
@@
 \noindent
-A plot of $\gamma(k)$ can be found in Figure~\ref{fig:gammak}. %
+A plot of $\gamma(k)$,  together with the results of computer experiments, can be found in Figure~\ref{fig:gammak}. %
 %
@@
     \caption{Plot $\gamma(k)$ for $k$ varying from 2 to 25 on the horizontal axis, for $\alpha=0.8$ and $\nu=\frac{1}{2}$ 
-    (blue), $\nu=1$ (purple), $\nu=2$ (green); simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
+    (blue), $\nu=1$ (purple), $\nu=2$ (green). Simulations (squares in corresponding colour) with $n=10000$ and $100$ repetitions.\label{fig:gammak}}
 \end{figure}%

### 2020-03-10 proofs_finite_k.tex
Updates from Overleaf

--- 2020-03-10 proofs_finite_k.tex
@@
 We will now show that the clustering function of the KPKVB model $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for a fixed $k$. 
-The key ideas are that the coupling of the poissonized KPKVB model with the box model is guaranteed to be exact 
+The key ideas are that the coupling of the Poissonized KPKVB model with the box model is guaranteed to be exact 
 (in the sense that it also preserves edges) for all vertices up to height $R/4$; and that when computing 
@@
 
-As $N\isd\Po(n)$, by Chebyschev's inequality, we have that $|N-n| < \eps n$ a.a.s.
+As $N\isd\Po(n)$, by Chebychev's inequality, we have that $|N-n| < \eps n$ a.a.s.
 So in particular, under our coupling we have $G_- \subseteq G_n, \GPo \subseteq G_+$ a.a.s. 
@@
 %Under the standard coupling of $G_n$ and $\GPo$, we have
-For every kixed $k\geq 2$, we have
+For every fixed $k\geq 2$, we have
 
@@
 Next, we turn attention to $X(X-1) = \sum_{u\neq v \in N_{\GboxH}(k)} c(v)c(u)$.
-Another application of Cambell-Mecke shows that
+Another application of Campbell-Mecke shows that
 
@@
 $\Var X = \Ee X(X-1) + \Ee X - \left(\Ee X\right)^2 = o\left( \left(\Ee X\right)^2 \right)$.
- By Chebyschev's inequality, we therefore have
+ By Chebychev's inequality, we therefore have
 
@@
 \noindent
-where the convergence in probability can be justified using Slutksy's theorem together 
+where the convergence in probability can be justified using Slutsky's theorem together 
 with the fact that $\sum_{k=0}^\infty \pmf(k) = 1$ (one convenient way to convince oneself that this is true, is to note that 

### 2020-03-10 proofs_infinite_k.tex

@@
 In this section we explain the challenges associated with each step and give a detailed overview of the structure for the proof of Theorem~\ref{thm:mainktoinfty} using intermediate results for each of the steps.
-To this end we define the scaling function
+We first define the scaling function
 \begin{equation}\label{eq:def_scaling_function}
@@
 \end{equation}
+
 Notice that the only difference between $c(k;G)$ and $c^\ast(k;G)$ is that we replace $N(k)$ by its expectation $\Exp{N(k)}$.
@@
 We start with an observation on the dependence between the degree of a point $p = (x,y)$ and its height $y$.
-
-%\subsection{Restricting the height for vertices with degree $k_n$}
+%=======
+%Notice that the only difference between $c(k;G)$ and $c^\ast(k;G)$ is that we replace $N_k$ by its expectation $\Exp{N_k}$.
+The advantage is that now, the only randomness is in the formation of triangles.
+In addition, note that since $\Exp{N_k} > 0$ a case distinction for $N_k$ is no longer needed for $c^\ast(k;G)$.
+It is however still relevant since we are eventually interested in $c(k;G)$.
+Following the notation convention, throughout the remainder of this paper we write $c^\ast(k; \GPo)$ and $c^\ast(k; \Gbox)$ to denote the modified local clustering function in $\GPo$ and $G_{\mathcal{P},n}(\alpha,\nu)$, respectively.
 %
-%In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a^-(k), a^+(k)]$, with
-%\[
-%	a^\pm(k) = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
-%\]
-%The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and Poisson random variables are well concentrated around their mean, i.e.
-around heights $y$ for which $\mu(y) \approx k$.
-Since $\mu(y) = \mu(\BallPo{y}) = \xi e^{y/2}$, this implies that integration with respect to $\rho(y,k)$ is concentrated around $y \approx 2\log(k/\xi)$.
-In the remainder of this paper we will often encounter integrands involving the function $\Prob{\Po(\mu_n(y)) = k_n} := \hat{\rho}_n(y,k_n)$, for some $\mu_n(y)$ which is asymptoticly equivalent to $\mu(y)$.
-In these cases we also want to be able to restrict our integration around those heights $y$ for which $y \approx 2\log(k_n/\xi)$.
-Such results are established in Section~\ref{sec:concentration_argument}.
-Moreover, we prove that if $\mu_n$ corresponds to either $\Mu{\BallHyp{y}}$ or $\Mu{\BallPon{y}}$, then for a certain classs of functions $h$
-%\[
-%	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y 
-%	= (1+\smallO{1}) \int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
-%\]
-%i.e. we may replace $\hat{\rho}_n(y,k_n)$ in the integrand with $\rho(y,k_n)$.
+%Figure~\ref{fig:overview_proof} shows a schematic overview of the proof of Theorem~\ref{thm:mainktoinfty} based on the different propositions described below, plus the sections in which theses propositions are proved.
+Observe that the order in which the intermediate results are proved is reversed with respect to the natural order of reasoning.
+This does not create any circular logic, since each intermediate result is independent of the others.
+We choose this order because results proved in the later stages are helpful to deal with error terms coming up in proofs at earlier stages and hence help streamline those proofs.
+Below we briefly describe each of the intermediate steps leading up to the proof of Theorem~\ref{thm:mainktoinfty}.
+We start with an observation on the dependence between the degree of a point $p = (x,y)$ and its height $y$.
+%>>>>>>> Stashed changes
 
@@
 The proof, found in Section~\ref{ssec:coupling_H_HP}, is based on a standard coupling between a Binomial Point Process and Poisson Point Process.
+%=======
+%We then establish that the modified local clustering function for KPKVB graphs $G_n$ behaves similarly to that in the $\GPo$.
+The proof, found in Section~\ref{ssec:coupling_H_HP}, is based on the standard coupling between a Binomial Point Process and Poisson Point Process which we already encountered twice, once for the number of nodes with degree $k$ in Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson} and once for the proof of Lemma~\ref{lem:trunc}.
+%>>>>>>> Stashed changes
 
@@
 Together, the three results described so far imply that the difference between the clustering function for a KPKVB graph and the adjusted clustering function for the finite box graph $\Gbox$ converges to zero faster than the proposed scaling $\gamma(k_n)$ in Theorem~\ref{thm:mainktoinfty}.
-Hence, to prove this theorem it is enough to prove it for $c^\ast(k; \Gbox)$.
+Hence, it is enough to prove the result for $c^\ast(k; \Gbox)$.
 
@@
 For the proof, we first identify the specific range of heights that give the main contribution to the triangle count, showing that the triangles coming from nodes with heights outside this range is of smaller order.
-Then we prove a concentration result for the main term, by carefully analyzing the joint neighbourhoods of two nodes whose heights fall into the identified range.
+Then we prove a concentration result for the main term, using that the neighbourhoods of two nodes whose $x$-coordinates are sufficiently separated can be considered to be disjoint (see Section~\ref{ssec:joint_degrees_GPo}).
 The full details are found in Section~\ref{sec:concentration_c_P_n}.
 
-Assuming this concentration result, we are left to compute expectation $\Exp{c^\ast(k_n; \Gbox)}$ and show that it is asymptotically equivalent to $\gamma(k_n)$ as $n \to \infty$.
+Assuming this concentration result, we are left to compute the expectation $\Exp{c^\ast(k_n; \Gbox)}$ and show that it is asymptotically equivalent to $\gamma(k_n)$ as $n \to \infty$.
 To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of $c^\ast(k;\Gbox)$ and $\gamma(k_n)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.

### 2020-03-10 transition.tex

@@
 \]
-Here we slightly abuse notation and write $\BallPo{y}$ for $\BallPo{(0,y)}$.
-We will adopt this notational convention throughout the remainder of this section, to keep notation concise.
-We also recall that $\Nbox(k)$ denotes the number of vertices with degree $k$ in $\Gbox$.
+Recall that, slightly abusing notation, we write $\BallPo{y}$ for $\BallPo{(0,y)}$ and that $\Nbox(k)$ denotes the number of vertices with degree $k$ in $\Gbox$.
 
@@
 Recall the definition of $y_{k,C}^\pm$ from~\eqref{eq:def_y_k_C} and the interval $\Kcal_{C}(k_n) = [y_{k_n,C}^-, y_{k_n,C}^+]$.
-Note that for any $y \in \Kcal_C(k_n)$ it holds that as
+Note that for any $y \in \Kcal_C(k_n)$ it holds that
 \begin{equation}\label{eq:def_K_C_set}
@@
 
-To analyze $T_{\text{box}}(y_0) - T_\infty(y_0)$ we first reiterate that the difference between the indicator $\ind{p_1 \in \BallPon{p}}$ in the finite box model and $\ind{p_1 \in \BallPo{p}}$ is that in $\Gbox$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2} e^{R/2}]$ and we stop at height $y = R$.
+To analyze the difference $\left|T_{\text{box}}(y) - T_\infty(y)\right|$ we first reiterate that the difference between the indicator $\ind{p_1 \in \BallPon{p}}$ in the finite box model and $\ind{p_1 \in \BallPo{p}}$ is that in $\Gbox$ we identified the boundaries of the interval $[-\frac{\pi}{2}e^{R/2}, \frac{\pi}{2} e^{R/2}]$ and we stop at height $y = R$.
 This induces a difference in triangle counts between both models.
@@
 
-The first key implication of Lemma~\ref{lem:clustering_error_T_term} is that the triangle count in the finite box model is equivalent to $k_n^2 P(y)$, where $P(y)$ is defined in [??].
+The first key implication of Lemma~\ref{lem:clustering_error_T_term} is that the triangle count in the finite box model is equivalent to $k_n^2 P(y)$, where $P(y)$ is defined by~\eqref{eq:def_Py}.
 
@@
 	\left|\Exp{T_{\text{box}}(p_0) - T_{\infty}(p_0)}\right|
-	&\le \Exp{\left|T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right|}\\
-	&\hspace{10pt}+ \int_{\Rcal^\prime}\int_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
-		\dd x_2 \dd y_2 \dd x_1 \dd y_1. 
+	&\le \Exp{\left|T_{\text{box}}(p_0) - \widetilde{T}_{\text{box}}(p_0)\right|}
+		+ \int_{\Rcal^\prime}\int_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) \dd \mu(p_1) \dd \mu(p_2). 
 \end{align*}
@@
 \begin{align*}
-	&\hspace{-30pt}\iint_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) f(x_1,y_1) f(x_2,y_2)
-		\dd x_2 \dd y_2 \dd x_1 \dd y_1\\
-	&\le \left(\int_{\Rcal^\prime} \ind{p_1 \in \BallPo{p_0}} f(x_1,y_1) \dd x_1 \dd y_1\right)^2
-		= \bigO{\left(e^{y/2} \int_{R}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}\\
+	\iint_{\Rcal^\prime} T_{\infty}(p_0,p_1,p_2) \dd \mu(p_1) \dd \mu(p_2)
+	&\le \left(\int_{\Rcal^\prime} \ind{p_1 \in \BallPo{p_0}} f(x_1,y_1) \dd x_1 \dd y_1\right)^2\\
+	&= \bigO{\left(e^{y/2} \int_{R}^\infty e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\right)^2}\\
 	&= \bigO{e^{y} e^{-(2\alpha-1)R}} = \bigO{e^y n^{-(4\alpha - 2)}}.
@@
 From the proof of Proposition~\ref{prop:convergence_average_clustering_P_n} we immediately obtain the following useful corollary, which will be used in Section~\ref{sec:concentration_c_P_n}.
+Recall from~\eqref{eq:def_stripe} that $\stripknc = \Rcal \cap (\R_+ \times [y_{k_n,C}^-, y_{k_n,C}^+])$.
 
@@
 \[
-	\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p_0)} f(x,y) \dd x \dd y
+	\int_{\stripknc} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p_0)} f(x,y) \dd x \dd y
 	= \bigT{n k_n^{-(2\alpha - 1)} s(k_n)}.
@@
 
-%Note that $\hat{y}_{\text{left}}(p,p^\prime)$ and $\hat{x}_{\text{left}}(p,p^\prime)$ correspond to, respectively, $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ considered in Section~\ref{ssec:missing_triangles}.
-The derivation of $\hat{y}_{\text{right}}(p,p^\prime)$ and $\hat{x}_{\text{right}}(p,p^\prime)$ is done in a similar manner and we omit the details here.
-
-To further analyze this, let us introduce some notation. For any $p = (x,y) \in \Rcal$ we will define the left and right boundary functions as, respectively,
-\begin{align}
-	b_p^-(z) &= \begin{cases}
-		2 \log\left(x-z\right) - y &\mbox{if }  -\frac{\pi}{2} e^{R/2} \le z \le x - e^{y/2}  \\
-		2\log\left(\pi e^{R/2} + x - z\right) - y 
-			&\mbox{if } x - e^{(y + R)/2} + \pi e^{R/2} \le z \le \frac{\pi}{2} e^{R/2}\\
-		0 &\mbox{otherwise}
-	\end{cases}\\
-	b_p^+(z) &= \begin{cases}
-		2 \log\left(z-x\right) - y &\mbox{if } x + e^{y/2} \le z \le \frac{\pi}{2} e^{R/2} \\
-		2\log\left(\pi e^{R/2} + z - x\right) - y 
-			&\mbox{if } -\frac{\pi}{2} e^{R/2} \le z \le x + e^{(y + R)/2} - \pi e^{R/2}\\
-		0 &\mbox{otherwise}
-	\end{cases}
-\end{align}
-Note that these functions describe the boundaries of the ball $\BallPon{p}$.
-In particular, $p^\prime = (x^\prime, y^\prime) \in \BallPon{p}$ if and only if $y^\prime \ge \min\left\{b_p^-(x^\prime), b_p^+(x^\prime)\right\}$.
-
-Since we have identified the left and right boundary of $\Rcal$ we can assume, without loss of generality that $x = 0$.
-Due to symmetry it is then enough to restrict the analysis to the case where $x^\prime > 0$.
-%\TM{ does this not depend on $p$? }\PvdH{I do not think so, because we can always take $p = (0,y)$ due to the invariance in the $x$-direction. I have updated the text to better reflect this.} 
-For this case there are two important points in the box $\Rcal$.
-These are the intersection between the left boundary of $p^\prime$ and the right boundary of $p^\prime$, as it continues from the left side of the box, and the left boundary of $p$.
-We denote by $(x^\ast(p^\prime), y^\ast(p^\prime))$ the intersection between the left and right boundary of $p^\prime$ and by $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$ the intersection between the left boundary of $p$ and the right boundary of $p^\prime$, see Figure \ref{fig:comparing_triangles_diff_intersections}.
-
-Let us derive the expressions for the coordinates of these two points, starting with $(x^\ast(p^\prime), y^\ast(p^\prime))$.
-The $x$-coordinate $x^\ast(p^\prime)$ is the solution to the equation $b_{p^\prime}^+(z) = b_{p^\prime}^-(z)$ for $-\frac{\pi}{2} e^{R/2} \le z \le x + e^{(y + R)/2} - \pi e^{R/2}$.
-This equation becomes
-\[
-	2\log\left(\pi e^{R/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x^\prime-z\right) - y^\prime,
-\]
-whose solution is $x^\ast(p^\prime) := x^\prime - \frac{\pi}{2} e^{R/2}$.
-Plugging this into either the left or right hand side of the above equation yields the $y$-coordinate $y^\ast(p^\prime) = 2\log\left(\frac{\pi}{2}e^{R/2}\right) - y^\prime$.
-In a similar way, the $x$-coordinate $\hat{x}(p,p^\prime)$ is the solution to the equation $b_{p^\prime}^+(z) = b_{p}^-(z)$ for $-\frac{\pi}{2} e^{R/2} \le z \le x + e^{(y + R)/2} - \pi e^{R/2}$, i.e.
-\[
-	2\log\left(\pi e^{R/2} + z - x^\prime\right) - y^\prime = 2 \log\left(x-z\right) - y.
-\] 
-This solution is $\frac{x^\prime - \pi e^{R/2}}{1 + e^{(y^\prime - y)/2}}$ and again $\hat{y}(p,p^\prime)$ is obtained by plugging the solution into either the left or right hand side of the equation, yielding $\hat{y}(p,p^\prime) = 2 \log\left(\frac{\pi e^{R/2} - x^\prime}{e^{y/2} + e^{y^\prime/2}}\right)$.
-
-To summarize we have:
-% After some simple algebra \TM{ I am not a big fan of writing "after some simple algebra" or similar.
-This is how errors can creep into your argument.
-Maybe we can just give the details?
-} we obtain the following expressions for the coordinates of these two points
+The point $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime))$ is the same as $(\hat{x}_{\mathrm{left}}, \hat{y}_{\mathrm{left}})$ from Section~\ref{ssec:joint_degrees_GPo}).
+Using the same approach as there we can compute the other two coordinates, $x^\ast(p^\prime)$ and $y^\ast(p^\prime)$.
+In total we have the following four expressions:
 \begin{align*}
@@
 The crucial observation is that $\mathcal{T}(p,p^\prime) = \emptyset$ as long as the point $(x^\ast(p^\prime), y^\ast(p^\prime))$ is above the left boundary of $p$.
-This happens exactly when $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$.
+This happens exactly when $y^\ast(p^\prime) > b_p^-(x^\ast(p^\prime))$, where $b_p^-(z)$ is defined in~\eqref{eq:def_left_boundary_Bp}.
 Therefore the boundary of this event is given by the equation $y^\ast(p^\prime) = b_p^-(x^\ast(p^\prime))$ which reads
@@
 \begin{equation}\label{eq:clustering_error_T_main}
-	\int_0^{R}\int_0^{I_n} \mu\left(\mathcal{T}(p,p_1)\right) f(x_1,y_1) 
-	\dd x_1 \dd y_1 = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
+	\int_0^{R}\int_0^{I_n} \mu\left(\mathcal{T}(p,p_1)\right) \dd \mu(p_1) = \bigO{y n^{-(2\alpha - 1)} + n^{-(2\alpha-1)} e^{y}}
 \end{equation}

### 2020-03-10 concentration_argument.tex

@@
 \end{equation}
-In particular, since $R-y$ is an increrasing function of $n$ uniformly on $0 < y < (1-\varepsilon)R$, there exists a $0 < \delta < 1$ such that $1/2 \le \Xi(y,y^\prime) < 2$ for all $y + y^\prime < R$ and $(1-\delta)(R-y) < y^\prime < R$ and $n$ large enough.
+In particular, since $R-y$ is an increasing function of $n$ uniformly on $0 < y < (1-\varepsilon)R$, there exists a $0 < \delta < 1$ such that $1/2 \le \Xi(y,y^\prime) < 2$ for all $y + y^\prime < R$ and $(1-\delta)(R-y) < y^\prime < R$ and $n$ large enough.
 
@@
 \end{align*}
-We will oroceed to bound the term inside the integral. For this we first note that for $0 \le y^\prime \le (1-\delta)(R-y)$,
+We will proceed to bound the term inside the integral. For this we first note that for $0 \le y^\prime \le (1-\delta)(R-y)$,
 \[

### 2020-03-11 concentration.tex
Edits by Tobias
merging with tobias edits
Updates from Overleaf
small corrections

@@
 \[
-	 T_{\text{box}}(k_n) = \sum_{p \in \Pcal} \ind{\Dbox(p) = k_n} \sum_({p_1, p_2) \in \Pcal \setminus \{p\}}^{\ne} 
+	 T_{\text{box}}(k_n) = \sum_{p \in \Pcal} \ind{\Dbox(p) = k_n} \sum_{(p_1, p_2) \in \Pcal \setminus \{p\}, \atop \text{distinct}} 
 	 \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPon{p_1}}
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:concentration_local_clustering_P_n}]
+\begin{proofof}{Proposition \ref{prop:concentration_local_clustering_P_n}}
 We bound the expectation as follows,
@@
 
-Since $\Exp{N_{\text{box}}(k_n)} = (1+\smallO{1}n p_{k_n}$ it follows that
+Since $\Exp{N_{\text{box}}(k_n)} = (1+\smallO{1}n \pmf(k_n)$ it follows that
 \[
 	\widetilde{c}_{\text{box}}(k_n) = \frac{\Exp{\widetilde{T}_{\text{box}}(k_n,C)}}{\binom{k_n}{2}\Exp{N_{\text{box}}(k_n)}}
-	= (1+\smallO{1}) \frac{\int_0^\infty P(y) \alpha e^{-\alpha y} \dd y}{p_{k_n}}
+	= (1+\smallO{1}) \frac{\int_0^\infty P(y) \alpha e^{-\alpha y} \dd y}{\pmf(k_n)}
 	= (1 + \smallO{1}) \gamma(k_n).
@@
 which finishes the proof.
-\end{proof}
+\end{proofof}
 
@@
 		\hspace{-3pt} \ind{\Dbox(p), \, \Dbox(p^\prime) = k_n} 
-		\sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in \Pcal_n}^{\ne} \hspace{-3pt}
+		\sum_{(p_1, p_2), (p_1^\prime, p_2^\prime) \in \Pcal_n, \atop \text{distinct}} \hspace{-3pt}
 		\widetilde{T}_{\Pcal}(p,p_1,p_2) \widetilde{T}_{\Pcal}(p^\prime, p_1^\prime, p_2^\prime),
@@
 \[
-	J_b(p,p^\prime) = \hspace{-10pt} \sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal_n 
-		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b}^{\ne}
+	J_b(p,p^\prime) = \hspace{-10pt} \sum_{{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal_n 
+		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b,} \atop \text{distinct}}
 		\hspace{-5pt} T_{\Pcal,n}(p,p_1,p_2) T_{\Pcal,n}(p^\prime, p_1^\prime, p_2^\prime),
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:concentration_tilde_T_P_n}]
+\begin{proofof}{Proposition \ref{prop:concentration_tilde_T_P_n}}
 
@@
 	&\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n} J_b(p,p^\prime)}\\
-	&= \Exp{\sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal_n 
-		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b}^{\ne}
+	&= \Exp{\sum_{{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal_n 
+		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = b,} \atop \text{distinct}}
 			\hspace{-7pt} \widetilde{D}_{\text{box}}(p,p^\prime, k_n-i,k_n- i^\prime) \,
@@
 	&\Exp{\ind{\Dbox(p) = k_n, \Dbox(p^\prime) = k_n} J_0(p,p^\prime)}\\
-	&= \Exp{\sum_{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal \setminus \{p,p^\prime\} 
-		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = 0}^{\ne}
+	&= \Exp{\sum_{{p_1, p_2, p_1^\prime, p_2^\prime \in \Pcal \setminus \{p,p^\prime\} 
+		\atop |\{p_1, p_2\} \cap \{p_1^\prime, p_2^\prime\}| = 0,} \atop \text{distinct}}
 		\hspace{-7pt} \widetilde{D}_{\text{box}}(p,p^\prime, k_n-i,k_n- i^\prime) \,
 		\widetilde{T}_{\text{box}}(p,p_1,p_2) \widetilde{T}_{\text{box}}(p^\prime, p_1^\prime, p_2^\prime)}\\
-	&= \Exp{D_{\text{box}}(p,p^\prime, k_n-j-2,k_n- j^\prime-2) \, \sum_{p_1,p_2 \in \Pcal \setminus p}^{\ne} 
+	&= \Exp{D_{\text{box}}(p,p^\prime, k_n-j-2,k_n- j^\prime-2) \, \sum_{p_1,p_2 \in \Pcal \setminus p, \atop \text{distinct}}
 		\widetilde{T}_{\text{box}}(p,p_1,p_2)
-		\sum_{p_1^\prime,p_2^\prime \in \Pcal \setminus p^\prime}^{\ne} 
+		\sum_{p_1^\prime,p_2^\prime \in \Pcal \setminus p^\prime, \atop \text{distinct}} 
 			\widetilde{T}_{\text{box}}(p^\prime,p_1^\prime,p_2^\prime)}\\
@@
 \[
-	J_{0,1} = \sum_{(p_1, p_2) \in \Pcal \setminus \{p\}}^{\ne} \widetilde{T}_{\text{box}}(p,p_1,p_2) 
+	J_{0,1} = \sum_{(p_1, p_2) \in \Pcal \setminus \{p\},\atop \text{distinct}} \widetilde{T}_{\text{box}}(p,p_1,p_2) 
 	\sum_{p_2^\prime \in \Pcal \setminus \{p^\prime, p_1\}} \widetilde{T}_{\text{box}}(p^\prime,p_1,p_2^\prime). 
@@
 
-\end{proof}
+\end{proofof}

### 2020-03-11 hyperbolic_degrees.tex
small corrections

@@
 where 
-\[
+\begin{equation}\label{eq:def_average_degree_Gbox_phi}
 	\phi_n(y) :=  \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)} \hspace{-3pt} e^{-(\alpha - \frac{1}{2})(R - y)}
 				+ \frac{\nu}{\xi}e^{-(\alpha - \frac{1}{2})R - \frac{y}{2}} - \frac{\nu}{\xi}\left(\frac{\pi}{2}\right)^{-2\alpha} e^{-(\alpha-\frac{1}{2})(R - y)}.
-\]
+\end{equation}
 Since $R - y \ge \varepsilon R$ we have that $|\phi_n(y)|$ is uniformly bounded by
@@
 
-\begin{proof}[Proof of Lemma~\ref{lem:factmoment}]
+\begin{proofof}{Lemma~\ref{lem:factmoment}}
 We give the proof for the Poissonized KPKVB model. The proof for the finite box model $\Gbox$ follows using similar arguments.
@@
 \end{align*}
-\end{proof}
+\end{proofof}
 
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:degrees_hyperbolic}]
+\begin{proofof}{Theorem~\ref{thm:degrees_hyperbolic}}
 
@@
 \end{enumerate}
-\end{proof}
+\end{proofof}

### 2020-03-11 preliminaries.tex
small corrections

@@
 Borel-measurable subset $S \subseteq \eR^2$ we have $\mu(S) = \int_S f(x,y) \dd x \dd y$.
+Using the notation $p = (x,y)$ for a point in $\R \times \R_+$ we shall write $\int_S h(p) \dd \mu(p)$ for the integral of $h$ over $S$ with respect to the intensity measure $\mu$, i.e.
+$\int_S h(p) \dd \mu(p) = \int_{S} h(x,y) f(x,y) \dd x \dd y$.
 
@@
 
-In particular, if $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$, we have the following Chernoff bound (c.f. \cite[Lemma 1.2]{penrose2003random})
+Let $\Po(\lambda)$ denote a Poisson random variable with mean $\lambda$. Then we have the following Chernoff bound (c.f. \cite[Lemma 1.2]{penrose2003random})
 \begin{equation}\label{eq:def_chernoff_bound_poisson}
@@
 Then for any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, it holds that
-\begin{equation}\label{eq:error_bound_int_rho_not_K}
+\begin{equation*}%\label{eq:error_bound_int_rho_not_K}
 	\int_0^\infty \hspace{-3pt} h(y) \Prob{\Po(\hat{\mu}(y)) = k_n} \alpha e^{-\alpha y} \dd y
 	\sim \int_{\Kcal_C(k_n)} \hspace{-8pt} h(y) \Prob{\Po(\hat{\mu}(y)) = k_n} \alpha e^{-\alpha y} \dd y,
-\end{equation}
+\end{equation*}
 as $n \to \infty$.

### 2020-03-11 proofs_infinite_k.tex
small corrections

@@
 We choose this order because results proved in the later stages are helpful to deal with error terms coming up in proofs at earlier stages and hence help streamline those proofs.
-Below briefly describe each of the intermediate steps leading up to the proof of Theorem~\ref{thm:mainktoinfty}.
-We start with an observation on the dependence between the degree of a point $p = (x,y)$ and its height $y$.
+Below we briefly describe each of the intermediate steps leading up to the proof of Theorem~\ref{thm:mainktoinfty}.
+
+%We start with an observation on the dependence between the degree of a point $p = (x,y)$ and its height $y$.
 %=======
@@
 
-\caption{Overview of the proof strategy for Theorem \ref{thm:local_clustering_hyperbolic}.
+\caption{Overview of the proof strategy for Theorem \ref{thm:mainktoinfty}.
 The left column denote the models in which the true hyperbolic balls are used while the right column contains the models that use an approximation of these.
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:mainktoinfty}]
+\begin{proofof}{Theorem~\ref{thm:mainktoinfty}}
 Note that the second of the theorem follows immediately from the first.
@@
 which establishes the first statement of the theorem and finishes the proof.  
-\end{proof}
+\end{proofof}

### 2020-03-11 transition.tex
small corrections

@@
 
-\begin{proof}[Proof of Proposition~\ref{prop:convergence_average_clustering_P_n}]
+\begin{proofof}{Proposition~\ref{prop:convergence_average_clustering_P_n}}
 First, by Lemma~\ref{lem:appox_triangle_count_box} and~\eqref{eq:alt_c_ast_kn} we have
@@
 %%\end{align*}
-\end{proof}
+\end{proofof}
 
@@
 \caption{Example for a given $p$ of the boundary function $x^\prime \mapsto b^\ast_p(x^\prime)$, given by the red curve, which determines whether $\mathcal{T}(p,p^\prime) = \emptyset$.
-We see that when $y^\prime = b^\ast_p(x^\prime)$ then $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime)) = (x^\ast(p^\prime), y^\ast(\prime))$.}
+We see that when $y^\prime = b^\ast_p(x^\prime)$ then $(\hat{x}(p,p^\prime), \hat{y}(p,p^\prime)) = (x^\ast(p^\prime), y^\ast(p^\prime))$.}
 \label{fig:comparing_triangles_diff_analysis}
@@
 
-\begin{proof}[Proof of Lemma \ref{lem:clustering_error_T_term}]
+\begin{proofof}{Lemma \ref{lem:clustering_error_T_term}}
 Due to symmetry it is enough to show that

### 2020-03-11 clustering_infinite_model.tex
small corrections
Updates from Overleaf

@@
 Note that this does not depend on the value of $k$. For notational convenience, we will write 
-\[ 
+\begin{equation}\label{eq:def_Py}
 	P(y_0) := \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
-\]
+\end{equation}
 with $u_1, u_2$ as above.
@@
 $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$, respectively. We then have that
+
 \begin{equation}\label{eq:delta_P}
@@
 change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$. 
-We will write $y_i(z_i)$ to stress the dependence between $y_i$ and $z_i$. 
-The following result completely characterizes $P(y_0,y_1,y_2)$.
+The following result will turn out to be
+all we need to compute the integral~\eqref{eq:delta_P}.
 
 \begin{lemma}\label{lem:triangle_prob_y_coordinates}
-\begin{align*}
-P(y_0(z_0),y_1(z_1),y_2(z_2)) = \begin{cases}
+Set $z_i = e^{-y_i/2}$, $i=0,1,2$. We have
+\begin{align*}
+P(y_0,y_1,y_2) = \begin{cases}
 	1, &\text{ if } z_0 \geq z_1+z_2, z_0 > z_1 > z_2, \\
@@
 \begin{lemma}\label{lem:ordered}
-Let $z_i = e^{-y_i/2}$, $i=0,1,2$. If $y_0<y_1<y_2$ (or equivalently $z_0 > z_1 > z_2$), then
-\begin{align*}
-P(y_0(z_0),y_1(z_1),y_2(z_2)) = \begin{cases}
+Write $z_i = e^{-y_i/2}$, $i=0,1,2$. If $y_0<y_1<y_2$ (or equivalently $z_0 > z_1 > z_2$), then
+\begin{align*}
+P(y_0,y_1,y_2) = \begin{cases}
 1, &\text{ if } z_0 \geq z_1+z_2,  \\
@@
 
-Although we've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
-taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$, it is still helpful
-to derive an alternative, more explicit expression. This is what we will do in the current section.
+We've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
+taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completene. This is what we will do in the current section.
 

### 2020-03-11 introduction.tex
small corrections
Updates from Overleaf

@@
 
-A general expression of the clustering function for KPKVB random graphs is given in~\cite[Equation (59)]{krioukov2010hyperbolic}. 
-The authors conjecture that as $k$ tends to infinity, the clustering function decays as $k^{-1}$. 
-They based this prediction on observations (Figure 8 in \cite{krioukov2010hyperbolic}) in experiments on the infrastructure of the Internet obtained in~\cite{claffy2009internet}.
-Despite these interesting observations and the attention the KPKVB model has generated since then, the behaviour of the clustering function in KPKVB random graphs had not been completely determined.
-In particular it has not been established whether it converges as $n\to\infty$ to some suitable limit function, nor how $c(k;G(n; \alpha,\nu))$ scales with $k$.
-Theorems~\ref{thm:mainkfixed},~\ref{thm:mainktoinfty} and Proposition~\ref{prop:asymp} below settle these questions.
+Krioukov et al.~state (\cite{krioukov2010hyperbolic}, last sentence on page 036106-10) that as $k$ tends to infinity, the clustering function decays as $k^{-1}$.
+This seems to be based on computations that were not included in the paper.
+Despite the attention the KPKVB model has generated since then, the behaviour of the clustering function in KPKVB random graphs has not been rigorously determined yet.
+In particular it has not been established whether it converges as $n\to\infty$ to some suitable limit function.
+Theorems~\ref{thm:mainkfixed} and~\ref{thm:mainktoinfty} below settle this question.
 Theorem~\ref{thm:mainkfixed} shows that for each fixed $k$, the value $c(k;G(n;\alpha,\nu))$ converges in probability to a constant $\gamma(k)$ that we again give explicitly as a closed form expression involving $\alpha,\nu$ and several classical special functions.
@@
 This depends on the parameter $\alpha$, and $\gamma(k)$ only scales with $k^{-1}$ when $\alpha > 3/4$, which corresponds to the exponent of the degree distribution exceeding $5/2$.
-So in particular our findings disprove the above-mentioned conjecture of Krioukov et al.~\cite{krioukov2010hyperbolic}.
+So in particular our findings contradict the above-mentioned claim of Krioukov et al.~\cite{krioukov2010hyperbolic}.
 
@@
 Proposition~\ref{prop:asymp} makes clear how $\gamma(k)$ behaves as $k$ grows.
-In particular, these results contradict the scaling conjectured in~\cite{krioukov2010hyperbolic} for 
+In particular, these results contradict the scaling claimed in~\cite{krioukov2010hyperbolic} for 
 $\alpha \leq \frac{3}{4}$, and confirms it only for $\alpha > \frac{3}{4}$.

### 2020-03-11 paper.tex

@@
 \author[1]{Nikolaos Fountoulakis\thanks{Research partially supported by the Alan Turing Institute, grant no. EP/N510129/1.}}
-\author[2]{Pim van der Hoorn\thanks{Research partially supported by ARO Grant W911NF-16-1-0391 and W911NF-17-1-0491}}
-\author[3]{Tobias M\"{u}ller\thanks{Research partially supported by NWO grants 639.032.529 and 612.001.409.}}
-\author[3]{Markus Schepers\thanks{Research partially supported by NWO grant 639.032.529.}}
+\author[2,3]{Pim van der Hoorn\thanks{Research partially supported by ARO Grant W911NF-16-1-0391 and W911NF-17-1-0491}}
+\author[4]{Tobias M\"{u}ller\thanks{Research partially supported by NWO grants 639.032.529 and 612.001.409.}}
+\author[4]{Markus Schepers\thanks{Research partially supported by NWO grant 639.032.529.}}
 
 \affil[1]{ School of Mathematics, University of Birmingham, United Kingdom.}
-\affil[2]{Department of Physics, Northeastern University, United States.}
-\affil[3]{Bernoulli Institute, University of Groningen, The Netherlands.}
+\affil[2]{Department of Mathematics and Computer Science, Eindhoven University of Technology, The Netherlands}
+\affil[3]{Department of Physics, Northeastern University, United States.}
+\affil[4]{Bernoulli Institute, University of Groningen, The Netherlands.}
 
@@
 if $\alpha=\frac{3}{4}$ and $\gamma(k) \sim c_{\alpha,\nu} \cdot k^{-1}$ when $\alpha > \frac{3}{4}$. 
-These results contradict a conjecture of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale 
+These results contradict a claim of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale 
 with $k^{-1}$ as we let $k$ grow. 
@@
 
+%=======
+%\TM{ Maybe a ``conclusion and further work'' section here,  before the references and appendix?}
+%
+%\section{Conclusion and further work}
+%
+%??
+%>>>>>>> Stashed changes
+
 \paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model 

### 2020-03-11 proofs_finite_k.tex

@@
 \begin{corollary}\label{cor:NGPok} 
-For every fixed $k\geq 0$ we have
+For every fixed $k\geq 1$ we have
 
@@
 \end{corollary}
-
-\noindent
-(The case $k=0$ follows from all the other cases together with the fact that the $\pmf(k)$ sum to one.)
 
@@
 \begin{corollary}\label{cor:GPoHdegseq}
-For every fixed $k$ we have
+For every fixed $k \geq 1$ we have
 
@@
 
-By Theorem~\ref{thm:mainkfixed} and~\eqref{eq:gugeldegseqaap} we have, for any fixed $K\geq 2$:
+By Theorem~\ref{thm:mainkfixed} and~\eqref{eq:gugeldegseqaap} we have, for any fixed $k\geq 2$:
 

### 2020-03-11 clustering_infinite_model.tex
Overleaf merge

@@
     	z^{k -2\alpha-1} e^{-z} \, dz\\
-    &= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!},
+    &= \frac{2\alpha \xi^{2\alpha}\Gamma^+(k - 2\alpha, \xi)}{k!}, \numberthis \label{eq:def_pk}
 \end{align*}
@@
 The proof is structured using headers, to aid the reader.
-
-%\begin{proof}[Proof of Proposition~\ref{prop:full_expression_delta_P}]\hfill
-
-%\paragraph{When $\bm{\alpha \notin \{3/4,1\}}$}
 
@@
 We've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
-taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completene. This is what we will do in the current section.
+taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completeness. This is what we will do in the current section.
 
@@
 
-\begin{proof}[Proof of Proposition~\ref{prop:asymp}]
+\begin{proofof}{Proposition~\ref{prop:asymp}}
 We split the proof over the different cases for $\alpha$.
@@
 \]
-\end{proof}
+\end{proofof}

### 2020-03-12 clustering_infinite_model.tex
Removed several LaTeX warnings

@@
-\section{Clustering and the degree of the typical point in $\Ginf$\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
+\section{Clustering and the degree of the typical point in \texorpdfstring{$\Ginf$}{G infinity}\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
 
@@
 	\CExp{C}{D=k, y=y_0} 
-	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
+	= \frac{1}{\binom{k}{2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
 	= \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
@@
 
-\subsubsection{Determining $P(y_0,y_1,y_2)$}
+\subsubsection{Determining \texorpdfstring{$P(y_0,y_1,y_2)$}{P(y0,y1,y2)}}
 
@@
 
-\subsubsection{Integrating over $y_1, y_2$}
+\subsubsection{Integrating over \texorpdfstring{$y_1, y_2$}{y1, y2}}
 
@@
 		\dd z_2 \dd z_1 \right. \\
-	&\hspace{10pt} \left. - \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} G(z_0,z_1,z_2) \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
+	&\hspace{10pt} \left. - \int_{\substack{{z_0>z_1>z_2>0,}\\{z_0 < z_1+z_2}}} G(z_0,z_1,z_2) \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
 		\dd z_2 \dd z_1 \right) \\
@@
 \begin{equation}\label{eq:def_Delta_P_computation_int_J_1}
-	J_{a,b,c}(z_0) := z_0^a \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2\dd z_1.
+	J_{a,b,c}(z_0) := z_0^a \int_{\substack{{z_0>z_1>z_2>0,}\\{z_0 < z_1+z_2}}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2\dd z_1.
 \end{equation}
@@
 		 \dd z_2 \dd z_1 \right. \\
-	&\hspace{10pt}\left. - \int_{{1>z_1>z_0,z_2>0}\atop{z_1 < z_0+z_2}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
+	&\hspace{10pt}\left. - \int_{\substack{{1>z_1>z_0,z_2>0}\\{z_1 < z_0+z_2}}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
 		z_2^{2\alpha-2} \dd z_2 \dd z_1 \right) \\
@@
 \[
-	J_{a,b,c}^\prime(z_0) := z_0^a \int_{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\atop{z_1 < z_0+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1
+	J_{a,b,c}^\prime(z_0) := z_0^a \int_{\substack{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\\{z_1 < z_0+z_2}}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1
 \]
@@
 
-\subsubsection{Computing $\gamma$ and $\gamma(k)$\label{ssec:exact_expressions_clustering_P}}
+\subsubsection{Computing \texorpdfstring{$\gamma$}{gamma} and \texorpdfstring{$\gamma(k)$}{gamma(k)}\label{ssec:exact_expressions_clustering_P}}
 
@@
 
-\subsubsection{Explicit expressions for $\gamma, \gamma(k)$ when $\alpha=1$.}\label{ssec:alphais1}
+\subsubsection{Explicit expressions for \texorpdfstring{$\gamma, \gamma(k)$}{gamma, gamma(k)} when \texorpdfstring{$\alpha=1$}{alpha equals 1}.}\label{ssec:alphais1}
 
 We've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
-taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completeness. This is what we will do in the current section.
+taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completeness. Since the rest of our 
+proofs do not the depend on it the reader could decide to skip this section on a first reading.
 

### 2020-03-12 hyperbolic_degrees.tex
Removed several LaTeX warnings

@@
-\section{Degrees when $k\to\infty$: proof of Theorem~\ref{thm:degrees_hyperbolic}\label{sec:degrees}}
+\section{Degrees when \texorpdfstring{$k\to\infty$}{k tends to infinity}: proof of Theorem~\ref{thm:degrees_hyperbolic}\label{sec:degrees}}
 
@@
 
-\subsection{Expected degrees in $\Gbox$ and $\GPo$}\label{ssec:expected_degrees_GPo}
+\subsection{Expected degrees in \texorpdfstring{$\Gbox$}{G box} and \texorpdfstring{$\GPo$}{G Po}}\label{ssec:expected_degrees_GPo}
 
@@
 
-\subsection{Joint degrees in $\Gbox$ and $\GPo$}\label{ssec:joint_degrees_GPo}
+\subsection{Joint degrees in \texorpdfstring{$\Gbox$}{G box} and \texorpdfstring{$\GPo$}{G Po}}\label{ssec:joint_degrees_GPo}
 

### 2020-03-12 introduction.tex
Removed several LaTeX warnings

@@
 	c(v) := \left\{\begin{array}{cl}
-		\displaystyle \frac{1}{{\text{deg}(v)\choose 2}} \sum_{u,w\sim v} 1_{\{uw \in E(G)\}}, 
+		\displaystyle \frac{1}{\binom{\text{deg}(v)}{2}} \sum_{u,w\sim v} 1_{\{uw \in E(G)\}}, 
 			& \text{ if $\text{deg}(v) \geq 2$, }\\
@@
 	c(k; G) := \begin{cases}
-		\displaystyle \frac{1}{N(k)} \sum_{v \in V(G), \atop \text{deg}(v)=k}  c(v),  &\mbox{ if } N(k) \ge 1,\\
+		\displaystyle \frac{1}{N(k)} \sum_{\substack{v \in V(G), \\ \text{deg}(v)=k}}  c(v),  &\mbox{ if } N(k) \ge 1,\\
 		0, &\mbox{else,}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
     \centering
@@
 %
-\begin{figure}[H]
+\begin{figure}[ht]
     \centering
@@
 
-\subsubsection{Scaling of $\gamma(k)$}
+\subsubsection{Scaling of \texorpdfstring{$\gamma(k)$}{gamma(k)}}
 
@@
 
-\subsubsection{The degree distribution and the range of $k_n$ in Theorem~\ref{thm:mainktoinfty}}
+\subsubsection{The degree distribution and the range of \texorpdfstring{$k_n$}{kn} in Theorem~\ref{thm:mainktoinfty}}
 
@@
 
-\subsubsection{Transition in scaling at $\alpha = 3/4$.}
+\subsubsection{Transition in scaling at \texorpdfstring{$\alpha = 3/4$}{alpha equals 3/4}.}
 

### 2020-03-12 preliminaries.tex
Removed several LaTeX warnings

@@
 
-\subsection{The infinite limit model $\Ginf$\label{ssec:infinite_model}}
+\subsection{The infinite limit model \texorpdfstring{$\Ginf$}{G infinity}\label{ssec:infinite_model}}
 
@@
 
-\subsection{The finite box model $\Gbox$\label{ssec:finite_model}}
+\subsection{The finite box model \texorpdfstring{$\Gbox$}{G box}\label{ssec:finite_model}}
 
@@
 
-\subsection{The Poissonized KPKVB model $\GPo$}
+\subsection{The Poissonized KPKVB model \texorpdfstring{$\GPo$}{G Po}}
 
@@
 
-\subsection{Coupling $\GPo$ and $\Gbox$\label{ssec:coupling_H_P}}
+\subsection{Coupling \texorpdfstring{$\GPo$}{G Po} and \texorpdfstring{$\Gbox$}{G box}\label{ssec:coupling_H_P}}
 
@@
 \begin{array}{c}
-\displaystyle	\Exp{\sum_{p_1, \dots, p_k \in \Pcal, \atop \text{distinct}} h(p_1, \dots, p_k, \Pcal)} \\
+\displaystyle	\Exp{\sum_{\substack{p_1, \dots, p_k \in \Pcal, \\ \text{distinct}}} h(p_1, \dots, p_k, \Pcal)} \\
 = \\

### 2020-03-12 proofs_finite_k.tex
Removed several LaTeX warnings

--- 2020-03-10 proofs_finite_k.tex
@@
 
-\subsection{Clustering function for fixed $k$, proving Theorem~\ref{thm:mainkfixed}}
+\subsection{Clustering function for fixed \texorpdfstring{$k$}{k}, proving Theorem~\ref{thm:mainkfixed}}
+%=======
+%\subsection{Clustering function, proving Theorem~\ref{thm:mainkfixed}}
+%In this subsection, we want to show that the clustering function of the KPKVB model $c(k; G(n;\alpha,\nu)) \xrightarrow{\Pee} \gamma(k)$ for any fixed $k$.
+The key idea is that for the poissonized KPKVB model the coupling with the box model is guaranteed to be exact (in the sense that it also preserves edges) for all vertices up to height $H = \frac{R}{4}$ (which is all we need to show the convergence of the clustering function for constant $k$).
+%>>>>>>> Stashed changes
 
@@
 & = & \displaystyle
-\left| \sum_{v\in V(G), \atop\text{deg}_G(v)=k} \frac{c_G(v)}{N_G(k)} - 
-\sum_{v\in V(H), \atop\text{deg}_{H}(v)=k} \frac{c_{H}(v)}{N_{H}(k)} \right| \\[8ex]
+\left| \sum_{\substack{v\in V(G), \\ \text{deg}_G(v)=k}} \frac{c_G(v)}{N_G(k)} - 
+\sum_{\substack{v\in V(H), \\ \text{deg}_{H}(v)=k}} \frac{c_{H}(v)}{N_{H}(k)} \right| \\[8ex]
 & = & \displaystyle 
-\left| \frac{1}{N_G(k)} \left( \sum_{v\in V(G)\setminus V(H), \atop\text{deg}_G(v)=k} c_G(v)
-+ \sum_{v\in V(G)\cap V(H), \atop{\text{deg}_G(v)=k, \atop\text{deg}_{H}(v)\neq k}} c_G(v) \right) \right. \\
+\left| \frac{1}{N_G(k)} \left( \sum_{\substack{v\in V(G)\setminus V(H), \\ \text{deg}_G(v)=k} } c_G(v)
++ \sum_{\substack{v\in V(G)\cap V(H), \\ \text{deg}_G(v)=k, \\ \text{deg}_{H}(v)\neq k}} c_G(v) \right) \right. \\
 & & \displaystyle
-- \frac{1}{N_{H}(k)} \left(\sum_{v\in V(H)\setminus V(G), \atop\text{deg}_{H}(v)=k} c_{H}(v)
-+ \sum_{v\in V(G)\cap V(H), \atop{\text{deg}_G(v)\neq k, \atop\text{deg}_{H}(v)=k}} c_{H}(v) \right) \\
+- \frac{1}{N_{H}(k)} \left(\sum_{\substack{ v\in V(H)\setminus V(G), \\ \text{deg}_{H}(v)=k} } c_{H}(v)
++ \sum_{\substack{v\in V(G)\cap V(H), \\ \text{deg}_G(v)\neq k, \\ \text{deg}_{H}(v)=k}} c_{H}(v) \right) \\
 & & \displaystyle  
 \left. + \left(\frac{1}{N_G(k)}-\frac{1}{N_{H}(k)} \right) \cdot 
-\left( \sum_{v \in V(G)\cap V(H), \atop\text{deg}_G(v)=\text{deg}_{H}(v)=k}
+\left( \sum_{\substack{v \in V(G)\cap V(H), \\ \text{deg}_G(v)=\text{deg}_{H}(v)=k}}
 c_G(v) \right) \right| \\[8ex]
@@
 
-$$ c(k; G_n)-c(k; \GPo) \xrightarrow[n\to\infty]{\Pee} 0, $$
-
-%\noindent
-%for every fixed $k\geq 2$.
-\end{corollary}
-
-Since $N_{G_n}(k) - 2|E(G_n)\Delta E(\GPo)| \leq N_{\GPo}(k) \leq N_{G_n}(k) + 2|E(G_n)\Delta E(\GPo)|$ for all $k\geq 1$,
-we can also conclude from~\eqref{eq:gugeldegseqaap} and Lemma~\ref{lem:NDGnGPo} that:
-
-\begin{corollary}\label{cor:NGPok} 
-For every fixed $k\geq 0$ we have
-
-$$ \frac{N_{\GPo}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$
+$$ c(k; G_n)-c(k; \GPo) \xrightarrow[n\to\infty]{\Pee} 0, \quad\text{ and }\quad
+\frac{N_{\GPo}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$
 
@@
 \noindent
-(The case $k=0$ follows from all the other cases together with the fact that the $\pmf(k)$ sum to one.)
+(For the second statement we use that $N_{G_n}(k) - 2|E(G_n)\Delta E(\GPo)| \leq N_{\GPo}(k) \leq N_{G_n}(k) + 2|E(G_n)\Delta E(\GPo)|$.)
 
@@
 
-Analogously to Corollaries~\ref{cor:pok} and~\ref{cor:NGPok} we obtain:
-
-\begin{corollary}\label{cor:GPoHdegseq}
-For every fixed $k$ we have
-
-$$\frac{N_{\GboxH}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$
-
-\end{corollary}
+Analogously to Corollary~\ref{cor:pok} we obtain:
 
@@
 
-$$c(k;\GPo) - c(k;\GboxH) \xrightarrow[n \rightarrow \infty]{\Pee} 0. $$
+$$c(k;\GPo) - c(k;\GboxH) \xrightarrow[n \rightarrow \infty]{\Pee} 0, \quad\text{ and }\quad  
+\frac{N_{\GboxH}(k)}{n} \xrightarrow[n\to\infty]{\Pee} \pmf(k). $$
 
@@
 
-In combination with Corollary~\ref{cor:GPoHdegseq} we can conclude that
+In combination with Corollary~\ref{cor:GPoGboxH} (second limit) we can conclude that
 

### 2020-03-12 proofs_infinite_k.tex
Removed several LaTeX warnings

@@
-\section{Clustering when $k\to\infty$ : overview of the proof strategy}
+\section{Clustering when \texorpdfstring{$k\to\infty$}{k tends to infinity} : overview of the proof strategy}
 
@@
 
-\subsection{Coupling of local clustering between $\GPo$ and $\Gbox$}
+\subsection{Coupling of local clustering between \texorpdfstring{$\GPo$}{G Po} and \texorpdfstring{$\Gbox$}{G box}}
 

### 2020-03-12 transition.tex
Removed several LaTeX warnings

@@
-\section{From $\Gbox$ to $\Ginf$ (Proving Proposition \ref{prop:convergence_average_clustering_P_n})}\label{sec:clustering_Pn_to_P}
+\section{From \texorpdfstring{$\Gbox$}{G box} to \texorpdfstring{$\Ginf$}{G infinity} (Proving Proposition \ref{prop:convergence_average_clustering_P_n})}\label{sec:clustering_Pn_to_P}
 
@@
 
-\subsection{Comparing triangles between $\Ginf$ and $\Gbox$}
+\subsection{Comparing triangles between \texorpdfstring{$\Ginf$}{G infinity} and \texorpdfstring{$\Gbox$}{G box}}
 

### 2020-05-04 clustering_infinite_model.tex
Corrections to Lemma D 4.1 by Markus

@@
 \begin{equation}\label{eq:general_integral_rho_y_k}
-	\int_0^\infty e^{\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
+	\int_0^\infty e^{-\beta y} \rho(y, k) \alpha e^{-\alpha y} \, dy
     \sim 2\alpha \xi^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
@@
 \]
-where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{y_0}$ with the above mentioned density.
+where $u_1,\dots, u_k$ are i.i.d.~points in $\BallPo{y_0}$ with the above mentioned density.
 Note that this does not depend on the value of $k$. For notational convenience, we will write 
@@
 
-\subsubsection{Explicit expressions for \texorpdfstring{$\gamma, \gamma(k)$}{gamma, gamma(k)} when \texorpdfstring{$\alpha=1$}{alpha equals 1}.}\label{ssec:alphais1}
-
-We've already established that $\gamma, \gamma(k)$ can be obtained at $\alpha=1$ by
-taking the $\alpha\to 1$ limit of the expression obtained for $\alpha=1$. Here we derive an alternative explicit expression for completeness. Since the rest of our 
-proofs do not the depend on it the reader could decide to skip this section on a first reading.
-
-Recall that $\Gamma^\ast(q,z) = \Gamma^+(q+1,z) + \Gamma^+(q,z)$. We will prove the following.
-
-\begin{proposition}\label{prop:gammaais1}
-If $\alpha=1$ then 
-\begin{align*} 
-\gamma &= \frac{575 - 12 \pi^2}{576} + \frac{\eta^4(7 + \pi^2)\Gamma^\ast(-4, \eta)}{4}\\
- 	&\hspace{10pt}- \frac{1}{2} \int_0^1 (1 - 4z + 3z^3)\log(1-z)(z + \eta)e^{-\eta/z} \dd z\\
- 	&\hspace{10pt}- \int_0^1 \Li_2(z)(z^3 + \eta z^2) e^{-\eta/z} \dd z,		
- \end{align*}
-and
-\begin{align*}
- \gamma(k) &= \frac{9 \eta^3}{2 k!} \Gamma^+(k-3,\eta)-\frac{\xi^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
- 	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
- 	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
- \end{align*}
-with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm 
-function.
-\end{proposition}
-
-Naturally, the proof proceeds by proving the analogue of Lemma~\ref{lem:Paneq1}:
-
-\begin{lemma}\label{lem:Pais1}
-If $\alpha = 1$, then
-	\begin{align*}
-	&P(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
-e^{-y}  + 
-\frac{1}{2}e^{-y}\Li_2(e^{-y})
-	\end{align*}
-	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dilogarithm function.
-\end{lemma}
-
-\begin{proof}
-We want to compute the limit $\lim_{\alpha \rightarrow 1} P_\alpha(y_0(z_0))$. For $\alpha \neq 1$, we label the terms as follows:
-%\begin{align*}
-%&P_\alpha(y_0(z_0)) \\
-%&= \frac{1}{\alpha-1}\left(s_1(\alpha,z_0)+s_2(\alpha,z_0)+s_3(\alpha,z_0)+s_4(\alpha,z_0) 
-%+s_5(\alpha,z_0)+s_6(\alpha,z_0)+s_7(\alpha,z_0)\right)
-%\end{align*}
-\begin{align*}
-&P_\alpha(y_0(z_0)) \\
-&= \frac{1}{\alpha-1}\left(s_1(\alpha,z_0)+s_2(\alpha,z_0)+\frac{1}{\alpha-1}(s_3(\alpha,z_0)+s_4(\alpha,z_0)) 
-+s_5(\alpha,z_0)+s_6(\alpha,z_0)+s_7(\alpha,z_0)\right)
-\end{align*}
-where
-\begin{align*}
-s_1(\alpha,z_0) &= -\frac{1}{8 \alpha}\\
-s_2(\alpha,z_0) &= (\alpha-1/2)z_0 \\
-s_3(\alpha,z_0) &= - \frac{(\alpha - 1/2)^2 z_0^2}{4}\\
-s_4(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha}\\
-s_5(\alpha,z_0) &= z_0^{-2 + 4 \alpha} \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2\alpha}\\
-s_6(\alpha,z_0) &= \frac{(1 - z_0)^{2 \alpha}}{8 \alpha} \\
-s_7(\alpha,z_0) &= - \frac{z_0^{4 \alpha - 2} B^-(1 - z_0; 2 \alpha, 3 - 4 \alpha)}{4}
-\end{align*}
-Now, we consider the functions $s_i(\alpha) = s_i(\alpha,z_0)$ as functions of $\alpha$ only and compute their Taylor 
-expansion at $\alpha=1$, for $i\in \{1,2,5,6,7\}$ up to linear and for $i\in \{3,4\}$ up to quadratic order, i.e. we 
-write $s_i(\alpha) = s_i(1)+s_i'(1)(\alpha-1)+o(\alpha-1)$ for $i\in \{1,2,5,6,7\}$ and 
-$s_i(\alpha)=s_i(1)+s_i'(1)(\alpha-1)+\frac{s_i''(1)}{2}(\alpha-1)^2+o((\alpha-1)^2)$ for $i\in \{3,4\}$. Using these expansions, we can rewrite
-%\begin{align*}
-%&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
-%s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
-%&\left.+\frac{1}{\alpha-1}(s_3(1)+s_4(1)+(s_3'(1)+s_4'(1))(\alpha-1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1)^2 +o((\alpha-1)^2)) \right)
-%\end{align*}
-\begin{align*}
-&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 
-s_i'(1)(\alpha-1)+o(\alpha-1) \right. \\
-&\left.+\frac{s_3(1)+s_4(1)}{\alpha-1} + s_3'(1)+s_4'(1)+\frac{1}{2}(s_3''(1)+s_4''(1))(\alpha-1) +o((\alpha-1)) \right)
-\end{align*}
-In order to continue, we compute:
-\begin{align*}
-s_1(\alpha) &=-\frac{1}{8}+\frac{1}{8}(\alpha-1)+o(\alpha-1) \\
-s_2(\alpha) &=\frac{1}{2}z_0 +z_0 (\alpha-1)+o(\alpha-1) \\
-%s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{4}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
-s_3(\alpha) &= -\frac{1}{16}z_0^2 -\frac{1}{4}z_0^2(\alpha-1)-\frac{1}{2}z_0^2(\alpha-1)^2+o( (\alpha-1)^2) \\
-%s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
-%&\qquad+\frac{z_0^2}{8}\left(4\left(\ln\frac{z_0}{2}\right)^2+\ln\frac{z_0}{2} - \frac{1}{4}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
-s_4(\alpha) &= \frac{1}{16}z_0^2 +\frac{z_0^2}{4}\left(\frac{1}{8}+\ln\frac{z_0}{2}\right)(\alpha-1)\\
-&\qquad+\frac{z_0^2}{8}\left(8\left(\ln\frac{z_0}{2}\right)^2+2\ln\frac{z_0}{2} - \frac{1}{2}\right)(\alpha-1)^2+o( (\alpha-1)^2)\\
-s_5(\alpha) &= \frac{z_0^2}{4} B^-(1/2;3,0) +o(\alpha-1) \\
-	&\hspace{10pt}+ z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0) +1/2\int_0^{\frac{1}{2}} \ln(t(1-t))t^2(1-t)^{-1} \dd t \right)  (\alpha-1)+o (\alpha-1)\\
-s_6(\alpha) &= \frac{(1-z_0)^2}{8}+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )(\alpha-1 + \smallO{a-1})\\
-%s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) - z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) \right. \\
-%&\qquad \left.+\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2}dt \right) (\alpha-1)+o(\alpha-1)
-s_7(\alpha) &= -\frac{z_0^2}{4}B^-(1-z_0;2,-1) +o(\alpha-1) \\
-	&\hspace{10pt}- z_0^2 \left(\ln(z_0)B^-(1-z_0;2,-1) 
-		+\int_0^{1-z_0} t(1-t)^{-2}\ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} \dd t \right) (\alpha-1).
-\end{align*}
-Based on this we see that
-\begin{align*}
-s_3(1)+s_4(1)=-\frac{1}{16}z_0^2+\frac{1}{16}z_0^2 =0
-\end{align*}
-and
-\begin{align*}
-&\sum_{i\in \{1,2,5,6,7\}} s_i(1) + s_3'(1)+s_4'(1) \\
-&= -\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\frac{z_0^2}{4}\ln(\frac{z_0}{2}) 
-+\frac{z_0^2}{4}B^-(1/2;3,0)+\frac{(1-z_0)^2}{8}-\frac{z_0^2}{4}B^-(1-z_0;2,-1) \\
-&=-\frac{1}{8}+\frac{1}{2}z_0-\frac{1}{4}z_0^2+\frac{z_0^2}{32}+\left(\frac{z_0^2}{4}\ln(z_0)-\frac{z_0^2}{4}\ln 2\right) 
-+\left(-\frac{5z_0^2}{32}+\frac{z_0^2}{4}\ln2\right) \\ 
-&\hspace{50pt}+\left(\frac{1}{8}-\frac{z_0}{4}+\frac{z_0^2}{8}\right)+\left(\frac{z_0^2}{4}-\frac{z_0}{4}-\frac{z_0^2}{4}\ln z_0\right) &=0,
-\end{align*}
-using that %$B^-(\frac{1}{2};3,0)=-\frac{5}{8}+\ln 2$ and $B^-(1-z_0;2,-1)=-1+z_0^{-1}+\ln z_0$.
-\begin{align*}
-B^-(\frac{1}{2};3,0)&=\int_0^\frac{1}{2}t^2(1-t)^-1dt=\int_\frac{1}{2}^1 (1-s)^2 s^{-1}ds\\
-&=\int_\frac{1}{2}^1 s^{-1}-2+sds = -2+\frac{1}{2}-\ln\frac{1}{2}+1-\frac{1}{8}=-\frac{5}{8}+\ln 2
-\end{align*}
-and
-\begin{align*}
-B^-(1-z_0;2,-1)&=\int_0^{1-z_0} t(1-t)^{-2}dt = \int_{z_0}^1 (1-s)s^{-2}ds \\
-&=\int_{z_0}^1 s^{-2}-s^{-1}ds = -1+z_0^{-1}+\ln z_0.
-\end{align*}
-
-Finally, it follows that as $\alpha \to 1$,
-\begin{align*}
-P(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)
-\end{align*}
-Therefore, the desired value of $\lim_{\alpha \rightarrow 1} P(y_0(z_0))$ is given by
-\begin{align*}
-&\sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1))\\
-	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{8}(4(\ln\frac{z_0}{2})^2+\ln\frac{z_0}{2} - \frac{1}{4}) 
-		+\frac{(1-z_0)^2}{4} (\ln(1-z_0)-1/2 )\\
-	&\hspace{10pt}+z_0^2\left(\left(\ln(z_0)+\frac{1}{4}\right) B^-(1/2;3,0)+ \frac{1}{2}\int_0^{\frac{1}{2}} 
-		\ln(t(1-t)) \, t^2(1-t)^{-1} \dd t \right) \\
-	&\hspace{10pt}- z_0^{2}\left(\ln(z_0)B^-(1-z_0;2,-1)+\int_0^{1-z_0}\ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} 
-		\dd t \right) \\
-	&=\frac{1}{8}+z_0-\frac{z_0^2}{4}+\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2
-		+\frac{z_0^2}{8}\ln\frac{z_0}{2} - \frac{z_0^2}{32} \\
-	&\hspace{10pt}-\frac{5}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2-\frac{5z_0^2}{32} +\frac{z_0^2 \ln2}{4}\\
-	&\hspace{10pt}+z_0^2/2\int_0^{\frac{1}{2}} \ln(t(1-t)) \, t^2(1-t)^{-1}\dd t \\
-	&\hspace{10pt}+\frac{(1-z_0)^2}{4}\ln(1-z_0) -\frac{1}{8}+\frac{z_0}{4}-\frac{z_0^2}{8}\\
-	&\hspace{10pt}+ z_0^2\ln(z_0)-z_0 \ln z_0-z_0^2(\ln z_0)^2
-		-z_0^2\int_0^{1-z_0} \ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2}  \dd t \\
-	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
-		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
-	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
-		+z_0^2/2\int_0^{\frac{1}{2}} \ln(t(1-t)) \, t^2(1-t)^{-1} \dd t \\
-	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2-z_0^2\int_0^{1-z_0} \ln\left(\frac{\sqrt{t}}{1-t}\right)t(1-t)^{-2} \dd t \\
-	&=\frac{5}{4}z_0-\frac{9}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
-		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
-	&\hspace{10pt}+\frac{3}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
-		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2)) \\
-	&\hspace{10pt}-z_0 \ln z_0-z_0^2(\ln z_0)^2+z_0(1 + \frac{1}{2}(2-z_0) \ln(z_0) 
-		+ \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) \\
-	&\hspace{10pt}+\frac{1}{2}z_0 \Li_2(z_0)) - z_0^2   -\frac{1}{2}  z_0^2\Li_2(1) \\
-	&=\frac{9}{4}z_0-\frac{25}{16}z_0^2 +\frac{z_0^2}{2}(\ln\frac{z_0}{2})^2+\frac{z_0^2}{8}\ln\frac{z_0}{2} 
-		+\frac{(1-z_0)^2}{4}\ln(1-z_0) \\
-	&\hspace{10pt}-\frac{1}{8}z_0^2\ln(z_0)+z_0^2\ln(z_0)\ln 2+\frac{z_0^2 \ln2}{4}
-		+z_0^2/2(11/8 -1/4 \ln 2 -3/2\ln(2)^2 \\
-	&\hspace{10pt}- \Li_2(1/2)-\Li_2(1)+\Li_2(z_0)) -\frac{1}{2}z_0^2(\ln z_0)^2 - \frac{1}{2} z_0(1-z_0) \ln(1-z_0)
-\end{align*}
-where we used that
-\begin{align*}
-	z_0^2/2\int_0^{\frac{1}{2}} \ln(t)t^2(1-t)^{-1}+\ln(1-t)t^2(1-t)^{-1} \dd t
-	&= 11/8 -1/4 \ln 2 -3/2\ln(2)^2 -  \Li_2(1/2),
-\end{align*}
-and
-\begin{align*}
-	&z_0^2\int_0^{1-z_0} 1/2\ln(t)t(1-t)^{-2}-t\ln(1-t)(1-t)^{-2} \dd t\\
-	&= -\frac{1}{z_0} (1 + \frac{1}{2}(2-z_0) \ln(z_0) + \frac{1}{2}z_0 \ln(z_0)^2 - \frac{1}{2} (1-z_0) \ln(1-z_0) +\frac{1}{2}z_0 \Li_2(z_0))+1   +\frac{1}{2}  \Li_2(1).
-\end{align*}
-By expanding the squares and collecting terms, the last expression can be simplified to
-\begin{align*}
-&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) + 
-z_0^2 \left(-7/8 - \frac{\ln(2)^2+2\Li_2(1/2) + 2\Li_2(1)}{4} \right) + 
-\frac{1}{2}z_0^2 \Li_2(z) \\
-=&\frac{9}{4} z_0 + \frac{1 - 4 z_0 + 3 z_0^2}{4}\ln(1 - z_0) - \frac{7+\pi^2}{8}
-z_0^2  + 
-\frac{1}{2}z_0^2 \Li_2(z)
-\end{align*}
-which finishes the computation.
-\end{proof}
-
-\begin{proofof}{Proposition~\ref{prop:gammaais1}}
-It suffices to find the value of $J$ and $I^{(k)}$ 
-at $\alpha = 1$. We can do this by computing the integrals with the expression for $P(y)$ that we found for $\alpha=1$, i.e.
-\begin{align*}
-	J &= 2\alpha\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) - \frac{7+\pi^2}{8}
-		z^2  + \frac{1}{2}z^2 \Li_2(z)\right) z^{2\alpha -1} \dd z \\
-	&=\frac{575-12\pi^2}{576}
-\end{align*}
-and 
-\begin{align*}
-	I^{(k)} &= \frac{2\alpha \xi^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
-		- \frac{7+\pi^2}{8}	z^2  + \frac{1}{2}z^2 \Li_2(z) \right)z^{2\alpha-k-1} e^{-\xi/z} \dd z \\
-	&= \frac{2 \eta^k}{k!}\int_0^1 \left(\frac{9}{4} z + \frac{1 - 4 z + 3 z^2}{4}\ln(1 - z) 
-		- \frac{7+\pi^2}{8} z^2  + \frac{1}{2}z^2 \Li_2(z) \right)z^{1-k} e^{-\eta/z} \dd z \\
-	&= \frac{9 \eta^k}{2 k!}\eta^{3-k}\Gamma^+(k-3,\eta)-\frac{\eta^k}{k!}\frac{7+\pi^2}{4}\eta^{4-k}\Gamma^+(k-4,\eta)\\
-	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}dz+\frac{\eta^k}{k!}\int_0^1 z^{3-k} 
-		\Li_2(z) e^{-\eta/z} \dd z \\
-	&=\frac{9 \eta^3}{2 k!}\Gamma^+(k-3,\eta)-\frac{\eta^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
-	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}dz+\frac{\eta^k}{k!}\int_0^1 z^{3-k} 
-		\Li_2(z) e^{-\eta/z} \dd z
-\end{align*}
-where $\eta = \frac{4\nu}{\pi}$ and and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function. 
-Plugging this into ~\eqref{eq:gammaint} and~\eqref{eq:gammakint} yields the expressions in the statement of the proposition.
-\end{proofof}
-
 \subsection{The proof of Proposition~\ref{prop:asymp}\label{ssec:asymptotics_local_clustering_P}}

### 2020-05-04 introduction.tex
Corrections to Lemma D 4.1 by Markus

@@
 For a sequence $(X_n)_n$ of random variables, we write $X_n \xrightarrow[n\to\infty]{\Pee} X$ to denote that $X_n$ converges in 
-probability to $X$, and we write $X_n \xrightarrow[n\to\infty]{L_1} X$ if $X_n$ converges to $X$ in the $L_1$ sense 
-(i.e.~if $\Ee |X_n-X| \to 0$.)
+probability to $X$. %, and we write $X_n \xrightarrow[n\to\infty]{L_1} X$ if $X_n$ converges to $X$ in the $L_1$ sense (i.e.~if $\Ee |X_n-X| \to 0$.)
 
@@
 
-$$ \frac{c(k_n;G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{L_1} 1. $$
+$$ \frac{c(k_n;G_n)}{\gamma(k_n)} \xrightarrow[n\to\infty]{\Pee} 1. $$
 
@@
 \noindent
-The conclusion of Theorem~\ref{thm:mainktoinfty} is slightly stronger than $c(k_n; G_n)/\gamma(k_n) 
-\xrightarrow[n\to\infty]{\Pee} 1$, which might alternatively be written as $c(k_n;G_n) = (1+o(1)) \gamma(k_n)$ a.a.s., using notation that is common in the random graphs community.
+The statement of Theorem~\ref{thm:mainktoinfty} is equivalent to $c(k_n;G_n) = (1+o(1)) \gamma(k_n)$ a.a.s., using notation that is common in the random graphs community.
+%$c(k_n; G_n)/\gamma(k_n)\xrightarrow[n\to\infty]{\Pee} 1$, which might alternatively be written as
 
@@
 
-\subsubsection{Uniform convergence.}
+%\subsubsection{Uniform convergence.}
 
-Our results for the local clustering function in fact imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ 
-where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. 
-To see this we first observe that for {\em fixed} $k$, the statement $c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k)$
-is equivalent to $c(k;G_n)/\gamma(k) \xrightarrow[n\to\infty]{L_1} 1$.
-Now let
-\[
-	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|}.
-\]
-Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainkfixed} and Theorem~\ref{thm:mainktoinfty}
-\[
-	\lim_{n \to \infty} \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|} 
-	= \lim_{n \to \infty}\Exp{\left|\frac{c(b_n; G_n)}{\gamma(b_n)} - 1\right|} = 0.
-\]
+%Our results for the local clustering function in fact imply uniform convergence of $c(k; G_n)$ for all $2 \le k \le a_n$ 
+%where $a_n \ll n^{\frac{1}{2\alpha + 1}}$. 
+%To see this we first observe that for {\em fixed} $k$, the statement $c(k;G_n) \xrightarrow[n\to\infty]{\Pee} \gamma(k)$
+%is equivalent to $c(k;G_n)/\gamma(k) \xrightarrow[n\to\infty]{L_1} 1$.
+%Now let
+%\[
+%	b_n = \arg \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|}.
+%\]
+%Then $b_n \le a_n \ll n^{\frac{1}{2\alpha + 1}}$ and therefore by Theorem~\ref{thm:mainkfixed} and Theorem~\ref{thm:mainktoinfty}
+%\[
+%	\lim_{n \to \infty} \max_{2 \le k \le a_n} \Exp{\left|\frac{c(k; G_n)}{\gamma(k)} - 1\right|} 
+%	= \lim_{n \to \infty}\Exp{\left|\frac{c(b_n; G_n)}{\gamma(b_n)} - 1\right|} = 0.
+%\]
 

### 2020-05-04 proofs_infinite_k.tex
Corrections to Lemma D 4.1 by Markus
corrected proof Theorem 1.3 and Lemma 6.1

@@
 \[
-	\Exp{\left|c(k_n;G_n) - c^\ast(k_n;G_n)\right|} = \smallO{s(k_n)}.
+\left|c^\ast(k_n; G_n) - c(k_n; G_n)\right| = \smallOp{s(k_n)}.
 \]
+%\[
+%	\Exp{\left|c(k_n;G_n) - c^\ast(k_n;G_n)\right|} = \smallO{s(k_n)}.
+%\]
 \end{lemma}
@@
 \begin{proofof}{Theorem~\ref{thm:mainktoinfty}}
-Note that the second of the theorem follows immediately from the first.
-
-To prove the first statement, we rewrite $c(k_n; G_n)$ as
+We first rewrite $c(k_n; G_n)$ as
 \begin{align*}
@@
     &\hspace{10pt}+ \left(c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right)
-    	+ \left(c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)\right)\\
-    &\hspace{10pt}+ \E c^\ast(k_n; \Gbox)-\gamma(k_n)
+    	+ \left(c^\ast(k_n; \Gbox)-\Exp{c^\ast(k_n; \Gbox)}\right)\\
+    &\hspace{10pt}+ \Exp{c^\ast(k_n; \Gbox)}-\gamma(k_n)
 \end{align*}
-Then, we take absolute values and apply the triangle inequality. By monotonicity of expectation, we can apply it to both sides and obtain
+Then, we take absolute values and apply the triangle inequality. 
 \begin{align*}
-    \Exp{\left|c(k_n;G_n)-\gamma(k_n)\right|} 
-    &\le \Exp{\left|c(k_n;G_n)-c^\ast(k_n;G_n)\right|}
-    	+\Exp{\left|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)\right|}\\
-    &\hspace{10pt}+ \Exp{\left|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right|} 
-    	+ \Exp{\left|c^\ast(k_n; \Gbox)-\E c^\ast(k_n; \Gbox)\right|}\\
+    \left|c(k_n;G_n)-\gamma(k_n)\right|
+    &\le \left|c(k_n;G_n)-c^\ast(k_n;G_n)\right|
+    	+\left|c^\ast(k_n;G_n)-c^\ast(k_n; \GPo)\right|\\
+    &\hspace{10pt}+ \left|c^\ast(k_n; \GPo)-c^\ast(k_n; \Gbox)\right|
+    	+ \left|c^\ast(k_n; \Gbox)-\Exp{c^\ast(k_n; \Gbox)}\right|\\
     &+ \left|\Exp{c^\ast(k_n; \Gbox)}-\gamma(k_n)\right|
 \end{align*}
-At this point, the lemmas and propositions presented above in this section can be applied in order to show that all summands are $\smallO{\gamma(k_n)}$: Lemma~\ref{lem:clustering_ast_H} for the transition to the modified clustering function in the first term, Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling between the Poissonized KPKVB and the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model.
+The first term is $\smallOp{s(k_n)}$ by Lemma~\ref{lem:clustering_ast_H}.
+For the other terms, the propositions presented above in this section can be applied in order to show that the expectation of each difference is $\smallO{s(k_n)}$: Proposition~\ref{prop:clustering_ast_H_Pois} for the Poissonization in the second term, Proposition~\ref{prop:couling_c_H_P} for the coupling between the Poissonized KPKVB and the finite box model in the third term, Proposition~\ref{prop:concentration_local_clustering_P_n} for the concentration in the fourth term and finally Proposition~\ref{prop:convergence_average_clustering_P_n} for the transition to the infinite limit model.
 
-All of this together yields that:
+In particular, this implies that all terms are $\smallOp{s(k_n)}$. We thus conclude that
 \begin{align*}
-    \Exp{\left|c(k_n;G_n)-\gamma(k_n)\right|} = \smallO{s(k_n)} = \smallO{\gamma(k_n)},
+    \left|c(k_n;G_n)-\gamma(k_n)\right| = \smallOp{s(k_n)} = \smallOp{\gamma(k_n)},
 \end{align*}

### 2020-12-11 clustering_infinite_model.tex
Edits by Tobias

@@
 the typical point. 
-For $p = (x,y) \in \eR\times[0,\infty)$ we define
+For $y \geq 0$ we define
 \begin{equation}
-	\rho(p,k) := \Prob{\Po(\mu(y)) = k},
+	\rho(y,k) := \Prob{\Po(\mu(y)) = k},
 \end{equation}
@@
 where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. 
-We will often write $\rho(y,k)$ instead of $\rho(p,k)$.
+%We will often write $\rho(y,k)$ instead of $\rho(p,k)$.
 
@@
 \end{equation}
+
+\noindent
+(In a bit more detail: we use that 
+$\Gamma(a,b) = (1+o_a(1))\cdot \Gamma(a)$ if $a$ tends to infinity and $b$ remains constant, and that 
+$\Gamma(a+1) = (1+o_a(1))\cdot \sqrt{2\pi a} \cdot (a/e)^{a}$ as $a$ tends to infinity by Stirling's approximation.
+For a proof of Stirling's approximation to the $\Gamma$ function, also for non-integer values of the argument, see for instance~\cite{DiaconisFreedman}.)
 
@@
 	I_1(y_0) &:= \int_{0<y_0<y_1<y_2} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)}  \dd y_2 \dd y_1 \\ 
-	I_2(y_0) &:= \int_{0<y_1<y_0,y_2} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)} \dd y_2 \dd y_1 \\ 
-\end{align*}
-
-We proceed with computing each of these two integrals, each of which is split in two parts. 
+	I_2(y_0) &:= \int_{0<y_1<\min(y_0,y_2)} P(y_0,y_1,y_2) \cdot (\alpha-1/2)^2 e^{-(\alpha-1/2)(y_1+y_2)} \dd y_2 \dd y_1 \\ 
+\end{align*}
+
+We proceed with computing these two integrals, each of which is split into two parts.
 The final expressions of those four integrals can be found 
@@
 \begin{align*}
-	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0,y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
+	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>\max(z_2,z_0), \atop z_0,z_2>0} P(y_0,y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
 		\dd z_2 \dd z_1 \\
-	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{1>z_1>z_0,z_2>0}  z_0 z_1^{2\alpha-3} z_2^{2\alpha-2} 
+	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{1>z_1>\max(z_0,z_2)>0, \atop z_0,z_2>0}  z_0 z_1^{2\alpha-3} z_2^{2\alpha-2} 
 		 \dd z_2 \dd z_1 \right. \\
-	&\hspace{10pt}\left. - \int_{\substack{{1>z_1>z_0,z_2>0}\\{z_1 < z_0+z_2}}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
+	&\hspace{10pt}\left. - \int_{{1>z_1>\max(z_0,z_2),}\atop{z_0,z_2>0,\atop{z_1 < z_0+z_2}}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
 		z_2^{2\alpha-2} \dd z_2 \dd z_1 \right) \\
@@
 \begin{align*}
-	I_{21}(y_0) &= z_0 \int_{1>z_1>\max(z_2,z_0);z_0,z_2>0} z_1^{2\alpha-3} z_2^{2\alpha-2}  \dd z_2 \dd z_1   
+	I_{21}(y_0) &= z_0 \int_{1>z_1>\max(z_2,z_0),\atop z_0,z_2>0} z_1^{2\alpha-3} z_2^{2\alpha-2}  \dd z_2 \dd z_1   
 		= z_0 \int_{z_0}^1 \int_{0}^{z_1} z_1^{2\alpha-3} z_2^{2\alpha-2}  \dd z_2 \dd z_1\\
@@
 \[
-	J_{a,b,c}^\prime(z_0) := z_0^a \int_{\substack{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\\{z_1 < z_0+z_2}}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1
+	J_{a,b,c}^\prime(z_0) := z_0^a \int_{ {1>z_1>\max(z_0,z_2),} \atop{{z_0,z_2>0,}\atop{z_1 < z_0+z_2}} } z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} \dd z_2 \dd z_1
 \]

### 2020-12-11 paper.tex
Removed several LaTeX warnings
Corrections to Lemma D 4.1 by Markus
corrected proof Theorem 1.3 and Lemma 6.1
Edits by Tobias

@@
 \usepackage{appendix}
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks = true,
-    urlcolor = {magenta},
-    citecolor = {green},
-    linkcolor = {blue}
-}
+
 \usepackage{graphicx}
@@
     stringstyle=\color{red} % string color
+}
+
+\usepackage[nottoc,numbib]{tocbibind}
+\settocbibname{References}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks = true,
+    urlcolor = {magenta},
+    citecolor = {green},
+    linkcolor = {blue}
 }
@@
 
-\affil[1]{ School of Mathematics, University of Birmingham, United Kingdom.}
+\affil[1]{School of Mathematics, University of Birmingham, United Kingdom.}
 \affil[2]{Department of Mathematics and Computer Science, Eindhoven University of Technology, The Netherlands}
@@
 
+\pgfplotsset{compat=1.14}
 \begin{document}
@@
 In this paper we consider the clustering coefficient, and clustering function in a random graph model proposed by Krioukov et al.~in 2010. 
-In this model, nodes are chosen randomly inside a disk in the hyperbolic plane and two nodes are connected if they are at most a certain 
+In this model, nodes are chosen randomly inside a disk in the hyperbolic plane and two nodes are connected if they are at most at a certain 
 hyperbolic distance from each other. It has been previously shown that this model has various properties associated with complex networks, 
@@
 
-%=======
-%\TM{ Maybe a ``conclusion and further work'' section here,  before the references and appendix?}
-%
-%\section{Conclusion and further work}
-%
-%??
-%>>>>>>> Stashed changes
-
 \paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model 
-and his helpful insights during discussions of the topic.
+and his helpful insights during discussions of the topic. We are grateful to Remco van der Hofstad for pointing out a mistake in an earlier version of the proof of Theorem~\ref{thm:mainktoinfty}.
 

### 2020-12-11 preliminaries.tex
Edits by Tobias

@@
 
-Imagine that we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ in the hyperbolic plane $\Haa$ chosen according to the $(\alpha, R)$-quasi uniform distribution.
+Imagine that we have an infinite supply of i.i.d.~points $u_1, u_2, \dots$ in the hyperbolic plane $\Haa$ chosen according to a distribution we'll define shortly, in~\eqref{eq:def_quasi_uniform_density} below.
 In the standard KPKVB random graph $G(n;\alpha,\nu)$ we take $u_1,\dots, u_n$ as our vertex set and add edges between points at hyperbolic distance at most $R = 2\log(n/\nu)$.
@@
 The following lemma provides useful bounds on the function $\Phi(r,r^\prime)$.
-Note that in~\cite{fountoulakis2018law} the function $\Phi$ is written in terms of where $r := R - y, r^\prime := R - y^\prime$.
+Note that in~\cite{fountoulakis2018law} the function $\Phi$ is written in terms of $r := R - y, r^\prime := R - y^\prime$.
 
@@
 \end{equation}
-where we set $y_{k,C}^- = 0$ if $k - C \sqrt{k \log(k)} < \xi$ and likewise if $k + C \sqrt{k \log(k)} < \xi$ we set $y_{k,C}^+=0$, but  note that as we consider $k\rightarrow\infty$, we can assume that this case does not occur.
+where we set $y_{k,C}^- = 0$ if $k - C \sqrt{k \log(k)} < \xi$ (recall that we define $\xi := 4\alpha\nu/\pi(2\alpha-1)$ throughout the paper) 
+and likewise if $k + C \sqrt{k \log(k)} < \xi$ 
+we set $y_{k,C}^+=0$, but  note that as we consider $k\rightarrow\infty$, we can assume that this case does not occur.
 For convenience we write $\Kcal_C(k_n) := [y_{k_n,C}^-, y_{k_n,C}^+]$.
@@
 
-The key implication of Proposition~\ref{prop:concentration_height_general} is that if the function $h(y)$ does not increase too fast, then we can restrict integration to the interval $\Kcal_C(y)$.
+The key implication of Proposition~\ref{prop:concentration_height_general} is that if the function $h(y)$ does not increase too fast, then we can restrict integration to the interval $\Kcal_C(k_n)$.
 The full details associated with these concentration of heights and the proof of Proposition~\ref{prop:concentration_height_general} can be found in the Section~\ref{sec:concentration_argument} of the Appendix.

### 2020-12-11 clustering_infinite_model.tex
Processed referee comments

@@
 
-    \draw node[fill,black!60!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
-    \path (p2)+(0.25,-0.2) node {\color{black!60!green}$p_2$};
+    \draw node[fill,black!20!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
+    \path (p2)+(0.25,-0.2) node {\color{black!20!green}$p_2$};
 
@@
 	\pgfmathsetmacro{\rightbounduuuvvv}{\uuu+exp((\vvv)/2)}
-	\draw[domain=\rightbounduuuvvv:\r,smooth,variable=\x,black!60!green,line width=1pt] plot (\x, {2*ln(\x-\uuu)-\vvv});
+	\draw[domain=\rightbounduuuvvv:\r,smooth,variable=\x,black!20!green,line width=1pt] plot (\x, {2*ln(\x-\uuu)-\vvv});
     %Left boundary
     \pgfmathsetmacro{\leftbounduuuvvv}{\uuu-exp((\vvv)/2)}
-    \draw[domain=\leftbounduuuvvv:-\r,smooth,variable=\x,black!60!green,line width=1pt] plot (\x, {2*ln(\uuu-\x)-\vvv});
+    \draw[domain=\leftbounduuuvvv:-\r,smooth,variable=\x,black!20!green,line width=1pt] plot (\x, {2*ln(\uuu-\x)-\vvv});
 
@@
 
-    \draw node[fill,black!60!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
-    \path (p2)+(-0.2,0.2) node {\color{black!60!green}$p_2$};
+    \draw node[fill,black!20!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
+    \path (p2)+(-0.2,0.2) node {\color{black!20!green}$p_2$};
 

### 2020-12-11 hyperbolic_degrees.tex
Processed referee comments

@@
 Recall that when $y^\prime \ge R - y$ then $p^\prime \in \BallHyp{y}$ while for $y^\prime < R - y$ this is true when~\eqref{eq:def_Omega_hyperbolic} holds.
-We does split the integral for $\mu_{Po,n}(y)$ accordingly, into two integrals $I_1$ and $I_2$,
+We split the integral for $\mu_{Po,n}(y)$ accordingly, into two integrals $I_1$ and $I_2$,
 \begin{align*}
@@
 This implies the result because the last integral equals $(1+o(1))2\alpha \xi^{2\alpha} k_n^{-(2\alpha+1)} = (1+o(1))\pmf(k_n)$.
+Where the last asymptotic equality follows from~\eqref{eq:degree_distribution_P_asymptotics}.
 
@@
 where $|x|_n = \min\{|x|, \pi e^{R/2} - |x|\}$ denotes the norm on the finite box $\Rcal$ where the left and right boundaries are identified.
-Then for any two points $p,p^\prime \in \mathcal{E}_\varepsilon(k_n)$ the expect number of joint neighbours is $\smallO{k_n}$.
+Then for any two points $p,p^\prime \in \mathcal{E}_\varepsilon(k_n)$ the expected number of joint neighbours is $\smallO{k_n}$.
 
@@
 
-We now proof the result for the factorial moments.
+We now prove the result for the factorial moments.
 
@@
 	&\le \bigO{1} \sum_{t = 1}^{N-n} \frac{\Exp{Z(n,t)}}{t}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
-	&= \bigO{1} \sum_{t = 1}^{N-n} \frac{(N-m)(k_n + t)}{N}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
+	&= \bigO{1} \sum_{t = 1}^{N-n} \frac{(N-n)(k_n + t)}{N}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
 	&= \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n} \frac{k_n}{t}
@@
 
-If $k_n=(1+o(1))c n^{\frac{1}{2\alpha+1}}$, then by Lemma~\ref{lem:expnnkn},
+If $k_n=(1+o(1))c n^{\frac{1}{2\alpha+1}}$, for some positive constant $c > 0$. then by Lemma~\ref{lem:expnnkn},
 \begin{align*}

### 2020-12-11 paper.tex
Processed referee comments

@@
 
-\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model 
-and his helpful insights during discussions of the topic. We are grateful to Remco van der Hofstad for pointing out a mistake in an earlier version of the proof of Theorem~\ref{thm:mainktoinfty}.
+\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model and his helpful insights during discussions of the topic.
+We thank Remco van der Hofstad for pointing out a mistake in an earlier version of the proof of Theorem~\ref{thm:mainktoinfty}.
+We also thank an anonymous referee for his/her suggestions and comments on improving the manuscript.
 

### 2020-12-16 clustering_infinite_model.tex
Edits Nikolaos

@@
-\section{Clustering and the degree of the typical point in \texorpdfstring{$\Ginf$}{G infinity}\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
+\section{Clustering and the degree of a typical point in \texorpdfstring{$\Ginf$}{G infinity}\label{sec:Ginf}\label{sec:asymptotics_average_clustering_ast_P}}
 

### 2020-12-16 hyperbolic_degrees.tex
Edits Nikolaos

@@
 From Lemma~\ref{lem:factmoment}, it then follows that $\Exp{{N_{Po}(k_n) \choose r}} =(1+o(1))\frac{(\Exp{ N_{Po}(k_n)})^r}{r!}\rightarrow \frac{\zeta^r}{r!}$.
-Thus, it follows from \cite[Theorem 8.3.1]{alon2016probabilistic} that $N_{Po}(k_n) \xrightarrow{d} Po(\zeta)$ for the Poissonized version.
+Thus, it follows from \cite[Theorem 8.3.1]{alon2016probabilistic} that $N_{Po}(k_n) \xrightarrow{d} \mathrm{Po}(\zeta)$ for the Poissonized version.
 
 Finally, since $k_n = \bigO{n^{\frac{1}{2\alpha+1}}}$, by Lemma~\ref{lem:diff_Nk_hyperbolic_binomial_poisson}, $\Exp{| N_n(k_n) - N_{Po}(k_n)|} = o(\Exp{N_{Po}(k_n)}) = o(\zeta)$, from which it follows that $\Prob{|N_n(k_n)-N_{Po}(k_n)|\geq 1} \leq \Exp{ |N_n(k_n)-N_{Po}(k_n)|} = o(\zeta)$.
-Hence, it also holds in the original KPKVB model that $N_n(k_n) \xrightarrow{d} Po(\zeta)$.
+Hence, it also holds in the original KPKVB model that $N_n(k_n) \xrightarrow{d} \mathrm{Po}(\zeta)$.
 

### 2020-12-16 proofs_finite_k.tex
Edits by Tobias
Edits Nikolaos

@@
 We will repeatedly rely on the following observation.
+When we are simultaneously considering two graphs $G,H$
+we will use the notations $N_G(k), N_H(k)$ to 
+denote the number of vertices of degree $k$ in $G$, respectively $H$.
 
@@
 
-In the remainder of this section, we'll denote by $\GboxH$ the subgraph of $\Gbox$ induced by all 
+In the remainder of this section, we will denote by $\GboxH$ the subgraph of $\Gbox$ induced by all 
 vertices $(x,y) \in \Vbox = \Pcal \cap \Rcal$ of height at most $R/4$.
@@
 the last equality holding provided $\eps$ was chosen sufficiently small (using that $\alpha > 1/2$).
-We conclude that, a.a.s., there are no vertices of height $\geq (1-\eps) R$.
+We conclude that, a.a.s., there are no vertices of height at least 
+$(1-\eps) R$.
 
@@
 
-Next, we turn attention to $X(X-1) = \sum_{u\neq v \in N_{\GboxH}(k)} c(v)c(u)$.
+Next, we turn attention our to $X(X-1) = \sum_{u\neq v \in N_{\GboxH}(k)} c(v)c(u)$.
 Another application of Campbell-Mecke shows that
